### 2021-10-03 Supplemental-Material-B-Annotated-Analysis.Rmd
Updates from Overleaf

---
title: "Supplemental Information B: Full Annotated Analysis and Reproducible Code"
subtitle: "Suppplemental Material for 'Psychological Needs During Intergroup Contact [working title]'"
author:
- Jannis Kreienkamp^1,2^
- Maximilian Agostini^1,2^
- Laura Bringmann^1,2^
- Peter de Jonge^1,2^
- Kai Epstude^1,2^
- ^1^University of Groningen
- ^2^Author order to be discussed currently alphabetic by last name
- "Author Information:"
- "Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: <a href='mailto:j.kreienkamp@rug.nl'>j.kreienkamp@rug.nl</a>"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io" target="_blank">OSF link goes here</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://janniscodes.github.io/intergroup-contact-needs/" target="_blank">janniscodes.github.io/intergroup-contact-needs/</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: apa.csl
---

<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
.table {
  margin-left:auto; 
  margin-right:auto;
}
</style>

```{r setup, include=FALSE}
# R Studio Clean-Up
  cat("\014") # clear console
  #rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
  gc() # garbage collector

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra",
         "sessioninfo", "tibble", "pander", "devtools",
         "data.table", "dplyr", "tidyr", "Hmisc", "kableExtra", 
         "stringr", "stringi", "reshape2", "lubridate")
invisible(lapply(lib, library, character.only = TRUE))  
rm(lib)

# Load Custom Packages  
  source("./scripts/functions/fun.panel.R")
  source("./scripts/functions/themes.R")
  source("./scripts/functions/binaryCor.R")

# Markdown Options
  knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
  knitr::opts_knit$get("root.dir") # check working directory
  options(scipen = 999, digits = 4, width = 400) #removes scientific quotation
  #knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
  knitr::knit_hooks$set(
   error = function(x, options) {
     paste('\n\n<div class="alert alert-danger">',
           gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
           '</div>', sep = '\n')
   },
   warning = function(x, options) {
     paste('\n\n<div class="alert alert-warning">',
           gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
           '</div>', sep = '\n')
   },
   message = function(x, options) {
     paste('\n\n<div class="alert alert-info">',
           gsub('##', '\n', x),
           '</div>', sep = '\n')
   }
  )
  htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Global Chunk Options
  knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figures/',
                        echo=TRUE, warning=FALSE, message=FALSE)
```

<br/>

Note. Boxplots display the interquartile range (IQR, center box), and the whiskers extend 1.5*IQR from the lower and upper hinge. The white point indicates the mean and the white center line indicates the median.

<br/>

# **Data Preparation**

## Data Import

## Data Cleaning

## Data Exclusions

# **Software Information**  
The full session information with all relevant system information and all loaded and installed packages is available in the collapsible section below.

<details>
  <summary>System Info</summary>

  \renewcommand{\arraystretch}{0.8} <!-- decrease line spacing for the table -->
```{r Reproducibility-SessionInfo-R-environment, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center", out.width='100%', results='asis'}
  df_session_platform <- devtools::session_info()$platform %>% 
    unlist(.) %>% 
    as.data.frame(.) %>% 
    rownames_to_column(.)

  colnames(df_session_platform) <- c("Setting", "Value")

  kbl(
    df_session_platform, 
    booktabs = T, 
    align = "l",
    caption = "R environment session info for reproducibility of results" # complete caption for main document
  ) %>% 
    kable_classic(full_width = F, 
                  lightable_options = "hover", 
                  html_font = "Cambria") 
```
  \renewcommand{\arraystretch}{1} <!-- reset row height/line spacing -->
 </details>
 <br>
 <details>
  <summary>Package Info</summary>

\renewcommand{\arraystretch}{0.6} <!-- decrease line spacing for the table -->
```{r Reproducibility-SessionInfo-R-packages, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center", out.width='100%', results='asis'}
df_session_packages <- devtools::session_info()$packages %>% 
  as.data.frame(.) %>% 
  filter(attached == TRUE) %>% 
  dplyr::select(loadedversion, date, source) %>% 
  rownames_to_column

colnames(df_session_packages) <- c("Package", "Loaded version", "Date", "Source")

kbl(
  df_session_packages, 
  booktabs = T, 
  align = "l",
  caption = "Package info for reproducibility of results" # complete caption for main document
) %>% 
  kable_classic(full_width = F, 
                  lightable_options = "hover", 
                  html_font = "Cambria") 
```
\renewcommand{\arraystretch}{1} <!-- reset row height/line spacing -->
</details>
<br>
<details>
  <summary>Full Session Info (including loaded but unattached packages --- for troubleshooting only)</summary>
    `r pander(sessionInfo(), compact = FALSE)`
</details>

--------------------------------------------------------------------

</br>

# **References**

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>

### 2021-10-03 TitlePage.tex
Updates from Overleaf

% define document type (i.e., template. Here: A4 APA manuscript with 12pt font)
\documentclass[man, 12pt, a4paper, donotrepeattitle]{apa7}

% change margins (e.g., for margin comments):
%\usepackage{geometry}
% \geometry{
% a4paper,
% marginparwidth=30mm,
% right=50mm,
%}

% add packages
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[style=apa, sortcites=true, sorting=nyt, backend=biber, natbib=true, uniquename=false, uniquelist=false, useprefix=true]{biblatex}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{setspace,caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{fourier}
\usepackage{stackengine}
\usepackage{scalerel}
\usepackage{fontawesome}
\usepackage[normalem]{ulem}
% \usepackage{longtable}
\usepackage{amsmath}
\usepackage{afterpage}
\usepackage{float}
\usepackage{array}
\usepackage{censor}

% formatting links in the PDF file
\hypersetup{
pdfpagemode={UseOutlines},
bookmarksopen=true,
bookmarksopenlevel=0,
hypertexnames=false,
colorlinks   = true, %Colours links instead of ugly boxes
urlcolor     = blue, %Colour for external hyperlinks
linkcolor    = blue, %Colour of internal links
citecolor   = cyan, %Colour of citations
pdfstartview={FitV},
unicode,
breaklinks=true,
}

% language settings
\DeclareLanguageMapping{american}{american-apa}

% add reference library file
\addbibresource{references.bib}

% add reference library file
\addbibresource{references.bib}

% Title and header
\title{The Migration Experience: A Conceptual Framework and Systematic Review of Psychological Acculturation}
\shorttitle{Acculturation Experience Framework}

% Authors
\author[*,1]{Jannis Kreienkamp}
\author[1]{Laura F. Bringmann}
\author[1]{Raili F. Engler}
\author[1]{Peter de Jonge}
\author[1]{Kai Epstude}
\affiliation{\hfill}
\affil[1]{University of Groningen, Department of Psychology}

\authornote{
   \addORCIDlink{* Jannis Kreienkamp}{0000-0002-1831-5604}\\
   \addORCIDlink{Laura F. Bringmann}{0000-0002-8091-9935}\\
   \addORCIDlink{Peter de Jonge}{0000-0002-0866-6929}\\
   \addORCIDlink{Kai Epstude}{0000-0001-9817-3847}

We have no known conflict of interest to declare. The authors received no specific funding for this work. Source data and  software is available at \url{https://github.com/JannisCodes/acculturation-review} \citep{Kreienkamp2021b}. Protocols, materials, analysis data, and code are available at \url{https://doi.org/10.34894/U988DU} \citep{Kreienkamp2021a}.

Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: j.kreienkamp@rug.nl}

\leftheader{Kreienkamp}

\setlength\parindent{1.27cm}

% Start of the main document:
\begin{document}

% add title information (incl. title page and abstract)
\maketitle

\printbibliography

\end{document}

### 2021-10-03 Supplemental-Material-B-Annotated-Analysis.Rmd
Updates from Overleaf

@@
 - Kai Epstude^1,2^
-- ^1^University of Groningen
+- ^1^University of Groningen, Department of Psychology
 - ^2^Author order to be discussed currently alphabetic by last name

### 2021-10-03 manuscript.tex
main renamed to match Overleaf

% define document type (i.e., template. Here: A4 APA manuscript with 12pt font)
\documentclass[man, 12pt, a4paper]{apa7}

% change margins (e.g., for margin comments):
%\usepackage{geometry}
% \geometry{
% a4paper,
% marginparwidth=30mm,
% right=50mm,
%}

% add packages
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[style=apa, sortcites=true, sorting=nyt, backend=biber, natbib=true, uniquename=false, uniquelist=false, useprefix=true]{biblatex}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{setspace,caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{fourier}
\usepackage{stackengine}
\usepackage{scalerel}
\usepackage{fontawesome}
\usepackage[normalem]{ulem}
% \usepackage{longtable}
\usepackage{amsmath}
\usepackage{afterpage}
\usepackage{float}
\usepackage{array}
\usepackage{censor}

% add definition sections
\newtheorem{definition}{Definition}

% Select what to do with to-do notes: 
% \usepackage[disable]{todonotes} % notes not showed
% \usepackage[draft]{todonotes}   % notes showed

% make warning with red triangle
\newcommand\Warning[1][2ex]{%
  \renewcommand\stacktype{L}%
  \scaleto{\stackon[1.3pt]{\color{red}$\triangle$}{\tiny\bfseries !}}{#1}}%

% make question with red triangle
\newcommand\Question[1][2ex]{%
  \renewcommand\stacktype{L}%
  \scaleto{\stackon[1.3pt]{\color{red}$\triangle$}{\tiny\bfseries ?}}{#1}}%

% formatting links in the PDF file
\hypersetup{
pdfpagemode={UseOutlines},
bookmarksopen=true,
bookmarksopenlevel=0,
hypertexnames=false,
colorlinks   = true, %Colours links instead of ugly boxes
urlcolor     = blue, %Colour for external hyperlinks
linkcolor    = blue, %Colour of internal links
citecolor   = cyan, %Colour of citations
pdfstartview={FitV},
unicode,
breaklinks=true,
}

% language settings
\DeclareLanguageMapping{american}{american-apa}

% add reference library file
\addbibresource{references.bib}

% Title and header
\title{Psychological Needs During Intergroup Contact}
\shorttitle{Needs in Intergroup Contact}

% Authors
\author[*,1,2]{Jannis Kreienkamp}
\author[1,2]{Maximilian Agostini}
\author[1,2]{Laura F. Bringmann}
\author[1,2]{Peter de Jonge}
\author[1,2]{Kai Epstude}
\affiliation{\hfill}

\affil[1]{University of Groningen, Department of Psychology}
\affil[2]{Author order to be discussed currently alphabetic by last name.}

\authornote{
   \addORCIDlink{* Jannis Kreienkamp}{0000-0002-1831-5604}\\
   \addORCIDlink{Maximilian Agostini}{0000-0001-6435-7621}\\
   \addORCIDlink{Laura F. Bringmann}{0000-0002-8091-9935}\\
   \addORCIDlink{Peter de Jonge}{0000-0002-0866-6929}\\
   \addORCIDlink{Kai Epstude}{0000-0001-9817-3847}

We have no known conflict of interest to declare. The authors received no specific funding for this work. Source data and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}. Protocols, materials, analysis data, and code are available at \url{osf.io}.

Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).  E-mail: j.kreienkamp@rug.nl}

\leftheader{Kreienkamp}

% Abstract
\abstract{
Abstract goes here.

\noindent\textbf{Public significance statement}: Significance Statement goes here.
}

\keywords{Intergroup Contact, Psychological Needs, Outgroup Attitudes, Interaction Quality, Extensive Longitudinal Data}

% set indentation size
\setlength\parindent{1.27cm}

% Start of the main document:
\begin{document}

% add title information (incl. title page and abstract)
\maketitle

% **CHEAT SHEET / LEGEND**
%
% Comments:
% '%' starts a comment in LaTeX (not printed)
% '\todo[inline]{} makes orange boxes in PDF
% '\marginpar{}' notes in margins
% '\footnote{}' footnote
% '\Warning' important note indicator in PDF (triangle with exclamation mark)
% '\Question' question note indicator in PDF (triangle with question mark)
%
% Citation (with Natbib citation style):
% '\citep[e.g.][p. 15]{CitationKey}' citation in parentheses "(e.g., Berry, 2003, p. 15)"
% '\citet{CitationKey}' citation in text "Berry (2003)"
% '\citealt' and '\citealp' alternate citation without parentheses
% '\citeauthor' and '\citeyear' only year or author
% 
% Headings:
% '\part{}' and '\chapter{}' only relevant for multi-part or multi-chapter documents
% '\section{}' heading level 1
% '\subsection{}' heading level 2
% '\subsubsection{}' heading level 3
% '\paragraph{}' heading level 4
% '\subparagraph{}' heading level 5
%
% formatting:
% '\textbf{}' text bold font
% '\textit{}' text italic font
% '\underline{}' text underline
% '\sout{}' text strike out
% '\textsc{}' text small caps
% '\vspace{1em}' add vertical space
% '\hspace{1em}' add horizontal space
% '\\' new line (i.e., line break)
% '\pagebreak' start new page (i.e., page break)
% '\noindent' do not indent current line (e.g., current paragraph)
% 'begin{center}...end{center}' center text or object
%
% Math mode:
% '$\alpha = .8$' mathematical equation inline
% '$$\hat{y} = b_0 + b_1x$$' mathematical equation in its own line
% '\begin{equation}...\end{equation}' multi-line equation
% '\approx' approximate symbol
% '\neq' not equal
% '\bar' mean bar over letter
% '\pm' plus minus sign 
% '^{}' superscript
% '_{}' subscript
% '\fraq{numerator}{denominator}' fraction
% '\sqrt[n]{}' square root
% '\sum_{k=1}^n' sum for 1 through n
%
% Insert things from elsewhere:
% '\input{filename}' inputs the raw (tex) file as a command (e.g., tables and R-Markdown imports)
% '\include{filename}' includes section on new page (incl. possible auxiliary info)
% '\includegraphics[settings]{filename}' add a figure or graph
% '\caption{}' adds a caption to a table or figure
% '\label{}' labels sections, tables, figures, etc. so that they can be referred to.
% '\ref{}' refer to a labelled sections, tables, figures, etc.
% '\begin{enumerate}...\end{enumerate}' numbered list
% '\begin{itemize}...\end{itemize}' bullet-ed list
% '\item' item in list section 
%
% Symbols:
% '\&' and sign
% '\%' percent sign
% '\_' three dotes
% '\#' hash symbol
% ------------------------------------------------------------------

% Relevance
Conflict between social groups and their individual members remains a prevalent feature of the modern human condition. Prejudices, discrimination, and animosities continue to plague societies around the world. One of the main ameliorations proposed by social psychologists has been positive intergroup contact. Based on Allport's (\citeyear{Allport1954b}) contact hypothesis, a plethora of studies and interventions have worked on bringing different social groups together\footnote{Cite interventions of British ministries.}.

\printbibliography

\appendix

\section{Appendix A}
\label{app:AppendixA}

Here goes the Appendix.

\end{document}

### 2021-10-03 scripts/functions/prismaGraph.R
Updates from Overleaf

@@ -1,0 +1,58 @@
+prismaGr <- function (found, found_other, no_dupes, screened, screen_exclusions, 
+          full_text, full_text_exclusions, qualitative, quantitative = NULL, 
+          labels = NULL, extra_dupes_box = FALSE, title = "", ..., dpi = 72, font_size = 10) {
+  
+  dupes <- found + found_other - no_dupes
+  labels <- list(found = paste("Records identified through", "database searching", sprintf("(n = %d)", found), sep = "\n"), 
+                 found_other = paste("Additional records identified", "through other sources", sprintf("(n = %d)", found_other), sep = "\n"), 
+                 no_dupes = paste("Records after duplicates removed", sprintf("(n = %d)", no_dupes), sep = "\n"), 
+                 dupes = paste("Duplicates excluded", sprintf("(n = %d)", dupes), sep = "\n"), 
+                 screened = paste("Records screened", sprintf("(n = %d)", screened), sep = "\n"), 
+                 screen_exclusions = paste("Records excluded", "[reasons, see Table 2]", sprintf("(n = %d)", screen_exclusions), sep = "\n"), 
+                 full_text = paste("Full-text articles assessed", "for eligibility", sprintf("(n = %d)", full_text), sep = "\n"), 
+                 full_text_exclusions = paste("Full-text articles excluded", "[reasons, see Table 2]", sprintf("(n = %d)", full_text_exclusions), sep = "\n"), 
+                 qualitative = paste("Studies included in qualitative synthesis",sprintf("(n = %d)", qualitative), sep = "\n"), 
+                 quantitative = paste("Studies included in", "quantitative synthesis", "(empirical)", sprintf("(n = %d)", quantitative), sep = "\n"))
+  
+  dupes_box <- sprintf("nodups -> incex;\n    nodups [label=\"%s\"];", 
+                       labels$no_dupes)
+  if (extra_dupes_box) 
+    dupes_box <- sprintf("nodups -> {incex; dups};\n       nodups [label=\"%s\"];\n       dups [label=\"%s\"]; {rank=same; nodups dups}", 
+                         labels$no_dupes, labels$dupes)
[…]

### 2021-10-03 scripts/functions/kappa.R
Updates from Overleaf

@@ -1,0 +1,67 @@
+kappa.full <- function(x, name, ...){
+  xtab <- table(x)
+  diagonal.counts <- diag(xtab)
+  N <- sum(xtab)
+  row.marginal.props <- rowSums(xtab)/N
+  col.marginal.props <- colSums(xtab)/N
+  # Compute kappa (k)
+  Po <- sum(diagonal.counts)/N
+  Pe <- sum(row.marginal.props*col.marginal.props)
+  k <- (Po - Pe)/(1 - Pe)
+  se <- sqrt((Po*(1-Po))/(N*(1-Pe)^2)) # according to PMID: 23092060
+  lwr <- k-1.96*se
+  upr <- k+1.96*se
+  
+  data.frame(name,Po,Pe,k,se,lwr,upr)
+}
+
+# # Minimally reproducible dataset
+# coders <- data.table(Affect1 = rbinom(250, 1,.62), Affect2 = rbinom(250, 1,.58))
+# name <- "affect"
+# kappa.full(coders, name)
+
+# --------------------------------------------------------------------------------
+
+kappa.full.multiple <- function(x, names, ...){
+  kComb <- list()
+  for (i in 1:length(names)) {
+    kComb[[i]] <- kappa.full(x %>% select(contains(names[i])), names[i])
+  }
+  do.call(rbind.data.frame, kComb)  
+}
+
+# # Minimally reproducible dataset
+# coders <- data.table(Affect1 = rbinom(250, 1,.62), Affect2 = rbinom(250, 1,.58),
+#                      Behavior1 = rbinom(250, 1,.32), Behavior2 = rbinom(250, 1,.40),
+#                      Cognition1 = rbinom(250, 1,.52), Cognition2 = rbinom(250, 1,.55),
+#                      Desire1 = rbinom(250, 1,.78), Desire2 = rbinom(250, 1,.82))
+# names <- c("affect", "behavior", "cognition", "desire")
+# kappa.full.multiple(coders, names)
+
+# --------------------------------------------------------------------------------
+
+kappa.pooled <- function(ktab, ...){
+  (mean(ktab$Po, na.rm = TRUE) - mean(ktab$Pe, na.rm = TRUE))/(1 - mean(ktab$Pe, na.rm = TRUE))
+}
+
+kappa.pooled2 <- function(ktab, ...){
+  k <- kappa.pooled(ktab)
+  require(boot)
+  set.seed(42)
[…]

### 2021-10-04 Supplemental-Material-B-Annotated-Analysis.Rmd
Update Supplemental-Material-B-Annotated-Analysis.Rmd

--- 2021-10-03 Supplemental-Material-B-Annotated-Analysis.Rmd
@@
 - Kai Epstude^1,2^
-- ^1^University of Groningen
-- ^2^Author order to be discussed currently alphabetic by last name
+- ^1^University of Groningen, Department of Psychology
+- ^2^Author order to be discussed; currently alphabetic by last name
 - "Author Information:"

### 2021-10-04 PreregistrationAOT-M.Rmd
description and citation method added

---
title           : "Preregistration of Psychological Needs During Intergroup Contact --- Sample: Young Medical Professionals"
shorttitle      : "Preregistration AOT-M"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1,2"
  - name        : Maximilian Agostini
    affiliation : "1,2"
  - name        : Laura Bringmann
    affiliation : "1,2"
  - name        : Peter de Jonge
    affiliation : "1,2"
  - name        : Kai Epstude
    affiliation : "1,2"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
  - id          : 2
    institution : Author order to be discussed; currently alphabetic by last name.
bibliography: references.bib
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# R Studio Clean-Up
  cat("\014") # clear console
  #rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
  gc() # garbage collector

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra",
         "sessioninfo", "tibble", "pander", "devtools",
         "data.table", "dplyr", "tidyr", "Hmisc", "kableExtra", 
         "stringr", "stringi", "reshape2", "lubridate")
invisible(lapply(lib, library, character.only = TRUE))  
rm(lib)

# Markdown Options
  knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory

# Global Chunk Options
  knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figures/',
                        echo=TRUE, warning=FALSE, message=FALSE)
```

# Study Information

## Title
<!-- Provide the working title of your study. It may be the same title that you submit for publication of your final manuscript, but it is not a requirement. The title should be a specific and informative description of a project. Vague titles such as 'Fruit fly preregistration plan' are not appropriate.

Example: Effect of sugar on brownie tastiness. -->

`r rmarkdown::metadata$title`

## Description
<!-- Please give a brief description of your study, including some background, the purpose of the of the study, or broad research questions. The description should be no longer than the length of an abstract. It can give some context for the proposed study, but great detail is not needed here for your preregistration.

Example: Though there is strong evidence to suggest that sugar affects taste preferences, the effect has never been demonstrated in brownies. Therefore, we will measure taste preference for four different levels of sugar concentration in a standard brownie recipe to determine if the effect exists in this pastry. -->

In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group [@Hewstone1996; @Pettigrew1998]. A key condition for these contact benefits, has been that the interaction is indeed perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact [e.g., @MacInnis2015]. It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact [Allport's Optimal Contact conditions, @Allport1954b]. And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met. However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met.But they don't discuss Allport's conditions. It, thus, remains unclear why exactly Allport's conditions work and whether there might be an underlying psychological mechanism at play.

We propose that Allport's optimal contact conditions are effective in creating positive contact because they constitute common psychological needs of the interacting individuals. If this is indeed the case, the impact of fulfilling other fundamental needs should produce similar beneficial contact results. And more importantly, the satisfaction of key situation needs during the interaction should predict the positive contact effects most strongly.

## Hypotheses
<!-- List specific, concise, and testable hypotheses. Please state if the hypotheses are directional or non-directional. If directional, state the direction. A predicted effect is also appropriate here. If a specific interaction or moderation is important to your research, you can list that as a separate hypothesis.

Example: If taste affects preference, then mean preference indices will be higher with higher concentrations of sugar. -->

Enter your response here.

# Design Plan
<!-- In this section, you will be asked to describe the overall design of your study. Remember that this research plan is designed to register a single study, so if you have multiple experimental designs, please complete a separate preregistration. -->

## Study type

**Observational Study**. Data is collected from study subjects that are not randomly assigned to a treatment. This includes surveys, natural experiments, and regression discontinuity designs.

## Blinding
<!-- Blinding describes who is aware of the experimental manipulations within a study. Select all that apply. Is there any additional blinding in this study? -->

No blinding is involved in this study.

## Study design
<!-- Describe your study design. Examples include two-group, factorial, randomized block, and repeated measures. Is it a between (unpaired), within-subject (paired), or mixed design? Describe any counterbalancing required. Typical study designs for observation studies include cohort, cross sectional, and case-control studies.

This question has a variety of possible answers. The key is for a researcher to be as detailed as is necessary given the specifics of their design. Be careful to determine if every parameter has been specified in the description of the study design. There may be some overlap between this question and the following questions. That is OK, as long as sufficient detail is given in one of the areas to provide all of the requested information. For example, if the study design describes a complete factorial, 2 X 3 design and the treatments and levels are specified previously, you do not have to repeat that information.

Example: We have a between subjects design with 1 factor (sugar by mass) with 4 levels. -->

Enter your response here.

## Randomization
<!-- If you are doing a randomized study, how will you randomize, and at what level? Typical randomization techniques include: simple, block, stratified, and adaptive covariate randomization. If randomization is required for the study, the method should be specified here, not simply the source of random numbers.

Example: We will use block randomization, where each participant will be randomly assigned to one of the four equally sized, predetermined blocks. The random number list used to create these four blocks will be created using the web applications available at https://random.org. -->

Enter your response here.

# Sampling Plan
<!-- In this section we’ll ask you to describe how you plan to collect samples, as well as the number of samples you plan to collect and your rationale for this decision. Please keep in mind that the data described in this section should be the actual data used for analysis, so if you are using a subset of a larger dataset, please describe the subset that will actually be used in your study. -->

## Existing data
<!-- Preregistration is designed to make clear the distinction between confirmatory tests, specified prior to seeing the data, and exploratory analyses conducted after observing the data. Therefore, creating a research plan in which existing data will be used presents unique challenges. Please select the description that best describes your situation. Please do not hesitate to contact us if you have questions about how to answer this question (prereg@cos.io). -->

**Registration prior to any human observation of the data**. As of the date of submission, the data exist but have not yet been quantified, constructed, observed, or reported by anyone - including individuals that are not associated with the proposed study. Examples include museum specimens that have not been measured and data that have been collected by non-human collectors and are inaccessible.

**Registration prior to accessing the data**. As of the date of submission, the data exist, but have not been accessed by you or your collaborators. Commonly, this includes data that has been collected by another researcher or institution.

## Explanation of existing data
<!-- If you indicate that you will be using some data that already exist in this study, please describe the steps you have taken to assure that you are unaware of any patterns or summary statistics in the data. This may include an explanation of how access to the data has been limited, who has observed the data, or how you have avoided observing any analysis of the specific data you will use in your study.

An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point.

Example: An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point. -->

Enter your response here.

## Data collection procedures
<!-- Please describe the process by which you will collect your data. If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g. inclusion and exclusion rules), and your study timeline. For studies that donÍt include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use.

The answer to this question requires a specific set of instructions so that another person could repeat the data collection procedures and recreate the study population. Alternatively, if the study population would be unable to be reproduced because it relies on a specific set of circumstances unlikely to be recreated (e.g., a community of people from a specific time and location), the criteria and methods for creating the group and the rationale for this unique set of subjects should be clear.

Example: Participants will be recruited through advertisements at local pastry shops. Participants will be paid $10 for agreeing to participate (raised to $30 if our sample size is not reached within 15 days of beginning recruitment). Participants must be at least 18 years old and be able to eat the ingredients of the pastries. -->

Enter your response here.

## Sample size
<!-- Describe the sample size of your study. How many units will be analyzed in the study? This could be the number of people, birds, classrooms, plots, interactions, or countries included. If the units are not individuals, then describe the size requirements for each unit. If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis? For some studies, this will simply be the number of samples or the number of clusters. For others, this could be an expected range, minimum, or maximum number.

Example: Our target sample size is 280 participants. We will attempt to recruit up to 320, assuming that not all will complete the total task. -->

Enter your response here.

## Sample size rationale
<!-- This could include a power analysis or an arbitrary constraint such as time, money, or personnel. This gives you an opportunity to specifically state how the sample size will be determined. A wide range of possible answers is acceptable; remember that transparency is more important than principled justifications. If you state any reason for a sample size upfront, it is better than stating no reason and leaving the reader to "fill in the blanks." Acceptable rationales include: a power analysis, an arbitrary number of subjects, or a number based on time or monetary constraints.

Example: We used the software program G*Power to conduct a power analysis. Our goal was to obtain .95 power to detect a medium effect size of .25 at the standard .05 alpha error probability. -->

Enter your response here.

## Stopping rule
<!-- If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection.

You may specify a stopping rule based on p-values only in the specific case of sequential analyses with pre-specified checkpoints, alphas levels, and stopping rules. Unacceptable rationales include stopping based on p-values if checkpoints and stopping rules are not specified. If you have control over your sample size, then including a stopping rule is not necessary, though it must be clear in this question or a previous question how an exact sample size is attained.

Example: We will post participant sign-up slots by week on the preceding Friday night, with 20 spots posted per week. We will post 20 new slots each week if, on that Friday night, we are below 320 participants. -->

Enter your response here.

# Variables
<!-- In this section you can describe all variables (both manipulated and measured variables) that will later be used in your confirmatory analysis plan. In your analysis plan, you will have the opportunity to describe how each variable will be used. If you have variables which you are measuring for exploratory analyses, you are not required to list them, though you are permitted to do so. -->

## Manipulated variables
<!-- Describe all variables you plan to manipulate and the levels or treatment arms of each variable. This is not applicable to any observational study. For any experimental manipulation, you should give a precise definition of each manipulated variable. This must include a precise description of the levels at which each variable will be set, or a specific definition for each categorical treatment. For example, “loud or quiet,” should instead give either a precise decibel level or a means of recreating each level. 'Presence/absence' or 'positive/negative' is an acceptable description if the variable is precisely described.

Example: We manipulated the percentage of sugar by mass added to brownies. The four levels of this categorical variable are: 15%, 20%, 25%, or 40% cane sugar by mass. -->

Enter your response here.

## Measured variables
<!-- Describe each variable that you will measure. This will include outcome measures, as well as any predictors or covariates that you will measure. You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.

Observational studies and meta-analyses will include only measured variables. As with the previous questions, the answers here must be precise. For example, 'intelligence,' 'accuracy,' 'aggression,' and 'color' are too vague. Acceptable alternatives could be 'IQ as measured by Wechsler Adult Intelligence Scale' 'percent correct,' 'number of threat displays,' and 'percent reflectance at 400 nm.'

Example: The single outcome variable will be the perceived tastiness of the single brownie each participant will eat. We will measure this by asking participants ‘How much did you enjoy eating the brownie’ (on a scale of 1-7, 1 being 'not at all', 7 being 'a great deal') and 'How good did the brownie taste' (on a scale of 1-7, 1 being 'very bad', 7 being 'very good'). -->

Enter your response here.

## Indices
<!-- If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method. If your are using a more complicated statistical method to combine measures (e.g. a factor analysis), you can note that here but describe the exact method in the analysis plan section.

If you are using multiple pieces of data to construct a single variable, how will this occur? Both the data that are included and the formula or weights for each measure must be specified. Standard summary statistics, such as "means" do not require a formula, though more complicated indices require either the exact formula or, if it is an established index in the field, the index must be unambiguously defined. For example, "biodiversity index" is too broad, whereas "Shannon’s biodiversity index" is appropriate.

Example: We will take the mean of the two questions above to create a single measure of 'brownie enjoyment.'  -->

Enter your response here.

# Analysis Plan
<!-- You may describe one or more confirmatory analysis in this preregistration. Please remember that all analyses specified below must be reported in the final article, and any additional analyses must be noted as exploratory or hypothesis generating.

A confirmatory analysis plan must state up front which variables are predictors (independent) and which are the outcomes (dependent), otherwise it is an exploratory analysis. You are allowed to describe any exploratory work here, but a clear confirmatory analysis is required. -->

## Statistical models
<!-- What statistical model will you use to test each hypothesis? Please include the type of model (e.g. ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates). Please specify any interactions, subgroup analyses, pairwise or complex contrasts, or follow-up tests from omnibus tests. If you plan on using any positive controls, negative controls, or manipulation checks you may mention that here. Remember that any test not included here must be noted as an exploratory test in your final article.

This is perhaps the most important and most complicated question within the preregistration. As with all of the other questions, the key is to provide a specific recipe for analyzing the collected data. Ask yourself: is enough detail provided to run the same analysis again with the information provided by the user? Be aware for instances where the statistical models appear specific, but actually leave openings for the precise test. See the following examples:

- If someone specifies a 2x3 ANOVA with both factors within subjects, there is still flexibility with the various types of ANOVAs that could be run. Either a repeated measures ANOVA (RMANOVA) or a multivariate ANOVA (MANOVA) could be used for that design, which are two different tests. 
- If you are going to perform a sequential analysis and check after 50, 100, and 150 samples, you must also specify the p-values you’ll test against at those three points.

Example:  We will use a one-way between subjects ANOVA to analyze our results. The manipulated, categorical independent variable is 'sugar' whereas the dependent variable is our taste index. -->

Enter your response here.

## Transformations
<!-- If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process. If any categorical predictors are included in a regression, indicate how those variables will be coded (e.g. dummy coding, summation coding, etc.) and what the reference category will be.

Example: The "Effect of sugar on brownie tastiness" does not require any additional transformations. However, if it were using a regression analysis and each level of sweet had been categorically described (e.g. not sweet, somewhat sweet, sweet, and very sweet), 'sweet' could be dummy coded with 'not sweet' as the reference category. -->

Enter your response here.

## Inference criteria
<!-- What criteria will you use to make inferences? Please describe the information youÍll use (e.g. p-values, bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?

p-values, confidence intervals, and effect sizes are standard means for making an inference, and any level is acceptable, though some criteria must be specified in this or previous fields. Bayesian analyses should specify a Bayes factor or a credible interval. If you are selecting models, then how will you determine the relative quality of each? In regards to multiple comparisons, this is a question with few "wrong" answers. In other words, transparency is more important than any specific method of controlling the false discovery rate or false error rate. One may state an intention to report all tests conducted or one may conduct a specific correction procedure; either strategy is acceptable.

Example: We will use the standard p<.05 criteria for determining if the ANOVA and the post hoc test suggest that the results are significantly different from those expected if the null hypothesis were correct. The post-hoc Tukey-Kramer test adjusts for multiple comparisons. -->

## Data exclusion
<!-- How will you determine what data or samples, if any, to exclude from your analyses? How will outliers be handled? Will you use any awareness check? Any rule for excluding a particular set of data is acceptable. One may describe rules for excluding a participant or for identifying outlier data.

Example: No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the three tastiness indices. Outliers will be included in the analysis. -->

Enter your response here.

## Missing data
<!-- How will you deal with incomplete or missing data? Any relevant explanation is acceptable. As a final reminder, remember that the final analysis must follow the specified plan, and deviations must be either strongly justified or included as a separate, exploratory analysis.

Example: If a subject does not complete any of the three indices of tastiness, that subject will not be included in the analysis. -->

Enter your response here.

## Exploratory analyses (optional)
<!-- If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here. An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use. A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.

Example: We expect that certain demographic traits may be related to taste preferences. Therefore, we will look for relationships between demographic variables (age, gender, income, and marital status) and the primary outcome measures of taste preferences. -->

Enter your response here.

# Other

## Other (Optional)
<!-- If there is any additional information that you feel needs to be included in your preregistration, please enter it here. Literature cited, disclosures of any related work such as replications or work that uses the same data, or other context that will be helpful for future readers would be appropriate here. -->

Enter your response here.

# References
## 
\vspace{-2pc}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{-1in}
\setlength{\parskip}{8pt}
\noindent

### 2021-10-04 PreregistrationAOT-M.Rmd
sampling plan added

@@
 
-Enter your response here.
+1.
+\label{hyp:contact}Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
+    a. \label{hyp:contactFreq}Participants with more intergroup interactions should have a more favorable outgroup attitudes.
+    b.
+\label{hyp:contactDummy}Outgroup attitudes should be higher after an intergroup interaction compared to a time with no outgroup interaction.
+OR: Outgroup attitudes should increase more after an intergroup interaction compared to a time with no outgroup interaction.
+    c. \label{hyp:contactFreqQual}Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
+    d. \label{hyp:contactQualCor}Alternative to H\ref{hyp:contactFreqQual}: Interaction quality should relate positively with outgroup attitudes.
+2.
+\label{hyp:AllportsConditions}Based on Allport's optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+    a.
+\label{hyp:AllportsPred}Based on Allport's optimal contact conditions, outgroup attitudes should be more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
+    b.
+\label{hyp:AllportsQuality}Based on past research on the role of interaction quality, interaction quality should be more perceived as more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
+    c.
+\label{hyp:AllportsQualityMediation}Based on past research on the role of interaction quality, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extend be assumed by interaction quality.
+3.
+\label{hyp:keyNeed}Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+    a. \label{hyp:keyNeedPred}Outgroup attitudes should be more favorable after intergroup interactions with high key need fulfillment.
+    b. \label{hyp:keyNeedQual}Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
+    c. \label{hyp:keyNeedMediation}The variance explained in outgroup attitudes by key need fulfillment should to a large extend be assumed by interaction quality.
+    d.
+\label{hyp:keyNeedContactType}The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
+Thus, the effect of key need fulfillment on outgroup attitudes should stronger for intergroup interact than for ingroup interactions.
+    e.
+\label{hyp:keyNeedSDT}The effect of key need fulfillment on outgroup attitudes should be persist even when taking other fundamental psychological needs into account.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
+4. \label{hyp:comparison}Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict outgroup attitudes at least as well as Allport's conditions.
+    a. \label{hyp:compModel}The need model (H\ref{hyp:keyNeedPred}) should predict more variance in outgroup attitudes than the model based on Allport's conditions (H\ref{hyp:AllportsPred}).
+    b.
+\label{hyp:compTogether}The  effect of key need fulfillment on outgroup attitudes should  persist even when taking other Allport's conditions into account.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for equal status, common goals, collaboration, and structural support.
 
@@
 
-Enter your response here.
+This study used an extensive longitudinal design.
+Using a daily diary format, for at least 30 days participants received a short survey twice per day (at around 12pm and 7pm).
+We additionally included a longer pre- and post measurement survey the days before and after the extensive longitudinal data collection.
 
@@
 
-Enter your response here.
+No randomization is involved in this study.
 
@@
 -->
-
-**Registration prior to any human observation of the data**.
-As of the date of submission, the data exist but have not yet been quantified, constructed, observed, or reported by anyone - including individuals that are not associated with the proposed study.
-Examples include museum specimens that have not been measured and data that have been collected by non-human collectors and are inaccessible.
 
@@
 
-Enter your response here.
+The data was collected as part of a larger collaboration on daily intergroup relations.
+The researchers have had no direct access to the data, as the data was collected using an automated system using the FormR framework [@Arslan2020].
 
@@
 
-Enter your response here.
+The data was collected in a three step procedure:
+
+1. Entry Survey: A pre-measurement questionnaire (appr. 25 minutes) including demographic information, and relations to the Dutch majority. (payment: 2 Euros)
+2. Experience Recaps: At least 30 days of short reflection surveys (appr. 3—5 minutes) on intergroup interactions twice a day. (payment: 1 Euro per Recap; up to 2 Euros per day)
+3. Conclusion Survey: On the last day, we conclude with a post-measurement questionnaire (appr. 25 minutes) with some questions on habits and reflection of the study. (payment: 2 Euros)
+
+After the initial 30 day duration, participants are offered the possibility to continue participating in the study either with payment if daily diary measures were missed during the initial study phase or without payment after a total of 60 daily diary measurements were completed.
+After the initial 30-day period, participants receive automated feedback based on their own well-being, attitudes, and motive responses as an additional initiative give participants access to their own data and to compensate study participation.
 
@@
 
-Enter your response here.
+Our target sample size is a sum of 4,000 daily diary measurements.
+With 100% completion rate that would be archieved with 67 participants (60 daily diary responses each).
+Given that we expect some incomplete daily diary measurements, we aimed to recruit 80 participants.
 
@@
 
-Enter your response here.
+The targeted sample size depended on a combination of different factors.
+Different analyses were planned as part of the collaboration and budgeting was a practical constraint.
+Some analyses were planned based on (1) the pre- to post measurements, (2) the dynamic developments over the daily diary measurements, as well (3) the contemporary effects within the daily diary measurements.
+
+Power considerations of mixed effects model such as with extensive longitudinal data are difficult to estimate because of the complex covariance structures.
+Simulation studies based on the first two samples within this project indicated that with well-distributed scales, and small to medium effect sizes, 70-80 participants with at least seven daily diary measurements and a simple pre--post survey were sufficiently powerful (power = .8, alpha = .05) to answer most of the key research questions of the collaboration.
+
+The ultimate sampling procedure decision was made as a practical balancing of the number of participants and the number of measurements provided by each participants.
+Given that this study primarily focuses on the contemporaneous effects within the daily diary measurements, power should thus be high enough.
 
@@
 
-Enter your response here.
+Participants will be recruited until 80 participants finish the pre-measurement.
+Invitations to complete additional daily diary measurements will be extended until participants chose to leave the study or at the most until two months (i.e., 64 days) after the initial entry survey (i.e., from the pre measurement survey).
 

### 2021-10-04 PreregistrationAOT-M.Rmd
Model and transformations added

@@
     a. \label{hyp:contactFreq}Participants with more intergroup interactions should have a more favorable outgroup attitudes.
-    b.
-\label{hyp:contactDummy}Outgroup attitudes should be higher after an intergroup interaction compared to a time with no outgroup interaction.
-OR: Outgroup attitudes should increase more after an intergroup interaction compared to a time with no outgroup interaction.
+    b. \label{hyp:contactDummy}Outgroup attitudes should be higher after an intergroup interaction compared to a non-outgroup interaction.
     c. \label{hyp:contactFreqQual}Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
-    d. \label{hyp:contactQualCor}Alternative to H\ref{hyp:contactFreqQual}: Interaction quality should relate positively with outgroup attitudes.
 2.
@@
 
-No blinding is involved in this study.
+No participant blinding is involved in this study.
 
@@
 
-Enter your response here.
+Not applicable given that the study design is observational.
 
@@
 
-Enter your response here.
+**Key variables:**
+
+1. Whether an interaction happened during the past daytime period
+    a. Did you meet a Dutch person this [morning/afternoon]?
+    a. Did you meet a Non-Dutch person [morning/afternoon]?
+1. Number of interactions during the past daytime period
+    a. How many interactions with Dutch people did you have this [morning/afternoon]?
+    a. How many interactions with Non-Dutch people did you have this [morning/afternoon]?
+1. Key need assessment
+    a. What was your main goal during the interaction with [name interaction partner]?
+    a. During the interaction with [name interaction partner] your goal [free-text entry interaction key need] was fulfilled.
+1. Allport's Conditions (equal status, common goal, collaboration, and structural support)
+    a. The interaction with [name interaction partner] was on equal footing (same status)
+    a. [name interaction partner] shared your goal ([free-text entry interaction key need])
+    a. The interaction with [name interaction partner] was cooperative
+    a. The interaction with [name interaction partner] was voluntary
+1. Interaction Quality
+    a. Overall, the interaction with [name interaction partner] was: Unpleasant to Pleasant
+1. Outgroup Attitudes
+    a. After the interaction, how favorably do you feel towards the Dutch.
+
+**Control variables:**
+
+1. Self Determination Theory needs ("During the interaction with [name interaction partner]")
+    a. I was myself.
+    a. I felt competent.
+    a. I shared information about myself. 
+    a. [name interaction partner] shared information about themselves.
+1. General key need during daytime
+    a. What was your main goal during this [morning/afternoon]?
+    a. During this [morning/afternoon] your goal ([free-text entry daytime key need]) was fulfilled
+    a. How important was your goal ([free-text entry daytime key need]) to you:
+1. Student Goals ("Please rate the importance of each goal during the interaction with [name interaction partner]"):
+    a. Social support / social connection goals
+    a. Romantic or sexual relationship goals
+    a. Academic goals
+    a. Career goals
+    a. Financial goals
+    a. Health / fitness goals
+    a. Leisure / fun goals
+    a. Personal improvement / growth goals
+    a. Service / helping goals
+    a. Spiritual / religious goals
+
+**Additional Analyses:**
+
+1. Generalization from interaction partner to outgroup
+    a. After the interaction, how favorably do you feel towards [name interaction partner].
+    a. The interaction with [name interaction partner] was representative of the Dutch.
+1. Alternative interaction quality definition ("Overall, the interaction with [name interaction partner] was ...")
+    a. Unpleasant to Pleasant
+    a. Superficial to Meaningful
+    a. Ineffective to Effective
+    a. Unimportant to Important
+1. Potential moderation by the relationship with interaction partner
+    a. How close do you feel to [name interaction partner]?
+    a. How much do you trust [name interaction partner]?
+    a. What is your relationship with [name interaction partner]?
+1. Potential moderation by key need characteristics
+    a. [name interaction partner] helped fulfill your goal [free-text entry interaction key need].
+    a. How important was your goal ([free-text interaction key need]) to you?
+1. Potential moderation by the interaction characteristics
+    a. How long was the interaction? (in minutes)
+    a. What was the main language during the interaction?
+    a. The interaction was: With a single other / In a group
+
+_Full variable information is available in the codebook ('Codebook_AOT-M_ItemsPerSection.xlsx')_
 
@@
 
-Enter your response here.
+1. Mean Allport's conditions 
+    a. The interaction with [name interaction partner] was on equal footing (same status)
+    a. [name interaction partner] shared your goal ([free-text entry interaction key need])
+    a. The interaction with [name interaction partner] was cooperative
+    a. The interaction with [name interaction partner] was voluntary
+1. Mean belongingness during intergroup contact
+    a. I shared information about myself. 
+    a. [name interaction partner] shared information about themselves.
+1. Mean alternative interaction quality definition ("Overall, the interaction with [name interaction partner] was ...")
+    a. Unpleasant to Pleasant
+    a. Superficial to Meaningful
+    a. Ineffective to Effective
+    a. Unimportant to Important
 
@@
 
-Enter your response here.
+1. Contact Hypothesis
+    a. Correlation: $r_{InteractionFrequency, OutgroupAttitudes} \neq 0$
+    a. T-test: $\mu_{OutgroupInteraction} > \mu_{IngroupInteraction}$
+    a. Regression: $Attitude \sim AverageContactFreq \times AverageContactQual$
+1. Allport's Conditions
+    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}AllportConditions_{ij} + u_{oj} + r_{ij}$
+    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}AllportConditions_{ij} + \gamma_{20}InteractionQuality_{ij} + u_{oj} + r_{ij}$
+
+        with $u_{oj} \sim \mathcal{N}(0,\tau^2_{00})$ and $r_{ij} \sim \mathcal{N}(0,\sigma^2)$
+1. Key Need Fulfillment
+    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + u_{oj} + r_{ij}$
+    a. Regression: $InteractionQuality_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + u_{oj} + r_{ij}$
+    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + \gamma_{20}InteractionQuality_{ij} + u_{oj} + r_{ij}$
+    a. Regression: $Attitude_{ij} \sim KeyNeedFulfill_{ij} \times OutgroupInteraction_{ij}$
+    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + \gamma_{20}Autonomy_{ij} + \gamma_{30}Competence_{ij} + \gamma_{40}Relatedness_{ij} + u_{oj} + r_{ij}$
+
+        with $u_{oj} \sim \mathcal{N}(0,\tau^2_{00})$ and $r_{ij} \sim \mathcal{N}(0,\sigma^2)$
+1. Comparison with Allport's Conditions
+    a. Model Comparison: $AIC_{KeyNeedModel} > AIC_{AllportModel}$
+    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + \gamma_{20}AllportConditions_{ij} + u_{oj} + r_{ij}$
+
+        with $u_{oj} \sim \mathcal{N}(0,\tau^2_{00})$ and $r_{ij} \sim \mathcal{N}(0,\sigma^2)$
 
@@
 
-Enter your response here.
+We will mean-center all level one predictors within participants (i.e., cluster mean centering).
+This is relevant for any predictor variable during the interaction (e.g., key need fulfillment, interaction quality, ...).
+We mean-center within-person predictors, because we obtain a meaningful intercept when having a random slope model [e.g., @Hamaker2014]
 
@@
 -->
+
+Enter your response here.
 
@@
 
-Enter your response here.
+Not applicable.
 

### 2021-10-04 PreregistrationAOT-M.Rmd
first draft

@@
 ---
-title           : "Preregistration of Psychological Needs During Intergroup Contact --- Sample: Young Medical Professionals"
-shorttitle      : "Preregistration AOT-M"
+title           : "Psychological Needs During Intergroup Contact: Young Medical Professionals Sample"
+shorttitle      : "Preregistration: Needs During Intergroup Contact"
 date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
@@
     a. Correlation: $r_{InteractionFrequency, OutgroupAttitudes} \neq 0$
-    a. T-test: $\mu_{OutgroupInteraction} > \mu_{IngroupInteraction}$
+    a.
+T-test: $\mu_{OutgroupInteraction} > \mu_{IngroupInteraction}$ (to build confidence in the persistence of the contact effect, we additionally compare the attitudes after an outgroup interaction to attitudes after no outgroup interaction (i.e., including instances where participants had no interaction at all).)
     a. Regression: $Attitude \sim AverageContactFreq \times AverageContactQual$
@@
 
-Enter your response here.
+We will use the standard p<.05 criteria for determining whether the correlation and regression coefficients are statistically significant.
+However, given the large sample size we will place a particular emphasis on effect sizes in our interpretations of the results.
 
@@
 
-Enter your response here.
+No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the variables of interest for a given analysis.
+Outliers will be included in the analysis.
 
@@
 
-Enter your response here.
+Given the (unexpectedly) large sample size of contemporaneous measurements, we will remove all instances during which a participant did not respond to any of the relevant variables.
 
@@
 
-Enter your response here.
+@Brown2005 proposed in their integrative theory of intergroup contact that "group salience" should moderate the positive effect of intergroup contact on outgroup attitudes.
+They argue that especially when the outgroup membership is salient, the positive attitudes should generalize from the outgroup individual to the general outgroup.
+We have data to test this hypothesis within a large intensive longitudinal dataset of daily intergroup interactions.
+We do this by seperately assessing attitudes towards the outgroup interaction partner and the outgroup generally.
+And by assessing whether perceiving the interaction as representative of the outgroup moderates the positive contact effects.
+
+To build confidence in our conclusions about the role of contact quality we calculate an alternative measure of interaction quality that includes perceived pleasantness, meaning, effectiveness, and importance of the interaction.
+
+We expect that certain contextual characteristics may be related to the positive effects of high quality outgroup interactions.
+Therefore, we will look for the effect of key need fulfillment on outgroup attitudes while also including information about the interaction partner (perceived closeness, trust, relationship), the interaction characteristics (duration, interaction language, group vs.
+dyadic), as well as characteristics of the key need (importance of the need, fulfillment due to the interaction partner).
 

### 2021-10-06 PreregistrationAOT-M.Rmd
typos

@@
 2. Experience Recaps: At least 30 days of short reflection surveys (appr. 3—5 minutes) on intergroup interactions twice a day. (payment: 1 Euro per Recap; up to 2 Euros per day)
-3. Conclusion Survey: On the last day, we conclude with a post-measurement questionnaire (appr. 25 minutes) with some questions on habits and reflection of the study. (payment: 2 Euros)
+3. Conclusion Survey: On the last day, we conclude with a post-measurement questionnaire (appr. 25 minutes) with some questions on habits and reflections on the study. (payment: 2 Euros)
 
 After the initial 30 day duration, participants are offered the possibility to continue participating in the study either with payment if daily diary measures were missed during the initial study phase or without payment after a total of 60 daily diary measurements were completed.
-After the initial 30-day period, participants receive automated feedback based on their own well-being, attitudes, and motive responses as an additional initiative give participants access to their own data and to compensate study participation.
+After the initial 30-day period, participants receive automated feedback visualizing the development of their own well-being, attitudes, and motive responses as an additional initiative to give participants access to their own data and to compensate study participation.
 
@@
 Our target sample size is a sum of 4,000 daily diary measurements.
-With 100% completion rate that would be archieved with 67 participants (60 daily diary responses each).
+With 100% completion rate that would be archived with 67 participants (60 daily diary responses each).
 Given that we expect some incomplete daily diary measurements, we aimed to recruit 80 participants.
@@
 Different analyses were planned as part of the collaboration and budgeting was a practical constraint.
-Some analyses were planned based on (1) the pre- to post measurements, (2) the dynamic developments over the daily diary measurements, as well (3) the contemporary effects within the daily diary measurements.
+Some analyses were planned based on (1) the pre- to post measurements, (2) the dynamic developments over the daily diary measurements, or (3) the contemporary effects within the daily diary measurements.
 
@@
 
-Given the (unexpectedly) large sample size of contemporaneous measurements, we will remove all instances during which a participant did not respond to any of the relevant variables.
+Given the (expectedly) large sample size of contemporaneous measurements, we will remove all instances during which a participant did not respond to any of the relevant variables.
 

### 2021-10-06 Supplemental-Material-B-Annotated-Analysis.Rmd
data import added

@@
 
+```{r formrImport}
+# workers
+dtWorker <- list(
+  raw.pre = read_spss("data/S1_Workers/processed/cleaned/MT - Pre-Measure - 06-15-2018.sav"),
+  raw.post = read_spss("data/S1_Workers/processed/cleaned/MT - Post-Measure - 06-15-2018.sav"),
+  raw.morning = read_spss("data/S1_Workers/processed/cleaned/MT - Morning - 06-15-2018.sav"),
+  raw.afternoon = read_spss("data/S1_Workers/processed/cleaned/MT - Afternoon - 06-15-2018.sav")
+)
+
+# students
+dtStudents <- list(
+  raw.pre = read.csv(file = "data/S2_Students/raw/AOTS_Pre.csv", header = T, sep = ","),
+  raw.post = read.csv(file = "data/S2_Students/raw/AOTS_Post.csv", header = T, sep = ","),
+  raw.daily = read.csv(file = "data/S2_Students/raw/AOTS_Daily.csv", header = T, sep = ",")
+)
+
+# young medical professionals
+
+```
+
 ## Data Cleaning

### 2021-10-07 PreregristrationS3/PreregistrationAOT-M.Rmd
moved to subfolder

--- 2021-10-06 PreregistrationAOT-M.Rmd
@@
     institution : Author order to be discussed; currently alphabetic by last name.
-bibliography: references.bib
+bibliography: "../references.bib"
 csl: apa.csl

### 2021-10-07 Supplemental-Material-B-Annotated-Analysis.Rmd
Update Supplemental-Material-B-Annotated-Analysis.Rmd

--- 2021-10-04 Supplemental-Material-B-Annotated-Analysis.Rmd
@@
 
+```{r formrImport}
+# workers
+# initial data cleaning was done in SPSS (syntax files are available in "")
+dtWorker <- list(
+  raw.pre = read_spss("data/S1_Workers/processed/cleaned/MT - Pre-Measure - 06-15-2018.sav"),
+  raw.post = read_spss("data/S1_Workers/processed/cleaned/MT - Post-Measure - 06-15-2018.sav"),
+  raw.morning = read_spss("data/S1_Workers/processed/cleaned/MT - Morning - 06-15-2018.sav"),
+  raw.afternoon = read_spss("data/S1_Workers/processed/cleaned/MT - Afternoon - 06-15-2018.sav")
+)
+
+# students
+dtStudents <- list(
+  raw.pre = read.csv(file = "data/S2_Students/raw/AOTS_Pre.csv", header = T, sep = ","),
+  raw.post = read.csv(file = "data/S2_Students/raw/AOTS_Post.csv", header = T, sep = ","),
+  raw.daily = read.csv(file = "data/S2_Students/raw/AOTS_Daily.csv", header = T, sep = ",")
+)
+
+# young medical professionals
+dtMedical <- list(
+  raw.pre = c(),
+  raw.post = c(),
+  raw.daily = c()
+)
+
+```
+
 ## Data Cleaning

### 2021-10-08 PreregristrationS3/PreregistrationAOT-M.Rmd
feedback LFB 1/n

--- 2021-10-06 PreregistrationAOT-M.Rmd
@@
   - name        : Jannis Kreienkamp
-    affiliation : "1,2"
+    affiliation : "1"
   - name        : Maximilian Agostini
-    affiliation : "1,2"
+    affiliation : "1"
   - name        : Laura Bringmann
-    affiliation : "1,2"
+    affiliation : "1"
   - name        : Peter de Jonge
-    affiliation : "1,2"
+    affiliation : "1"
   - name        : Kai Epstude
-    affiliation : "1,2"
+    affiliation : "1"
 affiliation:
@@
     institution : University of Groningen, Department of Psychology
-  - id          : 2
-    institution : Author order to be discussed; currently alphabetic by last name.
-bibliography: references.bib
+bibliography: "../references.bib"
 csl: apa.csl
@@
 In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group [@Hewstone1996; @Pettigrew1998].
-A key condition for these contact benefits, has been that the interaction is indeed perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact [e.g., @MacInnis2015].
+A key condition for these contact benefits, has been that the interaction is perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact [e.g., @MacInnis2015].
 It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact [Allport's Optimal Contact conditions, @Allport1954b].
 And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met.
-However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met.But they don't discuss Allport's conditions.
+However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met.
 It, thus, remains unclear why exactly Allport's conditions work and whether there might be an underlying psychological mechanism at play.
@@
 The researchers have had no direct access to the data, as the data was collected using an automated system using the FormR framework [@Arslan2020].
+The data were then downloaded and stored securely on an encrypted device until the eventual data analysis.
+None of the researchers have accessed the data thus far.
 
@@
 
+We will use a sequential analysis strategy in line with our proposed hypotheses.
+Given the nested structure of much of our data we test many of our hypotheses using a multilevel approach, where $y_{ti}$ denotes the response at measurement occasion $t$ ($t = 1, ...,T_i$, level 1) for individual $i$ ($i = 1, ..., n$, level 2).
+It should be noted that we will follow a hierarchical regression approach.
+We follow the common three-step procedure [e.g., @Bliese2013]:
+
 1. Contact Hypothesis
@@
     a.
-T-test: $\mu_{OutgroupInteraction} > \mu_{IngroupInteraction}$ (to build confidence in the persistence of the contact effect, we additionally compare the attitudes after an outgroup interaction to attitudes after no outgroup interaction (i.e., including instances where participants had no interaction at all).)
-    a. Regression: $Attitude \sim AverageContactFreq \times AverageContactQual$
+T-test: $\mu_{0utgroupInteraction} > \mu_{IngroupInteraction}$ (to build confidence in the persistence of the contact effect, we additionally compare the attitudes after an outgroup interaction to attitudes after no outgroup interaction (i.e., including instances where participants had no interaction at all).)
+    a. Regression: $Attitude = AverageContactFreq \times AverageContactQual$
 1. Allport's Conditions
-    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}AllportConditions_{ij} + u_{oj} + r_{ij}$
-    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}AllportConditions_{ij} + \gamma_{20}InteractionQuality_{ij} + u_{oj} + r_{ij}$
+    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}AllportConditions_{ti} + u_{0i} + u_{1i} + e_{ti}$
+    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}AllportConditions_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}$
 
-        with $u_{oj} \sim \mathcal{N}(0,\tau^2_{00})$ and $r_{ij} \sim \mathcal{N}(0,\sigma^2)$
+        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
 1. Key Need Fulfillment
-    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + u_{oj} + r_{ij}$
-    a. Regression: $InteractionQuality_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + u_{oj} + r_{ij}$
-    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + \gamma_{20}InteractionQuality_{ij} + u_{oj} + r_{ij}$
-    a. Regression: $Attitude_{ij} \sim KeyNeedFulfill_{ij} \times OutgroupInteraction_{ij}$
-    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + \gamma_{20}Autonomy_{ij} + \gamma_{30}Competence_{ij} + \gamma_{40}Relatedness_{ij} + u_{oj} + r_{ij}$
+    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}$
+    a. Regression: $InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}$
+    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}$
+    a. Regression: $Attitude_{ti} = KeyNeedFulfill_{ti} \times OutgroupInteraction_{ti} + u_{0i} + u_{1i} + e_{ti}$
+    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + u_{1i} + e_{ti}$
 
-        with $u_{oj} \sim \mathcal{N}(0,\tau^2_{00})$ and $r_{ij} \sim \mathcal{N}(0,\sigma^2)$
+        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
 1. Comparison with Allport's Conditions
     a. Model Comparison: $AIC_{KeyNeedModel} > AIC_{AllportModel}$
-    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + \gamma_{20}AllportConditions_{ij} + u_{oj} + r_{ij}$
+    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}AllportConditions_{ti} + u_{0i} + u_{1i} + e_{ti}$
 
-        with $u_{oj} \sim \mathcal{N}(0,\tau^2_{00})$ and $r_{ij} \sim \mathcal{N}(0,\sigma^2)$
+        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
 

### 2021-10-08 Supplemental-Material-B-Annotated-Analysis.Rmd
Update Supplemental-Material-B-Annotated-Analysis.Rmd

@@
          "sessioninfo", "tibble", "pander", "devtools",
-         "data.table", "dplyr", "tidyr", "Hmisc", "kableExtra", 
+         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", 
          "stringr", "stringi", "reshape2", "lubridate")
@@
 
+```{r cleanWorker}
+#  important names for Morning and Afternoon
+  names.m <- c(
+    "StartDate",
+    "EndDate",
+    "Finished",
+    "Duration__in_seconds_",
+    "RecordedDate",
+    "ExternalReference",
+    "Meta_Operating_System",
+    "Contact_dum",
+    "number",
+    "time",
+    "duration_1",
+    "dyad.group",
+    "gr_size",
+    "gr_type_1",
+    "gr_type_2",
+    "gr_type_3",
+    "gr_type_4",
+    "gr_type_5",
+    "gr_type_6",
+    "gr_type_7",
+    "gr_type_8",
+    "gr_type_9",
+    "gr_type_10",
+    "gr_type_11",
+    "gr_type_12",
+    "gr_type_13",
+    "gr_type_14",
+    "gr_type_15",
+    "gr_type_16",
+    "gr_type_17_TEXT",
+    "gr_context_1",
+    "gr_context_2",
+    "gr_context_3",
+    "gr_context_4",
+    "gr_context_5",
+    "gr_context_6",
+    "gr_context_7",
+    "gr_context_8",
+    "gr_context_9",
+    "gr_context_10",
+    "gr_context_11",
+    "gr_context_12",
+    "gr_context_13_TEXT",
+    "gr_context_14_TEXT",
+    "gr_dutchness",
+    "dyad_type_1",
+    "dyad_type_2",
+    "dyad_type_3",
+    "dyad_type_4",
+    "dyad_type_5",
+    "dyad_type_6",
+    "dyad_type_7",
+    "dyad_type_8",
+    "dyad_type_9",
+    "dyad_type_10",
+    "dyad_type_11",
+    "dyad_type_12",
+    "dyad_type_13",
+    "dyad_type_14",
+    "dyad_type_15",
+    "dyad_type_16",
+    "dyad_type_17_TEXT",
+    "Context_1",
+    "Context_2",
+    "Context_3",
+    "Context_4",
+    "Context_5",
+    "Context_6",
+    "Context_7",
+    "Context_8",
+    "Context_9",
+    "Context_10",
+    "Context_11",
+    "Context_12",
+    "Context_13_TEXT",
+    "Context_14_TEXT",
+    "keyMotive",
+    "keymotive_fulfillemt_1",
+    "keyMotive_Dutch_1",
+    "autonomy_1",
+    "competence_1",
+    "relatedness_self_1",
+    "relatedness_other_1",
+    "qualityAccidental_1",
+    "qualityVoluntary_1",
+    "qualityCooperative_1",
+    "qualityDutchy_1",
+    "quality_overall_1",
+    "quality_meaning_1",
+    "quality_star_1",
+    "wantInt",
+    "desire_type_1",
+    "desire_type_2",
+    "desire_type_3",
+    "desire_type_4",
+    "desire_type_5",
+    "desire_type_6",
+    "desire_type_7",
+    "desire_type_8",
+    "desire_type_9",
+    "desire_type_10",
+    "desire_type_11",
+    "desire_type_12",
+    "desire_type_13",
+    "desire_type_14",
+    "desire_type_15",
+    "desire_type_16",
+    "desire_type_17_TEXT",
+    "desire_context_1",
+    "desire_context_2",
+    "desire_context_3",
+    "desire_context_4",
+    "desire_context_5",
+    "desire_context_6",
+    "desire_context_7",
+    "desire_context_8",
+    "desire_context_9",
+    "desire_context_10",
+    "desire_context_11",
+    "desire_context_12",
+    "desire_context_13_TEXT",
+    "desire_context_14_TEXT",
+    "Reason_nodesire",
+    "keyMotive_noInt",
+    "keyMotive_noInt_fulf_1",
+    "autonomy_NoInt_1",
+    "competence_NoInt_1",
+    "relatedness_1_NoInt_1",
+    "thermometerDutch_1",
+    "thermometerDutchInt_2",
+    "ExWB_1",
+    "alertness1",
+    "calmness1",
+    "valence1",
+    "alertness2",
+    "calmness2",
+    "valence2",
+    "inNonDutch",
+    "NonDutchNum",
+    "NonDutchType_1",
+    "NonDutchType_2",
+    "NonDutchType_3",
+    "NonDutchType_4",
+    "NonDutchType_5",
+    "NonDutchType_6",
+    "NonDutchType_7",
+    "NonDutchType_8",
+    "NonDutchType_9",
+    "NonDutchType_10",
+    "NonDutchType_11",
+    "NonDutchType_12",
+    "NonDutchType_13",
+    "NonDutchType_14",
+    "NonDutchType_15_TEXT",
+    "date",
+    "time.0",
+    "LocationLatitude",
+    "LocationLongitude"
+  )
+
+  names.a <- c(names.m, "keyInteraction_1", "keyInteractionTime")
+
+# Create reduced data sets for morning and afternoon
+  dat.mo <- dtWorker$raw.morning[, names.m]
+  dat.mo$daytime <- "morning"
+
+  dat.af <- dtWorker$raw.afternoon[, names.a]
+  dat.af$daytime <- "afternoon"
+
+# merge morning and afternoon measurements with indicator [+ clean up]
+  daily.dat <- rbind.fill(dat.mo, dat.af)
+  daily.dat <- daily.dat[daily.dat$ExternalReference != 55951, ]
+  dtWorker$daily <- daily.dat
+  rm(dat.mo, dat.af, names.m, names.a, daily.dat)
+
+# names for pre-measurement
+  names.pre <- c(
+    "Finished",
+    "age",
+    "Gender",
+    "Living",
+    "roommate_1",
+    "roommate_2",
+    "roommate_3",
+    "nationality",
+    "SecondNationality",
+    "timeNL_1",
+    "Reason_2",
+    "Reason_5",
+    "Reason_7",
+    "Reason_8_TEXT",
+    "DutchLang",
+    "occupation_1",
+    "occupation_2",
+    "occupation_3",
+    "occupation_4",
+    "occupation_7",
+    "CurrentEducation_1",
+    "education_level",
+    "EduLang_2",
+    "RUG_faculty",
+    "Study.0",
+    "association",
+    "DutchMeetNum",
+    "DutchFriends_1",
+    "assimilation",
+    "separation",
+    "integration",
+    "marginalization",
+    "VIA_heritage",
+    "VIA_Dutch",
+    "SSAS_surrounding",
+    "SSAS_privat",
+    "SSAS_public",
+    "autonomy",
+    "relatedness",
+    "competence",
+    "anxiety",
+    "swl",
+    "alertness",
+    "calmness",
+    "valence",
+    "date",
+    "time",
+    "City",
+    "ZIP",
+    "id"
+  )
+
+# reduced data set for pre measurement
+  dat.pre.red <- dtWorker$raw.pre[, names.pre]
+
+# merge with daily data [+ clean up]
+  df.pre <- merge(
+    x = dtWorker$daily,
+    y = dat.pre.red,
+    by.x = "ExternalReference",
+    by.y = "id",
+    all = T
+  )
+  rm(names.pre)
+
+# adjust duplicate names to fit to indicate daily or pre measurement  
+  names(df.pre) <- gsub("[[:punct:]]x", ".daily", names(df.pre))
+  names(df.pre) <- gsub("[[:punct:]]y", ".pre", names(df.pre))
+
+# names for post measurement  
+  names.post <- c(
+    "ExternalReference",
+    "assimilation",
+    "separation",
+    "integration",
+    "marginalization",
+    "VIA_heritage",
+    "VIA_Dutch",
+    "anxiety",
+    "swl",
+    "rosenberg",
+    "social_support",
+    "stress",
+    "discrimination",
+    "discrimination_month",
+    "NLE_1month",
+    "NLE_6month",
+    "NLE_12month"
+  )
+
+# reduced data set for post-measurement  
+  dat.post.red <- dtWorker$raw.post[, names.post]
+
+# merge post measurement with pre- and daily data  
+  df <- merge(
+    x = df.pre,
+    y = dat.post.red,
+    by.x = "ExternalReference",
+    by.y = "ExternalReference",
+    all = T
+  )
+
+# adjust duplicate names to indicate pre or post  
+  names(df) <- gsub("[[:punct:]]x", ".pre", names(df))
+  names(df) <- gsub("[[:punct:]]y", ".post", names(df))
+
+# add to list
+  dtWorker$combined <- df
+
+# create data frame with cleaned data
+  df <- dtWorker$combined %>%
+    filter(Finished.pre == 1,
+           Finished.daily == 1,
+           !is.na(ExternalReference))
+
+# add running number as measurement ID within participants   
+  df$measureID = rowidv(df, cols = c("ExternalReference"))
+
+  dtWorker$clean <- df
+
+# clean up
+  rm(df.pre, names.post, dat.post.red, dat.pre.red, df)
+
+# Export reduced Data
+  #write.csv(dtWorker$clean, "data/processed/MT_clean-merged_07-05-2018.csv", row.names = F)
+  #save(dtWorker$clean, file = "data/processed/MT_clean-merged_07-05-2018.RData")
+```
+
+```{r cleanStudents}
+
+```
+
+```{r cleanMedical}
+
+```
+
 ## Data Exclusions

### 2021-10-08 PreregristrationS3/PreregistrationAOT-M.Rmd
Feedback LFB 2/2

@@
 ---
-title           : "Psychological Needs During Intergroup Contact: Young Medical Professionals Sample"
+title           : "Psychological Needs During Intergroup Contact: An Extensive Longitudinal Study (Young Medical Professionals Sample)"
 shorttitle      : "Preregistration: Needs During Intergroup Contact"
@@
 
-1. Mean Allport's conditions 
+1.
+Mean Allport's conditions.
+We create a mean-averaged index of Allport's conditions in response to past findings indicating that the conditions are best conceptualized jointly and as functioning together rather than as fully independent factors [@Pettigrew2006, p.
+766].
+Similar to past studies we thus hope to build a global indicator [e.g., see @Pettigrew2006].
+As with other indices we will ensure that the individual items indeed relate to a common latent construct and are  meaningfully combine in an index.
+If this is not possible we will create sub-indices and/or assess the impact of the conditions separately.
     a. The interaction with [name interaction partner] was on equal footing (same status)
@@
 We will use a sequential analysis strategy in line with our proposed hypotheses.
-Given the nested structure of much of our data we test many of our hypotheses using a multilevel approach, where $y_{ti}$ denotes the response at measurement occasion $t$ ($t = 1, ...,T_i$, level 1) for individual $i$ ($i = 1, ..., n$, level 2).
-It should be noted that we will follow a hierarchical regression approach.
-We follow the common three-step procedure [e.g., @Bliese2013]:
+Given the nested structure of much of our data we test many of our hypotheses using a multilevel approach, where $y_{ti}$ denotes the response at measurement occasion $t$ ($t = 1, ...,T_i$; level 1) for individual $i$ ($i = 1, ..., n$; level 2).
+It should be noted that we will follow a hierarchical modeling approach.
+We follow the common four-step procedure [e.g., @Bliese2013]: (1) Test whether enough variation exists within and between participants to justify a multilevel structure, (2) (sequentially) add key predictors, (3) check whether a random slope explains an adequate amount of variance, and (4) check for autocorrelations and heteroscedasticity.
+For brevity we will only present the full multilevel regression formulas below.
 
-1. Contact Hypothesis
+1. Contact Hypothesis (using between participant aggregates only to meaningfully include interaction frequency)
     a. Correlation: $r_{InteractionFrequency, OutgroupAttitudes} \neq 0$
@@
 
-We will mean-center all level one predictors within participants (i.e., cluster mean centering).
+We will mean-center all level-one predictors within participants (i.e., cluster mean centering).
 This is relevant for any predictor variable during the interaction (e.g., key need fulfillment, interaction quality, ...).
-We mean-center within-person predictors, because we obtain a meaningful intercept when having a random slope model [e.g., @Hamaker2014]
+We mean-center within-person predictors, to meaningfully distinguish within and between person variances and because we obtain a meaningful intercept when having a random slope model [e.g., @Hamaker2014].
 
@@
 No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the variables of interest for a given analysis.
-Outliers will be included in the analysis.
+Outliers will generally be included in analyses, however we will use sensitivity analyses to assess the robustness of the results to outliers.
 

### 2021-10-08 PreregristrationS3/PreregistrationAOT-M.Rmd
introduction adjusted

@@
 In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group [@Hewstone1996; @Pettigrew1998].
-A key condition for these contact benefits, has been that the interaction is perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact [e.g., @MacInnis2015].
+A key condition for these contact benefits has been that the interaction is perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact [e.g., @MacInnis2015].
 It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact [Allport's Optimal Contact conditions, @Allport1954b].
 And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met.
-However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met.
-It, thus, remains unclear why exactly Allport's conditions work and whether there might be an underlying psychological mechanism at play.
+However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met [@Pettigrew2006].
+It, thus, remains unclear why and how exactly Allport's conditions work.
 

### 2021-10-08 Supplemental-Material-B-Annotated-Analysis.Rmd
AOT-S cleaning addded

@@
 ```{r cleanStudents}
+# our own test IDs
+ownIDs <- c(
+  "beautifulLionfishXXXR5rcgVBzGu8hPvOqrK8UBJBw4owvi9nfRFSFu3lMzYhE",
+  "niceDogoXXXmB8JI5SFu78SF3DVof84mGUPPNUr14p2HYFTtp31a6D1OwAzM6F-K",
+  "amusedQuailXXXmhuc_fpTp8vPkMwDH1BzjaH1d1kHSO1bsPEfsnaEYk4WeVBfPi",
+  "juwGAbtXX0_1kmZtSVqKh3PGaHOICqUyU4iBkrT3nDsI_uifuD1gzKcZerxaM5FL"
+)
 
+# Prepare dfs for Cleaning
+df.pre <- dtStudents$raw.pre %>%
+  mutate_all(na_if,"") %>%
+  mutate_all(na_if,"NA") %>%
+  filter(!is.na(ended)) %>% # remove all who did not finish
+  filter(!e_mail %in% .$e_mail[duplicated(.$e_mail)]) %>% # remove all who did the pre questionnaire multiple times (b/c inconsistent ratings scales)
+  filter(!session %in% ownIDs) %>% # remove our own test 
+  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)
+
+df.post <- dtStudents$raw.post %>%
+  mutate_all(na_if,"") %>%
+  mutate_all(na_if,"NA") %>%
+  filter(!is.na(session)) %>% # remove own test runs
+  filter(!session %in% ownIDs) %>% # remove our own test 
+  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
+  filter(!is.na(ended)) %>% # remove all who never finished
+  filter(!session %in% .$session[duplicated(.$session)]) %>% # remove all duplicate sessions
+  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)
+
+df.daily <- dtStudents$raw.daily %>%
+  mutate_all(na_if,"") %>%
+  mutate_all(na_if,"NA") %>%
+  filter(!session %in% ownIDs) %>% # remove our own test 
+  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
+  filter(!is.na(ended)) %>% # remove all who never finished
+  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)
+
+# merge daily with pre
+dfPreDaily = merge(
+  x = df.daily,
+  y = df.pre,
+  by = "session",
+  suffixes = c(".daily", ".pre"),
+  all = F
+)
+
+# merge daily with post 
+dfCombined = merge(
+  x = dfPreDaily,
+  y = df.post,
+  by = "session",
+  suffixes = c(".pre", ".post"),
+  all = F
+)
+
+# add to list
+dtStudents$clean <- dfCombined
+
+# clean up workspace
+rm(df.pre, df.daily, df.post, dfPreDaily, dfCombined, ownIDs)
 ```
@@
 ```{r cleanMedical}
-
+#TBD
 ```

### 2021-10-10 Supplemental-Material-B-Annotated-Analysis.Rmd
Update Supplemental-Material-B-Annotated-Analysis.Rmd

@@
 
-## Data Cleaning
+## Data Cleaning & Data Exclusions
 
@@
 
-## Data Exclusions
+## Calculate needed transformations
+
+```{r newVarsWorkers}
+# ID variables
+  short <- dtWorker$clean %>%
+    mutate(
+      PID = as.numeric(factor(ExternalReference)), # participant ID
+      TID = measureID-1, # time ID with t0 = 0 for meaningfull intercept interpretations
+      date = substr(StartDate,1,10), # awkward way of extracting date (best converted to )
+      time = substr(StartDate,12,19), # awkward way of extracting time
+      daynum = as.numeric(factor(date)), # all days as numeric for ordering
+      daycor = ifelse(daytime=="morning" & period_to_seconds(hms(time))<period_to_seconds(hms("12:00:00")) | daytime=="afternoon" & period_to_seconds(hms(time))<period_to_seconds(hms("19:00:00")),daynum-1,daynum), # correctly identify which date the questionnaire is about
+      daycor.lead = sprintf("%02d", daycor),
+      daytime.lt = ifelse(daytime=="morning","a","b"), # morning / afternoon to a / b 
+      day_time = paste(daycor.lead, daytime.lt, sep="_"), # combine day id with morning / afternoon
+      session = as.numeric(factor(day_time)) # day and time identifier as numeric id
+    )
+
+  df <- dtWorker$clean
+
+  df$PID = as.numeric(factor(df$ExternalReference)) # participant ID
+  df$TID = df$measureID-1 # time ID with t0 = 0 for meaningful intercept interpretations
+
+# Time and Date Variables: Correct morning / afternoon date where survey was collected the day after to indicate the correct date that was targeted
+  df$SubTime = chron::times(df$time.0)
+  df$SubTime[df$daytime == "afternoon"] = paste0(substring(as.character(df$time.0[df$daytime == "afternoon"]),4,8),":00")
+
+  df$PPDate = as.Date(df$date.daily)
+  df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"] = df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"]-1
+  df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"] = df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"]-1
+
+  df$time.daily = as.character(df$time.daily)
+  df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")] = paste0(substring(as.character(df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")]),4,8),":00")
+
+# Mood scales
+  df$calmness.daily = rowSums(df[, c("calmness1", "calmness2")], na.rm = T)
+  df$alertness.daily = rowSums(df[, c("alertness1", "alertness2")], na.rm =T)
+  df$valence.daily = rowSums(df[, c("valence1", "valence2")], na.rm = T)
+
+# Need scales
+  df$keyMotiveFulfilled = rowSums(df[,c("keymotive_fulfillemt_1","keyMotive_noInt_fulf_1")], na.rm=T)
+  df$autonomy.daily.all = rowSums(df[,c("autonomy_1","autonomy_NoInt_1")], na.rm=T)
+  df$competence.daily.all = rowSums(df[,c("competence_1","competence_NoInt_1")], na.rm=T)
+  #cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
+  df$relatedness.daily.all = rowMeans(df[,c("relatedness_other_1","relatedness_self_1","relatedness_1_NoInt_1")], na.rm=T)
+
+# summarize by participant
+  df$number[is.na(df$number)] = 0
+  df$NonDutchNum[is.na(df$NonDutchNum)] = 0
+  count = aggregate(list(CtContactNL=df$Contact_dum,
+                         CtContactNonNl=df$inNonDutch,
+                         CtContactNLAll=df$number,
+                         CtContactNonNlAll=df$NonDutchNum), 
+                    by=list(ExternalReference=df$ExternalReference), 
+                    FUN=sum)
+  average = aggregate(list(AvKeyNeed=df$keyMotiveFulfilled,
+                           AvKeyNeedInt=df$keymotive_fulfillemt_1,
+                           AvKeyNeedNoInt=df$keyMotive_noInt_fulf_1,
+                           AvAutonomy=df$autonomy.daily.all,
+                           AvCompetence=df$competence.daily.all,
+                           AvRelatedness=df$relatedness.daily.all,
+                           AvThermo=df$thermometerDutch_1,
+                           AvWB=df$ExWB_1),
+                      by=list(ExternalReference=df$ExternalReference), 
+                      FUN=mean, na.rm=T)
+
+  df.btw = df[,-c(9:162)]
+  df.btw = df.btw[,-grep(names(df.btw),pattern="daily|ID|keyMotive")]
+
+  df.btw = Reduce(function(x, y) merge(x, y, by="ExternalReference", all=TRUE), list(df.btw, count, average))
+  df.btw = df.btw[!duplicated(df.btw$ExternalReference),]
+
+  df.btw[!is.na(df.btw$assimilation.post),]
+
+  df.btw$CtContactNL_c = scale(df.btw$CtContactNL, scale = FALSE)
+  df.btw$AvKeyNeedInt_c = scale(df.btw$AvKeyNeedInt, scale = FALSE)
+  df.btw$AvKeyNeed_c = scale(df.btw$AvKeyNeed, scale = FALSE)
+  df.btw$CtContactNL_z = scale(df.btw$CtContactNL, scale = T)
+  df.btw$AvKeyNeedInt_z = scale(df.btw$AvKeyNeedInt, scale = T)
+  df.btw$AvKeyNeed_z = scale(df.btw$AvKeyNeed, scale = T)
+
+  .GlobalEnv$df.btw = df.btw
+
+  save(df.btw, file = "data/processed/df.btw.RData")  
+  #write_sav(df.btw, "data/processed/MT_clean-merged_pre-post.sav")
+
+# export data to Mplus
+
+  df.mplus = remove_all_labels(select(df, PID, session, thermometerDutch_1, inNonDutch, Contact_dum, keyMotiveFulfilled, autonomy.daily.all, competence.daily.all, relatedness.daily.all))
+  names(df.mplus)= c("PID", "session", "att", "intin", "intout", "keymot", "aut", "comp", "rel")
+  mplus = df.mplus[order(df.mplus$PID, df.mplus$session),]
+  mplus.intcont = mplus[mplus$intout==1,]
+  prepareMplusData(mplus.intcont, "data/processed/dynamic-subset-intonly.dat")
+
+```
 

### 2021-10-10 Supplemental-Material-B-Annotated-Analysis.Rmd
dtWorker munge added

--- 2021-10-08 Supplemental-Material-B-Annotated-Analysis.Rmd
@@
 
+  df <- df %>%
+    mutate(
+      PID = as.numeric(factor(ExternalReference)), # participant ID
+      TID = measureID-1, # time ID with t0 = 0 for meaningfull intercept interpretations
+      date = substr(StartDate,1,10), # awkward way of extracting date (best converted to )
+      time = substr(StartDate,12,19), # awkward way of extracting time
+      daynum = as.numeric(factor(date)), # all days as numeric for ordering
+      daycor = ifelse(daytime=="morning" & period_to_seconds(hms(time))<period_to_seconds(hms("12:00:00")) | daytime=="afternoon" & period_to_seconds(hms(time))<period_to_seconds(hms("19:00:00")),daynum-1,daynum), # correctly identify which date the questionnaire is about
+      daycor.lead = sprintf("%02d", daycor),
+      daytime.lt = ifelse(daytime=="morning","a","b"), # morning / afternoon to a / b 
+      day_time = paste(daycor.lead, daytime.lt, sep="_"), # combine day id with morning / afternoon
+      session = as.numeric(factor(day_time)), # day and time identifier as numeric id
+      SubTime = chron::times(time.0),
+      time.daily = as.character(time.daily),
+      PPDate = as.Date(df$date.daily),
+      number = replace_na(number, 0),
+      NonDutchNum = replace_na(NonDutchNum, 0)
+    )
+
   dtWorker$clean <- df
@@
 
-## Data Exclusions
+## Calculate needed transformations
+
+```{r newVarsWorkers}
+df <- dtWorker$clean
+
+# Time and Date Variables
+  # remove seconds from afternoon time
+  df$SubTime[df$daytime == "afternoon"] = paste0(substring(as.character(df$time.0[df$daytime == "afternoon"]),4,8),":00") 
+  df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")] = paste0(substring(as.character(df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")]),4,8),":00")
+
+  # Correct morning / afternoon date where survey was collected the day after to indicate the correct date that was targeted
+  df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"] = df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"]-1
+  df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"] = df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"]-1
+
+# Mood scales
+  df$calmness.daily = rowSums(df[, c("calmness1", "calmness2")], na.rm = T)
+  df$alertness.daily = rowSums(df[, c("alertness1", "alertness2")], na.rm =T)
+  df$valence.daily = rowSums(df[, c("valence1", "valence2")], na.rm = T)
+
+# Need scales
+  df$keyMotiveFulfilled = rowSums(df[,c("keymotive_fulfillemt_1","keyMotive_noInt_fulf_1")], na.rm=T)
+  df$autonomy.daily.all = rowSums(df[,c("autonomy_1","autonomy_NoInt_1")], na.rm=T)
+  df$competence.daily.all = rowSums(df[,c("competence_1","competence_NoInt_1")], na.rm=T)
+  #cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
+  df$relatedness.daily.all = rowMeans(df[,c("relatedness_other_1","relatedness_self_1","relatedness_1_NoInt_1")], na.rm=T)
+  df$relatedness.daily.int = rowMeans(df[,c("relatedness_other_1","relatedness_self_1")], na.rm=T)
+
+# summarize by participant (check that everything is within pp might not be the case for )
+  between <- df %>%
+    group_by(ExternalReference) %>%
+    mutate(
+      CtContactNL = sum(Contact_dum),
+      CtContactNonNl = sum(inNonDutch),
+      CtContactNLAll = sum(number),
+      CtContactNonNlAll = sum(NonDutchNum),
+      AvKeyNeed = mean(keyMotiveFulfilled, na.rm=T),
+      AvKeyNeedInt = mean(keymotive_fulfillemt_1, na.rm=T),
+      AvKeyNeedNoInt = mean(keyMotive_noInt_fulf_1, na.rm=T),
+      AvAutonomy = mean(autonomy.daily.all, na.rm=T),
+      AvCompetence = mean(competence.daily.all, na.rm=T),
+      AvRelatedness = mean(relatedness.daily.all, na.rm=T),
+      AvThermo = mean(thermometerDutch_1, na.rm=T),
+      AvWB = mean(ExWB_1, na.rm=T)) %>%
+    ungroup() %>%
+    mutate(
+      CtContactNL_c = scale(CtContactNL, scale = FALSE),
+      AvKeyNeedInt_c = scale(AvKeyNeedInt, scale = FALSE),
+      AvKeyNeed_c = scale(AvKeyNeed, scale = FALSE),
+      CtContactNL_z = scale(CtContactNL, scale = TRUE),
+      AvKeyNeedInt_z = scale(AvKeyNeedInt, scale = TRUE),
+      AvKeyNeed_z = scale(AvKeyNeed, scale = TRUE)
+    )
+
+  warning("some variable transformations (esp. _c and _z) might be across all participants (i.e., not within PP).")
+
+  dtWorker$munge <- between
+
+  rm(df, between)
+
+  #save(df.btw, file = "data/processed/df.btw.RData")  
+  #write_sav(df.btw, "data/processed/MT_clean-merged_pre-post.sav")
+
+# export data to Mplus
+  # df.mplus = remove_all_labels(select(df, PID, session, thermometerDutch_1, inNonDutch, Contact_dum, keyMotiveFulfilled, autonomy.daily.all, competence.daily.all, relatedness.daily.all))
+  # names(df.mplus)= c("PID", "session", "att", "intin", "intout", "keymot", "aut", "comp", "rel")
+  # mplus = df.mplus[order(df.mplus$PID, df.mplus$session),]
+  # mplus.intcont = mplus[mplus$intout==1,]
+  # prepareMplusData(mplus.intcont, "data/processed/dynamic-subset-intonly.dat")
+
+```
+
+```{r newVarsStudents}
+df <-
+
+# Add ID variables
+  df$PID = as.numeric(factor(df$session)) # participant ID
+
+# order time
+  # move this here? 
+  # date.period.order <- unique(raw$dat.daily$date_period)
+  date.period.order <- .GlobalEnv$date.period.order # <- @Max: Do you still need this? Order should be fine natively from FormR
+
+  df$TID <- factor(df$date_period, levels = date.period.order)
+  df$TIDnum <- as.numeric(df$TID) #get numeric TID
+
+  # check whether time ordering worked
+  df_ordered <- df %>%
+    arrange(PID, TID) #%>%
+    #View()
+
+# Interaction as Factor
+  df$interaction.f <- factor(df$Interaction, levels = c("no interaction", "Dutch", "Non-Dutch"))
+  df$intNL <- ifelse(df$Interaction=="Dutch",1,0)
+  df$intNonNL<- ifelse(df$Interaction=="Non-Dutch",1,0)
+
+# ------------------------------------------------------------------------------------------------------------- 
+#                                       Combine Variables
+# -------------------------------------------------------------------------------------------------------------
+source("lib/fun.panel.R")
+# Relatedness
+  .GlobalEnv$pairs.panels.new(df[c("RelatednessSelf","RelatednessOther")], 
+                              labels = c("I shared information about myself.", "X shared information about themselves."))
+  df$RelatednessInteraction <- rowMeans(df[c("RelatednessSelf","RelatednessOther")], na.rm=T)
+  df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <- NA
+# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
+  df$Relatedness <- rowMeans(df[,c("RelatednessInteraction", "RelatednessNoInteraction")], na.rm=T)
+# Pro-Sociality
+  df$ProSo <- rowMeans(df[,c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm=T)
+# Anti-Sociality
+  df$AntiSo <- rowMeans(df[,c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm=T)
+
+# ------------------------------------------------------------------------------------------------------------- 
+#                                 Create Time Variables
+# -------------------------------------------------------------------------------------------------------------
+createTimeDf <- function(tmp) {
+# make dataframe for all variables that need t-1
+# @Max: LAGS AREN'T REALLY MEANINGFUL BECAUSE OF THE TIME INTERVAL DIFFERENCES, WE WILL DO THIS IN DSEM (MPLUS).
+  tmp <- data.frame(KeyNeedFullfillment = tmp$KeyNeedFullfillment,
+                    ProSo = tmp$ProSo,
+                    AntiSo = tmp$AntiSo,
+                    AttitudesDutch = tmp$AttitudesDutch)
+    length <- ncol(tmp) # get the length of tmp for later renaming of columns
+
+  # use dplyr to create time series
+    tmp <- tmp %>% mutate_each(funs(lag(.,1))) %>% cbind(tmp, .)
+    colnames(tmp)[(length+1):ncol(tmp)] <- paste(colnames(tmp)[1:length], "Lag1", sep = "") #rename after specific length (add one so new columns get renamed after that)
+  tmp
+}
+
+# split df per participants and run function
+  PP <- split(df, df$PID)
+  PP <- lapply(PP, createTimeDf); rm(createTimeDf)
+
+# add variables back to df
+  tmp <- do.call(rbind.data.frame, PP)
+    colnames(tmp) <- paste(colnames(tmp), "Calc", sep = "")
+df <- cbind(tmp, df);rm(tmp)
+
+# ------------------------------------------------------------------------------------------------------------- 
+#                                 Add Variables related to interaction partner
+# -------------------------------------------------------------------------------------------------------------
+
+# create function for later lapply
+createIntPartDf <- function(inp) {
+
+  # prepare the dataframe so that we can forloop over it later
+    tmp <- data.frame(CC = as.character(inp$CC),
+                    NewCC = as.character(inp$NewCC),
+                    NewName = as.character(inp$NewName),
+                    NewCloseness = inp$NewCloseness,
+                    NewGender = inp$NewGender,
+                    NewEthnicity = as.character(inp$NewEthnicity),
+                    NewRelationship = as.character(inp$NewRelationship))
+
+    tmp$CC2 <- recode(tmp$CC, "'SOMEONE ELSE' = NA")
+    tmp$CC2 <- ifelse(tmp$CC == 1 | tmp$CC == "SOMEONE ELSE", as.character(tmp$NewName), as.character(tmp$CC2)) 
+    # maybe add [[:space:]]\b to remove space before word boundary or ^[[:space:]] to remove space in the beginning of a string
+    tmp$CC2 <- gsub("^[[:space:]]", "", tmp$CC2)
+    tmp$NewName <- gsub("^[[:space:]]", "", tmp$NewName)
+
+  # open the variables that will be filled up in the foor-loop
+    tmp$closeness <- rep(NA, nrow(tmp))
+    tmp$gender <- rep(NA, nrow(tmp))
+    tmp$ethnicity <- rep(NA, nrow(tmp))
+    tmp$relationship <- rep(NA, nrow(tmp))
+
+    # Run the for-loop. It finds the variables related to the name of the interaction partner. If there is a repeating interaction
+    # partner (i.e. CC2) it takes the value (i.e. NewCloseness) from the first interaction (i.e. NewName)
+      for (i in 1:nrow(tmp)) {
+         if (is.na(tmp$CC2[i])) {
+           next
+         } else {
+           tmp$closeness[i] <- na.omit(tmp$NewCloseness[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] #find closeness where CC2 matches NewName (na.omit + [1] to get the number)
+           tmp$gender[i] <- na.omit(tmp$NewGender[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] #(na.omit + [1] to get the number and not the rest of the na.omit list)
+           tmp$ethnicity[i] <- na.omit(as.character(tmp$NewEthnicity[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1] #PROBLEM IS THAT THERE ARE TOO MANY NA's: Difficult to deal with
+           tmp$relationship[i] <- na.omit(as.character(tmp$NewRelationship[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1]
+         }
+      }
+
+    out <- tmp
+    out
+}
+
+# split df per participants and run function
+  PP <- split(df, df$PID)
+  PP <- lapply(PP, createIntPartDf); rm(createIntPartDf)
+
+# add variables back to df
+  remergePP <- do.call(rbind.data.frame, PP)
+    colnames(remergePP) <- paste(colnames(remergePP), "_Calc", sep = "")
+df <- cbind(remergePP, df);rm(remergePP)
+print("Test whether newly calculate df and old df have the same order:")
+print(table(as.character(df$CC_Calc) == as.character(df$CC)))
+print("If we also add the NAs we get the exact number:")
+print(sum(is.na(df$CC_Calc))+table(as.character(df$CC_Calc) == as.character(df$CC)))
+
+# ------------------------------------------------------------------------------------------------------------- 
+#                                 Center Relevant Variables
+# -------------------------------------------------------------------------------------------------------------
+  # center within participant
+  # @Max: I removed the lagged variables so we can do it proberly in MPlus
+    df$ProSo_c <- ave(df$ProSoCalc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
+    #df$ProSoLag1_c <- ave(df$ProSoLag1Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
+    df$AntiSo_c <- ave(df$AntiSoCalc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
+    #df$AntiSoLag1_c <- ave(df$AntiSoLag1Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
+    df$KeyNeedFullfillment_c <- ave(df$KeyNeedFullfillmentCalc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
+    #df$KeyNeedFullfillmentLag1_c <- ave(df$KeyNeedFullfillmentLag1Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
+
+    df$closeness_c <- ave(df$closeness_Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
+
+# variancec
+  df$var.AntiSo <- ave(df$AntiSo, df$PID, FUN=var)
+
+# send back to global environment
+  .GlobalEnv$df.full = df
+
+```
 

### 2021-10-11 Supplemental-Material-B-Annotated-Analysis.Rmd
rendered

@@
          "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra",
-         "sessioninfo", "tibble", "pander", "devtools",
+         "sessioninfo", "tibble", "pander", "devtools", "mada",
          "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", 
@@
 
-  dtWorker$munge <- between
+  dtWorker$full <- between
 
@@
 ```{r newVarsStudents}
-df <-
+df <- dtStudents$clean
 
@@
 # order time
-  # move this here? 
-  # date.period.order <- unique(raw$dat.daily$date_period)
-  date.period.order <- .GlobalEnv$date.period.order # <- @Max: Do you still need this? Order should be fine natively from FormR
-
-  df$TID <- factor(df$date_period, levels = date.period.order)
+  df$TID <- factor(df$date_period, levels = unique(dtStudents$raw.daily$date_period))
   df$TIDnum <- as.numeric(df$TID) #get numeric TID
@@
   # check whether time ordering worked
-  df_ordered <- df %>%
+  df <- df %>%
     arrange(PID, TID) #%>%
@@
 # -------------------------------------------------------------------------------------------------------------
-source("lib/fun.panel.R")
 # Relatedness
-  .GlobalEnv$pairs.panels.new(df[c("RelatednessSelf","RelatednessOther")], 
+  pairs.panels.new(df[c("RelatednessSelf","RelatednessOther")], 
                               labels = c("I shared information about myself.", "X shared information about themselves."))
@@
 # ------------------------------------------------------------------------------------------------------------- 
-#                                 Create Time Variables
-# -------------------------------------------------------------------------------------------------------------
-createTimeDf <- function(tmp) {
-# make dataframe for all variables that need t-1
-# @Max: LAGS AREN'T REALLY MEANINGFUL BECAUSE OF THE TIME INTERVAL DIFFERENCES, WE WILL DO THIS IN DSEM (MPLUS).
-  tmp <- data.frame(KeyNeedFullfillment = tmp$KeyNeedFullfillment,
-                    ProSo = tmp$ProSo,
-                    AntiSo = tmp$AntiSo,
-                    AttitudesDutch = tmp$AttitudesDutch)
-    length <- ncol(tmp) # get the length of tmp for later renaming of columns
-
-  # use dplyr to create time series
-    tmp <- tmp %>% mutate_each(funs(lag(.,1))) %>% cbind(tmp, .)
-    colnames(tmp)[(length+1):ncol(tmp)] <- paste(colnames(tmp)[1:length], "Lag1", sep = "") #rename after specific length (add one so new columns get renamed after that)
-  tmp
-}
-
-# split df per participants and run function
-  PP <- split(df, df$PID)
-  PP <- lapply(PP, createTimeDf); rm(createTimeDf)
-
-# add variables back to df
-  tmp <- do.call(rbind.data.frame, PP)
-    colnames(tmp) <- paste(colnames(tmp), "Calc", sep = "")
-df <- cbind(tmp, df);rm(tmp)
-
-# ------------------------------------------------------------------------------------------------------------- 
 #                                 Add Variables related to interaction partner
 # -------------------------------------------------------------------------------------------------------------
-
 # create function for later lapply
@@
 
-    tmp$CC2 <- recode(tmp$CC, "'SOMEONE ELSE' = NA")
+    tmp$CC2 <- recode(tmp$CC, 'SOMEONE ELSE' = "NA")
     tmp$CC2 <- ifelse(tmp$CC == 1 | tmp$CC == "SOMEONE ELSE", as.character(tmp$NewName), as.character(tmp$CC2)) 
@@
     colnames(remergePP) <- paste(colnames(remergePP), "_Calc", sep = "")
-df <- cbind(remergePP, df);rm(remergePP)
-print("Test whether newly calculate df and old df have the same order:")
+df <- cbind(df, remergePP);rm(remergePP)
+writeLines("Test whether newly calculate df and old df have the same order:")
 print(table(as.character(df$CC_Calc) == as.character(df$CC)))
-print("If we also add the NAs we get the exact number:")
+writeLines("If we also add the NAs we get the exact number:")
 print(sum(is.na(df$CC_Calc))+table(as.character(df$CC_Calc) == as.character(df$CC)))
@@
 # -------------------------------------------------------------------------------------------------------------
-  # center within participant
-  # @Max: I removed the lagged variables so we can do it proberly in MPlus
-    df$ProSo_c <- ave(df$ProSoCalc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
-    #df$ProSoLag1_c <- ave(df$ProSoLag1Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
-    df$AntiSo_c <- ave(df$AntiSoCalc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
-    #df$AntiSoLag1_c <- ave(df$AntiSoLag1Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
-    df$KeyNeedFullfillment_c <- ave(df$KeyNeedFullfillmentCalc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
-    #df$KeyNeedFullfillmentLag1_c <- ave(df$KeyNeedFullfillmentLag1Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
 
-    df$closeness_c <- ave(df$closeness_Calc, df$PID, FUN=function(x) scale(x, center = T, scale = F))
+df <- df %>%
+  group_by(PID) %>% 
+  mutate(
+    KeyNeedFullfillment.cm = mean(KeyNeedFullfillment, na.rm = TRUE), # cluster mean (mean of PP)
+    KeyNeedFullfillment.cwc = KeyNeedFullfillment - KeyNeedFullfillment.cm, # cluster mean centered (within PP centered)
+    closeness.cm = mean(closeness_Calc, na.rm = TRUE),
+    closeness.cwc = closeness_Calc - closeness.cm
+    ) %>%  
+  ungroup()
 
-# variancec
-  df$var.AntiSo <- ave(df$AntiSo, df$PID, FUN=var)
-
-# send back to global environment
-  .GlobalEnv$df.full = df
-
+# store
+  dtStudents$full = df
 ```

### 2021-10-11 PreregristrationS3/PreregistrationAOT-M.Rmd
worker until key need

@@
     a.
-T-test: $\mu_{0utgroupInteraction} > \mu_{IngroupInteraction}$ (to build confidence in the persistence of the contact effect, we additionally compare the attitudes after an outgroup interaction to attitudes after no outgroup interaction (i.e., including instances where participants had no interaction at all).)
-    a. Regression: $Attitude = AverageContactFreq \times AverageContactQual$
+T-test: $\mu_{i,0utgroupInteraction} > \mu_{i,IngroupInteraction}$ (to build confidence in the persistence of the contact effect, we additionally compare the attitudes after an outgroup interaction to attitudes after no outgroup interaction (i.e., including instances where participants had no interaction at all).)
+    a. Regression: $Attitude = ContactFreq \times AverageContactQual$
 1. Allport's Conditions

### 2021-10-11 Supplemental-Material-B-Annotated-Analysis.Rmd
overall headings h2
worker until key need

@@
 lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
-         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra",
+         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra", "ggpattern",
+         "lme4", "nlme", "jtools",
          "sessioninfo", "tibble", "pander", "devtools", "mada",
-         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", 
+         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", "papaja",
          "stringr", "stringi", "reshape2", "lubridate")
@@
 
-Note.
+<i class="fas fa-exclamation-circle"></i> Note.
 Boxplots display the interquartile range (IQR, center box), and the whiskers extend 1.5*IQR from the lower and upper hinge.
@@
 df <- cbind(df, remergePP);rm(remergePP)
-writeLines("Test whether newly calculate df and old df have the same order:")
-print(table(as.character(df$CC_Calc) == as.character(df$CC)))
-writeLines("If we also add the NAs we get the exact number:")
-print(sum(is.na(df$CC_Calc))+table(as.character(df$CC_Calc) == as.character(df$CC)))
 
@@
 
+```{r newVarsMedical}
+# TBD
+```
+
+# **Worker Sample**
+
+## Data Description
+
+<i class="fas fa-exclamation-triangle"></i> Still in 'scr/workerDescriptive.R'. Needs to be merged with this document.
+
+## Contact Hypothesis
+
+### Interaction Frequency and Outgroup Attitudes
+
+\begin{equation}
+(\#eq:WorkerFreqQualR)
+r_{ContactFrequency, OutgroupAttitudes} \neq 0
+\end{equation}
+
+```{r WorkerFreqAttCor}
+# prepare data
+workerContactFreq <- dtWorker$full %>% 
+  group_by(ExternalReference) %>%
+  summarise(
+    n = n(),
+    SumContactNL = sum(Contact_dum),
+    PercContactNL = SumContactNL/n*100,
+    SumContactNLAll = sum(number),
+    AvAttitude = mean(thermometerDutch_1, na.rm=T)
+  ) %>%
+  mutate(
+    WinSumContactNL = DescTools::Winsorize(SumContactNL),
+    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
+  )
+
+# correlation panel 
+pairs.panels.new(workerContactFreq %>% select(SumContactNL, SumContactNLAll, AvAttitude), 
+                 labels = c("Sum:\nNumer of beeps with Outgroup Contact (NL)", 
+                            "Sum:\nNumber of Outgroup Contacts (NL)", 
+                            "Mean:\nOutgroup Attitudes (NL)"))
+
+# correlation panel with interaction sums winsorized
+pairs.panels.new(workerContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvAttitude), 
+                 labels = c("Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]", 
+                            "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]", 
+                            "Mean:\nOutgroup Attitudes (NL)"))
+```
+
+TL;DR: Neither the number of interactions nor the number of measurement beeps with an interaction are significantly related with the average outgroup attitudes.
+This is to say that within our data participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
+This might be due to the aggregation within the participants or the small sample size of between participant data.
+Nonetheless, the aggregate data does not support the notion that simply having more interactions with an outgroup results in more positive outgroup attitudes.
+
+### Outgroup Attitudes by Interaction Type
+
+\begin{equation}
+(\#eq:WorkerIntTypeQual)
+\mu_{i,0utgroupInteraction} > \mu_{i,IngroupInteraction}  \\
+Attitude = OutgroupInteraction \times NonOutgroupInteraction
+\end{equation}
+
+<div class="alert alert-info alert-dismissible fade in" role="alert">
+  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
+  <i class="fas fa-exclamation-triangle"></i> <b>Note: </b><br/>
+  mean difference alone probably even more stupid than only ignoring nested data, because we drop lots of data unnecessarily.  
+  And only outgroup interaction Yes / No also weird because interaction group includes people who had only an outgroup interaction and those who also had an interaction with a non-outgroup person, and the no outgroup interaction group includes those who had no interaction at all and those who had an interaction with a non-outgroup person (but no outgroup interaction).
+</div>
+
+#### Regression with interaction term
+
+Across participants: impact of different interaction types [probably meaningless because ignores response sets between participants]
+
+```{r workerInteractionTypePlt, fig.height=12}
+workerContactType <- dtWorker$full %>% 
+  group_by(
+    Contact_dum,
+    inNonDutch
+    ) %>%
+  summarise(
+    n = n(),
+    AttitudeM = mean(thermometerDutch_1, na.rm=T),
+    AttitudeSD = sd(thermometerDutch_1, na.rm=T),
+    AttitudeSE = AttitudeSD/sqrt(n),
+    AttitudeLwr = AttitudeM - 1.96*AttitudeSE,
+    AttitudeUpr = AttitudeM + 1.96*AttitudeSE
+  ) %>%
+  ungroup %>%
+  mutate(
+    InteractionType = paste(
+      ifelse(Contact_dum == 1, "Out", "NoOut"),
+      ifelse(inNonDutch == 1, "In", "NoIn"),
+      sep = ", "
+    )
+  )
+
+ggplot(workerContactType, aes(y = AttitudeM, x = as_factor(Contact_dum), fill = as_factor(inNonDutch))) +
+  geom_bar(stat = "identity", 
+                   color = "black", 
+                   position=position_dodge()) +
+  geom_errorbar(aes(ymin=AttitudeM, ymax=AttitudeUpr), width=.2,
+                 position=position_dodge(.9)) +
+  labs(
+    fill = "Non-Outgroup Interaction",
+    x = "Outgroup Interaction",
+    y = "Outgroup Attitude",
+    title = "Outgroup Attitudes by Interaction Type [95% CI]"
+  ) +
+  scale_fill_grey(
+    start = 0.2,
+    end = 0.8
+    ) +
+  scale_y_continuous(
+    limits = c(0, 100),
+    breaks = c(0, 15, 30, 40, 50, 60, 70, 85, 100),
+    labels = c("Very cold or unfavorable feelings 0°", 
+               "Quite cold and unfavorable feelings 15°", 
+               "Fairly cold and unfavorable feelings 30°", 
+               "A bit cold and unfavorable feelings 40°", 
+               "No feeling at all 50°", 
+               "A bit warm and favorable feelings 60°", 
+               "Fairly warm and favorable feelings 70° ", 
+               "Quite warm and favorable feelings 85° ", 
+               "Very warm and favorable feelings 100° ")
+  ) +
+  theme_Publication()
+```
+
+```{r workerInteractionTypeReg}
+# prepare dataframe
+workerInteractionType <- dtWorker$full %>%
+  mutate(
+    OutgroupInteraction = as_factor(Contact_dum),
+    NonOutgroupInteraction = as_factor(inNonDutch)
+  )
+
+# regression
+lmWorkerInteraction <- lm(thermometerDutch_1 ~ OutgroupInteraction * NonOutgroupInteraction, data = workerInteractionType)
+#summary(lmWorkerInteraction)
+# apa_table(
+#   apa_print(lmWorkerInteraction)$table, 
+#   caption = "Regression across all measurement points [ignoring nested data]."
+# )
+
+summ(
+  lmWorkerInteraction,
+  confint = TRUE, 
+  digits = 3,
+  center = TRUE
+     )
+```
+
+TL;DR: While controlling for interactions with non-Dutch people, outgroup attitudes were significantly higher when participants had an interaction with a Dutch person.
+The effect is relatively small (`r format(round(lmWorkerInteraction$coefficients["OutgroupInteractionYes"], 2), nsmall=2)` points on a 0--100 scale).
+More importantly, however, this analysis lumps all ESM beeps from every participants together and ignores that the data is nested within participants.
+
+#### ML Regression with interaction term
+
+##### Unconditional model
+
+make a model with only the data but a random intercept (unconditional model)
+
+\begin{equation}
+(\#eq:WorkerEmptyModel)
+Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r Worker.Null.Model.ML}
+df <- dtWorker$full
+# Create and save Model
+  Null.ML.r = lme4::lmer(thermometerDutch_1~1 + (1|PID),data=df) #use optim if it does not converge
+  Null.ML = lme(thermometerDutch_1~1,random=~1|PID,data=df, control=list(opt="nlmimb")) #use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+  #summary(Null.ML.r) #or with the lme function
+  summ(Null.ML.r, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+  #write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=df),
+  #                  method="boot",nsim=1000, 
+  #                  parallel = "multicore", ncpus = 4, seed = 42),
+  #          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+  v.null <- VarCorr(Null.ML) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+  tau <- as.numeric(v.null[1])
+# and the estimate of (within-group or residual variancel, sigma^2) is:
+  sigma <- as.numeric(v.null[2])
+# The ICC estimate (between/between+within) is:
+  ICC <- (as.numeric(v.null[1])/(as.numeric(v.null[1])+as.numeric(v.null[2])))
+  ICC.Perc <- ((as.numeric(v.null[1])/(as.numeric(v.null[1])+as.numeric(v.null[2]))))*100
+```
+
+ICC $\tau_{00}^2 / (\tau_{00}^2 + \sigma^2)$: The ratio of the between-cluster variance to the total variance is called the Intraclass Correlation.
+It tells you the proportion of the total variance in Y that is accounted for by the clustering.
+(In this case the clustering means clustering observations per participant)
+
+compare the random intercept model to a model without a random intercept (i.e., without levels at all)
+
+```{r Null.Model.GLS}
+# Create and save Model
+  Null.gls <-  gls(thermometerDutch_1~1,data=df, control=list(opt="nlmimb"))
+
+# calculate Deviances manually:
+  Deviance.gls <- logLik(Null.gls)*-2
+  Deviance.null <- logLik(Null.ML)*-2
+
+# Compare the two null models:
+  anova(Null.gls, Null.ML) %>%
+    as.data.frame %>%
+    select(-call) %>%
+    kbl(., 
+        #label = "",
+        caption = "Worker: Model Comparison",
+        format = "html", 
+        linesep = "",
+        booktabs = T,
+        align = rep('c', ncol(.)),
+        digits = 3)  %>%
+  kable_styling(position = "left")
+```
+
+We find that an estimated `r format(round(ICC.Perc, 2), nsmall=2)`% of the variation in Feeling Thermometer scores is explained by between participant differences (clustering by PID).
+This is to say that `r format(round(ICC.Perc, 2), nsmall=2)`% of the variance in any individual report of Attitudes towards the Dutch can be explained by the properties of the individual who provided the rating.
+And we find that including 'participant' as a predictor adds significantly to the model.
+
+##### Add level one predictors
+
+\begin{equation}
+(\#eq:WorkerInteractionTypeModel)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r interactionType}
+# Create and save Model
+  model.int = lme(thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction, random=~1|PID,data=workerInteractionType)
+
+# Get summary with p-values (Satterthwaite's method)
+  summ(lmer(thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction + (1|PID),data=workerInteractionType), 
+       confint = TRUE, digits = 3, center = TRUE)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+  #write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=df), 
+  #                  method="boot",nsim=1000, parallel = "multicore", 
+  #                  ncpus = 4, seed = 42),
+  #          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+  anova(Null.ML, model.int) %>%
+    as.data.frame %>%
+    select(-call) %>%
+    kbl(., 
+        #label = "",
+        caption = "Worker: Model Comparison",
+        format = "html", 
+        linesep = "",
+        booktabs = T,
+        align = rep('c', ncol(.)),
+        digits = 3)  %>%
+  kable_styling(position = "left")
+
+# Save variances
+  v.int <- lme4::VarCorr(model.int)
+
+# The estimate of between-group (or Intercept variance) explained: 
+  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+    v.int.btw <- 1 - (as.numeric(v.int[1])/as.numeric(v.null[1]))
+    v.int.btw.perc <-  (1 - (as.numeric(v.int[1])/as.numeric(v.null[1])))*100
+  # and the estimate of within-group (or residual variancel) explained is:
+    v.int.within <- 1 - (as.numeric(v.int[2])/as.numeric(v.null[2]))
+    v.int.within.perc <- (1 - (as.numeric(v.int[2])/as.numeric(v.null[2])))*100
+```
+
+tl;dr: Interaction with Dutch is great predictor, interactions with non-Dutch is not.
+
+\begin{equation}
+(\#eq:interactionTypeInteractionEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} \times \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r interactionTypeInteraction}
+# Create and save Model
+  model.intX = lme(thermometerDutch_1 ~ OutgroupInteraction * NonOutgroupInteraction, random=~1|PID,data=workerInteractionType)
+
+# Get summary with p-values (Satterthwaite's method)
+  summ(lmer(thermometerDutch_1 ~ OutgroupInteraction * NonOutgroupInteraction + (1|PID),data=workerInteractionType), 
+       confint = TRUE, digits = 3, center = TRUE)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+  #write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=df), 
+  #                  method="boot",nsim=1000, parallel = "multicore", 
+  #                  ncpus = 4, seed = 42),
+  #          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+  anova(model.int, model.intX) %>%
+    as.data.frame %>%
+    select(-call) %>%
+    kbl(., 
+        #label = "",
+        caption = "Worker: Model Comparison",
+        format = "html", 
+        linesep = "",
+        booktabs = T,
+        align = rep('c', ncol(.)),
+        digits = 3)  %>%
+  kable_styling(position = "left")
+
+# Save variances
+  v.intX <- lme4::VarCorr(model.intX)
+
+# The estimate of between-group (or Intercept variance) explained: 
+  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+    v.intX.btw <- 1 - (as.numeric(v.intX[1])/as.numeric(v.int[1]))
+    v.intX.btw.perc <-  (1 - (as.numeric(v.intX[1])/as.numeric(v.int[1])))*100
+  # and the estimate of within-group (or residual variancel) explained is:
+    v.intX.within <- 1 - (as.numeric(v.intX[2])/as.numeric(v.int[2]))
+    v.intX.within.perc <- (1 - (as.numeric(v.intX[2])/as.numeric(v.int[2])))*100
+```
+
+TL;DR: Interaction term does not add anything at all.
+
+##### Check for Random Slopes
+
+\begin{equation}
+(\#eq:RandSlopesEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r RandSlopes}
+# Create and save Model (optimizer needed to reach convergence)
+  model.ran = lme(thermometerDutch_1~
+                         OutgroupInteraction + NonOutgroupInteraction, 
+                         random=~1+OutgroupInteraction+NonOutgroupInteraction|PID,
+                       control=lmeControl(opt='optim'), data=workerInteractionType)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+  summ(model.ran0 <- lmer(thermometerDutch_1 ~
+                           OutgroupInteraction + NonOutgroupInteraction + 
+                           (1+OutgroupInteraction+NonOutgroupInteraction|PID), 
+                         data=workerInteractionType), 
+       confint = TRUE, digits = 3, center = TRUE)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+  #write.csv(confint(model.ran0,
+  #               method="boot",nsim=1000, 
+  #               parallel = "multicore", ncpus = 4, seed = 42),
+  #          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+  anova(model.int, model.ran) %>%
+    as.data.frame %>%
+    select(-call) %>%
+    kbl(., 
+        #label = "",
+        caption = "Worker: Model Comparison",
+        format = "html", 
+        linesep = "",
+        booktabs = T,
+        align = rep('c', ncol(.)),
+        digits = 3)  %>%
+  kable_styling(position = "left")
+
+# Save variances
+  v.ran = lme4::VarCorr(model.ran)
+
+# The estimate of between-group (or Intercept variance) explained: 
+  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+    v.ran.btw <- 1 - (as.numeric(v.ran[1])/as.numeric(v.int[1]))
+    v.ran.btw.perc <-  (1 - (as.numeric(v.ran[1])/as.numeric(v.int[1])))*100
+  # and the estimate of within-group (or residual variancel) explained is:
+    v.ran.within <- 1 - (as.numeric(v.ran[2])/as.numeric(v.int[2]))
+    v.ran.within.perc <- (1 - (as.numeric(v.ran[2])/as.numeric(v.int[2])))*100
+
+# Assumption Checks: 
+  diag = sjPlot::plot_model(model.ran0, type = "diag")
+  grid.arrange(diag[[1]],diag[[2]]$`PID`,diag[[3]],diag[[4]])
+
+# Plot prediction model
+  dat.new = workerInteractionType[,c("thermometerDutch_1","session","PID")]
+  dat.new$measure = predict(model.ran, workerInteractionType, re.form=NA)
+
+  (t.ppt = ggplot(data=dat.new, aes(x=session, y=measure)) + 
+    geom_line(alpha=1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha=1)+
+    facet_wrap(~PID, ncol = 6)+
+    xlab("Time")+
+    ylab("Outgroup Attitudes")+
+    theme_bw())
+  ggsave(filename = "Figures/Development per PPT.png", t.ppt,
+       width = 18, height = 12, dpi = 800, units = "cm", device='png')
+
+  rm(dat.new)
+
+```
+
+TL;DR: Random slopes don't add much for this super simple model.
+
+### Interaction Frequency and Interaction Quality
+
+\begin{equation}
+(\#eq:FreqQual)
+Attitude = ContactFreq \times AverageContactQual
+\end{equation}
+
+```{r WorkerFreqQualCor}
+# prepare data
+workerAvFreQual <- dtWorker$full %>% 
+  group_by(ExternalReference) %>%
+  summarise(
+    n = n(),
+    SumContactNL = sum(Contact_dum),
+    PercContactNL = SumContactNL/n*100,
+    SumContactNLAll = sum(number),
+    AvAttitude = mean(thermometerDutch_1, na.rm = TRUE),
+    AvQuality = mean(quality_overall_1, na.rm = TRUE)
+  ) %>%
+  mutate(
+    WinSumContactNL = DescTools::Winsorize(SumContactNL),
+    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
+  )
+
+# correlation panel 
+pairs.panels.new(workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude), 
+                 labels = c("Sum:\nNumer of beeps with Outgroup Contact (NL)", 
+                            "Sum:\nNumber of Outgroup Contacts (NL)", 
+                            "Mean:\nInteraction Quality",
+                            "Mean:\nOutgroup Attitudes (NL)"))
+
+# correlation panel with interaction sums winsorized
+pairs.panels.new(workerAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude), 
+                 labels = c("Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]", 
+                            "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]", 
+                            "Mean:\nInteraction Quality",
+                            "Mean:\nOutgroup Attitudes (NL)"))
+```
+
+TL;DR: There is a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
+Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
+However, the frequency of intergroup interactions had no meaningfull correlation with either the average interaction quality or average outgroup attitudes.
+
+```{r WorkerFreqQualReg}
+# regression
+lmworkerFreqInt <- lm(AvAttitude ~ SumContactNL * AvQuality, data = workerAvFreQual)
+#summary(lmWorkerInteraction)
+# apa_table(
+#   apa_print(lmworkerFreqInt)$table, 
+#   caption = "Regression across all measurement points [ignoring nested data]."
+# )
+
+summ(
+  lmworkerFreqInt,
+  confint = TRUE, 
+  digits = 3,
+  center = TRUE
+     )
+
+interactions::interact_plot(lmworkerFreqInt, pred = AvQuality, modx = SumContactNL, interval = TRUE, partial.residuals = TRUE)
+
+interactions::johnson_neyman(lmworkerFreqInt, pred = AvQuality, modx = SumContactNL, alpha = .05)
+```
+
+TL;DR: We find that interaction quality is significantly related to higher outgroup attitudes (albeit with a small effect size).
+We also find that in our sample with an increasing number of interactions the positive effect of interaction quality becomes weaker.
+However, note that this is based on data aggregating all within participant nuances and is only the date of 21 people.
+
+## Need Fulfillment
+
+### Need fulfillment and Attitudes
+
+#### random intercept
+
+\begin{equation}
+(\#eq:AttitudeNeedEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+#### check for random slope
+
+\begin{equation}
+(\#eq:AttitudeNeedRandEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+### Need fulfillment and Interaction Quality
+
+#### random intercept
+
+\begin{equation}
+(\#eq:QualityNeedEq)
+InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+#### check for random slope
+
+\begin{equation}
+(\#eq:QualityNeedRandEq)
+InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+### Need fulfillment, Interaction Quality, and Attitudes
+
+#### random intercept
+
+\begin{equation}
+(\#eq:AttitudeQualityNeedEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+#### check for random slope
+
+\begin{equation}
+(\#eq:AttitudeQualityNeedRandEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+#### Compare models
+
+### Check for robustness
+
+#### Interaction Type
+
+##### random intercept
+
+\begin{equation}
+(\#eq:AttitudeNeedInteractionEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+##### check for random slope
+
+\begin{equation}
+(\#eq:AttitudeNeedInteractionRandEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti}  + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+#### Other psychological needs
+
+##### random intercept
+
+\begin{equation}
+(\#eq:AttitudeNeedSdtEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+##### check for random slope
+
+\begin{equation}
+(\#eq:AttitudeNeedSdtRandEq)
+Attitude_{ti} = \\gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+# **Student Sample**
+
+## Contact Hypothesis
+
+## Need Fulfillment
+
+# **Young Medical Professional Sample**
+
+## Contact Hypothesis
+
+## Allport's Conditions
+
+## Need Fulfillment
+
 # **Software Information**  

### 2021-10-14 Supplemental-Material-B-Annotated-Analysis.Rmd
worker att-keyneed added

@@
          "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra", "ggpattern",
-         "lme4", "nlme", "jtools",
+         "lme4", "nlme", "jtools", "gtsummary",
          "sessioninfo", "tibble", "pander", "devtools", "mada",
@@
 
+##### Unconditional model
+
+make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
+
+```{r workerOutPrep}
+# see how large our outgroup interaction subset actually is 
+tbl_cross(workerInteractionType, row=OutgroupInteraction, col=NonOutgroupInteraction, percent="row")
+
+# create outgroup interaction subset
+workerOutgroupInteraction <- workerInteractionType %>%
+  filter(OutgroupInteraction == "Yes")
+```
+
+\begin{equation}
+(\#eq:WorkerOutEmptyModel)
+Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r Worker.Out.Null.Model.ML}
+# Create and save Model
+  Null.Out.ML.r = lme4::lmer(thermometerDutch_1~1 + (1|PID),data=workerOutgroupInteraction) #use optim if it does not converge
+  Null.Out.ML = lme(thermometerDutch_1~1,random=~1|PID, data=workerOutgroupInteraction, control=list(opt="nlmimb")) #use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+  #summary(Null.ML.r) #or with the lme function
+  summ(Null.Out.ML.r, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+  #write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=df),
+  #                  method="boot",nsim=1000, 
+  #                  parallel = "multicore", ncpus = 4, seed = 42),
+  #          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+  v.out.null <- VarCorr(Null.Out.ML) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+  tau <- as.numeric(v.out.null[1])
+# and the estimate of (within-group or residual variancel, sigma^2) is:
+  sigma <- as.numeric(v.out.null[2])
+# The ICC estimate (between/between+within) is:
+  ICC <- (as.numeric(v.out.null[1])/(as.numeric(v.out.null[1])+as.numeric(v.out.null[2])))
+  ICC.Perc <- ((as.numeric(v.out.null[1])/(as.numeric(v.out.null[1])+as.numeric(v.out.null[2]))))*100
+```
+
 #### random intercept
@@
 
+```{r interceptAttKeyNeed}
+# Create and save Model
+  model.keyneed = lme(thermometerDutch_1 ~ keymotive_fulfillemt_1, random=~1|PID,data=workerOutgroupInteraction)
+
+# Get summary with p-values (Satterthwaite's method)
+  summ(lmer(thermometerDutch_1 ~ keymotive_fulfillemt_1 + (1|PID),data=workerOutgroupInteraction), 
+       confint = TRUE, digits = 3, center = TRUE)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+  #write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=df), 
+  #                  method="boot",nsim=1000, parallel = "multicore", 
+  #                  ncpus = 4, seed = 42),
+  #          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+  anova(Null.Out.ML, model.keyneed) %>%
+    as.data.frame %>%
+    select(-call) %>%
+    kbl(., 
+        #label = "",
+        caption = "Worker: Model Comparison",
+        format = "html", 
+        linesep = "",
+        booktabs = T,
+        align = rep('c', ncol(.)),
+        digits = 3)  %>%
+  kable_styling(position = "left")
+
+# Save variances
+  v.keyneed <- lme4::VarCorr(model.keyneed)
+
+# The estimate of between-group (or Intercept variance) explained: 
+  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+    v.keyneed.btw <- 1 - (as.numeric(v.keyneed[1])/as.numeric(v.out.null[1]))
+    v.keyneed.btw.perc <-  (1 - (as.numeric(v.keyneed[1])/as.numeric(v.out.null[1])))*100
+  # and the estimate of within-group (or residual variancel) explained is:
+    v.keyneed.within <- 1 - (as.numeric(v.keyneed[2])/as.numeric(v.out.null[2]))
+    v.keyneed.within.perc <- (1 - (as.numeric(v.keyneed[2])/as.numeric(v.out.null[2])))*100
+```
+
 #### check for random slope
@@
 \end{equation}
+
+```{r slopesAttKeyNeed}
+# Create and save Model (optimizer needed to reach convergence)
+  model.keyneed.ran = lme(thermometerDutch_1~
+                         keymotive_fulfillemt_1, 
+                         random=~1+keymotive_fulfillemt_1|PID,
+                       control=lmeControl(opt='optim'), data=workerOutgroupInteraction)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+  summ(model.keyneed.ran0 <- lmer(thermometerDutch_1 ~
+                           keymotive_fulfillemt_1 + 
+                           (1+keymotive_fulfillemt_1|PID), 
+                         data=workerOutgroupInteraction), 
+       confint = TRUE, digits = 3, center = TRUE)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+  #write.csv(confint(model.ran0,
+  #               method="boot",nsim=1000, 
+  #               parallel = "multicore", ncpus = 4, seed = 42),
+  #          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+  anova(model.keyneed, model.keyneed.ran) %>%
+    as.data.frame %>%
+    select(-call) %>%
+    kbl(., 
+        #label = "",
+        caption = "Worker: Model Comparison",
+        format = "html", 
+        linesep = "",
+        booktabs = T,
+        align = rep('c', ncol(.)),
+        digits = 3)  %>%
+  kable_styling(position = "left")
+
+# Save variances
+  v.keyneed.ran = lme4::VarCorr(model.keyneed.ran)
+
+# The estimate of between-group (or Intercept variance) explained: 
+  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+    v.keyneed.ran.btw <- 1 - (as.numeric(v.keyneed.ran[1])/as.numeric(v.keyneed[1]))
+    v.keyneed.ran.btw.perc <-  (1 - (as.numeric(v.keyneed.ran[1])/as.numeric(v.keyneed[1])))*100
+  # and the estimate of within-group (or residual variancel) explained is:
+    v.keyneed.ran.within <- 1 - (as.numeric(v.keyneed.ran[2])/as.numeric(v.keyneed[2]))
+    v.keyneed.ran.within.perc <- (1 - (as.numeric(v.keyneed.ran[2])/as.numeric(v.keyneed[2])))*100
+
+# Assumption Checks: 
+  diag = sjPlot::plot_model(model.keyneed.ran0, type = "diag")
+  grid.arrange(diag[[1]],diag[[2]]$`PID`,diag[[3]],diag[[4]])
+
+# Plot prediction model
+  dat.new = workerOutgroupInteraction[,c("thermometerDutch_1","session","PID")]
+  dat.new$measure = predict(model.keyneed.ran, workerOutgroupInteraction, re.form=NA)
+
+  (t.ppt = ggplot(data=dat.new, aes(x=session, y=measure)) + 
+    geom_line(alpha=1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha=1)+
+    facet_wrap(~PID, ncol = 6)+
+    xlab("Time")+
+    ylab("Outgroup Attitudes")+
+    theme_bw())
+  ggsave(filename = "Figures/Development per PPT Out Keyneed.png", t.ppt,
+       width = 18, height = 12, dpi = 800, units = "cm", device='png')
+
+  rm(dat.new)
+
+```
 

### 2021-10-14 Supplemental-Material-B-Annotated-Analysis.Rmd
worker qual keyneed random intercept added

@@
 
-#### check for random slope
+#### random slope
 
@@
 
+##### Unconditional model
+
+make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
+
+\begin{equation}
+(\#eq:WorkerOutQualEmptyModel)
+Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r workerNullQualKeyNeed}
+# Create and save Model
+  Null.Out.Qual.ML.r = lme4::lmer(quality_overall_1~1 + (1|PID),data=workerOutgroupInteraction) #use optim if it does not converge
+  Null.Out.Qual.ML = lme(quality_overall_1~1,random=~1|PID, data=workerOutgroupInteraction, control=list(opt="nlmimb")) #use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+  #summary(Null.ML.r) #or with the lme function
+  summ(Null.Out.Qual.ML.r, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+  #write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=df),
+  #                  method="boot",nsim=1000, 
+  #                  parallel = "multicore", ncpus = 4, seed = 42),
+  #          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+  v.out.qual.null <- VarCorr(Null.Out.Qual.ML) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+  tau <- as.numeric(v.out.qual.null[1])
+# and the estimate of (within-group or residual variancel, sigma^2) is:
+  sigma <- as.numeric(v.out.qual.null[2])
+# The ICC estimate (between/between+within) is:
+  ICC <- (as.numeric(v.out.qual.null[1])/(as.numeric(v.out.qual.null[1])+as.numeric(v.out.qual.null[2])))
+  ICC.Perc <- ((as.numeric(v.out.qual.null[1])/(as.numeric(v.out.qual.null[1])+as.numeric(v.out.qual.null[2]))))*100
+```
+
 #### random intercept
@@
 
-#### check for random slope
+```{r workerInterceptQualKeyNeed}
+# Create and save Model
+  model.qual.keyneed = lme(quality_overall_1 ~ keymotive_fulfillemt_1, random=~1|PID,data=workerOutgroupInteraction)
+
+# Get summary with p-values (Satterthwaite's method)
+  summ(lmer(quality_overall_1 ~ keymotive_fulfillemt_1 + (1|PID),data=workerOutgroupInteraction), 
+       confint = TRUE, digits = 3, center = TRUE)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+  #write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=df), 
+  #                  method="boot",nsim=1000, parallel = "multicore", 
+  #                  ncpus = 4, seed = 42),
+  #          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+  anova(Null.Out.Qual.ML, model.qual.keyneed) %>%
+    as.data.frame %>%
+    select(-call) %>%
+    kbl(., 
+        #label = "",
+        caption = "Worker: Model Comparison",
+        format = "html", 
+        linesep = "",
+        booktabs = T,
+        align = rep('c', ncol(.)),
+        digits = 3)  %>%
+  kable_styling(position = "left")
+
+# Save variances
+  v.qual.keyneed <- lme4::VarCorr(model.qual.keyneed)
+
+# The estimate of between-group (or Intercept variance) explained: 
+  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+    v.qual.keyneed.btw <- 1 - (as.numeric(v.qual.keyneed[1])/as.numeric(v.out.qual.null[1]))
+    v.qual.keyneed.btw.perc <-  (1 - (as.numeric(v.qual.keyneed[1])/as.numeric(v.out.qual.null[1])))*100
+  # and the estimate of within-group (or residual variancel) explained is:
+    v.qual.keyneed.within <- 1 - (as.numeric(v.qual.keyneed[2])/as.numeric(v.out.qual.null[2]))
+    v.qual.keyneed.within.perc <- (1 - (as.numeric(v.qual.keyneed[2])/as.numeric(v.out.qual.null[2])))*100
+```
+
+#### random slope
 

### 2021-10-14 Supplemental-Material-B-Annotated-Analysis.Rmd
worker qual keyneed added. +tl;dr added

@@
 
+TL;DR: Situational core need relates significantly to outgroup addititudes.
+The core need has little explained variance between participants (compared to the null model: Variance Explained = 1 – (Var with Predictor/Var without Predictor); `r format(round(v.keyneed.btw.perc, 2),nsmall=2)`%).
+The variance explained within participants is small to medium (`r format(round(v.keyneed.within.perc, 2),nsmall=2)`%)
+
 #### random slope
@@
 
+TL;DR: The random slope adds significantly to the prediction model.
+
+<div class="alert alert-warning alert-dismissible fade in" role="alert">
+  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
+  <i class="fas fa-exclamation-triangle"></i> <b>Check needed: </b><br/>
+  Something is with the variances explained (between = `r format(round(v.keyneed.ran.btw.perc, 2),nsmall=2)`%, within = `r format(round(v.keyneed.ran.within.perc, 2),nsmall=2)`%).
+This is when comparing the random intercepts to the random slopes model.
+</div>
+
 ### Need fulfillment and Interaction Quality
@@
 
+TL;DR: Situational core need relates significantly to interaction quality.
+The core need explained substantial variance between participants (`r format(round(v.qual.keyneed.btw.perc, 2),nsmall=2)`%).
+The variance explained within participants is also medium (`r format(round(v.qual.keyneed.within.perc, 2),nsmall=2)`%)
+
 #### random slope
@@
 \end{equation}
+
+```{r slopesQualKeyNeed}
+# Create and save Model (optimizer needed to reach convergence)
+  model.qual.keyneed.ran = lme(quality_overall_1~
+                         keymotive_fulfillemt_1, 
+                         random=~1+keymotive_fulfillemt_1|PID,
+                       control=lmeControl(opt='optim'), data=workerOutgroupInteraction)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+  summ(model.qual.keyneed.ran0 <- lmer(quality_overall_1 ~
+                           keymotive_fulfillemt_1 + 
+                           (1+keymotive_fulfillemt_1|PID), 
+                         data=workerOutgroupInteraction), 
+       confint = TRUE, digits = 3, center = TRUE)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+  #write.csv(confint(model.ran0,
+  #               method="boot",nsim=1000, 
+  #               parallel = "multicore", ncpus = 4, seed = 42),
+  #          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+  anova(model.qual.keyneed, model.qual.keyneed.ran) %>%
+    as.data.frame %>%
+    select(-call) %>%
+    kbl(., 
+        #label = "",
+        caption = "Worker: Model Comparison",
+        format = "html", 
+        linesep = "",
+        booktabs = T,
+        align = rep('c', ncol(.)),
+        digits = 3)  %>%
+  kable_styling(position = "left")
+
+# Save variances
+  v.qual.keyneed.ran = lme4::VarCorr(model.qual.keyneed.ran)
+
+# The estimate of between-group (or Intercept variance) explained: 
+  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+    v.qual.keyneed.ran.btw <- 1 - (as.numeric(v.qual.keyneed.ran[1])/as.numeric(v.qual.keyneed[1]))
+    v.qual.keyneed.ran.btw.perc <-  (1 - (as.numeric(v.qual.keyneed.ran[1])/as.numeric(v.qual.keyneed[1])))*100
+  # and the estimate of within-group (or residual variancel) explained is:
+    v.qual.keyneed.ran.within <- 1 - (as.numeric(v.qual.keyneed.ran[2])/as.numeric(v.qual.keyneed[2]))
+    v.qual.keyneed.ran.within.perc <- (1 - (as.numeric(v.qual.keyneed.ran[2])/as.numeric(v.qual.keyneed[2])))*100
+```
+
+TL;DR: random slopes does not add significantly. Stay with simpler model.
 

### 2021-10-17 Supplemental-Material-B-Annotated-Analysis.Rmd
clean up

--- 2021-10-14 Supplemental-Material-B-Annotated-Analysis.Rmd
@@
 cat("\014") # clear console
-  #rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
+# rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
 gc() # garbage collector
@@
 # to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
-lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
-         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra", "ggpattern",
-         "lme4", "nlme", "jtools", "gtsummary",
-         "sessioninfo", "tibble", "pander", "devtools", "mada",
-         "data.table", "plyr", "dplyr", "tidyr", "Hmisc", "kableExtra", "papaja",
-         "stringr", "stringi", "reshape2", "lubridate")
+lib <- c(
+  "rmarkdown",
+  "knitr",
+  "remedy",
+  "bookdown",
+  "brms",
+  "psych",
+  "ggplot2",
+  "ggthemes",
+  "haven",
+  "RColorBrewer",
+  "plotly",
+  "gridExtra",
+  "ggpattern",
+  "lme4",
+  "nlme",
+  "jtools",
+  "gtsummary",
+  "sessioninfo",
+  "tibble",
+  "pander",
+  "devtools",
+  "mada",
+  "data.table",
+  "plyr",
+  "dplyr",
+  "tidyr",
+  "Hmisc",
+  "kableExtra",
+  "papaja",
+  "stringr",
+  "stringi",
+  "reshape2",
+  "lubridate"
+)
 invisible(lapply(lib, library, character.only = TRUE))
@@
 knitr::opts_knit$get("root.dir") # check working directory
-  options(scipen = 999, digits = 4, width = 400) #removes scientific quotation
-  #knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
+options(
+  scipen = 999,
+  digits = 4,
+  width = 400
+) # removes scientific quotation
+# knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
 knitr::knit_hooks$set(
@@
     paste('\n\n<div class="alert alert-danger">',
-           gsub('##', '\n', gsub('^##\ Error', '**Error**', x)),
-           '</div>', sep = '\n')
+      gsub("##", "\n", gsub("^##\ Error", "**Error**", x)),
+      "</div>",
+      sep = "\n"
+    )
   },
@@
     paste('\n\n<div class="alert alert-warning">',
-           gsub('##', '\n', gsub('^##\ Warning:', '**Warning**', x)),
-           '</div>', sep = '\n')
+      gsub("##", "\n", gsub("^##\ Warning:", "**Warning**", x)),
+      "</div>",
+      sep = "\n"
+    )
   },
@@
     paste('\n\n<div class="alert alert-info">',
-           gsub('##', '\n', x),
-           '</div>', sep = '\n')
+      gsub("##", "\n", x),
+      "</div>",
+      sep = "\n"
+    )
   }
@@
 # Global Chunk Options
-  knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figures/',
-                        echo=TRUE, warning=FALSE, message=FALSE)
+knitr::opts_chunk$set(
+  fig.width = 12,
+  fig.height = 8,
+  fig.path = "Figures/",
+  echo = TRUE,
+  warning = FALSE,
+  message = FALSE
+)
 ```
@@
 )
-
 ```
@@
 df <- dtWorker$combined %>%
-    filter(Finished.pre == 1,
+  filter(
+    Finished.pre == 1,
     Finished.daily == 1,
-           !is.na(ExternalReference))
+    !is.na(ExternalReference)
+  )
 
 # add running number as measurement ID within participants
-  df$measureID = rowidv(df, cols = c("ExternalReference"))
+df$measureID <- rowidv(df, cols = c("ExternalReference"))
 
@@
   mutate(
-      PID = as.numeric(factor(ExternalReference)), # participant ID
-      TID = measureID-1, # time ID with t0 = 0 for meaningfull intercept interpretations
-      date = substr(StartDate,1,10), # awkward way of extracting date (best converted to )
-      time = substr(StartDate,12,19), # awkward way of extracting time
-      daynum = as.numeric(factor(date)), # all days as numeric for ordering
-      daycor = ifelse(daytime=="morning" & period_to_seconds(hms(time))<period_to_seconds(hms("12:00:00")) | daytime=="afternoon" & period_to_seconds(hms(time))<period_to_seconds(hms("19:00:00")),daynum-1,daynum), # correctly identify which date the questionnaire is about
+    PID = as.numeric(factor(ExternalReference)),
+    # participant ID
+    TID = measureID - 1,
+    # time ID with t0 = 0 for meaningfull intercept interpretations
+    date = substr(StartDate, 1, 10),
+    # awkward way of extracting date (best converted to )
+    time = substr(StartDate, 12, 19),
+    # awkward way of extracting time
+    daynum = as.numeric(factor(date)),
+    # all days as numeric for ordering
+    daycor = ifelse(
+      daytime == "morning" &
+        period_to_seconds(hms(time)) < period_to_seconds(hms("12:00:00")) |
+        daytime == "afternoon" &
+          period_to_seconds(hms(time)) < period_to_seconds(hms("19:00:00")),
+      daynum - 1,
+      daynum
+    ),
+    # correctly identify which date the questionnaire is about
     daycor.lead = sprintf("%02d", daycor),
-      daytime.lt = ifelse(daytime=="morning","a","b"), # morning / afternoon to a / b 
-      day_time = paste(daycor.lead, daytime.lt, sep="_"), # combine day id with morning / afternoon
-      session = as.numeric(factor(day_time)), # day and time identifier as numeric id
+    daytime.lt = ifelse(daytime == "morning", "a", "b"),
+    # morning / afternoon to a / b
+    day_time = paste(daycor.lead, daytime.lt, sep = "_"),
+    # combine day id with morning / afternoon
+    session = as.numeric(factor(day_time)),
+    # day and time identifier as numeric id
     SubTime = chron::times(time.0),
@@
 # Export reduced Data
-  #write.csv(dtWorker$clean, "data/processed/MT_clean-merged_07-05-2018.csv", row.names = F)
-  #save(dtWorker$clean, file = "data/processed/MT_clean-merged_07-05-2018.RData")
+# write.csv(dtWorker$clean, "data/processed/MT_clean-merged_07-05-2018.csv", row.names = F)
+# save(dtWorker$clean, file = "data/processed/MT_clean-merged_07-05-2018.RData")
 ```
@@
 df.pre <- dtStudents$raw.pre %>%
-  mutate_all(na_if,"") %>%
-  mutate_all(na_if,"NA") %>%
+  mutate_all(na_if, "") %>%
+  mutate_all(na_if, "NA") %>%
   filter(!is.na(ended)) %>% # remove all who did not finish
@@
 df.post <- dtStudents$raw.post %>%
-  mutate_all(na_if,"") %>%
-  mutate_all(na_if,"NA") %>%
+  mutate_all(na_if, "") %>%
+  mutate_all(na_if, "NA") %>%
   filter(!is.na(session)) %>% # remove own test runs
@@
 df.daily <- dtStudents$raw.daily %>%
-  mutate_all(na_if,"") %>%
-  mutate_all(na_if,"NA") %>%
+  mutate_all(na_if, "") %>%
+  mutate_all(na_if, "NA") %>%
   filter(!session %in% ownIDs) %>% # remove our own test
@@
 # merge daily with pre
-dfPreDaily = merge(
+dfPreDaily <- merge(
   x = df.daily,
@@
 # merge daily with post
-dfCombined = merge(
+dfCombined <- merge(
   x = dfPreDaily,
@@
 ```{r cleanMedical}
-#TBD
+# TBD
 ```
@@
 # remove seconds from afternoon time
-  df$SubTime[df$daytime == "afternoon"] = paste0(substring(as.character(df$time.0[df$daytime == "afternoon"]),4,8),":00") 
-  df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")] = paste0(substring(as.character(df$time.daily[df$daytime == "afternoon" & !is.na(df$time.daily!="<NA>")]),4,8),":00")
+df$SubTime[df$daytime == "afternoon"] <- paste0(substring(as.character(df$time.0[df$daytime == "afternoon"]), 4, 8), ":00")
+df$time.daily[df$daytime == "afternoon" &
+  !is.na(df$time.daily != "<NA>")] <- paste0(substring(as.character(df$time.daily[df$daytime == "afternoon" &
+  !is.na(df$time.daily != "<NA>")]), 4, 8), ":00")
 
 # Correct morning / afternoon date where survey was collected the day after to indicate the correct date that was targeted
-  df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"] = df$PPDate[df$SubTime < "11:50:00" & df$daytime == "morning"]-1
-  df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"] = df$PPDate[df$SubTime < "18:50:00" & df$daytime == "afternoon"]-1
+df$PPDate[df$SubTime < "11:50:00" &
+  df$daytime == "morning"] <- df$PPDate[df$SubTime < "11:50:00" &
+  df$daytime == "morning"] - 1
+df$PPDate[df$SubTime < "18:50:00" &
+  df$daytime == "afternoon"] <- df$PPDate[df$SubTime < "18:50:00" &
+  df$daytime == "afternoon"] - 1
 
 # Mood scales
-  df$calmness.daily = rowSums(df[, c("calmness1", "calmness2")], na.rm = T)
-  df$alertness.daily = rowSums(df[, c("alertness1", "alertness2")], na.rm =T)
-  df$valence.daily = rowSums(df[, c("valence1", "valence2")], na.rm = T)
+df$calmness.daily <- rowSums(df[, c("calmness1", "calmness2")], na.rm = T)
+df$alertness.daily <- rowSums(df[, c("alertness1", "alertness2")], na.rm = T)
+df$valence.daily <- rowSums(df[, c("valence1", "valence2")], na.rm = T)
 
 # Need scales
-  df$keyMotiveFulfilled = rowSums(df[,c("keymotive_fulfillemt_1","keyMotive_noInt_fulf_1")], na.rm=T)
-  df$autonomy.daily.all = rowSums(df[,c("autonomy_1","autonomy_NoInt_1")], na.rm=T)
-  df$competence.daily.all = rowSums(df[,c("competence_1","competence_NoInt_1")], na.rm=T)
-  #cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
-  df$relatedness.daily.all = rowMeans(df[,c("relatedness_other_1","relatedness_self_1","relatedness_1_NoInt_1")], na.rm=T)
-  df$relatedness.daily.int = rowMeans(df[,c("relatedness_other_1","relatedness_self_1")], na.rm=T)
+df$keyMotiveFulfilled <- rowSums(df[, c("keymotive_fulfillemt_1", "keyMotive_noInt_fulf_1")], na.rm = T)
+df$autonomy.daily.all <- rowSums(df[, c("autonomy_1", "autonomy_NoInt_1")], na.rm = T)
+df$competence.daily.all <- rowSums(df[, c("competence_1", "competence_NoInt_1")], na.rm = T)
+# cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
+df$relatedness.daily.all <- rowMeans(df[, c(
+  "relatedness_other_1",
+  "relatedness_self_1",
+  "relatedness_1_NoInt_1"
+)], na.rm = T)
+df$relatedness.daily.int <- rowMeans(df[, c("relatedness_other_1", "relatedness_self_1")], na.rm = T)
 
@@
     CtContactNonNlAll = sum(NonDutchNum),
-      AvKeyNeed = mean(keyMotiveFulfilled, na.rm=T),
-      AvKeyNeedInt = mean(keymotive_fulfillemt_1, na.rm=T),
-      AvKeyNeedNoInt = mean(keyMotive_noInt_fulf_1, na.rm=T),
-      AvAutonomy = mean(autonomy.daily.all, na.rm=T),
-      AvCompetence = mean(competence.daily.all, na.rm=T),
-      AvRelatedness = mean(relatedness.daily.all, na.rm=T),
-      AvThermo = mean(thermometerDutch_1, na.rm=T),
-      AvWB = mean(ExWB_1, na.rm=T)) %>%
+    AvKeyNeed = mean(keyMotiveFulfilled, na.rm = T),
+    AvKeyNeedInt = mean(keymotive_fulfillemt_1, na.rm = T),
+    AvKeyNeedNoInt = mean(keyMotive_noInt_fulf_1, na.rm = T),
+    AvAutonomy = mean(autonomy.daily.all, na.rm = T),
+    AvCompetence = mean(competence.daily.all, na.rm = T),
+    AvRelatedness = mean(relatedness.daily.all, na.rm = T),
+    AvThermo = mean(thermometerDutch_1, na.rm = T),
+    AvWB = mean(ExWB_1, na.rm = T)
+  ) %>%
   ungroup() %>%
@@
 
-  warning("some variable transformations (esp. _c and _z) might be across all participants (i.e., not within PP).")
+warning(
+  "some variable transformations (esp. _c and _z) might be across all participants (i.e., not within PP)."
+)
 
 dtWorker$full <- between
-
 rm(df, between)
 
-  #save(df.btw, file = "data/processed/df.btw.RData")  
-  #write_sav(df.btw, "data/processed/MT_clean-merged_pre-post.sav")
+# Between participants contact frequency
+workerContactFreq <- dtWorker$full %>%
+  group_by(ExternalReference) %>%
+  summarise(
+    n = n(),
+    SumContactNL = sum(Contact_dum),
+    PercContactNL = SumContactNL / n * 100,
+    SumContactNLAll = sum(number),
+    AvAttitude = mean(thermometerDutch_1, na.rm = T)
+  ) %>%
+  mutate(
+    WinSumContactNL = DescTools::Winsorize(SumContactNL),
+    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
+  )
+
+# dataframe where interaction types are recoded
+workerInteractionType <- dtWorker$full %>%
+  mutate(
+    OutgroupInteraction = as_factor(Contact_dum),
+    NonOutgroupInteraction = as_factor(inNonDutch)
+  )
+
+# save cleaned data
+# save(df.btw, file = "data/processed/df.btw.RData")
+# write_sav(df.btw, "data/processed/MT_clean-merged_pre-post.sav")
 
 # export data to Mplus
-  # df.mplus = remove_all_labels(select(df, PID, session, thermometerDutch_1, inNonDutch, Contact_dum, keyMotiveFulfilled, autonomy.daily.all, competence.daily.all, relatedness.daily.all))
+# df.mplus = remove_all_labels(select(df,
+#                                     PID, session,
+#                                     thermometerDutch_1, inNonDutch, Contact_dum,
+#                                     keyMotiveFulfilled, autonomy.daily.all, competence.daily.all, relatedness.daily.all))
 # names(df.mplus)= c("PID", "session", "att", "intin", "intout", "keymot", "aut", "comp", "rel")
@@
 # prepareMplusData(mplus.intcont, "data/processed/dynamic-subset-intonly.dat")
-
 ```
@@
 # Add ID variables
-  df$PID = as.numeric(factor(df$session)) # participant ID
+df$PID <- as.numeric(factor(df$session)) # participant ID
 
 # order time
-  df$TID <- factor(df$date_period, levels = unique(dtStudents$raw.daily$date_period))
-  df$TIDnum <- as.numeric(df$TID) #get numeric TID
+df$TID <-
+  factor(df$date_period, levels = unique(dtStudents$raw.daily$date_period))
+df$TIDnum <- as.numeric(df$TID) # get numeric TID
 
@@
 df <- df %>%
-    arrange(PID, TID) #%>%
-    #View()
+  arrange(PID, TID) # %>%
+# View()
 
 # Interaction as Factor
-  df$interaction.f <- factor(df$Interaction, levels = c("no interaction", "Dutch", "Non-Dutch"))
-  df$intNL <- ifelse(df$Interaction=="Dutch",1,0)
-  df$intNonNL<- ifelse(df$Interaction=="Non-Dutch",1,0)
+df$interaction.f <-
+  factor(df$Interaction,
+    levels = c("no interaction", "Dutch", "Non-Dutch")
+  )
+df$intNL <- ifelse(df$Interaction == "Dutch", 1, 0)
+df$intNonNL <- ifelse(df$Interaction == "Non-Dutch", 1, 0)
 
@@
 # Relatedness
-  pairs.panels.new(df[c("RelatednessSelf","RelatednessOther")], 
-                              labels = c("I shared information about myself.", "X shared information about themselves."))
-  df$RelatednessInteraction <- rowMeans(df[c("RelatednessSelf","RelatednessOther")], na.rm=T)
-  df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <- NA
+pairs.panels.new(
+  df[c("RelatednessSelf", "RelatednessOther")],
+  labels = c(
+    "I shared information about myself.",
+    "X shared information about themselves."
+  )
+)
+df$RelatednessInteraction <-
+  rowMeans(df[c("RelatednessSelf", "RelatednessOther")], na.rm = T)
+df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <-
+  NA
 # Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
-  df$Relatedness <- rowMeans(df[,c("RelatednessInteraction", "RelatednessNoInteraction")], na.rm=T)
+df$Relatedness <-
+  rowMeans(df[, c("RelatednessInteraction", "RelatednessNoInteraction")],
+    na.rm =
+      T
+  )
 # Pro-Sociality
-  df$ProSo <- rowMeans(df[,c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm=T)
+df$ProSo <-
+  rowMeans(df[, c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm = T)
 # Anti-Sociality
-  df$AntiSo <- rowMeans(df[,c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm=T)
+df$AntiSo <-
+  rowMeans(df[, c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm = T)
 
@@
 createIntPartDf <- function(inp) {
-
   # prepare the dataframe so that we can forloop over it later
-    tmp <- data.frame(CC = as.character(inp$CC),
+  tmp <- data.frame(
+    CC = as.character(inp$CC),
     NewCC = as.character(inp$NewCC),
@@
     NewEthnicity = as.character(inp$NewEthnicity),
-                    NewRelationship = as.character(inp$NewRelationship))
-
-    tmp$CC2 <- recode(tmp$CC, 'SOMEONE ELSE' = "NA")
-    tmp$CC2 <- ifelse(tmp$CC == 1 | tmp$CC == "SOMEONE ELSE", as.character(tmp$NewName), as.character(tmp$CC2)) 
+    NewRelationship = as.character(inp$NewRelationship)
+  )
+
+  tmp$CC2 <- recode(tmp$CC, "SOMEONE ELSE" = "NA")
+  tmp$CC2 <-
+    ifelse(
+      tmp$CC == 1 |
+        tmp$CC == "SOMEONE ELSE",
+      as.character(tmp$NewName),
+      as.character(tmp$CC2)
+    )
   # maybe add [[:space:]]\b to remove space before word boundary or ^[[:space:]] to remove space in the beginning of a string
@@
     } else {
-           tmp$closeness[i] <- na.omit(tmp$NewCloseness[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] #find closeness where CC2 matches NewName (na.omit + [1] to get the number)
-           tmp$gender[i] <- na.omit(tmp$NewGender[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] #(na.omit + [1] to get the number and not the rest of the na.omit list)
-           tmp$ethnicity[i] <- na.omit(as.character(tmp$NewEthnicity[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1] #PROBLEM IS THAT THERE ARE TOO MANY NA's: Difficult to deal with
-           tmp$relationship[i] <- na.omit(as.character(tmp$NewRelationship[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1]
+      tmp$closeness[i] <-
+        na.omit(tmp$NewCloseness[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] # find closeness where CC2 matches NewName (na.omit + [1] to get the number)
+      tmp$gender[i] <-
+        na.omit(tmp$NewGender[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] # (na.omit + [1] to get the number and not the rest of the na.omit list)
+      tmp$ethnicity[i] <-
+        na.omit(as.character(tmp$NewEthnicity[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1] # PROBLEM IS THAT THERE ARE TOO MANY NA's: Difficult to deal with
+      tmp$relationship[i] <-
+        na.omit(as.character(tmp$NewRelationship[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1]
     }
@@
 PP <- split(df, df$PID)
-  PP <- lapply(PP, createIntPartDf); rm(createIntPartDf)
+PP <- lapply(PP, createIntPartDf)
+rm(createIntPartDf)
 
@@
 remergePP <- do.call(rbind.data.frame, PP)
-    colnames(remergePP) <- paste(colnames(remergePP), "_Calc", sep = "")
-df <- cbind(df, remergePP);rm(remergePP)
+colnames(remergePP) <-
+  paste(colnames(remergePP), "_Calc", sep = "")
+df <- cbind(df, remergePP)
+rm(remergePP, PP)
 
@@
   mutate(
-    KeyNeedFullfillment.cm = mean(KeyNeedFullfillment, na.rm = TRUE), # cluster mean (mean of PP)
-    KeyNeedFullfillment.cwc = KeyNeedFullfillment - KeyNeedFullfillment.cm, # cluster mean centered (within PP centered)
+    KeyNeedFullfillment.cm = mean(KeyNeedFullfillment, na.rm = TRUE),
+    # cluster mean (mean of PP)
+    KeyNeedFullfillment.cwc = KeyNeedFullfillment - KeyNeedFullfillment.cm,
+    # cluster mean centered (within PP centered)
     closeness.cm = mean(closeness_Calc, na.rm = TRUE),
@@
 # store
-  dtStudents$full = df
+dtStudents$full <- df
+rm(df)
 ```
@@
 ```{r WorkerFreqAttCor}
-# prepare data
-workerContactFreq <- dtWorker$full %>% 
-  group_by(ExternalReference) %>%
-  summarise(
-    n = n(),
-    SumContactNL = sum(Contact_dum),
-    PercContactNL = SumContactNL/n*100,
-    SumContactNLAll = sum(number),
-    AvAttitude = mean(thermometerDutch_1, na.rm=T)
-  ) %>%
-  mutate(
-    WinSumContactNL = DescTools::Winsorize(SumContactNL),
-    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
-  )
-
 # correlation panel
-pairs.panels.new(workerContactFreq %>% select(SumContactNL, SumContactNLAll, AvAttitude), 
-                 labels = c("Sum:\nNumer of beeps with Outgroup Contact (NL)", 
+pairs.panels.new(
+  workerContactFreq %>% select(SumContactNL, SumContactNLAll, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
     "Sum:\nNumber of Outgroup Contacts (NL)",
-                            "Mean:\nOutgroup Attitudes (NL)"))
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
 
 # correlation panel with interaction sums winsorized
-pairs.panels.new(workerContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvAttitude), 
-                 labels = c("Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]", 
+pairs.panels.new(
+  workerContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
     "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
-                            "Mean:\nOutgroup Attitudes (NL)"))
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
 ```
@@
 ```{r workerInteractionTypePlt, fig.height=12}
+# between participants interaction type
 workerContactType <- dtWorker$full %>%
@@
     n = n(),
-    AttitudeM = mean(thermometerDutch_1, na.rm=T),
-    AttitudeSD = sd(thermometerDutch_1, na.rm=T),
-    AttitudeSE = AttitudeSD/sqrt(n),
-    AttitudeLwr = AttitudeM - 1.96*AttitudeSE,
-    AttitudeUpr = AttitudeM + 1.96*AttitudeSE
+    AttitudeM = mean(thermometerDutch_1, na.rm = T),
+    AttitudeSD = sd(thermometerDutch_1, na.rm = T),
+    AttitudeSE = AttitudeSD / sqrt(n),
+    AttitudeLwr = AttitudeM - 1.96 * AttitudeSE,
+    AttitudeUpr = AttitudeM + 1.96 * AttitudeSE
   ) %>%
-  ungroup %>%
-  mutate(
-    InteractionType = paste(
+  ungroup() %>%
+  mutate(InteractionType = paste(
     ifelse(Contact_dum == 1, "Out", "NoOut"),
@@
     sep = ", "
-    )
-  )
-
-ggplot(workerContactType, aes(y = AttitudeM, x = as_factor(Contact_dum), fill = as_factor(inNonDutch))) +
-  geom_bar(stat = "identity", 
+  ))
+
+# plot bar chart
+ggplot(
+  workerContactType,
+  aes(
+    y = AttitudeM,
+    x = as_factor(Contact_dum),
+    fill = as_factor(inNonDutch)
+  )
+) +
+  geom_bar(
+    stat = "identity",
     color = "black",
-                   position=position_dodge()) +
-  geom_errorbar(aes(ymin=AttitudeM, ymax=AttitudeUpr), width=.2,
-                 position=position_dodge(.9)) +
+    position = position_dodge()
+  ) +
+  geom_errorbar(aes(ymin = AttitudeM, ymax = AttitudeUpr),
+    width = .2,
+    position = position_dodge(.9)
+  ) +
   labs(
@@
     breaks = c(0, 15, 30, 40, 50, 60, 70, 85, 100),
-    labels = c("Very cold or unfavorable feelings 0°", 
+    labels = c(
+      "Very cold or unfavorable feelings 0°",
       "Quite cold and unfavorable feelings 15°",
@@
       "Quite warm and favorable feelings 85° ",
-               "Very warm and favorable feelings 100° ")
+      "Very warm and favorable feelings 100° "
+    )
   ) +
@@
 
-```{r workerInteractionTypeReg}
-# prepare dataframe
-workerInteractionType <- dtWorker$full %>%
-  mutate(
-    OutgroupInteraction = as_factor(Contact_dum),
-    NonOutgroupInteraction = as_factor(inNonDutch)
-  )
+```{r workerModelOlsInteractionType}
+# create list to store Worker models
+mdlWorker <- list()
 
 # regression
-lmWorkerInteraction <- lm(thermometerDutch_1 ~ OutgroupInteraction * NonOutgroupInteraction, data = workerInteractionType)
-#summary(lmWorkerInteraction)
-# apa_table(
-#   apa_print(lmWorkerInteraction)$table, 
-#   caption = "Regression across all measurement points [ignoring nested data]."
-# )
+mdlWorker$lmAttInt <-
+  lm(thermometerDutch_1 ~ OutgroupInteraction * NonOutgroupInteraction,
+    data = workerInteractionType
+  )
+# summary(lmWorkerAttInteraction)
 
 summ(
-  lmWorkerInteraction,
+  mdlWorker$lmAttInt,
   confint = TRUE,
@@
 TL;DR: While controlling for interactions with non-Dutch people, outgroup attitudes were significantly higher when participants had an interaction with a Dutch person.
-The effect is relatively small (`r format(round(lmWorkerInteraction$coefficients["OutgroupInteractionYes"], 2), nsmall=2)` points on a 0--100 scale).
+The effect is relatively small (`r format(round(mdlWorker$lmAttInt$coefficients["OutgroupInteractionYes"], 2), nsmall=2)` points on a 0--100 scale).
 More importantly, however, this analysis lumps all ESM beeps from every participants together and ignores that the data is nested within participants.
@@
 
-```{r Worker.Null.Model.ML}
-df <- dtWorker$full
+```{r workerModelMLAttNull}
 # Create and save Model
-  Null.ML.r = lme4::lmer(thermometerDutch_1~1 + (1|PID),data=df) #use optim if it does not converge
-  Null.ML = lme(thermometerDutch_1~1,random=~1|PID,data=df, control=list(opt="nlmimb")) #use optim if it does not converge
+mdlWorker$lmerAttNull <-
+  lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID),
+    data = dtWorker$full
+  ) # use optim if it does not converge
+
+mdlWorker$lmeAttNull <-
+  lme(
+    thermometerDutch_1 ~ 1,
+    random = ~ 1 | PID,
+    data = dtWorker$full,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
 
 # Get summary with p-values (Satterthwaite's method)
-  #summary(Null.ML.r) #or with the lme function
-  summ(Null.ML.r, digits = 3, center = TRUE)
+# summary(lmerWorkerAttNull) #or with the lme function
+summ(mdlWorker$lmerAttNull, digits = 3, center = TRUE)
 
 # generate 95% parametric bootstrap CIs (and save them as a csv-file):
-  #write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=df),
+# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=dtWorker$full),
 #                  method="boot",nsim=1000,
@@
 # Save variances
-  v.null <- VarCorr(Null.ML) # save variances
+mdlWorker$varAttNull <- 
+  VarCorr(mdlWorker$lmeAttNull) # save variances
 # The estimate of (between-group or Intercept variance, tau_{00}^2):
-  tau <- as.numeric(v.null[1])
-# and the estimate of (within-group or residual variancel, sigma^2) is:
-  sigma <- as.numeric(v.null[2])
+mdlWorker$tauAttNull <- 
+  as.numeric(mdlWorker$varAttNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlWorker$sigmaAttNull <- 
+  as.numeric(mdlWorker$varAttNull[2])
 # The ICC estimate (between/between+within) is:
-  ICC <- (as.numeric(v.null[1])/(as.numeric(v.null[1])+as.numeric(v.null[2])))
-  ICC.Perc <- ((as.numeric(v.null[1])/(as.numeric(v.null[1])+as.numeric(v.null[2]))))*100
+mdlWorker$IccAttNull <-
+  (as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2])))
+mdlWorker$IccPercAttNull <-
+  ((as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2])))) * 100
 ```
@@
 
-```{r Null.Model.GLS}
+```{r workerModelInterceptNull}
 # Create and save Model
-  Null.gls <-  gls(thermometerDutch_1~1,data=df, control=list(opt="nlmimb"))
+mdlWorker$glsAttNull  <-
+  gls(thermometerDutch_1 ~ 1,
+      data = dtWorker$full,
+      control = list(opt = "nlmimb"))
 
 # calculate Deviances manually:
-  Deviance.gls <- logLik(Null.gls)*-2
-  Deviance.null <- logLik(Null.ML)*-2
+mdlWorker$DevianceGlsNull <- logLik(mdlWorker$glsAttNull) * -2
+mdlWorker$DevianceMlNull <- logLik(mdlWorker$lmeAttNull) * -2
 
 # Compare the two null models:
-  anova(Null.gls, Null.ML) %>%
-    as.data.frame %>%
+anova(mdlWorker$glsAttNull,
+      mdlWorker$lmeAttNull) %>% 
+  as.data.frame() %>%
   select(-call) %>%
-    kbl(., 
-        #label = "",
+  kbl(
+    .,
     caption = "Worker: Model Comparison",
@@
     booktabs = T,
-        align = rep('c', ncol(.)),
-        digits = 3)  %>%
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
   kable_styling(position = "left")
@@
 
-We find that an estimated `r format(round(ICC.Perc, 2), nsmall=2)`% of the variation in Feeling Thermometer scores is explained by between participant differences (clustering by PID).
-This is to say that `r format(round(ICC.Perc, 2), nsmall=2)`% of the variance in any individual report of Attitudes towards the Dutch can be explained by the properties of the individual who provided the rating.
+We find that an estimated `r format(round(mdlWorker$IccPercAttNull, 2), nsmall=2)`% of the variation in Feeling Thermometer scores is explained by between participant differences (clustering by PID).
+This is to say that `r format(round(mdlWorker$IccPercAttNull, 2), nsmall=2)`% of the variance in any individual report of Attitudes towards the Dutch can be explained by the properties of the individual who provided the rating.
 And we find that including 'participant' as a predictor adds significantly to the model.
 
-##### Add level one predictors
+##### random intercept
 
@@
 
-```{r interactionType}
+```{r workerModelInterceptAttType}
 # Create and save Model
-  model.int = lme(thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction, random=~1|PID,data=workerInteractionType)
+mdlWorker$lmeInterceptAttType <-
+  lme(
+    thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction,
+    random =  ~ 1 | PID,
+    data = workerInteractionType
+  )
 
 # Get summary with p-values (Satterthwaite's method)
-  summ(lmer(thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction + (1|PID),data=workerInteractionType), 
-       confint = TRUE, digits = 3, center = TRUE)
+summ(
+  lmer(
+    thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    data = workerInteractionType
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
 
 # Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-  #write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=df), 
+# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
 #                  method="boot",nsim=1000, parallel = "multicore",
@@
 # Compare new model to previous step
-  anova(Null.ML, model.int) %>%
-    as.data.frame %>%
+anova(mdlWorker$lmeAttNull, 
+      mdlWorker$lmeInterceptAttType) %>%
+  as.data.frame() %>%
   select(-call) %>%
-    kbl(., 
-        #label = "",
+  kbl(
+    .,
     caption = "Worker: Model Comparison",
@@
 # Save variances
-  v.int <- lme4::VarCorr(model.int)
+mdlWorker$varInterceptAttType <- 
+  lme4::VarCorr(mdlWorker$lmeInterceptAttType)
 
@@
 # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-    v.int.btw <- 1 - (as.numeric(v.int[1])/as.numeric(v.null[1]))
-    v.int.btw.perc <-  (1 - (as.numeric(v.int[1])/as.numeric(v.null[1])))*100
-  # and the estimate of within-group (or residual variancel) explained is:
-    v.int.within <- 1 - (as.numeric(v.int[2])/as.numeric(v.null[2]))
-    v.int.within.perc <- (1 - (as.numeric(v.int[2])/as.numeric(v.null[2])))*100
+mdlWorker$varBtwInterceptAttType <-
+  1 - (as.numeric(mdlWorker$varInterceptAttType[1]) / as.numeric(mdlWorker$varAttNull[1]))
+mdlWorker$varBtwPercInterceptAttType <-
+  (1 - (as.numeric(mdlWorker$varInterceptAttType[1]) / as.numeric(mdlWorker$varAttNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorker$varWithinInterceptAttType <-
+  1 - (as.numeric(mdlWorker$varInterceptAttType[2]) / as.numeric(mdlWorker$varAttNull[2]))
+mdlWorker$varWithinPercInterceptAttType <-
+  (1 - (as.numeric(mdlWorker$varInterceptAttType[2]) / as.numeric(mdlWorker$varAttNull[2]))) * 100
 ```
@@
 
-\begin{equation}
-(\#eq:interactionTypeInteractionEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} \times \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r interactionTypeInteraction}
-# Create and save Model
-  model.intX = lme(thermometerDutch_1 ~ OutgroupInteraction * NonOutgroupInteraction, random=~1|PID,data=workerInteractionType)
-
-# Get summary with p-values (Satterthwaite's method)
-  summ(lmer(thermometerDutch_1 ~ OutgroupInteraction * NonOutgroupInteraction + (1|PID),data=workerInteractionType), 
-       confint = TRUE, digits = 3, center = TRUE)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-  #write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=df), 
-  #                  method="boot",nsim=1000, parallel = "multicore", 
-  #                  ncpus = 4, seed = 42),
-  #          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-  anova(model.int, model.intX) %>%
-    as.data.frame %>%
-    select(-call) %>%
-    kbl(., 
-        #label = "",
-        caption = "Worker: Model Comparison",
-        format = "html", 
-        linesep = "",
-        booktabs = T,
-        align = rep('c', ncol(.)),
-        digits = 3)  %>%
-  kable_styling(position = "left")
-
-# Save variances
-  v.intX <- lme4::VarCorr(model.intX)
-
-# The estimate of between-group (or Intercept variance) explained: 
-  # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-    v.intX.btw <- 1 - (as.numeric(v.intX[1])/as.numeric(v.int[1]))
-    v.intX.btw.perc <-  (1 - (as.numeric(v.intX[1])/as.numeric(v.int[1])))*100
-  # and the estimate of within-group (or residual variancel) explained is:
-    v.intX.within <- 1 - (as.numeric(v.intX[2])/as.numeric(v.int[2]))
-    v.intX.within.perc <- (1 - (as.numeric(v.intX[2])/as.numeric(v.int[2])))*100
-```
-
-TL;DR: Interaction term does not add anything at all.
-
-##### Check for Random Slopes
+##### random slope
 
@@
 
-```{r RandSlopes}
+```{r workerModelSlopesInteractionType}
 # Create and save Model (optimizer needed to reach convergence)
-  model.ran = lme(thermometerDutch_1~
+mdlWorker$lmeSlopesAttType <- lme(
+  thermometerDutch_1 ~
     OutgroupInteraction + NonOutgroupInteraction,
-                         random=~1+OutgroupInteraction+NonOutgroupInteraction|PID,
-                       control=lmeControl(opt='optim'), data=workerInteractionType)
+  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  data = workerInteractionType
+)
 
 # Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-  summ(model.ran0 <- lmer(thermometerDutch_1 ~
+summ(
+  mdlWorker$lmerSlopesAttType <- lmer(
+    thermometerDutch_1 ~
       OutgroupInteraction + NonOutgroupInteraction +
-                           (1+OutgroupInteraction+NonOutgroupInteraction|PID), 
-                         data=workerInteractionType), 
-       confint = TRUE, digits = 3, center = TRUE)
+      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+    data = workerInteractionType
+  ), 
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
 
 # Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-  #write.csv(confint(model.ran0,
+# write.csv(confint(model.ran0,
 #               method="boot",nsim=1000,
@@
 # Compare new model to previous step
-  anova(model.int, model.ran) %>%
-    as.data.frame %>%
+anova(mdlWorker$lmeInterceptAttType, 
+      mdlWorker$lmeSlopesAttType) %>%
+  as.data.frame() %>%
   select(-call) %>%
-    kbl(., 
-        #label = "",
+  kbl(
+    .,
     caption = "Worker: Model Comparison",
@@
 # Save variances
-  v.ran = lme4::VarCorr(model.ran)
+mdlWorker$varSlopesAttType <- 
+  lme4::VarCorr(mdlWorker$lmeSlopesAttType)
 
@@
 # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-    v.ran.btw <- 1 - (as.numeric(v.ran[1])/as.numeric(v.int[1]))
-    v.ran.btw.perc <-  (1 - (as.numeric(v.ran[1])/as.numeric(v.int[1])))*100
-  # and the estimate of within-group (or residual variancel) explained is:
-    v.ran.within <- 1 - (as.numeric(v.ran[2])/as.numeric(v.int[2]))
-    v.ran.within.perc <- (1 - (as.numeric(v.ran[2])/as.numeric(v.int[2])))*100
+mdlWorker$varBtwSlopesAttType <- 
+  1 - (as.numeric(mdlWorker$varSlopesAttType[1]) / as.numeric(mdlWorker$varInterceptAttType[1]))
+mdlWorker$varBtwPercSlopesAttType <- 
+  (1 - (as.numeric(mdlWorker$varSlopesAttType[1]) / as.numeric(mdlWorker$varInterceptAttType[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorker$varWithinSlopesAttType <- 
+  1 - (as.numeric(mdlWorker$varSlopesAttType[2]) / as.numeric(mdlWorker$varInterceptAttType[2]))
+mdlWorker$varWithinPercSlopesAttType <- 
+  (1 - (as.numeric(mdlWorker$varSlopesAttType[2]) / as.numeric(mdlWorker$varInterceptAttType[2]))) * 100
 
 # Assumption Checks:
-  diag = sjPlot::plot_model(model.ran0, type = "diag")
-  grid.arrange(diag[[1]],diag[[2]]$`PID`,diag[[3]],diag[[4]])
+mdlWorker$diagSlopesAttType <-
+  sjPlot::plot_model(mdlWorker$lmerSlopesAttType, type = "diag")
+grid.arrange(
+  mdlWorker$diagSlopesAttType[[1]],
+  mdlWorker$diagSlopesAttType[[2]]$`PID`,
+  mdlWorker$diagSlopesAttType[[3]],
+  mdlWorker$diagSlopesAttType[[4]]
+)
 
 # Plot prediction model
-  dat.new = workerInteractionType[,c("thermometerDutch_1","session","PID")]
-  dat.new$measure = predict(model.ran, workerInteractionType, re.form=NA)
-
-  (t.ppt = ggplot(data=dat.new, aes(x=session, y=measure)) + 
-    geom_line(alpha=1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha=1)+
-    facet_wrap(~PID, ncol = 6)+
-    xlab("Time")+
-    ylab("Outgroup Attitudes")+
-    theme_bw())
-  ggsave(filename = "Figures/Development per PPT.png", t.ppt,
-       width = 18, height = 12, dpi = 800, units = "cm", device='png')
-
-  rm(dat.new)
-
+mdlWorker$predSlopesAttType <- 
+  workerInteractionType %>%
+  select(thermometerDutch_1, session, PID) %>% 
+  mutate(measure = predict(mdlWorker$lmeSlopesAttType,
+                           workerInteractionType,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlWorker$predPltSlopesAttType <-
+    ggplot(data = mdlWorker$predSlopesAttType, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_bw()
+)
+ggsave(
+  filename = "Figures/Worker_PredictionPlot_SlopesAttType.png",
+  mdlWorker$predPltSlopesAttType,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
 ```
@@
 
-```{r WorkerFreqQualCor}
+```{r workerFreqQualCor}
 # prepare data
@@
     SumContactNL = sum(Contact_dum),
-    PercContactNL = SumContactNL/n*100,
+    PercContactNL = SumContactNL / n * 100,
     SumContactNLAll = sum(number),
@@
 # correlation panel
-pairs.panels.new(workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude), 
-                 labels = c("Sum:\nNumer of beeps with Outgroup Contact (NL)", 
+pairs.panels.new(
+  workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
     "Sum:\nNumber of Outgroup Contacts (NL)",
     "Mean:\nInteraction Quality",
-                            "Mean:\nOutgroup Attitudes (NL)"))
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
 
 # correlation panel with interaction sums winsorized
-pairs.panels.new(workerAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude), 
-                 labels = c("Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]", 
+pairs.panels.new(
+  workerAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
     "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
     "Mean:\nInteraction Quality",
-                            "Mean:\nOutgroup Attitudes (NL)"))
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
 ```
@@
 
-```{r WorkerFreqQualReg}
+```{r workerModelOlsAttFreqQual}
 # regression
-lmworkerFreqInt <- lm(AvAttitude ~ SumContactNL * AvQuality, data = workerAvFreQual)
-#summary(lmWorkerInteraction)
-# apa_table(
-#   apa_print(lmworkerFreqInt)$table, 
-#   caption = "Regression across all measurement points [ignoring nested data]."
-# )
+mdlWorker$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL * AvQuality, data = workerAvFreQual)
+# summary(lmWorkerAttFreqQualX)
 
 summ(
-  lmworkerFreqInt,
+  mdlWorker$lmAttFreqQualX,
   confint = TRUE,
@@
 
-interactions::interact_plot(lmworkerFreqInt, pred = AvQuality, modx = SumContactNL, interval = TRUE, partial.residuals = TRUE)
-
-interactions::johnson_neyman(lmworkerFreqInt, pred = AvQuality, modx = SumContactNL, alpha = .05)
+interactions::interact_plot(
+  mdlWorker$lmAttFreqQualX,
+  pred = AvQuality,
+  modx = SumContactNL,
+  interval = TRUE,
+  partial.residuals = TRUE
+)
+
+interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
+                             pred = AvQuality,
+                             modx = SumContactNL,
+                             alpha = .05)
 ```
@@
 
-```{r workerOutPrep}
+```{r workerPrepOutgroupSubsample}
 # see how large our outgroup interaction subset actually is
-tbl_cross(workerInteractionType, row=OutgroupInteraction, col=NonOutgroupInteraction, percent="row")
+tbl_cross(
+  workerInteractionType,
+  row = OutgroupInteraction,
+  col = NonOutgroupInteraction,
+  percent = "row"
+)
 
@@
   filter(OutgroupInteraction == "Yes")
+
+# create empty list to organize models
+mdlWorkerOut <- 
+  list(
+    Att = list(),
+    Qlt = list()
+  )
 ```
@@
 
-```{r Worker.Out.Null.Model.ML}
+```{r workerOutModelMLAttNull}
 # Create and save Model
-  Null.Out.ML.r = lme4::lmer(thermometerDutch_1~1 + (1|PID),data=workerOutgroupInteraction) #use optim if it does not converge
-  Null.Out.ML = lme(thermometerDutch_1~1,random=~1|PID, data=workerOutgroupInteraction, control=list(opt="nlmimb")) #use optim if it does not converge
+mdlWorkerOut$Att$lmerNull <-
+  lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID), 
+             data = workerOutgroupInteraction) # use optim if it does not converge
+mdlWorkerOut$Att$lmeNull <-
+  lme(
+    thermometerDutch_1 ~ 1,
+    random = ~ 1 | PID,
+    data = workerOutgroupInteraction,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
 
 # Get summary with p-values (Satterthwaite's method)
-  #summary(Null.ML.r) #or with the lme function
-  summ(Null.Out.ML.r, digits = 3, center = TRUE)
+# summary(Null.Out.ML.r) #or with the lme function
+summ(mdlWorkerOut$Att$lmerNull, digits = 3, center = TRUE)
 
 # generate 95% parametric bootstrap CIs (and save them as a csv-file):
-  #write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=df),
+# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=dtWorker$full),
 #                  method="boot",nsim=1000,
@@
 # Save variances
-  v.out.null <- VarCorr(Null.Out.ML) # save variances
+mdlWorkerOut$Att$varNull <- 
+  VarCorr(mdlWorkerOut$Att$lmeNull) # save variances
 # The estimate of (between-group or Intercept variance, tau_{00}^2):
-  tau <- as.numeric(v.out.null[1])
-# and the estimate of (within-group or residual variancel, sigma^2) is:
-  sigma <- as.numeric(v.out.null[2])
+mdlWorkerOut$Att$tauNull <- 
+  as.numeric(mdlWorkerOut$Att$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlWorkerOut$Att$sigmaNull <- 
+  as.numeric(mdlWorkerOut$Att$varNull[2])
 # The ICC estimate (between/between+within) is:
-  ICC <- (as.numeric(v.out.null[1])/(as.numeric(v.out.null[1])+as.numeric(v.out.null[2])))
-  ICC.Perc <- ((as.numeric(v.out.null[1])/(as.numeric(v.out.null[1])+as.numeric(v.out.null[2]))))*100
+mdlWorkerOut$Att$IccNull <-
+  (as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2])))
+mdlWorkerOut$Att$IccPercNull <-
+  ((as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2])))) * 100
 ```
@@
 
-```{r interceptAttKeyNeed}
+```{r workerOutModelInterceptAttCore}
 # Create and save Model
-  model.keyneed = lme(thermometerDutch_1 ~ keymotive_fulfillemt_1, random=~1|PID,data=workerOutgroupInteraction)
+mdlWorkerOut$Att$lmeInterceptCore <-
+  lme(
+    thermometerDutch_1 ~ keymotive_fulfillemt_1,
+    random = ~ 1 | PID,
+    data = workerOutgroupInteraction
+  )
 
 # Get summary with p-values (Satterthwaite's method)
-  summ(lmer(thermometerDutch_1 ~ keymotive_fulfillemt_1 + (1|PID),data=workerOutgroupInteraction), 
-       confint = TRUE, digits = 3, center = TRUE)
+summ(
+  lmer(thermometerDutch_1 ~ keymotive_fulfillemt_1 + (1 | PID), 
+       data = workerOutgroupInteraction),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
 
 # Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-  #write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=df), 
+# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
 #                  method="boot",nsim=1000, parallel = "multicore",
@@
 # Compare new model to previous step
-  anova(Null.Out.ML, model.keyneed) %>%
-    as.data.frame %>%
+anova(mdlWorkerOut$Att$lmeNull, 
+      mdlWorkerOut$Att$lmeInterceptCore) %>%
+  as.data.frame() %>%
   select(-call) %>%
-    kbl(., 
-        #label = "",
+  kbl(
+    .,
     caption = "Worker: Model Comparison",
@@
 # Save variances
-  v.keyneed <- lme4::VarCorr(model.keyneed)
+mdlWorkerOut$Att$varInterceptCore <-
+  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCore)
 
@@
 # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-    v.keyneed.btw <- 1 - (as.numeric(v.keyneed[1])/as.numeric(v.out.null[1]))
-    v.keyneed.btw.perc <-  (1 - (as.numeric(v.keyneed[1])/as.numeric(v.out.null[1])))*100
-  # and the estimate of within-group (or residual variancel) explained is:
-    v.keyneed.within <- 1 - (as.numeric(v.keyneed[2])/as.numeric(v.out.null[2]))
-    v.keyneed.within.perc <- (1 - (as.numeric(v.keyneed[2])/as.numeric(v.out.null[2])))*100
-```
-
-#### check for random slope
+mdlWorkerOut$Att$varBtwInterceptCore <- 
+  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCore[1]) / as.numeric(mdlWorkerOut$Att$varNull[1]))
+mdlWorkerOut$Att$varBtwPercInterceptCore <- 
+  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCore[1]) / as.numeric(mdlWorkerOut$Att$varNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorkerOut$Att$varWithinInterceptCore <-
+  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCore[2]) / as.numeric(mdlWorkerOut$Att$varNull[2]))
+mdlWorkerOut$Att$varWithinPercInterceptCore <-
+  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCore[2]) / as.numeric(mdlWorkerOut$Att$varNull[2]))) * 100
+```
+
+TL;DR: Situational core need relates significantly to outgroup attitudes.
+The core need has little explained variance between participants (compared to the null model: Variance Explained = 1 – (Var with Predictor/Var without Predictor); `r format(round(mdlWorkerOut$Att$varBtwPercInterceptCore, 2),nsmall=2)`%).
+The variance explained within participants is small to medium (`r format(round(mdlWorkerOut$Att$varWithinPercInterceptCore, 2),nsmall=2)`%)
+
+#### random slope
 
@@
 
-```{r slopesAttKeyNeed}
+```{r workerOutModelSlopesAttCore}
 # Create and save Model (optimizer needed to reach convergence)
-  model.keyneed.ran = lme(thermometerDutch_1~
+mdlWorkerOut$Att$lmeSlopesCore <-
+  lme(
+    thermometerDutch_1 ~
       keymotive_fulfillemt_1,
-                         random=~1+keymotive_fulfillemt_1|PID,
-                       control=lmeControl(opt='optim'), data=workerOutgroupInteraction)
+    random = ~ 1 + keymotive_fulfillemt_1 | PID,
+    control = lmeControl(opt = "optim"),
+    data = workerOutgroupInteraction
+  )
 
 # Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-  summ(model.keyneed.ran0 <- lmer(thermometerDutch_1 ~
+summ(
+  mdlWorkerOut$Att$lmerSlopesCore <- lmer(
+    thermometerDutch_1 ~
       keymotive_fulfillemt_1 +
-                           (1+keymotive_fulfillemt_1|PID), 
-                         data=workerOutgroupInteraction), 
-       confint = TRUE, digits = 3, center = TRUE)
+      (1 + keymotive_fulfillemt_1 | PID),
+    data = workerOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
 
 # Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-  #write.csv(confint(model.ran0,
+# write.csv(confint(model.ran0,
 #               method="boot",nsim=1000,
@@
 # Compare new model to previous step
-  anova(model.keyneed, model.keyneed.ran) %>%
-    as.data.frame %>%
+anova(mdlWorkerOut$Att$lmeInterceptCore, 
+      mdlWorkerOut$Att$lmeSlopesCore) %>%
+  as.data.frame() %>%
   select(-call) %>%
-    kbl(., 
-        #label = "",
+  kbl(
+    .,
     caption = "Worker: Model Comparison",
@@
 # Save variances
-  v.keyneed.ran = lme4::VarCorr(model.keyneed.ran)
+mdlWorkerOut$Att$varSlopesCore <- 
+  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCore)
 
@@
 # Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-    v.keyneed.ran.btw <- 1 - (as.numeric(v.keyneed.ran[1])/as.numeric(v.keyneed[1]))
-    v.keyneed.ran.btw.perc <-  (1 - (as.numeric(v.keyneed.ran[1])/as.numeric(v.keyneed[1])))*100
-  # and the estimate of within-group (or residual variancel) explained is:
-    v.keyneed.ran.within <- 1 - (as.numeric(v.keyneed.ran[2])/as.numeric(v.keyneed[2]))
-    v.keyneed.ran.within.perc <- (1 - (as.numeric(v.keyneed.ran[2])/as.numeric(v.keyneed[2])))*100
+mdlWorkerOut$Att$varBtwSlopesCore <-
+  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCore[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[1]))
+mdlWorkerOut$Att$varBtwPercSlopesCore <-
+  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCore[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorkerOut$Att$varWithinSlopesCore <-
+  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCore[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[2]))
+mdlWorkerOut$Att$varWithinPercSlopesCore <-
+  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCore[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[2]))) * 100
 
 # Assumption Checks:
-  diag = sjPlot::plot_model(model.keyneed.ran0, type = "diag")
-  grid.arrange(diag[[1]],diag[[2]]$`PID`,diag[[3]],diag[[4]])
+mdlWorkerOut$Att$diagSlopesCore <- 
+  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlWorkerOut$Att$diagSlopesCore[[1]],
+  mdlWorkerOut$Att$diagSlopesCore[[2]]$`PID`,
+  mdlWorkerOut$Att$diagSlopesCore[[3]],
+  mdlWorkerOut$Att$diagSlopesCore[[4]]
+)
 
 # Plot prediction model
-  dat.new = workerOutgroupInteraction[,c("thermometerDutch_1","session","PID")]
-  dat.new$measure = predict(model.keyneed.ran, workerOutgroupInteraction, re.form=NA)
-
-  (t.ppt = ggplot(data=dat.new, aes(x=session, y=measure)) + 
-    geom_line(alpha=1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha=1)+
-    facet_wrap(~PID, ncol = 6)+
-    xlab("Time")+
-    ylab("Outgroup Attitudes")+
-    theme_bw())
-  ggsave(filename = "Figures/Development per PPT Out Keyneed.png", t.ppt,
-       width = 18, height = 12, dpi = 800, units = "cm", device='png')
-
-  rm(dat.new)
-
-```
+mdlWorkerOut$Att$predSlopesCore <- 
+  workerOutgroupInteraction %>%
+  select(thermometerDutch_1, session, PID) %>% 
+  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCore,
+                           workerOutgroupInteraction,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlWorkerOut$Att$predPltSlopesCore <-
+    ggplot(data = mdlWorkerOut$Att$predSlopesCore, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_bw()
+)
+ggsave(
+  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCore.png",
+  mdlWorkerOut$Att$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+TL;DR: The random slope adds significantly to the prediction model.
+
+<div class="alert alert-warning alert-dismissible fade in" role="alert">
+  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
+  <i class="fas fa-exclamation-triangle"></i> <b>Check needed: </b><br/>
+  Something is with the variances explained (between = `r format(round(mdlWorkerOut$Att$varBtwPercSlopesCore, 2),nsmall=2)`%, within = `r format(round(mdlWorkerOut$Att$varWithinPercSlopesCore, 2),nsmall=2)`%).
+This is when comparing the random intercepts to the random slopes model.
+</div>
 
 ### Need fulfillment and Interaction Quality
+
+##### Unconditional model
+
+make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
+
+\begin{equation}
+(\#eq:WorkerOutQualEmptyModel)
+Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r workerOutModelMLQltNull}
+# Create and save Model
+mdlWorkerOut$Qlt$lmerNull <-
+  lme4::lmer(quality_overall_1 ~ 1 + (1 | PID), 
+             data = workerOutgroupInteraction) # use optim if it does not converge
+mdlWorkerOut$Qlt$lmeNull <-
+  lme(
+    quality_overall_1 ~ 1,
+    random = ~ 1 | PID,
+    data = workerOutgroupInteraction,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.Qual.ML.r) #or with the lme function
+summ(mdlWorkerOut$Qlt$lmerNull, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=workerOutgroupInteraction),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlWorkerOut$Qlt$varNull <- 
+  VarCorr(mdlWorkerOut$Qlt$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlWorkerOut$Qlt$tauNull <- 
+  as.numeric(mdlWorkerOut$Qlt$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlWorkerOut$Qlt$sigmaNull <- 
+  as.numeric(mdlWorkerOut$Qlt$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlWorkerOut$Qlt$IccNull <-
+  (as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2])))
+mdlWorkerOut$Qlt$IccPercNull <-
+  ((as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2])))) * 100
+```
 
@@
 
-#### check for random slope
+```{r workerOutModelInterceptQltCore}
+# Create and save Model
+mdlWorkerOut$Qlt$lmeInterceptCore <-
+  lme(
+    quality_overall_1 ~ keymotive_fulfillemt_1,
+    random = ~ 1 | PID,
+    data = workerOutgroupInteraction
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  lmer(quality_overall_1 ~ keymotive_fulfillemt_1 + (1 | PID), 
+       data = workerOutgroupInteraction),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(quality_overall_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorkerOut$Qlt$lmeNull, 
+      mdlWorkerOut$Qlt$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Qlt$varInterceptCore <-
+  lme4::VarCorr(mdlWorkerOut$Qlt$lmeInterceptCore)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorkerOut$Qlt$varBtwInterceptCore <- 
+  1 - (as.numeric(mdlWorkerOut$Qlt$varInterceptCore[1]) / as.numeric(mdlWorkerOut$Qlt$varNull[1]))
+mdlWorkerOut$Qlt$varBtwPercInterceptCore <- 
+  (1 - (as.numeric(mdlWorkerOut$Qlt$varInterceptCore[1]) / as.numeric(mdlWorkerOut$Qlt$varNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorkerOut$Qlt$varWithinInterceptCore <-
+  1 - (as.numeric(mdlWorkerOut$Qlt$varInterceptCore[2]) / as.numeric(mdlWorkerOut$Qlt$varNull[2]))
+mdlWorkerOut$Qlt$varWithinPercInterceptCore <-
+  (1 - (as.numeric(mdlWorkerOut$Qlt$varInterceptCore[2]) / as.numeric(mdlWorkerOut$Qlt$varNull[2]))) * 100
+```
+
+TL;DR: Situational core need relates significantly to interaction quality.
+The core need explained substantial variance between participants (`r format(round(mdlWorkerOut$Qlt$varBtwPercInterceptCore, 2),nsmall=2)`%).
+The variance explained within participants is also medium (`r format(round(mdlWorkerOut$Qlt$varWithinPercInterceptCore, 2),nsmall=2)`%)
+
+#### random slope
 
@@
 
+```{r workerOutModelSlopesQltCore}
+# Create and save Model (optimizer needed to reach convergence)
+mdlWorkerOut$Qlt$lmeSlopesCore <-
+  lme(
+    quality_overall_1 ~
+      keymotive_fulfillemt_1,
+    random = ~ 1 + keymotive_fulfillemt_1 | PID,
+    control = lmeControl(opt = "optim"),
+    data = workerOutgroupInteraction
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlWorkerOut$Qlt$lmerSlopesCore <-
+    lmer(
+      quality_overall_1 ~
+        keymotive_fulfillemt_1 +
+        (1 + keymotive_fulfillemt_1 | PID),
+      data = workerOutgroupInteraction
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(mdlWorkerOut$Qlt$lmerSlopesCore,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorkerOut$Qlt$lmeInterceptCore, 
+      mdlWorkerOut$Qlt$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Qlt$varSlopesCore <- 
+  lme4::VarCorr(mdlWorkerOut$Qlt$lmeSlopesCore)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorkerOut$Qlt$varBtwSlopesCore <-
+  1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[1]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[1]))
+mdlWorkerOut$Qlt$varBtwPercSlopesCore <-
+  (1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[1]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorkerOut$Qlt$varWithinSlopesCore <-
+  1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[2]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[2]))
+mdlWorkerOut$Qlt$varWithinPercSlopesCore <-
+  (1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[2]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[2]))) * 100
+```
+
+TL;DR: random slopes does not add significantly. Stay with simpler model.
+
 ### Need fulfillment, Interaction Quality, and Attitudes
@@
 
-#### check for random slope
+```{r workerOutModelInterceptAttCoreQlt}
+# Create and save Model
+mdlWorkerOut$Att$lmeInterceptCoreQlt <-
+  lme(
+    thermometerDutch_1 ~ keymotive_fulfillemt_1 + quality_overall_1,
+    random = ~ 1 | PID,
+    data = workerOutgroupInteraction
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  lmer(
+    thermometerDutch_1 ~ keymotive_fulfillemt_1 + quality_overall_1 + (1 | PID),
+    data = workerOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlWorkerOut$Att$lmeNull, 
+  mdlWorkerOut$Att$lmeInterceptCoreQlt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Att$varInterceptCoreQlt <-
+  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreQlt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorkerOut$Att$varBtwInterceptCoreQlt <- 
+  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[1]) / as.numeric(mdlWorkerOut$Att$varNull[1]))
+mdlWorkerOut$Att$varBtwPercInterceptCoreQlt <- 
+  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[1]) / as.numeric(mdlWorkerOut$Att$varNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorkerOut$Att$varWithinInterceptCoreQlt <-
+  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[2]) / as.numeric(mdlWorkerOut$Att$varNull[2]))
+mdlWorkerOut$Att$varWithinPercInterceptCoreQlt <-
+  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[2]) / as.numeric(mdlWorkerOut$Att$varNull[2]))) * 100
+```
+
+TL;DR: Variance explained in outgroup attitudes is of medium effect size (between: `r format(round(mdlWorkerOut$Att$varBtwPercInterceptCoreQlt,2),nsmall=2)`%, within: `r format(round(mdlWorkerOut$Att$varWithinPercInterceptCoreQlt,2),nsmall=2)`%)
+
+#### random slope
 
@@
 
+```{r workerOutModelSlopesAttCoreQlt}
+# Create and save Model (optimizer needed to reach convergence)
+mdlWorkerOut$Att$lmeSlopesCoreQlt <-
+  lme(
+    thermometerDutch_1 ~
+      keymotive_fulfillemt_1 + quality_overall_1,
+    random = ~ 1 + keymotive_fulfillemt_1 + quality_overall_1 | PID,
+    control = lmeControl(opt = "optim"),
+    data = workerOutgroupInteraction
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlWorkerOut$Att$lmerSlopesCoreQlt <- lmer(
+    thermometerDutch_1 ~
+      keymotive_fulfillemt_1 + quality_overall_1 +
+      (1 + keymotive_fulfillemt_1 + quality_overall_1 | PID),
+    data = workerOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlWorkerOut$Att$lmeNull,
+  mdlWorkerOut$Att$lmeInterceptCoreQlt,
+  mdlWorkerOut$Att$lmeSlopesCoreQlt
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Att$varSlopesCoreQlt <- 
+  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreQlt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorkerOut$Att$varBtwSlopesCoreQlt <-
+  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[1]))
+mdlWorkerOut$Att$varBtwPercSlopesCoreQlt <-
+  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorkerOut$Att$varWithinSlopesCoreQlt <-
+  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[2]))
+mdlWorkerOut$Att$varWithinPercSlopesCoreQlt <-
+  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[2]))) * 100
+
+# Assumption Checks:
+mdlWorkerOut$Att$diagSlopesCoreQlt <- 
+  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreQlt, type = "diag")
+grid.arrange(
+  mdlWorkerOut$Att$diagSlopesCoreQlt[[1]],
+  mdlWorkerOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
+  mdlWorkerOut$Att$diagSlopesCoreQlt[[3]],
+  mdlWorkerOut$Att$diagSlopesCoreQlt[[4]]
+)
+
+# Plot prediction model
+mdlWorkerOut$Att$predSlopesCoreQlt <- 
+  workerOutgroupInteraction %>%
+  select(thermometerDutch_1, session, PID) %>% 
+  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreQlt,
+                           workerOutgroupInteraction,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlWorkerOut$Att$predPltSlopesCoreQlt <-
+    ggplot(data = mdlWorkerOut$Att$predSlopesCoreQlt, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_bw()
+)
+ggsave(
+  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreQlt.png",
+  mdlWorkerOut$Att$predPltSlopesCoreQlt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
 #### Compare models
+
+Interpretation of Mediation like results.
 
@@
 
-##### check for random slope
+```{r workerModelInterceptAttCoreInt}
+# Create and save Model
+mdlWorker$lmeInterceptAttCoreInt <-
+  lme(
+    thermometerDutch_1 ~ keyMotiveFulfilled * c,
+    random =  ~ 1 | PID,
+    data = workerInteractionType
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlWorker$lmerInterceptAttCoreInt <- lmer(
+    thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction + (1 | PID),
+    data = workerInteractionType
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorker$lmeAttNull, 
+      mdlWorker$lmeInterceptAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorker$varInterceptAttCoreInt <- 
+  lme4::VarCorr(mdlWorker$lmeInterceptAttCoreInt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorker$varBtwInterceptAttCoreInt <-
+  1 - (as.numeric(mdlWorker$varInterceptAttCoreInt[1]) / as.numeric(mdlWorker$varAttNull[1]))
+mdlWorker$varBtwPercInterceptAttCoreInt <-
+  (1 - (as.numeric(mdlWorker$varInterceptAttCoreInt[1]) / as.numeric(mdlWorker$varAttNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorker$varWithinInterceptAttCoreInt <-
+  1 - (as.numeric(mdlWorker$varInterceptAttCoreInt[2]) / as.numeric(mdlWorker$varAttNull[2]))
+mdlWorker$varWithinPercInterceptAttCoreInt <-
+  (1 - (as.numeric(mdlWorker$varInterceptAttCoreInt[2]) / as.numeric(mdlWorker$varAttNull[2]))) * 100
+
+# visualize interaction
+## Without ML structure
+ggplot(data = workerInteractionType,
+       aes(x = keyMotiveFulfilled, 
+           y = thermometerDutch_1,
+           fill = OutgroupInteraction)) +
+  #geom_point()+
+  geom_smooth(method = 'lm',
+              aes(linetype = OutgroupInteraction),
+              color = "black") +
+  #facet_wrap(~PID, ncol = 6)+
+  scale_linetype_manual(values = c("dashed", "solid")) +
+  scale_fill_manual(values = c("darkgrey", "black")) +
+  #scale_colour_manual(values=c("grey20", "black"), name="Intergroup Contact")+
+  scale_y_continuous(
+    limits = c(50, 100),
+    breaks = seq(50, 100, by = 10),
+    position = "left"
+  ) +
+  scale_x_continuous(limits = c(-50, 50), breaks = seq(-50, 50, by = 10)) +
+  labs(
+    title = "Without ML stucture",
+    x = "Fulfillment Core Need",
+    y = "Outgroup Attitudes",
+    fill = "Intergroup Contact",
+    linetype = "Intergroup Contact"
+  ) +
+  theme_Publication() +
+  theme(legend.position = "bottom",
+        legend.key.size = unit(1, "cm"))
+## With ML structure 
+# get predicted values and calculate SE
+plot.int <-
+  sjPlot::get_model_data(
+    mdlWorker$lmeInterceptAttCoreInt,
+    type = "pred",
+    terms = c(
+      "OutgroupInteraction",
+      paste("keyMotiveFulfilled [",paste(seq(-50, 50, 10), collapse = ", "),"]",collapse = "")
+    ),
+    pretty = F
+  )
+plot.int$se = (plot.int$conf.high - plot.int$predicted)/1.96
+
+# plot predicted values with SE band
+ggplot(plot.int,
+       aes(
+         x = as.numeric(as.character(group)),
+         y = predicted,
+         group = as.factor(x)
+       )) +
+  geom_line(aes(linetype = as.factor(x)), size = 1) +
+  #geom_point(aes(shape=as.factor(x)), size=2, position = position_dodge(0.0)) +
+  geom_ribbon(aes(ymin = predicted - se, ymax = predicted + se), alpha =
+                0.2) +
+  scale_y_continuous(
+    limits = c(50, 100),
+    breaks = seq(50, 100, by = 10),
+    position = "left"
+  ) +
+  scale_x_continuous(breaks = seq(-50, 50, 10)) +
+  scale_linetype_manual(values = c("dashed", "solid")) +
+  xlab("Fulfillment Relatedness") +
+  ylab("Outgroup Attitudes") +
+  guides(
+    shape = guide_legend(title = "Intergroup Contact"),
+    linetype = guide_legend(title = "Intergroup Contact")
+  ) +
+  theme_bw() +
+  theme(legend.position = "bottom",
+        legend.key.size = unit(1, "cm"))
+
+#### Predict Standard errors with Options ####
+  # create parameters for prediction
+mdlWorker$predInterceptAttCoreInt <- 
+  workerOutgroupInteraction %>%
+  select(PID, thermometerDutch_1, OutgroupInteraction) %>% 
+  mutate(measure = predict(mdlWorker$lmerInterceptAttCoreInt,
+                           workerOutgroupInteraction,
+                           re.form = NA
+                           )
+         )
+
+datNew = data.frame(
+  OutgroupInteraction = rep(c("No", "Yes"), each = 21),
+  keyMotiveFulfilled = rep(seq(-50, 50, 5), 2)
+)
+
+# Predict values, clean up and calculate SE
+PI <-
+  merTools::predictInterval(
+    merMod = mdlWorker$lmerInterceptAttCoreInt,
+    newdata = datNew,
+    level = 0.95,
+    n.sims = 10000,
+    stat = "mean",
+    type = "linear.prediction",
+    include.resid.var = F,
+    fix.intercept.variance = F
+  )
+
+dat.mod = cbind(datNew, PI)
+dat.mod$se = (dat.mod$upr - dat.mod$fit) / 1.96
+
+# Plot predicted values with SE
+ggplot(dat.mod,
+       aes(x = keyMotiveFulfilled, 
+           y = thermometerDutch_1,
+           fill = OutgroupInteraction)) +
+  #geom_point() +
+  #geom_smooth(method="loess") +
+  #geom_ribbon(data=dat.mod,aes(ymin=lwr,ymax=upr),alpha=0.3) +
+  geom_line(aes(linetype = as.factor(Contact_dum.f)), size = 1) +
+  #facet_wrap(~PID, ncol = 6)+
+  geom_ribbon(data = dat.mod,
+              aes(ymin = fit - se, ymax = fit + se),
+              alpha = 0.3) +
+  scale_linetype_manual(values = c("dashed", "solid")) +
+  xlab("Fulfilment Relatedness") +
+  ylab("Outgroup Attitudes") +
+  guides(
+    color = guide_legend(title = "Intergroup Contact"),
+    linetype = guide_legend(title = "Intergroup Contact")
+  ) +
+  theme_Publication()
+
+#### Bayesian estimation ####
+library(brms)
+options(mc.cores = parallel::detectCores())  # Run many chains simultaneously
+brmfit <- brm(
+  thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction + (1 | PID),
+  data = workerInteractionType,
+  family = gaussian,
+  iter = 1000,
+  chains = 4
+)
+
+# create parameters for prediction:
+datNew2 = data.frame(
+  OutgroupInteraction = rep(c("No", "Yes"), each = 101),
+  keyMotiveFulfilled = rep(seq(-50, 50, 1), 2)
+)
+# Save predicted values and adjust names and labels
+fitavg <-
+  cbind(datNew2,
+        fitted(brmfit, newdata = datNew2, re_formula = NA)[, -2])
+names(fitavg)[names(fitavg) == "Estimate"] = "pred"
+fitavg$se <- (fitavg$Q97.5 - fitavg$pred) / 1.96
+
+# Plot Bayesian SE prediction interval
+ggplot(fitavg,
+       aes(x = keyMotiveFulfilled,
+           y = pred,
+           group = OutgroupInteraction)) +
+  scale_x_continuous(breaks = seq(-50, 50, 10)) +
+  scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
+  geom_line(aes(linetype = OutgroupInteraction), size = 1) +
+  geom_ribbon(aes(ymin = pred - se, ymax = pred + se), alpha = 0.2) +
+  scale_linetype_manual(values = c("dashed", "solid")) +
+  xlab("Fulfillment Competence") +
+  ylab("Outgroup Attitudes") +
+  guides(
+    color = guide_legend(title = "Intergroup Contact"),
+    linetype = guide_legend(title = "Intergroup Contact")
+  ) +
+  theme_Publication()
+
+# plot all overlayed posteriors:
+pst <- posterior_samples(brmfit, "b")
+ggplot(workerInteractionType, aes(x = keyMotiveFulfilled, y = thermometerDutch_1)) +
+  geom_point(shape=4, alpha = .1) +
+  geom_tile() +
+  geom_abline(
+    data = pst,
+    aes(intercept = b_Intercept, slope = b_keyMotiveFulfilled),
+    alpha = .025,
+    size = .4
+  ) +
+  labs(
+    title = "slope Posteriors",
+    x = "Fulfillment Core Need",
+    y = "Outgroup Attitudes (NL)"
+  ) +
+  theme_Publication()
+```
+
+##### random slope
 
@@
 #### Other psychological needs
+
+Also check key need fulfillment generally.
 
@@
 ) %>%
-    kable_classic(full_width = F, 
+  kable_classic(
+    full_width = F,
     lightable_options = "hover",
-                  html_font = "Cambria") 
+    html_font = "Cambria"
+  )
 ```
@@
   dplyr::select(loadedversion, date, source) %>%
-  rownames_to_column
+  rownames_to_column()
 
@@
 ) %>%
-  kable_classic(full_width = F, 
+  kable_classic(
+    full_width = F,
     lightable_options = "hover",
-                  html_font = "Cambria") 
+    html_font = "Cambria"
+  )
 ```

### 2021-10-17 Supplemental-Material-B-Annotated-Analysis.Rmd
AOT-P fully added

@@
 )], na.rm = T)
-df$relatedness.daily.int <- rowMeans(df[, c("relatedness_other_1", "relatedness_self_1")], na.rm = T)
+df$relatedness_1 <- rowMeans(df[, c("relatedness_other_1", "relatedness_self_1")], na.rm = T)
 
@@
     ylab("Outgroup Attitudes") +
-    theme_bw()
+    theme_Publication()
 )
@@
   lme(
-    thermometerDutch_1 ~ keyMotiveFulfilled * c,
+    thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction,
     random =  ~ 1 | PID,
@@
   (1 - (as.numeric(mdlWorker$varInterceptAttCoreInt[2]) / as.numeric(mdlWorker$varAttNull[2]))) * 100
-
+```
+
+##### random slope
+
+\begin{equation}
+(\#eq:AttitudeNeedInteractionRandEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti}  + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r workerModelSlopesAttCoreIntX}
+# Create and save Model (optimizer needed to reach convergence)
+mdlWorker$lmeSlopesAttCoreInt <- lme(
+  thermometerDutch_1 ~
+    keyMotiveFulfilled * OutgroupInteraction,
+  random = ~ 1 + keyMotiveFulfilled + OutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  data = workerInteractionType
+)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlWorker$lmerSlopesAttCoreInt <- lmer(
+    thermometerDutch_1 ~
+      keyMotiveFulfilled * OutgroupInteraction +
+      (1 + keyMotiveFulfilled + OutgroupInteraction | PID),
+    data = workerInteractionType
+  ), 
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorker$lmeAttNull, 
+      mdlWorker$lmeInterceptAttCoreInt,
+      mdlWorker$lmeSlopesAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorker$varSlopesAttCoreInt <- 
+  lme4::VarCorr(mdlWorker$lmeSlopesAttCoreInt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorker$varBtwSlopesAttCoreInt <- 
+  1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[1]) / as.numeric(mdlWorker$varInterceptAttCoreInt[1]))
+mdlWorker$varBtwPercSlopesAttCoreInt <- 
+  (1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[1]) / as.numeric(mdlWorker$varInterceptAttCoreInt[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorker$varWithinSlopesAttCoreInt <- 
+  1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[2]) / as.numeric(mdlWorker$varInterceptAttCoreInt[2]))
+mdlWorker$varWithinPercSlopesAttCoreInt <- 
+  (1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[2]) / as.numeric(mdlWorker$varInterceptAttCoreInt[2]))) * 100
+
+# Assumption Checks:
+mdlWorker$diagSlopesAttCoreInt <-
+  sjPlot::plot_model(mdlWorker$lmerSlopesAttCoreInt, type = "diag")
+grid.arrange(
+  mdlWorker$diagSlopesAttCoreInt[[1]],
+  mdlWorker$diagSlopesAttCoreInt[[2]]$`PID`,
+  mdlWorker$diagSlopesAttCoreInt[[3]],
+  mdlWorker$diagSlopesAttCoreInt[[4]]
+)
+
+# Plot prediction model
+mdlWorker$predSlopesAttCoreInt <- 
+  workerInteractionType %>%
+  select(thermometerDutch_1, session, PID) %>% 
+  mutate(measure = predict(mdlWorker$lmeSlopesAttCoreInt,
+                           workerInteractionType,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlWorker$predPltSlopesAttCoreInt <-
+    ggplot(data = mdlWorker$predSlopesAttCoreInt, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/Worker_PredictionPlot_SlopesAttCoreInt.png",
+  mdlWorker$predPltSlopesAttCoreInt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+##### Plot Interaction
+
+```{r workerModelInterceptAttCoreIntPlt}
 # visualize interaction
@@
 ## With ML structure
-# get predicted values and calculate SE
-plot.int <-
-  sjPlot::get_model_data(
-    mdlWorker$lmeInterceptAttCoreInt,
-    type = "pred",
-    terms = c(
-      "OutgroupInteraction",
-      paste("keyMotiveFulfilled [",paste(seq(-50, 50, 10), collapse = ", "),"]",collapse = "")
-    ),
-    pretty = F
-  )
-plot.int$se = (plot.int$conf.high - plot.int$predicted)/1.96
-
-# plot predicted values with SE band
-ggplot(plot.int,
-       aes(
-         x = as.numeric(as.character(group)),
-         y = predicted,
-         group = as.factor(x)
-       )) +
-  geom_line(aes(linetype = as.factor(x)), size = 1) +
-  #geom_point(aes(shape=as.factor(x)), size=2, position = position_dodge(0.0)) +
-  geom_ribbon(aes(ymin = predicted - se, ymax = predicted + se), alpha =
-                0.2) +
-  scale_y_continuous(
-    limits = c(50, 100),
-    breaks = seq(50, 100, by = 10),
-    position = "left"
-  ) +
-  scale_x_continuous(breaks = seq(-50, 50, 10)) +
-  scale_linetype_manual(values = c("dashed", "solid")) +
-  xlab("Fulfillment Relatedness") +
-  ylab("Outgroup Attitudes") +
-  guides(
-    shape = guide_legend(title = "Intergroup Contact"),
-    linetype = guide_legend(title = "Intergroup Contact")
-  ) +
-  theme_bw() +
-  theme(legend.position = "bottom",
-        legend.key.size = unit(1, "cm"))
-
-#### Predict Standard errors with Options ####
 # create parameters for prediction
-mdlWorker$predInterceptAttCoreInt <- 
-  workerOutgroupInteraction %>%
-  select(PID, thermometerDutch_1, OutgroupInteraction) %>% 
-  mutate(measure = predict(mdlWorker$lmerInterceptAttCoreInt,
-                           workerOutgroupInteraction,
-                           re.form = NA
-                           )
-         )
-
 datNew = data.frame(
-  OutgroupInteraction = rep(c("No", "Yes"), each = 21),
-  keyMotiveFulfilled = rep(seq(-50, 50, 5), 2)
+  OutgroupInteraction = factor(rep(c("No", "Yes"), each = 21)),
+  keyMotiveFulfilled = rep(seq(-50, 50, 5), 2),
+  PID = 0
 )
@@
   merTools::predictInterval(
-    merMod = mdlWorker$lmerInterceptAttCoreInt,
+    merMod = mdlWorker$lmerSlopesAttCoreInt,
     newdata = datNew,
     level = 0.95,
-    n.sims = 10000,
     stat = "mean",
@@
   )
-
-dat.mod = cbind(datNew, PI)
-dat.mod$se = (dat.mod$upr - dat.mod$fit) / 1.96
+mdlWorker$predInterceptAttCoreIntX <- 
+  cbind(datNew, PI)
+mdlWorker$predInterceptAttCoreIntX$se <-
+  (mdlWorker$predInterceptAttCoreIntX$upr - mdlWorker$predInterceptAttCoreIntX$fit) / 1.96
+rm(datNew, PI)
 
 # Plot predicted values with SE
-ggplot(dat.mod,
+ggplot(
+  mdlWorker$predInterceptAttCoreIntX,
   aes(x = keyMotiveFulfilled,
-           y = thermometerDutch_1,
-           fill = OutgroupInteraction)) +
+      y = fit,
+      fill = OutgroupInteraction)
+)+
   #geom_point() +
-  #geom_smooth(method="loess") +
-  #geom_ribbon(data=dat.mod,aes(ymin=lwr,ymax=upr),alpha=0.3) +
-  geom_line(aes(linetype = as.factor(Contact_dum.f)), size = 1) +
+  geom_line(aes(linetype = as.factor(OutgroupInteraction)), size = 1) +
   #facet_wrap(~PID, ncol = 6)+
-  geom_ribbon(data = dat.mod,
+  geom_ribbon(data = mdlWorker$predInterceptAttCoreIntX,
               aes(ymin = fit - se, ymax = fit + se),
               alpha = 0.3) +
+  scale_x_continuous(breaks = seq(-50, 50, 10)) +
+  scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
   scale_linetype_manual(values = c("dashed", "solid")) +
-  xlab("Fulfilment Relatedness") +
-  ylab("Outgroup Attitudes") +
-  guides(
-    color = guide_legend(title = "Intergroup Contact"),
-    linetype = guide_legend(title = "Intergroup Contact")
+  scale_fill_manual(values = c("darkgrey", "black")) +
+  labs(
+    x = "Fulfillment Core Need",
+    y = "Outgroup Attitude (NL)",
+    fill = "Intergroup Contact",
+    linetype = "Intergroup Contact",
+    title = "Based on Model Predictions"
   ) +
@@
 
-#### Bayesian estimation ####
-library(brms)
-options(mc.cores = parallel::detectCores())  # Run many chains simultaneously
-brmfit <- brm(
-  thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction + (1 | PID),
-  data = workerInteractionType,
-  family = gaussian,
-  iter = 1000,
-  chains = 4
-)
-
-# create parameters for prediction:
-datNew2 = data.frame(
-  OutgroupInteraction = rep(c("No", "Yes"), each = 101),
-  keyMotiveFulfilled = rep(seq(-50, 50, 1), 2)
-)
-# Save predicted values and adjust names and labels
-fitavg <-
-  cbind(datNew2,
-        fitted(brmfit, newdata = datNew2, re_formula = NA)[, -2])
-names(fitavg)[names(fitavg) == "Estimate"] = "pred"
-fitavg$se <- (fitavg$Q97.5 - fitavg$pred) / 1.96
-
-# Plot Bayesian SE prediction interval
-ggplot(fitavg,
-       aes(x = keyMotiveFulfilled,
-           y = pred,
-           group = OutgroupInteraction)) +
-  scale_x_continuous(breaks = seq(-50, 50, 10)) +
-  scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
-  geom_line(aes(linetype = OutgroupInteraction), size = 1) +
-  geom_ribbon(aes(ymin = pred - se, ymax = pred + se), alpha = 0.2) +
-  scale_linetype_manual(values = c("dashed", "solid")) +
-  xlab("Fulfillment Competence") +
-  ylab("Outgroup Attitudes") +
-  guides(
-    color = guide_legend(title = "Intergroup Contact"),
-    linetype = guide_legend(title = "Intergroup Contact")
-  ) +
-  theme_Publication()
-
-# plot all overlayed posteriors:
-pst <- posterior_samples(brmfit, "b")
-ggplot(workerInteractionType, aes(x = keyMotiveFulfilled, y = thermometerDutch_1)) +
-  geom_point(shape=4, alpha = .1) +
-  geom_tile() +
-  geom_abline(
-    data = pst,
-    aes(intercept = b_Intercept, slope = b_keyMotiveFulfilled),
-    alpha = .025,
-    size = .4
-  ) +
-  labs(
-    title = "slope Posteriors",
-    x = "Fulfillment Core Need",
-    y = "Outgroup Attitudes (NL)"
-  ) +
-  theme_Publication()
-```
-
-##### random slope
-
-\begin{equation}
-(\#eq:AttitudeNeedInteractionRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti}  + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
+# #### Bayesian estimation !! ONLY RUN ON FINAL RENDER !! Takes forever ####
+# options(mc.cores = parallel::detectCores())  # Run many chains simultaneously
+# brmfit <- brm(
+#   thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction + 
+#     (1 + keyMotiveFulfilled + OutgroupInteraction | PID),
+#   data = workerInteractionType,
+#   family = gaussian,
+#   iter = 1000,
+#   chains = 4
+# )
+# 
+# # create parameters for prediction:
+# datNew = data.frame(
+#   OutgroupInteraction = rep(c("No", "Yes"), each = 101),
+#   keyMotiveFulfilled = rep(seq(-50, 50, 1), 2)
+# )
+# # Save predicted values and adjust names and labels
+# fitavg <-
+#   cbind(datNew,
+#         fitted(brmfit, newdata = datNew, re_formula = NA)[, -2])
+# names(fitavg)[names(fitavg) == "Estimate"] = "pred"
+# fitavg$se <- (fitavg$Q97.5 - fitavg$pred) / 1.96
+# 
+# # Plot Bayesian SE prediction interval
+# ggplot(fitavg,
+#        aes(x = keyMotiveFulfilled,
+#            y = pred,
+#            fill = OutgroupInteraction)) +
+#   scale_x_continuous(breaks = seq(-50, 50, 10)) +
+#   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
+#   geom_line(aes(linetype = OutgroupInteraction), size = 1) +
+#   geom_ribbon(aes(ymin = pred - se, ymax = pred + se), alpha = 0.2) +
+#   scale_linetype_manual(values = c("dashed", "solid")) +
+#   scale_fill_manual(values = c("darkgrey", "black")) +
+#   labs(
+#     x = "Fulfillment Core Need",
+#     y = "Outgroup Attitude (NL)",
+#     fill = "Intergroup Contact",
+#     linetype = "Intergroup Contact",
+#     title = "Based on Bayesian Prediction Interval"
+#   ) +
+#   theme_Publication()
+# 
+# # plot all overlayed posteriors:
+# pst <- posterior_samples(brmfit, "b")
+# ggplot(workerInteractionType,
+#        aes(x = keyMotiveFulfilled, y = thermometerDutch_1)) +
+#   geom_point(shape = 4, alpha = .1) +
+#   geom_tile() +
+#   geom_abline(
+#     data = pst,
+#     aes(intercept = b_Intercept, slope = b_keyMotiveFulfilled),
+#     alpha = .025,
+#     size = .4
+#   ) +
+#   labs(title = "slope Posteriors",
+#        x = "Fulfillment Core Need",
+#        y = "Outgroup Attitudes (NL)") +
+#   theme_Publication()
+# rm(datNew, brmfit, fitavg, pst)
+```
 
 #### Other psychological needs
-
-Also check key need fulfillment generally.
 
@@
 
-##### check for random slope
+```{r workerOutModelInterceptAttCoreSdt}
+# Create and save Model
+mdlWorkerOut$Att$lmeInterceptCoreSdt <-
+  lme(
+    thermometerDutch_1 ~ keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1,
+    random = ~ 1 | PID,
+    data = workerOutgroupInteraction,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlWorkerOut$Att$lmerInterceptCoreSdt <- lmer(
+    thermometerDutch_1 ~ keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 + (1 | PID),
+    data = workerOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# compute lme for core model with same number of observations for comparison
+# !! LOOK INTO MISSINGNESS (only one observation) !!
+lmeInterceptCoreRed <-
+  lme(
+    thermometerDutch_1 ~ keymotive_fulfillemt_1,
+    random = ~ 1 | PID,
+    data = workerOutgroupInteraction %>% filter(!is.na(autonomy_1))
+  )
+
+# Compare new model to previous step
+anova(
+  lmeInterceptCoreRed, 
+  mdlWorkerOut$Att$lmeInterceptCoreSdt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+rm(lmeInterceptCoreRed)
+
+# Save variances
+mdlWorkerOut$Att$varInterceptCoreSdt <-
+  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreSdt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorkerOut$Att$varBtwInterceptCoreSdt <- 
+  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[1]))
+mdlWorkerOut$Att$varBtwPercInterceptCoreSdt <- 
+  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorkerOut$Att$varWithinInterceptCoreSdt <-
+  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[2]))
+mdlWorkerOut$Att$varWithinPercInterceptCoreSdt <-
+  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[2]))) * 100
+```
+
+##### random slope
 
@@
 \end{equation}
+
+```{r workerOutModelSlopesAttCoreSdt}
+# Create and save Model (optimizer needed to reach convergence)
+mdlWorkerOut$Att$lmeSlopesCoreSdt <-
+  lme(
+    thermometerDutch_1 ~
+      keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1,
+    random = ~ 1 + keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 | PID,
+    control = lmeControl(opt = "optim"),
+    data = workerOutgroupInteraction,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlWorkerOut$Att$lmerSlopesCoreSdt <- lmer(
+    thermometerDutch_1 ~
+      keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 +
+      (1 + keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 | PID),
+    data = workerOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorkerOut$Att$lmeInterceptCoreSdt, 
+      mdlWorkerOut$Att$lmeSlopesCoreSdt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Att$varSlopesCoreSdt <- 
+  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreSdt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorkerOut$Att$varBtwSlopesCoreSdt <-
+  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]))
+mdlWorkerOut$Att$varBtwPercSlopesCoreSdt <-
+  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorkerOut$Att$varWithinSlopesCoreSdt <-
+  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]))
+mdlWorkerOut$Att$varWithinPercSlopesCoreSdt <-
+  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]))) * 100
+
+# Assumption Checks:
+mdlWorkerOut$Att$diagSlopesCoreSdt <- 
+  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreSdt, type = "diag")
+grid.arrange(
+  mdlWorkerOut$Att$diagSlopesCoreSdt[[1]],
+  mdlWorkerOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
+  mdlWorkerOut$Att$diagSlopesCoreSdt[[3]],
+  mdlWorkerOut$Att$diagSlopesCoreSdt[[4]]
+)
+
+# Plot prediction model
+mdlWorkerOut$Att$predSlopesCoreSdt <- 
+  workerOutgroupInteraction %>%
+  filter(!is.na(autonomy_1)) %>%
+  select(thermometerDutch_1, session, PID, autonomy_1) %>% 
+  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreSdt,
+                           workerOutgroupInteraction %>% filter(!is.na(autonomy_1)),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlWorkerOut$Att$predPltSlopesCoreSdt <-
+    ggplot(data = mdlWorkerOut$Att$predSlopesCoreSdt, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreStd.png",
+  mdlWorkerOut$Att$predPltSlopesCoreSdt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
 

### 2021-10-17 Supplemental-Material-B-Annotated-Analysis.Rmd
Update Supplemental-Material-B-Annotated-Analysis.Rmd

@@
 
+### Worker
+
 ```{r newVarsWorkers}
@@
 
+### Student
+
 ```{r newVarsStudents}
@@
 rm(df)
-```
+
+# Between participants contact frequency
+studentContactFreq <- dtStudents$full %>%
+  group_by(PID) %>%
+  summarise(
+    n = n(),
+    SumContactNL = sum(InteractionDumDutch),
+    PercContactNL = SumContactNL / n * 100,
+    SumContactNLAll = sum(ContactNum[InteractionDumDutch == 1], na.rm = TRUE),
+    AvAttitude = mean(AttitudesDutch, na.rm = TRUE)
+  ) %>%
+  mutate(
+    WinSumContactNL = DescTools::Winsorize(SumContactNL),
+    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
+  )
+
+# dataframe where interaction types are recoded
+studentInteractionType <- dtStudents$full %>%
+  mutate(
+    NonDutchContact = replace_na(NonDutchContact, 2), # make second non-Dutch countable
+    NonDutchContact = NonDutchContact*-1+2 # recode (yes = 1 -> 1, no = 2 -> 0)
+  ) %>%
+  mutate(
+    OutgroupInteraction = factor(
+      InteractionDumDutch,
+      levels = c(0, 1),
+      labels = c("No", "Yes")
+    ),
+    NonOutgroupInteraction = factor(
+      rowSums(select(., c(InteractionDumNonDutch, NonDutchContact))), # combine the two non-Dutch Q.,
+      levels = c(0, 1),
+      labels = c("No", "Yes")
+    )
+  )
+```
+
+### Medical
 
@@
 
+## Data Description
+
+<i class="fas fa-exclamation-triangle"></i> Still in 'scr/studentDescriptive.R'. Needs to be merged with this document.
+
 ## Contact Hypothesis
 
+### Interaction Frequency and Outgroup Attitudes
+
+\begin{equation}
+(\#eq:studentFreqQualR)
+r_{ContactFrequency, OutgroupAttitudes} \neq 0
+\end{equation}
+
+```{r studentFreqAttCor}
+# correlation panel
+pairs.panels.new(
+  studentContactFreq %>% select(SumContactNL, SumContactNLAll, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
+    "Sum:\nNumber of Outgroup Contacts (NL)",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+
+# correlation panel with interaction sums winsorized
+pairs.panels.new(
+  studentContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
+    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+```
+
+TL;DR: Neither the number of interactions nor the number of measurement beeps with an interaction are significantly related with the average outgroup attitudes.
+This is to say that within our data participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
+This might be due to the aggregation within the participants or the small sample size of between participant data.
+Nonetheless, the aggregate data does not support the notion that simply having more interactions with an outgroup results in more positive outgroup attitudes.
+
+### Outgroup Attitudes by Interaction Type
+
+\begin{equation}
+(\#eq:studentIntTypeQual)
+\mu_{i,0utgroupInteraction} > \mu_{i,IngroupInteraction}  \\
+Attitude = OutgroupInteraction \times NonOutgroupInteraction
+\end{equation}
+
+<div class="alert alert-info alert-dismissible fade in" role="alert">
+  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
+  <i class="fas fa-exclamation-triangle"></i> <b>Note: </b><br/>
+  mean difference alone probably even more stupid than only ignoring nested data, because we drop lots of data unnecessarily.  
+  And only outgroup interaction Yes / No also weird because interaction group includes people who had only an outgroup interaction and those who also had an interaction with a non-outgroup person, and the no outgroup interaction group includes those who had no interaction at all and those who had an interaction with a non-outgroup person (but no outgroup interaction).
+</div>
+
+#### Regression with interaction term
+
+Across participants: impact of different interaction types [probably meaningless because ignores response sets between participants]
+
+```{r studentInteractionTypePlt, fig.height=12}
+# between participants interaction type
+studentContactType <- studentInteractionType %>%
+  group_by(
+    OutgroupInteraction,
+    NonOutgroupInteraction
+  ) %>%
+  summarise(
+    n = n(),
+    AttitudeM = mean(AttitudesDutch, na.rm = TRUE),
+    AttitudeSD = sd(AttitudesDutch, na.rm = TRUE),
+    AttitudeSE = AttitudeSD / sqrt(n),
+    AttitudeLwr = AttitudeM - 1.96 * AttitudeSE,
+    AttitudeUpr = AttitudeM + 1.96 * AttitudeSE
+  ) %>%
+  ungroup()
+
+# plot bar chart
+ggplot(
+  studentContactType,
+  aes(
+    y = AttitudeM,
+    x = OutgroupInteraction,
+    fill = NonOutgroupInteraction
+  )
+) +
+  geom_bar(
+    stat = "identity",
+    color = "black",
+    position = position_dodge()
+  ) +
+  geom_errorbar(aes(ymin = AttitudeM, ymax = AttitudeUpr),
+    width = .2,
+    position = position_dodge(.9)
+  ) +
+  labs(
+    fill = "Non-Outgroup Interaction",
+    x = "Outgroup Interaction",
+    y = "Outgroup Attitude",
+    title = "Outgroup Attitudes by Interaction Type [95% CI]"
+  ) +
+  scale_fill_grey(
+    start = 0.2,
+    end = 0.8
+  ) +
+  scale_y_continuous(
+    limits = c(0, 100),
+    breaks = c(0, 15, 30, 40, 50, 60, 70, 85, 100),
+    labels = c(
+      "Very cold or unfavorable feelings 0°",
+      "Quite cold and unfavorable feelings 15°",
+      "Fairly cold and unfavorable feelings 30°",
+      "A bit cold and unfavorable feelings 40°",
+      "No feeling at all 50°",
+      "A bit warm and favorable feelings 60°",
+      "Fairly warm and favorable feelings 70° ",
+      "Quite warm and favorable feelings 85° ",
+      "Very warm and favorable feelings 100° "
+    )
+  ) +
+  theme_Publication()
+```
+
+```{r studentModelOlsInteractionType}
+# create list to store student models
+mdlStudent <- list()
+
+# regression
+mdlStudent$lmAttInt <-
+  lm(AttitudesDutch ~ OutgroupInteraction * NonOutgroupInteraction,
+    data = studentInteractionType
+  )
+# summary(lmstudentAttInteraction)
+
+summ(
+  mdlStudent$lmAttInt,
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+```
+
+TL;DR: While controlling for interactions with non-Dutch people, outgroup attitudes were significantly higher when participants had an interaction with a Dutch person.
+The effect is relatively small (`r format(round(mdlStudent$lmAttInt$coefficients["OutgroupInteractionYes"], 2), nsmall=2)` points on a 0--100 scale).
+More importantly, however, this analysis lumps all ESM beeps from every participants together and ignores that the data is nested within participants.
+
+#### ML Regression with interaction term
+
+##### Unconditional model
+
+make a model with only the data but a random intercept (unconditional model)
+
+\begin{equation}
+(\#eq:studentEmptyModel)
+Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentModelMLAttNull}
+# Create and save Model
+mdlStudent$lmerAttNull <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
+    data = dtStudents$full
+  ) # use optim if it does not converge
+
+mdlStudent$lmeAttNull <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = dtStudents$full,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(mdlStudent$lmerAttNull) #or with the lme function
+summ(mdlStudent$lmerAttNull, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlStudent$varAttNull <- 
+  VarCorr(mdlStudent$lmeAttNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlStudent$tauAttNull <- 
+  as.numeric(mdlStudent$varAttNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlStudent$sigmaAttNull <- 
+  as.numeric(mdlStudent$varAttNull[2])
+# The ICC estimate (between/between+within) is:
+mdlStudent$IccAttNull <-
+  (as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))
+mdlStudent$IccPercAttNull <-
+  ((as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))) * 100
+```
+
+ICC $\tau_{00}^2 / (\tau_{00}^2 + \sigma^2)$: The ratio of the between-cluster variance to the total variance is called the Intraclass Correlation.
+It tells you the proportion of the total variance in Y that is accounted for by the clustering.
+(In this case the clustering means clustering observations per participant)
+
+compare the random intercept model to a model without a random intercept (i.e., without levels at all)
+
+```{r studentModelInterceptNull}
+# Create and save Model
+mdlStudent$glsAttNull  <-
+  gls(AttitudesDutch ~ 1,
+      data = dtStudents$full,
+      control = list(opt = "nlmimb"))
+
+# calculate Deviances manually:
+mdlStudent$DevianceGlsNull <- logLik(mdlStudent$glsAttNull) * -2
+mdlStudent$DevianceMlNull <- logLik(mdlStudent$lmeAttNull) * -2
+
+# Compare the two null models:
+anova(mdlStudent$glsAttNull,
+      mdlStudent$lmeAttNull) %>% 
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+```
+
+We find that an estimated `r format(round(mdlStudent$IccPercAttNull, 2), nsmall=2)`% of the variation in Feeling Thermometer scores is explained by between participant differences (clustering by PID).
+This is to say that `r format(round(mdlStudent$IccPercAttNull, 2), nsmall=2)`% of the variance in any individual report of Attitudes towards the Dutch can be explained by the properties of the individual who provided the rating.
+And we find that including 'participant' as a predictor adds significantly to the model.
+
+##### random intercept
+
+\begin{equation}
+(\#eq:StudentInteractionTypeModel)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentModelInterceptAttType}
+# Create and save Model
+mdlStudent$lmeInterceptAttType <-
+  lme(
+    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
+    random =  ~ 1 | PID,
+    data = studentInteractionType
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  lmer(
+    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    data = studentInteractionType
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudent$lmeAttNull, 
+      mdlStudent$lmeInterceptAttType) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudent$varInterceptAttType <- 
+  lme4::VarCorr(mdlStudent$lmeInterceptAttType)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudent$varBtwInterceptAttType <-
+  1 - (as.numeric(mdlStudent$varInterceptAttType[1]) / as.numeric(mdlStudent$varAttNull[1]))
+mdlStudent$varBtwPercInterceptAttType <-
+  (1 - (as.numeric(mdlStudent$varInterceptAttType[1]) / as.numeric(mdlStudent$varAttNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudent$varWithinInterceptAttType <-
+  1 - (as.numeric(mdlStudent$varInterceptAttType[2]) / as.numeric(mdlStudent$varAttNull[2]))
+mdlStudent$varWithinPercInterceptAttType <-
+  (1 - (as.numeric(mdlStudent$varInterceptAttType[2]) / as.numeric(mdlStudent$varAttNull[2]))) * 100
+```
+
+tl;dr: Interaction with Dutch is great predictor, interactions with non-Dutch is not.
+
+##### random slope
+
+\begin{equation}
+(\#eq:RandSlopesEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentModelSlopesInteractionType}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudent$lmeSlopesAttType <- lme(
+  AttitudesDutch ~
+    OutgroupInteraction + NonOutgroupInteraction,
+  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  data = studentInteractionType
+)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudent$lmerSlopesAttType <- lmer(
+    AttitudesDutch ~
+      OutgroupInteraction + NonOutgroupInteraction +
+      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+    data = studentInteractionType
+  ), 
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudent$lmeInterceptAttType, 
+      mdlStudent$lmeSlopesAttType) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudent$varSlopesAttType <- 
+  lme4::VarCorr(mdlStudent$lmeSlopesAttType)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudent$varBtwSlopesAttType <- 
+  1 - (as.numeric(mdlStudent$varSlopesAttType[1]) / as.numeric(mdlStudent$varInterceptAttType[1]))
+mdlStudent$varBtwPercSlopesAttType <- 
+  (1 - (as.numeric(mdlStudent$varSlopesAttType[1]) / as.numeric(mdlStudent$varInterceptAttType[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudent$varWithinSlopesAttType <- 
+  1 - (as.numeric(mdlStudent$varSlopesAttType[2]) / as.numeric(mdlStudent$varInterceptAttType[2]))
+mdlStudent$varWithinPercSlopesAttType <- 
+  (1 - (as.numeric(mdlStudent$varSlopesAttType[2]) / as.numeric(mdlStudent$varInterceptAttType[2]))) * 100
+
+# Assumption Checks:
+mdlStudent$diagSlopesAttType <-
+  sjPlot::plot_model(mdlStudent$lmerSlopesAttType, type = "diag")
+grid.arrange(
+  mdlStudent$diagSlopesAttType[[1]],
+  mdlStudent$diagSlopesAttType[[2]]$`PID`,
+  mdlStudent$diagSlopesAttType[[3]],
+  mdlStudent$diagSlopesAttType[[4]]
+)
+
+# Plot prediction model
+mdlStudent$predSlopesAttType <- 
+  studentInteractionType %>%
+  select(AttitudesDutch, session, PID) %>% 
+  mutate(measure = predict(mdlStudent$lmeSlopesAttType,
+                           studentInteractionType,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudent$predPltSlopesAttType <-
+    ggplot(data = mdlStudent$predSlopesAttType, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/Student_PredictionPlot_SlopesAttType.png",
+  mdlStudent$predPltSlopesAttType,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+TL;DR: Random slopes don't add much for this super simple model.
+
+### Interaction Frequency and Interaction Quality
+
+\begin{equation}
+(\#eq:FreqQual)
+Attitude = ContactFreq \times AverageContactQual
+\end{equation}
+
+```{r studentFreqQualCor}
+# prepare data
+studentAvFreQual <- dtStudents$full %>%
+  group_by(ExternalReference) %>%
+  summarise(
+    n = n(),
+    SumContactNL = sum(Contact_dum),
+    PercContactNL = SumContactNL / n * 100,
+    SumContactNLAll = sum(number),
+    AvAttitude = mean(AttitudesDutch, na.rm = TRUE),
+    AvQuality = mean(quality_overall_1, na.rm = TRUE)
+  ) %>%
+  mutate(
+    WinSumContactNL = DescTools::Winsorize(SumContactNL),
+    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
+  )
+
+# correlation panel
+pairs.panels.new(
+  studentAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
+    "Sum:\nNumber of Outgroup Contacts (NL)",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+
+# correlation panel with interaction sums winsorized
+pairs.panels.new(
+  studentAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
+    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+```
+
+TL;DR: There is a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
+Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
+However, the frequency of intergroup interactions had no meaningfull correlation with either the average interaction quality or average outgroup attitudes.
+
+```{r studentModelOlsAttFreqQual}
+# regression
+mdlStudent$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL * AvQuality, data = studentAvFreQual)
+# summary(mdlStudent$lmAttFreqQualX)
+
+summ(
+  mdlStudent$lmAttFreqQualX,
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+interactions::interact_plot(
+  mdlStudent$lmAttFreqQualX,
+  pred = AvQuality,
+  modx = SumContactNL,
+  interval = TRUE,
+  partial.residuals = TRUE
+)
+
+interactions::johnson_neyman(mdlStudent$lmAttFreqQualX,
+                             pred = AvQuality,
+                             modx = SumContactNL,
+                             alpha = .05)
+```
+
+TL;DR: We find that interaction quality is significantly related to higher outgroup attitudes (albeit with a small effect size).
+We also find that in our sample with an increasing number of interactions the positive effect of interaction quality becomes weaker.
+However, note that this is based on data aggregating all within participant nuances and is only the date of 21 people.
+
 ## Need Fulfillment
+
+### Need fulfillment and Attitudes
+
+##### Unconditional model
+
+make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
+
+```{r studentPrepOutgroupSubsample}
+# see how large our outgroup interaction subset actually is
+tbl_cross(
+  studentInteractionType,
+  row = OutgroupInteraction,
+  col = NonOutgroupInteraction,
+  percent = "row"
+)
+
+# create outgroup interaction subset
+studentOutgroupInteraction <- studentInteractionType %>%
+  filter(OutgroupInteraction == "Yes")
+
+# create empty list to organize models
+mdlStudentOut <- 
+  list(
+    Att = list(),
+    Qlt = list()
+  )
+```
+
+\begin{equation}
+(\#eq:studentOutEmptyModel)
+Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentOutModelMLAttNull}
+# Create and save Model
+mdlStudentOut$Att$lmerNull <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), 
+             data = studentOutgroupInteraction) # use optim if it does not converge
+mdlStudentOut$Att$lmeNull <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = studentOutgroupInteraction,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.ML.r) #or with the lme function
+summ(mdlStudentOut$Att$lmerNull, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlStudentOut$Att$varNull <- 
+  VarCorr(mdlStudentOut$Att$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlStudentOut$Att$tauNull <- 
+  as.numeric(mdlStudentOut$Att$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlStudentOut$Att$sigmaNull <- 
+  as.numeric(mdlStudentOut$Att$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlStudentOut$Att$IccNull <-
+  (as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))
+mdlStudentOut$Att$IccPercNull <-
+  ((as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))) * 100
+```
+
+#### random intercept
+
+\begin{equation}
+(\#eq:AttitudeNeedEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentOutModelInterceptAttCore}
+# Create and save Model
+mdlStudentOut$Att$lmeInterceptCore <-
+  lme(
+    AttitudesDutch ~ keymotive_fulfillemt_1,
+    random = ~ 1 | PID,
+    data = studentOutgroupInteraction
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  lmer(AttitudesDutch ~ keymotive_fulfillemt_1 + (1 | PID), 
+       data = studentOutgroupInteraction),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudentOut$Att$lmeNull, 
+      mdlStudentOut$Att$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Att$varInterceptCore <-
+  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCore)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudentOut$Att$varBtwInterceptCore <- 
+  1 - (as.numeric(mdlStudentOut$Att$varInterceptCore[1]) / as.numeric(mdlStudentOut$Att$varNull[1]))
+mdlStudentOut$Att$varBtwPercInterceptCore <- 
+  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCore[1]) / as.numeric(mdlStudentOut$Att$varNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudentOut$Att$varWithinInterceptCore <-
+  1 - (as.numeric(mdlStudentOut$Att$varInterceptCore[2]) / as.numeric(mdlStudentOut$Att$varNull[2]))
+mdlStudentOut$Att$varWithinPercInterceptCore <-
+  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCore[2]) / as.numeric(mdlStudentOut$Att$varNull[2]))) * 100
+```
+
+TL;DR: Situational core need relates significantly to outgroup attitudes.
+The core need has little explained variance between participants (compared to the null model: Variance Explained = 1 – (Var with Predictor/Var without Predictor); `r format(round(mdlStudentOut$Att$varBtwPercInterceptCore, 2),nsmall=2)`%).
+The variance explained within participants is small to medium (`r format(round(mdlStudentOut$Att$varWithinPercInterceptCore, 2),nsmall=2)`%)
+
+#### random slope
+
+\begin{equation}
+(\#eq:AttitudeNeedRandEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentOutModelSlopesAttCore}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudentOut$Att$lmeSlopesCore <-
+  lme(
+    AttitudesDutch ~
+      keymotive_fulfillemt_1,
+    random = ~ 1 + keymotive_fulfillemt_1 | PID,
+    control = lmeControl(opt = "optim"),
+    data = studentOutgroupInteraction
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudentOut$Att$lmerSlopesCore <- lmer(
+    AttitudesDutch ~
+      keymotive_fulfillemt_1 +
+      (1 + keymotive_fulfillemt_1 | PID),
+    data = studentOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudentOut$Att$lmeInterceptCore, 
+      mdlStudentOut$Att$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Att$varSlopesCore <- 
+  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCore)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudentOut$Att$varBtwSlopesCore <-
+  1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))
+mdlStudentOut$Att$varBtwPercSlopesCore <-
+  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudentOut$Att$varWithinSlopesCore <-
+  1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))
+mdlStudentOut$Att$varWithinPercSlopesCore <-
+  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))) * 100
+
+# Assumption Checks:
+mdlStudentOut$Att$diagSlopesCore <- 
+  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlStudentOut$Att$diagSlopesCore[[1]],
+  mdlStudentOut$Att$diagSlopesCore[[2]]$`PID`,
+  mdlStudentOut$Att$diagSlopesCore[[3]],
+  mdlStudentOut$Att$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlStudentOut$Att$predSlopesCore <- 
+  studentOutgroupInteraction %>%
+  select(AttitudesDutch, session, PID) %>% 
+  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCore,
+                           studentOutgroupInteraction,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudentOut$Att$predPltSlopesCore <-
+    ggplot(data = mdlStudentOut$Att$predSlopesCore, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCore.png",
+  mdlStudentOut$Att$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+TL;DR: The random slope adds significantly to the prediction model.
+
+<div class="alert alert-warning alert-dismissible fade in" role="alert">
+  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
+  <i class="fas fa-exclamation-triangle"></i> <b>Check needed: </b><br/>
+  Something is with the variances explained (between = `r format(round(mdlStudentOut$Att$varBtwPercSlopesCore, 2),nsmall=2)`%, within = `r format(round(mdlStudentOut$Att$varWithinPercSlopesCore, 2),nsmall=2)`%).
+This is when comparing the random intercepts to the random slopes model.
+</div>
+
+### Need fulfillment and Interaction Quality
+
+##### Unconditional model
+
+make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
+
+\begin{equation}
+(\#eq:studentOutQualEmptyModel)
+Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentOutModelMLQltNull}
+# Create and save Model
+mdlStudentOut$Qlt$lmerNull <-
+  lme4::lmer(quality_overall_1 ~ 1 + (1 | PID), 
+             data = studentOutgroupInteraction) # use optim if it does not converge
+mdlStudentOut$Qlt$lmeNull <-
+  lme(
+    quality_overall_1 ~ 1,
+    random = ~ 1 | PID,
+    data = studentOutgroupInteraction,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.Qual.ML.r) #or with the lme function
+summ(mdlStudentOut$Qlt$lmerNull, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlStudentOut$Qlt$varNull <- 
+  VarCorr(mdlStudentOut$Qlt$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlStudentOut$Qlt$tauNull <- 
+  as.numeric(mdlStudentOut$Qlt$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlStudentOut$Qlt$sigmaNull <- 
+  as.numeric(mdlStudentOut$Qlt$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlStudentOut$Qlt$IccNull <-
+  (as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))
+mdlStudentOut$Qlt$IccPercNull <-
+  ((as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))) * 100
+```
+
+#### random intercept
+
+\begin{equation}
+(\#eq:QualityNeedEq)
+InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentOutModelInterceptQltCore}
+# Create and save Model
+mdlStudentOut$Qlt$lmeInterceptCore <-
+  lme(
+    quality_overall_1 ~ keymotive_fulfillemt_1,
+    random = ~ 1 | PID,
+    data = studentOutgroupInteraction
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  lmer(quality_overall_1 ~ keymotive_fulfillemt_1 + (1 | PID), 
+       data = studentOutgroupInteraction),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(quality_overall_1 ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudentOut$Qlt$lmeNull, 
+      mdlStudentOut$Qlt$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Qlt$varInterceptCore <-
+  lme4::VarCorr(mdlStudentOut$Qlt$lmeInterceptCore)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudentOut$Qlt$varBtwInterceptCore <- 
+  1 - (as.numeric(mdlStudentOut$Qlt$varInterceptCore[1]) / as.numeric(mdlStudentOut$Qlt$varNull[1]))
+mdlStudentOut$Qlt$varBtwPercInterceptCore <- 
+  (1 - (as.numeric(mdlStudentOut$Qlt$varInterceptCore[1]) / as.numeric(mdlStudentOut$Qlt$varNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudentOut$Qlt$varWithinInterceptCore <-
+  1 - (as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]) / as.numeric(mdlStudentOut$Qlt$varNull[2]))
+mdlStudentOut$Qlt$varWithinPercInterceptCore <-
+  (1 - (as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]) / as.numeric(mdlStudentOut$Qlt$varNull[2]))) * 100
+```
+
+TL;DR: Situational core need relates significantly to interaction quality.
+The core need explained substantial variance between participants (`r format(round(mdlStudentOut$Qlt$varBtwPercInterceptCore, 2),nsmall=2)`%).
+The variance explained within participants is also medium (`r format(round(mdlStudentOut$Qlt$varWithinPercInterceptCore, 2),nsmall=2)`%)
+
+#### random slope
+
+\begin{equation}
+(\#eq:QualityNeedRandEq)
+InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentOutModelSlopesQltCore}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudentOut$Qlt$lmeSlopesCore <-
+  lme(
+    quality_overall_1 ~
+      keymotive_fulfillemt_1,
+    random = ~ 1 + keymotive_fulfillemt_1 | PID,
+    control = lmeControl(opt = "optim"),
+    data = studentOutgroupInteraction
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudentOut$Qlt$lmerSlopesCore <-
+    lmer(
+      quality_overall_1 ~
+        keymotive_fulfillemt_1 +
+        (1 + keymotive_fulfillemt_1 | PID),
+      data = studentOutgroupInteraction
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(mdlStudentOut$Qlt$lmerSlopesCore,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudentOut$Qlt$lmeInterceptCore, 
+      mdlStudentOut$Qlt$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Qlt$varSlopesCore <- 
+  lme4::VarCorr(mdlStudentOut$Qlt$lmeSlopesCore)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudentOut$Qlt$varBtwSlopesCore <-
+  1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[1]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[1]))
+mdlStudentOut$Qlt$varBtwPercSlopesCore <-
+  (1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[1]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudentOut$Qlt$varWithinSlopesCore <-
+  1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[2]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]))
+mdlStudentOut$Qlt$varWithinPercSlopesCore <-
+  (1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[2]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]))) * 100
+```
+
+TL;DR: random slopes does not add significantly. Stay with simpler model.
+
+### Need fulfillment, Interaction Quality, and Attitudes
+
+#### random intercept
+
+\begin{equation}
+(\#eq:AttitudeQualityNeedEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentOutModelInterceptAttCoreQlt}
+# Create and save Model
+mdlStudentOut$Att$lmeInterceptCoreQlt <-
+  lme(
+    AttitudesDutch ~ keymotive_fulfillemt_1 + quality_overall_1,
+    random = ~ 1 | PID,
+    data = studentOutgroupInteraction
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  lmer(
+    AttitudesDutch ~ keymotive_fulfillemt_1 + quality_overall_1 + (1 | PID),
+    data = studentOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlStudentOut$Att$lmeNull, 
+  mdlStudentOut$Att$lmeInterceptCoreQlt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Att$varInterceptCoreQlt <-
+  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreQlt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudentOut$Att$varBtwInterceptCoreQlt <- 
+  1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[1]) / as.numeric(mdlStudentOut$Att$varNull[1]))
+mdlStudentOut$Att$varBtwPercInterceptCoreQlt <- 
+  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[1]) / as.numeric(mdlStudentOut$Att$varNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudentOut$Att$varWithinInterceptCoreQlt <-
+  1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[2]) / as.numeric(mdlStudentOut$Att$varNull[2]))
+mdlStudentOut$Att$varWithinPercInterceptCoreQlt <-
+  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[2]) / as.numeric(mdlStudentOut$Att$varNull[2]))) * 100
+```
+
+TL;DR: Variance explained in outgroup attitudes is of medium effect size (between: `r format(round(mdlStudentOut$Att$varBtwPercInterceptCoreQlt,2),nsmall=2)`%, within: `r format(round(mdlStudentOut$Att$varWithinPercInterceptCoreQlt,2),nsmall=2)`%)
+
+#### random slope
+
+\begin{equation}
+(\#eq:AttitudeQualityNeedRandEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentOutModelSlopesAttCoreQlt}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudentOut$Att$lmeSlopesCoreQlt <-
+  lme(
+    AttitudesDutch ~
+      keymotive_fulfillemt_1 + quality_overall_1,
+    random = ~ 1 + keymotive_fulfillemt_1 + quality_overall_1 | PID,
+    control = lmeControl(opt = "optim"),
+    data = studentOutgroupInteraction
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudentOut$Att$lmerSlopesCoreQlt <- lmer(
+    AttitudesDutch ~
+      keymotive_fulfillemt_1 + quality_overall_1 +
+      (1 + keymotive_fulfillemt_1 + quality_overall_1 | PID),
+    data = studentOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlStudentOut$Att$lmeNull,
+  mdlStudentOut$Att$lmeInterceptCoreQlt,
+  mdlStudentOut$Att$lmeSlopesCoreQlt
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Att$varSlopesCoreQlt <- 
+  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreQlt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudentOut$Att$varBtwSlopesCoreQlt <-
+  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[1]))
+mdlStudentOut$Att$varBtwPercSlopesCoreQlt <-
+  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudentOut$Att$varWithinSlopesCoreQlt <-
+  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[2]))
+mdlStudentOut$Att$varWithinPercSlopesCoreQlt <-
+  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[2]))) * 100
+
+# Assumption Checks:
+mdlStudentOut$Att$diagSlopesCoreQlt <- 
+  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreQlt, type = "diag")
+grid.arrange(
+  mdlStudentOut$Att$diagSlopesCoreQlt[[1]],
+  mdlStudentOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
+  mdlStudentOut$Att$diagSlopesCoreQlt[[3]],
+  mdlStudentOut$Att$diagSlopesCoreQlt[[4]]
+)
+
+# Plot prediction model
+mdlStudentOut$Att$predSlopesCoreQlt <- 
+  studentOutgroupInteraction %>%
+  select(AttitudesDutch, session, PID) %>% 
+  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreQlt,
+                           studentOutgroupInteraction,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudentOut$Att$predPltSlopesCoreQlt <-
+    ggplot(data = mdlStudentOut$Att$predSlopesCoreQlt, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreQlt.png",
+  mdlStudentOut$Att$predPltSlopesCoreQlt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+#### Compare models
+
+Interpretation of Mediation like results.
+
+### Check for robustness
+
+#### Interaction Type
+
+##### random intercept
+
+\begin{equation}
+(\#eq:AttitudeNeedInteractionEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentModelInterceptAttCoreInt}
+# Create and save Model
+mdlStudent$lmeInterceptAttCoreInt <-
+  lme(
+    AttitudesDutch ~ keyMotiveFulfilled * OutgroupInteraction,
+    random =  ~ 1 | PID,
+    data = studentInteractionType
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlStudent$lmerInterceptAttCoreInt <- lmer(
+    AttitudesDutch ~ keyMotiveFulfilled * OutgroupInteraction + (1 | PID),
+    data = studentInteractionType
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudent$lmeAttNull, 
+      mdlStudent$lmeInterceptAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudent$varInterceptAttCoreInt <- 
+  lme4::VarCorr(mdlStudent$lmeInterceptAttCoreInt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudent$varBtwInterceptAttCoreInt <-
+  1 - (as.numeric(mdlStudent$varInterceptAttCoreInt[1]) / as.numeric(mdlStudent$varAttNull[1]))
+mdlStudent$varBtwPercInterceptAttCoreInt <-
+  (1 - (as.numeric(mdlStudent$varInterceptAttCoreInt[1]) / as.numeric(mdlStudent$varAttNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudent$varWithinInterceptAttCoreInt <-
+  1 - (as.numeric(mdlStudent$varInterceptAttCoreInt[2]) / as.numeric(mdlStudent$varAttNull[2]))
+mdlStudent$varWithinPercInterceptAttCoreInt <-
+  (1 - (as.numeric(mdlStudent$varInterceptAttCoreInt[2]) / as.numeric(mdlStudent$varAttNull[2]))) * 100
+```
+
+##### random slope
+
+\begin{equation}
+(\#eq:AttitudeNeedInteractionRandEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti}  + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentModelSlopesAttCoreIntX}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudent$lmeSlopesAttCoreInt <- lme(
+  AttitudesDutch ~
+    keyMotiveFulfilled * OutgroupInteraction,
+  random = ~ 1 + keyMotiveFulfilled + OutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  data = studentInteractionType
+)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudent$lmerSlopesAttCoreInt <- lmer(
+    AttitudesDutch ~
+      keyMotiveFulfilled * OutgroupInteraction +
+      (1 + keyMotiveFulfilled + OutgroupInteraction | PID),
+    data = studentInteractionType
+  ), 
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudent$lmeAttNull, 
+      mdlStudent$lmeInterceptAttCoreInt,
+      mdlStudent$lmeSlopesAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudent$varSlopesAttCoreInt <- 
+  lme4::VarCorr(mdlStudent$lmeSlopesAttCoreInt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudent$varBtwSlopesAttCoreInt <- 
+  1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[1]) / as.numeric(mdlStudent$varInterceptAttCoreInt[1]))
+mdlStudent$varBtwPercSlopesAttCoreInt <- 
+  (1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[1]) / as.numeric(mdlStudent$varInterceptAttCoreInt[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudent$varWithinSlopesAttCoreInt <- 
+  1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[2]) / as.numeric(mdlStudent$varInterceptAttCoreInt[2]))
+mdlStudent$varWithinPercSlopesAttCoreInt <- 
+  (1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[2]) / as.numeric(mdlStudent$varInterceptAttCoreInt[2]))) * 100
+
+# Assumption Checks:
+mdlStudent$diagSlopesAttCoreInt <-
+  sjPlot::plot_model(mdlStudent$lmerSlopesAttCoreInt, type = "diag")
+grid.arrange(
+  mdlStudent$diagSlopesAttCoreInt[[1]],
+  mdlStudent$diagSlopesAttCoreInt[[2]]$`PID`,
+  mdlStudent$diagSlopesAttCoreInt[[3]],
+  mdlStudent$diagSlopesAttCoreInt[[4]]
+)
+
+# Plot prediction model
+mdlStudent$predSlopesAttCoreInt <- 
+  studentInteractionType %>%
+  select(AttitudesDutch, session, PID) %>% 
+  mutate(measure = predict(mdlStudent$lmeSlopesAttCoreInt,
+                           studentInteractionType,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudent$predPltSlopesAttCoreInt <-
+    ggplot(data = mdlStudent$predSlopesAttCoreInt, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/Student_PredictionPlot_SlopesAttCoreInt.png",
+  mdlStudent$predPltSlopesAttCoreInt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+##### Plot Interaction
+
+```{r studentModelInterceptAttCoreIntPlt}
+# visualize interaction
+## Without ML structure
+ggplot(data = studentInteractionType,
+       aes(x = keyMotiveFulfilled,
+           y = AttitudesDutch,
+           fill = OutgroupInteraction)) +
+  #geom_point()+
+  geom_smooth(method = 'lm',
+              aes(linetype = OutgroupInteraction),
+              color = "black") +
+  #facet_wrap(~PID, ncol = 6)+
+  scale_linetype_manual(values = c("dashed", "solid")) +
+  scale_fill_manual(values = c("darkgrey", "black")) +
+  #scale_colour_manual(values=c("grey20", "black"), name="Intergroup Contact")+
+  scale_y_continuous(
+    limits = c(50, 100),
+    breaks = seq(50, 100, by = 10),
+    position = "left"
+  ) +
+  scale_x_continuous(limits = c(-50, 50), breaks = seq(-50, 50, by = 10)) +
+  labs(
+    title = "Without ML stucture",
+    x = "Fulfillment Core Need",
+    y = "Outgroup Attitudes",
+    fill = "Intergroup Contact",
+    linetype = "Intergroup Contact"
+  ) +
+  theme_Publication() +
+  theme(legend.position = "bottom",
+        legend.key.size = unit(1, "cm"))
+## With ML structure
+# create parameters for prediction
+datNew = data.frame(
+  OutgroupInteraction = factor(rep(c("No", "Yes"), each = 21)),
+  keyMotiveFulfilled = rep(seq(-50, 50, 5), 2),
+  PID = 0
+)
+
+# Predict values, clean up and calculate SE
+PI <-
+  merTools::predictInterval(
+    merMod = mdlStudent$lmerSlopesAttCoreInt,
+    newdata = datNew,
+    level = 0.95,
+    stat = "mean",
+    type = "linear.prediction",
+    include.resid.var = F,
+    fix.intercept.variance = F
+  )
+mdlStudent$predInterceptAttCoreIntX <- 
+  cbind(datNew, PI)
+mdlStudent$predInterceptAttCoreIntX$se <-
+  (mdlStudent$predInterceptAttCoreIntX$upr - mdlStudent$predInterceptAttCoreIntX$fit) / 1.96
+rm(datNew, PI)
+
+# Plot predicted values with SE
+ggplot(
+  mdlStudent$predInterceptAttCoreIntX,
+  aes(x = keyMotiveFulfilled,
+      y = fit,
+      fill = OutgroupInteraction)
+)+
+  #geom_point() +
+  geom_line(aes(linetype = as.factor(OutgroupInteraction)), size = 1) +
+  #facet_wrap(~PID, ncol = 6)+
+  geom_ribbon(data = mdlStudent$predInterceptAttCoreIntX,
+              aes(ymin = fit - se, ymax = fit + se),
+              alpha = 0.3) +
+  scale_x_continuous(breaks = seq(-50, 50, 10)) +
+  scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
+  scale_linetype_manual(values = c("dashed", "solid")) +
+  scale_fill_manual(values = c("darkgrey", "black")) +
+  labs(
+    x = "Fulfillment Core Need",
+    y = "Outgroup Attitude (NL)",
+    fill = "Intergroup Contact",
+    linetype = "Intergroup Contact",
+    title = "Based on Model Predictions"
+  ) +
+  theme_Publication()
+
+# #### Bayesian estimation !! ONLY RUN ON FINAL RENDER !! Takes forever ####
+# options(mc.cores = parallel::detectCores())  # Run many chains simultaneously
+# brmfit <- brm(
+#   AttitudesDutch ~ keyMotiveFulfilled * OutgroupInteraction + 
+#     (1 + keyMotiveFulfilled + OutgroupInteraction | PID),
+#   data = studentInteractionType,
+#   family = gaussian,
+#   iter = 1000,
+#   chains = 4
+# )
+# 
+# # create parameters for prediction:
+# datNew = data.frame(
+#   OutgroupInteraction = rep(c("No", "Yes"), each = 101),
+#   keyMotiveFulfilled = rep(seq(-50, 50, 1), 2)
+# )
+# # Save predicted values and adjust names and labels
+# fitavg <-
+#   cbind(datNew,
+#         fitted(brmfit, newdata = datNew, re_formula = NA)[, -2])
+# names(fitavg)[names(fitavg) == "Estimate"] = "pred"
+# fitavg$se <- (fitavg$Q97.5 - fitavg$pred) / 1.96
+# 
+# # Plot Bayesian SE prediction interval
+# ggplot(fitavg,
+#        aes(x = keyMotiveFulfilled,
+#            y = pred,
+#            fill = OutgroupInteraction)) +
+#   scale_x_continuous(breaks = seq(-50, 50, 10)) +
+#   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
+#   geom_line(aes(linetype = OutgroupInteraction), size = 1) +
+#   geom_ribbon(aes(ymin = pred - se, ymax = pred + se), alpha = 0.2) +
+#   scale_linetype_manual(values = c("dashed", "solid")) +
+#   scale_fill_manual(values = c("darkgrey", "black")) +
+#   labs(
+#     x = "Fulfillment Core Need",
+#     y = "Outgroup Attitude (NL)",
+#     fill = "Intergroup Contact",
+#     linetype = "Intergroup Contact",
+#     title = "Based on Bayesian Prediction Interval"
+#   ) +
+#   theme_Publication()
+# 
+# # plot all overlayed posteriors:
+# pst <- posterior_samples(brmfit, "b")
+# ggplot(studentInteractionType,
+#        aes(x = keyMotiveFulfilled, y = AttitudesDutch)) +
+#   geom_point(shape = 4, alpha = .1) +
+#   geom_tile() +
+#   geom_abline(
+#     data = pst,
+#     aes(intercept = b_Intercept, slope = b_keyMotiveFulfilled),
+#     alpha = .025,
+#     size = .4
+#   ) +
+#   labs(title = "slope Posteriors",
+#        x = "Fulfillment Core Need",
+#        y = "Outgroup Attitudes (NL)") +
+#   theme_Publication()
+# rm(datNew, brmfit, fitavg, pst)
+```
+
+#### Other psychological needs
+
+##### random intercept
+
+\begin{equation}
+(\#eq:AttitudeNeedSdtEq)
+Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + e_{ti} \\
+\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentOutModelInterceptAttCoreSdt}
+# Create and save Model
+mdlStudentOut$Att$lmeInterceptCoreSdt <-
+  lme(
+    AttitudesDutch ~ keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1,
+    random = ~ 1 | PID,
+    data = studentOutgroupInteraction,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlStudentOut$Att$lmerInterceptCoreSdt <- lmer(
+    AttitudesDutch ~ keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 + (1 | PID),
+    data = studentOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# compute lme for core model with same number of observations for comparison
+# !! LOOK INTO MISSINGNESS (only one observation) !!
+lmeInterceptCoreRed <-
+  lme(
+    AttitudesDutch ~ keymotive_fulfillemt_1,
+    random = ~ 1 | PID,
+    data = studentOutgroupInteraction %>% filter(!is.na(autonomy_1))
+  )
+
+# Compare new model to previous step
+anova(
+  lmeInterceptCoreRed, 
+  mdlStudentOut$Att$lmeInterceptCoreSdt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+rm(lmeInterceptCoreRed)
+
+# Save variances
+mdlStudentOut$Att$varInterceptCoreSdt <-
+  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreSdt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudentOut$Att$varBtwInterceptCoreSdt <- 
+  1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))
+mdlStudentOut$Att$varBtwPercInterceptCoreSdt <- 
+  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudentOut$Att$varWithinInterceptCoreSdt <-
+  1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))
+mdlStudentOut$Att$varWithinPercInterceptCoreSdt <-
+  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))) * 100
+```
+
+##### random slope
+
+\begin{equation}
+(\#eq:AttitudeNeedSdtRandEq)
+Attitude_{ti} = \\gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
+\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+\end{equation}
+
+```{r studentOutModelSlopesAttCoreSdt}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudentOut$Att$lmeSlopesCoreSdt <-
+  lme(
+    AttitudesDutch ~
+      keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1,
+    random = ~ 1 + keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 | PID,
+    control = lmeControl(opt = "optim"),
+    data = studentOutgroupInteraction,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudentOut$Att$lmerSlopesCoreSdt <- lmer(
+    AttitudesDutch ~
+      keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 +
+      (1 + keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 | PID),
+    data = studentOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudentOut$Att$lmeInterceptCoreSdt, 
+      mdlStudentOut$Att$lmeSlopesCoreSdt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Att$varSlopesCoreSdt <- 
+  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreSdt)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlStudentOut$Att$varBtwSlopesCoreSdt <-
+  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]))
+mdlStudentOut$Att$varBtwPercSlopesCoreSdt <-
+  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlStudentOut$Att$varWithinSlopesCoreSdt <-
+  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]))
+mdlStudentOut$Att$varWithinPercSlopesCoreSdt <-
+  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]))) * 100
+
+# Assumption Checks:
+mdlStudentOut$Att$diagSlopesCoreSdt <- 
+  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreSdt, type = "diag")
+grid.arrange(
+  mdlStudentOut$Att$diagSlopesCoreSdt[[1]],
+  mdlStudentOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
+  mdlStudentOut$Att$diagSlopesCoreSdt[[3]],
+  mdlStudentOut$Att$diagSlopesCoreSdt[[4]]
+)
+
+# Plot prediction model
+mdlStudentOut$Att$predSlopesCoreSdt <- 
+  studentOutgroupInteraction %>%
+  filter(!is.na(autonomy_1)) %>%
+  select(AttitudesDutch, session, PID, autonomy_1) %>% 
+  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreSdt,
+                           studentOutgroupInteraction %>% filter(!is.na(autonomy_1)),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudentOut$Att$predPltSlopesCoreSdt <-
+    ggplot(data = mdlStudentOut$Att$predSlopesCoreSdt, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreStd.png",
+  mdlStudentOut$Att$predPltSlopesCoreSdt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
 

### 2021-10-18 Supplemental-Material-B-Annotated-Analysis.Rmd
AOT-S added

@@
     SumContactNLAll = sum(ContactNum[InteractionDumDutch == 1], na.rm = TRUE),
-    AvAttitude = mean(AttitudesDutch, na.rm = TRUE)
+    AvAttitude = mean(AttitudesDutch, na.rm = TRUE),
+    AvQuality = mean(quality_overall, na.rm = TRUE)
   ) %>%
@@
   )
+
+# select a subset of IDs to display in plots
+studentPltIDs <-
+  studentInteractionType %>%
+  group_by(PID) %>%
+  summarise(n = n()) %>%
+  slice_max(n, n = 20) %>% # chose the 20 with the most number of measurements
+  select(PID) %>%
+  as.matrix %>%
+  as.vector
+
+# select a subset of IDs to display in plots (only outgroup interactions)
+studentOutPltIDs <-
+  studentInteractionType %>%
+  filter(OutgroupInteraction == "Yes") %>%
+  group_by(PID) %>%
+  summarise(n = n()) %>%
+  slice_max(n, n = 20) %>% # chose the 20 with the most number of measurements
+  select(PID) %>%
+  as.matrix %>%
+  as.vector
 ```
@@
   studentInteractionType %>%
-  select(AttitudesDutch, session, PID) %>% 
+  select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlStudent$lmeSlopesAttType,
@@
   mdlStudent$predPltSlopesAttType <-
-    ggplot(data = mdlStudent$predSlopesAttType, aes(x = session, y = measure)) +
+    ggplot(data = mdlStudent$predSlopesAttType %>% filter(PID %in% studentPltIDs), 
+           aes(x = TIDnum, y = measure)) +
     geom_line(alpha = 1, color = "blue") +
@@
 ```{r studentFreqQualCor}
-# prepare data
-studentAvFreQual <- dtStudents$full %>%
-  group_by(ExternalReference) %>%
-  summarise(
-    n = n(),
-    SumContactNL = sum(Contact_dum),
-    PercContactNL = SumContactNL / n * 100,
-    SumContactNLAll = sum(number),
-    AvAttitude = mean(AttitudesDutch, na.rm = TRUE),
-    AvQuality = mean(quality_overall_1, na.rm = TRUE)
-  ) %>%
-  mutate(
-    WinSumContactNL = DescTools::Winsorize(SumContactNL),
-    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
-  )
-
 # correlation panel
 pairs.panels.new(
-  studentAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  studentContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
   labels = c(
@@
 pairs.panels.new(
-  studentAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  studentContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
   labels = c(
@@
 
-TL;DR: There is a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
-Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
-However, the frequency of intergroup interactions had no meaningfull correlation with either the average interaction quality or average outgroup attitudes.
+TL;DR: There is no meaningfull correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
+However, the frequency of intergroup interactions had a significant correlation with both the average interaction quality and average outgroup attitudes.
 
@@
 mdlStudent$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL * AvQuality, data = studentAvFreQual)
+  lm(AvAttitude ~ SumContactNL * AvQuality, data = studentContactFreq)
 # summary(mdlStudent$lmAttFreqQualX)
@@
   mdlStudent$lmAttFreqQualX,
-  pred = AvQuality,
-  modx = SumContactNL,
+  pred = SumContactNL,
+  modx = AvQuality,
   interval = TRUE,
@@
 interactions::johnson_neyman(mdlStudent$lmAttFreqQualX,
-                             pred = AvQuality,
-                             modx = SumContactNL,
+                             pred = SumContactNL,
+                             modx = AvQuality,
                              alpha = .05)
@@
 
-TL;DR: We find that interaction quality is significantly related to higher outgroup attitudes (albeit with a small effect size).
-We also find that in our sample with an increasing number of interactions the positive effect of interaction quality becomes weaker.
-However, note that this is based on data aggregating all within participant nuances and is only the date of 21 people.
+TL;DR: We find that, although the effect goes into the right direction (i.e., higher average interaction quality increases the positive effect of intergroup contact), there was no effect of average interaction quality (neither directly nor in a moderating role of interaction frequency).
+However, this regression ignores within person relationships of these variables (i.e., summarizes all within person variances into average scores).
 
@@
   lme(
-    AttitudesDutch ~ keymotive_fulfillemt_1,
+    AttitudesDutch ~ KeyNeedFullfillment,
     random = ~ 1 | PID,
@@
 summ(
-  lmer(AttitudesDutch ~ keymotive_fulfillemt_1 + (1 | PID), 
+  lmer(AttitudesDutch ~ KeyNeedFullfillment + (1 | PID), 
        data = studentOutgroupInteraction),
@@
     AttitudesDutch ~
-      keymotive_fulfillemt_1,
-    random = ~ 1 + keymotive_fulfillemt_1 | PID,
+      KeyNeedFullfillment,
+    random = ~ 1 + KeyNeedFullfillment | PID,
     control = lmeControl(opt = "optim"),
@@
     AttitudesDutch ~
-      keymotive_fulfillemt_1 +
-      (1 + keymotive_fulfillemt_1 | PID),
+      KeyNeedFullfillment +
+      (1 + KeyNeedFullfillment | PID),
     data = studentOutgroupInteraction
@@
   studentOutgroupInteraction %>%
-  select(AttitudesDutch, session, PID) %>% 
+  select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCore,
@@
   mdlStudentOut$Att$predPltSlopesCore <-
-    ggplot(data = mdlStudentOut$Att$predSlopesCore, aes(x = session, y = measure)) +
+    ggplot(data = mdlStudentOut$Att$predSlopesCore %>% filter(PID %in% studentOutPltIDs), 
+           aes(x = TIDnum, y = measure)) +
     geom_line(alpha = 1, color = "blue") +
@@
 (\#eq:studentOutQualEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
+InteractionQuality_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
 \textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
@@
 mdlStudentOut$Qlt$lmerNull <-
-  lme4::lmer(quality_overall_1 ~ 1 + (1 | PID), 
+  lme4::lmer(quality_overall ~ 1 + (1 | PID), 
              data = studentOutgroupInteraction) # use optim if it does not converge
@@
   lme(
-    quality_overall_1 ~ 1,
+    quality_overall ~ 1,
     random = ~ 1 | PID,
@@
   lme(
-    quality_overall_1 ~ keymotive_fulfillemt_1,
+    quality_overall ~ KeyNeedFullfillment,
     random = ~ 1 | PID,
@@
 summ(
-  lmer(quality_overall_1 ~ keymotive_fulfillemt_1 + (1 | PID), 
+  mdlStudentOut$Qlt$lmerInterceptCore <- lmer(quality_overall ~ KeyNeedFullfillment + (1 | PID), 
        data = studentOutgroupInteraction),
@@
 # Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(quality_overall_1 ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+# write.csv(confint(lmer(quality_overall ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
 #                  method="boot",nsim=1000, parallel = "multicore",
@@
   lme(
-    quality_overall_1 ~
-      keymotive_fulfillemt_1,
-    random = ~ 1 + keymotive_fulfillemt_1 | PID,
+    quality_overall ~
+      KeyNeedFullfillment,
+    random = ~ 1 + KeyNeedFullfillment | PID,
     control = lmeControl(opt = "optim"),
@@
     lmer(
-      quality_overall_1 ~
-        keymotive_fulfillemt_1 +
-        (1 + keymotive_fulfillemt_1 | PID),
+      quality_overall ~
+        KeyNeedFullfillment +
+        (1 + KeyNeedFullfillment | PID),
       data = studentOutgroupInteraction
@@
   (1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[2]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]))) * 100
-```
-
-TL;DR: random slopes does not add significantly. Stay with simpler model.
+
+# Assumption Checks:
+mdlStudentOut$Qlt$diagSlopesCore <-
+  sjPlot::plot_model(mdlStudentOut$Qlt$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlStudentOut$Qlt$diagSlopesCore[[1]],
+  mdlStudentOut$Qlt$diagSlopesCore[[2]]$`PID`,
+  mdlStudentOut$Qlt$diagSlopesCore[[3]],
+  mdlStudentOut$Qlt$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlStudentOut$Qlt$predSlopesCore <- 
+  studentOutgroupInteraction %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlStudentOut$Qlt$lmeSlopesCore,
+                           studentOutgroupInteraction,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudentOut$Qlt$predPltSlopesCore <-
+    ggplot(data = mdlStudentOut$Qlt$predSlopesCore %>% filter(PID %in% studentOutPltIDs), 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/StudentOut_PredictionPlot_SlopesCore.png",
+  mdlStudentOut$Qlt$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+TL;DR: random slopes does add significantly.
 
@@
   lme(
-    AttitudesDutch ~ keymotive_fulfillemt_1 + quality_overall_1,
+    AttitudesDutch ~ KeyNeedFullfillment + quality_overall,
     random = ~ 1 | PID,
@@
   lmer(
-    AttitudesDutch ~ keymotive_fulfillemt_1 + quality_overall_1 + (1 | PID),
+    AttitudesDutch ~ KeyNeedFullfillment + quality_overall + (1 | PID),
     data = studentOutgroupInteraction
@@
     AttitudesDutch ~
-      keymotive_fulfillemt_1 + quality_overall_1,
-    random = ~ 1 + keymotive_fulfillemt_1 + quality_overall_1 | PID,
+      KeyNeedFullfillment + quality_overall,
+    random = ~ 1 + KeyNeedFullfillment + quality_overall | PID,
     control = lmeControl(opt = "optim"),
@@
     AttitudesDutch ~
-      keymotive_fulfillemt_1 + quality_overall_1 +
-      (1 + keymotive_fulfillemt_1 + quality_overall_1 | PID),
+      KeyNeedFullfillment + quality_overall +
+      (1 + KeyNeedFullfillment + quality_overall | PID),
     data = studentOutgroupInteraction
@@
   studentOutgroupInteraction %>%
-  select(AttitudesDutch, session, PID) %>% 
+  select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreQlt,
@@
   mdlStudentOut$Att$predPltSlopesCoreQlt <-
-    ggplot(data = mdlStudentOut$Att$predSlopesCoreQlt, aes(x = session, y = measure)) +
+    ggplot(data = mdlStudentOut$Att$predSlopesCoreQlt %>% filter(PID %in% studentOutPltIDs), 
+           aes(x = TIDnum, y = measure)) +
     geom_line(alpha = 1, color = "blue") +
@@
   lme(
-    AttitudesDutch ~ keyMotiveFulfilled * OutgroupInteraction,
+    AttitudesDutch ~ KeyNeedFullfillment * OutgroupInteraction,
     random =  ~ 1 | PID,
@@
   mdlStudent$lmerInterceptAttCoreInt <- lmer(
-    AttitudesDutch ~ keyMotiveFulfilled * OutgroupInteraction + (1 | PID),
+    AttitudesDutch ~ KeyNeedFullfillment * OutgroupInteraction + (1 | PID),
     data = studentInteractionType
@@
   AttitudesDutch ~
-    keyMotiveFulfilled * OutgroupInteraction,
-  random = ~ 1 + keyMotiveFulfilled + OutgroupInteraction | PID,
+    KeyNeedFullfillment * OutgroupInteraction,
+  random = ~ 1 + KeyNeedFullfillment + OutgroupInteraction | PID,
   control = lmeControl(opt = "optim"),
@@
     AttitudesDutch ~
-      keyMotiveFulfilled * OutgroupInteraction +
-      (1 + keyMotiveFulfilled + OutgroupInteraction | PID),
+      KeyNeedFullfillment * OutgroupInteraction +
+      (1 + KeyNeedFullfillment + OutgroupInteraction | PID),
     data = studentInteractionType
@@
   studentInteractionType %>%
-  select(AttitudesDutch, session, PID) %>% 
+  select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlStudent$lmeSlopesAttCoreInt,
@@
   mdlStudent$predPltSlopesAttCoreInt <-
-    ggplot(data = mdlStudent$predSlopesAttCoreInt, aes(x = session, y = measure)) +
+    ggplot(data = mdlStudent$predSlopesAttCoreInt %>% filter(PID %in% studentPltIDs), 
+           aes(x = TIDnum, y = measure)) +
     geom_line(alpha = 1, color = "blue") +
@@
 ggplot(data = studentInteractionType,
-       aes(x = keyMotiveFulfilled,
+       aes(x = KeyNeedFullfillment,
            y = AttitudesDutch,
@@
   ) +
-  scale_x_continuous(limits = c(-50, 50), breaks = seq(-50, 50, by = 10)) +
+  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
   labs(
@@
   OutgroupInteraction = factor(rep(c("No", "Yes"), each = 21)),
-  keyMotiveFulfilled = rep(seq(-50, 50, 5), 2),
+  KeyNeedFullfillment = rep(seq(0, 100, 5), 2),
   PID = 0
@@
   mdlStudent$predInterceptAttCoreIntX,
-  aes(x = keyMotiveFulfilled,
+  aes(x = KeyNeedFullfillment,
       y = fit,
@@
               alpha = 0.3) +
-  scale_x_continuous(breaks = seq(-50, 50, 10)) +
+  scale_x_continuous(breaks = seq(0, 100, 10)) +
   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
@@
 # brmfit <- brm(
-#   AttitudesDutch ~ keyMotiveFulfilled * OutgroupInteraction + 
-#     (1 + keyMotiveFulfilled + OutgroupInteraction | PID),
+#   AttitudesDutch ~ KeyNeedFullfillment * OutgroupInteraction + 
+#     (1 + KeyNeedFullfillment + OutgroupInteraction | PID),
 #   data = studentInteractionType,
@@
 #   OutgroupInteraction = rep(c("No", "Yes"), each = 101),
-#   keyMotiveFulfilled = rep(seq(-50, 50, 1), 2)
+#   KeyNeedFullfillment = rep(seq(0, 100, 1), 2)
 # )
@@
 # ggplot(fitavg,
-#        aes(x = keyMotiveFulfilled,
+#        aes(x = KeyNeedFullfillment,
 #            y = pred,
 #            fill = OutgroupInteraction)) +
-#   scale_x_continuous(breaks = seq(-50, 50, 10)) +
+#   scale_x_continuous(breaks = seq(0, 100, 10)) +
 #   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
@@
 # ggplot(studentInteractionType,
-#        aes(x = keyMotiveFulfilled, y = AttitudesDutch)) +
+#        aes(x = KeyNeedFullfillment, y = AttitudesDutch)) +
 #   geom_point(shape = 4, alpha = .1) +
@@
 #     data = pst,
-#     aes(intercept = b_Intercept, slope = b_keyMotiveFulfilled),
+#     aes(intercept = b_Intercept, slope = b_KeyNeedFullfillment),
 #     alpha = .025,
@@
   lme(
-    AttitudesDutch ~ keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1,
+    AttitudesDutch ~ KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction,
     random = ~ 1 | PID,
@@
   mdlStudentOut$Att$lmerInterceptCoreSdt <- lmer(
-    AttitudesDutch ~ keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 + (1 | PID),
+    AttitudesDutch ~ KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction + (1 | PID),
     data = studentOutgroupInteraction
@@
 
-# compute lme for core model with same number of observations for comparison
-# !! LOOK INTO MISSINGNESS (only one observation) !!
-lmeInterceptCoreRed <-
-  lme(
-    AttitudesDutch ~ keymotive_fulfillemt_1,
-    random = ~ 1 | PID,
-    data = studentOutgroupInteraction %>% filter(!is.na(autonomy_1))
-  )
-
 # Compare new model to previous step
 anova(
-  lmeInterceptCoreRed, 
+  mdlStudentOut$Att$lmeInterceptCore, 
   mdlStudentOut$Att$lmeInterceptCoreSdt
@@
   kable_styling(position = "left")
-rm(lmeInterceptCoreRed)
 
@@
 ```{r studentOutModelSlopesAttCoreSdt}
+# Check Correlations 
+studentOutgroupInteraction %>% 
+  select(AttitudesDutch, KeyNeedFullfillment, Competence, Autonomy, RelatednessInteraction) %>%
+  pairs.panels.new
+
+studentRed <- 
+  studentOutgroupInteraction %>% 
+  # select(PID, AttitudesDutch, KeyNeedFullfillment, Competence, Autonomy, RelatednessInteraction) %>%
+  group_by(PID) %>%
+  filter(
+    sd(AttitudesDutch) != 0,
+    sd(KeyNeedFullfillment) != 0,
+    sd(Competence) != 0,
+    sd(Autonomy) != 0,
+    sd(RelatednessInteraction) != 0
+  ) %>%
+  ungroup
+
+studentRedCor <- 
+  studentOutgroupInteraction %>%
+  group_by(PID) %>%
+  summarise(
+    rAttCore = cor(AttitudesDutch, KeyNeedFullfillment),
+    rAttComp = cor(AttitudesDutch, Competence),
+    rAttAut = cor(AttitudesDutch, Autonomy),
+    rAttRel = cor(AttitudesDutch, RelatednessInteraction),
+    rCoreComp = cor(KeyNeedFullfillment, Competence),
+    rCoreAut = cor(KeyNeedFullfillment, Autonomy),
+    rCoreRel = cor(KeyNeedFullfillment, RelatednessInteraction),
+    rCompAut = cor(Competence, Autonomy),
+    rCompRel = cor(Competence, RelatednessInteraction),
+    rAutRel = cor(Autonomy, RelatednessInteraction)
+  ) %>%
+  filter_at(vars(-PID), all_vars(abs(.) != "1"))
+  # mutate(corMean = rowMeans(abs(.[2:ncol(.)]))) %>%
+  # filter(corMean != "1")
+
+studentRed2 <- 
+  studentOutgroupInteraction %>%
+  filter(PID %in% studentRedCor$PID)
+
 # Create and save Model (optimizer needed to reach convergence) 
+# Problem because some PPTs have 100 on all measures (SD = 0) AND/OR
+# For some all cor = 1 or -1
+# Removing these PPTs or their measurement beeps doesn't help
+# However, removing eithe the Core Need, Autonomy, or Relatedness from the random slopes lets the model converge
+# --> looks like there is an overfitting issue? But why does it work in lmer?
+# FOR NOW: Autonomy removed from random slopes because weakest predictor
 mdlStudentOut$Att$lmeSlopesCoreSdt <-
-  lme(
+  nlme::lme(
     AttitudesDutch ~
-      keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1,
-    random = ~ 1 + keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 | PID,
-    control = lmeControl(opt = "optim"),
-    data = studentOutgroupInteraction,
-    na.action = na.exclude
+      KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction,
+    random = ~ 1 + KeyNeedFullfillment + Competence + RelatednessInteraction | PID, # Autonomy + 
+    #method = "ML",
+    #control = lmeControl(opt = "optim", optimMethod = "L-BFGS-B"),
+    control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
+    data = studentOutgroupInteraction
   )
@@
     AttitudesDutch ~
-      keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 +
-      (1 + keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 | PID),
+      KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction +
+      (1 + KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction | PID),
     data = studentOutgroupInteraction
@@
   studentOutgroupInteraction %>%
-  filter(!is.na(autonomy_1)) %>%
-  select(AttitudesDutch, session, PID, autonomy_1) %>% 
+  select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreSdt,
-                           studentOutgroupInteraction %>% filter(!is.na(autonomy_1)),
+                           studentOutgroupInteraction,
                            re.form = NA
@@
   mdlStudentOut$Att$predPltSlopesCoreSdt <-
-    ggplot(data = mdlStudentOut$Att$predSlopesCoreSdt, aes(x = session, y = measure)) +
+    ggplot(data = mdlStudentOut$Att$predSlopesCoreSdt %>% filter(PID %in% studentOutPltIDs),
+           aes(x = TIDnum, y = measure)) +
     geom_line(alpha = 1, color = "blue") +

### 2021-10-18 Supplemental-Material-B-Annotated-Analysis.Rmd
descriptions, annotations, and interpretations AOT-P added

@@
 
+In an initial preparatory step, we import the data into the R project environment and prepare the variables for further processing and later analyses.
+
 ## Data Import
+
+The data were collected using two different survey tools.
+For the study with sojourners (Study 1: worker) we used the survey platform Qualtrics XM, whereas the studies with international students (Study 2: student), and the international medical professionals (Study 3: medical) were conducted using the survey framework FormR.
+This means that the datasets had inconsistent file formats and naming conventions.
+For the Qualtrics study we pre-processed some variables to ease the import process (for the syntax files see the SPS files in '_data/S1_Workers/processed/cleaned_' and for the raw data files see '_data/S1_Workers/raw_').
+For the two other studies, we import the raw csv files from their respective folders.
 
@@
 ## Data Cleaning & Data Exclusions
+
+### Worker
+
+For the sojourner sample data was collected in four separate surveys: (1) the pre-measurement, (2) the daily morning survey, (3) the daily afternoon survey, as well as (4) a post-measurement.
+We combine the four individual surveys into one cohesive dataframe and drop superfluous variables that are not relevant to the analyses relevant here.
+We then format the time and date variables and add person- and measurement indices (for easy and meaningful addressing of the data).
+We also exclude our own test data.
+<i class="fas fa-info-circle"></i> _Note:_ All data preparation steps are saved in the '_dtWorker_' list.
 
@@
 
+### Student
+
+For the student sample data was, similarly, collected in three separate surveys: (1) the pre-measurement, (2) the daily survey sent out at lunch and dinner time, and (3) a post-measurement.
+We combine the three individual surveys into one large dataframe and drop superfluous variables that are not relevant to the analyses relevant here.
+We exclude our own test data as well as one participant who entered the study twice (but gave different responses during the pre-measurement).
+We also reformat missing values and format core ID variables.
+<i class="fas fa-info-circle"></i> _Note:_ All data preparation steps are saved in the '_dtStudents_' list.
+
 ```{r cleanStudents}
@@
 
+### Medical
+
+To be done after preregistration.
+
 ```{r cleanMedical}
@@
 ### Worker
+
+For the worker sample, the data transformation stage had three main aims:
+
+1.
+We first corrected time indicators within the surveys.
+In some cases participants completed their daily diary surveys for the afternoon after midnight.
+In these cases the measurement still is in reference to the previous day and is indicated in the corrected variable.
+2.
+We then created indices of scales.
+Some indices were multi-item scales while some indices combine equivalent measurement for different situational circumstances (e.g., competence perceptions after interactions and at measurement occasions without interactions).
+3. Finally, we calculated several basic participant summaries (averages across all measurement occasions).
 
@@
   df$daytime == "afternoon"] - 1
-
-# Mood scales
-df$calmness.daily <- rowSums(df[, c("calmness1", "calmness2")], na.rm = T)
-df$alertness.daily <- rowSums(df[, c("alertness1", "alertness2")], na.rm = T)
-df$valence.daily <- rowSums(df[, c("valence1", "valence2")], na.rm = T)
 
@@
 )], na.rm = T)
+
+pairs.panels.new(
+  df[c("relatedness_self_1", "relatedness_other_1")],
+  labels = c(
+    "I shared information about myself.",
+    "X shared information about themselves."
+  )
+)
 df$relatedness_1 <- rowMeans(df[, c("relatedness_other_1", "relatedness_self_1")], na.rm = T)
@@
 
+For the worker sample, the data transformation stage had three main aims:
+
+1. We first create person, survey type, and measurement ID variables.   
+2.
+We then created indices of scales.
+Some indices were multi-item scales while some indices combine equivalent measurement for different situational circumstances (e.g., competence perceptions after interactions and at measurement occasions without interactions).
+3. We add information about the interaction partner to the beep during which a person was selected as an interaction partner.   
+4. We cluster mean-center key variables within participants.   
+5. Finally, we calculated several basic participant summaries (averages across all measurement occasions).
+
 ```{r newVarsStudents}
@@
 
+To be done after preregistration.
+
 ```{r newVarsMedical}
@@
 
+The first sample we assess is the smaller sojourner study. We will sequentially test our main hypotheses for this study:
+
+1.
+\label{hyp:contact}Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
+    a. \label{hyp:contactFreq}Participants with more intergroup interactions should have a more favorable outgroup attitudes.
+    b. \label{hyp:contactDummy}Outgroup attitudes should be higher after an intergroup interaction compared to a non-outgroup interaction.
+    c. \label{hyp:contactFreqQual}Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
+2.
+\label{hyp:keyNeed}Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+    a. \label{hyp:keyNeedPred}Outgroup attitudes should be more favorable after intergroup interactions with high key need fulfillment.
+    b. \label{hyp:keyNeedQual}Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
+    c. \label{hyp:keyNeedMediation}The variance explained in outgroup attitudes by key need fulfillment should to a large extend be assumed by interaction quality.
+    d.
+\label{hyp:keyNeedContactType}The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
+Thus, the effect of key need fulfillment on outgroup attitudes should stronger for intergroup interact than for ingroup interactions.
+    e.
+\label{hyp:keyNeedSDT}The effect of key need fulfillment on outgroup attitudes should be persist even when taking other fundamental psychological needs into account.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
+
 ## Data Description
@@
 
+We test the most general contact hypothesis in two steps.
+First, we assess whether more intergroup interactions are related to to more positive outgroup attitudes.
+Second, we test whether a potential positive effect on outgroup attitudes depends on the interaction quality (jointly with the number of interactions).
+
 ### Interaction Frequency and Outgroup Attitudes
+
+To test the impact of the overall number of interactions, we hope to find that there is a significant relationship between the number of interactions a participant had and the average outgroup attitude.
 
@@
 
-TL;DR: Neither the number of interactions nor the number of measurement beeps with an interaction are significantly related with the average outgroup attitudes.
-This is to say that within our data participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
+We find that neither the number of interactions nor the number of measurement beeps with an interaction are significantly related with the average outgroup attitudes.
+This is to say that within our data, participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
 This might be due to the aggregation within the participants or the small sample size of between participant data.
@@
 
+In a next step we take into account that having an interaction with an outgroup member, does not happen in a social vacuum.
+Participants who indicated that they had an interaction with an outgroup member include measurement occasions during which someone either only had an interaction with an outgroup member as well as times during which a person also had interaction(s) with a non-Dutch person.
+Inversely, participants who indicated that they did not have an interaction with a Dutch person might either have had no interaction at all or had an interaction with a non-Dutch person.
+We, thus consider all possible combinations and their independent influences on outgroup attitudes.
+
+#### OLS regression
+
+We first assess the impact of the different interaction types across all measurement points (lumping all beeps together).
+
 \begin{equation}
 (\#eq:WorkerIntTypeQual)
-\mu_{i,0utgroupInteraction} > \mu_{i,IngroupInteraction}  \\
-Attitude = OutgroupInteraction \times NonOutgroupInteraction
+Attitude = OutgroupInteraction + NonOutgroupInteraction
 \end{equation}
@@
   <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
-  <i class="fas fa-exclamation-triangle"></i> <b>Note: </b><br/>
-  mean difference alone probably even more stupid than only ignoring nested data, because we drop lots of data unnecessarily.  
-  And only outgroup interaction Yes / No also weird because interaction group includes people who had only an outgroup interaction and those who also had an interaction with a non-outgroup person, and the no outgroup interaction group includes those who had no interaction at all and those who had an interaction with a non-outgroup person (but no outgroup interaction).
+  <i class="fas fa-info-circle"></i> <b>Note: </b><br/>
+  This step ignores the nested nature of the data (and consequently, response sets between participants).
+However, a purely cross-sectional approach with retrospective evaluations is common within the field and the analysis here offers a first cross-sectional insight (even with the independence assumption violated).
 </div>
-
-#### Regression with interaction term
-
-Across participants: impact of different interaction types [probably meaningless because ignores response sets between participants]
 
@@
 
-TL;DR: While controlling for interactions with non-Dutch people, outgroup attitudes were significantly higher when participants had an interaction with a Dutch person.
+We find that while controlling for interactions with non-Dutch people, outgroup attitudes were significantly higher when participants had an interaction with a Dutch person.
 The effect is relatively small (`r format(round(mdlWorker$lmAttInt$coefficients["OutgroupInteractionYes"], 2), nsmall=2)` points on a 0--100 scale).
@@
 
-#### ML Regression with interaction term
+#### ML regression
+
+We, thus, proceed with a multilevel analysis, which acknowledges that the measurements are nested within participants.
 
@@
 
-make a model with only the data but a random intercept (unconditional model)
+We start by creating an empty random intercept model (i.e., let the outgroup attitude intercept be different between participants; unconditional model)
 
@@
 
-ICC $\tau_{00}^2 / (\tau_{00}^2 + \sigma^2)$: The ratio of the between-cluster variance to the total variance is called the Intraclass Correlation.
-It tells you the proportion of the total variance in Y that is accounted for by the clustering.
-(In this case the clustering means clustering observations per participant)
-
-compare the random intercept model to a model without a random intercept (i.e., without levels at all)
+We then compare the random intercept model to a model without a random intercept (i.e., without levels at all).
 
@@
   select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
   kbl(
@@
 
+Comapring the two empty model, we find that there is indeed a significant amount of variance explained by including a random intercept.
+
+To assess the variances within and between participants we look at the ICC $\tau_{00}^2 / (\tau_{00}^2 + \sigma^2)$: The ratio of the between-cluster variance to the total variance is called the Intraclass Correlation.
+It tells you the proportion of the total variance in Y that is accounted for by the clustering.
+(In this case the clustering means clustering observations per participant)
+
 We find that an estimated `r format(round(mdlWorker$IccPercAttNull, 2), nsmall=2)`% of the variation in Feeling Thermometer scores is explained by between participant differences (clustering by PID).
@@
 
-##### random intercept
+##### random intercept with predictors
+
+To this random intercept model we now add the two types of interactions possible at each measurement point as contemporaneous predictors of outgroup attitudes.
+That is: We check whether within participants having an outgroup interaction (or a non-outgroup interaction) is associated with more positive outgroup attitudes at the same measurement point.
 
@@
 
-tl;dr: Interaction with Dutch is great predictor, interactions with non-Dutch is not.
+We find that a random intercept model with the two interaction types as predictors explains significantly more variance then an empty random intercept model.
+Looking at the individual coefficients, we find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes, while having an interaction with a non-Dutch person does not significantly relate to more positive or negative attitudes towards the Dutch.
+
+TL;DR: Interaction with Dutch is great predictor, interactions with non-Dutch is not.
 
 ##### random slope
+
+In a next step, we check whether further letting the effect of the different interaction types vary between participants explains additional variance in outgroup attitudes (i.e., random slopes).
 
@@
 
+We find that adding the random slopes does not add significantly beyond the random intercept model.
+This is unusual because this might indicate the the effect is very consistent across participants.
+However, this might also be the case due to a small number of participants, or other measurement issues.
+
 TL;DR: Random slopes don't add much for this super simple model.
@@
 ### Interaction Frequency and Interaction Quality
+
+In a final step we check whether the effect outgroup interactions, in part, depends on the quality during the interactions.
+Because we can only assess interaction quality when there is an interaction, it is difficult to assess this with the interaction dummy as a within person predictor.
+Instead, we will use an aggregate measure of interaction qualtity and average interaction quality to consider the two predictors jointly.
 
@@
 
-TL;DR: There is a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
+Within the data, we find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
 Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
@@
 
-TL;DR: We find that interaction quality is significantly related to higher outgroup attitudes (albeit with a small effect size).
+We find that interaction quality is significantly related to higher outgroup attitudes (albeit with a small effect size).
 We also find that in our sample with an increasing number of interactions the positive effect of interaction quality becomes weaker.
-However, note that this is based on data aggregating all within participant nuances and is only the date of 21 people.
+However, it should be noted that this is based on data aggregating all within participant nuances and is only the date of 21 people.
 
@@
 
+The main proposal of our article is that the success of an outgroup interaction might be explained by whether or not the interaction fulfilled the person's core situational need.
+This should, in turn, be due to a higher perceived interaction quality.
+We will this sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+
 ### Need fulfillment and Attitudes
 
+In a first step we, thus, test the relationship between outgroup attitudes and the fulfillment of the core situational need during the interaction.
+
 ##### Unconditional model
 
-make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
+We again start by creating an empty random intercept model (i.e., let the outgroup attitude intercept be different between participants; unconditional model).
+Note that this unconditional model differs from the empty model created earlier because for this set of analyses we will only consider the subsample of measurement points during which an outgroup interaction was reported.
+This is necessary because measurements of needs during the interaction and perceived interaction quality are only meaningful within an interaction context.
 
@@
 ```
+
+<i class="fas fa-question-circle"></i> _Note to self:_ For completeness, we should probably check this against an empty model without random intercept.
 
@@
 
-#### random intercept
+#### random intercept with level one predictors
+
+We thus add the core interaction need fulfillment to the multilevel random intercept model.
 
@@
   select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
   kbl(
@@
 
-TL;DR: Situational core need relates significantly to outgroup attitudes.
+We find that the the model with the added predictor indeed explains more variance in outgroup attitudes than the unconditional model.
+Looking at the individual coefficients, we find that the situational core need relates significantly to outgroup attitudes.
 The core need has little explained variance between participants (compared to the null model: Variance Explained = 1 – (Var with Predictor/Var without Predictor); `r format(round(mdlWorkerOut$Att$varBtwPercInterceptCore, 2),nsmall=2)`%).
-The variance explained within participants is small to medium (`r format(round(mdlWorkerOut$Att$varWithinPercInterceptCore, 2),nsmall=2)`%)
+The variance explained within participants is small to medium (`r format(round(mdlWorkerOut$Att$varWithinPercInterceptCore, 2),nsmall=2)`%).
 
 #### random slope
+
+In a next step, we check whether further letting the effect of core need fulfillment vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
 
@@
 
+We find that adding the random slopes does add significantly beyond the random intercept model.
+We also find that the core need remains a strong predictor (even when letting the influence vary between participants).
+
 TL;DR: The random slope adds significantly to the prediction model.
@@
 This is when comparing the random intercepts to the random slopes model.
+Check with materials from Laura!!
 </div>
@@
 
+Based on the assertion that the relationship between core need fulfillment and outgroup attitudes is explained by a higher perceived interaction, the core need fulfillement should also significantly predict perceived interaction quality.
+
 ##### Unconditional model
 
-make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
+Given that we now have the perceived interaction quality as our outcome variable of interest we again begin with an unconditional model (i.e., empty random intercept model), to see whether there is enough variance to explain within the participants.
+Similarly to before this is again done wihin the subsample of measurements during which an outgroup interaction was reported.
 
@@
 
-#### random intercept
+We again find a reasonable amount of variance within the participants.
+
+<i class="fas fa-question-circle"></i> _Note to self:_ For completeness, we should probably check this against an empty model without random intercept.
+
+#### random intercept with level one predictor
+
+We again add the core interaction need fulfillment to the multilevel random intercept model.
 
@@
 
-TL;DR: Situational core need relates significantly to interaction quality.
+The predictor again adds a significant amount of explained variances beyond the empty model and looking at the slope coefficient, we find that the situational core need fulifillment relates significantly to perceived interaction quality.
 The core need explained substantial variance between participants (`r format(round(mdlWorkerOut$Qlt$varBtwPercInterceptCore, 2),nsmall=2)`%).
-The variance explained within participants is also medium (`r format(round(mdlWorkerOut$Qlt$varWithinPercInterceptCore, 2),nsmall=2)`%)
+The variance explained within participants is also medium (`r format(round(mdlWorkerOut$Qlt$varWithinPercInterceptCore, 2),nsmall=2)`%).
 
 #### random slope
+
+As before, we check whether further letting the effect of core need fulfillment vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
 
@@
 
-TL;DR: random slopes does not add significantly. Stay with simpler model.
+We find that adding the random slopes does not add significantly beyond the random intercept model.
+This is unusual because this might indicate the the effect is very consistent across participants.
+However, we also see that when taking the possibility to varying slopes into account, the core need fulfillment remains a significant predictor of perceived interaction quality.
 
@@
 
-#### random intercept
+In our final main step, we will jointly consider the effect of core need fulfillment and perceived interaction quality on outgroup attitudes.
+We expect that if the relationship between core need fulfillment and outgroup attitudes is indeed explained by a higher perceived interaction quality, the interaction quality perception should assume the explained variance of the core contact need fulfillment.
+
+#### random intercept with level one predictors
+
+We thus add both the core need fulfillment and perceived interaction quality to a random intercept model of outgroup attitudes.
 
@@
 
-TL;DR: Variance explained in outgroup attitudes is of medium effect size (between: `r format(round(mdlWorkerOut$Att$varBtwPercInterceptCoreQlt,2),nsmall=2)`%, within: `r format(round(mdlWorkerOut$Att$varWithinPercInterceptCoreQlt,2),nsmall=2)`%)
+Unsurprisingly, the model with the two predictors adds significantly beyond the empty unconditional model.
+However, more importantly, looking at the coefficients, we find that the effect of core need fulfillemnt indeed is indeed strongly reduced and the variance is explained by the perceived interaction quality.
+The variance explained in outgroup attitudes is of medium effect size (between: `r format(round(mdlWorkerOut$Att$varBtwPercInterceptCoreQlt,2),nsmall=2)`%, within: `r format(round(mdlWorkerOut$Att$varWithinPercInterceptCoreQlt,2),nsmall=2)`%).
 
 #### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
 
@@
 \end{equation}
+
+<i class="fas fa-question-circle"></i> Check whether the omega matrix is correct should probably have as many taus as gammas.
 
@@
 
-#### Compare models
-
-Interpretation of Mediation like results.
+We find that adding the random slopes does add significantly beyond the random intercept model.
+We also find that the perceived interaction quality remains a strong predictor (even when letting the slopes vary between participants).
 
@@
 
+To build further confidence in our results, we assess a few additional models that might offer alternative explanations of the effects we find.
+
 #### Interaction Type
 
+To make certain that the effect of core need fulfillment is specific to the interaction we compare the the effect to fulfillment of the situation core need when no outgroup interaction took place.
+
 ##### random intercept
+
+Here we go back to the full dataset and add generalized situational core need fulfillment (either during an interaction or about the daytime in general) and whether an outgroup interaction happened as well as their interaction term to a random intercept model of outgroup attitudes.
 
@@
     booktabs = T,
-    align = rep("c", ncol(.)),
+    align = c("l", rep("c", ncol(.)-1)),
     digits = 3
@@
 
+We find that the model explains significantly more variance than the empty null model.
+However, more interestingly, looking at the coefficients, we find that, as seen earlier, having an outgroup interaction has a strong effect on outgroup attitudes.
+Importantly, we find that there is no main effect of key need fulfillment but a significant interaction effect of core need fulfillment and outgroup contact.
+This indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+
 ##### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
 
@@
 
+We find that adding the random slopes does add significantly beyond the random intercept model.
+We also see that when taking the possibility to varying slopes into account, the coefficient interpretations remains consistent (i.e., outgroup contact and its interaction with core need fulfillment remain significant predictors of positive outgroup attitudes).
+
 ##### Plot Interaction
+
+Before we move on, we shortly illustrate the interaction effect of how the effect of core need fulfillment differed by whether an outgroup contact took place or not.
+To this end we illustrate (1) the raw data points (without taking the nested nature into account), as well as a plot of the model predicted values and their prediction interval (taking the nested structure into account based; similar to an interaction plot).
 
@@
 
-##### random intercept
+In a final step we check whether during the interaction the core situational need is a meaningful predictor even when taking other fundamental psychological needs into account.
+We focus on the three commonly considered self determination needs: competence, autonomy, and relatedness.
+
+##### random intercept with level ome predictors
+
+We add the core need fulfillment with the three self determiantion needs to a random intercept model of outgroup attitudes.
 
@@
 
-# compute lme for core model with same number of observations for comparison
-# !! LOOK INTO MISSINGNESS (only one observation) !!
-lmeInterceptCoreRed <-
+# To be compared against a model with only the self determination theory needs
+mdlWorkerOut$Att$lmeInterceptSdt <-
   lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1,
+    thermometerDutch_1 ~ competence_1 + autonomy_1 + relatedness_1,
     random = ~ 1 | PID,
-    data = workerOutgroupInteraction %>% filter(!is.na(autonomy_1))
-  )
-
-# Compare new model to previous step
+    data = workerOutgroupInteraction,
+    na.action = na.exclude
+  )
+
+summ(
+  mdlWorkerOut$Att$lmerInterceptSdt <- lmer(
+    thermometerDutch_1 ~ competence_1 + autonomy_1 + relatedness_1 + (1 | PID),
+    data = workerOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+# Compare new model to previous steps
 anova(
-  lmeInterceptCoreRed, 
+  mdlWorkerOut$Att$lmeInterceptSdt,
   mdlWorkerOut$Att$lmeInterceptCoreSdt
@@
 
+We compare the models of the core need and the SDT need fulfillments to a model that only includes the SDT needs.
+We find that the core need adds significantly above the SDT needs.
+We find that next to relatedness, the core need explains the most variance and compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs (i.e., reduction in SDT beta weights).
+
 ##### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
 
@@
 ```
+
+We find that adding the random slopes does add significantly beyond the random intercept model.
+We also see that when taking the possibility to varying slopes into account, the coefficient interpretations remains consistent (i.e., core need and relatedness remain the strongest and only significant predictors).
+Note however a slight reduction in the p value of the core need fulfillment.
 
@@
     linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
+    booktabs = TRUE,
+    align = rep("l", ncol(.)),
     digits = 3
@@
 
+# To be compared against a model with only SDT needs
+mdlStudentOut$Att$lmeInterceptSdt <-
+  lme(
+    AttitudesDutch ~ Competence + Autonomy + RelatednessInteraction,
+    random = ~ 1 | PID,
+    data = studentOutgroupInteraction,
+    na.action = na.exclude
+  )
+
+summ(
+  mdlStudentOut$Att$lmerInterceptSdt <- lmer(
+    AttitudesDutch ~ Competence + Autonomy + RelatednessInteraction + (1 | PID),
+    data = studentOutgroupInteraction
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
 # Compare new model to previous step
 anova(
-  mdlStudentOut$Att$lmeInterceptCore, 
+  mdlStudentOut$Att$lmeInterceptSdt, 
   mdlStudentOut$Att$lmeInterceptCoreSdt

### 2021-10-20 Supplemental-Material-B-Annotated-Analysis.Rmd
AOT-S annotations and interpretations added

@@
 
-We start by creating an empty random intercept model (i.e., let the outgroup attitude intercept be different between participants; unconditional model)
+We start by creating an empty random intercept model (i.e., let the outgroup attitude intercept be different between participants; unconditional model).
 
@@
 
-Comapring the two empty model, we find that there is indeed a significant amount of variance explained by including a random intercept.
+Comparing the two empty model, we find that there is indeed a significant amount of variance explained by including a random intercept.
 
@@
 It tells you the proportion of the total variance in Y that is accounted for by the clustering.
-(In this case the clustering means clustering observations per participant)
+(In this case the clustering means clustering observations per participant).
 
@@
 Because we can only assess interaction quality when there is an interaction, it is difficult to assess this with the interaction dummy as a within person predictor.
-Instead, we will use an aggregate measure of interaction qualtity and average interaction quality to consider the two predictors jointly.
+Instead, we will use an aggregate measure of interaction quality and average interaction quality to consider the two predictors jointly.
 
@@
 Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
-However, the frequency of intergroup interactions had no meaningfull correlation with either the average interaction quality or average outgroup attitudes.
+However, the frequency of intergroup interactions had no meaningful correlation with either the average interaction quality or average outgroup attitudes.
 
@@
 Given that we now have the perceived interaction quality as our outcome variable of interest we again begin with an unconditional model (i.e., empty random intercept model), to see whether there is enough variance to explain within the participants.
-Similarly to before this is again done wihin the subsample of measurements during which an outgroup interaction was reported.
+Similarly to before this is again done within the subsample of measurements during which an outgroup interaction was reported.
 
@@
 
-We add the core need fulfillment with the three self determiantion needs to a random intercept model of outgroup attitudes.
+We add the core need fulfillment with the three self determination needs to a random intercept model of outgroup attitudes.
 
@@
 
+The second sample we assess is larger study with international psychology students at Western European university. The hypotheses mirror those of the first study and are re-iterated here:
+
+1.
+\label{hyp:contact}Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
+    a. \label{hyp:contactFreq}Participants with more intergroup interactions should have a more favorable outgroup attitudes.
+    b. \label{hyp:contactDummy}Outgroup attitudes should be higher after an intergroup interaction compared to a non-outgroup interaction.
+    c. \label{hyp:contactFreqQual}Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
+2.
+\label{hyp:keyNeed}Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+    a. \label{hyp:keyNeedPred}Outgroup attitudes should be more favorable after intergroup interactions with high key need fulfillment.
+    b. \label{hyp:keyNeedQual}Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
+    c. \label{hyp:keyNeedMediation}The variance explained in outgroup attitudes by key need fulfillment should to a large extend be assumed by interaction quality.
+    d.
+\label{hyp:keyNeedContactType}The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
+Thus, the effect of key need fulfillment on outgroup attitudes should stronger for intergroup interact than for ingroup interactions.
+    e.
+\label{hyp:keyNeedSDT}The effect of key need fulfillment on outgroup attitudes should be persist even when taking other fundamental psychological needs into account.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
+
+We will test our main hypotheses for this study in a sequential manner.
+
 ## Data Description
@@
 
+We again test the most general contact hypothesis in two steps.
+First, we assess whether more intergroup interactions are related to to more positive outgroup attitudes.
+Second, we test whether a potential positive effect on outgroup attitudes depends on the interaction quality (jointly with the number of interactions).
+
 ### Interaction Frequency and Outgroup Attitudes
+
+To test the impact of the overall number of interactions, we hope to find a significant relationship between the number of interactions a participant had and the average outgroup attitude.
 
@@
 
-TL;DR: Neither the number of interactions nor the number of measurement beeps with an interaction are significantly related with the average outgroup attitudes.
-This is to say that within our data participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
-This might be due to the aggregation within the participants or the small sample size of between participant data.
-Nonetheless, the aggregate data does not support the notion that simply having more interactions with an outgroup results in more positive outgroup attitudes.
+We find that both the number of interactions and the number of measurement beeps with an interaction are significantly related with the average outgroup attitudes.
+This is to say that within our data, participants with more outgroup interactions did have significantly more positive outgroup attitudes.
+This is inconsistent with the results we found in the worker sample.
 
 ### Outgroup Attitudes by Interaction Type
+
+In a next step we take into account that having an interaction with an outgroup member, does not happen in a social vacuum.
+Participants who indicated that they had an interaction with an outgroup member include measurement occasions during which someone either only had an interaction with an outgroup member as well as times during which a person also had interaction(s) with a non-Dutch person.
+Inversely, participants who indicated that they did not have an interaction with a Dutch person might either have had no interaction at all or had an interaction with a non-Dutch person.
+We, thus consider all possible combinations and their independent influences on outgroup attitudes.
+
+#### OLS regression
+
+We first assess the impact of the different interaction types across all measurement points (lumping all beeps together).
 
@@
 
-TL;DR: While controlling for interactions with non-Dutch people, outgroup attitudes were significantly higher when participants had an interaction with a Dutch person.
-The effect is relatively small (`r format(round(mdlStudent$lmAttInt$coefficients["OutgroupInteractionYes"], 2), nsmall=2)` points on a 0--100 scale).
-More importantly, however, this analysis lumps all ESM beeps from every participants together and ignores that the data is nested within participants.
+We find that while controlling for interactions with non-Dutch people, outgroup attitudes were significantly higher when participants had an interaction with a Dutch person.
+The effect is of a medium size (`r format(round(mdlStudent$lmAttInt$coefficients["OutgroupInteractionYes"], 2), nsmall=2)` points on a 0--100 scale).
+However, this analysis lumps all ESM beeps from every participants together and ignores that the data is nested within participants.
 
@@
 
+We, thus, proceed with a multilevel analysis, which acknowledges that the measurements are nested within participants.
+
 ##### Unconditional model
 
-make a model with only the data but a random intercept (unconditional model)
+We start by creating an empty random intercept model (i.e., let the outgroup attitude intercept be different between participants; unconditional model).
 
@@
 
+Comparing the two empty model, we find that there is indeed a significant amount of variance explained by including a random intercept.
+
+To assess the variances within and between participants we look at the ICC $\tau_{00}^2 / (\tau_{00}^2 + \sigma^2)$: The ratio of the between-cluster variance to the total variance is called the Intraclass Correlation.
+It tells you the proportion of the total variance in Y that is accounted for by the clustering.
+(In this case the clustering means clustering observations per participant).
+
 We find that an estimated `r format(round(mdlStudent$IccPercAttNull, 2), nsmall=2)`% of the variation in Feeling Thermometer scores is explained by between participant differences (clustering by PID).
@@
 
-TL;DR: Random slopes don't add much for this super simple model.
+We find that adding the random slopes does add significantly beyond the random intercept model. This is is different to the previous study where the random slope did not add significantly.
+
+TL;DR: Random slopes adds significantly.
 
 ### Interaction Frequency and Interaction Quality
+
+In a final step we check whether the effect outgroup interactions, in part, depends on the quality during the interactions.
+Because we can only assess interaction quality when there is an interaction, it is difficult to assess this with the interaction dummy as a within person predictor.
+Instead, we will use an aggregate measure of interaction quality and average interaction quality to consider the two predictors jointly.
 
@@
 
-TL;DR: There is no meaningfull correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
-However, the frequency of intergroup interactions had a significant correlation with both the average interaction quality and average outgroup attitudes.
+Within the data, we find no significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
+Thus, within our data participants with a higher quality outgroup interactions did not hold more positive attitudes towards that group.
+However, the frequency of intergroup interactions had a meaningful correlation with both the average interaction quality or average outgroup attitudes.
 
@@
 
-TL;DR: We find that, although the effect goes into the right direction (i.e., higher average interaction quality increases the positive effect of intergroup contact), there was no effect of average interaction quality (neither directly nor in a moderating role of interaction frequency).
-However, this regression ignores within person relationships of these variables (i.e., summarizes all within person variances into average scores).
+We find that in our student sample there is only a relationship between the number of outgroup contacts but no significant effect of average perceived contact quality.
+Nor do we find that in this sample the impact of the number of interactions is moderated by the average contact quality.
+This is not entirely consistent with the sojourner sample, where average contact quality did have a meaningful effect on outgroup attitudes.
+This effect is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.
 
@@
 
-TL;DR: Situational core need relates significantly to outgroup attitudes.
+We find that the the model with the added predictor indeed explains more variance in outgroup attitudes than the unconditional model.
+Looking at the individual coefficients, we find that the situational core need relates significantly to outgroup attitudes.
 The core need has little explained variance between participants (compared to the null model: Variance Explained = 1 – (Var with Predictor/Var without Predictor); `r format(round(mdlStudentOut$Att$varBtwPercInterceptCore, 2),nsmall=2)`%).
-The variance explained within participants is small to medium (`r format(round(mdlStudentOut$Att$varWithinPercInterceptCore, 2),nsmall=2)`%)
+The variance explained within participants is small to medium (`r format(round(mdlStudentOut$Att$varWithinPercInterceptCore, 2),nsmall=2)`%).
 
 #### random slope
+
+In a next step, we check whether further letting the effect of core need fulfillment vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
 
@@
 
+Based on the assertion that the relationship between core need fulfillment and outgroup attitudes is explained by a higher perceived interaction, the core need fulfillment should also significantly predict perceived interaction quality.
+
 ##### Unconditional model
 
-make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
+Given that we now have the perceived interaction quality as our outcome variable of interest we again begin with an unconditional model (i.e., empty random intercept model), to see whether there is enough variance to explain within the participants.
+Similarly to before this is again done within the subsample of measurements during which an outgroup interaction was reported.
 
@@
 
-TL;DR: Situational core need relates significantly to interaction quality.
+The predictor again adds a significant amount of explained variances beyond the empty model and looking at the slope coefficient, we find that the situational core need fulfillment relates significantly to perceived interaction quality.
 The core need explained substantial variance between participants (`r format(round(mdlStudentOut$Qlt$varBtwPercInterceptCore, 2),nsmall=2)`%).
-The variance explained within participants is also medium (`r format(round(mdlStudentOut$Qlt$varWithinPercInterceptCore, 2),nsmall=2)`%)
+The variance explained within participants is also medium (`r format(round(mdlStudentOut$Qlt$varWithinPercInterceptCore, 2),nsmall=2)`%).
 
 #### random slope
+
+As before, we check whether further letting the effect of core need fulfillment vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
 
@@
 
-TL;DR: random slopes does add significantly.
+We find that adding the random slopes does add significantly beyond the random intercept model.
 
@@
 
-TL;DR: Variance explained in outgroup attitudes is of medium effect size (between: `r format(round(mdlStudentOut$Att$varBtwPercInterceptCoreQlt,2),nsmall=2)`%, within: `r format(round(mdlStudentOut$Att$varWithinPercInterceptCoreQlt,2),nsmall=2)`%)
+Unsurprisingly, the model with the two predictors adds significantly beyond the empty unconditional model.
+However, more importantly, looking at the coefficients, we find that the effect of core need fulfillment indeed is indeed strongly reduced and the variance is explained by the perceived interaction quality.
+The variance explained in outgroup attitudes is of medium effect size (between: `r format(round(mdlStudentOut$Att$varBtwPercInterceptCoreQlt,2),nsmall=2)`%, within: `r format(round(mdlStudentOut$Att$varWithinPercInterceptCoreQlt,2),nsmall=2)`%).
 
 #### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
 
@@
 
+We find that the model explains significantly more variance than the empty null model.
+However, more interestingly, looking at the coefficients, we find that, as seen earlier, having an outgroup interaction has a strong effect on outgroup attitudes.
+Importantly, we find that there is a main effect of key need fulfillment but also a significant interaction effect of core need fulfillment and outgroup contact.
+This indicates that it is not simply key need fulfillment in general --- but especially key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+
 ##### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
 
@@
 
+We find that adding the random slopes does add significantly beyond the random intercept model.
+We also see that when taking the possibility to varying slopes into account, the coefficient interpretations remains consistent (i.e., outgroup contact and its interaction with core need fulfillment remain important predictors of positive outgroup attitudes).
+
 ##### Plot Interaction
+
+Before we move on, we shortly illustrate the interaction effect of how the effect of core need fulfillment differed by whether an outgroup contact took place or not.
+To this end we illustrate (1) the raw data points (without taking the nested nature into account), as well as a plot of the model predicted values and their prediction interval (taking the nested structure into account based; similar to an interaction plot).
 
@@
 
+The plots indicate that especially once we take the nested data structure into account we can see a substantially stronger effect of core need fulfillment on outgroup attitudes during outgroup contacts than without outgroup contacts.
+
 #### Other psychological needs
 
-##### random intercept
+In a final step we check whether during the interaction the core situational need is a meaningful predictor even when taking other fundamental psychological needs into account.
+We focus on the three commonly considered self determination needs: competence, autonomy, and relatedness.
+
+##### random intercept with level ome predictors
+
+We add the core need fulfillment with the three self determination needs to a random intercept model of outgroup attitudes.
 
@@
 anova(
+  mdlStudentOut$Att$lmeNull,
   mdlStudentOut$Att$lmeInterceptSdt, 
@@
 
+We find that the the model with the added predictor indeed explains more variance in outgroup attitudes than the unconditional model and we find that adding the core need adds further explained variance --- beyond the self determination needs.
+Looking at the individual coefficients, we find that the situational core need relates significantly to outgroup attitudes, that it is a stronger predictor than any of the self determination theory needs and that it assumes some of the variance explained by the self determination theory needs (when compared to a model without the core need).
+
 ##### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
 
@@
 
+We find that adding the random slopes does add significantly beyond the random intercept model.
+We also see that when taking the possibility to varying slopes into account, the coefficient interpretations remains consistent (i.e., core need and relatedness remain the strongest and only significant predictors).
+
 # **Young Medical Professional Sample**

### 2021-10-21 Methods-and-Results.Rmd
Create Methods-and-Results.Rmd

--- 2021-10-18 Supplemental-Material-B-Annotated-Analysis.Rmd
@@
 ---
-title: "Supplemental Information B: Full Annotated Analysis and Reproducible Code"
-subtitle: "Suppplemental Material for 'Psychological Needs During Intergroup Contact [working title]'"
-author:
-- Jannis Kreienkamp^1,2^
-- Maximilian Agostini^1,2^
-- Laura Bringmann^1,2^
-- Peter de Jonge^1,2^
-- Kai Epstude^1,2^
-- ^1^University of Groningen, Department of Psychology
-- ^2^Author order to be discussed; currently alphabetic by last name
-- "Author Information:"
-- "Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).
-E-mail: <a href='mailto:j.kreienkamp@rug.nl'>j.kreienkamp@rug.nl</a>"
-- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
-- 'The data repository for this manuscript is available at <a href="https://osf.io" target="_blank">OSF link goes here</a>'
-- 'The GitHub repository for this manuscript is available at <a href="https://janniscodes.github.io/intergroup-contact-needs/" target="_blank">janniscodes.github.io/intergroup-contact-needs/</a>'
-date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
-output: 
-  bookdown::html_document2:
-    fig_caption: yes
-    md_extensions: +footnotes
-    code_folding: hide
-    mathjax: default
-    theme: yeti
-    toc: yes
-    toc_float: yes
-    number_sections: false
-    css: style.css
-    includes:
-      in_header: "_includes/head-custom-rmd.html" 
+output: latex_fragment
 editor_options:
@@
 ---
-
-<style type="text/css">
-.main-container {
-  max-width: 1300px;
-  margin-left: auto;
-  margin-right: auto;
-}
-.table {
-  margin-left:auto; 
-  margin-right:auto;
-}
-</style>
 
@@
 
-<br/>
-
-<i class="fas fa-exclamation-circle"></i> Note.
-Boxplots display the interquartile range (IQR, center box), and the whiskers extend 1.5*IQR from the lower and upper hinge.
-The white point indicates the mean and the white center line indicates the median.
-
-<br/>
-
-# **Data Preparation**
-
-## Data Import
-
-```{r formrImport}
-# workers
-# initial data cleaning was done in SPSS (syntax files are available in "")
-dtWorker <- list(
-  raw.pre = read_spss("data/S1_Workers/processed/cleaned/MT - Pre-Measure - 06-15-2018.sav"),
-  raw.post = read_spss("data/S1_Workers/processed/cleaned/MT - Post-Measure - 06-15-2018.sav"),
-  raw.morning = read_spss("data/S1_Workers/processed/cleaned/MT - Morning - 06-15-2018.sav"),
-  raw.afternoon = read_spss("data/S1_Workers/processed/cleaned/MT - Afternoon - 06-15-2018.sav")
-)
-
-# students
-dtStudents <- list(
-  raw.pre = read.csv(file = "data/S2_Students/raw/AOTS_Pre.csv", header = T, sep = ","),
-  raw.post = read.csv(file = "data/S2_Students/raw/AOTS_Post.csv", header = T, sep = ","),
-  raw.daily = read.csv(file = "data/S2_Students/raw/AOTS_Daily.csv", header = T, sep = ",")
-)
-
-# young medical professionals
-dtMedical <- list(
-  raw.pre = c(),
-  raw.post = c(),
-  raw.daily = c()
-)
+```{r import}
+load("data/wrangled.RData")
 ```
 
-## Data Cleaning & Data Exclusions
+\newcommand{\nTheo}{`r nrow(dt.Theories.Included)`}
+\newcommand{\nMeth}{`r nrow(dt.Scales.Included)`}
+\newcommand{\nEmp}{`r nrow(dt.Empirical.included)`}
 
-```{r cleanWorker}
-#  important names for Morning and Afternoon
-names.m <- c(
-  "StartDate",
-  "EndDate",
-  "Finished",
-  "Duration__in_seconds_",
-  "RecordedDate",
-  "ExternalReference",
-  "Meta_Operating_System",
-  "Contact_dum",
-  "number",
-  "time",
-  "duration_1",
-  "dyad.group",
-  "gr_size",
-  "gr_type_1",
-  "gr_type_2",
-  "gr_type_3",
-  "gr_type_4",
-  "gr_type_5",
-  "gr_type_6",
-  "gr_type_7",
-  "gr_type_8",
-  "gr_type_9",
-  "gr_type_10",
-  "gr_type_11",
-  "gr_type_12",
-  "gr_type_13",
-  "gr_type_14",
-  "gr_type_15",
-  "gr_type_16",
-  "gr_type_17_TEXT",
-  "gr_context_1",
-  "gr_context_2",
-  "gr_context_3",
-  "gr_context_4",
-  "gr_context_5",
-  "gr_context_6",
-  "gr_context_7",
-  "gr_context_8",
-  "gr_context_9",
-  "gr_context_10",
-  "gr_context_11",
-  "gr_context_12",
-  "gr_context_13_TEXT",
-  "gr_context_14_TEXT",
-  "gr_dutchness",
-  "dyad_type_1",
-  "dyad_type_2",
-  "dyad_type_3",
-  "dyad_type_4",
-  "dyad_type_5",
-  "dyad_type_6",
-  "dyad_type_7",
-  "dyad_type_8",
-  "dyad_type_9",
-  "dyad_type_10",
-  "dyad_type_11",
-  "dyad_type_12",
-  "dyad_type_13",
-  "dyad_type_14",
-  "dyad_type_15",
-  "dyad_type_16",
-  "dyad_type_17_TEXT",
-  "Context_1",
-  "Context_2",
-  "Context_3",
-  "Context_4",
-  "Context_5",
-  "Context_6",
-  "Context_7",
-  "Context_8",
-  "Context_9",
-  "Context_10",
-  "Context_11",
-  "Context_12",
-  "Context_13_TEXT",
-  "Context_14_TEXT",
-  "keyMotive",
-  "keymotive_fulfillemt_1",
-  "keyMotive_Dutch_1",
-  "autonomy_1",
-  "competence_1",
-  "relatedness_self_1",
-  "relatedness_other_1",
-  "qualityAccidental_1",
-  "qualityVoluntary_1",
-  "qualityCooperative_1",
-  "qualityDutchy_1",
-  "quality_overall_1",
-  "quality_meaning_1",
-  "quality_star_1",
-  "wantInt",
-  "desire_type_1",
-  "desire_type_2",
-  "desire_type_3",
-  "desire_type_4",
-  "desire_type_5",
-  "desire_type_6",
-  "desire_type_7",
-  "desire_type_8",
-  "desire_type_9",
-  "desire_type_10",
-  "desire_type_11",
-  "desire_type_12",
-  "desire_type_13",
-  "desire_type_14",
-  "desire_type_15",
-  "desire_type_16",
-  "desire_type_17_TEXT",
-  "desire_context_1",
-  "desire_context_2",
-  "desire_context_3",
-  "desire_context_4",
-  "desire_context_5",
-  "desire_context_6",
-  "desire_context_7",
-  "desire_context_8",
-  "desire_context_9",
-  "desire_context_10",
-  "desire_context_11",
-  "desire_context_12",
-  "desire_context_13_TEXT",
-  "desire_context_14_TEXT",
-  "Reason_nodesire",
-  "keyMotive_noInt",
-  "keyMotive_noInt_fulf_1",
-  "autonomy_NoInt_1",
-  "competence_NoInt_1",
-  "relatedness_1_NoInt_1",
-  "thermometerDutch_1",
-  "thermometerDutchInt_2",
-  "ExWB_1",
-  "alertness1",
-  "calmness1",
-  "valence1",
-  "alertness2",
-  "calmness2",
-  "valence2",
-  "inNonDutch",
-  "NonDutchNum",
-  "NonDutchType_1",
-  "NonDutchType_2",
-  "NonDutchType_3",
-  "NonDutchType_4",
-  "NonDutchType_5",
-  "NonDutchType_6",
-  "NonDutchType_7",
-  "NonDutchType_8",
-  "NonDutchType_9",
-  "NonDutchType_10",
-  "NonDutchType_11",
-  "NonDutchType_12",
-  "NonDutchType_13",
-  "NonDutchType_14",
-  "NonDutchType_15_TEXT",
-  "date",
-  "time.0",
-  "LocationLatitude",
-  "LocationLongitude"
-)
+\section{Study 1}
 
-names.a <- c(names.m, "keyInteraction_1", "keyInteractionTime")
+\subsectio{Methods}
 
-# Create reduced data sets for morning and afternoon
-dat.mo <- dtWorker$raw.morning[, names.m]
-dat.mo$daytime <- "morning"
+\subsection{Results}
 
-dat.af <- dtWorker$raw.afternoon[, names.a]
-dat.af$daytime <- "afternoon"
+\section{Study 2}
 
-# merge morning and afternoon measurements with indicator [+ clean up]
-daily.dat <- rbind.fill(dat.mo, dat.af)
-daily.dat <- daily.dat[daily.dat$ExternalReference != 55951, ]
-dtWorker$daily <- daily.dat
-rm(dat.mo, dat.af, names.m, names.a, daily.dat)
+\subsectio{Methods}
 
-# names for pre-measurement
-names.pre <- c(
-  "Finished",
-  "age",
-  "Gender",
-  "Living",
-  "roommate_1",
-  "roommate_2",
-  "roommate_3",
-  "nationality",
-  "SecondNationality",
-  "timeNL_1",
-  "Reason_2",
-  "Reason_5",
-  "Reason_7",
-  "Reason_8_TEXT",
-  "DutchLang",
-  "occupation_1",
-  "occupation_2",
-  "occupation_3",
-  "occupation_4",
-  "occupation_7",
-  "CurrentEducation_1",
-  "education_level",
-  "EduLang_2",
-  "RUG_faculty",
-  "Study.0",
-  "association",
-  "DutchMeetNum",
-  "DutchFriends_1",
-  "assimilation",
-  "separation",
-  "integration",
-  "marginalization",
-  "VIA_heritage",
-  "VIA_Dutch",
-  "SSAS_surrounding",
-  "SSAS_privat",
-  "SSAS_public",
-  "autonomy",
-  "relatedness",
-  "competence",
-  "anxiety",
-  "swl",
-  "alertness",
-  "calmness",
-  "valence",
-  "date",
-  "time",
-  "City",
-  "ZIP",
-  "id"
-)
+\subsection{Results}
 
-# reduced data set for pre measurement
-dat.pre.red <- dtWorker$raw.pre[, names.pre]
+\section{Study 2}
 
-# merge with daily data [+ clean up]
-df.pre <- merge(
-  x = dtWorker$daily,
-  y = dat.pre.red,
-  by.x = "ExternalReference",
-  by.y = "id",
-  all = T
-)
-rm(names.pre)
+\subsectio{Methods}
 
-# adjust duplicate names to fit to indicate daily or pre measurement
-names(df.pre) <- gsub("[[:punct:]]x", ".daily", names(df.pre))
-names(df.pre) <- gsub("[[:punct:]]y", ".pre", names(df.pre))
+\subsection{Results}
 
-# names for post measurement
-names.post <- c(
-  "ExternalReference",
-  "assimilation",
-  "separation",
-  "integration",
-  "marginalization",
-  "VIA_heritage",
-  "VIA_Dutch",
-  "anxiety",
-  "swl",
-  "rosenberg",
-  "social_support",
-  "stress",
-  "discrimination",
-  "discrimination_month",
-  "NLE_1month",
-  "NLE_6month",
-  "NLE_12month"
-)
+\begin{figure}[h]
+\centering
+\caption{PRISMA Diagrams for the Theoretical, Methodological, and Empirical Literature.}
+\makebox[\textwidth]{\includegraphics[width=\paperwidth]{Figures/PrismaCombined}}
+\label{fig:PrismaCombined}
+\end{figure}
 
-# reduced data set for post-measurement
-dat.post.red <- dtWorker$raw.post[, names.post]
+\input{Tables/ExclusionsCombined} <!-- Placing this here is not ideal because it is only being created later but probably works. -->
+<!-- \input{Tables/TheoreticalExclusion} -->
 
-# merge post measurement with pre- and daily data
-df <- merge(
-  x = df.pre,
-  y = dat.post.red,
-  by.x = "ExternalReference",
-  by.y = "ExternalReference",
-  all = T
-)
-
-# adjust duplicate names to indicate pre or post
-names(df) <- gsub("[[:punct:]]x", ".pre", names(df))
-names(df) <- gsub("[[:punct:]]y", ".post", names(df))
-
-# add to list
-dtWorker$combined <- df
-
-# create data frame with cleaned data
-df <- dtWorker$combined %>%
-  filter(
-    Finished.pre == 1,
-    Finished.daily == 1,
-    !is.na(ExternalReference)
-  )
-
-# add running number as measurement ID within participants
-df$measureID <- rowidv(df, cols = c("ExternalReference"))
-
-df <- df %>%
-  mutate(
-    PID = as.numeric(factor(ExternalReference)),
-    # participant ID
-    TID = measureID - 1,
-    # time ID with t0 = 0 for meaningfull intercept interpretations
-    date = substr(StartDate, 1, 10),
-    # awkward way of extracting date (best converted to )
-    time = substr(StartDate, 12, 19),
-    # awkward way of extracting time
-    daynum = as.numeric(factor(date)),
-    # all days as numeric for ordering
-    daycor = ifelse(
-      daytime == "morning" &
-        period_to_seconds(hms(time)) < period_to_seconds(hms("12:00:00")) |
-        daytime == "afternoon" &
-          period_to_seconds(hms(time)) < period_to_seconds(hms("19:00:00")),
-      daynum - 1,
-      daynum
-    ),
-    # correctly identify which date the questionnaire is about
-    daycor.lead = sprintf("%02d", daycor),
-    daytime.lt = ifelse(daytime == "morning", "a", "b"),
-    # morning / afternoon to a / b
-    day_time = paste(daycor.lead, daytime.lt, sep = "_"),
-    # combine day id with morning / afternoon
-    session = as.numeric(factor(day_time)),
-    # day and time identifier as numeric id
-    SubTime = chron::times(time.0),
-    time.daily = as.character(time.daily),
-    PPDate = as.Date(df$date.daily),
-    number = replace_na(number, 0),
-    NonDutchNum = replace_na(NonDutchNum, 0)
-  )
-
-dtWorker$clean <- df
-
-# clean up
-rm(df.pre, names.post, dat.post.red, dat.pre.red, df)
-
-# Export reduced Data
-# write.csv(dtWorker$clean, "data/processed/MT_clean-merged_07-05-2018.csv", row.names = F)
-# save(dtWorker$clean, file = "data/processed/MT_clean-merged_07-05-2018.RData")
-```
-
-```{r cleanStudents}
-# our own test IDs
-ownIDs <- c(
-  "beautifulLionfishXXXR5rcgVBzGu8hPvOqrK8UBJBw4owvi9nfRFSFu3lMzYhE",
-  "niceDogoXXXmB8JI5SFu78SF3DVof84mGUPPNUr14p2HYFTtp31a6D1OwAzM6F-K",
-  "amusedQuailXXXmhuc_fpTp8vPkMwDH1BzjaH1d1kHSO1bsPEfsnaEYk4WeVBfPi",
-  "juwGAbtXX0_1kmZtSVqKh3PGaHOICqUyU4iBkrT3nDsI_uifuD1gzKcZerxaM5FL"
-)
-
-# Prepare dfs for Cleaning
-df.pre <- dtStudents$raw.pre %>%
-  mutate_all(na_if, "") %>%
-  mutate_all(na_if, "NA") %>%
-  filter(!is.na(ended)) %>% # remove all who did not finish
-  filter(!e_mail %in% .$e_mail[duplicated(.$e_mail)]) %>% # remove all who did the pre questionnaire multiple times (b/c inconsistent ratings scales)
-  filter(!session %in% ownIDs) %>% # remove our own test
-  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)
-
-df.post <- dtStudents$raw.post %>%
-  mutate_all(na_if, "") %>%
-  mutate_all(na_if, "NA") %>%
-  filter(!is.na(session)) %>% # remove own test runs
-  filter(!session %in% ownIDs) %>% # remove our own test
-  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
-  filter(!is.na(ended)) %>% # remove all who never finished
-  filter(!session %in% .$session[duplicated(.$session)]) %>% # remove all duplicate sessions
-  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)
-
-df.daily <- dtStudents$raw.daily %>%
-  mutate_all(na_if, "") %>%
-  mutate_all(na_if, "NA") %>%
-  filter(!session %in% ownIDs) %>% # remove our own test
-  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
-  filter(!is.na(ended)) %>% # remove all who never finished
-  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)
-
-# merge daily with pre
-dfPreDaily <- merge(
-  x = df.daily,
-  y = df.pre,
-  by = "session",
-  suffixes = c(".daily", ".pre"),
-  all = F
-)
-
-# merge daily with post
-dfCombined <- merge(
-  x = dfPreDaily,
-  y = df.post,
-  by = "session",
-  suffixes = c(".pre", ".post"),
-  all = F
-)
-
-# add to list
-dtStudents$clean <- dfCombined
-
-# clean up workspace
-rm(df.pre, df.daily, df.post, dfPreDaily, dfCombined, ownIDs)
-```
-
-```{r cleanMedical}
-# TBD
-```
-
-## Calculate needed transformations
-
-### Worker
-
-```{r newVarsWorkers}
-df <- dtWorker$clean
-
-# Time and Date Variables
-# remove seconds from afternoon time
-df$SubTime[df$daytime == "afternoon"] <- paste0(substring(as.character(df$time.0[df$daytime == "afternoon"]), 4, 8), ":00")
-df$time.daily[df$daytime == "afternoon" &
-  !is.na(df$time.daily != "<NA>")] <- paste0(substring(as.character(df$time.daily[df$daytime == "afternoon" &
-  !is.na(df$time.daily != "<NA>")]), 4, 8), ":00")
-
-# Correct morning / afternoon date where survey was collected the day after to indicate the correct date that was targeted
-df$PPDate[df$SubTime < "11:50:00" &
-  df$daytime == "morning"] <- df$PPDate[df$SubTime < "11:50:00" &
-  df$daytime == "morning"] - 1
-df$PPDate[df$SubTime < "18:50:00" &
-  df$daytime == "afternoon"] <- df$PPDate[df$SubTime < "18:50:00" &
-  df$daytime == "afternoon"] - 1
-
-# Mood scales
-df$calmness.daily <- rowSums(df[, c("calmness1", "calmness2")], na.rm = T)
-df$alertness.daily <- rowSums(df[, c("alertness1", "alertness2")], na.rm = T)
-df$valence.daily <- rowSums(df[, c("valence1", "valence2")], na.rm = T)
-
-# Need scales
-df$keyMotiveFulfilled <- rowSums(df[, c("keymotive_fulfillemt_1", "keyMotive_noInt_fulf_1")], na.rm = T)
-df$autonomy.daily.all <- rowSums(df[, c("autonomy_1", "autonomy_NoInt_1")], na.rm = T)
-df$competence.daily.all <- rowSums(df[, c("competence_1", "competence_NoInt_1")], na.rm = T)
-# cor(df$relatedness_other_1, df$relatedness_self_1,use="complete.obs")
-df$relatedness.daily.all <- rowMeans(df[, c(
-  "relatedness_other_1",
-  "relatedness_self_1",
-  "relatedness_1_NoInt_1"
-)], na.rm = T)
-df$relatedness_1 <- rowMeans(df[, c("relatedness_other_1", "relatedness_self_1")], na.rm = T)
-
-# summarize by participant (check that everything is within pp might not be the case for )
-between <- df %>%
-  group_by(ExternalReference) %>%
-  mutate(
-    CtContactNL = sum(Contact_dum),
-    CtContactNonNl = sum(inNonDutch),
-    CtContactNLAll = sum(number),
-    CtContactNonNlAll = sum(NonDutchNum),
-    AvKeyNeed = mean(keyMotiveFulfilled, na.rm = T),
-    AvKeyNeedInt = mean(keymotive_fulfillemt_1, na.rm = T),
-    AvKeyNeedNoInt = mean(keyMotive_noInt_fulf_1, na.rm = T),
-    AvAutonomy = mean(autonomy.daily.all, na.rm = T),
-    AvCompetence = mean(competence.daily.all, na.rm = T),
-    AvRelatedness = mean(relatedness.daily.all, na.rm = T),
-    AvThermo = mean(thermometerDutch_1, na.rm = T),
-    AvWB = mean(ExWB_1, na.rm = T)
-  ) %>%
-  ungroup() %>%
-  mutate(
-    CtContactNL_c = scale(CtContactNL, scale = FALSE),
-    AvKeyNeedInt_c = scale(AvKeyNeedInt, scale = FALSE),
-    AvKeyNeed_c = scale(AvKeyNeed, scale = FALSE),
-    CtContactNL_z = scale(CtContactNL, scale = TRUE),
-    AvKeyNeedInt_z = scale(AvKeyNeedInt, scale = TRUE),
-    AvKeyNeed_z = scale(AvKeyNeed, scale = TRUE)
-  )
-
-warning(
-  "some variable transformations (esp. _c and _z) might be across all participants (i.e., not within PP)."
-)
-
-dtWorker$full <- between
-rm(df, between)
-
-# Between participants contact frequency
-workerContactFreq <- dtWorker$full %>%
-  group_by(ExternalReference) %>%
-  summarise(
-    n = n(),
-    SumContactNL = sum(Contact_dum),
-    PercContactNL = SumContactNL / n * 100,
-    SumContactNLAll = sum(number),
-    AvAttitude = mean(thermometerDutch_1, na.rm = T)
-  ) %>%
-  mutate(
-    WinSumContactNL = DescTools::Winsorize(SumContactNL),
-    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
-  )
-
-# dataframe where interaction types are recoded
-workerInteractionType <- dtWorker$full %>%
-  mutate(
-    OutgroupInteraction = as_factor(Contact_dum),
-    NonOutgroupInteraction = as_factor(inNonDutch)
-  )
-
-# save cleaned data
-# save(df.btw, file = "data/processed/df.btw.RData")
-# write_sav(df.btw, "data/processed/MT_clean-merged_pre-post.sav")
-
-# export data to Mplus
-# df.mplus = remove_all_labels(select(df,
-#                                     PID, session,
-#                                     thermometerDutch_1, inNonDutch, Contact_dum,
-#                                     keyMotiveFulfilled, autonomy.daily.all, competence.daily.all, relatedness.daily.all))
-# names(df.mplus)= c("PID", "session", "att", "intin", "intout", "keymot", "aut", "comp", "rel")
-# mplus = df.mplus[order(df.mplus$PID, df.mplus$session),]
-# mplus.intcont = mplus[mplus$intout==1,]
-# prepareMplusData(mplus.intcont, "data/processed/dynamic-subset-intonly.dat")
-```
-
-### Student
-
-```{r newVarsStudents}
-df <- dtStudents$clean
-
-# Add ID variables
-df$PID <- as.numeric(factor(df$session)) # participant ID
-
-# order time
-df$TID <-
-  factor(df$date_period, levels = unique(dtStudents$raw.daily$date_period))
-df$TIDnum <- as.numeric(df$TID) # get numeric TID
-
-# check whether time ordering worked
-df <- df %>%
-  arrange(PID, TID) # %>%
-# View()
-
-# Interaction as Factor
-df$interaction.f <-
-  factor(df$Interaction,
-    levels = c("no interaction", "Dutch", "Non-Dutch")
-  )
-df$intNL <- ifelse(df$Interaction == "Dutch", 1, 0)
-df$intNonNL <- ifelse(df$Interaction == "Non-Dutch", 1, 0)
-
-# -------------------------------------------------------------------------------------------------------------
-#                                       Combine Variables
-# -------------------------------------------------------------------------------------------------------------
-# Relatedness
-pairs.panels.new(
-  df[c("RelatednessSelf", "RelatednessOther")],
-  labels = c(
-    "I shared information about myself.",
-    "X shared information about themselves."
-  )
-)
-df$RelatednessInteraction <-
-  rowMeans(df[c("RelatednessSelf", "RelatednessOther")], na.rm = T)
-df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <-
-  NA
-# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
-df$Relatedness <-
-  rowMeans(df[, c("RelatednessInteraction", "RelatednessNoInteraction")],
-    na.rm =
-      T
-  )
-# Pro-Sociality
-df$ProSo <-
-  rowMeans(df[, c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm = T)
-# Anti-Sociality
-df$AntiSo <-
-  rowMeans(df[, c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm = T)
-
-# -------------------------------------------------------------------------------------------------------------
-#                                 Add Variables related to interaction partner
-# -------------------------------------------------------------------------------------------------------------
-# create function for later lapply
-createIntPartDf <- function(inp) {
-  # prepare the dataframe so that we can forloop over it later
-  tmp <- data.frame(
-    CC = as.character(inp$CC),
-    NewCC = as.character(inp$NewCC),
-    NewName = as.character(inp$NewName),
-    NewCloseness = inp$NewCloseness,
-    NewGender = inp$NewGender,
-    NewEthnicity = as.character(inp$NewEthnicity),
-    NewRelationship = as.character(inp$NewRelationship)
-  )
-
-  tmp$CC2 <- recode(tmp$CC, "SOMEONE ELSE" = "NA")
-  tmp$CC2 <-
-    ifelse(
-      tmp$CC == 1 |
-        tmp$CC == "SOMEONE ELSE",
-      as.character(tmp$NewName),
-      as.character(tmp$CC2)
-    )
-  # maybe add [[:space:]]\b to remove space before word boundary or ^[[:space:]] to remove space in the beginning of a string
-  tmp$CC2 <- gsub("^[[:space:]]", "", tmp$CC2)
-  tmp$NewName <- gsub("^[[:space:]]", "", tmp$NewName)
-
-  # open the variables that will be filled up in the foor-loop
-  tmp$closeness <- rep(NA, nrow(tmp))
-  tmp$gender <- rep(NA, nrow(tmp))
-  tmp$ethnicity <- rep(NA, nrow(tmp))
-  tmp$relationship <- rep(NA, nrow(tmp))
-
-  # Run the for-loop. It finds the variables related to the name of the interaction partner. If there is a repeating interaction
-  # partner (i.e. CC2) it takes the value (i.e. NewCloseness) from the first interaction (i.e. NewName)
-  for (i in 1:nrow(tmp)) {
-    if (is.na(tmp$CC2[i])) {
-      next
-    } else {
-      tmp$closeness[i] <-
-        na.omit(tmp$NewCloseness[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] # find closeness where CC2 matches NewName (na.omit + [1] to get the number)
-      tmp$gender[i] <-
-        na.omit(tmp$NewGender[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] # (na.omit + [1] to get the number and not the rest of the na.omit list)
-      tmp$ethnicity[i] <-
-        na.omit(as.character(tmp$NewEthnicity[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1] # PROBLEM IS THAT THERE ARE TOO MANY NA's: Difficult to deal with
-      tmp$relationship[i] <-
-        na.omit(as.character(tmp$NewRelationship[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1]
-    }
-  }
-
-  out <- tmp
-  out
-}
-
-# split df per participants and run function
-PP <- split(df, df$PID)
-PP <- lapply(PP, createIntPartDf)
-rm(createIntPartDf)
-
-# add variables back to df
-remergePP <- do.call(rbind.data.frame, PP)
-colnames(remergePP) <-
-  paste(colnames(remergePP), "_Calc", sep = "")
-df <- cbind(df, remergePP)
-rm(remergePP, PP)
-
-# -------------------------------------------------------------------------------------------------------------
-#                                 Center Relevant Variables
-# -------------------------------------------------------------------------------------------------------------
-
-df <- df %>%
-  group_by(PID) %>%
-  mutate(
-    KeyNeedFullfillment.cm = mean(KeyNeedFullfillment, na.rm = TRUE),
-    # cluster mean (mean of PP)
-    KeyNeedFullfillment.cwc = KeyNeedFullfillment - KeyNeedFullfillment.cm,
-    # cluster mean centered (within PP centered)
-    closeness.cm = mean(closeness_Calc, na.rm = TRUE),
-    closeness.cwc = closeness_Calc - closeness.cm
-  ) %>%
-  ungroup()
-
-# store
-dtStudents$full <- df
-rm(df)
-
-# Between participants contact frequency
-studentContactFreq <- dtStudents$full %>%
-  group_by(PID) %>%
-  summarise(
-    n = n(),
-    SumContactNL = sum(InteractionDumDutch),
-    PercContactNL = SumContactNL / n * 100,
-    SumContactNLAll = sum(ContactNum[InteractionDumDutch == 1], na.rm = TRUE),
-    AvAttitude = mean(AttitudesDutch, na.rm = TRUE),
-    AvQuality = mean(quality_overall, na.rm = TRUE)
-  ) %>%
-  mutate(
-    WinSumContactNL = DescTools::Winsorize(SumContactNL),
-    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
-  )
-
-# dataframe where interaction types are recoded
-studentInteractionType <- dtStudents$full %>%
-  mutate(
-    NonDutchContact = replace_na(NonDutchContact, 2), # make second non-Dutch countable
-    NonDutchContact = NonDutchContact*-1+2 # recode (yes = 1 -> 1, no = 2 -> 0)
-  ) %>%
-  mutate(
-    OutgroupInteraction = factor(
-      InteractionDumDutch,
-      levels = c(0, 1),
-      labels = c("No", "Yes")
-    ),
-    NonOutgroupInteraction = factor(
-      rowSums(select(., c(InteractionDumNonDutch, NonDutchContact))), # combine the two non-Dutch Q.,
-      levels = c(0, 1),
-      labels = c("No", "Yes")
-    )
-  )
-
-# select a subset of IDs to display in plots
-studentPltIDs <-
-  studentInteractionType %>%
-  group_by(PID) %>%
-  summarise(n = n()) %>%
-  slice_max(n, n = 20) %>% # chose the 20 with the most number of measurements
-  select(PID) %>%
-  as.matrix %>%
-  as.vector
-
-# select a subset of IDs to display in plots (only outgroup interactions)
-studentOutPltIDs <-
-  studentInteractionType %>%
-  filter(OutgroupInteraction == "Yes") %>%
-  group_by(PID) %>%
-  summarise(n = n()) %>%
-  slice_max(n, n = 20) %>% # chose the 20 with the most number of measurements
-  select(PID) %>%
-  as.matrix %>%
-  as.vector
-```
-
-### Medical
-
-```{r newVarsMedical}
-# TBD
-```
-
-# **Worker Sample**
-
-## Data Description
-
-<i class="fas fa-exclamation-triangle"></i> Still in 'scr/workerDescriptive.R'. Needs to be merged with this document.
-
-## Contact Hypothesis
-
-### Interaction Frequency and Outgroup Attitudes
-
-\begin{equation}
-(\#eq:WorkerFreqQualR)
-r_{ContactFrequency, OutgroupAttitudes} \neq 0
-\end{equation}
-
-```{r WorkerFreqAttCor}
-# correlation panel
-pairs.panels.new(
-  workerContactFreq %>% select(SumContactNL, SumContactNLAll, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
-    "Sum:\nNumber of Outgroup Contacts (NL)",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-
-# correlation panel with interaction sums winsorized
-pairs.panels.new(
-  workerContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
-    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-```
-
-TL;DR: Neither the number of interactions nor the number of measurement beeps with an interaction are significantly related with the average outgroup attitudes.
-This is to say that within our data participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
-This might be due to the aggregation within the participants or the small sample size of between participant data.
-Nonetheless, the aggregate data does not support the notion that simply having more interactions with an outgroup results in more positive outgroup attitudes.
-
-### Outgroup Attitudes by Interaction Type
-
-\begin{equation}
-(\#eq:WorkerIntTypeQual)
-\mu_{i,0utgroupInteraction} > \mu_{i,IngroupInteraction}  \\
-Attitude = OutgroupInteraction \times NonOutgroupInteraction
-\end{equation}
-
-<div class="alert alert-info alert-dismissible fade in" role="alert">
-  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
-  <i class="fas fa-exclamation-triangle"></i> <b>Note: </b><br/>
-  mean difference alone probably even more stupid than only ignoring nested data, because we drop lots of data unnecessarily.  
-  And only outgroup interaction Yes / No also weird because interaction group includes people who had only an outgroup interaction and those who also had an interaction with a non-outgroup person, and the no outgroup interaction group includes those who had no interaction at all and those who had an interaction with a non-outgroup person (but no outgroup interaction).
-</div>
-
-#### Regression with interaction term
-
-Across participants: impact of different interaction types [probably meaningless because ignores response sets between participants]
-
-```{r workerInteractionTypePlt, fig.height=12}
-# between participants interaction type
-workerContactType <- dtWorker$full %>%
-  group_by(
-    Contact_dum,
-    inNonDutch
-  ) %>%
-  summarise(
-    n = n(),
-    AttitudeM = mean(thermometerDutch_1, na.rm = T),
-    AttitudeSD = sd(thermometerDutch_1, na.rm = T),
-    AttitudeSE = AttitudeSD / sqrt(n),
-    AttitudeLwr = AttitudeM - 1.96 * AttitudeSE,
-    AttitudeUpr = AttitudeM + 1.96 * AttitudeSE
-  ) %>%
-  ungroup() %>%
-  mutate(InteractionType = paste(
-    ifelse(Contact_dum == 1, "Out", "NoOut"),
-    ifelse(inNonDutch == 1, "In", "NoIn"),
-    sep = ", "
-  ))
-
-# plot bar chart
-ggplot(
-  workerContactType,
-  aes(
-    y = AttitudeM,
-    x = as_factor(Contact_dum),
-    fill = as_factor(inNonDutch)
-  )
-) +
-  geom_bar(
-    stat = "identity",
-    color = "black",
-    position = position_dodge()
-  ) +
-  geom_errorbar(aes(ymin = AttitudeM, ymax = AttitudeUpr),
-    width = .2,
-    position = position_dodge(.9)
-  ) +
-  labs(
-    fill = "Non-Outgroup Interaction",
-    x = "Outgroup Interaction",
-    y = "Outgroup Attitude",
-    title = "Outgroup Attitudes by Interaction Type [95% CI]"
-  ) +
-  scale_fill_grey(
-    start = 0.2,
-    end = 0.8
-  ) +
-  scale_y_continuous(
-    limits = c(0, 100),
-    breaks = c(0, 15, 30, 40, 50, 60, 70, 85, 100),
-    labels = c(
-      "Very cold or unfavorable feelings 0°",
-      "Quite cold and unfavorable feelings 15°",
-      "Fairly cold and unfavorable feelings 30°",
-      "A bit cold and unfavorable feelings 40°",
-      "No feeling at all 50°",
-      "A bit warm and favorable feelings 60°",
-      "Fairly warm and favorable feelings 70° ",
-      "Quite warm and favorable feelings 85° ",
-      "Very warm and favorable feelings 100° "
-    )
-  ) +
-  theme_Publication()
-```
-
-```{r workerModelOlsInteractionType}
-# create list to store Worker models
-mdlWorker <- list()
-
-# regression
-mdlWorker$lmAttInt <-
-  lm(thermometerDutch_1 ~ OutgroupInteraction * NonOutgroupInteraction,
-    data = workerInteractionType
-  )
-# summary(lmWorkerAttInteraction)
-
-summ(
-  mdlWorker$lmAttInt,
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-```
-
-TL;DR: While controlling for interactions with non-Dutch people, outgroup attitudes were significantly higher when participants had an interaction with a Dutch person.
-The effect is relatively small (`r format(round(mdlWorker$lmAttInt$coefficients["OutgroupInteractionYes"], 2), nsmall=2)` points on a 0--100 scale).
-More importantly, however, this analysis lumps all ESM beeps from every participants together and ignores that the data is nested within participants.
-
-#### ML Regression with interaction term
-
-##### Unconditional model
-
-make a model with only the data but a random intercept (unconditional model)
-
-\begin{equation}
-(\#eq:WorkerEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerModelMLAttNull}
-# Create and save Model
-mdlWorker$lmerAttNull <-
-  lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID),
-    data = dtWorker$full
-  ) # use optim if it does not converge
-
-mdlWorker$lmeAttNull <-
-  lme(
-    thermometerDutch_1 ~ 1,
-    random = ~ 1 | PID,
-    data = dtWorker$full,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(lmerWorkerAttNull) #or with the lme function
-summ(mdlWorker$lmerAttNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=dtWorker$full),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
-# Save variances
-mdlWorker$varAttNull <- 
-  VarCorr(mdlWorker$lmeAttNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlWorker$tauAttNull <- 
-  as.numeric(mdlWorker$varAttNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlWorker$sigmaAttNull <- 
-  as.numeric(mdlWorker$varAttNull[2])
-# The ICC estimate (between/between+within) is:
-mdlWorker$IccAttNull <-
-  (as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2])))
-mdlWorker$IccPercAttNull <-
-  ((as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2])))) * 100
-```
-
-ICC $\tau_{00}^2 / (\tau_{00}^2 + \sigma^2)$: The ratio of the between-cluster variance to the total variance is called the Intraclass Correlation.
-It tells you the proportion of the total variance in Y that is accounted for by the clustering.
-(In this case the clustering means clustering observations per participant)
-
-compare the random intercept model to a model without a random intercept (i.e., without levels at all)
-
-```{r workerModelInterceptNull}
-# Create and save Model
-mdlWorker$glsAttNull  <-
-  gls(thermometerDutch_1 ~ 1,
-      data = dtWorker$full,
-      control = list(opt = "nlmimb"))
-
-# calculate Deviances manually:
-mdlWorker$DevianceGlsNull <- logLik(mdlWorker$glsAttNull) * -2
-mdlWorker$DevianceMlNull <- logLik(mdlWorker$lmeAttNull) * -2
-
-# Compare the two null models:
-anova(mdlWorker$glsAttNull,
-      mdlWorker$lmeAttNull) %>% 
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-```
-
-We find that an estimated `r format(round(mdlWorker$IccPercAttNull, 2), nsmall=2)`% of the variation in Feeling Thermometer scores is explained by between participant differences (clustering by PID).
-This is to say that `r format(round(mdlWorker$IccPercAttNull, 2), nsmall=2)`% of the variance in any individual report of Attitudes towards the Dutch can be explained by the properties of the individual who provided the rating.
-And we find that including 'participant' as a predictor adds significantly to the model.
-
-##### random intercept
-
-\begin{equation}
-(\#eq:WorkerInteractionTypeModel)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerModelInterceptAttType}
-# Create and save Model
-mdlWorker$lmeInterceptAttType <-
-  lme(
-    thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction,
-    random =  ~ 1 | PID,
-    data = workerInteractionType
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  lmer(
-    thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
-    data = workerInteractionType
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(mdlWorker$lmeAttNull, 
-      mdlWorker$lmeInterceptAttType) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorker$varInterceptAttType <- 
-  lme4::VarCorr(mdlWorker$lmeInterceptAttType)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorker$varBtwInterceptAttType <-
-  1 - (as.numeric(mdlWorker$varInterceptAttType[1]) / as.numeric(mdlWorker$varAttNull[1]))
-mdlWorker$varBtwPercInterceptAttType <-
-  (1 - (as.numeric(mdlWorker$varInterceptAttType[1]) / as.numeric(mdlWorker$varAttNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorker$varWithinInterceptAttType <-
-  1 - (as.numeric(mdlWorker$varInterceptAttType[2]) / as.numeric(mdlWorker$varAttNull[2]))
-mdlWorker$varWithinPercInterceptAttType <-
-  (1 - (as.numeric(mdlWorker$varInterceptAttType[2]) / as.numeric(mdlWorker$varAttNull[2]))) * 100
-```
-
-tl;dr: Interaction with Dutch is great predictor, interactions with non-Dutch is not.
-
-##### random slope
-
-\begin{equation}
-(\#eq:RandSlopesEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerModelSlopesInteractionType}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorker$lmeSlopesAttType <- lme(
-  thermometerDutch_1 ~
-    OutgroupInteraction + NonOutgroupInteraction,
-  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  data = workerInteractionType
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorker$lmerSlopesAttType <- lmer(
-    thermometerDutch_1 ~
-      OutgroupInteraction + NonOutgroupInteraction +
-      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
-    data = workerInteractionType
-  ), 
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlWorker$lmeInterceptAttType, 
-      mdlWorker$lmeSlopesAttType) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorker$varSlopesAttType <- 
-  lme4::VarCorr(mdlWorker$lmeSlopesAttType)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorker$varBtwSlopesAttType <- 
-  1 - (as.numeric(mdlWorker$varSlopesAttType[1]) / as.numeric(mdlWorker$varInterceptAttType[1]))
-mdlWorker$varBtwPercSlopesAttType <- 
-  (1 - (as.numeric(mdlWorker$varSlopesAttType[1]) / as.numeric(mdlWorker$varInterceptAttType[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorker$varWithinSlopesAttType <- 
-  1 - (as.numeric(mdlWorker$varSlopesAttType[2]) / as.numeric(mdlWorker$varInterceptAttType[2]))
-mdlWorker$varWithinPercSlopesAttType <- 
-  (1 - (as.numeric(mdlWorker$varSlopesAttType[2]) / as.numeric(mdlWorker$varInterceptAttType[2]))) * 100
-
-# Assumption Checks:
-mdlWorker$diagSlopesAttType <-
-  sjPlot::plot_model(mdlWorker$lmerSlopesAttType, type = "diag")
-grid.arrange(
-  mdlWorker$diagSlopesAttType[[1]],
-  mdlWorker$diagSlopesAttType[[2]]$`PID`,
-  mdlWorker$diagSlopesAttType[[3]],
-  mdlWorker$diagSlopesAttType[[4]]
-)
-
-# Plot prediction model
-mdlWorker$predSlopesAttType <- 
-  workerInteractionType %>%
-  select(thermometerDutch_1, session, PID) %>% 
-  mutate(measure = predict(mdlWorker$lmeSlopesAttType,
-                           workerInteractionType,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorker$predPltSlopesAttType <-
-    ggplot(data = mdlWorker$predSlopesAttType, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Worker_PredictionPlot_SlopesAttType.png",
-  mdlWorker$predPltSlopesAttType,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-TL;DR: Random slopes don't add much for this super simple model.
-
-### Interaction Frequency and Interaction Quality
-
-\begin{equation}
-(\#eq:FreqQual)
-Attitude = ContactFreq \times AverageContactQual
-\end{equation}
-
-```{r workerFreqQualCor}
-# prepare data
-workerAvFreQual <- dtWorker$full %>%
-  group_by(ExternalReference) %>%
-  summarise(
-    n = n(),
-    SumContactNL = sum(Contact_dum),
-    PercContactNL = SumContactNL / n * 100,
-    SumContactNLAll = sum(number),
-    AvAttitude = mean(thermometerDutch_1, na.rm = TRUE),
-    AvQuality = mean(quality_overall_1, na.rm = TRUE)
-  ) %>%
-  mutate(
-    WinSumContactNL = DescTools::Winsorize(SumContactNL),
-    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
-  )
-
-# correlation panel
-pairs.panels.new(
-  workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
-    "Sum:\nNumber of Outgroup Contacts (NL)",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-
-# correlation panel with interaction sums winsorized
-pairs.panels.new(
-  workerAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
-    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-```
-
-TL;DR: There is a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
-Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
-However, the frequency of intergroup interactions had no meaningfull correlation with either the average interaction quality or average outgroup attitudes.
-
-```{r workerModelOlsAttFreqQual}
-# regression
-mdlWorker$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL * AvQuality, data = workerAvFreQual)
-# summary(lmWorkerAttFreqQualX)
-
-summ(
-  mdlWorker$lmAttFreqQualX,
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-interactions::interact_plot(
-  mdlWorker$lmAttFreqQualX,
-  pred = AvQuality,
-  modx = SumContactNL,
-  interval = TRUE,
-  partial.residuals = TRUE
-)
-
-interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
-                             pred = AvQuality,
-                             modx = SumContactNL,
-                             alpha = .05)
-```
-
-TL;DR: We find that interaction quality is significantly related to higher outgroup attitudes (albeit with a small effect size).
-We also find that in our sample with an increasing number of interactions the positive effect of interaction quality becomes weaker.
-However, note that this is based on data aggregating all within participant nuances and is only the date of 21 people.
-
-## Need Fulfillment
-
-### Need fulfillment and Attitudes
-
-##### Unconditional model
-
-make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
-
-```{r workerPrepOutgroupSubsample}
-# see how large our outgroup interaction subset actually is
-tbl_cross(
-  workerInteractionType,
-  row = OutgroupInteraction,
-  col = NonOutgroupInteraction,
-  percent = "row"
-)
-
-# create outgroup interaction subset
-workerOutgroupInteraction <- workerInteractionType %>%
-  filter(OutgroupInteraction == "Yes")
-
-# create empty list to organize models
-mdlWorkerOut <- 
-  list(
-    Att = list(),
-    Qlt = list()
-  )
-```
-
-\begin{equation}
-(\#eq:WorkerOutEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerOutModelMLAttNull}
-# Create and save Model
-mdlWorkerOut$Att$lmerNull <-
-  lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID), 
-             data = workerOutgroupInteraction) # use optim if it does not converge
-mdlWorkerOut$Att$lmeNull <-
-  lme(
-    thermometerDutch_1 ~ 1,
-    random = ~ 1 | PID,
-    data = workerOutgroupInteraction,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.ML.r) #or with the lme function
-summ(mdlWorkerOut$Att$lmerNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=dtWorker$full),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
-# Save variances
-mdlWorkerOut$Att$varNull <- 
-  VarCorr(mdlWorkerOut$Att$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlWorkerOut$Att$tauNull <- 
-  as.numeric(mdlWorkerOut$Att$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlWorkerOut$Att$sigmaNull <- 
-  as.numeric(mdlWorkerOut$Att$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlWorkerOut$Att$IccNull <-
-  (as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2])))
-mdlWorkerOut$Att$IccPercNull <-
-  ((as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2])))) * 100
-```
-
-#### random intercept
-
-\begin{equation}
-(\#eq:AttitudeNeedEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerOutModelInterceptAttCore}
-# Create and save Model
-mdlWorkerOut$Att$lmeInterceptCore <-
-  lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1,
-    random = ~ 1 | PID,
-    data = workerOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  lmer(thermometerDutch_1 ~ keymotive_fulfillemt_1 + (1 | PID), 
-       data = workerOutgroupInteraction),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeNull, 
-      mdlWorkerOut$Att$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varInterceptCore <-
-  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwInterceptCore <- 
-  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCore[1]) / as.numeric(mdlWorkerOut$Att$varNull[1]))
-mdlWorkerOut$Att$varBtwPercInterceptCore <- 
-  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCore[1]) / as.numeric(mdlWorkerOut$Att$varNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinInterceptCore <-
-  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCore[2]) / as.numeric(mdlWorkerOut$Att$varNull[2]))
-mdlWorkerOut$Att$varWithinPercInterceptCore <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCore[2]) / as.numeric(mdlWorkerOut$Att$varNull[2]))) * 100
-```
-
-TL;DR: Situational core need relates significantly to outgroup attitudes.
-The core need has little explained variance between participants (compared to the null model: Variance Explained = 1 – (Var with Predictor/Var without Predictor); `r format(round(mdlWorkerOut$Att$varBtwPercInterceptCore, 2),nsmall=2)`%).
-The variance explained within participants is small to medium (`r format(round(mdlWorkerOut$Att$varWithinPercInterceptCore, 2),nsmall=2)`%)
-
-#### random slope
-
-\begin{equation}
-(\#eq:AttitudeNeedRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerOutModelSlopesAttCore}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Att$lmeSlopesCore <-
-  lme(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1,
-    random = ~ 1 + keymotive_fulfillemt_1 | PID,
-    control = lmeControl(opt = "optim"),
-    data = workerOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Att$lmerSlopesCore <- lmer(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1 +
-      (1 + keymotive_fulfillemt_1 | PID),
-    data = workerOutgroupInteraction
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeInterceptCore, 
-      mdlWorkerOut$Att$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varSlopesCore <- 
-  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwSlopesCore <-
-  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCore[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[1]))
-mdlWorkerOut$Att$varBtwPercSlopesCore <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCore[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinSlopesCore <-
-  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCore[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[2]))
-mdlWorkerOut$Att$varWithinPercSlopesCore <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCore[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[2]))) * 100
-
-# Assumption Checks:
-mdlWorkerOut$Att$diagSlopesCore <- 
-  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCore, type = "diag")
-grid.arrange(
-  mdlWorkerOut$Att$diagSlopesCore[[1]],
-  mdlWorkerOut$Att$diagSlopesCore[[2]]$`PID`,
-  mdlWorkerOut$Att$diagSlopesCore[[3]],
-  mdlWorkerOut$Att$diagSlopesCore[[4]]
-)
-
-# Plot prediction model
-mdlWorkerOut$Att$predSlopesCore <- 
-  workerOutgroupInteraction %>%
-  select(thermometerDutch_1, session, PID) %>% 
-  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCore,
-                           workerOutgroupInteraction,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorkerOut$Att$predPltSlopesCore <-
-    ggplot(data = mdlWorkerOut$Att$predSlopesCore, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCore.png",
-  mdlWorkerOut$Att$predPltSlopesCore,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-TL;DR: The random slope adds significantly to the prediction model.
-
-<div class="alert alert-warning alert-dismissible fade in" role="alert">
-  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
-  <i class="fas fa-exclamation-triangle"></i> <b>Check needed: </b><br/>
-  Something is with the variances explained (between = `r format(round(mdlWorkerOut$Att$varBtwPercSlopesCore, 2),nsmall=2)`%, within = `r format(round(mdlWorkerOut$Att$varWithinPercSlopesCore, 2),nsmall=2)`%).
-This is when comparing the random intercepts to the random slopes model.
-</div>
-
-### Need fulfillment and Interaction Quality
-
-##### Unconditional model
-
-make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
-
-\begin{equation}
-(\#eq:WorkerOutQualEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerOutModelMLQltNull}
-# Create and save Model
-mdlWorkerOut$Qlt$lmerNull <-
-  lme4::lmer(quality_overall_1 ~ 1 + (1 | PID), 
-             data = workerOutgroupInteraction) # use optim if it does not converge
-mdlWorkerOut$Qlt$lmeNull <-
-  lme(
-    quality_overall_1 ~ 1,
-    random = ~ 1 | PID,
-    data = workerOutgroupInteraction,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.Qual.ML.r) #or with the lme function
-summ(mdlWorkerOut$Qlt$lmerNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
-# Save variances
-mdlWorkerOut$Qlt$varNull <- 
-  VarCorr(mdlWorkerOut$Qlt$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlWorkerOut$Qlt$tauNull <- 
-  as.numeric(mdlWorkerOut$Qlt$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlWorkerOut$Qlt$sigmaNull <- 
-  as.numeric(mdlWorkerOut$Qlt$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlWorkerOut$Qlt$IccNull <-
-  (as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2])))
-mdlWorkerOut$Qlt$IccPercNull <-
-  ((as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2])))) * 100
-```
-
-#### random intercept
-
-\begin{equation}
-(\#eq:QualityNeedEq)
-InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerOutModelInterceptQltCore}
-# Create and save Model
-mdlWorkerOut$Qlt$lmeInterceptCore <-
-  lme(
-    quality_overall_1 ~ keymotive_fulfillemt_1,
-    random = ~ 1 | PID,
-    data = workerOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  lmer(quality_overall_1 ~ keymotive_fulfillemt_1 + (1 | PID), 
-       data = workerOutgroupInteraction),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(quality_overall_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Qlt$lmeNull, 
-      mdlWorkerOut$Qlt$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Qlt$varInterceptCore <-
-  lme4::VarCorr(mdlWorkerOut$Qlt$lmeInterceptCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Qlt$varBtwInterceptCore <- 
-  1 - (as.numeric(mdlWorkerOut$Qlt$varInterceptCore[1]) / as.numeric(mdlWorkerOut$Qlt$varNull[1]))
-mdlWorkerOut$Qlt$varBtwPercInterceptCore <- 
-  (1 - (as.numeric(mdlWorkerOut$Qlt$varInterceptCore[1]) / as.numeric(mdlWorkerOut$Qlt$varNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Qlt$varWithinInterceptCore <-
-  1 - (as.numeric(mdlWorkerOut$Qlt$varInterceptCore[2]) / as.numeric(mdlWorkerOut$Qlt$varNull[2]))
-mdlWorkerOut$Qlt$varWithinPercInterceptCore <-
-  (1 - (as.numeric(mdlWorkerOut$Qlt$varInterceptCore[2]) / as.numeric(mdlWorkerOut$Qlt$varNull[2]))) * 100
-```
-
-TL;DR: Situational core need relates significantly to interaction quality.
-The core need explained substantial variance between participants (`r format(round(mdlWorkerOut$Qlt$varBtwPercInterceptCore, 2),nsmall=2)`%).
-The variance explained within participants is also medium (`r format(round(mdlWorkerOut$Qlt$varWithinPercInterceptCore, 2),nsmall=2)`%)
-
-#### random slope
-
-\begin{equation}
-(\#eq:QualityNeedRandEq)
-InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerOutModelSlopesQltCore}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Qlt$lmeSlopesCore <-
-  lme(
-    quality_overall_1 ~
-      keymotive_fulfillemt_1,
-    random = ~ 1 + keymotive_fulfillemt_1 | PID,
-    control = lmeControl(opt = "optim"),
-    data = workerOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Qlt$lmerSlopesCore <-
-    lmer(
-      quality_overall_1 ~
-        keymotive_fulfillemt_1 +
-        (1 + keymotive_fulfillemt_1 | PID),
-      data = workerOutgroupInteraction
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(mdlWorkerOut$Qlt$lmerSlopesCore,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Qlt$lmeInterceptCore, 
-      mdlWorkerOut$Qlt$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Qlt$varSlopesCore <- 
-  lme4::VarCorr(mdlWorkerOut$Qlt$lmeSlopesCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Qlt$varBtwSlopesCore <-
-  1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[1]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[1]))
-mdlWorkerOut$Qlt$varBtwPercSlopesCore <-
-  (1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[1]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Qlt$varWithinSlopesCore <-
-  1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[2]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[2]))
-mdlWorkerOut$Qlt$varWithinPercSlopesCore <-
-  (1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[2]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[2]))) * 100
-```
-
-TL;DR: random slopes does not add significantly. Stay with simpler model.
-
-### Need fulfillment, Interaction Quality, and Attitudes
-
-#### random intercept
-
-\begin{equation}
-(\#eq:AttitudeQualityNeedEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerOutModelInterceptAttCoreQlt}
-# Create and save Model
-mdlWorkerOut$Att$lmeInterceptCoreQlt <-
-  lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1 + quality_overall_1,
-    random = ~ 1 | PID,
-    data = workerOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  lmer(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1 + quality_overall_1 + (1 | PID),
-    data = workerOutgroupInteraction
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(
-  mdlWorkerOut$Att$lmeNull, 
-  mdlWorkerOut$Att$lmeInterceptCoreQlt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varInterceptCoreQlt <-
-  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreQlt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwInterceptCoreQlt <- 
-  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[1]) / as.numeric(mdlWorkerOut$Att$varNull[1]))
-mdlWorkerOut$Att$varBtwPercInterceptCoreQlt <- 
-  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[1]) / as.numeric(mdlWorkerOut$Att$varNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinInterceptCoreQlt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[2]) / as.numeric(mdlWorkerOut$Att$varNull[2]))
-mdlWorkerOut$Att$varWithinPercInterceptCoreQlt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[2]) / as.numeric(mdlWorkerOut$Att$varNull[2]))) * 100
-```
-
-TL;DR: Variance explained in outgroup attitudes is of medium effect size (between: `r format(round(mdlWorkerOut$Att$varBtwPercInterceptCoreQlt,2),nsmall=2)`%, within: `r format(round(mdlWorkerOut$Att$varWithinPercInterceptCoreQlt,2),nsmall=2)`%)
-
-#### random slope
-
-\begin{equation}
-(\#eq:AttitudeQualityNeedRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerOutModelSlopesAttCoreQlt}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Att$lmeSlopesCoreQlt <-
-  lme(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1 + quality_overall_1,
-    random = ~ 1 + keymotive_fulfillemt_1 + quality_overall_1 | PID,
-    control = lmeControl(opt = "optim"),
-    data = workerOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Att$lmerSlopesCoreQlt <- lmer(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1 + quality_overall_1 +
-      (1 + keymotive_fulfillemt_1 + quality_overall_1 | PID),
-    data = workerOutgroupInteraction
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(
-  mdlWorkerOut$Att$lmeNull,
-  mdlWorkerOut$Att$lmeInterceptCoreQlt,
-  mdlWorkerOut$Att$lmeSlopesCoreQlt
-) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varSlopesCoreQlt <- 
-  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreQlt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwSlopesCoreQlt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[1]))
-mdlWorkerOut$Att$varBtwPercSlopesCoreQlt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinSlopesCoreQlt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[2]))
-mdlWorkerOut$Att$varWithinPercSlopesCoreQlt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[2]))) * 100
-
-# Assumption Checks:
-mdlWorkerOut$Att$diagSlopesCoreQlt <- 
-  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreQlt, type = "diag")
-grid.arrange(
-  mdlWorkerOut$Att$diagSlopesCoreQlt[[1]],
-  mdlWorkerOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
-  mdlWorkerOut$Att$diagSlopesCoreQlt[[3]],
-  mdlWorkerOut$Att$diagSlopesCoreQlt[[4]]
-)
-
-# Plot prediction model
-mdlWorkerOut$Att$predSlopesCoreQlt <- 
-  workerOutgroupInteraction %>%
-  select(thermometerDutch_1, session, PID) %>% 
-  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreQlt,
-                           workerOutgroupInteraction,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorkerOut$Att$predPltSlopesCoreQlt <-
-    ggplot(data = mdlWorkerOut$Att$predSlopesCoreQlt, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreQlt.png",
-  mdlWorkerOut$Att$predPltSlopesCoreQlt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-#### Compare models
-
-Interpretation of Mediation like results.
-
-### Check for robustness
-
-#### Interaction Type
-
-##### random intercept
-
-\begin{equation}
-(\#eq:AttitudeNeedInteractionEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerModelInterceptAttCoreInt}
-# Create and save Model
-mdlWorker$lmeInterceptAttCoreInt <-
-  lme(
-    thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction,
-    random =  ~ 1 | PID,
-    data = workerInteractionType
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlWorker$lmerInterceptAttCoreInt <- lmer(
-    thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction + (1 | PID),
-    data = workerInteractionType
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(mdlWorker$lmeAttNull, 
-      mdlWorker$lmeInterceptAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorker$varInterceptAttCoreInt <- 
-  lme4::VarCorr(mdlWorker$lmeInterceptAttCoreInt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorker$varBtwInterceptAttCoreInt <-
-  1 - (as.numeric(mdlWorker$varInterceptAttCoreInt[1]) / as.numeric(mdlWorker$varAttNull[1]))
-mdlWorker$varBtwPercInterceptAttCoreInt <-
-  (1 - (as.numeric(mdlWorker$varInterceptAttCoreInt[1]) / as.numeric(mdlWorker$varAttNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorker$varWithinInterceptAttCoreInt <-
-  1 - (as.numeric(mdlWorker$varInterceptAttCoreInt[2]) / as.numeric(mdlWorker$varAttNull[2]))
-mdlWorker$varWithinPercInterceptAttCoreInt <-
-  (1 - (as.numeric(mdlWorker$varInterceptAttCoreInt[2]) / as.numeric(mdlWorker$varAttNull[2]))) * 100
-```
-
-##### random slope
-
-\begin{equation}
-(\#eq:AttitudeNeedInteractionRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti}  + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerModelSlopesAttCoreIntX}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorker$lmeSlopesAttCoreInt <- lme(
-  thermometerDutch_1 ~
-    keyMotiveFulfilled * OutgroupInteraction,
-  random = ~ 1 + keyMotiveFulfilled + OutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  data = workerInteractionType
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorker$lmerSlopesAttCoreInt <- lmer(
-    thermometerDutch_1 ~
-      keyMotiveFulfilled * OutgroupInteraction +
-      (1 + keyMotiveFulfilled + OutgroupInteraction | PID),
-    data = workerInteractionType
-  ), 
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlWorker$lmeAttNull, 
-      mdlWorker$lmeInterceptAttCoreInt,
-      mdlWorker$lmeSlopesAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorker$varSlopesAttCoreInt <- 
-  lme4::VarCorr(mdlWorker$lmeSlopesAttCoreInt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorker$varBtwSlopesAttCoreInt <- 
-  1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[1]) / as.numeric(mdlWorker$varInterceptAttCoreInt[1]))
-mdlWorker$varBtwPercSlopesAttCoreInt <- 
-  (1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[1]) / as.numeric(mdlWorker$varInterceptAttCoreInt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorker$varWithinSlopesAttCoreInt <- 
-  1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[2]) / as.numeric(mdlWorker$varInterceptAttCoreInt[2]))
-mdlWorker$varWithinPercSlopesAttCoreInt <- 
-  (1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[2]) / as.numeric(mdlWorker$varInterceptAttCoreInt[2]))) * 100
-
-# Assumption Checks:
-mdlWorker$diagSlopesAttCoreInt <-
-  sjPlot::plot_model(mdlWorker$lmerSlopesAttCoreInt, type = "diag")
-grid.arrange(
-  mdlWorker$diagSlopesAttCoreInt[[1]],
-  mdlWorker$diagSlopesAttCoreInt[[2]]$`PID`,
-  mdlWorker$diagSlopesAttCoreInt[[3]],
-  mdlWorker$diagSlopesAttCoreInt[[4]]
-)
-
-# Plot prediction model
-mdlWorker$predSlopesAttCoreInt <- 
-  workerInteractionType %>%
-  select(thermometerDutch_1, session, PID) %>% 
-  mutate(measure = predict(mdlWorker$lmeSlopesAttCoreInt,
-                           workerInteractionType,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorker$predPltSlopesAttCoreInt <-
-    ggplot(data = mdlWorker$predSlopesAttCoreInt, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Worker_PredictionPlot_SlopesAttCoreInt.png",
-  mdlWorker$predPltSlopesAttCoreInt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-##### Plot Interaction
-
-```{r workerModelInterceptAttCoreIntPlt}
-# visualize interaction
-## Without ML structure
-ggplot(data = workerInteractionType,
-       aes(x = keyMotiveFulfilled,
-           y = thermometerDutch_1,
-           fill = OutgroupInteraction)) +
-  #geom_point()+
-  geom_smooth(method = 'lm',
-              aes(linetype = OutgroupInteraction),
-              color = "black") +
-  #facet_wrap(~PID, ncol = 6)+
-  scale_linetype_manual(values = c("dashed", "solid")) +
-  scale_fill_manual(values = c("darkgrey", "black")) +
-  #scale_colour_manual(values=c("grey20", "black"), name="Intergroup Contact")+
-  scale_y_continuous(
-    limits = c(50, 100),
-    breaks = seq(50, 100, by = 10),
-    position = "left"
-  ) +
-  scale_x_continuous(limits = c(-50, 50), breaks = seq(-50, 50, by = 10)) +
-  labs(
-    title = "Without ML stucture",
-    x = "Fulfillment Core Need",
-    y = "Outgroup Attitudes",
-    fill = "Intergroup Contact",
-    linetype = "Intergroup Contact"
-  ) +
-  theme_Publication() +
-  theme(legend.position = "bottom",
-        legend.key.size = unit(1, "cm"))
-## With ML structure
-# create parameters for prediction
-datNew = data.frame(
-  OutgroupInteraction = factor(rep(c("No", "Yes"), each = 21)),
-  keyMotiveFulfilled = rep(seq(-50, 50, 5), 2),
-  PID = 0
-)
-
-# Predict values, clean up and calculate SE
-PI <-
-  merTools::predictInterval(
-    merMod = mdlWorker$lmerSlopesAttCoreInt,
-    newdata = datNew,
-    level = 0.95,
-    stat = "mean",
-    type = "linear.prediction",
-    include.resid.var = F,
-    fix.intercept.variance = F
-  )
-mdlWorker$predInterceptAttCoreIntX <- 
-  cbind(datNew, PI)
-mdlWorker$predInterceptAttCoreIntX$se <-
-  (mdlWorker$predInterceptAttCoreIntX$upr - mdlWorker$predInterceptAttCoreIntX$fit) / 1.96
-rm(datNew, PI)
-
-# Plot predicted values with SE
-ggplot(
-  mdlWorker$predInterceptAttCoreIntX,
-  aes(x = keyMotiveFulfilled,
-      y = fit,
-      fill = OutgroupInteraction)
-)+
-  #geom_point() +
-  geom_line(aes(linetype = as.factor(OutgroupInteraction)), size = 1) +
-  #facet_wrap(~PID, ncol = 6)+
-  geom_ribbon(data = mdlWorker$predInterceptAttCoreIntX,
-              aes(ymin = fit - se, ymax = fit + se),
-              alpha = 0.3) +
-  scale_x_continuous(breaks = seq(-50, 50, 10)) +
-  scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
-  scale_linetype_manual(values = c("dashed", "solid")) +
-  scale_fill_manual(values = c("darkgrey", "black")) +
-  labs(
-    x = "Fulfillment Core Need",
-    y = "Outgroup Attitude (NL)",
-    fill = "Intergroup Contact",
-    linetype = "Intergroup Contact",
-    title = "Based on Model Predictions"
-  ) +
-  theme_Publication()
-
-# #### Bayesian estimation !! ONLY RUN ON FINAL RENDER !! Takes forever ####
-# options(mc.cores = parallel::detectCores())  # Run many chains simultaneously
-# brmfit <- brm(
-#   thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction + 
-#     (1 + keyMotiveFulfilled + OutgroupInteraction | PID),
-#   data = workerInteractionType,
-#   family = gaussian,
-#   iter = 1000,
-#   chains = 4
-# )
-# 
-# # create parameters for prediction:
-# datNew = data.frame(
-#   OutgroupInteraction = rep(c("No", "Yes"), each = 101),
-#   keyMotiveFulfilled = rep(seq(-50, 50, 1), 2)
-# )
-# # Save predicted values and adjust names and labels
-# fitavg <-
-#   cbind(datNew,
-#         fitted(brmfit, newdata = datNew, re_formula = NA)[, -2])
-# names(fitavg)[names(fitavg) == "Estimate"] = "pred"
-# fitavg$se <- (fitavg$Q97.5 - fitavg$pred) / 1.96
-# 
-# # Plot Bayesian SE prediction interval
-# ggplot(fitavg,
-#        aes(x = keyMotiveFulfilled,
-#            y = pred,
-#            fill = OutgroupInteraction)) +
-#   scale_x_continuous(breaks = seq(-50, 50, 10)) +
-#   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
-#   geom_line(aes(linetype = OutgroupInteraction), size = 1) +
-#   geom_ribbon(aes(ymin = pred - se, ymax = pred + se), alpha = 0.2) +
-#   scale_linetype_manual(values = c("dashed", "solid")) +
-#   scale_fill_manual(values = c("darkgrey", "black")) +
-#   labs(
-#     x = "Fulfillment Core Need",
-#     y = "Outgroup Attitude (NL)",
-#     fill = "Intergroup Contact",
-#     linetype = "Intergroup Contact",
-#     title = "Based on Bayesian Prediction Interval"
-#   ) +
-#   theme_Publication()
-# 
-# # plot all overlayed posteriors:
-# pst <- posterior_samples(brmfit, "b")
-# ggplot(workerInteractionType,
-#        aes(x = keyMotiveFulfilled, y = thermometerDutch_1)) +
-#   geom_point(shape = 4, alpha = .1) +
-#   geom_tile() +
-#   geom_abline(
-#     data = pst,
-#     aes(intercept = b_Intercept, slope = b_keyMotiveFulfilled),
-#     alpha = .025,
-#     size = .4
-#   ) +
-#   labs(title = "slope Posteriors",
-#        x = "Fulfillment Core Need",
-#        y = "Outgroup Attitudes (NL)") +
-#   theme_Publication()
-# rm(datNew, brmfit, fitavg, pst)
-```
-
-#### Other psychological needs
-
-##### random intercept
-
-\begin{equation}
-(\#eq:AttitudeNeedSdtEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerOutModelInterceptAttCoreSdt}
-# Create and save Model
-mdlWorkerOut$Att$lmeInterceptCoreSdt <-
-  lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1,
-    random = ~ 1 | PID,
-    data = workerOutgroupInteraction,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlWorkerOut$Att$lmerInterceptCoreSdt <- lmer(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 + (1 | PID),
-    data = workerOutgroupInteraction
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# compute lme for core model with same number of observations for comparison
-# !! LOOK INTO MISSINGNESS (only one observation) !!
-lmeInterceptCoreRed <-
-  lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1,
-    random = ~ 1 | PID,
-    data = workerOutgroupInteraction %>% filter(!is.na(autonomy_1))
-  )
-
-# Compare new model to previous step
-anova(
-  lmeInterceptCoreRed, 
-  mdlWorkerOut$Att$lmeInterceptCoreSdt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-rm(lmeInterceptCoreRed)
-
-# Save variances
-mdlWorkerOut$Att$varInterceptCoreSdt <-
-  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreSdt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwInterceptCoreSdt <- 
-  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[1]))
-mdlWorkerOut$Att$varBtwPercInterceptCoreSdt <- 
-  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinInterceptCoreSdt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[2]))
-mdlWorkerOut$Att$varWithinPercInterceptCoreSdt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[2]))) * 100
-```
-
-##### random slope
-
-\begin{equation}
-(\#eq:AttitudeNeedSdtRandEq)
-Attitude_{ti} = \\gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r workerOutModelSlopesAttCoreSdt}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Att$lmeSlopesCoreSdt <-
-  lme(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1,
-    random = ~ 1 + keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 | PID,
-    control = lmeControl(opt = "optim"),
-    data = workerOutgroupInteraction,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Att$lmerSlopesCoreSdt <- lmer(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 +
-      (1 + keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 | PID),
-    data = workerOutgroupInteraction
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeInterceptCoreSdt, 
-      mdlWorkerOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varSlopesCoreSdt <- 
-  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreSdt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwSlopesCoreSdt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]))
-mdlWorkerOut$Att$varBtwPercSlopesCoreSdt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinSlopesCoreSdt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]))
-mdlWorkerOut$Att$varWithinPercSlopesCoreSdt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]))) * 100
-
-# Assumption Checks:
-mdlWorkerOut$Att$diagSlopesCoreSdt <- 
-  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreSdt, type = "diag")
-grid.arrange(
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[1]],
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[3]],
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[4]]
-)
-
-# Plot prediction model
-mdlWorkerOut$Att$predSlopesCoreSdt <- 
-  workerOutgroupInteraction %>%
-  filter(!is.na(autonomy_1)) %>%
-  select(thermometerDutch_1, session, PID, autonomy_1) %>% 
-  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreSdt,
-                           workerOutgroupInteraction %>% filter(!is.na(autonomy_1)),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorkerOut$Att$predPltSlopesCoreSdt <-
-    ggplot(data = mdlWorkerOut$Att$predSlopesCoreSdt, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreStd.png",
-  mdlWorkerOut$Att$predPltSlopesCoreSdt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-# **Student Sample**
-
-## Data Description
-
-<i class="fas fa-exclamation-triangle"></i> Still in 'scr/studentDescriptive.R'. Needs to be merged with this document.
-
-## Contact Hypothesis
-
-### Interaction Frequency and Outgroup Attitudes
-
-\begin{equation}
-(\#eq:studentFreqQualR)
-r_{ContactFrequency, OutgroupAttitudes} \neq 0
-\end{equation}
-
-```{r studentFreqAttCor}
-# correlation panel
-pairs.panels.new(
-  studentContactFreq %>% select(SumContactNL, SumContactNLAll, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
-    "Sum:\nNumber of Outgroup Contacts (NL)",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-
-# correlation panel with interaction sums winsorized
-pairs.panels.new(
-  studentContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
-    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-```
-
-TL;DR: Neither the number of interactions nor the number of measurement beeps with an interaction are significantly related with the average outgroup attitudes.
-This is to say that within our data participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
-This might be due to the aggregation within the participants or the small sample size of between participant data.
-Nonetheless, the aggregate data does not support the notion that simply having more interactions with an outgroup results in more positive outgroup attitudes.
-
-### Outgroup Attitudes by Interaction Type
-
-\begin{equation}
-(\#eq:studentIntTypeQual)
-\mu_{i,0utgroupInteraction} > \mu_{i,IngroupInteraction}  \\
-Attitude = OutgroupInteraction \times NonOutgroupInteraction
-\end{equation}
-
-<div class="alert alert-info alert-dismissible fade in" role="alert">
-  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
-  <i class="fas fa-exclamation-triangle"></i> <b>Note: </b><br/>
-  mean difference alone probably even more stupid than only ignoring nested data, because we drop lots of data unnecessarily.  
-  And only outgroup interaction Yes / No also weird because interaction group includes people who had only an outgroup interaction and those who also had an interaction with a non-outgroup person, and the no outgroup interaction group includes those who had no interaction at all and those who had an interaction with a non-outgroup person (but no outgroup interaction).
-</div>
-
-#### Regression with interaction term
-
-Across participants: impact of different interaction types [probably meaningless because ignores response sets between participants]
-
-```{r studentInteractionTypePlt, fig.height=12}
-# between participants interaction type
-studentContactType <- studentInteractionType %>%
-  group_by(
-    OutgroupInteraction,
-    NonOutgroupInteraction
-  ) %>%
-  summarise(
-    n = n(),
-    AttitudeM = mean(AttitudesDutch, na.rm = TRUE),
-    AttitudeSD = sd(AttitudesDutch, na.rm = TRUE),
-    AttitudeSE = AttitudeSD / sqrt(n),
-    AttitudeLwr = AttitudeM - 1.96 * AttitudeSE,
-    AttitudeUpr = AttitudeM + 1.96 * AttitudeSE
-  ) %>%
-  ungroup()
-
-# plot bar chart
-ggplot(
-  studentContactType,
-  aes(
-    y = AttitudeM,
-    x = OutgroupInteraction,
-    fill = NonOutgroupInteraction
-  )
-) +
-  geom_bar(
-    stat = "identity",
-    color = "black",
-    position = position_dodge()
-  ) +
-  geom_errorbar(aes(ymin = AttitudeM, ymax = AttitudeUpr),
-    width = .2,
-    position = position_dodge(.9)
-  ) +
-  labs(
-    fill = "Non-Outgroup Interaction",
-    x = "Outgroup Interaction",
-    y = "Outgroup Attitude",
-    title = "Outgroup Attitudes by Interaction Type [95% CI]"
-  ) +
-  scale_fill_grey(
-    start = 0.2,
-    end = 0.8
-  ) +
-  scale_y_continuous(
-    limits = c(0, 100),
-    breaks = c(0, 15, 30, 40, 50, 60, 70, 85, 100),
-    labels = c(
-      "Very cold or unfavorable feelings 0°",
-      "Quite cold and unfavorable feelings 15°",
-      "Fairly cold and unfavorable feelings 30°",
-      "A bit cold and unfavorable feelings 40°",
-      "No feeling at all 50°",
-      "A bit warm and favorable feelings 60°",
-      "Fairly warm and favorable feelings 70° ",
-      "Quite warm and favorable feelings 85° ",
-      "Very warm and favorable feelings 100° "
-    )
-  ) +
-  theme_Publication()
-```
-
-```{r studentModelOlsInteractionType}
-# create list to store student models
-mdlStudent <- list()
-
-# regression
-mdlStudent$lmAttInt <-
-  lm(AttitudesDutch ~ OutgroupInteraction * NonOutgroupInteraction,
-    data = studentInteractionType
-  )
-# summary(lmstudentAttInteraction)
-
-summ(
-  mdlStudent$lmAttInt,
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-```
-
-TL;DR: While controlling for interactions with non-Dutch people, outgroup attitudes were significantly higher when participants had an interaction with a Dutch person.
-The effect is relatively small (`r format(round(mdlStudent$lmAttInt$coefficients["OutgroupInteractionYes"], 2), nsmall=2)` points on a 0--100 scale).
-More importantly, however, this analysis lumps all ESM beeps from every participants together and ignores that the data is nested within participants.
-
-#### ML Regression with interaction term
-
-##### Unconditional model
-
-make a model with only the data but a random intercept (unconditional model)
-
-\begin{equation}
-(\#eq:studentEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentModelMLAttNull}
-# Create and save Model
-mdlStudent$lmerAttNull <-
-  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
-    data = dtStudents$full
-  ) # use optim if it does not converge
-
-mdlStudent$lmeAttNull <-
-  lme(
-    AttitudesDutch ~ 1,
-    random = ~ 1 | PID,
-    data = dtStudents$full,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(mdlStudent$lmerAttNull) #or with the lme function
-summ(mdlStudent$lmerAttNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
-# Save variances
-mdlStudent$varAttNull <- 
-  VarCorr(mdlStudent$lmeAttNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlStudent$tauAttNull <- 
-  as.numeric(mdlStudent$varAttNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlStudent$sigmaAttNull <- 
-  as.numeric(mdlStudent$varAttNull[2])
-# The ICC estimate (between/between+within) is:
-mdlStudent$IccAttNull <-
-  (as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))
-mdlStudent$IccPercAttNull <-
-  ((as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))) * 100
-```
-
-ICC $\tau_{00}^2 / (\tau_{00}^2 + \sigma^2)$: The ratio of the between-cluster variance to the total variance is called the Intraclass Correlation.
-It tells you the proportion of the total variance in Y that is accounted for by the clustering.
-(In this case the clustering means clustering observations per participant)
-
-compare the random intercept model to a model without a random intercept (i.e., without levels at all)
-
-```{r studentModelInterceptNull}
-# Create and save Model
-mdlStudent$glsAttNull  <-
-  gls(AttitudesDutch ~ 1,
-      data = dtStudents$full,
-      control = list(opt = "nlmimb"))
-
-# calculate Deviances manually:
-mdlStudent$DevianceGlsNull <- logLik(mdlStudent$glsAttNull) * -2
-mdlStudent$DevianceMlNull <- logLik(mdlStudent$lmeAttNull) * -2
-
-# Compare the two null models:
-anova(mdlStudent$glsAttNull,
-      mdlStudent$lmeAttNull) %>% 
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-```
-
-We find that an estimated `r format(round(mdlStudent$IccPercAttNull, 2), nsmall=2)`% of the variation in Feeling Thermometer scores is explained by between participant differences (clustering by PID).
-This is to say that `r format(round(mdlStudent$IccPercAttNull, 2), nsmall=2)`% of the variance in any individual report of Attitudes towards the Dutch can be explained by the properties of the individual who provided the rating.
-And we find that including 'participant' as a predictor adds significantly to the model.
-
-##### random intercept
-
-\begin{equation}
-(\#eq:StudentInteractionTypeModel)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentModelInterceptAttType}
-# Create and save Model
-mdlStudent$lmeInterceptAttType <-
-  lme(
-    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
-    random =  ~ 1 | PID,
-    data = studentInteractionType
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  lmer(
-    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
-    data = studentInteractionType
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(mdlStudent$lmeAttNull, 
-      mdlStudent$lmeInterceptAttType) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudent$varInterceptAttType <- 
-  lme4::VarCorr(mdlStudent$lmeInterceptAttType)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudent$varBtwInterceptAttType <-
-  1 - (as.numeric(mdlStudent$varInterceptAttType[1]) / as.numeric(mdlStudent$varAttNull[1]))
-mdlStudent$varBtwPercInterceptAttType <-
-  (1 - (as.numeric(mdlStudent$varInterceptAttType[1]) / as.numeric(mdlStudent$varAttNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudent$varWithinInterceptAttType <-
-  1 - (as.numeric(mdlStudent$varInterceptAttType[2]) / as.numeric(mdlStudent$varAttNull[2]))
-mdlStudent$varWithinPercInterceptAttType <-
-  (1 - (as.numeric(mdlStudent$varInterceptAttType[2]) / as.numeric(mdlStudent$varAttNull[2]))) * 100
-```
-
-tl;dr: Interaction with Dutch is great predictor, interactions with non-Dutch is not.
-
-##### random slope
-
-\begin{equation}
-(\#eq:RandSlopesEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentModelSlopesInteractionType}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudent$lmeSlopesAttType <- lme(
-  AttitudesDutch ~
-    OutgroupInteraction + NonOutgroupInteraction,
-  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  data = studentInteractionType
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudent$lmerSlopesAttType <- lmer(
-    AttitudesDutch ~
-      OutgroupInteraction + NonOutgroupInteraction +
-      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
-    data = studentInteractionType
-  ), 
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlStudent$lmeInterceptAttType, 
-      mdlStudent$lmeSlopesAttType) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudent$varSlopesAttType <- 
-  lme4::VarCorr(mdlStudent$lmeSlopesAttType)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudent$varBtwSlopesAttType <- 
-  1 - (as.numeric(mdlStudent$varSlopesAttType[1]) / as.numeric(mdlStudent$varInterceptAttType[1]))
-mdlStudent$varBtwPercSlopesAttType <- 
-  (1 - (as.numeric(mdlStudent$varSlopesAttType[1]) / as.numeric(mdlStudent$varInterceptAttType[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudent$varWithinSlopesAttType <- 
-  1 - (as.numeric(mdlStudent$varSlopesAttType[2]) / as.numeric(mdlStudent$varInterceptAttType[2]))
-mdlStudent$varWithinPercSlopesAttType <- 
-  (1 - (as.numeric(mdlStudent$varSlopesAttType[2]) / as.numeric(mdlStudent$varInterceptAttType[2]))) * 100
-
-# Assumption Checks:
-mdlStudent$diagSlopesAttType <-
-  sjPlot::plot_model(mdlStudent$lmerSlopesAttType, type = "diag")
-grid.arrange(
-  mdlStudent$diagSlopesAttType[[1]],
-  mdlStudent$diagSlopesAttType[[2]]$`PID`,
-  mdlStudent$diagSlopesAttType[[3]],
-  mdlStudent$diagSlopesAttType[[4]]
-)
-
-# Plot prediction model
-mdlStudent$predSlopesAttType <- 
-  studentInteractionType %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudent$lmeSlopesAttType,
-                           studentInteractionType,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudent$predPltSlopesAttType <-
-    ggplot(data = mdlStudent$predSlopesAttType %>% filter(PID %in% studentPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Student_PredictionPlot_SlopesAttType.png",
-  mdlStudent$predPltSlopesAttType,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-TL;DR: Random slopes don't add much for this super simple model.
-
-### Interaction Frequency and Interaction Quality
-
-\begin{equation}
-(\#eq:FreqQual)
-Attitude = ContactFreq \times AverageContactQual
-\end{equation}
-
-```{r studentFreqQualCor}
-# correlation panel
-pairs.panels.new(
-  studentContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
-    "Sum:\nNumber of Outgroup Contacts (NL)",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-
-# correlation panel with interaction sums winsorized
-pairs.panels.new(
-  studentContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
-    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-```
-
-TL;DR: There is no meaningfull correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
-However, the frequency of intergroup interactions had a significant correlation with both the average interaction quality and average outgroup attitudes.
-
-```{r studentModelOlsAttFreqQual}
-# regression
-mdlStudent$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL * AvQuality, data = studentContactFreq)
-# summary(mdlStudent$lmAttFreqQualX)
-
-summ(
-  mdlStudent$lmAttFreqQualX,
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-interactions::interact_plot(
-  mdlStudent$lmAttFreqQualX,
-  pred = SumContactNL,
-  modx = AvQuality,
-  interval = TRUE,
-  partial.residuals = TRUE
-)
-
-interactions::johnson_neyman(mdlStudent$lmAttFreqQualX,
-                             pred = SumContactNL,
-                             modx = AvQuality,
-                             alpha = .05)
-```
-
-TL;DR: We find that, although the effect goes into the right direction (i.e., higher average interaction quality increases the positive effect of intergroup contact), there was no effect of average interaction quality (neither directly nor in a moderating role of interaction frequency).
-However, this regression ignores within person relationships of these variables (i.e., summarizes all within person variances into average scores).
-
-## Need Fulfillment
-
-### Need fulfillment and Attitudes
-
-##### Unconditional model
-
-make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
-
-```{r studentPrepOutgroupSubsample}
-# see how large our outgroup interaction subset actually is
-tbl_cross(
-  studentInteractionType,
-  row = OutgroupInteraction,
-  col = NonOutgroupInteraction,
-  percent = "row"
-)
-
-# create outgroup interaction subset
-studentOutgroupInteraction <- studentInteractionType %>%
-  filter(OutgroupInteraction == "Yes")
-
-# create empty list to organize models
-mdlStudentOut <- 
-  list(
-    Att = list(),
-    Qlt = list()
-  )
-```
-
-\begin{equation}
-(\#eq:studentOutEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentOutModelMLAttNull}
-# Create and save Model
-mdlStudentOut$Att$lmerNull <-
-  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), 
-             data = studentOutgroupInteraction) # use optim if it does not converge
-mdlStudentOut$Att$lmeNull <-
-  lme(
-    AttitudesDutch ~ 1,
-    random = ~ 1 | PID,
-    data = studentOutgroupInteraction,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.ML.r) #or with the lme function
-summ(mdlStudentOut$Att$lmerNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
-# Save variances
-mdlStudentOut$Att$varNull <- 
-  VarCorr(mdlStudentOut$Att$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlStudentOut$Att$tauNull <- 
-  as.numeric(mdlStudentOut$Att$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlStudentOut$Att$sigmaNull <- 
-  as.numeric(mdlStudentOut$Att$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlStudentOut$Att$IccNull <-
-  (as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))
-mdlStudentOut$Att$IccPercNull <-
-  ((as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))) * 100
-```
-
-#### random intercept
-
-\begin{equation}
-(\#eq:AttitudeNeedEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentOutModelInterceptAttCore}
-# Create and save Model
-mdlStudentOut$Att$lmeInterceptCore <-
-  lme(
-    AttitudesDutch ~ KeyNeedFullfillment,
-    random = ~ 1 | PID,
-    data = studentOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  lmer(AttitudesDutch ~ KeyNeedFullfillment + (1 | PID), 
-       data = studentOutgroupInteraction),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(mdlStudentOut$Att$lmeNull, 
-      mdlStudentOut$Att$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varInterceptCore <-
-  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Att$varBtwInterceptCore <- 
-  1 - (as.numeric(mdlStudentOut$Att$varInterceptCore[1]) / as.numeric(mdlStudentOut$Att$varNull[1]))
-mdlStudentOut$Att$varBtwPercInterceptCore <- 
-  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCore[1]) / as.numeric(mdlStudentOut$Att$varNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Att$varWithinInterceptCore <-
-  1 - (as.numeric(mdlStudentOut$Att$varInterceptCore[2]) / as.numeric(mdlStudentOut$Att$varNull[2]))
-mdlStudentOut$Att$varWithinPercInterceptCore <-
-  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCore[2]) / as.numeric(mdlStudentOut$Att$varNull[2]))) * 100
-```
-
-TL;DR: Situational core need relates significantly to outgroup attitudes.
-The core need has little explained variance between participants (compared to the null model: Variance Explained = 1 – (Var with Predictor/Var without Predictor); `r format(round(mdlStudentOut$Att$varBtwPercInterceptCore, 2),nsmall=2)`%).
-The variance explained within participants is small to medium (`r format(round(mdlStudentOut$Att$varWithinPercInterceptCore, 2),nsmall=2)`%)
-
-#### random slope
-
-\begin{equation}
-(\#eq:AttitudeNeedRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentOutModelSlopesAttCore}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudentOut$Att$lmeSlopesCore <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFullfillment,
-    random = ~ 1 + KeyNeedFullfillment | PID,
-    control = lmeControl(opt = "optim"),
-    data = studentOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Att$lmerSlopesCore <- lmer(
-    AttitudesDutch ~
-      KeyNeedFullfillment +
-      (1 + KeyNeedFullfillment | PID),
-    data = studentOutgroupInteraction
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlStudentOut$Att$lmeInterceptCore, 
-      mdlStudentOut$Att$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varSlopesCore <- 
-  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Att$varBtwSlopesCore <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))
-mdlStudentOut$Att$varBtwPercSlopesCore <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Att$varWithinSlopesCore <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))
-mdlStudentOut$Att$varWithinPercSlopesCore <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))) * 100
-
-# Assumption Checks:
-mdlStudentOut$Att$diagSlopesCore <- 
-  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCore, type = "diag")
-grid.arrange(
-  mdlStudentOut$Att$diagSlopesCore[[1]],
-  mdlStudentOut$Att$diagSlopesCore[[2]]$`PID`,
-  mdlStudentOut$Att$diagSlopesCore[[3]],
-  mdlStudentOut$Att$diagSlopesCore[[4]]
-)
-
-# Plot prediction model
-mdlStudentOut$Att$predSlopesCore <- 
-  studentOutgroupInteraction %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCore,
-                           studentOutgroupInteraction,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudentOut$Att$predPltSlopesCore <-
-    ggplot(data = mdlStudentOut$Att$predSlopesCore %>% filter(PID %in% studentOutPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCore.png",
-  mdlStudentOut$Att$predPltSlopesCore,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-TL;DR: The random slope adds significantly to the prediction model.
-
-<div class="alert alert-warning alert-dismissible fade in" role="alert">
-  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
-  <i class="fas fa-exclamation-triangle"></i> <b>Check needed: </b><br/>
-  Something is with the variances explained (between = `r format(round(mdlStudentOut$Att$varBtwPercSlopesCore, 2),nsmall=2)`%, within = `r format(round(mdlStudentOut$Att$varWithinPercSlopesCore, 2),nsmall=2)`%).
-This is when comparing the random intercepts to the random slopes model.
-</div>
-
-### Need fulfillment and Interaction Quality
-
-##### Unconditional model
-
-make a model with only the data but a random intercept (unconditional model) for the outgroup interaction subset.
-
-\begin{equation}
-(\#eq:studentOutQualEmptyModel)
-InteractionQuality_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentOutModelMLQltNull}
-# Create and save Model
-mdlStudentOut$Qlt$lmerNull <-
-  lme4::lmer(quality_overall ~ 1 + (1 | PID), 
-             data = studentOutgroupInteraction) # use optim if it does not converge
-mdlStudentOut$Qlt$lmeNull <-
-  lme(
-    quality_overall ~ 1,
-    random = ~ 1 | PID,
-    data = studentOutgroupInteraction,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.Qual.ML.r) #or with the lme function
-summ(mdlStudentOut$Qlt$lmerNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
-# Save variances
-mdlStudentOut$Qlt$varNull <- 
-  VarCorr(mdlStudentOut$Qlt$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlStudentOut$Qlt$tauNull <- 
-  as.numeric(mdlStudentOut$Qlt$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlStudentOut$Qlt$sigmaNull <- 
-  as.numeric(mdlStudentOut$Qlt$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlStudentOut$Qlt$IccNull <-
-  (as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))
-mdlStudentOut$Qlt$IccPercNull <-
-  ((as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))) * 100
-```
-
-#### random intercept
-
-\begin{equation}
-(\#eq:QualityNeedEq)
-InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentOutModelInterceptQltCore}
-# Create and save Model
-mdlStudentOut$Qlt$lmeInterceptCore <-
-  lme(
-    quality_overall ~ KeyNeedFullfillment,
-    random = ~ 1 | PID,
-    data = studentOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudentOut$Qlt$lmerInterceptCore <- lmer(quality_overall ~ KeyNeedFullfillment + (1 | PID), 
-       data = studentOutgroupInteraction),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(quality_overall ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(mdlStudentOut$Qlt$lmeNull, 
-      mdlStudentOut$Qlt$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Qlt$varInterceptCore <-
-  lme4::VarCorr(mdlStudentOut$Qlt$lmeInterceptCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Qlt$varBtwInterceptCore <- 
-  1 - (as.numeric(mdlStudentOut$Qlt$varInterceptCore[1]) / as.numeric(mdlStudentOut$Qlt$varNull[1]))
-mdlStudentOut$Qlt$varBtwPercInterceptCore <- 
-  (1 - (as.numeric(mdlStudentOut$Qlt$varInterceptCore[1]) / as.numeric(mdlStudentOut$Qlt$varNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Qlt$varWithinInterceptCore <-
-  1 - (as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]) / as.numeric(mdlStudentOut$Qlt$varNull[2]))
-mdlStudentOut$Qlt$varWithinPercInterceptCore <-
-  (1 - (as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]) / as.numeric(mdlStudentOut$Qlt$varNull[2]))) * 100
-```
-
-TL;DR: Situational core need relates significantly to interaction quality.
-The core need explained substantial variance between participants (`r format(round(mdlStudentOut$Qlt$varBtwPercInterceptCore, 2),nsmall=2)`%).
-The variance explained within participants is also medium (`r format(round(mdlStudentOut$Qlt$varWithinPercInterceptCore, 2),nsmall=2)`%)
-
-#### random slope
-
-\begin{equation}
-(\#eq:QualityNeedRandEq)
-InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentOutModelSlopesQltCore}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudentOut$Qlt$lmeSlopesCore <-
-  lme(
-    quality_overall ~
-      KeyNeedFullfillment,
-    random = ~ 1 + KeyNeedFullfillment | PID,
-    control = lmeControl(opt = "optim"),
-    data = studentOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Qlt$lmerSlopesCore <-
-    lmer(
-      quality_overall ~
-        KeyNeedFullfillment +
-        (1 + KeyNeedFullfillment | PID),
-      data = studentOutgroupInteraction
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(mdlStudentOut$Qlt$lmerSlopesCore,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlStudentOut$Qlt$lmeInterceptCore, 
-      mdlStudentOut$Qlt$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Qlt$varSlopesCore <- 
-  lme4::VarCorr(mdlStudentOut$Qlt$lmeSlopesCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Qlt$varBtwSlopesCore <-
-  1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[1]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[1]))
-mdlStudentOut$Qlt$varBtwPercSlopesCore <-
-  (1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[1]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Qlt$varWithinSlopesCore <-
-  1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[2]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]))
-mdlStudentOut$Qlt$varWithinPercSlopesCore <-
-  (1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[2]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]))) * 100
-
-# Assumption Checks:
-mdlStudentOut$Qlt$diagSlopesCore <-
-  sjPlot::plot_model(mdlStudentOut$Qlt$lmerSlopesCore, type = "diag")
-grid.arrange(
-  mdlStudentOut$Qlt$diagSlopesCore[[1]],
-  mdlStudentOut$Qlt$diagSlopesCore[[2]]$`PID`,
-  mdlStudentOut$Qlt$diagSlopesCore[[3]],
-  mdlStudentOut$Qlt$diagSlopesCore[[4]]
-)
-
-# Plot prediction model
-mdlStudentOut$Qlt$predSlopesCore <- 
-  studentOutgroupInteraction %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudentOut$Qlt$lmeSlopesCore,
-                           studentOutgroupInteraction,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudentOut$Qlt$predPltSlopesCore <-
-    ggplot(data = mdlStudentOut$Qlt$predSlopesCore %>% filter(PID %in% studentOutPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/StudentOut_PredictionPlot_SlopesCore.png",
-  mdlStudentOut$Qlt$predPltSlopesCore,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-TL;DR: random slopes does add significantly.
-
-### Need fulfillment, Interaction Quality, and Attitudes
-
-#### random intercept
-
-\begin{equation}
-(\#eq:AttitudeQualityNeedEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentOutModelInterceptAttCoreQlt}
-# Create and save Model
-mdlStudentOut$Att$lmeInterceptCoreQlt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFullfillment + quality_overall,
-    random = ~ 1 | PID,
-    data = studentOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  lmer(
-    AttitudesDutch ~ KeyNeedFullfillment + quality_overall + (1 | PID),
-    data = studentOutgroupInteraction
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(
-  mdlStudentOut$Att$lmeNull, 
-  mdlStudentOut$Att$lmeInterceptCoreQlt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varInterceptCoreQlt <-
-  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreQlt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Att$varBtwInterceptCoreQlt <- 
-  1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[1]) / as.numeric(mdlStudentOut$Att$varNull[1]))
-mdlStudentOut$Att$varBtwPercInterceptCoreQlt <- 
-  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[1]) / as.numeric(mdlStudentOut$Att$varNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Att$varWithinInterceptCoreQlt <-
-  1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[2]) / as.numeric(mdlStudentOut$Att$varNull[2]))
-mdlStudentOut$Att$varWithinPercInterceptCoreQlt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[2]) / as.numeric(mdlStudentOut$Att$varNull[2]))) * 100
-```
-
-TL;DR: Variance explained in outgroup attitudes is of medium effect size (between: `r format(round(mdlStudentOut$Att$varBtwPercInterceptCoreQlt,2),nsmall=2)`%, within: `r format(round(mdlStudentOut$Att$varWithinPercInterceptCoreQlt,2),nsmall=2)`%)
-
-#### random slope
-
-\begin{equation}
-(\#eq:AttitudeQualityNeedRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentOutModelSlopesAttCoreQlt}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudentOut$Att$lmeSlopesCoreQlt <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFullfillment + quality_overall,
-    random = ~ 1 + KeyNeedFullfillment + quality_overall | PID,
-    control = lmeControl(opt = "optim"),
-    data = studentOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Att$lmerSlopesCoreQlt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFullfillment + quality_overall +
-      (1 + KeyNeedFullfillment + quality_overall | PID),
-    data = studentOutgroupInteraction
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(
-  mdlStudentOut$Att$lmeNull,
-  mdlStudentOut$Att$lmeInterceptCoreQlt,
-  mdlStudentOut$Att$lmeSlopesCoreQlt
-) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varSlopesCoreQlt <- 
-  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreQlt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Att$varBtwSlopesCoreQlt <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[1]))
-mdlStudentOut$Att$varBtwPercSlopesCoreQlt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Att$varWithinSlopesCoreQlt <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[2]))
-mdlStudentOut$Att$varWithinPercSlopesCoreQlt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[2]))) * 100
-
-# Assumption Checks:
-mdlStudentOut$Att$diagSlopesCoreQlt <- 
-  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreQlt, type = "diag")
-grid.arrange(
-  mdlStudentOut$Att$diagSlopesCoreQlt[[1]],
-  mdlStudentOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
-  mdlStudentOut$Att$diagSlopesCoreQlt[[3]],
-  mdlStudentOut$Att$diagSlopesCoreQlt[[4]]
-)
-
-# Plot prediction model
-mdlStudentOut$Att$predSlopesCoreQlt <- 
-  studentOutgroupInteraction %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreQlt,
-                           studentOutgroupInteraction,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudentOut$Att$predPltSlopesCoreQlt <-
-    ggplot(data = mdlStudentOut$Att$predSlopesCoreQlt %>% filter(PID %in% studentOutPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreQlt.png",
-  mdlStudentOut$Att$predPltSlopesCoreQlt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-#### Compare models
-
-Interpretation of Mediation like results.
-
-### Check for robustness
-
-#### Interaction Type
-
-##### random intercept
-
-\begin{equation}
-(\#eq:AttitudeNeedInteractionEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentModelInterceptAttCoreInt}
-# Create and save Model
-mdlStudent$lmeInterceptAttCoreInt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFullfillment * OutgroupInteraction,
-    random =  ~ 1 | PID,
-    data = studentInteractionType
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudent$lmerInterceptAttCoreInt <- lmer(
-    AttitudesDutch ~ KeyNeedFullfillment * OutgroupInteraction + (1 | PID),
-    data = studentInteractionType
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(mdlStudent$lmeAttNull, 
-      mdlStudent$lmeInterceptAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudent$varInterceptAttCoreInt <- 
-  lme4::VarCorr(mdlStudent$lmeInterceptAttCoreInt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudent$varBtwInterceptAttCoreInt <-
-  1 - (as.numeric(mdlStudent$varInterceptAttCoreInt[1]) / as.numeric(mdlStudent$varAttNull[1]))
-mdlStudent$varBtwPercInterceptAttCoreInt <-
-  (1 - (as.numeric(mdlStudent$varInterceptAttCoreInt[1]) / as.numeric(mdlStudent$varAttNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudent$varWithinInterceptAttCoreInt <-
-  1 - (as.numeric(mdlStudent$varInterceptAttCoreInt[2]) / as.numeric(mdlStudent$varAttNull[2]))
-mdlStudent$varWithinPercInterceptAttCoreInt <-
-  (1 - (as.numeric(mdlStudent$varInterceptAttCoreInt[2]) / as.numeric(mdlStudent$varAttNull[2]))) * 100
-```
-
-##### random slope
-
-\begin{equation}
-(\#eq:AttitudeNeedInteractionRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti}  + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentModelSlopesAttCoreIntX}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudent$lmeSlopesAttCoreInt <- lme(
-  AttitudesDutch ~
-    KeyNeedFullfillment * OutgroupInteraction,
-  random = ~ 1 + KeyNeedFullfillment + OutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  data = studentInteractionType
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudent$lmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFullfillment * OutgroupInteraction +
-      (1 + KeyNeedFullfillment + OutgroupInteraction | PID),
-    data = studentInteractionType
-  ), 
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlStudent$lmeAttNull, 
-      mdlStudent$lmeInterceptAttCoreInt,
-      mdlStudent$lmeSlopesAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudent$varSlopesAttCoreInt <- 
-  lme4::VarCorr(mdlStudent$lmeSlopesAttCoreInt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudent$varBtwSlopesAttCoreInt <- 
-  1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[1]) / as.numeric(mdlStudent$varInterceptAttCoreInt[1]))
-mdlStudent$varBtwPercSlopesAttCoreInt <- 
-  (1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[1]) / as.numeric(mdlStudent$varInterceptAttCoreInt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudent$varWithinSlopesAttCoreInt <- 
-  1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[2]) / as.numeric(mdlStudent$varInterceptAttCoreInt[2]))
-mdlStudent$varWithinPercSlopesAttCoreInt <- 
-  (1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[2]) / as.numeric(mdlStudent$varInterceptAttCoreInt[2]))) * 100
-
-# Assumption Checks:
-mdlStudent$diagSlopesAttCoreInt <-
-  sjPlot::plot_model(mdlStudent$lmerSlopesAttCoreInt, type = "diag")
-grid.arrange(
-  mdlStudent$diagSlopesAttCoreInt[[1]],
-  mdlStudent$diagSlopesAttCoreInt[[2]]$`PID`,
-  mdlStudent$diagSlopesAttCoreInt[[3]],
-  mdlStudent$diagSlopesAttCoreInt[[4]]
-)
-
-# Plot prediction model
-mdlStudent$predSlopesAttCoreInt <- 
-  studentInteractionType %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudent$lmeSlopesAttCoreInt,
-                           studentInteractionType,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudent$predPltSlopesAttCoreInt <-
-    ggplot(data = mdlStudent$predSlopesAttCoreInt %>% filter(PID %in% studentPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Student_PredictionPlot_SlopesAttCoreInt.png",
-  mdlStudent$predPltSlopesAttCoreInt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-##### Plot Interaction
-
-```{r studentModelInterceptAttCoreIntPlt}
-# visualize interaction
-## Without ML structure
-ggplot(data = studentInteractionType,
-       aes(x = KeyNeedFullfillment,
-           y = AttitudesDutch,
-           fill = OutgroupInteraction)) +
-  #geom_point()+
-  geom_smooth(method = 'lm',
-              aes(linetype = OutgroupInteraction),
-              color = "black") +
-  #facet_wrap(~PID, ncol = 6)+
-  scale_linetype_manual(values = c("dashed", "solid")) +
-  scale_fill_manual(values = c("darkgrey", "black")) +
-  #scale_colour_manual(values=c("grey20", "black"), name="Intergroup Contact")+
-  scale_y_continuous(
-    limits = c(50, 100),
-    breaks = seq(50, 100, by = 10),
-    position = "left"
-  ) +
-  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
-  labs(
-    title = "Without ML stucture",
-    x = "Fulfillment Core Need",
-    y = "Outgroup Attitudes",
-    fill = "Intergroup Contact",
-    linetype = "Intergroup Contact"
-  ) +
-  theme_Publication() +
-  theme(legend.position = "bottom",
-        legend.key.size = unit(1, "cm"))
-## With ML structure
-# create parameters for prediction
-datNew = data.frame(
-  OutgroupInteraction = factor(rep(c("No", "Yes"), each = 21)),
-  KeyNeedFullfillment = rep(seq(0, 100, 5), 2),
-  PID = 0
-)
-
-# Predict values, clean up and calculate SE
-PI <-
-  merTools::predictInterval(
-    merMod = mdlStudent$lmerSlopesAttCoreInt,
-    newdata = datNew,
-    level = 0.95,
-    stat = "mean",
-    type = "linear.prediction",
-    include.resid.var = F,
-    fix.intercept.variance = F
-  )
-mdlStudent$predInterceptAttCoreIntX <- 
-  cbind(datNew, PI)
-mdlStudent$predInterceptAttCoreIntX$se <-
-  (mdlStudent$predInterceptAttCoreIntX$upr - mdlStudent$predInterceptAttCoreIntX$fit) / 1.96
-rm(datNew, PI)
-
-# Plot predicted values with SE
-ggplot(
-  mdlStudent$predInterceptAttCoreIntX,
-  aes(x = KeyNeedFullfillment,
-      y = fit,
-      fill = OutgroupInteraction)
-)+
-  #geom_point() +
-  geom_line(aes(linetype = as.factor(OutgroupInteraction)), size = 1) +
-  #facet_wrap(~PID, ncol = 6)+
-  geom_ribbon(data = mdlStudent$predInterceptAttCoreIntX,
-              aes(ymin = fit - se, ymax = fit + se),
-              alpha = 0.3) +
-  scale_x_continuous(breaks = seq(0, 100, 10)) +
-  scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
-  scale_linetype_manual(values = c("dashed", "solid")) +
-  scale_fill_manual(values = c("darkgrey", "black")) +
-  labs(
-    x = "Fulfillment Core Need",
-    y = "Outgroup Attitude (NL)",
-    fill = "Intergroup Contact",
-    linetype = "Intergroup Contact",
-    title = "Based on Model Predictions"
-  ) +
-  theme_Publication()
-
-# #### Bayesian estimation !! ONLY RUN ON FINAL RENDER !! Takes forever ####
-# options(mc.cores = parallel::detectCores())  # Run many chains simultaneously
-# brmfit <- brm(
-#   AttitudesDutch ~ KeyNeedFullfillment * OutgroupInteraction + 
-#     (1 + KeyNeedFullfillment + OutgroupInteraction | PID),
-#   data = studentInteractionType,
-#   family = gaussian,
-#   iter = 1000,
-#   chains = 4
-# )
-# 
-# # create parameters for prediction:
-# datNew = data.frame(
-#   OutgroupInteraction = rep(c("No", "Yes"), each = 101),
-#   KeyNeedFullfillment = rep(seq(0, 100, 1), 2)
-# )
-# # Save predicted values and adjust names and labels
-# fitavg <-
-#   cbind(datNew,
-#         fitted(brmfit, newdata = datNew, re_formula = NA)[, -2])
-# names(fitavg)[names(fitavg) == "Estimate"] = "pred"
-# fitavg$se <- (fitavg$Q97.5 - fitavg$pred) / 1.96
-# 
-# # Plot Bayesian SE prediction interval
-# ggplot(fitavg,
-#        aes(x = KeyNeedFullfillment,
-#            y = pred,
-#            fill = OutgroupInteraction)) +
-#   scale_x_continuous(breaks = seq(0, 100, 10)) +
-#   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
-#   geom_line(aes(linetype = OutgroupInteraction), size = 1) +
-#   geom_ribbon(aes(ymin = pred - se, ymax = pred + se), alpha = 0.2) +
-#   scale_linetype_manual(values = c("dashed", "solid")) +
-#   scale_fill_manual(values = c("darkgrey", "black")) +
-#   labs(
-#     x = "Fulfillment Core Need",
-#     y = "Outgroup Attitude (NL)",
-#     fill = "Intergroup Contact",
-#     linetype = "Intergroup Contact",
-#     title = "Based on Bayesian Prediction Interval"
-#   ) +
-#   theme_Publication()
-# 
-# # plot all overlayed posteriors:
-# pst <- posterior_samples(brmfit, "b")
-# ggplot(studentInteractionType,
-#        aes(x = KeyNeedFullfillment, y = AttitudesDutch)) +
-#   geom_point(shape = 4, alpha = .1) +
-#   geom_tile() +
-#   geom_abline(
-#     data = pst,
-#     aes(intercept = b_Intercept, slope = b_KeyNeedFullfillment),
-#     alpha = .025,
-#     size = .4
-#   ) +
-#   labs(title = "slope Posteriors",
-#        x = "Fulfillment Core Need",
-#        y = "Outgroup Attitudes (NL)") +
-#   theme_Publication()
-# rm(datNew, brmfit, fitavg, pst)
-```
-
-#### Other psychological needs
-
-##### random intercept
-
-\begin{equation}
-(\#eq:AttitudeNeedSdtEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentOutModelInterceptAttCoreSdt}
-# Create and save Model
-mdlStudentOut$Att$lmeInterceptCoreSdt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction,
-    random = ~ 1 | PID,
-    data = studentOutgroupInteraction,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudentOut$Att$lmerInterceptCoreSdt <- lmer(
-    AttitudesDutch ~ KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction + (1 | PID),
-    data = studentOutgroupInteraction
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(
-  mdlStudentOut$Att$lmeInterceptCore, 
-  mdlStudentOut$Att$lmeInterceptCoreSdt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varInterceptCoreSdt <-
-  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreSdt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Att$varBtwInterceptCoreSdt <- 
-  1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))
-mdlStudentOut$Att$varBtwPercInterceptCoreSdt <- 
-  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Att$varWithinInterceptCoreSdt <-
-  1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))
-mdlStudentOut$Att$varWithinPercInterceptCoreSdt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))) * 100
-```
-
-##### random slope
-
-\begin{equation}
-(\#eq:AttitudeNeedSdtRandEq)
-Attitude_{ti} = \\gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
-\end{equation}
-
-```{r studentOutModelSlopesAttCoreSdt}
-# Check Correlations 
-studentOutgroupInteraction %>% 
-  select(AttitudesDutch, KeyNeedFullfillment, Competence, Autonomy, RelatednessInteraction) %>%
-  pairs.panels.new
-
-studentRed <- 
-  studentOutgroupInteraction %>% 
-  # select(PID, AttitudesDutch, KeyNeedFullfillment, Competence, Autonomy, RelatednessInteraction) %>%
-  group_by(PID) %>%
-  filter(
-    sd(AttitudesDutch) != 0,
-    sd(KeyNeedFullfillment) != 0,
-    sd(Competence) != 0,
-    sd(Autonomy) != 0,
-    sd(RelatednessInteraction) != 0
-  ) %>%
-  ungroup
-
-studentRedCor <- 
-  studentOutgroupInteraction %>%
-  group_by(PID) %>%
-  summarise(
-    rAttCore = cor(AttitudesDutch, KeyNeedFullfillment),
-    rAttComp = cor(AttitudesDutch, Competence),
-    rAttAut = cor(AttitudesDutch, Autonomy),
-    rAttRel = cor(AttitudesDutch, RelatednessInteraction),
-    rCoreComp = cor(KeyNeedFullfillment, Competence),
-    rCoreAut = cor(KeyNeedFullfillment, Autonomy),
-    rCoreRel = cor(KeyNeedFullfillment, RelatednessInteraction),
-    rCompAut = cor(Competence, Autonomy),
-    rCompRel = cor(Competence, RelatednessInteraction),
-    rAutRel = cor(Autonomy, RelatednessInteraction)
-  ) %>%
-  filter_at(vars(-PID), all_vars(abs(.) != "1"))
-  # mutate(corMean = rowMeans(abs(.[2:ncol(.)]))) %>%
-  # filter(corMean != "1")
-
-studentRed2 <- 
-  studentOutgroupInteraction %>%
-  filter(PID %in% studentRedCor$PID)
-
-# Create and save Model (optimizer needed to reach convergence) 
-# Problem because some PPTs have 100 on all measures (SD = 0) AND/OR
-# For some all cor = 1 or -1
-# Removing these PPTs or their measurement beeps doesn't help
-# However, removing eithe the Core Need, Autonomy, or Relatedness from the random slopes lets the model converge
-# --> looks like there is an overfitting issue? But why does it work in lmer?
-# FOR NOW: Autonomy removed from random slopes because weakest predictor
-mdlStudentOut$Att$lmeSlopesCoreSdt <-
-  nlme::lme(
-    AttitudesDutch ~
-      KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction,
-    random = ~ 1 + KeyNeedFullfillment + Competence + RelatednessInteraction | PID, # Autonomy + 
-    #method = "ML",
-    #control = lmeControl(opt = "optim", optimMethod = "L-BFGS-B"),
-    control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
-    data = studentOutgroupInteraction
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Att$lmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction +
-      (1 + KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction | PID),
-    data = studentOutgroupInteraction
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlStudentOut$Att$lmeInterceptCoreSdt, 
-      mdlStudentOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "html",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varSlopesCoreSdt <- 
-  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreSdt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Att$varBtwSlopesCoreSdt <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]))
-mdlStudentOut$Att$varBtwPercSlopesCoreSdt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Att$varWithinSlopesCoreSdt <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]))
-mdlStudentOut$Att$varWithinPercSlopesCoreSdt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]))) * 100
-
-# Assumption Checks:
-mdlStudentOut$Att$diagSlopesCoreSdt <- 
-  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreSdt, type = "diag")
-grid.arrange(
-  mdlStudentOut$Att$diagSlopesCoreSdt[[1]],
-  mdlStudentOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
-  mdlStudentOut$Att$diagSlopesCoreSdt[[3]],
-  mdlStudentOut$Att$diagSlopesCoreSdt[[4]]
-)
-
-# Plot prediction model
-mdlStudentOut$Att$predSlopesCoreSdt <- 
-  studentOutgroupInteraction %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreSdt,
-                           studentOutgroupInteraction,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudentOut$Att$predPltSlopesCoreSdt <-
-    ggplot(data = mdlStudentOut$Att$predSlopesCoreSdt %>% filter(PID %in% studentOutPltIDs),
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreStd.png",
-  mdlStudentOut$Att$predPltSlopesCoreSdt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-# **Young Medical Professional Sample**
-
-## Contact Hypothesis
-
-## Allport's Conditions
-
-## Need Fulfillment
-
-# **Software Information**  
-The full session information with all relevant system information and all loaded and installed packages is available in the collapsible section below.
-
-<details>
-  <summary>System Info</summary>
-
-  \renewcommand{\arraystretch}{0.8} <!-- decrease line spacing for the table -->
-```{r Reproducibility-SessionInfo-R-environment, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center", out.width='100%', results='asis'}
-df_session_platform <- devtools::session_info()$platform %>%
-  unlist(.) %>%
-  as.data.frame(.) %>%
-  rownames_to_column(.)
-
-colnames(df_session_platform) <- c("Setting", "Value")
-
-kbl(
-  df_session_platform,
-  booktabs = T,
-  align = "l",
-  caption = "R environment session info for reproducibility of results" # complete caption for main document
-) %>%
-  kable_classic(
-    full_width = F,
-    lightable_options = "hover",
-    html_font = "Cambria"
-  )
-```
-  \renewcommand{\arraystretch}{1} <!-- reset row height/line spacing -->
- </details>
- <br>
- <details>
-  <summary>Package Info</summary>
-
-\renewcommand{\arraystretch}{0.6} <!-- decrease line spacing for the table -->
-```{r Reproducibility-SessionInfo-R-packages, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center", out.width='100%', results='asis'}
-df_session_packages <- devtools::session_info()$packages %>%
-  as.data.frame(.) %>%
-  filter(attached == TRUE) %>%
-  dplyr::select(loadedversion, date, source) %>%
-  rownames_to_column()
-
-colnames(df_session_packages) <- c("Package", "Loaded version", "Date", "Source")
-
-kbl(
-  df_session_packages,
-  booktabs = T,
-  align = "l",
-  caption = "Package info for reproducibility of results" # complete caption for main document
-) %>%
-  kable_classic(
-    full_width = F,
-    lightable_options = "hover",
-    html_font = "Cambria"
-  )
-```
-\renewcommand{\arraystretch}{1} <!-- reset row height/line spacing -->
-</details>
-<br>
-<details>
-  <summary>Full Session Info (including loaded but unattached packages --- for troubleshooting only)</summary>
-    `r pander(sessionInfo(), compact = FALSE)`
-</details>
-
---------------------------------------------------------------------
-
-</br>
-
-# **References**
-
-<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
+\begin{figure}[h]
+\centering
+\caption{Literature Levels: (A) Bar graph of the experience aspect frequencies for theoretical, methodological, and broader empirical literature.
+(B) Bar graph of the number of experience aspects used for theoretical, methodological, and broader empirical literature.
+(C) Average number of additional aspects included when the aspect was considered for theoretical, methodological, and broader empirical literature [Mean ± 95\%CI].}
+\includegraphics[width=\textwidth]{Figures/LiteratureComparison-1}
+\caption*{Note that in (C) within each literature body the aspects are not mutually exclusive (and thus not independent) because scales can include multiple experience aspects.}
+\label{fig:LiteratureComparison}
+\end{figure}

### 2021-10-21 Supplemental-Material-B-Annotated-Analysis.Rmd
headings updated
data export added

@@
 
-### Interaction Frequency and Outgroup Attitudes
+### Interaction Frequency and Attitudes
 
@@
 
-### Need fulfillment, Interaction Quality, and Attitudes
+### Interaction Needs,Quality, and Attitudes
 
@@
 
+# **Export for Methods and Results**
+
+We also export all relevant data for the Methods and Results section, which are written in a separate RMarkdown file and is linked to the full $\LaTeX{}$ manuscript file in Overleaf.
+
+```{r dataExport}
+# collect supplementary data files
+# Worker sample
+dtWorkerSupp <- lapply(ls(pattern = "worker"), get)
+names(dtWorkerSupp) <- ls(pattern = "worker")
+
+# Student sample
+dtStudentSupp <- lapply(ls(pattern = "student"), get)
+names(dtStudentSupp) <- ls(pattern = "student")
+
+# Medical sample
+dtMedicalSupp <- lapply(ls(pattern = "medical"), get)
+names(dtMedicalSupp) <- ls(pattern = "medical")
+
+# collect and export all data files
+save(list = ls(pattern = "dt"), file = "data/wrangled.RData")
+```
+
 # **Software Information**  

### 2021-10-21 Methods-and-Results.Rmd
Update Methods-and-Results.Rmd
initial structure

@@
 # knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
-knitr::knit_hooks$set(
-  error = function(x, options) {
-    paste('\n\n<div class="alert alert-danger">',
-      gsub("##", "\n", gsub("^##\ Error", "**Error**", x)),
-      "</div>",
-      sep = "\n"
-    )
-  },
-  warning = function(x, options) {
-    paste('\n\n<div class="alert alert-warning">',
-      gsub("##", "\n", gsub("^##\ Warning:", "**Warning**", x)),
-      "</div>",
-      sep = "\n"
-    )
-  },
-  message = function(x, options) {
-    paste('\n\n<div class="alert alert-info">',
-      gsub("##", "\n", x),
-      "</div>",
-      sep = "\n"
-    )
-  }
-)
-htmltools::tagList(rmarkdown::html_dependency_font_awesome())
 
@@
 
-\newcommand{\nTheo}{`r nrow(dt.Theories.Included)`}
-\newcommand{\nMeth}{`r nrow(dt.Scales.Included)`}
-\newcommand{\nEmp}{`r nrow(dt.Empirical.included)`}
-
 \section{Study 1}
 
-\subsectio{Methods}
+Our first study
+
+\subsection{Methods}
 
@@
 
-\subsectio{Methods}
+\subsection{Methods}
 

### 2021-10-21 Methods-and-Results.tex
initial structure

--- 2021-10-21 Methods-and-Results.Rmd
@@
----
-output: latex_fragment
-editor_options:
-  chunk_output_type: console
-bibliography: references.bib
-csl: apa.csl
----
-
-```{r setup, include=FALSE}
-# R Studio Clean-Up
-cat("\014") # clear console
-# rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
-gc() # garbage collector
-
-# Install and Load Packages
-# !IMPORTANT!
-# BEFORE FIRST RENDER:
-# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
-# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
-lib <- c(
-  "rmarkdown",
-  "knitr",
-  "remedy",
-  "bookdown",
-  "brms",
-  "psych",
-  "ggplot2",
-  "ggthemes",
-  "haven",
-  "RColorBrewer",
-  "plotly",
-  "gridExtra",
-  "ggpattern",
-  "lme4",
-  "nlme",
-  "jtools",
-  "gtsummary",
-  "sessioninfo",
-  "tibble",
-  "pander",
-  "devtools",
-  "mada",
-  "data.table",
-  "plyr",
-  "dplyr",
-  "tidyr",
-  "Hmisc",
-  "kableExtra",
-  "papaja",
-  "stringr",
-  "stringi",
-  "reshape2",
-  "lubridate"
-)
-invisible(lapply(lib, library, character.only = TRUE))
-rm(lib)
-
-# Load Custom Packages
-source("./scripts/functions/fun.panel.R")
-source("./scripts/functions/themes.R")
-source("./scripts/functions/binaryCor.R")
-
-# Markdown Options
-knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
-knitr::opts_knit$get("root.dir") # check working directory
-options(
-  scipen = 999,
-  digits = 4,
-  width = 400
-) # removes scientific quotation
-# knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
-
-# Global Chunk Options
-knitr::opts_chunk$set(
-  fig.width = 12,
-  fig.height = 8,
-  fig.path = "Figures/",
-  echo = TRUE,
-  warning = FALSE,
-  message = FALSE
-)
-```
-
-```{r import}
-load("data/wrangled.RData")
-```
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{load}\NormalTok{(}\StringTok{"data/wrangled.RData"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
-\input{Tables/ExclusionsCombined} <!-- Placing this here is not ideal because it is only being created later but probably works. -->
-<!-- \input{Tables/TheoreticalExclusion} -->
+\input{Tables/ExclusionsCombined}
 

### 2021-10-21 Methods-and-Results.Rmd
hide R code

@@
 
-```{r import}
+```{r import, include=FALSE}
 load("data/wrangled.RData")
@@
 
-\begin{figure}[h]
-\centering
-\caption{PRISMA Diagrams for the Theoretical, Methodological, and Empirical Literature.}
-\makebox[\textwidth]{\includegraphics[width=\paperwidth]{Figures/PrismaCombined}}
-\label{fig:PrismaCombined}
-\end{figure}
+<!-- \begin{figure}[h] -->
+<!-- \centering -->
+<!-- \caption{PRISMA Diagrams for the Theoretical, Methodological, and Empirical Literature.} -->
+<!-- \makebox[\textwidth]{\includegraphics[width=\paperwidth]{Figures/PrismaCombined}} -->
+<!-- \label{fig:PrismaCombined} -->
+<!-- \end{figure} -->
 
-\input{Tables/ExclusionsCombined} <!-- Placing this here is not ideal because it is only being created later but probably works. -->
-<!-- \input{Tables/TheoreticalExclusion} -->
+<!-- \input{Tables/ExclusionsCombined} <!-- Placing this here is not ideal because it is only being created later but probably works. --> -->
+<!-- <!-- \input{Tables/TheoreticalExclusion} --> -->
 
-\begin{figure}[h]
-\centering
-\caption{Literature Levels: (A) Bar graph of the experience aspect frequencies for theoretical, methodological, and broader empirical literature.
+<!-- \begin{figure}[h] -->
+<!-- \centering -->
+<!-- \caption{Literature Levels: (A) Bar graph of the experience aspect frequencies for theoretical, methodological, and broader empirical literature.
 (B) Bar graph of the number of experience aspects used for theoretical, methodological, and broader empirical literature.
-(C) Average number of additional aspects included when the aspect was considered for theoretical, methodological, and broader empirical literature [Mean ± 95\%CI].}
-\includegraphics[width=\textwidth]{Figures/LiteratureComparison-1}
-\caption*{Note that in (C) within each literature body the aspects are not mutually exclusive (and thus not independent) because scales can include multiple experience aspects.}
-\label{fig:LiteratureComparison}
-\end{figure}
+(C) Average number of additional aspects included when the aspect was considered for theoretical, methodological, and broader empirical literature [Mean ± 95\%CI].} -->
+<!-- \includegraphics[width=\textwidth]{Figures/LiteratureComparison-1} -->
+<!-- \caption*{Note that in (C) within each literature body the aspects are not mutually exclusive (and thus not independent) because scales can include multiple experience aspects.} -->
+<!-- \label{fig:LiteratureComparison} -->
+<!-- \end{figure} -->

### 2021-10-21 Methods-and-Results.tex
hide R code

@@
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{load}\NormalTok{(}\StringTok{"data/wrangled.RData"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
 \section{Study 1}
@@
 
-\begin{figure}[h]
-\centering
-\caption{PRISMA Diagrams for the Theoretical, Methodological, and Empirical Literature.}
-\makebox[\textwidth]{\includegraphics[width=\paperwidth]{Figures/PrismaCombined}}
-\label{fig:PrismaCombined}
-\end{figure}
-
-\input{Tables/ExclusionsCombined}
-
-\begin{figure}[h]
-\centering
-\caption{Literature Levels: (A) Bar graph of the experience aspect frequencies for theoretical, methodological, and broader empirical literature.
-(B) Bar graph of the number of experience aspects used for theoretical, methodological, and broader empirical literature.
-(C) Average number of additional aspects included when the aspect was considered for theoretical, methodological, and broader empirical literature [Mean ± 95\%CI].}
-\includegraphics[width=\textwidth]{Figures/LiteratureComparison-1}
-\caption*{Note that in (C) within each literature body the aspects are not mutually exclusive (and thus not independent) because scales can include multiple experience aspects.}
-\label{fig:LiteratureComparison}
-\end{figure}
+--\textgreater{} --\textgreater{}

### 2021-10-22 Methods-and-Results.Rmd
clean slate
methods structure

--- 2021-10-21 Methods-and-Results.Rmd
@@
 
-Our first study
+Based on our main hypotheses, the aim of our first study is to specifically test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
+To this aim, we conducted an intensive longitudinal survey study with recent economic migrants to the Netherlands, gathering a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations.
 
 \subsection{Methods}
+
+\subsubsection{Participants}
+
+\subsubsection{Procedure}
+
+\subsubsection{Materials}
 
@@
 
-\begin{figure}[h]
-\centering
-\caption{PRISMA Diagrams for the Theoretical, Methodological, and Empirical Literature.}
-\makebox[\textwidth]{\includegraphics[width=\paperwidth]{Figures/PrismaCombined}}
-\label{fig:PrismaCombined}
-\end{figure}
+<!-- \begin{figure}[h] -->
 
-\input{Tables/ExclusionsCombined} <!-- Placing this here is not ideal because it is only being created later but probably works. -->
+<!-- \centering -->
+
+<!-- \caption{PRISMA Diagrams for the Theoretical, Methodological, and Empirical Literature.} -->
+
+<!-- \makebox[\textwidth]{\includegraphics[width=\paperwidth]{Figures/PrismaCombined}} -->
+
+<!-- \label{fig:PrismaCombined} -->
+
+<!-- \end{figure} -->
+
+<!-- \input{Tables/ExclusionsCombined} -->
+
 <!-- \input{Tables/TheoreticalExclusion} -->
 
-\begin{figure}[h]
-\centering
-\caption{Literature Levels: (A) Bar graph of the experience aspect frequencies for theoretical, methodological, and broader empirical literature.
+<!-- \begin{figure}[h] -->
+
+<!-- \centering -->
+
+<!-- \caption{Literature Levels: (A) Bar graph of the experience aspect frequencies for theoretical, methodological, and broader empirical literature.
 (B) Bar graph of the number of experience aspects used for theoretical, methodological, and broader empirical literature.
-(C) Average number of additional aspects included when the aspect was considered for theoretical, methodological, and broader empirical literature [Mean ± 95\%CI].}
-\includegraphics[width=\textwidth]{Figures/LiteratureComparison-1}
-\caption*{Note that in (C) within each literature body the aspects are not mutually exclusive (and thus not independent) because scales can include multiple experience aspects.}
-\label{fig:LiteratureComparison}
-\end{figure}
+(C) Average number of additional aspects included when the aspect was considered for theoretical, methodological, and broader empirical literature [Mean ± 95\%CI].} -->
+
+<!-- \includegraphics[width=\textwidth]{Figures/LiteratureComparison-1} -->
+
+<!-- \caption*{Note that in (C) within each literature body the aspects are not mutually exclusive (and thus not independent) because scales can include multiple experience aspects.} -->
+
+<!-- \label{fig:LiteratureComparison} -->
+
+<!-- \end{figure} -->

### 2021-10-22 Methods-and-Results.tex
clean slate
methods structure

@@
 
-Our first study
+Based on our main hypotheses, the aim of our first study is to
+specifically test the general contact hypothesis, the influence of core
+need fulfillment, and perceived interaction quality during intergroup
+contacts. To this aim, we conducted an intensive longitudinal survey
+study with recent economic migrants to the Netherlands, gathering a
+large body of ecologically valid data on need satisfaction in real-life
+intergroup contact situations.
 
 \subsection{Methods}
+
+\subsubsection{Participants}
+
+\subsubsection{Procedure}
+
+\subsubsection{Materials}
 
@@
 \subsection{Results}
-
---\textgreater{} --\textgreater{}

### 2021-10-22 manuscript.tex
fontawesome adjusted

@@
 \usepackage{scalerel}
-\usepackage{fontawesome}
+\usepackage{fontawesome5}
 \usepackage[normalem]{ulem}
@@
 \usepackage{amsmath}
+\usepackage{ntheorem}
 \usepackage{afterpage}
@@
 \usepackage{censor}
-
-% add definition sections
-\newtheorem{definition}{Definition}
-
-% Select what to do with to-do notes: 
-% \usepackage[disable]{todonotes} % notes not showed
-% \usepackage[draft]{todonotes}   % notes showed
 
@@
   \scaleto{\stackon[1.3pt]{\color{red}$\triangle$}{\tiny\bfseries ?}}{#1}}%
+
+% add definition sections
+\theoremstyle{break}
+\newtheorem{definition}{Definition}
+
+% add hypothesis sections
+\theoremstyle{plain}
+\theoremseparator{:}
+\newtheorem{hyp}{Hypothesis}
+
+\newtheorem{subhyp}{Hypothesis}
+   \renewcommand\thesubhyp{\thehyp\alph{subhyp}}
+
+% add quote section
+\usepackage{csquotes}
+
+% framed box section
+\usepackage{framed}
+\emergencystretch=1em
 
@@
 \affil[1]{University of Groningen, Department of Psychology}
-\affil[2]{Author order to be discussed currently alphabetic by last name.}
+\affil[2]{Author order to be discussed; currently alphabetic by last name.}
 
@@
 
+\section{The Present Research}
+
+\faQuestionCircle\ Not sure where this goes: To ensure that our sample would have a considerable number of intergroup contacts we focused on the minority group perspective in our second study.
+We followed a group of young migrants who had (daily) intergroup contacts with majority Dutch people.
+This design allowed us to test whether intergroup interactions and the fulfillment of psychological needs could jointly predict the development of attitudes towards the outgroup (i.e., the Dutch host society).
+
+\input{Methods-and-Results}
+
+\section{Discussion}
+
 \printbibliography
@@
 
-Here goes the Appendix.
+The Appendix text goes here.
 

### 2021-10-22 Methods-and-Results.Rmd
AOT-Participants added

@@
 
+\faQuestionCircle\ Unsure about order of study one and two.
+Currently chronological.
+But could also be: (1) main model works in larger student sample, (2) works in economic migrant sample, (3) test full thing in medical sample.
+
 \section{Study 1}
@@
 
-\subsubsection{Participants}
+```{r workerSampleInfo, include=FALSE}
+
+workerOccupation <- 
+  dtWorker$clean %>%
+  select(PID, starts_with("occupation")) %>%
+  mutate_all(as_factor) %>% 
+  mutate_all(as.character) %>%
+  replace(is.na(.), "") %>%
+  unite("occupation", -PID, sep = "/") %>%
+  mutate(occupation = trimws(occupation, which = "both", whitespace = "[/]")) %>%
+  distinct
+
+workerSampleInfo <- 
+  dtWorker$clean %>%
+  group_by(PID) %>%
+  summarise(
+    dailiesN = n(), 
+    age = age,
+    gender = as_factor(Gender),
+    edu = as_factor(education_level)
+  ) %>%
+  distinct
+
+workerSampleInfo <- merge(workerSampleInfo, workerOccupation)
+rm(workerOccupation)
+
+table(workerSampleInfo$gender)
+table(workerSampleInfo$edu)
+table(workerSampleInfo$occupation)
+```
+
+\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(workerSampleInfo)` migrants using the local paid participant pool and specifically targeted non-Dutch migrants to participate in our study for a compensation of up to 34 Euros – each two Euros for pre- and post-questionnaire as well as 50 Eurocents for every experience sampling measure.
+Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
+With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{M} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`).
+This is a common number of measurements found in experience sampling studies \citep[e.g., for a systematic review see][]{AanhetRot2012} and should offer sufficient power to model processes within and between participants.
+The sample consisted of relatively young, educated, and western migrants from the global north ($M_{age}$ = `r format(round(mean(workerSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(workerSampleInfo$age),2), nsmall=2)`, `r nrow(workerSampleInfo %>% filter(gender == "Female"))` women, `r nrow(workerSampleInfo %>% filter(occupation == "student"))` students).
+The sample accurately describes one of the largest groups of migrants in the region \citep[][]{GemeenteGroningen2015}.
 

### 2021-10-22 Methods-and-Results.tex
Update Methods-and-Results.tex

@@
+\faQuestionCircle~Unsure about order of study one and two. Currently
+chronological. But could also be: (1) main model works in larger student
+sample, (2) works in economic migrant sample, (3) test full thing in
+medical sample.
+
 \section{Study 1}
@@
 \subsubsection{Participants}
+
+After receiving ethical approval from the University of Groningen, we
+recruited 23 migrants using the local paid participant pool and
+specifically targeted non-Dutch migrants to participate in our study for
+a compensation of up to 34 Euros -- each two Euros for pre- and
+post-questionnaire as well as 50 Eurocents for every experience sampling
+measure. Participants reported on their interactions for at least 30
+days with two daily measures (capturing the morning and afternoon). With
+this design, we aimed at getting 50-60 measurements per participant
+(\textit{M} = 53.26, \textit{M} = 16.72). This is a common number of
+measurements found in experience sampling studies
+\citep[e.g., for a systematic review see][]{AanhetRot2012} and should
+offer sufficient power to model processes within and between
+participants. The sample consisted of relatively young, educated, and
+western migrants from the global north (\(M_{age}\) = 24.35,
+\(SD_{age}\) = 4.73, 19 women, 15 students). The sample accurately
+describes one of the largest groups of migrants in the region
+\citep[][]{GemeenteGroningen2015}.
 

### 2021-10-22 Methods-and-Results.Rmd
adjusted and commented

@@
 ```{r workerSampleInfo, include=FALSE}
-
+# combine education measure
 workerOccupation <- 
@@
 
+# summarize participant characteristics
 workerSampleInfo <- 
@@
     gender = as_factor(Gender),
-    edu = as_factor(education_level)
+    edu = as_factor(education_level),
+    nationality = as_factor(nationality)
   ) %>%
@@
 
+# add occupation variable
 workerSampleInfo <- merge(workerSampleInfo, workerOccupation)
@@
 
+# look at frequencies of characteristics 
 table(workerSampleInfo$gender)
@@
 table(workerSampleInfo$occupation)
+table(as.character(workerSampleInfo$nationality))
 ```
@@
 Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
-With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{M} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`).
-This is a common number of measurements found in experience sampling studies \citep[e.g., for a systematic review see][]{AanhetRot2012} and should offer sufficient power to model processes within and between participants.
+With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{M} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(workerSampleInfo$dailiesN)`).
+This is a common number of measurements found in experience sampling studies and should offer sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
 The sample consisted of relatively young, educated, and western migrants from the global north ($M_{age}$ = `r format(round(mean(workerSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(workerSampleInfo$age),2), nsmall=2)`, `r nrow(workerSampleInfo %>% filter(gender == "Female"))` women, `r nrow(workerSampleInfo %>% filter(occupation == "student"))` students).

### 2021-10-22 Methods-and-Results.tex
adjusted and commented

@@
 this design, we aimed at getting 50-60 measurements per participant
-(\textit{M} = 53.26, \textit{M} = 16.72). This is a common number of
-measurements found in experience sampling studies
-\citep[e.g., for a systematic review see][]{AanhetRot2012} and should
-offer sufficient power to model processes within and between
-participants. The sample consisted of relatively young, educated, and
-western migrants from the global north (\(M_{age}\) = 24.35,
-\(SD_{age}\) = 4.73, 19 women, 15 students). The sample accurately
-describes one of the largest groups of migrants in the region
-\citep[][]{GemeenteGroningen2015}.
+(\textit{M} = 53.26, \textit{M} = 16.72, \textit{total N} = 1225). This
+is a common number of measurements found in experience sampling studies
+and should offer sufficient power to model processes within and between
+participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
+The sample consisted of relatively young, educated, and western migrants
+from the global north (\(M_{age}\) = 24.35, \(SD_{age}\) = 4.73, 19
+women, 15 students). The sample accurately describes one of the largest
+groups of migrants in the region \citep[][]{GemeenteGroningen2015}.
 

### 2021-10-22 Methods-and-Results.Rmd
AOT-P procedure added

@@
 Based on our main hypotheses, the aim of our first study is to specifically test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
-To this aim, we conducted an intensive longitudinal survey study with recent economic migrants to the Netherlands, gathering a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations.
+To this aim, we conducted an intensive longitudinal survey study with recent migrants to the Netherlands, gathering a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations.
+Data was collected from May 5th through June 6th, 2018 (and all participants started the study within the first two days).
+
+The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
 
@@
 
-\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(workerSampleInfo)` migrants using the local paid participant pool and specifically targeted non-Dutch migrants to participate in our study for a compensation of up to 34 Euros – each two Euros for pre- and post-questionnaire as well as 50 Eurocents for every experience sampling measure.
+\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(workerSampleInfo)` migrants using the local paid participant pool and specifically targeted non-Dutch migrants to participate in our study.
 Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
@@
 This is a common number of measurements found in experience sampling studies and should offer sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
+Participants were compensated for their participation with up to 34 Euros – each two Euros for pre- and post-questionnaire as well as 50 Eurocents for every experience sampling measurement occasion.
 The sample consisted of relatively young, educated, and western migrants from the global north ($M_{age}$ = `r format(round(mean(workerSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(workerSampleInfo$age),2), nsmall=2)`, `r nrow(workerSampleInfo %>% filter(gender == "Female"))` women, `r nrow(workerSampleInfo %>% filter(occupation == "student"))` students).
@@
 
-\subsubsection{Procedure}
+\subsubsection{Procedure} The study itself consisted of three main parts, an introductory pre-measurement, and the daily experience sampling measurements, as well as a concluding post-measurement.
+After giving informed consent, participants started by filling in an online pre-questionnaire assessing demographics and general information about their immigration.
+Over the next thirty days, the participants then were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_))`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_)))`).
+After the final day of daily diary measurements, participants were invited to fill in a longer post measurement survey that mirrored the pre-measurement.
+All key variables in for this study were part of the short daily diary surveys.
 
 \subsubsection{Materials}
+
+\subsubsubsection{Intergroup Contact} 
+To test the prerequisite effect of intergroup contact, every ‘Experience Recap’ started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
+(In person interaction for at least 10 minutes)}”
 

### 2021-10-22 Methods-and-Results.tex
AOT-P procedure added

@@
 contacts. To this aim, we conducted an intensive longitudinal survey
-study with recent economic migrants to the Netherlands, gathering a
-large body of ecologically valid data on need satisfaction in real-life
-intergroup contact situations.
+study with recent migrants to the Netherlands, gathering a large body of
+ecologically valid data on need satisfaction in real-life intergroup
+contact situations. Data was collected from May 5th through June 6th,
+2018 (and all participants started the study within the first two days).
+
+The full surveys are available in our Online Supplementary Material A
+and the full data description is available in Online Supplementary
+Materials B.
 
@@
 recruited 23 migrants using the local paid participant pool and
-specifically targeted non-Dutch migrants to participate in our study for
-a compensation of up to 34 Euros -- each two Euros for pre- and
-post-questionnaire as well as 50 Eurocents for every experience sampling
-measure. Participants reported on their interactions for at least 30
-days with two daily measures (capturing the morning and afternoon). With
-this design, we aimed at getting 50-60 measurements per participant
+specifically targeted non-Dutch migrants to participate in our study.
+Participants reported on their interactions for at least 30 days with
+two daily measures (capturing the morning and afternoon). With this
+design, we aimed at getting 50-60 measurements per participant
 (\textit{M} = 53.26, \textit{M} = 16.72, \textit{total N} = 1225). This
@@
 participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
-The sample consisted of relatively young, educated, and western migrants
-from the global north (\(M_{age}\) = 24.35, \(SD_{age}\) = 4.73, 19
-women, 15 students). The sample accurately describes one of the largest
-groups of migrants in the region \citep[][]{GemeenteGroningen2015}.
+Participants were compensated for their participation with up to 34
+Euros -- each two Euros for pre- and post-questionnaire as well as 50
+Eurocents for every experience sampling measurement occasion. The sample
+consisted of relatively young, educated, and western migrants from the
+global north (\(M_{age}\) = 24.35, \(SD_{age}\) = 4.73, 19 women, 15
+students). The sample accurately describes one of the largest groups of
+migrants in the region \citep[][]{GemeenteGroningen2015}.
 
@@
 
+The study itself consisted of three main parts, an introductory
+pre-measurement, and the daily experience sampling measurements, as well
+as a concluding post-measurement. After giving informed consent,
+participants started by filling in an online pre-questionnaire assessing
+demographics and general information about their immigration. Over the
+next thirty days, the participants then were invited twice a day (at 12
+pm and 7pm) to reflect upon their interactions, psychological need
+fulfillments, and current attitudes towards the Dutch outgroup
+(\textit{median duration} = 22, \textit{MAD duration} = 19). After the
+final day of daily diary measurements, participants were invited to fill
+in a longer post measurement survey that mirrored the pre-measurement.
+All key variables in for this study were part of the short daily diary
+surveys.
+
 \subsubsection{Materials}
+
+\subsubsubsection{Intergroup Contact}
+
+To test the prerequisite effect of intergroup contact, every `Experience
+Recap' started with the question
+``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''
 

### 2021-10-22 Methods-and-Results.Rmd
paragraph test

@@
 
-\subsubsubsection{Intergroup Contact} 
+\paragraph{Intergroup Contact} 
 To test the prerequisite effect of intergroup contact, every ‘Experience Recap’ started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
+(In person interaction for at least 10 minutes)}”
+
+\paragraph{Intergroup Contact} To test the prerequisite effect of intergroup contact, every ‘Experience Recap’ started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
 (In person interaction for at least 10 minutes)}”

### 2021-10-23 Methods-and-Results.Rmd
structure updated

@@
 table(as.character(workerSampleInfo$nationality))
+
+histogram(dtWorkerSupp$workerAvFreQual$SumContactNL)
+
 ```
@@
 
-\paragraph{Intergroup Contact} 
-To test the prerequisite effect of intergroup contact, every ‘Experience Recap’ started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
-(In person interaction for at least 10 minutes)}”
+\paragraph{Intergroup Contact}To test the prerequisite effect of intergroup contact, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
+(In person interaction for at least 10 minutes)}” (`r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses).
 
-\paragraph{Intergroup Contact} To test the prerequisite effect of intergroup contact, every ‘Experience Recap’ started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
-(In person interaction for at least 10 minutes)}”
+\paragraph{Psychological Needs}
+
+\paragraph{Perceived Interaction Quality}
+
+\paragraph{Outgroup Attitudes}
 

### 2021-10-23 Supplemental-Material-B-Annotated-Analysis.Rmd
AOT-Participants added
structure updated

@@
 
+### Participants
+
+```{r workerSampleInfo}
+# combine education measure
+workerOccupation <- 
+  dtWorker$clean %>%
+  select(PID, starts_with("occupation")) %>%
+  mutate_all(as_factor) %>% 
+  mutate_all(as.character) %>%
+  replace(is.na(.), "") %>%
+  unite("occupation", -PID, sep = "/") %>%
+  mutate(occupation = trimws(occupation, which = "both", whitespace = "[/]")) %>%
+  distinct
+
+# summarize participant characteristics
+workerSampleInfo <- 
+  dtWorker$clean %>%
+  group_by(PID) %>%
+  summarise(
+    dailiesN = n(), 
+    age = age,
+    gender = as_factor(Gender),
+    edu = as_factor(education_level),
+    nationality = as_factor(nationality)
+  ) %>%
+  distinct
+
+# add occupation variable
+workerSampleInfo <- merge(workerSampleInfo, workerOccupation)
+rm(workerOccupation)
+
+# look at frequencies of characteristics 
+table(workerSampleInfo$gender)
+table(workerSampleInfo$edu)
+table(workerSampleInfo$occupation)
+table(as.character(workerSampleInfo$nationality))
+```
+
+### Interactions
+
+```{r workerInteractionInfo}
+# duration of survey should include median and MAD
+seconds_to_period(median(dtWorker$clean$Duration__in_seconds_))
+seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_)))
+
+workerOutIntPerc <- (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)
+
+```
+
+To test the prerequisite effect of intergroup contact, every daily diary measurement started with the question “_Did you meet a Dutch person this morning [/afternoon]?
+(In person interaction for at least 10 minutes)_” (`r workerOutIntPerc`% of all `r nrow(dtWorkerSupp$workerInteractionType)` recorded Recaps included an interaction with Dutch majority members).
+This question is our main predictor to test whether having an intergroup contact indeed has an influence on one’s rating of the outgroup attitudes during the respective morning or afternoon (i.e., a longitudinal test of the contact hypothesis).
+Methodologically, this question also determined the following survey flow for the participants.
+If they had interactions with Dutch people, they were asked to report details on the duration, type, and quality of the interaction.
+If they did not have interactions with Dutch people, participants were asked to report on their desire to have an interaction – this was done to balance the duration of the two answer options to not make it more attractive for a participant to answer that they did not have an interaction.
+
+### Variable distributions
+
 ## Contact Hypothesis

### 2021-10-24 Methods-and-Results.tex
paragraph test
results structure added

@@
 
-\subsubsubsection{Intergroup Contact}
+\paragraph{Intergroup Contact}
 
-To test the prerequisite effect of intergroup contact, every `Experience
-Recap' started with the question
+To test the prerequisite effect of intergroup contact, every experience
+sampling measurement started with the question
 ``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''
+(31.59\% of all 1225 daily diary responses).
+
+\paragraph{Psychological Needs}
+
+\paragraph{Perceived Interaction Quality}
+
+\paragraph{Outgroup Attitudes}
 
 \subsection{Results}
+
+\paragraph{Contact Hypothesis}
+
+\paragraph{Core Need}
+
+\begin{itemize}
+\tightlist
+\item
+  Att \textasciitilde{} Need \& Qlt \textasciitilde{} Need
+\item
+  Att \textasciitilde{} Need + Qual
+\end{itemize}
+
+\paragraph{Robustness}
 

### 2021-10-24 Methods-and-Results.Rmd
results structure added
intergroup contact added

@@
 histogram(dtWorkerSupp$workerAvFreQual$SumContactNL)
+histogram(dtWorkerSupp$workerAvFreQual$PercContactNL)
 
+histogram(dtWorkerSupp$workerAvFreQual$WinSumContactNL)
+
+dtWorkerSupp$workerAvFreQual$WinSumContactNL %>% max
+
+DescTools::Winsorize(dtWorkerSupp$workerAvFreQual$PercContactNL)
+
+dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)
+
+# misty::multilevel.descript(dtWorkerSupp$workerAvFreQual$SumContactNL, cluster = dtWorkerSupp$workerAvFreQual$ExternalReference)
 ```
@@
 \paragraph{Intergroup Contact}To test the prerequisite effect of intergroup contact, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
-(In person interaction for at least 10 minutes)}” (`r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses).
+(In person interaction for at least 10 minutes)}”.
+Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
+(`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; $N_{total}$ = `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
+These participants are removed from any analyses including outgroup contacts.}.
 
@@
 \subsection{Results}
+
+\paragraph{Contact Hypothesis}
+
+\paragraph{Core Need}
+
+- Att ~ Need & Qlt ~ Need
+- Att ~ Need + Qual
+
+\paragraph{Robustness}
 

### 2021-10-24 Methods-and-Results.tex
intergroup contact added

@@
 sampling measurement started with the question
-``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''
-(31.59\% of all 1225 daily diary responses).
+``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''.
+Our participants recorded between 2--51 (3.23--3.23\% of individual
+daily diary measurements; \(N_{total}\) = 31.59\% of all 1225 daily
+diary
+responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
+These participants are removed from any analyses including outgroup contacts.}.
 

### 2021-10-24 Methods-and-Results.Rmd
worker descriptives added

--- 2021-10-23 Methods-and-Results.Rmd
@@
   "ggthemes",
+  "purrr",
   "haven",
@@
   "reshape2",
-  "lubridate"
+  "lubridate",
+  "misty"
 )
@@
 source("./scripts/functions/binaryCor.R")
+source("./scripts/functions/MlCorMat.R")
 
@@
 
-histogram(dtWorkerSupp$workerAvFreQual$SumContactNL)
+# categorical variables:
+# - outgroup contact
+# - non-outgroup contact
 
+# continuous variables:
+# - Core Need fulfillment
+# - SDT Competence
+# - SDT Autonomy
+# - SDT Relatedness
+# - Interaction Quality
+# - Outgroup Attitudes
+######
+# within cor
+# between cor
+# ---
+# Grand mean
+# SD between
+# SD within
+# Proportion of variance
+# __ __ __
+# Note:
+# N within ppt.s 
+######
+
+# divide into trait and state
+dtWorkerSupp$workerWithinBetween <-
+  MlTraitState(
+    data = dtWorkerSupp$workerInteractionType,
+    id = "PID",
+    selection =
+      c(
+        "keyMotiveFulfilled",
+        "competence.daily.all",
+        "autonomy.daily.all",
+        "relatedness.daily.all",
+        "thermometerDutch_1",
+        "keymotive_fulfillemt_1",
+        "competence_1",
+        "autonomy_1",
+        "relatedness_1"
+      )
+  )
+
+workerMlCor <-
+  MlCorMat(
+    data = dtWorkerSupp$workerInteractionType,
+    id = "PID",
+    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "thermometerDutch_1") ,
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
+  )
+
+workerMlCor %>%
+  kable(
+    .,
+    caption = "Worker: Multilevel Core Variable Descriptives",
+    format = "latex",
+    booktabs = TRUE,
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person coorelations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  save_kable("Tables/workerVarDescr.tex")
+
+workerOutMlCor <-
+  MlCorMat(
+    data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "thermometerDutch_1") ,
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
+  )
+
+workerOutMlCor %>%
+  kable(
+    .,
+    caption = "Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
+    format = "latex",
+    booktabs = TRUE,
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person coorelations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  save_kable("Tables/workerOutVarDescr.tex")
+
+# misty::multilevel.descript(dtWorkerSupp$workerWithinBetween$keyMotiveFulfilled, cluster = dtWorkerSupp$workerWithinBetween$PID)
 ```
@@
 \paragraph{Intergroup Contact}To test the prerequisite effect of intergroup contact, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
-(In person interaction for at least 10 minutes)}” (`r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses).
+(In person interaction for at least 10 minutes)}”.
+Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
+(`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
+These participants are removed from any analyses including outgroup contacts.}.
 
-\paragraph{Psychological Needs}
+\paragraph{Psychological Needs} Irrespective of whether participants had an interaction with Dutch people or not, everyone answered a short series of questions on psychological need fulfillment.
+However, whereas participants with interactions reported on the need fulfillment during the interaction, people without interactions with Dutch people judged the past daytime period in general.
+To assess the fulfillment of psychological needs, we included two types of need measurement: (1) the core situational need and (2) general self-determination theory needs.
+
+For the core situational need, we asked participants in an open ended text field: “\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}”.
+We then used the participant’s open text entry of their core need to see how much this was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / you] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).
+
+We, additionally, included a common measure of three self-determination theory needs \citep[taken from][]{Downie2008}.
+The items were introduced either by “\textit{During the interaction:}” or “\textit{This morning [/afternoon]:}” and measured autonomy (“\textit{I was myself.}”), competence (“\textit{I felt competent.}”), and relatedness (without intergroup contact “\textit{I had a strong need to belong}”; with intergroup contact: “\textit{I shared information about myself.}” and “\textit{The other(s) shared information about themselves.}”).
+All items were rated on a continuous slider scale from very little (-50) to a great deal (+50).
 
@@
 
+\input{Tables/workerVarDescr}
+\input{Tables/workerOutVarDescr}
+
 \subsection{Results}
+
+\paragraph{Contact Hypothesis}
+
+\paragraph{Core Need}
+
+- Att ~ Need & Qlt ~ Need
+- Att ~ Need + Qual
+
+\paragraph{Robustness}
 

### 2021-10-24 Methods-and-Results.tex
worker descriptives added

--- 2021-10-24 Methods-and-Results.tex
@@
 sampling measurement started with the question
-``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''
-(31.59\% of all 1225 daily diary responses).
+``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''.
+Our participants recorded between 2--51 (3.23--91.07\% of individual
+daily diary measurements; 31.59\% of all 1225 daily diary
+responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
+These participants are removed from any analyses including outgroup contacts.}.
 
 \paragraph{Psychological Needs}
+
+Irrespective of whether participants had an interaction with Dutch
+people or not, everyone answered a short series of questions on
+psychological need fulfillment. However, whereas participants with
+interactions reported on the need fulfillment during the interaction,
+people without interactions with Dutch people judged the past daytime
+period in general. To assess the fulfillment of psychological needs, we
+included two types of need measurement: (1) the core situational need
+and (2) general self-determination theory needs.
+
+For the core situational need, we asked participants in an open ended
+text field:
+``\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}''.
+We then used the participant's open text entry of their core need to see
+how much this was fulfilled during the interaction or the past daytime
+period:
+``\textit{[The interaction / you] fulfilled your goal: [-previous text entry-]}''
+on a continuous slider scale ranging from strongly disagree (-50) to
+strongly agree (+50).
+
+We, additionally, included a common measure of three self-determination
+theory needs \citep[taken from][]{Downie2008}. The items were introduced
+either by ``\textit{During the interaction:}'' or
+``\textit{This morning [/afternoon]:}'' and measured autonomy
+(``\textit{I was myself.}''), competence
+(``\textit{I felt competent.}''), and relatedness (without intergroup
+contact ``\textit{I had a strong need to belong}''; with intergroup
+contact: ``\textit{I shared information about myself.}'' and
+``\textit{The other(s) shared information about themselves.}''). All
+items were rated on a continuous slider scale from very little (-50) to
+a great deal (+50).
 
@@
 \paragraph{Outgroup Attitudes}
+
+\input{Tables/workerVarDescr}
+\input{Tables/workerOutVarDescr}
 

### 2021-10-24 Tables/workerOutVarDescr.tex
worker descriptives added

\begin{table}

\caption{\label{tab:workerSampleInfo}Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
\centering
\begin{tabular}[t]{llcccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Attitudes NL\\
\midrule
Core Need &  & 0.84*** & 0.60*** & 0.27 & -0.02\\
Competence & 0.36*** &  & 0.88*** & 0.17 & -0.24\\
Autonomy & 0.29*** & 0.24*** &  & 0.20 & 0.02\\
Relatedness & 0.50*** & 0.23*** & 0.24*** &  & 0.17\\
Attitudes NL & 0.17** & 0.27*** & 0.27*** & 0.37*** & \\
\addlinespace
Grand Mean & 32.20 & 16.53 & 22.64 & 1.58 & 72.46\\
Between-person SD & 12.42 & 13.41 & 10.22 & 14.16 & 13.62\\
Within-person SD & 17.66 & 18.78 & 14.93 & 23.97 & 9.50\\
ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.68\\
ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.98\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
\multicolumn{6}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}
\end{table}

### 2021-10-24 Tables/workerVarDescr.tex
worker descriptives added

--- 2021-10-24 Tables/workerOutVarDescr.tex
@@
 
-\caption{\label{tab:workerSampleInfo}Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
+\caption{\label{tab:workerSampleInfo}Worker: Multilevel Core Variable Descriptives}
 \centering
@@
 \midrule
-Core Need &  & 0.84*** & 0.60*** & 0.27 & -0.02\\
-Competence & 0.36*** &  & 0.88*** & 0.17 & -0.24\\
-Autonomy & 0.29*** & 0.24*** &  & 0.20 & 0.02\\
-Relatedness & 0.50*** & 0.23*** & 0.24*** &  & 0.17\\
-Attitudes NL & 0.17** & 0.27*** & 0.27*** & 0.37*** & \\
+Core Need &  & 0.67*** & 0.54*** & 0.01 & -0.23\\
+Competence & 0.36*** &  & 0.72*** & -0.14 & -0.20\\
+Autonomy & 0.31*** & 0.09** &  & -0.05 & 0.19\\
+Relatedness & 0.45*** & 0.09** & 0.14*** &  & -0.06\\
+Attitudes NL & 0.05 & 0.11*** & 0.12*** & 0.14*** & \\
 \addlinespace
-Grand Mean & 32.20 & 16.53 & 22.64 & 1.58 & 72.46\\
-Between-person SD & 12.42 & 13.41 & 10.22 & 14.16 & 13.62\\
-Within-person SD & 17.66 & 18.78 & 14.93 & 23.97 & 9.50\\
-ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.68\\
-ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.98\\
+Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 71.49\\
+Between-person SD & 14.68 & 13.72 & 12.09 & 14.59 & 12.91\\
+Within-person SD & 20.83 & 20.89 & 15.15 & 23.29 & 8.11\\
+ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.70\\
+ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.99\\
 \bottomrule

### 2021-10-24 scripts/functions/MlCorMat.R

@@ -1,0 +1,224 @@
+MlCorMat <-
+  function(data,
+           id,
+           selection,
+           labels = selection,
+           method = c("pearson", "spearman"),
+           removeTriangle = c("upper", "lower"),
+           result = c("none", "html", "latex")) {
+    # for testing
+    # data <- dtWorkerSupp$workerInteractionType
+    # id <- "PID"
+    # selection <- varSelection
+    # labels <- varlabels
+    
+    # calculate trait scores (participant means)
+    data <- 
+      data %>%
+      select(id, selection) %>%
+      group_by_at(vars(matches(id))) %>%
+      mutate_at(selection, list(trait = ~mean(., na.rm=TRUE))) %>%
+      ungroup 
+    
+    data <-
+      map_dfc(selection,
+              ~ data %>%
+                transmute(
+                  !!str_c(.x, '_state') :=
+                    !!rlang::sym(.x)-!!rlang::sym(str_c(.x, "_trait"))
+                )) %>%
+      bind_cols(data, .)
+    
+    # Fid out why own is different
+    # raw <-
+    #   data %>%
+    #   select(selection) %>%
+    #   as.matrix
+    # 
+    # corRaw <- rcorr(raw, type=method[1])
+    # rRaw <- corRaw$r # Matrix of correlation coeficients
+    # pRaw <- corRaw$P # Matrix of p-value 
+    # 
+    # ## Define notions for significance levels; spacing is important.
+    # starsRaw <- ifelse(pRaw < .001, "***", ifelse(pRaw < .01, "**", ifelse(pRaw < .05, "* ", "   ")))
+    # 
+    # ## trunctuate the correlation matrix to two decimal
+    # rRaw <- format(round(cbind(rep(-1.11, ncol(raw)), rRaw), 2))[,-1]
+    # 
+    # ## build a new matrix that includes the correlations with their apropriate stars
+    # rRawStar <- matrix(paste(rRaw, starsRaw, sep=""), ncol=ncol(raw))
+    # 
+    # 
+    # trait <-
+    #   data %>%
+    #   select(paste0(selection, "_trait")) %>%
+    #   as.matrix
+    # 
+    # corTrait <- rcorr(trait, type=method[1])
+    # rTrait <- corTrait$r # Matrix of correlation coeficients
+    # pTrait <- corTrait$P # Matrix of p-value 
+    # 
+    # ## Define notions for significance levels; spacing is important.
[…]

### 2021-10-25 Methods-and-Results.Rmd
AOT-P methods added

@@
 The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
+Correlations and descriptive statistics of the included variables are available in Table \ref{tab:workerVarDescr} and Table \ref{tab:workerOutVarDescr}.
 
@@
   )
+```
 
+```{r workerVarDescr, include=FALSE}
 workerMlCor <-
@@
   save_kable("Tables/workerVarDescr.tex")
+```
 
+```{r workerOutVarDescr, include=FALSE}
 workerOutMlCor <-
@@
 
-\paragraph{Psychological Needs} Irrespective of whether participants had an interaction with Dutch people or not, everyone answered a short series of questions on psychological need fulfillment.
+\paragraph{Psychological Needs}Irrespective of whether participants had an interaction with Dutch people or not, everyone answered a short series of questions on psychological need fulfillment.
 However, whereas participants with interactions reported on the need fulfillment during the interaction, people without interactions with Dutch people judged the past daytime period in general.
@@
 For the core situational need, we asked participants in an open ended text field: “\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}”.
-We then used the participant’s open text entry of their core need to see how much this was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / you] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).
+Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / you] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).
 
-We, additionally, included a common measure of three self-determination theory needs \citep[taken from][]{Downie2008}.
+We, additionally, included a common measure of three self-determination theory needs \citep[see][]{Downie2008}.
 The items were introduced either by “\textit{During the interaction:}” or “\textit{This morning [/afternoon]:}” and measured autonomy (“\textit{I was myself.}”), competence (“\textit{I felt competent.}”), and relatedness (without intergroup contact “\textit{I had a strong need to belong}”; with intergroup contact: “\textit{I shared information about myself.}” and “\textit{The other(s) shared information about themselves.}”).
@@
 
-\paragraph{Perceived Interaction Quality}
+\paragraph{Perceived Interaction Quality}As an explanatory mechanism, we assessed ratings of the perceived interaction quality.
+As our main measurement, participants rated the statement “\textit{Overall the interaction was …}” on two continuous slider scales measuring pleasantness \citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
 
-\paragraph{Outgroup Attitudes}
+\paragraph{Outgroup Attitudes}At the end of every daily diary measurement we asked all participants about their current attitudes towards the Dutch – our main dependent variable.
+To assess the momentary outgroup evaluation we used the common feeling thermometer: “How favorable do you feel towards the Dutch?” \citep[][]{Lavrakas2008}.
+Participants then rated their attitude on a continuous slider scale from “very cold – 0” through “no feeling – 50” to “very warm – 100”.
+Both the question phrasing as well as the tick labels were consistent with large-scale panel surveys \citep[e.g.,][]{DeBell2010}.
 

### 2021-10-25 Methods-and-Results.tex
AOT-P methods added

@@
 and the full data description is available in Online Supplementary
-Materials B.
+Materials B. Correlations and descriptive statistics of the included
+variables are available in Table \ref{tab:workerVarDescr} and Table
+\ref{tab:workerOutVarDescr}.
 
@@
 ``\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}''.
-We then used the participant's open text entry of their core need to see
-how much this was fulfilled during the interaction or the past daytime
-period:
+Then, with reference to the text entry, we asked how much this core need
+was fulfilled during the interaction or the past daytime period:
 ``\textit{[The interaction / you] fulfilled your goal: [-previous text entry-]}''
@@
 We, additionally, included a common measure of three self-determination
-theory needs \citep[taken from][]{Downie2008}. The items were introduced
-either by ``\textit{During the interaction:}'' or
+theory needs \citep[see][]{Downie2008}. The items were introduced either
+by ``\textit{During the interaction:}'' or
 ``\textit{This morning [/afternoon]:}'' and measured autonomy
@@
 
+As an explanatory mechanism, we assessed ratings of the perceived
+interaction quality. As our main measurement, participants rated the
+statement ``\textit{Overall the interaction was …}'' on two continuous
+slider scales measuring pleasantness
+\citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
+
 \paragraph{Outgroup Attitudes}
+
+At the end of every daily diary measurement we asked all participants
+about their current attitudes towards the Dutch -- our main dependent
+variable. To assess the momentary outgroup evaluation we used the common
+feeling thermometer: ``How favorable do you feel towards the Dutch?''
+\citep[][]{Lavrakas2008}. Participants then rated their attitude on a
+continuous slider scale from ``very cold -- 0'' through ``no feeling --
+50'' to ``very warm -- 100''. Both the question phrasing as well as the
+tick labels were consistent with large-scale panel surveys
+\citep[e.g.,][]{DeBell2010}.
 

### 2021-10-25 Methods-and-Results.Rmd
table fix

@@
   ) %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
   save_kable("Tables/workerVarDescr.tex")
@@
   ) %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
   save_kable("Tables/workerOutVarDescr.tex")

### 2021-10-25 Methods-and-Results.Rmd
AOT-P contact hypothesis added

@@
     dailiesN = n(), 
+    morningN = sum(daytime=="morning"),
+    afternoonN = sum(daytime=="afternoon"),
     age = age,
@@
 Over the next thirty days, the participants then were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_))`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_)))`).
+General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%)}.
+The response rates were approximately equal during mornings (\textit{n} = `r sum(workerSampleInfo$morningN)`) and afternoons (\textit{n} = `r sum(workerSampleInfo$afternoonN)`) and most measurements were completed within four hours of the invitation.
 After the final day of daily diary measurements, participants were invited to fill in a longer post measurement survey that mirrored the pre-measurement.
@@
 
-\paragraph{Contact Hypothesis}
+```{r WorkerFreqAttCor}
+# correlation panel
+pairs.panels.new(
+  dtWorkerSupp$workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
+    "Sum:\nNumber of Outgroup Contacts (NL)",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+
+# correlation panel with interaction sums winsorized
+pairs.panels.new(
+  dtWorkerSupp$workerAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
+    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+```
+
+\paragraph{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
+First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
+Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
+We find that neither the number of interactions nor the number of daily diary responses with an interaction were significantly related with the average outgroup attitudes.
+This is to say that within our data, participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
+This might be due to the aggregation within the participants or the small sample size of between participant data.
+Nonetheless, the aggregate data does not support the notion that simply having more interactions with an outgroup results in more positive outgroup attitudes.
+
+```{r workerModelOlsAttFreqQual}
+# create list to store Worker models
+mdlWorker <- list()
+
+# regression
+mdlWorker$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL * AvQuality, data = dtWorkerSupp$workerAvFreQual)
+# summary(lmWorkerAttFreqQualX)
+
+summ(
+  mdlWorker$lmAttFreqQualX,
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+mdlWorker$lmAttFreqQualXEta <-
+  effectsize::eta_squared(mdlWorker$lmAttFreqQualX, partial = TRUE)
+
+interactions::interact_plot(
+  mdlWorker$lmAttFreqQualX,
+  pred = AvQuality,
+  modx = SumContactNL,
+  interval = TRUE,
+  partial.residuals = TRUE
+)
+
+interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
+                             pred = AvQuality,
+                             modx = SumContactNL,
+                             alpha = .05)
+```
+
+However, despite the missing relationship with the number of interactions, we find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
+Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
+And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL:AvQuality","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL:AvQuality","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL:AvQuality","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL:AvQuality") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
+Looking at a floodlight analysis of the effect, we find that in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker.
+However, it should be noted that this is based on data aggregating all within participant nuances and is only the date of 21 people.
+
+```{r workerModelMLAttNull}
+# Create and save Model
+mdlWorker$lmerAttNull <-
+  lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID),
+    data = dtWorker$full
+  ) # use optim if it does not converge
+
+mdlWorker$lmeAttNull <-
+  lme(
+    thermometerDutch_1 ~ 1,
+    random = ~ 1 | PID,
+    data = dtWorker$full,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(lmerWorkerAttNull) #or with the lme function
+summ(mdlWorker$lmerAttNull, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=dtWorker$full),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlWorker$varAttNull <- 
+  VarCorr(mdlWorker$lmeAttNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlWorker$tauAttNull <- 
+  as.numeric(mdlWorker$varAttNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlWorker$sigmaAttNull <- 
+  as.numeric(mdlWorker$varAttNull[2])
+# The ICC estimate (between/between+within) is:
+mdlWorker$IccAttNull <-
+  (as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2])))
+mdlWorker$IccPercAttNull <-
+  ((as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2])))) * 100
+```
+```{r workerModelInterceptAttType}
+# Create and save Model
+mdlWorker$lmeInterceptAttType <-
+  lme(
+    thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction,
+    random =  ~ 1 | PID,
+    data = dtWorkerSupp$workerInteractionType
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlWorker$lmerInterceptAttType <- lmer(
+    thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    data = dtWorkerSupp$workerInteractionType
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlWorker$lmerInterceptAttTypeCI <- confint(mdlWorker$lmerInterceptAttType)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorker$lmeAttNull, 
+      mdlWorker$lmeInterceptAttType) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorker$varInterceptAttType <- 
+  lme4::VarCorr(mdlWorker$lmeInterceptAttType)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorker$varBtwInterceptAttType <-
+  1 - (as.numeric(mdlWorker$varInterceptAttType[1]) / as.numeric(mdlWorker$varAttNull[1]))
+mdlWorker$varBtwPercInterceptAttType <-
+  (1 - (as.numeric(mdlWorker$varInterceptAttType[1]) / as.numeric(mdlWorker$varAttNull[1]))) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorker$varWithinInterceptAttType <-
+  1 - (as.numeric(mdlWorker$varInterceptAttType[2]) / as.numeric(mdlWorker$varAttNull[2]))
+mdlWorker$varWithinPercInterceptAttType <-
+  (1 - (as.numeric(mdlWorker$varInterceptAttType[2]) / as.numeric(mdlWorker$varAttNull[2]))) * 100
+```
+
+We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (\textit{b} = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","Value"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmeInterceptAttType$fixDF$X["OutgroupInteractionYes"] %>% as.numeric`) = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","t-value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} `r ifelse(coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"]<.001, "< .001", paste0("= ", coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"] %>% round(3) %>% format(nsmall=3)))`, \textit{95\%CI}[`r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "2.5 %"]`, `r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "97.5 %"]`]), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
 

### 2021-10-25 Supplemental-Material-B-Annotated-Analysis.Rmd
AOT-P contact hypothesis added

@@
 summ(
-  lmer(
+  mdlWorker$lmerInterceptAttType <- lmer(
     thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
@@
 )
+
+mdlWorker$lmAttFreqQualXEta <-
+  effectsize::eta_squared(mdlWorker$lmAttFreqQualX, partial = TRUE)
 

### 2021-10-25 Methods-and-Results.tex
AOT-P contact hypothesis added rendered

@@
 fulfillments, and current attitudes towards the Dutch outgroup
-(\textit{median duration} = 22, \textit{MAD duration} = 19). After the
-final day of daily diary measurements, participants were invited to fill
-in a longer post measurement survey that mirrored the pre-measurement.
-All key variables in for this study were part of the short daily diary
-surveys.
+(\textit{median duration} = 22, \textit{MAD duration} = 19). General
+compliance was high (85.90\% of all invited surveys were filled
+in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%)}.
+The response rates were approximately equal during mornings (\textit{n}
+= 621) and afternoons (\textit{n} = 604) and most measurements were
+completed within four hours of the invitation. After the final day of
+daily diary measurements, participants were invited to fill in a longer
+post measurement survey that mirrored the pre-measurement. All key
+variables in for this study were part of the short daily diary surveys.
 
@@
 
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# correlation panel}
+\FunctionTok{pairs.panels.new}\NormalTok{(}
+\NormalTok{  dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerAvFreQual }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{select}\NormalTok{(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),}
+  \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}
+    \StringTok{"Sum:}\SpecialCharTok{\textbackslash{}n}\StringTok{Numer of beeps with Outgroup Contact (NL)"}\NormalTok{,}
+    \StringTok{"Sum:}\SpecialCharTok{\textbackslash{}n}\StringTok{Number of Outgroup Contacts (NL)"}\NormalTok{,}
+    \StringTok{"Mean:}\SpecialCharTok{\textbackslash{}n}\StringTok{Interaction Quality"}\NormalTok{,}
+    \StringTok{"Mean:}\SpecialCharTok{\textbackslash{}n}\StringTok{Outgroup Attitudes (NL)"}
+\NormalTok{  )}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{Figures/WorkerFreqAttCor-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# correlation panel with interaction sums winsorized}
+\FunctionTok{pairs.panels.new}\NormalTok{(}
+\NormalTok{  dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerAvFreQual }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{select}\NormalTok{(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),}
+  \AttributeTok{labels =} \FunctionTok{c}\NormalTok{(}
+    \StringTok{"Sum:}\SpecialCharTok{\textbackslash{}n}\StringTok{Numer of beeps with Outgroup Contact (NL)}\SpecialCharTok{\textbackslash{}n}\StringTok{[Winsorized]"}\NormalTok{,}
+    \StringTok{"Sum:}\SpecialCharTok{\textbackslash{}n}\StringTok{Number of Outgroup Contacts (NL)}\SpecialCharTok{\textbackslash{}n}\StringTok{[Winsorized]"}\NormalTok{,}
+    \StringTok{"Mean:}\SpecialCharTok{\textbackslash{}n}\StringTok{Interaction Quality"}\NormalTok{,}
+    \StringTok{"Mean:}\SpecialCharTok{\textbackslash{}n}\StringTok{Outgroup Attitudes (NL)"}
+\NormalTok{  )}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{Figures/WorkerFreqAttCor-2.pdf}
+
 \paragraph{Contact Hypothesis}
+
+We tested the most general contact hypothesis in two steps. First, we
+assessed whether more intergroup interactions were related to to more
+positive outgroup attitudes. Second, we tested whether a potential
+positive effect on outgroup attitudes depended on the interaction
+quality (jointly with the number of interactions). We find that neither
+the number of interactions nor the number of daily diary responses with
+an interaction were significantly related with the average outgroup
+attitudes. This is to say that within our data, participants with more
+outgroup interactions did not have significantly more positive outgroup
+attitudes. This might be due to the aggregation within the participants
+or the small sample size of between participant data. Nonetheless, the
+aggregate data does not support the notion that simply having more
+interactions with an outgroup results in more positive outgroup
+attitudes.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# create list to store Worker models}
+\NormalTok{mdlWorker }\OtherTok{\textless{}{-}} \FunctionTok{list}\NormalTok{()}
+
+\CommentTok{\# regression}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualX }\OtherTok{\textless{}{-}}
+  \FunctionTok{lm}\NormalTok{(AvAttitude }\SpecialCharTok{\textasciitilde{}}\NormalTok{ SumContactNL }\SpecialCharTok{*}\NormalTok{ AvQuality, }\AttributeTok{data =}\NormalTok{ dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerAvFreQual)}
+\CommentTok{\# summary(lmWorkerAttFreqQualX)}
+
+\FunctionTok{summ}\NormalTok{(}
+\NormalTok{  mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualX,}
+  \AttributeTok{confint =} \ConstantTok{TRUE}\NormalTok{,}
+  \AttributeTok{digits =} \DecValTok{3}\NormalTok{,}
+  \AttributeTok{center =} \ConstantTok{TRUE}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}[!h]
+\centering
+\begin{tabular}{lr}
+\toprule
+\cellcolor{gray!6}{Observations} & \cellcolor{gray!6}{21 (2 missing obs. deleted)}\\
+Dependent variable & AvAttitude\\
+\cellcolor{gray!6}{Type} & \cellcolor{gray!6}{OLS linear regression}\\
+\bottomrule
+\end{tabular}
+\end{table} \begin{table}[!h]
+\centering
+\begin{tabular}{lr}
+\toprule
+\cellcolor{gray!6}{F(3,17)} & \cellcolor{gray!6}{6.663}\\
+R² & 0.540\\
+\cellcolor{gray!6}{Adj. R²} & \cellcolor{gray!6}{0.459}\\
+\bottomrule
+\end{tabular}
+\end{table} \begin{table}[!h]
+\centering
+\begin{threeparttable}
+\begin{tabular}{lrrrrr}
+\toprule
+  & Est. & 2.5\% & 97.5\% & t val. & p\\
+\midrule
+\cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{70.930} & \cellcolor{gray!6}{66.519} & \cellcolor{gray!6}{75.341} & \cellcolor{gray!6}{33.927} & \cellcolor{gray!6}{0.000}\\
+SumContactNL & 0.269 & -0.150 & 0.688 & 1.354 & 0.193\\
+\cellcolor{gray!6}{AvQuality} & \cellcolor{gray!6}{0.765} & \cellcolor{gray!6}{0.288} & \cellcolor{gray!6}{1.242} & \cellcolor{gray!6}{3.385} & \cellcolor{gray!6}{0.004}\\
+SumContactNL:AvQuality & -0.049 & -0.085 & -0.014 & -2.954 & 0.009\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item Standard errors: OLS; Continuous predictors are mean-centered.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualXEta }\OtherTok{\textless{}{-}}
+\NormalTok{  effectsize}\SpecialCharTok{::}\FunctionTok{eta\_squared}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualX, }\AttributeTok{partial =} \ConstantTok{TRUE}\NormalTok{)}
+
+\NormalTok{interactions}\SpecialCharTok{::}\FunctionTok{interact\_plot}\NormalTok{(}
+\NormalTok{  mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualX,}
+  \AttributeTok{pred =}\NormalTok{ AvQuality,}
+  \AttributeTok{modx =}\NormalTok{ SumContactNL,}
+  \AttributeTok{interval =} \ConstantTok{TRUE}\NormalTok{,}
+  \AttributeTok{partial.residuals =} \ConstantTok{TRUE}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{Figures/workerModelOlsAttFreqQual-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{interactions}\SpecialCharTok{::}\FunctionTok{johnson\_neyman}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmAttFreqQualX,}
+                             \AttributeTok{pred =}\NormalTok{ AvQuality,}
+                             \AttributeTok{modx =}\NormalTok{ SumContactNL,}
+                             \AttributeTok{alpha =}\NormalTok{ .}\DecValTok{05}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## JOHNSON-NEYMAN INTERVAL 
+## 
+## When SumContactNL is OUTSIDE the interval [23.66, 75.42], the slope of AvQuality is p < .05.
+## 
+## Note: The range of observed values of SumContactNL is [2.00, 51.00]
+\end{verbatim}
+
+\includegraphics{Figures/workerModelOlsAttFreqQual-2.pdf}
+
+However, despite the missing relationship with the number of
+interactions, we find a medium sized correlation between the
+participants' Average Interaction Quality and their Average Outgroup
+Attitudes. Thus within our data participants with a higher quality
+outgroup interactions also held more positive attitudes towards that
+group. And when considering the number of interactions and average
+interaction quality jointly in a linear regression, we additionally find
+a statistically significant interaction term (\textit{b} = -0.05,
+\textit{t}(17) = -2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34).
+Looking at a floodlight analysis of the effect, we find that in our
+sample with an increasing number of interactions the positive effect of
+average interaction quality becomes weaker. However, it should be noted
+that this is based on data aggregating all within participant nuances
+and is only the date of 21 people.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# Create and save Model}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmerAttNull }\OtherTok{\textless{}{-}}
+\NormalTok{  lme4}\SpecialCharTok{::}\FunctionTok{lmer}\NormalTok{(thermometerDutch\_1 }\SpecialCharTok{\textasciitilde{}} \DecValTok{1} \SpecialCharTok{+}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{|}\NormalTok{ PID),}
+    \AttributeTok{data =}\NormalTok{ dtWorker}\SpecialCharTok{$}\NormalTok{full}
+\NormalTok{  ) }\CommentTok{\# use optim if it does not converge}
+
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmeAttNull }\OtherTok{\textless{}{-}}
+  \FunctionTok{lme}\NormalTok{(}
+\NormalTok{    thermometerDutch\_1 }\SpecialCharTok{\textasciitilde{}} \DecValTok{1}\NormalTok{,}
+    \AttributeTok{random =} \SpecialCharTok{\textasciitilde{}} \DecValTok{1} \SpecialCharTok{|}\NormalTok{ PID,}
+    \AttributeTok{data =}\NormalTok{ dtWorker}\SpecialCharTok{$}\NormalTok{full,}
+    \AttributeTok{control =} \FunctionTok{list}\NormalTok{(}\AttributeTok{opt =} \StringTok{"nlmimb"}\NormalTok{)}
+\NormalTok{  ) }\CommentTok{\# use optim if it does not converge}
+
+\CommentTok{\# Get summary with p{-}values (Satterthwaite\textquotesingle{}s method)}
+\CommentTok{\# summary(lmerWorkerAttNull) \#or with the lme function}
+\FunctionTok{summ}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmerAttNull, }\AttributeTok{digits =} \DecValTok{3}\NormalTok{, }\AttributeTok{center =} \ConstantTok{TRUE}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}[!h]
+\centering
+\begin{tabular}{lr}
+\toprule
+\cellcolor{gray!6}{Observations} & \cellcolor{gray!6}{1225}\\
+Dependent variable & thermometerDutch\_1\\
+\cellcolor{gray!6}{Type} & \cellcolor{gray!6}{Mixed effects linear regression}\\
+\bottomrule
+\end{tabular}
+\end{table} \begin{table}[!h]
+\centering
+\begin{tabular}{lr}
+\toprule
+\cellcolor{gray!6}{AIC} & \cellcolor{gray!6}{8805.880}\\
+BIC & 8821.213\\
+\cellcolor{gray!6}{Pseudo-R² (fixed effects)} & \cellcolor{gray!6}{0.000}\\
+Pseudo-R² (total) & 0.698\\
+\bottomrule
+\end{tabular}
+\end{table} \begin{table}[!h]
+\centering
+\begin{threeparttable}
+\begin{tabular}{lrrrrr}
+\toprule
+\multicolumn{6}{c}{Fixed Effects} \\
+\cmidrule(l{3pt}r{3pt}){1-6}
+  & Est. & S.E. & t val. & d.f. & p\\
+\midrule
+\cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{71.338} & \cellcolor{gray!6}{2.695} & \cellcolor{gray!6}{26.466} & \cellcolor{gray!6}{22.053} & \cellcolor{gray!6}{0.000}\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item  p values calculated using Satterthwaite d.f. ; Continuous predictors are mean-centered.
+\end{tablenotes}
+\end{threeparttable}
+\end{table} \begin{table}[!h]
+\centering
+\begin{tabular}{lll}
+\toprule
+\multicolumn{3}{c}{Random Effects} \\
+\cmidrule(l{3pt}r{3pt}){1-3}
+Group & Parameter & Std. Dev.\\
+\midrule
+\cellcolor{gray!6}{PID} & \cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{12.797}\\
+Residual &  & 8.425\\
+\bottomrule
+\end{tabular}
+\end{table} \begin{table}[!h]
+\centering
+\begin{tabular}{lrl}
+\toprule
+\multicolumn{3}{c}{Grouping Variables} \\
+\cmidrule(l{3pt}r{3pt}){1-3}
+Group & \# groups & ICC\\
+\midrule
+\cellcolor{gray!6}{PID} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0.698}\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# generate 95\% parametric bootstrap CIs (and save them as a csv{-}file):}
+\CommentTok{\# write.csv(confint(lmer(thermometerDutch\_1\textasciitilde{}1 + (1|PID),data=dtWorker$full),}
+\CommentTok{\#                  method="boot",nsim=1000,}
+\CommentTok{\#                  parallel = "multicore", ncpus = 4, seed = 42),}
+\CommentTok{\#          "output/tables/ML{-}Null{-}CI.csv")}
+
+\CommentTok{\# Save variances}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull }\OtherTok{\textless{}{-}} 
+  \FunctionTok{VarCorr}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmeAttNull) }\CommentTok{\# save variances}
+\CommentTok{\# The estimate of (between{-}group or Intercept variance, tau\_\{00\}\^{}2):}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{tauAttNull }\OtherTok{\textless{}{-}} 
+  \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{])}
+\CommentTok{\# and the estimate of (within{-}group or residual variance, sigma\^{}2) is:}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{sigmaAttNull }\OtherTok{\textless{}{-}} 
+  \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{2}\NormalTok{])}
+\CommentTok{\# The ICC estimate (between/between+within) is:}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{IccAttNull }\OtherTok{\textless{}{-}}
+\NormalTok{  (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{/}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{+} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{2}\NormalTok{])))}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{IccPercAttNull }\OtherTok{\textless{}{-}}
+\NormalTok{  ((}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{/}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{+} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{2}\NormalTok{])))) }\SpecialCharTok{*} \DecValTok{100}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# Create and save Model}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmeInterceptAttType }\OtherTok{\textless{}{-}}
+  \FunctionTok{lme}\NormalTok{(}
+\NormalTok{    thermometerDutch\_1 }\SpecialCharTok{\textasciitilde{}}\NormalTok{ OutgroupInteraction }\SpecialCharTok{+}\NormalTok{ NonOutgroupInteraction,}
+    \AttributeTok{random =}  \SpecialCharTok{\textasciitilde{}} \DecValTok{1} \SpecialCharTok{|}\NormalTok{ PID,}
+    \AttributeTok{data =}\NormalTok{ dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerInteractionType}
+\NormalTok{  )}
+
+\CommentTok{\# Get summary with p{-}values (Satterthwaite\textquotesingle{}s method)}
+\FunctionTok{summ}\NormalTok{(}
+\NormalTok{  mdlWorker}\SpecialCharTok{$}\NormalTok{lmerInterceptAttType }\OtherTok{\textless{}{-}} \FunctionTok{lmer}\NormalTok{(}
+\NormalTok{    thermometerDutch\_1 }\SpecialCharTok{\textasciitilde{}}\NormalTok{ OutgroupInteraction }\SpecialCharTok{+}\NormalTok{ NonOutgroupInteraction }\SpecialCharTok{+}\NormalTok{ (}\DecValTok{1} \SpecialCharTok{|}\NormalTok{ PID),}
+    \AttributeTok{data =}\NormalTok{ dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerInteractionType}
+\NormalTok{  ),}
+  \AttributeTok{confint =} \ConstantTok{TRUE}\NormalTok{,}
+  \AttributeTok{digits =} \DecValTok{3}\NormalTok{,}
+  \AttributeTok{center =} \ConstantTok{FALSE}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}[!h]
+\centering
+\begin{tabular}{lr}
+\toprule
+\cellcolor{gray!6}{Observations} & \cellcolor{gray!6}{1225}\\
+Dependent variable & thermometerDutch\_1\\
+\cellcolor{gray!6}{Type} & \cellcolor{gray!6}{Mixed effects linear regression}\\
+\bottomrule
+\end{tabular}
+\end{table} \begin{table}[!h]
+\centering
+\begin{tabular}{lr}
+\toprule
+\cellcolor{gray!6}{AIC} & \cellcolor{gray!6}{8788.218}\\
+BIC & 8813.771\\
+\cellcolor{gray!6}{Pseudo-R² (fixed effects)} & \cellcolor{gray!6}{0.006}\\
+Pseudo-R² (total) & 0.703\\
+\bottomrule
+\end{tabular}
+\end{table} \begin{table}[!h]
+\centering
+\begin{threeparttable}
+\begin{tabular}{lrrrrrr}
+\toprule
+\multicolumn{7}{c}{Fixed Effects} \\
+\cmidrule(l{3pt}r{3pt}){1-7}
+  & Est. & 2.5\% & 97.5\% & t val. & d.f. & p\\
+\midrule
+\cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{70.343} & \cellcolor{gray!6}{65.002} & \cellcolor{gray!6}{75.683} & \cellcolor{gray!6}{25.814} & \cellcolor{gray!6}{22.897} & \cellcolor{gray!6}{0.000}\\
+OutgroupInteractionYes & 2.477 & 1.364 & 3.589 & 4.365 & 1204.135 & 0.000\\
+\cellcolor{gray!6}{NonOutgroupInteractionyes} & \cellcolor{gray!6}{0.427} & \cellcolor{gray!6}{-0.683} & \cellcolor{gray!6}{1.538} & \cellcolor{gray!6}{0.754} & \cellcolor{gray!6}{1204.911} & \cellcolor{gray!6}{0.451}\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item  p values calculated using Satterthwaite d.f. 
+\end{tablenotes}
+\end{threeparttable}
+\end{table} \begin{table}[!h]
+\centering
+\begin{tabular}{lll}
+\toprule
+\multicolumn{3}{c}{Random Effects} \\
+\cmidrule(l{3pt}r{3pt}){1-3}
+Group & Parameter & Std. Dev.\\
+\midrule
+\cellcolor{gray!6}{PID} & \cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{12.811}\\
+Residual &  & 8.362\\
+\bottomrule
+\end{tabular}
+\end{table} \begin{table}[!h]
+\centering
+\begin{tabular}{lrl}
+\toprule
+\multicolumn{3}{c}{Grouping Variables} \\
+\cmidrule(l{3pt}r{3pt}){1-3}
+Group & \# groups & ICC\\
+\midrule
+\cellcolor{gray!6}{PID} & \cellcolor{gray!6}{23} & \cellcolor{gray!6}{0.701}\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{lmerInterceptAttTypeCI }\OtherTok{\textless{}{-}} \FunctionTok{confint}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmerInterceptAttType)}
+
+\CommentTok{\# Generate 95\% parametric bootstrap CIs (and save them as a csv{-}file):}
+\CommentTok{\# write.csv(confint(lmer(thermometerDutch\_1 \textasciitilde{} Contact\_dum + inNonDutch + (1|PID),data=dtWorker$full),}
+\CommentTok{\#                  method="boot",nsim=1000, parallel = "multicore",}
+\CommentTok{\#                  ncpus = 4, seed = 42),}
+\CommentTok{\#          "output/tables/ML{-}Inter{-}CI.csv")}
+
+\CommentTok{\# Compare new model to previous step}
+\FunctionTok{anova}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmeAttNull, }
+\NormalTok{      mdlWorker}\SpecialCharTok{$}\NormalTok{lmeInterceptAttType) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{as.data.frame}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{call) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate}\NormalTok{(}
+    \AttributeTok{L.Ratio =} \FunctionTok{round}\NormalTok{(L.Ratio, }\DecValTok{3}\NormalTok{),}
+    \StringTok{\textasciigrave{}}\AttributeTok{p{-}value}\StringTok{\textasciigrave{}} \OtherTok{=} \FunctionTok{ifelse}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{p{-}value}\StringTok{\textasciigrave{}}\SpecialCharTok{\textgreater{}=}\NormalTok{.}\DecValTok{001}\NormalTok{, }\FunctionTok{round}\NormalTok{(}\StringTok{\textasciigrave{}}\AttributeTok{p{-}value}\StringTok{\textasciigrave{}}\NormalTok{, }\DecValTok{3}\NormalTok{), }\StringTok{"\textless{} .001"}\NormalTok{)}
+\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{replace}\NormalTok{(}\FunctionTok{is.na}\NormalTok{(.), }\StringTok{""}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{add\_rownames}\NormalTok{(., }\AttributeTok{var =} \StringTok{"Description"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{Description =} \FunctionTok{gsub}\NormalTok{(}\StringTok{".*}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{$"}\NormalTok{, }\StringTok{""}\NormalTok{, Description)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kbl}\NormalTok{(}
+\NormalTok{    .,}
+    \AttributeTok{caption =} \StringTok{"Worker: Model Comparison"}\NormalTok{,}
+    \AttributeTok{format =} \StringTok{"latex"}\NormalTok{,}
+    \AttributeTok{linesep =} \StringTok{""}\NormalTok{,}
+    \AttributeTok{booktabs =}\NormalTok{ T,}
+    \AttributeTok{align =} \FunctionTok{rep}\NormalTok{(}\StringTok{"c"}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(.)),}
+    \AttributeTok{digits =} \DecValTok{3}
+\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{position =} \StringTok{"left"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}
+
+\caption{\label{tab:workerModelInterceptAttType}Worker: Model Comparison}
+\begin{tabular}[t]{ccccccccc}
+\toprule
+Description & Model & df & AIC & BIC & logLik & Test & L.Ratio & p-value\\
+\midrule
+lmeAttNull & 1 & 3 & 8806 & 8821 & -4400 &  &  & \\
+lmeInterceptAttType & 2 & 5 & 8788 & 8814 & -4389 & 1 vs 2 & 21.663 & < .001\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# Save variances}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varInterceptAttType }\OtherTok{\textless{}{-}} 
+\NormalTok{  lme4}\SpecialCharTok{::}\FunctionTok{VarCorr}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{lmeInterceptAttType)}
+
+\CommentTok{\# The estimate of between{-}group (or Intercept variance) explained:}
+\CommentTok{\# Variance Explained = 1 – (Var with Predictor/Var without Predictor)}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varBtwInterceptAttType }\OtherTok{\textless{}{-}}
+  \DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varInterceptAttType[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{/} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]))}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varBtwPercInterceptAttType }\OtherTok{\textless{}{-}}
+\NormalTok{  (}\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varInterceptAttType[}\DecValTok{1}\NormalTok{]) }\SpecialCharTok{/} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{1}\NormalTok{]))) }\SpecialCharTok{*} \DecValTok{100}
+\CommentTok{\# and the estimate of within{-}group (or residual variance) explained is:}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varWithinInterceptAttType }\OtherTok{\textless{}{-}}
+  \DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varInterceptAttType[}\DecValTok{2}\NormalTok{]) }\SpecialCharTok{/} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{2}\NormalTok{]))}
+\NormalTok{mdlWorker}\SpecialCharTok{$}\NormalTok{varWithinPercInterceptAttType }\OtherTok{\textless{}{-}}
+\NormalTok{  (}\DecValTok{1} \SpecialCharTok{{-}}\NormalTok{ (}\FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varInterceptAttType[}\DecValTok{2}\NormalTok{]) }\SpecialCharTok{/} \FunctionTok{as.numeric}\NormalTok{(mdlWorker}\SpecialCharTok{$}\NormalTok{varAttNull[}\DecValTok{2}\NormalTok{]))) }\SpecialCharTok{*} \DecValTok{100}
+\end{Highlighting}
+\end{Shaded}
+
+We additionally used a multilevel regression to check whether having an
+interaction with an outgroup member had a situational (i.e.,
+contemporaneous) effect within the participants. We find that having an
+outgroup interaction is indeed associated with significantly more
+positive outgroup attitudes within the participants (\textit{b} = 2.48,
+\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}1.3644, 3.5884{]}), even after controlling for having
+an interaction with a non-Dutch (which did not relate to outgroup
+attitudes independently; For full results see Online Supplementary
+Materials B).
 

### 2021-10-25 Methods-and-Results.Rmd
r output removed

@@
 
-```{r WorkerFreqAttCor}
+```{r WorkerFreqAttCor, include=FALSE}
 # correlation panel
@@
 
-```{r workerModelOlsAttFreqQual}
+```{r workerModelOlsAttFreqQual, include=FALSE}
 # create list to store Worker models
@@
 
-```{r workerModelMLAttNull}
+```{r workerModelMLAttNull, include=FALSE}
 # Create and save Model
@@
 ```
-```{r workerModelInterceptAttType}
+```{r workerModelInterceptAttType, include=FALSE}
 # Create and save Model

### 2021-10-25 Methods-and-Results.tex
r output removed

--- 2021-10-25 Methods-and-Results.tex
@@
 
+We tested the most general contact hypothesis in two steps. First, we
+assessed whether more intergroup interactions were related to to more
+positive outgroup attitudes. Second, we tested whether a potential
+positive effect on outgroup attitudes depended on the interaction
+quality (jointly with the number of interactions). We find that neither
+the number of interactions nor the number of daily diary responses with
+an interaction were significantly related with the average outgroup
+attitudes. This is to say that within our data, participants with more
+outgroup interactions did not have significantly more positive outgroup
+attitudes. This might be due to the aggregation within the participants
+or the small sample size of between participant data. Nonetheless, the
+aggregate data does not support the notion that simply having more
+interactions with an outgroup results in more positive outgroup
+attitudes.
+
+However, despite the missing relationship with the number of
+interactions, we find a medium sized correlation between the
+participants' Average Interaction Quality and their Average Outgroup
+Attitudes. Thus within our data participants with a higher quality
+outgroup interactions also held more positive attitudes towards that
+group. And when considering the number of interactions and average
+interaction quality jointly in a linear regression, we additionally find
+a statistically significant interaction term (\textit{b} = -0.05,
+\textit{t}(17) = -2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34).
+Looking at a floodlight analysis of the effect, we find that in our
+sample with an increasing number of interactions the positive effect of
+average interaction quality becomes weaker. However, it should be noted
+that this is based on data aggregating all within participant nuances
+and is only the date of 21 people.
+
+We additionally used a multilevel regression to check whether having an
+interaction with an outgroup member had a situational (i.e.,
+contemporaneous) effect within the participants. We find that having an
+outgroup interaction is indeed associated with significantly more
+positive outgroup attitudes within the participants (\textit{b} = 2.48,
+\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}1.3644, 3.5884{]}), even after controlling for having
+an interaction with a non-Dutch (which did not relate to outgroup
+attitudes independently; For full results see Online Supplementary
+Materials B).
+
 \paragraph{Core Need}

### 2021-10-25 Methods-and-Results.Rmd
AOT-P contact H. conclusion added

@@
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (\textit{b} = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","Value"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmeInterceptAttType$fixDF$X["OutgroupInteractionYes"] %>% as.numeric`) = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","t-value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} `r ifelse(coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"]<.001, "< .001", paste0("= ", coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"] %>% round(3) %>% format(nsmall=3)))`, \textit{95\%CI}[`r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "2.5 %"]`, `r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "97.5 %"]`]), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (\textit{b} = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","Value"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmeInterceptAttType$fixDF$X["OutgroupInteractionYes"] %>% as.numeric`) = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","t-value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} `r ifelse(coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"]<.001, "< .001", paste0("= ", coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"] %>% round(3) %>% format(nsmall=3)))`, \textit{95\%CI}[`r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "2.5 %"] %>% round(2) %>% format(nsmall=2)`, `r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "97.5 %"] %>% round(2) %>% format(nsmall=2)`]), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
+Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants, keeping in mind that the between-participant effects in the aggregated form are based in a small sample size.
 

### 2021-10-25 Methods-and-Results.tex
AOT-P contact H. conclusion added

@@
 \textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}1.3644, 3.5884{]}), even after controlling for having
-an interaction with a non-Dutch (which did not relate to outgroup
-attitudes independently; For full results see Online Supplementary
-Materials B).
+\textit{95\%CI}{[}1.36, 3.59{]}), even after controlling for having an
+interaction with a non-Dutch (which did not relate to outgroup attitudes
+independently; For full results see Online Supplementary Materials B).
+Thus, in our first data we find mixed results, where outgroup contacts
+show a positive effect on outgroup attitudes in the moment but these
+results do not translate into average differences between participants,
+keeping in mind that the between-participant effects in the aggregated
+form are based in a small sample size.
 

### 2021-10-25 Methods-and-Results.Rmd
paragraph check

--- 2021-10-25 Methods-and-Results.Rmd
@@
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (\textit{b} = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","Value"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmeInterceptAttType$fixDF$X["OutgroupInteractionYes"] %>% as.numeric`) = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","t-value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} `r ifelse(coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"]<.001, "< .001", paste0("= ", coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"] %>% round(3) %>% format(nsmall=3)))`, \textit{95\%CI}[`r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "2.5 %"]`, `r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "97.5 %"]`]), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (\textit{b} = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","Value"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmeInterceptAttType$fixDF$X["OutgroupInteractionYes"] %>% as.numeric`) = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","t-value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} `r ifelse(coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"]<.001, "< .001", paste0("= ", coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"] %>% round(3) %>% format(nsmall=3)))`, \textit{95\%CI}[`r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "2.5 %"] %>% round(2) %>% format(nsmall=2)`, `r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "97.5 %"] %>% round(2) %>% format(nsmall=2)`]), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance.
+This is unusual because this might indicate the the effect is very consistent across participants.
+However, this might also be the case due to a small number of participants, or other measurement issues.}.
+Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants, keeping in mind that the between-participant analyses in the aggregated form are based in a small sample size.
 
-\paragraph{Core Need}
+\paragraph{Core Need}t be explained by whether or not the interaction fulfilled the person's core situational need.
+This should, in turn, be due to a higher perceived interaction quality.
+We will this sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
 

### 2021-10-25 Methods-and-Results.tex
paragraph check

--- 2021-10-25 Methods-and-Results.tex
@@
 \textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}1.3644, 3.5884{]}), even after controlling for having
-an interaction with a non-Dutch (which did not relate to outgroup
-attitudes independently; For full results see Online Supplementary
-Materials B).
+\textit{95\%CI}{[}1.36, 3.59{]}), even after controlling for having an
+interaction with a non-Dutch (which did not relate to outgroup attitudes
+independently; For full results see Online Supplementary Materials
+B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance.
+This is unusual because this might indicate the the effect is very consistent across participants.
+However, this might also be the case due to a small number of participants, or other measurement issues.}.
+Thus, in our first data we find mixed results, where outgroup contacts
+show a positive effect on outgroup attitudes in the moment but these
+results do not translate into average differences between participants,
+keeping in mind that the between-participant analyses in the aggregated
+form are based in a small sample size.
 
 \paragraph{Core Need}
+
+t be explained by whether or not the interaction fulfilled the person's
+core situational need. This should, in turn, be due to a higher
+perceived interaction quality. We will this sequentially test whether
+the fulfillment of the core need during an interaction is (1) related to
+more positive outgroup attitudes, (2) higher perceived interaction
+quality, and (3) whether the variance explained by the core need is
+assumed by the perceived interaction quality if considered jointly.
 

### 2021-10-25 Methods-and-Results.Rmd
effect size trials

@@
   )
+dtWorkerSupp$workerOutWithinBetween <-
+  MlTraitState(
+    data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection =
+      c(
+        "keyMotiveFulfilled",
+        "competence.daily.all",
+        "autonomy.daily.all",
+        "relatedness.daily.all",
+        "thermometerDutch_1",
+        "keymotive_fulfillemt_1",
+        "competence_1",
+        "autonomy_1",
+        "relatedness_1"
+      )
+  )
+
 ```
@@
 
-\paragraph{Core Need}t be explained by whether or not the interaction fulfilled the person's core situational need.
+\paragraph{Core Need}The main proposal of our article is that the success of an outgroup interaction might be explained by whether or not the interaction fulfilled the person's core situational need.
 This should, in turn, be due to a higher perceived interaction quality.
 We will this sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+
+```{r workerOutModelMLAttNull, include=FALSE}
+# create empty list to organize models
+mdlWorkerOut <- 
+  list(
+    Att = list(),
+    Qlt = list()
+  )
+
+# Create and save Model
+mdlWorkerOut$Att$lmerNull <-
+  lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID), 
+             data = dtWorkerSupp$workerOutgroupInteraction) # use optim if it does not converge
+mdlWorkerOut$Att$lmeNull <-
+  lme(
+    thermometerDutch_1 ~ 1,
+    random = ~ 1 | PID,
+    data = dtWorkerSupp$workerOutgroupInteraction,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.ML.r) #or with the lme function
+summ(mdlWorkerOut$Att$lmerNull, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=dtWorker$full),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlWorkerOut$Att$varNull <- 
+  VarCorr(mdlWorkerOut$Att$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlWorkerOut$Att$tauNull <- 
+  as.numeric(mdlWorkerOut$Att$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlWorkerOut$Att$sigmaNull <- 
+  as.numeric(mdlWorkerOut$Att$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlWorkerOut$Att$IccNull <-
+  (as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2])))
+mdlWorkerOut$Att$IccPercNull <-
+  ((as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2])))) * 100
+```
+```{r workerOutModelInterceptAttCore, include=FALSE}
+# Create and save Model
+mdlWorkerOut$Att$lmeInterceptCore <-
+  lme(
+    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc,
+    random = ~ 1 | PID,
+    data = dtWorkerSupp$workerOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlWorkerOut$Att$lmerInterceptCore <-
+    lmer(
+      thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + (1 | PID),
+      data = dtWorkerSupp$workerOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorkerOut$Att$lmeNull, 
+      mdlWorkerOut$Att$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Att$varInterceptCore <-
+  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCore)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorkerOut$Att$varBtwInterceptCore <-
+  1 - (mdlWorkerOut$Att$varInterceptCore["(Intercept)", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varNull["(Intercept)", "Variance"] %>% as.numeric)
+mdlWorkerOut$Att$varBtwPercInterceptCore <-
+  (1 - (mdlWorkerOut$Att$varInterceptCore["(Intercept)", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varNull["(Intercept)", "Variance"] %>% as.numeric)) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorkerOut$Att$varWithinInterceptCore <-
+  1 - (mdlWorkerOut$Att$varInterceptCore["Residual", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varNull["Residual", "Variance"] %>% as.numeric)
+mdlWorkerOut$Att$varWithinPercInterceptCore <-
+  (1 - (mdlWorkerOut$Att$varInterceptCore["Residual", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varNull["Residual", "Variance"] %>% as.numeric)) * 100
+```
+```{r workerOutModelSlopesAttCore, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlWorkerOut$Att$lmeSlopesCore <-
+  lme(
+    thermometerDutch_1 ~
+      keymotive_fulfillemt_1_cwc,
+    random = ~ 1 + keymotive_fulfillemt_1_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtWorkerSupp$workerOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlWorkerOut$Att$lmerSlopesCore <- lmer(
+    thermometerDutch_1 ~
+      keymotive_fulfillemt_1_cwc +
+      (1 + keymotive_fulfillemt_1_cwc | PID),
+    data = dtWorkerSupp$workerOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlWorkerOut$Att$lmerSlopesCoreCI <- confint(mdlWorkerOut$Att$lmerSlopesCore)
+
+r2mlm::r2mlm(mdlWorkerOut$Att$lmerSlopesCore, bargraph = TRUE)
+mitml::multilevelR2(mdlWorkerOut$Att$lmerSlopesCore)
+sjstats::r2(mdlWorkerOut$Att$lmerSlopesCore, mdlWorkerOut$Att$lmerNull)
+performance::r2(mdlWorkerOut$Att$lmerSlopesCore)
+performance::model_performance(mdlWorkerOut$Att$lmerSlopesCore)
+performance::compare_performance(mdlWorkerOut$Att$lmerNull, mdlWorkerOut$Att$lmerSlopesCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorkerOut$Att$lmeNull, 
+      mdlWorkerOut$Att$lmeInterceptCore, 
+      mdlWorkerOut$Att$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Att$varSlopesCore <- 
+  lme4::VarCorr(mdlWorkerOut$Att$lmerSlopesCore)
+
+# The estimate of between-group (or Intercept variance) explained:
+# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
+mdlWorkerOut$Att$varBtwSlopesCore <-
+  1 - (mdlWorkerOut$Att$varSlopesCore["(Intercept)", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varInterceptCore["(Intercept)", "Variance"] %>% as.numeric)
+mdlWorkerOut$Att$varBtwPercSlopesCore <-
+  (1 - (mdlWorkerOut$Att$varSlopesCore["(Intercept)", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varInterceptCore["(Intercept)", "Variance"] %>% as.numeric)) * 100
+# and the estimate of within-group (or residual variance) explained is:
+mdlWorkerOut$Att$varWithinSlopesCore <-
+  1 - (mdlWorkerOut$Att$varSlopesCore["Residual", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varInterceptCore["Residual", "Variance"] %>% as.numeric)
+mdlWorkerOut$Att$varWithinPercSlopesCore <-
+  (1 - (mdlWorkerOut$Att$varSlopesCore["Residual", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varInterceptCore["Residual", "Variance"] %>% as.numeric)) * 100
+
+# Assumption Checks:
+mdlWorkerOut$Att$diagSlopesCore <- 
+  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlWorkerOut$Att$diagSlopesCore[[1]],
+  mdlWorkerOut$Att$diagSlopesCore[[2]]$`PID`,
+  mdlWorkerOut$Att$diagSlopesCore[[3]],
+  mdlWorkerOut$Att$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlWorkerOut$Att$predSlopesCore <- 
+  dtWorkerSupp$workerOutWithinBetween %>%
+  select(thermometerDutch_1, session, PID) %>% 
+  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCore,
+                           dtWorkerSupp$workerOutWithinBetween,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlWorkerOut$Att$predPltSlopesCore <-
+    ggplot(data = mdlWorkerOut$Att$predSlopesCore, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCore.png",
+  mdlWorkerOut$Att$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
 

### 2021-10-25 scripts/functions/MlCorMat.R

@@ -206,19 +206,39 @@ MlTraitState <-
     # calculate trait scores (participant means)
     data <- 
       data %>%
-      select(id, selection) %>%
+      #select(id, selection) %>%
+      mutate_at(selection, list(gm = ~mean(., na.rm=TRUE))) %>% # grand mean
+      mutate_at(selection, list(gmc = ~.-mean(., na.rm=TRUE))) %>% # grand mean centered
       group_by_at(vars(matches(id))) %>%
-      mutate_at(selection, list(trait = ~mean(., na.rm=TRUE))) %>%
+      mutate_at(selection, list(cm = ~mean(., na.rm=TRUE))) %>% # cluster mean
       ungroup 
     
+    # center within cluster
     data <-
       map_dfc(selection,
               ~ data %>%
                 transmute(
-                  !!str_c(.x, '_state') :=
-                    !!rlang::sym(.x)-!!rlang::sym(str_c(.x, "_trait"))
+                  !!str_c(.x, '_cwc') :=
+                    !!rlang::sym(.x)-!!rlang::sym(str_c(.x, "_cm"))
                 )) %>%
       bind_cols(data, .)
     
+    # cluster mean centered
+    data <- 
+      data %>%
+      mutate_at(paste0(selection, "_cm"), list(c = ~.-mean(., na.rm=TRUE))) # grand mean
+    
     data
   }
+
+
+var_reduction = function(m0, m1){
+  library(tidyverse)
+  lme4::VarCorr(m0) %>% 
+    as.data.frame %>% 
+    select(grp, var_m0 = vcov) %>% 
+    left_join(lme4::VarCorr(m1) %>% 
+                as.data.frame %>% 
+                select(grp, var_m1 = vcov)) %>% 
+    mutate(var_red = 1 - var_m1 / var_m0) 
+}

### 2021-10-25 manuscript.tex
notes added
Updates from Overleaf

@@
 One of the main ameliorations proposed by social psychologists has been positive intergroup contact.
-Based on Allport's (\citeyear{Allport1954b}) contact hypothesis, a plethora of studies and interventions have worked on bringing different social groups together\footnote{Cite interventions of British ministries.}.
+Based on Allport's \citeyear{Allport1954b} contact hypothesis, a plethora of studies and interventions have worked on bringing different social groups together\footnote{Cite interventions of British ministries.}.
+% Yet, despite ...
+
+In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group \citep[e.g.,][]{Hewstone1996, Pettigrew1998}.
+A key condition for these contact benefits, has been that the interaction is indeed perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact \citep[e.g.,][]{MacInnis2015}.
+It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact \citep[Allport's Optimal Contact conditions,][]{Allport1954b}.
+And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met.
+However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met.
+It, thus, remains unclear why and how exactly Allport's conditions work.
+
+In this article, we propose that Allport's optimal contact conditions are effective in creating positive contact because they constitute common psychological needs of the interacting individuals.
+If this is indeed the case, the impact of fulfilling other fundamental needs should produce similar beneficial contact results.
+And more importantly, the satisfaction of key situation needs during the interaction should predict the positive contact effects most strongly.
+
+\faKeyboard\ We should probably add a short section on past literature that has examined psychological needs in intergroup contact in general \citep[e.g.,][]{Shnabel2008} as well as for particular groups, including migrants \citep[e.g.,][]{Celebi2017}.
+
+\noindent We should probably also include:
+\begin{displayquote}
+    Psychological needs might “explain the asymmetry of experiences and outcomes in intergroup interactions and identify an essential element for interventions: To achieve truly constructive intergroup relations, it is important that intergroup exchanges meet the psychological needs of both majority- and minority-group members” \\
+    \hfill --- \citep[][p. 611]{Dovidio2017}
+\end{displayquote}
+
+We probably need to note that there are really good papers on the likely mechanisms of intergroup contact \citep[e.g.,][]{Brown2005}. But they don't discuss Allport's conditions.
+
+Plus, recent work Nurit Shnabel.
 
 \section{The Present Research}
+\faKeyboard\ To be written out.
 
@@
 This design allowed us to test whether intergroup interactions and the fulfillment of psychological needs could jointly predict the development of attitudes towards the outgroup (i.e., the Dutch host society).
+
+Based on this we formulated four main hypotheses:
+
+\begin{hyp}[H\ref{hyp:contact}] \label{hyp:contact}
+Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
+\end{hyp}
+
+\begin{subhyp}[H\ref{hyp:contactFreq}] \label{hyp:contactFreq}
+\addtolength{\leftskip}{2.5em}
+Participants with more intergroup interactions should have a more favorable outgroup attitudes.
+\end{subhyp}
+
+\begin{subhyp}[H\ref{hyp:contactDummy}] \label{hyp:contactDummy}
+\addtolength{\leftskip}{2.5em}
+Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
+\end{subhyp}
+
+\begin{subhyp}[H\ref{hyp:contactFreqQual}] \label{hyp:contactFreqQual}
+\addtolength{\leftskip}{2.5em}
+Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
+\end{subhyp}
+
+\begin{hyp}[H\ref{hyp:AllportsConditions}] \label{hyp:AllportsConditions}
+Based on Allport's optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+\end{hyp}
+
+\setcounter{subhyp}{0}
+\begin{subhyp}[H\ref{hyp:AllportsPred}] \label{hyp:AllportsPred}
+\addtolength{\leftskip}{2.5em}
+Based on Allport's optimal contact conditions, outgroup attitudes should be more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
+\end{subhyp}
+
+\begin{subhyp}[H\ref{hyp:AllportsQuality}] \label{hyp:AllportsQuality}
+\addtolength{\leftskip}{2.5em}
+Based on past research on the role of interaction quality, interaction quality should be more perceived as more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
+\end{subhyp}
+
+\begin{subhyp}[H\ref{hyp:AllportsQualityMediation}] \label{hyp:AllportsQualityMediation}
+\addtolength{\leftskip}{2.5em}
+Based on past research on the role of interaction quality, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extend be assumed by interaction quality.
+\end{subhyp}
+
+\begin{hyp}[H\ref{hyp:keyNeed}] \label{hyp:keyNeed}
+Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+\end{hyp}
+
+\setcounter{subhyp}{0}
+\begin{subhyp}[H\ref{hyp:keyNeedPred}] \label{hyp:keyNeedPred}
+\addtolength{\leftskip}{2.5em}
+Outgroup attitudes should be more favorable after intergroup interactions with high key need fulfillment.
+\end{subhyp}
+
+\begin{subhyp}[H\ref{hyp:keyNeedQual}] \label{hyp:keyNeedQual}
+\addtolength{\leftskip}{2.5em}
+Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
+\end{subhyp}
+
+\begin{subhyp}[H\ref{hyp:keyNeedMediation}] \label{hyp:keyNeedMediation}
+\addtolength{\leftskip}{2.5em}
+The variance explained in outgroup attitudes by key need fulfillment should to a large extend be assumed by interaction quality.
+\end{subhyp}
+
+\begin{subhyp}[H\ref{hyp:keyNeedContactType}] \label{hyp:keyNeedContactType}
+\addtolength{\leftskip}{2.5em}
+The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
+Thus, the effect of key need fulfillment on outgroup attitudes should stronger for intergroup interact than for ingroup interactions.
+\end{subhyp}
+
+\begin{subhyp}[H\ref{hyp:keyNeedSDT}] \label{hyp:keyNeedSDT}
+\addtolength{\leftskip}{2.5em}
+The effect of key need fulfillment on outgroup attitudes should be persist even when taking other fundamental psychological needs into account.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
+\end{subhyp}
+
+\begin{hyp}[H\ref{hyp:comparison}] \label{hyp:comparison}
+Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict outgroup attitudes at least as well as Allport's conditions.
+\end{hyp}
+
+\setcounter{subhyp}{0}
+\begin{subhyp}[H\ref{hyp:compModel}] \label{hyp:compModel}
+\addtolength{\leftskip}{2.5em}
+The need model (H\ref{hyp:keyNeedPred}) should predict more variance in outgroup attitudes than the model based on Allport's conditions (H\ref{hyp:AllportsPred}).
+\end{subhyp}
+
+\begin{subhyp}[H\ref{hyp:compTogether}] \label{hyp:compTogether}
+\addtolength{\leftskip}{2.5em}
+The  effect of key need fulfillment on outgroup attitudes should  persist even when taking other Allport's conditions into account.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for equal status, common goals, collaboration, and structural support.
+\end{subhyp}
+
+\faKeyboard\ all assumptions were fine (see Online Supplementary Materials B).
 

### 2021-10-26 Methods-and-Results.Rmd
AOT-P core need analyses added

@@
         "autonomy_1",
-        "relatedness_1"
+        "relatedness_1", 
+        "quality_overall_1"
       )
@@
         "keyMotiveFulfilled",
-        "competence.daily.all",
-        "autonomy.daily.all",
-        "relatedness.daily.all",
         "thermometerDutch_1",
@@
         "autonomy_1",
-        "relatedness_1"
+        "relatedness_1", 
+        "quality_overall_1"
       )
   )
-
 ```
@@
                              alpha = .05)
+
 ```
@@
   lme4::VarCorr(mdlWorker$lmeInterceptAttType)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorker$varBtwInterceptAttType <-
-  1 - (as.numeric(mdlWorker$varInterceptAttType[1]) / as.numeric(mdlWorker$varAttNull[1]))
-mdlWorker$varBtwPercInterceptAttType <-
-  (1 - (as.numeric(mdlWorker$varInterceptAttType[1]) / as.numeric(mdlWorker$varAttNull[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorker$varWithinInterceptAttType <-
-  1 - (as.numeric(mdlWorker$varInterceptAttType[2]) / as.numeric(mdlWorker$varAttNull[2]))
-mdlWorker$varWithinPercInterceptAttType <-
-  (1 - (as.numeric(mdlWorker$varInterceptAttType[2]) / as.numeric(mdlWorker$varAttNull[2]))) * 100
 ```
@@
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (\textit{b} = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","Value"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmeInterceptAttType$fixDF$X["OutgroupInteractionYes"] %>% as.numeric`) = `r coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","t-value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} `r ifelse(coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"]<.001, "< .001", paste0("= ", coef(summary(mdlWorker$lmeInterceptAttType))["OutgroupInteractionYes","p-value"] %>% round(3) %>% format(nsmall=3)))`, \textit{95\%CI}[`r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "2.5 %"] %>% round(2) %>% format(nsmall=2)`, `r mdlWorker$lmerInterceptAttTypeCI["OutgroupInteractionYes", "97.5 %"] %>% round(2) %>% format(nsmall=2)`]), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance.
 This is unusual because this might indicate the the effect is very consistent across participants.
@@
 
+mdlWorkerOut$Att$lmerInterceptCoreCI <- 
+  confint(mdlWorkerOut$Att$lmerInterceptCore)
+
 # Generate 95% parametric bootstrap CIs (and save them as a csv-file):
@@
     caption = "Worker: Model Comparison",
-    format = "html",
+    format = "latex",
     linesep = "",
@@
 
+# all variables standardized within PPT
+summ(
+  mdlWorkerOut$Att$lmerSlopesCoreZ <- lmer(
+    thermometerDutch_1_zwc ~
+      keymotive_fulfillemt_1_zwc +
+      (1 + keymotive_fulfillemt_1_zwc | PID),
+    data = dtWorkerSupp$workerOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# standardized coefficients
+stdCoef.merMod(mdlWorkerOut$Att$lmerSlopesCore)
+
+# 95%CIs
 mdlWorkerOut$Att$lmerSlopesCoreCI <- confint(mdlWorkerOut$Att$lmerSlopesCore)
 
+# Attempts at R^2
 r2mlm::r2mlm(mdlWorkerOut$Att$lmerSlopesCore, bargraph = TRUE)
 mitml::multilevelR2(mdlWorkerOut$Att$lmerSlopesCore)
-sjstats::r2(mdlWorkerOut$Att$lmerSlopesCore, mdlWorkerOut$Att$lmerNull)
 performance::r2(mdlWorkerOut$Att$lmerSlopesCore)
 performance::model_performance(mdlWorkerOut$Att$lmerSlopesCore)
-performance::compare_performance(mdlWorkerOut$Att$lmerNull, mdlWorkerOut$Att$lmerSlopesCore)
+performance::compare_performance(mdlWorkerOut$Att$lmerNull, 
+                                 mdlWorkerOut$Att$lmerInterceptCore, 
+                                 mdlWorkerOut$Att$lmerSlopesCore)
 
@@
 mdlWorkerOut$Att$varSlopesCore <- 
-  lme4::VarCorr(mdlWorkerOut$Att$lmerSlopesCore)
+  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCore)
 
@@
 
-- Att ~ Need & Qlt ~ Need
-- Att ~ Need + Qual
+```{r workerOutModelMLQltNull, include=FALSE}
+# Create and save Model
+mdlWorkerOut$Qlt$lmerNull <-
+  lme4::lmer(quality_overall_1 ~ 1 + (1 | PID), 
+             data = dtWorkerSupp$workerOutWithinBetween) # use optim if it does not converge
+mdlWorkerOut$Qlt$lmeNull <-
+  mdlWorkerOut$Qlt$lmeNull <-lme(
+    quality_overall_1 ~ 1,
+    random = ~ 1 | PID,
+    data = dtWorkerSupp$workerOutWithinBetween,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.Qual.ML.r) #or with the lme function
+summ(mdlWorkerOut$Qlt$lmerNull, digits = 3)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=workerOutgroupInteraction),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlWorkerOut$Qlt$varNull <- 
+  VarCorr(mdlWorkerOut$Qlt$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlWorkerOut$Qlt$tauNull <- 
+  as.numeric(mdlWorkerOut$Qlt$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlWorkerOut$Qlt$sigmaNull <- 
+  as.numeric(mdlWorkerOut$Qlt$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlWorkerOut$Qlt$IccNull <-
+  (as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2])))
+mdlWorkerOut$Qlt$IccPercNull <-
+  ((as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2])))) * 100
+```
+```{r workerOutModelInterceptQltCore, include=FALSE}
+# Create and save Model
+mdlWorkerOut$Qlt$lmeInterceptCore <-
+  lme(
+    quality_overall_1 ~ keymotive_fulfillemt_1_cwc,
+    random = ~ 1 | PID,
+    data = dtWorkerSupp$workerOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlWorkerOut$Qlt$lmerInterceptCore <-
+    lmer(
+      quality_overall_1 ~ keymotive_fulfillemt_1_cwc + (1 | PID),
+      data = dtWorkerSupp$workerOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlWorkerOut$Qlt$lmerInterceptCoreCI <- 
+  confint(mdlWorkerOut$Qlt$lmerInterceptCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(quality_overall_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorkerOut$Qlt$lmeNull, 
+      mdlWorkerOut$Qlt$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Qlt$varInterceptCore <-
+  lme4::VarCorr(mdlWorkerOut$Qlt$lmeInterceptCore)
+```
+```{r workerOutModelSlopesQltCore, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlWorkerOut$Qlt$lmeSlopesCore <-
+  lme(
+    quality_overall_1 ~
+      keymotive_fulfillemt_1_cwc,
+    random = ~ 1 + keymotive_fulfillemt_1_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtWorkerSupp$workerOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlWorkerOut$Qlt$lmerSlopesCore <-
+    lmer(
+      quality_overall_1 ~
+        keymotive_fulfillemt_1_cwc +
+        (1 + keymotive_fulfillemt_1_cwc | PID),
+      data = dtWorkerSupp$workerOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlWorkerOut$Qlt$lmerSlopesCoreCI <- 
+  confint(mdlWorkerOut$Qlt$lmerSlopesCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(mdlWorkerOut$Qlt$lmerSlopesCore,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorkerOut$Qlt$lmeNull, 
+      mdlWorkerOut$Qlt$lmeInterceptCore, 
+      mdlWorkerOut$Qlt$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Qlt$varSlopesCore <- 
+  lme4::VarCorr(mdlWorkerOut$Qlt$lmeSlopesCore)
+```
+```{r workerOutModelInterceptAttCoreQlt, include=FALSE}
+# Create and save Model
+mdlWorkerOut$Att$lmeInterceptCoreQlt <-
+  lme(
+    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + quality_overall_1_cwc,
+    random = ~ 1 | PID,
+    data = dtWorkerSupp$workerOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlWorkerOut$Att$lmerInterceptCoreQlt <-
+    lmer(
+      thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + quality_overall_1_cwc + (1 | PID),
+      data = dtWorkerSupp$workerOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlWorkerOut$Att$lmerInterceptCoreQltCI <- 
+  confint(mdlWorkerOut$Att$lmerInterceptCoreQlt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlWorkerOut$Att$lmeNull, 
+  mdlWorkerOut$Att$lmeInterceptCoreQlt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Att$varInterceptCoreQlt <-
+  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreQlt)
+```
+```{r workerOutModelSlopesAttCoreQlt, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlWorkerOut$Att$lmeSlopesCoreQlt <-
+  lme(
+    thermometerDutch_1 ~
+      keymotive_fulfillemt_1_cwc + quality_overall_1_cwc,
+    random = ~ 1 + keymotive_fulfillemt_1_cwc + quality_overall_1_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtWorkerSupp$workerOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlWorkerOut$Att$lmerSlopesCoreQlt <- lmer(
+    thermometerDutch_1 ~
+      keymotive_fulfillemt_1_cwc + quality_overall_1_cwc +
+      (1 + keymotive_fulfillemt_1_cwc + quality_overall_1_cwc | PID),
+    data = dtWorkerSupp$workerOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlWorkerOut$Att$lmerSlopesCoreQltCI <- 
+  confint(mdlWorkerOut$Att$lmerSlopesCoreQlt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlWorkerOut$Att$lmeNull,
+  mdlWorkerOut$Att$lmeInterceptCoreQlt,
+  mdlWorkerOut$Att$lmeSlopesCoreQlt
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Att$varSlopesCoreQlt <- 
+  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreQlt)
+
+# Assumption Checks:
+mdlWorkerOut$Att$diagSlopesCoreQlt <- 
+  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreQlt, type = "diag")
+grid.arrange(
+  mdlWorkerOut$Att$diagSlopesCoreQlt[[1]],
+  mdlWorkerOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
+  mdlWorkerOut$Att$diagSlopesCoreQlt[[3]],
+  mdlWorkerOut$Att$diagSlopesCoreQlt[[4]]
+)
+
+# Plot prediction model
+mdlWorkerOut$Att$predSlopesCoreQlt <- 
+  dtWorkerSupp$workerOutWithinBetween %>%
+  select(thermometerDutch_1, session, PID) %>% 
+  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreQlt,
+                           dtWorkerSupp$workerOutWithinBetween,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlWorkerOut$Att$predPltSlopesCoreQlt <-
+    ggplot(data = mdlWorkerOut$Att$predSlopesCoreQlt, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreQlt.png",
+  mdlWorkerOut$Att$predPltSlopesCoreQlt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We find that in the highest multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCore, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreCI, varName = "keymotive_fulfillemt_1_cwc")`) and also predicted higher perceived interaction quality (random intercept model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Qlt$lmeInterceptCore, lmerCI = mdlWorkerOut$Qlt$lmerInterceptCoreCI, varName = "keymotive_fulfillemt_1_cwc")`).
+However, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`).
+We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
+
+\faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?
 
 \paragraph{Robustness}
+
+\subparagraph{Interaction Type}
+
+\subparagraph{Other Needs}
+
+For full results see Online Supplementary Information B.
 

### 2021-10-26 Methods-and-Results.tex
AOT-P core need analyses added

@@
 outgroup interaction is indeed associated with significantly more
-positive outgroup attitudes within the participants (\textit{b} = 2.48,
-\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}1.36, 3.59{]}), even after controlling for having an
-interaction with a non-Dutch (which did not relate to outgroup attitudes
-independently; For full results see Online Supplementary Materials
+positive outgroup attitudes within the participants ( extit\{b\} = 2.48,
+t(1200) = 4.36, extit\{p\} = \textless{} .001, extit\{95\%CI{[}1.36,
+3.59{]}), even after controlling for having an interaction with a
+non-Dutch (which did not relate to outgroup attitudes independently; For
+full results see Online Supplementary Materials
 B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance.
@@
 
-t be explained by whether or not the interaction fulfilled the person's
-core situational need. This should, in turn, be due to a higher
-perceived interaction quality. We will this sequentially test whether
-the fulfillment of the core need during an interaction is (1) related to
-more positive outgroup attitudes, (2) higher perceived interaction
-quality, and (3) whether the variance explained by the core need is
-assumed by the perceived interaction quality if considered jointly.
+The main proposal of our article is that the success of an outgroup
+interaction might be explained by whether or not the interaction
+fulfilled the person's core situational need. This should, in turn, be
+due to a higher perceived interaction quality. We will this sequentially
+test whether the fulfillment of the core need during an interaction is
+(1) related to more positive outgroup attitudes, (2) higher perceived
+interaction quality, and (3) whether the variance explained by the core
+need is assumed by the perceived interaction quality if considered
+jointly.
 
-\begin{itemize}
-\tightlist
-\item
-  Att \textasciitilde{} Need \& Qlt \textasciitilde{} Need
-\item
-  Att \textasciitilde{} Need + Qual
-\end{itemize}
+We find that in the highest multilevel models, the fulfillment of core
+situational needs during outgroup contacts was associated with more
+positive outgroup attitudes (random slopes model; extit\{b\} = 0.17,
+t(365) = 2.93, extit\{p\} = = 0.004, extit\{95\%CI{[}0.06, 0.30{]}) and
+also predicted higher perceived interaction quality (random intercept
+model; extit\{b\} = 0.42, t(365) = 8.07, extit\{p\} = \textless{} .001,
+extit\{95\%CI{[}0.32, 0.52{]}). However, if we consider the influences
+of core need fulfillment and interaction quality on outgroup attitudes
+jointly, we find that virtually all variance is explained by perceived
+interaction quality (random slopes mode; extit\{b\} = 0.23, t(364) =
+4.22, extit\{p\} = \textless{} .001, extit\{95\%CI{[}0.12, 0.33{]}) and
+only little unique variance is still explained by core need fulfillment
+( extit\{b\} = 0.04, t(364) = 0.64, extit\{p\} = = 0.523,
+extit\{95\%CI{[}-0.08, 0.15{]}). We thus find support for our hypotheses
+and can conclude that in this data set the fulfillment of core
+situational needs had a significant influence on outgroup attitudes and
+that this effect is likely explained by its effect through perceived
+interaction quality.
+
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
 
 \paragraph{Robustness}
+
+\subparagraph{Interaction Type}
+
+\subparagraph{Other Needs}
+
+For full results see Online Supplementary Information B.
 

### 2021-10-26 scripts/functions/MlCorMat.R
Update MlCorMat.R

@@ -211,6 +211,7 @@ MlTraitState <-
       mutate_at(selection, list(gmc = ~.-mean(., na.rm=TRUE))) %>% # grand mean centered
       group_by_at(vars(matches(id))) %>%
       mutate_at(selection, list(cm = ~mean(., na.rm=TRUE))) %>% # cluster mean
+      mutate_at(selection, list(csd = ~sd(., na.rm=TRUE))) %>% # cluster sd
       ungroup 
     
     # center within cluster
@@ -220,6 +221,15 @@ MlTraitState <-
                 transmute(
                   !!str_c(.x, '_cwc') :=
                     !!rlang::sym(.x)-!!rlang::sym(str_c(.x, "_cm"))
+                )) %>%
+      bind_cols(data, .)
+    
+    data <-
+      map_dfc(selection,
+              ~ data %>%
+                transmute(
+                  !!str_c(.x, '_zwc') :=
+                    (!!rlang::sym(.x)-!!rlang::sym(str_c(.x, "_cm")))/!!rlang::sym(str_c(.x, "_csd"))
                 )) %>%
       bind_cols(data, .)
     
@@ -241,4 +251,38 @@ var_reduction = function(m0, m1){
                 as.data.frame %>% 
                 select(grp, var_m1 = vcov)) %>% 
     mutate(var_red = 1 - var_m1 / var_m0) 
+}
+
+stdCoef.merMod <- function(object) {
+  sdy <- sd(getME(object, "y"))
+  sdx <- apply(getME(object, "X"), 2, sd)
+  sc <- fixef(object) * sdx / sdy
+  se.fixef <- coef(summary(object))[, "Std. Error"]
+  se <- se.fixef * sdx / sdy
+  return(data.frame(stdcoef = sc, stdse = se))
+}
+
+MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
+  b <- coef(summary(lmeMdl))[varName,"Value"] %>% round(2) %>% format(nsmall=2)
+  df <- lmeMdl$fixDF$X[varName] %>% as.numeric
+  t <- coef(summary(lmeMdl))[varName,"t-value"] %>% round(2) %>% format(nsmall=2)
[…]

### 2021-10-26 Supplemental-Material-B-Annotated-Analysis.Rmd
re-render

@@
 The white point indicates the mean and the white center line indicates the median.
+
+<br/>
+
+<i class="fas fa-exclamation-circle"></i> Note. Multilevel effect size could be: 
+\begin{equation}
+(\#eq:MlEffectSize)
+f_b^2 = \frac{R_{ab}^2 - R_a^2}{1 - R_{ab}^2} \\
+R^2 = \frac{V_{null} - V_{model}}{V_{null}} \\
+f_b^2 = \frac{\frac{V_{null} - V_{ab}}{V_{null}} - \frac{V_{null} - V_{a}}{V_{null}}}{1 - \frac{V_{null} - V_{ab}}{V_{null}}}
+\end{equation}
 
@@
 
-workerOutIntPerc <- (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)
-
-```
-
-To test the prerequisite effect of intergroup contact, every daily diary measurement started with the question “_Did you meet a Dutch person this morning [/afternoon]?
-(In person interaction for at least 10 minutes)_” (`r workerOutIntPerc`% of all `r nrow(dtWorkerSupp$workerInteractionType)` recorded Recaps included an interaction with Dutch majority members).
+#workerOutIntPerc <- (sum(workerAvFreQual$SumContactNL) / nrow(workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)
+# To test the prerequisite effect of intergroup contact, every daily diary measurement started with the question “_Did you meet a Dutch person this morning [/afternoon]?
+(In person interaction for at least 10 minutes)_” (`r workerOutIntPerc`% of all `r nrow(workerInteractionType)` recorded Recaps included an interaction with Dutch majority members).
 This question is our main predictor to test whether having an intergroup contact indeed has an influence on one’s rating of the outgroup attitudes during the respective morning or afternoon (i.e., a longitudinal test of the contact hypothesis).
@@
 If they did not have interactions with Dutch people, participants were asked to report on their desire to have an interaction – this was done to balance the duration of the two answer options to not make it more attractive for a participant to answer that they did not have an interaction.
+```
 
@@
 
+<!-- taken from: https://stats.idre.ucla.edu/stata/faq/how-can-i-estimate-effect-size-for-mixed/ -->
+<!-- also check: https://largescaleassessmentsineducation.springeropen.com/articles/10.1186/s40536-018-0061-2 -->
 \begin{equation}

### 2021-10-26 Methods-and-Results.tex
ml coeff latex fix

--- 2021-10-25 Methods-and-Results.tex
@@
 positive outgroup attitudes within the participants (\textit{b} = 2.48,
-\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}1.36, 3.59{]}), even after controlling for having an
-interaction with a non-Dutch (which did not relate to outgroup attitudes
-independently; For full results see Online Supplementary Materials
+t(1200) = 4.36, \textit{p} = \textless{} .001,
+\textbackslash textit\{95\%CI{[}1.36, 3.59{]}), even after controlling
+for having an interaction with a non-Dutch (which did not relate to
+outgroup attitudes independently; For full results see Online
+Supplementary Materials
 B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance.
@@
 
-t be explained by whether or not the interaction fulfilled the person's
-core situational need. This should, in turn, be due to a higher
-perceived interaction quality. We will this sequentially test whether
-the fulfillment of the core need during an interaction is (1) related to
-more positive outgroup attitudes, (2) higher perceived interaction
-quality, and (3) whether the variance explained by the core need is
-assumed by the perceived interaction quality if considered jointly.
+The main proposal of our article is that the success of an outgroup
+interaction might be explained by whether or not the interaction
+fulfilled the person's core situational need. This should, in turn, be
+due to a higher perceived interaction quality. We will this sequentially
+test whether the fulfillment of the core need during an interaction is
+(1) related to more positive outgroup attitudes, (2) higher perceived
+interaction quality, and (3) whether the variance explained by the core
+need is assumed by the perceived interaction quality if considered
+jointly.
 
-\begin{itemize}
-\tightlist
-\item
-  Att \textasciitilde{} Need \& Qlt \textasciitilde{} Need
-\item
-  Att \textasciitilde{} Need + Qual
-\end{itemize}
+We find that in the highest multilevel models, the fulfillment of core
+situational needs during outgroup contacts was associated with more
+positive outgroup attitudes (random slopes model; \textit{b} = 0.17,
+t(365) = 2.93, \textit{p} = = 0.004,
+\textbackslash textit\{95\%CI{[}0.06, 0.30{]}) and also predicted higher
+perceived interaction quality (random intercept model; \textit{b} =
+0.42, t(365) = 8.07, \textit{p} = \textless{} .001,
+\textbackslash textit\{95\%CI{[}0.32, 0.52{]}). However, if we consider
+the influences of core need fulfillment and interaction quality on
+outgroup attitudes jointly, we find that virtually all variance is
+explained by perceived interaction quality (random slopes mode;
+\textit{b} = 0.23, t(364) = 4.22, \textit{p} = \textless{} .001,
+\textbackslash textit\{95\%CI{[}0.12, 0.33{]}) and only little unique
+variance is still explained by core need fulfillment (\textit{b} = 0.04,
+t(364) = 0.64, \textit{p} = = 0.523,
+\textbackslash textit\{95\%CI{[}-0.08, 0.15{]}). We thus find support
+for our hypotheses and can conclude that in this data set the
+fulfillment of core situational needs had a significant influence on
+outgroup attitudes and that this effect is likely explained by its
+effect through perceived interaction quality.
+
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
 
 \paragraph{Robustness}
+
+\subparagraph{Interaction Type}
+
+\subparagraph{Other Needs}
+
+For full results see Online Supplementary Information B.
 

### 2021-10-26 scripts/functions/MlCorMat.R

@@ -270,19 +270,19 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
   
   if (is.null(lmerCI)) {
     paste0(
-      "\textit{b} = ", b, 
+      "\\textit{b} = ", b, 
       ", t(", df, ") = ", t,
-      ", \textit{p} = ", p
+      ", \\textit{p} = ", p
     )
   } else {
     CIlwr <- lmerCI[varName, "2.5 %"] %>% round(2) %>% format(nsmall=2)
     CIupr <- lmerCI[varName, "97.5 %"] %>% round(2) %>% format(nsmall=2)
     
     paste0(
-      "\textit{b} = ", b, 
+      "\\textit{b} = ", b, 
       ", t(", df, ") = ", t,
-      ", \textit{p} = ", p,
-      ", \textit{95%CI[", CIlwr, ", ", CIupr, "]"
+      ", \\textit{p} = ", p,
+      ", \\textit{95%CI[", CIlwr, ", ", CIupr, "]"
     )
   }
 }

### 2021-10-26 Methods-and-Results.tex
coeff fix

@@
 t(1200) = 4.36, \textit{p} = \textless{} .001,
-\textbackslash textit\{95\%CI{[}1.36, 3.59{]}), even after controlling
+\textbackslash textit\{95\%CI\}{[}1.36, 3.59{]}), even after controlling
 for having an interaction with a non-Dutch (which did not relate to
@@
 t(365) = 2.93, \textit{p} = = 0.004,
-\textbackslash textit\{95\%CI{[}0.06, 0.30{]}) and also predicted higher
-perceived interaction quality (random intercept model; \textit{b} =
-0.42, t(365) = 8.07, \textit{p} = \textless{} .001,
-\textbackslash textit\{95\%CI{[}0.32, 0.52{]}). However, if we consider
-the influences of core need fulfillment and interaction quality on
-outgroup attitudes jointly, we find that virtually all variance is
+\textbackslash textit\{95\%CI\}{[}0.06, 0.30{]}) and also predicted
+higher perceived interaction quality (random intercept model; \textit{b}
+= 0.42, t(365) = 8.07, \textit{p} = \textless{} .001,
+\textbackslash textit\{95\%CI\}{[}0.32, 0.52{]}). However, if we
+consider the influences of core need fulfillment and interaction quality
+on outgroup attitudes jointly, we find that virtually all variance is
 explained by perceived interaction quality (random slopes mode;
 \textit{b} = 0.23, t(364) = 4.22, \textit{p} = \textless{} .001,
-\textbackslash textit\{95\%CI{[}0.12, 0.33{]}) and only little unique
+\textbackslash textit\{95\%CI\}{[}0.12, 0.33{]}) and only little unique
 variance is still explained by core need fulfillment (\textit{b} = 0.04,
 t(364) = 0.64, \textit{p} = = 0.523,
-\textbackslash textit\{95\%CI{[}-0.08, 0.15{]}). We thus find support
+\textbackslash textit\{95\%CI\}{[}-0.08, 0.15{]}). We thus find support
 for our hypotheses and can conclude that in this data set the

### 2021-10-26 scripts/functions/MlCorMat.R

@@ -282,7 +282,7 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
       "\\textit{b} = ", b, 
       ", t(", df, ") = ", t,
       ", \\textit{p} = ", p,
-      ", \\textit{95%CI[", CIlwr, ", ", CIupr, "]"
+      ", \\textit{95%CI}[", CIlwr, ", ", CIupr, "]"
     )
   }
 }

### 2021-10-26 Methods-and-Results.tex
coeff ci fix

--- 2021-10-26 Methods-and-Results.tex
@@
 positive outgroup attitudes within the participants (\textit{b} = 2.48,
-t(1200) = 4.36, \textit{p} = \textless{} .001,
-\textbackslash textit\{95\%CI{[}1.36, 3.59{]}), even after controlling
-for having an interaction with a non-Dutch (which did not relate to
-outgroup attitudes independently; For full results see Online
-Supplementary Materials
+t(1200) = 4.36, \textit{p} = \textless{} .001, \textit{95\%CI}{[}1.36,
+3.59{]}), even after controlling for having an interaction with a
+non-Dutch (which did not relate to outgroup attitudes independently; For
+full results see Online Supplementary Materials
 B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance.
@@
 positive outgroup attitudes (random slopes model; \textit{b} = 0.17,
-t(365) = 2.93, \textit{p} = = 0.004,
-\textbackslash textit\{95\%CI{[}0.06, 0.30{]}) and also predicted higher
-perceived interaction quality (random intercept model; \textit{b} =
-0.42, t(365) = 8.07, \textit{p} = \textless{} .001,
-\textbackslash textit\{95\%CI{[}0.32, 0.52{]}). However, if we consider
-the influences of core need fulfillment and interaction quality on
-outgroup attitudes jointly, we find that virtually all variance is
+t(365) = 2.93, \textit{p} = = 0.004, \textit{95\%CI}{[}0.06, 0.30{]})
+and also predicted higher perceived interaction quality (random
+intercept model; \textit{b} = 0.42, t(365) = 8.07, \textit{p} =
+\textless{} .001, \textit{95\%CI}{[}0.32, 0.52{]}). However, if we
+consider the influences of core need fulfillment and interaction quality
+on outgroup attitudes jointly, we find that virtually all variance is
 explained by perceived interaction quality (random slopes mode;
 \textit{b} = 0.23, t(364) = 4.22, \textit{p} = \textless{} .001,
-\textbackslash textit\{95\%CI{[}0.12, 0.33{]}) and only little unique
-variance is still explained by core need fulfillment (\textit{b} = 0.04,
-t(364) = 0.64, \textit{p} = = 0.523,
-\textbackslash textit\{95\%CI{[}-0.08, 0.15{]}). We thus find support
-for our hypotheses and can conclude that in this data set the
-fulfillment of core situational needs had a significant influence on
+\textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
+still explained by core need fulfillment (\textit{b} = 0.04, t(364) =
+0.64, \textit{p} = = 0.523, \textit{95\%CI}{[}-0.08, 0.15{]}). We thus
+find support for our hypotheses and can conclude that in this data set
+the fulfillment of core situational needs had a significant influence on
 outgroup attitudes and that this effect is likely explained by its

### 2021-10-26 scripts/functions/MlCorMat.R

@@ -282,7 +282,7 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
       "\\textit{b} = ", b, 
       ", t(", df, ") = ", t,
       ", \\textit{p} = ", p,
-      ", \\textit{95%CI}[", CIlwr, ", ", CIupr, "]"
+      ", \\textit{95\\%CI}[", CIlwr, ", ", CIupr, "]"
     )
   }
 }

### 2021-10-26 Methods-and-Results.tex
coeff equal sign fix

@@
 positive outgroup attitudes within the participants (\textit{b} = 2.48,
-t(1200) = 4.36, \textit{p} = \textless{} .001, \textit{95\%CI}{[}1.36,
+t(1200) = 4.36, \textit{p} \textless{} .001, \textit{95\%CI}{[}1.36,
 3.59{]}), even after controlling for having an interaction with a
@@
 positive outgroup attitudes (random slopes model; \textit{b} = 0.17,
-t(365) = 2.93, \textit{p} = = 0.004, \textit{95\%CI}{[}0.06, 0.30{]})
-and also predicted higher perceived interaction quality (random
-intercept model; \textit{b} = 0.42, t(365) = 8.07, \textit{p} =
-\textless{} .001, \textit{95\%CI}{[}0.32, 0.52{]}). However, if we
-consider the influences of core need fulfillment and interaction quality
-on outgroup attitudes jointly, we find that virtually all variance is
-explained by perceived interaction quality (random slopes mode;
-\textit{b} = 0.23, t(364) = 4.22, \textit{p} = \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
-still explained by core need fulfillment (\textit{b} = 0.04, t(364) =
-0.64, \textit{p} = = 0.523, \textit{95\%CI}{[}-0.08, 0.15{]}). We thus
-find support for our hypotheses and can conclude that in this data set
-the fulfillment of core situational needs had a significant influence on
-outgroup attitudes and that this effect is likely explained by its
-effect through perceived interaction quality.
+t(365) = 2.93, \textit{p} = 0.004, \textit{95\%CI}{[}0.06, 0.30{]}) and
+also predicted higher perceived interaction quality (random intercept
+model; \textit{b} = 0.42, t(365) = 8.07, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.32, 0.52{]}). However, if we consider the influences
+of core need fulfillment and interaction quality on outgroup attitudes
+jointly, we find that virtually all variance is explained by perceived
+interaction quality (random slopes mode; \textit{b} = 0.23, t(364) =
+4.22, \textit{p} \textless{} .001, \textit{95\%CI}{[}0.12, 0.33{]}) and
+only little unique variance is still explained by core need fulfillment
+(\textit{b} = 0.04, t(364) = 0.64, \textit{p} = 0.523,
+\textit{95\%CI}{[}-0.08, 0.15{]}). We thus find support for our
+hypotheses and can conclude that in this data set the fulfillment of
+core situational needs had a significant influence on outgroup attitudes
+and that this effect is likely explained by its effect through perceived
+interaction quality.
 

### 2021-10-26 scripts/functions/MlCorMat.R

@@ -281,7 +281,7 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
     paste0(
       "\\textit{b} = ", b, 
       ", t(", df, ") = ", t,
-      ", \\textit{p} = ", p,
+      ", \\textit{p} ", p,
       ", \\textit{95\\%CI}[", CIlwr, ", ", CIupr, "]"
     )
   }

### 2021-10-26 scripts/functions/MlCorMat.R
Update MlCorMat.R

@@ -271,8 +271,8 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
   if (is.null(lmerCI)) {
     paste0(
       "\\textit{b} = ", b, 
-      ", t(", df, ") = ", t,
-      ", \\textit{p} = ", p
+      ", \\textit{t}(", df, ") = ", t,
+      ", \\textit{p} ", p
     )
   } else {
     CIlwr <- lmerCI[varName, "2.5 %"] %>% round(2) %>% format(nsmall=2)
@@ -280,7 +280,7 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
     
     paste0(
       "\\textit{b} = ", b, 
-      ", t(", df, ") = ", t,
+      ", \\textit{t}(", df, ") = ", t,
       ", \\textit{p} ", p,
       ", \\textit{95\\%CI}[", CIlwr, ", ", CIupr, "]"
     )

### 2021-10-26 Methods-and-Results.tex
coeff t fix

--- 2021-10-26 Methods-and-Results.tex
@@
 positive outgroup attitudes within the participants (\textit{b} = 2.48,
-t(1200) = 4.36, \textit{p} = \textless{} .001, \textit{95\%CI}{[}1.36,
-3.59{]}), even after controlling for having an interaction with a
-non-Dutch (which did not relate to outgroup attitudes independently; For
-full results see Online Supplementary Materials
+\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}1.36, 3.59{]}), even after controlling for having an
+interaction with a non-Dutch (which did not relate to outgroup attitudes
+independently; For full results see Online Supplementary Materials
 B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance.
@@
 positive outgroup attitudes (random slopes model; \textit{b} = 0.17,
-t(365) = 2.93, \textit{p} = = 0.004, \textit{95\%CI}{[}0.06, 0.30{]})
-and also predicted higher perceived interaction quality (random
-intercept model; \textit{b} = 0.42, t(365) = 8.07, \textit{p} =
+\textit{t}(365) = 2.93, \textit{p} = 0.004, \textit{95\%CI}{[}0.06,
+0.30{]}) and also predicted higher perceived interaction quality (random
+intercept model; \textit{b} = 0.42, \textit{t}(365) = 8.07, \textit{p}
 \textless{} .001, \textit{95\%CI}{[}0.32, 0.52{]}). However, if we
@@
 explained by perceived interaction quality (random slopes mode;
-\textit{b} = 0.23, t(364) = 4.22, \textit{p} = \textless{} .001,
+\textit{b} = 0.23, \textit{t}(364) = 4.22, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
-still explained by core need fulfillment (\textit{b} = 0.04, t(364) =
-0.64, \textit{p} = = 0.523, \textit{95\%CI}{[}-0.08, 0.15{]}). We thus
-find support for our hypotheses and can conclude that in this data set
-the fulfillment of core situational needs had a significant influence on
-outgroup attitudes and that this effect is likely explained by its
-effect through perceived interaction quality.
+still explained by core need fulfillment (\textit{b} = 0.04,
+\textit{t}(364) = 0.64, \textit{p} = 0.523, \textit{95\%CI}{[}-0.08,
+0.15{]}). We thus find support for our hypotheses and can conclude that
+in this data set the fulfillment of core situational needs had a
+significant influence on outgroup attitudes and that this effect is
+likely explained by its effect through perceived interaction quality.
 

### 2021-10-26 Methods-and-Results.Rmd
AOT-P results done

@@
 This might be due to the aggregation within the participants or the small sample size of between participant data.
-Nonetheless, the aggregate data does not support the notion that simply having more interactions with an outgroup results in more positive outgroup attitudes.
+Nonetheless, the aggregated data does not support the notion that simply having more interactions with an outgroup results in more positive outgroup attitudes.
 
@@
 \paragraph{Robustness}
-
-\subparagraph{Interaction Type}
-
-\subparagraph{Other Needs}
-
+```{r workerModelInterceptAttCoreInt, include=FALSE}
+# Create and save Model
+mdlWorker$lmeInterceptAttCoreInt <-
+  lme(
+    thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction,
+    random =  ~ 1 | PID,
+    data = dtWorkerSupp$workerWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlWorker$lmerInterceptAttCoreInt <- lmer(
+    thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction + (1 | PID),
+    data = dtWorkerSupp$workerWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlWorker$lmerInterceptAttCoreIntCI <- 
+  confint(mdlWorker$lmerInterceptAttCoreInt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorker$lmeAttNull, 
+      mdlWorker$lmeInterceptAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = c("l", rep("c", ncol(.)-1)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorker$varInterceptAttCoreInt <- 
+  lme4::VarCorr(mdlWorker$lmeInterceptAttCoreInt)
+```
+```{r workerModelSlopesAttCoreIntX, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlWorker$lmeSlopesAttCoreInt <- lme(
+  thermometerDutch_1 ~
+    keyMotiveFulfilled_cwc * OutgroupInteraction,
+  random = ~ 1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  data = dtWorkerSupp$workerWithinBetween
+)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlWorker$lmerSlopesAttCoreInt <- lmer(
+    thermometerDutch_1 ~
+      keyMotiveFulfilled_cwc * OutgroupInteraction +
+      (1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID),
+    data = dtWorkerSupp$workerWithinBetween
+  ), 
+  confint = TRUE,
+  digits = 3
+)
+
+mdlWorker$lmerSlopesAttCoreIntCI <- 
+  confint(mdlWorker$lmerSlopesAttCoreInt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorker$lmeAttNull, 
+      mdlWorker$lmeInterceptAttCoreInt,
+      mdlWorker$lmeSlopesAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorker$varSlopesAttCoreInt <- 
+  lme4::VarCorr(mdlWorker$lmeSlopesAttCoreInt)
+
+# Assumption Checks:
+mdlWorker$diagSlopesAttCoreInt <-
+  sjPlot::plot_model(mdlWorker$lmerSlopesAttCoreInt, type = "diag")
+grid.arrange(
+  mdlWorker$diagSlopesAttCoreInt[[1]],
+  mdlWorker$diagSlopesAttCoreInt[[2]]$`PID`,
+  mdlWorker$diagSlopesAttCoreInt[[3]],
+  mdlWorker$diagSlopesAttCoreInt[[4]]
+)
+
+# Plot prediction model
+mdlWorker$predSlopesAttCoreInt <- 
+  dtWorkerSupp$workerWithinBetween %>%
+  select(thermometerDutch_1, session, PID) %>% 
+  mutate(measure = predict(mdlWorker$lmeSlopesAttCoreInt,
+                           dtWorkerSupp$workerWithinBetween,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlWorker$predPltSlopesAttCoreInt <-
+    ggplot(data = mdlWorker$predSlopesAttCoreInt, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/Worker_PredictionPlot_SlopesAttCoreInt.png",
+  mdlWorker$predPltSlopesAttCoreInt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+To build further confidence in our results, we assessed two additional models that might offer alternative explanations of the effects we find.
+First, to make certain that the effect of core need fulfillment is specific to the interaction we compare the the effect to fulfillment of the situation core need when no outgroup interaction took place.
+Here we go back to the full dataset and assess the generalized situational core need fulfillment (either during an interaction or about the daytime in general) and whether the effect differed during daily diary measurements with and without outgroup contacts.
+We find that there is no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteractionYes")`).
+Together with a significant main effect of having an outgroup contact, this indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+
+```{r workerOutModelInterceptAttCoreSdt, include=FALSE}
+# Create and save Model
+mdlWorkerOut$Att$lmeInterceptCoreSdt <-
+  lme(
+    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
+    random = ~ 1 | PID,
+    data = dtWorkerSupp$workerOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlWorkerOut$Att$lmerInterceptCoreSdt <- lmer(
+    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID),
+    data = dtWorkerSupp$workerOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# To be compared against a model with only the self determination theory needs
+mdlWorkerOut$Att$lmeInterceptSdt <-
+  lme(
+    thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
+    random = ~ 1 | PID,
+    data = dtWorkerSupp$workerOutWithinBetween,
+    na.action = na.exclude
+  )
+
+summ(
+  mdlWorkerOut$Att$lmerInterceptSdt <- lmer(
+    thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID),
+    data = dtWorkerSupp$workerOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Compare new model to previous steps
+anova(
+  mdlWorkerOut$Att$lmeInterceptSdt,
+  mdlWorkerOut$Att$lmeInterceptCoreSdt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+rm(lmeInterceptCoreRed)
+
+# Save variances
+mdlWorkerOut$Att$varInterceptCoreSdt <-
+  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreSdt)
+```
+```{r workerOutModelSlopesAttCoreSdt, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlWorkerOut$Att$lmeSlopesCoreSdt <-
+  lme(
+    thermometerDutch_1 ~
+      keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
+    random = ~ 1 + keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtWorkerSupp$workerOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlWorkerOut$Att$lmerSlopesCoreSdt <- lmer(
+    thermometerDutch_1 ~
+      keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc +
+      (1 + keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID),
+    data = dtWorkerSupp$workerOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlWorkerOut$Att$lmerSlopesCoreSdtCI <- 
+  confint(mdlWorkerOut$Att$lmerSlopesCoreSdt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlWorkerOut$Att$lmeInterceptSdt,
+      mdlWorkerOut$Att$lmeInterceptCoreSdt, 
+      mdlWorkerOut$Att$lmeSlopesCoreSdt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# model with SDT only
+# Create and save Model (optimizer needed to reach convergence)
+mdlWorkerOut$Att$lmeSlopesSdt <-
+  lme(
+    thermometerDutch_1 ~
+      competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
+    random = ~ 1 + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtWorkerSupp$workerOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlWorkerOut$Att$lmerSlopesSdt <- lmer(
+    thermometerDutch_1 ~
+      competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc +
+      (1 + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID),
+    data = dtWorkerSupp$workerOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Compare new model to previous step
+anova(mdlWorkerOut$Att$lmeInterceptSdt,
+      mdlWorkerOut$Att$lmeSlopesSdt, 
+      mdlWorkerOut$Att$lmeSlopesCoreSdt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Worker: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlWorkerOut$Att$varSlopesCoreSdt <- 
+  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreSdt)
+
+# Assumption Checks:
+mdlWorkerOut$Att$diagSlopesCoreSdt <- 
+  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreSdt, type = "diag")
+grid.arrange(
+  mdlWorkerOut$Att$diagSlopesCoreSdt[[1]],
+  mdlWorkerOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
+  mdlWorkerOut$Att$diagSlopesCoreSdt[[3]],
+  mdlWorkerOut$Att$diagSlopesCoreSdt[[4]]
+)
+
+# Plot prediction model
+mdlWorkerOut$Att$predSlopesCoreSdt <- 
+  dtWorkerSupp$workerOutWithinBetween %>%
+  filter(!is.na(autonomy_1)) %>%
+  select(thermometerDutch_1, session, PID, autonomy_1) %>% 
+  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreSdt,
+                           dtWorkerSupp$workerOutWithinBetween %>% filter(!is.na(autonomy_1)),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlWorkerOut$Att$predPltSlopesCoreSdt <-
+    ggplot(data = mdlWorkerOut$Att$predSlopesCoreSdt, aes(x = session, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreStd.png",
+  mdlWorkerOut$Att$predPltSlopesCoreSdt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+
+# Model comparison
+SdtComp <-
+  anova(
+    mdlWorkerOut$Att$lmerSlopesSdt, 
+    mdlWorkerOut$Att$lmerSlopesCoreSdt
+  ) %>%
+  as.data.frame()
+SdtCompDf <- SdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Df"]
+SdtCompN <- sapply(ranef(mdlWorkerOut$Att$lmerSlopesCoreSdt), nrow)
+SdtCompP <-
+  ifelse(SdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
+         "< .001",
+         paste0("= ", SdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
+
+SdtCompChiSq <- paste0("$\\chi^2$(", SdtCompDf, "\\textit{N} = ", SdtCompN, ") ", SdtCompP)
+```
+
+In a final step we check whether during the interaction the core situational need is a meaningful predictor even when taking other fundamental psychological needs into account.
+We focus on the three commonly considered self determination needs: competence, autonomy, and relatedness.
+We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r SdtCompChiSq`).
+We find that next to relatedness (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "relatedness_1_cwc")`), the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "keymotive_fulfillemt_1_cwc")`).
+When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs and competence and autonomy needs are non-significant (all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
 For full results see Online Supplementary Information B.

### 2021-10-26 Methods-and-Results.tex
AOT-P results done

@@
 or the small sample size of between participant data. Nonetheless, the
-aggregate data does not support the notion that simply having more
+aggregated data does not support the notion that simply having more
 interactions with an outgroup results in more positive outgroup
@@
 
-\subparagraph{Interaction Type}
+To build further confidence in our results, we assessed two additional
+models that might offer alternative explanations of the effects we find.
+First, to make certain that the effect of core need fulfillment is
+specific to the interaction we compare the the effect to fulfillment of
+the situation core need when no outgroup interaction took place. Here we
+go back to the full dataset and assess the generalized situational core
+need fulfillment (either during an interaction or about the daytime in
+general) and whether the effect differed during daily diary measurements
+with and without outgroup contacts. We find that there is no main effect
+of core need fulfillment (random slopes model; \textit{b} = 0.03,
+\textit{t}(1199) = 1.07, \textit{p} = 0.284, \textit{95\%CI}{[}-0.02,
+0.08{]}) but a significant interaction effect of core need fulfillment
+and outgroup contact (\textit{b} = 0.13, \textit{t}(1199) = 4.31,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.19{]}). Together
+with a significant main effect of having an outgroup contact, this
+indicates that it is not key need fulfillment in general --- but only
+key need fulfillment during an outgroup contact that predicts more
+positive outgroup attitudes.
 
-\subparagraph{Other Needs}
-
-For full results see Online Supplementary Information B.
+In a final step we check whether during the interaction the core
+situational need is a meaningful predictor even when taking other
+fundamental psychological needs into account. We focus on the three
+commonly considered self determination needs: competence, autonomy, and
+relatedness. We find that the core need adds significantly above a model
+with only the self determination theory needs (random slopes models;
+\(\chi^2\)(6\textit{N} = 21) = 0.003). We find that next to relatedness
+(\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.05, 0.14{]}), the core need explains the most
+variance in outgroup attitudes after an outgroup contact (\textit{b} =
+0.09, \textit{t}(361) = 2.23, \textit{p} = 0.026,
+\textit{95\%CI}{[}0.02, 0.17{]}). When compared to the model with only
+the SDT needs, the core need fulfillment flexibly takes on some of the
+explained variance of all of the three fundamental needs and competence
+and autonomy needs are non-significant (all \textit{b} \textless{} 0.05,
+all \textit{p} \textgreater{} 0.544). For full results see Online
+Supplementary Information B.
 

### 2021-10-26 Methods-and-Results.tex
chi sq fix

@@
 with only the self determination theory needs (random slopes models;
-\(\chi^2\)(6\textit{N} = 21) = 0.003). We find that next to relatedness
-(\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.05, 0.14{]}), the core need explains the most
-variance in outgroup attitudes after an outgroup contact (\textit{b} =
-0.09, \textit{t}(361) = 2.23, \textit{p} = 0.026,
+\(\chi^2\)(6, \textit{N} = 21) \textit{p} = 0.003). We find that next to
+relatedness (\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the core need
+explains the most variance in outgroup attitudes after an outgroup
+contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p} = 0.026,
 \textit{95\%CI}{[}0.02, 0.17{]}). When compared to the model with only

### 2021-10-26 Methods-and-Results.Rmd
chi sq fix
AOT-S Methods added

@@
 Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
-With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{M} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(workerSampleInfo$dailiesN)`).
+With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(workerSampleInfo$dailiesN)`).
 This is a common number of measurements found in experience sampling studies and should offer sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
@@
 
-\paragraph{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
+\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
 First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
@@
 
-\paragraph{Core Need}The main proposal of our article is that the success of an outgroup interaction might be explained by whether or not the interaction fulfilled the person's core situational need.
+\subsubsection{Core Need}The main proposal of our article is that the success of an outgroup interaction might be explained by whether or not the interaction fulfilled the person's core situational need.
 This should, in turn, be due to a higher perceived interaction quality.
@@
 
-\paragraph{Robustness}
+\subsubsection{Robustness}
 ```{r workerModelInterceptAttCoreInt, include=FALSE}
@@
 
-SdtCompChiSq <- paste0("$\\chi^2$(", SdtCompDf, "\\textit{N} = ", SdtCompN, ") ", SdtCompP)
+SdtCompChiSq <- paste0("$\\chi^2$(", SdtCompDf, ", \\textit{N} = ", SdtCompN, "), \\textit{p} ", SdtCompP)
 ```
@@
 
+The aim of our study is similar to to that of the first study, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
+However, in this second study we collected a substantially larger intensive longitudinal survey study with recently arrived international students in the Netherlands.
+The survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations as these students will likely interact with the Dutch majority outgroup on a daily basis.
+Data was collected from November 19th, 2018 through January 6th, 2019.
+
+The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
+Correlations and descriptive statistics of the included variables are available in Table \ref{tab:studentVarDescr} and Table \ref{tab:studentOutVarDescr}.
+
 \subsection{Methods}
 
+```{r studentSampleInfo, include=FALSE}
+# summarize participant characteristics
+studentSampleInfo <- 
+  dtStudents$full %>%
+  mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>%
+  group_by(PID) %>%
+  summarise(
+    dailiesN = n(), 
+    morningN = sum(periodMA=="morning"),
+    afternoonN = sum(periodMA=="afternoon"),
+    age = age,
+    gender = gender,
+    nationality = nationality
+  ) %>%
+  distinct
+
+# look at frequencies of characteristics 
+table(studentSampleInfo$gender)
+table(as.character(studentSampleInfo$nationality))
+
+# categorical variables:
+# - outgroup contact
+# - non-outgroup contact
+
+# continuous variables:
+# - Core Need fulfillment
+# - SDT Competence
+# - SDT Autonomy
+# - SDT Relatedness
+# - Interaction Quality
+# - Outgroup Attitudes
+######
+# within cor
+# between cor
+# ---
+# Grand mean
+# SD between
+# SD within
+# Proportion of variance
+# __ __ __
+# Note:
+# N within ppt.s 
+######
+
+# divide into trait and state
+dtStudentSupp$studentWithinBetween <-
+  MlTraitState(
+    data = dtStudentSupp$studentInteractionType,
+    id = "PID",
+    selection =
+      c(
+        "KeyNeedFullfillment",
+        "Competence",
+        "Autonomy",
+        "Relatedness",
+        "AttitudesDutch",
+        "quality_overall"
+      )
+  )
+dtStudentSupp$studentOutWithinBetween <-
+  MlTraitState(
+    data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection =
+      c(
+        "KeyNeedFullfillment",
+        "Competence",
+        "Autonomy",
+        "Relatedness",
+        "AttitudesDutch",
+        "quality_overall"
+      )
+  )
+```
+
+```{r studentVarDescr, include=FALSE}
+studentMlCor <-
+  MlCorMat(
+    data = dtStudentSupp$studentInteractionType,
+    id = "PID",
+    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "AttitudesDutch") ,
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
+  )
+
+studentMlCor %>%
+  kable(
+    .,
+    caption = "Student: Multilevel Core Variable Descriptives",
+    format = "latex",
+    booktabs = TRUE,
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person coorelations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/studentVarDescr.tex")
+```
+
+```{r studentOutVarDescr, include=FALSE}
+studentOutMlCor <-
+  MlCorMat(
+    data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
+  )
+
+studentOutMlCor %>%
+  kable(
+    .,
+    caption = "Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
+    format = "latex",
+    booktabs = TRUE,
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person coorelations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/studentOutVarDescr.tex")
+
+# misty::multilevel.descript(dtStudentsSupp$studentWithinBetween$keyMotiveFulfilled, cluster = dtStudentsSupp$studentWithinBetween$PID)
+```
+
+\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(studentSampleInfo)` international students using a local participant pool and specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
+Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
+With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(studentSampleInfo$dailiesN)`).
+As with the previous study this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
+Participants were compensated for their participation with partial course credits --- depending on their participation.
+The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(studentSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(studentSampleInfo$age),2), nsmall=2)`, `r nrow(studentSampleInfo %>% filter(gender == "women"))` women).
+The sample fairly accurately describes the local population of international students.
+
+\subsubsection{Procedure} The study procedure mirrored the setup of study one and consisted of pre-, daily diary-, and post-measurement.
+The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily)))`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily))))`).
+General compliance was high (`r format(round(sum(studentSampleInfo$dailiesN)/(nrow(studentSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in).
+The response rates were approximately equal during mornings (\textit{n} = `r sum(studentSampleInfo$morningN)`) and afternoons (\textit{n} = `r sum(studentSampleInfo$afternoonN)`).
+All key variables in for this study were part of the short daily diary surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}To measure intergroup contacts, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
+(in-person interaction for at least 10 minutes)}”.
+Participants were additionally offered a pop-up explanation: "With in-person interaction, we mean a continued interaction with another person (potentially in a group) that lasted at least 10 minutes.
+This interaction should be offline and face-to-face.
+It should include some form of verbal communication and should be uninterrupted to still count as the same interaction.
+Any individual interaction can last minutes or hours.
+If there were multiple interaction partners, we would like you to focus on the person that was most important to you during the interaction.".
+The participants recorded between `r dtStudentSupp$studentContactFreq$SumContactNL[dtStudentSupp$studentContactFreq$SumContactNL > 0] %>% min`--`r dtStudentSupp$studentContactFreq$SumContactNL %>% max`
+(`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtStudentSupp$studentContactFreq$SumContactNL) / nrow(dtStudentSupp$studentInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtStudentSupp$studentInteractionType)` daily diary responses).
+
+\paragraph{Psychological Needs}For the core situational need, we asked participants in an open ended text field: “\textit{What was your main goal [during the interaction with X / this morning / this afternoon]?}”.
+Participants could additionally click on a pop-up explanation: "Your main goal during an interaction can vary depending on the interaction.
+It could be to connect with friends, to find or provide help, to achieve academic ambitions, work on your fitness, work for a job, or simply to get a coffee, just as well as many many other concrete or abstract goals that are import to you in the moment.
+It really depends on your subjective experience of the interaction.".
+Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{During your interaction with X [this morning / this evening] your goal (-previous text entry-) was fulfilled.}” on a continuous slider scale ranging from strongly disagree (1) to strongly agree (100).
+
+The measurement of the self determination needs was identical to study 1.
+
+\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to study one..
+
+\paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup was again measured using the feeling thermometer, as in study one.
+All survey details are also available in Online Supplemental Materials A and B.
+
+\input{Tables/studentVarDescr}
+\input{Tables/studentOutVarDescr}
+
 \subsection{Results}
 
-\section{Study 2}
+\subsubsection{Contact Hypothesis}
+
+\subsubsection{Core Need}
+
+\subsubsection{Robustness}
+
+\paragraph{interaction type}
+
+\paragraph{other needs}
+
+\section{Study 3}
 

### 2021-10-26 Methods-and-Results.tex
AOT-S Methods added

@@
 design, we aimed at getting 50-60 measurements per participant
-(\textit{M} = 53.26, \textit{M} = 16.72, \textit{total N} = 1225). This
+(\textit{M} = 53.26, \textit{SD} = 16.72, \textit{total N} = 1225). This
 is a common number of measurements found in experience sampling studies
@@
 
-\paragraph{Contact Hypothesis}
+\subsubsection{Contact Hypothesis}
 
@@
 
-\paragraph{Core Need}
+\subsubsection{Core Need}
 
@@
 
-\paragraph{Robustness}
+\subsubsection{Robustness}
 
@@
 with only the self determination theory needs (random slopes models;
-\(\chi^2\)(6, \textit{N} = 21) \textit{p} = 0.003). We find that next to
-relatedness (\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p}
+\(\chi^2\)(6, \textit{N} = 21), \textit{p} = 0.003). We find that next
+to relatedness (\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p}
 \textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the core need
@@
 
+The aim of our study is similar to to that of the first study, as we
+again test the general contact hypothesis, the influence of core need
+fulfillment, and perceived interaction quality during intergroup
+contacts. However, in this second study we collected a substantially
+larger intensive longitudinal survey study with recently arrived
+international students in the Netherlands. The survey method again
+offers a large body of ecologically valid data on need satisfaction in
+real-life intergroup contact situations as these students will likely
+interact with the Dutch majority outgroup on a daily basis. Data was
+collected from November 19th, 2018 through January 6th, 2019.
+
+The full surveys are available in our Online Supplementary Material A
+and the full data description is available in Online Supplementary
+Materials B. Correlations and descriptive statistics of the included
+variables are available in Table \ref{tab:studentVarDescr} and Table
+\ref{tab:studentOutVarDescr}.
+
 \subsection{Methods}
+
+\subsubsection{Participants}
+
+After receiving ethical approval from the University of Groningen, we
+recruited 113 international students using a local participant pool and
+specifically targeted non-Dutch students, who had recently arrived in
+the Netherlands. Participants reported on their interactions for at
+least 30 days with two daily measures (capturing the morning and
+afternoon). With this design, we aimed at getting 50-60 measurements per
+participant (\textit{M} = 43.94, \textit{SD} = 15.00, \textit{total N} =
+4965). As with the previous study this should offer sufficient power to
+model processes within participants and will lend stronger weight to
+between-participant results. Participants were compensated for their
+participation with partial course credits --- depending on their
+participation. The sample consisted of relatively young migrants, who
+were mostly from the global north (\(M_{age}\) = 20.24, \(SD_{age}\) =
+2.12, 84 women). The sample fairly accurately describes the local
+population of international students.
+
+\subsubsection{Procedure}
+
+The study procedure mirrored the setup of study one and consisted of
+pre-, daily diary-, and post-measurement. The participants were invited
+for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days
+(\textit{median duration} = 46, \textit{MAD duration} = 54). General
+compliance was high (70.87\% of all invited surveys were filled in). The
+response rates were approximately equal during mornings (\textit{n} =
+2608) and afternoons (\textit{n} = 2357). All key variables in for this
+study were part of the short daily diary surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+To measure intergroup contacts, every experience sampling measurement
+started with the question
+``\textit{Did you meet a Dutch person this morning [/afternoon]? (in-person interaction for at least 10 minutes)}''.
+Participants were additionally offered a pop-up explanation: ``With
+in-person interaction, we mean a continued interaction with another
+person (potentially in a group) that lasted at least 10 minutes. This
+interaction should be offline and face-to-face. It should include some
+form of verbal communication and should be uninterrupted to still count
+as the same interaction. Any individual interaction can last minutes or
+hours. If there were multiple interaction partners, we would like you to
+focus on the person that was most important to you during the
+interaction.''. The participants recorded between 1--43 (1.64--93.75\%
+of individual daily diary measurements; 18.83\% of all 4965 daily diary
+responses).
+
+\paragraph{Psychological Needs}
+
+For the core situational need, we asked participants in an open ended
+text field:
+``\textit{What was your main goal [during the interaction with X / this morning / this afternoon]?}''.
+Participants could additionally click on a pop-up explanation: ``Your
+main goal during an interaction can vary depending on the interaction.
+It could be to connect with friends, to find or provide help, to achieve
+academic ambitions, work on your fitness, work for a job, or simply to
+get a coffee, just as well as many many other concrete or abstract goals
+that are import to you in the moment. It really depends on your
+subjective experience of the interaction.''. Then, with reference to the
+text entry, we asked how much this core need was fulfilled during the
+interaction or the past daytime period:
+``\textit{During your interaction with X [this morning / this evening] your goal (-previous text entry-) was fulfilled.}''
+on a continuous slider scale ranging from strongly disagree (1) to
+strongly agree (100).
+
+The measurement of the self determination needs was identical to study
+1.
+
+\paragraph{Perceived Interaction Quality}
+
+The ratings of the perceived interaction quality was identical to study
+one..
+
+\paragraph{Outgroup Attitudes}
+
+Attitudes towards the Dutch majority outgroup was again measured using
+the feeling thermometer, as in study one. All survey details are also
+available in Online Supplemental Materials A and B.
+
+\input{Tables/studentVarDescr}
+\input{Tables/studentOutVarDescr}
 
@@
 
-\section{Study 2}
+\subsubsection{Contact Hypothesis}
+
+\subsubsection{Core Need}
+
+\subsubsection{Robustness}
+
+\paragraph{interaction type}
+
+\paragraph{other needs}
+
+\section{Study 3}
 

### 2021-10-26 Tables/studentOutVarDescr.tex
AOT-S Methods added

--- 2021-10-24 Tables/workerVarDescr.tex
@@
 \begin{table}
+\begin{minipage}[t][\textheight][t]{\textwidth}
 
-\caption{\label{tab:workerSampleInfo}Worker: Multilevel Core Variable Descriptives}
+\caption{\label{tab:studentOutVarDescr}Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
 \centering
@@
 \midrule
-Core Need &  & 0.67*** & 0.54*** & 0.01 & -0.23\\
-Competence & 0.36*** &  & 0.72*** & -0.14 & -0.20\\
-Autonomy & 0.31*** & 0.09** &  & -0.05 & 0.19\\
-Relatedness & 0.45*** & 0.09** & 0.14*** &  & -0.06\\
-Attitudes NL & 0.05 & 0.11*** & 0.12*** & 0.14*** & \\
+Core Need &  & 0.46*** & 0.50*** & -0.19 & 0.15\\
+Competence & 0.23*** &  & 0.59*** & 0.39** & 0.22\\
+Autonomy & 0.12*** & 0.32*** &  & 0.23 & 0.07\\
+Relatedness & 0.48*** & 0.25*** & 0.19*** &  & -0.09\\
+Attitudes NL & 0.18*** & 0.16*** & 0.15*** & 0.22*** & \\
 \addlinespace
-Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 71.49\\
-Between-person SD & 14.68 & 13.72 & 12.09 & 14.59 & 12.91\\
-Within-person SD & 20.83 & 20.89 & 15.15 & 23.29 & 8.11\\
-ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.70\\
-ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.99\\
+Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 70.41\\
+Between-person SD & 11.20 & 13.95 & 14.07 & 17.35 & 17.13\\
+Within-person SD & 15.87 & 16.81 & 14.24 & 26.14 & 9.87\\
+ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.72\\
+ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.96\\
 \bottomrule
@@
 \end{tabular}
+\end{minipage}
 \end{table}

### 2021-10-26 scripts/functions/MlCorMat.R

@@ -168,7 +168,8 @@ MlCorMat <-
             cluster = dataRed %>% select(id),
             fun = "var",
             expand = FALSE
-          )
+          ), 
+          na.rm = TRUE
         ) / nrow(unique(data %>% select(id))))
     }
     

### 2021-10-26 Methods-and-Results.Rmd
AOT-S contac H results added

@@
 
-\subsubsection{Contact Hypothesis}
+```{r studentFreqAttCor, include=FALSE}
+
+dtStudentSupp$studentContactFreq <-
+  dtStudentSupp$studentContactFreq %>%
+  mutate(
+    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
+    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
+    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
+    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
+  )
+
+# correlation panel
+pairs.panels.new(
+  dtStudentSupp$studentContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
+    "Sum:\nNumber of Outgroup Contacts (NL)",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+
+# correlation panel with interaction sums winsorized
+pairs.panels.new(
+  dtStudentSupp$studentContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
+    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+```
+
+\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
+First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
+Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
+We find a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+This is to say that within our data, participants with more outgroup interactions did have significantly more positive outgroup attitudes.
+This is inconsistent with the results we found in the first study and might be due to the larger number of participants.
+
+```{r studentModelOlsAttFreqQual, include=FALSE}
+# create list to store Worker models
+mdlStudent <- list()
+
+# regression
+mdlStudent$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtStudentSupp$studentContactFreq)
+
+summ(
+  mdlStudent$lmAttFreqQualX,
+  confint = TRUE,
+  digits = 3
+)
+
+mdlStudent$lmAttFreqQualXEta <-
+  effectsize::eta_squared(mdlStudent$lmAttFreqQualX, partial = TRUE)
+
+interactions::interact_plot(
+  mdlStudent$lmAttFreqQualX,
+  pred = SumContactNL_c,
+  modx = AvQuality_c,
+  interval = TRUE,
+  partial.residuals = TRUE
+)
+
+interactions::johnson_neyman(mdlStudent$lmAttFreqQualX,
+                             pred = SumContactNL_c,
+                             modx = AvQuality_c,
+                             alpha = .05)
+```
+
+However, we find no significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
+Given the missing aggregate relationship between average interaction quality and outgroup attitudes, we find no significant effect of average perceived contact quality.
+Nor do we find that in this sample the impact of the number of interactions is moderated by the average contact quality.
+This is not entirely consistent with the first study, where average contact quality did have a meaningful effect on outgroup attitudes.
+This finding is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.
+
+```{r studentModelMLAttNull, include=FALSE}
+# Create and save Model
+mdlStudent$lmerAttNull <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
+    data = dtStudents$full
+  ) # use optim if it does not converge
+
+mdlStudent$lmeAttNull <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = dtStudents$full,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(mdlStudent$lmerAttNull) #or with the lme function
+summ(mdlStudent$lmerAttNull, digits = 3)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlStudent$varAttNull <- 
+  VarCorr(mdlStudent$lmeAttNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlStudent$tauAttNull <- 
+  as.numeric(mdlStudent$varAttNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlStudent$sigmaAttNull <- 
+  as.numeric(mdlStudent$varAttNull[2])
+# The ICC estimate (between/between+within) is:
+mdlStudent$IccAttNull <-
+  (as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))
+mdlStudent$IccPercAttNull <-
+  ((as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))) * 100
+```
+```{r studentModelInterceptAttType, include = FALSE}
+# Create and save Model
+mdlStudent$lmeInterceptAttType <-
+  lme(
+    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
+    random =  ~ 1 | PID,
+    data = dtStudentSupp$studentInteractionType
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlStudent$lmerInterceptAttType <- lmer(
+    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    data = dtStudentSupp$studentInteractionType
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlStudent$lmerInterceptAttTypeCI <- confint(mdlStudent$lmerInterceptAttType)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudent$lmeAttNull, 
+      mdlStudent$lmeInterceptAttType) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudent$varInterceptAttType <- 
+  lme4::VarCorr(mdlStudent$lmeInterceptAttType)
+```
+```{r studentModelSlopesInteractionType, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudent$lmeSlopesAttType <- lme(
+  AttitudesDutch ~
+    OutgroupInteraction + NonOutgroupInteraction,
+  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  data = dtStudentSupp$studentInteractionType
+)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudent$lmerSlopesAttType <- lmer(
+    AttitudesDutch ~
+      OutgroupInteraction + NonOutgroupInteraction +
+      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+    data = dtStudentSupp$studentInteractionType
+  ), 
+  confint = TRUE,
+  digits = 3
+)
+
+mdlStudent$lmerSlopesAttTypeCI <- confint(mdlStudent$lmerSlopesAttType)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudent$lmeAttNull,
+      mdlStudent$lmeInterceptAttType, 
+      mdlStudent$lmeSlopesAttType) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudent$varSlopesAttType <- 
+  lme4::VarCorr(mdlStudent$lmeSlopesAttType)
+
+# Assumption Checks:
+mdlStudent$diagSlopesAttType <-
+  sjPlot::plot_model(mdlStudent$lmerSlopesAttType, type = "diag")
+grid.arrange(
+  mdlStudent$diagSlopesAttType[[1]],
+  mdlStudent$diagSlopesAttType[[2]]$`PID`,
+  mdlStudent$diagSlopesAttType[[3]],
+  mdlStudent$diagSlopesAttType[[4]]
+)
+
+# Plot prediction model
+mdlStudent$predSlopesAttType <- 
+  dtStudentSupp$studentInteractionType %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlStudent$lmeSlopesAttType,
+                           dtStudentSupp$studentInteractionType,
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudent$predPltSlopesAttType <-
+    ggplot(data = mdlStudent$predSlopesAttType %>% filter(PID %in% dtStudentSupp$studentPltIDs), 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/Student_PredictionPlot_SlopesAttType.png",
+  mdlStudent$predPltSlopesAttType,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
+Thus, in our second dataset we find mixed results, outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
+However, we find that this effect does not depend on the average perceived interaction quality.
+However, this might be due to the aggregation process and the following analyses will focus in on the role of the perceived interaction quality during an outgroup interaction.
 

### 2021-10-26 Methods-and-Results.tex
AOT-S contac H results added

@@
 
+We tested the most general contact hypothesis in two steps. First, we
+assessed whether more intergroup interactions were related to to more
+positive outgroup attitudes. Second, we tested whether a potential
+positive effect on outgroup attitudes depended on the interaction
+quality (jointly with the number of interactions). We find a significant
+correlation with average outgroup attitudes for both the total number of
+outgroup interactions (\textit{r} = 0.22, \textit{p} = 0.019) and the
+number of measurement beeps with an interaction (\textit{r} = 0.28,
+\textit{p} = 0.003). This is to say that within our data, participants
+with more outgroup interactions did have significantly more positive
+outgroup attitudes. This is inconsistent with the results we found in
+the first study and might be due to the larger number of participants.
+
+However, we find no significant correlation between the participants'
+Average Interaction Quality and their Average Outgroup Attitudes
+(\textit{r} = 0.04, \textit{p} = 0.679). Thus, when considering the
+number of interactions and average interaction quality jointly in a
+linear regression, we a main effect of intergroup contacts to predict
+outgroup attitudes (\textit{b} = 0.81, \textit{t}(109) = 3.29,
+\textit{p} = 0.001, \(\eta_p^2\) = 0.08). Given the missing aggregate
+relationship between average interaction quality and outgroup attitudes,
+we find no significant effect of average perceived contact quality. Nor
+do we find that in this sample the impact of the number of interactions
+is moderated by the average contact quality. This is not entirely
+consistent with the first study, where average contact quality did have
+a meaningful effect on outgroup attitudes. This finding is not
+necessarily surprising given that the variables aggregate all within
+person variation and there were substantially more measurements where
+participants did not have an interaction (but reported their outgroup
+attitudes) than measurements that followed an outgroup contact.
+
+We additionally used a multilevel regression to check whether having an
+interaction with an outgroup member had a situational (i.e.,
+contemporaneous) effect within the participants. We find that having an
+outgroup interaction is indeed associated with significantly more
+positive outgroup attitudes within the participants (random slopes
+model; \textit{b} = 2.99, \textit{t}(4850) = 3.80, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}1.44, 4.56{]}), even after
+controlling for having an interaction with a non-Dutch (which did not
+relate to outgroup attitudes independently; For full results see Online
+Supplementary Materials B). Thus, in our second dataset we find mixed
+results, outgroup contacts show a positive effect on outgroup attitudes
+in the moment and on average between participants. However, we find that
+this effect does not depend on the average perceived interaction
+quality. However, this might be due to the aggregation process and the
+following analyses will focus in on the role of the perceived
+interaction quality during an outgroup interaction.
+
 \subsubsection{Core Need}

### 2021-10-26 Methods-and-Results.Rmd
AOT-S core need results added

@@
 \subsubsection{Core Need}
+```{r studentOutModelMLAttNull, include=FALSE}
+# create empty list to organize models
+mdlStudentOut <- 
+  list(
+    Att = list(),
+    Qlt = list()
+  )
+
+# Create and save Model
+mdlStudentOut$Att$lmerNull <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), 
+             data = dtStudentSupp$studentOutgroupInteraction) # use optim if it does not converge
+mdlStudentOut$Att$lmeNull <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = dtStudentSupp$studentOutgroupInteraction,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.ML.r) #or with the lme function
+summ(mdlStudentOut$Att$lmerNull, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlStudentOut$Att$varNull <- 
+  VarCorr(mdlStudentOut$Att$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlStudentOut$Att$tauNull <- 
+  as.numeric(mdlStudentOut$Att$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlStudentOut$Att$sigmaNull <- 
+  as.numeric(mdlStudentOut$Att$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlStudentOut$Att$IccNull <-
+  (as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))
+mdlStudentOut$Att$IccPercNull <-
+  ((as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))) * 100
+```
+```{r studentOutModelInterceptAttCore, include=FALSE}
+# Create and save Model
+mdlStudentOut$Att$lmeInterceptCore <-
+  lme(
+    AttitudesDutch ~ KeyNeedFullfillment_cwc,
+    random = ~ 1 | PID,
+    data = dtStudentSupp$studentOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlStudentOut$Att$lmerInterceptCore <-
+    lmer(
+      AttitudesDutch ~ KeyNeedFullfillment_cwc + (1 | PID),
+      data = dtStudentSupp$studentOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlStudentOut$Att$lmerInterceptCoreCI <- 
+  confint(mdlStudentOut$Att$lmerInterceptCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudentOut$Att$lmeNull, 
+      mdlStudentOut$Att$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Att$varInterceptCore <-
+  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCore)
+```
+```{r studentOutModelSlopesAttCore, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudentOut$Att$lmeSlopesCore <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFullfillment_cwc,
+    random = ~ 1 + KeyNeedFullfillment_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtStudentSupp$studentOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudentOut$Att$lmerSlopesCore <- lmer(
+    AttitudesDutch ~
+      KeyNeedFullfillment_cwc +
+      (1 + KeyNeedFullfillment_cwc | PID),
+    data = dtStudentSupp$studentOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# all variables standardized within PPT
+summ(
+  mdlStudentOut$Att$lmerSlopesCoreZ <- lmer(
+    AttitudesDutch_zwc ~
+      KeyNeedFullfillment_zwc +
+      (1 + KeyNeedFullfillment_zwc | PID),
+    data = dtStudentSupp$studentOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# standardized coefficients
+stdCoef.merMod(mdlStudentOut$Att$lmerSlopesCore)
+
+# 95%CIs
+mdlStudentOut$Att$lmerSlopesCoreCI <- confint(mdlStudentOut$Att$lmerSlopesCore)
+
+# Attempts at R^2
+r2mlm::r2mlm(mdlStudentOut$Att$lmerSlopesCore, bargraph = TRUE)
+mitml::multilevelR2(mdlStudentOut$Att$lmerSlopesCore)
+performance::r2(mdlStudentOut$Att$lmerSlopesCore)
+performance::model_performance(mdlStudentOut$Att$lmerSlopesCore)
+performance::compare_performance(mdlStudentOut$Att$lmerNull, 
+                                 mdlStudentOut$Att$lmerInterceptCore, 
+                                 mdlStudentOut$Att$lmerSlopesCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudentOut$Att$lmeNull, 
+      mdlStudentOut$Att$lmeInterceptCore, 
+      mdlStudentOut$Att$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Att$varSlopesCore <- 
+  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCore)
+
+# Assumption Checks:
+mdlStudentOut$Att$diagSlopesCore <- 
+  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlStudentOut$Att$diagSlopesCore[[1]],
+  mdlStudentOut$Att$diagSlopesCore[[2]]$`PID`,
+  mdlStudentOut$Att$diagSlopesCore[[3]],
+  mdlStudentOut$Att$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlStudentOut$Att$predSlopesCore <- 
+  dtStudentSupp$studentOutWithinBetween %>% 
+  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCore,
+                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudentOut$Att$predPltSlopesCore <-
+    ggplot(data = mdlStudentOut$Att$predSlopesCore, 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCore.png",
+  mdlStudentOut$Att$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+```{r studentOutModelMLQltNull, include=FALSE}
+# Create and save Model
+mdlStudentOut$Qlt$lmerNull <-
+  lme4::lmer(quality_overall ~ 1 + (1 | PID), 
+             data = dtStudentSupp$studentOutWithinBetween) # use optim if it does not converge
+mdlStudentOut$Qlt$lmeNull <-
+  mdlStudentOut$Qlt$lmeNull <-lme(
+    quality_overall ~ 1,
+    random = ~ 1 | PID,
+    data = dtStudentSupp$studentOutWithinBetween,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.Qual.ML.r) #or with the lme function
+summ(mdlStudentOut$Qlt$lmerNull, digits = 3)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlStudentOut$Qlt$varNull <- 
+  VarCorr(mdlStudentOut$Qlt$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlStudentOut$Qlt$tauNull <- 
+  as.numeric(mdlStudentOut$Qlt$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlStudentOut$Qlt$sigmaNull <- 
+  as.numeric(mdlStudentOut$Qlt$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlStudentOut$Qlt$IccNull <-
+  (as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))
+mdlStudentOut$Qlt$IccPercNull <-
+  ((as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))) * 100
+```
+```{r studentOutModelInterceptQltCore, include=FALSE}
+# Create and save Model
+mdlStudentOut$Qlt$lmeInterceptCore <-
+  lme(
+    quality_overall ~ KeyNeedFullfillment_cwc,
+    random = ~ 1 | PID,
+    data = dtStudentSupp$studentOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlStudentOut$Qlt$lmerInterceptCore <-
+    lmer(
+      quality_overall ~ KeyNeedFullfillment_cwc + (1 | PID),
+      data = dtStudentSupp$studentOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlStudentOut$Qlt$lmerInterceptCoreCI <- 
+  confint(mdlStudentOut$Qlt$lmerInterceptCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(quality_overall ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudentOut$Qlt$lmeNull, 
+      mdlStudentOut$Qlt$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Qlt$varInterceptCore <-
+  lme4::VarCorr(mdlStudentOut$Qlt$lmeInterceptCore)
+```
+```{r studentOutModelSlopesQltCore, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudentOut$Qlt$lmeSlopesCore <-
+  lme(
+    quality_overall ~
+      KeyNeedFullfillment_cwc,
+    random = ~ 1 + KeyNeedFullfillment_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtStudentSupp$studentOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudentOut$Qlt$lmerSlopesCore <-
+    lmer(
+      quality_overall ~
+        KeyNeedFullfillment_cwc +
+        (1 + KeyNeedFullfillment_cwc | PID),
+      data = dtStudentSupp$studentOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlStudentOut$Qlt$lmerSlopesCoreCI <- 
+  confint(mdlStudentOut$Qlt$lmerSlopesCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(mdlStudentOut$Qlt$lmerSlopesCore,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudentOut$Qlt$lmeNull, 
+      mdlStudentOut$Qlt$lmeInterceptCore, 
+      mdlStudentOut$Qlt$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Qlt$varSlopesCore <- 
+  lme4::VarCorr(mdlStudentOut$Qlt$lmeSlopesCore)
+
+# Assumption Checks:
+mdlStudentOut$Qlt$diagSlopesCore <-
+  sjPlot::plot_model(mdlStudentOut$Qlt$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlStudentOut$Qlt$diagSlopesCore[[1]],
+  mdlStudentOut$Qlt$diagSlopesCore[[2]]$`PID`,
+  mdlStudentOut$Qlt$diagSlopesCore[[3]],
+  mdlStudentOut$Qlt$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlStudentOut$Qlt$predSlopesCore <- 
+  dtStudentSupp$studentOutWithinBetween %>%
+  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlStudentOut$Qlt$lmeSlopesCore,
+                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudentOut$Qlt$predPltSlopesCore <-
+    ggplot(data = mdlStudentOut$Qlt$predSlopesCore %>% filter(PID %in% dtStudentSupp$studentOutPltIDs), 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/StudentOut_PredictionPlot_SlopesCore.png",
+  mdlStudentOut$Qlt$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+
+```
+```{r studentOutModelInterceptAttCoreQlt, include=FALSE}
+# Create and save Model
+mdlStudentOut$Att$lmeInterceptCoreQlt <-
+  lme(
+    AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc,
+    random = ~ 1 | PID,
+    data = dtStudentSupp$studentOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlStudentOut$Att$lmerInterceptCoreQlt <-
+    lmer(
+      AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc + (1 | PID),
+      data = dtStudentSupp$studentOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlStudentOut$Att$lmerInterceptCoreQltCI <- 
+  confint(mdlStudentOut$Att$lmerInterceptCoreQlt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlStudentOut$Att$lmeNull, 
+  mdlStudentOut$Att$lmeInterceptCoreQlt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Att$varInterceptCoreQlt <-
+  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreQlt)
+```
+```{r studentOutModelSlopesAttCoreQlt, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudentOut$Att$lmeSlopesCoreQlt <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFullfillment_cwc + quality_overall_cwc,
+    random = ~ 1 + KeyNeedFullfillment_cwc + quality_overall_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtStudentSupp$studentOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudentOut$Att$lmerSlopesCoreQlt <- lmer(
+    AttitudesDutch ~
+      KeyNeedFullfillment_cwc + quality_overall_cwc +
+      (1 + KeyNeedFullfillment_cwc + quality_overall_cwc | PID),
+    data = dtStudentSupp$studentOutWithinBetween,
+    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlStudentOut$Att$lmerSlopesCoreQltCI <- 
+  confint(mdlStudentOut$Att$lmerSlopesCoreQlt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlStudentOut$Att$lmeNull,
+  mdlStudentOut$Att$lmeInterceptCoreQlt,
+  mdlStudentOut$Att$lmeSlopesCoreQlt
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Att$varSlopesCoreQlt <- 
+  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreQlt)
+
+# Assumption Checks:
+mdlStudentOut$Att$diagSlopesCoreQlt <- 
+  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreQlt, type = "diag")
+grid.arrange(
+  mdlStudentOut$Att$diagSlopesCoreQlt[[1]],
+  mdlStudentOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
+  mdlStudentOut$Att$diagSlopesCoreQlt[[3]],
+  mdlStudentOut$Att$diagSlopesCoreQlt[[4]]
+)
+
+# Plot prediction model
+mdlStudentOut$Att$predSlopesCoreQlt <- 
+  dtStudentSupp$studentOutWithinBetween %>% 
+  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreQlt,
+                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudentOut$Att$predPltSlopesCoreQlt <-
+    ggplot(data = mdlStudentOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreQlt.png",
+  mdlStudentOut$Att$predPltSlopesCoreQlt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`).
+However, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`).
+These results are consistent with the results in study one and we thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
+
+\faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?
 

### 2021-10-26 Methods-and-Results.tex
AOT-S core need results added

@@
 
+We again sequentially tested whether the fulfillment of the core need
+during an interaction was (1) related to more positive outgroup
+attitudes, (2) higher perceived interaction quality, and (3) whether the
+variance explained by the core need is assumed by the perceived
+interaction quality if considered jointly. We find that in the
+multilevel models, the fulfillment of core situational needs during
+outgroup contacts was associated with more positive outgroup attitudes
+(random slopes model; \textit{b} = 0.13, \textit{t}(826) = 4.18,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.19{]}) and also
+predicted higher perceived interaction quality (random slopes model;
+\textit{b} = 0.40, \textit{t}(826) = 6.46, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.28, 0.53{]}). However, if we consider the influences
+of core need fulfillment and interaction quality on outgroup attitudes
+jointly, we find that virtually all variance is explained by perceived
+interaction quality (random slopes mode; \textit{b} = 0.17,
+\textit{t}(825) = 5.56, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.11, 0.23{]}) and only little unique variance is
+still explained by core need fulfillment (\textit{b} = 0.03,
+\textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
+0.08{]}). These results are consistent with the results in study one and
+we thus find support for our hypotheses and can conclude that in this
+data set the fulfillment of core situational needs had a significant
+influence on outgroup attitudes and that this effect is likely explained
+by its effect through perceived interaction quality.
+
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
+
 \subsubsection{Robustness}

### 2021-10-26 Methods-and-Results.Rmd
AOT-P results added

@@
 # Model comparison
-SdtComp <-
+workerSdtComp <-
   anova(
@@
   as.data.frame()
-SdtCompDf <- SdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Df"]
-SdtCompN <- sapply(ranef(mdlWorkerOut$Att$lmerSlopesCoreSdt), nrow)
-SdtCompP <-
-  ifelse(SdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
+workerSdtCompDf <- workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Df"]
+workerSdtCompN <- sapply(ranef(mdlWorkerOut$Att$lmerSlopesCoreSdt), nrow)
+workerSdtCompChi <- workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
+workerSdtCompP <-
+  ifelse(workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
          "< .001",
-         paste0("= ", SdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
-
-SdtCompChiSq <- paste0("$\\chi^2$(", SdtCompDf, ", \\textit{N} = ", SdtCompN, "), \\textit{p} ", SdtCompP)
+         paste0("= ", workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
+
+workerSdtCompChiSq <- paste0("$\\chi^2$(", workerSdtCompDf, ", \\textit{N} = ", workerSdtCompN, ") = ", workerSdtCompChi, ", \\textit{p} ", workerSdtCompP)
 ```
@@
 We focus on the three commonly considered self determination needs: competence, autonomy, and relatedness.
-We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r SdtCompChiSq`).
+We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r workerSdtCompChiSq`).
 We find that next to relatedness (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "relatedness_1_cwc")`), the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "keymotive_fulfillemt_1_cwc")`).
@@
 \subsubsection{Robustness}
-
-\paragraph{interaction type}
-
-\paragraph{other needs}
+```{r studentModelInterceptAttCoreInt, include=FALSE}
+# Create and save Model
+mdlStudent$lmeInterceptAttCoreInt <-
+  lme(
+    AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction,
+    random =  ~ 1 | PID,
+    data = dtStudentSupp$studentWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlStudent$lmerInterceptAttCoreInt <- lmer(
+    AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction + (1 | PID),
+    data = dtStudentSupp$studentWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlStudent$lmerInterceptAttCoreIntCI <- 
+  confint(mdlStudent$lmerInterceptAttCoreInt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=dtStudent$full),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudent$lmeAttNull, 
+      mdlStudent$lmeInterceptAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = c("l", rep("c", ncol(.)-1)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudent$varInterceptAttCoreInt <- 
+  lme4::VarCorr(mdlStudent$lmeInterceptAttCoreInt)
+```
+```{r studentModelSlopesAttCoreIntX, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudent$lmeSlopesAttCoreInt <- lme(
+  AttitudesDutch ~
+    KeyNeedFullfillment_cwc * OutgroupInteraction,
+  random = ~ 1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  data = dtStudentSupp$studentWithinBetween
+)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudent$lmerSlopesAttCoreInt <- lmer(
+    AttitudesDutch ~
+      KeyNeedFullfillment_cwc * OutgroupInteraction +
+      (1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID),
+    data = dtStudentSupp$studentWithinBetween
+  ), 
+  confint = TRUE,
+  digits = 3
+)
+
+mdlStudent$lmerSlopesAttCoreIntCI <- 
+  confint(mdlStudent$lmerSlopesAttCoreInt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudent$lmeAttNull, 
+      mdlStudent$lmeInterceptAttCoreInt,
+      mdlStudent$lmeSlopesAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudent$varSlopesAttCoreInt <- 
+  lme4::VarCorr(mdlStudent$lmeSlopesAttCoreInt)
+
+# Assumption Checks:
+mdlStudent$diagSlopesAttCoreInt <-
+  sjPlot::plot_model(mdlStudent$lmerSlopesAttCoreInt, type = "diag")
+grid.arrange(
+  mdlStudent$diagSlopesAttCoreInt[[1]],
+  mdlStudent$diagSlopesAttCoreInt[[2]]$`PID`,
+  mdlStudent$diagSlopesAttCoreInt[[3]],
+  mdlStudent$diagSlopesAttCoreInt[[4]]
+)
+
+# Plot prediction model
+mdlStudent$predSlopesAttCoreInt <- 
+  dtStudentSupp$studentWithinBetween %>%
+  filter(PID %in% dtStudentSupp$studentPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlStudent$lmeSlopesAttCoreInt,
+                           dtStudentSupp$studentWithinBetween %>% filter(PID %in% dtStudentSupp$studentPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudent$predPltSlopesAttCoreInt <-
+    ggplot(data = mdlStudent$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/Student_PredictionPlot_SlopesAttCoreInt.png",
+  mdlStudent$predPltSlopesAttCoreInt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We again checked for alternative models.
+First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is only a minuscule main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc:OutgroupInteractionYes")`).
+Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteractionYes")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+This finding is consistent with the results of the previous study, albeit with slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction).
+
+```{r studentOutModelInterceptAttCoreSdt, include=FALSE}
+# Create and save Model
+mdlStudentOut$Att$lmeInterceptCoreSdt <-
+  lme(
+    AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 | PID,
+    data = dtStudentSupp$studentOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlStudentOut$Att$lmerInterceptCoreSdt <- lmer(
+    AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
+    data = dtStudentSupp$studentOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# To be compared against a model with only the self determination theory needs
+mdlStudentOut$Att$lmeInterceptSdt <-
+  lme(
+    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 | PID,
+    data = dtStudentSupp$studentOutWithinBetween,
+    na.action = na.exclude
+  )
+
+summ(
+  mdlStudentOut$Att$lmerInterceptSdt <- lmer(
+    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
+    data = dtStudentSupp$studentOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Compare new model to previous steps
+anova(
+  mdlStudentOut$Att$lmeInterceptSdt,
+  mdlStudentOut$Att$lmeInterceptCoreSdt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+rm(lmeInterceptCoreRed)
+
+# Save variances
+mdlStudentOut$Att$varInterceptCoreSdt <-
+  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreSdt)
+```
+```{r studentOutModelSlopesAttCoreSdt, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudentOut$Att$lmeSlopesCoreSdt <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 + KeyNeedFullfillment_cwc + Competence_cwc + Relatedness_cwc | PID,
+    control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
+    data = dtStudentSupp$studentOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudentOut$Att$lmerSlopesCoreSdt <- lmer(
+    AttitudesDutch ~
+      KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = dtStudentSupp$studentOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlStudentOut$Att$lmerSlopesCoreSdtCI <- 
+  confint(mdlStudentOut$Att$lmerSlopesCoreSdt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlStudentOut$Att$lmeInterceptSdt,
+      mdlStudentOut$Att$lmeInterceptCoreSdt, 
+      mdlStudentOut$Att$lmeSlopesCoreSdt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# model with SDT only
+# Create and save Model (optimizer needed to reach convergence)
+mdlStudentOut$Att$lmeSlopesSdt <-
+  lme(
+    AttitudesDutch ~
+      Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtStudentSupp$studentOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlStudentOut$Att$lmerSlopesSdt <- lmer(
+    AttitudesDutch ~
+      Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = dtStudentSupp$studentOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Compare new model to previous step
+anova(mdlStudentOut$Att$lmeInterceptSdt,
+      mdlStudentOut$Att$lmeSlopesSdt, 
+      mdlStudentOut$Att$lmeSlopesCoreSdt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlStudentOut$Att$varSlopesCoreSdt <- 
+  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreSdt)
+
+# Assumption Checks:
+mdlStudentOut$Att$diagSlopesCoreSdt <- 
+  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreSdt, type = "diag")
+grid.arrange(
+  mdlStudentOut$Att$diagSlopesCoreSdt[[1]],
+  mdlStudentOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
+  mdlStudentOut$Att$diagSlopesCoreSdt[[3]],
+  mdlStudentOut$Att$diagSlopesCoreSdt[[4]]
+)
+
+# Plot prediction model
+mdlStudentOut$Att$predSlopesCoreSdt <- 
+  dtStudentSupp$studentOutWithinBetween %>%
+  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID, Autonomy) %>% 
+  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreSdt,
+                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlStudentOut$Att$predPltSlopesCoreSdt <-
+    ggplot(data = mdlStudentOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreStd.png",
+  mdlStudentOut$Att$predPltSlopesCoreSdt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+
+# Model comparison
+studentSdtComp <-
+  anova(
+    mdlStudentOut$Att$lmerSlopesSdt, 
+    mdlStudentOut$Att$lmerSlopesCoreSdt
+  ) %>%
+  as.data.frame()
+studentSdtCompDf <- studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Df"]
+studentSdtCompN <- sapply(ranef(mdlStudentOut$Att$lmerSlopesCoreSdt), nrow)
+studentSdtCompChi <- studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
+studentSdtCompP <-
+  ifelse(studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
+         "< .001",
+         paste0("= ", studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
+
+studentSdtCompChiSq <- paste0("$\\chi^2$(", studentSdtCompDf, ", \\textit{N} = ", studentSdtCompN, ") = ", studentSdtCompChi, ", \\textit{p} ", studentSdtCompP)
+```
+
+In a final step we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
+We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r studentSdtCompChiSq`).
+We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFullfillment_cwc")`).
+When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
+However, different from the first study, in this larger study relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) predicted positive outgroup attitudes.
+For full results see Online Supplementary Information B.
 

### 2021-10-28 Methods-and-Results.Rmd
Update Methods-and-Results.Rmd

@@
   )
+
 dtWorkerSupp$workerOutWithinBetween <-

### 2021-10-29 PreregristrationS3/PreregistrationAOT-M.Rmd
pre-reg fix 1

@@
     a. \label{hyp:contactFreq}Participants with more intergroup interactions should have a more favorable outgroup attitudes.
-    b. \label{hyp:contactDummy}Outgroup attitudes should be higher after an intergroup interaction compared to a non-outgroup interaction.
+    b. \label{hyp:contactDummy}Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
     c. \label{hyp:contactFreqQual}Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
@@
     b. \label{hyp:keyNeedQual}Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
-    c. \label{hyp:keyNeedMediation}The variance explained in outgroup attitudes by key need fulfillment should to a large extend be assumed by interaction quality.
+    c. \label{hyp:keyNeedMediation}The variance explained in outgroup attitudes by key need fulfillment should to a large extend be explained by interaction quality.
     d.
@@
 Given the (expectedly) large sample size of contemporaneous measurements, we will remove all instances during which a participant did not respond to any of the relevant variables.
+Given that we are not necessarily interested in individual trajectories in our analyses, we will use all available data (i.e., will not remove entire participants but rather individual incomplete daily diary measurements).
 
@@
 We have data to test this hypothesis within a large intensive longitudinal dataset of daily intergroup interactions.
-We do this by seperately assessing attitudes towards the outgroup interaction partner and the outgroup generally.
+We do this by separately assessing attitudes towards the outgroup interaction partner and the outgroup generally.
 And by assessing whether perceiving the interaction as representative of the outgroup moderates the positive contact effects.

### 2021-11-02 Methods-and-Results.tex
re render

@@
 with only the self determination theory needs (random slopes models;
-\(\chi^2\)(6, \textit{N} = 21), \textit{p} = 0.003). We find that next
-to relatedness (\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the core need
-explains the most variance in outgroup attitudes after an outgroup
+\(\chi^2\)(6, \textit{N} = 21) = 19.60, \textit{p} = 0.003). We find
+that next to relatedness (\textit{b} = 0.10, \textit{t}(361) = 4.04,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the core
+need explains the most variance in outgroup attitudes after an outgroup
 contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p} = 0.026,
@@
 
-\paragraph{interaction type}
+We again checked for alternative models. First, when considering
+generalized situational core need fulfillment together with whether an
+intergroup contact took place, we find that there is only a minuscule
+main effect of core need fulfillment (random slopes model; \textit{b} =
+0.03, \textit{t}(4849) = 3.06, \textit{p} = 0.002,
+\textit{95\%CI}{[}0.01, 0.05{]}) but a stronger interaction effect of
+core need fulfillment and outgroup contact (\textit{b} = 0.06,
+\textit{t}(4849) = 3.03, \textit{p} = 0.002, \textit{95\%CI}{[}0.02,
+0.10{]}). Together with a significant main effect of having an outgroup
+contact (\textit{b} = 2.88, \textit{t}(4849) = 3.71, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}1.35, 4.42{]}), this indicates that
+it is not key need fulfillment in general --- but key need fulfillment
+during an outgroup contact that predicts more positive outgroup
+attitudes. This finding is consistent with the results of the previous
+study, albeit with slightly weaker effect (likely because of the large
+number of measurements that did not include an outgroup interaction).
 
-\paragraph{other needs}
+In a final step we again checked whether during the interaction the core
+situational need remains a meaningful predictor even when taking other
+fundamental psychological needs into account. We find that the core need
+adds significantly above a model with only the self determination theory
+needs (random slopes models; \(\chi^2\)(6, \textit{N} = 108) = 22.90,
+\textit{p} \textless{} .001). We find that the core need explains the
+most variance in outgroup attitudes after an outgroup contact
+(\textit{b} = 0.08, \textit{t}(823) = 2.95, \textit{p} = 0.003,
+\textit{95\%CI}{[}0.02, 0.14{]}). When compared to the model with only
+the SDT needs, the core need fulfillment flexibly takes on some of the
+explained variance of all of the three fundamental needs. However,
+different from the first study, in this larger study relatedness
+(\textit{b} = 0.07, \textit{t}(823) = 4.26, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.04, 0.10{]}) and autonomy (\textit{b} = 0.02,
+\textit{t}(823) = 0.93, \textit{p} = 0.353, \textit{95\%CI}{[}-0.03,
+0.08{]}) predicted positive outgroup attitudes. For full results see
+Online Supplementary Information B.
 

### 2021-11-02 PreregristrationS3/PreregistrationAOT-M.Rmd
equation first fix
pre-registration formulas ML corrected

@@
   chunk_output_type: console
+header-includes:
+   - \usepackage{amsmath, nccmath}
 ---
@@
 
-1. Contact Hypothesis (using between participant aggregates only to meaningfully include interaction frequency)
-    a. Correlation: $r_{InteractionFrequency, OutgroupAttitudes} \neq 0$
-    a.
-T-test: $\mu_{i,0utgroupInteraction} > \mu_{i,IngroupInteraction}$ (to build confidence in the persistence of the contact effect, we additionally compare the attitudes after an outgroup interaction to attitudes after no outgroup interaction (i.e., including instances where participants had no interaction at all).)
-    a. Regression: $Attitude = ContactFreq \times AverageContactQual$
+\setlength{\abovedisplayskip}{0pt}
+\setlength{\belowdisplayskip}{0pt}
+\setlength{\abovedisplayshortskip}{0pt}
+\setlength{\belowdisplayshortskip}{0pt}
+
+1. Contact Hypothesis (partially using between participant aggregates to meaningfully include interaction frequency)
+    a. Correlation:
+      \begin{fleqn}[\parindent] 
+        \begin{equation}
+          r_{ContactFreq, Attitude} \neq 0
+        \end{equation}
+      \end{fleqn}
+    a. Regression:
+        <!-- 
+          Explanation: 
+          - 'fleqn' aligns whole math left 
+          - 'equation' adds number
+          - 'split' aligns after level header
+          - 'aligned[t]' aligns after equal sign
+        -->
+        \begin{fleqn}[\parindent] 
+        \begin{equation}
+          \begin{split}
+            \textrm{Level 1:} &
+              \begin{aligned}[t]
+                \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
+                                   &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
+              \end{aligned} \\
+            \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                              &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                              &\ \beta_{2i} = \gamma_{20} + u_{2i}
+          \end{split} 
+        \end{equation}
+        \end{fleqn}
+    a. Regression: 
+      \begin{fleqn}[\parindent] 
+        \begin{equation}
+          Attitude = ContactFreq \times AverageQual
+        \end{equation}
+      \end{fleqn}
 1. Allport's Conditions
-    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}AllportConditions_{ti} + u_{0i} + u_{1i} + e_{ti}$
-    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}AllportConditions_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}$
+    a. Regression:
+        \begin{fleqn}[\parindent]
+          \begin{equation} \label{eq:SlopesAttAllport}
+            \begin{split}
+                \textrm{Level 1:} &\ Attitude_{ti} = \beta_{0i} + \beta_{1i}AllportConditions_{ti} + e_{ti}\\
+                \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                                  &\ \beta_{1i} = \gamma_{10} + u_{1i}
+            \end{split}
+          \end{equation}
+        \end{fleqn}
+    a. Regression:
+        \begin{fleqn}[\parindent]
+          \begin{equation} \label{eq:SlopesQualAllport}
+            \begin{split}
+                \textrm{Level 1:} &\ InteractionQuality_{ti} = \beta_{0i} + \beta_{1i}AllportConditions_{ti} + e_{ti}\\
+                \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                                  &\ \beta_{1i} = \gamma_{10} + u_{1i}
+            \end{split}
+          \end{equation}
+        \end{fleqn}
+    a. Regression:
+        \begin{fleqn}[\parindent]
+          \begin{equation} \label{eq:SlopesAttAllportQual}
+            \begin{split}
+              \textrm{Level 1:} &
+                \begin{aligned}[t]
+                  \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}AllportConditions_{ti} + \\
+                                     &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+                \end{aligned} \\
+              \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                                &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                                &\ \beta_{2i} = \gamma_{20} + u_{2i}
+            \end{split} 
+          \end{equation}
+        \end{fleqn}  
+1. Key Need Fulfillment
+    a. Regression: 
+        \begin{fleqn}[\parindent]
+          \begin{equation} \label{eq:SlopesAttCore}
+            \begin{split}
+                \textrm{Level 1:} &\ Attitude_{ti} = \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}\\
+                \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                                  &\ \beta_{1i} = \gamma_{10} + u_{1i}
+            \end{split}
+          \end{equation}
+        \end{fleqn}
+    a. Regression:
+        \begin{fleqn}[\parindent]
+          \begin{equation} \label{eq:SlopesQltCore}
+            \begin{split}
+                \textrm{Level 1:} &\ InteractionQuality_{ti} = \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}\\
+                \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                                  &\ \beta_{1i} = \gamma_{10} + u_{1i}
+            \end{split}
+          \end{equation}
+        \end{fleqn}
+    a. Regression:
+        \begin{fleqn}[\parindent]
+          \begin{equation} \label{eq:SlopesAttCoreQual}
+            \begin{split}
+              \textrm{Level 1:} &
+                \begin{aligned}[t]
+                  \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                                     &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+                \end{aligned} \\
+              \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                                &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                                &\ \beta_{2i} = \gamma_{20} + u_{2i}
+            \end{split} 
+          \end{equation}
+        \end{fleqn}
+    a. Regression: 
+        \begin{fleqn}[\parindent]
+          \begin{equation} \label{eq:SlopesAttCoreQualX}
+            \begin{split}
+              \textrm{Level 1:} &
+                \begin{aligned}[t]
+                  \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                                     &\ \beta_{2i}InteractionQuality_{ti} + \\
+                                     &\ \beta_{3i}KeyNeedFulfill*InteractionQuality_{ti} + e_{ti}
+                \end{aligned} \\
+              \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                                &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                                &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                                &\ \beta_{3i} = \gamma_{30} + u_{3i}
+            \end{split} 
+          \end{equation}
+        \end{fleqn}
+    a. Regression: 
+        \begin{fleqn}[\parindent]
+          \begin{equation} \label{eq:SlopesAttCoreSdt}
+            \begin{split}
+              \textrm{Level 1:} &
+                \begin{aligned}[t]
+                  \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \beta_{2i}Autonomy_{ti} + \\
+                                     &\ \beta_{3i}Competence_{ti} + \beta_{4i}Relatedness_{ti} + e_{ti}
+                \end{aligned} \\
+              \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                                &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                                &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                                &\ \beta_{3i} = \gamma_{30} + u_{3i} \\
+                                &\ \beta_{4i} = \gamma_{40} + u_{4i}
+            \end{split} 
+          \end{equation}
+        \end{fleqn}
+1. Comparison with Allport's Conditions
+    a. Model Comparison:
+      \begin{fleqn}[\parindent] 
+        \begin{equation}
+          AIC_{KeyNeedModel} < AIC_{AllportModel}
+        \end{equation}
+      \end{fleqn}
+    a. Regression: 
+        \begin{fleqn}[\parindent]
+          \begin{equation} \label{eq:SlopesAttCoreAllport}
+            \begin{split}
+              \textrm{Level 1:} &
+                \begin{aligned}[t]
+                  \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                                     &\ \beta_{2i}AllportConditions_{ti} + e_{ti}
+                \end{aligned} \\
+              \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                                &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                                &\ \beta_{2i} = \gamma_{20} + u_{2i}
+            \end{split} 
+          \end{equation}
+        \end{fleqn}
 
-        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
-1. Key Need Fulfillment
-    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}$
-    a. Regression: $InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}$
-    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}$
-    a. Regression: $Attitude_{ti} = KeyNeedFulfill_{ti} \times OutgroupInteraction_{ti} + u_{0i} + u_{1i} + e_{ti}$
-    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + u_{1i} + e_{ti}$
+All multilevel assumptions are tested as usual including (e.g., for random slopes model with _j_ within person predictors):
 
-        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
-1. Comparison with Allport's Conditions
-    a. Model Comparison: $AIC_{KeyNeedModel} > AIC_{AllportModel}$
-    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}AllportConditions_{ti} + u_{0i} + u_{1i} + e_{ti}$
-
-        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
+\begin{flalign}
+  &\textrm{Level 1 Variance:}\ e_{ti} \sim \mathcal{N}(0,\sigma^2) \\
+  &\textrm{Level 2 Variance:}\ \begin{bmatrix} u_{0i}\\ \vdots\\ u_{ji}\end{bmatrix} 
+  \sim \mathcal{N}
+  \begin{pmatrix}
+    \begin{bmatrix} 
+      0 \\ 
+      \vdots \\
+      0
+    \end{bmatrix}, 
+    \begin{bmatrix} 
+      \tau_{00}^2 &  & \\ 
+      \vdots & \ddots & \\
+      \tau_{j0} & \ldots & \tau_{jj}^2
+    \end{bmatrix}
+  \end{pmatrix}
+\end{flalign}
 

### 2021-11-03 Supplemental-Material-B-Annotated-Analysis.Rmd
methods and results re-run

@@
 dtMedical <- list(
-  raw.pre = c(),
-  raw.post = c(),
-  raw.daily = c()
+  raw.eligibility = read.csv("data/S3_Medical/raw/AOTM_Eligibility.csv"),
+  raw.pre = read.csv("data/S3_Medical/raw/AOTM_Pre.csv"),
+  raw.post = read.csv("data/S3_Medical/raw/AOTM_Post.csv"),
+  raw.daily = read.csv("data/S3_Medical/raw/AOTM_Daily.csv")
 )
@@
 
-To be done after preregistration.
+For the medical professionals sample data was, again, collected in three separate surveys: (1) the pre-measurement, (2) the daily survey sent out at lunch and dinner time, and (3) a post-measurement.
+We combine the three individual surveys into one large dataframe.
+We exclude our own test data.
+We also reformat missing values and format core ID variables.
+<i class="fas fa-info-circle"></i> _Note:_ All data preparation steps are saved in the '_dtMedical_' list.
 
 ```{r cleanMedical}
-# TBD
+# our own test IDs
+ownIDs <- c(
+  "test_LeonieXXXSklxecPLW0-FBPM4796o3pUwUhAY5jb9KGw8jQsKxWmGpa1Jiy", 
+  "test_MaxXXXtOp_5dTNefIq0yKXtXt2IN6eEKxeHoPY9mlyvdsqPpLp1B0NGg4UL",
+  "test_JannisXXXBsNqk62fOpX6chbd2tMWPptUdjjnhAqnQ3uBqckZ7gLIEoPlfZ",
+  "quaintLeopardCatXXXAJ9cfSj-_SZLwNwMDxv_xv_iyr1Bg5YFLTlYdrjW0UXZY",
+  "blue-eyedIndianElephantXXXLf5zPMpQCDGS3umFzIj-YVky7ivTItvvozW49m"
+)
+
+# Prepare dfs for Cleaning
+df.pre <- dtMedical$raw.pre %>%
+  mutate_all(na_if, "") %>%
+  mutate_all(na_if, "NA") %>%
+  filter(!is.na(ended)) %>% # remove all who did not finish
+  filter(!session %in% ownIDs) %>% # remove our own test
+  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)
+
+df.post <- dtMedical$raw.post %>%
+  mutate_all(na_if, "") %>%
+  mutate_all(na_if, "NA") %>% 
+  filter(!is.na(session)) %>% # remove own test runs
+  filter(!session %in% ownIDs) %>% # remove our own test
+  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
+  #filter(!is.na(ended)) %>% # remove all who never finished [disabled because only relevant if data is missing]
+  filter(!session %in% .$session[duplicated(.$session)]) %>% # remove all duplicate sessions
+  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)
+
+df.daily <- dtMedical$raw.daily %>%
+  mutate_all(na_if, "") %>%
+  mutate_all(na_if, "NA") %>%
+  filter(!session %in% ownIDs) %>% # remove our own test
+  filter(session %in% df.pre$session) %>% # remove anyone who wasn't in the pre
+  #filter(!is.na(ended)) %>% # remove all who never finished [disabled because only relevant if data is missing]
+  mutate(session = as.character(session)) # turn factor into character strings (probably just precaution)
+
+# merge daily with pre
+dfPreDaily <- merge(
+  x = df.daily,
+  y = df.pre,
+  by = "session",
+  suffixes = c(".daily", ".pre"),
+  all = F
+)
+
+# merge daily with post
+dfCombined <- merge(
+  x = dfPreDaily,
+  y = df.post,
+  by = "session",
+  suffixes = c(".pre", ".post"),
+  all = F
+)
+
+# add to list
+dtMedical$clean <- dfCombined
+
+# clean up workspace
+rm(df.pre, df.daily, df.post, dfPreDaily, dfCombined, ownIDs)
 ```
@@
 
-For the worker sample, the data transformation stage had three main aims:
+For the student sample, the data transformation stage had five main aims:
 
@@
 
-To be done after preregistration.
+For the medical professional sample, the data transformation stage had five main aims:
+
+1. We first create person, survey type, and measurement ID variables.   
+2.
+We then created indices of scales.
+Some indices were multi-item scales while some indices combine equivalent measurement for different situational circumstances (e.g., competence perceptions after interactions and at measurement occasions without interactions).
+3. We cluster mean-center key variables within participants.   
+4. Finally, we calculated several basic participant summaries (averages across all measurement occasions).
 
 ```{r newVarsMedical}
-# TBD
+df <- dtMedical$clean
+
+# Add ID variables
+df$PID <- as.numeric(factor(df$session)) # participant ID
+
+# order time
+df$TID <-
+  factor(df$date_period, levels = unique(dtMedical$raw.daily$date_period))
+df$TIDnum <- as.numeric(df$TID) # get numeric TID
+
+# check whether time ordering worked
+df <- df %>%
+  arrange(PID, TID) # %>%
+# View()
+
+# Interaction as Factor
+df$interaction.f <-
+  factor(df$Interaction,
+    levels = c("no interaction", "Dutch", "Non-Dutch")
+  )
+df$intNL <- ifelse(df$Interaction == "Dutch", 1, 0)
+df$intNonNL <- ifelse(df$Interaction == "Non-Dutch", 1, 0)
+
+# -------------------------------------------------------------------------------------------------------------
+#                                       Combine Variables
+# -------------------------------------------------------------------------------------------------------------
+# Relatedness
+pairs.panels.new(
+  df[c("RelatednessSelf", "RelatednessOther")],
+  labels = c(
+    "I shared information about myself.",
+    "X shared information about themselves."
+  )
+)
+df$RelatednessInteraction <-
+  rowMeans(df[c("RelatednessSelf", "RelatednessOther")], na.rm = T)
+df$RelatednessInteraction[df$RelatednessInteraction == "NaN"] <-
+  NA
+# Relatedness Overall (JANNIS NOT SURE THESE ARE CORRECT, CHANGE ROWS?; J: Changed "NaN" in df$RelatednessInteraction to NA() should work now)
+df$Relatedness <-
+  rowMeans(df[, c("RelatednessInteraction", "RelatednessNoInteraction")],
+           na.rm = TRUE)
+# Pro-Sociality
+df$ProSo <-
+  rowMeans(df[, c("ProSo1", "ProSo2", "ProSo3", "ProSo4")], na.rm = T)
+# Anti-Sociality
+df$AntiSo <-
+  rowMeans(df[, c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm = T)
+
+# -------------------------------------------------------------------------------------------------------------
+#                                 Add Variables related to interaction partner
+# -------------------------------------------------------------------------------------------------------------
+# create function for later lapply
+createIntPartDf <- function(inp) {
+  # prepare the dataframe so that we can forloop over it later
+  tmp <- data.frame(
+    CC = as.character(inp$CC),
+    NewCC = as.character(inp$NewCC),
+    NewName = as.character(inp$NewName),
+    NewCloseness = inp$NewCloseness,
+    NewGender = inp$NewGender,
+    NewEthnicity = as.character(inp$NewEthnicity),
+    NewRelationship = as.character(inp$NewRelationship)
+  )
+
+  tmp$CC2 <- recode(tmp$CC, "SOMEONE ELSE" = "NA")
+  tmp$CC2 <-
+    ifelse(
+      tmp$CC == 1 |
+        tmp$CC == "SOMEONE ELSE",
+      as.character(tmp$NewName),
+      as.character(tmp$CC2)
+    )
+  # maybe add [[:space:]]\b to remove space before word boundary or ^[[:space:]] to remove space in the beginning of a string
+  tmp$CC2 <- gsub("^[[:space:]]", "", tmp$CC2)
+  tmp$NewName <- gsub("^[[:space:]]", "", tmp$NewName)
+
+  # open the variables that will be filled up in the foor-loop
+  tmp$closeness <- rep(NA, nrow(tmp))
+  tmp$gender <- rep(NA, nrow(tmp))
+  tmp$ethnicity <- rep(NA, nrow(tmp))
+  tmp$relationship <- rep(NA, nrow(tmp))
+
+  # Run the for-loop. It finds the variables related to the name of the interaction partner. If there is a repeating interaction
+  # partner (i.e. CC2) it takes the value (i.e. NewCloseness) from the first interaction (i.e. NewName)
+  for (i in 1:nrow(tmp)) {
+    if (is.na(tmp$CC2[i])) {
+      next
+    } else {
+      tmp$closeness[i] <-
+        na.omit(tmp$NewCloseness[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] # find closeness where CC2 matches NewName (na.omit + [1] to get the number)
+      tmp$gender[i] <-
+        na.omit(tmp$NewGender[as.character(tmp$CC2[i]) == as.character(tmp$NewName)])[1] # (na.omit + [1] to get the number and not the rest of the na.omit list)
+      tmp$ethnicity[i] <-
+        na.omit(as.character(tmp$NewEthnicity[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1] # PROBLEM IS THAT THERE ARE TOO MANY NA's: Difficult to deal with
+      tmp$relationship[i] <-
+        na.omit(as.character(tmp$NewRelationship[as.character(tmp$CC2[i]) == as.character(tmp$NewName)]))[1]
+    }
+  }
+
+  out <- tmp
+  out
+}
+
+# split df per participants and run function
+PP <- split(df, df$PID)
+PP <- lapply(PP, createIntPartDf)
+rm(createIntPartDf)
+
+# add variables back to df
+remergePP <- do.call(rbind.data.frame, PP)
+colnames(remergePP) <-
+  paste(colnames(remergePP), "_Calc", sep = "")
+df <- cbind(df, remergePP)
+rm(remergePP, PP)
+
+```
+
+```{r newVarsStudents}
+
+# -------------------------------------------------------------------------------------------------------------
+#                                 Center Relevant Variables
+# -------------------------------------------------------------------------------------------------------------
+
+df <- df %>%
+  group_by(PID) %>%
+  mutate(
+    KeyNeedFullfillment.cm = mean(KeyNeedFullfillment, na.rm = TRUE),
+    # cluster mean (mean of PP)
+    KeyNeedFullfillment.cwc = KeyNeedFullfillment - KeyNeedFullfillment.cm,
+    # cluster mean centered (within PP centered)
+    closeness.cm = mean(closeness_Calc, na.rm = TRUE),
+    closeness.cwc = closeness_Calc - closeness.cm
+  ) %>%
+  ungroup()
+
+# store
+dtStudents$full <- df
+rm(df)
+
+# Between participants contact frequency
+studentContactFreq <- dtStudents$full %>%
+  group_by(PID) %>%
+  summarise(
+    n = n(),
+    SumContactNL = sum(InteractionDumDutch),
+    PercContactNL = SumContactNL / n * 100,
+    SumContactNLAll = sum(ContactNum[InteractionDumDutch == 1], na.rm = TRUE),
+    AvAttitude = mean(AttitudesDutch, na.rm = TRUE),
+    AvQuality = mean(quality_overall, na.rm = TRUE)
+  ) %>%
+  mutate(
+    WinSumContactNL = DescTools::Winsorize(SumContactNL),
+    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
+  )
+
+# dataframe where interaction types are recoded
+studentInteractionType <- dtStudents$full %>%
+  mutate(
+    NonDutchContact = replace_na(NonDutchContact, 2), # make second non-Dutch countable
+    NonDutchContact = NonDutchContact*-1+2 # recode (yes = 1 -> 1, no = 2 -> 0)
+  ) %>%
+  mutate(
+    OutgroupInteraction = factor(
+      InteractionDumDutch,
+      levels = c(0, 1),
+      labels = c("No", "Yes")
+    ),
+    NonOutgroupInteraction = factor(
+      rowSums(select(., c(InteractionDumNonDutch, NonDutchContact))), # combine the two non-Dutch Q.,
+      levels = c(0, 1),
+      labels = c("No", "Yes")
+    )
+  )
+
+# select a subset of IDs to display in plots
+studentPltIDs <-
+  studentInteractionType %>%
+  group_by(PID) %>%
+  summarise(n = n()) %>%
+  slice_max(n, n = 20) %>% # chose the 20 with the most number of measurements
+  select(PID) %>%
+  as.matrix %>%
+  as.vector
+
+# select a subset of IDs to display in plots (only outgroup interactions)
+studentOutPltIDs <-
+  studentInteractionType %>%
+  filter(OutgroupInteraction == "Yes") %>%
+  group_by(PID) %>%
+  summarise(n = n()) %>%
+  slice_max(n, n = 20) %>% # chose the 20 with the most number of measurements
+  select(PID) %>%
+  as.matrix %>%
+  as.vector
 ```

### 2021-11-03 Supplemental-Material-B-Annotated-Analysis.Rmd
AOT-M data cleaning done ✅

@@
   "reshape2",
-  "lubridate"
+  "lubridate",
+  "purrr"
 )
@@
 
+df <- df %>%
+  mutate(
+    NonDutchContact = replace_na(NonDutchNum, 0), # make second non-Dutch countable
+    NonDutchContact = ifelse(NonDutchContact > 1, 1, 0) # recode (yes = 1 -> 1, no = 2 -> 0)
+  ) %>%
+  mutate(
+    OutgroupInteraction = factor(
+      InteractionDumDutch,
+      levels = c(0, 1),
+      labels = c("No", "Yes")
+    ),
+    NonOutgroupInteraction = factor(
+      rowSums(select(., c(InteractionDumNonDutch, NonDutchContact)), na.rm = TRUE), # combine the two non-Dutch Q.,
+      levels = c(0, 1),
+      labels = c("No", "Yes")
+    )
+  )
+
 # -------------------------------------------------------------------------------------------------------------
@@
   rowMeans(df[, c("AntiSo1", "AntiSo2", "AntiSo3", "AntiSo4")], na.rm = T)
+
+# Allport's Conditions
+df %>%
+  #filter(OutgroupInteraction == "Yes") %>%
+  select(
+    InteractionContextEqualStatus,
+    KeyNeedShared,
+    InteractionContextCooperative,
+    InteractionContextvoluntary
+  ) %>%
+  pairs.panels.new
+
+df %>%
+  #filter(OutgroupInteraction == "Yes") %>%
+  select(
+    InteractionContextEqualStatus,
+    KeyNeedShared,
+    InteractionContextCooperative,
+    InteractionContextvoluntary
+  ) %>%
+  psych::describe(., skew=F,ranges=T) %>%
+  as.data.frame() %>%
+  select(-vars) %>%
+  kable(., caption = "Descriptives of Allport's Condition items") %>% 
+  kable_styling("hover", full_width = F, latex_options = "hold_position")
+
+iaWorkerAllport <- 
+  df %>%
+  #filter(OutgroupInteraction == "Yes") %>%
+  select(
+    InteractionContextEqualStatus,
+    KeyNeedShared,
+    InteractionContextCooperative,
+    InteractionContextvoluntary
+  )
+
+sjPlot::tab_itemscale(iaWorkerAllport)
+
+pca <- parameters::principal_components(iaWorkerAllport)
+factor.groups <- parameters::closest_component(pca)
+
+sjPlot::tab_itemscale(iaWorkerAllport, factor.groups)
+
+ltm::cronbach.alpha(na.omit(iaWorkerAllport), CI = TRUE)
+
+data <- 
+  df %>%
+  select(
+    PID,
+    TIDnum,
+    InteractionContextEqualStatus,
+    KeyNeedShared,
+    InteractionContextCooperative,
+    InteractionContextvoluntary
+  ) %>%
+  drop_na %>%
+  melt(
+    ., 
+    id.vars = c("PID", "TIDnum")
+  )
+
+horst::nestedAlpha(item.level.1 = "value",
+                   level.2      = "TIDnum",
+                   level.3      = "PID",
+                   data         = data)
+rm(data)
+
+iaWorkerAllportScale <- 
+  iaWorkerAllport %>%
+  Scale::Scale() %>%
+  Scale::ItemAnalysis()
+
+df$AllportsCondition <-
+  scoreItems(
+    keys = c(1, 1, 1, 1),
+    items = df %>% select(
+      InteractionContextEqualStatus,
+      KeyNeedShared,
+      InteractionContextCooperative,
+      InteractionContextvoluntary
+    ),
+    min = 0,
+    max = 100
+  )$scores
+
+as.data.frame(psych::describe(df$AllportsCondition, skew=T)) %>%
+  mutate(vars = "Allport's Conditions Index") %>%
+  kable(., caption = "Allport's Conditions: Scale Descriptives", row.names = FALSE) %>% 
+  kable_styling("hover", full_width = F, latex_options = "hold_position")
+
+histogram(df$AllportsCondition)
 
@@
 
-```
-
-```{r newVarsStudents}
-
 # -------------------------------------------------------------------------------------------------------------
@@
 # -------------------------------------------------------------------------------------------------------------
-
-df <- df %>%
-  group_by(PID) %>%
-  mutate(
-    KeyNeedFullfillment.cm = mean(KeyNeedFullfillment, na.rm = TRUE),
-    # cluster mean (mean of PP)
-    KeyNeedFullfillment.cwc = KeyNeedFullfillment - KeyNeedFullfillment.cm,
-    # cluster mean centered (within PP centered)
-    closeness.cm = mean(closeness_Calc, na.rm = TRUE),
-    closeness.cwc = closeness_Calc - closeness.cm
-  ) %>%
-  ungroup()
+# divide into trait and state
+medicalOutWithinBetween <-
+  MlTraitState(
+    data = df %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection =
+      c(
+        "KeyNeedFulfillment",
+        "Competence",
+        "Autonomy",
+        "Relatedness",
+        "AllportsCondition",
+        "AttitudesDutch",
+        "qualityOverall"
+      )
+  )
+
+df <-
+  MlTraitState(
+    data = df,
+    id = "PID",
+    selection =
+      c(
+        "KeyNeedFulfillment",
+        "Competence",
+        "Autonomy",
+        "Relatedness",
+        "AllportsCondition",
+        "AttitudesDutch",
+        "qualityOverall"
+      )
+  )
 
 # store
-dtStudents$full <- df
+dtMedical$full <- df
 rm(df)
@@
 # Between participants contact frequency
-studentContactFreq <- dtStudents$full %>%
+medicalContactFreq <- 
+  dtMedical$full %>%
   group_by(PID) %>%
@@
     n = n(),
-    SumContactNL = sum(InteractionDumDutch),
+    SumContactNL = sum(InteractionDumDutch, na.rm = TRUE),
     PercContactNL = SumContactNL / n * 100,
@@
     AvAttitude = mean(AttitudesDutch, na.rm = TRUE),
-    AvQuality = mean(quality_overall, na.rm = TRUE)
+    AvQuality = mean(qualityOverall, na.rm = TRUE)
   ) %>%
@@
 
-# dataframe where interaction types are recoded
-studentInteractionType <- dtStudents$full %>%
-  mutate(
-    NonDutchContact = replace_na(NonDutchContact, 2), # make second non-Dutch countable
-    NonDutchContact = NonDutchContact*-1+2 # recode (yes = 1 -> 1, no = 2 -> 0)
-  ) %>%
-  mutate(
-    OutgroupInteraction = factor(
-      InteractionDumDutch,
-      levels = c(0, 1),
-      labels = c("No", "Yes")
-    ),
-    NonOutgroupInteraction = factor(
-      rowSums(select(., c(InteractionDumNonDutch, NonDutchContact))), # combine the two non-Dutch Q.,
-      levels = c(0, 1),
-      labels = c("No", "Yes")
-    )
-  )
-
 # select a subset of IDs to display in plots
-studentPltIDs <-
-  studentInteractionType %>%
+medicalPltIDs <-
+  dtMedical$full %>%
   group_by(PID) %>%
@@
 # select a subset of IDs to display in plots (only outgroup interactions)
-studentOutPltIDs <-
-  studentInteractionType %>%
+medicalOutPltIDs <-
+  dtMedical$full %>%
   filter(OutgroupInteraction == "Yes") %>%

### 2021-11-03 Methods-and-Results.Rmd
methods and results re-run
AOT-M Participants and procedures added

@@
 
+```{r medicalSampleInfo, include=FALSE}
+
+medicalDemographicSupp <- 
+  dtMedical$raw.eligibility %>%
+  filter(session %in% dtMedical$full$session) %>%
+  select(session, nationality, studentBachMa)
+# summarize participant characteristics
+
+medicalSampleInfo <-
+  merge(dtMedical$full, medicalDemographicSupp, by = "session") %>%
+  mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>%
+  group_by(PID) %>%
+  summarise(
+    dailiesN = n(), 
+    morningN = sum(periodMA=="morning"),
+    afternoonN = sum(periodMA=="afternoon"),
+    age = age,
+    gender = gender,
+    nationality = nationality
+  ) %>%
+  distinct
+
+# look at frequencies of characteristics 
+table(medicalSampleInfo$age)
+table(medicalSampleInfo$gender)
+table(as.character(medicalSampleInfo$nationality))
+```
+
+```{r studentVarDescr, include=FALSE}
+medicalMlCor <-
+  MlCorMat(
+    data = dtMedical$full,
+    id = "PID",
+    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
+  )
+
+medicalMlCor %>%
+  kable(
+    .,
+    caption = "Medical: Multilevel Core Variable Descriptives",
+    format = "latex",
+    booktabs = TRUE,
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person coorelations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/medicalVarDescr.tex")
+```
+
+```{r studentOutVarDescr, include=FALSE}
+medicalOutMlCor <-
+  MlCorMat(
+    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
+  )
+
+medicalOutMlCor %>%
+  kable(
+    .,
+    caption = "Medical: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
+    format = "latex",
+    booktabs = TRUE,
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person coorelations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/medicalOutVarDescr.tex")
+
+# misty::multilevel.descript(dtStudentsSupp$studentWithinBetween$keyMotiveFulfilled, cluster = dtStudentsSupp$studentWithinBetween$PID)
+```
+
+\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(medicalSampleInfo)` international medical students using a contacts within the University Medical Department and specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
+Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
+With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(medicalSampleInfo$dailiesN)`).
+As with the previous study this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
+Participants were compensated for their participation with partial course credits --- depending on their participation.
+The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(medicalSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(medicalSampleInfo$age),2), nsmall=2)`, `r nrow(medicalSampleInfo %>% filter(gender == "women"))` women).
+The sample fairly accurately describes the local population of international students.
+
+\subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, daily diary-, and post-measurement.
+The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)))`).
+General compliance was high (`r format(round(sum(medicalSampleInfo$dailiesN)/(nrow(medicalSampleInfo)*62)*100,2), nsmall=2)`\% filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS).
+The response rates were approximately equal during mornings (\textit{n} = `r sum(medicalSampleInfo$morningN)`) and afternoons (\textit{n} = `r sum(medicalSampleInfo$afternoonN)`).
+All key variables in for this study were part of the short daily diary surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+\paragraph{Psychological Needs}
+
+\paragraph{Allport's Conditions}
+
+\paragraph{Perceived Interaction Quality}
+
+\paragraph{Outgroup Attitudes}
+
 \subsection{Results}

### 2021-11-03 Tables/studentVarDescr.tex
AOT-M Participants and procedures added

--- 2021-10-26 Tables/studentOutVarDescr.tex
@@
 
-\caption{\label{tab:studentOutVarDescr}Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
+\caption{Student: Multilevel Core Variable Descriptives}
 \centering
@@
 \midrule
-Core Need &  & 0.46*** & 0.50*** & -0.19 & 0.15\\
-Competence & 0.23*** &  & 0.59*** & 0.39** & 0.22\\
-Autonomy & 0.12*** & 0.32*** &  & 0.23 & 0.07\\
-Relatedness & 0.48*** & 0.25*** & 0.19*** &  & -0.09\\
-Attitudes NL & 0.18*** & 0.16*** & 0.15*** & 0.22*** & \\
+Core Need &  & 0.65*** & 0.67*** & 0.28** & 0.27**\\
+Competence & 0.30*** &  & 0.66*** & 0.59*** & 0.08\\
+Autonomy & 0.18*** & 0.33*** &  & 0.43*** & -0.08\\
+Relatedness & 0.43*** & 0.21*** & 0.12*** &  & -0.13\\
+Attitudes NL & 0.17*** & 0.08*** & 0.08*** & 0.08*** & \\
 \addlinespace
-Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 70.41\\
-Between-person SD & 11.20 & 13.95 & 14.07 & 17.35 & 17.13\\
-Within-person SD & 15.87 & 16.81 & 14.24 & 26.14 & 9.87\\
-ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.72\\
-ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.96\\
+Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 67.26\\
+Between-person SD & 9.17 & 14.47 & 11.21 & 13.36 & 18.64\\
+Within-person SD & 20.33 & 21.17 & 16.06 & 28.74 & 9.40\\
+ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.80\\
+ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.99\\
 \bottomrule

### 2021-11-03 Methods-and-Results.Rmd
AOT-M Methods first draft

@@
 
-The aim of our study is similar to to that of the first study, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
+The aim of our study is similar to that of the first study, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
 However, in this second study we collected a substantially larger intensive longitudinal survey study with recently arrived international students in the Netherlands.
@@
 
+The aim of this final study is to extend the previous studies by additionally testing Allport's conditions in an extensive longitudinal design and to compare the predictive powers of Allport's conditions and the core situational need fulfillment.
+We will, thus, again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
+However, we additionally have the opportunity to also assess the role of Allport's conditions in this and to compare the two approaches (Allport's conditions and core need fulfillment) directly.
+
+For this study we specifically recruited international medical students, because they represent a particular group of migrants who face structural requirements to integrate and interact with Dutch majority outgroup members on a daily basis.
+As part of their educational program, the migrants are required to take language courses and interact with patients as part of their medical internships and medical residency.
+The extensive longitudinal survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations.
+Data were collected from November 8th, 2019 to January 10th, 2020.
+
+The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
+Correlations and descriptive statistics of the included variables are available in Table \ref{tab:medicalVarDescr} and Table \ref{tab:medicalOutVarDescr}.
+
 \subsection{Methods}
@@
 ```{r medicalSampleInfo, include=FALSE}
-
+# extract demographic information from eligibility questionnaire
 medicalDemographicSupp <- 
@@
 
-```{r studentVarDescr, include=FALSE}
+```{r medicalVarDescr, include=FALSE}
 medicalMlCor <-
@@
 
-```{r studentOutVarDescr, include=FALSE}
+```{r medicalOutVarDescr, include=FALSE}
 medicalOutMlCor <-
@@
 
-\paragraph{Intergroup Contact}
-
-\paragraph{Psychological Needs}
-
-\paragraph{Allport's Conditions}
-
-\paragraph{Perceived Interaction Quality}
-
-\paragraph{Outgroup Attitudes}
+\paragraph{Intergroup Contact}The measurement of intergroup contacts was identical to study two.
+The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max`
+(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtMedical$full)` daily diary responses).
+
+\paragraph{Psychological Needs}The measurement of the core situational need and its fulfillment was identical to study two.
+Similarly, the measurement of the self determination needs was identical to studies one and two.
+
+\paragraph{Allport's Conditions}To measure how much each of the interactions fulfilled Allport's conditions of optimal contact we asked participants to rate how much the interaction had equal status ("\textit{The interaction with [name interaction partner] was on equal footing (same status)}"), a common goal ("\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}"), support of authorities ("\textit{The interaction with [name interaction partner] was voluntary}"), and intergroup cooperation ("\textit{The interaction with [name interaction partner] was cooperative}").
+
+\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to study one.
+
+\paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup was again measured using the feeling thermometer, as in studies one and two.
+All survey details are also available in Online Supplemental Materials A and B.
+
+\input{Tables/medicalVarDescr}
+\input{Tables/medicalOutVarDescr}
 

### 2021-11-03 Methods-and-Results.tex
methods and results re-run
AOT-M Methods first draft

@@
 
-The aim of our study is similar to to that of the first study, as we
-again test the general contact hypothesis, the influence of core need
+The aim of our study is similar to that of the first study, as we again
+test the general contact hypothesis, the influence of core need
 fulfillment, and perceived interaction quality during intergroup
@@
 
+The aim of this final study is to extend the previous studies by
+additionally testing Allport's conditions in an extensive longitudinal
+design and to compare the predictive powers of Allport's conditions and
+the core situational need fulfillment. We will, thus, again test the
+general contact hypothesis, the influence of core need fulfillment, and
+perceived interaction quality during intergroup contacts. However, we
+additionally have the opportunity to also assess the role of Allport's
+conditions in this and to compare the two approaches (Allport's
+conditions and core need fulfillment) directly.
+
+For this study we specifically recruited international medical students,
+because they represent a particular group of migrants who face
+structural requirements to integrate and interact with Dutch majority
+outgroup members on a daily basis. As part of their educational program,
+the migrants are required to take language courses and interact with
+patients as part of their medical internships and medical residency. The
+extensive longitudinal survey method again offers a large body of
+ecologically valid data on need satisfaction in real-life intergroup
+contact situations. Data were collected from November 8th, 2019 to
+January 10th, 2020.
+
+The full surveys are available in our Online Supplementary Material A
+and the full data description is available in Online Supplementary
+Materials B. Correlations and descriptive statistics of the included
+variables are available in Table \ref{tab:medicalVarDescr} and Table
+\ref{tab:medicalOutVarDescr}.
+
 \subsection{Methods}
 
+\subsubsection{Participants}
+
+After receiving ethical approval from the University of Groningen, we
+recruited 71 international medical students using a contacts within the
+University Medical Department and specifically targeted non-Dutch
+students, who had recently arrived in the Netherlands. Participants
+reported on their interactions for at least 30 days with two daily
+measures (capturing the morning and afternoon). With this design, we
+aimed at getting 50-60 measurements per participant (\textit{M} = 57.85,
+\textit{SD} = 20.68, \textit{total N} = 4107). As with the previous
+study this should offer sufficient power to model processes within
+participants and will lend stronger weight to between-participant
+results. Participants were compensated for their participation with
+partial course credits --- depending on their participation. The sample
+consisted of relatively young migrants, who were mostly from the global
+north (\(M_{age}\) = 22.68, \(SD_{age}\) = 3.10, 59 women). The sample
+fairly accurately describes the local population of international
+students.
+
+\subsubsection{Procedure}
+
+The study procedure mirrored the setup of studies one and two, in that
+it consisted of pre-, daily diary-, and post-measurement. The
+participants were invited for daily diary measurements twice a day (at
+12 pm and 7pm) for 30 days (\textit{median duration} = 13,
+\textit{MAD duration} = 6). General compliance was high (93.30\% filled
+daily diary surveys for 31 days or more NEED TO RE-CHECK THIS). The
+response rates were approximately equal during mornings (\textit{n} =
+2092) and afternoons (\textit{n} = 2015). All key variables in for this
+study were part of the short daily diary surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+The measurement of intergroup contacts was identical to study two. The
+participants recorded between 1--71 (2.13--87.18\% of individual daily
+diary measurements; 41.44\% of all 4107 daily diary responses).
+
+\paragraph{Psychological Needs}
+
+The measurement of the core situational need and its fulfillment was
+identical to study two. Similarly, the measurement of the self
+determination needs was identical to studies one and two.
+
+\paragraph{Allport's Conditions}
+
+To measure how much each of the interactions fulfilled Allport's
+conditions of optimal contact we asked participants to rate how much the
+interaction had equal status
+(``\textit{The interaction with [name interaction partner] was on equal footing (same status)}''),
+a common goal
+(``\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}''),
+support of authorities
+(``\textit{The interaction with [name interaction partner] was voluntary}''),
+and intergroup cooperation
+(``\textit{The interaction with [name interaction partner] was cooperative}'').
+
+\paragraph{Perceived Interaction Quality}
+
+The ratings of the perceived interaction quality was identical to study
+one.
+
+\paragraph{Outgroup Attitudes}
+
+Attitudes towards the Dutch majority outgroup was again measured using
+the feeling thermometer, as in studies one and two. All survey details
+are also available in Online Supplemental Materials A and B.
+
+\input{Tables/medicalVarDescr}
+\input{Tables/medicalOutVarDescr}
+
 \subsection{Results}

### 2021-11-03 Methods-and-Results.Rmd
Update Methods-and-Results.Rmd

@@
 After giving informed consent, participants started by filling in an online pre-questionnaire assessing demographics and general information about their immigration.
-Over the next thirty days, the participants then were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_))`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_)))`).
+Over the next thirty days, the participants then were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_))) %>% as.character`).
 General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%)}.
@@
 \subsubsection{Procedure} The study procedure mirrored the setup of study one and consisted of pre-, daily diary-, and post-measurement.
-The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily)))`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily))))`).
+The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily))) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily)))) %>% as.character`).
 General compliance was high (`r format(round(sum(studentSampleInfo$dailiesN)/(nrow(studentSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in).
@@
 \subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, daily diary-, and post-measurement.
-The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)))`).
+The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).
 General compliance was high (`r format(round(sum(medicalSampleInfo$dailiesN)/(nrow(medicalSampleInfo)*62)*100,2), nsmall=2)`\% filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS).
@@
 \paragraph{Intergroup Contact}The measurement of intergroup contacts was identical to study two.
-The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max`
+The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
 (`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtMedical$full)` daily diary responses).

### 2021-11-04 Methods-and-Results.Rmd
AOT-M results structure
table rotation test

@@
   ) %>%
+  kableExtra::landscape() %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
@@
 
+\subsubsection{Contact Hypothesis}
+
+\subsubsection{Allport's Conditions}
+
+\subsubsection{Core Need}
+
+\subsubsection{Robustness}
+
 <!-- \begin{figure}[h] -->

### 2021-11-04 Methods-and-Results.Rmd
tbl resize fix attempt

@@
   ) %>%
+  kable_styling(latex_options = "scale_down") %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position

### 2021-11-04 Methods-and-Results.Rmd
tbl spacing fix attempt

--- 2021-11-04 Methods-and-Results.Rmd
@@
     booktabs = TRUE,
+    linesep = linesep(c(ncol(.))),
     align = c("l", rep("c", ncol(.) - 1))
@@
     id = "PID",
-    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
+    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
     labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
@@
   ) %>%
-  kableExtra::landscape() %>%
+  landscape() %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position

### 2021-11-04 scripts/functions/MlCorMat.R
linesep function added

@@ -288,7 +288,7 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
   }
 }
 
-linesep<-function(x,y=character()){
+linesep <- function(x,y=character()){
   if(!length(x))
     return(y)
   linesep(x[-length(x)], c(rep('',x[length(x)]-1),'\\addlinespace',y))  

### 2021-11-04 scripts/functions/MlCorMat.R
Delete MlCorMat.R

@@ -1,295 +1,0 @@
-MlCorMat <-
-  function(data,
-           id,
-           selection,
-           labels = selection,
-           method = c("pearson", "spearman"),
-           removeTriangle = c("upper", "lower"),
-           result = c("none", "html", "latex")) {
-    # for testing
-    # data <- dtWorkerSupp$workerInteractionType
-    # id <- "PID"
-    # selection <- varSelection
-    # labels <- varlabels
-    
-    # calculate trait scores (participant means)
-    data <- 
-      data %>%
-      select(id, selection) %>%
-      group_by_at(vars(matches(id))) %>%
-      mutate_at(selection, list(trait = ~mean(., na.rm=TRUE))) %>%
-      ungroup 
-    
-    data <-
-      map_dfc(selection,
-              ~ data %>%
-                transmute(
-                  !!str_c(.x, '_state') :=
-                    !!rlang::sym(.x)-!!rlang::sym(str_c(.x, "_trait"))
-                )) %>%
-      bind_cols(data, .)
-    
-    # Fid out why own is different
-    # raw <-
-    #   data %>%
-    #   select(selection) %>%
-    #   as.matrix
-    # 
-    # corRaw <- rcorr(raw, type=method[1])
-    # rRaw <- corRaw$r # Matrix of correlation coeficients
-    # pRaw <- corRaw$P # Matrix of p-value 
-    # 
-    # ## Define notions for significance levels; spacing is important.
-    # starsRaw <- ifelse(pRaw < .001, "***", ifelse(pRaw < .01, "**", ifelse(pRaw < .05, "* ", "   ")))
-    # 
-    # ## trunctuate the correlation matrix to two decimal
-    # rRaw <- format(round(cbind(rep(-1.11, ncol(raw)), rRaw), 2))[,-1]
-    # 
-    # ## build a new matrix that includes the correlations with their apropriate stars
-    # rRawStar <- matrix(paste(rRaw, starsRaw, sep=""), ncol=ncol(raw))
-    # 
-    # 
-    # trait <-
-    #   data %>%
-    #   select(paste0(selection, "_trait")) %>%
-    #   as.matrix
-    # 
-    # corTrait <- rcorr(trait, type=method[1])
-    # rTrait <- corTrait$r # Matrix of correlation coeficients
[…]

### 2021-11-04 scripts/functions/MlCorMat.R
Update manuscript.tex

@@ -1,289 +1,0 @@
-MlCorMat <-
-  function(data,
-           id,
-           selection,
-           labels = selection,
-           method = c("pearson", "spearman"),
-           removeTriangle = c("upper", "lower"),
-           result = c("none", "html", "latex")) {
-    # for testing
-    # data <- dtWorkerSupp$workerInteractionType
-    # id <- "PID"
-    # selection <- varSelection
-    # labels <- varlabels
-    
-    # calculate trait scores (participant means)
-    data <- 
-      data %>%
-      select(id, selection) %>%
-      group_by_at(vars(matches(id))) %>%
-      mutate_at(selection, list(trait = ~mean(., na.rm=TRUE))) %>%
-      ungroup 
-    
-    data <-
-      map_dfc(selection,
-              ~ data %>%
-                transmute(
-                  !!str_c(.x, '_state') :=
-                    !!rlang::sym(.x)-!!rlang::sym(str_c(.x, "_trait"))
-                )) %>%
-      bind_cols(data, .)
-    
-    # Fid out why own is different
-    # raw <-
-    #   data %>%
-    #   select(selection) %>%
-    #   as.matrix
-    # 
-    # corRaw <- rcorr(raw, type=method[1])
-    # rRaw <- corRaw$r # Matrix of correlation coeficients
-    # pRaw <- corRaw$P # Matrix of p-value 
-    # 
-    # ## Define notions for significance levels; spacing is important.
-    # starsRaw <- ifelse(pRaw < .001, "***", ifelse(pRaw < .01, "**", ifelse(pRaw < .05, "* ", "   ")))
-    # 
-    # ## trunctuate the correlation matrix to two decimal
-    # rRaw <- format(round(cbind(rep(-1.11, ncol(raw)), rRaw), 2))[,-1]
-    # 
-    # ## build a new matrix that includes the correlations with their apropriate stars
-    # rRawStar <- matrix(paste(rRaw, starsRaw, sep=""), ncol=ncol(raw))
-    # 
-    # 
-    # trait <-
-    #   data %>%
-    #   select(paste0(selection, "_trait")) %>%
-    #   as.matrix
-    # 
-    # corTrait <- rcorr(trait, type=method[1])
-    # rTrait <- corTrait$r # Matrix of correlation coeficients
-    # pTrait <- corTrait$P # Matrix of p-value 
[…]

### 2021-11-04 scripts/functions/binaryCor.R

@@ -1,28 +1,0 @@
-BinaryCor <- function(x, type=c("pearson", "spearman"), ...){
-  
-  x <- as.matrix(x)
-  C <- crossprod(x)
-  R <- rcorr(x, type=type)$r
-  p <- rcorr(x, type=type)$P
-  
-  ## define notions for significance levels; spacing is important.
-  mystars <- ifelse(p < .001, "***", ifelse(p < .01, "** ", ifelse(p < .05, "* ", " ")))
-  
-  ## trunctuate the matrix that holds the correlations to two decimal
-  R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]
-  
-  ## build a new matrix that includes the correlations with their apropriate stars
-  Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
-  diag(Rnew) <- paste("N = ", diag(C), " ", sep="")
-  rownames(Rnew) <- colnames(x)
-  colnames(Rnew) <- paste(colnames(x), "", sep="")
-  
-  ## remove upper triangle
-  Rnew <- as.matrix(Rnew)
-  Rnew[lower.tri(Rnew, diag = FALSE)] <- C[lower.tri(C, diag = FALSE)]
-  Rnew <- as.data.frame(Rnew)
-  
-  ## remove last column and return the matrix (which is now a data frame)
-  #Rnew <- cbind(Rnew[1:length(Rnew)-1])
-  return(Rnew)
-}

### 2021-11-04 scripts/functions/fun.panel.R

@@ -1,284 +1,0 @@
-# factor numeric --------------------------------------------------------------
-as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}
-
-# Panels with correlation -------------------------------------------------
-pairs.panels.new = function (x, smooth = TRUE, scale = FALSE, density = TRUE, ellipses = TRUE, 
-                    digits = 2, method = "pearson", pch = 20, lm = FALSE, cor = TRUE, 
-                    jiggle = FALSE, factor = 2, hist.col = "grey", show.points = TRUE, 
-                    rug = TRUE, breaks = "Sturges", cex.cor = 1, ...) 
-{
-  "panel.hist.density" <- function(x, ...) {
-    usr <- par("usr")
-    on.exit(par(usr))
-    par(usr = c(usr[1:2], 0, 1.5))
-    h <- hist(x, breaks = breaks, plot = FALSE)
-    breaks <- h$breaks
-    nB <- length(breaks)
-    y <- h$counts
-    y <- y/max(y)
-    rect(breaks[-nB], 0, breaks[-1], y, col = hist.col)
-    if (density) {
-      tryd <- try(d <- density(x, na.rm = TRUE, bw = "nrd", 
-                               adjust = 1.2), silent = TRUE)
-      if (class(tryd) != "try-error") {
-        d$y <- d$y/max(d$y)
-        lines(d)
-      }
-    }
-    if (rug) 
-      rug(x)
-  }
-  "panel.cor" <- function(x, y, digits = 2, prefix = "", ...) {
-    usr <- par("usr")
-    on.exit(par(usr))
-    par(usr = c(0, 1, 0, 1))
-    r <- cor(x, y, use = "pairwise", method = method)
-    txt <- format(c(round(r, digits), 0.123456789), digits = digits)[1]
-    txt <- paste(prefix, txt, sep = "")
-    cex <- cex.cor * 0.8/strwidth(txt)
-	  test <- rcorr(x,y, type = method)
-	  CI <- CIrho(test$r[2], test$n[2], level = 0.95)
-    Signif <- symnum(test$P[2], corr = FALSE, na = FALSE,
-                     cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
-                     symbols = c("***", "**", "*", ".", " "))
-    if (scale) {
-      cex1 <- cex * abs(r)
-      if (cex1 < 0.25) 
-        cex1 <- 0.25
[…]

### 2021-11-04 scripts/functions/kappa.R

@@ -1,67 +1,0 @@
-kappa.full <- function(x, name, ...){
-  xtab <- table(x)
-  diagonal.counts <- diag(xtab)
-  N <- sum(xtab)
-  row.marginal.props <- rowSums(xtab)/N
-  col.marginal.props <- colSums(xtab)/N
-  # Compute kappa (k)
-  Po <- sum(diagonal.counts)/N
-  Pe <- sum(row.marginal.props*col.marginal.props)
-  k <- (Po - Pe)/(1 - Pe)
-  se <- sqrt((Po*(1-Po))/(N*(1-Pe)^2)) # according to PMID: 23092060
-  lwr <- k-1.96*se
-  upr <- k+1.96*se
-  
-  data.frame(name,Po,Pe,k,se,lwr,upr)
-}
-
-# # Minimally reproducible dataset
-# coders <- data.table(Affect1 = rbinom(250, 1,.62), Affect2 = rbinom(250, 1,.58))
-# name <- "affect"
-# kappa.full(coders, name)
-
-# --------------------------------------------------------------------------------
-
-kappa.full.multiple <- function(x, names, ...){
-  kComb <- list()
-  for (i in 1:length(names)) {
-    kComb[[i]] <- kappa.full(x %>% select(contains(names[i])), names[i])
-  }
-  do.call(rbind.data.frame, kComb)  
-}
-
-# # Minimally reproducible dataset
-# coders <- data.table(Affect1 = rbinom(250, 1,.62), Affect2 = rbinom(250, 1,.58),
-#                      Behavior1 = rbinom(250, 1,.32), Behavior2 = rbinom(250, 1,.40),
-#                      Cognition1 = rbinom(250, 1,.52), Cognition2 = rbinom(250, 1,.55),
-#                      Desire1 = rbinom(250, 1,.78), Desire2 = rbinom(250, 1,.82))
-# names <- c("affect", "behavior", "cognition", "desire")
-# kappa.full.multiple(coders, names)
-
-# --------------------------------------------------------------------------------
-
-kappa.pooled <- function(ktab, ...){
-  (mean(ktab$Po, na.rm = TRUE) - mean(ktab$Pe, na.rm = TRUE))/(1 - mean(ktab$Pe, na.rm = TRUE))
-}
-
-kappa.pooled2 <- function(ktab, ...){
-  k <- kappa.pooled(ktab)
-  require(boot)
-  set.seed(42)
[…]

### 2021-11-04 scripts/functions/prismaGraph.R

@@ -1,58 +1,0 @@
-prismaGr <- function (found, found_other, no_dupes, screened, screen_exclusions, 
-          full_text, full_text_exclusions, qualitative, quantitative = NULL, 
-          labels = NULL, extra_dupes_box = FALSE, title = "", ..., dpi = 72, font_size = 10) {
-  
-  dupes <- found + found_other - no_dupes
-  labels <- list(found = paste("Records identified through", "database searching", sprintf("(n = %d)", found), sep = "\n"), 
-                 found_other = paste("Additional records identified", "through other sources", sprintf("(n = %d)", found_other), sep = "\n"), 
-                 no_dupes = paste("Records after duplicates removed", sprintf("(n = %d)", no_dupes), sep = "\n"), 
-                 dupes = paste("Duplicates excluded", sprintf("(n = %d)", dupes), sep = "\n"), 
-                 screened = paste("Records screened", sprintf("(n = %d)", screened), sep = "\n"), 
-                 screen_exclusions = paste("Records excluded", "[reasons, see Table 2]", sprintf("(n = %d)", screen_exclusions), sep = "\n"), 
-                 full_text = paste("Full-text articles assessed", "for eligibility", sprintf("(n = %d)", full_text), sep = "\n"), 
-                 full_text_exclusions = paste("Full-text articles excluded", "[reasons, see Table 2]", sprintf("(n = %d)", full_text_exclusions), sep = "\n"), 
-                 qualitative = paste("Studies included in qualitative synthesis",sprintf("(n = %d)", qualitative), sep = "\n"), 
-                 quantitative = paste("Studies included in", "quantitative synthesis", "(empirical)", sprintf("(n = %d)", quantitative), sep = "\n"))
-  
-  dupes_box <- sprintf("nodups -> incex;\n    nodups [label=\"%s\"];", 
-                       labels$no_dupes)
-  if (extra_dupes_box) 
-    dupes_box <- sprintf("nodups -> {incex; dups};\n       nodups [label=\"%s\"];\n       dups [label=\"%s\"]; {rank=same; nodups dups}", 
-                         labels$no_dupes, labels$dupes)
[…]

### 2021-11-04 scripts/functions/summarizeSE.R

@@ -1,137 +1,0 @@
-## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
-##   data: a data frame.
-##   measurevar: the name of a column that contains the variable to be summariezed
-##   groupvars: a vector containing names of columns that contain grouping variables
-##   na.rm: a boolean that indicates whether to ignore NA's
-##   conf.interval: the percent range of the confidence interval (default is 95%)
-summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
-                      conf.interval=.95, .drop=TRUE) {
-  library(plyr)
-  
-  # New version of length which can handle NA's: if na.rm==T, don't count them
-  length2 <- function (x, na.rm=FALSE) {
-    if (na.rm) sum(!is.na(x))
-    else       length(x)
-  }
-  
-  # This does the summary. For each group's data frame, return a vector with
-  # N, mean, and sd
-  datac <- ddply(data, groupvars, .drop=.drop,
-                 .fun = function(xx, col) {
-                   c(N    = length2(xx[[col]], na.rm=na.rm),
-                     mean = mean   (xx[[col]], na.rm=na.rm),
-                     sd   = sd     (xx[[col]], na.rm=na.rm)
-                   )
-                 },
-                 measurevar
-  )
-  
-  # Rename the "mean" column    
-  datac <- plyr::rename(datac, c("mean" = measurevar))
-  
-  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
-  
-  # Confidence interval multiplier for standard error
-  # Calculate t-statistic for confidence interval: 
-  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
-  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
-  datac$ci <- datac$se * ciMult
-  
-  return(datac)
-}
-
-## Norms the data within specified groups in a data frame; it normalizes each
-## subject (identified by idvar) so that they have the same mean, within each group
-## specified by betweenvars.
-##   data: a data frame.
-##   idvar: the name of a column that identifies each subject (or matched subjects)
-##   measurevar: the name of a column that contains the variable to be summariezed
-##   betweenvars: a vector containing names of columns that are between-subjects variables
-##   na.rm: a boolean that indicates whether to ignore NA's
[…]

### 2021-11-04 scripts/functions/themes.R

@@ -1,43 +1,0 @@
-# create theme
-theme_Publication <- function(base_size=14, base_family="") {
-  library(grid)
-  library(ggthemes)
-  (theme_foundation(base_size=base_size, base_family=base_family)
-    + theme(plot.title = element_text(face = "bold",
-                                      size = rel(1.2), hjust = 0.5),
-            text = element_text(),
-            panel.background = element_rect(colour = NA),
-            plot.background = element_rect(colour = NA),
-            panel.border = element_rect(colour = NA),
-            axis.title = element_text(face = "bold",size = rel(1)),
-            axis.title.y = element_text(angle=90,vjust =2),
-            axis.title.x = element_text(vjust = -0.2),
-            axis.text = element_text(), 
-            axis.line = element_line(colour="black"),
-            axis.ticks = element_line(),
-            panel.grid.major = element_line(colour="#f0f0f0"),
-            panel.grid.minor = element_blank(),
-            legend.key = element_rect(colour = NA),
-            legend.position = "bottom",
-            legend.direction = "horizontal",
-            legend.key.size= unit(0.2, "cm"),
-            #legend.margin = unit(0, "cm"),
-            legend.title = element_text(face="italic"),
-            plot.margin=unit(c(10,5,5,5),"mm"),
-            strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
-            strip.text = element_text(face="bold")
-    ))
-  
-}
-
-scale_fill_Publication <- function(...){
-  library(scales)
-  discrete_scale("fill","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
-  
-}
-
-scale_colour_Publication <- function(...){
-  library(scales)
-  discrete_scale("colour","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)
-  
-}

### 2021-11-04 Methods-and-Results.tex
after re-base

@@
 fulfillments, and current attitudes towards the Dutch outgroup
-(\textit{median duration} = 22, \textit{MAD duration} = 19). General
-compliance was high (85.90\% of all invited surveys were filled
+(\textit{median duration} = 2M 22S, \textit{MAD duration} = 1M 19S).
+General compliance was high (85.90\% of all invited surveys were filled
 in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%)}.
@@
 for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days
-(\textit{median duration} = 46, \textit{MAD duration} = 54). General
-compliance was high (70.87\% of all invited surveys were filled in). The
-response rates were approximately equal during mornings (\textit{n} =
-2608) and afternoons (\textit{n} = 2357). All key variables in for this
-study were part of the short daily diary surveys.
+(\textit{median duration} = 3M 46S, \textit{MAD duration} = 1M 54S).
+General compliance was high (70.87\% of all invited surveys were filled
+in). The response rates were approximately equal during mornings
+(\textit{n} = 2608) and afternoons (\textit{n} = 2357). All key
+variables in for this study were part of the short daily diary surveys.
 
@@
 participants were invited for daily diary measurements twice a day (at
-12 pm and 7pm) for 30 days (\textit{median duration} = 13,
-\textit{MAD duration} = 6). General compliance was high (93.30\% filled
-daily diary surveys for 31 days or more NEED TO RE-CHECK THIS). The
-response rates were approximately equal during mornings (\textit{n} =
-2092) and afternoons (\textit{n} = 2015). All key variables in for this
-study were part of the short daily diary surveys.
+12 pm and 7pm) for 30 days (\textit{median duration} = 4M 13S,
+\textit{MAD duration} = 2M 6S). General compliance was high (93.30\%
+filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS).
+The response rates were approximately equal during mornings (\textit{n}
+= 2092) and afternoons (\textit{n} = 2015). All key variables in for
+this study were part of the short daily diary surveys.
 
@@
 The measurement of intergroup contacts was identical to study two. The
-participants recorded between 1--71 (2.13--87.18\% of individual daily
-diary measurements; 41.44\% of all 4107 daily diary responses).
+participants recorded between 1--71 interactions with Dutch outgroup
+members (2.13--87.18\% of individual daily diary measurements; 41.44\%
+of all 4107 daily diary responses).
 

### 2021-11-04 PreregristrationS3/PreregistrationAOT-M.Rmd
after re-base

@@
 \label{hyp:contact}Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
-    a. \label{hyp:contactFreq}Participants with more intergroup interactions should have a more favorable outgroup attitudes.
+    a. \label{hyp:contactFreq}Participants with more intergroup interactions should have more favorable outgroup attitudes.
     b. \label{hyp:contactDummy}Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
-    c. \label{hyp:contactFreqQual}Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
+    c. \label{hyp:contactFreqQual}Participants with more intergroup interactions should have more favorable outgroup attitudes depending on the average interaction quality.
 2.
@@
     b.
-\label{hyp:AllportsQuality}Based on past research on the role of interaction quality, interaction quality should be more perceived as more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
-    c.
-\label{hyp:AllportsQualityMediation}Based on past research on the role of interaction quality, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extend be assumed by interaction quality.
+\label{hyp:AllportsQuality}Based on past research on the role of interaction quality, interaction quality should be perceived as more positive after intergroup interactions with equal status, common goals, collaboration, and structural support.
+    c. \label{hyp:AllportsQualityMediation}Taken together, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extend be explained by interaction quality.
 3.
@@
 \label{hyp:keyNeedContactType}The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
-Thus, the effect of key need fulfillment on outgroup attitudes should stronger for intergroup interact than for ingroup interactions.
+Thus, the effect of key need fulfillment on outgroup attitudes should be stronger for intergroup interact than for non-outgroup interactions (or need fulfillment during a time of no interaction).
     e.
-\label{hyp:keyNeedSDT}The effect of key need fulfillment on outgroup attitudes should be persist even when taking other fundamental psychological needs into account.
+\label{hyp:keyNeedSDT}The effect of key need fulfillment on outgroup attitudes should persist even when taking other fundamental psychological needs into account.
 Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
@@
     b.
-\label{hyp:compTogether}The  effect of key need fulfillment on outgroup attitudes should  persist even when taking other Allport's conditions into account.
+\label{hyp:compTogether}The  effect of key need fulfillment on outgroup attitudes should  persist even when taking Allport's conditions into account.
 Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for equal status, common goals, collaboration, and structural support.
@@
 
-1. Entry Survey: A pre-measurement questionnaire (appr. 25 minutes) including demographic information, and relations to the Dutch majority. (payment: 2 Euros)
-2. Experience Recaps: At least 30 days of short reflection surveys (appr. 3—5 minutes) on intergroup interactions twice a day. (payment: 1 Euro per Recap; up to 2 Euros per day)
-3. Conclusion Survey: On the last day, we conclude with a post-measurement questionnaire (appr. 25 minutes) with some questions on habits and reflections on the study. (payment: 2 Euros)
+1. Entry Survey: A pre-measurement questionnaire (appr. 25 minutes) including demographic information, and relations to the Dutch majority (payment: 2 Euros).
+2. Experience Recaps: At least 30 days of short reflection surveys (appr. 3—5 minutes) on intergroup interactions twice a day (payment: 1 Euro per Recap; up to 2 Euros per day).
+3. Conclusion Survey: On the last day, we conclude with a post-measurement questionnaire (appr. 25 minutes) with some questions on habits and reflections on the study (payment: 2 Euros).
 
 After the initial 30 day duration, participants are offered the possibility to continue participating in the study either with payment if daily diary measures were missed during the initial study phase or without payment after a total of 60 daily diary measurements were completed.
-After the initial 30-day period, participants receive automated feedback visualizing the development of their own well-being, attitudes, and motive responses as an additional initiative to give participants access to their own data and to compensate study participation.
+After the initial 30-day period, participants receive automated feedback visualizing the development of their own well-being, attitudes, and motive responses as an additional initiative and to give participants access to their own data and to compensate study participation.
 
@@
 The ultimate sampling procedure decision was made as a practical balancing of the number of participants and the number of measurements provided by each participants.
-Given that this study primarily focuses on the contemporaneous effects within the daily diary measurements, power should thus be high enough.
+Given that this study primarily focuses on the contemporaneous effects within the daily diary measurements, power should be high enough.
 
@@
         \end{fleqn}  
-1. Key Need Fulfillment
+1. Key Need fulfillment
     a. Regression: 
@@
 
-# References
 ## 

### 2021-11-04 scripts/functions/MlCorMat.R

@@ -1,0 +1,289 @@
+MlCorMat <-
+  function(data,
+           id,
+           selection,
+           labels = selection,
+           method = c("pearson", "spearman"),
+           removeTriangle = c("upper", "lower"),
+           result = c("none", "html", "latex")) {
+    # for testing
+    # data <- dtWorkerSupp$workerInteractionType
+    # id <- "PID"
+    # selection <- varSelection
+    # labels <- varlabels
+    
+    # calculate trait scores (participant means)
+    data <- 
+      data %>%
+      select(id, selection) %>%
+      group_by_at(vars(matches(id))) %>%
+      mutate_at(selection, list(trait = ~mean(., na.rm=TRUE))) %>%
+      ungroup 
+    
+    data <-
+      map_dfc(selection,
+              ~ data %>%
+                transmute(
+                  !!str_c(.x, '_state') :=
+                    !!rlang::sym(.x)-!!rlang::sym(str_c(.x, "_trait"))
+                )) %>%
+      bind_cols(data, .)
+    
+    # Fid out why own is different
+    # raw <-
+    #   data %>%
+    #   select(selection) %>%
+    #   as.matrix
+    # 
+    # corRaw <- rcorr(raw, type=method[1])
+    # rRaw <- corRaw$r # Matrix of correlation coeficients
+    # pRaw <- corRaw$P # Matrix of p-value 
+    # 
+    # ## Define notions for significance levels; spacing is important.
+    # starsRaw <- ifelse(pRaw < .001, "***", ifelse(pRaw < .01, "**", ifelse(pRaw < .05, "* ", "   ")))
+    # 
+    # ## trunctuate the correlation matrix to two decimal
+    # rRaw <- format(round(cbind(rep(-1.11, ncol(raw)), rRaw), 2))[,-1]
+    # 
+    # ## build a new matrix that includes the correlations with their apropriate stars
+    # rRawStar <- matrix(paste(rRaw, starsRaw, sep=""), ncol=ncol(raw))
+    # 
+    # 
+    # trait <-
+    #   data %>%
+    #   select(paste0(selection, "_trait")) %>%
+    #   as.matrix
+    # 
+    # corTrait <- rcorr(trait, type=method[1])
+    # rTrait <- corTrait$r # Matrix of correlation coeficients
+    # pTrait <- corTrait$P # Matrix of p-value 
[…]

### 2021-11-04 Methods-and-Results.Rmd
linesep added

@@
     id = "PID",
-    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "thermometerDutch_1") ,
+    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "thermometerDutch_1"),
     labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
@@
     id = "PID",
-    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "thermometerDutch_1") ,
+    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "thermometerDutch_1"),
     labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
@@
     id = "PID",
-    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
+    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
     labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
@@
   ) %>%
-  landscape() %>%
+  kableExtra::landscape() %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position

### 2021-11-04 scripts/functions/MlCorMat.R

@@ -287,3 +287,9 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
     )
   }
 }
+
+linesep<-function(x,y=character()){
+  if(!length(x))
+    return(y)
+  linesep(x[-length(x)], c(rep('',x[length(x)]-1),'\\addlinespace',y))  
+}

### 2021-11-04 Methods-and-Results.Rmd
cor code fix

@@
     id = "PID",
-    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "thermometerDutch_1"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
+    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "quality_overall_1", "thermometerDutch_1"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
   )
@@
     id = "PID",
-    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "thermometerDutch_1"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
+    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "quality_overall_1", "thermometerDutch_1"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
   )
@@
     id = "PID",
-    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "AttitudesDutch") ,
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
+    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "quality_overall", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
   )
@@
     id = "PID",
-    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Attitudes NL")
+    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "quality_overall", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
   )
@@
     id = "PID",
-    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch") ,
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport's Conditions", "Interaction Quality", "Attitudes NL")
+    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
   )

### 2021-11-04 Tables/studentOutVarDescr.tex
AOT-M Participants and procedures added
methods results re-render

@@
 \centering
-\begin{tabular}[t]{llcccc}
+\begin{tabular}[t]{llccccc}
 \toprule
-  & Core Need & Competence & Autonomy & Relatedness & Attitudes NL\\
+  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
 \midrule
-Core Need &  & 0.46*** & 0.50*** & -0.19 & 0.15\\
-Competence & 0.23*** &  & 0.59*** & 0.39** & 0.22\\
-Autonomy & 0.12*** & 0.32*** &  & 0.23 & 0.07\\
-Relatedness & 0.48*** & 0.25*** & 0.19*** &  & -0.09\\
-Attitudes NL & 0.18*** & 0.16*** & 0.15*** & 0.22*** & \\
+Core Need &  & 0.44** & 0.49*** & -0.22 & 0.51*** & 0.14\\
+Competence & 0.23*** &  & 0.58*** & 0.40** & 0.55*** & 0.21\\
+Autonomy & 0.12*** & 0.24*** &  & 0.22 & 0.61*** & 0.05\\
+Relatedness & 0.48*** & 0.31*** & 0.38*** &  & 0.35* & -0.09\\
+Quality & 0.19*** & 0.40*** & 0.16*** & 0.15*** &  & 0.16\\
+Attitudes NL & 0.32*** & 0.36*** & 0.19*** & 0.23*** & 0.30*** & \\
 \addlinespace
-Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 70.41\\
-Between-person SD & 11.20 & 13.95 & 14.07 & 17.35 & 17.13\\
-Within-person SD & 15.87 & 16.81 & 14.24 & 26.14 & 9.87\\
-ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.72\\
-ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.96\\
+Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 78.80 & 70.41\\
+Between-person SD & 11.20 & 13.95 & 14.07 & 17.35 & 10.71 & 17.13\\
+Within-person SD & 15.87 & 16.81 & 14.24 & 26.14 & 17.88 & 9.87\\
+ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.14 & 0.72\\
+ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.59 & 0.96\\
 \bottomrule
-\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
 \end{tabular}

### 2021-11-04 Tables/workerOutVarDescr.tex
AOT-P methods added
effect size trials
local stash
methods results re-render

@@
 \begin{table}
+\begin{minipage}[t][\textheight][t]{\textwidth}
 
-\caption{\label{tab:workerSampleInfo}Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
+\caption{\label{tab:workerOutVarDescr}Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
 \centering
-\begin{tabular}[t]{llcccc}
+\begin{tabular}[t]{llccccc}
 \toprule
-  & Core Need & Competence & Autonomy & Relatedness & Attitudes NL\\
+  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
 \midrule
-Core Need &  & 0.84*** & 0.60*** & 0.27 & -0.02\\
-Competence & 0.36*** &  & 0.88*** & 0.17 & -0.24\\
-Autonomy & 0.29*** & 0.24*** &  & 0.20 & 0.02\\
-Relatedness & 0.50*** & 0.23*** & 0.24*** &  & 0.17\\
-Attitudes NL & 0.17** & 0.27*** & 0.27*** & 0.37*** & \\
+Core Need &  & 0.82*** & 0.60*** & 0.32 & 0.52** & -0.03\\
+Competence & 0.36*** &  & 0.89*** & 0.24 & 0.38 & -0.24\\
+Autonomy & 0.28*** & 0.23*** &  & 0.29 & 0.56** & 0.02\\
+Relatedness & 0.51*** & 0.39*** & 0.37*** &  & -0.09 & 0.14\\
+Quality & 0.17*** & 0.44*** & 0.27*** & 0.27*** &  & 0.50*\\
+Attitudes NL & 0.24*** & 0.37*** & 0.24*** & 0.37*** & 0.52*** & \\
 \addlinespace
-Grand Mean & 32.20 & 16.53 & 22.64 & 1.58 & 72.46\\
-Between-person SD & 12.42 & 13.41 & 10.22 & 14.16 & 13.62\\
-Within-person SD & 17.66 & 18.78 & 14.93 & 23.97 & 9.50\\
-ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.68\\
-ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.98\\
+Grand Mean & 32.20 & 16.53 & 22.64 & 1.58 & 24.10 & 72.46\\
+Between-person SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.50 & 13.62\\
+Within-person SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.85 & 9.50\\
+ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.18 & 0.68\\
+ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.80 & 0.98\\
 \bottomrule
-\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
 \end{tabular}
+\end{minipage}
 \end{table}

### 2021-11-05 Methods-and-Results.Rmd
tbl scale fix

@@
   ) %>%
-  kableExtra::landscape() %>%
+  kable_styling(latex_options = "scale_down") %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position

### 2021-11-05 Tables/studentVarDescr.tex
AOT-M Methods first draft
AOT-M contact hypothesis code added

@@
 
-\caption{Student: Multilevel Core Variable Descriptives}
+\caption{\label{tab:studentVarDescr}Student: Multilevel Core Variable Descriptives}
 \centering
-\begin{tabular}[t]{llcccc}
+\begin{tabular}[t]{llccccc}
 \toprule
-  & Core Need & Competence & Autonomy & Relatedness & Attitudes NL\\
+  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
 \midrule
-Core Need &  & 0.65*** & 0.67*** & 0.28** & 0.27**\\
-Competence & 0.30*** &  & 0.66*** & 0.59*** & 0.08\\
-Autonomy & 0.18*** & 0.33*** &  & 0.43*** & -0.08\\
-Relatedness & 0.43*** & 0.21*** & 0.12*** &  & -0.13\\
-Attitudes NL & 0.17*** & 0.08*** & 0.08*** & 0.08*** & \\
+Core Need &  & 0.60*** & 0.66*** & 0.43*** & 0.78*** & 0.11\\
+Competence & 0.24*** &  & 0.71*** & 0.65*** & 0.74*** & 0.09\\
+Autonomy & 0.15*** & 0.34*** &  & 0.56*** & 0.67*** & -0.06\\
+Relatedness & 0.45*** & 0.29*** & 0.42*** &  & 0.54*** & -0.11\\
+Quality & 0.17*** & 0.39*** & 0.08*** & 0.05** &  & 0.10\\
+Attitudes NL & 0.35*** & 0.43*** & 0.11*** & 0.10*** & 0.12*** & \\
 \addlinespace
-Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 67.26\\
-Between-person SD & 9.17 & 14.47 & 11.21 & 13.36 & 18.64\\
-Within-person SD & 20.33 & 21.17 & 16.06 & 28.74 & 9.40\\
-ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.80\\
-ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.99\\
+Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 83.77 & 67.26\\
+Between-person SD & 9.17 & 14.47 & 11.21 & 13.36 & 9.12 & 18.64\\
+Within-person SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
+ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.20 & 0.80\\
+ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.88 & 0.99\\
 \bottomrule
-\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
 \end{tabular}

### 2021-11-05 Tables/workerVarDescr.tex
AOT-P methods added
effect size trials
AOT-M Methods first draft
AOT-M contact hypothesis code added

@@
 \begin{table}
+\begin{minipage}[t][\textheight][t]{\textwidth}
 
-\caption{\label{tab:workerSampleInfo}Worker: Multilevel Core Variable Descriptives}
+\caption{\label{tab:workerVarDescr}Worker: Multilevel Core Variable Descriptives}
 \centering
-\begin{tabular}[t]{llcccc}
+\begin{tabular}[t]{llccccc}
 \toprule
-  & Core Need & Competence & Autonomy & Relatedness & Attitudes NL\\
+  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
 \midrule
-Core Need &  & 0.67*** & 0.54*** & 0.01 & -0.23\\
-Competence & 0.36*** &  & 0.72*** & -0.14 & -0.20\\
-Autonomy & 0.31*** & 0.09** &  & -0.05 & 0.19\\
-Relatedness & 0.45*** & 0.09** & 0.14*** &  & -0.06\\
-Attitudes NL & 0.05 & 0.11*** & 0.12*** & 0.14*** & \\
+Core Need &  & 0.82*** & 0.60*** & 0.33 & 0.52** & -0.03\\
+Competence & 0.36*** &  & 0.89*** & 0.26 & 0.39 & -0.23\\
+Autonomy & 0.28*** & 0.22*** &  & 0.31 & 0.57** & 0.02\\
+Relatedness & 0.50*** & 0.39*** & 0.37*** &  & -0.07 & 0.14\\
+Quality & 0.17*** & 0.44*** & 0.27*** & 0.26*** &  & 0.50*\\
+Attitudes NL & 0.24*** & 0.36*** & 0.24*** & 0.37*** & 0.52*** & \\
 \addlinespace
-Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 71.49\\
-Between-person SD & 14.68 & 13.72 & 12.09 & 14.59 & 12.91\\
-Within-person SD & 20.83 & 20.89 & 15.15 & 23.29 & 8.11\\
-ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.70\\
-ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.99\\
+Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 24.10 & 71.49\\
+Between-person SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.50 & 12.91\\
+Within-person SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
+ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.18 & 0.70\\
+ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.79 & 0.99\\
 \bottomrule
-\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
-\multicolumn{6}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
 \end{tabular}
+\end{minipage}
 \end{table}

### 2021-11-05 Methods-and-Results.tex
AOT-M contact H results rendered

@@
 \subsection{Results}
+
+\subsubsection{Contact Hypothesis}
+
+We tested the most general contact hypothesis in two steps. First, we
+assessed whether more intergroup interactions were related to to more
+positive outgroup attitudes. Second, we tested whether a potential
+positive effect on outgroup attitudes depended on the interaction
+quality (jointly with the number of interactions). We find no
+significant correlation between intergroup contact and average outgroup
+attitudes --- for neither the total number of outgroup interactions
+(\textit{r} = 0.01, \textit{p} = 0.946) and the number of measurement
+beeps with an interaction (\textit{r} = 0.13, \textit{p} = 0.291). This
+is to say that within our data, participants with more outgroup
+interactions did not have significantly more positive or negative
+outgroup attitudes. This is again consistent with the results we found
+in the first study but inconsitent with the significant relationship we
+find in the second study.
+
+However, we do find a significant correlation between the participants'
+Average Interaction Quality and their Average Outgroup Attitudes
+(\textit{r} = 0.25, \textit{p} = 0.036). Thus, when considering the
+number of interactions and average interaction quality jointly in a
+linear regression, we only find a main effect of average perceived
+interaction quality on predict outgroup attitudes (\textit{b} = 0.36,
+\textit{t}(67) = 2.22, \textit{p} = 0.030, \(\eta_p^2\) = 0.07). Given
+the missing aggregate relationship between number of interactions and
+outgroup attitudes, we find no significant effect of interactions
+themselves nor do we find a significant interaction effect. This result
+mirrors that of study one but is inconsistent with the second study. But
+again this inconsistency is not necessarily surprising given that the
+variables aggregate all within person variation and there were
+substantially more measurements where participants did not have an
+interaction (but reported their outgroup attitudes) than measurements
+that followed an outgroup contact.
+
+We additionally used a multilevel regression to check whether having an
+interaction with an outgroup member had a situational (i.e.,
+contemporaneous) effect within the participants. We find that having an
+outgroup interaction is indeed associated with significantly more
+positive outgroup attitudes within the participants (random slopes
+model; \textit{b} = 5.63, \textit{t}(3834) = 6.61, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}3.96, 7.31{]}), even after
+controlling for having an interaction with a non-Dutch (which did not
+relate to outgroup attitudes independently; For full results see Online
+Supplementary Materials B). Thus, in our third dataset we find some
+mixed results, outgroup contacts are not significantly related to
+outgroup attitudes on aggregate between participants and this effect is
+also not suppressed by a average interaction quality (i.e., no
+interaction effect). However, while the aggregate data is partly
+inconsistent with the first two studies, the within person contemoranous
+effect of intergroup contact is consistent across all three studies.
+
+\subsubsection{Allport's Conditions}
+
+\subsubsection{Core Need}
+
+\subsubsection{Robustness}

### 2021-11-05 Methods-and-Results.Rmd
Updates from Overleaf

@@
     data = dtWorker$full,
+    na.action=na.omit,
     control = list(opt = "nlmimb")
@@
     random =  ~ 1 | PID,
+    na.action=na.omit,
     data = dtWorkerSupp$workerInteractionType
@@
     data = dtWorkerSupp$workerOutgroupInteraction,
+    na.action=na.omit,
     control = list(opt = "nlmimb")
@@
     random = ~ 1 | PID,
+    na.action=na.omit,
     data = dtWorkerSupp$workerOutWithinBetween
@@
     control = lmeControl(opt = "optim"),
+    na.action=na.omit,
     data = dtWorkerSupp$workerOutWithinBetween
@@
     data = dtWorkerSupp$workerOutWithinBetween,
+    na.action=na.omit,
     control = list(opt = "nlmimb")
@@
     random =  ~ 1 | PID,
+    na.action=na.omit,
     data = dtWorkerSupp$workerWithinBetween
@@
   control = lmeControl(opt = "optim"),
+  na.action=na.omit,
   data = dtWorkerSupp$workerWithinBetween
@@
 
-\subsubsection{Contact Hypothesis}
+```{r medicalFreqAttCor, include=FALSE}
+dtMedicalSupp$medicalContactFreq <-
+  dtMedicalSupp$medicalContactFreq %>%
+  mutate(
+    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
+    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
+    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
+    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
+  )
+
+# correlation panel
+pairs.panels.new(
+  dtMedicalSupp$medicalContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
+    "Sum:\nNumber of Outgroup Contacts (NL)",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+
+# correlation panel with interaction sums winsorized
+pairs.panels.new(
+  dtMedicalSupp$medicalContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
+    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+```
+
+\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
+First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
+Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
+We find no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+This is to say that within our data, participants with more outgroup interactions did not have significantly more positive or negative outgroup attitudes.
+This is again consistent with the results we found in the first study but inconsitent with the significant relationship we find in the second study.
+
+```{r medicalModelOlsAttFreqQual, include=FALSE}
+# create list to store Worker models
+mdlMedical <- list()
+
+# regression
+mdlMedical$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)
+
+summ(
+  mdlMedical$lmAttFreqQualX,
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedical$lmAttFreqQualXEta <-
+  effectsize::eta_squared(mdlMedical$lmAttFreqQualX, partial = TRUE)
+
+interactions::interact_plot(
+  mdlMedical$lmAttFreqQualX,
+  pred = SumContactNL_c,
+  modx = AvQuality_c,
+  interval = TRUE,
+  partial.residuals = TRUE
+)
+
+interactions::johnson_neyman(mdlMedical$lmAttFreqQualX,
+                             pred = SumContactNL_c,
+                             modx = AvQuality_c,
+                             alpha = .05)
+```
+
+However, we do find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
+Given the missing aggregate relationship between number of interactions and outgroup attitudes, we find no significant effect of interactions themselves nor do we find a significant interaction effect.
+This result mirrors that of study one but is inconsistent with the second study.
+But again this inconsistency is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.
+
+```{r medicalModelMLAttNull, include=FALSE}
+# Create and save Model
+mdlMedical$lmerAttNullType <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
+             data = dtMedical$full %>%
+               filter(complete.cases(
+                 OutgroupInteraction, NonOutgroupInteraction
+               ))) # use optim if it does not converge
+
+mdlMedical$lmeAttNullType <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = dtMedical$full %>%
+      filter(complete.cases(
+        OutgroupInteraction, NonOutgroupInteraction
+      )),
+    na.action = na.omit,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(mdlMedical$lmerAttNull) #or with the lme function
+summ(mdlMedical$lmerAttNullType, digits = 3)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlMedical$varAttNullType <- 
+  VarCorr(mdlMedical$lmeAttNullType) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlMedical$tauAttNullType <- 
+  as.numeric(mdlMedical$varAttNullType[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlMedical$sigmaAttNullType <- 
+  as.numeric(mdlMedical$varAttNullType[2])
+# The ICC estimate (between/between+within) is:
+mdlMedical$IccAttNullType <-
+  (as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))
+mdlMedical$IccPercAttNull <-
+  ((as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))) * 100
+```
+```{r medicalModelInterceptAttType, include = FALSE}
+# Create and save Model
+mdlMedical$lmeInterceptAttType <-
+  lme(
+    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
+    random =  ~ 1 | PID,
+    na.action=na.omit,
+    data = dtMedical$full
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedical$lmerInterceptAttType <- lmer(
+    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    data = dtMedical$full
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedical$lmerInterceptAttTypeCI <- confint(mdlMedical$lmerInterceptAttType)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedical$lmeAttNullType, 
+      mdlMedical$lmeInterceptAttType) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedical$varInterceptAttType <- 
+  lme4::VarCorr(mdlMedical$lmeInterceptAttType)
+```
+```{r medicalModelSlopesInteractionType, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedical$lmeSlopesAttType <- lme(
+  AttitudesDutch ~
+    OutgroupInteraction + NonOutgroupInteraction,
+  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  na.action=na.omit,
+  data = dtMedical$full
+)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedical$lmerSlopesAttType <- lmer(
+    AttitudesDutch ~
+      OutgroupInteraction + NonOutgroupInteraction +
+      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+    data = dtMedical$full
+  ), 
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedical$lmerSlopesAttTypeCI <- confint(mdlMedical$lmerSlopesAttType)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedical$lmeAttNullType,
+      mdlMedical$lmeInterceptAttType, 
+      mdlMedical$lmeSlopesAttType) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedical$varSlopesAttType <- 
+  lme4::VarCorr(mdlMedical$lmeSlopesAttType)
+
+# Assumption Checks:
+mdlMedical$diagSlopesAttType <-
+  sjPlot::plot_model(mdlMedical$lmerSlopesAttType, type = "diag")
+grid.arrange(
+  mdlMedical$diagSlopesAttType[[1]],
+  mdlMedical$diagSlopesAttType[[2]]$`PID`,
+  mdlMedical$diagSlopesAttType[[3]],
+  mdlMedical$diagSlopesAttType[[4]]
+)
+
+# Plot prediction model
+mdlMedical$predSlopesAttType <-
+  dtMedical$full %>%
+  filter(complete.cases(OutgroupInteraction, NonOutgroupInteraction)) %>%
+  select(AttitudesDutch, TIDnum, PID) %>%
+  mutate(measure = predict(
+    mdlMedical$lmeSlopesAttType,
+    dtMedical$full %>%
+      filter(complete.cases(
+        OutgroupInteraction, NonOutgroupInteraction
+      )),
+    re.form = NA
+  ))
+
+(
+  mdlMedical$predPltSlopesAttType <-
+    ggplot(data = mdlMedical$predSlopesAttType %>% filter(PID %in% dtMedicalSupp$medicalPltIDs), 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/Medical_PredictionPlot_SlopesAttType.png",
+  mdlMedical$predPltSlopesAttType,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
+Thus, in our third dataset we find some mixed results, outgroup contacts are not significantly related to outgroup attitudes on aggregate between participants and this effect is also not suppressed by a average interaction quality (i.e., no interaction effect).
+However, while the aggregate data is partly inconsistent with the first two studies, the within person contemoranous effect of intergroup contact is consistent across all three studies.
 

### 2021-11-06 Methods-and-Results.Rmd
Updates from Overleaf

@@
   control = lmeControl(opt = "optim"),
-  na.action=na.omit,
+  na.action = na.omit,
   data = dtMedical$full
@@
 
+```{r medicalOutModelMLAttNull, include=FALSE}
+# create empty list to organize models
+mdlMedicalOut <- 
+  list(
+    Att = list(),
+    Qlt = list()
+  )
+
+# Create and save Model
+mdlMedicalOut$Att$lmerNull <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
+             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
+mdlMedicalOut$Att$lmeNull <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.omit,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.ML.r) #or with the lme function
+summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlMedicalOut$Att$varNull <- 
+  VarCorr(mdlMedicalOut$Att$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlMedicalOut$Att$tauNull <- 
+  as.numeric(mdlMedicalOut$Att$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlMedicalOut$Att$sigmaNull <- 
+  as.numeric(mdlMedicalOut$Att$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlMedicalOut$Att$IccNull <-
+  (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))
+mdlMedicalOut$Att$IccPercNull <-
+  ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100
+```
+```{r medicalOutModelInterceptAttAllport, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptAllport <-
+  lme(
+    AttitudesDutch ~ AllportsCondition_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptAllport <-
+    lmer(
+      AttitudesDutch ~ AllportsCondition_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Att$lmerInterceptAllportCI <- 
+  confint(mdlMedicalOut$Att$lmerInterceptAllport)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull, 
+      mdlMedicalOut$Att$lmeInterceptAllport) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptAllport <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllport)
+```
+```{r medicalOutModelSlopesAttAllport, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesAllport <-
+  lme(
+    AttitudesDutch ~
+      AllportsCondition_cwc,
+    random = ~ 1 + AllportsCondition_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesAllport <- lmer(
+    AttitudesDutch ~
+      AllportsCondition_cwc +
+      (1 + AllportsCondition_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# all variables standardized within PPT
+summ(
+  mdlMedicalOut$Att$lmerSlopesAllportZ <- lmer(
+    AttitudesDutch_zwc ~
+      AllportsCondition_zwc +
+      (1 + AllportsCondition_zwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# standardized coefficients
+stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesAllport)
+
+# 95%CIs
+mdlMedicalOut$Att$lmerSlopesAllportCI <- confint(mdlMedicalOut$Att$lmerSlopesAllport)
+
+# Attempts at R^2
+r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesAllport, bargraph = TRUE)
+mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesAllport)
+performance::r2(mdlMedicalOut$Att$lmerSlopesAllport)
+performance::model_performance(mdlMedicalOut$Att$lmerSlopesAllport)
+performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
+                                 mdlMedicalOut$Att$lmerInterceptAllport, 
+                                 mdlMedicalOut$Att$lmerSlopesAllport)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull, 
+      mdlMedicalOut$Att$lmeInterceptAllport, 
+      mdlMedicalOut$Att$lmeSlopesAllport) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesAllport <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesAllport)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesAllport <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesAllport, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesAllport[[1]],
+  mdlMedicalOut$Att$diagSlopesAllport[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesAllport[[3]],
+  mdlMedicalOut$Att$diagSlopesAllport[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesAllport <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllport,
+                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesAllport <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesAllport, 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllport.png",
+  mdlMedicalOut$Att$predPltSlopesAllport,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+```{r medicalOutModelMLQltNull, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Qlt$lmerNull <-
+  lme4::lmer(qualityOverall ~ 1 + (1 | PID), 
+             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
+mdlMedicalOut$Qlt$lmeNull <-
+  mdlMedicalOut$Qlt$lmeNull <-lme(
+    qualityOverall ~ 1,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.Qual.ML.r) #or with the lme function
+summ(mdlMedicalOut$Qlt$lmerNull, digits = 3)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=medicalOutgroupInteraction),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlMedicalOut$Qlt$varNull <- 
+  VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlMedicalOut$Qlt$tauNull <- 
+  as.numeric(mdlMedicalOut$Qlt$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlMedicalOut$Qlt$sigmaNull <- 
+  as.numeric(mdlMedicalOut$Qlt$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlMedicalOut$Qlt$IccNull <-
+  (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))
+mdlMedicalOut$Qlt$IccPercNull <-
+  ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100
+```
+```{r medicalOutModelInterceptQltAllport, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Qlt$lmeInterceptAllport <-
+  lme(
+    qualityOverall ~ AllportsCondition_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Qlt$lmerInterceptAllport <-
+    lmer(
+      qualityOverall ~ AllportsCondition_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Qlt$lmerInterceptAllportCI <- 
+  confint(mdlMedicalOut$Qlt$lmerInterceptAllport)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(qualityOverall ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Qlt$lmeNull, 
+      mdlMedicalOut$Qlt$lmeInterceptAllport) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Qlt$varInterceptAllport <-
+  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptAllport)
+```
+```{r medicalOutModelSlopesQltAllport, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Qlt$lmeSlopesAllport <-
+  lme(
+    qualityOverall ~
+      AllportsCondition_cwc,
+    random = ~ 1 + AllportsCondition_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Qlt$lmerSlopesAllport <-
+    lmer(
+      qualityOverall ~
+        AllportsCondition_cwc +
+        (1 + AllportsCondition_cwc | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Qlt$lmerSlopesAllportCI <- 
+  confint(mdlMedicalOut$Qlt$lmerSlopesAllport)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(mdlMedicalOut$Qlt$lmerSlopesAllport,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Qlt$lmeNull, 
+      mdlMedicalOut$Qlt$lmeInterceptAllport, 
+      mdlMedicalOut$Qlt$lmeSlopesAllport) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Qlt$varSlopesAllport <- 
+  lme4::VarCorr(mdlMedicalOut$Qlt$lmeSlopesAllport)
+
+# Assumption Checks:
+mdlMedicalOut$Qlt$diagSlopesAllport <-
+  sjPlot::plot_model(mdlMedicalOut$Qlt$lmerSlopesAllport, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Qlt$diagSlopesAllport[[1]],
+  mdlMedicalOut$Qlt$diagSlopesAllport[[2]]$`PID`,
+  mdlMedicalOut$Qlt$diagSlopesAllport[[3]],
+  mdlMedicalOut$Qlt$diagSlopesAllport[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Qlt$predSlopesAllport <- 
+  dtMedicalSupp$medicalOutWithinBetween %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesAllport,
+                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Qlt$predPltSlopesAllport <-
+    ggplot(data = mdlMedicalOut$Qlt$predSlopesAllport %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAllport.png",
+  mdlMedicalOut$Qlt$predPltSlopesAllport,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+
+```
+```{r medicalOutModelInterceptAttAllportQlt, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptAllportQlt <-
+  lme(
+    AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptAllportQlt <-
+    lmer(
+      AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerInterceptAllportQltCI <- 
+  confint(mdlMedicalOut$Att$lmerInterceptAllportQlt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull, 
+  mdlMedicalOut$Att$lmeInterceptAllportQlt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptAllportQlt <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllportQlt)
+```
+```{r medicalOutModelSlopesAttAllportQlt, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesAllportQlt <-
+  lme(
+    AttitudesDutch ~
+      AllportsCondition_cwc + qualityOverall_cwc,
+    random = ~ 1 + AllportsCondition_cwc + qualityOverall_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesAllportQlt <- lmer(
+    AttitudesDutch ~
+      AllportsCondition_cwc + qualityOverall_cwc +
+      (1 + AllportsCondition_cwc + qualityOverall_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerSlopesAllportQltCI <- 
+  confint(mdlMedicalOut$Att$lmerSlopesAllportQlt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull,
+  mdlMedicalOut$Att$lmeInterceptAllportQlt,
+  mdlMedicalOut$Att$lmeSlopesAllportQlt
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesAllportQlt <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesAllportQlt)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesAllportQlt <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesAllportQlt, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesAllportQlt[[1]],
+  mdlMedicalOut$Att$diagSlopesAllportQlt[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesAllportQlt[[3]],
+  mdlMedicalOut$Att$diagSlopesAllportQlt[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesAllportQlt <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(complete.cases(AllportsCondition, qualityOverall)) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllportQlt,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(AllportsCondition, qualityOverall)) %>%
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesAllportQlt <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesAllportQlt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllportQlt.png",
+  mdlMedicalOut$Att$predPltSlopesAllportQlt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We sequentially tested whether the fulfillment of Allport's Contact Conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly.
+We find that in the multilevel models, the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
+However, if we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`).
+These results indicate that in this dataset the the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
+
+\faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?
+
 \subsubsection{Core Need}
+
+```{r medicalOutModelMLAttNull, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Att$lmerNull <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
+             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
+mdlMedicalOut$Att$lmeNull <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.omit,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.ML.r) #or with the lme function
+summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlMedicalOut$Att$varNull <- 
+  VarCorr(mdlMedicalOut$Att$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlMedicalOut$Att$tauNull <- 
+  as.numeric(mdlMedicalOut$Att$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlMedicalOut$Att$sigmaNull <- 
+  as.numeric(mdlMedicalOut$Att$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlMedicalOut$Att$IccNull <-
+  (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))
+mdlMedicalOut$Att$IccPercNull <-
+  ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100
+```
+```{r medicalOutModelInterceptAttCore, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptCore <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptCore <-
+    lmer(
+      AttitudesDutch ~ KeyNeedFulfillment_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Att$lmerInterceptCoreCI <- 
+  confint(mdlMedicalOut$Att$lmerInterceptCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull, 
+      mdlMedicalOut$Att$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptCore <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCore)
+```
+```{r medicalOutModelSlopesAttCore, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesCore <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesCore <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc +
+      (1 + KeyNeedFulfillment_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# all variables standardized within PPT
+summ(
+  mdlMedicalOut$Att$lmerSlopesCoreZ <- lmer(
+    AttitudesDutch_zwc ~
+      KeyNeedFulfillment_zwc +
+      (1 + KeyNeedFulfillment_zwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# standardized coefficients
+stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesCore)
+
+# 95%CIs
+mdlMedicalOut$Att$lmerSlopesCoreCI <- confint(mdlMedicalOut$Att$lmerSlopesCore)
+
+# Attempts at R^2
+r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesCore, bargraph = TRUE)
+mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesCore)
+performance::r2(mdlMedicalOut$Att$lmerSlopesCore)
+performance::model_performance(mdlMedicalOut$Att$lmerSlopesCore)
+performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
+                                 mdlMedicalOut$Att$lmerInterceptCore, 
+                                 mdlMedicalOut$Att$lmerSlopesCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull, 
+      mdlMedicalOut$Att$lmeInterceptCore, 
+      mdlMedicalOut$Att$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesCore <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCore)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesCore <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesCore[[1]],
+  mdlMedicalOut$Att$diagSlopesCore[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesCore[[3]],
+  mdlMedicalOut$Att$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesCore <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(complete.cases(KeyNeedFulfillment)) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCore,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment)) %>% 
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesCore <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesCore, 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCore.png",
+  mdlMedicalOut$Att$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+```{r medicalOutModelMLQltNull, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Qlt$lmerNull <-
+  lme4::lmer(qualityOverall ~ 1 + (1 | PID), 
+             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
+mdlMedicalOut$Qlt$lmeNull <-
+  mdlMedicalOut$Qlt$lmeNull <-lme(
+    qualityOverall ~ 1,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.Qual.ML.r) #or with the lme function
+summ(mdlMedicalOut$Qlt$lmerNull, digits = 3)
+
+# generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=medicalOutgroupInteraction),
+#                  method="boot",nsim=1000,
+#                  parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-Null-CI.csv")
+
+# Save variances
+mdlMedicalOut$Qlt$varNull <- 
+  VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlMedicalOut$Qlt$tauNull <- 
+  as.numeric(mdlMedicalOut$Qlt$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlMedicalOut$Qlt$sigmaNull <- 
+  as.numeric(mdlMedicalOut$Qlt$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlMedicalOut$Qlt$IccNull <-
+  (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))
+mdlMedicalOut$Qlt$IccPercNull <-
+  ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100
+```
+```{r medicalOutModelInterceptQltCore, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Qlt$lmeInterceptCore <-
+  lme(
+    qualityOverall ~ KeyNeedFulfillment_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Qlt$lmerInterceptCore <-
+    lmer(
+      qualityOverall ~ KeyNeedFulfillment_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Qlt$lmerInterceptCoreCI <- 
+  confint(mdlMedicalOut$Qlt$lmerInterceptCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(qualityOverall ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Qlt$lmeNull, 
+      mdlMedicalOut$Qlt$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Qlt$varInterceptCore <-
+  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptCore)
+```
+```{r medicalOutModelSlopesQltCore, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Qlt$lmeSlopesCore <-
+  lme(
+    qualityOverall ~
+      KeyNeedFulfillment_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Qlt$lmerSlopesCore <-
+    lmer(
+      qualityOverall ~
+        KeyNeedFulfillment_cwc +
+        (1 + KeyNeedFulfillment_cwc | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Qlt$lmerSlopesCoreCI <- 
+  confint(mdlMedicalOut$Qlt$lmerSlopesCore)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(mdlMedicalOut$Qlt$lmerSlopesCore,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Qlt$lmeNull, 
+      mdlMedicalOut$Qlt$lmeInterceptCore, 
+      mdlMedicalOut$Qlt$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Qlt$varSlopesCore <- 
+  lme4::VarCorr(mdlMedicalOut$Qlt$lmeSlopesCore)
+
+# Assumption Checks:
+mdlMedicalOut$Qlt$diagSlopesCore <-
+  sjPlot::plot_model(mdlMedicalOut$Qlt$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Qlt$diagSlopesCore[[1]],
+  mdlMedicalOut$Qlt$diagSlopesCore[[2]]$`PID`,
+  mdlMedicalOut$Qlt$diagSlopesCore[[3]],
+  mdlMedicalOut$Qlt$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Qlt$predSlopesCore <- 
+  dtMedicalSupp$medicalOutWithinBetween %>%
+  filter(complete.cases(KeyNeedFulfillment)) %>% 
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesCore,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment)) %>% 
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Qlt$predPltSlopesCore <-
+    ggplot(data = mdlMedicalOut$Qlt$predSlopesCore %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesCore.png",
+  mdlMedicalOut$Qlt$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+
+```
+```{r medicalOutModelInterceptAttCoreQlt, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptCoreQlt <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptCoreQlt <-
+    lmer(
+      AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerInterceptCoreQltCI <- 
+  confint(mdlMedicalOut$Att$lmerInterceptCoreQlt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull, 
+  mdlMedicalOut$Att$lmeInterceptCoreQlt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptCoreQlt <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreQlt)
+```
+```{r medicalOutModelSlopesAttCoreQlt, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesCoreQlt <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + qualityOverall_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesCoreQlt <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + qualityOverall_cwc +
+      (1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerSlopesCoreQltCI <- 
+  confint(mdlMedicalOut$Att$lmerSlopesCoreQlt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull,
+  mdlMedicalOut$Att$lmeInterceptCoreQlt,
+  mdlMedicalOut$Att$lmeSlopesCoreQlt
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesCoreQlt <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreQlt)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesCoreQlt <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreQlt, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[1]],
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[3]],
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesCoreQlt <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreQlt,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesCoreQlt <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreQlt.png",
+  mdlMedicalOut$Att$predPltSlopesCoreQlt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+We find that in the multilevel models, the fulfillment of core need fulfillment during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
+However, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`).
+These results indicate that in this dataset the the fulfillment of core situational needs had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
+
+\faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?
+
+\subsubsection{Compare Fulfillment of Core Need and Allport's Conditions}
 

### 2021-11-06 Methods-and-Results.tex
fromm pull request
Updates from Overleaf

@@
 
+We sequentially tested whether the fulfillment of Allport's Contact
+Conditions was (1) related to more positive outgroup attitudes, (2)
+higher perceived interaction quality, and (3) whether the variance
+explained by Allport's Conditions is assumed by the perceived
+interaction quality if considered jointly. We find that in the
+multilevel models, the fulfillment of Allport's Conditions during
+outgroup contacts was associated with more positive outgroup attitudes
+(random slopes model; \textit{b} = 0.22, \textit{t}(1601) = 5.86,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.15, 0.30{]}) and also
+predicted higher perceived interaction quality (random slopes model;
+\textit{b} = 0.65, \textit{t}(1605) = 11.82, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.54, 0.76{]}). However, if we consider the
+influences of Allport's Conditions and interaction quality on outgroup
+attitudes jointly, we find that perceived interaction quality is a
+substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
+\textit{t}(1600) = 6.25, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
+Allport's Conditions was less than half of its original effect size
+(\textit{b} = 0.09, \textit{t}(1600) = 2.89, \textit{p} = 0.004,
+\textit{95\%CI}{[}0.03, 0.15{]}). These results indicate that in this
+dataset the the fulfillment of Allport's conditions had a significant
+influence on outgroup attitudes and this effect is likely in parts
+explained by its effect through perceived interaction quality.
+
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
+
 \subsubsection{Core Need}
 
+We again sequentially tested whether the fulfillment of the core need
+during an interaction was (1) related to more positive outgroup
+attitudes, (2) higher perceived interaction quality, and (3) whether the
+variance explained by the core need is assumed by the perceived
+interaction quality if considered jointly. We find that in the
+multilevel models, the fulfillment of core need fulfillment during
+outgroup contacts was associated with more positive outgroup attitudes
+(random slopes model; \textit{b} = 0.19, \textit{t}(1601) = 5.29,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.12, 0.27{]}) and also
+predicted higher perceived interaction quality (random slopes model;
+\textit{b} = 0.43, \textit{t}(1605) = 8.35, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.33, 0.54{]}). However, if we consider the influences
+of core need fulfillment and interaction quality on outgroup attitudes
+jointly, we find that perceived interaction quality is a substantially
+stronger predictor (random slopes mode; \textit{b} = 0.17,
+\textit{t}(1600) = 6.86, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.22{]}) and the unique variance explained by
+core need fulfillment was roughly half of its original effect size
+(\textit{b} = 0.11, \textit{t}(1600) = 3.50, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.05, 0.17{]}). These results indicate that in
+this dataset the the fulfillment of core situational needs had a
+significant influence on outgroup attitudes and this effect is likely in
+parts explained by its effect through perceived interaction quality.
+
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
+
+\subsubsection{Compare Fulfillment of Core Need and Allport's Conditions}
+
 \subsubsection{Robustness}

### 2021-11-08 Methods-and-Results.Rmd
AOT-M Allport vs. Core comparison code added

@@
 ```
+
 ```{r medicalModelInterceptAttType, include = FALSE}
@@
 ```
+
 ```{r medicalModelSlopesInteractionType, include=FALSE}
@@
 ```
+
 ```{r medicalOutModelInterceptAttAllport, include=FALSE}
@@
 ```
+
 ```{r medicalOutModelSlopesAttAllport, include=FALSE}
@@
 # Attempts at R^2
-r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesAllport, bargraph = TRUE)
+#r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesAllport, bargraph = TRUE)
 mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesAllport)
@@
 ```
+
 ```{r medicalOutModelInterceptQltAllport, include=FALSE}
@@
 ```
+
 ```{r medicalOutModelSlopesQltAllport, include=FALSE}
@@
 ```
+
 ```{r medicalOutModelInterceptAttAllportQlt, include=FALSE}
@@
 ```
+
 ```{r medicalOutModelSlopesAttAllportQlt, include=FALSE}
@@
 
-```{r medicalOutModelMLAttNull, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmerNull <-
-  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
-             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
-mdlMedicalOut$Att$lmeNull <-
-  lme(
-    AttitudesDutch ~ 1,
-    random = ~ 1 | PID,
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.omit,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.ML.r) #or with the lme function
-summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
-# Save variances
-mdlMedicalOut$Att$varNull <- 
-  VarCorr(mdlMedicalOut$Att$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlMedicalOut$Att$tauNull <- 
-  as.numeric(mdlMedicalOut$Att$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlMedicalOut$Att$sigmaNull <- 
-  as.numeric(mdlMedicalOut$Att$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlMedicalOut$Att$IccNull <-
-  (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))
-mdlMedicalOut$Att$IccPercNull <-
-  ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100
-```
+<!-- ```{r medicalOutModelMLAttNull, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlMedicalOut$Att$lmerNull <- -->
+<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
+<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
+<!-- mdlMedicalOut$Att$lmeNull <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
+<!--     na.action = na.omit, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(Null.Out.ML.r) #or with the lme function -->
+<!-- summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE) -->
+
+<!-- # generate 95% parametric bootstrap CIs (and save them as a csv-file): -->
+<!-- # write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full), -->
+<!-- #                  method="boot",nsim=1000, -->
+<!-- #                  parallel = "multicore", ncpus = 4, seed = 42), -->
+<!-- #          "output/tables/ML-Null-CI.csv") -->
+
+<!-- # Save variances -->
+<!-- mdlMedicalOut$Att$varNull <-  -->
+<!--   VarCorr(mdlMedicalOut$Att$lmeNull) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlMedicalOut$Att$tauNull <-  -->
+<!--   as.numeric(mdlMedicalOut$Att$varNull[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlMedicalOut$Att$sigmaNull <-  -->
+<!--   as.numeric(mdlMedicalOut$Att$varNull[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlMedicalOut$Att$IccNull <- -->
+<!--   (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2]))) -->
+<!-- mdlMedicalOut$Att$IccPercNull <- -->
+<!--   ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100 -->
+<!-- ``` -->
 ```{r medicalOutModelInterceptAttCore, include=FALSE}
@@
 ```
+
 ```{r medicalOutModelSlopesAttCore, include=FALSE}
@@
 
-```{r medicalOutModelMLQltNull, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Qlt$lmerNull <-
-  lme4::lmer(qualityOverall ~ 1 + (1 | PID), 
-             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
-mdlMedicalOut$Qlt$lmeNull <-
-  mdlMedicalOut$Qlt$lmeNull <-lme(
-    qualityOverall ~ 1,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.Qual.ML.r) #or with the lme function
-summ(mdlMedicalOut$Qlt$lmerNull, digits = 3)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=medicalOutgroupInteraction),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
-# Save variances
-mdlMedicalOut$Qlt$varNull <- 
-  VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlMedicalOut$Qlt$tauNull <- 
-  as.numeric(mdlMedicalOut$Qlt$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlMedicalOut$Qlt$sigmaNull <- 
-  as.numeric(mdlMedicalOut$Qlt$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlMedicalOut$Qlt$IccNull <-
-  (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))
-mdlMedicalOut$Qlt$IccPercNull <-
-  ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100
-```
+<!-- ```{r medicalOutModelMLQltNull, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlMedicalOut$Qlt$lmerNull <- -->
+<!--   lme4::lmer(qualityOverall ~ 1 + (1 | PID),  -->
+<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
+<!-- mdlMedicalOut$Qlt$lmeNull <- -->
+<!--   mdlMedicalOut$Qlt$lmeNull <-lme( -->
+<!--     qualityOverall ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     na.action = na.omit, -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(Null.Out.Qual.ML.r) #or with the lme function -->
+<!-- summ(mdlMedicalOut$Qlt$lmerNull, digits = 3) -->
+
+<!-- # generate 95% parametric bootstrap CIs (and save them as a csv-file): -->
+<!-- # write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=medicalOutgroupInteraction), -->
+<!-- #                  method="boot",nsim=1000, -->
+<!-- #                  parallel = "multicore", ncpus = 4, seed = 42), -->
+<!-- #          "output/tables/ML-Null-CI.csv") -->
+
+<!-- # Save variances -->
+<!-- mdlMedicalOut$Qlt$varNull <-  -->
+<!--   VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlMedicalOut$Qlt$tauNull <-  -->
+<!--   as.numeric(mdlMedicalOut$Qlt$varNull[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlMedicalOut$Qlt$sigmaNull <-  -->
+<!--   as.numeric(mdlMedicalOut$Qlt$varNull[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlMedicalOut$Qlt$IccNull <- -->
+<!--   (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2]))) -->
+<!-- mdlMedicalOut$Qlt$IccPercNull <- -->
+<!--   ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100 -->
+<!-- ``` -->
+
 ```{r medicalOutModelInterceptQltCore, include=FALSE}
@@
 ```
+
 ```{r medicalOutModelSlopesQltCore, include=FALSE}
@@
 ```
+
 ```{r medicalOutModelInterceptAttCoreQlt, include=FALSE}
@@
 ```
+
 ```{r medicalOutModelSlopesAttCoreQlt, include=FALSE}
@@
 
+```{r AllportVsCore, include=FALSE}
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeSlopesAllport, 
+      mdlMedicalOut$Att$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Medical: Comparison of Allport's Conditions to Core Situational Need",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+AIC(
+
+)
+
+performance::compare_performance(
+  mdlMedicalOut$Att$lmerSlopesAllport,
+  mdlMedicalOut$Att$lmerSlopesCore
+)
+```
+
+```{r medicalOutModelInterceptAttCoreAllport, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptCoreAllport <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptCoreAllport <-
+    lmer(
+      AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerInterceptCoreAllportCI <- 
+  confint(mdlMedicalOut$Att$lmerInterceptCoreAllport)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull, 
+  mdlMedicalOut$Att$lmeInterceptAllport,
+  mdlMedicalOut$Att$lmeInterceptCoreAllport
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptCoreAllport <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreAllport)
+```
+
+```{r medicalOutModelSlopesAttCoreAllport, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesCoreAllport <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + AllportsCondition_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesCoreAllport <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + AllportsCondition_cwc +
+      (1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerSlopesCoreAllportCI <- 
+  confint(mdlMedicalOut$Att$lmerSlopesCoreAllport, method = "Wald")
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull,
+  mdlMedicalOut$Att$lmeInterceptCoreAllport,
+  mdlMedicalOut$Att$lmeSlopesCoreAllport
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesCoreAllport <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreAllport)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesCoreAllport <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreAllport, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[1]],
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[3]],
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesCoreAllport <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreAllport,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesCoreAllport <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreAllport.png",
+  mdlMedicalOut$Att$predPltSlopesCoreAllport,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+When comparing the
+
 \subsubsection{Robustness}

### 2021-11-08 Methods-and-Results.Rmd
AOT-M robustness code and interpretation added

@@
 
-When comparing the
+When we compare the model using the
 
 \subsubsection{Robustness}
+
+```{r medicalModelAttNullInt, include=FALSE}
+# Create and save Model
+mdlMedical$lmerAttNullInt <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
+             data = dtMedical$full %>%
+               filter(complete.cases(
+                 OutgroupInteraction
+               ))) # use optim if it does not converge
+
+mdlMedical$lmeAttNullInt <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = dtMedical$full %>%
+      filter(complete.cases(
+        OutgroupInteraction
+      )),
+    na.action = na.omit,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(mdlMedical$lmerAttNull) #or with the lme function
+summ(mdlMedical$lmerAttNullInt, digits = 3)
+```
+
+```{r medicalModelInterceptAttCoreInt, include=FALSE}
+# Create and save Model
+mdlMedical$lmeInterceptAttCoreInt <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction,
+    random =  ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedical$full
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedical$lmerInterceptAttCoreInt <- lmer(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction + (1 | PID),
+    data = dtMedical$full
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedical$lmerInterceptAttCoreIntCI <- 
+  confint(mdlMedical$lmerInterceptAttCoreInt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=dtMedical$full),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedical$lmeAttNullInt, 
+      mdlMedical$lmeInterceptAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = c("l", rep("c", ncol(.)-1)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedical$varInterceptAttCoreInt <- 
+  lme4::VarCorr(mdlMedical$lmeInterceptAttCoreInt)
+```
+```{r medicalModelSlopesAttCoreIntX, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedical$lmeSlopesAttCoreInt <- lme(
+  AttitudesDutch ~
+    KeyNeedFulfillment_cwc * OutgroupInteraction,
+  random = ~ 1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  na.action = na.omit,
+  data = dtMedical$full
+)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedical$lmerSlopesAttCoreInt <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc * OutgroupInteraction +
+      (1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID),
+    data = dtMedical$full
+  ), 
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedical$lmerSlopesAttCoreIntCI <- 
+  confint(mdlMedical$lmerSlopesAttCoreInt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedical$lmeAttNullInt, 
+      mdlMedical$lmeInterceptAttCoreInt,
+      mdlMedical$lmeSlopesAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedical$varSlopesAttCoreInt <- 
+  lme4::VarCorr(mdlMedical$lmeSlopesAttCoreInt)
+
+# Assumption Checks:
+mdlMedical$diagSlopesAttCoreInt <-
+  sjPlot::plot_model(mdlMedical$lmerSlopesAttCoreInt, type = "diag")
+grid.arrange(
+  mdlMedical$diagSlopesAttCoreInt[[1]],
+  mdlMedical$diagSlopesAttCoreInt[[2]]$`PID`,
+  mdlMedical$diagSlopesAttCoreInt[[3]],
+  mdlMedical$diagSlopesAttCoreInt[[4]]
+)
+
+# Plot prediction model
+mdlMedical$predSlopesAttCoreInt <- 
+  dtMedical$full %>%
+  filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
+  filter(PID %in% dtMedicalSupp$medicalPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedical$lmeSlopesAttCoreInt,
+                           dtMedical$full %>% 
+                             filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
+                             filter(PID %in% dtMedicalSupp$medicalPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedical$predPltSlopesAttCoreInt <-
+    ggplot(data = mdlMedical$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/Medical_PredictionPlot_SlopesAttCoreInt.png",
+  mdlMedical$predPltSlopesAttCoreInt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We again checked for alternative models to the core need fulfillment.
+First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
+Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "OutgroupInteractionYes")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+This finding is consistent with the results of the previous studies.
+
+```{r medicalOutModelInterceptAttCoreSdt, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptCoreSdt <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 | PID,
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptCoreSdt <- lmer(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
+#                  method="boot",nsim=1000, parallel = "multicore",
+#                  ncpus = 4, seed = 42),
+#          "output/tables/ML-Inter-CI.csv")
+
+# To be compared against a model with only the self determination theory needs
+mdlMedicalOut$Att$lmeInterceptSdt <-
+  lme(
+    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 | PID,
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.exclude
+  )
+
+summ(
+  mdlMedicalOut$Att$lmerInterceptSdt <- lmer(
+    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Compare new model to previous steps
+anova(
+  mdlMedicalOut$Att$lmeInterceptSdt,
+  mdlMedicalOut$Att$lmeInterceptCoreSdt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptCoreSdt <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreSdt)
+```
+
+```{r medicalOutModelSlopesAttCoreSdt, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesCoreSdt <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc + Competence_cwc + Relatedness_cwc | PID,
+    control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesCoreSdt <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerSlopesCoreSdtCI <- 
+  confint(mdlMedicalOut$Att$lmerSlopesCoreSdt)
+
+# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
+# write.csv(confint(model.ran0,
+#               method="boot",nsim=1000,
+#               parallel = "multicore", ncpus = 4, seed = 42),
+#          "output/tables/ML-RandomSlopes-CI.csv")
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeInterceptSdt,
+      mdlMedicalOut$Att$lmeInterceptCoreSdt, 
+      mdlMedicalOut$Att$lmeSlopesCoreSdt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# model with SDT only
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesSdt <-
+  lme(
+    AttitudesDutch ~
+      Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesSdt <- lmer(
+    AttitudesDutch ~
+      Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeInterceptSdt,
+      mdlMedicalOut$Att$lmeSlopesSdt, 
+      mdlMedicalOut$Att$lmeSlopesCoreSdt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesCoreSdt <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreSdt)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesCoreSdt <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreSdt, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesCoreSdt[[1]],
+  mdlMedicalOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesCoreSdt[[3]],
+  mdlMedicalOut$Att$diagSlopesCoreSdt[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesCoreSdt <- 
+  dtMedicalSupp$medicalOutWithinBetween %>%
+  filter(complete.cases(
+    KeyNeedFulfillment,
+    Autonomy, Competence, Relatedness
+    )) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID, Autonomy, Competence, Relatedness) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreSdt,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(
+                               KeyNeedFulfillment,
+                               Autonomy, Competence, Relatedness
+                             )) %>%
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesCoreSdt <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreStd.png",
+  mdlMedicalOut$Att$predPltSlopesCoreSdt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+
+# Model comparison
+medicalSdtComp <-
+  anova(
+    mdlMedicalOut$Att$lmerSlopesSdt, 
+    mdlMedicalOut$Att$lmerSlopesCoreSdt
+  ) %>%
+  as.data.frame()
+medicalSdtCompDf <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Df"]
+medicalSdtCompN <- sapply(ranef(mdlMedicalOut$Att$lmerSlopesCoreSdt), nrow)
+medicalSdtCompChi <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
+medicalSdtCompP <-
+  ifelse(medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
+         "< .001",
+         paste0("= ", medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
+
+medicalSdtCompChiSq <- paste0("$\\chi^2$(", medicalSdtCompDf, ", \\textit{N} = ", medicalSdtCompN, ") = ", medicalSdtCompChi, ", \\textit{p} ", medicalSdtCompP)
+```
+
+In a final step we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
+We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r medicalSdtCompChiSq`).
+We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFulfillment_cwc")`).
+When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
+However, similar to the previous study, in this large sample relatedness (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each predicted positive outgroup attitudes independently.
+However, the regression coefficient is three times as large for the core need fulfillment (with all scaling being equal).
+For full results see Online Supplementary Information B.
 

### 2021-11-08 Methods-and-Results.Rmd
AOT-M model comparison interpretation added

@@
 AIC(
-
+  mdlMedicalOut$Att$lmerSlopesAllport,
+  mdlMedicalOut$Att$lmerSlopesCore
+)
+
+BIC(
+  mdlMedicalOut$Att$lmerSlopesAllport,
+  mdlMedicalOut$Att$lmerSlopesCore
 )
@@
 
-When we compare the model using the
+To compare the models using either Allport's conditions or the core need fulfillment to predict outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
+When comparing the model selection indices we find that the fulfillment of the situation core need, indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r AIC(mdlMedicalOut$Att$lmerSlopesCore)` < `r AIC(mdlMedicalOut$Att$lmerSlopesAllport)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r BIC(mdlMedicalOut$Att$lmerSlopesCore)` < `r BIC(mdlMedicalOut$Att$lmerSlopesAllport)` $BIC_{Allport}$).
+Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`).
+This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
 

### 2021-11-08 Methods-and-Results.Rmd
confint set to "Wald"for fixed effects for quicker renders

@@
 
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=dtWorker$full),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
 # Save variances
@@
 
-mdlWorker$lmerInterceptAttTypeCI <- confint(mdlWorker$lmerInterceptAttType)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+mdlWorker$lmerInterceptAttTypeCI <- 
+  confint(method = "Wald", mdlWorker$lmerInterceptAttType)
 
@@
 summ(mdlWorkerOut$Att$lmerNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=dtWorker$full),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
 
@@
 mdlWorkerOut$Att$lmerInterceptCoreCI <- 
-  confint(mdlWorkerOut$Att$lmerInterceptCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCore)
 
@@
 # 95%CIs
-mdlWorkerOut$Att$lmerSlopesCoreCI <- confint(mdlWorkerOut$Att$lmerSlopesCore)
+mdlWorkerOut$Att$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCore)
 
@@
                                  mdlWorkerOut$Att$lmerSlopesCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
 
@@
 
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
 # Save variances
@@
 mdlWorkerOut$Qlt$lmerInterceptCoreCI <- 
-  confint(mdlWorkerOut$Qlt$lmerInterceptCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(quality_overall_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlWorkerOut$Qlt$lmerInterceptCore)
 
@@
 mdlWorkerOut$Qlt$lmerSlopesCoreCI <- 
-  confint(mdlWorkerOut$Qlt$lmerSlopesCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(mdlWorkerOut$Qlt$lmerSlopesCore,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlWorkerOut$Qlt$lmerSlopesCore)
 
@@
 mdlWorkerOut$Att$lmerInterceptCoreQltCI <- 
-  confint(mdlWorkerOut$Att$lmerInterceptCoreQlt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCoreQlt)
 
@@
 mdlWorkerOut$Att$lmerSlopesCoreQltCI <- 
-  confint(mdlWorkerOut$Att$lmerSlopesCoreQlt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreQlt)
 
@@
 mdlWorker$lmerInterceptAttCoreIntCI <- 
-  confint(mdlWorker$lmerInterceptAttCoreInt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlWorker$lmerInterceptAttCoreInt)
 
@@
 mdlWorker$lmerSlopesAttCoreIntCI <- 
-  confint(mdlWorker$lmerSlopesAttCoreInt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlWorker$lmerSlopesAttCoreInt)
 
@@
 
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
 # To be compared against a model with only the self determination theory needs
@@
 mdlWorkerOut$Att$lmerSlopesCoreSdtCI <- 
-  confint(mdlWorkerOut$Att$lmerSlopesCoreSdt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreSdt)
 
@@
 
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
 # Save variances
@@
 
-mdlStudent$lmerInterceptAttTypeCI <- confint(mdlStudent$lmerInterceptAttType)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+mdlStudent$lmerInterceptAttTypeCI <- 
+  confint(method = "Wald", mdlStudent$lmerInterceptAttType)
 
@@
 
-mdlStudent$lmerSlopesAttTypeCI <- confint(mdlStudent$lmerSlopesAttType)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+mdlStudent$lmerSlopesAttTypeCI <- 
+  confint(method = "Wald", mdlStudent$lmerSlopesAttType)
 
@@
 summ(mdlStudentOut$Att$lmerNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
 
@@
 mdlStudentOut$Att$lmerInterceptCoreCI <- 
-  confint(mdlStudentOut$Att$lmerInterceptCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCore)
 
@@
 # 95%CIs
-mdlStudentOut$Att$lmerSlopesCoreCI <- confint(mdlStudentOut$Att$lmerSlopesCore)
+mdlStudentOut$Att$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCore)
 
@@
                                  mdlStudentOut$Att$lmerSlopesCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
 
@@
 summ(mdlStudentOut$Qlt$lmerNull, digits = 3)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
 
@@
 mdlStudentOut$Qlt$lmerInterceptCoreCI <- 
-  confint(mdlStudentOut$Qlt$lmerInterceptCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(quality_overall ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlStudentOut$Qlt$lmerInterceptCore)
 
@@
 mdlStudentOut$Qlt$lmerSlopesCoreCI <- 
-  confint(mdlStudentOut$Qlt$lmerSlopesCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(mdlStudentOut$Qlt$lmerSlopesCore,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlStudentOut$Qlt$lmerSlopesCore)
 
@@
 mdlStudentOut$Att$lmerInterceptCoreQltCI <- 
-  confint(mdlStudentOut$Att$lmerInterceptCoreQlt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCoreQlt)
 
@@
 mdlStudentOut$Att$lmerSlopesCoreQltCI <- 
-  confint(mdlStudentOut$Att$lmerSlopesCoreQlt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreQlt)
 
@@
 mdlStudent$lmerInterceptAttCoreIntCI <- 
-  confint(mdlStudent$lmerInterceptAttCoreInt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=dtStudent$full),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlStudent$lmerInterceptAttCoreInt)
 
@@
 mdlStudent$lmerSlopesAttCoreIntCI <- 
-  confint(mdlStudent$lmerSlopesAttCoreInt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlStudent$lmerSlopesAttCoreInt)
 
@@
 
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
 # To be compared against a model with only the self determination theory needs
@@
 mdlStudentOut$Att$lmerSlopesCoreSdtCI <- 
-  confint(mdlStudentOut$Att$lmerSlopesCoreSdt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreSdt)
 
@@
 summ(mdlMedical$lmerAttNullType, digits = 3)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
 
@@
 
-mdlMedical$lmerInterceptAttTypeCI <- confint(mdlMedical$lmerInterceptAttType)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+mdlMedical$lmerInterceptAttTypeCI <- 
+  confint(method = "Wald", mdlMedical$lmerInterceptAttType)
 
@@
 
-mdlMedical$lmerSlopesAttTypeCI <- confint(mdlMedical$lmerSlopesAttType)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+mdlMedical$lmerSlopesAttTypeCI <- 
+  confint(method = "Wald", mdlMedical$lmerSlopesAttType)
 
@@
 mdlMedicalOut$Att$lmerInterceptAllportCI <- 
-  confint(mdlMedicalOut$Att$lmerInterceptAllport)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllport)
 
@@
 # 95%CIs
-mdlMedicalOut$Att$lmerSlopesAllportCI <- confint(mdlMedicalOut$Att$lmerSlopesAllport)
+mdlMedicalOut$Att$lmerSlopesAllportCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllport)
 
@@
                                  mdlMedicalOut$Att$lmerSlopesAllport)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
 
@@
 
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=medicalOutgroupInteraction),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
-
 # Save variances
@@
 mdlMedicalOut$Qlt$lmerInterceptAllportCI <- 
-  confint(mdlMedicalOut$Qlt$lmerInterceptAllport)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(qualityOverall ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptAllport)
 
@@
 mdlMedicalOut$Qlt$lmerSlopesAllportCI <- 
-  confint(mdlMedicalOut$Qlt$lmerSlopesAllport)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(mdlMedicalOut$Qlt$lmerSlopesAllport,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesAllport)
 
@@
 mdlMedicalOut$Att$lmerInterceptAllportQltCI <- 
-  confint(mdlMedicalOut$Att$lmerInterceptAllportQlt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllportQlt)
 
@@
 mdlMedicalOut$Att$lmerSlopesAllportQltCI <- 
-  confint(mdlMedicalOut$Att$lmerSlopesAllportQlt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllportQlt)
 
@@
 
-<!-- ```{r medicalOutModelMLAttNull, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlMedicalOut$Att$lmerNull <- -->
-<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
-<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
-<!-- mdlMedicalOut$Att$lmeNull <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
-<!--     na.action = na.omit, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(Null.Out.ML.r) #or with the lme function -->
-<!-- summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE) -->
-
-<!-- # generate 95% parametric bootstrap CIs (and save them as a csv-file): -->
-<!-- # write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full), -->
-<!-- #                  method="boot",nsim=1000, -->
-<!-- #                  parallel = "multicore", ncpus = 4, seed = 42), -->
-<!-- #          "output/tables/ML-Null-CI.csv") -->
-
-<!-- # Save variances -->
-<!-- mdlMedicalOut$Att$varNull <-  -->
-<!--   VarCorr(mdlMedicalOut$Att$lmeNull) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlMedicalOut$Att$tauNull <-  -->
-<!--   as.numeric(mdlMedicalOut$Att$varNull[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlMedicalOut$Att$sigmaNull <-  -->
-<!--   as.numeric(mdlMedicalOut$Att$varNull[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlMedicalOut$Att$IccNull <- -->
-<!--   (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2]))) -->
-<!-- mdlMedicalOut$Att$IccPercNull <- -->
-<!--   ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100 -->
-<!-- ``` -->
 ```{r medicalOutModelInterceptAttCore, include=FALSE}
@@
 mdlMedicalOut$Att$lmerInterceptCoreCI <-
-  confint(mdlMedicalOut$Att$lmerInterceptCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCore)
 
@@
 # 95%CIs
-mdlMedicalOut$Att$lmerSlopesCoreCI <- confint(mdlMedicalOut$Att$lmerSlopesCore)
+mdlMedicalOut$Att$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCore)
 
@@
                                  mdlMedicalOut$Att$lmerSlopesCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
 
@@
 
-<!-- ```{r medicalOutModelMLQltNull, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlMedicalOut$Qlt$lmerNull <- -->
-<!--   lme4::lmer(qualityOverall ~ 1 + (1 | PID),  -->
-<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
-<!-- mdlMedicalOut$Qlt$lmeNull <- -->
-<!--   mdlMedicalOut$Qlt$lmeNull <-lme( -->
-<!--     qualityOverall ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     na.action = na.omit, -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(Null.Out.Qual.ML.r) #or with the lme function -->
-<!-- summ(mdlMedicalOut$Qlt$lmerNull, digits = 3) -->
-
-<!-- # generate 95% parametric bootstrap CIs (and save them as a csv-file): -->
-<!-- # write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=medicalOutgroupInteraction), -->
-<!-- #                  method="boot",nsim=1000, -->
-<!-- #                  parallel = "multicore", ncpus = 4, seed = 42), -->
-<!-- #          "output/tables/ML-Null-CI.csv") -->
-
-<!-- # Save variances -->
-<!-- mdlMedicalOut$Qlt$varNull <-  -->
-<!--   VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlMedicalOut$Qlt$tauNull <-  -->
-<!--   as.numeric(mdlMedicalOut$Qlt$varNull[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlMedicalOut$Qlt$sigmaNull <-  -->
-<!--   as.numeric(mdlMedicalOut$Qlt$varNull[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlMedicalOut$Qlt$IccNull <- -->
-<!--   (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2]))) -->
-<!-- mdlMedicalOut$Qlt$IccPercNull <- -->
-<!--   ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100 -->
-<!-- ``` -->
-
 ```{r medicalOutModelInterceptQltCore, include=FALSE}
@@
 mdlMedicalOut$Qlt$lmerInterceptCoreCI <- 
-  confint(mdlMedicalOut$Qlt$lmerInterceptCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(qualityOverall ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptCore)
 
@@
 mdlMedicalOut$Qlt$lmerSlopesCoreCI <- 
-  confint(mdlMedicalOut$Qlt$lmerSlopesCore)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(mdlMedicalOut$Qlt$lmerSlopesCore,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesCore)
 
@@
 mdlMedicalOut$Att$lmerInterceptCoreQltCI <- 
-  confint(mdlMedicalOut$Att$lmerInterceptCoreQlt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCoreQlt)
 
@@
 mdlMedicalOut$Att$lmerSlopesCoreQltCI <- 
-  confint(mdlMedicalOut$Att$lmerSlopesCoreQlt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreQlt)
 
@@
 mdlMedicalOut$Att$lmerInterceptCoreAllportCI <- 
-  confint(mdlMedicalOut$Att$lmerInterceptCoreAllport)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCoreAllport)
 
@@
 mdlMedicalOut$Att$lmerSlopesCoreAllportCI <- 
-  confint(mdlMedicalOut$Att$lmerSlopesCoreAllport, method = "Wald")
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreAllport)
 
@@
 mdlMedical$lmerInterceptAttCoreIntCI <- 
-  confint(mdlMedical$lmerInterceptAttCoreInt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=dtMedical$full),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  confint(method = "Wald", mdlMedical$lmerInterceptAttCoreInt)
 
@@
 mdlMedical$lmerSlopesAttCoreIntCI <- 
-  confint(mdlMedical$lmerSlopesAttCoreInt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlMedical$lmerSlopesAttCoreInt)
 
@@
 
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
 # To be compared against a model with only the self determination theory needs
@@
 mdlMedicalOut$Att$lmerSlopesCoreSdtCI <- 
-  confint(mdlMedicalOut$Att$lmerSlopesCoreSdt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreSdt)
 

### 2021-11-08 Methods-and-Results.tex
AOT-M model comparison and robustness rendered

@@
 
+To compare the models using either Allport's conditions or the core need
+fulfillment to predict outgroup attitudes, we first assess relative
+model performance indices (i.e., Akaike information criterion, and
+Bayesian information criterion), and then consider the two predictors in
+a joint model to see whether the two approaches predict the same
+variance in outgroup attitudes. When comparing the model selection
+indices we find that the fulfillment of the situation core need, indeed
+performs slightly better than the model using Allport's conditions
+(\(AIC_{CoreNeed}\) 12632.0183 \textless{} 12651.5868 \(AIC_{Allport}\),
+and \(BIC_{CoreNeed}\) 12664.549 \textless{} 12684.1174
+\(BIC_{Allport}\)). Additionally, when considering the predictors
+jointly, we find that both significantly predict outgroup attitudes with
+similar sized regression parameters (random slopes model; Allport's
+Conditions: \textit{b} = 0.16, \textit{t}(1600) = 4.92, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.09, 0.24{]}, Core Need: \textit{b}
+= 0.14, \textit{t}(1600) = 3.85, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.08, 0.17{]}). This indicates that, although both
+Allport's conditions and the core need fulfillment seem to (in part)
+work through perceived interaction quality, they explain different
+aspects of the variance in outgroup attitudes and do not constitute one
+another.
+
 \subsubsection{Robustness}
+
+We again checked for alternative models to the core need fulfillment.
+First, when considering generalized situational core need fulfillment
+together with whether an intergroup contact took place, we find that
+there is no significant main effect of core need fulfillment (random
+slopes model; \textit{b} = 0.03, \textit{t}(3835) = 1.51, \textit{p} =
+0.131, \textit{95\%CI}{[}-0.01, 0.06{]}) but a stronger interaction
+effect of core need fulfillment and outgroup contact (\textit{b} = 0.17,
+\textit{t}(3835) = 7.32, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.21{]}). Together with a significant main
+effect of having an outgroup contact (\textit{b} = 5.41,
+\textit{t}(3835) = 6.36, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}3.73, 7.09{]}), this indicates that it is not key need
+fulfillment in general --- but key need fulfillment during an outgroup
+contact that predicts more positive outgroup attitudes. This finding is
+consistent with the results of the previous studies.
+
+In a final step we again checked whether during the interaction the core
+situational need remains a meaningful predictor even when taking other
+fundamental psychological needs into account. We find that the core need
+adds significantly above a model with only the self determination theory
+needs (random slopes models; \(\chi^2\)(6, \textit{N} = 70) = 100.20,
+\textit{p} \textless{} .001). We find that the core need explains the
+most variance in outgroup attitudes after an outgroup contact
+(\textit{b} = 0.15, \textit{t}(1598) = 3.88, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.07, 0.22{]}). When compared to the model with
+only the SDT needs, the core need fulfillment flexibly takes on some of
+the explained variance of all of the three fundamental needs. However,
+similar to the previous study, in this large sample relatedness
+(\textit{b} = 0.05, \textit{t}(1598) = 3.31, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.02, 0.09{]}), competence (\textit{b} = 0.06,
+\textit{t}(1598) = 2.73, \textit{p} = 0.006, \textit{95\%CI}{[}0.01,
+0.10{]}) and autonomy (\textit{b} = 0.04, \textit{t}(1598) = 2.12,
+\textit{p} = 0.034, \textit{95\%CI}{[}-0.01, 0.08{]}) each predicted
+positive outgroup attitudes independently. However, the regression
+coefficient is three times as large for the core need fulfillment (with
+all scaling being equal). For full results see Online Supplementary
+Information B.

### 2021-11-08 scripts/functions/MlCorMat.R

@@ -288,6 +288,31 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
   }
 }
 
+MlCoeffHtml <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
+  b <- coef(summary(lmeMdl))[varName,"Value"] %>% round(2) %>% format(nsmall=2)
+  df <- lmeMdl$fixDF$X[varName] %>% as.numeric
+  t <- coef(summary(lmeMdl))[varName,"t-value"] %>% round(2) %>% format(nsmall=2)
+  p <- ifelse(coef(summary(lmeMdl))[varName,"p-value"]<.001, "< .001", paste0("= ", coef(summary(lmeMdl))[varName,"p-value"] %>% round(3) %>% format(nsmall=3)))
+  
+  if (is.null(lmerCI)) {
+    paste0(
+      "<i>b</i> = ", b, 
+      ", <i>t</i>(", df, ") = ", t,
+      ", <i>p</i> ", p
+    )
+  } else {
+    CIlwr <- lmerCI[varName, "2.5 %"] %>% round(2) %>% format(nsmall=2)
+    CIupr <- lmerCI[varName, "97.5 %"] %>% round(2) %>% format(nsmall=2)
+    
+    paste0(
+      "<i>b</i> = ", b, 
+      ", <i>t</i>(", df, ") = ", t,
+      ", <i>p</i> ", p,
+      ", <i>95%CI</i>[", CIlwr, ", ", CIupr, "]"
+    )
+  }
+}
+
 linesep<-function(x,y=character()){
   if(!length(x))
     return(y)

### 2021-11-08 Supplemental-Material-B-Annotated-Analysis.Rmd
AOT-M code added

@@
 
+```{r medicalSampleInfo}
+# extract demographic information from eligibility questionnaire
+medicalDemographicSupp <- 
+  dtMedical$raw.eligibility %>%
+  filter(session %in% dtMedical$full$session) %>%
+  select(session, nationality, studentBachMa)
+# summarize participant characteristics
+
+medicalSampleInfo <-
+  merge(dtMedical$full, medicalDemographicSupp, by = "session") %>%
+  mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>%
+  group_by(PID) %>%
+  summarise(
+    dailiesN = n(), 
+    morningN = sum(periodMA=="morning"),
+    afternoonN = sum(periodMA=="afternoon"),
+    age = age,
+    gender = gender,
+    nationality = nationality
+  ) %>%
+  distinct
+
+# look at frequencies of characteristics 
+table(medicalSampleInfo$age)
+table(medicalSampleInfo$gender)
+table(as.character(medicalSampleInfo$nationality))
+```
+
+```{r medicalVarDescr}
+medicalMlCor <-
+  MlCorMat(
+    data = dtMedical$full,
+    id = "PID",
+    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
+  )
+
+medicalMlCor %>%
+  kable(
+    .,
+    caption = "Medical: Multilevel Core Variable Descriptives",
+    format = "html",
+    booktabs = TRUE,
+    linesep = linesep(c(ncol(.))),
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person coorelations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  )
+```
+
+```{r medicalOutVarDescr}
+medicalOutMlCor <-
+  MlCorMat(
+    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
+  )
+
+medicalOutMlCor %>%
+  kable(
+    .,
+    caption = "Medical: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
+    format = "html",
+    booktabs = TRUE,
+    linesep = linesep(c(ncol(.))),
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person coorelations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  )
+
+# misty::multilevel.descript(dtStudentsSupp$studentWithinBetween$keyMotiveFulfilled, cluster = dtStudentsSupp$studentWithinBetween$PID)
+```
+
+After receiving ethical approval from the University of Groningen, we recruited `r nrow(medicalSampleInfo)` international medical students using a contacts within the University Medical Department and specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
+Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
+With this design, we aimed at getting 50-60 measurements per participant (*M* = `r format(round(mean(medicalSampleInfo$dailiesN),2), nsmall=2)`, *SD* = `r format(round(sd(medicalSampleInfo$dailiesN),2), nsmall=2)`, *total N* = `r sum(medicalSampleInfo$dailiesN)`).
+As with the previous study this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
+Participants were compensated for their participation with partial course credits --- depending on their participation.
+The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(medicalSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(medicalSampleInfo$age),2), nsmall=2)`, `r nrow(medicalSampleInfo %>% filter(gender == "women"))` women).
+The sample fairly accurately describes the local population of international students.
+
+The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, daily diary-, and post-measurement.
+The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (*median duration* = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, *MAD duration* = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).
+General compliance was high (`r format(round(sum(medicalSampleInfo$dailiesN)/(nrow(medicalSampleInfo)*62)*100,2), nsmall=2)`% filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS).
+The response rates were approximately equal during mornings (*n* = `r sum(medicalSampleInfo$morningN)`) and afternoons (*n* = `r sum(medicalSampleInfo$afternoonN)`).
+All key variables in for this study were part of the short daily diary surveys.
+The measurement of intergroup contacts was identical to study two.
+The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
+(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`% of individual daily diary measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`% of all `r nrow(dtMedical$full)` daily diary responses).
+
+```{r medicalFreqAttCor}
+dtMedicalSupp$medicalContactFreq <-
+  dtMedicalSupp$medicalContactFreq %>%
+  mutate(
+    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
+    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
+    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
+    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
+  )
+
+# correlation panel
+pairs.panels.new(
+  dtMedicalSupp$medicalContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
+    "Sum:\nNumber of Outgroup Contacts (NL)",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+
+# correlation panel with interaction sums winsorized
+pairs.panels.new(
+  dtMedicalSupp$medicalContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
+    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+```
+
 ## Contact Hypothesis
 
+We tested the most general contact hypothesis in two steps.
+First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
+Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
+We find no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions (*r* = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (*r* = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+This is to say that within our data, participants with more outgroup interactions did not have significantly more positive or negative outgroup attitudes.
+This is again consistent with the results we found in the first study but inconsitent with the significant relationship we find in the second study.
+
+```{r medicalModelOlsAttFreqQual}
+# create list to store Worker models
+mdlMedical <- list()
+
+# regression
+mdlMedical$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)
+
+summ(
+  mdlMedical$lmAttFreqQualX,
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedical$lmAttFreqQualXEta <-
+  effectsize::eta_squared(mdlMedical$lmAttFreqQualX, partial = TRUE)
+
+interactions::interact_plot(
+  mdlMedical$lmAttFreqQualX,
+  pred = SumContactNL_c,
+  modx = AvQuality_c,
+  interval = TRUE,
+  partial.residuals = TRUE
+)
+
+interactions::johnson_neyman(mdlMedical$lmAttFreqQualX,
+                             pred = SumContactNL_c,
+                             modx = AvQuality_c,
+                             alpha = .05)
+```
+
+However, we do find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (*r* = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (*b* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, *t*(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, *p* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
+Given the missing aggregate relationship between number of interactions and outgroup attitudes, we find no significant effect of interactions themselves nor do we find a significant interaction effect.
+This result mirrors that of study one but is inconsistent with the second study.
+But again this inconsistency is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.
+
+```{r medicalModelMLAttNull}
+# Create and save Model
+mdlMedical$lmerAttNullType <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
+             data = dtMedical$full %>%
+               filter(complete.cases(
+                 OutgroupInteraction, NonOutgroupInteraction
+               ))) # use optim if it does not converge
+
+mdlMedical$lmeAttNullType <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = dtMedical$full %>%
+      filter(complete.cases(
+        OutgroupInteraction, NonOutgroupInteraction
+      )),
+    na.action = na.omit,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(mdlMedical$lmerAttNull) #or with the lme function
+summ(mdlMedical$lmerAttNullType, digits = 3)
+
+# Save variances
+mdlMedical$varAttNullType <- 
+  VarCorr(mdlMedical$lmeAttNullType) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlMedical$tauAttNullType <- 
+  as.numeric(mdlMedical$varAttNullType[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlMedical$sigmaAttNullType <- 
+  as.numeric(mdlMedical$varAttNullType[2])
+# The ICC estimate (between/between+within) is:
+mdlMedical$IccAttNullType <-
+  (as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))
+mdlMedical$IccPercAttNull <-
+  ((as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))) * 100
+```
+
+```{r medicalModelInterceptAttType, include = FALSE}
+# Create and save Model
+mdlMedical$lmeInterceptAttType <-
+  lme(
+    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
+    random =  ~ 1 | PID,
+    na.action=na.omit,
+    data = dtMedical$full
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedical$lmerInterceptAttType <- lmer(
+    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    data = dtMedical$full
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedical$lmerInterceptAttTypeCI <- 
+  confint(method = "Wald", mdlMedical$lmerInterceptAttType)
+
+# Compare new model to previous step
+anova(mdlMedical$lmeAttNullType, 
+      mdlMedical$lmeInterceptAttType) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedical$varInterceptAttType <- 
+  lme4::VarCorr(mdlMedical$lmeInterceptAttType)
+```
+
+```{r medicalModelSlopesInteractionType}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedical$lmeSlopesAttType <- lme(
+  AttitudesDutch ~
+    OutgroupInteraction + NonOutgroupInteraction,
+  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  na.action = na.omit,
+  data = dtMedical$full
+)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedical$lmerSlopesAttType <- lmer(
+    AttitudesDutch ~
+      OutgroupInteraction + NonOutgroupInteraction +
+      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+    data = dtMedical$full
+  ), 
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedical$lmerSlopesAttTypeCI <- 
+  confint(method = "Wald", mdlMedical$lmerSlopesAttType)
+
+# Compare new model to previous step
+anova(mdlMedical$lmeAttNullType,
+      mdlMedical$lmeInterceptAttType, 
+      mdlMedical$lmeSlopesAttType) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedical$varSlopesAttType <- 
+  lme4::VarCorr(mdlMedical$lmeSlopesAttType)
+
+# Assumption Checks:
+mdlMedical$diagSlopesAttType <-
+  sjPlot::plot_model(mdlMedical$lmerSlopesAttType, type = "diag")
+grid.arrange(
+  mdlMedical$diagSlopesAttType[[1]],
+  mdlMedical$diagSlopesAttType[[2]]$`PID`,
+  mdlMedical$diagSlopesAttType[[3]],
+  mdlMedical$diagSlopesAttType[[4]]
+)
+
+# Plot prediction model
+mdlMedical$predSlopesAttType <-
+  dtMedical$full %>%
+  filter(complete.cases(OutgroupInteraction, NonOutgroupInteraction)) %>%
+  select(AttitudesDutch, TIDnum, PID) %>%
+  mutate(measure = predict(
+    mdlMedical$lmeSlopesAttType,
+    dtMedical$full %>%
+      filter(complete.cases(
+        OutgroupInteraction, NonOutgroupInteraction
+      )),
+    re.form = NA
+  ))
+
+(
+  mdlMedical$predPltSlopesAttType <-
+    ggplot(data = mdlMedical$predSlopesAttType %>% filter(PID %in% dtMedicalSupp$medicalPltIDs), 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/Medical_PredictionPlot_SlopesAttType.png",
+  mdlMedical$predPltSlopesAttType,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
+Thus, in our third dataset we find some mixed results, outgroup contacts are not significantly related to outgroup attitudes on aggregate between participants and this effect is also not suppressed by a average interaction quality (i.e., no interaction effect).
+However, while the aggregate data is partly inconsistent with the first two studies, the within person contemoranous effect of intergroup contact is consistent across all three studies.
+
 ## Allport's Conditions
 
+```{r medicalOutModelMLAttNull}
+# create empty list to organize models
+mdlMedicalOut <- 
+  list(
+    Att = list(),
+    Qlt = list()
+  )
+
+# Create and save Model
+mdlMedicalOut$Att$lmerNull <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
+             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
+mdlMedicalOut$Att$lmeNull <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.omit,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.ML.r) #or with the lme function
+summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE)
+
+# Save variances
+mdlMedicalOut$Att$varNull <- 
+  VarCorr(mdlMedicalOut$Att$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlMedicalOut$Att$tauNull <- 
+  as.numeric(mdlMedicalOut$Att$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlMedicalOut$Att$sigmaNull <- 
+  as.numeric(mdlMedicalOut$Att$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlMedicalOut$Att$IccNull <-
+  (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))
+mdlMedicalOut$Att$IccPercNull <-
+  ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100
+```
+
+```{r medicalOutModelInterceptAttAllport}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptAllport <-
+  lme(
+    AttitudesDutch ~ AllportsCondition_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptAllport <-
+    lmer(
+      AttitudesDutch ~ AllportsCondition_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Att$lmerInterceptAllportCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllport)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull, 
+      mdlMedicalOut$Att$lmeInterceptAllport) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptAllport <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllport)
+```
+
+```{r medicalOutModelSlopesAttAllport}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesAllport <-
+  lme(
+    AttitudesDutch ~
+      AllportsCondition_cwc,
+    random = ~ 1 + AllportsCondition_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesAllport <- lmer(
+    AttitudesDutch ~
+      AllportsCondition_cwc +
+      (1 + AllportsCondition_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# all variables standardized within PPT
+summ(
+  mdlMedicalOut$Att$lmerSlopesAllportZ <- lmer(
+    AttitudesDutch_zwc ~
+      AllportsCondition_zwc +
+      (1 + AllportsCondition_zwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# standardized coefficients
+stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesAllport)
+
+# 95%CIs
+mdlMedicalOut$Att$lmerSlopesAllportCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllport)
+
+# Attempts at R^2
+#r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesAllport, bargraph = TRUE)
+mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesAllport)
+performance::r2(mdlMedicalOut$Att$lmerSlopesAllport)
+performance::model_performance(mdlMedicalOut$Att$lmerSlopesAllport)
+performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
+                                 mdlMedicalOut$Att$lmerInterceptAllport, 
+                                 mdlMedicalOut$Att$lmerSlopesAllport)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull, 
+      mdlMedicalOut$Att$lmeInterceptAllport, 
+      mdlMedicalOut$Att$lmeSlopesAllport) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesAllport <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesAllport)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesAllport <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesAllport, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesAllport[[1]],
+  mdlMedicalOut$Att$diagSlopesAllport[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesAllport[[3]],
+  mdlMedicalOut$Att$diagSlopesAllport[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesAllport <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllport,
+                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesAllport <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesAllport, 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllport.png",
+  mdlMedicalOut$Att$predPltSlopesAllport,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+```{r medicalOutModelMLQltNull}
+# Create and save Model
+mdlMedicalOut$Qlt$lmerNull <-
+  lme4::lmer(qualityOverall ~ 1 + (1 | PID), 
+             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
+mdlMedicalOut$Qlt$lmeNull <-
+  mdlMedicalOut$Qlt$lmeNull <-lme(
+    qualityOverall ~ 1,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(Null.Out.Qual.ML.r) #or with the lme function
+summ(mdlMedicalOut$Qlt$lmerNull, digits = 3)
+
+# Save variances
+mdlMedicalOut$Qlt$varNull <- 
+  VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances
+# The estimate of (between-group or Intercept variance, tau_{00}^2):
+mdlMedicalOut$Qlt$tauNull <- 
+  as.numeric(mdlMedicalOut$Qlt$varNull[1])
+# and the estimate of (within-group or residual variance, sigma^2) is:
+mdlMedicalOut$Qlt$sigmaNull <- 
+  as.numeric(mdlMedicalOut$Qlt$varNull[2])
+# The ICC estimate (between/between+within) is:
+mdlMedicalOut$Qlt$IccNull <-
+  (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))
+mdlMedicalOut$Qlt$IccPercNull <-
+  ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100
+```
+
+```{r medicalOutModelInterceptQltAllport}
+# Create and save Model
+mdlMedicalOut$Qlt$lmeInterceptAllport <-
+  lme(
+    qualityOverall ~ AllportsCondition_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Qlt$lmerInterceptAllport <-
+    lmer(
+      qualityOverall ~ AllportsCondition_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Qlt$lmerInterceptAllportCI <- 
+  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptAllport)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Qlt$lmeNull, 
+      mdlMedicalOut$Qlt$lmeInterceptAllport) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Qlt$varInterceptAllport <-
+  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptAllport)
+```
+
+```{r medicalOutModelSlopesQltAllport}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Qlt$lmeSlopesAllport <-
+  lme(
+    qualityOverall ~
+      AllportsCondition_cwc,
+    random = ~ 1 + AllportsCondition_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Qlt$lmerSlopesAllport <-
+    lmer(
+      qualityOverall ~
+        AllportsCondition_cwc +
+        (1 + AllportsCondition_cwc | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Qlt$lmerSlopesAllportCI <- 
+  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesAllport)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Qlt$lmeNull, 
+      mdlMedicalOut$Qlt$lmeInterceptAllport, 
+      mdlMedicalOut$Qlt$lmeSlopesAllport) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Qlt$varSlopesAllport <- 
+  lme4::VarCorr(mdlMedicalOut$Qlt$lmeSlopesAllport)
+
+# Assumption Checks:
+mdlMedicalOut$Qlt$diagSlopesAllport <-
+  sjPlot::plot_model(mdlMedicalOut$Qlt$lmerSlopesAllport, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Qlt$diagSlopesAllport[[1]],
+  mdlMedicalOut$Qlt$diagSlopesAllport[[2]]$`PID`,
+  mdlMedicalOut$Qlt$diagSlopesAllport[[3]],
+  mdlMedicalOut$Qlt$diagSlopesAllport[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Qlt$predSlopesAllport <- 
+  dtMedicalSupp$medicalOutWithinBetween %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesAllport,
+                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Qlt$predPltSlopesAllport <-
+    ggplot(data = mdlMedicalOut$Qlt$predSlopesAllport %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAllport.png",
+  mdlMedicalOut$Qlt$predPltSlopesAllport,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+
+```
+
+```{r medicalOutModelInterceptAttAllportQlt}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptAllportQlt <-
+  lme(
+    AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptAllportQlt <-
+    lmer(
+      AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerInterceptAllportQltCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllportQlt)
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull, 
+  mdlMedicalOut$Att$lmeInterceptAllportQlt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptAllportQlt <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllportQlt)
+```
+
+```{r medicalOutModelSlopesAttAllportQlt}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesAllportQlt <-
+  lme(
+    AttitudesDutch ~
+      AllportsCondition_cwc + qualityOverall_cwc,
+    random = ~ 1 + AllportsCondition_cwc + qualityOverall_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesAllportQlt <- lmer(
+    AttitudesDutch ~
+      AllportsCondition_cwc + qualityOverall_cwc +
+      (1 + AllportsCondition_cwc + qualityOverall_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerSlopesAllportQltCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllportQlt)
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull,
+  mdlMedicalOut$Att$lmeInterceptAllportQlt,
+  mdlMedicalOut$Att$lmeSlopesAllportQlt
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesAllportQlt <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesAllportQlt)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesAllportQlt <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesAllportQlt, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesAllportQlt[[1]],
+  mdlMedicalOut$Att$diagSlopesAllportQlt[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesAllportQlt[[3]],
+  mdlMedicalOut$Att$diagSlopesAllportQlt[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesAllportQlt <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(complete.cases(AllportsCondition, qualityOverall)) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllportQlt,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(AllportsCondition, qualityOverall)) %>%
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesAllportQlt <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesAllportQlt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllportQlt.png",
+  mdlMedicalOut$Att$predPltSlopesAllportQlt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We sequentially tested whether the fulfillment of Allport's Contact Conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly.
+We find that in the multilevel models, the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
+However, if we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`).
+These results indicate that in this dataset the the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
+
 ## Need Fulfillment
+
+```{r medicalOutModelInterceptAttCore}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptCore <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptCore <-
+    lmer(
+      AttitudesDutch ~ KeyNeedFulfillment_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Att$lmerInterceptCoreCI <-
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCore)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull,
+      mdlMedicalOut$Att$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptCore <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCore)
+```
+
+```{r medicalOutModelSlopesAttCore}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesCore <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesCore <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc +
+      (1 + KeyNeedFulfillment_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# all variables standardized within PPT
+summ(
+  mdlMedicalOut$Att$lmerSlopesCoreZ <- lmer(
+    AttitudesDutch_zwc ~
+      KeyNeedFulfillment_zwc +
+      (1 + KeyNeedFulfillment_zwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# standardized coefficients
+stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesCore)
+
+# 95%CIs
+mdlMedicalOut$Att$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCore)
+
+# Attempts at R^2
+r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesCore, bargraph = TRUE)
+mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesCore)
+performance::r2(mdlMedicalOut$Att$lmerSlopesCore)
+performance::model_performance(mdlMedicalOut$Att$lmerSlopesCore)
+performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
+                                 mdlMedicalOut$Att$lmerInterceptCore, 
+                                 mdlMedicalOut$Att$lmerSlopesCore)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull, 
+      mdlMedicalOut$Att$lmeInterceptCore, 
+      mdlMedicalOut$Att$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesCore <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCore)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesCore <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesCore[[1]],
+  mdlMedicalOut$Att$diagSlopesCore[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesCore[[3]],
+  mdlMedicalOut$Att$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesCore <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(complete.cases(KeyNeedFulfillment)) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCore,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment)) %>% 
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesCore <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesCore, 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCore.png",
+  mdlMedicalOut$Att$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+```{r medicalOutModelInterceptQltCore}
+# Create and save Model
+mdlMedicalOut$Qlt$lmeInterceptCore <-
+  lme(
+    qualityOverall ~ KeyNeedFulfillment_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Qlt$lmerInterceptCore <-
+    lmer(
+      qualityOverall ~ KeyNeedFulfillment_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Qlt$lmerInterceptCoreCI <- 
+  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptCore)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Qlt$lmeNull, 
+      mdlMedicalOut$Qlt$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Qlt$varInterceptCore <-
+  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptCore)
+```
+
+```{r medicalOutModelSlopesQltCore}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Qlt$lmeSlopesCore <-
+  lme(
+    qualityOverall ~
+      KeyNeedFulfillment_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Qlt$lmerSlopesCore <-
+    lmer(
+      qualityOverall ~
+        KeyNeedFulfillment_cwc +
+        (1 + KeyNeedFulfillment_cwc | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Qlt$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesCore)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Qlt$lmeNull, 
+      mdlMedicalOut$Qlt$lmeInterceptCore, 
+      mdlMedicalOut$Qlt$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Qlt$varSlopesCore <- 
+  lme4::VarCorr(mdlMedicalOut$Qlt$lmeSlopesCore)
+
+# Assumption Checks:
+mdlMedicalOut$Qlt$diagSlopesCore <-
+  sjPlot::plot_model(mdlMedicalOut$Qlt$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Qlt$diagSlopesCore[[1]],
+  mdlMedicalOut$Qlt$diagSlopesCore[[2]]$`PID`,
+  mdlMedicalOut$Qlt$diagSlopesCore[[3]],
+  mdlMedicalOut$Qlt$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Qlt$predSlopesCore <- 
+  dtMedicalSupp$medicalOutWithinBetween %>%
+  filter(complete.cases(KeyNeedFulfillment)) %>% 
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesCore,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment)) %>% 
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Qlt$predPltSlopesCore <-
+    ggplot(data = mdlMedicalOut$Qlt$predSlopesCore %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesCore.png",
+  mdlMedicalOut$Qlt$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+```{r medicalOutModelInterceptAttCoreQlt}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptCoreQlt <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptCoreQlt <-
+    lmer(
+      AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerInterceptCoreQltCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCoreQlt)
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull, 
+  mdlMedicalOut$Att$lmeInterceptCoreQlt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptCoreQlt <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreQlt)
+```
+
+```{r medicalOutModelSlopesAttCoreQlt}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesCoreQlt <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + qualityOverall_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesCoreQlt <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + qualityOverall_cwc +
+      (1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerSlopesCoreQltCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreQlt)
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull,
+  mdlMedicalOut$Att$lmeInterceptCoreQlt,
+  mdlMedicalOut$Att$lmeSlopesCoreQlt
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesCoreQlt <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreQlt)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesCoreQlt <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreQlt, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[1]],
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[3]],
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesCoreQlt <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreQlt,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesCoreQlt <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreQlt.png",
+  mdlMedicalOut$Att$predPltSlopesCoreQlt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+We find that in the multilevel models, the fulfillment of core need fulfillment during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
+However, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`).
+These results indicate that in this dataset the the fulfillment of core situational needs had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
+
+## Compare Fulfillment of Core Need and Allport's Conditions
+
+```{r AllportVsCore}
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeSlopesAllport, 
+      mdlMedicalOut$Att$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  kbl(
+    .,
+    caption = "Medical: Comparison of Allport's Conditions to Core Situational Need",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+AIC(
+  mdlMedicalOut$Att$lmerSlopesAllport,
+  mdlMedicalOut$Att$lmerSlopesCore
+)
+
+BIC(
+  mdlMedicalOut$Att$lmerSlopesAllport,
+  mdlMedicalOut$Att$lmerSlopesCore
+)
+
+performance::compare_performance(
+  mdlMedicalOut$Att$lmerSlopesAllport,
+  mdlMedicalOut$Att$lmerSlopesCore
+)
+```
+
+```{r medicalOutModelInterceptAttCoreAllport}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptCoreAllport <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptCoreAllport <-
+    lmer(
+      AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerInterceptCoreAllportCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCoreAllport)
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull, 
+  mdlMedicalOut$Att$lmeInterceptAllport,
+  mdlMedicalOut$Att$lmeInterceptCoreAllport
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptCoreAllport <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreAllport)
+```
+
+```{r medicalOutModelSlopesAttCoreAllport}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesCoreAllport <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + AllportsCondition_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesCoreAllport <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + AllportsCondition_cwc +
+      (1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerSlopesCoreAllportCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreAllport)
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull,
+  mdlMedicalOut$Att$lmeInterceptCoreAllport,
+  mdlMedicalOut$Att$lmeSlopesCoreAllport
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesCoreAllport <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreAllport)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesCoreAllport <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreAllport, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[1]],
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[3]],
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesCoreAllport <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreAllport,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesCoreAllport <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreAllport.png",
+  mdlMedicalOut$Att$predPltSlopesCoreAllport,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+To compare the models using either Allport's conditions or the core need fulfillment to predict outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
+When comparing the model selection indices we find that the fulfillment of the situation core need, indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r AIC(mdlMedicalOut$Att$lmerSlopesCore)` < `r AIC(mdlMedicalOut$Att$lmerSlopesAllport)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r BIC(mdlMedicalOut$Att$lmerSlopesCore)` < `r BIC(mdlMedicalOut$Att$lmerSlopesAllport)` $BIC_{Allport}$).
+Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`).
+This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
+
+## Robustness
+
+```{r medicalModelAttNullInt}
+# Create and save Model
+mdlMedical$lmerAttNullInt <-
+  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
+             data = dtMedical$full %>%
+               filter(complete.cases(
+                 OutgroupInteraction
+               ))) # use optim if it does not converge
+
+mdlMedical$lmeAttNullInt <-
+  lme(
+    AttitudesDutch ~ 1,
+    random = ~ 1 | PID,
+    data = dtMedical$full %>%
+      filter(complete.cases(
+        OutgroupInteraction
+      )),
+    na.action = na.omit,
+    control = list(opt = "nlmimb")
+  ) # use optim if it does not converge
+
+# Get summary with p-values (Satterthwaite's method)
+# summary(mdlMedical$lmerAttNull) #or with the lme function
+summ(mdlMedical$lmerAttNullInt, digits = 3)
+```
+
+```{r medicalModelInterceptAttCoreInt}
+# Create and save Model
+mdlMedical$lmeInterceptAttCoreInt <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction,
+    random =  ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedical$full
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedical$lmerInterceptAttCoreInt <- lmer(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction + (1 | PID),
+    data = dtMedical$full
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedical$lmerInterceptAttCoreIntCI <- 
+  confint(method = "Wald", mdlMedical$lmerInterceptAttCoreInt)
+
+# Compare new model to previous step
+anova(mdlMedical$lmeAttNullInt, 
+      mdlMedical$lmeInterceptAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = c("l", rep("c", ncol(.)-1)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedical$varInterceptAttCoreInt <- 
+  lme4::VarCorr(mdlMedical$lmeInterceptAttCoreInt)
+```
+
+```{r medicalModelSlopesAttCoreIntX}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedical$lmeSlopesAttCoreInt <- lme(
+  AttitudesDutch ~
+    KeyNeedFulfillment_cwc * OutgroupInteraction,
+  random = ~ 1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID,
+  control = lmeControl(opt = "optim"),
+  na.action = na.omit,
+  data = dtMedical$full
+)
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedical$lmerSlopesAttCoreInt <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc * OutgroupInteraction +
+      (1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID),
+    data = dtMedical$full
+  ), 
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedical$lmerSlopesAttCoreIntCI <- 
+  confint(method = "Wald", mdlMedical$lmerSlopesAttCoreInt)
+
+# Compare new model to previous step
+anova(mdlMedical$lmeAttNullInt, 
+      mdlMedical$lmeInterceptAttCoreInt,
+      mdlMedical$lmeSlopesAttCoreInt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  add_rownames(., var = "Description") %>%
+  mutate(Description = gsub(".*\\$", "", Description)) %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedical$varSlopesAttCoreInt <- 
+  lme4::VarCorr(mdlMedical$lmeSlopesAttCoreInt)
+
+# Assumption Checks:
+mdlMedical$diagSlopesAttCoreInt <-
+  sjPlot::plot_model(mdlMedical$lmerSlopesAttCoreInt, type = "diag")
+grid.arrange(
+  mdlMedical$diagSlopesAttCoreInt[[1]],
+  mdlMedical$diagSlopesAttCoreInt[[2]]$`PID`,
+  mdlMedical$diagSlopesAttCoreInt[[3]],
+  mdlMedical$diagSlopesAttCoreInt[[4]]
+)
+
+# Plot prediction model
+mdlMedical$predSlopesAttCoreInt <- 
+  dtMedical$full %>%
+  filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
+  filter(PID %in% dtMedicalSupp$medicalPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedical$lmeSlopesAttCoreInt,
+                           dtMedical$full %>% 
+                             filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
+                             filter(PID %in% dtMedicalSupp$medicalPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedical$predPltSlopesAttCoreInt <-
+    ggplot(data = mdlMedical$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/Medical_PredictionPlot_SlopesAttCoreInt.png",
+  mdlMedical$predPltSlopesAttCoreInt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+We again checked for alternative models to the core need fulfillment.
+First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffHtml(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
+Together with a significant main effect of having an outgroup contact (`r MlCoeffHtml(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "OutgroupInteractionYes")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+This finding is consistent with the results of the previous studies.
+
+```{r medicalOutModelInterceptAttCoreSdt}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptCoreSdt <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 | PID,
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptCoreSdt <- lmer(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# To be compared against a model with only the self determination theory needs
+mdlMedicalOut$Att$lmeInterceptSdt <-
+  lme(
+    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 | PID,
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.exclude
+  )
+
+summ(
+  mdlMedicalOut$Att$lmerInterceptSdt <- lmer(
+    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Compare new model to previous steps
+anova(
+  mdlMedicalOut$Att$lmeInterceptSdt,
+  mdlMedicalOut$Att$lmeInterceptCoreSdt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptCoreSdt <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreSdt)
+```
+
+```{r medicalOutModelSlopesAttCoreSdt}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesCoreSdt <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc + Competence_cwc + Relatedness_cwc | PID,
+    control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesCoreSdt <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerSlopesCoreSdtCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreSdt)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeInterceptSdt,
+      mdlMedicalOut$Att$lmeInterceptCoreSdt, 
+      mdlMedicalOut$Att$lmeSlopesCoreSdt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# model with SDT only
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesSdt <-
+  lme(
+    AttitudesDutch ~
+      Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    na.action = na.exclude
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesSdt <- lmer(
+    AttitudesDutch ~
+      Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeInterceptSdt,
+      mdlMedicalOut$Att$lmeSlopesSdt, 
+      mdlMedicalOut$Att$lmeSlopesCoreSdt) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "html",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesCoreSdt <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreSdt)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesCoreSdt <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreSdt, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesCoreSdt[[1]],
+  mdlMedicalOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesCoreSdt[[3]],
+  mdlMedicalOut$Att$diagSlopesCoreSdt[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesCoreSdt <- 
+  dtMedicalSupp$medicalOutWithinBetween %>%
+  filter(complete.cases(
+    KeyNeedFulfillment,
+    Autonomy, Competence, Relatedness
+    )) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID, Autonomy, Competence, Relatedness) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreSdt,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(
+                               KeyNeedFulfillment,
+                               Autonomy, Competence, Relatedness
+                             )) %>%
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesCoreSdt <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreStd.png",
+  mdlMedicalOut$Att$predPltSlopesCoreSdt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+
+# Model comparison
+medicalSdtComp <-
+  anova(
+    mdlMedicalOut$Att$lmerSlopesSdt, 
+    mdlMedicalOut$Att$lmerSlopesCoreSdt
+  ) %>%
+  as.data.frame()
+medicalSdtCompDf <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Df"]
+medicalSdtCompN <- sapply(ranef(mdlMedicalOut$Att$lmerSlopesCoreSdt), nrow)
+medicalSdtCompChi <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
+medicalSdtCompP <-
+  ifelse(medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
+         "< .001",
+         paste0("= ", medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
+
+medicalSdtCompChiSq <- paste0("$chi^2$(", medicalSdtCompDf, ", <i>N</i> = ", medicalSdtCompN, ") = ", medicalSdtCompChi, ", <i>p</i> ", medicalSdtCompP)
+```
+
+In a final step we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
+We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r medicalSdtCompChiSq`).
+We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFulfillment_cwc")`).
+When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
+However, similar to the previous study, in this large sample relatedness (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each predicted positive outgroup attitudes independently.
+However, the regression coefficient is three times as large for the core need fulfillment (with all scaling being equal).
 

### 2021-11-08 Supplemental-Material-B-Annotated-Analysis.Rmd
SI-B re-rendered

@@
 The measurement of intergroup contacts was identical to study two.
-The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
-(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`% of individual daily diary measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`% of all `r nrow(dtMedical$full)` daily diary responses).
+The participants recorded between `r medicalContactFreq$SumContactNL[medicalContactFreq$SumContactNL > 0] %>% min`--`r medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
+(`r medicalContactFreq$PercContactNL[medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`% of individual daily diary measurements; `r (sum(medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`% of all `r nrow(dtMedical$full)` daily diary responses).
 
 ```{r medicalFreqAttCor}
-dtMedicalSupp$medicalContactFreq <-
-  dtMedicalSupp$medicalContactFreq %>%
+medicalContactFreq <-
+  medicalContactFreq %>%
   mutate(
@@
 pairs.panels.new(
-  dtMedicalSupp$medicalContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  medicalContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
   labels = c(
@@
 pairs.panels.new(
-  dtMedicalSupp$medicalContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  medicalContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
   labels = c(
@@
 Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
-We find no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions (*r* = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (*r* = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+We find no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions (*r* = `r cor(medicalContactFreq$SumContactNLAll, medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(medicalContactFreq$SumContactNLAll, medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (*r* = `r cor(medicalContactFreq$SumContactNL, medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(medicalContactFreq$SumContactNL, medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
 This is to say that within our data, participants with more outgroup interactions did not have significantly more positive or negative outgroup attitudes.
@@
 mdlMedical$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)
+  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = medicalContactFreq)
 
@@
 
-However, we do find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (*r* = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+However, we do find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (*r* = `r cor(medicalContactFreq$AvQuality, medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(medicalContactFreq$AvQuality, medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
 Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (*b* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, *t*(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, *p* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
@@
   mdlMedical$predPltSlopesAttType <-
-    ggplot(data = mdlMedical$predSlopesAttType %>% filter(PID %in% dtMedicalSupp$medicalPltIDs), 
+    ggplot(data = mdlMedical$predSlopesAttType %>% filter(PID %in% medicalPltIDs), 
            aes(x = TIDnum, y = measure)) +
@@
   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
-             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
+             data = medicalOutWithinBetween) # use optim if it does not converge
 mdlMedicalOut$Att$lmeNull <-
@@
     random = ~ 1 | PID,
-    data = dtMedicalSupp$medicalOutWithinBetween,
+    data = medicalOutWithinBetween,
     na.action = na.omit,
@@
     na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   )
@@
       AttitudesDutch ~ AllportsCondition_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
+      data = medicalOutWithinBetween
     ),
@@
     control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   )
@@
       (1 + AllportsCondition_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   ),
@@
       (1 + AllportsCondition_zwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   ),
@@
 mdlMedicalOut$Att$predSlopesAllport <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  medicalOutWithinBetween %>% 
+  filter(PID %in% medicalOutPltIDs) %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllport,
-                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           medicalOutWithinBetween %>% filter(PID %in% medicalOutPltIDs),
                            re.form = NA
@@
   lme4::lmer(qualityOverall ~ 1 + (1 | PID), 
-             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
+             data = medicalOutWithinBetween) # use optim if it does not converge
 mdlMedicalOut$Qlt$lmeNull <-
@@
     na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween,
+    data = medicalOutWithinBetween,
     control = list(opt = "nlmimb")
@@
       qualityOverall ~ AllportsCondition_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
+      data = medicalOutWithinBetween
     ),
@@
         (1 + AllportsCondition_cwc | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
+      data = medicalOutWithinBetween
     ),
@@
 mdlMedicalOut$Qlt$predSlopesAllport <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  medicalOutWithinBetween %>%
+  filter(PID %in% medicalOutPltIDs) %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesAllport,
-                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           medicalOutWithinBetween %>% filter(PID %in% medicalOutPltIDs),
                            re.form = NA
@@
   mdlMedicalOut$Qlt$predPltSlopesAllport <-
-    ggplot(data = mdlMedicalOut$Qlt$predSlopesAllport %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
+    ggplot(data = mdlMedicalOut$Qlt$predSlopesAllport %>% filter(PID %in% medicalOutPltIDs), 
            aes(x = TIDnum, y = measure)) +
@@
       AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
+      data = medicalOutWithinBetween
     ),
@@
       (1 + AllportsCondition_cwc + qualityOverall_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween,
+    data = medicalOutWithinBetween,
     control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
@@
 mdlMedicalOut$Att$predSlopesAllportQlt <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
+  medicalOutWithinBetween %>% 
   filter(complete.cases(AllportsCondition, qualityOverall)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  filter(PID %in% medicalOutPltIDs) %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllportQlt,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                           medicalOutWithinBetween %>% 
                              filter(complete.cases(AllportsCondition, qualityOverall)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                             filter(PID %in% medicalOutPltIDs),
                            re.form = NA
@@
       AttitudesDutch ~ KeyNeedFulfillment_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
+      data = medicalOutWithinBetween
     ),
@@
       (1 + KeyNeedFulfillment_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   ),
@@
       (1 + KeyNeedFulfillment_zwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   ),
@@
 mdlMedicalOut$Att$predSlopesCore <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
+  medicalOutWithinBetween %>% 
   filter(complete.cases(KeyNeedFulfillment)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  filter(PID %in% medicalOutPltIDs) %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCore,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                           medicalOutWithinBetween %>% 
                              filter(complete.cases(KeyNeedFulfillment)) %>% 
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                             filter(PID %in% medicalOutPltIDs),
                            re.form = NA
@@
       qualityOverall ~ KeyNeedFulfillment_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
+      data = medicalOutWithinBetween
     ),
@@
         (1 + KeyNeedFulfillment_cwc | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
+      data = medicalOutWithinBetween
     ),
@@
 mdlMedicalOut$Qlt$predSlopesCore <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
+  medicalOutWithinBetween %>%
   filter(complete.cases(KeyNeedFulfillment)) %>% 
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  filter(PID %in% medicalOutPltIDs) %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesCore,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                           medicalOutWithinBetween %>% 
                              filter(complete.cases(KeyNeedFulfillment)) %>% 
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                             filter(PID %in% medicalOutPltIDs),
                            re.form = NA
@@
   mdlMedicalOut$Qlt$predPltSlopesCore <-
-    ggplot(data = mdlMedicalOut$Qlt$predSlopesCore %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
+    ggplot(data = mdlMedicalOut$Qlt$predSlopesCore %>% filter(PID %in% medicalOutPltIDs), 
            aes(x = TIDnum, y = measure)) +
@@
       AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
+      data = medicalOutWithinBetween
     ),
@@
       (1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween,
+    data = medicalOutWithinBetween,
     control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
@@
 mdlMedicalOut$Att$predSlopesCoreQlt <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
+  medicalOutWithinBetween %>% 
   filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  filter(PID %in% medicalOutPltIDs) %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreQlt,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                           medicalOutWithinBetween %>% 
                              filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                             filter(PID %in% medicalOutPltIDs),
                            re.form = NA
@@
       AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
+      data = medicalOutWithinBetween
     ),
@@
       (1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   ),
@@
 mdlMedicalOut$Att$predSlopesCoreAllport <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
+  medicalOutWithinBetween %>% 
   filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  filter(PID %in% medicalOutPltIDs) %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreAllport,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                           medicalOutWithinBetween %>% 
                              filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                             filter(PID %in% medicalOutPltIDs),
                            re.form = NA
@@
   filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
-  filter(PID %in% dtMedicalSupp$medicalPltIDs) %>%
+  filter(PID %in% medicalPltIDs) %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
@@
                              filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalPltIDs),
+                             filter(PID %in% medicalPltIDs),
                            re.form = NA
@@
     random = ~ 1 | PID,
-    data = dtMedicalSupp$medicalOutWithinBetween,
+    data = medicalOutWithinBetween,
     na.action = na.exclude
@@
     AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   ),
@@
     AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   ),
@@
     control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
-    data = dtMedicalSupp$medicalOutWithinBetween,
+    data = medicalOutWithinBetween,
     na.action = na.exclude
@@
       (1 + KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   ),
@@
     control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween,
+    data = medicalOutWithinBetween,
     na.action = na.exclude
@@
       (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
+    data = medicalOutWithinBetween
   ),
@@
 mdlMedicalOut$Att$predSlopesCoreSdt <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
+  medicalOutWithinBetween %>%
   filter(complete.cases(
@@
     )) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  filter(PID %in% medicalOutPltIDs) %>%
   select(AttitudesDutch, TIDnum, PID, Autonomy, Competence, Relatedness) %>% 
   mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreSdt,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                           medicalOutWithinBetween %>% 
                              filter(complete.cases(
@@
                              )) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                             filter(PID %in% medicalOutPltIDs),
                            re.form = NA

### 2021-11-08 Methods-and-Results.tex
Methods and Results re-render with Wald CIs

@@
 \textit{t}(365) = 2.93, \textit{p} = 0.004, \textit{95\%CI}{[}0.06,
-0.30{]}) and also predicted higher perceived interaction quality (random
+0.29{]}) and also predicted higher perceived interaction quality (random
 intercept model; \textit{b} = 0.42, \textit{t}(365) = 8.07, \textit{p}
@@
 and outgroup contact (\textit{b} = 0.13, \textit{t}(1199) = 4.31,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.19{]}). Together
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.18{]}). Together
 with a significant main effect of having an outgroup contact, this
@@
 contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p} = 0.026,
-\textit{95\%CI}{[}0.02, 0.17{]}). When compared to the model with only
+\textit{95\%CI}{[}0.01, 0.18{]}). When compared to the model with only
 the SDT needs, the core need fulfillment flexibly takes on some of the
@@
 model; \textit{b} = 2.99, \textit{t}(4850) = 3.80, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}1.44, 4.56{]}), even after
+\textless{} .001, \textit{95\%CI}{[}1.45, 4.54{]}), even after
 controlling for having an interaction with a non-Dutch (which did not
@@
 \textit{b} = 0.40, \textit{t}(826) = 6.46, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.28, 0.53{]}). However, if we consider the influences
+\textit{95\%CI}{[}0.28, 0.52{]}). However, if we consider the influences
 of core need fulfillment and interaction quality on outgroup attitudes
@@
 \textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
-0.08{]}). These results are consistent with the results in study one and
+0.07{]}). These results are consistent with the results in study one and
 we thus find support for our hypotheses and can conclude that in this
@@
 contact (\textit{b} = 2.88, \textit{t}(4849) = 3.71, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}1.35, 4.42{]}), this indicates that
+\textless{} .001, \textit{95\%CI}{[}1.36, 4.38{]}), this indicates that
 it is not key need fulfillment in general --- but key need fulfillment
@@
 (\textit{b} = 0.08, \textit{t}(823) = 2.95, \textit{p} = 0.003,
-\textit{95\%CI}{[}0.02, 0.14{]}). When compared to the model with only
+\textit{95\%CI}{[}0.03, 0.13{]}). When compared to the model with only
 the SDT needs, the core need fulfillment flexibly takes on some of the
@@
 \textit{95\%CI}{[}0.04, 0.10{]}) and autonomy (\textit{b} = 0.02,
-\textit{t}(823) = 0.93, \textit{p} = 0.353, \textit{95\%CI}{[}-0.03,
+\textit{t}(823) = 0.93, \textit{p} = 0.353, \textit{95\%CI}{[}-0.02,
 0.08{]}) predicted positive outgroup attitudes. For full results see
@@
 model; \textit{b} = 5.63, \textit{t}(3834) = 6.61, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}3.96, 7.31{]}), even after
+\textless{} .001, \textit{95\%CI}{[}3.97, 7.29{]}), even after
 controlling for having an interaction with a non-Dutch (which did not
@@
 (random slopes model; \textit{b} = 0.22, \textit{t}(1601) = 5.86,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.15, 0.30{]}) and also
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.15, 0.29{]}) and also
 predicted higher perceived interaction quality (random slopes model;
@@
 \textit{t}(3835) = 6.36, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}3.73, 7.09{]}), this indicates that it is not key need
+\textit{95\%CI}{[}3.74, 7.08{]}), this indicates that it is not key need
 fulfillment in general --- but key need fulfillment during an outgroup
@@
 .001, \textit{95\%CI}{[}0.02, 0.09{]}), competence (\textit{b} = 0.06,
-\textit{t}(1598) = 2.73, \textit{p} = 0.006, \textit{95\%CI}{[}0.01,
+\textit{t}(1598) = 2.73, \textit{p} = 0.006, \textit{95\%CI}{[}0.02,
 0.10{]}) and autonomy (\textit{b} = 0.04, \textit{t}(1598) = 2.12,

### 2021-11-08 scripts/functions/MlCorMat.R
Update MlCorMat.R

@@ -243,15 +243,15 @@ MlTraitState <-
   }
 
 
-var_reduction = function(m0, m1){
+var_reduction = function(m0, m1) {
   library(tidyverse)
-  lme4::VarCorr(m0) %>% 
-    as.data.frame %>% 
-    select(grp, var_m0 = vcov) %>% 
-    left_join(lme4::VarCorr(m1) %>% 
-                as.data.frame %>% 
-                select(grp, var_m1 = vcov)) %>% 
-    mutate(var_red = 1 - var_m1 / var_m0) 
+  lme4::VarCorr(m0) %>%
+    as.data.frame %>%
+    select(grp, var_m0 = vcov) %>%
+    left_join(lme4::VarCorr(m1) %>%
+                as.data.frame %>%
+                select(grp, var_m1 = vcov)) %>%
+    mutate(var_red = 1 - var_m1 / var_m0)
 }
 
 stdCoef.merMod <- function(object) {

### 2021-11-08 Methods-and-Results.Rmd
Updates from Overleaf

--- 2021-11-08 Methods-and-Results.Rmd
@@
 ```
-
 ```{r medicalModelInterceptAttType, include = FALSE}
@@
 ```
-
 ```{r medicalModelSlopesInteractionType, include=FALSE}
@@
 ```
-
 ```{r medicalOutModelInterceptAttAllport, include=FALSE}
@@
 ```
-
 ```{r medicalOutModelSlopesAttAllport, include=FALSE}
@@
 ```
-
 ```{r medicalOutModelInterceptQltAllport, include=FALSE}
@@
 ```
-
 ```{r medicalOutModelSlopesQltAllport, include=FALSE}
@@
 ```
-
 ```{r medicalOutModelInterceptAttAllportQlt, include=FALSE}
@@
 ```
-
 ```{r medicalOutModelSlopesAttAllportQlt, include=FALSE}
@@
 ```
-
 ```{r medicalOutModelSlopesAttCore, include=FALSE}
@@
 ```
-
 ```{r medicalOutModelSlopesQltCore, include=FALSE}
@@
 ```
-
 ```{r medicalOutModelInterceptAttCoreQlt, include=FALSE}
@@
 ```
-
 ```{r medicalOutModelSlopesAttCoreQlt, include=FALSE}
@@
 
-```{r AllportVsCore, include=FALSE}
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeSlopesAllport, 
-      mdlMedicalOut$Att$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Medical: Comparison of Allport's Conditions to Core Situational Need",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-AIC(
-
-)
-
-performance::compare_performance(
-  mdlMedicalOut$Att$lmerSlopesAllport,
-  mdlMedicalOut$Att$lmerSlopesCore
-)
-```
-
-```{r medicalOutModelInterceptAttCoreAllport, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptCoreAllport <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptCoreAllport <-
-    lmer(
-      AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerInterceptCoreAllportCI <- 
-  confint(mdlMedicalOut$Att$lmerInterceptCoreAllport)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(
-  mdlMedicalOut$Att$lmeNull, 
-  mdlMedicalOut$Att$lmeInterceptAllport,
-  mdlMedicalOut$Att$lmeInterceptCoreAllport
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptCoreAllport <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreAllport)
-```
-
-```{r medicalOutModelSlopesAttCoreAllport, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesCoreAllport <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + AllportsCondition_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesCoreAllport <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + AllportsCondition_cwc +
-      (1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerSlopesCoreAllportCI <- 
-  confint(mdlMedicalOut$Att$lmerSlopesCoreAllport, method = "Wald")
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(
-  mdlMedicalOut$Att$lmeNull,
-  mdlMedicalOut$Att$lmeInterceptCoreAllport,
-  mdlMedicalOut$Att$lmeSlopesCoreAllport
-) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesCoreAllport <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreAllport)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesCoreAllport <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreAllport, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[1]],
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[3]],
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesCoreAllport <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreAllport,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesCoreAllport <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreAllport.png",
-  mdlMedicalOut$Att$predPltSlopesCoreAllport,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-When we compare the model using the
-
 \subsubsection{Robustness}
-
-```{r medicalModelAttNullInt, include=FALSE}
-# Create and save Model
-mdlMedical$lmerAttNullInt <-
-  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
-             data = dtMedical$full %>%
-               filter(complete.cases(
-                 OutgroupInteraction
-               ))) # use optim if it does not converge
-
-mdlMedical$lmeAttNullInt <-
-  lme(
-    AttitudesDutch ~ 1,
-    random = ~ 1 | PID,
-    data = dtMedical$full %>%
-      filter(complete.cases(
-        OutgroupInteraction
-      )),
-    na.action = na.omit,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(mdlMedical$lmerAttNull) #or with the lme function
-summ(mdlMedical$lmerAttNullInt, digits = 3)
-```
-
-```{r medicalModelInterceptAttCoreInt, include=FALSE}
-# Create and save Model
-mdlMedical$lmeInterceptAttCoreInt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction,
-    random =  ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedical$full
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedical$lmerInterceptAttCoreInt <- lmer(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction + (1 | PID),
-    data = dtMedical$full
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedical$lmerInterceptAttCoreIntCI <- 
-  confint(mdlMedical$lmerInterceptAttCoreInt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=dtMedical$full),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# Compare new model to previous step
-anova(mdlMedical$lmeAttNullInt, 
-      mdlMedical$lmeInterceptAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.)-1)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedical$varInterceptAttCoreInt <- 
-  lme4::VarCorr(mdlMedical$lmeInterceptAttCoreInt)
-```
-```{r medicalModelSlopesAttCoreIntX, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedical$lmeSlopesAttCoreInt <- lme(
-  AttitudesDutch ~
-    KeyNeedFulfillment_cwc * OutgroupInteraction,
-  random = ~ 1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  na.action = na.omit,
-  data = dtMedical$full
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedical$lmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc * OutgroupInteraction +
-      (1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID),
-    data = dtMedical$full
-  ), 
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedical$lmerSlopesAttCoreIntCI <- 
-  confint(mdlMedical$lmerSlopesAttCoreInt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlMedical$lmeAttNullInt, 
-      mdlMedical$lmeInterceptAttCoreInt,
-      mdlMedical$lmeSlopesAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedical$varSlopesAttCoreInt <- 
-  lme4::VarCorr(mdlMedical$lmeSlopesAttCoreInt)
-
-# Assumption Checks:
-mdlMedical$diagSlopesAttCoreInt <-
-  sjPlot::plot_model(mdlMedical$lmerSlopesAttCoreInt, type = "diag")
-grid.arrange(
-  mdlMedical$diagSlopesAttCoreInt[[1]],
-  mdlMedical$diagSlopesAttCoreInt[[2]]$`PID`,
-  mdlMedical$diagSlopesAttCoreInt[[3]],
-  mdlMedical$diagSlopesAttCoreInt[[4]]
-)
-
-# Plot prediction model
-mdlMedical$predSlopesAttCoreInt <- 
-  dtMedical$full %>%
-  filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
-  filter(PID %in% dtMedicalSupp$medicalPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedical$lmeSlopesAttCoreInt,
-                           dtMedical$full %>% 
-                             filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedical$predPltSlopesAttCoreInt <-
-    ggplot(data = mdlMedical$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Medical_PredictionPlot_SlopesAttCoreInt.png",
-  mdlMedical$predPltSlopesAttCoreInt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-We again checked for alternative models to the core need fulfillment.
-First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
-Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "OutgroupInteractionYes")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous studies.
-
-```{r medicalOutModelInterceptAttCoreSdt, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptCoreSdt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 | PID,
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptCoreSdt <- lmer(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=medicalOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
-
-# To be compared against a model with only the self determination theory needs
-mdlMedicalOut$Att$lmeInterceptSdt <-
-  lme(
-    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 | PID,
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-summ(
-  mdlMedicalOut$Att$lmerInterceptSdt <- lmer(
-    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous steps
-anova(
-  mdlMedicalOut$Att$lmeInterceptSdt,
-  mdlMedicalOut$Att$lmeInterceptCoreSdt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptCoreSdt <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreSdt)
-```
-
-```{r medicalOutModelSlopesAttCoreSdt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesCoreSdt <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc + Competence_cwc + Relatedness_cwc | PID,
-    control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerSlopesCoreSdtCI <- 
-  confint(mdlMedicalOut$Att$lmerSlopesCoreSdt)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeInterceptSdt,
-      mdlMedicalOut$Att$lmeInterceptCoreSdt, 
-      mdlMedicalOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# model with SDT only
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesSdt <-
-  lme(
-    AttitudesDutch ~
-      Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesSdt <- lmer(
-    AttitudesDutch ~
-      Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeInterceptSdt,
-      mdlMedicalOut$Att$lmeSlopesSdt, 
-      mdlMedicalOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesCoreSdt <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreSdt)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesCoreSdt <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreSdt, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[1]],
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[3]],
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesCoreSdt <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
-  filter(complete.cases(
-    KeyNeedFulfillment,
-    Autonomy, Competence, Relatedness
-    )) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID, Autonomy, Competence, Relatedness) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreSdt,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(
-                               KeyNeedFulfillment,
-                               Autonomy, Competence, Relatedness
-                             )) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesCoreSdt <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreStd.png",
-  mdlMedicalOut$Att$predPltSlopesCoreSdt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-# Model comparison
-medicalSdtComp <-
-  anova(
-    mdlMedicalOut$Att$lmerSlopesSdt, 
-    mdlMedicalOut$Att$lmerSlopesCoreSdt
-  ) %>%
-  as.data.frame()
-medicalSdtCompDf <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Df"]
-medicalSdtCompN <- sapply(ranef(mdlMedicalOut$Att$lmerSlopesCoreSdt), nrow)
-medicalSdtCompChi <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
-medicalSdtCompP <-
-  ifelse(medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
-         "< .001",
-         paste0("= ", medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
-
-medicalSdtCompChiSq <- paste0("$\\chi^2$(", medicalSdtCompDf, ", \\textit{N} = ", medicalSdtCompN, ") = ", medicalSdtCompChi, ", \\textit{p} ", medicalSdtCompP)
-```
-
-In a final step we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
-We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r medicalSdtCompChiSq`).
-We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFulfillment_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, similar to the previous study, in this large sample relatedness (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each predicted positive outgroup attitudes independently.
-However, the regression coefficient is three times as large for the core need fulfillment (with all scaling being equal).
-For full results see Online Supplementary Information B.
 

### 2021-11-08 Methods-and-Results.Rmd
decimal formatting fixed

--- 2021-11-08 Methods-and-Results.Rmd
@@
 To compare the models using either Allport's conditions or the core need fulfillment to predict outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
-When comparing the model selection indices we find that the fulfillment of the situation core need, indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r AIC(mdlMedicalOut$Att$lmerSlopesCore)` < `r AIC(mdlMedicalOut$Att$lmerSlopesAllport)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r BIC(mdlMedicalOut$Att$lmerSlopesCore)` < `r BIC(mdlMedicalOut$Att$lmerSlopesAllport)` $BIC_{Allport}$).
+When comparing the model selection indices we find that the fulfillment of the situation core need, indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
 Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`).

### 2021-11-08 Methods-and-Results.tex
decimal formatting fixed

@@
 performs slightly better than the model using Allport's conditions
-(\(AIC_{CoreNeed}\) 12632.0183 \textless{} 12651.5868 \(AIC_{Allport}\),
-and \(BIC_{CoreNeed}\) 12664.549 \textless{} 12684.1174
-\(BIC_{Allport}\)). Additionally, when considering the predictors
-jointly, we find that both significantly predict outgroup attitudes with
-similar sized regression parameters (random slopes model; Allport's
-Conditions: \textit{b} = 0.16, \textit{t}(1600) = 4.92, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}0.09, 0.24{]}, Core Need: \textit{b}
-= 0.14, \textit{t}(1600) = 3.85, \textit{p} \textless{} .001,
+(\(AIC_{CoreNeed}\) 12632.02 \textless{} 12651.59 \(AIC_{Allport}\), and
+\(BIC_{CoreNeed}\) 12664.55 \textless{} 12684.12 \(BIC_{Allport}\)).
+Additionally, when considering the predictors jointly, we find that both
+significantly predict outgroup attitudes with similar sized regression
+parameters (random slopes model; Allport's Conditions: \textit{b} =
+0.16, \textit{t}(1600) = 4.92, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.09, 0.24{]}, Core Need: \textit{b} = 0.14,
+\textit{t}(1600) = 3.85, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.08, 0.17{]}). This indicates that, although both

### 2021-11-18 manuscript.tex
Updates from Overleaf
intervention refs added

@@
 \usepackage{censor}
+\usepackage{lscape}
+\usepackage{pdflscape}
+\usepackage{pdfpages}
 
@@
 One of the main ameliorations proposed by social psychologists has been positive intergroup contact.
-Based on Allport's \citeyear{Allport1954b} contact hypothesis, a plethora of studies and interventions have worked on bringing different social groups together\footnote{Cite interventions of British ministries.}.
+Based on Allport's (\citeyear{Allport1954b}) contact hypothesis, a plethora of studies and interventions have worked on bringing different social groups together \citep[e.g.,][]{AlRamiah2012a, Reimer2021}.
 % Yet, despite ...
@@
 And more importantly, the satisfaction of key situation needs during the interaction should predict the positive contact effects most strongly.
+
+Re-Framing: Allport's conditions not enough.
+
+\section{Psychological Needs in Intergroup Relations}
 

### 2021-11-18 PreregristrationS3/AnalysisPlan_AOT-M.Rmd
references removed

--- 2021-11-04 PreregristrationS3/PreregistrationAOT-M.Rmd
@@
 ---
-title           : "Psychological Needs During Intergroup Contact: An Extensive Longitudinal Study (Young Medical Professionals Sample)"
-shorttitle      : "Preregistration: Needs During Intergroup Contact"
+title           : "Psychological Needs During Intergroup Contact — An Extensive Longitudinal Study (Young Medical Professionals Sample)"
+shorttitle      : "Preregistration — Statistical Models"
 date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
@@
 ---
-
-```{r setup, include=FALSE}
-# R Studio Clean-Up
-  cat("\014") # clear console
-  #rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
-  gc() # garbage collector
-
-# Install and Load Packages
-# !IMPORTANT!
-# BEFORE FIRST RENDER:
-# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
-# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file 
-lib <- c("rmarkdown", "knitr", "remedy", "bookdown", "psych",
-         "ggplot2", "ggthemes", "haven", "RColorBrewer", "plotly", "gridExtra",
-         "sessioninfo", "tibble", "pander", "devtools",
-         "data.table", "dplyr", "tidyr", "Hmisc", "kableExtra", 
-         "stringr", "stringi", "reshape2", "lubridate")
-invisible(lapply(lib, library, character.only = TRUE))  
-rm(lib)
-
-# Markdown Options
-  knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
-
-# Global Chunk Options
-  knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figures/',
-                        echo=TRUE, warning=FALSE, message=FALSE)
-```
-
-# Study Information
-
-## Title
-<!-- Provide the working title of your study.
-It may be the same title that you submit for publication of your final manuscript, but it is not a requirement.
-The title should be a specific and informative description of a project.
-Vague titles such as 'Fruit fly preregistration plan' are not appropriate.
-
-Example: Effect of sugar on brownie tastiness. -->
-
-`r rmarkdown::metadata$title`
-
-## Description
-<!-- Please give a brief description of your study, including some background, the purpose of the of the study, or broad research questions.
-The description should be no longer than the length of an abstract.
-It can give some context for the proposed study, but great detail is not needed here for your preregistration.
-
-Example: Though there is strong evidence to suggest that sugar affects taste preferences, the effect has never been demonstrated in brownies.
-Therefore, we will measure taste preference for four different levels of sugar concentration in a standard brownie recipe to determine if the effect exists in this pastry.
--->
-
-In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group [@Hewstone1996; @Pettigrew1998].
-A key condition for these contact benefits has been that the interaction is perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact [e.g., @MacInnis2015].
-It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact [Allport's Optimal Contact conditions, @Allport1954b].
-And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met.
-However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met [@Pettigrew2006].
-It, thus, remains unclear why and how exactly Allport's conditions work.
-
-We propose that Allport's optimal contact conditions are effective in creating positive contact because they constitute common psychological needs of the interacting individuals.
-If this is indeed the case, the impact of fulfilling other fundamental needs should produce similar beneficial contact results.
-And more importantly, the satisfaction of key situation needs during the interaction should predict the positive contact effects most strongly.
-
-## Hypotheses
-<!-- List specific, concise, and testable hypotheses.
-Please state if the hypotheses are directional or non-directional.
-If directional, state the direction.
-A predicted effect is also appropriate here.
-If a specific interaction or moderation is important to your research, you can list that as a separate hypothesis.
-
-Example: If taste affects preference, then mean preference indices will be higher with higher concentrations of sugar. -->
-
-1.
-\label{hyp:contact}Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
-    a. \label{hyp:contactFreq}Participants with more intergroup interactions should have more favorable outgroup attitudes.
-    b. \label{hyp:contactDummy}Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
-    c. \label{hyp:contactFreqQual}Participants with more intergroup interactions should have more favorable outgroup attitudes depending on the average interaction quality.
-2.
-\label{hyp:AllportsConditions}Based on Allport's optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
-    a.
-\label{hyp:AllportsPred}Based on Allport's optimal contact conditions, outgroup attitudes should be more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
-    b.
-\label{hyp:AllportsQuality}Based on past research on the role of interaction quality, interaction quality should be perceived as more positive after intergroup interactions with equal status, common goals, collaboration, and structural support.
-    c. \label{hyp:AllportsQualityMediation}Taken together, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extend be explained by interaction quality.
-3.
-\label{hyp:keyNeed}Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
-    a. \label{hyp:keyNeedPred}Outgroup attitudes should be more favorable after intergroup interactions with high key need fulfillment.
-    b. \label{hyp:keyNeedQual}Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
-    c. \label{hyp:keyNeedMediation}The variance explained in outgroup attitudes by key need fulfillment should to a large extend be explained by interaction quality.
-    d.
-\label{hyp:keyNeedContactType}The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
-Thus, the effect of key need fulfillment on outgroup attitudes should be stronger for intergroup interact than for non-outgroup interactions (or need fulfillment during a time of no interaction).
-    e.
-\label{hyp:keyNeedSDT}The effect of key need fulfillment on outgroup attitudes should persist even when taking other fundamental psychological needs into account.
-Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
-4. \label{hyp:comparison}Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict outgroup attitudes at least as well as Allport's conditions.
-    a. \label{hyp:compModel}The need model (H\ref{hyp:keyNeedPred}) should predict more variance in outgroup attitudes than the model based on Allport's conditions (H\ref{hyp:AllportsPred}).
-    b.
-\label{hyp:compTogether}The  effect of key need fulfillment on outgroup attitudes should  persist even when taking Allport's conditions into account.
-Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for equal status, common goals, collaboration, and structural support.
-
-# Design Plan
-<!-- In this section, you will be asked to describe the overall design of your study.
-Remember that this research plan is designed to register a single study, so if you have multiple experimental designs, please complete a separate preregistration.
--->
-
-## Study type
-
-**Observational Study**. Data is collected from study subjects that are not randomly assigned to a treatment. This includes surveys, natural experiments, and regression discontinuity designs.
-
-## Blinding
-<!-- Blinding describes who is aware of the experimental manipulations within a study. Select all that apply. Is there any additional blinding in this study? -->
-
-No participant blinding is involved in this study.
-
-## Study design
-<!-- Describe your study design.
-Examples include two-group, factorial, randomized block, and repeated measures.
-Is it a between (unpaired), within-subject (paired), or mixed design?
-Describe any counterbalancing required.
-Typical study designs for observation studies include cohort, cross sectional, and case-control studies.
-
-This question has a variety of possible answers.
-The key is for a researcher to be as detailed as is necessary given the specifics of their design.
-Be careful to determine if every parameter has been specified in the description of the study design.
-There may be some overlap between this question and the following questions.
-That is OK, as long as sufficient detail is given in one of the areas to provide all of the requested information.
-For example, if the study design describes a complete factorial, 2 X 3 design and the treatments and levels are specified previously, you do not have to repeat that information.
-
-Example: We have a between subjects design with 1 factor (sugar by mass) with 4 levels. -->
-
-This study used an extensive longitudinal design.
-Using a daily diary format, for at least 30 days participants received a short survey twice per day (at around 12pm and 7pm).
-We additionally included a longer pre- and post measurement survey the days before and after the extensive longitudinal data collection.
-
-## Randomization
-<!-- If you are doing a randomized study, how will you randomize, and at what level?
-Typical randomization techniques include: simple, block, stratified, and adaptive covariate randomization.
-If randomization is required for the study, the method should be specified here, not simply the source of random numbers.
-
-Example: We will use block randomization, where each participant will be randomly assigned to one of the four equally sized, predetermined blocks.
-The random number list used to create these four blocks will be created using the web applications available at https://random.org.
--->
-
-No randomization is involved in this study.
-
-# Sampling Plan
-<!-- In this section we’ll ask you to describe how you plan to collect samples, as well as the number of samples you plan to collect and your rationale for this decision.
-Please keep in mind that the data described in this section should be the actual data used for analysis, so if you are using a subset of a larger dataset, please describe the subset that will actually be used in your study.
--->
-
-## Existing data
-<!-- Preregistration is designed to make clear the distinction between confirmatory tests, specified prior to seeing the data, and exploratory analyses conducted after observing the data.
-Therefore, creating a research plan in which existing data will be used presents unique challenges.
-Please select the description that best describes your situation.
-Please do not hesitate to contact us if you have questions about how to answer this question (prereg@cos.io).
--->
-
-**Registration prior to accessing the data**.
-As of the date of submission, the data exist, but have not been accessed by you or your collaborators.
-Commonly, this includes data that has been collected by another researcher or institution.
-
-## Explanation of existing data
-<!-- If you indicate that you will be using some data that already exist in this study, please describe the steps you have taken to assure that you are unaware of any patterns or summary statistics in the data.
-This may include an explanation of how access to the data has been limited, who has observed the data, or how you have avoided observing any analysis of the specific data you will use in your study.
-
-An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results.
-After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point.
-
-Example: An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results.
-After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point.
--->
-
-The data was collected as part of a larger collaboration on daily intergroup relations.
-The researchers have had no direct access to the data, as the data was collected using an automated system using the FormR framework [@Arslan2020].
-The data were then downloaded and stored securely on an encrypted device until the eventual data analysis.
-None of the researchers have accessed the data thus far.
-
-## Data collection procedures
-<!-- Please describe the process by which you will collect your data.
-If you are using human subjects, this should include the population from which you obtain subjects, recruitment efforts, payment for participation, how subjects will be selected for eligibility from the initial pool (e.g.
-inclusion and exclusion rules), and your study timeline.
-For studies that donÍt include human subjects, include information about how you will collect samples, duration of data gathering efforts, source or location of samples, or batch numbers you will use.
-
-The answer to this question requires a specific set of instructions so that another person could repeat the data collection procedures and recreate the study population.
-Alternatively, if the study population would be unable to be reproduced because it relies on a specific set of circumstances unlikely to be recreated (e.g., a community of people from a specific time and location), the criteria and methods for creating the group and the rationale for this unique set of subjects should be clear.
-
-Example: Participants will be recruited through advertisements at local pastry shops.
-Participants will be paid $10 for agreeing to participate (raised to $30 if our sample size is not reached within 15 days of beginning recruitment).
-Participants must be at least 18 years old and be able to eat the ingredients of the pastries.
--->
-
-The data was collected in a three step procedure:
-
-1. Entry Survey: A pre-measurement questionnaire (appr. 25 minutes) including demographic information, and relations to the Dutch majority (payment: 2 Euros).
-2. Experience Recaps: At least 30 days of short reflection surveys (appr. 3—5 minutes) on intergroup interactions twice a day (payment: 1 Euro per Recap; up to 2 Euros per day).
-3. Conclusion Survey: On the last day, we conclude with a post-measurement questionnaire (appr. 25 minutes) with some questions on habits and reflections on the study (payment: 2 Euros).
-
-After the initial 30 day duration, participants are offered the possibility to continue participating in the study either with payment if daily diary measures were missed during the initial study phase or without payment after a total of 60 daily diary measurements were completed.
-After the initial 30-day period, participants receive automated feedback visualizing the development of their own well-being, attitudes, and motive responses as an additional initiative and to give participants access to their own data and to compensate study participation.
-
-## Sample size
-<!-- Describe the sample size of your study.
-How many units will be analyzed in the study?
-This could be the number of people, birds, classrooms, plots, interactions, or countries included.
-If the units are not individuals, then describe the size requirements for each unit.
-If you are using a clustered or multilevel design, how many units are you collecting at each level of the analysis?
-For some studies, this will simply be the number of samples or the number of clusters.
-For others, this could be an expected range, minimum, or maximum number.
-
-Example: Our target sample size is 280 participants. We will attempt to recruit up to 320, assuming that not all will complete the total task. -->
-
-Our target sample size is a sum of 4,000 daily diary measurements.
-With 100% completion rate that would be archived with 67 participants (60 daily diary responses each).
-Given that we expect some incomplete daily diary measurements, we aimed to recruit 80 participants.
-
-## Sample size rationale
-<!-- This could include a power analysis or an arbitrary constraint such as time, money, or personnel.
-This gives you an opportunity to specifically state how the sample size will be determined.
-A wide range of possible answers is acceptable; remember that transparency is more important than principled justifications.
-If you state any reason for a sample size upfront, it is better than stating no reason and leaving the reader to "fill in the blanks." Acceptable rationales include: a power analysis, an arbitrary number of subjects, or a number based on time or monetary constraints.
-
-Example: We used the software program G*Power to conduct a power analysis. Our goal was to obtain .95 power to detect a medium effect size of .25 at the standard .05 alpha error probability. -->
-
-The targeted sample size depended on a combination of different factors.
-Different analyses were planned as part of the collaboration and budgeting was a practical constraint.
-Some analyses were planned based on (1) the pre- to post measurements, (2) the dynamic developments over the daily diary measurements, or (3) the contemporary effects within the daily diary measurements.
-
-Power considerations of mixed effects model such as with extensive longitudinal data are difficult to estimate because of the complex covariance structures.
-Simulation studies based on the first two samples within this project indicated that with well-distributed scales, and small to medium effect sizes, 70-80 participants with at least seven daily diary measurements and a simple pre--post survey were sufficiently powerful (power = .8, alpha = .05) to answer most of the key research questions of the collaboration.
-
-The ultimate sampling procedure decision was made as a practical balancing of the number of participants and the number of measurements provided by each participants.
-Given that this study primarily focuses on the contemporaneous effects within the daily diary measurements, power should be high enough.
-
-## Stopping rule
-<!-- If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection.
-
-You may specify a stopping rule based on p-values only in the specific case of sequential analyses with pre-specified checkpoints, alphas levels, and stopping rules.
-Unacceptable rationales include stopping based on p-values if checkpoints and stopping rules are not specified.
-If you have control over your sample size, then including a stopping rule is not necessary, though it must be clear in this question or a previous question how an exact sample size is attained.
-
-Example: We will post participant sign-up slots by week on the preceding Friday night, with 20 spots posted per week.
-We will post 20 new slots each week if, on that Friday night, we are below 320 participants.
--->
-
-Participants will be recruited until 80 participants finish the pre-measurement.
-Invitations to complete additional daily diary measurements will be extended until participants chose to leave the study or at the most until two months (i.e., 64 days) after the initial entry survey (i.e., from the pre measurement survey).
-
-# Variables
-<!-- In this section you can describe all variables (both manipulated and measured variables) that will later be used in your confirmatory analysis plan.
-In your analysis plan, you will have the opportunity to describe how each variable will be used.
-If you have variables which you are measuring for exploratory analyses, you are not required to list them, though you are permitted to do so.
--->
-
-## Manipulated variables
-<!-- Describe all variables you plan to manipulate and the levels or treatment arms of each variable.
-This is not applicable to any observational study.
-For any experimental manipulation, you should give a precise definition of each manipulated variable.
-This must include a precise description of the levels at which each variable will be set, or a specific definition for each categorical treatment.
-For example, “loud or quiet,” should instead give either a precise decibel level or a means of recreating each level.
-'Presence/absence' or 'positive/negative' is an acceptable description if the variable is precisely described.
-
-Example: We manipulated the percentage of sugar by mass added to brownies. The four levels of this categorical variable are: 15%, 20%, 25%, or 40% cane sugar by mass. -->
-
-Not applicable given that the study design is observational.
-
-## Measured variables
-<!-- Describe each variable that you will measure.
-This will include outcome measures, as well as any predictors or covariates that you will measure.
-You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.
-
-Observational studies and meta-analyses will include only measured variables.
-As with the previous questions, the answers here must be precise.
-For example, 'intelligence,' 'accuracy,' 'aggression,' and 'color' are too vague.
-Acceptable alternatives could be 'IQ as measured by Wechsler Adult Intelligence Scale' 'percent correct,' 'number of threat displays,' and 'percent reflectance at 400 nm.'
-
-Example: The single outcome variable will be the perceived tastiness of the single brownie each participant will eat.
-We will measure this by asking participants ‘How much did you enjoy eating the brownie’ (on a scale of 1-7, 1 being 'not at all', 7 being 'a great deal') and 'How good did the brownie taste' (on a scale of 1-7, 1 being 'very bad', 7 being 'very good').
--->
-
-**Key variables:**
-
-1. Whether an interaction happened during the past daytime period
-    a. Did you meet a Dutch person this [morning/afternoon]?
-    a. Did you meet a Non-Dutch person [morning/afternoon]?
-1. Number of interactions during the past daytime period
-    a. How many interactions with Dutch people did you have this [morning/afternoon]?
-    a. How many interactions with Non-Dutch people did you have this [morning/afternoon]?
-1. Key need assessment
-    a. What was your main goal during the interaction with [name interaction partner]?
-    a. During the interaction with [name interaction partner] your goal [free-text entry interaction key need] was fulfilled.
-1. Allport's Conditions (equal status, common goal, collaboration, and structural support)
-    a. The interaction with [name interaction partner] was on equal footing (same status)
-    a. [name interaction partner] shared your goal ([free-text entry interaction key need])
-    a. The interaction with [name interaction partner] was cooperative
-    a. The interaction with [name interaction partner] was voluntary
-1. Interaction Quality
-    a. Overall, the interaction with [name interaction partner] was: Unpleasant to Pleasant
-1. Outgroup Attitudes
-    a. After the interaction, how favorably do you feel towards the Dutch.
-
-**Control variables:**
-
-1. Self Determination Theory needs ("During the interaction with [name interaction partner]")
-    a. I was myself.
-    a. I felt competent.
-    a. I shared information about myself. 
-    a. [name interaction partner] shared information about themselves.
-1. General key need during daytime
-    a. What was your main goal during this [morning/afternoon]?
-    a. During this [morning/afternoon] your goal ([free-text entry daytime key need]) was fulfilled
-    a. How important was your goal ([free-text entry daytime key need]) to you:
-1. Student Goals ("Please rate the importance of each goal during the interaction with [name interaction partner]"):
-    a. Social support / social connection goals
-    a. Romantic or sexual relationship goals
-    a. Academic goals
-    a. Career goals
-    a. Financial goals
-    a. Health / fitness goals
-    a. Leisure / fun goals
-    a. Personal improvement / growth goals
-    a. Service / helping goals
-    a. Spiritual / religious goals
-
-**Additional Analyses:**
-
-1. Generalization from interaction partner to outgroup
-    a. After the interaction, how favorably do you feel towards [name interaction partner].
-    a. The interaction with [name interaction partner] was representative of the Dutch.
-1. Alternative interaction quality definition ("Overall, the interaction with [name interaction partner] was ...")
-    a. Unpleasant to Pleasant
-    a. Superficial to Meaningful
-    a. Ineffective to Effective
-    a. Unimportant to Important
-1. Potential moderation by the relationship with interaction partner
-    a. How close do you feel to [name interaction partner]?
-    a. How much do you trust [name interaction partner]?
-    a. What is your relationship with [name interaction partner]?
-1. Potential moderation by key need characteristics
-    a. [name interaction partner] helped fulfill your goal [free-text entry interaction key need].
-    a. How important was your goal ([free-text interaction key need]) to you?
-1. Potential moderation by the interaction characteristics
-    a. How long was the interaction? (in minutes)
-    a. What was the main language during the interaction?
-    a. The interaction was: With a single other / In a group
-
-_Full variable information is available in the codebook ('Codebook_AOT-M_ItemsPerSection.xlsx')_
-
-## Indices
-<!-- If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined?
-Include either a formula or a precise description of your method.
-If your are using a more complicated statistical method to combine measures (e.g.
-a factor analysis), you can note that here but describe the exact method in the analysis plan section.
-
-If you are using multiple pieces of data to construct a single variable, how will this occur?
-Both the data that are included and the formula or weights for each measure must be specified.
-Standard summary statistics, such as "means" do not require a formula, though more complicated indices require either the exact formula or, if it is an established index in the field, the index must be unambiguously defined.
-For example, "biodiversity index" is too broad, whereas "Shannon’s biodiversity index" is appropriate.
-
-Example: We will take the mean of the two questions above to create a single measure of 'brownie enjoyment.'  -->
-
-1.
-Mean Allport's conditions.
-We create a mean-averaged index of Allport's conditions in response to past findings indicating that the conditions are best conceptualized jointly and as functioning together rather than as fully independent factors [@Pettigrew2006, p.
-766].
-Similar to past studies we thus hope to build a global indicator [e.g., see @Pettigrew2006].
-As with other indices we will ensure that the individual items indeed relate to a common latent construct and are  meaningfully combine in an index.
-If this is not possible we will create sub-indices and/or assess the impact of the conditions separately.
-    a. The interaction with [name interaction partner] was on equal footing (same status)
-    a. [name interaction partner] shared your goal ([free-text entry interaction key need])
-    a. The interaction with [name interaction partner] was cooperative
-    a. The interaction with [name interaction partner] was voluntary
-1. Mean belongingness during intergroup contact
-    a. I shared information about myself. 
-    a. [name interaction partner] shared information about themselves.
-1. Mean alternative interaction quality definition ("Overall, the interaction with [name interaction partner] was ...")
-    a. Unpleasant to Pleasant
-    a. Superficial to Meaningful
-    a. Ineffective to Effective
-    a. Unimportant to Important
 
@@
 
-## Transformations
-<!-- If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process.
-If any categorical predictors are included in a regression, indicate how those variables will be coded (e.g.
-dummy coding, summation coding, etc.) and what the reference category will be.
-
-Example: The "Effect of sugar on brownie tastiness" does not require any additional transformations.
-However, if it were using a regression analysis and each level of sweet had been categorically described (e.g.
-not sweet, somewhat sweet, sweet, and very sweet), 'sweet' could be dummy coded with 'not sweet' as the reference category.
--->
-
-We will mean-center all level-one predictors within participants (i.e., cluster mean centering).
-This is relevant for any predictor variable during the interaction (e.g., key need fulfillment, interaction quality, ...).
-We mean-center within-person predictors, to meaningfully distinguish within and between person variances and because we obtain a meaningful intercept when having a random slope model [e.g., @Hamaker2014].
-
-## Inference criteria
-<!-- What criteria will you use to make inferences?
-Please describe the information youÍll use (e.g.
-p-values, bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate.
-Will you be using one or two tailed tests for each of your analyses?
-If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?
-
-p-values, confidence intervals, and effect sizes are standard means for making an inference, and any level is acceptable, though some criteria must be specified in this or previous fields.
-Bayesian analyses should specify a Bayes factor or a credible interval.
-If you are selecting models, then how will you determine the relative quality of each?
-In regards to multiple comparisons, this is a question with few "wrong" answers.
-In other words, transparency is more important than any specific method of controlling the false discovery rate or false error rate.
-One may state an intention to report all tests conducted or one may conduct a specific correction procedure; either strategy is acceptable.
-
-Example: We will use the standard p<.05 criteria for determining if the ANOVA and the post hoc test suggest that the results are significantly different from those expected if the null hypothesis were correct.
-The post-hoc Tukey-Kramer test adjusts for multiple comparisons.
--->
-
-We will use the standard p<.05 criteria for determining whether the correlation and regression coefficients are statistically significant.
-However, given the large sample size we will place a particular emphasis on effect sizes in our interpretations of the results.
-
-## Data exclusion
-<!-- How will you determine what data or samples, if any, to exclude from your analyses?
-How will outliers be handled?
-Will you use any awareness check?
-Any rule for excluding a particular set of data is acceptable.
-One may describe rules for excluding a participant or for identifying outlier data.
-
-Example: No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the three tastiness indices.
-Outliers will be included in the analysis.
--->
-
-No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the variables of interest for a given analysis.
-Outliers will generally be included in analyses, however we will use sensitivity analyses to assess the robustness of the results to outliers.
-
-## Missing data
-<!-- How will you deal with incomplete or missing data?
-Any relevant explanation is acceptable.
-As a final reminder, remember that the final analysis must follow the specified plan, and deviations must be either strongly justified or included as a separate, exploratory analysis.
-
-Example: If a subject does not complete any of the three indices of tastiness, that subject will not be included in the analysis. -->
-
-Given the (expectedly) large sample size of contemporaneous measurements, we will remove all instances during which a participant did not respond to any of the relevant variables.
-Given that we are not necessarily interested in individual trajectories in our analyses, we will use all available data (i.e., will not remove entire participants but rather individual incomplete daily diary measurements).
-
-## Exploratory analyses (optional)
-<!-- If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here.
-An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use.
-A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.
-
-Example: We expect that certain demographic traits may be related to taste preferences.
-Therefore, we will look for relationships between demographic variables (age, gender, income, and marital status) and the primary outcome measures of taste preferences.
--->
-
-@Brown2005 proposed in their integrative theory of intergroup contact that "group salience" should moderate the positive effect of intergroup contact on outgroup attitudes.
-They argue that especially when the outgroup membership is salient, the positive attitudes should generalize from the outgroup individual to the general outgroup.
-We have data to test this hypothesis within a large intensive longitudinal dataset of daily intergroup interactions.
-We do this by separately assessing attitudes towards the outgroup interaction partner and the outgroup generally.
-And by assessing whether perceiving the interaction as representative of the outgroup moderates the positive contact effects.
-
-To build confidence in our conclusions about the role of contact quality we calculate an alternative measure of interaction quality that includes perceived pleasantness, meaning, effectiveness, and importance of the interaction.
-
-We expect that certain contextual characteristics may be related to the positive effects of high quality outgroup interactions.
-Therefore, we will look for the effect of key need fulfillment on outgroup attitudes while also including information about the interaction partner (perceived closeness, trust, relationship), the interaction characteristics (duration, interaction language, group vs.
-dyadic), as well as characteristics of the key need (importance of the need, fulfillment due to the interaction partner).
-
-# Other
-
-## Other (Optional)
-<!-- If there is any additional information that you feel needs to be included in your preregistration, please enter it here.
-Literature cited, disclosures of any related work such as replications or work that uses the same data, or other context that will be helpful for future readers would be appropriate here.
--->
-
-Not applicable.
-
 ## 

### 2021-11-18 manuscript.tex
references updated
intro aim

@@
 However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met.
-It, thus, remains unclear why and how exactly Allport's conditions work.
+It, thus, remains unclear when and why exactly an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects.
 
-In this article, we propose that Allport's optimal contact conditions are effective in creating positive contact because they constitute common psychological needs of the interacting individuals.
-If this is indeed the case, the impact of fulfilling other fundamental needs should produce similar beneficial contact results.
-And more importantly, the satisfaction of key situation needs during the interaction should predict the positive contact effects most strongly.
-
-Re-Framing: Allport's conditions not enough.
+In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and in extension positive outgroup attitudes.
+Additionally, such needs might even explain the effectiveness of Allport's optimal contact conditions, if these conditions constitute common psychological needs of the interacting individuals.
+To test this we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with host majority group members.
 
 \section{Psychological Needs in Intergroup Relations}
+
+\faQuestionCircle\ Past research on the mechanisms of Allport's Conditions + research on interaction quality.
 

### 2021-11-21 manuscript.tex
Updates from Overleaf

@@
 In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and in extension positive outgroup attitudes.
+That is to say, that if someone seeks/wishes to ...
+.
 Additionally, such needs might even explain the effectiveness of Allport's optimal contact conditions, if these conditions constitute common psychological needs of the interacting individuals.
@@
 
+\section{Intergroup Contact Mechanisms}
+\begin{itemize}
+    \item theoretical mechanisms (moderator and mediators) \citep[][]{Brown2005}. They don't discuss Allport's conditions(?)
+    \item Allport's conditions
+    \item interaction quality
+\end{itemize}
+
 \section{Psychological Needs in Intergroup Relations}
+\begin{itemize}
+    \item general \citep[][]{Shnabel2008}. + Nurit's recent papers 
+    \item migrants \citep[][]{Celebi2017}
+    \item intergroup contact \citep[][]{Dovidio2017}
+\end{itemize}
 
-\faQuestionCircle\ Past research on the mechanisms of Allport's Conditions + research on interaction quality.
-
-\faKeyboard\ We should probably add a short section on past literature that has examined psychological needs in intergroup contact in general \citep[e.g.,][]{Shnabel2008} as well as for particular groups, including migrants \citep[e.g.,][]{Celebi2017}.
-
-\noindent We should probably also include:
 \begin{displayquote}
@@
 
-We probably need to note that there are really good papers on the likely mechanisms of intergroup contact \citep[e.g.,][]{Brown2005}. But they don't discuss Allport's conditions.
-
-Plus, recent work Nurit Shnabel.
-
-\section{The Present Research}
-\faKeyboard\ To be written out.
+\section{Process Data}
+\begin{itemize}
+    \item retrospective vs. near-time data
+    \item need for real-life data
+    \item barriers
+    \item innovations like 'contact logger' \citep[][]{Keil2020}, and FormR \citep[][]{Arslan2020} make this possible now
+\end{itemize}
 
@@
 
+\section{The Present Research}
+
+\begin{itemize}
+    \item aims
+    \item shortened hypotheses
+    \item analysis strategy
+    \item assumptions, materials, preregistration
+\end{itemize}
+
 Based on this we formulated four main hypotheses:
+\begin{enumerate}
+    \item 
+    \item
+    \item
+\end{enumerate}
+
+\input{Methods-and-Results}
+
+\section{Discussion}
+
+\printbibliography
+
+\appendix
+
+\section{Appendix A: Hypotheses}
+\label{app:AppendixA}
 
@@
 
-\faKeyboard\ all assumptions were fine (see Online Supplementary Materials B).
-
-\input{Methods-and-Results}
-
-\section{Discussion}
-
-\printbibliography
-
-\appendix
-
-\section{Appendix A}
-\label{app:AppendixA}
-
-The Appendix text goes here.
-
 \end{document}

### 2021-11-22 manuscript.tex
introduction structure added
first draft Intergroup Contact Mechanisms

@@
 A key condition for these contact benefits, has been that the interaction is indeed perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact \citep[e.g.,][]{MacInnis2015}.
-It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact \citep[Allport's Optimal Contact conditions,][]{Allport1954b}.
+It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact \citep[Allport's Optimal Contact conditions,][]{Allport1954b, Pettigrew1969}.
 And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met.
-However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met.
+However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met \citep[][]{Pettigrew2006}.
 It, thus, remains unclear when and why exactly an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects.
@@
 \section{Intergroup Contact Mechanisms}
-\begin{itemize}
-    \item theoretical mechanisms (moderator and mediators) \citep[][]{Brown2005}. They don't discuss Allport's conditions(?)
-    \item Allport's conditions
-    \item interaction quality
-\end{itemize}
+\faQuestionCircle\ Not sure whether we need this section
+
+As one of the most researched and practically implemented theories of social psychology, intergroup contact has received a vast amount of empirical, and theoretical attention \citep[][]{Dovidio2017}.
+Several meta-analytic reviews have found moderately sized positive effects of intergroup contact \citep[][]{Tropp2005, Pettigrew2006, Davies2011}.
+Additional meta-analyses have additionally shown that intergroup contact is also effective outside the lab \citep[][]{Beelmann2014, Lemmer2015}, during online contact \citep[][]{White2020}, as well as during several more indirect forms of contact \citep[][]{Miles2014, Zhou2019, Harwood2021}.
+
+With such a persistent and meaningful effect, researchers have long proposed theoretical models to understand these intergroup contact effects.
+These searches for moderators and mediators have, for example, highlighted different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}.
+
+Interestingly, one concept that has arguably remained at the center of theoretical debates throughout the decades has been the role of 'positive' contact.
+\st{Although Gordon Allport was not generally optimistic of intergroup contact (especially if it was casual or by too deeply prejudiced individuals), he did see immense potential if only such interactions led to positive associations.} In his now famous chapter on 'the effects of contact', Gordon Allport (\citeyear{Allport1954b}) set out to summarize under what circumstances an interaction between groups tends to be positive, leading to favourable attitudes and reduced prejudice.
+In the years that followed, several additional conditions were proposed under which a positive intergroup contact would occur \citep[for a critical review see][]{Pettigrew1986}.
+As a counter-movement to this rather restrictive approach, with the beginning of the 21\textsuperscript{st} century attention had shifted towards investigating the psychological mechanisms of intergroup contact \citep[e.g.
+see,][]{Paolini2021}.
+With this shift in focus, the idea of 'positive contact' has seemingly seen a renaissance, where the adjective positive is now not merely an evaluation of the outcome, but rather a feature of the interaction itself.
+As such, recent work has focused on the role of 'perceived interaction quality' \citep[e.g.,][]{Brown2007, Voci2003} or 'interaction valence' \citep[e.g.,][]{Tropp2016, Barlow2012}, to show that whether a
+
+MAYBE: Yet, relatively little research has investigated why interactions are perceived as positive.
+That is to say that although a sizeable number of moderators and mediators of intergroup contact have been proposed and interaction quality is seen as an important to the betterment of intergroup relations,
+
+ALTERNATIVE: The literature on intergroup contacts, has thus far mostly ignored the role of individual and social motivations within the intergroup contact process.
 
@@
 \begin{itemize}
-    \item general \citep[][]{Shnabel2008}. + Nurit's recent papers 
+    \item general \citep[][]{Shnabel2008, Downie2008}. + Nurit's recent papers 
     \item migrants \citep[][]{Celebi2017}
@@
     \item retrospective vs. near-time data
-    \item need for real-life data
+    \item need for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life data \citep[][]{MacInnis2015, McKeown2017}
     \item barriers
-    \item innovations like 'contact logger' \citep[][]{Keil2020}, and FormR \citep[][]{Arslan2020} make this possible now
+    \item innovations like 'contact logger' \citep[][]{Keil2020}, and FormR \citep[][]{Arslan2020} make this possible now \citep[also see, e.g.,][]{ODonnell2021}
 \end{itemize}

### 2021-11-22 manuscript.tex
Psychological Needs in Intergroup Relations

@@
 .
-Additionally, such needs might even explain the effectiveness of Allport's optimal contact conditions, if these conditions constitute common psychological needs of the interacting individuals.
+Additionally, such needs might even explain the effectiveness of Allport's optimal contact conditions, if these conditions constitute common psychological needs of the interacting individual.
 To test this we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with host majority group members.
@@
 \section{Intergroup Contact Mechanisms}
-\faQuestionCircle\ Not sure whether we need this section
+\faQuestionCircle\ Not sure whether we need this section.
+
+\faExclamationCircle\ This section has become way too complex (i.e., too many arguments to get to our own proposed work).
+I think we ultimately need to introduce the concept of interaction quality and that we don't necessarily know why interactions are perceived as positive, therefore we propose that we can look towards the motivational literature for this.
+The issue for me came up when I tried to give credit to past theoretical work (which I thought we need to acknowledge in some way).
 
 As one of the most researched and practically implemented theories of social psychology, intergroup contact has received a vast amount of empirical, and theoretical attention \citep[][]{Dovidio2017}.
-Several meta-analytic reviews have found moderately sized positive effects of intergroup contact \citep[][]{Tropp2005, Pettigrew2006, Davies2011}.
-Additional meta-analyses have additionally shown that intergroup contact is also effective outside the lab \citep[][]{Beelmann2014, Lemmer2015}, during online contact \citep[][]{White2020}, as well as during several more indirect forms of contact \citep[][]{Miles2014, Zhou2019, Harwood2021}.
-
+Several meta-analytic reviews have found moderately sized positive effects of intergroup contact \citep[][]{Tropp2005, Pettigrew2006, Davies2011} and later meta-analyses have additionally shown that intergroup contact is also effective outside the lab \citep[][]{Beelmann2014, Lemmer2015}, during online contact \citep[][]{White2020}, as well as during several more indirect forms of contact \citep[][]{Miles2014, Zhou2019, Harwood2021}.
 With such a persistent and meaningful effect, researchers have long proposed theoretical models to understand these intergroup contact effects.
-These searches for moderators and mediators have, for example, highlighted different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}.
 
@@
 see,][]{Paolini2021}.
-With this shift in focus, the idea of 'positive contact' has seemingly seen a renaissance, where the adjective positive is now not merely an evaluation of the outcome, but rather a feature of the interaction itself.
-As such, recent work has focused on the role of 'perceived interaction quality' \citep[e.g.,][]{Brown2007, Voci2003} or 'interaction valence' \citep[e.g.,][]{Tropp2016, Barlow2012}, to show that whether a
+With this shift in focus, the idea of 'positive contact' has seemingly seen a renaissance, where the adjective 'positive' is now not merely an evaluation of the outcome, but rather a feature of the interaction itself.
+As such, recent work has focused on the role of 'perceived interaction quality' \citep[e.g.,][]{Brown2007, Voci2003} or 'interaction valence' \citep[e.g.,][]{Tropp2016, Barlow2012}, to show that only if an interaction is perceived as positive will it lead to more favourable intergroup relations.
+And inversely interactions that are perceived as negative have the strong propensity to harm outgroup attitudes.
+However, relatively little research has investigated why interactions are perceived as positive.
 
-MAYBE: Yet, relatively little research has investigated why interactions are perceived as positive.
-That is to say that although a sizeable number of moderators and mediators of intergroup contact have been proposed and interaction quality is seen as an important to the betterment of intergroup relations,
+Thus although a sizeable number of moderators and mediators of intergroup contact have been proposed, their effects might be undermined if they do not result in a 'positive' contact.
+As an example, important moderators and mediators that have been identified are different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}.
+However, there is a discernible disconnect between these mechanisms and perceptions that an interaction is positive.
+That is to say that, just because someone learns something new about the other group, or reduces their threat perceptions does not mean that such an interaction is perceived as positive.
+Or inversely, an interaction can, for example, be very intimate but perceived as negative.
+If that were the case, there is a reasonable chance that such an interaction might not translate into improved outgroup attitudes \citep[e.g.,][]{Barlow2012}.
+We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
 
-ALTERNATIVE: The literature on intergroup contacts, has thus far mostly ignored the role of individual and social motivations within the intergroup contact process.
+ALTERNATIVE: One potential remedy might come from looking to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
 
 \section{Psychological Needs in Intergroup Relations}
-\begin{itemize}
-    \item general \citep[][]{Shnabel2008, Downie2008}. + Nurit's recent papers 
-    \item migrants \citep[][]{Celebi2017}
-    \item intergroup contact \citep[][]{Dovidio2017}
-\end{itemize}
+Although considerations of psychological needs and motivations have remained markedly absent within the intergroup contact literature, the concepts are in no way foreign to the general topic of intergroup relations.
+On the most general level, research on intergroup conflicts has, for example, shown that addressing the group-specific needs predicts willingness to reconcile with the other group \citep[][]{Shnabel2008}.
+For the case of refugee migrants in their relationship with a majority group, a recent study found that identity needs will buffer against discrimination experiences and will protect personal health \citep[][]{Celebi2017}.
 
-\begin{displayquote}
-    Psychological needs might “explain the asymmetry of experiences and outcomes in intergroup interactions and identify an essential element for interventions: To achieve truly constructive intergroup relations, it is important that intergroup exchanges meet the psychological needs of both majority- and minority-group members” \\
-    \hfill --- \citep[][p. 611]{Dovidio2017}
-\end{displayquote}
+Additionally, within the field of interpersonal relations, we find first evidence that the fulfillment of fundamental psychological needs might predict perceived interaction quality in non-intergroup interactions \citep[][]{Downie2008}.
+And even within the field of intergroup contact the idea of need fulfillment as a psychological mechanism is not entirely novel.
+\citet{Dovidio2017} in their narrative review have suggested that understanding psychological needs might be essential to constructive intergroup contact.
+And recently first empirical research has even found psychological need fulfillment during intergroup contacts to predict support for social change  \citep[][]{Hassler2021}.
+There is thus initial evidence to suggest that need fulfillment during intergroup contact might offer a promising psychological mechanism to understand perceived interaction quality and positive outgroup attitudes.
 

### 2021-11-22 manuscript.tex
Real-Life Process Data

@@
 \section{Intergroup Contact Mechanisms}
-\faQuestionCircle\ Not sure whether we need this section.
+\faQuestionCircle\ \textit{Not sure whether we need this section.}
 
-\faExclamationCircle\ This section has become way too complex (i.e., too many arguments to get to our own proposed work).
+\faExclamationCircle\ \textit{This section has become way too complex (i.e., too many arguments to get to our own proposed work).
 I think we ultimately need to introduce the concept of interaction quality and that we don't necessarily know why interactions are perceived as positive, therefore we propose that we can look towards the motivational literature for this.
-The issue for me came up when I tried to give credit to past theoretical work (which I thought we need to acknowledge in some way).
+The difficulties started for me when I tried to give credit to past theoretical work (which I thought we need to acknowledge in some way).}
 
@@
 Interestingly, one concept that has arguably remained at the center of theoretical debates throughout the decades has been the role of 'positive' contact.
-\st{Although Gordon Allport was not generally optimistic of intergroup contact (especially if it was casual or by too deeply prejudiced individuals), he did see immense potential if only such interactions led to positive associations.} In his now famous chapter on 'the effects of contact', Gordon Allport (\citeyear{Allport1954b}) set out to summarize under what circumstances an interaction between groups tends to be positive, leading to favourable attitudes and reduced prejudice.
+In his now famous chapter on 'the effects of contact', Gordon Allport (\citeyear{Allport1954b}) set out to summarize under what circumstances an interaction between groups tends to be positive, leading to favourable attitudes and reduced prejudice.
 In the years that followed, several additional conditions were proposed under which a positive intergroup contact would occur \citep[for a critical review see][]{Pettigrew1986}.
@@
 
-\section{Process Data}
-\begin{itemize}
-    \item retrospective vs. near-time data
-    \item need for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life data \citep[][]{MacInnis2015, McKeown2017}
-    \item barriers
-    \item innovations like 'contact logger' \citep[][]{Keil2020}, and FormR \citep[][]{Arslan2020} make this possible now \citep[also see, e.g.,][]{ODonnell2021}
-\end{itemize}
+\section{Real-Life Process Data}
+Over the past two decades several reviewers of the field have advocated that to truly understand intergroup contacts, there is a need for studies that collect longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
+The reasoning behind these calls for longitudinal real-life data has been manifold.
+Among the most pressing issues is concern that past investigations of intergroup contact have either focused on the dynamics of individual interactions but within artificial laboratory settings or have collected data situated within the lived experiences but used retrospective self-report data that asked about past interactions in general.
+The collection of data over time would, thus, allow researchers to follow the development of intergroup relations as they develop across multiple interactions.
+At the same time, such longitudinal data would also be situated within the real-life experiences of the participant.
+Additionally, such experience-sampling data can be close to the intergroup interactions would largely mitigate recall biases.
+Moreover, intensive longitudinal data often allows to capture large amounts of high-quality data with relatively few participants.
 
-\faQuestionCircle\ Not sure where this goes: To ensure that our sample would have a considerable number of intergroup contacts we focused on the minority group perspective in our second study.
-We followed a group of young migrants who had (daily) intergroup contacts with majority Dutch people.
-This design allowed us to test whether intergroup interactions and the fulfillment of psychological needs could jointly predict the development of attitudes towards the outgroup (i.e., the Dutch host society).
+In the past such data collections were often unfeasible because they were either physically impractical or too expensive.
+However, recent technological developments allow us to easily collect experience sampling data on mobile devices \citep[e.g.,][]{Keil2020} or using web-based applications \citep[e.g.,][]{Arslan2020}.
+At the same time, analytical methods for such more complex data have become more readily available, making the analyses more approachable \citep[see, e.g.,][]{ODonnell2021}.
+Given these, technological and methodological developments, we were able to collect a large amount of real-life data following the daily intergroup interactions of recent migrants with the majority group members.
 

### 2021-11-22 manuscript.tex
situational core need intro

@@
 For the case of refugee migrants in their relationship with a majority group, a recent study found that identity needs will buffer against discrimination experiences and will protect personal health \citep[][]{Celebi2017}.
+Additionally, within the field of interpersonal relations, we find first evidence that the fulfillment of fundamental psychological needs might predict perceived interaction quality in non-intergroup interactions \citep[][]{Downie2008}.
 
-Additionally, within the field of interpersonal relations, we find first evidence that the fulfillment of fundamental psychological needs might predict perceived interaction quality in non-intergroup interactions \citep[][]{Downie2008}.
 And even within the field of intergroup contact the idea of need fulfillment as a psychological mechanism is not entirely novel.
@@
 There is thus initial evidence to suggest that need fulfillment during intergroup contact might offer a promising psychological mechanism to understand perceived interaction quality and positive outgroup attitudes.
+
+One reason why motivational considerations might have remained absent from the intergroup contact literature is that people might enter into a contact with a plethora of individual needs or goals that might be relevant to them in that particular situation.
+Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad range of fundamental psychological needs.
+To avoid this predicament we propose to start by using adaptive and responsive survey designs that allow a tailored approach based on the participants inputs \citep[e.g.,][]{Tourangeau2017}.
+In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., situation core need) and with reference to their own response the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment).
+Such an adaptive approach allows us to test the fundamental psychological mechanism of whether situational psychological needs indeed predict perceived interaction quality and positive outgroup attitudes.
 
@@
 \begin{enumerate}
-    \item 
-    \item
-    \item
+    \item Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
+    \item Based on Allport’s optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+    \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+    \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict outgroup attitudes at least as well as Allport’s conditions.
 \end{enumerate}

### 2021-11-23 manuscript.tex
discussion results

@@
 \usepackage{pdfpages}
+\usepackage{enumitem}
 
@@
 \section{The Present Research}
+The aim of this paper is essentially threefold.
+First, our study is among the first to test the fundamental tenets intergroup contact and Allport's conditions in real-life extensive longitudinal data.
+Second, we test whether the fulfillment situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
+And third, we test the role of interaction quality in  the relationship of psychological need fulfillment and outgroup attitudes.
+Based on this we formulated three main hypotheses:
+\begin{enumerate}[label=H\arabic*:]
+    \item Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes across extensive longitudinal data.
+    \item Based on Allport’s optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
+    \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
+\end{enumerate}
+Beyond these main hypotheses we have formulated several sub-hypotheses that form the basis for our analysis plan (these sub-hypotheses also include several robustness checks and are available in Appendix \ref{app:AppendixHypotheses}).
+Given the more complex data structure of the extensive longitudinal data, we opted to test our hypotheses using a multilevel regression model, where the measurement occasions (level 1) were nested within the participants (level 2).
+Given that more complex dynamic modeling procedures are not necessary to test these more basic hypotheses, we will focus on the contemporaneous effect of the data (e.g., need fulfillment during the intergroup interaction predicts outgroup attitudes following the interaction).
+Such an approach is also tolerant to missing data and uneven case numbers within participants.
 
-\begin{itemize}
-    \item aims
-    \item shortened hypotheses
-    \item analysis strategy
-    \item assumptions, materials, preregistration
-\end{itemize}
-
-Based on this we formulated four main hypotheses:
-\begin{enumerate}
-    \item Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
-    \item Based on Allport’s optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
-    \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
-    \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict outgroup attitudes at least as well as Allport’s conditions.
-\end{enumerate}
+To test our main hypotheses, we collected three independent sets of extensive longitudinal data (Studies 1–3).
+The full surveys are available in Supplementary Materials A as well as in our open science repository (including a complete codebook, see OSF-REFERENCE).
+Our most comprehensive study (Study 3), was fully preregistered and is also available via our open science repository \citep[][]{Kreienkamp2021f}.
+The full annotated analysis is available in Supplementary Material B.
+As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text (e.g., random slopes model; for the full modeling process see Supplementary Material B).
 
@@
 \section{Discussion}
+In this paper we set out to (1) test the basic predictions of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data, (2) we proposed that the fulfillment situational psychological needs meaningfully predicts positive outgroup attitudes, and (3) that the fulfillment of psychological needs (and Allport's conditions) have their effect (partially) through perceived interaction quality.
+
+When considering the results of the three studies jointly we find that for the basic intergroup contact hypothesis we find mixed results.
+The aggregated number of interactions with the outgroup across all measurements only had a significant effect on average outgroup attitudes in one of the three studies and in that study there was no significant effect of average interaction quality on outgroup attitudes (which was significant for the other two studies).
+This meant that only for our smallest study did we find the expected interaction between interaction frequency and interaction quality when looking at the aggregated data across all measurements.
+However, once we considered the effect of having an interaction with an outgroup member (vs.
+not having an outgroup interaction) within the participants, we find that intergroup contact is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account).
+This finding is surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
+Even though this inconsistency with past research might be a data artefact (e.g., because most people reported more substantially mode measurements during which they did not have an outgroup interaction), the absence of this aggregate effect could underline the fact that cross-sectional retrospective data might suffer from a recall bias (e.g., where times with no outgroup interactions are undervalued by participants during retrospective evaluations).
+However, coming to the rescue of the basic intergroup contact tenets are the results from the within-person data.
+Across all studies, we find that after intergroup contacts participants have substantially more positive outgroup attitudes then at times when they did not have an outgroup interaction.
+In summary, we thus find that when we aggregate interaction frequencies and interaction quality from our intensive longitudinal data we find inconsistent results from the past literature but within participants intergroup contacts are significantly related with positive outgroup attitudes.
+
+Using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
+And when we consider interaction quality and Allport's conditions jointly, we find further evidence that part of the benefits of Allport's conditions are due to the case that such interactions are also perceived as more positive.
+We thus find first evidence that Allport's conditions of optimal contact are also relevant to the daily interactions recent migrants have in their interactions with majority group members.
+
+Finally, when looking at the results for our main proposal about the importance of situational key needs we find highly consistent positive results across all three studies.
+We find that in all three extensive longitudinal datasets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
+We find that in all three studies the effect of core needs on outgroup attitudes is either fully or partially through quality perceptions, and we find that this is the case even when taking other fundamental psychological needs or Allport's conditions into account.
+In fact we find that our core situational needs measure predicts outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
+In most cases the core need even takes over the variances previously explained by the self-determination theory needs.
+We thus find strong evidence that within everyday life interactions of recent migrants with majority group members, the perception that one's interaction specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
+As such the data offers a first test of the motivational basis of intergroup contact.
+
+\subsection{Limitations}
+\begin{enumerate}
+    \item minority perspective only
+    \item lagged effects left for future studies (potentially not relevant, time scale)
+    \item ESM: real-life data comes at the expense of having short/single item operationalizations
+\end{enumerate}
+
+\subsection{Implications}
+to be discussed, potentially:
+\begin{enumerate}
+    \item feasible to collect large amount of data on intergroup contact using ESM method
+    \item role of motivation in intergroup contact promising (potential for interventions, e.g., most immediate to the data: settlement practices). 
+    \item potential to identify context specific needs
+\end{enumerate}
+
+\subsection{Conclusion paragraph (not a real heading)}
+to be written after co-author meeting.
 
@@
 \section{Appendix A: Hypotheses}
-\label{app:AppendixA}
+\label{app:AppendixHypotheses}
 

### 2021-11-23 Methods-and-Results.Rmd
unnecessary comments removed
wording issues fix

@@
 
-\faQuestionCircle\ Unsure about order of study one and two.
-Currently chronological.
-But could also be: (1) main model works in larger student sample, (2) works in economic migrant sample, (3) test full thing in medical sample.
-
 \section{Study 1}
@@
 We find that in the highest multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCore, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreCI, varName = "keymotive_fulfillemt_1_cwc")`) and also predicted higher perceived interaction quality (random intercept model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Qlt$lmeInterceptCore, lmerCI = mdlWorkerOut$Qlt$lmerInterceptCoreCI, varName = "keymotive_fulfillemt_1_cwc")`).
-However, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`).
+Moreover, when we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`).
 We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
@@
 However, we find that this effect does not depend on the average perceived interaction quality.
-However, this might be due to the aggregation process and the following analyses will focus in on the role of the perceived interaction quality during an outgroup interaction.
+This unexpected results, might be due to the aggregation process and the following analyses will focus in on the role of the perceived interaction quality during an outgroup interaction.
 
@@
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`).
-However, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`).
+Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`).
 These results are consistent with the results in study one and we thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
@@
 When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, different from the first study, in this larger study relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) predicted positive outgroup attitudes.
+However, different from the first study, in this larger sample relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes.
 For full results see Online Supplementary Information B.
@@
 We find that in the multilevel models, the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
-However, if we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`).
+Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`).
 These results indicate that in this dataset the the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
@@
 We find that in the multilevel models, the fulfillment of core need fulfillment during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
-However, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`).
+Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`).
 These results indicate that in this dataset the the fulfillment of core situational needs had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
@@
 When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, similar to the previous study, in this large sample relatedness (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each predicted positive outgroup attitudes independently.
+However, similar to the previous study, in this large sample relatedness (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each also predicted positive outgroup attitudes independently.
 However, the regression coefficient is three times as large for the core need fulfillment (with all scaling being equal).

### 2021-11-23 Methods-and-Results.tex
unnecessary comments removed
wording issues fix

@@
-\faQuestionCircle~Unsure about order of study one and two. Currently
-chronological. But could also be: (1) main model works in larger student
-sample, (2) works in economic migrant sample, (3) test full thing in
-medical sample.
-
 \section{Study 1}
@@
 intercept model; \textit{b} = 0.42, \textit{t}(365) = 8.07, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}0.32, 0.52{]}). However, if we
+\textless{} .001, \textit{95\%CI}{[}0.32, 0.52{]}). Moreover, when we
 consider the influences of core need fulfillment and interaction quality
@@
 this effect does not depend on the average perceived interaction
-quality. However, this might be due to the aggregation process and the
-following analyses will focus in on the role of the perceived
-interaction quality during an outgroup interaction.
+quality. This unexpected results, might be due to the aggregation
+process and the following analyses will focus in on the role of the
+perceived interaction quality during an outgroup interaction.
 
@@
 \textit{b} = 0.40, \textit{t}(826) = 6.46, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.28, 0.52{]}). However, if we consider the influences
-of core need fulfillment and interaction quality on outgroup attitudes
-jointly, we find that virtually all variance is explained by perceived
-interaction quality (random slopes mode; \textit{b} = 0.17,
+\textit{95\%CI}{[}0.28, 0.52{]}). Additionally, if we consider the
+influences of core need fulfillment and interaction quality on outgroup
+attitudes jointly, we find that virtually all variance is explained by
+perceived interaction quality (random slopes mode; \textit{b} = 0.17,
 \textit{t}(825) = 5.56, \textit{p} \textless{} .001,
@@
 explained variance of all of the three fundamental needs. However,
-different from the first study, in this larger study relatedness
+different from the first study, in this larger sample relatedness
 (\textit{b} = 0.07, \textit{t}(823) = 4.26, \textit{p} \textless{} .001,
@@
 \textit{t}(823) = 0.93, \textit{p} = 0.353, \textit{95\%CI}{[}-0.02,
-0.08{]}) predicted positive outgroup attitudes. For full results see
-Online Supplementary Information B.
+0.08{]}) also predicted positive outgroup attitudes. For full results
+see Online Supplementary Information B.
 
@@
 \textit{b} = 0.65, \textit{t}(1605) = 11.82, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}0.54, 0.76{]}). However, if we consider the
+.001, \textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we consider the
 influences of Allport's Conditions and interaction quality on outgroup
@@
 \textit{b} = 0.43, \textit{t}(1605) = 8.35, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.33, 0.54{]}). However, if we consider the influences
-of core need fulfillment and interaction quality on outgroup attitudes
-jointly, we find that perceived interaction quality is a substantially
-stronger predictor (random slopes mode; \textit{b} = 0.17,
+\textit{95\%CI}{[}0.33, 0.54{]}). Additionally, once we consider the
+influences of core need fulfillment and interaction quality on outgroup
+attitudes jointly, we find that perceived interaction quality is a
+substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
 \textit{t}(1600) = 6.86, \textit{p} \textless{} .001,
@@
 0.10{]}) and autonomy (\textit{b} = 0.04, \textit{t}(1598) = 2.12,
-\textit{p} = 0.034, \textit{95\%CI}{[}-0.01, 0.08{]}) each predicted
-positive outgroup attitudes independently. However, the regression
-coefficient is three times as large for the core need fulfillment (with
-all scaling being equal). For full results see Online Supplementary
-Information B.
+\textit{p} = 0.034, \textit{95\%CI}{[}-0.01, 0.08{]}) each also
+predicted positive outgroup attitudes independently. However, the
+regression coefficient is three times as large for the core need
+fulfillment (with all scaling being equal). For full results see Online
+Supplementary Information B.

### 2021-11-24 manuscript.tex
paragraph comments added

@@
 Based on Allport's (\citeyear{Allport1954b}) contact hypothesis, a plethora of studies and interventions have worked on bringing different social groups together \citep[e.g.,][]{AlRamiah2012a, Reimer2021}.
-% Yet, despite ...
 
+% Problem
 In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group \citep[e.g.,][]{Hewstone1996, Pettigrew1998}.
@@
 
-In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and in extension positive outgroup attitudes.
-That is to say, that if someone seeks/wishes to ...
-.
+% Aim / Solution
+In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and positive outgroup attitudes.
+That is to say, that if a person, for example, seeks to feel accepted by their interaction partner and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
 Additionally, such needs might even explain the effectiveness of Allport's optimal contact conditions, if these conditions constitute common psychological needs of the interacting individual.
-To test this we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with host majority group members.
+To test this we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with majority group members.
 
@@
 
+% Intergroup contact = Robust and strong effect (from meta-analyses) → much theoretical interest
 As one of the most researched and practically implemented theories of social psychology, intergroup contact has received a vast amount of empirical, and theoretical attention \citep[][]{Dovidio2017}.
@@
 
+% what makes a 'positive contact' has received much theoretical interest. (1) conditions of positive contact, then (2) contact quality. But why is it perceived as positive? 
 Interestingly, one concept that has arguably remained at the center of theoretical debates throughout the decades has been the role of 'positive' contact.
@@
 
+% many moderators and mediators but none of these necessarily leads to higher interaction quality. Solution: look at need fulfillment (motivational literature)
 Thus although a sizeable number of moderators and mediators of intergroup contact have been proposed, their effects might be undermined if they do not result in a 'positive' contact.
@@
 \section{Psychological Needs in Intergroup Relations}
+% Important in broader field: needs have been found to be important in broader intergroup relations and interpersonal contact literature.
 Although considerations of psychological needs and motivations have remained markedly absent within the intergroup contact literature, the concepts are in no way foreign to the general topic of intergroup relations.
@@
 
+% Promising for intergroup contact: Asked for in intergroup contact reviews and first research looked at social change
 And even within the field of intergroup contact the idea of need fulfillment as a psychological mechanism is not entirely novel.
@@
 
-One reason why motivational considerations might have remained absent from the intergroup contact literature is that people might enter into a contact with a plethora of individual needs or goals that might be relevant to them in that particular situation.
+% Difficult to test general mechanism: Either consider too many needs (situationally relevant but not feasible) or too few (feasible but not transferable).
+Solution: ask for main need + rating of main need
+One reason why motivational considerations might have remained absent from the intergroup contact literature is that there is an overwhelming number of individual needs or goals that might be relevant to a person during an intergroup interaction.
 Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad range of fundamental psychological needs.
@@
 \section{Real-Life Process Data}
+% call for longitudinal and real-life data b/c: lab process test vs. real-life retrospective. + less recall bias + much data from few PPTs
 Over the past two decades several reviewers of the field have advocated that to truly understand intergroup contacts, there is a need for studies that collect longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
@@
 At the same time, such longitudinal data would also be situated within the real-life experiences of the participant.
-Additionally, such experience-sampling data can be close to the intergroup interactions would largely mitigate recall biases.
+Additionally, such experience-sampling data can be close to the intergroup interactions and would, thus, largely mitigate recall biases.
 Moreover, intensive longitudinal data often allows to capture large amounts of high-quality data with relatively few participants.
 
+% Used to be difficult but technological and methodological developments (e.g., FormR + HLM) → collect large body of intensive longitudinal data
 In the past such data collections were often unfeasible because they were either physically impractical or too expensive.
@@
 The aim of this paper is essentially threefold.
-First, our study is among the first to test the fundamental tenets intergroup contact and Allport's conditions in real-life extensive longitudinal data.
+First, our study is among the first to test the fundamental tenets of intergroup contact and Allport's conditions in real-life extensive longitudinal data.
 Second, we test whether the fulfillment situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
@@
 The full surveys are available in Supplementary Materials A as well as in our open science repository (including a complete codebook, see OSF-REFERENCE).
-Our most comprehensive study (Study 3), was fully preregistered and is also available via our open science repository \citep[][]{Kreienkamp2021f}.
-The full annotated analysis is available in Supplementary Material B.
+Our most comprehensive study (Study 3), was fully preregistered, which is also available via our open science repository \citep[][]{Kreienkamp2021f}.
+The full annotated analyses are available in Supplementary Material B.
 As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text (e.g., random slopes model; for the full modeling process see Supplementary Material B).
@@
 \section{Discussion}
+% aims re-iterated
 In this paper we set out to (1) test the basic predictions of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data, (2) we proposed that the fulfillment situational psychological needs meaningfully predicts positive outgroup attitudes, and (3) that the fulfillment of psychological needs (and Allport's conditions) have their effect (partially) through perceived interaction quality.
 
-When considering the results of the three studies jointly we find that for the basic intergroup contact hypothesis we find mixed results.
-The aggregated number of interactions with the outgroup across all measurements only had a significant effect on average outgroup attitudes in one of the three studies and in that study there was no significant effect of average interaction quality on outgroup attitudes (which was significant for the other two studies).
+% Contact hypothesis in ESM data [inconsistent in aggregate but consistent in ML analysis]
+When considering the results of the three studies jointly, we find mixed results for the basic intergroup contact hypothesis.
+The aggregated number of outgroup interactions across all measurements only had a significant effect on average outgroup attitudes in one of the three studies and in that study there was no significant effect of average interaction quality on outgroup attitudes (which was significant for the other two studies).
 This meant that only for our smallest study did we find the expected interaction between interaction frequency and interaction quality when looking at the aggregated data across all measurements.
@@
 not having an outgroup interaction) within the participants, we find that intergroup contact is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account).
-This finding is surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
-Even though this inconsistency with past research might be a data artefact (e.g., because most people reported more substantially mode measurements during which they did not have an outgroup interaction), the absence of this aggregate effect could underline the fact that cross-sectional retrospective data might suffer from a recall bias (e.g., where times with no outgroup interactions are undervalued by participants during retrospective evaluations).
-However, coming to the rescue of the basic intergroup contact tenets are the results from the within-person data.
-Across all studies, we find that after intergroup contacts participants have substantially more positive outgroup attitudes then at times when they did not have an outgroup interaction.
+While this later results is in line with our expectations, the earlier aggregate findings are surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
+Even though this inconsistency with past research might be a data artefact (e.g., because most people reported more substantially mode measurements during which they did not have an outgroup interaction), the absence of this aggregate effect could underline the fact that cross-sectional retrospective data might suffer from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
 In summary, we thus find that when we aggregate interaction frequencies and interaction quality from our intensive longitudinal data we find inconsistent results from the past literature but within participants intergroup contacts are significantly related with positive outgroup attitudes.
 
+% Allport's conditions in ESM data [consistent predictor and partially through quality]
 Using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
@@
 
-Finally, when looking at the results for our main proposal about the importance of situational key needs we find highly consistent positive results across all three studies.
+% Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
+Finally, when looking at the results for our main proposal about the importance of situational key needs, we find highly consistent positive results across all three studies.
 We find that in all three extensive longitudinal datasets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
-We find that in all three studies the effect of core needs on outgroup attitudes is either fully or partially through quality perceptions, and we find that this is the case even when taking other fundamental psychological needs or Allport's conditions into account.
-In fact we find that our core situational needs measure predicts outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
-In most cases the core need even takes over the variances previously explained by the self-determination theory needs.
+We find that in all three studies the effect of core need fulfillment on outgroup attitudes is either fully or partially through its effect on quality perceptions, and we find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
+In fact we find that our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
+In most cases the core need even took over the variances previously explained by the self-determination theory needs.
 We thus find strong evidence that within everyday life interactions of recent migrants with majority group members, the perception that one's interaction specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
@@
 \subsection{Limitations}
+to be discussed, potentially:
 \begin{enumerate}

### 2021-12-09 Methods-and-Results.Rmd
Updates from Overleaf

@@
       "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person coorelations;",
+      "Lower triangle: Within-person correlations;",
       "*** p < .001, ** p < .01,  * p < .05"
@@
 After the final day of daily diary measurements, participants were invited to fill in a longer post measurement survey that mirrored the pre-measurement.
-All key variables in for this study were part of the short daily diary surveys.
+All key variables for this study were part of the short daily diary surveys.
 
@@
 For the core situational need, we asked participants in an open ended text field: “\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}”.
-Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / you] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).
+Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).
 
@@
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance.
-This is unusual because this might indicate the the effect is very consistent across participants.
-However, this might also be the case due to a small number of participants, or other measurement issues.}.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+This is unusual and might indicate the the effect is very consistent across participants.
+However, the small number of participants, or other measurement issues provide an alternative explanation}.
 Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants, keeping in mind that the between-participant analyses in the aggregated form are based in a small sample size.
@@
 This should, in turn, be due to a higher perceived interaction quality.
-We will this sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+We will sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
 
@@
 Moreover, when we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`).
-We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
+We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes; this effect likely being explained by its effect through perceived interaction quality.
 
@@
 
-To build further confidence in our results, we assessed two additional models that might offer alternative explanations of the effects we find.
-First, to make certain that the effect of core need fulfillment is specific to the interaction we compare the the effect to fulfillment of the situation core need when no outgroup interaction took place.
-Here we go back to the full dataset and assess the generalized situational core need fulfillment (either during an interaction or about the daytime in general) and whether the effect differed during daily diary measurements with and without outgroup contacts.
-We find that there is no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteractionYes")`).
+To build further confidence in our results, we assessed two additional models that might offer alternative explanations.
+First, to ensure that the effect of core need fulfillment is specific to an actual interaction, we compared it core need fulfillement in situations without an interaction.
+For this, we analzed the generalized situational core need fulfillment (either during an interaction or about the daytime in general) and tested whether the effect differed during daily diary measurements with and without outgroup contacts.
+We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteractionYes")`).
 Together with a significant main effect of having an outgroup contact, this indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
@@
 
-In a final step we check whether during the interaction the core situational need is a meaningful predictor even when taking other fundamental psychological needs into account.
+In a final step, we controlled for other fundamental psychological needs during the interaction.
 We focus on the three commonly considered self determination needs: competence, autonomy, and relatedness.
@@
 We find that next to relatedness (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "relatedness_1_cwc")`), the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "keymotive_fulfillemt_1_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs and competence and autonomy needs are non-significant (all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
+When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all three fundamental needs (competence and autonomy needs turning non-significant; all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
 For full results see Online Supplementary Information B.
@@
 
-The aim of our study is similar to that of the first study, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
-However, in this second study we collected a substantially larger intensive longitudinal survey study with recently arrived international students in the Netherlands.
+The aim of Study 2 is similar to Study 1, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
+However, in this second study we collected a substantially larger sample of international students who recently arrived in the Netherlands and also improved the study design (e.g.
+pop up explanations described later).
 The survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations as these students will likely interact with the Dutch majority outgroup on a daily basis.
@@
 
-\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(studentSampleInfo)` international students using a local participant pool and specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
+\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(studentSampleInfo)` international students using a local participant pool.
+We specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
 Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
@@
 The response rates were approximately equal during mornings (\textit{n} = `r sum(studentSampleInfo$morningN)`) and afternoons (\textit{n} = `r sum(studentSampleInfo$afternoonN)`).
-All key variables in for this study were part of the short daily diary surveys.
+All key variables for this study were part of the short daily diary surveys.
 
@@
 
-\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to study one..
-
-\paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup was again measured using the feeling thermometer, as in study one.
+\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to study one.
+
+\paragraph{Outgroup Attitudes}As in Study 1, attitudes towards the Dutch majority outgroup were again measured using the feeling thermometer.
 All survey details are also available in Online Supplemental Materials A and B.
@@
 However, we find no significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
+Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
 Given the missing aggregate relationship between average interaction quality and outgroup attitudes, we find no significant effect of average perceived contact quality.
-Nor do we find that in this sample the impact of the number of interactions is moderated by the average contact quality.
+We also do not find that in this sample the impact of the number of interactions is moderated by the average contact quality.
 This is not entirely consistent with the first study, where average contact quality did have a meaningful effect on outgroup attitudes.
@@
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
 Thus, in our second dataset we find mixed results, outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
@@
 When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, different from the first study, in this larger sample relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes.
+However, different from the first study, relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes in this larger sample.
 For full results see Online Supplementary Information B.

### 2021-12-09 manuscript.tex
comments before feedback LFB
notes prior to re-write
Updates from Overleaf

@@
 \affil[1]{University of Groningen, Department of Psychology}
-\affil[2]{Author order to be discussed; currently alphabetic by last name.}
+\affil[2]{Author-order to be discussed; currently alphabetic by last name.}
 
@@
 
-% Relevance
+% Relevance v.02: Conflict is a problem, positive contact as solution, but little research on when daily contact is perceived positive
 Conflict between social groups and their individual members remains a prevalent feature of the modern human condition.
-Prejudices, discrimination, and animosities continue to plague societies around the world.
-One of the main ameliorations proposed by social psychologists has been positive intergroup contact.
-Based on Allport's (\citeyear{Allport1954b}) contact hypothesis, a plethora of studies and interventions have worked on bringing different social groups together \citep[e.g.,][]{AlRamiah2012a, Reimer2021}.
+Experiences of prejudices, discrimination, and animosities with other groups continue to plague the everyday lives of many people around the world.
+One of the main ameliorations proposed by social psychologists has been the intergroup contact hypothesis.
+In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
+And even though over the past 70 years, a plethoray of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}, relatively little research has thus far explained when and why people's everyday inter-group interactions are perceived as positive.
 
-% Problem
-In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group \citep[e.g.,][]{Hewstone1996, Pettigrew1998}.
-A key condition for these contact benefits, has been that the interaction is indeed perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact \citep[e.g.,][]{MacInnis2015}.
-It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact \citep[Allport's Optimal Contact conditions,][]{Allport1954b, Pettigrew1969}.
-And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met.
-However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met \citep[][]{Pettigrew2006}.
-It, thus, remains unclear when and why exactly an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects.
+% Problem v.02: theoretical interaction quality central to understanding outcomes, practical many impactful negative interactions in everyday life
+There are however substantial theoretical and practical consequences of these understudied mechanisms of everyday intergroup contact.
+Theoretically, interaction quality or -valence sits at the heart of intergroup contact theory, as it gauges whether the interaction will result to positive intergroup outcomes \citep[][]{Tropp2016, Brown2007}.
+And practically, a longstanding body of literature, has been showing that negative interactions are common in everyday life and often result in a substantial decline of intergroup relations \citep[][]{Barlow2012, Shelton2009}.
+It is thus important that we explore which psychological mechanisms explain when and why intergroup contacts are positive and lead to better intergroup perceptions, especially during everyday intergroup encounters \citep[e.g.,][]{MacInnis2015}.
 
-% Aim / Solution
+% Aim / Solution v.02: look at need fulfillment as mechanism in daily interactions of migrants
 In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and positive outgroup attitudes.
 That is to say, that if a person, for example, seeks to feel accepted by their interaction partner and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
-Additionally, such needs might even explain the effectiveness of Allport's optimal contact conditions, if these conditions constitute common psychological needs of the interacting individual.
-To test this we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with majority group members.
+To test this, we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with majority group members.
 
-\section{Intergroup Contact Mechanisms}
-\faQuestionCircle\ \textit{Not sure whether we need this section.}
+\section{Need Mechanism in Intergroup Contact}
+% Motivational mechanism:
+% interaction quality is important
+% past research has either focused on conditions or cognitive-affective processes
+% neither are necessary or explain why an interaction is positive
 
-\faExclamationCircle\ \textit{This section has become way too complex (i.e., too many arguments to get to our own proposed work).
-I think we ultimately need to introduce the concept of interaction quality and that we don't necessarily know why interactions are perceived as positive, therefore we propose that we can look towards the motivational literature for this.
-The difficulties started for me when I tried to give credit to past theoretical work (which I thought we need to acknowledge in some way).}
-
-% Intergroup contact = Robust and strong effect (from meta-analyses) → much theoretical interest
-As one of the most researched and practically implemented theories of social psychology, intergroup contact has received a vast amount of empirical, and theoretical attention \citep[][]{Dovidio2017}.
-Several meta-analytic reviews have found moderately sized positive effects of intergroup contact \citep[][]{Tropp2005, Pettigrew2006, Davies2011} and later meta-analyses have additionally shown that intergroup contact is also effective outside the lab \citep[][]{Beelmann2014, Lemmer2015}, during online contact \citep[][]{White2020}, as well as during several more indirect forms of contact \citep[][]{Miles2014, Zhou2019, Harwood2021}.
-With such a persistent and meaningful effect, researchers have long proposed theoretical models to understand these intergroup contact effects.
-
-% what makes a 'positive contact' has received much theoretical interest. (1) conditions of positive contact, then (2) contact quality. But why is it perceived as positive? 
-Interestingly, one concept that has arguably remained at the center of theoretical debates throughout the decades has been the role of 'positive' contact.
-In his now famous chapter on 'the effects of contact', Gordon Allport (\citeyear{Allport1954b}) set out to summarize under what circumstances an interaction between groups tends to be positive, leading to favourable attitudes and reduced prejudice.
-In the years that followed, several additional conditions were proposed under which a positive intergroup contact would occur \citep[for a critical review see][]{Pettigrew1986}.
-As a counter-movement to this rather restrictive approach, with the beginning of the 21\textsuperscript{st} century attention had shifted towards investigating the psychological mechanisms of intergroup contact \citep[e.g.
+Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
+It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for such positive contact effects \citep[Allport's Optimal Contact conditions;][]{Allport1954b, Pettigrew1969}.
+However, a major meta-analysis of these contact conditions showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met \citep[][]{Pettigrew2006}.
+It, thus, remains unclear when and why exactly an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects\footnote{It should be noted here that following Allport's original conditions, several additional conditions of optimal contact were proposed \citep[for a critical discussion see][]{Pettigrew1986}.
+Similarly, since the early 21\textsuperscript{st} century many psychological processes during intergroup contact were examined \citep[e.g.
 see,][]{Paolini2021}.
-With this shift in focus, the idea of 'positive contact' has seemingly seen a renaissance, where the adjective 'positive' is now not merely an evaluation of the outcome, but rather a feature of the interaction itself.
-As such, recent work has focused on the role of 'perceived interaction quality' \citep[e.g.,][]{Brown2007, Voci2003} or 'interaction valence' \citep[e.g.,][]{Tropp2016, Barlow2012}, to show that only if an interaction is perceived as positive will it lead to more favourable intergroup relations.
-And inversely interactions that are perceived as negative have the strong propensity to harm outgroup attitudes.
-However, relatively little research has investigated why interactions are perceived as positive.
-
-% many moderators and mediators but none of these necessarily leads to higher interaction quality. Solution: look at need fulfillment (motivational literature)
-Thus although a sizeable number of moderators and mediators of intergroup contact have been proposed, their effects might be undermined if they do not result in a 'positive' contact.
-As an example, important moderators and mediators that have been identified are different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}.
-However, there is a discernible disconnect between these mechanisms and perceptions that an interaction is positive.
-That is to say that, just because someone learns something new about the other group, or reduces their threat perceptions does not mean that such an interaction is perceived as positive.
-Or inversely, an interaction can, for example, be very intimate but perceived as negative.
-If that were the case, there is a reasonable chance that such an interaction might not translate into improved outgroup attitudes \citep[e.g.,][]{Barlow2012}.
+Among others, researchers have for example explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}.
+However, all these advances share the underlying criticism that they are not geared towards understanding when and why an interaction is perceived as positive.}.
 We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
 
-ALTERNATIVE: One potential remedy might come from looking to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
+% ALTERNATIVE: SHORTER BUT NOT FOCUSED ON ALLPORT'S CONDITIONS (WHICH WE TEST LATER)
+% Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
+Past research has either focused on conditions under which interactions tend to have favorable effects \citep[e.g., Allport's optimal conditions;][]{Allport1954b, Pettigrew1969} or has investigated cognitive-affective processes during contact \citep[e.g., group salience, intimacy, attachment, or intergroup anxiety;][]{Brown2005, Marinucci2021, Tropp2021, Paolini2004}.
+However, neither the contact conditions nor the cognitive-affective processes are particularly well equipped to explain when and why an interaction will be perceived as positive.
+We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
 
-\section{Psychological Needs in Intergroup Relations}
 % Important in broader field: needs have been found to be important in broader intergroup relations and interpersonal contact literature.
-Although considerations of psychological needs and motivations have remained markedly absent within the intergroup contact literature, the concepts are in no way foreign to the general topic of intergroup relations.
-On the most general level, research on intergroup conflicts has, for example, shown that addressing the group-specific needs predicts willingness to reconcile with the other group \citep[][]{Shnabel2008}.
+Although considerations of psychological needs and motivations have remained markedly absent within the intergroup contact literature, the concepts are in no way foreign to the broader topic of intergroup relations.
+Psychological needs have for example found fruitful utility in reconciliation research \citep[][]{Shnabel2008}, the study of minority's discrimination experiences \citep[][]{Celebi2017}, and in non-intergroup interactions \citep[][]{Downie2008}.
+% On the most general level, research on intergroup conflicts has, for example, shown that addressing the group-specific needs predicts willingness to reconcile with the other group \citep[][]{Shnabel2008}.
 For the case of refugee migrants in their relationship with a majority group, a recent study found that identity needs will buffer against discrimination experiences and will protect personal health \citep[][]{Celebi2017}.
 Additionally, within the field of interpersonal relations, we find first evidence that the fulfillment of fundamental psychological needs might predict perceived interaction quality in non-intergroup interactions \citep[][]{Downie2008}.
-
 % Promising for intergroup contact: Asked for in intergroup contact reviews and first research looked at social change
@@
 Solution: ask for main need + rating of main need
+% MAYBE MOVE THIS TO 'The Present Research Section'
 One reason why motivational considerations might have remained absent from the intergroup contact literature is that there is an overwhelming number of individual needs or goals that might be relevant to a person during an intergroup interaction.
@@
 In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., situation core need) and with reference to their own response the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment).
-Such an adaptive approach allows us to test the fundamental psychological mechanism of whether situational psychological needs indeed predict perceived interaction quality and positive outgroup attitudes.
+Such an adaptive approach would allow us to test the fundamental psychological mechanism of whether situational psychological needs indeed predict perceived interaction quality and positive outgroup attitudes.
 
 \section{Real-Life Process Data}
-% call for longitudinal and real-life data b/c: lab process test vs. real-life retrospective. + less recall bias + much data from few PPTs
-Over the past two decades several reviewers of the field have advocated that to truly understand intergroup contacts, there is a need for studies that collect longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
-The reasoning behind these calls for longitudinal real-life data has been manifold.
-Among the most pressing issues is concern that past investigations of intergroup contact have either focused on the dynamics of individual interactions but within artificial laboratory settings or have collected data situated within the lived experiences but used retrospective self-report data that asked about past interactions in general.
-The collection of data over time would, thus, allow researchers to follow the development of intergroup relations as they develop across multiple interactions.
-At the same time, such longitudinal data would also be situated within the real-life experiences of the participant.
-Additionally, such experience-sampling data can be close to the intergroup interactions and would, thus, largely mitigate recall biases.
-Moreover, intensive longitudinal data often allows to capture large amounts of high-quality data with relatively few participants.
+While we have argued that a need fulfillment mechanism is relevant to intergroup contact generally, its flexible and broad applicability might be ideally suited to address the pressing issue of understanding natural intergroup contacts outside the lab.
+Investigations of such 'real-life interactions' often suffer from the difficulty that past intergroup contact research has either focused on the mechanisms of individual interactions in artificial lab studies or has focused on longer-term recall self-reports of natural interactions \citep[e.g.,][]{Pettigrew2006}.
+Even with extended intervention studies, the most fine-grained data available is usually limited to pre-post-control designs.
+Such empirical practices stand, however, in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the core idea of the contact hypothesis, which was focused on the daily interactions of people \citep[see][]{Allport1954b}.
+As a result, prominent figures within the intergroup contact field have called for studies that collect longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
+Such data would be able to capture real-life interactions that include interaction-specific mechanism information close the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
+Moreover, because data is nested within participants, experience-sampling data often allows to capture large amounts of high-quality data with relatively few participants.}.
 
 % Used to be difficult but technological and methodological developments (e.g., FormR + HLM) → collect large body of intensive longitudinal data
-In the past such data collections were often unfeasible because they were either physically impractical or too expensive.
+In the past, such data collections were often unfeasible because they were either physically impractical or too expensive.
 However, recent technological developments allow us to easily collect experience sampling data on mobile devices \citep[e.g.,][]{Keil2020} or using web-based applications \citep[e.g.,][]{Arslan2020}.
@@
 The full surveys are available in Supplementary Materials A as well as in our open science repository (including a complete codebook, see OSF-REFERENCE).
-Our most comprehensive study (Study 3), was fully preregistered, which is also available via our open science repository \citep[][]{Kreienkamp2021f}.
-The full annotated analyses are available in Supplementary Material B.
-As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text (e.g., random slopes model; for the full modeling process see Supplementary Material B).
+Our most comprehensive study (Study 3) was fully preregistered  \citep[available at][]{Kreienkamp2021f}.
+The fully annotated analyses are available in Supplementary Material B.
+As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text (for the full modeling process see Supplementary Material B).
 
@@
 % Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results for our main proposal about the importance of situational key needs, we find highly consistent positive results across all three studies.
+Finally, when looking at the results for our main proposal regarding the importance of situational key needs, we find highly consistent positive results across all three studies.
 We find that in all three extensive longitudinal datasets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
@@
 \begin{enumerate}
+    \item migrants are not refugees (generalizability potentially even more relevant?)
     \item minority perspective only
@@
 \begin{enumerate}
-    \item feasible to collect large amount of data on intergroup contact using ESM method
+    \item feasible to collect large amount of data on intergroup contact using ESM method (do we have a formR ref in there?; set up is feasible but not the easiest; maybe even advertise the reusability of the formR survey?)
     \item role of motivation in intergroup contact promising (potential for interventions, e.g., most immediate to the data: settlement practices). 

### 2021-12-12 Tables/workerOutVarDescr.tex
z test
methods and results re-run
run but not rendered

@@
 
-\caption{\label{tab:workerOutVarDescr}Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
+\caption{Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
 \centering
+\resizebox{\linewidth}{!}{
 \begin{tabular}[t]{llccccc}
@@
 \multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
+\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
 \multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
-\end{tabular}
+\end{tabular}}
 \end{minipage}

### 2021-12-13 Methods-and-Results.Rmd
coef names consistent

@@
   "lubridate",
-  "misty"
+  "misty",
+  "sjPlot",
+  "sjmisc",
+  "sjmisc"
 )
@@
 source("./scripts/functions/MlCorMat.R")
+source("./scripts/functions/MlTbl.R")
 
@@
 
+```{r intergroupGeneralTbl, include=FALSE}
+# Table of intergroup contact in ESM data:
+# lm
+#    #Contact
+#     AvQual
+#     #Contact*AvQual
+# lme
+#     OutgroupInteraction
+#     NonOutgroupInteraction
+
+```
+
+```{r intergroupNeedsTbl, include=FALSE}
+# Table of core need and Allports Conditions (potentially two tables — e.g., needs + allport)
+# all lmer models :-)
+# make different options
+
+# collect relevant models
+# Study 1:
+# Rename variables for consistency
+tblDtS1Needs <- dtWorkerSupp$workerOutWithinBetween %>%
+  select(
+    Attitude = thermometerDutch_1,
+    AttitudeZ = thermometerDutch_1_zwc,
+    CoreNeed = keymotive_fulfillemt_1_cwc,
+    CoreNeedZ = keymotive_fulfillemt_1_zwc,
+    QualityRaw = quality_overall_1,
+    Quality = quality_overall_1_cwc,
+    QualityZ = quality_overall_1_zwc,
+    PID = PID
+  )
+# Quality ~ CoreNeed
+tblLmerS1QltInterceptCore <- lmer(
+  QualityRaw ~ CoreNeed + (1 | PID),
+  data = tblDtS1Needs
+)
+tblLmerS1QltInterceptCoreZ <- lmer(
+  QualityZ ~ CoreNeedZ + (1 | PID),
+  data = tblDtS1Needs
+)
+# Attitude ~ CoreNeed
+tblLmerS1AttSlopeCore <- lmer(
+  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS1Needs
+)
+tblLmerS1AttSlopeCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS1Needs
+)
+# Attitude ~ CoreNeed + Quality
+tblLmerS1AttSlopeCoreQlt <- lmer(
+  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
+  data = tblDtS1Needs
+)
+tblLmerS1AttSlopeCoreQltZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
+  data = tblDtS1Needs
+)
+
+# Study 2:
+# Rename variables for consistency
+tblDtS2Needs <- dtStudentSupp$studentOutWithinBetween %>%
+  select(
+    Attitude = AttitudesDutch,
+    AttitudeZ = AttitudesDutch_zwc,
+    CoreNeed = KeyNeedFullfillment_cwc,
+    CoreNeedZ = KeyNeedFullfillment_zwc,
+    QualityRaw = quality_overall,
+    Quality = quality_overall_cwc,
+    QualityZ = quality_overall_zwc,
+    PID = PID
+  )
+# Quality ~ CoreNeed
+tblLmerS2QltSlopesCore <- lmer(
+  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS2Needs
+)
+tblLmerS2QltSlopesCoreZ <- lmer(
+  QualityZ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS2Needs
+)
+# Attitude ~ CoreNeed
+tblLmerS2AttSlopesCore <- lmer(
+  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS2Needs
+)
+tblLmerS2AttSlopesCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS2Needs
+)
+# Attitude ~ CoreNeed + Quality
+tblLmerS2AttSlopesCoreQlt <- lmer(
+  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
+  data = tblDtS2Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+tblLmerS2AttSlopesCoreQltZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
+  data = tblDtS2Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+
+# Study 3:
+# Rename variables for consistency
+tblDtS3Needs <- dtMedicalSupp$medicalOutWithinBetween %>%
+  select(
+    Attitude = AttitudesDutch,
+    AttitudeZ = AttitudesDutch_zwc,
+    CoreNeed = KeyNeedFulfillment_cwc,
+    CoreNeedZ = KeyNeedFulfillment_zwc,
+    Allport = AllportsCondition_cwc,
+    AllportZ = AllportsCondition_zwc,
+    QualityRaw = qualityOverall,
+    Quality = qualityOverall_cwc,
+    QualityZ = qualityOverall_zwc,
+    PID = PID
+  )
+# Quality ~ CoreNeed
+tblLmerS3QltSlopesCore <- lmer(
+  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3QltSlopesCoreZ <- lmer(
+  QualityZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ CoreNeed
+tblLmerS3AttSlopesCore <- lmer(
+  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3AttSlopesCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ CoreNeed + Quality
+tblLmerS3AttSlopesCoreQlt <- lmer(
+  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+tblLmerS3AttSlopesCoreQltZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+# Quality ~ Allport
+tblLmerS3QltSlopesAllport <- lmer(
+  QualityRaw ~ Allport + (1 + Allport | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3QltSlopesAllportZ <- lmer(
+  QualityZ ~ AllportZ + (1 + AllportZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ Allport
+tblLmerS3AttSlopesAllport <- lmer(
+  Attitude ~ Allport + (1 + Allport | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3AttSlopesAllportZ <- lmer(
+  AttitudeZ ~ AllportZ + (1 + AllportZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ Allport + Quality
+tblLmerS3AttSlopesAllportQlt <- lmer(
+  Attitude ~ Allport + Quality + (1 + Allport + Quality | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+tblLmerS3AttSlopesAllportQltZ <- lmer(
+  AttitudeZ ~ AllportZ + QualityZ + (1 + AllportZ + QualityZ | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+# Attitude ~ Allport + CoreNeed
+tblLmerS3AttSlopesAllportCore <- lmer(
+  Attitude ~ CoreNeed + Allport + (1 + CoreNeed + Allport | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3AttSlopesAllportCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + AllportZ + (1 + CoreNeedZ + AllportZ | PID),
+  data = tblDtS3Needs
+)
+
+tab_model(
+  # Study 1:
+  tblLmerS1QltInterceptCore,
+  tblLmerS1AttSlopeCore,
+  tblLmerS1AttSlopeCoreQlt,
+  # Study 2:
+  tblLmerS2QltSlopesCore,
+  tblLmerS2AttSlopesCore,
+  tblLmerS2AttSlopesCoreQlt,
+  # Study 3:
+  tblLmerS3QltSlopesCore,
+  tblLmerS3AttSlopesCore,
+  tblLmerS3AttSlopesCoreQlt, 
+  tblLmerS3QltSlopesAllport, 
+  tblLmerS3AttSlopesAllport,
+  tblLmerS3AttSlopesAllportQlt,
+  tblLmerS3AttSlopesAllportCore,
+  # Settings
+  show.std = TRUE,
+  show.re.var = TRUE
+)
+
+lmerTblPrep(tblLmerS1QltInterceptCore, tblLmerS1QltInterceptCoreZ)
+
+mdlTblElements <- list(
+  tblLmerS1QltInterceptCore,
+  tblLmerS1AttSlopeCore,
+  tblLmerS1AttSlopeCoreQlt
+  )
+
+mdlPrep <- list()
+
+for (i in 1:length(mdlTblElements)) {
+  mdlPrep[[i]] <- lmerTblPrep(mdlTblElements[[i]])
+}
+
+stargazer::stargazer(
+  tblLmerS1QltInterceptCore,
+  tblLmerS1AttSlopeCore,
+  tblLmerS1AttSlopeCoreQlt, 
+  title="Regression Results", 
+  align=TRUE
+  )
+
+```
+
+```{r robustnessTbl, include=FALSE}
+# Table of all robustness checks (w/ and w/out SDT only)
+
+```
+
 <!-- \begin{figure}[h] -->

### 2021-12-13 scripts/functions/MlTbl.R

@@ -1,0 +1,123 @@
+#obj <- tblLmerS3AttSlopesAllportCore
+#objz <- tblLmerS3AttSlopesAllportCoreZ
+
+lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
+  # Summarize models
+  smry <- summ(obj)
+  smryZ <- summ(objz)
+  
+  # save grouing variable
+  groupNam <- as.character(as.data.frame(smry$gvars)["Group"])
+  
+  # Get standardized coefficients 
+  coefZ <- smryZ$coeftable %>% 
+    as.data.frame %>%
+    tibble::rownames_to_column(., "coef")
+  confZ <- confint(objz, method = "boot") %>% 
+    as.data.frame %>%
+    tibble::rownames_to_column(., "coef")
+  coefZOut <- merge(coefZ, confZ)
+  colnames(coefZOut) <- c("coef", "est", "se", "tval", "df", "p", "lwr", "upr")
+  coefZOut$Beta <- paste0(
+    format(round(coefZOut$est, 2), nsmall = 2),
+    " [", 
+    format(round(coefZOut$lwr, 2), nsmall = 2),
+    ", ",
+    format(round(coefZOut$upr, 2), nsmall = 2),
+    "]"
+  )
+  
+  # Get unstandardized coefficients
+  coef <- smry$coeftable %>% 
+    as.data.frame %>%
+    tibble::rownames_to_column(., "coef")
+  conf <- confint(obj) %>% 
+    as.data.frame %>%
+    tibble::rownames_to_column(., "coef")
+  coefOut <- merge(coef, conf)
+  colnames(coefOut) <- c("coef", "est", "se", "tval", "df", "p", "lwr", "upr")
+  coefOut$B <- paste0(
+    format(round(coefOut$est, 2), nsmall = 2),
+    ifelse(coefOut$p < .0001, "****", 
+           ifelse(coefOut$p < .001, "***", 
+                  ifelse(coefOut$p < .01, "**", 
+                         ifelse(coefOut$p < .05, "*", "")))),
+    " [", 
+    format(round(coefOut$lwr, 2), nsmall = 2),
+    ", ",
+    format(round(coefOut$upr, 2), nsmall = 2),
+    "]"
+  )
+  coefOut <- 
+    merge(
+      coefOut, 
+      coefZOut %>% 
+        select(coef, Beta) %>% 
+        mutate(coef = gsub('Z$', '', coef))
[…]

### 2021-12-14 Methods-and-Results.Rmd
fixes

@@
 
+# OLS 
+# Study 1:
+mdlWorker$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL * AvQuality, data = dtWorkerSupp$workerAvFreQual)
+# Study 2:
+mdlStudent$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtStudentSupp$studentContactFreq)
+# Study 3: 
+mdlMedical$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)
+
 ```
@@
 
-lmerTblPrep(tblLmerS1QltInterceptCore, tblLmerS1QltInterceptCoreZ)
-
 mdlTblElements <- list(
-  tblLmerS1QltInterceptCore,
-  tblLmerS1AttSlopeCore,
-  tblLmerS1AttSlopeCoreQlt
-  )
+  # Study 1:
+  c(tblLmerS1QltInterceptCore, tblLmerS1QltInterceptCoreZ),
+  c(tblLmerS1AttSlopeCore, tblLmerS1AttSlopeCoreZ),
+  c(tblLmerS1AttSlopeCoreQlt, tblLmerS1AttSlopeCoreQltZ),
+  # Study 2:
+  c(tblLmerS2QltSlopesCore, tblLmerS2QltSlopesCoreZ),
+  c(tblLmerS2AttSlopesCore, tblLmerS2AttSlopesCoreZ),
+  c(tblLmerS2AttSlopesCoreQlt, tblLmerS2AttSlopesCoreQltZ),
+  # Study 3:
+  c(tblLmerS3QltSlopesCore, tblLmerS3QltSlopesCoreZ),
+  c(tblLmerS3AttSlopesCore, tblLmerS3AttSlopesCoreZ),
+  c(tblLmerS3AttSlopesCoreQlt, tblLmerS3AttSlopesCoreQlt),
+  c(tblLmerS3QltSlopesAllport, tblLmerS3QltSlopesAllportZ),
+  c(tblLmerS3AttSlopesAllport, tblLmerS3AttSlopesAllportZ),
+  c(tblLmerS3AttSlopesAllportQlt, tblLmerS3AttSlopesAllportQltZ),
+  c(tblLmerS3AttSlopesAllportCore, tblLmerS3AttSlopesAllportCoreZ)
+  )
+
+# lmerTblPrep(mdlTblElements[[1]][[1]], mdlTblElements[[1]][[2]])
 
 mdlPrep <- list()
-
 for (i in 1:length(mdlTblElements)) {
-  mdlPrep[[i]] <- lmerTblPrep(mdlTblElements[[i]])
+  mdlPrep[[i]] <- lmerTblPrep(mdlTblElements[[i]][[1]], mdlTblElements[[i]][[2]])
 }
 
-stargazer::stargazer(
-  tblLmerS1QltInterceptCore,
-  tblLmerS1AttSlopeCore,
-  tblLmerS1AttSlopeCoreQlt, 
-  title="Regression Results", 
-  align=TRUE
-  )
+mdlTbl <- data.frame(
+  coef = c(
+    "(Intercept)",
+    "CoreNeed",
+    "Quality",
+    "Allport",
+    names(mdlPrep[[1]]$random),
+    names(mdlPrep[[1]]$fit)
+  )
+)
+for (i in 1:length(mdlPrep)){
+  mdlTbl <- join(mdlTbl, mdlPrep[[i]]$mdlTbl, by = "coef")
+  #mdlTbl <- merge(mdlTbl, mdlPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", ""))
+}
+
+mdlTblHeader <- data.frame(
+  data = as.character(mdlTbl[mdlTbl$coef == "data",]),
+  formula = as.character(mdlTbl[mdlTbl$coef == "formula",])
+) %>%
+  filter(data != "",
+         data != "data") %>%
+  mutate(study = str_extract(data, "S1|S2|S3")) %>%
+  mutate(study = gsub("S", "Study ", study)) %>%
+  mutate(dv = sub(" ~.*", "", formula)) %>%
+  mutate(dv = gsub("Raw", " ", dv)) %>%
+  mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>%
+  mutate(header = paste(study, pred))
+
+mdlTblHeaderFreq <- rbind.data.frame(rle(mdlTblHeader$header)) %>%
+  mutate(lengths = lengths*2) %>%
+  rename(names = values, span = lengths) %>%
+  rbind(c(1, ""), .) %>%
+  mutate(span = as.numeric(span)) %>%
+  select(names, span)
+
+mdlTblHeader2 <- data.frame(names = mdlTblHeader$dv, span = 2) %>% 
+  mutate(names = as.character(names)) %>%
+  rbind(c("", 1), .) %>%
+  mutate(span = as.numeric(span))
+
+mdlTblHeader2.2 <- rbind.data.frame(rle(mdlTblHeader$dv)) %>%
+  mutate(lengths = lengths*2) %>%
+  rename(names = values, span = lengths) %>%
+  rbind(c(1, ""), .) %>%
+  mutate(span = as.numeric(span)) %>%
+  select(names, span)
+
+mdlTbl$coef <- mapvalues(mdlTbl$coef, 
+          from = c("sigmaSq", "tau00", "tau11", "rho01", "rho00"), 
+          to = c("\\sigma^2", "\\tau_{00}", "\\tau_{11}", "\\rho_{01}", "\\rho_{00}"))
+
+# Still need to pack rows
+mdlTbl %>%
+  select(-one_of(coef2)) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Test",
+    #format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    escape = FALSE,
+    digits = 3
+  ) %>%
+  kable_classic() %>%
+  add_header_above(., mdlTblHeader2) %>%
+  add_header_above(., mdlTblHeaderFreq) %>%
+  pack_rows("Fixed", 1, 4) %>%
+  pack_rows("Random", 5, 9) %>%
+  pack_rows("Fit", 10, 21)
 

### 2021-12-14 scripts/functions/MlTbl.R

@@ -84,14 +84,16 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   # collect random effect statistics
   restat <- list(
     sigmaSq = sigmaSq,
-    tau00 = tau00,
-    tau11 = tau11,
-    rho01 = rho01,
-    rho00 = rho00
+    tau00 = ifelse(length(tau00)>1, paste(tau00, collapse = "\n"), tau00),
+    tau11 = ifelse(length(tau11)>1, paste(tau11, collapse = "\n"), tau11),
+    rho01 = ifelse(length(rho01)>1, paste(rho01, collapse = "\n"), rho01),
+    rho00 = ifelse(length(rho00)>1, paste(rho00, collapse = "\n"), rho00)
   )
   
   
   ## Model fit statistics.
+  data = deparse(as.list(obj@call)$data)
+  formula = Reduce(paste, deparse(as.list(obj@call)$formula))
   ll <- logLik(obj)[1]
   deviance <- deviance(obj)
   AIC <- AIC(obj)
@@ -102,6 +104,8 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   rSqMarg <- as.numeric(performance::r2(obj)$R2_marginal) # Marginal R2
   rSqCond <- as.numeric(performance::r2(obj)$R2_conditional) # Conditional R2
   sumstat <- list(
+    data = data,
+    formula = formula,
     groupId = groupNam,
     logLik = ll, 
     deviance = deviance, 
@@ -114,10 +118,30 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
     R2_conditional = rSqCond
   )
   
+  # Combined Table output
+  mdlCoefTbl <- data.frame(
+    coef = coefOut$coef,
+    B = coefOut$B,
+    Beta = coefOut$Beta
+  )
+  mdlRandomTbl <- t(as.data.frame(restat)) %>%
+    magrittr::set_colnames(c("B")) %>%
+    as.data.frame %>%
+    tibble::rownames_to_column(., "coef") %>%
+    mutate(B = gsub("\\(\\)|\\(\\.\\)", "", B),
+           Beta = "")
+  mdlFitTbl <- t(as.data.frame(sumstat)) %>%
+    magrittr::set_colnames(c("B")) %>%
+    as.data.frame %>%
[…]

### 2021-12-15 Methods-and-Results.Rmd
robust tbl started

@@
         "relatedness_1", 
-        "quality_overall_1"
+        "quality_overall_1", 
+        "OutgroupInteraction",
+        "NonOutgroupInteraction"
       )
@@
 ```{r WorkerFreqAttCor, include=FALSE}
+dtWorkerSupp$workerAvFreQual <-
+  dtWorkerSupp$workerAvFreQual %>%
+  mutate(
+    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
+    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
+    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
+    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
+  )
+
 # correlation panel
@@
 mdlWorker$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL * AvQuality, data = dtWorkerSupp$workerAvFreQual)
+  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtWorkerSupp$workerAvFreQual)
 # summary(lmWorkerAttFreqQualX)
@@
   confint = TRUE,
-  digits = 3,
-  center = TRUE
+  digits = 3
 )
@@
   mdlWorker$lmAttFreqQualX,
-  pred = AvQuality,
-  modx = SumContactNL,
+  pred = AvQuality_c,
+  modx = SumContactNL_c,
   interval = TRUE,
@@
 interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
-                             pred = AvQuality,
-                             modx = SumContactNL,
+                             pred = AvQuality_c,
+                             modx = SumContactNL_c,
                              alpha = .05)
@@
 Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
-And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL:AvQuality","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL:AvQuality","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL:AvQuality","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL:AvQuality") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
+And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
 Looking at a floodlight analysis of the effect, we find that in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker.
@@
         "AttitudesDutch",
-        "quality_overall"
+        "quality_overall",
+        "OutgroupInteraction",
+        "NonOutgroupInteraction"
       )
@@
 table(as.character(medicalSampleInfo$nationality))
+
+# divide into trait and state
+dtMedicalSupp$medicalWithinBetween <- 
+  MlTraitState(
+    data = dtMedical$full,
+    id = "PID",
+    selection =
+      c(
+        "OutgroupInteraction",
+        "NonOutgroupInteraction"
+      )
+  )
 ```
@@
 mdlWorker$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL * AvQuality, data = dtWorkerSupp$workerAvFreQual)
+  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtWorkerSupp$workerAvFreQual)
 # Study 2:
@@
   lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)
+
+tabModelTest <- tab_model(mdlWorker$lmAttFreqQualX,
+                          mdlStudent$lmAttFreqQualX,
+                          mdlMedical$lmAttFreqQualX)
+
+library(XML)
+df <- data.frame(readHTMLTable(htmlParse(tabModelTest))[1])
+# first row as colnames
+colnames(df) <- df[1,]
+# remove the fake first row
+df <- df[-1,]
+
+# lme
+# Study 1: 
+dtWorkerSupp$workerWithinBetween$AttitudesDutch <- dtWorkerSupp$workerWithinBetween$thermometerDutch_1
+mdlWorker$lmerInterceptAttTypeTbl <- lmer(
+    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    data = dtWorkerSupp$workerWithinBetween
+  )
+dtWorkerSupp$workerWithinBetween$AttitudesDutch_zwc <- dtWorkerSupp$workerWithinBetween$thermometerDutch_1
+mdlWorker$lmerInterceptAttTypeTblZ <- lmer(
+    AttitudesDutch_zwc ~ OutgroupInteraction_zwc + NonOutgroupInteraction_zwc + (1 | PID),
+    data = dtWorkerSupp$workerWithinBetween
+  )
+# Study 2:
+mdlStudent$lmerSlopesAttType <- lmer(
+    AttitudesDutch ~
+      OutgroupInteraction + NonOutgroupInteraction +
+      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+    data = dtStudentSupp$studentWithinBetween
+  )
+mdlStudent$lmerSlopesAttTypeZ <- lmer(
+    AttitudesDutch_zwc ~
+      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc +
+      (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
+    data = dtStudentSupp$studentWithinBetween
+  )
+# Study 3:
+mdlMedical$lmerSlopesAttType <- lmer(
+    AttitudesDutch ~
+      OutgroupInteraction + NonOutgroupInteraction +
+      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+    data = dtMedicalSupp$medicalWithinBetween
+  )
+mdlMedical$lmerSlopesAttTypeZ <- lmer(
+    AttitudesDutch_zwc ~
+      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc +
+      (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
+    data = dtMedicalSupp$medicalWithinBetween
+  )
+
+tab_model(
+  mdlWorker$lmerInterceptAttTypeTbl,
+  mdlStudent$lmerSlopesAttType,
+  mdlMedical$lmerSlopesAttType
+)
+
+mdlTblElementsGeneralLmer <- list(
+  c(mdlWorker$lmerInterceptAttTypeTbl, mdlWorker$lmerInterceptAttTypeTblZ),
+  c(mdlStudent$lmerSlopesAttType, mdlStudent$lmerSlopesAttTypeZ),
+  c(mdlMedical$lmerSlopesAttType, mdlMedical$lmerSlopesAttTypeZ)
+  )
+
+mdlPrepGeneral <- list()
+for (i in 1:length(mdlTblElementsGeneralLmer)) {
+  mdlPrepGeneral[[i]] <- lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])
+}
+
+mdlTblGeneral <- data.frame(
+  coef = c(
+    "(Intercept)",
+    "OutgroupInteraction",
+    "NonOutgroupInteraction",
+    names(mdlPrepGeneral[[1]]$random),
+    names(mdlPrepGeneral[[1]]$fit)
+  )
+)
+for (i in 1:length(mdlPrepGeneral)){
+  mdlTblGeneral <- join(mdlTblGeneral, mdlPrepGeneral[[i]]$mdlTbl, by = "coef")
+}
+
+mdlTblHeaderGeneral <- data.frame(
+  data = as.character(mdlTblGeneral[mdlTblGeneral$coef == "data",]),
+  formula = as.character(mdlTblGeneral[mdlTblGeneral$coef == "formula",])
+) %>%
+  filter(data != "",
+         data != "data") %>%
+  mutate(study = str_extract(data, "S1|S2|S3")) %>%
+  mutate(study = gsub("S", "Study ", study)) %>%
+  mutate(dv = sub(" ~.*", "", formula)) %>%
+  mutate(dv = gsub("Raw", " ", dv)) %>%
+  mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>%
+  mutate(header = paste(study, pred))
+
+mdlTblHeaderGeneralFreq <- rbind.data.frame(rle(mdlTblHeaderGeneral$header)) %>%
+  mutate(lengths = lengths*2) %>%
+  rename(names = values, span = lengths) %>%
+  rbind(c(1, ""), .) %>%
+  mutate(span = as.numeric(span)) %>%
+  select(names, span)
+
+mdlTblHeaderGeneral2 <- data.frame(names = mdlTblHeaderGeneral$dv, span = 2) %>% 
+  mutate(names = as.character(names)) %>%
+  rbind(c("", 1), .) %>%
+  mutate(span = as.numeric(span))
+
+mdlTblHeaderGeneral2.2 <- rbind.data.frame(rle(mdlTblHeaderGeneral$dv)) %>%
+  mutate(lengths = lengths*2) %>%
+  rename(names = values, span = lengths) %>%
+  rbind(c(1, ""), .) %>%
+  mutate(span = as.numeric(span)) %>%
+  select(names, span)
+
+mdlTblGeneral$coef <- mapvalues(
+  mdlTblGeneral$coef,
+  from = c(
+    "sigmaSq",
+    "tau00",
+    "tau11",
+    "rho01",
+    "rho00",
+    "R2_marginal",
+    "R2_conditional",
+    "R2Marg_R2Cond"
+  ),
+  to = c(
+    "$\\sigma^2$",
+    "$\\tau_{00}$",
+    "$\\tau_{11}$",
+    "$\\rho_{01}$",
+    "$\\rho_{00}$",
+    "$R^2_{marginal}$",
+    "$R^2_{conditional}$",
+    "$R^2_{marginal} / R^2_{conditional}$"
+  )
+)
+
+# Still need to pack rows
+mdlTblGeneral %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Intergroup Contact General within PPT.",
+    #format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = c("l", rep("c", ncol(.)-1)),
+    escape = FALSE,
+    digits = 3
+  ) %>%
+  kable_classic() %>%
+  add_header_above(., mdlTblHeaderGeneral2) %>%
+  pack_rows("Fixed", 1, 3) %>%
+  pack_rows("Random", 4, 8) %>%
+  pack_rows("Fit", 9, 21)
 
@@
 mdlTbl$coef <- mapvalues(mdlTbl$coef, 
-          from = c("sigmaSq", "tau00", "tau11", "rho01", "rho00"), 
-          to = c("\\sigma^2", "\\tau_{00}", "\\tau_{11}", "\\rho_{01}", "\\rho_{00}"))
+          from = c("sigmaSq", "tau00", "tau11", "rho01", "rho00", "R2_marginal", "R2_conditional"), 
+          to = c("$\\sigma^2$", "$\\tau_{00}$", "$\\tau_{11}$", "$\\rho_{01}$", "$\\rho_{00}$", "$R^2_{marginal}$", "$R^2_{conditional}$"))
 
@@
 mdlTbl %>%
-  select(-one_of(coef2)) %>%
   replace(is.na(.), "") %>%
@@
     .,
-    caption = "Test",
+    caption = "Core Need Fulfillment and Allport's Conditions",
     #format = "latex",
@@
 
+# Full Sample
+# Study 1:
+robustTblWorkerFull <- 
+  dtWorkerSupp$workerWithinBetween %>%
+  select(
+    AttitudesDutch = thermometerDutch_1,
+    AttitudesDutch_zwc = thermometerDutch_1_zwc,
+    CoreNeed_cwc = keyMotiveFulfilled_cwc,
+    CoreNeed_zwc = keyMotiveFulfilled_zwc,
+    OutgroupInteraction = OutgroupInteraction,
+    OutgroupInteraction_zwc = OutgroupInteraction_zwc,
+    PID = PID
+  )
+mdlWorkerLmerSlopesAttCoreInt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc * OutgroupInteraction +
+      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
+    data = robustTblWorkerFull
+  )
+mdlWorkerLmerSlopesAttCoreIntZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc * OutgroupInteraction_zwc +
+      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
+    data = robustTblWorkerFull
+  )
+#Study 2:
+robustTblStudentFull <- 
+  dtStudentSupp$studentWithinBetween %>%
+  select(
+    AttitudesDutch = AttitudesDutch,
+    AttitudesDutch_zwc = AttitudesDutch_zwc,
+    CoreNeed_cwc = KeyNeedFullfillment_cwc,
+    CoreNeed_zwc = KeyNeedFullfillment_zwc,
+    OutgroupInteraction = OutgroupInteraction,
+    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
+    PID = PID
+  )
+mdlStudentLmerSlopesAttCoreInt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc * OutgroupInteraction +
+      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
+    data = robustTblStudentFull
+  )
+mdlStudentLmerSlopesAttCoreIntZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc * OutgroupInteraction_zwc +
+      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
+    data = robustTblStudentFull
+  )
+#Study 3:
+robustTblMedicalFull <- 
+  dtMedicalSupp$medicalWithinBetween %>%
+  select(
+    AttitudesDutch = AttitudesDutch,
+    AttitudesDutch_zwc = AttitudesDutch_zwc,
+    CoreNeed_cwc = KeyNeedFulfillment_cwc,
+    CoreNeed_zwc = KeyNeedFulfillment_zwc,
+    OutgroupInteraction = OutgroupInteraction,
+    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
+    PID = PID
+  )
+mdlMedicalLmerSlopesAttCoreInt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc * OutgroupInteraction +
+      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
+    #data = dtMedical$full
+    data = robustTblMedicalFull
+  )
+mdlMedicalLmerSlopesAttCoreIntZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc * OutgroupInteraction_zwc +
+      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
+    #data = dtMedical$full
+    data = robustTblMedicalFull
+  )
+
+# SDT
+# Study 1:
+robustTblWorkerOut <- 
+  dtWorkerSupp$workerOutWithinBetween %>%
+  select(
+    AttitudesDutch = thermometerDutch_1,
+    AttitudesDutch_zwc = thermometerDutch_1_zwc,
+    CoreNeed_cwc = keymotive_fulfillemt_1_cwc,
+    CoreNeed_zwc = keymotive_fulfillemt_1_zwc,
+    Competence_cwc = competence_1_cwc,
+    Competence_zwc = competence_1_zwc,
+    Autonomy_cwc = autonomy_1_cwc,
+    Autonomy_zwc = autonomy_1_zwc,
+    Relatedness_cwc = relatedness_1_cwc,
+    Relatedness_zwc = relatedness_1_zwc,
+    PID = PID
+  )
+mdlWorkerOutLmerSlopesCoreSdt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = robustTblWorkerOut
+  )
+mdlWorkerOutLmerSlopesCoreSdtZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
+      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
+    data = robustTblWorkerOut
+  )
+# Study 2:
+robustTblStudentOut <- 
+  dtStudentSupp$studentOutWithinBetween %>%
+  select(
+    AttitudesDutch = AttitudesDutch,
+    AttitudesDutch_zwc = AttitudesDutch_zwc,
+    CoreNeed_cwc = KeyNeedFullfillment_cwc,
+    CoreNeed_zwc = KeyNeedFullfillment_zwc,
+    Competence_cwc = Competence_cwc,
+    Competence_zwc = Competence_zwc,
+    Autonomy_cwc = Autonomy_cwc,
+    Autonomy_zwc = Autonomy_zwc,
+    Relatedness_cwc = Relatedness_cwc,
+    Relatedness_zwc = Relatedness_zwc,
+    PID = PID
+  )
+mdlStudentOutLmerSlopesCoreSdt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = robustTblStudentOut
+  )
+mdlStudentOutLmerSlopesCoreSdtZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
+      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
+    data = robustTblStudentOut
+  )
+# Study 3:
+robustTblMedicalOut <- 
+  dtMedicalSupp$medicalOutWithinBetween %>%
+  select(
+    AttitudesDutch = AttitudesDutch,
+    AttitudesDutch_zwc = AttitudesDutch_zwc,
+    CoreNeed_cwc = KeyNeedFulfillment_cwc,
+    CoreNeed_zwc = KeyNeedFulfillment_zwc,
+    Competence_cwc = Competence_cwc,
+    Competence_zwc = Competence_zwc,
+    Autonomy_cwc = Autonomy_cwc,
+    Autonomy_zwc = Autonomy_zwc,
+    Relatedness_cwc = Relatedness_cwc,
+    Relatedness_zwc = Relatedness_zwc,
+    PID = PID
+  )
+mdlMedicalOutLmerSlopesCoreSdt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = robustTblMedicalOut
+  )
+mdlMedicalOutLmerSlopesCoreSdtZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
+      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
+    data = robustTblMedicalOut
+  )
+
+# collect models for table
+mdlRobustTblElements <- list(
+  # full
+  c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ),
+  c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ),
+  c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ),
+  # outgroup
+  c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ),
+  c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ),
+  c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ)
+  )
+
+mdlRobustPrep <- list()
+for (i in 1:length(mdlRobustTblElements)) {
+  mdlRobustPrep[[i]] <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])
+}
+
+sapply(mdlRobustPrep, "[[", 1)
+sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef)
+
+mdlRobustPrep[[1]]$coeficients$coef
+
+mdlRobustTbl <- data.frame(
+  coef = c(
+    "(Intercept)",
+    "CoreNeed",
+    "Quality",
+    "Allport",
+    names(mdlRobustPrep[[1]]$random),
+    names(mdlRobustPrep[[1]]$fit)
+  )
+)
+for (i in 1:length(mdlRobustPrep)){
+  mdlRobustTbl <- join(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef")
+  #mdlTbl <- merge(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", ""))
+}
+
+mdlTblHeader <- data.frame(
+  data = as.character(mdlRobustTbl[mdlRobustTbl$coef == "data",]),
+  formula = as.character(mdlRobustTbl[mdlRobustTbl$coef == "formula",])
+) %>%
+  filter(data != "",
+         data != "data") %>%
+  mutate(study = str_extract(data, "S1|S2|S3")) %>%
+  mutate(study = gsub("S", "Study ", study)) %>%
+  mutate(dv = sub(" ~.*", "", formula)) %>%
+  mutate(dv = gsub("Raw", " ", dv)) %>%
+  mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>%
+  mutate(header = paste(study, pred))
+
+mdlTblHeaderFreq <- rbind.data.frame(rle(mdlTblHeader$header)) %>%
+  mutate(lengths = lengths*2) %>%
+  rename(names = values, span = lengths) %>%
+  rbind(c(1, ""), .) %>%
+  mutate(span = as.numeric(span)) %>%
+  select(names, span)
+
+mdlTblHeader2 <- data.frame(names = mdlTblHeader$dv, span = 2) %>% 
+  mutate(names = as.character(names)) %>%
+  rbind(c("", 1), .) %>%
+  mutate(span = as.numeric(span))
+
+mdlTblHeader2.2 <- rbind.data.frame(rle(mdlTblHeader$dv)) %>%
+  mutate(lengths = lengths*2) %>%
+  rename(names = values, span = lengths) %>%
+  rbind(c(1, ""), .) %>%
+  mutate(span = as.numeric(span)) %>%
+  select(names, span)
+
+mdlTbl$coef <- mapvalues(mdlTbl$coef, 
+          from = c("sigmaSq", "tau00", "tau11", "rho01", "rho00", "R2_marginal", "R2_conditional"), 
+          to = c("$\\sigma^2$", "$\\tau_{00}$", "$\\tau_{11}$", "$\\rho_{01}$", "$\\rho_{00}$", "$R^2_{marginal}$", "$R^2_{conditional}$"))
+
+# Still need to pack rows
+mdlTbl %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Core Need Fulfillment and Allport's Conditions",
+    #format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    escape = FALSE,
+    digits = 3
+  ) %>%
+  kable_classic() %>%
+  add_header_above(., mdlTblHeader2) %>%
+  add_header_above(., mdlTblHeaderFreq) %>%
+  pack_rows("Fixed", 1, 4) %>%
+  pack_rows("Random", 5, 9) %>%
+  pack_rows("Fit", 10, 21)
+
 ```

### 2021-12-15 scripts/functions/MlCorMat.R

@@ -208,6 +208,8 @@ MlTraitState <-
     data <- 
       data %>%
       #select(id, selection) %>%
+      #mutate_if(is.factor, as.numeric) %>% # let's hope this doesn't cause any problems :-D
+      mutate_at(selection, as.numeric) %>% # let's hope this works 
       mutate_at(selection, list(gm = ~mean(., na.rm=TRUE))) %>% # grand mean
       mutate_at(selection, list(gmc = ~.-mean(., na.rm=TRUE))) %>% # grand mean centered
       group_by_at(vars(matches(id))) %>%

### 2021-12-15 scripts/functions/MlTbl.R

@@ -1,5 +1,5 @@
-#obj <- tblLmerS3AttSlopesAllportCore
-#objz <- tblLmerS3AttSlopesAllportCoreZ
+#obj <- mdlWorker$lmerInterceptAttTypeTbl
+#objz <- mdlWorker$lmerInterceptAttTypeTblZ
 
 lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   # Summarize models
@@ -13,7 +13,10 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   coefZ <- smryZ$coeftable %>% 
     as.data.frame %>%
     tibble::rownames_to_column(., "coef")
-  confZ <- confint(objz, method = "boot") %>% 
+  confZ <- confint(objz, 
+                   method = "boot", 
+                   parallel = "multicore", 
+                   ncpus = parallel::detectCores(logical = TRUE)) %>% 
     as.data.frame %>%
     tibble::rownames_to_column(., "coef")
   coefZOut <- merge(coefZ, confZ)
@@ -53,7 +56,7 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
       coefOut, 
       coefZOut %>% 
         select(coef, Beta) %>% 
-        mutate(coef = gsub('Z$', '', coef))
+        mutate(coef = gsub('_zwc|Z$', '', coef))
     )
   
   
@@ -103,6 +106,9 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   ICC <- performance::icc(obj)$ICC_adjusted
   rSqMarg <- as.numeric(performance::r2(obj)$R2_marginal) # Marginal R2
   rSqCond <- as.numeric(performance::r2(obj)$R2_conditional) # Conditional R2
+  R2Marg_R2Cond <- paste(format(round(rSqMarg, 3), nsmall = 3), 
+                         format(round(rSqCond, 3), nsmall = 3), 
+                         sep = " / ")
   sumstat <- list(
     data = data,
     formula = formula,
@@ -115,7 +121,8 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
     Groups = G,
     ICC = ICC,
     R2_marginal = rSqMarg,
-    R2_conditional = rSqCond
+    R2_conditional = rSqCond,
+    R2Marg_R2Cond = R2Marg_R2Cond
   )
   
   # Combined Table output

### 2021-12-16 Methods-and-Results.Rmd
pre re-render

@@
   "knitr",
+  "berryFunctions",
   "remedy",
@@
 
-tabModelTest <- tab_model(mdlWorker$lmAttFreqQualX,
+# tabModelTest <- tab_model(mdlWorker$lmAttFreqQualX,
+#                           mdlStudent$lmAttFreqQualX,
+#                           mdlMedical$lmAttFreqQualX)
+
+summ(mdlWorker$lmAttFreqQualX)
+
+mdlTblElementsGeneralLm <- list(mdlWorker$lmAttFreqQualX,
                                 mdlStudent$lmAttFreqQualX,
@@
 
-library(XML)
-df <- data.frame(readHTMLTable(htmlParse(tabModelTest))[1])
-# first row as colnames
-colnames(df) <- df[1,]
-# remove the fake first row
-df <- df[-1,]
+mdlPrepLmGeneral <- list()
+for (i in 1:length(mdlTblElementsGeneralLm)) {
+  mdlPrepLmGeneral[[i]] <- lmTblPrep(mdlTblElementsGeneralLm[[i]])
+}
+mdlTblGeneralLm <- data.frame(
+  coef = c(
+    sapply(mdlPrepLmGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique,
+    names(mdlPrepLmGeneral[[1]]$fit)
+  )
+)
+for (i in 1:length(mdlPrepGeneral)){
+  mdlTblGeneralLm <- join(mdlTblGeneralLm, mdlPrepLmGeneral[[i]]$mdlTbl, by = "coef")
+}
 
@@
 
-tab_model(
-  mdlWorker$lmerInterceptAttTypeTbl,
-  mdlStudent$lmerSlopesAttType,
-  mdlMedical$lmerSlopesAttType
-)
-
 mdlTblElementsGeneralLmer <- list(
@@
 
-mdlTblGeneral <- data.frame(
+mdlTblGeneralLmer <- data.frame(
   coef = c(
-    "(Intercept)",
-    "OutgroupInteraction",
-    "NonOutgroupInteraction",
+    sapply(mdlPrepGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique,
     names(mdlPrepGeneral[[1]]$random),
@@
 for (i in 1:length(mdlPrepGeneral)){
-  mdlTblGeneral <- join(mdlTblGeneral, mdlPrepGeneral[[i]]$mdlTbl, by = "coef")
+  mdlTblGeneralLmer <- join(mdlTblGeneralLmer, mdlPrepGeneral[[i]]$mdlTbl, by = "coef")
 }
 
-mdlTblHeaderGeneral <- data.frame(
+names(mdlTblGeneralLmer) <- make.unique(names(mdlTblGeneralLmer))
+mdlTblGeneral <-
+  merge(mdlTblGeneralLm,
+        mdlTblGeneralLmer %>% 
+          mutate(coef = gsub("R2Marg_R2Cond", "R2_R2_adjusted", coef)),
+        by = "coef",
+        all = TRUE) 
+names(mdlTblGeneral) <- make.unique(names(mdlTblGeneral))
+mdlTblGeneral <- mdlTblGeneral %>%
+  arrange(match(coef, c(
+    sapply(mdlPrepLmGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique,
+    sapply(mdlPrepGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique %>% setdiff(., "(Intercept)"),
+    names(mdlPrepGeneral[[1]]$random),
+    "Groups",
+    names(mdlPrepLmGeneral[[1]]$fit),
+    setdiff(names(mdlPrepGeneral[[1]]$fit), c(names(mdlPrepLmGeneral[[1]]$fit), "Groups"))
+  ))) %>%
+  replace(is.na(.), "")
+
+mdlTblGeneral$coef <- mapvalues(
+  mdlTblGeneral$coef,
+  from = c(
+    "sigmaSq",
+    "tau00",
+    "tau11",
+    "rho01",
+    "rho00",
+    "fTest",
+    "R2",
+    "R2_adjusted",
+    "R2_R2_adjusted",
+    "R2_marginal",
+    "R2_conditional",
+    "R2Marg_R2Cond"
+  ),
+  to = c(
+    "$\\sigma^2$",
+    "$\\tau_{00}$",
+    "$\\tau_{11}$",
+    "$\\rho_{01}$",
+    "$\\rho_{00}$",
+    "F Test",
+    "$R^2$",
+    "$R^2_{adjusted}$",
+    "$R^{2 (a)}$",
+    "$R^2_{marginal}$",
+    "$R^2_{conditional}$",
+    "$R^2_{marginal} / R^2_{conditional}$"
+  )
+)
+
+# Headers
+mdlTblGeneralHeader <- data.frame(
   data = as.character(mdlTblGeneral[mdlTblGeneral$coef == "data",]),
   formula = as.character(mdlTblGeneral[mdlTblGeneral$coef == "formula",])
+) %>%
+  filter(data != "",
+         data != "data") %>%
+  mutate(study = str_extract(data, "Worker|Student|Medical")) %>%
+  mutate(study = gsub("Worker", "Study 1", study)) %>%
+  mutate(study = gsub("Student", "Study 2", study)) %>%
+  mutate(study = gsub("Medical", "Study 3", study)) %>%
+  mutate(dv = sub(" ~.*", "", formula)) %>%
+  mutate(dv = gsub("Raw", " ", dv))
+
+mdlTblGeneralHeaderDv <- data.frame(names = mdlTblGeneralHeader$dv, span = 2) %>% 
+  mutate(names = as.character(names)) %>%
+  rbind(c("", 1), .) %>%
+  mutate(span = as.numeric(span))
+
+mdlTblGeneralHeaderStudy <- rbind.data.frame(rle(mdlTblGeneralHeader$study)) %>%
+  mutate(lengths = lengths*2) %>%
+  rename(names = values, span = lengths) %>%
+  rbind(c(1, ""), .) %>%
+  mutate(span = as.numeric(span)) %>%
+  select(names, span)
+
+# Long Table
+mdlTblGeneralLong <- mdlTblGeneral %>%
+  kbl(
+    .,
+    caption = "Robustness Analyses",
+    #format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = c("l", rep("c", ncol(.) - 1)),
+    escape = FALSE,
+    digits = 3
+  ) %>%
+  kable_classic() %>%
+  add_header_above(., mdlTblGeneralHeaderStudy) %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Contact [Full Sample]" = 6,
+      "Self-Determination Theory [Outgroup Interactions only]" = 6
+    )
+  ) %>%
+  pack_rows("Random", 7, 11) %>%
+  pack_rows("Fit", 12, 27) %>%
+  footnote(
+    general = c("PID = Participant ID number (grouping variable)",
+                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
+                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
+    )
+  ) %>%
+  gsub("_cwc", "", ., fixed = TRUE)
+
+# shortened Table
+mdlTblGeneralShort <- mdlTblGeneral %>%
+  filter(
+    !coef %in% c(
+      "data",
+      "formula",
+      "groupId",
+      "$R^2$",
+      "$R^2_{adjusted}$",
+      "$R^2_{marginal}$",
+      "$R^2_{conditional}$",
+      "logLik",
+      "deviance"
+    )
+  ) %>%
+  kbl(
+    .,
+    caption = "Intergroup General",
+    format = "latex",
+    linesep = "",
+    booktabs = TRUE,
+    col.names = c("", rep(c("$B$", "$\\eta_p$"), (ncol(.)-1)/4), rep(c("$B$", "$\\beta$"), (ncol(.)-1)/4)),
+    align = c("l", rep("c", ncol(.) - 1)),
+    escape = FALSE,
+    digits = 3
+  )  %>%
+  kable_classic() %>%
+  add_header_above(., mdlRobustTblHeaderStudy) %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Aggregated [across participants]" = 6,
+      "Contemporaneous [within participants]" = 6
+    )
+  ) %>%
+  pack_rows("Random", 7, 11) %>%
+  pack_rows("Fit", 12, 18) %>%
+  footnote(
+    general = c("PID = Participant ID number (grouping variable)",
+                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
+                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
+    ),
+    alphabet = c("For linear regression: $R^2 / R^2_{adjusted}$, for multilevel regression: $R^2_{marginal} / R^2_{conditional}$ ")
+  ) %>%
+  gsub("_cwc", "", ., fixed = TRUE)   %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/mdlContactGeneral.tex")
+mdlTblGeneralShort
+```
+
+```{r intergroupNeedsTbl, include=FALSE}
+# Table of core need and Allports Conditions (potentially two tables — e.g., needs + allport)
+# all lmer models :-)
+# make different options
+
+# collect relevant models
+# Study 1:
+# Rename variables for consistency
+tblDtS1Needs <- dtWorkerSupp$workerOutWithinBetween %>%
+  select(
+    Attitude = thermometerDutch_1,
+    AttitudeZ = thermometerDutch_1_zwc,
+    CoreNeed = keymotive_fulfillemt_1_cwc,
+    CoreNeedZ = keymotive_fulfillemt_1_zwc,
+    QualityRaw = quality_overall_1,
+    Quality = quality_overall_1_cwc,
+    QualityZ = quality_overall_1_zwc,
+    PID = PID
+  )
+# Quality ~ CoreNeed
+tblLmerS1QltInterceptCore <- lmer(
+  QualityRaw ~ CoreNeed + (1 | PID),
+  data = tblDtS1Needs
+)
+tblLmerS1QltInterceptCoreZ <- lmer(
+  QualityZ ~ CoreNeedZ + (1 | PID),
+  data = tblDtS1Needs
+)
+# Attitude ~ CoreNeed
+tblLmerS1AttSlopeCore <- lmer(
+  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS1Needs
+)
+tblLmerS1AttSlopeCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS1Needs
+)
+# Attitude ~ CoreNeed + Quality
+tblLmerS1AttSlopeCoreQlt <- lmer(
+  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
+  data = tblDtS1Needs
+)
+tblLmerS1AttSlopeCoreQltZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
+  data = tblDtS1Needs
+)
+
+# Study 2:
+# Rename variables for consistency
+tblDtS2Needs <- dtStudentSupp$studentOutWithinBetween %>%
+  select(
+    Attitude = AttitudesDutch,
+    AttitudeZ = AttitudesDutch_zwc,
+    CoreNeed = KeyNeedFullfillment_cwc,
+    CoreNeedZ = KeyNeedFullfillment_zwc,
+    QualityRaw = quality_overall,
+    Quality = quality_overall_cwc,
+    QualityZ = quality_overall_zwc,
+    PID = PID
+  )
+# Quality ~ CoreNeed
+tblLmerS2QltSlopesCore <- lmer(
+  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS2Needs
+)
+tblLmerS2QltSlopesCoreZ <- lmer(
+  QualityZ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS2Needs
+)
+# Attitude ~ CoreNeed
+tblLmerS2AttSlopesCore <- lmer(
+  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS2Needs
+)
+tblLmerS2AttSlopesCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS2Needs
+)
+# Attitude ~ CoreNeed + Quality
+tblLmerS2AttSlopesCoreQlt <- lmer(
+  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
+  data = tblDtS2Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+tblLmerS2AttSlopesCoreQltZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
+  data = tblDtS2Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+
+# Study 3:
+# Rename variables for consistency
+tblDtS3Needs <- dtMedicalSupp$medicalOutWithinBetween %>%
+  select(
+    Attitude = AttitudesDutch,
+    AttitudeZ = AttitudesDutch_zwc,
+    CoreNeed = KeyNeedFulfillment_cwc,
+    CoreNeedZ = KeyNeedFulfillment_zwc,
+    Allport = AllportsCondition_cwc,
+    AllportZ = AllportsCondition_zwc,
+    QualityRaw = qualityOverall,
+    Quality = qualityOverall_cwc,
+    QualityZ = qualityOverall_zwc,
+    PID = PID
+  )
+# Quality ~ CoreNeed
+tblLmerS3QltSlopesCore <- lmer(
+  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3QltSlopesCoreZ <- lmer(
+  QualityZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ CoreNeed
+tblLmerS3AttSlopesCore <- lmer(
+  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3AttSlopesCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ CoreNeed + Quality
+tblLmerS3AttSlopesCoreQlt <- lmer(
+  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+tblLmerS3AttSlopesCoreQltZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+# Quality ~ Allport
+tblLmerS3QltSlopesAllport <- lmer(
+  QualityRaw ~ Allport + (1 + Allport | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3QltSlopesAllportZ <- lmer(
+  QualityZ ~ AllportZ + (1 + AllportZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ Allport
+tblLmerS3AttSlopesAllport <- lmer(
+  Attitude ~ Allport + (1 + Allport | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3AttSlopesAllportZ <- lmer(
+  AttitudeZ ~ AllportZ + (1 + AllportZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ Allport + Quality
+tblLmerS3AttSlopesAllportQlt <- lmer(
+  Attitude ~ Allport + Quality + (1 + Allport + Quality | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+tblLmerS3AttSlopesAllportQltZ <- lmer(
+  AttitudeZ ~ AllportZ + QualityZ + (1 + AllportZ + QualityZ | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+# Attitude ~ Allport + CoreNeed
+tblLmerS3AttSlopesAllportCore <- lmer(
+  Attitude ~ CoreNeed + Allport + (1 + CoreNeed + Allport | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3AttSlopesAllportCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + AllportZ + (1 + CoreNeedZ + AllportZ | PID),
+  data = tblDtS3Needs
+)
+
+mdlTblElements <- list(
+  # Study 1:
+  c(tblLmerS1QltInterceptCore, tblLmerS1QltInterceptCoreZ),
+  c(tblLmerS1AttSlopeCore, tblLmerS1AttSlopeCoreZ),
+  c(tblLmerS1AttSlopeCoreQlt, tblLmerS1AttSlopeCoreQltZ),
+  # Study 2:
+  c(tblLmerS2QltSlopesCore, tblLmerS2QltSlopesCoreZ),
+  c(tblLmerS2AttSlopesCore, tblLmerS2AttSlopesCoreZ),
+  c(tblLmerS2AttSlopesCoreQlt, tblLmerS2AttSlopesCoreQltZ),
+  # Study 3:
+  c(tblLmerS3QltSlopesCore, tblLmerS3QltSlopesCoreZ),
+  c(tblLmerS3AttSlopesCore, tblLmerS3AttSlopesCoreZ),
+  c(tblLmerS3AttSlopesCoreQlt, tblLmerS3AttSlopesCoreQlt),
+  c(tblLmerS3QltSlopesAllport, tblLmerS3QltSlopesAllportZ),
+  c(tblLmerS3AttSlopesAllport, tblLmerS3AttSlopesAllportZ),
+  c(tblLmerS3AttSlopesAllportQlt, tblLmerS3AttSlopesAllportQltZ),
+  c(tblLmerS3AttSlopesAllportCore, tblLmerS3AttSlopesAllportCoreZ)
+  )
+
+# lmerTblPrep(mdlTblElements[[1]][[1]], mdlTblElements[[1]][[2]])
+
+mdlPrep <- list()
+for (i in 1:length(mdlTblElements)) {
+  mdlPrep[[i]] <- lmerTblPrep(mdlTblElements[[i]][[1]], mdlTblElements[[i]][[2]])
+}
+
+mdlTbl <- data.frame(
+  coef = c(
+    sapply(mdlPrep, function(x) x[1]$coeficients$coef) %>% unlist %>% unique,
+    names(mdlPrep[[1]]$random),
+    names(mdlPrep[[1]]$fit)
+  )
+)
+for (i in 1:length(mdlPrep)){
+  mdlTbl <- join(mdlTbl, mdlPrep[[i]]$mdlTbl, by = "coef")
+  #mdlTbl <- merge(mdlTbl, mdlPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", ""))
+}
+
+mdlTblHeader <- data.frame(
+  data = as.character(mdlTbl[mdlTbl$coef == "data",]),
+  formula = as.character(mdlTbl[mdlTbl$coef == "formula",])
 ) %>%
@@
   mutate(dv = gsub("Raw", " ", dv)) %>%
-  mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>%
-  mutate(header = paste(study, pred))
-
-mdlTblHeaderGeneralFreq <- rbind.data.frame(rle(mdlTblHeaderGeneral$header)) %>%
+  mutate(pred = str_extract(formula, "(CoreNeed \\+ Allport)|CoreNeed|Allport")) %>%
+  mutate(header = paste(study, pred, sep = " - "))
+
+mdlTblHeaderFreq <- rbind.data.frame(rle(mdlTblHeader$header)) %>%
   mutate(lengths = lengths*2) %>%
@@
 
-mdlTblHeaderGeneral2 <- data.frame(names = mdlTblHeaderGeneral$dv, span = 2) %>% 
+mdlTblHeader2 <- data.frame(names = mdlTblHeader$dv, span = 2) %>% 
   mutate(names = as.character(names)) %>%
@@
 
-mdlTblHeaderGeneral2.2 <- rbind.data.frame(rle(mdlTblHeaderGeneral$dv)) %>%
+mdlTblHeader2.2 <- rbind.data.frame(rle(mdlTblHeader$dv)) %>%
   mutate(lengths = lengths*2) %>%
@@
 
-mdlTblGeneral$coef <- mapvalues(
-  mdlTblGeneral$coef,
+mdlTbl$coef <- mapvalues(
+  mdlTbl$coef,
   from = c(
@@
     "$R^2_{conditional}$",
-    "$R^2_{marginal} / R^2_{conditional}$"
-  )
-)
-
-# Still need to pack rows
-mdlTblGeneral %>%
+    "$R^2_{marginal}$ / $R^2_{conditional}$"
+  )
+)
+
+# Full Table
+mdlTblTheoreticalLong <- mdlTbl %>%
   replace(is.na(.), "") %>%
@@
     .,
-    caption = "Intergroup Contact General within PPT.",
-    #format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.)-1)),
-    escape = FALSE,
-    digits = 3
-  ) %>%
-  kable_classic() %>%
-  add_header_above(., mdlTblHeaderGeneral2) %>%
-  pack_rows("Fixed", 1, 3) %>%
-  pack_rows("Random", 4, 8) %>%
-  pack_rows("Fit", 9, 21)
-
-```
-
-```{r intergroupNeedsTbl, include=FALSE}
-# Table of core need and Allports Conditions (potentially two tables — e.g., needs + allport)
-# all lmer models :-)
-# make different options
-
-# collect relevant models
-# Study 1:
-# Rename variables for consistency
-tblDtS1Needs <- dtWorkerSupp$workerOutWithinBetween %>%
-  select(
-    Attitude = thermometerDutch_1,
-    AttitudeZ = thermometerDutch_1_zwc,
-    CoreNeed = keymotive_fulfillemt_1_cwc,
-    CoreNeedZ = keymotive_fulfillemt_1_zwc,
-    QualityRaw = quality_overall_1,
-    Quality = quality_overall_1_cwc,
-    QualityZ = quality_overall_1_zwc,
-    PID = PID
-  )
-# Quality ~ CoreNeed
-tblLmerS1QltInterceptCore <- lmer(
-  QualityRaw ~ CoreNeed + (1 | PID),
-  data = tblDtS1Needs
-)
-tblLmerS1QltInterceptCoreZ <- lmer(
-  QualityZ ~ CoreNeedZ + (1 | PID),
-  data = tblDtS1Needs
-)
-# Attitude ~ CoreNeed
-tblLmerS1AttSlopeCore <- lmer(
-  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
-  data = tblDtS1Needs
-)
-tblLmerS1AttSlopeCoreZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
-  data = tblDtS1Needs
-)
-# Attitude ~ CoreNeed + Quality
-tblLmerS1AttSlopeCoreQlt <- lmer(
-  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
-  data = tblDtS1Needs
-)
-tblLmerS1AttSlopeCoreQltZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
-  data = tblDtS1Needs
-)
-
-# Study 2:
-# Rename variables for consistency
-tblDtS2Needs <- dtStudentSupp$studentOutWithinBetween %>%
-  select(
-    Attitude = AttitudesDutch,
-    AttitudeZ = AttitudesDutch_zwc,
-    CoreNeed = KeyNeedFullfillment_cwc,
-    CoreNeedZ = KeyNeedFullfillment_zwc,
-    QualityRaw = quality_overall,
-    Quality = quality_overall_cwc,
-    QualityZ = quality_overall_zwc,
-    PID = PID
-  )
-# Quality ~ CoreNeed
-tblLmerS2QltSlopesCore <- lmer(
-  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
-  data = tblDtS2Needs
-)
-tblLmerS2QltSlopesCoreZ <- lmer(
-  QualityZ~ CoreNeedZ + (1 + CoreNeedZ | PID),
-  data = tblDtS2Needs
-)
-# Attitude ~ CoreNeed
-tblLmerS2AttSlopesCore <- lmer(
-  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
-  data = tblDtS2Needs
-)
-tblLmerS2AttSlopesCoreZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
-  data = tblDtS2Needs
-)
-# Attitude ~ CoreNeed + Quality
-tblLmerS2AttSlopesCoreQlt <- lmer(
-  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
-  data = tblDtS2Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-tblLmerS2AttSlopesCoreQltZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
-  data = tblDtS2Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-
-# Study 3:
-# Rename variables for consistency
-tblDtS3Needs <- dtMedicalSupp$medicalOutWithinBetween %>%
-  select(
-    Attitude = AttitudesDutch,
-    AttitudeZ = AttitudesDutch_zwc,
-    CoreNeed = KeyNeedFulfillment_cwc,
-    CoreNeedZ = KeyNeedFulfillment_zwc,
-    Allport = AllportsCondition_cwc,
-    AllportZ = AllportsCondition_zwc,
-    QualityRaw = qualityOverall,
-    Quality = qualityOverall_cwc,
-    QualityZ = qualityOverall_zwc,
-    PID = PID
-  )
-# Quality ~ CoreNeed
-tblLmerS3QltSlopesCore <- lmer(
-  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
-  data = tblDtS3Needs
-)
-tblLmerS3QltSlopesCoreZ <- lmer(
-  QualityZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
-  data = tblDtS3Needs
-)
-# Attitude ~ CoreNeed
-tblLmerS3AttSlopesCore <- lmer(
-  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
-  data = tblDtS3Needs
-)
-tblLmerS3AttSlopesCoreZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
-  data = tblDtS3Needs
-)
-# Attitude ~ CoreNeed + Quality
-tblLmerS3AttSlopesCoreQlt <- lmer(
-  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
-  data = tblDtS3Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-tblLmerS3AttSlopesCoreQltZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
-  data = tblDtS3Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-# Quality ~ Allport
-tblLmerS3QltSlopesAllport <- lmer(
-  QualityRaw ~ Allport + (1 + Allport | PID),
-  data = tblDtS3Needs
-)
-tblLmerS3QltSlopesAllportZ <- lmer(
-  QualityZ ~ AllportZ + (1 + AllportZ | PID),
-  data = tblDtS3Needs
-)
-# Attitude ~ Allport
-tblLmerS3AttSlopesAllport <- lmer(
-  Attitude ~ Allport + (1 + Allport | PID),
-  data = tblDtS3Needs
-)
-tblLmerS3AttSlopesAllportZ <- lmer(
-  AttitudeZ ~ AllportZ + (1 + AllportZ | PID),
-  data = tblDtS3Needs
-)
-# Attitude ~ Allport + Quality
-tblLmerS3AttSlopesAllportQlt <- lmer(
-  Attitude ~ Allport + Quality + (1 + Allport + Quality | PID),
-  data = tblDtS3Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-tblLmerS3AttSlopesAllportQltZ <- lmer(
-  AttitudeZ ~ AllportZ + QualityZ + (1 + AllportZ + QualityZ | PID),
-  data = tblDtS3Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-# Attitude ~ Allport + CoreNeed
-tblLmerS3AttSlopesAllportCore <- lmer(
-  Attitude ~ CoreNeed + Allport + (1 + CoreNeed + Allport | PID),
-  data = tblDtS3Needs
-)
-tblLmerS3AttSlopesAllportCoreZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + AllportZ + (1 + CoreNeedZ + AllportZ | PID),
-  data = tblDtS3Needs
-)
-
-tab_model(
-  # Study 1:
-  tblLmerS1QltInterceptCore,
-  tblLmerS1AttSlopeCore,
-  tblLmerS1AttSlopeCoreQlt,
-  # Study 2:
-  tblLmerS2QltSlopesCore,
-  tblLmerS2AttSlopesCore,
-  tblLmerS2AttSlopesCoreQlt,
-  # Study 3:
-  tblLmerS3QltSlopesCore,
-  tblLmerS3AttSlopesCore,
-  tblLmerS3AttSlopesCoreQlt, 
-  tblLmerS3QltSlopesAllport, 
-  tblLmerS3AttSlopesAllport,
-  tblLmerS3AttSlopesAllportQlt,
-  tblLmerS3AttSlopesAllportCore,
-  # Settings
-  show.std = TRUE,
-  show.re.var = TRUE
-)
-
-mdlTblElements <- list(
-  # Study 1:
-  c(tblLmerS1QltInterceptCore, tblLmerS1QltInterceptCoreZ),
-  c(tblLmerS1AttSlopeCore, tblLmerS1AttSlopeCoreZ),
-  c(tblLmerS1AttSlopeCoreQlt, tblLmerS1AttSlopeCoreQltZ),
-  # Study 2:
-  c(tblLmerS2QltSlopesCore, tblLmerS2QltSlopesCoreZ),
-  c(tblLmerS2AttSlopesCore, tblLmerS2AttSlopesCoreZ),
-  c(tblLmerS2AttSlopesCoreQlt, tblLmerS2AttSlopesCoreQltZ),
-  # Study 3:
-  c(tblLmerS3QltSlopesCore, tblLmerS3QltSlopesCoreZ),
-  c(tblLmerS3AttSlopesCore, tblLmerS3AttSlopesCoreZ),
-  c(tblLmerS3AttSlopesCoreQlt, tblLmerS3AttSlopesCoreQlt),
-  c(tblLmerS3QltSlopesAllport, tblLmerS3QltSlopesAllportZ),
-  c(tblLmerS3AttSlopesAllport, tblLmerS3AttSlopesAllportZ),
-  c(tblLmerS3AttSlopesAllportQlt, tblLmerS3AttSlopesAllportQltZ),
-  c(tblLmerS3AttSlopesAllportCore, tblLmerS3AttSlopesAllportCoreZ)
-  )
-
-# lmerTblPrep(mdlTblElements[[1]][[1]], mdlTblElements[[1]][[2]])
-
-mdlPrep <- list()
-for (i in 1:length(mdlTblElements)) {
-  mdlPrep[[i]] <- lmerTblPrep(mdlTblElements[[i]][[1]], mdlTblElements[[i]][[2]])
-}
-
-mdlTbl <- data.frame(
-  coef = c(
-    "(Intercept)",
-    "CoreNeed",
-    "Quality",
-    "Allport",
-    names(mdlPrep[[1]]$random),
-    names(mdlPrep[[1]]$fit)
-  )
-)
-for (i in 1:length(mdlPrep)){
-  mdlTbl <- join(mdlTbl, mdlPrep[[i]]$mdlTbl, by = "coef")
-  #mdlTbl <- merge(mdlTbl, mdlPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", ""))
-}
-
-mdlTblHeader <- data.frame(
-  data = as.character(mdlTbl[mdlTbl$coef == "data",]),
-  formula = as.character(mdlTbl[mdlTbl$coef == "formula",])
-) %>%
-  filter(data != "",
-         data != "data") %>%
-  mutate(study = str_extract(data, "S1|S2|S3")) %>%
-  mutate(study = gsub("S", "Study ", study)) %>%
-  mutate(dv = sub(" ~.*", "", formula)) %>%
-  mutate(dv = gsub("Raw", " ", dv)) %>%
-  mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>%
-  mutate(header = paste(study, pred))
-
-mdlTblHeaderFreq <- rbind.data.frame(rle(mdlTblHeader$header)) %>%
-  mutate(lengths = lengths*2) %>%
-  rename(names = values, span = lengths) %>%
-  rbind(c(1, ""), .) %>%
-  mutate(span = as.numeric(span)) %>%
-  select(names, span)
-
-mdlTblHeader2 <- data.frame(names = mdlTblHeader$dv, span = 2) %>% 
-  mutate(names = as.character(names)) %>%
-  rbind(c("", 1), .) %>%
-  mutate(span = as.numeric(span))
-
-mdlTblHeader2.2 <- rbind.data.frame(rle(mdlTblHeader$dv)) %>%
-  mutate(lengths = lengths*2) %>%
-  rename(names = values, span = lengths) %>%
-  rbind(c(1, ""), .) %>%
-  mutate(span = as.numeric(span)) %>%
-  select(names, span)
-
-mdlTbl$coef <- mapvalues(mdlTbl$coef, 
-          from = c("sigmaSq", "tau00", "tau11", "rho01", "rho00", "R2_marginal", "R2_conditional"), 
-          to = c("$\\sigma^2$", "$\\tau_{00}$", "$\\tau_{11}$", "$\\rho_{01}$", "$\\rho_{00}$", "$R^2_{marginal}$", "$R^2_{conditional}$"))
-
-# Still need to pack rows
-mdlTbl %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Core Need Fulfillment and Allport's Conditions",
+    caption = "Theoretical Test: Core Need Fulfillment and Allport's Conditions",
     #format = "latex",
@@
 
+# shortened Table
+mdlTblTheoreticalShort <- mdlTbl %>%
+  replace(is.na(.), "")
+names(mdlTblTheoreticalShort) <- make.unique(names(mdlTblTheoreticalShort))
+mdlTblTheoreticalShort <- mdlTblTheoreticalShort %>%
+  filter(
+    !coef %in% c(
+      "data",
+      "formula",
+      "groupId",
+      "$R^2_{marginal}$",
+      "$R^2_{conditional}$",
+      "logLik",
+      "deviance"
+    )
+  ) %>%
+  kbl(
+    .,
+    caption = "Core Need Fulfillment and Allport's Conditions",
+    format = "latex",
+    linesep = "",
+    booktabs = TRUE,
+    col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)),
+    align = rep("c", ncol(.)),
+    escape = FALSE,
+    digits = 3
+  ) %>%
+  kable_classic() %>%
+  add_header_above(., mdlTblHeader2) %>%
+  add_header_above(., mdlTblHeaderFreq) %>%
+  pack_rows("Fixed", 1, 4) %>%
+  pack_rows("Random", 5, 9) %>%
+  pack_rows("Fit", 10, 15) %>%
+  footnote(
+    general = c("PID = Participant ID number (grouping variable)",
+                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
+                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
+    )
+  )  %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/mdlTheory.tex")
+mdlTblTheoreticalShort
 ```
@@
 
-sapply(mdlRobustPrep, "[[", 1)
-sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef)
-
-mdlRobustPrep[[1]]$coeficients$coef
-
 mdlRobustTbl <- data.frame(
   coef = c(
-    "(Intercept)",
-    "CoreNeed",
-    "Quality",
-    "Allport",
+    sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef) %>% unlist %>% unique,
     names(mdlRobustPrep[[1]]$random),
@@
 
-mdlTblHeader <- data.frame(
+mdlRobustTblHeader <- data.frame(
   data = as.character(mdlRobustTbl[mdlRobustTbl$coef == "data",]),
@@
          data != "data") %>%
-  mutate(study = str_extract(data, "S1|S2|S3")) %>%
-  mutate(study = gsub("S", "Study ", study)) %>%
+  mutate(study = str_extract(data, "Worker|Student|Medical")) %>%
+  mutate(study = gsub("Worker", "Study 1", study)) %>%
+  mutate(study = gsub("Student", "Study 2", study)) %>%
+  mutate(study = gsub("Medical", "Study 3", study)) %>%
   mutate(dv = sub(" ~.*", "", formula)) %>%
@@
   mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>%
-  mutate(header = paste(study, pred))
-
-mdlTblHeaderFreq <- rbind.data.frame(rle(mdlTblHeader$header)) %>%
+  mutate(header = paste(study, pred, sep = " - "))
+
+mdlRobustTblHeaderFreq <- rbind.data.frame(rle(mdlRobustTblHeader$header)) %>%
   mutate(lengths = lengths*2) %>%
@@
 
-mdlTblHeader2 <- data.frame(names = mdlTblHeader$dv, span = 2) %>% 
+mdlRobustTblHeaderDv <- data.frame(names = mdlRobustTblHeader$dv, span = 2) %>% 
   mutate(names = as.character(names)) %>%
@@
 
-mdlTblHeader2.2 <- rbind.data.frame(rle(mdlTblHeader$dv)) %>%
+mdlRobustTblHeaderStudy <- rbind.data.frame(rle(mdlRobustTblHeader$study)) %>%
   mutate(lengths = lengths*2) %>%
@@
 
-mdlTbl$coef <- mapvalues(mdlTbl$coef, 
-          from = c("sigmaSq", "tau00", "tau11", "rho01", "rho00", "R2_marginal", "R2_conditional"), 
-          to = c("$\\sigma^2$", "$\\tau_{00}$", "$\\tau_{11}$", "$\\rho_{01}$", "$\\rho_{00}$", "$R^2_{marginal}$", "$R^2_{conditional}$"))
-
-# Still need to pack rows
-mdlTbl %>%
+mdlRobustTbl$coef <- mapvalues(
+  mdlRobustTbl$coef,
+  from = c(
+    "sigmaSq",
+    "tau00",
+    "tau11",
+    "rho01",
+    "rho00",
+    "R2_marginal",
+    "R2_conditional", 
+    "R2Marg_R2Cond"
+  ),
+  to = c(
+    "$\\sigma^2$",
+    "$\\tau_{00}$",
+    "$\\tau_{11}$",
+    "$\\rho_{01}$",
+    "$\\rho_{00}$",
+    "$R^2_{marginal}$",
+    "$R^2_{conditional}$",
+    "$R^2_{marginal}$ / $R^2_{conditional}$"
+  )
+)
+
+# Long Table
+mdlTblRobustLong <- mdlRobustTbl %>%
   replace(is.na(.), "") %>%
@@
     .,
-    caption = "Core Need Fulfillment and Allport's Conditions",
+    caption = "Robustness Analyses",
     #format = "latex",
@@
     booktabs = T,
-    align = rep("c", ncol(.)),
+    align = c("l", rep("c", ncol(.) - 1)),
     escape = FALSE,
@@
   kable_classic() %>%
-  add_header_above(., mdlTblHeader2) %>%
-  add_header_above(., mdlTblHeaderFreq) %>%
-  pack_rows("Fixed", 1, 4) %>%
-  pack_rows("Random", 5, 9) %>%
-  pack_rows("Fit", 10, 21)
-
-```
+  add_header_above(., mdlRobustTblHeaderStudy) %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Contact [Full Sample]" = 6,
+      "Self-Determination Theory [Outgroup Interactions only]" = 6
+    )
+  ) %>%
+  pack_rows("Fixed", 1, 7) %>%
+  pack_rows("Random", 8, 12) %>%
+  pack_rows("Fit", 13, 25) %>%
+  footnote(
+    general = c("PID = Participant ID number (grouping variable)",
+                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
+                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
+    )
+  ) %>%
+  gsub("_cwc", "", ., fixed = TRUE)
+
+# shortened Table
+mdlTblRobustShort <- mdlRobustTbl %>%
+  replace(is.na(.), "")
+names(mdlTblRobustShort) <- make.unique(names(mdlTblRobustShort))
+mdlTblRobustShort <- mdlTblRobustShort %>%
+  filter(
+    !coef %in% c(
+      "data",
+      "formula",
+      "groupId",
+      "$R^2_{marginal}$",
+      "$R^2_{conditional}$",
+      "logLik",
+      "deviance"
+    )
+  ) %>%
+  kbl(
+    .,
+    caption = "Robustness Analyses",
+    format = "latex",
+    linesep = "",
+    booktabs = TRUE,
+    col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)),
+    align = c("l", rep("c", ncol(.) - 1)),
+    escape = FALSE,
+    digits = 3
+  )  %>%
+  kable_classic() %>%
+  add_header_above(., mdlRobustTblHeaderStudy) %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Contact [Full Sample]" = 6,
+      "Self-Determination Theory [Outgroup Interactions only]" = 6
+    )
+  ) %>%
+  pack_rows("Fixed", 1, 7) %>%
+  pack_rows("Random", 8, 12) %>%
+  pack_rows("Fit", 13, 18) %>%
+  footnote(
+    general = c("PID = Participant ID number (grouping variable)",
+                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
+                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
+    )
+  ) %>%
+  gsub("_cwc", "", ., fixed = TRUE)  %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/mdlRobustness.tex")
+mdlTblRobustShort
+```
+
+\input{Tables/mdlContactGeneral}
+\input{Tables/mdlTheory}
+\input{Tables/mdlRobustness}
 

### 2021-12-16 scripts/functions/MlTbl.R

@@ -1,5 +1,5 @@
-#obj <- mdlWorker$lmerInterceptAttTypeTbl
-#objz <- mdlWorker$lmerInterceptAttTypeTblZ
+#obj <- mdlWorkerLmerSlopesAttCoreInt
+#objz <- mdlWorkerLmerSlopesAttCoreIntZ
 
 lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   # Summarize models
@@ -14,9 +14,10 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
     as.data.frame %>%
     tibble::rownames_to_column(., "coef")
   confZ <- confint(objz, 
-                   method = "boot", 
-                   parallel = "multicore", 
-                   ncpus = parallel::detectCores(logical = TRUE)) %>% 
+                   method = "Wald") %>% 
+                   #method = "boot", 
+                   #parallel = "multicore", 
+                   #ncpus = parallel::detectCores(logical = TRUE)) %>% 
     as.data.frame %>%
     tibble::rownames_to_column(., "coef")
   coefZOut <- merge(coefZ, confZ)
@@ -34,10 +35,12 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   coef <- smry$coeftable %>% 
     as.data.frame %>%
     tibble::rownames_to_column(., "coef")
-  conf <- confint(obj) %>% 
+  conf <- confint(obj,
+                  method = "Wald") %>% 
+                  #method = "profile") %>% 
     as.data.frame %>%
     tibble::rownames_to_column(., "coef")
-  coefOut <- merge(coef, conf)
+  coefOut <- join(coef, conf, by = "coef")
   colnames(coefOut) <- c("coef", "est", "se", "tval", "df", "p", "lwr", "upr")
   coefOut$B <- paste0(
     format(round(coefOut$est, 2), nsmall = 2),
@@ -52,11 +55,14 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
     "]"
   )
   coefOut <- 
-    merge(
-      coefOut, 
+    join(
+      coefOut %>% 
+        mutate(coef = gsub('_cwc', '', coef)), 
       coefZOut %>% 
         select(coef, Beta) %>% 
-        mutate(coef = gsub('_zwc|Z$', '', coef))
[…]

### 2021-12-16 Methods-and-Results.Rmd
results re-render with result tables

@@
 First, to ensure that the effect of core need fulfillment is specific to an actual interaction, we compared it core need fulfillement in situations without an interaction.
-For this, we analzed the generalized situational core need fulfillment (either during an interaction or about the daytime in general) and tested whether the effect differed during daily diary measurements with and without outgroup contacts.
-We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteractionYes")`).
+For this, we analyzed the generalized situational core need fulfillment (either during an interaction or about the daytime in general) and tested whether the effect differed during daily diary measurements with and without outgroup contacts.
+We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`).
 Together with a significant main effect of having an outgroup contact, this indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
@@
 We again checked for alternative models.
-First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is only a minuscule main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc:OutgroupInteractionYes")`).
-Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteractionYes")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is only a minuscule main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc:OutgroupInteraction")`).
+Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteraction")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
 This finding is consistent with the results of the previous study, albeit with slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction).
@@
 )
-for (i in 1:length(mdlPrepGeneral)){
+for (i in 1:length(mdlPrepLmGeneral)){
   mdlTblGeneralLm <- join(mdlTblGeneralLm, mdlPrepLmGeneral[[i]]$mdlTbl, by = "coef")
@@
   kable_classic() %>%
-  add_header_above(., mdlRobustTblHeaderStudy) %>%
+  add_header_above(., mdlTblGeneralHeaderStudy) %>%
   add_header_above(

### 2021-12-16 Methods-and-Results.tex
results re-render with result tables

@@
 post measurement survey that mirrored the pre-measurement. All key
-variables in for this study were part of the short daily diary surveys.
+variables for this study were part of the short daily diary surveys.
 
@@
 was fulfilled during the interaction or the past daytime period:
-``\textit{[The interaction / you] fulfilled your goal: [-previous text entry-]}''
+``\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}''
 on a continuous slider scale ranging from strongly disagree (-50) to
@@
 independently; For full results see Online Supplementary Materials
-B)\footnote{Interestingly, adding random slopes to this model did not significantly add explained variance.
-This is unusual because this might indicate the the effect is very consistent across participants.
-However, this might also be the case due to a small number of participants, or other measurement issues.}.
+B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+This is unusual and might indicate the the effect is very consistent across participants.
+However, the small number of participants, or other measurement issues provide an alternative explanation}.
 Thus, in our first data we find mixed results, where outgroup contacts
@@
 fulfilled the person's core situational need. This should, in turn, be
-due to a higher perceived interaction quality. We will this sequentially
-test whether the fulfillment of the core need during an interaction is
-(1) related to more positive outgroup attitudes, (2) higher perceived
+due to a higher perceived interaction quality. We will sequentially test
+whether the fulfillment of the core need during an interaction is (1)
+related to more positive outgroup attitudes, (2) higher perceived
 interaction quality, and (3) whether the variance explained by the core
@@
 in this data set the fulfillment of core situational needs had a
-significant influence on outgroup attitudes and that this effect is
-likely explained by its effect through perceived interaction quality.
+significant influence on outgroup attitudes; this effect likely being
+explained by its effect through perceived interaction quality.
 
@@
 To build further confidence in our results, we assessed two additional
-models that might offer alternative explanations of the effects we find.
-First, to make certain that the effect of core need fulfillment is
-specific to the interaction we compare the the effect to fulfillment of
-the situation core need when no outgroup interaction took place. Here we
-go back to the full dataset and assess the generalized situational core
+models that might offer alternative explanations. First, to ensure that
+the effect of core need fulfillment is specific to an actual
+interaction, we compared it core need fulfillement in situations without
+an interaction. For this, we analyzed the generalized situational core
 need fulfillment (either during an interaction or about the daytime in
-general) and whether the effect differed during daily diary measurements
-with and without outgroup contacts. We find that there is no main effect
-of core need fulfillment (random slopes model; \textit{b} = 0.03,
-\textit{t}(1199) = 1.07, \textit{p} = 0.284, \textit{95\%CI}{[}-0.02,
-0.08{]}) but a significant interaction effect of core need fulfillment
+general) and tested whether the effect differed during daily diary
+measurements with and without outgroup contacts. We found no main effect
+of core need fulfillment (random slopes model; \textit{b} = -0.10,
+\textit{t}(1199) = -2.22, \textit{p} = 0.026, \textit{95\%CI}{[}-0.18,
+-0.01{]}) but a significant interaction effect of core need fulfillment
 and outgroup contact (\textit{b} = 0.13, \textit{t}(1199) = 4.31,
@@
 
-In a final step we check whether during the interaction the core
-situational need is a meaningful predictor even when taking other
-fundamental psychological needs into account. We focus on the three
-commonly considered self determination needs: competence, autonomy, and
-relatedness. We find that the core need adds significantly above a model
-with only the self determination theory needs (random slopes models;
-\(\chi^2\)(6, \textit{N} = 21) = 19.60, \textit{p} = 0.003). We find
-that next to relatedness (\textit{b} = 0.10, \textit{t}(361) = 4.04,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the core
-need explains the most variance in outgroup attitudes after an outgroup
+In a final step, we controlled for other fundamental psychological needs
+during the interaction. We focus on the three commonly considered self
+determination needs: competence, autonomy, and relatedness. We find that
+the core need adds significantly above a model with only the self
+determination theory needs (random slopes models; \(\chi^2\)(6,
+\textit{N} = 21) = 19.60, \textit{p} = 0.003). We find that next to
+relatedness (\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the core need
+explains the most variance in outgroup attitudes after an outgroup
 contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p} = 0.026,
@@
 the SDT needs, the core need fulfillment flexibly takes on some of the
-explained variance of all of the three fundamental needs and competence
-and autonomy needs are non-significant (all \textit{b} \textless{} 0.05,
+explained variance of all three fundamental needs (competence and
+autonomy needs turning non-significant; all \textit{b} \textless{} 0.05,
 all \textit{p} \textgreater{} 0.544). For full results see Online
@@
 
-The aim of our study is similar to that of the first study, as we again
-test the general contact hypothesis, the influence of core need
-fulfillment, and perceived interaction quality during intergroup
-contacts. However, in this second study we collected a substantially
-larger intensive longitudinal survey study with recently arrived
-international students in the Netherlands. The survey method again
-offers a large body of ecologically valid data on need satisfaction in
-real-life intergroup contact situations as these students will likely
-interact with the Dutch majority outgroup on a daily basis. Data was
-collected from November 19th, 2018 through January 6th, 2019.
+The aim of Study 2 is similar to Study 1, as we again test the general
+contact hypothesis, the influence of core need fulfillment, and
+perceived interaction quality during intergroup contacts. However, in
+this second study we collected a substantially larger sample of
+international students who recently arrived in the Netherlands and also
+improved the study design (e.g.~pop up explanations described later).
+The survey method again offers a large body of ecologically valid data
+on need satisfaction in real-life intergroup contact situations as these
+students will likely interact with the Dutch majority outgroup on a
+daily basis. Data was collected from November 19th, 2018 through January
+6th, 2019.
 
@@
 After receiving ethical approval from the University of Groningen, we
-recruited 113 international students using a local participant pool and
+recruited 113 international students using a local participant pool. We
 specifically targeted non-Dutch students, who had recently arrived in
@@
 (\textit{n} = 2608) and afternoons (\textit{n} = 2357). All key
-variables in for this study were part of the short daily diary surveys.
+variables for this study were part of the short daily diary surveys.
 
@@
 The ratings of the perceived interaction quality was identical to study
-one..
+one.
 
@@
 
-Attitudes towards the Dutch majority outgroup was again measured using
-the feeling thermometer, as in study one. All survey details are also
+As in Study 1, attitudes towards the Dutch majority outgroup were again
+measured using the feeling thermometer. All survey details are also
 available in Online Supplemental Materials A and B.
@@
 number of interactions and average interaction quality jointly in a
-linear regression, we a main effect of intergroup contacts to predict
-outgroup attitudes (\textit{b} = 0.81, \textit{t}(109) = 3.29,
+linear regression, we find a main effect of intergroup contacts to
+predict outgroup attitudes (\textit{b} = 0.81, \textit{t}(109) = 3.29,
 \textit{p} = 0.001, \(\eta_p^2\) = 0.08). Given the missing aggregate
 relationship between average interaction quality and outgroup attitudes,
-we find no significant effect of average perceived contact quality. Nor
-do we find that in this sample the impact of the number of interactions
-is moderated by the average contact quality. This is not entirely
-consistent with the first study, where average contact quality did have
-a meaningful effect on outgroup attitudes. This finding is not
+we find no significant effect of average perceived contact quality. We
+also do not find that in this sample the impact of the number of
+interactions is moderated by the average contact quality. This is not
+entirely consistent with the first study, where average contact quality
+did have a meaningful effect on outgroup attitudes. This finding is not
 necessarily surprising given that the variables aggregate all within
@@
 \textless{} .001, \textit{95\%CI}{[}1.45, 4.54{]}), even after
-controlling for having an interaction with a non-Dutch (which did not
-relate to outgroup attitudes independently; For full results see Online
-Supplementary Materials B). Thus, in our second dataset we find mixed
-results, outgroup contacts show a positive effect on outgroup attitudes
-in the moment and on average between participants. However, we find that
-this effect does not depend on the average perceived interaction
-quality. This unexpected results, might be due to the aggregation
-process and the following analyses will focus in on the role of the
-perceived interaction quality during an outgroup interaction.
+controlling for having an interaction with a non-Dutch person (which did
+not relate to outgroup attitudes independently; For full results see
+Online Supplementary Materials B). Thus, in our second dataset we find
+mixed results, outgroup contacts show a positive effect on outgroup
+attitudes in the moment and on average between participants. However, we
+find that this effect does not depend on the average perceived
+interaction quality. This unexpected results, might be due to the
+aggregation process and the following analyses will focus in on the role
+of the perceived interaction quality during an outgroup interaction.
 
@@
 main effect of core need fulfillment (random slopes model; \textit{b} =
-0.03, \textit{t}(4849) = 3.06, \textit{p} = 0.002,
-\textit{95\%CI}{[}0.01, 0.05{]}) but a stronger interaction effect of
+-0.03, \textit{t}(4849) = -1.34, \textit{p} = 0.181,
+\textit{95\%CI}{[}-0.08, 0.02{]}) but a stronger interaction effect of
 core need fulfillment and outgroup contact (\textit{b} = 0.06,
@@
 contact (\textit{b} = 2.88, \textit{t}(4849) = 3.71, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}1.36, 4.38{]}), this indicates that
+\textless{} .001, \textit{95\%CI}{[}1.36, 4.40{]}), this indicates that
 it is not key need fulfillment in general --- but key need fulfillment
@@
 explained variance of all of the three fundamental needs. However,
-different from the first study, in this larger sample relatedness
-(\textit{b} = 0.07, \textit{t}(823) = 4.26, \textit{p} \textless{} .001,
+different from the first study, relatedness (\textit{b} = 0.07,
+\textit{t}(823) = 4.26, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.04, 0.10{]}) and autonomy (\textit{b} = 0.02,
 \textit{t}(823) = 0.93, \textit{p} = 0.353, \textit{95\%CI}{[}-0.02,
-0.08{]}) also predicted positive outgroup attitudes. For full results
-see Online Supplementary Information B.
+0.08{]}) also predicted positive outgroup attitudes in this larger
+sample. For full results see Online Supplementary Information B.
 
@@
 Supplementary Information B.
+
+\input{Tables/mdlContactGeneral}
+\input{Tables/mdlTheory}
+\input{Tables/mdlRobustness}

### 2021-12-16 Tables/mdlContactGeneral.tex
results re-render with result tables

\begin{table}
\begin{minipage}[t][\textheight][t]{\textwidth}

\caption{\label{tab:intergroupGeneralTbl}Intergroup General}
\centering
\begin{tabular}[t]{lcccccccccccc}
\toprule
\multicolumn{1}{c}{} & \multicolumn{6}{c}{Aggregated [across participants]} & \multicolumn{6}{c}{Contemporaneous [within participants]} \\
\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
\multicolumn{1}{c}{} & \multicolumn{2}{c}{Study 1} & \multicolumn{2}{c}{Study 2} & \multicolumn{2}{c}{Study 3} & \multicolumn{2}{c}{Study 1} & \multicolumn{2}{c}{Study 2} & \multicolumn{2}{c}{Study 3} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){12-13}
 & $B$ & $\eta_p$ & $B$ & $\eta_p$ & $B$ & $\eta_p$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$\\
\midrule
(Intercept) & 70.50**** [66.06, 74.94] &  & 67.62**** [64.16, 71.08] &  & 64.83**** [61.50, 68.16] &  & 67.44**** [61.71, 73.17] &  & 63.72**** [59.42, 68.01] &  & 56.30**** [51.58, 61.02] & \\
SumContactNL & 0.27 [-0.15,  0.69] & 0.02 & 0.81** [ 0.32,  1.29] & 0.08 & 0.15 [-0.08,  0.38] & 0.02 &  &  &  &  &  & \\
AvQuality & 0.84** [ 0.36,  1.33] & 0.39 & 0.25 [-0.14,  0.64] & 0.01 & 0.36* [ 0.04,  0.68] & 0.07 &  &  &  &  &  & \\
SumContactNL:AvQuality & -0.05** [-0.08, -0.01] & 0.34 & 0.02 [-0.03,  0.08] & 0.01 & 0.01 [-0.02,  0.03] & 0.01 &  &  &  &  &  & \\
OutgroupInteraction &  &  &  &  &  &  & 2.48**** [ 1.36,  3.59] & 1.07 [ 0.59,  1.54] & 2.99*** [ 1.45,  4.54] & 0.11 [ 0.07, 0.16] & 5.63**** [ 3.97,  7.29] & 0.21 [ 0.15, 0.27]\\
NonOutgroupInteraction &  &  &  &  &  &  & 0.43 [-0.68,  1.54] & 0.16 [-0.32,  0.63] & 0.01 [-0.76,  0.78] & 0.01 [-0.03, 0.05] & 0.34 [-0.49,  1.18] & 0.02 [-0.02, 0.05]\\
\addlinespace[0.3em]
\multicolumn{13}{l}{\textbf{Random}}\\
\hspace{1em}$\sigma^2$ &  &  &  &  &  &  & 69.92 &  & 77.46 &  & 88.1 & \\
\hspace{1em}$\tau_{00}$ &  &  &  &  &  &  & 164.13 (PID) &  & 488.38 (PID) &  & 366.51 (PID) & \\
$\tau_{11}$ &  &  &  &  &  &  &  &  & 48.94 (PID.OutgroupInteraction)
 7.23 (PID.NonOutgroupInteraction) &  & 40.53 (PID.OutgroupInteraction)
\hspace{1em} 3.43 (PID.NonOutgroupInteraction) & \\
$\rho_{01}$ &  &  &  &  &  &  &  &  & -0.72 (PID.OutgroupInteraction)
 0.12 (PID.NonOutgroupInteraction) &  & -0.70 (PID.OutgroupInteraction)
\hspace{1em}-0.28 (PID.NonOutgroupInteraction) & \\
\hspace{1em}$\rho_{00}$ &  &  &  &  &  &  &  &  & 0.00 (PID.OutgroupInteraction-NonOutgroupInteraction) &  & 0.26 (PID.OutgroupInteraction-NonOutgroupInteraction) & \\
\addlinespace[0.3em]
\multicolumn{13}{l}{\textbf{Fit}}\\
\hspace{1em}Groups &  &  &  &  &  &  & 23 &  & 113 &  & 71 & \\
\hspace{1em}N & 21 &  & 113 &  & 71 &  & 1225 &  & 4965 &  & 3907 & \\
\hspace{1em}F Test & F(3, 17) = 6.66, p =  0.004 &  & F(3, 109) = 3.75, p =  0.013 &  & F(3, 67) = 2.15, p =  0.102 &  &  &  &  &  &  & \\
\hspace{1em}$R^{2 (a)}$ & 0.540 / 0.459 &  & 0.094 / 0.069 &  & 0.088 / 0.047 &  & 0.006 / 0.703 &  & 0.003 / 0.817 &  & 0.026 / 0.708 & \\
\hspace{1em}AIC &  &  &  &  &  &  & 8788 &  & 36476 &  & 29074 & \\
\hspace{1em}BIC &  &  &  &  &  &  & 8814 &  & 36542 &  & 29137 & \\
\hspace{1em}ICC &  &  &  &  &  &  & 0.7013 &  & 0.8167 &  & 0.7007 & \\
\bottomrule
\multicolumn{13}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{13}{l}{\rule{0pt}{1em}PID = Participant ID number (grouping variable)}\\
\multicolumn{13}{l}{\rule{0pt}{1em}\$\textbackslash{}sigma\textasciicircum{}2\$: residual variance, \$\textbackslash{}tau\_\{00\}\$: random intercept variance, \$\textbackslash{}tau\_\{11\}\$: random slope variance(s), \$\textbackslash{}rho\_\{01\}\$: random slope-intercept correlation(s) , \$\textbackslash{}rho\_\{00\}\$: correlation(s) between random slopes}\\
\multicolumn{13}{l}{\rule{0pt}{1em}**** \$p\$ < .0001, *** \$p\$ < .001, ** \$p\$ < .01, * \$p\$ < .05}\\
\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{a} For linear regression: \$R\textasciicircum{}2 / R\textasciicircum{}2\_\{adjusted\}\$, for multilevel regression: \$R\textasciicircum{}2\_\{marginal\} / R\textasciicircum{}2\_\{conditional\}\$ }\\
\end{tabular}
\end{minipage}
\end{table}

### 2021-12-16 Tables/mdlRobustness.tex
results re-render with result tables

\begin{table}
\begin{minipage}[t][\textheight][t]{\textwidth}

\caption{\label{tab:robustnessTbl}Robustness Analyses}
\centering
\begin{tabular}[t]{lcccccccccccc}
\toprule
\multicolumn{1}{c}{} & \multicolumn{6}{c}{Contact [Full Sample]} & \multicolumn{6}{c}{Self-Determination Theory [Outgroup Interactions only]} \\
\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
\multicolumn{1}{c}{} & \multicolumn{2}{c}{Study 1} & \multicolumn{2}{c}{Study 2} & \multicolumn{2}{c}{Study 3} & \multicolumn{2}{c}{Study 1} & \multicolumn{2}{c}{Study 2} & \multicolumn{2}{c}{Study 3} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){12-13}
 & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$\\
\midrule
\addlinespace[0.3em]
\multicolumn{13}{l}{\textbf{Fixed}}\\
\hspace{1em}(Intercept) & 68.88**** [63.24, 74.53] &  & 63.90**** [59.56, 68.24] &  & 57.06**** [52.63, 61.48] &  & 72.53**** [66.79, 78.27] &  & 70.69**** [67.53, 73.85] &  & 68.32**** [65.11, 71.53] & \\
\hspace{1em}CoreNeed & -0.10* [-0.18, -0.01] & 0.15 [ 0.07, 0.22] & -0.03 [-0.08,  0.02] & 0.08 [ 0.05, 0.12] & -0.14**** [-0.21, -0.08] & 0.12 [ 0.08, 0.16] & 0.09* [ 0.01,  0.18] & 0.20 [ 0.09, 0.31] & 0.08** [ 0.03,  0.13] & 0.08 [ 0.00, 0.16] & 0.15*** [ 0.07,  0.22] & 0.13 [ 0.07, 0.20]\\
\hspace{1em}OutgroupInteraction & 1.81* [ 0.25,  3.37] & 0.14 [ 0.03, 0.24] & 2.88*** [ 1.36,  4.40] & 0.11 [ 0.06, 0.15] & 5.41**** [ 3.74,  7.07] & 0.21 [ 0.15, 0.27] &  &  &  &  &  & \\
\hspace{1em}CoreNeed:OutgroupInteraction & 0.13**** [ 0.07,  0.18] & 0.13 [ 0.07, 0.18] & 0.06** [ 0.02,  0.10] & 0.04 [ 0.01, 0.08] & 0.17**** [ 0.12,  0.21] & 0.08 [ 0.05, 0.11] &  &  &  &  &  & \\
\hspace{1em}Competence &  &  &  &  &  &  & 0.05 [-0.16,  0.25] & -0.05 [-0.21, 0.11] & 0.06* [ 0.01,  0.10] & 0.07 [-0.02, 0.17] & 0.06* [ 0.02,  0.10] & 0.09 [ 0.02, 0.15]\\
\hspace{1em}Autonomy &  &  &  &  &  &  & 0.06 [-0.12,  0.23] & 0.20 [ 0.09, 0.31] & 0.03 [-0.02,  0.08] & 0.04 [-0.06, 0.14] & 0.04 [-0.01,  0.08] & 0.06 [-0.01, 0.13]\\
\hspace{1em}Relatedness &  &  &  &  &  &  & 0.10*** [ 0.05,  0.14] & 0.23 [ 0.13, 0.34] & 0.07*** [ 0.04,  0.10] & 0.17 [ 0.09, 0.25] & 0.06** [ 0.02,  0.09] & 0.11 [ 0.05, 0.18]\\
\addlinespace[0.3em]
\multicolumn{13}{l}{\textbf{Random}}\\
\hspace{1em}$\sigma^2$ & 64.7 &  & 77.34 &  & 84.37 &  & 41.11 &  & 82.65 &  & 83.36 & \\
\hspace{1em}$\tau_{00}$ & 174.00 (PID) &  & 523.56 (PID) &  & 339.72 (PID) &  & 176.39 (PID) &  & 262.18 (PID) &  & 181.84 (PID) & \\
$\tau_{11}$ & 0.01 (PID.CoreNeed)
6.05 (PID.OutgroupInteraction) &  & 0.00 (PID.CoreNeed)
46.82 (PID.OutgroupInteraction) &  & 0.01 (PID.CoreNeed)
40.96 (PID.OutgroupInteraction) &  & 0.02 (PID.CoreNeed)
0.20 (PID.Competence)
0.14 (PID.Autonomy)
0.00 (PID.Relatedness) &  & 0.01 (PID.CoreNeed)
0.00 (PID.Competence)
0.00 (PID.Autonomy)
0.00 (PID.Relatedness) &  & 0.05 (PID.CoreNeed)
0.01 (PID.Competence)
0.00 (PID.Autonomy)
\hspace{1em}0.01 (PID.Relatedness) & \\
$\rho_{01}$ & 0.01 (PID.CoreNeed)
-0.27 (PID.OutgroupInteraction) &  & 0.27 (PID.CoreNeed)
-0.68 (PID.OutgroupInteraction) &  & -0.15 (PID.CoreNeed)
-0.68 (PID.OutgroupInteraction) &  & 0.55 (PID.CoreNeed)
-0.15 (PID.Competence)
-0.09 (PID.Autonomy)
 0.56 (PID.Relatedness) &  & -0.16 (PID.CoreNeed)
-0.05 (PID.Competence)
-0.44 (PID.Autonomy)
-0.20 (PID.Relatedness) &  & -0.25 (PID.CoreNeed)
-0.29 (PID.Competence)
-0.23 (PID.Autonomy)
\hspace{1em} 0.02 (PID.Relatedness) & \\
$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & 0.03 (PID.CoreNeed-Autonomy)
-0.93 (PID.Competence-Autonomy)
-0.11 (PID.CoreNeed-Competence)
 0.17 (PID.CoreNeed-Relatedness)
 0.16 (PID.Competence-Relatedness)
-0.10 (PID.Autonomy-Relatedness) &  & 0.60 (PID.CoreNeed-Autonomy)
 0.83 (PID.Competence-Autonomy)
 0.20 (PID.CoreNeed-Competence)
 0.42 (PID.CoreNeed-Relatedness)
-0.79 (PID.Competence-Relatedness)
-0.35 (PID.Autonomy-Relatedness) &  & 0.57 (PID.CoreNeed-Autonomy)
-0.68 (PID.Competence-Autonomy)
 0.09 (PID.CoreNeed-Competence)
-0.27 (PID.CoreNeed-Relatedness)
-0.31 (PID.Competence-Relatedness)
\hspace{1em}-0.08 (PID.Autonomy-Relatedness) & \\
\addlinespace[0.3em]
\multicolumn{13}{l}{\textbf{Fit}}\\
\hspace{1em}AIC & 8761 &  & 36475 &  & 28974 &  & 2757 &  & 7219 &  & 12581 & \\
\hspace{1em}BIC & 8817 &  & 36546 &  & 29043 &  & 2840 &  & 7321 &  & 12695 & \\
\hspace{1em}N & 1225 &  & 4965 &  & 3909 &  & 386 &  & 935 &  & 1672 & \\
\hspace{1em}Groups & 23 &  & 113 &  & 71 &  & 21 &  & 108 &  & 70 & \\
\hspace{1em}ICC & 0.722 &  & 0.8168 &  & 0.7112 &  &  &  &  &  & 0.6997 & \\
\hspace{1em}$R^2_{marginal}$ / $R^2_{conditional}$ & 0.017 / 0.727 &  & 0.005 / 0.818 &  & 0.036 / 0.722 &  & 0.249 / NA &  & 0.093 / NA &  & 0.035 / 0.710 & \\
\bottomrule
\multicolumn{13}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{13}{l}{\rule{0pt}{1em}PID = Participant ID number (grouping variable)}\\
\multicolumn{13}{l}{\rule{0pt}{1em}\$\textbackslash{}sigma\textasciicircum{}2\$: residual variance, \$\textbackslash{}tau\_\{00\}\$: random intercept variance, \$\textbackslash{}tau\_\{11\}\$: random slope variance(s), \$\textbackslash{}rho\_\{01\}\$: random slope-intercept correlation(s) , \$\textbackslash{}rho\_\{00\}\$: correlation(s) between random slopes}\\
\multicolumn{13}{l}{\rule{0pt}{1em}**** \$p\$ < .0001, *** \$p\$ < .001, ** \$p\$ < .01, * \$p\$ < .05}\\
\end{tabular}
\end{minipage}
\end{table}

### 2021-12-16 Tables/mdlTheory.tex
results re-render with result tables

\begin{table}
\begin{minipage}[t][\textheight][t]{\textwidth}

\caption{\label{tab:intergroupNeedsTbl}Core Need Fulfillment and Allport's Conditions}
\centering
\begin{tabular}[t]{ccccccccccccccccccccccccccc}
\toprule
\multicolumn{1}{c}{} & \multicolumn{6}{c}{Study 1 - CoreNeed} & \multicolumn{6}{c}{Study 2 - CoreNeed} & \multicolumn{6}{c}{Study 3 - CoreNeed} & \multicolumn{6}{c}{Study 3 - Allport} & \multicolumn{2}{c}{Study 3 - CoreNeed + Allport} \\
\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13} \cmidrule(l{3pt}r{3pt}){14-19} \cmidrule(l{3pt}r{3pt}){20-25} \cmidrule(l{3pt}r{3pt}){26-27}
\multicolumn{1}{c}{} & \multicolumn{2}{c}{Quality } & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Quality } & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Quality } & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Quality } & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Attitude} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){12-13} \cmidrule(l{3pt}r{3pt}){14-15} \cmidrule(l{3pt}r{3pt}){16-17} \cmidrule(l{3pt}r{3pt}){18-19} \cmidrule(l{3pt}r{3pt}){20-21} \cmidrule(l{3pt}r{3pt}){22-23} \cmidrule(l{3pt}r{3pt}){24-25} \cmidrule(l{3pt}r{3pt}){26-27}
 & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$\\
\midrule
\addlinespace[0.3em]
\multicolumn{27}{l}{\textbf{Fixed}}\\
\hspace{1em}(Intercept) & 24.28**** [20.20, 28.36] &  & 72.53**** [66.83, 78.24] &  & 72.50**** [66.75, 78.24] &  & 78.84**** [76.86, 80.83] &  & 70.71**** [67.55, 73.87] &  & 70.67**** [67.50, 73.84] &  & 81.36**** [78.53, 84.19] &  & 68.32**** [65.10, 71.54] &  & 68.32**** [65.09, 71.54] &  & 81.42**** [78.57, 84.26] &  & 68.36**** [65.16, 71.56] &  & 68.34**** [65.12, 71.56] &  & 68.33**** [65.05, 71.61] & \\
\hspace{1em}CoreNeed & 0.42**** [ 0.32,  0.52] & 0.40 [ 0.31, 0.49] & 0.17** [ 0.06,  0.29] & 0.30 [ 0.18, 0.41] & 0.04 [-0.08,  0.15] & 0.13 [ 0.00, 0.26] & 0.40**** [ 0.28,  0.52] & 0.27 [ 0.18, 0.37] & 0.13*** [ 0.07,  0.19] & 0.14 [ 0.06, 0.22] & 0.03 [-0.01,  0.07] & 0.07 [-0.01, 0.15] & 0.43**** [ 0.33,  0.54] & 0.31 [ 0.24, 0.38] & 0.19**** [ 0.12,  0.27] & 0.18 [ 0.11, 0.24] & 0.11** [ 0.05,  0.17] & 0.11 [ 0.05,  0.17] &  &  &  &  &  &  & 0.13**** [ 0.08,  0.17] & 0.12 [ 0.05, 0.18]\\
\hspace{1em}Quality &  &  &  &  & 0.23*** [ 0.12,  0.33] & 0.41 [ 0.29, 0.54] &  &  &  &  & 0.17**** [ 0.11,  0.23] & 0.24 [ 0.14, 0.34] &  &  &  &  & 0.17**** [ 0.12,  0.22] & 0.17 [ 0.12,  0.22] &  &  &  &  & 0.17**** [ 0.12,  0.23] & 0.22 [ 0.15, 0.29] &  & \\
\hspace{1em}Allport &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 0.65**** [ 0.54,  0.76] & 0.46 [ 0.39, 0.52] & 0.22**** [ 0.15,  0.29] & 0.21 [ 0.14, 0.27] & 0.09** [ 0.03,  0.15] & 0.10 [ 0.03, 0.16] & 0.17*** [ 0.09,  0.24] & 0.17 [ 0.11, 0.23]\\
\addlinespace[0.3em]
\multicolumn{27}{l}{\textbf{Random}}\\
\hspace{1em}$\sigma^2$ & 261.1 &  & 63.1 &  & 37.61 &  & 275.7 &  & 89.83 &  & 76.47 &  & 222.5 &  & 91.84 &  & 82.15 &  & 188.9 &  & 93.05 &  & 83.82 &  & 90.78 & \\
\hspace{1em}$\tau_{00}$ & 71.13 (PID) &  & 172.54 (PID) &  & 177.20 (PID) &  & 63.00 (PID) &  & 259.79 (PID) &  & 264.19 (PID) &  & 131.33 (PID) &  & 182.38 (PID) &  & 183.10 (PID) &  & 134.62 (PID) &  & 179.74 (PID) &  & 182.79 (PID) &  & 189.33 (PID) & \\
$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed)
0.04 (PID.Quality) &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & 0.00 (PID.CoreNeed)
0.04 (PID.Quality) &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & 0.03 (PID.CoreNeed)
0.02 (PID.Quality) &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & 0.02 (PID.Allport)
0.02 (PID.Quality) &  & 0.00 (PID.CoreNeed)
\hspace{1em}0.04 (PID.Allport) & \\
$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & 0.37 (PID.CoreNeed)
-0.22 (PID.Quality) &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & -0.18 (PID.CoreNeed)
-0.06 (PID.Quality) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.14 (PID.CoreNeed)
-0.41 (PID.Quality) &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & 0.12 (PID.Allport)
-0.51 (PID.Quality) &  & -1.00 (PID.CoreNeed)
\hspace{1em}-0.07 (PID.Allport) & \\
\hspace{1em}$\rho_{00}$ &  &  &  &  & -0.47 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.79 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.10 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.11 (PID.Allport-Quality) &  & 0.07 (PID.CoreNeed-Allport) & \\
\addlinespace[0.3em]
\multicolumn{27}{l}{\textbf{Fit}}\\
\hspace{1em}AIC & 3294 &  & 2816 &  & 2672 &  & 8073 &  & 7222 &  & 7141 &  & 14054 &  & 12632 &  & 12494 &  & 13805 &  & 12652 &  & 12519 &  & 12625 & \\
\hspace{1em}BIC & 3309 &  & 2839 &  & 2712 &  & 8102 &  & 7251 &  & 7190 &  & 14087 &  & 12665 &  & 12548 &  & 13838 &  & 12684 &  & 12573 &  & 12679 & \\
\hspace{1em}N & 387 &  & 387 &  & 387 &  & 935 &  & 935 &  & 935 &  & 1676 &  & 1672 &  & 1672 &  & 1676 &  & 1672 &  & 1672 &  & 1672 & \\
\hspace{1em}Groups & 21 &  & 21 &  & 21 &  & 108 &  & 108 &  & 108 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 & \\
\hspace{1em}ICC & 0.2141 &  & 0.7447 &  & 0.8399 &  & 0.2547 &  & 0.7471 &  & 0.7835 &  & 0.3933 &  & 0.6738 &  & 0.7006 &  & 0.4433 &  & 0.6679 &  & 0.6963 &  &  & \\
\hspace{1em}$R^2_{marginal}$ / $R^2_{conditional}$ & 0.117 / 0.306 &  & 0.030 / 0.752 &  & 0.067 / 0.851 &  & 0.102 / 0.331 &  & 0.012 / 0.750 &  & 0.028 / 0.789 &  & 0.070 / 0.436 &  & 0.019 / 0.680 &  & 0.041 / 0.713 &  & 0.149 / 0.526 &  & 0.024 / 0.676 &  & 0.040 / 0.709 &  & 0.086 / NA & \\
\bottomrule
\multicolumn{27}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{27}{l}{\rule{0pt}{1em}PID = Participant ID number (grouping variable)}\\
\multicolumn{27}{l}{\rule{0pt}{1em}\$\textbackslash{}sigma\textasciicircum{}2\$: residual variance, \$\textbackslash{}tau\_\{00\}\$: random intercept variance, \$\textbackslash{}tau\_\{11\}\$: random slope variance(s), \$\textbackslash{}rho\_\{01\}\$: random slope-intercept correlation(s) , \$\textbackslash{}rho\_\{00\}\$: correlation(s) between random slopes}\\
\multicolumn{27}{l}{\rule{0pt}{1em}**** \$p\$ < .0001, *** \$p\$ < .001, ** \$p\$ < .01, * \$p\$ < .05}\\
\end{tabular}
\end{minipage}
\end{table}

### 2021-12-16 manuscript.tex

@@
 There are however substantial theoretical and practical consequences of these understudied mechanisms of everyday intergroup contact.
-Theoretically, interaction quality or -valence sits at the heart of intergroup contact theory, as it gauges whether the interaction will result to positive intergroup outcomes \citep[][]{Tropp2016, Brown2007}.
-And practically, a longstanding body of literature, has been showing that negative interactions are common in everyday life and often result in a substantial decline of intergroup relations \citep[][]{Barlow2012, Shelton2009}.
-It is thus important that we explore which psychological mechanisms explain when and why intergroup contacts are positive and lead to better intergroup perceptions, especially during everyday intergroup encounters \citep[e.g.,][]{MacInnis2015}.
+Theoretically, interaction quality or -valence sits at the heart of intergroup contact theory, as it gauges whether the interaction will result in positive intergroup outcomes \citep[][]{Tropp2016, Brown2007}.
+Practically, a longstanding body of literature has shown that negative interactions are common in everyday life and often result in a substantial decline of intergroup relations \citep[][]{Barlow2012, Shelton2009}.
+It is thus important to explore which psychological mechanisms explain when and why intergroup contacts are positive and lead to better intergroup perceptions, especially during everyday intergroup encounters \citep[e.g.,][]{MacInnis2015}.
 

### 2021-12-16 Methods-and-Results.Rmd
small tables

@@
   ) %>%
+  kable_styling(latex_options = "scale_down") %>%
   gsub("_cwc", "", ., fixed = TRUE)   %>%
@@
   gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  kableExtra::landscape() 
   save_kable("Tables/mdlContactGeneral.tex")
@@
   ) %>%
+  kable_styling(latex_options = "scale_down") %>%
   gsub("_cwc", "", ., fixed = TRUE)  %>%

### 2021-12-16 Methods-and-Results.Rmd
table rotate

--- 2021-12-16 Methods-and-Results.Rmd
@@
   gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  kableExtra::landscape() %>%
   save_kable("Tables/mdlContactGeneral.tex")
@@
   ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  kableExtra::landscape() %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
@@
   ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  kableExtra::landscape() %>%
   gsub("_cwc", "", ., fixed = TRUE)  %>%

### 2021-12-16 scripts/functions/MlTbl.R

@@ -93,10 +93,10 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   # collect random effect statistics
   restat <- list(
     sigmaSq = sigmaSq,
-    tau00 = ifelse(length(tau00)>1, paste(tau00, collapse = "\n"), tau00),
-    tau11 = ifelse(length(tau11)>1, paste(tau11, collapse = "\n"), tau11),
-    rho01 = ifelse(length(rho01)>1, paste(rho01, collapse = "\n"), rho01),
-    rho00 = ifelse(length(rho00)>1, paste(rho00, collapse = "\n"), rho00)
+    tau00 = ifelse(length(tau00)>1, paste(tau00, collapse = "\\n"), tau00),
+    tau11 = ifelse(length(tau11)>1, paste(tau11, collapse = "\\n"), tau11),
+    rho01 = ifelse(length(rho01)>1, paste(rho01, collapse = "\\n"), rho01),
+    rho00 = ifelse(length(rho00)>1, paste(rho00, collapse = "\\n"), rho00)
   )
   
   

### 2021-12-16 Tables/mdlContactGeneral.tex
small tables
Updates from Overleaf
table rotate
line break table fix

@@
-\begin{table}
+\begin{landscape}\begin{table}
 \begin{minipage}[t][\textheight][t]{\textwidth}
@@
 \centering
+\resizebox{\linewidth}{!}{
 \begin{tabular}[t]{lcccccccccccc}
@@
 \hspace{1em}$\tau_{00}$ &  &  &  &  &  &  & 164.13 (PID) &  & 488.38 (PID) &  & 366.51 (PID) & \\
-$\tau_{11}$ &  &  &  &  &  &  &  &  & 48.94 (PID.OutgroupInteraction)
- 7.23 (PID.NonOutgroupInteraction) &  & 40.53 (PID.OutgroupInteraction)
-\hspace{1em} 3.43 (PID.NonOutgroupInteraction) & \\
-$\rho_{01}$ &  &  &  &  &  &  &  &  & -0.72 (PID.OutgroupInteraction)
- 0.12 (PID.NonOutgroupInteraction) &  & -0.70 (PID.OutgroupInteraction)
-\hspace{1em}-0.28 (PID.NonOutgroupInteraction) & \\
+\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & 48.94 (PID.OutgroupInteraction)\n 7.23 (PID.NonOutgroupInteraction) &  & 40.53 (PID.OutgroupInteraction)\n 3.43 (PID.NonOutgroupInteraction) & \\
+\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & -0.72 (PID.OutgroupInteraction)\n 0.12 (PID.NonOutgroupInteraction) &  & -0.70 (PID.OutgroupInteraction)\n-0.28 (PID.NonOutgroupInteraction) & \\
 \hspace{1em}$\rho_{00}$ &  &  &  &  &  &  &  &  & 0.00 (PID.OutgroupInteraction-NonOutgroupInteraction) &  & 0.26 (PID.OutgroupInteraction-NonOutgroupInteraction) & \\
@@
 \multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{a} For linear regression: \$R\textasciicircum{}2 / R\textasciicircum{}2\_\{adjusted\}\$, for multilevel regression: \$R\textasciicircum{}2\_\{marginal\} / R\textasciicircum{}2\_\{conditional\}\$ }\\
-\end{tabular}
+\end{tabular}}
 \end{minipage}
 \end{table}
+\end{landscape}

### 2021-12-16 Tables/mdlRobustness.tex
small tables
table rotate
line break table fix

@@
 \hspace{1em}$\tau_{00}$ & 174.00 (PID) &  & 523.56 (PID) &  & 339.72 (PID) &  & 176.39 (PID) &  & 262.18 (PID) &  & 181.84 (PID) & \\
-$\tau_{11}$ & 0.01 (PID.CoreNeed)
-6.05 (PID.OutgroupInteraction) &  & 0.00 (PID.CoreNeed)
-46.82 (PID.OutgroupInteraction) &  & 0.01 (PID.CoreNeed)
-40.96 (PID.OutgroupInteraction) &  & 0.02 (PID.CoreNeed)
-0.20 (PID.Competence)
-0.14 (PID.Autonomy)
-0.00 (PID.Relatedness) &  & 0.01 (PID.CoreNeed)
-0.00 (PID.Competence)
-0.00 (PID.Autonomy)
-0.00 (PID.Relatedness) &  & 0.05 (PID.CoreNeed)
-0.01 (PID.Competence)
-0.00 (PID.Autonomy)
-\hspace{1em}0.01 (PID.Relatedness) & \\
-$\rho_{01}$ & 0.01 (PID.CoreNeed)
--0.27 (PID.OutgroupInteraction) &  & 0.27 (PID.CoreNeed)
--0.68 (PID.OutgroupInteraction) &  & -0.15 (PID.CoreNeed)
--0.68 (PID.OutgroupInteraction) &  & 0.55 (PID.CoreNeed)
--0.15 (PID.Competence)
--0.09 (PID.Autonomy)
- 0.56 (PID.Relatedness) &  & -0.16 (PID.CoreNeed)
--0.05 (PID.Competence)
--0.44 (PID.Autonomy)
--0.20 (PID.Relatedness) &  & -0.25 (PID.CoreNeed)
--0.29 (PID.Competence)
--0.23 (PID.Autonomy)
-\hspace{1em} 0.02 (PID.Relatedness) & \\
-$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & 0.03 (PID.CoreNeed-Autonomy)
--0.93 (PID.Competence-Autonomy)
--0.11 (PID.CoreNeed-Competence)
- 0.17 (PID.CoreNeed-Relatedness)
- 0.16 (PID.Competence-Relatedness)
--0.10 (PID.Autonomy-Relatedness) &  & 0.60 (PID.CoreNeed-Autonomy)
- 0.83 (PID.Competence-Autonomy)
- 0.20 (PID.CoreNeed-Competence)
- 0.42 (PID.CoreNeed-Relatedness)
--0.79 (PID.Competence-Relatedness)
--0.35 (PID.Autonomy-Relatedness) &  & 0.57 (PID.CoreNeed-Autonomy)
--0.68 (PID.Competence-Autonomy)
- 0.09 (PID.CoreNeed-Competence)
--0.27 (PID.CoreNeed-Relatedness)
--0.31 (PID.Competence-Relatedness)
-\hspace{1em}-0.08 (PID.Autonomy-Relatedness) & \\
+\hspace{1em}$\tau_{11}$ & 0.01 (PID.CoreNeed)\n6.05 (PID.OutgroupInteraction) &  & 0.00 (PID.CoreNeed)\n46.82 (PID.OutgroupInteraction) &  & 0.01 (PID.CoreNeed)\n40.96 (PID.OutgroupInteraction) &  & 0.02 (PID.CoreNeed)\n0.20 (PID.Competence)\n0.14 (PID.Autonomy)\n0.00 (PID.Relatedness) &  & 0.01 (PID.CoreNeed)\n0.00 (PID.Competence)\n0.00 (PID.Autonomy)\n0.00 (PID.Relatedness) &  & 0.05 (PID.CoreNeed)\n0.01 (PID.Competence)\n0.00 (PID.Autonomy)\n0.01 (PID.Relatedness) & \\
+\hspace{1em}$\rho_{01}$ & 0.01 (PID.CoreNeed)\n-0.27 (PID.OutgroupInteraction) &  & 0.27 (PID.CoreNeed)\n-0.68 (PID.OutgroupInteraction) &  & -0.15 (PID.CoreNeed)\n-0.68 (PID.OutgroupInteraction) &  & 0.55 (PID.CoreNeed)\n-0.15 (PID.Competence)\n-0.09 (PID.Autonomy)\n 0.56 (PID.Relatedness) &  & -0.16 (PID.CoreNeed)\n-0.05 (PID.Competence)\n-0.44 (PID.Autonomy)\n-0.20 (PID.Relatedness) &  & -0.25 (PID.CoreNeed)\n-0.29 (PID.Competence)\n-0.23 (PID.Autonomy)\n 0.02 (PID.Relatedness) & \\
+\hspace{1em}$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & 0.03 (PID.CoreNeed-Autonomy)\n-0.93 (PID.Competence-Autonomy)\n-0.11 (PID.CoreNeed-Competence)\n 0.17 (PID.CoreNeed-Relatedness)\n 0.16 (PID.Competence-Relatedness)\n-0.10 (PID.Autonomy-Relatedness) &  & 0.60 (PID.CoreNeed-Autonomy)\n 0.83 (PID.Competence-Autonomy)\n 0.20 (PID.CoreNeed-Competence)\n 0.42 (PID.CoreNeed-Relatedness)\n-0.79 (PID.Competence-Relatedness)\n-0.35 (PID.Autonomy-Relatedness) &  & 0.57 (PID.CoreNeed-Autonomy)\n-0.68 (PID.Competence-Autonomy)\n 0.09 (PID.CoreNeed-Competence)\n-0.27 (PID.CoreNeed-Relatedness)\n-0.31 (PID.Competence-Relatedness)\n-0.08 (PID.Autonomy-Relatedness) & \\
 \addlinespace[0.3em]
@@
 \multicolumn{13}{l}{\rule{0pt}{1em}**** \$p\$ < .0001, *** \$p\$ < .001, ** \$p\$ < .01, * \$p\$ < .05}\\
-\end{tabular}
+\end{tabular}}
 \end{minipage}
 \end{table}
+\end{landscape}

### 2021-12-16 Tables/mdlTheory.tex
small tables
table rotate
line break table fix

@@
 \centering
+\resizebox{\linewidth}{!}{
 \begin{tabular}[t]{ccccccccccccccccccccccccccc}
@@
 \hspace{1em}$\tau_{00}$ & 71.13 (PID) &  & 172.54 (PID) &  & 177.20 (PID) &  & 63.00 (PID) &  & 259.79 (PID) &  & 264.19 (PID) &  & 131.33 (PID) &  & 182.38 (PID) &  & 183.10 (PID) &  & 134.62 (PID) &  & 179.74 (PID) &  & 182.79 (PID) &  & 189.33 (PID) & \\
-$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed)
-0.04 (PID.Quality) &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & 0.00 (PID.CoreNeed)
-0.04 (PID.Quality) &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & 0.03 (PID.CoreNeed)
-0.02 (PID.Quality) &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & 0.02 (PID.Allport)
-0.02 (PID.Quality) &  & 0.00 (PID.CoreNeed)
-\hspace{1em}0.04 (PID.Allport) & \\
-$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & 0.37 (PID.CoreNeed)
--0.22 (PID.Quality) &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & -0.18 (PID.CoreNeed)
--0.06 (PID.Quality) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.14 (PID.CoreNeed)
--0.41 (PID.Quality) &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & 0.12 (PID.Allport)
--0.51 (PID.Quality) &  & -1.00 (PID.CoreNeed)
-\hspace{1em}-0.07 (PID.Allport) & \\
+\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed)\n0.04 (PID.Quality) &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & 0.00 (PID.CoreNeed)\n0.04 (PID.Quality) &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & 0.03 (PID.CoreNeed)\n0.02 (PID.Quality) &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & 0.02 (PID.Allport)\n0.02 (PID.Quality) &  & 0.00 (PID.CoreNeed)\n0.04 (PID.Allport) & \\
+\hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & 0.37 (PID.CoreNeed)\n-0.22 (PID.Quality) &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & -0.18 (PID.CoreNeed)\n-0.06 (PID.Quality) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.14 (PID.CoreNeed)\n-0.41 (PID.Quality) &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & 0.12 (PID.Allport)\n-0.51 (PID.Quality) &  & -1.00 (PID.CoreNeed)\n-0.07 (PID.Allport) & \\
 \hspace{1em}$\rho_{00}$ &  &  &  &  & -0.47 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.79 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.10 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.11 (PID.Allport-Quality) &  & 0.07 (PID.CoreNeed-Allport) & \\
@@
 \multicolumn{27}{l}{\rule{0pt}{1em}**** \$p\$ < .0001, *** \$p\$ < .001, ** \$p\$ < .01, * \$p\$ < .05}\\
-\end{tabular}
+\end{tabular}}
 \end{minipage}
 \end{table}
+\end{landscape}

### 2021-12-16 Methods-and-Results.Rmd
linebreak tbl test

@@
     caption = "Theoretical Test: Core Need Fulfillment and Allport's Conditions",
-    #format = "latex",
+    format = "latex",
     linesep = "",
@@
   ) %>%
+  mutate_all(linebreak) %>%
   kbl(
@@
     caption = "Core Need Fulfillment and Allport's Conditions",
-    format = "latex",
+    #format = "latex",
     linesep = "",
@@
     col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)),
-    align = rep("c", ncol(.)),
+    align = c("l", rep("c", ncol(.)-1)),
     escape = FALSE,
@@
   ) %>%
-  kable_styling(latex_options = "scale_down") %>%
+  #kable_styling(latex_options = "scale_down") %>%
   kableExtra::landscape() %>%

### 2021-12-16 Methods-and-Results.Rmd
all line breaks

@@
   ) %>%
-  #kable_styling(latex_options = "scale_down") %>%
+  kable_styling(latex_options = "scale_down") %>%
   kableExtra::landscape() %>%

### 2021-12-16 Methods-and-Results.Rmd
re-run

@@
     ),
-    alphabet = c("For linear regression: $R^2 / R^2_{adjusted}$, for multilevel regression: $R^2_{marginal} / R^2_{conditional}$ ")
+    alphabet = c("For linear regression: $R^2 / R^2_{adjusted}$, for multilevel regression: $R^2_{marginal} / R^2_{conditional}$ "),
+    escape = FALSE
   ) %>%
@@
                 "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
-    )
+    ),
+    escape = FALSE
   ) %>%

### 2021-12-16 Tables/mdlContactGeneral.tex
re-run

@@
 \multicolumn{13}{l}{\rule{0pt}{1em}PID = Participant ID number (grouping variable)}\\
-\multicolumn{13}{l}{\rule{0pt}{1em}\$\textbackslash{}sigma\textasciicircum{}2\$: residual variance, \$\textbackslash{}tau\_\{00\}\$: random intercept variance, \$\textbackslash{}tau\_\{11\}\$: random slope variance(s), \$\textbackslash{}rho\_\{01\}\$: random slope-intercept correlation(s) , \$\textbackslash{}rho\_\{00\}\$: correlation(s) between random slopes}\\
-\multicolumn{13}{l}{\rule{0pt}{1em}**** \$p\$ < .0001, *** \$p\$ < .001, ** \$p\$ < .01, * \$p\$ < .05}\\
-\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{a} For linear regression: \$R\textasciicircum{}2 / R\textasciicircum{}2\_\{adjusted\}\$, for multilevel regression: \$R\textasciicircum{}2\_\{marginal\} / R\textasciicircum{}2\_\{conditional\}\$ }\\
+\multicolumn{13}{l}{\rule{0pt}{1em}$sigma^2$: residual variance, $tau_{00}$: random intercept variance, $tau_{11}$: random slope variance(s), $rho_{01}$: random slope-intercept correlation(s) , $rho_{00}$: correlation(s) between random slopes}\\
+\multicolumn{13}{l}{\rule{0pt}{1em}**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05}\\
+\multicolumn{13}{l}{\rule{0pt}{1em}\textsuperscript{a} For linear regression: $R^2 / R^2_{adjusted}$, for multilevel regression: $R^2_{marginal} / R^2_{conditional}$ }\\
 \end{tabular}}

### 2021-12-16 Tables/mdlTheory.tex
linebreak tbl test
all line breaks
re-run

@@
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{ccccccccccccccccccccccccccc}
+\begin{tabular}[t]{lcccccccccccccccccccccccccc}
 \toprule
@@
 \multicolumn{27}{l}{\rule{0pt}{1em}PID = Participant ID number (grouping variable)}\\
-\multicolumn{27}{l}{\rule{0pt}{1em}\$\textbackslash{}sigma\textasciicircum{}2\$: residual variance, \$\textbackslash{}tau\_\{00\}\$: random intercept variance, \$\textbackslash{}tau\_\{11\}\$: random slope variance(s), \$\textbackslash{}rho\_\{01\}\$: random slope-intercept correlation(s) , \$\textbackslash{}rho\_\{00\}\$: correlation(s) between random slopes}\\
-\multicolumn{27}{l}{\rule{0pt}{1em}**** \$p\$ < .0001, *** \$p\$ < .001, ** \$p\$ < .01, * \$p\$ < .05}\\
+\multicolumn{27}{l}{\rule{0pt}{1em}$sigma^2$: residual variance, $tau_{00}$: random intercept variance, $tau_{11}$: random slope variance(s), $rho_{01}$: random slope-intercept correlation(s) , $rho_{00}$: correlation(s) between random slopes}\\
+\multicolumn{27}{l}{\rule{0pt}{1em}**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05}\\
 \end{tabular}}

### 2021-12-16 Tables/mdlContactGeneral.tex
linebreaks

--- 2021-12-16 Tables/mdlContactGeneral.tex
@@
 \hspace{1em}$\tau_{00}$ &  &  &  &  &  &  & 164.13 (PID) &  & 488.38 (PID) &  & 366.51 (PID) & \\
-\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & 48.94 (PID.OutgroupInteraction)\n 7.23 (PID.NonOutgroupInteraction) &  & 40.53 (PID.OutgroupInteraction)\n 3.43 (PID.NonOutgroupInteraction) & \\
-\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & -0.72 (PID.OutgroupInteraction)\n 0.12 (PID.NonOutgroupInteraction) &  & -0.70 (PID.OutgroupInteraction)\n-0.28 (PID.NonOutgroupInteraction) & \\
+\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & \makecell[r]{48.94 (PID.OutgroupInteraction)\\ 7.23 (PID.NonOutgroupInteraction)} &  & \makecell[r]{40.53 (PID.OutgroupInteraction)\\ 3.43 (PID.NonOutgroupInteraction)} & \\
+\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & \makecell[l]{-0.72 (PID.OutgroupInteraction)\\ 0.12 (PID.NonOutgroupInteraction)} &  & \makecell[l]{-0.70 (PID.OutgroupInteraction)\\-0.28 (PID.NonOutgroupInteraction)} & \\
 \hspace{1em}$\rho_{00}$ &  &  &  &  &  &  &  &  & 0.00 (PID.OutgroupInteraction-NonOutgroupInteraction) &  & 0.26 (PID.OutgroupInteraction-NonOutgroupInteraction) & \\

### 2021-12-16 Tables/mdlRobustness.tex
linebreaks

@@
 \hspace{1em}$\tau_{00}$ & 174.00 (PID) &  & 523.56 (PID) &  & 339.72 (PID) &  & 176.39 (PID) &  & 262.18 (PID) &  & 181.84 (PID) & \\
-\hspace{1em}$\tau_{11}$ & 0.01 (PID.CoreNeed)\n6.05 (PID.OutgroupInteraction) &  & 0.00 (PID.CoreNeed)\n46.82 (PID.OutgroupInteraction) &  & 0.01 (PID.CoreNeed)\n40.96 (PID.OutgroupInteraction) &  & 0.02 (PID.CoreNeed)\n0.20 (PID.Competence)\n0.14 (PID.Autonomy)\n0.00 (PID.Relatedness) &  & 0.01 (PID.CoreNeed)\n0.00 (PID.Competence)\n0.00 (PID.Autonomy)\n0.00 (PID.Relatedness) &  & 0.05 (PID.CoreNeed)\n0.01 (PID.Competence)\n0.00 (PID.Autonomy)\n0.01 (PID.Relatedness) & \\
-\hspace{1em}$\rho_{01}$ & 0.01 (PID.CoreNeed)\n-0.27 (PID.OutgroupInteraction) &  & 0.27 (PID.CoreNeed)\n-0.68 (PID.OutgroupInteraction) &  & -0.15 (PID.CoreNeed)\n-0.68 (PID.OutgroupInteraction) &  & 0.55 (PID.CoreNeed)\n-0.15 (PID.Competence)\n-0.09 (PID.Autonomy)\n 0.56 (PID.Relatedness) &  & -0.16 (PID.CoreNeed)\n-0.05 (PID.Competence)\n-0.44 (PID.Autonomy)\n-0.20 (PID.Relatedness) &  & -0.25 (PID.CoreNeed)\n-0.29 (PID.Competence)\n-0.23 (PID.Autonomy)\n 0.02 (PID.Relatedness) & \\
-\hspace{1em}$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & 0.03 (PID.CoreNeed-Autonomy)\n-0.93 (PID.Competence-Autonomy)\n-0.11 (PID.CoreNeed-Competence)\n 0.17 (PID.CoreNeed-Relatedness)\n 0.16 (PID.Competence-Relatedness)\n-0.10 (PID.Autonomy-Relatedness) &  & 0.60 (PID.CoreNeed-Autonomy)\n 0.83 (PID.Competence-Autonomy)\n 0.20 (PID.CoreNeed-Competence)\n 0.42 (PID.CoreNeed-Relatedness)\n-0.79 (PID.Competence-Relatedness)\n-0.35 (PID.Autonomy-Relatedness) &  & 0.57 (PID.CoreNeed-Autonomy)\n-0.68 (PID.Competence-Autonomy)\n 0.09 (PID.CoreNeed-Competence)\n-0.27 (PID.CoreNeed-Relatedness)\n-0.31 (PID.Competence-Relatedness)\n-0.08 (PID.Autonomy-Relatedness) & \\
+\hspace{1em}$\tau_{11}$ & \makecell[l]{0.01 (PID.CoreNeed)\\6.05 (PID.OutgroupInteraction)} &  & \makecell[l]{ 0.00 (PID.CoreNeed)\\46.82 (PID.OutgroupInteraction)} &  & \makecell[l]{ 0.01 (PID.CoreNeed)\\40.96 (PID.OutgroupInteraction)} &  & \makecell[l]{0.02 (PID.CoreNeed)\\0.20 (PID.Competence)\\0.14 (PID.Autonomy)\\0.00 (PID.Relatedness)} &  & \makecell[l]{0.01 (PID.CoreNeed)\\0.00 (PID.Competence)\\0.00 (PID.Autonomy)\\0.00 (PID.Relatedness)} &  & \makecell[l]{0.05 (PID.CoreNeed)\\0.01 (PID.Competence)\\0.00 (PID.Autonomy)\\0.01 (PID.Relatedness)} & \\
+\hspace{1em}$\rho_{01}$ & \makecell[c]{ 0.01 (PID.CoreNeed)\\-0.27 (PID.OutgroupInteraction)} &  & \makecell[c]{ 0.27 (PID.CoreNeed)\\-0.68 (PID.OutgroupInteraction)} &  & \makecell[c]{-0.15 (PID.CoreNeed)\\-0.68 (PID.OutgroupInteraction)} &  & \makecell[c]{ 0.55 (PID.CoreNeed)\\-0.15 (PID.Competence)\\-0.09 (PID.Autonomy)\\ 0.56 (PID.Relatedness)} &  & \makecell[c]{-0.16 (PID.CoreNeed)\\-0.05 (PID.Competence)\\-0.44 (PID.Autonomy)\\-0.20 (PID.Relatedness)} &  & \makecell[c]{-0.25 (PID.CoreNeed)\\-0.29 (PID.Competence)\\-0.23 (PID.Autonomy)\\ 0.02 (PID.Relatedness)} & \\
+\hspace{1em}$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & \makecell[r]{ 0.03 (PID.CoreNeed-Autonomy)\\-0.93 (PID.Competence-Autonomy)\\-0.11 (PID.CoreNeed-Competence)\\ 0.17 (PID.CoreNeed-Relatedness)\\ 0.16 (PID.Competence-Relatedness)\\-0.10 (PID.Autonomy-Relatedness)} &  & \makecell[r]{ 0.60 (PID.CoreNeed-Autonomy)\\ 0.83 (PID.Competence-Autonomy)\\ 0.20 (PID.CoreNeed-Competence)\\ 0.42 (PID.CoreNeed-Relatedness)\\-0.79 (PID.Competence-Relatedness)\\-0.35 (PID.Autonomy-Relatedness)} &  & \makecell[r]{ 0.57 (PID.CoreNeed-Autonomy)\\-0.68 (PID.Competence-Autonomy)\\ 0.09 (PID.CoreNeed-Competence)\\-0.27 (PID.CoreNeed-Relatedness)\\-0.31 (PID.Competence-Relatedness)\\-0.08 (PID.Autonomy-Relatedness)} & \\
 \addlinespace[0.3em]

### 2021-12-16 Tables/mdlTheory.tex
linebreaks

@@
 \hspace{1em}$\tau_{00}$ & 71.13 (PID) &  & 172.54 (PID) &  & 177.20 (PID) &  & 63.00 (PID) &  & 259.79 (PID) &  & 264.19 (PID) &  & 131.33 (PID) &  & 182.38 (PID) &  & 183.10 (PID) &  & 134.62 (PID) &  & 179.74 (PID) &  & 182.79 (PID) &  & 189.33 (PID) & \\
-\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed)\n0.04 (PID.Quality) &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & 0.00 (PID.CoreNeed)\n0.04 (PID.Quality) &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & 0.03 (PID.CoreNeed)\n0.02 (PID.Quality) &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & 0.02 (PID.Allport)\n0.02 (PID.Quality) &  & 0.00 (PID.CoreNeed)\n0.04 (PID.Allport) & \\
-\hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & 0.37 (PID.CoreNeed)\n-0.22 (PID.Quality) &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & -0.18 (PID.CoreNeed)\n-0.06 (PID.Quality) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.14 (PID.CoreNeed)\n-0.41 (PID.Quality) &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & 0.12 (PID.Allport)\n-0.51 (PID.Quality) &  & -1.00 (PID.CoreNeed)\n-0.07 (PID.Allport) & \\
+\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[l]{0.05 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[l]{0.00 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[l]{0.03 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[l]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[l]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
+\hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.22 (PID.Quality)} &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & \makecell[c]{-0.18 (PID.CoreNeed)\\-0.06 (PID.Quality)} &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & \makecell[c]{-0.14 (PID.CoreNeed)\\-0.41 (PID.Quality)} &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & \makecell[c]{ 0.12 (PID.Allport)\\-0.51 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
 \hspace{1em}$\rho_{00}$ &  &  &  &  & -0.47 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.79 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.10 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.11 (PID.Allport-Quality) &  & 0.07 (PID.CoreNeed-Allport) & \\

### 2021-12-16 scripts/functions/MlTbl.R

@@ -93,10 +93,10 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   # collect random effect statistics
   restat <- list(
     sigmaSq = sigmaSq,
-    tau00 = ifelse(length(tau00)>1, paste(tau00, collapse = "\\n"), tau00),
-    tau11 = ifelse(length(tau11)>1, paste(tau11, collapse = "\\n"), tau11),
-    rho01 = ifelse(length(rho01)>1, paste(rho01, collapse = "\\n"), rho01),
-    rho00 = ifelse(length(rho00)>1, paste(rho00, collapse = "\\n"), rho00)
+    tau00 = ifelse(length(tau00)>1, paste(tau00, collapse = "\n"), tau00),
+    tau11 = ifelse(length(tau11)>1, paste(tau11, collapse = "\n"), tau11),
+    rho01 = ifelse(length(rho01)>1, paste(rho01, collapse = "\n"), rho01),
+    rho00 = ifelse(length(rho00)>1, paste(rho00, collapse = "\n"), rho00)
   )
   
   

### 2021-12-16 Methods-and-Results.Rmd
re-run

@@
                 "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
-    )
+    ), 
+    escape = TRUE
   ) %>%
@@
   gsub("_cwc", "", ., fixed = TRUE)   %>%
+  gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
@@
   kableExtra::landscape() %>%
+  gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
@@
                 "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
-    )
+    ), 
+    escape = FALSE
   ) %>%
@@
   gsub("_cwc", "", ., fixed = TRUE)  %>%
+  gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position

### 2021-12-16 Tables/localTables.tex
re-run

--- 2021-12-16 manuscript.tex
@@
-% define document type (i.e., template. Here: A4 APA manuscript with 12pt font)
-\documentclass[man, 12pt, a4paper]{apa7}
-
-% change margins (e.g., for margin comments):
-%\usepackage{geometry}
-% \geometry{
-% a4paper,
-% marginparwidth=30mm,
-% right=50mm,
-%}
-
-% add packages
+\documentclass{article}
+\usepackage{blindtext}
+\usepackage[a1paper, margin=5cm]{geometry}
+\usepackage{graphicx}
 \usepackage[american]{babel}
@@
 \usepackage{hyperref}
-\usepackage[style=apa, sortcites=true, sorting=nyt, backend=biber, natbib=true, uniquename=false, uniquelist=false, useprefix=true]{biblatex}
 \usepackage{authblk}
@@
 \usepackage{soul}
-\usepackage{xcolor}
 \usepackage{fourier}
@@
 \usepackage{enumitem}
+\usepackage{caption}
+\usepackage{adjustbox}
+\usepackage{booktabs}
+\usepackage{xcolor}
+\usepackage{makecell}
+\usepackage{tabu}
 
-% make warning with red triangle
-\newcommand\Warning[1][2ex]{%
-  \renewcommand\stacktype{L}%
-  \scaleto{\stackon[1.3pt]{\color{red}$\triangle$}{\tiny\bfseries !}}{#1}}%
-
-% make question with red triangle
-\newcommand\Question[1][2ex]{%
-  \renewcommand\stacktype{L}%
-  \scaleto{\stackon[1.3pt]{\color{red}$\triangle$}{\tiny\bfseries ?}}{#1}}%
-
-% add definition sections
-\theoremstyle{break}
-\newtheorem{definition}{Definition}
-
-% add hypothesis sections
-\theoremstyle{plain}
-\theoremseparator{:}
-\newtheorem{hyp}{Hypothesis}
-
-\newtheorem{subhyp}{Hypothesis}
-   \renewcommand\thesubhyp{\thehyp\alph{subhyp}}
-
-% add quote section
-\usepackage{csquotes}
-
-% framed box section
-\usepackage{framed}
-\emergencystretch=1em
-
-% formatting links in the PDF file
-\hypersetup{
-pdfpagemode={UseOutlines},
-bookmarksopen=true,
-bookmarksopenlevel=0,
-hypertexnames=false,
-colorlinks   = true, %Colours links instead of ugly boxes
-urlcolor     = blue, %Colour for external hyperlinks
-linkcolor    = blue, %Colour of internal links
-citecolor   = cyan, %Colour of citations
-pdfstartview={FitV},
-unicode,
-breaklinks=true,
-}
-
-% language settings
-\DeclareLanguageMapping{american}{american-apa}
-
-% add reference library file
-\addbibresource{references.bib}
-
-% Title and header
-\title{Psychological Needs During Intergroup Contact}
-\shorttitle{Needs in Intergroup Contact}
-
-% Authors
-\author[*,1,2]{Jannis Kreienkamp}
-\author[1,2]{Maximilian Agostini}
-\author[1,2]{Laura F. Bringmann}
-\author[1,2]{Peter de Jonge}
-\author[1,2]{Kai Epstude}
-\affiliation{\hfill}
-
-\affil[1]{University of Groningen, Department of Psychology}
-\affil[2]{Author-order to be discussed; currently alphabetic by last name.}
-
-\authornote{
-   \addORCIDlink{* Jannis Kreienkamp}{0000-0002-1831-5604}\\
-   \addORCIDlink{Maximilian Agostini}{0000-0001-6435-7621}\\
-   \addORCIDlink{Laura F. Bringmann}{0000-0002-8091-9935}\\
-   \addORCIDlink{Peter de Jonge}{0000-0002-0866-6929}\\
-   \addORCIDlink{Kai Epstude}{0000-0001-9817-3847}
-
-We have no known conflict of interest to declare.
-The authors received no specific funding for this work.
-Source data and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}.
-Protocols, materials, analysis data, and code are available at \url{osf.io}.
-
-Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).
-E-mail: j.kreienkamp@rug.nl}
-
-\leftheader{Kreienkamp}
-
-% Abstract
-\abstract{
-Abstract goes here.
-
-\noindent\textbf{Public significance statement}: Significance Statement goes here.
-}
-
-\keywords{Intergroup Contact, Psychological Needs, Outgroup Attitudes, Interaction Quality, Extensive Longitudinal Data}
-
-% set indentation size
-\setlength\parindent{1.27cm}
-
-% Start of the main document:
 \begin{document}
 
-% add title information (incl. title page and abstract)
-\maketitle
-
-% **CHEAT SHEET / LEGEND**
-%
-% Comments:
-% '%' starts a comment in LaTeX (not printed)
-% '\todo[inline]{} makes orange boxes in PDF
-% '\marginpar{}' notes in margins
-% '\footnote{}' footnote
-% '\Warning' important note indicator in PDF (triangle with exclamation mark)
-% '\Question' question note indicator in PDF (triangle with question mark)
-%
-% Citation (with Natbib citation style):
-% '\citep[e.g.][p. 15]{CitationKey}' citation in parentheses "(e.g., Berry, 2003, p. 15)"
-% '\citet{CitationKey}' citation in text "Berry (2003)"
-% '\citealt' and '\citealp' alternate citation without parentheses
-% '\citeauthor' and '\citeyear' only year or author
-% 
-% Headings:
-% '\part{}' and '\chapter{}' only relevant for multi-part or multi-chapter documents
-% '\section{}' heading level 1
-% '\subsection{}' heading level 2
-% '\subsubsection{}' heading level 3
-% '\paragraph{}' heading level 4
-% '\subparagraph{}' heading level 5
-%
-% formatting:
-% '\textbf{}' text bold font
-% '\textit{}' text italic font
-% '\underline{}' text underline
-% '\sout{}' text strike out
-% '\textsc{}' text small caps
-% '\vspace{1em}' add vertical space
-% '\hspace{1em}' add horizontal space
-% '\\' new line (i.e., line break)
-% '\pagebreak' start new page (i.e., page break)
-% '\noindent' do not indent current line (e.g., current paragraph)
-% 'begin{center}...end{center}' center text or object
-%
-% Math mode:
-% '$\alpha = .8$' mathematical equation inline
-% '$$\hat{y} = b_0 + b_1x$$' mathematical equation in its own line
-% '\begin{equation}...\end{equation}' multi-line equation
-% '\approx' approximate symbol
-% '\neq' not equal
-% '\bar' mean bar over letter
-% '\pm' plus minus sign 
-% '^{}' superscript
-% '_{}' subscript
-% '\fraq{numerator}{denominator}' fraction
-% '\sqrt[n]{}' square root
-% '\sum_{k=1}^n' sum for 1 through n
-%
-% Insert things from elsewhere:
-% '\input{filename}' inputs the raw (tex) file as a command (e.g., tables and R-Markdown imports)
-% '\include{filename}' includes section on new page (incl. possible auxiliary info)
-% '\includegraphics[settings]{filename}' add a figure or graph
-% '\caption{}' adds a caption to a table or figure
-% '\label{}' labels sections, tables, figures, etc. so that they can be referred to.
-% '\ref{}' refer to a labelled sections, tables, figures, etc.
-% '\begin{enumerate}...\end{enumerate}' numbered list
-% '\begin{itemize}...\end{itemize}' bullet-ed list
-% '\item' item in list section 
-%
-% Symbols:
-% '\&' and sign
-% '\%' percent sign
-% '\_' three dotes
-% '\#' hash symbol
-% ------------------------------------------------------------------
-
-% Relevance v.02: Conflict is a problem, positive contact as solution, but little research on when daily contact is perceived positive
-Conflict between social groups and their individual members remains a prevalent feature of the modern human condition.
-Experiences of prejudices, discrimination, and animosities with other groups continue to plague the everyday lives of many people around the world.
-One of the main ameliorations proposed by social psychologists has been the intergroup contact hypothesis.
-In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
-And even though over the past 70 years, a plethoray of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}, relatively little research has thus far explained when and why people's everyday inter-group interactions are perceived as positive.
-
-% Problem v.02: theoretical interaction quality central to understanding outcomes, practical many impactful negative interactions in everyday life
-There are however substantial theoretical and practical consequences of these understudied mechanisms of everyday intergroup contact.
-Theoretically, interaction quality or -valence sits at the heart of intergroup contact theory, as it gauges whether the interaction will result in positive intergroup outcomes \citep[][]{Tropp2016, Brown2007}.
-Practically, a longstanding body of literature has shown that negative interactions are common in everyday life and often result in a substantial decline of intergroup relations \citep[][]{Barlow2012, Shelton2009}.
-It is thus important to explore which psychological mechanisms explain when and why intergroup contacts are positive and lead to better intergroup perceptions, especially during everyday intergroup encounters \citep[e.g.,][]{MacInnis2015}.
-
-% Aim / Solution v.02: look at need fulfillment as mechanism in daily interactions of migrants
-In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and positive outgroup attitudes.
-That is to say, that if a person, for example, seeks to feel accepted by their interaction partner and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
-To test this, we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with majority group members.
-
-\section{Need Mechanism in Intergroup Contact}
-% Motivational mechanism:
-% interaction quality is important
-% past research has either focused on conditions or cognitive-affective processes
-% neither are necessary or explain why an interaction is positive
-
-Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
-It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for such positive contact effects \citep[Allport's Optimal Contact conditions;][]{Allport1954b, Pettigrew1969}.
-However, a major meta-analysis of these contact conditions showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met \citep[][]{Pettigrew2006}.
-It, thus, remains unclear when and why exactly an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects\footnote{It should be noted here that following Allport's original conditions, several additional conditions of optimal contact were proposed \citep[for a critical discussion see][]{Pettigrew1986}.
-Similarly, since the early 21\textsuperscript{st} century many psychological processes during intergroup contact were examined \citep[e.g.
-see,][]{Paolini2021}.
-Among others, researchers have for example explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}.
-However, all these advances share the underlying criticism that they are not geared towards understanding when and why an interaction is perceived as positive.}.
-We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
-
-% ALTERNATIVE: SHORTER BUT NOT FOCUSED ON ALLPORT'S CONDITIONS (WHICH WE TEST LATER)
-% Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
-Past research has either focused on conditions under which interactions tend to have favorable effects \citep[e.g., Allport's optimal conditions;][]{Allport1954b, Pettigrew1969} or has investigated cognitive-affective processes during contact \citep[e.g., group salience, intimacy, attachment, or intergroup anxiety;][]{Brown2005, Marinucci2021, Tropp2021, Paolini2004}.
-However, neither the contact conditions nor the cognitive-affective processes are particularly well equipped to explain when and why an interaction will be perceived as positive.
-We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
-
-% Important in broader field: needs have been found to be important in broader intergroup relations and interpersonal contact literature.
-Although considerations of psychological needs and motivations have remained markedly absent within the intergroup contact literature, the concepts are in no way foreign to the broader topic of intergroup relations.
-Psychological needs have for example found fruitful utility in reconciliation research \citep[][]{Shnabel2008}, the study of minority's discrimination experiences \citep[][]{Celebi2017}, and in non-intergroup interactions \citep[][]{Downie2008}.
-% On the most general level, research on intergroup conflicts has, for example, shown that addressing the group-specific needs predicts willingness to reconcile with the other group \citep[][]{Shnabel2008}.
-For the case of refugee migrants in their relationship with a majority group, a recent study found that identity needs will buffer against discrimination experiences and will protect personal health \citep[][]{Celebi2017}.
-Additionally, within the field of interpersonal relations, we find first evidence that the fulfillment of fundamental psychological needs might predict perceived interaction quality in non-intergroup interactions \citep[][]{Downie2008}.
-% Promising for intergroup contact: Asked for in intergroup contact reviews and first research looked at social change
-And even within the field of intergroup contact the idea of need fulfillment as a psychological mechanism is not entirely novel.
-\citet{Dovidio2017} in their narrative review have suggested that understanding psychological needs might be essential to constructive intergroup contact.
-And recently first empirical research has even found psychological need fulfillment during intergroup contacts to predict support for social change \citep[][]{Hassler2021}.
-There is thus initial evidence to suggest that need fulfillment during intergroup contact might offer a promising psychological mechanism to understand perceived interaction quality and positive outgroup attitudes.
-
-% Difficult to test general mechanism: Either consider too many needs (situationally relevant but not feasible) or too few (feasible but not transferable).
-Solution: ask for main need + rating of main need
-% MAYBE MOVE THIS TO 'The Present Research Section'
-One reason why motivational considerations might have remained absent from the intergroup contact literature is that there is an overwhelming number of individual needs or goals that might be relevant to a person during an intergroup interaction.
-Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad range of fundamental psychological needs.
-To avoid this predicament we propose to start by using adaptive and responsive survey designs that allow a tailored approach based on the participants inputs \citep[e.g.,][]{Tourangeau2017}.
-In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., situation core need) and with reference to their own response the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment).
-Such an adaptive approach would allow us to test the fundamental psychological mechanism of whether situational psychological needs indeed predict perceived interaction quality and positive outgroup attitudes.
-
-\section{Real-Life Process Data}
-While we have argued that a need fulfillment mechanism is relevant to intergroup contact generally, its flexible and broad applicability might be ideally suited to address the pressing issue of understanding natural intergroup contacts outside the lab.
-Investigations of such 'real-life interactions' often suffer from the difficulty that past intergroup contact research has either focused on the mechanisms of individual interactions in artificial lab studies or has focused on longer-term recall self-reports of natural interactions \citep[e.g.,][]{Pettigrew2006}.
-Even with extended intervention studies, the most fine-grained data available is usually limited to pre-post-control designs.
-Such empirical practices stand, however, in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the core idea of the contact hypothesis, which was focused on the daily interactions of people \citep[see][]{Allport1954b}.
-As a result, prominent figures within the intergroup contact field have called for studies that collect longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
-Such data would be able to capture real-life interactions that include interaction-specific mechanism information close the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
-Moreover, because data is nested within participants, experience-sampling data often allows to capture large amounts of high-quality data with relatively few participants.}.
-
-% Used to be difficult but technological and methodological developments (e.g., FormR + HLM) → collect large body of intensive longitudinal data
-In the past, such data collections were often unfeasible because they were either physically impractical or too expensive.
-However, recent technological developments allow us to easily collect experience sampling data on mobile devices \citep[e.g.,][]{Keil2020} or using web-based applications \citep[e.g.,][]{Arslan2020}.
-At the same time, analytical methods for such more complex data have become more readily available, making the analyses more approachable \citep[see, e.g.,][]{ODonnell2021}.
-Given these, technological and methodological developments, we were able to collect a large amount of real-life data following the daily intergroup interactions of recent migrants with the majority group members.
-
-\section{The Present Research}
-The aim of this paper is essentially threefold.
-First, our study is among the first to test the fundamental tenets of intergroup contact and Allport's conditions in real-life extensive longitudinal data.
-Second, we test whether the fulfillment situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
-And third, we test the role of interaction quality in  the relationship of psychological need fulfillment and outgroup attitudes.
-Based on this we formulated three main hypotheses:
-\begin{enumerate}[label=H\arabic*:]
-    \item Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes across extensive longitudinal data.
-    \item Based on Allport’s optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
-    \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
-\end{enumerate}
-Beyond these main hypotheses we have formulated several sub-hypotheses that form the basis for our analysis plan (these sub-hypotheses also include several robustness checks and are available in Appendix \ref{app:AppendixHypotheses}).
-Given the more complex data structure of the extensive longitudinal data, we opted to test our hypotheses using a multilevel regression model, where the measurement occasions (level 1) were nested within the participants (level 2).
-Given that more complex dynamic modeling procedures are not necessary to test these more basic hypotheses, we will focus on the contemporaneous effect of the data (e.g., need fulfillment during the intergroup interaction predicts outgroup attitudes following the interaction).
-Such an approach is also tolerant to missing data and uneven case numbers within participants.
-
-To test our main hypotheses, we collected three independent sets of extensive longitudinal data (Studies 1–3).
-The full surveys are available in Supplementary Materials A as well as in our open science repository (including a complete codebook, see OSF-REFERENCE).
-Our most comprehensive study (Study 3) was fully preregistered  \citep[available at][]{Kreienkamp2021f}.
-The fully annotated analyses are available in Supplementary Material B.
-As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text (for the full modeling process see Supplementary Material B).
-
-\input{Methods-and-Results}
-
-\section{Discussion}
-% aims re-iterated
-In this paper we set out to (1) test the basic predictions of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data, (2) we proposed that the fulfillment situational psychological needs meaningfully predicts positive outgroup attitudes, and (3) that the fulfillment of psychological needs (and Allport's conditions) have their effect (partially) through perceived interaction quality.
-
-% Contact hypothesis in ESM data [inconsistent in aggregate but consistent in ML analysis]
-When considering the results of the three studies jointly, we find mixed results for the basic intergroup contact hypothesis.
-The aggregated number of outgroup interactions across all measurements only had a significant effect on average outgroup attitudes in one of the three studies and in that study there was no significant effect of average interaction quality on outgroup attitudes (which was significant for the other two studies).
-This meant that only for our smallest study did we find the expected interaction between interaction frequency and interaction quality when looking at the aggregated data across all measurements.
-However, once we considered the effect of having an interaction with an outgroup member (vs.
-not having an outgroup interaction) within the participants, we find that intergroup contact is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account).
-While this later results is in line with our expectations, the earlier aggregate findings are surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
-Even though this inconsistency with past research might be a data artefact (e.g., because most people reported more substantially mode measurements during which they did not have an outgroup interaction), the absence of this aggregate effect could underline the fact that cross-sectional retrospective data might suffer from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
-In summary, we thus find that when we aggregate interaction frequencies and interaction quality from our intensive longitudinal data we find inconsistent results from the past literature but within participants intergroup contacts are significantly related with positive outgroup attitudes.
-
-% Allport's conditions in ESM data [consistent predictor and partially through quality]
-Using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
-And when we consider interaction quality and Allport's conditions jointly, we find further evidence that part of the benefits of Allport's conditions are due to the case that such interactions are also perceived as more positive.
-We thus find first evidence that Allport's conditions of optimal contact are also relevant to the daily interactions recent migrants have in their interactions with majority group members.
-
-% Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results for our main proposal regarding the importance of situational key needs, we find highly consistent positive results across all three studies.
-We find that in all three extensive longitudinal datasets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
-We find that in all three studies the effect of core need fulfillment on outgroup attitudes is either fully or partially through its effect on quality perceptions, and we find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
-In fact we find that our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
-In most cases the core need even took over the variances previously explained by the self-determination theory needs.
-We thus find strong evidence that within everyday life interactions of recent migrants with majority group members, the perception that one's interaction specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
-As such the data offers a first test of the motivational basis of intergroup contact.
-
-\subsection{Limitations}
-to be discussed, potentially:
-\begin{enumerate}
-    \item migrants are not refugees (generalizability potentially even more relevant?)
-    \item minority perspective only
-    \item lagged effects left for future studies (potentially not relevant, time scale)
-    \item ESM: real-life data comes at the expense of having short/single item operationalizations
-\end{enumerate}
-
-\subsection{Implications}
-to be discussed, potentially:
-\begin{enumerate}
-    \item feasible to collect large amount of data on intergroup contact using ESM method (do we have a formR ref in there?; set up is feasible but not the easiest; maybe even advertise the reusability of the formR survey?)
-    \item role of motivation in intergroup contact promising (potential for interventions, e.g., most immediate to the data: settlement practices). 
-    \item potential to identify context specific needs
-\end{enumerate}
-
-\subsection{Conclusion paragraph (not a real heading)}
-to be written after co-author meeting.
-
-\printbibliography
-
-\appendix
-
-\section{Appendix A: Hypotheses}
-\label{app:AppendixHypotheses}
-
-\begin{hyp}[H\ref{hyp:contact}] \label{hyp:contact}
-Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
-\end{hyp}
-
-\begin{subhyp}[H\ref{hyp:contactFreq}] \label{hyp:contactFreq}
-\addtolength{\leftskip}{2.5em}
-Participants with more intergroup interactions should have a more favorable outgroup attitudes.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:contactDummy}] \label{hyp:contactDummy}
-\addtolength{\leftskip}{2.5em}
-Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:contactFreqQual}] \label{hyp:contactFreqQual}
-\addtolength{\leftskip}{2.5em}
-Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
-\end{subhyp}
-
-\begin{hyp}[H\ref{hyp:AllportsConditions}] \label{hyp:AllportsConditions}
-Based on Allport's optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
-\end{hyp}
-
-\setcounter{subhyp}{0}
-\begin{subhyp}[H\ref{hyp:AllportsPred}] \label{hyp:AllportsPred}
-\addtolength{\leftskip}{2.5em}
-Based on Allport's optimal contact conditions, outgroup attitudes should be more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:AllportsQuality}] \label{hyp:AllportsQuality}
-\addtolength{\leftskip}{2.5em}
-Based on past research on the role of interaction quality, interaction quality should be more perceived as more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:AllportsQualityMediation}] \label{hyp:AllportsQualityMediation}
-\addtolength{\leftskip}{2.5em}
-Based on past research on the role of interaction quality, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extend be assumed by interaction quality.
-\end{subhyp}
-
-\begin{hyp}[H\ref{hyp:keyNeed}] \label{hyp:keyNeed}
-Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
-\end{hyp}
-
-\setcounter{subhyp}{0}
-\begin{subhyp}[H\ref{hyp:keyNeedPred}] \label{hyp:keyNeedPred}
-\addtolength{\leftskip}{2.5em}
-Outgroup attitudes should be more favorable after intergroup interactions with high key need fulfillment.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:keyNeedQual}] \label{hyp:keyNeedQual}
-\addtolength{\leftskip}{2.5em}
-Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:keyNeedMediation}] \label{hyp:keyNeedMediation}
-\addtolength{\leftskip}{2.5em}
-The variance explained in outgroup attitudes by key need fulfillment should to a large extend be assumed by interaction quality.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:keyNeedContactType}] \label{hyp:keyNeedContactType}
-\addtolength{\leftskip}{2.5em}
-The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
-Thus, the effect of key need fulfillment on outgroup attitudes should stronger for intergroup interact than for ingroup interactions.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:keyNeedSDT}] \label{hyp:keyNeedSDT}
-\addtolength{\leftskip}{2.5em}
-The effect of key need fulfillment on outgroup attitudes should be persist even when taking other fundamental psychological needs into account.
-Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
-\end{subhyp}
-
-\begin{hyp}[H\ref{hyp:comparison}] \label{hyp:comparison}
-Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict outgroup attitudes at least as well as Allport's conditions.
-\end{hyp}
-
-\setcounter{subhyp}{0}
-\begin{subhyp}[H\ref{hyp:compModel}] \label{hyp:compModel}
-\addtolength{\leftskip}{2.5em}
-The need model (H\ref{hyp:keyNeedPred}) should predict more variance in outgroup attitudes than the model based on Allport's conditions (H\ref{hyp:AllportsPred}).
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:compTogether}] \label{hyp:compTogether}
-\addtolength{\leftskip}{2.5em}
-The  effect of key need fulfillment on outgroup attitudes should  persist even when taking other Allport's conditions into account.
-Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for equal status, common goals, collaboration, and structural support.
-\end{subhyp}
+\input{mdlContactGeneral}
+\input{mdlTheory}
+\input{mdlRobustness}
 

### 2021-12-16 Tables/mdlContactGeneral.tex
re-run

@@
 \hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & \makecell[r]{48.94 (PID.OutgroupInteraction)\\ 7.23 (PID.NonOutgroupInteraction)} &  & \makecell[r]{40.53 (PID.OutgroupInteraction)\\ 3.43 (PID.NonOutgroupInteraction)} & \\
-\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & \makecell[l]{-0.72 (PID.OutgroupInteraction)\\ 0.12 (PID.NonOutgroupInteraction)} &  & \makecell[l]{-0.70 (PID.OutgroupInteraction)\\-0.28 (PID.NonOutgroupInteraction)} & \\
+\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & \makecell[c]{-0.72 (PID.OutgroupInteraction)\\ 0.12 (PID.NonOutgroupInteraction)} &  & \makecell[c]{-0.70 (PID.OutgroupInteraction)\\-0.28 (PID.NonOutgroupInteraction)} & \\
 \hspace{1em}$\rho_{00}$ &  &  &  &  &  &  &  &  & 0.00 (PID.OutgroupInteraction-NonOutgroupInteraction) &  & 0.26 (PID.OutgroupInteraction-NonOutgroupInteraction) & \\

### 2021-12-16 Tables/mdlRobustness.tex
re-run

@@
 \hspace{1em}$\tau_{00}$ & 174.00 (PID) &  & 523.56 (PID) &  & 339.72 (PID) &  & 176.39 (PID) &  & 262.18 (PID) &  & 181.84 (PID) & \\
-\hspace{1em}$\tau_{11}$ & \makecell[l]{0.01 (PID.CoreNeed)\\6.05 (PID.OutgroupInteraction)} &  & \makecell[l]{ 0.00 (PID.CoreNeed)\\46.82 (PID.OutgroupInteraction)} &  & \makecell[l]{ 0.01 (PID.CoreNeed)\\40.96 (PID.OutgroupInteraction)} &  & \makecell[l]{0.02 (PID.CoreNeed)\\0.20 (PID.Competence)\\0.14 (PID.Autonomy)\\0.00 (PID.Relatedness)} &  & \makecell[l]{0.01 (PID.CoreNeed)\\0.00 (PID.Competence)\\0.00 (PID.Autonomy)\\0.00 (PID.Relatedness)} &  & \makecell[l]{0.05 (PID.CoreNeed)\\0.01 (PID.Competence)\\0.00 (PID.Autonomy)\\0.01 (PID.Relatedness)} & \\
+\hspace{1em}$\tau_{11}$ & \makecell[c]{0.01 (PID.CoreNeed)\\6.05 (PID.OutgroupInteraction)} &  & \makecell[c]{ 0.00 (PID.CoreNeed)\\46.82 (PID.OutgroupInteraction)} &  & \makecell[c]{ 0.01 (PID.CoreNeed)\\40.96 (PID.OutgroupInteraction)} &  & \makecell[c]{0.02 (PID.CoreNeed)\\0.20 (PID.Competence)\\0.14 (PID.Autonomy)\\0.00 (PID.Relatedness)} &  & \makecell[c]{0.01 (PID.CoreNeed)\\0.00 (PID.Competence)\\0.00 (PID.Autonomy)\\0.00 (PID.Relatedness)} &  & \makecell[c]{0.05 (PID.CoreNeed)\\0.01 (PID.Competence)\\0.00 (PID.Autonomy)\\0.01 (PID.Relatedness)} & \\
 \hspace{1em}$\rho_{01}$ & \makecell[c]{ 0.01 (PID.CoreNeed)\\-0.27 (PID.OutgroupInteraction)} &  & \makecell[c]{ 0.27 (PID.CoreNeed)\\-0.68 (PID.OutgroupInteraction)} &  & \makecell[c]{-0.15 (PID.CoreNeed)\\-0.68 (PID.OutgroupInteraction)} &  & \makecell[c]{ 0.55 (PID.CoreNeed)\\-0.15 (PID.Competence)\\-0.09 (PID.Autonomy)\\ 0.56 (PID.Relatedness)} &  & \makecell[c]{-0.16 (PID.CoreNeed)\\-0.05 (PID.Competence)\\-0.44 (PID.Autonomy)\\-0.20 (PID.Relatedness)} &  & \makecell[c]{-0.25 (PID.CoreNeed)\\-0.29 (PID.Competence)\\-0.23 (PID.Autonomy)\\ 0.02 (PID.Relatedness)} & \\
@@
 \multicolumn{13}{l}{\rule{0pt}{1em}PID = Participant ID number (grouping variable)}\\
-\multicolumn{13}{l}{\rule{0pt}{1em}\$\textbackslash{}sigma\textasciicircum{}2\$: residual variance, \$\textbackslash{}tau\_\{00\}\$: random intercept variance, \$\textbackslash{}tau\_\{11\}\$: random slope variance(s), \$\textbackslash{}rho\_\{01\}\$: random slope-intercept correlation(s) , \$\textbackslash{}rho\_\{00\}\$: correlation(s) between random slopes}\\
-\multicolumn{13}{l}{\rule{0pt}{1em}**** \$p\$ < .0001, *** \$p\$ < .001, ** \$p\$ < .01, * \$p\$ < .05}\\
+\multicolumn{13}{l}{\rule{0pt}{1em}$sigma^2$: residual variance, $tau_{00}$: random intercept variance, $tau_{11}$: random slope variance(s), $rho_{01}$: random slope-intercept correlation(s) , $rho_{00}$: correlation(s) between random slopes}\\
+\multicolumn{13}{l}{\rule{0pt}{1em}**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05}\\
 \end{tabular}}

### 2021-12-16 Tables/mdlTheory.tex
re-run

@@
 \hspace{1em}$\tau_{00}$ & 71.13 (PID) &  & 172.54 (PID) &  & 177.20 (PID) &  & 63.00 (PID) &  & 259.79 (PID) &  & 264.19 (PID) &  & 131.33 (PID) &  & 182.38 (PID) &  & 183.10 (PID) &  & 134.62 (PID) &  & 179.74 (PID) &  & 182.79 (PID) &  & 189.33 (PID) & \\
-\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[l]{0.05 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[l]{0.00 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[l]{0.03 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[l]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[l]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
+\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.05 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[c]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
 \hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.22 (PID.Quality)} &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & \makecell[c]{-0.18 (PID.CoreNeed)\\-0.06 (PID.Quality)} &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & \makecell[c]{-0.14 (PID.CoreNeed)\\-0.41 (PID.Quality)} &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & \makecell[c]{ 0.12 (PID.Allport)\\-0.51 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\

### 2021-12-16 Methods-and-Results.Rmd
tabl fix

@@
   gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>%
+  gsub("\\makecell[r]", "\\makecell[c]", ., fixed = TRUE) %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
@@
     caption = "Core Need Fulfillment and Allport's Conditions",
-    #format = "latex",
+    format = "latex",
     linesep = "",

### 2021-12-16 Tables/mdlRobustness.tex
tabl fix

@@
 \hspace{1em}$\rho_{01}$ & \makecell[c]{ 0.01 (PID.CoreNeed)\\-0.27 (PID.OutgroupInteraction)} &  & \makecell[c]{ 0.27 (PID.CoreNeed)\\-0.68 (PID.OutgroupInteraction)} &  & \makecell[c]{-0.15 (PID.CoreNeed)\\-0.68 (PID.OutgroupInteraction)} &  & \makecell[c]{ 0.55 (PID.CoreNeed)\\-0.15 (PID.Competence)\\-0.09 (PID.Autonomy)\\ 0.56 (PID.Relatedness)} &  & \makecell[c]{-0.16 (PID.CoreNeed)\\-0.05 (PID.Competence)\\-0.44 (PID.Autonomy)\\-0.20 (PID.Relatedness)} &  & \makecell[c]{-0.25 (PID.CoreNeed)\\-0.29 (PID.Competence)\\-0.23 (PID.Autonomy)\\ 0.02 (PID.Relatedness)} & \\
-\hspace{1em}$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & \makecell[r]{ 0.03 (PID.CoreNeed-Autonomy)\\-0.93 (PID.Competence-Autonomy)\\-0.11 (PID.CoreNeed-Competence)\\ 0.17 (PID.CoreNeed-Relatedness)\\ 0.16 (PID.Competence-Relatedness)\\-0.10 (PID.Autonomy-Relatedness)} &  & \makecell[r]{ 0.60 (PID.CoreNeed-Autonomy)\\ 0.83 (PID.Competence-Autonomy)\\ 0.20 (PID.CoreNeed-Competence)\\ 0.42 (PID.CoreNeed-Relatedness)\\-0.79 (PID.Competence-Relatedness)\\-0.35 (PID.Autonomy-Relatedness)} &  & \makecell[r]{ 0.57 (PID.CoreNeed-Autonomy)\\-0.68 (PID.Competence-Autonomy)\\ 0.09 (PID.CoreNeed-Competence)\\-0.27 (PID.CoreNeed-Relatedness)\\-0.31 (PID.Competence-Relatedness)\\-0.08 (PID.Autonomy-Relatedness)} & \\
+\hspace{1em}$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & \makecell[c]{ 0.03 (PID.CoreNeed-Autonomy)\\-0.93 (PID.Competence-Autonomy)\\-0.11 (PID.CoreNeed-Competence)\\ 0.17 (PID.CoreNeed-Relatedness)\\ 0.16 (PID.Competence-Relatedness)\\-0.10 (PID.Autonomy-Relatedness)} &  & \makecell[c]{ 0.60 (PID.CoreNeed-Autonomy)\\ 0.83 (PID.Competence-Autonomy)\\ 0.20 (PID.CoreNeed-Competence)\\ 0.42 (PID.CoreNeed-Relatedness)\\-0.79 (PID.Competence-Relatedness)\\-0.35 (PID.Autonomy-Relatedness)} &  & \makecell[c]{ 0.57 (PID.CoreNeed-Autonomy)\\-0.68 (PID.Competence-Autonomy)\\ 0.09 (PID.CoreNeed-Competence)\\-0.27 (PID.CoreNeed-Relatedness)\\-0.31 (PID.Competence-Relatedness)\\-0.08 (PID.Autonomy-Relatedness)} & \\
 \addlinespace[0.3em]

### 2021-12-16 Methods-and-Results.Rmd
theory tbl fixed

--- 2021-12-16 Methods-and-Results.Rmd
@@
   gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>%
+  gsub("\\makecell[r]", "\\makecell[c]", ., fixed = TRUE) %>%
+  gsub("objVar$", "objVar.", ., fixed = TRUE) %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position

### 2021-12-16 Tables/mdlTheory.tex
theory tbl fixed

@@
 \hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.05 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[c]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
-\hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.22 (PID.Quality)} &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & \makecell[c]{-0.18 (PID.CoreNeed)\\-0.06 (PID.Quality)} &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & \makecell[c]{-0.14 (PID.CoreNeed)\\-0.41 (PID.Quality)} &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & \makecell[c]{ 0.12 (PID.Allport)\\-0.51 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
+\hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar.cor.slope_intercept.) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.22 (PID.Quality)} &  & -0.09 (objVar.cor.slope_intercept.) &  & -0.16 (objVar.cor.slope_intercept.) &  & \makecell[c]{-0.18 (PID.CoreNeed)\\-0.06 (PID.Quality)} &  & -0.26 (objVar.cor.slope_intercept.) &  & -0.26 (objVar.cor.slope_intercept.) &  & \makecell[c]{-0.14 (PID.CoreNeed)\\-0.41 (PID.Quality)} &  & -0.07 (objVar.cor.slope_intercept.) &  & -0.19 (objVar.cor.slope_intercept.) &  & \makecell[c]{ 0.12 (PID.Allport)\\-0.51 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
 \hspace{1em}$\rho_{00}$ &  &  &  &  & -0.47 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.79 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.10 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.11 (PID.Allport-Quality) &  & 0.07 (PID.CoreNeed-Allport) & \\

### 2021-12-16 Methods-and-Results.Rmd
main tbl fix

--- 2021-12-16 Methods-and-Results.Rmd
@@
   gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>%
+  gsub("\\makecell[r]", "\\makecell[c]", ., fixed = TRUE) %>%
+  gsub("objVar$", "", ., fixed = TRUE) %>%
+  gsub("slope_intercept.", "slope.intercept", ., fixed = TRUE) %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position

### 2021-12-16 Tables/localTables.tex
tabl fix
theory tbl fixed
main tbl fix

@@
 \usepackage{blindtext}
-\usepackage[a1paper, margin=5cm]{geometry}
+\usepackage[a4paper,
+left=20mm,
+ top=10mm,
+ bottom=20mm,
+ right=10mm
+]{geometry}
 \usepackage{graphicx}
@@
 \input{mdlContactGeneral}
-\input{mdlTheory}
+%\input{mdlTheory}
 \input{mdlRobustness}
 
+\begin{landscape}\begin{table}
+\begin{minipage}[t][\textheight][t]{\textwidth}
+
+\caption{\label{tab:intergroupNeedsTbl}Core Need Fulfillment and Allport's Conditions}
+\centering
+\begin{tabular}[t]{lcccccccccccccccccccccccccc}
+\toprule
+\multicolumn{1}{c}{} & \multicolumn{6}{c}{Study 1 - CoreNeed} & \multicolumn{6}{c}{Study 2 - CoreNeed} & \multicolumn{6}{c}{Study 3 - CoreNeed} & \multicolumn{6}{c}{Study 3 - Allport} & \multicolumn{2}{c}{Study 3 - CoreNeed + Allport} \\
+\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13} \cmidrule(l{3pt}r{3pt}){14-19} \cmidrule(l{3pt}r{3pt}){20-25} \cmidrule(l{3pt}r{3pt}){26-27}
+\multicolumn{1}{c}{} & \multicolumn{2}{c}{Quality } & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Quality } & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Quality } & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Quality } & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Attitude} & \multicolumn{2}{c}{Attitude} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){12-13} \cmidrule(l{3pt}r{3pt}){14-15} \cmidrule(l{3pt}r{3pt}){16-17} \cmidrule(l{3pt}r{3pt}){18-19} \cmidrule(l{3pt}r{3pt}){20-21} \cmidrule(l{3pt}r{3pt}){22-23} \cmidrule(l{3pt}r{3pt}){24-25} \cmidrule(l{3pt}r{3pt}){26-27}
+ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$ & $B$ & $\beta$\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{27}{l}{\textbf{Fixed}}\\
+\hspace{1em}(Intercept) & 24.28**** [20.20, 28.36] &  & 72.53**** [66.83, 78.24] &  & 72.50**** [66.75, 78.24] &  & 78.84**** [76.86, 80.83] &  & 70.71**** [67.55, 73.87] &  & 70.67**** [67.50, 73.84] &  & 81.36**** [78.53, 84.19] &  & 68.32**** [65.10, 71.54] &  & 68.32**** [65.09, 71.54] &  & 81.42**** [78.57, 84.26] &  & 68.36**** [65.16, 71.56] &  & 68.34**** [65.12, 71.56] &  & 68.33**** [65.05, 71.61] & \\
+\hspace{1em}CoreNeed & 0.42**** [ 0.32,  0.52] & 0.40 [ 0.31, 0.49] & 0.17** [ 0.06,  0.29] & 0.30 [ 0.18, 0.41] & 0.04 [-0.08,  0.15] & 0.13 [ 0.00, 0.26] & 0.40**** [ 0.28,  0.52] & 0.27 [ 0.18, 0.37] & 0.13*** [ 0.07,  0.19] & 0.14 [ 0.06, 0.22] & 0.03 [-0.01,  0.07] & 0.07 [-0.01, 0.15] & 0.43**** [ 0.33,  0.54] & 0.31 [ 0.24, 0.38] & 0.19**** [ 0.12,  0.27] & 0.18 [ 0.11, 0.24] & 0.11** [ 0.05,  0.17] & 0.11 [ 0.05,  0.17] &  &  &  &  &  &  & 0.13**** [ 0.08,  0.17] & 0.12 [ 0.05, 0.18]\\
+\hspace{1em}Quality &  &  &  &  & 0.23*** [ 0.12,  0.33] & 0.41 [ 0.29, 0.54] &  &  &  &  & 0.17**** [ 0.11,  0.23] & 0.24 [ 0.14, 0.34] &  &  &  &  & 0.17**** [ 0.12,  0.22] & 0.17 [ 0.12,  0.22] &  &  &  &  & 0.17**** [ 0.12,  0.23] & 0.22 [ 0.15, 0.29] &  & \\
+\hspace{1em}Allport &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 0.65**** [ 0.54,  0.76] & 0.46 [ 0.39, 0.52] & 0.22**** [ 0.15,  0.29] & 0.21 [ 0.14, 0.27] & 0.09** [ 0.03,  0.15] & 0.10 [ 0.03, 0.16] & 0.17*** [ 0.09,  0.24] & 0.17 [ 0.11, 0.23]\\
+\addlinespace[0.3em]
+\multicolumn{27}{l}{\textbf{Random}}\\
+\hspace{1em}$\sigma^2$ & 261.1 &  & 63.1 &  & 37.61 &  & 275.7 &  & 89.83 &  & 76.47 &  & 222.5 &  & 91.84 &  & 82.15 &  & 188.9 &  & 93.05 &  & 83.82 &  & 90.78 & \\
+\hspace{1em}$\tau_{00}$ & 71.13 (PID) &  & 172.54 (PID) &  & 177.20 (PID) &  & 63.00 (PID) &  & 259.79 (PID) &  & 264.19 (PID) &  & 131.33 (PID) &  & 182.38 (PID) &  & 183.10 (PID) &  & 134.62 (PID) &  & 179.74 (PID) &  & 182.79 (PID) &  & 189.33 (PID) & \\
+\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.05 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[c]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
+\hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar.cor.slope_intercept.) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.22 (PID.Quality)} &  & -0.09 (objVar.cor.slope_intercept.) &  & -0.16 (objVar.cor.slope_intercept.) &  & \makecell[c]{-0.18 (PID.CoreNeed)\\-0.06 (PID.Quality)} &  & -0.26 (objVar.cor.slope_intercept.) &  & -0.26 (objVar.cor.slope_intercept.) &  & \makecell[c]{-0.14 (PID.CoreNeed)\\-0.41 (PID.Quality)} &  & -0.07 (objVar.cor.slope_intercept.) &  & -0.19 (objVar.cor.slope_intercept.) &  & \makecell[c]{ 0.12 (PID.Allport)\\-0.51 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
+\hspace{1em}$\rho_{00}$ &  &  &  &  & -0.47 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.79 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.10 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.11 (PID.Allport-Quality) &  & 0.07 (PID.CoreNeed-Allport) & \\
+\addlinespace[0.3em]
+\multicolumn{27}{l}{\textbf{Fit}}\\
+\hspace{1em}AIC & 3294 &  & 2816 &  & 2672 &  & 8073 &  & 7222 &  & 7141 &  & 14054 &  & 12632 &  & 12494 &  & 13805 &  & 12652 &  & 12519 &  & 12625 & \\
+\hspace{1em}BIC & 3309 &  & 2839 &  & 2712 &  & 8102 &  & 7251 &  & 7190 &  & 14087 &  & 12665 &  & 12548 &  & 13838 &  & 12684 &  & 12573 &  & 12679 & \\
+\hspace{1em}N & 387 &  & 387 &  & 387 &  & 935 &  & 935 &  & 935 &  & 1676 &  & 1672 &  & 1672 &  & 1676 &  & 1672 &  & 1672 &  & 1672 & \\
+\hspace{1em}Groups & 21 &  & 21 &  & 21 &  & 108 &  & 108 &  & 108 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 & \\
+\hspace{1em}ICC & 0.2141 &  & 0.7447 &  & 0.8399 &  & 0.2547 &  & 0.7471 &  & 0.7835 &  & 0.3933 &  & 0.6738 &  & 0.7006 &  & 0.4433 &  & 0.6679 &  & 0.6963 &  &  & \\
+\hspace{1em}$R^2_{marginal}$ / $R^2_{conditional}$ & 0.117 / 0.306 &  & 0.030 / 0.752 &  & 0.067 / 0.851 &  & 0.102 / 0.331 &  & 0.012 / 0.750 &  & 0.028 / 0.789 &  & 0.070 / 0.436 &  & 0.019 / 0.680 &  & 0.041 / 0.713 &  & 0.149 / 0.526 &  & 0.024 / 0.676 &  & 0.040 / 0.709 &  & 0.086 / NA & \\
+\bottomrule
+\multicolumn{27}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{27}{l}{\rule{0pt}{1em}PID = Participant ID number (grouping variable)}\\
+\multicolumn{27}{l}{\rule{0pt}{1em}$sigma^2$: residual variance, $tau_{00}$: random intercept variance, $tau_{11}$: random slope variance(s), $rho_{01}$: random slope-intercept correlation(s) , $rho_{00}$: correlation(s) between random slopes}\\
+\multicolumn{27}{l}{\rule{0pt}{1em}**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05}\\
+\end{tabular}
+\end{minipage}
+\end{table}
+\end{landscape}
+
 \end{document}

### 2021-12-16 Tables/mdlTheory.tex
main tbl fix

@@
 \hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.05 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[c]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
-\hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar.cor.slope_intercept.) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.22 (PID.Quality)} &  & -0.09 (objVar.cor.slope_intercept.) &  & -0.16 (objVar.cor.slope_intercept.) &  & \makecell[c]{-0.18 (PID.CoreNeed)\\-0.06 (PID.Quality)} &  & -0.26 (objVar.cor.slope_intercept.) &  & -0.26 (objVar.cor.slope_intercept.) &  & \makecell[c]{-0.14 (PID.CoreNeed)\\-0.41 (PID.Quality)} &  & -0.07 (objVar.cor.slope_intercept.) &  & -0.19 (objVar.cor.slope_intercept.) &  & \makecell[c]{ 0.12 (PID.Allport)\\-0.51 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
+\hspace{1em}$\rho_{01}$ &  &  & 0.03 (cor.slope.intercept) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.22 (PID.Quality)} &  & -0.09 (cor.slope.intercept) &  & -0.16 (cor.slope.intercept) &  & \makecell[c]{-0.18 (PID.CoreNeed)\\-0.06 (PID.Quality)} &  & -0.26 (cor.slope.intercept) &  & -0.26 (cor.slope.intercept) &  & \makecell[c]{-0.14 (PID.CoreNeed)\\-0.41 (PID.Quality)} &  & -0.07 (cor.slope.intercept) &  & -0.19 (cor.slope.intercept) &  & \makecell[c]{ 0.12 (PID.Allport)\\-0.51 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
 \hspace{1em}$\rho_{00}$ &  &  &  &  & -0.47 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.79 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.10 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.11 (PID.Allport-Quality) &  & 0.07 (PID.CoreNeed-Allport) & \\

### 2021-12-23 manuscript.tex
Updates from Overleaf
updated

@@
 \usepackage{censor}
+\usepackage{pdflscape}
 \usepackage{lscape}
-\usepackage{pdflscape}
 \usepackage{pdfpages}
 \usepackage{enumitem}
+\usepackage{caption}
+\usepackage{adjustbox}
+\usepackage{makecell}
+\usepackage{tabu}
 
@@
 In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
-And even though over the past 70 years, a plethoray of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}, relatively little research has thus far explained when and why people's everyday inter-group interactions are perceived as positive.
+And even though over the past 70 years, a plethora of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}, relatively little research has thus far explained when and why people's everyday inter-group interactions are perceived as positive.
 

### 2021-12-28 Methods-and-Results.Rmd
initial descriptive table merge

@@
 
+```{r CombinedDescriptivesTbl, include=FALSE}
+
+workerMlCor
+workerOutMlCor
+ifelse(identical(names(workerMlCor), names(workerOutMlCor)), NA, warning("column names not identical"))
+workerDescrComb <- rbind(workerMlCor %>% rownames_to_column(., "Variable"), 
+                         workerOutMlCor %>% rownames_to_column(., "Variable"))
+
+studentMlCor
+studentOutMlCor
+ifelse(identical(names(studentMlCor), names(studentOutMlCor)), NA, warning("column names not identical"))
+studentDescrComb <- rbind(studentMlCor %>% rownames_to_column(., "Variable"), 
+                          studentOutMlCor %>% rownames_to_column(., "Variable"))
+
+medicalMlCor
+medicalOutMlCor
+ifelse(identical(names(medicalMlCor), names(medicalOutMlCor)), NA, warning("column names not identical"))
+medicalDescrComb <- rbind(medicalMlCor %>% rownames_to_column(., "Variable"), 
+                          medicalOutMlCor %>% rownames_to_column(., "Variable"))
+
+ifelse(identical(names(workerDescrComb), names(studentDescrComb)), NA, warning("column names not identical"))
+DescrComb1 <- rbind(workerDescrComb, studentDescrComb)
+
+ifelse(identical(names(DescrComb1), names(medicalDescrComb)), NA, warning("column names not identical"))
+
+rbind(DescrComb1 %>% mutate(Allport = ""), medicalDescrComb %>% select(names(studentDescrComb), "Allport"))
+
+```
+
 \input{Tables/mdlContactGeneral}

### 2021-12-28 Tables/studentOutVarDescr.tex
AOT-M contact H results rendered
z test
initial descriptive table merge

@@
 
-\caption{\label{tab:studentOutVarDescr}Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
+\caption{Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
 \centering
+\resizebox{\linewidth}{!}{
 \begin{tabular}[t]{llccccc}

### 2022-01-03 Methods-and-Results.Rmd
re-run with descriptives test

--- 2021-12-16 Methods-and-Results.Rmd
@@
 
+```{r CombinedDescriptivesTbl, include=FALSE}
+# Full Sample Descriptives Table
+rbind(
+  workerMlCor %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  studentMlCor %>%
+    select(names(workerMlCor)) %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  medicalMlCor %>%
+    select(names(workerMlCor), "Allport") %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1))) %>%
+  pack_rows("Study 1", 1, nrow(workerMlCor)) %>%
+  pack_rows("Study 2", nrow(workerMlCor) + 1,
+            sum(nrow(workerMlCor), nrow(studentMlCor))) %>%
+  pack_rows("Study 3", sum(nrow(workerMlCor), nrow(studentMlCor)) + 1,  
+            sum(nrow(workerMlCor), nrow(studentMlCor), nrow(medicalMlCor))) %>%
+  gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) # fix table position
+
+# Full Sample Descriptives Table --- wider version
+rbind(
+  workerMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  studentMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  medicalMlCor %>%
+    select(names(workerMlCor), "Allport") %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1)))  %>%
+  kable_classic() %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Correlations" = ncol(medicalMlCor),
+      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
+    )
+  ) %>%
+  pack_rows("Study 1", 1, ncol(workerMlCor)) %>%
+  pack_rows("Study 2", ncol(workerMlCor) + 1,
+            sum(ncol(workerMlCor), ncol(studentMlCor))) %>%
+  pack_rows("Study 3", sum(ncol(workerMlCor), ncol(studentMlCor)) + 1,  
+            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor)))
+
+# Outgroup Interaction Sample Descriptives Table
+rbind(
+  workerOutMlCor %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  studentOutMlCor %>%
+    select(names(workerOutMlCor)) %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  medicalOutMlCor %>%
+    select(names(workerOutMlCor), "Allport") %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1))) %>%
+  pack_rows("Study 1", 1, nrow(workerOutMlCor)) %>%
+  pack_rows("Study 2", nrow(workerOutMlCor) + 1,
+            sum(nrow(workerOutMlCor), nrow(studentOutMlCor))) %>%
+  pack_rows("Study 3", sum(nrow(workerOutMlCor), nrow(studentOutMlCor)) + 1,  
+            sum(nrow(workerOutMlCor), nrow(studentOutMlCor), nrow(medicalOutMlCor))) %>%
+  gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) # fix table position
+
+# Outgroup Interaction Sample Descriptives Table --- wider version
+rbind(
+  workerOutMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  studentOutMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  medicalOutMlCor %>%
+    select(names(workerOutMlCor), "Allport") %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1))) %>%
+  pack_rows("Study 1", 1, ncol(workerOutMlCor)) %>%
+  pack_rows("Study 2", ncol(workerOutMlCor) + 1,
+            sum(ncol(workerOutMlCor), ncol(studentOutMlCor))) %>%
+  pack_rows("Study 3", sum(ncol(workerOutMlCor), ncol(studentOutMlCor)) + 1,  
+            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor)))
+
+```
+
 \input{Tables/mdlContactGeneral}

### 2022-01-03 Tables/mdlContactGeneral.tex
re-run with descriptives test

@@
 \hspace{1em}$\tau_{00}$ &  &  &  &  &  &  & 164.13 (PID) &  & 488.38 (PID) &  & 366.51 (PID) & \\
-\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & \makecell[r]{48.94 (PID.OutgroupInteraction)\\ 7.23 (PID.NonOutgroupInteraction)} &  & \makecell[r]{40.53 (PID.OutgroupInteraction)\\ 3.43 (PID.NonOutgroupInteraction)} & \\
+\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & \makecell[c]{48.94 (PID.OutgroupInteraction)\\ 7.23 (PID.NonOutgroupInteraction)} &  & \makecell[c]{40.53 (PID.OutgroupInteraction)\\ 3.43 (PID.NonOutgroupInteraction)} & \\
 \hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & \makecell[c]{-0.72 (PID.OutgroupInteraction)\\ 0.12 (PID.NonOutgroupInteraction)} &  & \makecell[c]{-0.70 (PID.OutgroupInteraction)\\-0.28 (PID.NonOutgroupInteraction)} & \\

### 2022-01-04 Methods-and-Results.Rmd
descr tables added

--- 2021-12-16 Methods-and-Results.Rmd
@@
 
+```{r CombinedDescriptivesTbl, include=FALSE}
+
+# ALTERNATIVE:
+# Full Sample Descriptives Table [longer format (Descriptives below correlations)]
+rbind(
+  workerMlCor %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  studentMlCor %>%
+    select(names(workerMlCor)) %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  medicalMlCor %>%
+    select(names(workerMlCor), "Allport") %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1))) %>%
+  pack_rows("Study 1", 1, nrow(workerMlCor)) %>%
+  pack_rows("Study 2", nrow(workerMlCor) + 1,
+            sum(nrow(workerMlCor), nrow(studentMlCor))) %>%
+  pack_rows("Study 3", sum(nrow(workerMlCor), nrow(studentMlCor)) + 1,  
+            sum(nrow(workerMlCor), nrow(studentMlCor), nrow(medicalMlCor))) %>%
+  gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/descrFullLong.tex")
+
+# Full Sample Descriptives Table [wider format (descriptives next to correlation)]
+rbind(
+  workerMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  studentMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  medicalMlCor %>%
+    select(names(workerMlCor), "Allport") %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1)))  %>%
+  kable_classic() %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Correlations" = ncol(medicalMlCor),
+      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
+    )
+  ) %>%
+  pack_rows("Study 1", 1, ncol(workerMlCor)) %>%
+  pack_rows("Study 2", ncol(workerMlCor) + 1,
+            sum(ncol(workerMlCor), ncol(studentMlCor))) %>%
+  pack_rows("Study 3", sum(ncol(workerMlCor), ncol(studentMlCor)) + 1,  
+            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor))) %>% # fix table position
+  save_kable("Tables/descrFullWide.tex")
+
+# Outgroup Interaction Sample Descriptives Table
+rbind(
+  workerOutMlCor %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  studentOutMlCor %>%
+    select(names(workerOutMlCor)) %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  medicalOutMlCor %>%
+    select(names(workerOutMlCor), "Allport") %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1))) %>%
+  pack_rows("Study 1", 1, nrow(workerOutMlCor)) %>%
+  pack_rows("Study 2", nrow(workerOutMlCor) + 1,
+            sum(nrow(workerOutMlCor), nrow(studentOutMlCor))) %>%
+  pack_rows("Study 3", sum(nrow(workerOutMlCor), nrow(studentOutMlCor)) + 1,  
+            sum(nrow(workerOutMlCor), nrow(studentOutMlCor), nrow(medicalOutMlCor))) %>%
+  gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/descrOutLong.tex")
+
+# Outgroup Interaction Sample Descriptives Table --- wider version
+rbind(
+  workerOutMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  studentOutMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  medicalOutMlCor %>%
+    select(names(workerOutMlCor), "Allport") %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1))) %>%
+  pack_rows("Study 1", 1, ncol(workerOutMlCor)) %>%
+  pack_rows("Study 2", ncol(workerOutMlCor) + 1,
+            sum(ncol(workerOutMlCor), ncol(studentOutMlCor))) %>%
+  pack_rows("Study 3", sum(ncol(workerOutMlCor), ncol(studentOutMlCor)) + 1,  
+            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor))) %>% 
+  save_kable("Tables/descrOutWide.tex")
+
+```
+
+\input{Tables/descrFullWide}
+\input{Tables/descrOutWide}
+
 \input{Tables/mdlContactGeneral}

### 2022-01-04 Methods-and-Results.Rmd
Update Methods-and-Results.Rmd
descr tables individual export

--- 2021-12-28 Methods-and-Results.Rmd
@@
 
-```{r CombinedDescriptivesTbl, include=FALSE}
-
-workerMlCor
-workerOutMlCor
-ifelse(identical(names(workerMlCor), names(workerOutMlCor)), NA, warning("column names not identical"))
-workerDescrComb <- rbind(workerMlCor %>% rownames_to_column(., "Variable"), 
-                         workerOutMlCor %>% rownames_to_column(., "Variable"))
-
-studentMlCor
-studentOutMlCor
-ifelse(identical(names(studentMlCor), names(studentOutMlCor)), NA, warning("column names not identical"))
-studentDescrComb <- rbind(studentMlCor %>% rownames_to_column(., "Variable"), 
-                          studentOutMlCor %>% rownames_to_column(., "Variable"))
-
-medicalMlCor
-medicalOutMlCor
-ifelse(identical(names(medicalMlCor), names(medicalOutMlCor)), NA, warning("column names not identical"))
-medicalDescrComb <- rbind(medicalMlCor %>% rownames_to_column(., "Variable"), 
-                          medicalOutMlCor %>% rownames_to_column(., "Variable"))
-
-ifelse(identical(names(workerDescrComb), names(studentDescrComb)), NA, warning("column names not identical"))
-DescrComb1 <- rbind(workerDescrComb, studentDescrComb)
-
-ifelse(identical(names(DescrComb1), names(medicalDescrComb)), NA, warning("column names not identical"))
-
-rbind(DescrComb1 %>% mutate(Allport = ""), medicalDescrComb %>% select(names(studentDescrComb), "Allport"))
-
-```
+```{r descrFullLong, include=FALSE}
+# Full Sample Descriptives Table [longer format (Descriptives below correlations)]
+rbind(
+  workerMlCor %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  studentMlCor %>%
+    select(names(workerMlCor)) %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  medicalMlCor %>%
+    select(names(workerMlCor), "Allport") %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      caption = "Descr Full Long",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1))) %>%
+  pack_rows("Study 1", 1, nrow(workerMlCor)) %>%
+  pack_rows("Study 2", nrow(workerMlCor) + 1,
+            sum(nrow(workerMlCor), nrow(studentMlCor))) %>%
+  pack_rows("Study 3", sum(nrow(workerMlCor), nrow(studentMlCor)) + 1,  
+            sum(nrow(workerMlCor), nrow(studentMlCor), nrow(medicalMlCor))) %>%
+  gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) %>% # fix table position
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/descrFullLong.tex")
+```
+
+```{r descrFullWide, include=FALSE}
+# Full Sample Descriptives Table [wider format (descriptives next to correlation)]
+rbind(
+  workerMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  studentMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  medicalMlCor %>%
+    select(names(workerMlCor), "Allport") %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      caption = "Descr Full Wide",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1)))  %>%
+  kable_classic() %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Correlations" = ncol(medicalMlCor),
+      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
+    )
+  ) %>%
+  pack_rows("Study 1", 1, ncol(workerMlCor)) %>%
+  pack_rows("Study 2", ncol(workerMlCor) + 1,
+            sum(ncol(workerMlCor), ncol(studentMlCor))) %>%
+  pack_rows("Study 3", sum(ncol(workerMlCor), ncol(studentMlCor)) + 1,  
+            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor))) %>% # fix table position
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/descrFullWide.tex")
+```
+
+```{r descrOutLong, include=FALSE}
+# Outgroup Interaction Sample Descriptives Table
+rbind(
+  workerOutMlCor %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  studentOutMlCor %>%
+    select(names(workerOutMlCor)) %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = ""),
+  medicalOutMlCor %>%
+    select(names(workerOutMlCor), "Allport") %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      caption = "Descr Out Long",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1))) %>%
+  pack_rows("Study 1", 1, nrow(workerOutMlCor)) %>%
+  pack_rows("Study 2", nrow(workerOutMlCor) + 1,
+            sum(nrow(workerOutMlCor), nrow(studentOutMlCor))) %>%
+  pack_rows("Study 3", sum(nrow(workerOutMlCor), nrow(studentOutMlCor)) + 1,  
+            sum(nrow(workerOutMlCor), nrow(studentOutMlCor), nrow(medicalOutMlCor))) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/descrOutLong.tex")
+```
+
+```{r descrOutWide, include=FALSE}
+# Outgroup Interaction Sample Descriptives Table --- wider version
+rbind(
+  workerOutMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  studentOutMlCor %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean"),
+  medicalOutMlCor %>%
+    select(names(workerOutMlCor), "Allport") %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      caption = "Descr Out Wide",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1))) %>%
+  pack_rows("Study 1", 1, ncol(workerOutMlCor)) %>%
+  pack_rows("Study 2", ncol(workerOutMlCor) + 1,
+            sum(ncol(workerOutMlCor), ncol(studentOutMlCor))) %>%
+  pack_rows("Study 3", sum(ncol(workerOutMlCor), ncol(studentOutMlCor)) + 1,  
+            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor))) %>% 
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/descrOutWide.tex")
+
+```
+
+\input{Tables/descrFullWide}
+\input{Tables/descrOutWide}
+
+\input{Tables/descrFullLong}
+\input{Tables/descrOutLong}
 

### 2022-01-04 Methods-and-Results.Rmd
table adjustments

@@
       align = c("l", rep("c", ncol(.) - 1))) %>%
+  kable_classic() %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Correlations" = ncol(medicalMlCor),
+      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
+    )
+  ) %>%
   pack_rows("Study 1", 1, ncol(workerOutMlCor)) %>%

### 2022-01-04 Tables/studentOutVarDescr.tex
re-run with descriptives test
table adjustments

@@
 
-\caption{Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
+\caption{\label{tab:studentOutVarDescr}Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
 \centering
@@
 Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 78.80 & 70.41\\
-Between-person SD & 11.20 & 13.95 & 14.07 & 17.35 & 10.71 & 17.13\\
-Within-person SD & 15.87 & 16.81 & 14.24 & 26.14 & 17.88 & 9.87\\
+Between SD & 11.20 & 13.95 & 14.07 & 17.35 & 10.71 & 17.13\\
+Within SD & NA & NA & NA & NA & NA & NA\\
 ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.14 & 0.72\\
 ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.59 & 0.96\\
+Within.person.SD & 15.87 & 16.81 & 14.24 & 26.14 & 17.88 & 9.87\\
 \bottomrule

### 2022-01-04 Tables/studentVarDescr.tex
z test
methods and results re-run
initial descriptive table merge
re-run with descriptives test
table adjustments

@@
 \centering
+\resizebox{\linewidth}{!}{
 \begin{tabular}[t]{llccccc}
@@
 Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 83.77 & 67.26\\
-Between-person SD & 9.17 & 14.47 & 11.21 & 13.36 & 9.12 & 18.64\\
-Within-person SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
+Between SD & 9.17 & 14.47 & 11.21 & 13.36 & 9.12 & 18.64\\
+Within SD & NA & NA & NA & NA & NA & NA\\
 ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.20 & 0.80\\
 ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.88 & 0.99\\
+Within.person.SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
 \bottomrule

### 2022-01-04 Tables/workerOutVarDescr.tex
re-run with descriptives test
table adjustments

@@
 
-\caption{Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
+\caption{\label{tab:workerOutVarDescr}Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
 \centering
@@
 Grand Mean & 32.20 & 16.53 & 22.64 & 1.58 & 24.10 & 72.46\\
-Between-person SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.50 & 13.62\\
-Within-person SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.85 & 9.50\\
+Between SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.50 & 13.62\\
+Within SD & NA & NA & NA & NA & NA & NA\\
 ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.18 & 0.68\\
 ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.80 & 0.98\\
+Within.person.SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.85 & 9.50\\
 \bottomrule

### 2022-01-04 Tables/workerVarDescr.tex
AOT-M contact H results rendered
z test
run but not rendered
re-run with descriptives test
table adjustments

@@
 Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 24.10 & 71.49\\
-Between-person SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.50 & 12.91\\
-Within-person SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
+Between SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.50 & 12.91\\
+Within SD & NA & NA & NA & NA & NA & NA\\
 ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.18 & 0.70\\
 ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.79 & 0.99\\
+Within.person.SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
 \bottomrule

### 2022-01-04 scripts/functions/MlCorMat.R

@@ -135,13 +135,13 @@ MlCorMat <-
         select(paste0(selection, "_trait")) %>%
         distinct %>%
         colMeans(., na.rm = TRUE),
-      `Between-person SD` =
+      `Between SD` =
         data %>%
         select(paste0(selection, "_trait")) %>%
         distinct %>%
         summarise_all(sd, na.rm = TRUE) %>%
         unlist,
-      `Within-person SD` = NA,
+      `Within SD` = NA,
       `ICC(1)` =
         misty::multilevel.icc(
           data %>% select(selection),
@@ -186,8 +186,8 @@ MlCorMat <-
       rbind(rMlComb, t(descriptives)) %>%
       as.data.frame
     rownames(out)[rownames(out) == "Grand.Mean"] <- "Grand Mean"
-    rownames(out)[rownames(out) == "Between.person.SD"] <- "Between-person SD"
-    rownames(out)[rownames(out) == "Within.person.SD"] <- "Within-person SD"
+    rownames(out)[rownames(out) == "Between.SD"] <- "Between SD"
+    rownames(out)[rownames(out) == "Within.SD"] <- "Within SD"
     rownames(out)[rownames(out) == "ICC.1."] <- "ICC(1)"
     rownames(out)[rownames(out) == "ICC.2."] <- "ICC(2)"
     

### 2022-01-04 Tables/studentOutVarDescr.tex
descr table within sd fixed

@@
 Between SD & 11.20 & 13.95 & 14.07 & 17.35 & 10.71 & 17.13\\
-Within SD & NA & NA & NA & NA & NA & NA\\
+Within SD & 15.87 & 16.81 & 14.24 & 26.14 & 17.88 & 9.87\\
 ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.14 & 0.72\\
 ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.59 & 0.96\\
-Within.person.SD & 15.87 & 16.81 & 14.24 & 26.14 & 17.88 & 9.87\\
 \bottomrule

### 2022-01-04 Tables/workerOutVarDescr.tex
descr table within sd fixed

@@
 Between SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.50 & 13.62\\
-Within SD & NA & NA & NA & NA & NA & NA\\
+Within SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.85 & 9.50\\
 ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.18 & 0.68\\
 ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.80 & 0.98\\
-Within.person.SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.85 & 9.50\\
 \bottomrule

### 2022-01-04 scripts/functions/MlCorMat.R

@@ -161,7 +161,7 @@ MlCorMat <-
         data %>%
         select(id, selection[i]) %>%
         na.omit
-      descriptives$Within.person.SD[i] <-
+      descriptives$Within.SD[i] <-
         sqrt(sum(
           misty::cluster.scores(
             x = dataRed %>% select(selection[i]) ,

### 2022-01-05 Methods-and-Results.Rmd
surplus descr tables removed
new mdl tbl

@@
 
-\input{Tables/workerVarDescr}
-\input{Tables/workerOutVarDescr}
-
 \subsection{Results}
@@
 
-\input{Tables/studentVarDescr}
-\input{Tables/studentOutVarDescr}
-
 \subsection{Results}
@@
 All survey details are also available in Online Supplemental Materials A and B.
-
-\input{Tables/medicalVarDescr}
-\input{Tables/medicalOutVarDescr}
 
@@
 
-```{r intergroupNeedsTbl, include=FALSE}
+```{r intergroupNeedsTblLong, include=FALSE}
 # Table of core need and Allports Conditions (potentially two tables — e.g., needs + allport)
@@
 
+# Long format
+shortMdlPrep <- list()
+for(i in 1:length(mdlPrep)){
+  study <- gsub("S", "Study", str_extract(mdlPrep[[i]]$fit$data, "S1|S2|S3"))
+  dv <- gsub("Raw", "", sub(" ~.*", "", mdlPrep[[i]]$fit$formula)) 
+  pred <- gsub("\\(Intercept\\)", "", paste(mdlPrep[[i]]$coeficients$coef, collapse = ''))
+
+  name <- paste(study, dv, pred, sep='.')
+  tmp <- rbind(
+    mdlPrep[[i]]$coeficients[, c("coef", "B", "Beta")],
+    data.frame(
+      coef = "R2Marg_R2Cond",
+      B = mdlPrep[[i]]$fit$R2Marg_R2Cond,
+      Beta = ""
+    )
+  )
+  shortMdlPrep[[name]] <- tmp
+}
+
+# Manual assembly
+emptyNeedTbl <- data.frame(coef = shortMdlPrep$Study3.Attitude.CoreNeedQuality$coef, B = NA, Beta = NA)
+tmp <- shortMdlPrep[grepl("Study1", names(shortMdlPrep))]
+s1MdlTbl <- data.frame(coef = shortMdlPrep$Study1.Attitude.CoreNeedQuality$coef)
+for (i in 1:length(tmp)){
+  s1MdlTbl <- join(s1MdlTbl, tmp[[i]], by = "coef")
+}
+s1MdlTbl <- s1MdlTbl %>%
+  join(., emptyNeedTbl, by = "coef")
+tmp <- shortMdlPrep[grepl("Study2", names(shortMdlPrep))]
+s2MdlTbl <- data.frame(coef = shortMdlPrep$Study2.Attitude.CoreNeedQuality$coef)
+for (i in 1:length(tmp)){
+  s2MdlTbl <- join(s2MdlTbl, tmp[[i]], by = "coef")
+}
+s2MdlTbl <- s2MdlTbl %>%
+  join(., emptyNeedTbl, by = "coef")
+
+s3NeedMdlTbl <- data.frame(coef = shortMdlPrep$Study3.Attitude.CoreNeedQuality$coef) %>%
+  join(., shortMdlPrep$Study3.Quality.CoreNeed, by = "coef") %>%
+  join(., shortMdlPrep$Study3.Attitude.CoreNeed, by = "coef") %>%
+  join(., shortMdlPrep$Study3.Attitude.CoreNeedQuality, by = "coef") %>%
+  join(., emptyNeedTbl, by = "coef")
+
+s3AllportMdlTbl <- data.frame(coef = shortMdlPrep$Study3.Attitude.AllportQuality$coef) %>%
+  join(., shortMdlPrep$Study3.Quality.Allport, by = "coef") %>%
+  join(., shortMdlPrep$Study3.Attitude.Allport, by = "coef") %>%
+  join(., shortMdlPrep$Study3.Attitude.AllportQuality, by = "coef") %>%
+  join(., emptyNeedTbl, by = "coef")
+
+emptyNeedAllportTbl <- data.frame(coef = shortMdlPrep$Study3.Attitude.CoreNeedAllport$coef, B = NA, Beta = NA)
+s3NeedAllportMdlTbl <- emptyNeedAllportTbl %>%
+  join(., emptyNeedAllportTbl, by = "coef") %>%
+  join(., emptyNeedAllportTbl, by = "coef") %>%
+  join(., shortMdlPrep$Study3.Attitude.CoreNeedAllport, by = "coef")
+
+mdlTblLong <- rbind(
+  s1MdlTbl,
+  s2MdlTbl,
+  s3NeedMdlTbl,
+  s3AllportMdlTbl,
+  s3NeedAllportMdlTbl
+)
+
+mdlTblLong$coef <- mapvalues(
+  mdlTblLong$coef,
+  from = c(
+    "R2Marg_R2Cond"
+  ),
+  to = c(
+    "$R^2_{marginal}$ / $R^2_{conditional}$"
+  )
+)
+
+mdlTblTheoreticalLong <- mdlTblLong %>%
+  replace(is.na(.), "") %>%
+  #mutate_all(linebreak) %>%
+  kbl(
+    .,
+    caption = "Theoretical Test: Core Need Fulfillment and Allport's Conditions",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = c("l", rep("c", ncol(.)-1)),
+    escape = FALSE
+  ) %>%
+  kable_classic() %>%
+  add_header_above(., c(" ", "Quality" = 2, "Attitude" = 6)) %>%
+  pack_rows("Study 1: Needs", 1, 4) %>%
+  pack_rows("Study 2: Needs", 5, 8) %>%
+  pack_rows("Study 3: Needs", 9, 12) %>%
+  pack_rows("Study 3: Allport", 13, 16) %>%
+  pack_rows("Study 3: Needs & Allport", 17, 20)  %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/mdlTheorylong.tex")
+```
+
+```{r intergroupNeedsTblWide, include=FALSE}
+# wide format
 mdlTbl <- data.frame(
@@
 
+# Wide format
 mdlRobustTbl <- data.frame(
@@
 
-\input{Tables/descrFullWide}
-\input{Tables/descrOutWide}
+<!-- \input{Tables/descrFullWide} -->
+<!-- \input{Tables/descrOutWide} -->
 
@@
 \input{Tables/mdlContactGeneral}
-\input{Tables/mdlTheory}
+<!-- \input{Tables/mdlTheory} -->
+\input{Tables/mdlTheorylong}
 \input{Tables/mdlRobustness}

### 2022-01-05 Methods-and-Results.Rmd
mdl tbl resize

@@
   pack_rows("Study 3: Needs & Allport", 17, 20)  %>%
+  kable_styling(latex_options = "scale_down") %>%
+  kableExtra::landscape() %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position

### 2022-01-05 Methods-and-Results.Rmd
general tbl added

@@
 
-```{r intergroupGeneralTbl, include=FALSE}
+```{r intergroupGeneralTblLong, include=FALSE}
 # Table of intergroup contact in ESM data:
@@
 
-summ(mdlWorker$lmAttFreqQualX)
+# summ(mdlWorker$lmAttFreqQualX)
 
@@
 names(mdlTblGeneralLmer) <- make.unique(names(mdlTblGeneralLmer))
+names(mdlTblGeneralLmer) <- gsub("Beta", "ES", names(mdlTblGeneralLmer))
+names(mdlTblGeneralLm) <- make.unique(names(mdlTblGeneralLm))
+names(mdlTblGeneralLm) <- gsub("Eta2_partial", "ES", names(mdlTblGeneralLm))
+
+#mdlTblGeneralLong <- 
+  rbind(mdlTblGeneralLm %>%
+                             filter(
+                               coef %in% c(
+                                 "(Intercept)",
+                                 "SumContactNL",
+                                 "AvQuality",
+                                 "SumContactNL:AvQuality",
+                                 "R2_R2_adjusted"
+                               )
+                             ),
+                           mdlTblGeneralLmer %>%
+                             filter(
+                               coef %in% c(
+                                 "(Intercept)",
+                                 "OutgroupInteraction",
+                                 "NonOutgroupInteraction",
+                                 "R2Marg_R2Cond"
+                               )
+                             )) %>%
+    replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Intergroup General",
+    #format = "latex",
+    linesep = "",
+    booktabs = TRUE,
+    col.names = c("", rep(c("$B$", "Effect Size"), (ncol(.)-1)/2)),
+    align = c("l", rep("c", ncol(.) - 1)),
+    escape = FALSE,
+    digits = 3
+  )  %>%
+  kable_classic() %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Study 1" = 2,
+      "Study 2" = 2,
+      "Study 3" = 2
+    )
+  ) %>%
+  pack_rows("Between Participant [aggregated linear regression] (ES = $\\eta_{partial}$)", 1, 5) %>%
+  pack_rows("Within Participants [multilevel linear regression] (ES = $Beta$)", 6, 9) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  kableExtra::landscape() %>%
+  save_kable("Tables/mdlContactGeneralLong.tex")
+```
+
+```{r intergroupGeneralTblWide, include=FALSE}
 mdlTblGeneral <-
@@
 \input{Tables/mdlContactGeneral}
+\input{Tables/mdlContactGeneralLong}
 <!-- \input{Tables/mdlTheory} -->

### 2022-01-05 Methods-and-Results.Rmd
general tbl escape fix

@@
   ) %>%
-  pack_rows("Between Participant [aggregated linear regression] (ES = $\\eta_{partial}$)", 1, 5) %>%
-  pack_rows("Within Participants [multilevel linear regression] (ES = $Beta$)", 6, 9) %>%
+  pack_rows("Between Participant [aggregated linear regression] (ES = $\\eta_{partial}$)", 1, 5, escape = FALSE) %>%
+  pack_rows("Within Participants [multilevel linear regression] (ES = $Beta$)", 6, 9, escape = FALSE) %>%
   kable_styling(latex_options = "scale_down") %>%

### 2022-01-05 Methods-and-Results.Rmd
table footnotes

--- 2022-01-05 Methods-and-Results.Rmd
@@
 
-#mdlTblGeneralLong <- 
+mdlTblGeneralLong <- 
   rbind(mdlTblGeneralLm %>%
@@
                                )
-                             )) %>%
+                             ))
+mdlTblGeneralLong$coef <- mapvalues(
+  mdlTblGeneralLong$coef,
+  from = c(
+    "R2_R2_adjusted",
+    "R2Marg_R2Cond"
+  ),
+  to = c(
+    "$R^2 / R^2_{adjusted}$",
+    "$R^2_{marginal} / R^2_{conditional}$"
+  )
+)
+mdlTblGeneralLong %>%
     replace(is.na(.), "") %>%
@@
     caption = "Intergroup General",
-    #format = "latex",
+    format = "latex",
     linesep = "",
@@
   ) %>%
-  pack_rows("Between Participant [aggregated linear regression] (ES = $\\eta_{partial}$)", 1, 5) %>%
-  pack_rows("Within Participants [multilevel linear regression] (ES = $Beta$)", 6, 9) %>%
+  pack_rows("Between Participant [aggregated linear regression] (Effect Size = $\\eta_{partial}$)", 1, 5, escape = FALSE) %>%
+  pack_rows("Within Participants [multilevel linear regression] (Effect Size = $\\beta$)", 6, 9, escape = FALSE) %>%
+  footnote(
+    general = c("**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"), 
+    escape = FALSE
+  ) %>%
   kable_styling(latex_options = "scale_down") %>%

### 2022-01-05 Methods-and-Results.Rmd
robust long tbl added

@@
 
-```{r robustnessTbl, include=FALSE}
+```{r robustnessTblLong, include=FALSE}
 # Table of all robustness checks (w/ and w/out SDT only)
@@
 
+# manual assembly
+shortRobustPrep <- list()
+for(i in 1:length(mdlRobustPrep)){
+  study <- str_extract(mdlRobustPrep[[i]]$fit$data, "Worker|Student|Medical")
+  sample <- str_extract(mdlRobustPrep[[i]]$fit$data, "Full|Out")
+  #dv <- sub(" ~.*", "", mdlRobustPrep[[i]]$fit$formula)
+  #pred <- gsub("\\(Intercept\\)", "", paste(mdlRobustPrep[[i]]$coeficients$coef, collapse = ''))
+
+  name <- paste(study, sample, sep='.')
+  tmp <- rbind(
+    mdlRobustPrep[[i]]$coeficients[, c("coef", "B", "Beta")],
+    data.frame(
+      coef = "R2Marg_R2Cond",
+      B = mdlRobustPrep[[i]]$fit$R2Marg_R2Cond,
+      Beta = ""
+    )
+  )
+  shortRobustPrep[[name]] <- tmp
+}
+
+tmp <- shortRobustPrep[grepl("Full", names(shortRobustPrep))]
+fullRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Full$coef)
+for (i in 1:length(tmp)){
+  fullRobustTbl <- join(fullRobustTbl, tmp[[i]], by = "coef")
+}
+
+tmp <- shortRobustPrep[grepl("Out", names(shortRobustPrep))]
+outRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Out$coef)
+for (i in 1:length(tmp)){
+  outRobustTbl <- join(outRobustTbl, tmp[[i]], by = "coef")
+}
+
+robustTblLong <- rbind(
+  fullRobustTbl,
+  outRobustTbl
+)
+
+robustTblLong$coef <- mapvalues(
+  robustTblLong$coef,
+  from = c(
+    "R2Marg_R2Cond"
+  ),
+  to = c(
+    "$R^2_{marginal}$ / $R^2_{conditional}$"
+  )
+)
+
+mdlTblRobustLong <- robustTblLong %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Robustness Analyses",
+    #format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = c("l", rep("c", ncol(.)-1)),
+    escape = FALSE
+  ) %>%
+  kable_classic() %>%
+  add_header_above(., c(" ", "Study 1" = 2, "Study 2" = 2, "Study 3" = 2)) %>%
+  pack_rows("Contact [Full Sample]", 1, 5) %>%
+  pack_rows("Self-Determination Theory [Outgroup Interactions only]", 6, 11) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  kableExtra::landscape() %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/mdlRobustlong.tex")
+```
+
+```{r robustnessTblWide, include=FALSE}
 # Wide format
@@
 
-\input{Tables/mdlContactGeneral}
+<!-- \input{Tables/mdlContactGeneral} -->
 \input{Tables/mdlContactGeneralLong}
+
 <!-- \input{Tables/mdlTheory} -->
 \input{Tables/mdlTheorylong}
+
 \input{Tables/mdlRobustness}
+\input{Tables/mdlRobustlong}
 

### 2022-01-06 Methods-and-Results.Rmd
surplus table rm
s1 av cor added

@@
 Based on our main hypotheses, the aim of our first study is to specifically test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
-To this aim, we conducted an intensive longitudinal survey study with recent migrants to the Netherlands, gathering a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations.
-Data was collected from May 5th through June 6th, 2018 (and all participants started the study within the first two days).
+To this aim, we conducted an intensive longitudinal survey study with recent migrants to the Netherlands.
+Data was collected from May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all participants started the study within the first two days).
 
 The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
-Correlations and descriptive statistics of the included variables are available in Table \ref{tab:workerVarDescr} and Table \ref{tab:workerOutVarDescr}.
+Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullLong} and Table \ref{tab:descrOutLong}.
 
@@
 With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(workerSampleInfo$dailiesN)`).
-This is a common number of measurements found in experience sampling studies and should offer sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
+This is a common number of measurements found in experience sampling studies and offers sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
 Participants were compensated for their participation with up to 34 Euros – each two Euros for pre- and post-questionnaire as well as 50 Eurocents for every experience sampling measurement occasion.
@@
 )
+
+rContactAvg <- dtWorkerSupp$workerAvFreQual %>% 
+  select(SumContactNL, SumContactNLAll, AvAttitude) %>%
+  as.matrix %>%
+  rcorr
+
+rContactAvgMax <- format(round(max(abs(rContactAvg$r[rownames(rContactAvg$r) != "AvAttitude","AvAttitude"])),2), nsmall = 2)
+pContactAvgMin <- format(round(min(rContactAvg$P[rownames(rContactAvg$P) != "AvAttitude","AvAttitude"]),3), nsmall = 3)
 ```
@@
 Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
-We find that neither the number of interactions nor the number of daily diary responses with an interaction were significantly related with the average outgroup attitudes.
+We find that neither the number of interactions nor the number of daily diary responses with an interaction were significantly related with the average outgroup attitudes (all |\textit{r}| < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`).
 This is to say that within our data, participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
@@
 
-\input{Tables/mdlRobustness}
+<!-- \input{Tables/mdlRobustness} -->
 \input{Tables/mdlRobustlong}

### 2022-01-06 Methods-and-Results.tex
descr tables added
tables added
surplus descr tables removed
new mdl tbl
general tbl added
robust long tbl added
surplus table rm
s1 av cor added

@@
 contacts. To this aim, we conducted an intensive longitudinal survey
-study with recent migrants to the Netherlands, gathering a large body of
-ecologically valid data on need satisfaction in real-life intergroup
-contact situations. Data was collected from May 5th through June 6th,
-2018 (and all participants started the study within the first two days).
+study with recent migrants to the Netherlands. Data was collected from
+May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and
+all participants started the study within the first two days).
 
@@
 Materials B. Correlations and descriptive statistics of the included
-variables are available in Table \ref{tab:workerVarDescr} and Table
-\ref{tab:workerOutVarDescr}.
+variables are available in Table \ref{tab:descrFullLong} and Table
+\ref{tab:descrOutLong}.
 
@@
 is a common number of measurements found in experience sampling studies
-and should offer sufficient power to model processes within and between
+and offers sufficient power to model processes within and between
 participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
@@
 an interaction were significantly related with the average outgroup
-attitudes. This is to say that within our data, participants with more
-outgroup interactions did not have significantly more positive outgroup
-attitudes. This might be due to the aggregation within the participants
-or the small sample size of between participant data. Nonetheless, the
-aggregated data does not support the notion that simply having more
-interactions with an outgroup results in more positive outgroup
-attitudes.
+attitudes (all \textbar{}\textit{r}\textbar{} \textless{} 0.03, all
+\textit{p} \textgreater{} 0.887). This is to say that within our data,
+participants with more outgroup interactions did not have significantly
+more positive outgroup attitudes. This might be due to the aggregation
+within the participants or the small sample size of between participant
+data. Nonetheless, the aggregated data does not support the notion that
+simply having more interactions with an outgroup results in more
+positive outgroup attitudes.
 
@@
 available in Online Supplemental Materials A and B.
-
-\input{Tables/studentVarDescr}
-\input{Tables/studentOutVarDescr}
 
@@
 
-\input{Tables/medicalVarDescr}
-\input{Tables/medicalOutVarDescr}
-
 \subsection{Results}
@@
 
-\input{Tables/mdlContactGeneral}
-\input{Tables/mdlTheory}
-\input{Tables/mdlRobustness}
+\input{Tables/descrFullLong}
+\input{Tables/descrOutLong}
+
+\input{Tables/mdlContactGeneralLong}
+
+\input{Tables/mdlTheorylong}
+
+\input{Tables/mdlRobustlong}

### 2022-01-06 Methods-and-Results.Rmd
Feedback Max M&R

@@
 Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
-We find that neither the number of interactions nor the number of daily diary responses with an interaction were significantly related with the average outgroup attitudes (all |\textit{r}| < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`).
+We find that neither the number of interactions nor the number of daily diary responses with an interaction were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`).
 This is to say that within our data, participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
@@
 Looking at a floodlight analysis of the effect, we find that in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker.
-However, it should be noted that this is based on data aggregating all within participant nuances and is only the date of 21 people.
+However, it should be noted that this is based on data aggregating all within participant nuances and is only based on 21 people.
 
@@
 However, the small number of participants, or other measurement issues provide an alternative explanation}.
-Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants, keeping in mind that the between-participant analyses in the aggregated form are based in a small sample size.
+Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants, keeping in mind that the between-participant analyses in the aggregated form are based on a small sample size.
 
@@
 This should, in turn, be due to a higher perceived interaction quality.
-We will sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
 
@@
 Moreover, when we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`).
-We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes; this effect likely being explained by its effect through perceived interaction quality.
+We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes.
+Additionally, this effect is likely being explained by its effect through perceived interaction quality.
 
@@
 To build further confidence in our results, we assessed two additional models that might offer alternative explanations.
-First, to ensure that the effect of core need fulfillment is specific to an actual interaction, we compared it core need fulfillement in situations without an interaction.
+First, to ensure that the effect of core need fulfillment is specific to an actual interaction, we compared the effect to core need fulfillement in situations without an interaction.
 For this, we analyzed the generalized situational core need fulfillment (either during an interaction or about the daytime in general) and tested whether the effect differed during daily diary measurements with and without outgroup contacts.
@@
 The aim of Study 2 is similar to Study 1, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
-However, in this second study we collected a substantially larger sample of international students who recently arrived in the Netherlands and also improved the study design (e.g.
-pop up explanations described later).
+However, in this second study we collected a substantially larger sample of international students who recently arrived in the Netherlands and also improved the study design (e.g., pop up explanations described later).
 The survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations as these students will likely interact with the Dutch majority outgroup on a daily basis.
-Data was collected from November 19th, 2018 through January 6th, 2019.
+Data was collected from November 19\textsuperscript{th}, 2018 through January 6\textsuperscript{th}, 2019.
 
 The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
-Correlations and descriptive statistics of the included variables are available in Table \ref{tab:studentVarDescr} and Table \ref{tab:studentOutVarDescr}.
+Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullLong} and Table \ref{tab:descrOutLong}.
 
@@
 The participants recorded between `r dtStudentSupp$studentContactFreq$SumContactNL[dtStudentSupp$studentContactFreq$SumContactNL > 0] %>% min`--`r dtStudentSupp$studentContactFreq$SumContactNL %>% max`
-(`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtStudentSupp$studentContactFreq$SumContactNL) / nrow(dtStudentSupp$studentInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtStudentSupp$studentInteractionType)` daily diary responses).
+interactions with Dutch majority people (`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtStudentSupp$studentContactFreq$SumContactNL) / nrow(dtStudentSupp$studentInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtStudentSupp$studentInteractionType)` daily diary responses).
 
@@
 The extensive longitudinal survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations.
-Data were collected from November 8th, 2019 to January 10th, 2020.
+Data were collected from November 8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020.
 
 The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
-Correlations and descriptive statistics of the included variables are available in Table \ref{tab:medicalVarDescr} and Table \ref{tab:medicalOutVarDescr}.
+Correlations and descriptive statistics of the included variables are available in Tables \ref{tab:descrFullLong} and \ref{tab:descrOutLong}.
 

### 2022-01-06 Methods-and-Results.tex
Feedback Max M&R

@@
 an interaction were significantly related with the average outgroup
-attitudes (all \textbar{}\textit{r}\textbar{} \textless{} 0.03, all
+attitudes (all \textbar{} \textit{r} \textbar{} \textless{} 0.03, all
 \textit{p} \textgreater{} 0.887). This is to say that within our data,
@@
 that this is based on data aggregating all within participant nuances
-and is only the date of 21 people.
+and is only based on 21 people.
 
@@
 keeping in mind that the between-participant analyses in the aggregated
-form are based in a small sample size.
+form are based on a small sample size.
 
@@
 fulfilled the person's core situational need. This should, in turn, be
-due to a higher perceived interaction quality. We will sequentially test
+due to a higher perceived interaction quality. We sequentially test
 whether the fulfillment of the core need during an interaction is (1)
@@
 in this data set the fulfillment of core situational needs had a
-significant influence on outgroup attitudes; this effect likely being
-explained by its effect through perceived interaction quality.
+significant influence on outgroup attitudes. Additionally, this effect
+is likely being explained by its effect through perceived interaction
+quality.
 
@@
 the effect of core need fulfillment is specific to an actual
-interaction, we compared it core need fulfillement in situations without
-an interaction. For this, we analyzed the generalized situational core
-need fulfillment (either during an interaction or about the daytime in
-general) and tested whether the effect differed during daily diary
-measurements with and without outgroup contacts. We found no main effect
-of core need fulfillment (random slopes model; \textit{b} = -0.10,
-\textit{t}(1199) = -2.22, \textit{p} = 0.026, \textit{95\%CI}{[}-0.18,
--0.01{]}) but a significant interaction effect of core need fulfillment
-and outgroup contact (\textit{b} = 0.13, \textit{t}(1199) = 4.31,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.18{]}). Together
-with a significant main effect of having an outgroup contact, this
-indicates that it is not key need fulfillment in general --- but only
-key need fulfillment during an outgroup contact that predicts more
-positive outgroup attitudes.
+interaction, we compared the effect to core need fulfillement in
+situations without an interaction. For this, we analyzed the generalized
+situational core need fulfillment (either during an interaction or about
+the daytime in general) and tested whether the effect differed during
+daily diary measurements with and without outgroup contacts. We found no
+main effect of core need fulfillment (random slopes model; \textit{b} =
+-0.10, \textit{t}(1199) = -2.22, \textit{p} = 0.026,
+\textit{95\%CI}{[}-0.18, -0.01{]}) but a significant interaction effect
+of core need fulfillment and outgroup contact (\textit{b} = 0.13,
+\textit{t}(1199) = 4.31, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.07, 0.18{]}). Together with a significant main
+effect of having an outgroup contact, this indicates that it is not key
+need fulfillment in general --- but only key need fulfillment during an
+outgroup contact that predicts more positive outgroup attitudes.
 
@@
 international students who recently arrived in the Netherlands and also
-improved the study design (e.g.~pop up explanations described later).
+improved the study design (e.g., pop up explanations described later).
 The survey method again offers a large body of ecologically valid data
@@
 students will likely interact with the Dutch majority outgroup on a
-daily basis. Data was collected from November 19th, 2018 through January
-6th, 2019.
+daily basis. Data was collected from November 19\textsuperscript{th},
+2018 through January 6\textsuperscript{th}, 2019.
 
@@
 Materials B. Correlations and descriptive statistics of the included
-variables are available in Table \ref{tab:studentVarDescr} and Table
-\ref{tab:studentOutVarDescr}.
+variables are available in Table \ref{tab:descrFullLong} and Table
+\ref{tab:descrOutLong}.
 
@@
 focus on the person that was most important to you during the
-interaction.''. The participants recorded between 1--43 (1.64--93.75\%
-of individual daily diary measurements; 18.83\% of all 4965 daily diary
-responses).
+interaction.''. The participants recorded between 1--43 interactions
+with Dutch majority people (1.64--93.75\% of individual daily diary
+measurements; 18.83\% of all 4965 daily diary responses).
 
@@
 ecologically valid data on need satisfaction in real-life intergroup
-contact situations. Data were collected from November 8th, 2019 to
-January 10th, 2020.
+contact situations. Data were collected from November
+8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020.
 
@@
 Materials B. Correlations and descriptive statistics of the included
-variables are available in Table \ref{tab:medicalVarDescr} and Table
-\ref{tab:medicalOutVarDescr}.
+variables are available in Tables \ref{tab:descrFullLong} and
+\ref{tab:descrOutLong}.
 

### 2022-01-06 Backup/Before General Test Shortening/manuscript.tex
before General Analysis shortening

--- 2021-12-23 manuscript.tex
@@
 
-% Relevance v.02: Conflict is a problem, positive contact as solution, but little research on when daily contact is perceived positive
+% Migrant Example Pathways
+\textbf{Relevance (Version 1 of 2): Migrant Example Version:}
+
 Conflict between social groups and their individual members remains a prevalent feature of the modern human condition.
+One of the main examples to date are the struggles of many migrants across the world, hoping to build a positive relationship with the majority group.
+One of the main ameliorations proposed by social psychologists has been the intergroup contact hypothesis.
+In its most essential interpretation, the intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
+Over the past 70 years, a plethora of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}.
+However, even though a central assumption of intergroup contact theory has been that the contact should be positive, relatively little research has thus far explained when and why people perceive their everyday inter-group interactions as positive.
+
+% Full Migrant Pathway
+\textbf{Relevance (Version 2 of 2): Full Migrant Focus Version:}
+
+The adaptation of migrants in new cultural contexts has become an important issue for many societies around the world.
+A major aspect of such migrant adaptation arguably unfolds during the daily interactions migrants have with the cultural majority members \citep{Maxwell2017, Sam2010}.
+One of the main social psychological theories proposed for understanding how contact between groups functions has been the ’intergroup contact hypothesis’.
+In its most essential interpretation, the intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
+Over the past 70 years, a plethora of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}.
+However, even though a central assumption of intergroup contact theory has been that the contact should be positive, relatively little research has thus far explained when and why people perceive their everyday inter-group interactions as positive.
+
+% Old Relevance: Conflict is a problem, positive contact as solution, but little research on when daily contact is perceived positive
+%Conflict between social groups and their individual members remains a prevalent feature of the modern human condition.
 Experiences of prejudices, discrimination, and animosities with other groups continue to plague the everyday lives of many people around the world.
@@
 % Problem v.02: theoretical interaction quality central to understanding outcomes, practical many impactful negative interactions in everyday life
-There are however substantial theoretical and practical consequences of these understudied mechanisms of everyday intergroup contact.
-Theoretically, interaction quality or -valence sits at the heart of intergroup contact theory, as it gauges whether the interaction will result in positive intergroup outcomes \citep[][]{Tropp2016, Brown2007}.
-Practically, a longstanding body of literature has shown that negative interactions are common in everyday life and often result in a substantial decline of intergroup relations \citep[][]{Barlow2012, Shelton2009}.
-It is thus important to explore which psychological mechanisms explain when and why intergroup contacts are positive and lead to better intergroup perceptions, especially during everyday intergroup encounters \citep[e.g.,][]{MacInnis2015}.
+\textbf{Problem Illustration Paragraph:}
+
+Importantly, not understanding when and why an interaction is perceived as positive presents substantial theoretical and practical obstacles.
+There is now consistent evidence that negative intergroup contacts lead to worse attitudes, prejudice, and future interaction motivation \citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.
+Theoretically, understanding whether an interaction is perceived as positive or negative (i.e., interaction quality) thus sits at the heart of when the intergroup contact hypothesis is successful (e.g., Brown et al.
+\citeyear{Brown2007}, Tropp et al.
+\citeyear{Tropp2016}; also cf.
+Allport’s original sentiment, Allport \citeyear{Allport1954b}).
+Practically, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in every-day life contexts.
+Understanding the psychological mechanisms of when and why interactions are perceived as positive is, thus, an important issue for understanding whether an interaction leads to better intergroup perceptions, especially during everyday interactions outside the lab.
 
 % Aim / Solution v.02: look at need fulfillment as mechanism in daily interactions of migrants
+\textbf{Proposal Paragraph:}
+
 In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and positive outgroup attitudes.
@@
 Such empirical practices stand, however, in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the core idea of the contact hypothesis, which was focused on the daily interactions of people \citep[see][]{Allport1954b}.
-As a result, prominent figures within the intergroup contact field have called for studies that collect longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
+As a result, prominent figures within the intergroup contact field have called for studies that collect longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017, Dixon2005}.
 Such data would be able to capture real-life interactions that include interaction-specific mechanism information close the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.

### 2022-01-07 Methods-and-Results.Rmd
general shortened S1

@@
 After giving informed consent, participants started by filling in an online pre-questionnaire assessing demographics and general information about their immigration.
-Over the next thirty days, the participants then were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_))) %>% as.character`).
+Over the next thirty days, the participants were then invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_))) %>% as.character`).
 General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%)}.
@@
 Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
-(`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
+interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
 These participants are removed from any analyses including outgroup contacts.}.
@@
 
-\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
-First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
-Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
-We find that neither the number of interactions nor the number of daily diary responses with an interaction were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`).
-This is to say that within our data, participants with more outgroup interactions did not have significantly more positive outgroup attitudes.
-This might be due to the aggregation within the participants or the small sample size of between participant data.
-Nonetheless, the aggregated data does not support the notion that simply having more interactions with an outgroup results in more positive outgroup attitudes.
-
 ```{r workerModelOlsAttFreqQual, include=FALSE}
@@
 ```
-
-However, despite the missing relationship with the number of interactions, we find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
-Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
-And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
-Looking at a floodlight analysis of the effect, we find that in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker.
-However, it should be noted that this is based on data aggregating all within participant nuances and is only based on 21 people.
 
@@
 
+\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
+First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
+Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
+We find that neither the number of interactions nor the number of daily diary responses with an interaction were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`).
+However, we did find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = \hl{X.XX}, \textit{p} = \hl{X.XXX}.
+And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker.
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
@@
 However, the small number of participants, or other measurement issues provide an alternative explanation}.
-Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants, keeping in mind that the between-participant analyses in the aggregated form are based on a small sample size.
+Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants (eventough the average number of interactions does seem to interact with average interaction quality to predict outgroup attitudes).
+However, it should be noted that the between-participant analyses in the aggregated form are based on a small sample size.
 

### 2022-01-07 Methods-and-Results.tex
general shortened S1

@@
 demographics and general information about their immigration. Over the
-next thirty days, the participants then were invited twice a day (at 12
+next thirty days, the participants were then invited twice a day (at 12
 pm and 7pm) to reflect upon their interactions, psychological need
@@
 ``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''.
-Our participants recorded between 2--51 (3.23--91.07\% of individual
-daily diary measurements; 31.59\% of all 1225 daily diary
+Our participants recorded between 2--51 interactions with Dutch outgroup
+members (3.23--91.07\% of individual daily diary measurements; 31.59\%
+of all 1225 daily diary
 responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
@@
 attitudes (all \textbar{} \textit{r} \textbar{} \textless{} 0.03, all
-\textit{p} \textgreater{} 0.887). This is to say that within our data,
-participants with more outgroup interactions did not have significantly
-more positive outgroup attitudes. This might be due to the aggregation
-within the participants or the small sample size of between participant
-data. Nonetheless, the aggregated data does not support the notion that
-simply having more interactions with an outgroup results in more
-positive outgroup attitudes.
-
-However, despite the missing relationship with the number of
-interactions, we find a medium sized correlation between the
-participants' Average Interaction Quality and their Average Outgroup
-Attitudes. Thus within our data participants with a higher quality
-outgroup interactions also held more positive attitudes towards that
-group. And when considering the number of interactions and average
+\textit{p} \textgreater{} 0.887). However, we did find a medium sized
+correlation between the participants' Average Interaction Quality and
+their Average Outgroup Attitudes (\textit{r} = \hl{X.XX}, \textit{p} =
+\hl{X.XXX}. And when considering the number of interactions and average
 interaction quality jointly in a linear regression, we additionally find
 a statistically significant interaction term (\textit{b} = -0.05,
-\textit{t}(17) = -2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34).
-Looking at a floodlight analysis of the effect, we find that in our
-sample with an increasing number of interactions the positive effect of
-average interaction quality becomes weaker. However, it should be noted
-that this is based on data aggregating all within participant nuances
-and is only based on 21 people.
-
-We additionally used a multilevel regression to check whether having an
-interaction with an outgroup member had a situational (i.e.,
-contemporaneous) effect within the participants. We find that having an
-outgroup interaction is indeed associated with significantly more
-positive outgroup attitudes within the participants (\textit{b} = 2.48,
-\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}1.36, 3.59{]}), even after controlling for having an
-interaction with a non-Dutch (which did not relate to outgroup attitudes
-independently; For full results see Online Supplementary Materials
+\textit{t}(17) = -2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34), where
+in our sample with an increasing number of interactions the positive
+effect of average interaction quality becomes weaker. We additionally
+used a multilevel regression to check whether having an interaction with
+an outgroup member had a situational (i.e., contemporaneous) effect
+within the participants. We find that having an outgroup interaction is
+indeed associated with significantly more positive outgroup attitudes
+within the participants (\textit{b} = 2.48, \textit{t}(1200) = 4.36,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}1.36, 3.59{]}), even
+after controlling for having an interaction with a non-Dutch (which did
+not relate to outgroup attitudes independently; For full results see
+Online Supplementary Materials
 B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
@@
 show a positive effect on outgroup attitudes in the moment but these
-results do not translate into average differences between participants,
-keeping in mind that the between-participant analyses in the aggregated
+results do not translate into average differences between participants
+(eventough the average number of interactions does seem to interact with
+average interaction quality to predict outgroup attitudes). However, it
+should be noted that the between-participant analyses in the aggregated
 form are based on a small sample size.

### 2022-01-07 Methods-and-Results.Rmd
shortened General S2

@@
 
-The measurement of the self determination needs was identical to study 1.
+The measurement of the self determination needs was identical to Study 1.
 
@@
 
-\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
-First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
-Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
-We find a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-This is to say that within our data, participants with more outgroup interactions did have significantly more positive outgroup attitudes.
-This is inconsistent with the results we found in the first study and might be due to the larger number of participants.
-
 ```{r studentModelOlsAttFreqQual, include=FALSE}
@@
 ```
-
-However, we find no significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
-Given the missing aggregate relationship between average interaction quality and outgroup attitudes, we find no significant effect of average perceived contact quality.
-We also do not find that in this sample the impact of the number of interactions is moderated by the average contact quality.
-This is not entirely consistent with the first study, where average contact quality did have a meaningful effect on outgroup attitudes.
-This finding is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.
 
@@
 
+\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in the same manner as in Study 1.
+We found a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+However, we found no significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term.
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.

### 2022-01-07 Methods-and-Results.tex
shortened General S2

@@
 
-The measurement of the self determination needs was identical to study
+The measurement of the self determination needs was identical to Study
 1.
@@
 
-We tested the most general contact hypothesis in two steps. First, we
-assessed whether more intergroup interactions were related to to more
-positive outgroup attitudes. Second, we tested whether a potential
-positive effect on outgroup attitudes depended on the interaction
-quality (jointly with the number of interactions). We find a significant
-correlation with average outgroup attitudes for both the total number of
-outgroup interactions (\textit{r} = 0.22, \textit{p} = 0.019) and the
-number of measurement beeps with an interaction (\textit{r} = 0.28,
-\textit{p} = 0.003). This is to say that within our data, participants
-with more outgroup interactions did have significantly more positive
-outgroup attitudes. This is inconsistent with the results we found in
-the first study and might be due to the larger number of participants.
-
-However, we find no significant correlation between the participants'
-Average Interaction Quality and their Average Outgroup Attitudes
-(\textit{r} = 0.04, \textit{p} = 0.679). Thus, when considering the
-number of interactions and average interaction quality jointly in a
-linear regression, we find a main effect of intergroup contacts to
-predict outgroup attitudes (\textit{b} = 0.81, \textit{t}(109) = 3.29,
-\textit{p} = 0.001, \(\eta_p^2\) = 0.08). Given the missing aggregate
-relationship between average interaction quality and outgroup attitudes,
-we find no significant effect of average perceived contact quality. We
-also do not find that in this sample the impact of the number of
-interactions is moderated by the average contact quality. This is not
-entirely consistent with the first study, where average contact quality
-did have a meaningful effect on outgroup attitudes. This finding is not
-necessarily surprising given that the variables aggregate all within
-person variation and there were substantially more measurements where
-participants did not have an interaction (but reported their outgroup
-attitudes) than measurements that followed an outgroup contact.
-
-We additionally used a multilevel regression to check whether having an
-interaction with an outgroup member had a situational (i.e.,
-contemporaneous) effect within the participants. We find that having an
-outgroup interaction is indeed associated with significantly more
-positive outgroup attitudes within the participants (random slopes
-model; \textit{b} = 2.99, \textit{t}(4850) = 3.80, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}1.45, 4.54{]}), even after
-controlling for having an interaction with a non-Dutch person (which did
-not relate to outgroup attitudes independently; For full results see
-Online Supplementary Materials B). Thus, in our second dataset we find
-mixed results, outgroup contacts show a positive effect on outgroup
-attitudes in the moment and on average between participants. However, we
-find that this effect does not depend on the average perceived
-interaction quality. This unexpected results, might be due to the
-aggregation process and the following analyses will focus in on the role
-of the perceived interaction quality during an outgroup interaction.
+We tested the most general contact hypothesis in the same manner as in
+Study 1. We found a significant correlation with average outgroup
+attitudes for both the total number of outgroup interactions (\textit{r}
+= 0.22, \textit{p} = 0.019) and the number of measurement beeps with an
+interaction (\textit{r} = 0.28, \textit{p} = 0.003). However, we found
+no significant correlation between the participants' Average Interaction
+Quality and their Average Outgroup Attitudes (\textit{r} = 0.04,
+\textit{p} = 0.679). Thus, when considering the number of interactions
+and average interaction quality jointly in a linear regression, we find
+a main effect of intergroup contacts to predict outgroup attitudes
+(\textit{b} = 0.81, \textit{t}(109) = 3.29, \textit{p} = 0.001,
+\(\eta_p^2\) = 0.08) but no significant effect of average perceived
+contact quality and no significant interaction term. We additionally
+used a multilevel regression to check whether having an interaction with
+an outgroup member had a situational (i.e., contemporaneous) effect
+within the participants. We find that having an outgroup interaction is
+indeed associated with significantly more positive outgroup attitudes
+within the participants (random slopes model; \textit{b} = 2.99,
+\textit{t}(4850) = 3.80, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}1.45, 4.54{]}), even after controlling for having an
+interaction with a non-Dutch person (which did not relate to outgroup
+attitudes independently; For full results see Online Supplementary
+Materials B). Thus, in our second dataset we find mixed results,
+outgroup contacts show a positive effect on outgroup attitudes in the
+moment and on average between participants. However, we find that this
+effect does not depend on the average perceived interaction quality.
+This unexpected results, might be due to the aggregation process and the
+following analyses will focus in on the role of the perceived
+interaction quality during an outgroup interaction.
 

### 2022-01-07 Methods-and-Results.Rmd
shortened General S3

@@
 
-\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
-First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
-Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
-We find no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNLAll, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-This is to say that within our data, participants with more outgroup interactions did not have significantly more positive or negative outgroup attitudes.
-This is again consistent with the results we found in the first study but inconsitent with the significant relationship we find in the second study.
-
 ```{r medicalModelOlsAttFreqQual, include=FALSE}
@@
 ```
-
-However, we do find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
-Given the missing aggregate relationship between number of interactions and outgroup attitudes, we find no significant effect of interactions themselves nor do we find a significant interaction effect.
-This result mirrors that of study one but is inconsistent with the second study.
-But again this inconsistency is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.
 
@@
 
-We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
-Thus, in our third dataset we find some mixed results, outgroup contacts are not significantly related to outgroup attitudes on aggregate between participants and this effect is also not suppressed by a average interaction quality (i.e., no interaction effect).
-However, while the aggregate data is partly inconsistent with the first two studies, the within person contemoranous effect of intergroup contact is consistent across all three studies.
+\subsubsection{Contact Hypothesis}We again started with a general test of the contact hypothesis, as in Studies 1 and 2.
+We found no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (\textit{r} < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+However, we did find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+When considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of the number of contacts nor an interaction effect.
+This result mirrors that of study one but is inconsistent with the second study.
+Additionally in a multilevel regression to check for contemporaneous effects within the participants, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
+Thus, in our third data set we again found mixed results, outgroup contacts are not significantly related to outgroup attitudes on aggregate between participants and this effect is also not suppressed by a average interaction quality (i.e., no interaction effect).
+However, while the aggregate data is partly inconsistent with the first two studies, the within person contemporaneous effect of intergroup contact is consistent across all three studies.
 

### 2022-01-07 Methods-and-Results.tex
shortened General S3

@@
 
-We tested the most general contact hypothesis in two steps. First, we
-assessed whether more intergroup interactions were related to to more
-positive outgroup attitudes. Second, we tested whether a potential
-positive effect on outgroup attitudes depended on the interaction
-quality (jointly with the number of interactions). We find no
-significant correlation between intergroup contact and average outgroup
-attitudes --- for neither the total number of outgroup interactions
-(\textit{r} = 0.01, \textit{p} = 0.946) and the number of measurement
-beeps with an interaction (\textit{r} = 0.13, \textit{p} = 0.291). This
-is to say that within our data, participants with more outgroup
-interactions did not have significantly more positive or negative
-outgroup attitudes. This is again consistent with the results we found
-in the first study but inconsitent with the significant relationship we
-find in the second study.
-
-However, we do find a significant correlation between the participants'
-Average Interaction Quality and their Average Outgroup Attitudes
-(\textit{r} = 0.25, \textit{p} = 0.036). Thus, when considering the
+We again started with a general test of the contact hypothesis, as in
+Studies 1 and 2. We found no significant correlation between intergroup
+contact and average outgroup attitudes --- for neither the total number
+of outgroup interactions nor the number of measurement beeps with an
+interaction (\textit{r} \textless{} 0.13, \textit{p} \textgreater{}
+0.291). However, we did find a significant correlation between the
+participants' Average Interaction Quality and their Average Outgroup
+Attitudes (\textit{r} = 0.25, \textit{p} = 0.036). When considering the
 number of interactions and average interaction quality jointly in a
@@
 interaction quality on predict outgroup attitudes (\textit{b} = 0.36,
-\textit{t}(67) = 2.22, \textit{p} = 0.030, \(\eta_p^2\) = 0.07). Given
-the missing aggregate relationship between number of interactions and
-outgroup attitudes, we find no significant effect of interactions
-themselves nor do we find a significant interaction effect. This result
-mirrors that of study one but is inconsistent with the second study. But
-again this inconsistency is not necessarily surprising given that the
-variables aggregate all within person variation and there were
-substantially more measurements where participants did not have an
-interaction (but reported their outgroup attitudes) than measurements
-that followed an outgroup contact.
-
-We additionally used a multilevel regression to check whether having an
-interaction with an outgroup member had a situational (i.e.,
-contemporaneous) effect within the participants. We find that having an
-outgroup interaction is indeed associated with significantly more
+\textit{t}(67) = 2.22, \textit{p} = 0.030, \(\eta_p^2\) = 0.07) but no
+significant effect of the number of contacts nor an interaction effect.
+This result mirrors that of study one but is inconsistent with the
+second study. Additionally in a multilevel regression to check for
+contemporaneous effects within the participants, we found that having an
+outgroup interaction was indeed associated with significantly more
 positive outgroup attitudes within the participants (random slopes
@@
 relate to outgroup attitudes independently; For full results see Online
-Supplementary Materials B). Thus, in our third dataset we find some
+Supplementary Materials B). Thus, in our third data set we again found
 mixed results, outgroup contacts are not significantly related to
@@
 interaction effect). However, while the aggregate data is partly
-inconsistent with the first two studies, the within person contemoranous
-effect of intergroup contact is consistent across all three studies.
+inconsistent with the first two studies, the within person
+contemporaneous effect of intergroup contact is consistent across all
+three studies.
 

### 2022-01-09 Methods-and-Results.Rmd
meta structure added

@@
 
+```{r metaGeneral, include=FALSE}
+
+mdlTblElementsGeneralLm <- list(mdlWorker$lmAttFreqQualX,
+                                mdlStudent$lmAttFreqQualX,
+                                mdlMedical$lmAttFreqQualX)
+
+mdlTblElementsGeneralLmer <- list(
+  c(mdlWorker$lmerInterceptAttTypeTbl, mdlWorker$lmerInterceptAttTypeTblZ),
+  c(mdlStudent$lmerSlopesAttType, mdlStudent$lmerSlopesAttTypeZ),
+  c(mdlMedical$lmerSlopesAttType, mdlMedical$lmerSlopesAttTypeZ)
+  )
+
+# R2 of betas.
+# https://rdrr.io/cran/r2glmm/man/r2beta.html
+r2glmm::r2beta(
+  model = mdlWorker$lmAttFreqQualX,
+  partial = TRUE,
+  method = 'lm'
+)
+
+r2glmm::r2beta(
+  model = mdlWorker$lmerInterceptAttTypeTbl,
+  partial = TRUE,
+  # 'sgv' standardized generalized variance approach, 
+  # 'kr' (Kenward Roger approach; only with lme),
+  # 'nsj' (Nakagawa and Schielzeth approach)
+  method = 'sgv' 
+)
+
+# var = parameter name
+# https://www.rdocumentation.org/packages/metafor/versions/3.0-2/topics/escalc
+      md <- escalc(data = process[process$Parameter==var[i],],
+                   measure = "SPCOR",
+                   ti = t,
+                   ni = N,
+                   mi = m,
+                   r2i = r2,
+                   var.names = c(paste(var[i],".yi",sep=""),paste(var[i],".vi",sep="")))
+
+      meta.parametric[[var[i]]] <- rma(yi = get(paste(var[i],".yi",sep="")),
+                                       vi = get(paste(var[i],".vi",sep="")), 
+                                       data = md, 
+                                       method = "REML", 
+                                       slab = Study)
+
+# Alternative Meta:
+      Metaan::estmeta(
+        Beta = beta,
+        l = lowerCI,
+        u = upperCI,
+        test = "FIXED", # "RANDOM"
+      )
+
+```
+
+```{r metaTheory, include=FALSE}
+
+```
+
+```{r metaRobust, include=FALSE}
+
+```
+
 <!-- \input{Tables/descrFullWide} -->
@@
 <!-- \input{Tables/mdlContactGeneral} -->
+<!-- \input{Tables/mdlTheory} -->
+<!-- \input{Tables/mdlRobustness} -->
+
 \input{Tables/mdlContactGeneralLong}
-
-<!-- \input{Tables/mdlTheory} -->
 \input{Tables/mdlTheorylong}
-
-<!-- \input{Tables/mdlRobustness} -->
 \input{Tables/mdlRobustlong}

### 2022-01-09 Tables/mdlContactGeneral.tex
general tbl added
meta structure added

@@
 
-\caption{\label{tab:intergroupGeneralTbl}Intergroup General}
+\caption{Intergroup General}
 \centering

### 2022-01-10 Methods-and-Results.Rmd
meta General LM added

--- 2022-01-07 Methods-and-Results.Rmd
@@
   "sjmisc",
-  "sjmisc"
+  "metafor"
 )
@@
 
+```{r metaGeneralLm, include=FALSE}
+
+mdlTblElementsGeneralLm <- list(mdlWorker$lmAttFreqQualX,
+                                mdlStudent$lmAttFreqQualX,
+                                mdlMedical$lmAttFreqQualX)
+
+lmMetaTbl <- data.frame()
+for (i in 1:length(mdlTblElementsGeneralLm)){
+  lmTblTmp <- lmTblPrep(mdlTblElementsGeneralLm[[i]])$coeficients %>%
+  select(
+    coef,
+    B = est,
+    se,
+    lwr,
+    upr,
+    tval,
+    Rsq
+  ) %>%
+  mutate(
+    n = lmTblPrep(mdlTblElementsGeneralLm[[i]])$fit$N,
+    m = nrow(.)-1, 
+    sample = str_match(lmTblPrep(mdlTblElementsGeneralLm[[i]])$fit$data, "dt(.*?)Supp")[2],
+    coef = gsub(":", ".", coef)
+  )
+  lmMetaTbl <- rbind(lmMetaTbl, lmTblTmp)
+}
+
+lmMetaTbl <- lmMetaTbl %>% arrange(coef)
+
+# extract parameter names
+  name <- "Contact Hypothesis — Aggregate Linear Regression"
+  var <- as.character(unique(lmMetaTbl$coef))[!as.character(unique(lmMetaTbl$coef)) %in% c("(Intercept)")]
+  names <- qdap::mgsub(c("SumContactNL", "AvQuality", "SumContactNL.AvQuality"),
+                       c("Number of Outgroup Contacts","Average Interaction Quality", "Contact X Quality"), 
+                       var)
+  studies <- as.character(unique(lmMetaTbl$sample))
+
+### Parametric Meta-Analysis
+    meta.parametric <- list()
+    meta.parametric.sum <- data.frame(effect = var, 
+                                      name = names, 
+                                      beta.Worker = NA, 
+                                      CI.Worker = NA,
+                                      beta.Student = NA, 
+                                      CI.Student = NA,
+                                      beta.Medical = NA,
+                                      CI.Medical = NA, 
+                                      RE.beta = NA,
+                                      RE.CI = NA,
+                                      RE.pval = NA,
+                                      RE.star = NA)
+
+# i = 1
+for(i in 1:length(var)){
+      md <- escalc(data = lmMetaTbl[lmMetaTbl$coef==var[i],],
+                   measure = "SPCOR",
+                   ti = tval,
+                   ni = n,
+                   mi = m,
+                   r2i = Rsq,
+                   var.names = c(paste(var[i],".yi",sep=""),paste(var[i],".vi",sep="")))
+
+      meta.parametric[[var[i]]] <- rma(yi = get(paste(var[i],".yi",sep="")),
+                                       vi = get(paste(var[i],".vi",sep="")), 
+                                       data = md, 
+                                       method = "FE", # "REML", 
+                                       slab = sample)
+      #metafor::forest(meta.parametric[[var[i]]],
+      #                main = paste("Meta Analysis ",names[i],sep = ""))
+
+      meta.parametric.sum$effect[i] <- var[i]
+      meta.parametric.sum$beta.Worker[i] <- meta.parametric[[var[i]]]$yi[1]
+      meta.parametric.sum$beta.Student[i] <- meta.parametric[[var[i]]]$yi[2]
+      meta.parametric.sum$beta.Medical[i] <- meta.parametric[[var[i]]]$yi[3]
+      meta.parametric.sum$CI.Worker[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),", ",round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),"]",sep="")
+      meta.parametric.sum$CI.Student[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),", ",round(meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),"]",sep="")
+      meta.parametric.sum$CI.Medical[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),", ",round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),"]",sep="")
+      meta.parametric.sum$RE.beta[i] <- meta.parametric[[var[i]]]$b
+      meta.parametric.sum$RE.CI[i] <- paste("[",
+                                            round(meta.parametric[[var[i]]]$ci.lb, 2),
+                                            ", ", round(meta.parametric[[var[i]]]$ci.ub,2),"]", sep="")
+      meta.parametric.sum$RE.pval[i] <- meta.parametric[[var[i]]]$pval
+      meta.parametric.sum$RE.star[i] <- ifelse(meta.parametric.sum$RE.pval[i]<0.001,"***",ifelse(meta.parametric.sum$RE.pval[i]<0.01,"**",ifelse(meta.parametric.sum$RE.pval[i]<0.05,"*","")))
+}
+    #meta.parametric
+
+    eff <- escalc(data = lmMetaTbl, 
+                  slab = coef,
+                  measure = "SPCOR",
+                  ti = tval,
+                  ni = n,
+                  mi = m,
+                  r2i = Rsq)
+    meta <- rma(yi = yi,
+                vi = vi, 
+                data = eff, 
+                method = "FE", # "REML", 
+                slab = paste(coef, sample, sep=" - "))
+
+    k <- length(var) * length(studies)
+    png(file = "Figures/forestParametricGeneralLm.png", height = 200 + 40*k^.85) 
+      metafor::forest(meta, xlim=c(-2, 2), cex=0.75, ylim=c(-1, 20), rows=c(22:20,16:14,10:8,4:2), 
+                      slab = rep(c("Study 1","Study 2", "Study 3"),length(studies)+1),
+                      mlab="", main=paste0("Meta Analysis: Forest Plot [Parametric] \n(",name,")")) # , xlab = "Standardized Beta"
+      par(font=2)
+      text(-2.05, c(17,11,5), cex=0.75, pos=4, names)
+      m=1
+      for(i in 3:1){
+        addpoly(meta.parametric[[i]], row=m, cex=0.75, mlab=paste("►FE",names[i]),)
+        m <- m+6
+      }
+      text(-2.05, 19, "Predictors by study",  cex=.8, pos=4)
+      text(2, 19, "Semi-Partial Correlation [95% CI]", cex=.8, pos=2)
+    dev.off()
+
+### Bootstrapped Meta-Analysis
+    var.boot <- var
+    names.boot <- names
+    meta.bootstrapped <- list()
+    meta.bootstrapped.sum <- data.frame(effect = var.boot, 
+                                      name = names.boot, 
+                                      beta.Worker = NA, 
+                                      CI.Worker = NA,
+                                      beta.Student = NA, 
+                                      CI.Student = NA,
+                                      beta.Medical = NA,
+                                      CI.Medical = NA, 
+                                      RE.beta = NA,
+                                      RE.CI = NA,
+                                      RE.pval = NA,
+                                      RE.star = NA)
+
+    # i = 3
+    for(i in 1:length(var.boot)){
+      md <- escalc(data = lmMetaTbl[lmMetaTbl$coef==var.boot[i],],
+                   measure = "SPCOR",
+                   yi = B,
+                   sei = se,
+                   ni = n,
+                   mi = m,
+                   var.names = c(paste(var.boot[i],".yi",sep=""),paste(var.boot[i],".vi",sep="")))
+
+      meta.bootstrapped[[var.boot[i]]] <- rma(yi = get(paste(var.boot[i],".yi",sep="")),
+                                              vi = get(paste(var.boot[i],".vi",sep="")),
+                                              data = md,
+                                              method = "FE",
+                                              slab = sample)
+      #metafor::forest(meta.bootstrapped[[var.boot[i]]],
+      #                main = paste("Meta Analysis ",names.boot[i],sep = ""))
+      meta.bootstrapped.sum$effect[i] <- var[i]
+      meta.bootstrapped.sum$beta.Worker[i] <-
+        meta.bootstrapped[[var[i]]]$yi[1]
+      meta.bootstrapped.sum$beta.Student[i] <-
+        meta.bootstrapped[[var[i]]]$yi[2]
+      meta.bootstrapped.sum$beta.Medical[i] <-
+        meta.bootstrapped[[var[i]]]$yi[3]
+      meta.bootstrapped.sum$CI.Worker[i] <-
+        paste(
+          "[",
+          round(meta.bootstrapped[[var[i]]]$yi[1] -
+                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[1]), 2),
+          ", ",
+          round(meta.bootstrapped[[var[i]]]$yi[1] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[1]), 2),
+          "]",
+          sep = ""
+        )
+      meta.bootstrapped.sum$CI.Student[i] <-
+        paste(
+          "[",
+          round(meta.bootstrapped[[var[i]]]$yi[2] -
+                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[2]), 2),
+          ", ",
+          round(meta.bootstrapped[[var[i]]]$yi[2] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[2]), 2),
+          "]",
+          sep = ""
+        )
+      meta.bootstrapped.sum$CI.Medical[i] <-
+        paste(
+          "[",
+          round(meta.bootstrapped[[var[i]]]$yi[3] -
+                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[3]), 2),
+          ", ",
+          round(meta.bootstrapped[[var[i]]]$yi[3] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[3]), 2),
+          "]",
+          sep = ""
+        )
+      meta.bootstrapped.sum$RE.beta[i] <- meta.bootstrapped[[var[i]]]$b
+      meta.bootstrapped.sum$RE.CI[i] <- paste(
+        "[",
+        round(meta.bootstrapped[[var[i]]]$ci.lb, 2),
+        ", ",
+        round(meta.bootstrapped[[var[i]]]$ci.ub, 2),
+        "]",
+        sep = ""
+      )
+      meta.bootstrapped.sum$RE.pval[i] <- meta.bootstrapped[[var[i]]]$pval
+      meta.bootstrapped.sum$RE.star[i] <-
+        ifelse(
+          meta.bootstrapped.sum$RE.pval[i] < 0.001,
+          "***",
+          ifelse(
+            meta.bootstrapped.sum$RE.pval[i] < 0.01,
+            "**",
+            ifelse(meta.bootstrapped.sum$RE.pval[i] < 0.05, "*", "")
+          )
+        )
+    }
+    #meta.bootstrapped
+
+    eff.boot <- escalc(data = lmMetaTbl %>% filter(coef != "(Intercept)"), 
+                       slab = coef,
+                       measure = "SPCOR",
+                       yi = B,
+                       sei = se,
+                       ni = n,
+                       mi = m)
+    meta.boot <- rma(yi = yi,
+                     vi = vi, 
+                     data = eff.boot, 
+                     method = "FE", 
+                     slab = paste(coef, sample, sep=" - "))
+
+    k <- 3*3
+    png(file = "Figures/forestBootstrappedGeneralLm.png", height = 200 + 40*k^.85)
+      metafor::forest(meta.boot, cex=0.75, xlim=c(-2, 2.5), ylim=c(-1, 20), rows=c(16:14,10:8,4:2), 
+                      slab = rep(c("Study 1","Study 2", "Study 3"),length(studies)),
+                      mlab="", main=paste0("Meta Analysis: Forest Plot [Bootstrapped] \n(",name,")")) # , xlab = "Standardized Beta")
+      par(font=2)
+      text(-2.05, c(17,11,5), cex=0.75, pos=4, names)
+      m=1
+      for(i in 3:1){
+        addpoly(meta.bootstrapped[[i]], row=m, cex=0.75, mlab=paste("►FE",names.boot[i]),)
+        m <- m+6
+      }
+      text(-2.05, 19, "Predictors by study",  cex=.8, pos=4)
+      text(2.5, 19, "Semi-Partial Correlation [95% CI]", cex=.8, pos=2)
+    dev.off()
+
+mdlTblElementsGeneralLmer <- list(
+  c(mdlWorker$lmerInterceptAttTypeTbl, mdlWorker$lmerInterceptAttTypeTblZ),
+  c(mdlStudent$lmerSlopesAttType, mdlStudent$lmerSlopesAttTypeZ),
+  c(mdlMedical$lmerSlopesAttType, mdlMedical$lmerSlopesAttTypeZ)
+  )
+
+lmerTblPrep(mdlWorker$lmerInterceptAttTypeTbl, mdlWorker$lmerInterceptAttTypeTblZ)$beta
+
+# # Alternative Meta:
+#       Metaan::estmeta(
+#         Beta = beta,
+#         l = lowerCI,
+#         u = upperCI,
+#         test = "FIXED", # "RANDOM"
+#       )
+
+```
+
+```{r metaTheory, include=FALSE}
+
+```
+
+```{r metaRobust, include=FALSE}
+
+```
+
 <!-- \input{Tables/descrFullWide} -->

### 2022-01-10 scripts/functions/MlTbl.R

@@ -20,8 +20,26 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
                    #ncpus = parallel::detectCores(logical = TRUE)) %>% 
     as.data.frame %>%
     tibble::rownames_to_column(., "coef")
-  coefZOut <- merge(coefZ, confZ)
-  colnames(coefZOut) <- c("coef", "est", "se", "tval", "df", "p", "lwr", "upr")
+  coefZCI <- merge(coefZ, confZ)
+  colnames(coefZCI) <- c("coef", "est", "se", "tval", "df", "p", "lwr", "upr")
+  
+  coefZR2 <- r2glmm::r2beta(
+    model = objz,
+    partial = TRUE,
+    # 'sgv' standardized generalized variance approach, 
+    # 'kr' (Kenward Roger approach; only with lme),
+    # 'nsj' (Nakagawa and Schielzeth approach)
+    method = 'sgv' 
+  ) %>%
+    as.data.frame %>%
+    select(
+      coef = Effect,
+      Rsq,
+      RsqLower = lower.CL,
+      RsqUpper = upper.CL
+    )
+  coefZOut <- merge(coefZCI, coefZR2)
+  
   coefZOut$Beta <- paste0(
     format(round(coefZOut$est, 2), nsmall = 2),
     " [", 
@@ -156,6 +174,7 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   
   out <- list(
     coeficients = coefOut,
+    beta = coefZOut,
     random = restat,
     fit = sumstat,
     mdlTbl = mdlTbl
@@ -167,12 +186,25 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
 lmTblPrep <- function (obj, alpha = 0.05, ...) {
   # Summarize models
   smry <- summ(obj, confint = TRUE)
+  smrySE <- summ(obj, confint = FALSE)
   
   # Get unstandardized coefficients
-  coef <- smry$coeftable %>% 
+  coefCI <- smry$coeftable %>% 
     as.data.frame %>%
     tibble::rownames_to_column(., "coef")
-  colnames(coef) <- c("coef", "est", "lwr", "upr", "tval", "p")
+  colnames(coefCI) <- c("coef", "est", "lwr", "upr", "tval", "p")
+  
+  coefSE <- smrySE$coeftable %>% 
+    as.data.frame %>%
[…]

### 2022-01-10 Methods-and-Results.Rmd
theory meta added

@@
 source("./scripts/functions/MlTbl.R")
+source("./scripts/functions/metaLmer.R")
 
@@
   c(tblLmerS3AttSlopesCore, tblLmerS3AttSlopesCoreZ),
-  c(tblLmerS3AttSlopesCoreQlt, tblLmerS3AttSlopesCoreQlt),
+  c(tblLmerS3AttSlopesCoreQlt, tblLmerS3AttSlopesCoreQltZ),
   c(tblLmerS3QltSlopesAllport, tblLmerS3QltSlopesAllportZ),
@@
 ```{r metaGeneralLm, include=FALSE}
-
 mdlTblElementsGeneralLm <- list(mdlWorker$lmAttFreqQualX,
@@
     dev.off()    
-
+```
+
+```{r metaGeneralLmer, include=FALSE}
 mdlTblElementsGeneralLmer <- list(
@@
 
-lmerTblPrep(mdlWorker$lmerInterceptAttTypeTbl, mdlWorker$lmerInterceptAttTypeTblZ)$beta
-
-# # Alternative Meta:
-#       Metaan::estmeta(
-#         Beta = beta,
-#         l = lowerCI,
-#         u = upperCI,
-#         test = "FIXED", # "RANDOM"
-#       )
-
+# i =1
+GeneralLmerMetaTbl <- data.frame()
+for (i in 1:length(mdlTblElementsGeneralLmer)){
+  lmerTblTmp <- lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$beta %>%
+  select(
+    coef,
+    B = est,
+    se,
+    lwr,
+    upr,
+    tval,
+    Rsq
+  ) %>%
+  mutate(
+    n = lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$fit$N,
+    m = nrow(.), 
+    sample = str_match(lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$fit$data, "dt(.*?)Supp")[2],
+    coef = gsub(":", ".", coef)
+  )
+  GeneralLmerMetaTbl <- rbind(GeneralLmerMetaTbl, lmerTblTmp)
+}
+
+GeneralLmerMetaTbl <- GeneralLmerMetaTbl %>% arrange(coef)
+
+GeneralLmerMeta <- metaLmerOut(GeneralLmerMetaTbl,
+                               type = "FE",
+                               name = "GeneralLmer",
+                               title = "Contact Hypothesis — Mixed Effects Regression")
+
+# Alternative Meta:
+      Metaan::estmeta(
+        Beta = GeneralLmerMetaTbl$B[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
+        l = GeneralLmerMetaTbl$lwr[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
+        u = GeneralLmerMetaTbl$upr[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
+        test = "FIXED", # "RANDOM"
+      )
 ```
@@
 ```{r metaTheory, include=FALSE}
-
+mdlTblElementsTheoryLmer <- list(
+  # Study 1:
+  c(tblLmerS1QltInterceptCore, tblLmerS1QltInterceptCoreZ),
+  c(tblLmerS1AttSlopeCore, tblLmerS1AttSlopeCoreZ),
+  c(tblLmerS1AttSlopeCoreQlt, tblLmerS1AttSlopeCoreQltZ),
+  # Study 2:
+  c(tblLmerS2QltSlopesCore, tblLmerS2QltSlopesCoreZ),
+  c(tblLmerS2AttSlopesCore, tblLmerS2AttSlopesCoreZ),
+  c(tblLmerS2AttSlopesCoreQlt, tblLmerS2AttSlopesCoreQltZ),
+  # Study 3:
+  c(tblLmerS3QltSlopesCore, tblLmerS3QltSlopesCoreZ),
+  c(tblLmerS3AttSlopesCore, tblLmerS3AttSlopesCoreZ),
+  c(tblLmerS3AttSlopesCoreQlt, tblLmerS3AttSlopesCoreQltZ),
+  c(tblLmerS3QltSlopesAllport, tblLmerS3QltSlopesAllportZ),
+  c(tblLmerS3AttSlopesAllport, tblLmerS3AttSlopesAllportZ),
+  c(tblLmerS3AttSlopesAllportQlt, tblLmerS3AttSlopesAllportQltZ),
+  c(tblLmerS3AttSlopesAllportCore, tblLmerS3AttSlopesAllportCoreZ)
+  )
+
+# i =1
+theoryMetaTbl <- data.frame()
+for (i in 1:length(mdlTblElementsTheoryLmer)){
+  lmerTblTmp <- lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$beta %>%
+  select(
+    coef,
+    B = est,
+    se,
+    lwr,
+    upr,
+    tval,
+    Rsq
+  ) %>%
+  mutate(
+    n = lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$N,
+    m = nrow(.), 
+    dv = gsub("Raw", "", str_extract(lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$formula,".+?(?= ~)")),
+    sample = gsub("S", "Study", str_extract(lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$data, "S1|S2|S3")),
+    formula = lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$formula,
+    coef = gsub(":", ".", coef)
+  )
+  theoryMetaTbl <- rbind(theoryMetaTbl, lmerTblTmp)
+}
+
+theoryMetaTblNoAllport <- theoryMetaTbl %>%
+  filter(!grepl("Allport",formula)) %>% 
+  mutate(formula = gsub(" \\+ \\(.*", "", formula)) %>%
+  arrange(formula, coef, sample)
+
+TheoryMetaQualityNeed <-
+  metaLmerOut(
+    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "QualityRaw ~ CoreNeed"),
+    type = "FE",
+    name = "TheoryQualityCore",
+    title = "QualityRaw ~ CoreNeed"
+  )
+
+TheoryMetaAttitudeNeed <-
+  metaLmerOut(
+    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed"),
+    type = "FE",
+    name = "TheoryAttitudeCore",
+    title = "Attitude ~ CoreNeed"
+  )
+
+TheoryMetaAttitudeNeedQuality <-
+  metaLmerOut(
+    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed + Quality"),
+    type = "FE",
+    name = "TheoryAttitudeCoreQuality",
+    title = "Attitude ~ CoreNeed + Quality"
+  )
 ```
@@
 ```{r metaRobust, include=FALSE}
+mdlRobustTblElements <- list(
+  # full
+  c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ),
+  c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ),
+  c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ),
+  # outgroup
+  c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ),
+  c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ),
+  c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ)
+  )
+
+# i =1
+robustMetaTbl <- data.frame()
+for (i in 1:length(mdlRobustTblElements)){
+  lmerTblTmp <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$beta %>%
+  select(
+    coef,
+    B = est,
+    se,
+    lwr,
+    upr,
+    tval,
+    Rsq
+  ) %>%
+  mutate(
+    n = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$N,
+    m = nrow(.), 
+    dv = gsub("Raw", "", str_extract(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,".+?(?= ~)")),
+    sample = gsub("S", "Study", str_extract(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$data, "S1|S2|S3")),
+    formula = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,
+    coef = gsub(":", ".", coef)
+  )
+  robustMetaTbl <- rbind(robustMetaTbl, lmerTblTmp)
+}
+
+robustMetaTbl %>%
+  arrange(formula, coef, sample)
+
+theoryMetaTblNoAllport <- theoryMetaTbl %>%
+  filter(!grepl("Allport",formula)) %>% 
+  mutate(formula = gsub(" \\+ \\(.*", "", formula)) %>%
+  arrange(formula, coef, sample)
+
+TheoryMetaQualityNeed <-
+  metaLmerOut(
+    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "QualityRaw ~ CoreNeed"),
+    type = "FE",
+    name = "TheoryQualityCore",
+    title = "QualityRaw ~ CoreNeed"
+  )
+
+TheoryMetaAttitudeNeed <-
+  metaLmerOut(
+    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed"),
+    type = "FE",
+    name = "TheoryAttitudeCore",
+    title = "Attitude ~ CoreNeed"
+  )
+
+TheoryMetaAttitudeNeedQuality <-
+  metaLmerOut(
+    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed + Quality"),
+    type = "FE",
+    name = "TheoryAttitudeCoreQuality",
+    title = "Attitude ~ CoreNeed + Quality"
+  )
 

### 2022-01-10 Tables/studentVarDescr.tex
theory meta added

@@
 
-\caption{\label{tab:studentVarDescr}Student: Multilevel Core Variable Descriptives}
+\caption{Student: Multilevel Core Variable Descriptives}
 \centering
@@
 Between SD & 9.17 & 14.47 & 11.21 & 13.36 & 9.12 & 18.64\\
-Within SD & NA & NA & NA & NA & NA & NA\\
+Within SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
 ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.20 & 0.80\\
 ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.88 & 0.99\\
-Within.person.SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
 \bottomrule

### 2022-01-10 Tables/workerVarDescr.tex
theory meta added

@@
 
-\caption{\label{tab:workerVarDescr}Worker: Multilevel Core Variable Descriptives}
+\caption{Worker: Multilevel Core Variable Descriptives}
 \centering
@@
 Between SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.50 & 12.91\\
-Within SD & NA & NA & NA & NA & NA & NA\\
+Within SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
 ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.18 & 0.70\\
 ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.79 & 0.99\\
-Within.person.SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
 \bottomrule

### 2022-01-10 scripts/functions/metaLmer.R

@@ -1,0 +1,364 @@
+metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
+  # lmerDataTbl <- theoryMetaTbl
+  # name <- "Theory"
+  # title <- "Need Fullfillment — Mixed Effects Regression"
+  
+  # extract parameter names
+  var <-
+    as.character(unique(lmerDataTbl$coef))[!as.character(unique(lmerDataTbl$coef)) %in% c("(Intercept)")]
+  names <-
+    stri_replace_all_fixed(
+      var,
+      pattern = c(
+        "SumContactNL", 
+        "AvQuality", 
+        "SumContactNL.AvQuality",
+        "NonOutgroupInteraction",
+        "OutgroupInteraction",
+        "CoreNeedZ",
+        "QualityZ",
+        "_zwc"
+      ),
+      replacement = c(
+        "Number of Outgroup Contacts",
+        "Average Interaction Quality",
+        "Contact X Quality",
+        "Non-Outgroup Interaction",
+        "Outgroup Interaction",
+        "Core Need Fulfillment",
+        "Interaction Quality",
+        ""
+      ),
+      vectorize_all = FALSE
+    )
+  studies <- as.character(unique(lmerDataTbl$sample))
+  
+  ### Parametric Meta-Analysis
+  meta.parametric <- list()
+  
+  sum.names <- c("effect", 
+                 "name",
+                 paste(c("beta", "CI"),rep(studies, each = 2),sep="."),
+                 "meta.beta",
+                 "meta.CI",
+                 "meta.pval",
+                 "meta.star")
+  meta.parametric.sum <-
+    data.frame(matrix(
+      ncol = length(sum.names),
+      nrow = length(var),
+      dimnames = list(NULL, sum.names)
+    )) %>%
+    mutate(
+      effect = var,
+      name = names
+    )
+  
+  # i = 1
+  for (i in 1:length(var)) {
+    md <- escalc(
+      data = lmerDataTbl[lmerDataTbl$coef == var[i], ],
+      measure = "SPCOR",
+      ti = tval,
+      ni = n,
+      mi = m,
+      r2i = Rsq,
+      var.names = c(paste(var[i], ".yi", sep = ""), paste(var[i], ".vi", sep =
+                                                            ""))
+    )
+    
+    meta.parametric[[var[i]]] <-
+      rma(
+        yi = get(paste(var[i], ".yi", sep = "")),
[…]

### 2022-01-10 Methods-and-Results.Rmd
robust core code added

@@
     m = nrow(.), 
-    dv = gsub("Raw", "", str_extract(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,".+?(?= ~)")),
-    sample = gsub("S", "Study", str_extract(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$data, "S1|S2|S3")),
+    #dv = gsub("Dutch", "", str_extract(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,".+?(?= ~)")),
+    sample = str_match(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$data, "Tbl(.*?)(Full|Out)")[2],
     formula = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,
@@
 
-robustMetaTbl %>%
-  arrange(formula, coef, sample)
-
-theoryMetaTblNoAllport <- theoryMetaTbl %>%
-  filter(!grepl("Allport",formula)) %>% 
-  mutate(formula = gsub(" \\+ \\(.*", "", formula)) %>%
-  arrange(formula, coef, sample)
-
-TheoryMetaQualityNeed <-
+robustMetaTbl <- robustMetaTbl %>%
+  arrange(formula, match(
+    coef,
+    c(
+      "CoreNeed_zwc",
+      "OutgroupInteraction_zwc",
+      "CoreNeed_zwc.OutgroupInteraction_zwc",
+      "Autonomy_zwc",
+      "Competence_zwc",
+      "Relatedness_zwc",
+      "CoreNeed_zwc"
+    )
+  )) %>% 
+  mutate(formula = gsub(" \\+ \\(.*", "", formula))
+
+robustMetaContact <-
+  metaLmerOut(
+    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc * OutgroupInteraction"),
+    type = "FE",
+    name = "RobustContact",
+    title = "Attitudes ~ CoreNeed * Outgroup Interaction"
+  )
+
+robustMetaSDT <-
   metaLmerOut(

### 2022-01-10 scripts/functions/metaLmer.R

@@ -16,6 +16,7 @@ metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
         "NonOutgroupInteraction",
         "OutgroupInteraction",
         "CoreNeedZ",
+        "CoreNeed",
         "QualityZ",
         "_zwc"
       ),
@@ -25,6 +26,7 @@ metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
         "Contact X Quality",
         "Non-Outgroup Interaction",
         "Outgroup Interaction",
+        "Core Need Fulfillment",
         "Core Need Fulfillment",
         "Interaction Quality",
         ""

### 2022-01-10 Methods-and-Results.Rmd
robust meta added

@@
       "Competence_zwc",
-      "Relatedness_zwc",
-      "CoreNeed_zwc"
+      "Relatedness_zwc"
     )
@@
     name = "RobustContact",
-    title = "Attitudes ~ CoreNeed * Outgroup Interaction"
+    title = "Robustness — Contact and Need Fulfillment"
   )
@@
   metaLmerOut(
-    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "QualityRaw ~ CoreNeed"),
+    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc + Competence_cwc + Autonomy_cwc +      Relatedness_cwc"),
     type = "FE",
-    name = "TheoryQualityCore",
-    title = "QualityRaw ~ CoreNeed"
-  )
-
-TheoryMetaAttitudeNeed <-
-  metaLmerOut(
-    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed"),
-    type = "FE",
-    name = "TheoryAttitudeCore",
-    title = "Attitude ~ CoreNeed"
-  )
-
-TheoryMetaAttitudeNeedQuality <-
-  metaLmerOut(
-    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed + Quality"),
-    type = "FE",
-    name = "TheoryAttitudeCoreQuality",
-    title = "Attitude ~ CoreNeed + Quality"
-  )
-
+    name = "RobustSDT",
+    title = "Robustness — Other Needs"
+  )
 ```

### 2022-01-10 scripts/functions/metaLmer.R

@@ -18,7 +18,8 @@ metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
         "CoreNeedZ",
         "CoreNeed",
         "QualityZ",
-        "_zwc"
+        "_zwc",
+        "."
       ),
       replacement = c(
         "Number of Outgroup Contacts",
@@ -29,7 +30,8 @@ metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
         "Core Need Fulfillment",
         "Core Need Fulfillment",
         "Interaction Quality",
-        ""
+        "",
+        " X "
       ),
       vectorize_all = FALSE
     )
@@ -56,7 +58,7 @@ metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
       name = names
     )
   
-  # i = 1
+  # i = 2
   for (i in 1:length(var)) {
     md <- escalc(
       data = lmerDataTbl[lmerDataTbl$coef == var[i], ],
@@ -121,12 +123,15 @@ metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
             paste("CI", attributes(meta.parametric[[var[i]]]$yi)$slab, sep = ".")
           ))))
     
-    library(rqdatatable)
-    meta.parametric.sum <- natural_join(meta.parametric.sum,
-                              betaCI,
-                              by = "effect",
-                              jointype = "FULL") %>%
-      select(names(meta.parametric.sum))
+    for(r in 2:ncol(betaCI)) {
+      meta.parametric.sum[meta.parametric.sum$effect==betaCI$effect, names(betaCI[r])] <- betaCI[r]
+    }
+    # library(rqdatatable)
+    # meta.parametric.sum <- natural_join(meta.parametric.sum,
+    #                           betaCI,
+    #                           by = "effect",
+    #                           jointype = "FULL") %>%
+    #   select(names(meta.parametric.sum))
   }
   #meta.parametric
   
@@ -167,7 +172,7 @@ metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
       main = paste0("Meta Analysis: Forest Plot [Parametric] \n(", title, ")")
     ) 
     par(font = 2)
-    text(pltForest$xlim[1], c(11, 5), cex = 0.75, pos = 4, names)
+    text(pltForest$xlim[1], rev(seq(length(studies)+2, by = length(studies)+3, length.out = length(var))), cex = 0.75, pos = 4, names)
[…]

### 2022-01-10 Methods-and-Results.Rmd
fe label fixed

@@
       for(i in 3:1){
-        addpoly(meta.parametric[[i]], row=m, cex=0.75, mlab=paste("►FE",names[i]),)
+        addpoly(meta.parametric[[i]], row=m, cex=0.75, mlab="► Fixed Effect")
         m <- m+6
@@
       for(i in 3:1){
-        addpoly(meta.bootstrapped[[i]], row=m, cex=0.75, mlab=paste("►FE",names.boot[i]),)
+        addpoly(meta.bootstrapped[[i]], row=m, cex=0.75, mlab="► Fixed Effect")
         m <- m+6

### 2022-01-10 manuscript.tex
figures added

@@
 \input{Methods-and-Results}
+
+\begin{figure}
+  \caption{Contact Hypothesis}
+  \begin{subfigure}{\textwidth}
+    \caption{}
+    \centering\includegraphics[width=0.75\textwidth]{Figures/forestBootstrappedGeneralLm.png}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+    \caption{}
+    \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
+  \end{subfigure}
+  \caption*{Note: \\
+  (a) summary of regression results from the aggregated contact and interaction quality data.\\
+  (b) summary of mixed models results of the contemporaneous contact effects.\\
+  General: Fixed effects meta analytic results are presented for completeness only.}
+\end{figure}
+
+\begin{figure}
+  \caption{Core Need Fulfillment}
+  \begin{subfigure}{\textwidth}
+    \caption{}
+    \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryQualityCore.png}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+    \caption{}
+    \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCore.png}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+    \caption{}
+    \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCoreQuality.png}
+  \end{subfigure}
+  \caption*{Note: \\
+  (a) Core Need Fulfillment predicting Interaction Quality.\\
+  (b) Core Need Fulfillment predicting Outgroup Attitudes.\\
+  (c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.\\
+  General: Fixed effects meta analytic results are presented for completeness only.}
+\end{figure}
+
+\begin{figure}
+  \caption{Robustness Analyses}
+  \begin{subfigure}{\textwidth}
+    \caption{}
+    \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
+  \end{subfigure}
+  \begin{subfigure}{\textwidth}
+    \caption{}
+    \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
+  \end{subfigure}
+  \caption*{Note: \\
+  (a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).\\
+  (b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).\\
+  General: Fixed effects meta analytic results are presented for completeness only.}
+\end{figure}
 

### 2022-01-10 Methods-and-Results.Rmd
re-run with small label fixes

@@
       format = "latex",
-      caption = "Descr Full Long",
+      caption = "Full Sample: Correlation Table and Descriptive Statistics",
       booktabs = TRUE,
@@
       format = "latex",
-      caption = "Descr Full Wide",
+      caption = "Full Sample: Correlation Table and Descriptive Statistics",
       booktabs = TRUE,
@@
       format = "latex",
-      caption = "Descr Out Long",
+      caption = "Intergroup Contact Sample: Correlation Table and Descriptive Statistics",
       booktabs = TRUE,
@@
       format = "latex",
-      caption = "Descr Out Wide",
+      caption = "ntergroup Contact Sample: Correlation Table and Descriptive Statistics",
       booktabs = TRUE,
@@
     name = "TheoryQualityCore",
-    title = "QualityRaw ~ CoreNeed"
+    title = "Quality ~ CoreNeed"
   )

### 2022-01-11 Supplemental-Material-B-Annotated-Analysis.Rmd
SI B worker zwc

@@
 source("./scripts/functions/MlCorMat.R")
+source("./scripts/functions/MlTbl.R")
+source("./scripts/functions/metaLmer.R")
 
@@
 
-<i class="fas fa-exclamation-circle"></i> Note. Multilevel effect size could be: 
-\begin{equation}
-(\#eq:MlEffectSize)
-f_b^2 = \frac{R_{ab}^2 - R_a^2}{1 - R_{ab}^2} \\
-R^2 = \frac{V_{null} - V_{model}}{V_{null}} \\
-f_b^2 = \frac{\frac{V_{null} - V_{ab}}{V_{null}} - \frac{V_{null} - V_{a}}{V_{null}}}{1 - \frac{V_{null} - V_{ab}}{V_{null}}}
-\end{equation}
-
-<br/>
+<!-- <i class="fas fa-exclamation-circle"></i> Note. Multilevel effect size could be:  -->
+<!-- \begin{equation} -->
+<!-- (\#eq:MlEffectSize) -->
+<!-- f_b^2 = \frac{R_{ab}^2 - R_a^2}{1 - R_{ab}^2} \\ -->
+<!-- R^2 = \frac{V_{null} - V_{model}}{V_{null}} \\ -->
+<!-- f_b^2 = \frac{\frac{V_{null} - V_{ab}}{V_{null}} - \frac{V_{null} - V_{a}}{V_{null}}}{1 - \frac{V_{null} - V_{ab}}{V_{null}}} -->
+<!-- \end{equation} -->
+
+<!-- <br/> -->
 
@@
 warning(
-  "some variable transformations (esp. _c and _z) might be across all participants (i.e., not within PP)."
+  "some variable transformations (esp. _c and _z) might be across all participants (i.e., not within PP). See next step."
 )
@@
 
+# dataframe where interaction types are recoded
+workerInteractionType <- dtWorker$full %>%
+  mutate(
+    OutgroupInteraction = as_factor(Contact_dum),
+    NonOutgroupInteraction = as_factor(inNonDutch)
+  )
+
+# Create variables centered and standardized within Participant
+# i.e., divide into trait and state
+workerWithinBetween <-
+  MlTraitState(
+    data = workerInteractionType,
+    id = "PID",
+    selection =
+      c(
+        "keyMotiveFulfilled",
+        "competence.daily.all",
+        "autonomy.daily.all",
+        "relatedness.daily.all",
+        "thermometerDutch_1",
+        "keymotive_fulfillemt_1",
+        "competence_1",
+        "autonomy_1",
+        "relatedness_1", 
+        "quality_overall_1", 
+        "OutgroupInteraction",
+        "NonOutgroupInteraction"
+      )
+  )
+
+workerOutWithinBetween <-
+  MlTraitState(
+    data = workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection =
+      c(
+        "keyMotiveFulfilled",
+        "thermometerDutch_1",
+        "keymotive_fulfillemt_1",
+        "competence_1",
+        "autonomy_1",
+        "relatedness_1", 
+        "quality_overall_1"
+      )
+  )
+
 # Between participants contact frequency
 workerContactFreq <- dtWorker$full %>%
-  group_by(ExternalReference) %>%
+  group_by(PID) %>%
   summarise(
@@
     WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
-  )
-
-# dataframe where interaction types are recoded
-workerInteractionType <- dtWorker$full %>%
-  mutate(
-    OutgroupInteraction = as_factor(Contact_dum),
-    NonOutgroupInteraction = as_factor(inNonDutch)
   )
@@
 ### Variable distributions
+
+```{r WorkerVarDescr}
+
+workerMlCor <-
+  MlCorMat(
+    data = dtWorkerSupp$workerInteractionType,
+    id = "PID",
+    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "quality_overall_1", "thermometerDutch_1"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+  )
+
+workerMlCor %>%
+  kable(
+    .,
+    caption = "Worker: Multilevel Core Variable Descriptives",
+    format = "latex",
+    booktabs = TRUE,
+    linesep = linesep(c(ncol(.))),
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/workerVarDescr.tex")
+
+```
 

### 2022-01-12 Supplemental-Material-B-Annotated-Analysis.Rmd
worker sample descr tables

@@
 
-<i class="fas fa-exclamation-triangle"></i> Still in 'scr/workerDescriptive.R'. Needs to be merged with this document.
-
 ### Participants
@@
 # look at frequencies of characteristics 
-table(workerSampleInfo$gender)
-table(workerSampleInfo$edu)
-table(workerSampleInfo$occupation)
-table(as.character(workerSampleInfo$nationality))
-```
+workerSampleInfo %>% 
+  select(
+    "Number of Measurements" = dailiesN,
+    Age = age,
+    Gender = gender,
+    Education = edu,
+    Nationality = nationality,
+    Occupation = occupation
+  ) %>%
+  mutate(
+    Nationality = as.character(Nationality)
+  ) %>%
+  tbl_summary(.,
+              sort = list(everything() ~ "frequency"))
+```
+
+For the first study, we recruited `r nrow(workerSampleInfo)` migrants using the local paid participant pool and specifically targeted non-Dutch migrants to participate in our study.
+Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
+With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(workerSampleInfo$dailiesN)`).
+This is a common number of measurements found in experience sampling studies and offers sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
+Participants were compensated for their participation with up to 34 Euros – each two Euros for pre- and post-questionnaire as well as 50 Eurocents for every experience sampling measurement occasion.
+The sample consisted of relatively young, educated, and western migrants from the global north ($M_{age}$ = `r format(round(mean(workerSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(workerSampleInfo$age),2), nsmall=2)`, `r nrow(workerSampleInfo %>% filter(gender == "Female"))` women, `r nrow(workerSampleInfo %>% filter(occupation == "student"))` students).
+The sample accurately describes one of the largest groups of migrants in the region \citep[][]{GemeenteGroningen2015}.
 
@@
   MlCorMat(
-    data = dtWorkerSupp$workerInteractionType,
+    data = workerInteractionType,
     id = "PID",
@@
     caption = "Worker: Multilevel Core Variable Descriptives",
-    format = "latex",
+    format = "html",
     booktabs = TRUE,
@@
     )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/workerVarDescr.tex")
+  )
 

### 2022-01-14 Supplemental-Material-B-Annotated-Analysis.Rmd
worker att type plt

@@
 # duration of survey should include median and MAD
-seconds_to_period(median(dtWorker$clean$Duration__in_seconds_))
-seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_)))
-
-#workerOutIntPerc <- (sum(workerAvFreQual$SumContactNL) / nrow(workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)
-# To test the prerequisite effect of intergroup contact, every daily diary measurement started with the question “_Did you meet a Dutch person this morning [/afternoon]?
-(In person interaction for at least 10 minutes)_” (`r workerOutIntPerc`% of all `r nrow(workerInteractionType)` recorded Recaps included an interaction with Dutch majority members).
-This question is our main predictor to test whether having an intergroup contact indeed has an influence on one’s rating of the outgroup attitudes during the respective morning or afternoon (i.e., a longitudinal test of the contact hypothesis).
-Methodologically, this question also determined the following survey flow for the participants.
-If they had interactions with Dutch people, they were asked to report details on the duration, type, and quality of the interaction.
-If they did not have interactions with Dutch people, participants were asked to report on their desire to have an interaction – this was done to balance the duration of the two answer options to not make it more attractive for a participant to answer that they did not have an interaction.
+workerInteractions <- dtWorker$clean %>%
+  dplyr::select(Duration__in_seconds_) %>%
+  mutate_all(as.numeric)
+
+workerInteractions %>%
+  psych::describe(., trim = .2) %>%
+  as.data.frame %>%
+  mutate(vars = c("Duration [in seconds]"), # rownames(.),
+         na = nrow(dtWorker$clean)-n,
+         win.mean = sapply(workerInteractions,psych::winsor.mean,simplify=T),
+         win.sd = sapply(workerInteractions,psych::winsor.sd,simplify=T)) %>%
+  dplyr::select(characteristic = vars, n, na, 
+                mean, `mean win` = win.mean, `mean trim` = trimmed, median,
+                sd, `sd win` = win.sd, MAD = mad, min, max,
+                skew, kurtosis) %>%
+  kbl(., 
+      #label = "",
+      caption = "Study 1: Duration of Measurement in Seconds",
+      format = "html", 
+      #linesep = "",
+      #booktabs = T,
+      row.names = F,
+      digits = 2,
+      align = c('l', rep('c', ncol(.)-1)))  %>%
+  add_header_above(., c(" " = 3,"Centrality" = 4, "Dispersion" = 5, "Distribution" = 2)) %>%
+  footnote(general = "'na' indicates the number of measurements for which measurement duration is unknown.") %>%
+  kable_classic(full_width = F, 
+                lightable_options = "hover", 
+                html_font = "Cambria")
+
+workerInteractionType %>%
+  select(OutgroupInteraction,
+         NonOutgroupInteraction) %>%
+  tbl_summary(.,
+              sort = list(everything() ~ "frequency"))
 ```
@@
 ```{r WorkerVarDescr}
-
+# calculate correlations and descriptives
 workerMlCor <-
@@
     format = "html",
-    booktabs = TRUE,
+    #booktabs = TRUE,
     linesep = linesep(c(ncol(.))),
@@
   ) %>%
+  pack_rows("Correlations", 1, ncol(workerMlCor)) %>%
+  pack_rows("Descriptives", ncol(workerMlCor)+1, nrow(workerMlCor)) %>%
   footnote(
@@
     )
-  )
+  ) %>%
+  kable_classic(full_width = F, 
+                lightable_options = "hover", 
+                html_font = "Cambria")
 
@@
 # between participants interaction type
+workerAttInteractionType <- workerInteractionType %>%
+  select(
+    PID,
+    OutgroupInteraction,
+    NonOutgroupInteraction,
+    Attitude = thermometerDutch_1
+  ) %>%
+  mutate(InteractionType = paste(
+    ifelse(OutgroupInteraction == "Yes", "Out", ifelse(OutgroupInteraction == "No", "NoOut", NA)),
+    ifelse(NonOutgroupInteraction == "yes", "In", ifelse(NonOutgroupInteraction == "no", "NoIn", NA)),
+    sep = ", "
+  ))
+
+as.numeric(workerInteractionType$NonOutgroupInteraction)
+
+ggplot(workerAttInteractionType, aes(y=Attitude, x=OutgroupInteraction, group = interaction(OutgroupInteraction, NonOutgroupInteraction), fill=NonOutgroupInteraction))+
+  geom_violin(trim = T, width=.8, position = position_dodge(0.8)) +
+  geom_boxplot(width=0.04,
+               position = position_dodge(.8),
+               outlier.colour = NULL, 
+               outlier.shape = NA, 
+               notch=F, fill="black", 
+               lwd=1, color="black") + 
+  # geom_jitter(width = 0.15,
+  #            shape=18,
+  #            alpha=.2, size=1) +
+  stat_summary(fun.y=mean, 
+               geom="point", 
+               shape=16, 
+               size=1, 
+               position = position_dodge(0.8),
+               colour="white") +
+  #stat_summary(fun.data="mean_sdl",  
+  #             fun.args = list(mult=1), 
+  #             geom="pointrange", 
+  #             color = "red", 
+  #             width=.2)+
+  stat_summary(geom = "crossbar", 
+               width=0.04, 
+               fatten=0, 
+               position = position_dodge(0.8),
+               color="white", 
+               fun.data = function(x){ return(c(y=median(x), 
+                                                ymin=median(x), 
+                                                ymax=median(x))) })+
+  ylab("Outgroup Attitudes")+
+  xlab("Outgroup Interaction") +
+  ggtitle("Violin Plot:\nOutgroup Attitudes by Interaction Type")+
+  scale_y_continuous(
+    limits = c(0, 100),
+    breaks = c(0, 15, 30, 40, 50, 60, 70, 85, 100),
+    labels = c(
+      "Very cold or unfavorable feelings 0°",
+      "Quite cold and unfavorable feelings 15°",
+      "Fairly cold and unfavorable feelings 30°",
+      "A bit cold and unfavorable feelings 40°",
+      "No feeling at all 50°",
+      "A bit warm and favorable feelings 60°",
+      "Fairly warm and favorable feelings 70° ",
+      "Quite warm and favorable feelings 85° ",
+      "Very warm and favorable feelings 100° "
+    )
+  ) +
+  #coord_flip()+
+  scale_fill_brewer(palette = "Pastel2", name = "Non-Outgroup Interaction")+
+  theme_Publication()+
+  theme(strip.background =element_rect(fill="black", color="black"),
+        strip.text = element_text(colour = 'white', face="bold"))#,
+        #panel.border = element_rect(color="grey"),
+        #legend.position="none")
+
 workerContactType <- dtWorker$full %>%
@@
 
-# plot bar chart
-ggplot(
+# plot bar chart (alternative with less information about actual data)
+workerAttInteractionTypeBar <- ggplot(
   workerContactType,

### 2022-01-14 Methods-and-Results.Rmd

@@
 
-\subsubsection{Contact Hypothesis}We again started with a general test of the contact hypothesis, as in Studies 1 and 2.
-We found no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (\textit{r} < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+\subsubsection{Contact Hypothesis}As in Studies 1 and 2, we first conducted a general contact hypothesis test.
+We found no correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (\textit{r} < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
 However, we did find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-When considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of the number of contacts nor an interaction effect.
+When considering the number of interactions and average interaction quality jointly in a linear regression, we only found a main effect of average perceived interaction quality on outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of the number of contacts nor an interaction effect.
 This result mirrors that of study one but is inconsistent with the second study.
-Additionally in a multilevel regression to check for contemporaneous effects within the participants, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
-Thus, in our third data set we again found mixed results, outgroup contacts are not significantly related to outgroup attitudes on aggregate between participants and this effect is also not suppressed by a average interaction quality (i.e., no interaction effect).
-However, while the aggregate data is partly inconsistent with the first two studies, the within person contemporaneous effect of intergroup contact is consistent across all three studies.
+Additionally in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Online Supplementary Materials B).
+Thus, in our third data set we again found mixed results.
+Outgroup contacts were on average not significantly related to outgroup attitudes on a between participant level and this effect was also not suppressed by an average interaction quality (i.e., no interaction effect).
+However, while the aggregate data was partly inconsistent with the first two studies, the within person contemporaneous effect of intergroup contact was consistent across all three studies.
 
@@
 
-To compare the models using either Allport's conditions or the core need fulfillment to predict outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
-When comparing the model selection indices we find that the fulfillment of the situation core need, indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
+To test wether Allport's conditions or the core need fulfillment are better at predicting outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
+When comparing the model selection indices we find that the fulfillment of the situational core need, indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
 Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`).
@@
 
-We again checked for alternative models to the core need fulfillment.
+We again checked for alternative models.
 First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
@@
 However, similar to the previous study, in this large sample relatedness (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each also predicted positive outgroup attitudes independently.
-However, the regression coefficient is three times as large for the core need fulfillment (with all scaling being equal).
+This being said, the regression coefficient for the core need was three times larger (with all scaling being equal).
 For full results see Online Supplementary Information B.

### 2022-01-14 manuscript.tex
affil note

@@
 \affil[1]{University of Groningen, Department of Psychology}
-\affil[2]{Author-order to be discussed; currently alphabetic by last name.}
+\affil[2]{Author-order to be discussed; currently in alphabetical order by last name.}
 
@@
 A major aspect of such migrant adaptation arguably unfolds during the daily interactions migrants have with the cultural majority members \citep{Maxwell2017, Sam2010}.
-One of the main social psychological theories proposed for understanding how contact between groups functions has been the ’intergroup contact hypothesis’.
+One of the main social psychological theories aimed at understanding contact between migrants and cultural majority groups is ’intergroup contact hypothesis’.
 In its most essential interpretation, the intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
@@
 That is to say, that if a person, for example, seeks to feel accepted by their interaction partner and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
-To test this, we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with majority group members.
+To test this, we collected three sets of real-life data from recent immigrants.
+More specifically, we followed their daily interactions with majority group members, tracking situational needs, interaction quality, and outgroup attitudes.
 
@@
     \item ESM: real-life data comes at the expense of having short/single item operationalizations
+    \item are we presenting a relativistic model?
+i.e.
+are we breaking theoretical ground?
+at the end we are saying: it always depends what the main goal of the individual is.
+Is this hyper applied but not really theoretical?
+(just a though :) )
 \end{enumerate}

### 2022-01-14 Supplemental-Material-B-Annotated-Analysis.Rmd
notes added

@@
 
-as.numeric(workerInteractionType$NonOutgroupInteraction)
-
+# violin plot of attitudes by interaction type group
 ggplot(workerAttInteractionType, aes(y=Attitude, x=OutgroupInteraction, group = interaction(OutgroupInteraction, NonOutgroupInteraction), fill=NonOutgroupInteraction))+
@@
 
+# summarize by interaction type group
 workerContactType <- dtWorker$full %>%

### 2022-01-14 Methods-and-Results.tex
meta General LM added
descr tables wide

@@
 
-We again started with a general test of the contact hypothesis, as in
-Studies 1 and 2. We found no significant correlation between intergroup
-contact and average outgroup attitudes --- for neither the total number
-of outgroup interactions nor the number of measurement beeps with an
-interaction (\textit{r} \textless{} 0.13, \textit{p} \textgreater{}
-0.291). However, we did find a significant correlation between the
-participants' Average Interaction Quality and their Average Outgroup
-Attitudes (\textit{r} = 0.25, \textit{p} = 0.036). When considering the
-number of interactions and average interaction quality jointly in a
-linear regression, we only find a main effect of average perceived
-interaction quality on predict outgroup attitudes (\textit{b} = 0.36,
-\textit{t}(67) = 2.22, \textit{p} = 0.030, \(\eta_p^2\) = 0.07) but no
-significant effect of the number of contacts nor an interaction effect.
-This result mirrors that of study one but is inconsistent with the
-second study. Additionally in a multilevel regression to check for
-contemporaneous effects within the participants, we found that having an
-outgroup interaction was indeed associated with significantly more
-positive outgroup attitudes within the participants (random slopes
-model; \textit{b} = 5.63, \textit{t}(3834) = 6.61, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}3.97, 7.29{]}), even after
-controlling for having an interaction with a non-Dutch (which did not
-relate to outgroup attitudes independently; For full results see Online
-Supplementary Materials B). Thus, in our third data set we again found
-mixed results, outgroup contacts are not significantly related to
-outgroup attitudes on aggregate between participants and this effect is
-also not suppressed by a average interaction quality (i.e., no
-interaction effect). However, while the aggregate data is partly
+As in Studies 1 and 2, we first conducted a general contact hypothesis
+test. We found no correlation between intergroup contact and average
+outgroup attitudes --- for neither the total number of outgroup
+interactions nor the number of measurement beeps with an interaction
+(\textit{r} \textless{} 0.13, \textit{p} \textgreater{} 0.291). However,
+we did find a significant correlation between the participants' Average
+Interaction Quality and their Average Outgroup Attitudes (\textit{r} =
+0.25, \textit{p} = 0.036). When considering the number of interactions
+and average interaction quality jointly in a linear regression, we only
+found a main effect of average perceived interaction quality on outgroup
+attitudes (\textit{b} = 0.36, \textit{t}(67) = 2.22, \textit{p} = 0.030,
+\(\eta_p^2\) = 0.07) but no significant effect of the number of contacts
+nor an interaction effect. This result mirrors that of study one but is
+inconsistent with the second study. Additionally in a multilevel
+regression to check for contemporaneous within person effects, we found
+that having an outgroup interaction was indeed associated with
+significantly more positive outgroup attitudes within the participants
+(random slopes model; \textit{b} = 5.63, \textit{t}(3834) = 6.61,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}3.97, 7.29{]}), even
+after controlling for having an interaction with a non-Dutch (which did
+not relate to outgroup attitudes independently; for full results see
+Online Supplementary Materials B). Thus, in our third data set we again
+found mixed results. Outgroup contacts were on average not significantly
+related to outgroup attitudes on a between participant level and this
+effect was also not suppressed by an average interaction quality (i.e.,
+no interaction effect). However, while the aggregate data was partly
 inconsistent with the first two studies, the within person
-contemporaneous effect of intergroup contact is consistent across all
+contemporaneous effect of intergroup contact was consistent across all
 three studies.
@@
 
-To compare the models using either Allport's conditions or the core need
-fulfillment to predict outgroup attitudes, we first assess relative
-model performance indices (i.e., Akaike information criterion, and
-Bayesian information criterion), and then consider the two predictors in
-a joint model to see whether the two approaches predict the same
-variance in outgroup attitudes. When comparing the model selection
-indices we find that the fulfillment of the situation core need, indeed
-performs slightly better than the model using Allport's conditions
+To test wether Allport's conditions or the core need fulfillment are
+better at predicting outgroup attitudes, we first assess relative model
+performance indices (i.e., Akaike information criterion, and Bayesian
+information criterion), and then consider the two predictors in a joint
+model to see whether the two approaches predict the same variance in
+outgroup attitudes. When comparing the model selection indices we find
+that the fulfillment of the situational core need, indeed performs
+slightly better than the model using Allport's conditions
 (\(AIC_{CoreNeed}\) 12632.02 \textless{} 12651.59 \(AIC_{Allport}\), and
@@
 
-We again checked for alternative models to the core need fulfillment.
-First, when considering generalized situational core need fulfillment
-together with whether an intergroup contact took place, we find that
-there is no significant main effect of core need fulfillment (random
-slopes model; \textit{b} = 0.03, \textit{t}(3835) = 1.51, \textit{p} =
-0.131, \textit{95\%CI}{[}-0.01, 0.06{]}) but a stronger interaction
-effect of core need fulfillment and outgroup contact (\textit{b} = 0.17,
-\textit{t}(3835) = 7.32, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.21{]}). Together with a significant main
-effect of having an outgroup contact (\textit{b} = 5.41,
-\textit{t}(3835) = 6.36, \textit{p} \textless{} .001,
+We again checked for alternative models. First, when considering
+generalized situational core need fulfillment together with whether an
+intergroup contact took place, we find that there is no significant main
+effect of core need fulfillment (random slopes model; \textit{b} = 0.03,
+\textit{t}(3835) = 1.51, \textit{p} = 0.131, \textit{95\%CI}{[}-0.01,
+0.06{]}) but a stronger interaction effect of core need fulfillment and
+outgroup contact (\textit{b} = 0.17, \textit{t}(3835) = 7.32, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.12, 0.21{]}). Together with a
+significant main effect of having an outgroup contact (\textit{b} =
+5.41, \textit{t}(3835) = 6.36, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}3.74, 7.08{]}), this indicates that it is not key need
@@
 \textit{p} = 0.034, \textit{95\%CI}{[}-0.01, 0.08{]}) each also
-predicted positive outgroup attitudes independently. However, the
-regression coefficient is three times as large for the core need
-fulfillment (with all scaling being equal). For full results see Online
+predicted positive outgroup attitudes independently. This being said,
+the regression coefficient for the core need was three times larger
+(with all scaling being equal). For full results see Online
 Supplementary Information B.
 
-\input{Tables/descrFullLong}
-\input{Tables/descrOutLong}
+\input{Tables/descrFullWide}
+\input{Tables/descrOutWide}
 
 \input{Tables/mdlContactGeneralLong}
-
 \input{Tables/mdlTheorylong}
-
 \input{Tables/mdlRobustlong}

### 2022-01-14 Supplemental-Material-B-Annotated-Analysis.Rmd
worker ols regression adjusted

@@
 
-#### OLS regression
-
 We first assess the impact of the different interaction types across all measurement points (lumping all beeps together).
@@
 
-#### ML regression
+### Interaction Frequency and Interaction Quality
+
+In a next step we check whether the effect of outgroup interactions, in part, depends on the quality during the interactions.
+In this step we aggregate the within person data to remove any dependency issues.
+Additionally, because we can only assess interaction quality when there is an interaction, it is difficult to assess this with the interaction dummy as a within person predictor.
+Instead, we will use an aggregate measure of interaction quality and average interaction quality to consider the two predictors jointly.
+Such an aggregation in essence mirrors the general 'past recall' approach that dominates the field.
+The only difference being that we aggregate data that participants recorded shortly after the actual interactions, wheras in most recall studies this aggregation is done mentally by the participant.
+
+\begin{equation}
+(\#eq:FreqQual)
+Attitude = ContactFreq \times AverageContactQual
+\end{equation}
+
+```{r workerFreqQualCor}
+# prepare data
+workerAvFreQual <- dtWorker$full %>%
+  group_by(ExternalReference) %>%
+  summarise(
+    n = n(),
+    SumContactNL = sum(Contact_dum),
+    PercContactNL = SumContactNL / n * 100,
+    SumContactNLAll = sum(number),
+    AvAttitude = mean(thermometerDutch_1, na.rm = TRUE),
+    AvQuality = mean(quality_overall_1, na.rm = TRUE)
+  ) %>%
+  mutate(
+    WinSumContactNL = DescTools::Winsorize(SumContactNL),
+    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll),
+    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
+    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
+    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
+    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
+  )
+
+# correlation panel
+pairs.panels.new(
+  workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
+    "Sum:\nNumber of Outgroup Contacts (NL)",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+
+# correlation panel with interaction sums winsorized
+pairs.panels.new(
+  workerAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
+    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+```
+
+Within the data, we find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
+Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
+However, the frequency of intergroup interactions had no meaningful correlation with either the average interaction quality or average outgroup attitudes.
+
+```{r workerModelOlsAttFreqQual}
+# regression
+mdlWorker$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = workerAvFreQual)
+# summary(lmWorkerAttFreqQualX)
+
+summ(
+  mdlWorker$lmAttFreqQualX,
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+
+mdlWorker$lmAttFreqQualXEta <-
+  effectsize::eta_squared(mdlWorker$lmAttFreqQualX, partial = TRUE)
+
+interactions::interact_plot(
+  mdlWorker$lmAttFreqQualX,
+  pred = AvQuality_c,
+  modx = SumContactNL_c,
+  interval = TRUE,
+  partial.residuals = TRUE
+)
+
+interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
+                             pred = AvQuality_c,
+                             modx = SumContactNL_c,
+                             alpha = .05)
+```
+
+We find that interaction quality is significantly related to higher outgroup attitudes (albeit with a small effect size).
+We also find that in our sample with an increasing number of interactions the positive effect of interaction quality becomes weaker.
+However, it should be noted that this is based on data aggregating all within participant nuances and is only the date of 21 people.
+
+### ML regression
 
@@
 
-##### Unconditional model
+#### Unconditional model
 
@@
 
-##### random intercept with predictors
+#### random intercept with predictors
 
@@
 
-##### random slope
+#### random slope
 
@@
 TL;DR: Random slopes don't add much for this super simple model.
-
-### Interaction Frequency and Interaction Quality
-
-In a final step we check whether the effect outgroup interactions, in part, depends on the quality during the interactions.
-Because we can only assess interaction quality when there is an interaction, it is difficult to assess this with the interaction dummy as a within person predictor.
-Instead, we will use an aggregate measure of interaction quality and average interaction quality to consider the two predictors jointly.
-
-\begin{equation}
-(\#eq:FreqQual)
-Attitude = ContactFreq \times AverageContactQual
-\end{equation}
-
-```{r workerFreqQualCor}
-# prepare data
-workerAvFreQual <- dtWorker$full %>%
-  group_by(ExternalReference) %>%
-  summarise(
-    n = n(),
-    SumContactNL = sum(Contact_dum),
-    PercContactNL = SumContactNL / n * 100,
-    SumContactNLAll = sum(number),
-    AvAttitude = mean(thermometerDutch_1, na.rm = TRUE),
-    AvQuality = mean(quality_overall_1, na.rm = TRUE)
-  ) %>%
-  mutate(
-    WinSumContactNL = DescTools::Winsorize(SumContactNL),
-    WinSumContactNLAll = DescTools::Winsorize(SumContactNLAll)
-  )
-
-# correlation panel
-pairs.panels.new(
-  workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
-    "Sum:\nNumber of Outgroup Contacts (NL)",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-
-# correlation panel with interaction sums winsorized
-pairs.panels.new(
-  workerAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
-    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-```
-
-Within the data, we find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
-Thus within our data participants with a higher quality outgroup interactions also held more positive attitudes towards that group.
-However, the frequency of intergroup interactions had no meaningful correlation with either the average interaction quality or average outgroup attitudes.
-
-```{r workerModelOlsAttFreqQual}
-# regression
-mdlWorker$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL * AvQuality, data = workerAvFreQual)
-# summary(lmWorkerAttFreqQualX)
-
-summ(
-  mdlWorker$lmAttFreqQualX,
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-mdlWorker$lmAttFreqQualXEta <-
-  effectsize::eta_squared(mdlWorker$lmAttFreqQualX, partial = TRUE)
-
-interactions::interact_plot(
-  mdlWorker$lmAttFreqQualX,
-  pred = AvQuality,
-  modx = SumContactNL,
-  interval = TRUE,
-  partial.residuals = TRUE
-)
-
-interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
-                             pred = AvQuality,
-                             modx = SumContactNL,
-                             alpha = .05)
-```
-
-We find that interaction quality is significantly related to higher outgroup attitudes (albeit with a small effect size).
-We also find that in our sample with an increasing number of interactions the positive effect of interaction quality becomes weaker.
-However, it should be noted that this is based on data aggregating all within participant nuances and is only the date of 21 people.
 

### 2022-01-16 Supplemental-Material-B-Annotated-Analysis.Rmd
m&r re-render fro overleaf

@@
 csl: apa.csl
+header-includes:
+   - \usepackage{amsmath, nccmath}
 ---
@@
 <br/>
+
+<i class="fas fa-exclamation-circle"></i> Note. All multilevel assumptions are tested as usual including (e.g., for random slopes model with _j_ within person predictors):
+
+$$
+\begin{align}
+  &\textrm{Level 1 Variance:}\ e_{ti} \sim \mathcal{N}(0,\sigma^2) \\
+  &\textrm{Level 2 Variance:}\ \begin{bmatrix} u_{0i}\\ \vdots\\ u_{ji}\end{bmatrix} 
+  \sim \mathcal{N}
+  \begin{pmatrix}
+    \begin{bmatrix} 
+      0 \\ 
+      \vdots \\
+      0
+    \end{bmatrix}, 
+    \begin{bmatrix} 
+      \tau_{00}^2 &  & \\ 
+      \vdots & \ddots & \\
+      \tau_{j0} & \ldots & \tau_{jj}^2
+    \end{bmatrix}
+  \end{pmatrix}
+\end{align}
+$$
+
+</br>
 
@@
 
-### ML regression
-
-We, thus, proceed with a multilevel analysis, which acknowledges that the measurements are nested within participants.
+### Multi-Level Regression
+
+We then proceeded with a multilevel analysis, which also acknowledges that the measurements are nested within participants, but makes full use of the within participant variation.
 
@@
 (\#eq:WorkerEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
+  \end{split} 
 \end{equation}
@@
 
-```{r workerModelInterceptNull}
+```{r workerModelGls}
 # Create and save Model
@@
 (\#eq:WorkerInteractionTypeModel)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20}
+  \end{split} 
 \end{equation}
@@
 
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+mdlWorker$lmerInterceptAttTypeCI <- 
+  confint(method = "Wald", mdlWorker$lmerInterceptAttType)
 
@@
 \begin{equation}
-(\#eq:RandSlopesEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:WorkerRandomSlopes)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i}
+  \end{split} 
 \end{equation}
@@
 
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+# Simple (i.e., fast) CIs
+mdlWorker$lmerSlopesAttTypeCI <- 
+  confint(method = "Wald", mdlWorker$lmerSlopesAttType)
 
@@
 
-<i class="fas fa-question-circle"></i> _Note to self:_ For completeness, we should probably check this against an empty model without random intercept.
-
 \begin{equation}
 (\#eq:WorkerOutEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} +  e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
+  \end{split} 
 \end{equation}
@@
 \begin{equation}
-(\#eq:AttitudeNeedEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerOutInterceptAttNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10}
+  \end{split} 
 \end{equation}
@@
 \begin{equation}
-(\#eq:AttitudeNeedRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerOutSlopeAttNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i}
+  \end{split} 
 \end{equation}

### 2022-01-16 Methods-and-Results.Rmd
descr tables wide
table link fixed

@@
 The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
-Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullLong} and Table \ref{tab:descrOutLong}.
+Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
 
@@
 The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
-Correlations and descriptive statistics of the included variables are available in Tables \ref{tab:descrFullLong} and \ref{tab:descrOutLong}.
+Correlations and descriptive statistics of the included variables are available in Tables \ref{tab:descrFullWide} and \ref{tab:descrOutWide}.
 
@@
 
-<!-- \input{Tables/descrFullWide} -->
-<!-- \input{Tables/descrOutWide} -->
-
-\input{Tables/descrFullLong}
-\input{Tables/descrOutLong}
+\input{Tables/descrFullWide}
+\input{Tables/descrOutWide}
+
+<!-- \input{Tables/descrFullLong} -->
+<!-- \input{Tables/descrOutLong} -->
 

### 2022-01-16 Methods-and-Results.tex
table link fixed

@@
 Materials B. Correlations and descriptive statistics of the included
-variables are available in Table \ref{tab:descrFullLong} and Table
-\ref{tab:descrOutLong}.
+variables are available in Table \ref{tab:descrFullWide} and Table
+\ref{tab:descrOutWide}.
 
@@
 Materials B. Correlations and descriptive statistics of the included
-variables are available in Tables \ref{tab:descrFullLong} and
-\ref{tab:descrOutLong}.
+variables are available in Tables \ref{tab:descrFullWide} and
+\ref{tab:descrOutWide}.
 

### 2022-01-16 manuscript.tex
aff adj
Updates from Overleaf

@@
 \affil[1]{University of Groningen, Department of Psychology}
-\affil[2]{Author-order to be discussed; currently in alphabetical order by last name.}
+\affil[2]{Any additional affiliations still need to be added.}
 
@@
 % Migrant Example Pathways
-\textbf{Relevance (Version 1 of 2): Migrant Example Version:}
-
+% Relevance (Version 1 of 2): Migrant Example Version:
 Conflict between social groups and their individual members remains a prevalent feature of the modern human condition.
@@
 % Full Migrant Pathway
-\textbf{Relevance (Version 2 of 2): Full Migrant Focus Version:}
-
-The adaptation of migrants in new cultural contexts has become an important issue for many societies around the world.
+% Relevance (Version 2 of 2): Full Migrant Focus Version:
+%The adaptation of migrants in new cultural contexts has become an important issue for many societies around the world.
 A major aspect of such migrant adaptation arguably unfolds during the daily interactions migrants have with the cultural majority members \citep{Maxwell2017, Sam2010}.
-One of the main social psychological theories aimed at understanding contact between migrants and cultural majority groups is ’intergroup contact hypothesis’.
+One of the main social psychological theories aimed at understanding contact between social groups is ’intergroup contact hypothesis’.
 In its most essential interpretation, the intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
@@
 % Problem v.02: theoretical interaction quality central to understanding outcomes, practical many impactful negative interactions in everyday life
-\textbf{Problem Illustration Paragraph:}
-
+% Problem Illustration Paragraph:
 Importantly, not understanding when and why an interaction is perceived as positive presents substantial theoretical and practical obstacles.
-There is now consistent evidence that negative intergroup contacts lead to worse attitudes, prejudice, and future interaction motivation \citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.
+There is now consistent evidence that negative intergroup contacts lead to worse attitudes, prejudice, and reduced future interaction motivation \citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.
 Theoretically, understanding whether an interaction is perceived as positive or negative (i.e., interaction quality) thus sits at the heart of when the intergroup contact hypothesis is successful (e.g., Brown et al.
@@
 % Aim / Solution v.02: look at need fulfillment as mechanism in daily interactions of migrants
-\textbf{Proposal Paragraph:}
-
+% Proposal Paragraph:
 In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and positive outgroup attitudes.
@@
 % neither are necessary or explain why an interaction is positive
-
 Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
@@
 Is this hyper applied but not really theoretical?
-(just a though :) )
+(just a though :) ) Make sure to discuss: (1) practical relevance and (2) core situational need as initial test of the role of motivations.
 \end{enumerate}

### 2022-01-16 manuscript.tex
limitations added

@@
 \subsection{Limitations}
-to be discussed, potentially:
-\begin{enumerate}
-    \item migrants are not refugees (generalizability potentially even more relevant?)
-    \item minority perspective only
-    \item lagged effects left for future studies (potentially not relevant, time scale)
-    \item ESM: real-life data comes at the expense of having short/single item operationalizations
-    \item are we presenting a relativistic model?
-i.e.
-are we breaking theoretical ground?
-at the end we are saying: it always depends what the main goal of the individual is.
-Is this hyper applied but not really theoretical?
-(just a though :) ) Make sure to discuss: (1) practical relevance and (2) core situational need as initial test of the role of motivations.
-\end{enumerate}
+% (1) Sample = minority and (voluntary) migrants, (2) Methodology = short scales (reliability) and no lagged effects, (3) Core Need Concept = non-specific
+As with any approach our studies are not without practical and theoretical limitations.
+One limitation is our choice of samples.
+While we believe that a need–based mechanism should be relevant to any inter-group contact, our sample has focused on a minority- and (voluntary) migrant perspective.
+Without additional evidence it thus remains difficult to judge whether motivational effects will generalize to other migrant groups (e.g., forced migrants), other intergroup contexts (e.g., gender- or sexual orientation groups), and to majority groups in their outgroup attitudes.
+We know of no research that for other contexts psychological needs would not be relevant (once existential needs are met) but future research may extend our findings to other contexts to build an even broader understanding of psychological needs in intergroup contacts.
+A second limitation lies in our methodology.
+While extensive longitudinal data is close to the real-life events this method comes at the expense of longer and more robust scales.
+Long and repetitive scales are often not feasible in extensive longitudinal methods because of the increased burden to the participants.
+To circumvent this shortcoming, we have ensured that the measures we used were, whenever possible, based on past validations.
+However, the circumstance remains that extensive longitudinal data often does not allow the same scrutiny of measurement reliability as single–shot cross–section data sets.
+An additional methodological question lies in the unexplored potential of the longitudinal aspects of our data.
+For our research questions we have focused on contemporaneous effects within the data set, yet future investigations should seek to extend the mechanism to developmental trajectories within and between participants.
+And finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
+This has come at the expense of specificity in the situational needs (i.e., we have not explored which exact needs people had during their interactions).
+With the adaptive measurement we have proposed such an investigation would be possible (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
+Nonetheless, future research may explore which exact needs are most important in different intergroup contexts.
 
 \subsection{Implications}
+From our results we can draw a number of
+
 to be discussed, potentially:

### 2022-01-16 manuscript.tex
implications added

@@
 \subsection{Implications}
-From our results we can draw a number of
+Given these limitations, we can draw a number of implications for other researchers and practitioners from our results.
+A first implication concerns the feasibility and usefulness of extensive longitudinal data for intergroup contact research and the broader field of social psychology.
+While setting up an extensive longitudinal study is in no manner easy, given the amount and quality of the data, we believe the efforts to be similar to a sizable cross-section data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with 10,000 data-points).
+Given the comparable effort, this opens up the possibility to explore research questions that focus on real-life phenomena outside the lab or focus on phenomena that depend on changes and influences over time.
+In the context of intergroup contact research, we were among the first to answer calls to test intergroup contact mechanisms using on extended real-life data \citep[e.g.,][]{Pettigrew2011, MacInnis2015}.
+And in doing so, we not only collected a sizable amount of real-life data, but our consideration of extensive longitudinal data may present new inconsistencies in how participants perceive and cognitively aggregate their past interactions with other groups — which may suggest large-scale recall-biases or conflations of within and between participant effects in conventional cross-section studies.
 
-to be discussed, potentially:
-\begin{enumerate}
-    \item feasible to collect large amount of data on intergroup contact using ESM method (do we have a formR ref in there?; set up is feasible but not the easiest; maybe even advertise the reusability of the formR survey?)
-    \item role of motivation in intergroup contact promising (potential for interventions, e.g., most immediate to the data: settlement practices). 
-    \item potential to identify context specific needs
-\end{enumerate}
+A broader theoretical implication relates to role of situational motivation in intergroup contacts.
+Our results offer a first promising test of psychological needs in intergroup contact.
+While our results are tentative given their novelty within the field, they were highly consistent across studies and may offer new theoretical avenues moving forward.
+Psychological needs are a facet of the human experience that has thus far been under–emphasized in the intergroup contact literature.
+This stands in stark contrast of the many cognitive \citep[e.g.,][]{Pettigrew1998, Brown2005} and emotional aspects investigated within the field \citep[e.g.,][]{Stephan2008, Paolini2004}.
+However, if motivational mechanisms are indeed shown to be meaningful factors in intergroup contacts, future research may be able to integrate broader theoretical frameworks of intergroup contact (e.g., motivations guiding cognition and affect, which in turn drive behavior.
+cf., theory of reasoned goal pursuit; \citealp{Ajzen2019}).
 
-\subsection{Conclusion paragraph (not a real heading)}
-to be written after co-author meeting.
+Additionally, situational motivations in intergroup contact also offer promising avenues for practitioners and policy-makers.
+Intergroup contact theory is among the most implemented psychological theories \citep[e.g.,][]{Pettigrew2006, AlRamiah2012a, Reimer2021}.
+Given our findings that psychological needs in every-day intergroup contacts were at least as powerful as Allport's conditions in predicting outgroup attitudes, considerations of people's needs offer a substantially simpler mechanism to address.
+In cases where some or all optimal contact conditions are not possible to be fulfilled, needs offer an even more compelling alternative (e.g., where equal status is contextually not possible or in cases where people help despite a lack of institutional support).
+Additionally, our conceptualization of situational needs might offer an additional opportunity for practitioners and interventions.
+Instead of addressing needs as a one-size fits all solution (e.g., simply focusing on competence needs), one may at times ask outgroup interaction partners what they need during an interaction.
+This is not to say that we should not explore which needs tend to be relevant to specific groups in specific intergroup contact contexts.
+Rather, interventions for which such data is not available or infeasible to collect, a flexible and reactive approach to intergroup contact needs might be more fruitful.
+
+CONCLUSION PARAGRAPH
 

### 2022-01-17 manuscript.tex
conclusion added

@@
 \subsection{Implications}
+% ESM data
 Given these limitations, we can draw a number of implications for other researchers and practitioners from our results.
@@
 
+% Motivation and core needs 
 A broader theoretical implication relates to role of situational motivation in intergroup contacts.
@@
 
+% practical use of needs
 Additionally, situational motivations in intergroup contact also offer promising avenues for practitioners and policy-makers.
@@
 
-CONCLUSION PARAGRAPH
+% Conclusion paragraph
+In sum, in this paper we used extensive longitudinal methodologies to capture real-life data of recent migrants in their interactions with the majority outgroup.
+Our three studies showcase the feasibility and utility of such data to test intergroup contact theory.
+We provide evidence that the fulfillment of situational psychological needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
+Our results point to motivation as an understudied aspect of intergroup contact that is important in understanding when and why an interaction is perceived as positive and will lead to more positive outgroup attitudes.
 

### 2022-01-17 manuscript.tex
Abstract and Significance Statement

@@
 \abstract{
-Abstract goes here.
+One challenge of modern intergroup contact research has been a question of when and why an interaction is perceived as positive and carries the benefits of positive intergroup contact.
+The understudied mechanism of interaction quality is highlighted by a broad body of literature showing the adverse effects of negative intergroup interactions.
+To understand positive intergroup interactions, we propose to look at situational motivations and psychological needs in every-day intergroup interactions.
+We collected three extensive longitudinal studies of recent migrants to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297).
+Across the three studies, we find inconsistent evidence for interaction frequencies and average interaction quality in predicting outgroup attitudes.
+However, using non-aggregated data shows a strong influence of outgroup interactions on outgroup attitudes.
+We find that the fulfillment of psychological needs offers a strong predictor of the positive attitudes after interactions and that these positive effects go through perceived interaction quality.
+The situational needs remained the core predictor of outgroup attitudes even after controlling for Allport's contact conditions or more general fundamental needs.
+As one of the first studies to test intergroup contact theory using extensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
 
-\noindent\textbf{Public significance statement}: Significance Statement goes here.
+\noindent\textbf{Public significance statement}: In this paper we provide evidence that the fulfillment of situational psychological needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
+This offers testament both to emerging practice of capturing real-life interactions using extensive longitudinal data and that motivational fulfillment offer a flexible and relevant mechanism of understanding positive intergroup contact.
 }

### 2022-01-17 Methods-and-Results.Rmd
re-read and tbl/fig references

@@
 The sample consisted of relatively young, educated, and western migrants from the global north ($M_{age}$ = `r format(round(mean(workerSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(workerSampleInfo$age),2), nsmall=2)`, `r nrow(workerSampleInfo %>% filter(gender == "Female"))` women, `r nrow(workerSampleInfo %>% filter(occupation == "student"))` students).
-The sample accurately describes one of the largest groups of migrants in the region \citep[][]{GemeenteGroningen2015}.
+The sample accurately describes the largest groups of migrants in the region \citep[][]{GemeenteGroningen2015}.
 
@@
 interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
-These participants are removed from any analyses including outgroup contacts.}.
+These participants are removed from any analyses that focus on outgroup contacts.}.
 
@@
 However, we did find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = \hl{X.XX}, \textit{p} = \hl{X.XXX}.
-And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker.
+And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblWide}).
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblWide} and Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
 This is unusual and might indicate the the effect is very consistent across participants.
@@
 This should, in turn, be due to a higher perceived interaction quality.
-We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly (for full regression results see Table \ref{tab:intergroupNeedsTblWide}).
 
@@
 For this, we analyzed the generalized situational core need fulfillment (either during an interaction or about the daytime in general) and tested whether the effect differed during daily diary measurements with and without outgroup contacts.
-We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`).
+We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`; also see Table \ref{tab:robustnessTblWide}).
 Together with a significant main effect of having an outgroup contact, this indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
@@
 When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all three fundamental needs (competence and autonomy needs turning non-significant; all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
-For full results see Online Supplementary Information B.
+For full results see see Table \ref{tab:robustnessTblWide} and Online Supplementary Information B.
 
@@
 The aim of Study 2 is similar to Study 1, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
-However, in this second study we collected a substantially larger sample of international students who recently arrived in the Netherlands and also improved the study design (e.g., pop up explanations described later).
+However, in this second study we collected a substantially larger sample of international students who recently arrived in the Netherlands and also improved the study design (e.g., pop-up explanations described later).
 The survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations as these students will likely interact with the Dutch majority outgroup on a daily basis.
@@
 However, we found no significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term.
+Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblWide}).
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently; For full results see Online Supplementary Materials B).
-Thus, in our second dataset we find mixed results, outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblWide} and Online Supplementary Materials B).
+Thus, in our second data set we find mixed results, outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
 However, we find that this effect does not depend on the average perceived interaction quality.
@@
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`).
-Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`).
+Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblWide} for full results).
 These results are consistent with the results in study one and we thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
@@
 Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteraction")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous study, albeit with slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction).
+This finding is consistent with the results of the previous study, albeit with slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see Table \ref{tab:intergroupNeedsTblWide} and for visual comparison see Figure \ref{fig:AllportNeedFulfillment}).
 
@@
 However, different from the first study, relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes in this larger sample.
-For full results see Online Supplementary Information B.
+For full results see Table \ref{tab:intergroupNeedsTblWide} and Online Supplementary Information B.
 
@@
 This result mirrors that of study one but is inconsistent with the second study.
-Additionally in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Online Supplementary Materials B).
+Additionally in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Table \ref{tab:intergroupGeneralTblWide} and Online Supplementary Materials B).
 Thus, in our third data set we again found mixed results.
@@
 We find that in the multilevel models, the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
-Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`).
+Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see Table \ref{tab:intergroupNeedsTblWide} and Figure \ref{fig:AllportNeedFulfillment}).
 These results indicate that in this dataset the the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
@@
 We find that in the multilevel models, the fulfillment of core need fulfillment during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
-Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`).
-These results indicate that in this dataset the the fulfillment of core situational needs had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
+Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see Table \ref{tab:intergroupNeedsTblWide} and Figure \ref{fig:AllportNeedFulfillment}).
+These results indicate that in this data set the the fulfillment of core situational needs had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
 
@@
 When comparing the model selection indices we find that the fulfillment of the situational core need, indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
-Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`).
+Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblWide} and Figure \ref{fig:AllportNeedFulfillment}).
 This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
@@
 This being said, the regression coefficient for the core need was three times larger (with all scaling being equal).
-For full results see Online Supplementary Information B.
+For full results see Table \ref{tab:robustnessTblWide} and Figure \ref{fig:Robustness} as well as Online Supplementary Information B.
 

### 2022-01-17 Methods-and-Results.tex
re-read and tbl/fig references

@@
 global north (\(M_{age}\) = 24.35, \(SD_{age}\) = 4.73, 19 women, 15
-students). The sample accurately describes one of the largest groups of
+students). The sample accurately describes the largest groups of
 migrants in the region \citep[][]{GemeenteGroningen2015}.
@@
 responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
-These participants are removed from any analyses including outgroup contacts.}.
+These participants are removed from any analyses that focus on outgroup contacts.}.
 
@@
 in our sample with an increasing number of interactions the positive
-effect of average interaction quality becomes weaker. We additionally
-used a multilevel regression to check whether having an interaction with
-an outgroup member had a situational (i.e., contemporaneous) effect
-within the participants. We find that having an outgroup interaction is
-indeed associated with significantly more positive outgroup attitudes
-within the participants (\textit{b} = 2.48, \textit{t}(1200) = 4.36,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}1.36, 3.59{]}), even
-after controlling for having an interaction with a non-Dutch (which did
-not relate to outgroup attitudes independently; For full results see
-Online Supplementary Materials
+effect of average interaction quality becomes weaker (also see Table
+\ref{tab:intergroupGeneralTblWide}). We additionally used a multilevel
+regression to check whether having an interaction with an outgroup
+member had a situational (i.e., contemporaneous) effect within the
+participants. We find that having an outgroup interaction is indeed
+associated with significantly more positive outgroup attitudes within
+the participants (\textit{b} = 2.48, \textit{t}(1200) = 4.36, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}1.36, 3.59{]}), even after
+controlling for having an interaction with a non-Dutch (which did not
+relate to outgroup attitudes independently; For full results see Table
+\ref{tab:intergroupGeneralTblWide} and Online Supplementary Materials
 B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
@@
 need is assumed by the perceived interaction quality if considered
-jointly.
+jointly (for full regression results see Table
+\ref{tab:intergroupNeedsTblWide}).
 
@@
 \textit{t}(1199) = 4.31, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.07, 0.18{]}). Together with a significant main
-effect of having an outgroup contact, this indicates that it is not key
-need fulfillment in general --- but only key need fulfillment during an
+\textit{95\%CI}{[}0.07, 0.18{]}; also see Table
+\ref{tab:robustnessTblWide}). Together with a significant main effect of
+having an outgroup contact, this indicates that it is not key need
+fulfillment in general --- but only key need fulfillment during an
 outgroup contact that predicts more positive outgroup attitudes.
@@
 autonomy needs turning non-significant; all \textit{b} \textless{} 0.05,
-all \textit{p} \textgreater{} 0.544). For full results see Online
-Supplementary Information B.
+all \textit{p} \textgreater{} 0.544). For full results see see Table
+\ref{tab:robustnessTblWide} and Online Supplementary Information B.
 
@@
 international students who recently arrived in the Netherlands and also
-improved the study design (e.g., pop up explanations described later).
+improved the study design (e.g., pop-up explanations described later).
 The survey method again offers a large body of ecologically valid data
@@
 \(\eta_p^2\) = 0.08) but no significant effect of average perceived
-contact quality and no significant interaction term. We additionally
-used a multilevel regression to check whether having an interaction with
-an outgroup member had a situational (i.e., contemporaneous) effect
-within the participants. We find that having an outgroup interaction is
-indeed associated with significantly more positive outgroup attitudes
-within the participants (random slopes model; \textit{b} = 2.99,
+contact quality and no significant interaction term (for full results
+see Table \ref{tab:intergroupGeneralTblWide}). We additionally used a
+multilevel regression to check whether having an interaction with an
+outgroup member had a situational (i.e., contemporaneous) effect within
+the participants. We find that having an outgroup interaction is indeed
+associated with significantly more positive outgroup attitudes within
+the participants (random slopes model; \textit{b} = 2.99,
 \textit{t}(4850) = 3.80, \textit{p} \textless{} .001,
@@
 interaction with a non-Dutch person (which did not relate to outgroup
-attitudes independently; For full results see Online Supplementary
-Materials B). Thus, in our second dataset we find mixed results,
-outgroup contacts show a positive effect on outgroup attitudes in the
-moment and on average between participants. However, we find that this
-effect does not depend on the average perceived interaction quality.
-This unexpected results, might be due to the aggregation process and the
-following analyses will focus in on the role of the perceived
-interaction quality during an outgroup interaction.
+attitudes independently; For full results see Table
+\ref{tab:intergroupGeneralTblWide} and Online Supplementary Materials
+B). Thus, in our second data set we find mixed results, outgroup
+contacts show a positive effect on outgroup attitudes in the moment and
+on average between participants. However, we find that this effect does
+not depend on the average perceived interaction quality. This unexpected
+results, might be due to the aggregation process and the following
+analyses will focus in on the role of the perceived interaction quality
+during an outgroup interaction.
 
@@
 \textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
-0.07{]}). These results are consistent with the results in study one and
+0.07{]}; also see Table \ref{tab:intergroupNeedsTblWide} for full
+results). These results are consistent with the results in study one and
 we thus find support for our hypotheses and can conclude that in this
@@
 study, albeit with slightly weaker effect (likely because of the large
-number of measurements that did not include an outgroup interaction).
+number of measurements that did not include an outgroup interaction; For
+full results see Table \ref{tab:intergroupNeedsTblWide} and for visual
+comparison see Figure \ref{fig:AllportNeedFulfillment}).
 
@@
 0.08{]}) also predicted positive outgroup attitudes in this larger
-sample. For full results see Online Supplementary Information B.
+sample. For full results see Table \ref{tab:intergroupNeedsTblWide} and
+Online Supplementary Information B.
 
@@
 not relate to outgroup attitudes independently; for full results see
-Online Supplementary Materials B). Thus, in our third data set we again
-found mixed results. Outgroup contacts were on average not significantly
-related to outgroup attitudes on a between participant level and this
-effect was also not suppressed by an average interaction quality (i.e.,
-no interaction effect). However, while the aggregate data was partly
-inconsistent with the first two studies, the within person
-contemporaneous effect of intergroup contact was consistent across all
-three studies.
+Table \ref{tab:intergroupGeneralTblWide} and Online Supplementary
+Materials B). Thus, in our third data set we again found mixed results.
+Outgroup contacts were on average not significantly related to outgroup
+attitudes on a between participant level and this effect was also not
+suppressed by an average interaction quality (i.e., no interaction
+effect). However, while the aggregate data was partly inconsistent with
+the first two studies, the within person contemporaneous effect of
+intergroup contact was consistent across all three studies.
 
@@
 (\textit{b} = 0.09, \textit{t}(1600) = 2.89, \textit{p} = 0.004,
-\textit{95\%CI}{[}0.03, 0.15{]}). These results indicate that in this
+\textit{95\%CI}{[}0.03, 0.15{]}; also see Table
+\ref{tab:intergroupNeedsTblWide} and Figure
+\ref{fig:AllportNeedFulfillment}). These results indicate that in this
 dataset the the fulfillment of Allport's conditions had a significant
@@
 (\textit{b} = 0.11, \textit{t}(1600) = 3.50, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}0.05, 0.17{]}). These results indicate that in
-this dataset the the fulfillment of core situational needs had a
-significant influence on outgroup attitudes and this effect is likely in
-parts explained by its effect through perceived interaction quality.
+.001, \textit{95\%CI}{[}0.05, 0.17{]}; for full results see Table
+\ref{tab:intergroupNeedsTblWide} and Figure
+\ref{fig:AllportNeedFulfillment}). These results indicate that in this
+data set the the fulfillment of core situational needs had a significant
+influence on outgroup attitudes and this effect is likely in parts
+explained by its effect through perceived interaction quality.
 
@@
 \textit{t}(1600) = 3.85, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.08, 0.17{]}). This indicates that, although both
+\textit{95\%CI}{[}0.08, 0.17{]}; also see Table
+\ref{tab:intergroupNeedsTblWide} and Figure
+\ref{fig:AllportNeedFulfillment}). This indicates that, although both
 Allport's conditions and the core need fulfillment seem to (in part)
@@
 the regression coefficient for the core need was three times larger
-(with all scaling being equal). For full results see Online
-Supplementary Information B.
+(with all scaling being equal). For full results see Table
+\ref{tab:robustnessTblWide} and Figure \ref{fig:Robustness} as well as
+Online Supplementary Information B.
 

### 2022-01-17 manuscript.tex
figure ref labels added
discussion re-work

@@
   \caption{Contact Hypothesis}
+  \label{fig:ContactHypothesis}
   \begin{subfigure}{\textwidth}
@@
   \caption{Core Need Fulfillment}
+  \label{fig:AllportNeedFulfillment}
   \begin{subfigure}{\textwidth}
@@
   \caption{Robustness Analyses}
+  \label{fig:Robustness}
   \begin{subfigure}{\textwidth}
@@
 When considering the results of the three studies jointly, we find mixed results for the basic intergroup contact hypothesis.
-The aggregated number of outgroup interactions across all measurements only had a significant effect on average outgroup attitudes in one of the three studies and in that study there was no significant effect of average interaction quality on outgroup attitudes (which was significant for the other two studies).
-This meant that only for our smallest study did we find the expected interaction between interaction frequency and interaction quality when looking at the aggregated data across all measurements.
+For the data that aggregated people's interaction frequencies and average interaction quality we don't find a consistent predictor of outgroup attitudes.
+Neither interaction quality, or interaction quality, nor their interaction was a significant predictor across all studies (also see Figure \ref{fig:ContactHypothesis}a).
 However, once we considered the effect of having an interaction with an outgroup member (vs.
-not having an outgroup interaction) within the participants, we find that intergroup contact is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account).
+not having an outgroup interaction) within the participants in a multi-level model, we find that intergroup contact is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account; also see Figure \ref{fig:ContactHypothesis}b).
 While this later results is in line with our expectations, the earlier aggregate findings are surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
-Even though this inconsistency with past research might be a data artefact (e.g., because most people reported more substantially mode measurements during which they did not have an outgroup interaction), the absence of this aggregate effect could underline the fact that cross-sectional retrospective data might suffer from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
+Even though this inconsistency with past research might be a data artefact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction), the absence of this aggregate effect could underline the fact that cross-sectional retrospective data might might be misleading because it presents a mixture of within and between effects \citep[][]{Hamaker2020} or suffer from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
 In summary, we thus find that when we aggregate interaction frequencies and interaction quality from our intensive longitudinal data we find inconsistent results from the past literature but within participants intergroup contacts are significantly related with positive outgroup attitudes.
@@
 In most cases the core need even took over the variances previously explained by the self-determination theory needs.
-We thus find strong evidence that within everyday life interactions of recent migrants with majority group members, the perception that one's interaction specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
+We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
 As such the data offers a first test of the motivational basis of intergroup contact.

### 2022-01-17 Methods-and-Results.Rmd
tab ref fix

@@
 However, we did find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = \hl{X.XX}, \textit{p} = \hl{X.XXX}.
-And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblWide}).
+And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblLong}).
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblWide} and Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
 This is unusual and might indicate the the effect is very consistent across participants.
 However, the small number of participants, or other measurement issues provide an alternative explanation}.
-Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants (eventough the average number of interactions does seem to interact with average interaction quality to predict outgroup attitudes).
+Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants (even tough the average number of interactions does seem to interact with average interaction quality to predict outgroup attitudes).
 However, it should be noted that the between-participant analyses in the aggregated form are based on a small sample size.
@@
 This should, in turn, be due to a higher perceived interaction quality.
-We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly (for full regression results see Table \ref{tab:intergroupNeedsTblWide}).
+We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly (for full regression results see Table \ref{tab:intergroupNeedsTblLong}).
 
@@
 For this, we analyzed the generalized situational core need fulfillment (either during an interaction or about the daytime in general) and tested whether the effect differed during daily diary measurements with and without outgroup contacts.
-We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`; also see Table \ref{tab:robustnessTblWide}).
+We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`; also see Table \ref{tab:robustnessTblLong}).
 Together with a significant main effect of having an outgroup contact, this indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
@@
 When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all three fundamental needs (competence and autonomy needs turning non-significant; all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
-For full results see see Table \ref{tab:robustnessTblWide} and Online Supplementary Information B.
+For full results see see Table \ref{tab:robustnessTblLong} and Online Supplementary Information B.
 
@@
 However, we found no significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblWide}).
+Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblLong}).
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblWide} and Online Supplementary Materials B).
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials B).
 Thus, in our second data set we find mixed results, outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
@@
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`).
-Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblWide} for full results).
+Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} for full results).
 These results are consistent with the results in study one and we thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
@@
 Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteraction")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous study, albeit with slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see Table \ref{tab:intergroupNeedsTblWide} and for visual comparison see Figure \ref{fig:AllportNeedFulfillment}).
+This finding is consistent with the results of the previous study, albeit with slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see Table \ref{tab:intergroupNeedsTblLong} and for visual comparison see Figure \ref{fig:AllportNeedFulfillment}).
 
@@
 However, different from the first study, relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes in this larger sample.
-For full results see Table \ref{tab:intergroupNeedsTblWide} and Online Supplementary Information B.
+For full results see Table \ref{tab:intergroupNeedsTblLong} and Online Supplementary Information B.
 
@@
 This result mirrors that of study one but is inconsistent with the second study.
-Additionally in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Table \ref{tab:intergroupGeneralTblWide} and Online Supplementary Materials B).
+Additionally in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Table \ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials B).
 Thus, in our third data set we again found mixed results.
@@
 We find that in the multilevel models, the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
-Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see Table \ref{tab:intergroupNeedsTblWide} and Figure \ref{fig:AllportNeedFulfillment}).
+Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
 These results indicate that in this dataset the the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
@@
 We find that in the multilevel models, the fulfillment of core need fulfillment during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
-Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see Table \ref{tab:intergroupNeedsTblWide} and Figure \ref{fig:AllportNeedFulfillment}).
+Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
 These results indicate that in this data set the the fulfillment of core situational needs had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
@@
 When comparing the model selection indices we find that the fulfillment of the situational core need, indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
-Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblWide} and Figure \ref{fig:AllportNeedFulfillment}).
+Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
 This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
@@
 This being said, the regression coefficient for the core need was three times larger (with all scaling being equal).
-For full results see Table \ref{tab:robustnessTblWide} and Figure \ref{fig:Robustness} as well as Online Supplementary Information B.
+For full results see Table \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as Online Supplementary Information B.
 

### 2022-01-17 Methods-and-Results.tex
tab ref fix

@@
 effect of average interaction quality becomes weaker (also see Table
-\ref{tab:intergroupGeneralTblWide}). We additionally used a multilevel
+\ref{tab:intergroupGeneralTblLong}). We additionally used a multilevel
 regression to check whether having an interaction with an outgroup
@@
 relate to outgroup attitudes independently; For full results see Table
-\ref{tab:intergroupGeneralTblWide} and Online Supplementary Materials
+\ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials
 B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
@@
 jointly (for full regression results see Table
-\ref{tab:intergroupNeedsTblWide}).
+\ref{tab:intergroupNeedsTblLong}).
 
@@
 \textit{95\%CI}{[}0.07, 0.18{]}; also see Table
-\ref{tab:robustnessTblWide}). Together with a significant main effect of
+\ref{tab:robustnessTblLong}). Together with a significant main effect of
 having an outgroup contact, this indicates that it is not key need
@@
 all \textit{p} \textgreater{} 0.544). For full results see see Table
-\ref{tab:robustnessTblWide} and Online Supplementary Information B.
+\ref{tab:robustnessTblLong} and Online Supplementary Information B.
 
@@
 contact quality and no significant interaction term (for full results
-see Table \ref{tab:intergroupGeneralTblWide}). We additionally used a
+see Table \ref{tab:intergroupGeneralTblLong}). We additionally used a
 multilevel regression to check whether having an interaction with an
@@
 attitudes independently; For full results see Table
-\ref{tab:intergroupGeneralTblWide} and Online Supplementary Materials
+\ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials
 B). Thus, in our second data set we find mixed results, outgroup
@@
 \textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
-0.07{]}; also see Table \ref{tab:intergroupNeedsTblWide} for full
+0.07{]}; also see Table \ref{tab:intergroupNeedsTblLong} for full
 results). These results are consistent with the results in study one and
@@
 number of measurements that did not include an outgroup interaction; For
-full results see Table \ref{tab:intergroupNeedsTblWide} and for visual
+full results see Table \ref{tab:intergroupNeedsTblLong} and for visual
 comparison see Figure \ref{fig:AllportNeedFulfillment}).
@@
 0.08{]}) also predicted positive outgroup attitudes in this larger
-sample. For full results see Table \ref{tab:intergroupNeedsTblWide} and
+sample. For full results see Table \ref{tab:intergroupNeedsTblLong} and
 Online Supplementary Information B.
@@
 not relate to outgroup attitudes independently; for full results see
-Table \ref{tab:intergroupGeneralTblWide} and Online Supplementary
+Table \ref{tab:intergroupGeneralTblLong} and Online Supplementary
 Materials B). Thus, in our third data set we again found mixed results.
@@
 \textit{95\%CI}{[}0.03, 0.15{]}; also see Table
-\ref{tab:intergroupNeedsTblWide} and Figure
+\ref{tab:intergroupNeedsTblLong} and Figure
 \ref{fig:AllportNeedFulfillment}). These results indicate that in this
@@
 .001, \textit{95\%CI}{[}0.05, 0.17{]}; for full results see Table
-\ref{tab:intergroupNeedsTblWide} and Figure
+\ref{tab:intergroupNeedsTblLong} and Figure
 \ref{fig:AllportNeedFulfillment}). These results indicate that in this
@@
 \textit{95\%CI}{[}0.08, 0.17{]}; also see Table
-\ref{tab:intergroupNeedsTblWide} and Figure
+\ref{tab:intergroupNeedsTblLong} and Figure
 \ref{fig:AllportNeedFulfillment}). This indicates that, although both
@@
 (with all scaling being equal). For full results see Table
-\ref{tab:robustnessTblWide} and Figure \ref{fig:Robustness} as well as
+\ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as
 Online Supplementary Information B.

### 2022-01-17 Methods-and-Results.Rmd
order fix

@@
 
+\input{Tables/descrFullWide}
+\input{Tables/descrOutWide}
+
+\input{Tables/mdlContactGeneralLong}
+\input{Tables/mdlTheorylong}
+\input{Tables/mdlRobustlong}
+
+<!-- FIGURES: -->
+
 ```{r metaGeneralLm, include=FALSE}
@@
 ```
-
-\input{Tables/descrFullWide}
-\input{Tables/descrOutWide}
-
-<!-- \input{Tables/descrFullLong} -->
-<!-- \input{Tables/descrOutLong} -->
-
-<!-- \input{Tables/mdlContactGeneral} -->
-<!-- \input{Tables/mdlTheory} -->
-<!-- \input{Tables/mdlRobustness} -->
-
-\input{Tables/mdlContactGeneralLong}
-\input{Tables/mdlTheorylong}
-\input{Tables/mdlRobustlong}
-
-<!-- \begin{figure}[h] -->
-
-<!-- \centering -->
-
-<!-- \caption{PRISMA Diagrams for the Theoretical, Methodological, and Empirical Literature.} -->
-
-<!-- \makebox[\textwidth]{\includegraphics[width=\paperwidth]{Figures/PrismaCombined}} -->
-
-<!-- \label{fig:PrismaCombined} -->
-
-<!-- \end{figure} -->
-
-<!-- \input{Tables/ExclusionsCombined} -->
-
-<!-- \input{Tables/TheoreticalExclusion} -->
-
-<!-- \begin{figure}[h] -->
-
-<!-- \centering -->
-
-<!-- \caption{Literature Levels: (A) Bar graph of the experience aspect frequencies for theoretical, methodological, and broader empirical literature.
-(B) Bar graph of the number of experience aspects used for theoretical, methodological, and broader empirical literature.
-(C) Average number of additional aspects included when the aspect was considered for theoretical, methodological, and broader empirical literature [Mean ± 95\%CI].} -->
-
-<!-- \includegraphics[width=\textwidth]{Figures/LiteratureComparison-1} -->
-
-<!-- \caption*{Note that in (C) within each literature body the aspects are not mutually exclusive (and thus not independent) because scales can include multiple experience aspects.} -->
-
-<!-- \label{fig:LiteratureComparison} -->
-
-<!-- \end{figure} -->

### 2022-01-18 Methods-and-Results.tex
affil adj

@@
 results do not translate into average differences between participants
-(eventough the average number of interactions does seem to interact with
-average interaction quality to predict outgroup attitudes). However, it
-should be noted that the between-participant analyses in the aggregated
-form are based on a small sample size.
+(even tough the average number of interactions does seem to interact
+with average interaction quality to predict outgroup attitudes).
+However, it should be noted that the between-participant analyses in the
+aggregated form are based on a small sample size.
 
@@
 
-\faQuestionCircle~Are we sure that we don't want some sort of
-bootstrapped indirect effect?
-
 \subsubsection{Core Need}
@@
 explained by its effect through perceived interaction quality.
-
-\faQuestionCircle~Are we sure that we don't want some sort of
-bootstrapped indirect effect?
 

### 2022-01-31 Methods-and-Results.Rmd
adjusted

@@
              data = dtWorkerSupp$workerOutWithinBetween) # use optim if it does not converge
+
 mdlWorkerOut$Qlt$lmeNull <-
-  mdlWorkerOut$Qlt$lmeNull <-lme(
+  mdlWorkerOut$Qlt$lmeNull <- lme(
     quality_overall_1 ~ 1,
@@
 
+# 95%CI
 mdlWorkerOut$Qlt$lmerInterceptCoreCI <- 
@@
 
+# 95%CI
 mdlWorkerOut$Qlt$lmerSlopesCoreCI <- 
@@
 
+# 95% CI
 mdlWorkerOut$Att$lmerInterceptCoreQltCI <- 
@@
 
+# 95%CI
 mdlWorkerOut$Att$lmerSlopesCoreQltCI <- 
@@
 
+# 95%CI
 mdlWorker$lmerInterceptAttCoreIntCI <- 

### 2022-01-31 Supplemental-Material-B-Annotated-Analysis.Rmd
adjusted

@@
   as.vector
+
+# Center within and between
+# divide into trait and state
+studentWithinBetween <-
+  MlTraitState(
+    data = studentInteractionType,
+    id = "PID",
+    selection =
+      c(
+        "KeyNeedFullfillment",
+        "Competence",
+        "Autonomy",
+        "Relatedness",
+        "AttitudesDutch",
+        "quality_overall",
+        "OutgroupInteraction",
+        "NonOutgroupInteraction"
+      )
+  )
+studentOutWithinBetween <-
+  MlTraitState(
+    data = studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection =
+      c(
+        "KeyNeedFullfillment",
+        "Competence",
+        "Autonomy",
+        "Relatedness",
+        "AttitudesDutch",
+        "quality_overall"
+      )
+  )
+
 ```
@@
   lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1,
+    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc,
     random = ~ 1 | PID,
-    data = workerOutgroupInteraction
+    data = workerOutWithinBetween
   )
@@
 summ(
-  lmer(thermometerDutch_1 ~ keymotive_fulfillemt_1 + (1 | PID), 
-       data = workerOutgroupInteraction),
+  mdlWorkerOut$Att$lmerInterceptCore <- lmer(thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + (1 | PID), 
+       data = workerOutWithinBetween),
   confint = TRUE,
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  center = FALSE
+)
+
+# Generate 95% CIs
+mdlWorkerOut$Att$lmerInterceptCoreCI <- 
+  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCore)
 
@@
     thermometerDutch_1 ~
-      keymotive_fulfillemt_1,
-    random = ~ 1 + keymotive_fulfillemt_1 | PID,
+      keymotive_fulfillemt_1_cwc,
+    random = ~ 1 + keymotive_fulfillemt_1_cwc | PID,
     control = lmeControl(opt = "optim"),
-    data = workerOutgroupInteraction
+    data = workerOutWithinBetween
   )
@@
     thermometerDutch_1 ~
-      keymotive_fulfillemt_1 +
-      (1 + keymotive_fulfillemt_1 | PID),
-    data = workerOutgroupInteraction
+      keymotive_fulfillemt_1_cwc +
+      (1 + keymotive_fulfillemt_1_cwc | PID),
+    data = workerOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  center = FALSE
+)
+
+# all variables standardized within PPT
+summ(
+  mdlWorkerOut$Att$lmerSlopesCoreZ <- lmer(
+    thermometerDutch_1_zwc ~
+      keymotive_fulfillemt_1_zwc +
+      (1 + keymotive_fulfillemt_1_zwc | PID),
+    data = workerOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# standardized coefficients
+stdCoef.merMod(mdlWorkerOut$Att$lmerSlopesCore)
+
+# 95%CIs
+mdlWorkerOut$Att$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCore)
+
+# Attempts at R^2
+r2mlm::r2mlm(mdlWorkerOut$Att$lmerSlopesCore, bargraph = TRUE)
+mitml::multilevelR2(mdlWorkerOut$Att$lmerSlopesCore)
+performance::r2(mdlWorkerOut$Att$lmerSlopesCore)
+performance::model_performance(mdlWorkerOut$Att$lmerSlopesCore)
+performance::compare_performance(mdlWorkerOut$Att$lmerNull, 
+                                 mdlWorkerOut$Att$lmerInterceptCore, 
+                                 mdlWorkerOut$Att$lmerSlopesCore)
 
 # Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeInterceptCore, 
+anova(mdlWorkerOut$Att$lmeNull, 
+      mdlWorkerOut$Att$lmeInterceptCore, 
       mdlWorkerOut$Att$lmeSlopesCore) %>%
@@
 mdlWorkerOut$Att$predSlopesCore <- 
-  workerOutgroupInteraction %>%
+  workerOutWithinBetween %>%
   select(thermometerDutch_1, session, PID) %>% 
   mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCore,
-                           workerOutgroupInteraction,
+                           workerOutWithinBetween,
                            re.form = NA
@@
 
-<div class="alert alert-warning alert-dismissible fade in" role="alert">
-  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
-  <i class="fas fa-exclamation-triangle"></i> <b>Check needed: </b><br/>
-  Something is with the variances explained (between = `r format(round(mdlWorkerOut$Att$varBtwPercSlopesCore, 2),nsmall=2)`%, within = `r format(round(mdlWorkerOut$Att$varWithinPercSlopesCore, 2),nsmall=2)`%).
-This is when comparing the random intercepts to the random slopes model.
-Check with materials from Laura!!
-</div>
-
 ### Need fulfillment and Interaction Quality
@@
 \begin{equation}
-(\#eq:WorkerOutQualEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:WorkerOutQltEmptyModel)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ InteractionQuality_{ti} =  &\ \beta_{0i} +  e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
+  \end{split} 
 \end{equation}
@@
   lme4::lmer(quality_overall_1 ~ 1 + (1 | PID), 
-             data = workerOutgroupInteraction) # use optim if it does not converge
+             data = workerOutWithinBetween) # use optim if it does not converge
+
 mdlWorkerOut$Qlt$lmeNull <-
@@
     random = ~ 1 | PID,
-    data = workerOutgroupInteraction,
+    data = workerOutWithinBetween,
     control = list(opt = "nlmimb")
@@
 # summary(Null.Out.Qual.ML.r) #or with the lme function
-summ(mdlWorkerOut$Qlt$lmerNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1~1 + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
+summ(mdlWorkerOut$Qlt$lmerNull, digits = 3)
 
@@
 
-<i class="fas fa-question-circle"></i> _Note to self:_ For completeness, we should probably check this against an empty model without random intercept.
-
 #### random intercept with level one predictor
@@
 \begin{equation}
-(\#eq:QualityNeedEq)
-InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerOutInterceptQltNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ InteractionQuality_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10}
+  \end{split} 
 \end{equation}
@@
   lme(
-    quality_overall_1 ~ keymotive_fulfillemt_1,
+    quality_overall_1 ~ keymotive_fulfillemt_1_cwc,
     random = ~ 1 | PID,
-    data = workerOutgroupInteraction
+    data = workerOutWithinBetween
   )
@@
 summ(
-  lmer(quality_overall_1 ~ keymotive_fulfillemt_1 + (1 | PID), 
-       data = workerOutgroupInteraction),
+  mdlWorkerOut$Qlt$lmerInterceptCore <- 
+    lmer(quality_overall_1 ~ keymotive_fulfillemt_1_cwc + (1 | PID), 
+       data = workerOutWithinBetween),
   confint = TRUE,
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(quality_overall_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlWorkerOut$Qlt$lmerInterceptCoreCI <- 
+  confint(method = "Wald", mdlWorkerOut$Qlt$lmerInterceptCore)
 
@@
 
-<!-- taken from: https://stats.idre.ucla.edu/stata/faq/how-can-i-estimate-effect-size-for-mixed/ -->
-<!-- also check: https://largescaleassessmentsineducation.springeropen.com/articles/10.1186/s40536-018-0061-2 -->
 \begin{equation}
-(\#eq:QualityNeedRandEq)
-InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerOutSlopeQltNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ InteractionQuality_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i}
+  \end{split} 
 \end{equation}
@@
     quality_overall_1 ~
-      keymotive_fulfillemt_1,
-    random = ~ 1 + keymotive_fulfillemt_1 | PID,
+      keymotive_fulfillemt_1_cwc,
+    random = ~ 1 + keymotive_fulfillemt_1_cwc | PID,
     control = lmeControl(opt = "optim"),
-    data = workerOutgroupInteraction
+    data = workerOutWithinBetween
   )
@@
       quality_overall_1 ~
-        keymotive_fulfillemt_1 +
-        (1 + keymotive_fulfillemt_1 | PID),
-      data = workerOutgroupInteraction
+        keymotive_fulfillemt_1_cwc +
+        (1 + keymotive_fulfillemt_1_cwc | PID),
+      data = workerOutWithinBetween
     ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(mdlWorkerOut$Qlt$lmerSlopesCore,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlWorkerOut$Qlt$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlWorkerOut$Qlt$lmerSlopesCore)
 
 # Compare new model to previous step
-anova(mdlWorkerOut$Qlt$lmeInterceptCore, 
+anova(mdlWorkerOut$Qlt$lmeNull, 
+      mdlWorkerOut$Qlt$lmeInterceptCore, 
       mdlWorkerOut$Qlt$lmeSlopesCore) %>%
@@
   lme4::VarCorr(mdlWorkerOut$Qlt$lmeSlopesCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Qlt$varBtwSlopesCore <-
-  1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[1]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[1]))
-mdlWorkerOut$Qlt$varBtwPercSlopesCore <-
-  (1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[1]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Qlt$varWithinSlopesCore <-
-  1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[2]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[2]))
-mdlWorkerOut$Qlt$varWithinPercSlopesCore <-
-  (1 - (as.numeric(mdlWorkerOut$Qlt$varSlopesCore[2]) / as.numeric(mdlWorkerOut$Qlt$varInterceptCore[2]))) * 100
 ```
@@
 
-### Interaction Needs,Quality, and Attitudes
+### Interaction Needs, Quality, and Attitudes
 
@@
 \begin{equation}
-(\#eq:AttitudeQualityNeedEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerOutInterceptAttQltNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20}
+  \end{split} 
 \end{equation}
@@
   lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1 + quality_overall_1,
+    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + quality_overall_1_cwc,
     random = ~ 1 | PID,
-    data = workerOutgroupInteraction
+    data = workerOutWithinBetween
   )
@@
 summ(
+  mdlWorkerOut$Att$lmerInterceptCoreQlt <- 
     lmer(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1 + quality_overall_1 + (1 | PID),
-    data = workerOutgroupInteraction
+    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + quality_overall_1_cwc + (1 | PID),
+    data = workerOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  center = FALSE
+)
+
+# 95% CI
+mdlWorkerOut$Att$lmerInterceptCoreQltCI <- 
+  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCoreQlt)
 
@@
 \begin{equation}
-(\#eq:AttitudeQualityNeedRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerOutSlopeAttQltNeedEq)
+(\#eq:WorkerRandomSlopes)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i}
+  \end{split} 
 \end{equation}
-
-<i class="fas fa-question-circle"></i> Check whether the omega matrix is correct should probably have as many taus as gammas.
 
@@
     thermometerDutch_1 ~
-      keymotive_fulfillemt_1 + quality_overall_1,
-    random = ~ 1 + keymotive_fulfillemt_1 + quality_overall_1 | PID,
+      keymotive_fulfillemt_1_cwc + quality_overall_1_cwc,
+    random = ~ 1 + keymotive_fulfillemt_1_cwc + quality_overall_1_cwc | PID,
     control = lmeControl(opt = "optim"),
-    data = workerOutgroupInteraction
+    data = workerOutWithinBetween
   )
@@
     thermometerDutch_1 ~
-      keymotive_fulfillemt_1 + quality_overall_1 +
-      (1 + keymotive_fulfillemt_1 + quality_overall_1 | PID),
-    data = workerOutgroupInteraction
+      keymotive_fulfillemt_1_cwc + quality_overall_1_cwc +
+      (1 + keymotive_fulfillemt_1_cwc + quality_overall_1_cwc | PID),
+    data = workerOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlWorkerOut$Att$lmerSlopesCoreQltCI <- 
+  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreQlt)
 
@@
 
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwSlopesCoreQlt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[1]))
-mdlWorkerOut$Att$varBtwPercSlopesCoreQlt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinSlopesCoreQlt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[2]))
-mdlWorkerOut$Att$varWithinPercSlopesCoreQlt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreQlt[2]))) * 100
-
 # Assumption Checks:
@@
 mdlWorkerOut$Att$predSlopesCoreQlt <- 
-  workerOutgroupInteraction %>%
+  workerOutWithinBetween %>%
   select(thermometerDutch_1, session, PID) %>% 
   mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreQlt,
-                           workerOutgroupInteraction,
+                           workerOutWithinBetween,
                            re.form = NA
@@
 \begin{equation}
-(\#eq:AttitudeNeedInteractionEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerInterceptAttIntNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{3i}KeyNeedFulfillXOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20} \\
+                      &\ \beta_{3i} = \gamma_{30}
+  \end{split} 
 \end{equation}
@@
   lme(
-    thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction,
+    thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction,
     random =  ~ 1 | PID,
-    data = workerInteractionType
+    data = workerWithinBetween
   )
@@
   mdlWorker$lmerInterceptAttCoreInt <- lmer(
-    thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction + (1 | PID),
-    data = workerInteractionType
+    thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction + (1 | PID),
+    data = workerWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=dtWorker$full),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  center = FALSE
+)
+
+# 95% CI
+mdlWorker$lmerInterceptAttCoreIntCI <- 
+  confint(method = "Wald", mdlWorker$lmerInterceptAttCoreInt)
 
@@
 \begin{equation}
-(\#eq:AttitudeNeedInteractionRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti}  + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerSlopesAttIntNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{3i}KeyNeedFulfillXOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                      &\ \beta_{3i} = \gamma_{30} + u_{3i}
+  \end{split} 
 \end{equation}
@@
   thermometerDutch_1 ~
-    keyMotiveFulfilled * OutgroupInteraction,
-  random = ~ 1 + keyMotiveFulfilled + OutgroupInteraction | PID,
+    keyMotiveFulfilled_cwc * OutgroupInteraction,
+  random = ~ 1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID,
   control = lmeControl(opt = "optim"),
-  data = workerInteractionType
+  data = workerWithinBetween
 )
@@
     thermometerDutch_1 ~
-      keyMotiveFulfilled * OutgroupInteraction +
-      (1 + keyMotiveFulfilled + OutgroupInteraction | PID),
-    data = workerInteractionType
+      keyMotiveFulfilled_cwc * OutgroupInteraction +
+      (1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID),
+    data = workerWithinBetween
   ), 
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlWorker$lmerSlopesAttCoreIntCI <- 
+  confint(method = "Wald", mdlWorker$lmerSlopesAttCoreInt)
 
@@
 
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorker$varBtwSlopesAttCoreInt <- 
-  1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[1]) / as.numeric(mdlWorker$varInterceptAttCoreInt[1]))
-mdlWorker$varBtwPercSlopesAttCoreInt <- 
-  (1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[1]) / as.numeric(mdlWorker$varInterceptAttCoreInt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorker$varWithinSlopesAttCoreInt <- 
-  1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[2]) / as.numeric(mdlWorker$varInterceptAttCoreInt[2]))
-mdlWorker$varWithinPercSlopesAttCoreInt <- 
-  (1 - (as.numeric(mdlWorker$varSlopesAttCoreInt[2]) / as.numeric(mdlWorker$varInterceptAttCoreInt[2]))) * 100
-
 # Assumption Checks:
@@
 mdlWorker$predSlopesAttCoreInt <- 
-  workerInteractionType %>%
+  workerWithinBetween %>%
   select(thermometerDutch_1, session, PID) %>% 
   mutate(measure = predict(mdlWorker$lmeSlopesAttCoreInt,
-                           workerInteractionType,
+                           workerWithinBetween,
                            re.form = NA
@@
 datNew = data.frame(
-  OutgroupInteraction = factor(rep(c("No", "Yes"), each = 21)),
-  keyMotiveFulfilled = rep(seq(-50, 50, 5), 2),
+  keyMotiveFulfilled_cwc = rep(seq(
+    round_any(min(
+      workerWithinBetween$keyMotiveFulfilled_cwc
+    ), 5, f = floor), round_any(max(
+      workerWithinBetween$keyMotiveFulfilled_cwc
+    ), 5, f = ceiling), 5
+  ), 2),
   PID = 0
-)
+) %>%
+  mutate(OutgroupInteraction = rep(c(1, 2), each = nrow(.)/2)) %>%
+  select(PID, OutgroupInteraction, keyMotiveFulfilled_cwc)
 
@@
 rm(datNew, PI)
+mdlWorker$predInterceptAttCoreIntX$OutgroupInteractionLab <-
+  factor(
+    x = mdlWorker$predInterceptAttCoreIntX$OutgroupInteraction,
+    levels = sort(
+      unique(mdlWorker$predInterceptAttCoreIntX$OutgroupInteraction)
+    ),
+    labels = c("No", "Yes")
+  )
 
@@
   mdlWorker$predInterceptAttCoreIntX,
-  aes(x = keyMotiveFulfilled,
+  aes(x = keyMotiveFulfilled_cwc,
       y = fit,
-      fill = OutgroupInteraction)
+      fill = OutgroupInteractionLab)
 )+
   #geom_point() +
-  geom_line(aes(linetype = as.factor(OutgroupInteraction)), size = 1) +
+  geom_line(aes(linetype = OutgroupInteractionLab), size = 1) +
   #facet_wrap(~PID, ncol = 6)+
@@
               alpha = 0.3) +
-  scale_x_continuous(breaks = seq(-50, 50, 10)) +
+  scale_x_continuous(breaks = seq(
+    round_any(min(
+      workerWithinBetween$keyMotiveFulfilled_cwc
+    ), 5, f = floor), round_any(max(
+      workerWithinBetween$keyMotiveFulfilled_cwc
+    ), 5, f = ceiling), 10
+  )) +
   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
@@
 # brmfit <- brm(
-#   thermometerDutch_1 ~ keyMotiveFulfilled * OutgroupInteraction + 
-#     (1 + keyMotiveFulfilled + OutgroupInteraction | PID),
-#   data = workerInteractionType,
+#   thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction +
+#     (1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID),
+#   data = workerWithinBetween,
 #   family = gaussian,
@@
 # 
-# # create parameters for prediction:
+# create parameters for prediction:
 # datNew = data.frame(
-#   OutgroupInteraction = rep(c("No", "Yes"), each = 101),
-#   keyMotiveFulfilled = rep(seq(-50, 50, 1), 2)
-# )
+#   keyMotiveFulfilled_cwc = rep(seq(
+#     round_any(min(
+#       workerWithinBetween$keyMotiveFulfilled_cwc
+#     ), 2, f = floor), round_any(max(
+#       workerWithinBetween$keyMotiveFulfilled_cwc
+#     ), 2, f = ceiling), 2
+#   ), 2)
+# ) %>%
+#   mutate(OutgroupInteraction = rep(c(1, 2), each = nrow(.)/2))
+# 
 # # Save predicted values and adjust names and labels
@@
 # fitavg$se <- (fitavg$Q97.5 - fitavg$pred) / 1.96
+# fitavg$OutgroupInteractionLab <-
+#   factor(
+#     x = fitavg$OutgroupInteraction,
+#     levels = sort(
+#       unique(fitavg$OutgroupInteraction)
+#     ),
+#     labels = c("No", "Yes")
+#   )
 # 
@@
 # ggplot(fitavg,
-#        aes(x = keyMotiveFulfilled,
+#        aes(x = keyMotiveFulfilled_cwc,
 #            y = pred,
-#            fill = OutgroupInteraction)) +
-#   scale_x_continuous(breaks = seq(-50, 50, 10)) +
+#            fill = OutgroupInteractionLab)) +
+#   scale_x_continuous(breaks = seq(
+#     round_any(min(
+#       workerWithinBetween$keyMotiveFulfilled_cwc
+#     ), 5, f = floor), round_any(max(
+#       workerWithinBetween$keyMotiveFulfilled_cwc
+#     ), 5, f = ceiling), 10
+#   )) +
 #   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
-#   geom_line(aes(linetype = OutgroupInteraction), size = 1) +
+#   geom_line(aes(linetype = OutgroupInteractionLab), size = 1) +
 #   geom_ribbon(aes(ymin = pred - se, ymax = pred + se), alpha = 0.2) +
@@
 # pst <- posterior_samples(brmfit, "b")
-# ggplot(workerInteractionType,
-#        aes(x = keyMotiveFulfilled, y = thermometerDutch_1)) +
+# ggplot(workerWithinBetween,
+#        aes(x = keyMotiveFulfilled_cwc, y = thermometerDutch_1)) +
 #   geom_point(shape = 4, alpha = .1) +
@@
 #     data = pst,
-#     aes(intercept = b_Intercept, slope = b_keyMotiveFulfilled),
+#     aes(intercept = b_Intercept, slope = b_keyMotiveFulfilled_cwc),
 #     alpha = .025,
@@
 
-##### random intercept with level ome predictors
+##### random intercept with level oe predictors
 
@@
 \begin{equation}
-(\#eq:AttitudeNeedSdtEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerInterceptAttNeedSdtEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}Autonomy_{ti} + \\
+                           &\ \beta_{3i}Competence_{ti} + \\
+                           &\ \beta_{4i}Relatedness_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20} \\
+                      &\ \beta_{3i} = \gamma_{30} \\
+                      &\ \beta_{4i} = \gamma_{40}
+  \end{split} 
 \end{equation}
@@
   lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1,
+    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
     random = ~ 1 | PID,
-    data = workerOutgroupInteraction,
+    data = workerOutWithinBetween,
     na.action = na.exclude
@@
   mdlWorkerOut$Att$lmerInterceptCoreSdt <- lmer(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 + (1 | PID),
-    data = workerOutgroupInteraction
+    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID),
+    data = workerOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(thermometerDutch_1 ~ Contact_dum + inNonDutch + (1|PID),data=workerOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  center = FALSE
+)
+
+# 95% CI
+mdlWorkerOut$Att$lmerInterceptCoreSdtCI <- 
+  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCoreSdt)
 
@@
   lme(
-    thermometerDutch_1 ~ competence_1 + autonomy_1 + relatedness_1,
+    thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
     random = ~ 1 | PID,
-    data = workerOutgroupInteraction,
+    data = workerOutWithinBetween,
     na.action = na.exclude
@@
   mdlWorkerOut$Att$lmerInterceptSdt <- lmer(
-    thermometerDutch_1 ~ competence_1 + autonomy_1 + relatedness_1 + (1 | PID),
-    data = workerOutgroupInteraction
+    thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID),
+    data = workerOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
+  center = FALSE
 )
@@
   lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreSdt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwInterceptCoreSdt <- 
-  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[1]))
-mdlWorkerOut$Att$varBtwPercInterceptCoreSdt <- 
-  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinInterceptCoreSdt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[2]))
-mdlWorkerOut$Att$varWithinPercInterceptCoreSdt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCore[2]))) * 100
 ```
@@
 \begin{equation}
-(\#eq:AttitudeNeedSdtRandEq)
-Attitude_{ti} = \\gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerSlopesAttNeedSdtEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}Autonomy_{ti} + \\
+                           &\ \beta_{3i}Competence_{ti} + \\
+                           &\ \beta_{4i}Relatedness_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                      &\ \beta_{3i} = \gamma_{30} + u_{3i} \\
+                      &\ \beta_{4i} = \gamma_{40} + u_{4i}
+  \end{split} 
 \end{equation}
@@
     thermometerDutch_1 ~
-      keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1,
-    random = ~ 1 + keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 | PID,
+       keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
+    random = ~ 1 +  keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID,
     control = lmeControl(opt = "optim"),
-    data = workerOutgroupInteraction,
+    data = workerOutWithinBetween,
     na.action = na.exclude
@@
     thermometerDutch_1 ~
-      keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 +
-      (1 + keymotive_fulfillemt_1 + competence_1 + autonomy_1 + relatedness_1 | PID),
-    data = workerOutgroupInteraction
+       keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc +
+      (1 +  keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID),
+    data = workerOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  center = FALSE
+)
+
+# 95% CI
+mdlWorkerOut$Att$lmerSlopesCoreSdtCI <- 
+  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreSdt)
 
 # Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeInterceptCoreSdt, 
+anova(mdlWorkerOut$Att$lmeInterceptSdt,
+      mdlWorkerOut$Att$lmeInterceptCoreSdt, 
       mdlWorkerOut$Att$lmeSlopesCoreSdt) %>%
@@
 
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwSlopesCoreSdt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]))
-mdlWorkerOut$Att$varBtwPercSlopesCoreSdt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinSlopesCoreSdt <-
-  1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]))
-mdlWorkerOut$Att$varWithinPercSlopesCoreSdt <-
-  (1 - (as.numeric(mdlWorkerOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlWorkerOut$Att$varInterceptCoreSdt[2]))) * 100
-
 # Assumption Checks:
@@
 mdlWorkerOut$Att$predSlopesCoreSdt <- 
-  workerOutgroupInteraction %>%
+  workerOutWithinBetween %>%
   filter(!is.na(autonomy_1)) %>%
@@
   mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreSdt,
-                           workerOutgroupInteraction %>% filter(!is.na(autonomy_1)),
+                           workerOutWithinBetween %>% filter(!is.na(autonomy_1)),
                            re.form = NA
@@
 
-<i class="fas fa-exclamation-triangle"></i> Still in 'scr/studentDescriptive.R'. Needs to be merged with this document.
+### Participants
+
+```{r studentSampleInfo}
+# summarize participant characteristics
+studentSampleInfo <- 
+  dtStudents$full %>%
+  mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>%
+  group_by(PID) %>%
+  summarise(
+    dailiesN = n(), 
+    morningN = sum(periodMA=="morning"),
+    afternoonN = sum(periodMA=="afternoon"),
+    age = age,
+    gender = gender,
+    nationality = nationality
+  ) %>%
+  distinct
+
+# look at frequencies of characteristics 
+studentSampleInfo %>% 
+  ungroup %>%
+  select(
+    "Number of Measurements" = dailiesN,
+    Age = age,
+    Gender = gender,
+    Nationality = nationality
+  ) %>%
+  mutate(
+    Nationality = as.character(Nationality)
+  ) %>%
+  tbl_summary(.,
+              sort = list(everything() ~ "frequency"))
+```
+
+### Interactions
+
+```{r studentInteractionInfo}
+# duration of survey should include median and MAD
+studentInteractions <- dtStudents$full %>%
+  dplyr::select(created.daily, ended.daily) %>%
+  mutate_all(ymd_hms) %>%
+  mutate(duration = as.numeric(ended.daily-created.daily)) %>%
+  select(duration)
+
+studentInteractions %>%
+  as.data.frame %>%
+  psych::describe(., trim = .2) %>%
+  as.data.frame %>%
+  mutate(vars = c("Duration [in seconds]"), # rownames(.),
+         na = nrow(dtStudents$full)-n,
+         win.mean = sapply(studentInteractions,psych::winsor.mean,simplify=T),
+         win.sd = sapply(studentInteractions,psych::winsor.sd,simplify=T)) %>%
+  dplyr::select(characteristic = vars, n, na, 
+                mean, `mean win` = win.mean, `mean trim` = trimmed, median,
+                sd, `sd win` = win.sd, MAD = mad, min, max,
+                skew, kurtosis) %>%
+  kbl(., 
+      #label = "",
+      caption = "Study 2: Duration of Measurement in Seconds",
+      format = "html", 
+      #linesep = "",
+      #booktabs = T,
+      row.names = F,
+      digits = 2,
+      align = c('l', rep('c', ncol(.)-1)))  %>%
+  add_header_above(., c(" " = 3,"Centrality" = 4, "Dispersion" = 5, "Distribution" = 2)) %>%
+  footnote(general = "'na' indicates the number of measurements for which measurement duration is unknown.") %>%
+  kable_classic(full_width = F, 
+                lightable_options = "hover", 
+                html_font = "Cambria")
+
+studentInteractionType %>%
+  select(OutgroupInteraction,
+         NonOutgroupInteraction) %>%
+  tbl_summary(.,
+              sort = list(everything() ~ "frequency"))
+```
+
+### Variable distributions
+
+```{r studentVarDescr}
+# calculate correlations and descriptives
+studentMlCor <-
+  MlCorMat(
+    data = studentInteractionType,
+    id = "PID",
+    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "quality_overall", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+  )
+
+studentMlCor %>%
+  kable(
+    .,
+    caption = "Student: Multilevel Core Variable Descriptives",
+    format = "html",
+    #booktabs = TRUE,
+    linesep = linesep(c(ncol(.))),
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  pack_rows("Correlations", 1, ncol(studentMlCor)) %>%
+  pack_rows("Descriptives", ncol(studentMlCor)+1, nrow(studentMlCor)) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  kable_classic(full_width = F, 
+                lightable_options = "hover", 
+                html_font = "Cambria")
+
+```
+
+```{r studentOutVarDescr}
+# calculate correlations and descriptives
+studentOutMlCor <-
+  MlCorMat(
+    data = studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "quality_overall", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+  )
+
+studentOutMlCor %>%
+  kable(
+    .,
+    caption = "Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
+    format = "html",
+    #booktabs = TRUE,
+    linesep = linesep(c(ncol(.))),
+    align = c("l", rep("c", ncol(.) - 1))
+  ) %>%
+  pack_rows("Correlations", 1, ncol(studentMlCor)) %>%
+  pack_rows("Descriptives", ncol(studentMlCor)+1, nrow(studentMlCor)) %>%
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  kable_classic(full_width = F, 
+                lightable_options = "hover", 
+                html_font = "Cambria")
+
+```
 
@@
 (\#eq:studentIntTypeQual)
-\mu_{i,0utgroupInteraction} > \mu_{i,IngroupInteraction}  \\
-Attitude = OutgroupInteraction \times NonOutgroupInteraction
+Attitude = OutgroupInteraction + NonOutgroupInteraction
 \end{equation}
@@
 ```{r studentInteractionTypePlt, fig.height=12}
+# between participants interaction type
+studentAttInteractionType <- studentInteractionType %>%
+  select(
+    PID,
+    OutgroupInteraction,
+    NonOutgroupInteraction,
+    Attitude = AttitudesDutch
+  ) %>%
+  mutate(InteractionType = paste(
+    ifelse(OutgroupInteraction == "Yes", "Out", ifelse(OutgroupInteraction == "No", "NoOut", NA)),
+    ifelse(NonOutgroupInteraction == "Yes", "In", ifelse(NonOutgroupInteraction == "No", "NoIn", NA)),
+    sep = ", "
+  ))
+
+# violin plot of attitudes by interaction type group
+ggplot(studentAttInteractionType, aes(y=Attitude, x=OutgroupInteraction, group = interaction(OutgroupInteraction, NonOutgroupInteraction), fill=NonOutgroupInteraction))+
+  geom_violin(trim = T, width=.8, position = position_dodge(0.8)) +
+  geom_boxplot(width=0.04,
+               position = position_dodge(.8),
+               outlier.colour = NULL, 
+               outlier.shape = NA, 
+               notch=F, fill="black", 
+               lwd=1, color="black") + 
+  # geom_jitter(width = 0.15,
+  #            shape=18,
+  #            alpha=.2, size=1) +
+  stat_summary(fun.y=mean, 
+               geom="point", 
+               shape=16, 
+               size=1, 
+               position = position_dodge(0.8),
+               colour="white") +
+  #stat_summary(fun.data="mean_sdl",  
+  #             fun.args = list(mult=1), 
+  #             geom="pointrange", 
+  #             color = "red", 
+  #             width=.2)+
+  stat_summary(geom = "crossbar", 
+               width=0.04, 
+               fatten=0, 
+               position = position_dodge(0.8),
+               color="white", 
+               fun.data = function(x){ return(c(y=median(x), 
+                                                ymin=median(x), 
+                                                ymax=median(x))) })+
+  ylab("Outgroup Attitudes")+
+  xlab("Outgroup Interaction") +
+  ggtitle("Violin Plot:\nOutgroup Attitudes by Interaction Type")+
+  scale_y_continuous(
+    limits = c(0, 100),
+    breaks = c(0, 15, 30, 40, 50, 60, 70, 85, 100),
+    labels = c(
+      "Very cold or unfavorable feelings 0°",
+      "Quite cold and unfavorable feelings 15°",
+      "Fairly cold and unfavorable feelings 30°",
+      "A bit cold and unfavorable feelings 40°",
+      "No feeling at all 50°",
+      "A bit warm and favorable feelings 60°",
+      "Fairly warm and favorable feelings 70° ",
+      "Quite warm and favorable feelings 85° ",
+      "Very warm and favorable feelings 100° "
+    )
+  ) +
+  #coord_flip()+
+  scale_fill_brewer(palette = "Pastel2", name = "Non-Outgroup Interaction")+
+  theme_Publication()+
+  theme(strip.background =element_rect(fill="black", color="black"),
+        strip.text = element_text(colour = 'white', face="bold"))#,
+        #panel.border = element_rect(color="grey"),
+        #legend.position="none")
+
 # between participants interaction type
@@
 
-# plot bar chart
-ggplot(
+# plot bar chart (alternative with less information about actual data)
+studentAttInteractionTypeBar <- ggplot(
   studentContactType,
@@
 
-#### ML Regression with interaction term
+### Interaction Frequency and Interaction Quality
+
+In a final step we check whether the effect outgroup interactions, in part, depends on the quality during the interactions.
+Because we can only assess interaction quality when there is an interaction, it is difficult to assess this with the interaction dummy as a within person predictor.
+Instead, we will use an aggregate measure of interaction quality and average interaction quality to consider the two predictors jointly.
+
+\begin{equation}
+(\#eq:studentFreqQual)
+Attitude = ContactFreq \times AverageContactQual
+\end{equation}
+
+```{r studentFreqQualCor}
+# correlation panel
+pairs.panels.new(
+  studentContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
+    "Sum:\nNumber of Outgroup Contacts (NL)",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+
+# correlation panel with interaction sums winsorized
+pairs.panels.new(
+  studentContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  labels = c(
+    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
+    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
+    "Mean:\nInteraction Quality",
+    "Mean:\nOutgroup Attitudes (NL)"
+  )
+)
+```
+
+Within the data, we find no significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
+Thus, within our data participants with a higher quality outgroup interactions did not hold more positive attitudes towards that group.
+However, the frequency of intergroup interactions had a meaningful correlation with both the average interaction quality or average outgroup attitudes.
+
+```{r studentModelOlsAttFreqQual}
+# center remaining 
+studentContactFreq <-
+  studentContactFreq %>%
+  mutate(
+    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
+    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
+    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
+    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
+  )
+
+# regression
+mdlStudent$lmAttFreqQualX <-
+  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = studentContactFreq)
+
+summ(
+  mdlStudent$lmAttFreqQualX,
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# Partial Eta Squared
+mdlStudent$lmAttFreqQualXEta <-
+  effectsize::eta_squared(mdlStudent$lmAttFreqQualX, partial = TRUE)
+
+# Interaction Plots
+interactions::interact_plot(
+  mdlStudent$lmAttFreqQualX,
+  pred = SumContactNL_c,
+  modx = AvQuality_c,
+  interval = TRUE,
+  partial.residuals = TRUE
+)
+
+interactions::johnson_neyman(mdlStudent$lmAttFreqQualX,
+                             pred = SumContactNL_c,
+                             modx = AvQuality_c,
+                             alpha = .05)
+```
+
+We find that in our student sample there is only a relationship between the number of outgroup contacts but no significant effect of average perceived contact quality.
+Nor do we find that in this sample the impact of the number of interactions is moderated by the average contact quality.
+This is not entirely consistent with the sojourner sample, where average contact quality did have a meaningful effect on outgroup attitudes.
+This effect is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.
+
+### Multilevel Regression
 
@@
 (\#eq:studentEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
+  \end{split} 
 \end{equation}
@@
 # summary(mdlStudent$lmerAttNull) #or with the lme function
-summ(mdlStudent$lmerAttNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=dtStudent$full),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
+summ(mdlStudent$lmerAttNull, digits = 3)
 
@@
 (\#eq:StudentInteractionTypeModel)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20}
+  \end{split} 
 \end{equation}
@@
 summ(
-  lmer(
+  mdlStudent$lmerInterceptAttType <- lmer(
     AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
@@
 
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+# 95%CI
+mdlStudent$lmerInterceptAttTypeCI <- 
+  confint(method = "Wald", mdlStudent$lmerInterceptAttType)
 
@@
 \begin{equation}
-(\#eq:RandSlopesEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}OutgroupInteraction_{ti} + \gamma_{10}NonOutgroupInteraction_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentRandomSlopes)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i}
+  \end{split} 
 \end{equation}
@@
   confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  digits = 3
+)
+
+# 95%CI
+mdlStudent$lmerSlopesAttTypeCI <- 
+  confint(method = "Wald", mdlStudent$lmerSlopesAttType)
 
 # Compare new model to previous step
-anova(mdlStudent$lmeInterceptAttType, 
+anova(mdlStudent$lmeAttNull,
+      mdlStudent$lmeInterceptAttType, 
       mdlStudent$lmeSlopesAttType) %>%
@@
 
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudent$varBtwSlopesAttType <- 
-  1 - (as.numeric(mdlStudent$varSlopesAttType[1]) / as.numeric(mdlStudent$varInterceptAttType[1]))
-mdlStudent$varBtwPercSlopesAttType <- 
-  (1 - (as.numeric(mdlStudent$varSlopesAttType[1]) / as.numeric(mdlStudent$varInterceptAttType[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudent$varWithinSlopesAttType <- 
-  1 - (as.numeric(mdlStudent$varSlopesAttType[2]) / as.numeric(mdlStudent$varInterceptAttType[2]))
-mdlStudent$varWithinPercSlopesAttType <- 
-  (1 - (as.numeric(mdlStudent$varSlopesAttType[2]) / as.numeric(mdlStudent$varInterceptAttType[2]))) * 100
-
 # Assumption Checks:
@@
 
-### Interaction Frequency and Interaction Quality
-
-In a final step we check whether the effect outgroup interactions, in part, depends on the quality during the interactions.
-Because we can only assess interaction quality when there is an interaction, it is difficult to assess this with the interaction dummy as a within person predictor.
-Instead, we will use an aggregate measure of interaction quality and average interaction quality to consider the two predictors jointly.
-
-\begin{equation}
-(\#eq:FreqQual)
-Attitude = ContactFreq \times AverageContactQual
-\end{equation}
-
-```{r studentFreqQualCor}
-# correlation panel
-pairs.panels.new(
-  studentContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
-    "Sum:\nNumber of Outgroup Contacts (NL)",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-
-# correlation panel with interaction sums winsorized
-pairs.panels.new(
-  studentContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
-    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-```
-
-Within the data, we find no significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
-Thus, within our data participants with a higher quality outgroup interactions did not hold more positive attitudes towards that group.
-However, the frequency of intergroup interactions had a meaningful correlation with both the average interaction quality or average outgroup attitudes.
-
-```{r studentModelOlsAttFreqQual}
-# regression
-mdlStudent$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL * AvQuality, data = studentContactFreq)
-# summary(mdlStudent$lmAttFreqQualX)
-
-summ(
-  mdlStudent$lmAttFreqQualX,
-  confint = TRUE,
-  digits = 3,
-  center = TRUE
-)
-
-interactions::interact_plot(
-  mdlStudent$lmAttFreqQualX,
-  pred = SumContactNL,
-  modx = AvQuality,
-  interval = TRUE,
-  partial.residuals = TRUE
-)
-
-interactions::johnson_neyman(mdlStudent$lmAttFreqQualX,
-                             pred = SumContactNL,
-                             modx = AvQuality,
-                             alpha = .05)
-```
-
-We find that in our student sample there is only a relationship between the number of outgroup contacts but no significant effect of average perceived contact quality.
-Nor do we find that in this sample the impact of the number of interactions is moderated by the average contact quality.
-This is not entirely consistent with the sojourner sample, where average contact quality did have a meaningful effect on outgroup attitudes.
-This effect is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.
-
 ## Need Fulfillment
@@
 
-<i class="fas fa-question-circle"></i> _Note to self:_ For completeness, we should probably check this against an empty model without random intercept.
-
 \begin{equation}
-(\#eq:studentOutEmptyModel)
-Attitude_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentOutAttEmptyModel)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} +  e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
+  \end{split} 
 \end{equation}
@@
              data = studentOutgroupInteraction) # use optim if it does not converge
+
 mdlStudentOut$Att$lmeNull <-
@@
 summ(mdlStudentOut$Att$lmerNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
 
@@
 
-We thus add the core interaction need fulfillment to the multilevel random intercept model.
+We then add the core interaction need fulfillment to the multilevel random intercept model.
 
 \begin{equation}
-(\#eq:AttitudeNeedEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentOutInterceptAttNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10}
+  \end{split} 
 \end{equation}
@@
   lme(
-    AttitudesDutch ~ KeyNeedFullfillment,
+    AttitudesDutch ~ KeyNeedFullfillment_cwc,
     random = ~ 1 | PID,
-    data = studentOutgroupInteraction
+    data = studentOutWithinBetween
   )
@@
 summ(
-  lmer(AttitudesDutch ~ KeyNeedFullfillment + (1 | PID), 
-       data = studentOutgroupInteraction),
+  lmer(AttitudesDutch ~ KeyNeedFullfillment_cwc + (1 | PID), 
+       data = studentOutWithinBetween),
   confint = TRUE,
@@
 
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+# 95%CI
+mdlStudentOut$Att$lmerInterceptCoreCI <- 
+  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCore)
 
@@
 \begin{equation}
-(\#eq:AttitudeNeedRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentOutSlopeAttNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i}
+  \end{split} 
 \end{equation}
@@
     AttitudesDutch ~
-      KeyNeedFullfillment,
-    random = ~ 1 + KeyNeedFullfillment | PID,
+      KeyNeedFullfillment_cwc,
+    random = ~ 1 + KeyNeedFullfillment_cwc | PID,
     control = lmeControl(opt = "optim"),
-    data = studentOutgroupInteraction
+    data = studentOutWithinBetween
   )
@@
     AttitudesDutch ~
-      KeyNeedFullfillment +
-      (1 + KeyNeedFullfillment | PID),
-    data = studentOutgroupInteraction
+      KeyNeedFullfillment_cwc +
+      (1 + KeyNeedFullfillment_cwc | PID),
+    data = studentOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  center = FALSE
+)
+
+# all variables standardized within PPT
+summ(
+  mdlStudentOut$Att$lmerSlopesCoreZ <- lmer(
+    AttitudesDutch_zwc ~
+      KeyNeedFullfillment_zwc +
+      (1 + KeyNeedFullfillment_zwc | PID),
+    data = studentOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# standardized coefficients
+stdCoef.merMod(mdlStudentOut$Att$lmerSlopesCore)
+
+# 95%CIs
+mdlStudentOut$Att$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCore)
+
+# Attempts at R^2
+r2mlm::r2mlm(mdlStudentOut$Att$lmerSlopesCore, bargraph = TRUE)
+mitml::multilevelR2(mdlStudentOut$Att$lmerSlopesCore)
+performance::r2(mdlStudentOut$Att$lmerSlopesCore)
+performance::model_performance(mdlStudentOut$Att$lmerSlopesCore)
+performance::compare_performance(mdlStudentOut$Att$lmerNull, 
+                                 mdlStudentOut$Att$lmerInterceptCore, 
+                                 mdlStudentOut$Att$lmerSlopesCore)
 
 # Compare new model to previous step
-anova(mdlStudentOut$Att$lmeInterceptCore, 
+anova(mdlStudentOut$Att$lmeNull, 
+      mdlStudentOut$Att$lmeInterceptCore, 
       mdlStudentOut$Att$lmeSlopesCore)  %>%
@@
 
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Att$varBtwSlopesCore <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))
-mdlStudentOut$Att$varBtwPercSlopesCore <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Att$varWithinSlopesCore <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))
-mdlStudentOut$Att$varWithinPercSlopesCore <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCore[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))) * 100
-
 # Assumption Checks:
@@
 mdlStudentOut$Att$predSlopesCore <- 
-  studentOutgroupInteraction %>%
+  studentOutWithinBetween %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCore,
-                           studentOutgroupInteraction,
+                           studentOutWithinBetween,
                            re.form = NA
@@
 
-<div class="alert alert-warning alert-dismissible fade in" role="alert">
-  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
-  <i class="fas fa-exclamation-triangle"></i> <b>Check needed: </b><br/>
-  Something is with the variances explained (between = `r format(round(mdlStudentOut$Att$varBtwPercSlopesCore, 2),nsmall=2)`%, within = `r format(round(mdlStudentOut$Att$varWithinPercSlopesCore, 2),nsmall=2)`%).
-This is when comparing the random intercepts to the random slopes model.
-Check with materials from Laura!!
-</div>
-
 ### Need fulfillment and Interaction Quality
@@
 \begin{equation}
-(\#eq:studentOutQualEmptyModel)
-InteractionQuality_{ti} = \gamma_{00} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentOutQltEmptyModel)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ InteractionQuality_{ti} =  &\ \beta_{0i} +  e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
+  \end{split} 
 \end{equation}
@@
   lme4::lmer(quality_overall ~ 1 + (1 | PID), 
-             data = studentOutgroupInteraction) # use optim if it does not converge
+             data = studentOutWithinBetween) # use optim if it does not converge
 mdlStudentOut$Qlt$lmeNull <-
@@
     random = ~ 1 | PID,
-    data = studentOutgroupInteraction,
+    data = studentOutWithinBetween,
     control = list(opt = "nlmimb")
@@
 summ(mdlStudentOut$Qlt$lmerNull, digits = 3, center = TRUE)
-
-# generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch~1 + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000,
-#                  parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-Null-CI.csv")
 
@@
 \begin{equation}
-(\#eq:QualityNeedEq)
-InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentOutInterceptQltNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ InteractionQuality_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10}
+  \end{split} 
 \end{equation}
@@
   lme(
-    quality_overall ~ KeyNeedFullfillment,
+    quality_overall ~ KeyNeedFullfillment_cwc,
     random = ~ 1 | PID,
-    data = studentOutgroupInteraction
+    data = studentOutWithinBetween
   )
@@
 summ(
-  mdlStudentOut$Qlt$lmerInterceptCore <- lmer(quality_overall ~ KeyNeedFullfillment + (1 | PID), 
-       data = studentOutgroupInteraction),
+  mdlStudentOut$Qlt$lmerInterceptCore <- 
+    lmer(quality_overall ~ KeyNeedFullfillment_cwc + (1 | PID), 
+       data = studentOutWithinBetween),
   confint = TRUE,
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(quality_overall ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlStudentOut$Qlt$lmerInterceptCoreCI <- 
+  confint(method = "Wald", mdlStudentOut$Qlt$lmerInterceptCore)
 
@@
 \begin{equation}
-(\#eq:QualityNeedRandEq)
-InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentOutSlopeQltNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ InteractionQuality_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i}
+  \end{split} 
 \end{equation}
@@
     quality_overall ~
-      KeyNeedFullfillment,
-    random = ~ 1 + KeyNeedFullfillment | PID,
+      KeyNeedFullfillment_cwc,
+    random = ~ 1 + KeyNeedFullfillment_cwc | PID,
     control = lmeControl(opt = "optim"),
-    data = studentOutgroupInteraction
+    data = studentOutWithinBetween
   )
@@
       quality_overall ~
-        KeyNeedFullfillment +
-        (1 + KeyNeedFullfillment | PID),
-      data = studentOutgroupInteraction
+        KeyNeedFullfillment_cwc +
+        (1 + KeyNeedFullfillment_cwc | PID),
+      data = studentOutWithinBetween
     ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(mdlStudentOut$Qlt$lmerSlopesCore,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlStudentOut$Qlt$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlStudentOut$Qlt$lmerSlopesCore)
 
 # Compare new model to previous step
-anova(mdlStudentOut$Qlt$lmeInterceptCore, 
+anova(mdlStudentOut$Qlt$lmeNull, 
+      mdlStudentOut$Qlt$lmeInterceptCore, 
       mdlStudentOut$Qlt$lmeSlopesCore) %>%
@@
 
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Qlt$varBtwSlopesCore <-
-  1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[1]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[1]))
-mdlStudentOut$Qlt$varBtwPercSlopesCore <-
-  (1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[1]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Qlt$varWithinSlopesCore <-
-  1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[2]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]))
-mdlStudentOut$Qlt$varWithinPercSlopesCore <-
-  (1 - (as.numeric(mdlStudentOut$Qlt$varSlopesCore[2]) / as.numeric(mdlStudentOut$Qlt$varInterceptCore[2]))) * 100
-
 # Assumption Checks:
@@
 mdlStudentOut$Qlt$predSlopesCore <- 
-  studentOutgroupInteraction %>%
+  studentOutWithinBetween %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlStudentOut$Qlt$lmeSlopesCore,
-                           studentOutgroupInteraction,
+                           studentOutWithinBetween,
                            re.form = NA
@@
 \begin{equation}
-(\#eq:AttitudeQualityNeedEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentOutInterceptAttQltNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20}
+  \end{split} 
 \end{equation}
@@
   lme(
-    AttitudesDutch ~ KeyNeedFullfillment + quality_overall,
+    AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc,
     random = ~ 1 | PID,
-    data = studentOutgroupInteraction
+    data = studentOutWithinBetween
   )
@@
   lmer(
-    AttitudesDutch ~ KeyNeedFullfillment + quality_overall + (1 | PID),
-    data = studentOutgroupInteraction
+    AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc + (1 | PID),
+    data = studentOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlStudentOut$Att$lmerInterceptCoreQltCI <- 
+  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCoreQlt)
 
@@
 \begin{equation}
-(\#eq:AttitudeQualityNeedRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:workerOutSlopeAttQltNeedEq)
+(\#eq:WorkerRandomSlopes)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i}
+  \end{split} 
 \end{equation}
@@
     AttitudesDutch ~
-      KeyNeedFullfillment + quality_overall,
-    random = ~ 1 + KeyNeedFullfillment + quality_overall | PID,
+      KeyNeedFullfillment_cwc + quality_overall_cwc,
+    random = ~ 1 + KeyNeedFullfillment_cwc + quality_overall_cwc | PID,
     control = lmeControl(opt = "optim"),
-    data = studentOutgroupInteraction
+    data = studentOutWithinBetween
   )
@@
     AttitudesDutch ~
-      KeyNeedFullfillment + quality_overall +
-      (1 + KeyNeedFullfillment + quality_overall | PID),
-    data = studentOutgroupInteraction
+      KeyNeedFullfillment_cwc + quality_overall_cwc +
+      (1 + KeyNeedFullfillment_cwc + quality_overall_cwc | PID),
+    data = studentOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlStudentOut$Att$lmerSlopesCoreQltCI <- 
+  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreQlt)
 
@@
 
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Att$varBtwSlopesCoreQlt <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[1]))
-mdlStudentOut$Att$varBtwPercSlopesCoreQlt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Att$varWithinSlopesCoreQlt <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[2]))
-mdlStudentOut$Att$varWithinPercSlopesCoreQlt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreQlt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreQlt[2]))) * 100
-
 # Assumption Checks:
@@
 mdlStudentOut$Att$predSlopesCoreQlt <- 
-  studentOutgroupInteraction %>%
+  studentOutWithinBetween %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreQlt,
-                           studentOutgroupInteraction,
+                           studentOutWithinBetween,
                            re.form = NA
@@
 \begin{equation}
-(\#eq:AttitudeNeedInteractionEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentInterceptAttIntNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{3i}KeyNeedFulfillXOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20} \\
+                      &\ \beta_{3i} = \gamma_{30}
+  \end{split} 
 \end{equation}
@@
   lme(
-    AttitudesDutch ~ KeyNeedFullfillment * OutgroupInteraction,
+    AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction,
     random =  ~ 1 | PID,
-    data = studentInteractionType
+    data = studentWithinBetween
   )
@@
   mdlStudent$lmerInterceptAttCoreInt <- lmer(
-    AttitudesDutch ~ KeyNeedFullfillment * OutgroupInteraction + (1 | PID),
-    data = studentInteractionType
+    AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction + (1 | PID),
+    data = studentWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentInteractionType),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlStudent$lmerInterceptAttCoreIntCI <- 
+  confint(method = "Wald", mdlStudent$lmerInterceptAttCoreInt)
 
@@
 \begin{equation}
-(\#eq:AttitudeNeedInteractionRandEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}OutgroupInteraction_{ti} + \gamma_{30}KeyNeedFulfillXOutgroupInteraction_{ti}  + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentSlopesAttIntNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{3i}KeyNeedFulfillXOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                      &\ \beta_{3i} = \gamma_{30} + u_{3i}
+  \end{split} 
 \end{equation}
@@
   AttitudesDutch ~
-    KeyNeedFullfillment * OutgroupInteraction,
-  random = ~ 1 + KeyNeedFullfillment + OutgroupInteraction | PID,
+    KeyNeedFullfillment_cwc * OutgroupInteraction,
+  random = ~ 1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID,
   control = lmeControl(opt = "optim"),
-  data = studentInteractionType
+  data = studentWithinBetween
 )
@@
     AttitudesDutch ~
-      KeyNeedFullfillment * OutgroupInteraction +
-      (1 + KeyNeedFullfillment + OutgroupInteraction | PID),
-    data = studentInteractionType
+      KeyNeedFullfillment_cwc * OutgroupInteraction +
+      (1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID),
+    data = studentWithinBetween
   ), 
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlStudent$lmerSlopesAttCoreIntCI <- 
+  confint(method = "Wald", mdlStudent$lmerSlopesAttCoreInt)
 
@@
 
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudent$varBtwSlopesAttCoreInt <- 
-  1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[1]) / as.numeric(mdlStudent$varInterceptAttCoreInt[1]))
-mdlStudent$varBtwPercSlopesAttCoreInt <- 
-  (1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[1]) / as.numeric(mdlStudent$varInterceptAttCoreInt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudent$varWithinSlopesAttCoreInt <- 
-  1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[2]) / as.numeric(mdlStudent$varInterceptAttCoreInt[2]))
-mdlStudent$varWithinPercSlopesAttCoreInt <- 
-  (1 - (as.numeric(mdlStudent$varSlopesAttCoreInt[2]) / as.numeric(mdlStudent$varInterceptAttCoreInt[2]))) * 100
-
 # Assumption Checks:
@@
 mdlStudent$predSlopesAttCoreInt <- 
-  studentInteractionType %>%
+  studentWithinBetween %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlStudent$lmeSlopesAttCoreInt,
-                           studentInteractionType,
+                           studentWithinBetween,
                            re.form = NA
@@
         legend.key.size = unit(1, "cm"))
+
 ## With ML structure
@@
 datNew = data.frame(
-  OutgroupInteraction = factor(rep(c("No", "Yes"), each = 21)),
-  KeyNeedFullfillment = rep(seq(0, 100, 5), 2),
+  KeyNeedFullfillment_cwc = rep(seq(
+    round_any(min(
+      studentWithinBetween$KeyNeedFullfillment_cwc
+    ), 5, f = floor), round_any(max(
+      studentWithinBetween$KeyNeedFullfillment_cwc
+    ), 5, f = ceiling), 5
+  ), 2),
   PID = 0
-)
+) %>%
+  mutate(OutgroupInteraction = rep(c(1, 2), each = nrow(.)/2)) %>%
+  select(PID, OutgroupInteraction, KeyNeedFullfillment_cwc)
 
@@
 rm(datNew, PI)
+mdlStudent$predInterceptAttCoreIntX$OutgroupInteractionLab <-
+  factor(
+    x = mdlStudent$predInterceptAttCoreIntX$OutgroupInteraction,
+    levels = sort(
+      unique(mdlStudent$predInterceptAttCoreIntX$OutgroupInteraction)
+    ),
+    labels = c("No", "Yes")
+  )
 
@@
   mdlStudent$predInterceptAttCoreIntX,
-  aes(x = KeyNeedFullfillment,
+  aes(x = KeyNeedFullfillment_cwc,
       y = fit,
-      fill = OutgroupInteraction)
+      fill = OutgroupInteractionLab)
 )+
   #geom_point() +
-  geom_line(aes(linetype = as.factor(OutgroupInteraction)), size = 1) +
+  geom_line(aes(linetype = OutgroupInteractionLab), size = 1) +
   #facet_wrap(~PID, ncol = 6)+
@@
               alpha = 0.3) +
-  scale_x_continuous(breaks = seq(0, 100, 10)) +
+  scale_x_continuous(breaks = seq(
+    round_any(min(
+      studentWithinBetween$KeyNeedFullfillment_cwc
+    ), 5, f = floor), round_any(max(
+      studentWithinBetween$KeyNeedFullfillment_cwc
+    ), 5, f = ceiling), 10
+  )) +
   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
@@
 # brmfit <- brm(
-#   AttitudesDutch ~ KeyNeedFullfillment * OutgroupInteraction + 
-#     (1 + KeyNeedFullfillment + OutgroupInteraction | PID),
-#   data = studentInteractionType,
+#   AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction +
+#     (1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID),
+#   data = studentWithinBetween,
 #   family = gaussian,
@@
 # datNew = data.frame(
-#   OutgroupInteraction = rep(c("No", "Yes"), each = 101),
-#   KeyNeedFullfillment = rep(seq(0, 100, 1), 2)
-# )
+#   KeyNeedFullfillment_cwc = rep(seq(
+#     round_any(min(
+#       studentWithinBetween$KeyNeedFullfillment_cwc
+#     ), 2, f = floor), round_any(max(
+#       studentWithinBetween$KeyNeedFullfillment_cwc
+#     ), 2, f = ceiling), 2
+#   ), 2)
+# ) %>%
+#   mutate(OutgroupInteraction = rep(c(1, 2), each = nrow(.)/2))
+# 
 # # Save predicted values and adjust names and labels
@@
 # ggplot(fitavg,
-#        aes(x = KeyNeedFullfillment,
+#        aes(x = KeyNeedFullfillment_cwc,
 #            y = pred,
-#            fill = OutgroupInteraction)) +
-#   scale_x_continuous(breaks = seq(0, 100, 10)) +
+#            fill = OutgroupInteractionLab)) +
+#   scale_x_continuous(breaks = seq(
+#     round_any(min(
+#       studentWithinBetween$KeyNeedFullfillment_cwc
+#     ), 5, f = floor), round_any(max(
+#       studentWithinBetween$KeyNeedFullfillment_cwc
+#     ), 5, f = ceiling), 10
+#   )) +
 #   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
-#   geom_line(aes(linetype = OutgroupInteraction), size = 1) +
+#   geom_line(aes(linetype = OutgroupInteractionLab), size = 1) +
 #   geom_ribbon(aes(ymin = pred - se, ymax = pred + se), alpha = 0.2) +
@@
 # 
-# # plot all overlayed posteriors:
-# pst <- posterior_samples(brmfit, "b")
-# ggplot(studentInteractionType,
-#        aes(x = KeyNeedFullfillment, y = AttitudesDutch)) +
-#   geom_point(shape = 4, alpha = .1) +
-#   geom_tile() +
-#   geom_abline(
-#     data = pst,
-#     aes(intercept = b_Intercept, slope = b_KeyNeedFullfillment),
-#     alpha = .025,
-#     size = .4
-#   ) +
-#   labs(title = "slope Posteriors",
-#        x = "Fulfillment Core Need",
-#        y = "Outgroup Attitudes (NL)") +
-#   theme_Publication()
-# rm(datNew, brmfit, fitavg, pst)
+# # # plot all overlayed posteriors:
+# # pst <- posterior_samples(brmfit, "b")
+# # ggplot(studentWithinBetween,
+# #        aes(x = KeyNeedFullfillment_cwc, y = AttitudesDutch)) +
+# #   geom_point(shape = 4, alpha = .1) +
+# #   geom_tile() +
+# #   geom_abline(
+# #     data = pst,
+# #     aes(intercept = b_Intercept, slope = b_KeyNeedFullfillment_cwc),
+# #     alpha = .025,
+# #     size = .4
+# #   ) +
+# #   labs(title = "slope Posteriors",
+# #        x = "Fulfillment Core Need",
+# #        y = "Outgroup Attitudes (NL)") +
+# #   theme_Publication()
+# # rm(datNew, brmfit, fitavg, pst)
 ```
@@
 
-##### random intercept with level ome predictors
+##### random intercept with level one predictors
 
@@
 \begin{equation}
-(\#eq:AttitudeNeedSdtEq)
-Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + e_{ti} \\
-\textrm{with}\ u_{0i} \sim \mathcal{N}(0,\tau_{00}^2)\ \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentInterceptAttNeedSdtEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}Autonomy_{ti} + \\
+                           &\ \beta_{3i}Competence_{ti} + \\
+                           &\ \beta_{4i}Relatedness_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20} \\
+                      &\ \beta_{3i} = \gamma_{30} \\
+                      &\ \beta_{4i} = \gamma_{40}
+  \end{split} 
 \end{equation}
@@
   lme(
-    AttitudesDutch ~ KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction,
+    AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
     random = ~ 1 | PID,
-    data = studentOutgroupInteraction,
+    data = studentOutWithinBetween,
     na.action = na.exclude
@@
   mdlStudentOut$Att$lmerInterceptCoreSdt <- lmer(
-    AttitudesDutch ~ KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction + (1 | PID),
-    data = studentOutgroupInteraction
+    AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
+    data = studentOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(lmer(AttitudesDutch ~ Contact_dum + inNonDutch + (1|PID),data=studentOutgroupInteraction),
-#                  method="boot",nsim=1000, parallel = "multicore",
-#                  ncpus = 4, seed = 42),
-#          "output/tables/ML-Inter-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlStudentOut$Att$lmerInterceptCoreSdtCI <- 
+  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCoreSdt)
 
@@
   lme(
-    AttitudesDutch ~ Competence + Autonomy + RelatednessInteraction,
+    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc,
     random = ~ 1 | PID,
-    data = studentOutgroupInteraction,
+    data = studentOutWithinBetween,
     na.action = na.exclude
@@
   mdlStudentOut$Att$lmerInterceptSdt <- lmer(
-    AttitudesDutch ~ Competence + Autonomy + RelatednessInteraction + (1 | PID),
-    data = studentOutgroupInteraction
+    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
+    data = studentOutWithinBetween
   ),
@@
   lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreSdt)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Att$varBtwInterceptCoreSdt <- 
-  1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))
-mdlStudentOut$Att$varBtwPercInterceptCoreSdt <- 
-  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCore[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Att$varWithinInterceptCoreSdt <-
-  1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))
-mdlStudentOut$Att$varWithinPercInterceptCoreSdt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCore[2]))) * 100
 ```
@@
 \begin{equation}
-(\#eq:AttitudeNeedSdtRandEq)
-Attitude_{ti} = \\gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + u_{1i} + e_{ti}  \\
-\textrm{with}\ \begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix} \textrm{and}\ e_{ti} \sim \mathcal{N}(0,\sigma^2)
+(\#eq:studentSlopesAttNeedSdtEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}Autonomy_{ti} + \\
+                           &\ \beta_{3i}Competence_{ti} + \\
+                           &\ \beta_{4i}Relatedness_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                      &\ \beta_{3i} = \gamma_{30} + u_{3i} \\
+                      &\ \beta_{4i} = \gamma_{40} + u_{4i}
+  \end{split} 
 \end{equation}
@@
 ```{r studentOutModelSlopesAttCoreSdt}
-# Check Correlations 
-studentOutgroupInteraction %>% 
-  select(AttitudesDutch, KeyNeedFullfillment, Competence, Autonomy, RelatednessInteraction) %>%
-  pairs.panels.new
-
+# Reduced dataset if no variance in responses
 studentRed <- 
@@
 # However, removing eithe the Core Need, Autonomy, or Relatedness from the random slopes lets the model converge
-# --> looks like there is an overfitting issue? But why does it work in lmer?
 # FOR NOW: Autonomy removed from random slopes because weakest predictor
@@
     AttitudesDutch ~
-      KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction,
-    random = ~ 1 + KeyNeedFullfillment + Competence + RelatednessInteraction | PID, # Autonomy + 
-    #method = "ML",
-    #control = lmeControl(opt = "optim", optimMethod = "L-BFGS-B"),
+      KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
+    random = ~ 1 + KeyNeedFullfillment_cwc + Competence_cwc + Relatedness_cwc | PID, # Autonomy_cwc + 
     control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
-    data = studentOutgroupInteraction
+    data = studentOutWithinBetween
   )
@@
     AttitudesDutch ~
-      KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction +
-      (1 + KeyNeedFullfillment + Competence + Autonomy + RelatednessInteraction | PID),
-    data = studentOutgroupInteraction
+      KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = studentOutWithinBetween
   ),
@@
   digits = 3,
-  center = TRUE
-)
-
-# Generate 95% parametric bootstrap CIs (and save them as a csv-file):
-# write.csv(confint(model.ran0,
-#               method="boot",nsim=1000,
-#               parallel = "multicore", ncpus = 4, seed = 42),
-#          "output/tables/ML-RandomSlopes-CI.csv")
+  center = FALSE
+)
+
+# 95%CI
+mdlStudentOut$Att$lmerSlopesCoreSdtCI <- 
+  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreSdt)
 
 # Compare new model to previous step
-anova(mdlStudentOut$Att$lmeInterceptCoreSdt, 
+anova(mdlStudentOut$Att$lmeInterceptSdt,
+      mdlStudentOut$Att$lmeInterceptCoreSdt, 
       mdlStudentOut$Att$lmeSlopesCoreSdt) %>%
@@
 
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlStudentOut$Att$varBtwSlopesCoreSdt <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]))
-mdlStudentOut$Att$varBtwPercSlopesCoreSdt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[1]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[1]))) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlStudentOut$Att$varWithinSlopesCoreSdt <-
-  1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]))
-mdlStudentOut$Att$varWithinPercSlopesCoreSdt <-
-  (1 - (as.numeric(mdlStudentOut$Att$varSlopesCoreSdt[2]) / as.numeric(mdlStudentOut$Att$varInterceptCoreSdt[2]))) * 100
-
 # Assumption Checks:
@@
 mdlStudentOut$Att$predSlopesCoreSdt <- 
-  studentOutgroupInteraction %>%
+  studentOutWithinBetween %>%
   select(AttitudesDutch, TIDnum, PID) %>% 
   mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreSdt,
-                           studentOutgroupInteraction,
+                           studentOutWithinBetween,
                            re.form = NA
@@
 # **Young Medical Professional Sample**
+
+## Data Description
+
+### Participants
 
@@
 # look at frequencies of characteristics 
-table(medicalSampleInfo$age)
-table(medicalSampleInfo$gender)
-table(as.character(medicalSampleInfo$nationality))
-```
+medicalSampleInfo %>% 
+  ungroup %>%
+  select(
+    "Number of Measurements" = dailiesN,
+    Age = age,
+    Gender = gender,
+    Nationality = nationality
+  ) %>%
+  mutate(
+    Nationality = as.character(Nationality)
+  ) %>%
+  tbl_summary(.,
+              sort = list(everything() ~ "frequency"))
+```
+
+### Interactions
+
+```{r medicalInteractionInfo}
+# duration of survey should include median and MAD
+medicalInteractions <- dtMedical$full %>%
+  dplyr::select(created.daily, ended.daily) %>%
+  mutate_all(ymd_hms) %>%
+  mutate(duration = as.numeric(ended.daily-created.daily)) %>%
+  select(duration)
+
+medicalInteractions %>%
+  as.data.frame %>%
+  psych::describe(., trim = .2) %>%
+  as.data.frame %>%
+  mutate(vars = c("Duration [in seconds]"), # rownames(.),
+         na = nrow(dtStudents$full)-n,
+         win.mean = sapply(studentInteractions,psych::winsor.mean,simplify=T),
+         win.sd = sapply(studentInteractions,psych::winsor.sd,simplify=T)) %>%
+  dplyr::select(characteristic = vars, n, na, 
+                mean, `mean win` = win.mean, `mean trim` = trimmed, median,
+                sd, `sd win` = win.sd, MAD = mad, min, max,
+                skew, kurtosis) %>%
+  kbl(., 
+      #label = "",
+      caption = "Study 2: Duration of Measurement in Seconds",
+      format = "html", 
+      #linesep = "",
+      #booktabs = T,
+      row.names = F,
+      digits = 2,
+      align = c('l', rep('c', ncol(.)-1)))  %>%
+  add_header_above(., c(" " = 3,"Centrality" = 4, "Dispersion" = 5, "Distribution" = 2)) %>%
+  footnote(general = "'na' indicates the number of measurements for which measurement duration is unknown.") %>%
+  kable_classic(full_width = F, 
+                lightable_options = "hover", 
+                html_font = "Cambria")
+
+dtMedical$full %>%
+  select(OutgroupInteraction,
+         NonOutgroupInteraction) %>%
+  tbl_summary(.,
+              sort = list(everything() ~ "frequency"))
+```
+
+### Variable distributions
 
 ```{r medicalVarDescr}
+# calculate correlations and descriptives
 medicalMlCor <-
   MlCorMat(
-    data = dtMedical$full,
+    data = dtMedical$ful,
     id = "PID",
@@
     .,
-    caption = "Medical: Multilevel Core Variable Descriptives",
+    caption = "Study 3: Multilevel Core Variable Descriptives",
     format = "html",
-    booktabs = TRUE,
+    #booktabs = TRUE,
     linesep = linesep(c(ncol(.))),
@@
   ) %>%
+  pack_rows("Correlations", 1, ncol(medicalMlCor)) %>%
+  pack_rows("Descriptives", ncol(medicalMlCor)+1, nrow(medicalMlCor)) %>%
   footnote(
@@
       "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person coorelations;",
+      "Lower triangle: Within-person correlations;",
       "*** p < .001, ** p < .01,  * p < .05"
     )
-  )
+  ) %>%
+  kable_classic(full_width = F, 
+                lightable_options = "hover", 
+                html_font = "Cambria")
+
 ```
@@
 ```{r medicalOutVarDescr}
+# calculate correlations and descriptives
 medicalOutMlCor <-
@@
     .,
-    caption = "Medical: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
+    caption = "Study 3: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
     format = "html",
-    booktabs = TRUE,
+    #booktabs = TRUE,
     linesep = linesep(c(ncol(.))),
@@
   ) %>%
+  pack_rows("Correlations", 1, ncol(medicalOutMlCor)) %>%
+  pack_rows("Descriptives", ncol(medicalOutMlCor)+1, nrow(medicalOutMlCor)) %>%
   footnote(
@@
       "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person coorelations;",
+      "Lower triangle: Within-person correlations;",
       "*** p < .001, ** p < .01,  * p < .05"
     )
-  )
-
-# misty::multilevel.descript(dtStudentsSupp$studentWithinBetween$keyMotiveFulfilled, cluster = dtStudentsSupp$studentWithinBetween$PID)
-```
-
-After receiving ethical approval from the University of Groningen, we recruited `r nrow(medicalSampleInfo)` international medical students using a contacts within the University Medical Department and specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
-Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
-With this design, we aimed at getting 50-60 measurements per participant (*M* = `r format(round(mean(medicalSampleInfo$dailiesN),2), nsmall=2)`, *SD* = `r format(round(sd(medicalSampleInfo$dailiesN),2), nsmall=2)`, *total N* = `r sum(medicalSampleInfo$dailiesN)`).
-As with the previous study this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
-Participants were compensated for their participation with partial course credits --- depending on their participation.
-The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(medicalSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(medicalSampleInfo$age),2), nsmall=2)`, `r nrow(medicalSampleInfo %>% filter(gender == "women"))` women).
-The sample fairly accurately describes the local population of international students.
-
-The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, daily diary-, and post-measurement.
-The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (*median duration* = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, *MAD duration* = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).
-General compliance was high (`r format(round(sum(medicalSampleInfo$dailiesN)/(nrow(medicalSampleInfo)*62)*100,2), nsmall=2)`% filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS).
-The response rates were approximately equal during mornings (*n* = `r sum(medicalSampleInfo$morningN)`) and afternoons (*n* = `r sum(medicalSampleInfo$afternoonN)`).
-All key variables in for this study were part of the short daily diary surveys.
-The measurement of intergroup contacts was identical to study two.
-The participants recorded between `r medicalContactFreq$SumContactNL[medicalContactFreq$SumContactNL > 0] %>% min`--`r medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
-(`r medicalContactFreq$PercContactNL[medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`% of individual daily diary measurements; `r (sum(medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`% of all `r nrow(dtMedical$full)` daily diary responses).
+  ) %>%
+  kable_classic(full_width = F, 
+                lightable_options = "hover", 
+                html_font = "Cambria")
+
+```
+
+## Contact Hypothesis
+
+### Interaction Frequency and Attitudes
+
+To test the impact of the overall number of interactions, we hope to find a significant relationship between the number of interactions a participant had and the average outgroup attitude.
+
+\begin{equation}
+(\#eq:medicalFreqQualR)
+r_{ContactFrequency, OutgroupAttitudes} \neq 0
+\end{equation}
 
@@
 
-## Contact Hypothesis
-
-We tested the most general contact hypothesis in two steps.
-First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
-Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
-We find no significant correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions (*r* = `r cor(medicalContactFreq$SumContactNLAll, medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(medicalContactFreq$SumContactNLAll, medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (*r* = `r cor(medicalContactFreq$SumContactNL, medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(medicalContactFreq$SumContactNL, medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-This is to say that within our data, participants with more outgroup interactions did not have significantly more positive or negative outgroup attitudes.
-This is again consistent with the results we found in the first study but inconsitent with the significant relationship we find in the second study.
-
-```{r medicalModelOlsAttFreqQual}
+We find that neither the number of interactions nor the number of measurement beeps with an interaction are significantly related with the average outgroup attitudes.
+This is to say that within our data, participants with more outgroup interactions did have significantly more positive outgroup attitudes.
+However, we did find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes.
+
+### Outgroup Attitudes by Interaction Type
+
+In a next step we take into account that having an interaction with an outgroup member, does not happen in a social vacuum.
+Participants who indicated that they had an interaction with an outgroup member include measurement occasions during which someone either only had an interaction with an outgroup member as well as times during which a person also had interaction(s) with a non-Dutch person.
+Inversely, participants who indicated that they did not have an interaction with a Dutch person might either have had no interaction at all or had an interaction with a non-Dutch person.
+We, thus consider all possible combinations and their independent influences on outgroup attitudes.
+
+We first assess the impact of the different interaction types across all measurement points (lumping all beeps together).
+
+\begin{equation}
+(\#eq:medicalIntTypeQual)
+Attitude = OutgroupInteraction + NonOutgroupInteraction
+\end{equation}
+
+<div class="alert alert-info alert-dismissible fade in" role="alert">
+  <a class="close" data-dismiss="alert" aria-label="close">&times;</a>
+  <i class="fas fa-info-circle"></i> <b>Note: </b><br/>
+  This step ignores the nested nature of the data (and consequently, response sets between participants).
+However, a purely cross-sectional approach with retrospective evaluations is common within the field and the analysis here offers a first cross-sectional insight (even with the independence assumption violated).
+</div>
+
+```{r medicalInteractionTypePlt, fig.height=12}
+# between participants interaction type
+medicalAttInteractionType <- dtMedical$full %>%
+  select(
+    PID,
+    OutgroupInteraction,
+    NonOutgroupInteraction,
+    Attitude = AttitudesDutch
+  ) %>%
+  mutate(InteractionType = paste(
+    ifelse(OutgroupInteraction == "Yes", "Out", ifelse(OutgroupInteraction == "No", "NoOut", NA)),
+    ifelse(NonOutgroupInteraction == "Yes", "In", ifelse(NonOutgroupInteraction == "No", "NoIn", NA)),
+    sep = ", "
+  )) %>%
+  filter(
+    !is.na(NonOutgroupInteraction),
+    !is.na(Attitude)
+  )
+
+# violin plot of attitudes by interaction type group
+ggplot(medicalAttInteractionType, aes(y=Attitude, x=OutgroupInteraction, group = interaction(OutgroupInteraction, NonOutgroupInteraction), fill=NonOutgroupInteraction))+
+  geom_violin(trim = T, width=.8, position = position_dodge(0.8)) +
+  geom_boxplot(width=0.04,
+               position = position_dodge(.8),
+               outlier.colour = NULL, 
+               outlier.shape = NA, 
+               notch=F, fill="black", 
+               lwd=1, color="black") + 
+  # geom_jitter(width = 0.15,
+  #            shape=18,
+  #            alpha=.2, size=1) +
+  stat_summary(fun.y=mean, 
+               geom="point", 
+               shape=16, 
+               size=1, 
+               position = position_dodge(0.8),
+               colour="white") +
+  #stat_summary(fun.data="mean_sdl",  
+  #             fun.args = list(mult=1), 
+  #             geom="pointrange", 
+  #             color = "red", 
+  #             width=.2)+
+  stat_summary(geom = "crossbar", 
+               width=0.04, 
+               fatten=0, 
+               position = position_dodge(0.8),
+               color="white", 
+               fun.data = function(x){ return(c(y=median(x), 
+                                                ymin=median(x), 
+                                                ymax=median(x))) })+
+  ylab("Outgroup Attitudes")+
+  xlab("Outgroup Interaction") +
+  ggtitle("Violin Plot:\nOutgroup Attitudes by Interaction Type")+
+  scale_y_continuous(
+    limits = c(0, 100),
+    breaks = c(0, 15, 30, 40, 50, 60, 70, 85, 100),
+    labels = c(
+      "Very cold or unfavorable feelings 0°",
+      "Quite cold and unfavorable feelings 15°",
+      "Fairly cold and unfavorable feelings 30°",
+      "A bit cold and unfavorable feelings 40°",
+      "No feeling at all 50°",
+      "A bit warm and favorable feelings 60°",
+      "Fairly warm and favorable feelings 70° ",
+      "Quite warm and favorable feelings 85° ",
+      "Very warm and favorable feelings 100° "
+    )
+  ) +
+  #coord_flip()+
+  scale_fill_brewer(palette = "Pastel2", name = "Non-Outgroup Interaction")+
+  theme_Publication()+
+  theme(strip.background =element_rect(fill="black", color="black"),
+        strip.text = element_text(colour = 'white', face="bold"))#,
+        #panel.border = element_rect(color="grey"),
+        #legend.position="none")
+```
+
+```{r medicalModelOlsInteractionType}
 # create list to store Worker models
@@
 
+# regression
+mdlMedical$lmAttInt <-
+  lm(AttitudesDutch ~ OutgroupInteraction * NonOutgroupInteraction,
+    data = dtMedical$full
+  )
+# summary(lmstudentAttInteraction)
+
+summ(
+  mdlMedical$lmAttInt,
+  confint = TRUE,
+  digits = 3,
+  center = TRUE
+)
+```
+
+We find that while controlling for interactions with non-Dutch people, outgroup attitudes were significantly higher when participants had an interaction with a Dutch person.
+The effect is of a medium size (`r format(round(mdlMedical$lmAttInt$coefficients["OutgroupInteractionYes"], 2), nsmall=2)` points on a 0--100 scale).
+However, this analysis lumps all ESM beeps from every participants together and ignores that the data is nested within participants.
+
+### Interaction Frequency and Interaction Quality
+
+In a next step we check whether the effect outgroup interactions, in part, depends on the quality during the interactions.
+Because we can only assess interaction quality when there is an interaction, it is difficult to assess this with the interaction dummy as a within person predictor.
+Instead, we will use an aggregate measure of interaction quality and average interaction quality to consider the two predictors jointly.
+
+\begin{equation}
+(\#eq:studentFreqQual)
+Attitude = ContactFreq \times AverageContactQual
+\end{equation}
+
+```{r medicalModelOlsAttFreqQual}
 # regression
@@
 
-However, we do find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (*r* = `r cor(medicalContactFreq$AvQuality, medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, *p* = `r cor.test(medicalContactFreq$AvQuality, medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we only find a main effect of average perceived interaction quality on predict outgroup attitudes (*b* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, *t*(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, *p* = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`).
-Given the missing aggregate relationship between number of interactions and outgroup attitudes, we find no significant effect of interactions themselves nor do we find a significant interaction effect.
-This result mirrors that of study one but is inconsistent with the second study.
-But again this inconsistency is not necessarily surprising given that the variables aggregate all within person variation and there were substantially more measurements where participants did not have an interaction (but reported their outgroup attitudes) than measurements that followed an outgroup contact.
+We find that in the medical sample there is only a relationship between outgroup attitudes and average perceived contact quality but not the number of outgroup contacts.
+Nor do we find that in this sample the impact of the number of interactions is moderated by the average contact quality.
+
+### Multilevel Regression
+
+We, then, proceed with a multilevel analysis, which inherently acknowledges that the measurements are nested within participants.
+
+#### Unconditional model
+
+We start by creating an empty random intercept model (i.e., let the outgroup attitude intercept be different between participants; unconditional model).
+
+\begin{equation}
+(\#eq:medicalEmptyModel)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
+  \end{split} 
+\end{equation}
 
@@
 
+We find that an estimated `r format(round(mdlMedical$IccPercAttNull, 2), nsmall=2)`% of the variation in Feeling Thermometer scores is explained by between participant differences (clustering by PID).
+This is to say that `r format(round(mdlMedical$IccPercAttNull, 2), nsmall=2)`% of the variance in any individual report of Attitudes towards the Dutch can be explained by the properties of the individual who provided the rating.
+And we find that including 'participant' as a predictor adds significantly to the model.
+
+#### random intercept with predictors
+
+To this random intercept model we now add the two types of interactions possible at each measurement point as contemporaneous predictors of outgroup attitudes.
+That is: We check whether within participants having an outgroup interaction (or a non-outgroup interaction) is associated with more positive outgroup attitudes at the same measurement point.
+
+\begin{equation}
+(\#eq:medicalInteractionTypeModel)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20}
+  \end{split} 
+\end{equation}
+
 ```{r medicalModelInterceptAttType, include = FALSE}
@@
     random =  ~ 1 | PID,
-    na.action=na.omit,
+    na.action = na.omit,
     data = dtMedical$full
@@
 
+# 95%CI
 mdlMedical$lmerInterceptAttTypeCI <- 
@@
 
+We find that a random intercept model with the two interaction types as predictors explains significantly more variance then an empty random intercept model.
+Looking at the individual coefficients, we find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes, while having an interaction with a non-Dutch person does not significantly relate to more positive or negative attitudes towards the Dutch.
+
+TL;DR: Interaction with Dutch is great predictor, interactions with non-Dutch is not.
+
+#### random slope
+
+In a next step, we check whether further letting the effect of the different interaction types vary between participants explains additional variance in outgroup attitudes (i.e., random slopes).
+
+\begin{equation}
+(\#eq:medicalRandomSlopes)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i}
+  \end{split} 
+\end{equation}
+
 ```{r medicalModelSlopesInteractionType}
@@
 
+# 95%CI
 mdlMedical$lmerSlopesAttTypeCI <- 
@@
 
-We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
-Thus, in our third dataset we find some mixed results, outgroup contacts are not significantly related to outgroup attitudes on aggregate between participants and this effect is also not suppressed by a average interaction quality (i.e., no interaction effect).
-However, while the aggregate data is partly inconsistent with the first two studies, the within person contemoranous effect of intergroup contact is consistent across all three studies.
+We find that adding the random slopes does add significantly beyond the random intercept model. The individual regression coefficients remain the same in their interpretation.
+
+TL;DR: Random slopes adds significantly. Outgroup interactions still good predictors of contemporaneous outgroup attitudes.
 
 ## Allport's Conditions
+
+We begin our main analysis by outgroup attitudes after an intergroup contact are indeed explained by whether or not Allport's conditions were fulfilled.
+This should, in turn, be due to a higher perceived interaction quality.
+We will this sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+
+### Allport and Attitudes
+
+In a first step we, thus, test the relationship between outgroup attitudes and the fulfillment of the core situational need during the interaction.
+
+##### Unconditional model
+
+We again start by creating an empty random intercept model (i.e., let the outgroup attitude intercept be different between participants; unconditional model).
+This is again confined to the outgroup interaction sub-sample.
+
+\begin{equation}
+(\#eq:medicalOutEmptyModel)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} +  e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
+  \end{split} 
+\end{equation}
 
@@
              data = medicalOutWithinBetween) # use optim if it does not converge
+
 mdlMedicalOut$Att$lmeNull <-

### 2022-01-31 scripts/functions/MlCorMat.R

@@ -201,6 +201,7 @@ MlTraitState <-
     
     # for testing
     # data <- dtWorkerSupp$workerInteractionType
+    # data <- workerInteractionType
     # id <- "PID"
     # selection <- varSelection
     

### 2022-02-01 Supplemental-Material-B-Annotated-Analysis.Rmd
supplement B re-renders

@@
 (\#eq:workerOutSlopeAttQltNeedEq)
-(\#eq:WorkerRandomSlopes)
   \begin{split}
@@
 summ(
+  mdlStudentOut$Att$lmerInterceptCore <- 
     lmer(AttitudesDutch ~ KeyNeedFullfillment_cwc + (1 | PID), 
@@
 summ(
-  lmer(
+  mdlStudentOut$Att$lmerInterceptCoreQlt <- lmer(
     AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc + (1 | PID),
@@
 \begin{equation}
-(\#eq:workerOutSlopeAttQltNeedEq)
-(\#eq:WorkerRandomSlopes)
+(\#eq:studentOutSlopeAttQltNeedEq)
   \begin{split}
@@
 
+#### random intercept with level one predictors
+
+We then add the interaction-specific measure of how much Allport's conditions were fulfilled to the multilevel random intercept model.
+
+\begin{equation}
+(\#eq:medicalOutInterceptAttAllportEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}Allport_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10}
+  \end{split} 
+\end{equation}
+
 ```{r medicalOutModelInterceptAttAllport}
@@
 ```
+
+We find that the the model with the added predictor indeed explains more variance in outgroup attitudes than the unconditional model.
+Looking at the individual coefficients, we find that the the fulfillment of Allport's conditions relates significantly to outgroup attitudes.
+
+#### random slope
+
+In a next step, we check whether further letting the effect of Allport's conditions vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
+
+\begin{equation}
+(\#eq:medicalSlopeAttAllportEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}Allport_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i}
+  \end{split} 
+\end{equation}
 
@@
 ```
+
+We find that adding the random slopes does add significantly beyond the random intercept model.
+We also find that Allport's conditions remains a strong predictor (even when letting the influence vary between participants).
+
+TL;DR: The random slope adds significantly to the prediction model.
+
+### Allport and Interaction Quality
+
+Based on the assertion that the relationship between Allport's conditions and outgroup attitudes is explained by a higher perceived interaction, Allport's conditions should also significantly predict perceived interaction quality.
+
+##### Unconditional model
+
+Given that we now have the perceived interaction quality as our outcome variable of interest we again begin with an unconditional model (i.e., empty random intercept model), to see whether there is enough variance to explain within the participants.
+Similarly to before this is again done within the subsample of measurements during which an outgroup interaction was reported.
+
+\begin{equation}
+(\#eq:medicalOutQltEmptyModel)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ InteractionQuality_{ti} =  &\ \beta_{0i} +  e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i}
+  \end{split} 
+\end{equation}
 
@@
 
+#### random intercept with level one predictors
+
+We then add the fulfillment of Allport's conditions to the multilevel random intercept model.
+
+\begin{equation}
+(\#eq:medicalOutInterceptQltAllportEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}Allport_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10}
+  \end{split} 
+\end{equation}
+
 ```{r medicalOutModelInterceptQltAllport}
@@
 ```
+
+We find that the the model with the added predictor indeed explains more variance in outgroup attitudes than the unconditional model.
+Looking at the individual coefficients, we find that the the fulfillment of Allport's conditions relates significantly to perceived interaction quality.
+
+#### random slope
+
+In a next step, we check whether further letting the effect of Allport's conditions vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
+
+\begin{equation}
+(\#eq:medicalSlopeQltAllportEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}Allport_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i}
+  \end{split} 
+\end{equation}
 
@@
 
+We find that adding the random slopes does add significantly beyond the random intercept model.
+We also find that Allport's conditions remains a strong predictor (even when letting the influence vary between participants).
+
+TL;DR: The random slope adds significantly to the prediction model.
+
+### Allport, Quality, and Attitudes
+
+In our final main step, we will jointly consider the effect of Allport's conditions and perceived interaction quality on outgroup attitudes.
+We expect that if the relationship between Allport's conditions and outgroup attitudes is indeed explained by a higher perceived interaction quality, the interaction quality perception should assume the explained variance by the fulfillment of Allport's conditions.
+
+#### random intercept with level one predictors
+
+We thus add both Allport's conditions and perceived interaction quality to a random intercept model of outgroup attitudes.
+
+\begin{equation}
+(\#eq:medicalOutInterceptAttQltAllportEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}Allport_{ti} + \\
+                           &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20}
+  \end{split} 
+\end{equation}
+
 ```{r medicalOutModelInterceptAttAllportQlt}
@@
 ```
+
+Unsurprisingly, the model with the two predictors adds significantly beyond the empty unconditional model.
+However, more importantly, looking at the coefficients, we find that the effect of Allport's conditions is indeed is indeed strongly reduced and the variance is explained by the perceived interaction quality.
+Notably in this sample, the reduction of variance explained is not a much as we saw with core need fulfillment in previous studies.
+
+#### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
+
+\begin{equation}
+(\#eq:medicalOutSlopeAttQltAllportEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}Allport_{ti} + \\
+                           &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i}
+  \end{split} 
+\end{equation}
 
@@
 
-We sequentially tested whether the fulfillment of Allport's Contact Conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly.
-We find that in the multilevel models, the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
-However, if we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`).
-These results indicate that in this dataset the the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
+When we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor and the unique variance explained by Allport's Conditions was less than half of its original effect size.
 
 ## Need Fulfillment
+
+The main focus of our proposal is again the assessment of how much positive outgroup attitudes might be explained by whether or not an intergroup interaction fulfilled the person's core situational need.
+As with the previous two studies we also check to what extend this effect goes through perceived interaction quality.
+
+### Need fulfillment and Attitudes
+
+In a first step we, again, test the relationship between outgroup attitudes and the fulfillment of the core situational need during the interaction.
+
+#### random intercept with level one predictors
+
+We jump right in with the random intercept model because we have already assessed the unconditional model when we tested the influence of Allport's conditions on outgroup attitudes.
+We thus add the core interaction need fulfillment to the multilevel random intercept model.
+
+\begin{equation}
+(\#eq:medicalOutInterceptAttNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10}
+  \end{split} 
+\end{equation}
 
@@
 ```
+
+We find that the the model with the added predictor indeed explains more variance in outgroup attitudes than the unconditional model.
+Looking at the individual coefficients, we find that the situational core need relates significantly to outgroup attitudes.
+
+#### random slope
+
+In a next step, we check whether further letting the effect of core need fulfillment vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
+
+\begin{equation}
+(\#eq:medicalOutSlopeAttNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i}
+  \end{split} 
+\end{equation}
 
@@
 
+We find that adding the random slopes does add significantly beyond the random intercept model.
+We also find that the core need remains a strong predictor (even when letting the influence vary between participants).
+
+TL;DR: The random slope adds significantly to the prediction model.
+
+### Need fulfillment and Interaction Quality
+
+Based on the assertion that the relationship between core need fulfillment and outgroup attitudes is explained by a higher perceived interaction, the core need fulfillment should also significantly predict perceived interaction quality.
+
+#### random intercept with level one predictor
+
+We again do not need to calculate an unconditional model for the perceived interaction quality outcome variable because we have already done so for the previous assessment of Allport's conditions.
+So we add the core interaction need fulfillment to the multilevel random intercept model.
+
+\begin{equation}
+(\#eq:medicalOutInterceptQltNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ InteractionQuality_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10}
+  \end{split} 
+\end{equation}
+
 ```{r medicalOutModelInterceptQltCore}
@@
 ```
+
+The predictor again adds a significant amount of explained variances beyond the empty model and looking at the slope coefficient, we find that the situational core need fulfillment relates significantly to perceived interaction quality.
+
+#### random slope
+
+As before, we check whether further letting the effect of core need fulfillment vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
+
+\begin{equation}
+(\#eq:medicalOutSlopeQltNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ InteractionQuality_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i}
+  \end{split} 
+\end{equation}
 
@@
 
+We find that adding the random slopes does add significantly beyond the random intercept model and situation key need fulfillment remains a meaningful predictor of outgroup attitudes.
+
+### Interaction Needs, Quality, and Attitudes
+
+In our final main step, we will jointly consider the effect of core need fulfillment and perceived interaction quality on outgroup attitudes.
+We expect that if the relationship between core need fulfillment and outgroup attitudes is indeed explained by a higher perceived interaction quality, the interaction quality perception should assume the explained variance of the core contact need fulfillment.
+
+#### random intercept with level one predictors
+
+We thus add both the core need fulfillment and perceived interaction quality to a random intercept model of outgroup attitudes.
+
+\begin{equation}
+(\#eq:medicalOutInterceptAttQltNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20}
+  \end{split} 
+\end{equation}
+
 ```{r medicalOutModelInterceptAttCoreQlt}
@@
 
+# 95%CI
 mdlMedicalOut$Att$lmerInterceptCoreQltCI <- 
@@
 ```
+
+Unsurprisingly, the model with the two predictors adds significantly beyond the empty unconditional model.
+However, more importantly, looking at the coefficients, we find that the effect of core need fulfillment indeed is indeed strongly reduced and the variance is explained by the perceived interaction quality.
+However, similar to the equivalent analysis of Allport's conditions and interaction quality, the effect of need fulfillment remains a significant predictor of outgroup attitudes when controlling for perceived interaction quality.
+
+#### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
+
+\begin{equation}
+(\#eq:medicalOutSlopeAttQltNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i}
+  \end{split} 
+\end{equation}
 
@@
 
-We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
-We find that in the multilevel models, the fulfillment of core need fulfillment during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
-However, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`).
-These results indicate that in this dataset the the fulfillment of core situational needs had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
+The random slopes add significant explained variance to the model.
+When we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor and the unique variance explained by core need fulfillment was roughly half of its original effect size.
 
 ## Compare Fulfillment of Core Need and Allport's Conditions
+
+To compare the models using either Allport's conditions or the core need fulfillment to predict outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
+
+### Model fit parameters
+
+For the model fit parameters we look at the AIC, BIC, pseudo R^2^s, the ICC, RMSE, and Sigma.
 
@@
 
+When comparing the model selection indices we find that the fulfillment of the situation core need, indeed performs slightly better than the model using Allport's conditions.
+
+### Joint model
+
+We then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
+
+#### random intercept model
+
+We begin by adding both the core need fulfillment and Allport's conditions to a random intercept model of outgroup attitudes.
+
+\begin{equation}
+(\#eq:medicalOutInterceptAttNeedAllportEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}Allport_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20}
+  \end{split} 
+\end{equation}
+
 ```{r medicalOutModelInterceptAttCoreAllport}
@@
 ```
+
+For the random intercept model we find that the fulfillment of situational core needs adds significant explained variance beyond a model that only includes Allport's conditions.
+When looking at the regression parameters in the joint model we additionally find that the fulfillment of core situational needs is ever so slightly a stronger predictor of outgroup attitudes.
+
+#### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
+
+\begin{equation}
+(\#eq:medicalOutSlopeAttNeedAllportEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}Allport_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i}
+  \end{split} 
+\end{equation}
 
@@
 
+# 95%CI
 mdlMedicalOut$Att$lmerSlopesCoreAllportCI <- 
@@
 
-To compare the models using either Allport's conditions or the core need fulfillment to predict outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
-When comparing the model selection indices we find that the fulfillment of the situation core need, indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r AIC(mdlMedicalOut$Att$lmerSlopesCore)` < `r AIC(mdlMedicalOut$Att$lmerSlopesAllport)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r BIC(mdlMedicalOut$Att$lmerSlopesCore)` < `r BIC(mdlMedicalOut$Att$lmerSlopesAllport)` $BIC_{Allport}$).
-Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`).
+Again, the random slopes add significantly to the model.
+When considering the predictors jointly in the random slopes model, we find that both significantly predict outgroup attitudes with similar sized regression parameters.
 This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
@@
 
-```{r medicalModelAttNullInt}
-# Create and save Model
+To build further confidence in our results, we assess a few additional models that might offer alternative explanations of the effects we find.
+
+#### Interaction Type
+
+To make certain that the effect of core need fulfillment is specific to the interaction we compare the the effect to fulfillment of the situation core need when no outgroup interaction took place.
+
+##### random intercept
+
+Here we go back to the full dataset and add generalized situational core need fulfillment (either during an interaction or about the daytime in general) and whether an outgroup interaction happened as well as their interaction term to a random intercept model of outgroup attitudes.
+
+\begin{equation}
+(\#eq:medicalInterceptAttIntNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{3i}KeyNeedFulfillXOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20} \\
+                      &\ \beta_{3i} = \gamma_{30}
+  \end{split} 
+\end{equation}
+
+```{r medicalModelInterceptAttCoreInt}
+# Create and save empty model for comparison
 mdlMedical$lmerAttNullInt <-
@@
 # Get summary with p-values (Satterthwaite's method)
-# summary(mdlMedical$lmerAttNull) #or with the lme function
-summ(mdlMedical$lmerAttNullInt, digits = 3)
-```
-
-```{r medicalModelInterceptAttCoreInt}
+#summ(mdlMedical$lmerAttNullInt, digits = 3)
+
 # Create and save Model
@@
 
+# 95%CI
 mdlMedical$lmerInterceptAttCoreIntCI <- 
@@
 
+We find that the model explains significantly more variance than the empty null model.
+However, more interestingly, looking at the coefficients, we find that, as seen earlier, having an outgroup interaction has a strong effect on outgroup attitudes.
+Importantly, we find that there is no main effect of key need fulfillment by itself but the effect is qualified by a significant interaction effect of core need fulfillment and outgroup contact.
+This indicates that it is not simply key need fulfillment in general --- but especially key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+
+##### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
+
+\begin{equation}
+(\#eq:medicalSlopesAttIntNeedEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}OutgroupInteraction_{ti} + \\
+                           &\ \beta_{3i}KeyNeedFulfillXOutgroupInteraction_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                      &\ \beta_{3i} = \gamma_{30} + u_{3i}
+  \end{split} 
+\end{equation}
+
 ```{r medicalModelSlopesAttCoreIntX}
@@
 
-We again checked for alternative models to the core need fulfillment.
-First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffHtml(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffHtml(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
-Together with a significant main effect of having an outgroup contact (`r MlCoeffHtml(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "OutgroupInteractionYes")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous studies.
+We find that adding the random slopes does add significantly beyond the random intercept model.
+We also see that when taking the possibility to varying slopes into account, the coefficient interpretations remains consistent (i.e., outgroup contact and its interaction with core need fulfillment remain important predictors of positive outgroup attitudes).
+
+##### Plot Interaction
+
+Before we move on, we shortly illustrate the interaction effect of how the effect of core need fulfillment differed by whether an outgroup contact took place or not.
+To this end we illustrate (1) the raw data points (without taking the nested nature into account), as well as a plot of the model predicted values and their prediction interval (taking the nested structure into account based; similar to an interaction plot).
+
+```{r medicalModelInterceptAttCoreIntPlt}
+# visualize interaction
+## Without ML structure
+ggplot(data = dtMedical$full,
+       aes(x = KeyNeedFulfillment,
+           y = AttitudesDutch,
+           fill = OutgroupInteraction)) +
+  #geom_point()+
+  geom_smooth(method = 'lm',
+              aes(linetype = OutgroupInteraction),
+              color = "black") +
+  #facet_wrap(~PID, ncol = 6)+
+  scale_linetype_manual(values = c("dashed", "solid")) +
+  scale_fill_manual(values = c("darkgrey", "black")) +
+  #scale_colour_manual(values=c("grey20", "black"), name="Intergroup Contact")+
+  scale_y_continuous(
+    limits = c(50, 100),
+    breaks = seq(50, 100, by = 10),
+    position = "left"
+  ) +
+  scale_x_continuous(limits = c(0, 100), breaks = seq(0, 100, by = 10)) +
+  labs(
+    title = "Without ML stucture",
+    x = "Fulfillment Core Need",
+    y = "Outgroup Attitudes",
+    fill = "Intergroup Contact",
+    linetype = "Intergroup Contact"
+  ) +
+  theme_Publication() +
+  theme(legend.position = "bottom",
+        legend.key.size = unit(1, "cm"))
+
+## With ML structure
+# create parameters for prediction
+datNew = data.frame(
+  KeyNeedFulfillment_cwc = rep(seq(
+    round_any(min(
+      dtMedical$full$KeyNeedFulfillment_cwc %>% na.omit
+    ), 5, f = floor), round_any(max(
+      dtMedical$full$KeyNeedFulfillment_cwc %>% na.omit
+    ), 5, f = ceiling), 5
+  ), 2),
+  PID = 0
+) %>%
+  mutate(OutgroupInteraction = rep(c("No", "Yes"), each = nrow(.)/2)) %>%
+  select(PID, OutgroupInteraction, KeyNeedFulfillment_cwc)
+
+# Predict values, clean up and calculate SE
+PI <-
+  merTools::predictInterval(
+    merMod = mdlMedical$lmerSlopesAttCoreInt,
+    newdata = datNew,
+    level = 0.95,
+    stat = "mean",
+    type = "linear.prediction",
+    include.resid.var = F,
+    fix.intercept.variance = F
+  )
+mdlMedical$predInterceptAttCoreIntX <- 
+  cbind(datNew, PI)
+mdlMedical$predInterceptAttCoreIntX$se <-
+  (mdlMedical$predInterceptAttCoreIntX$upr - mdlMedical$predInterceptAttCoreIntX$fit) / 1.96
+rm(datNew, PI)
+mdlMedical$predInterceptAttCoreIntX$OutgroupInteractionLab <-
+  factor(
+    x = mdlMedical$predInterceptAttCoreIntX$OutgroupInteraction,
+    levels = sort(
+      unique(mdlMedical$predInterceptAttCoreIntX$OutgroupInteraction)
+    ),
+    labels = c("No", "Yes")
+  )
+
+# Plot predicted values with SE
+ggplot(
+  mdlMedical$predInterceptAttCoreIntX,
+  aes(x = KeyNeedFulfillment_cwc,
+      y = fit,
+      fill = OutgroupInteractionLab)
+)+
+  #geom_point() +
+  geom_line(aes(linetype = OutgroupInteractionLab), size = 1) +
+  #facet_wrap(~PID, ncol = 6)+
+  geom_ribbon(data = mdlMedical$predInterceptAttCoreIntX,
+              aes(ymin = fit - se, ymax = fit + se),
+              alpha = 0.3) +
+  scale_x_continuous(breaks = seq(
+    round_any(min(
+      studentWithinBetween$KeyNeedFullfillment_cwc
+    ), 5, f = floor), round_any(max(
+      studentWithinBetween$KeyNeedFullfillment_cwc
+    ), 5, f = ceiling), 10
+  )) +
+  scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
+  scale_linetype_manual(values = c("dashed", "solid")) +
+  scale_fill_manual(values = c("darkgrey", "black")) +
+  labs(
+    x = "Fulfillment Core Need",
+    y = "Outgroup Attitude (NL)",
+    fill = "Intergroup Contact",
+    linetype = "Intergroup Contact",
+    title = "Based on Model Predictions"
+  ) +
+  theme_Publication()
+
+# #### Bayesian estimation !! ONLY RUN ON FINAL RENDER !! Takes forever ####
+# options(mc.cores = parallel::detectCores())  # Run many chains simultaneously
+# brmfit <- brm(
+#   AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction +
+#     (1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID),
+#   data = dtMedical$full,
+#   family = gaussian,
+#   iter = 1000,
+#   chains = 4
+# )
+# 
+# # create parameters for prediction:
+# datNew = data.frame(
+#   KeyNeedFulfillment_cwc = rep(seq(
+#     round_any(min(
+#       dtMedical$full$KeyNeedFulfillment_cwc %>% na.omit
+#     ), 2, f = floor), round_any(max(
+#       dtMedical$full$KeyNeedFulfillment_cwc %>% na.omit
+#     ), 2, f = ceiling), 2
+#   ), 2)
+# ) %>%
+#   mutate(OutgroupInteraction = rep(c("No", "Yes"), each = nrow(.)/2))
+# 
+# # Save predicted values and adjust names and labels
+# fitavg <-
+#   cbind(datNew,
+#         fitted(brmfit, newdata = datNew, re_formula = NA)[, -2])
+# names(fitavg)[names(fitavg) == "Estimate"] = "pred"
+# fitavg$se <- (fitavg$Q97.5 - fitavg$pred) / 1.96
+# fitavg$OutgroupInteractionLab <-
+#   factor(
+#     x = fitavg$OutgroupInteraction,
+#     levels = sort(
+#       unique(fitavg$OutgroupInteraction)
+#     ),
+#     labels = c("No", "Yes")
+#   )
+# 
+# # Plot Bayesian SE prediction interval
+# ggplot(fitavg,
+#        aes(x = KeyNeedFulfillment_cwc,
+#            y = pred,
+#            fill = OutgroupInteractionLab)) +
+#   scale_x_continuous(breaks = seq(
+#     round_any(min(
+#       dtMedical$full$KeyNeedFulfillment_cwc %>% na.omit
+#     ), 5, f = floor), round_any(max(
+#       dtMedical$full$KeyNeedFulfillment_cwc %>% na.omit
+#     ), 5, f = ceiling), 10
+#   )) +
+#   scale_y_continuous(limits = c(50, 100), breaks = seq(50, 100, 10)) +
+#   geom_line(aes(linetype = OutgroupInteractionLab), size = 1) +
+#   geom_ribbon(aes(ymin = pred - se, ymax = pred + se), alpha = 0.2) +
+#   scale_linetype_manual(values = c("dashed", "solid")) +
+#   scale_fill_manual(values = c("darkgrey", "black")) +
+#   labs(
+#     x = "Fulfillment Core Need",
+#     y = "Outgroup Attitude (NL)",
+#     fill = "Intergroup Contact",
+#     linetype = "Intergroup Contact",
+#     title = "Based on Bayesian Prediction Interval"
+#   ) +
+#   theme_Publication()
+# 
+# # # plot all overlayed posteriors:
+# # pst <- posterior_samples(brmfit, "b")
+# # ggplot(dtMedical$full,
+# #        aes(x = KeyNeedFulfillment_cwc, y = AttitudesDutch)) +
+# #   geom_point(shape = 4, alpha = .1) +
+# #   geom_tile() +
+# #   geom_abline(
+# #     data = pst,
+# #     aes(intercept = b_Intercept, slope = b_KeyNeedFulfillment_cwc),
+# #     alpha = .025,
+# #     size = .4
+# #   ) +
+# #   labs(title = "slope Posteriors",
+# #        x = "Fulfillment Core Need",
+# #        y = "Outgroup Attitudes (NL)") +
+# #   theme_Publication()
+# # rm(datNew, brmfit, fitavg, pst)
+```
+
+The plots indicate that especially once we take the nested data structure into account we can see a substantially stronger effect of core need fulfillment on outgroup attitudes during outgroup contacts than without outgroup contacts.
+
+#### Other psychological needs
+
+In a final step we check whether during the interaction the core situational need is a meaningful predictor even when taking other fundamental psychological needs into account.
+We focus on the three commonly considered self determination needs: competence, autonomy, and relatedness.
+
+##### random intercept with level one predictors
+
+We add the core need fulfillment with the three self determination needs to a random intercept model of outgroup attitudes.
+
+\begin{equation}
+(\#eq:medicalInterceptAttNeedSdtEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}Autonomy_{ti} + \\
+                           &\ \beta_{3i}Competence_{ti} + \\
+                           &\ \beta_{4i}Relatedness_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} \\
+                      &\ \beta_{2i} = \gamma_{20} \\
+                      &\ \beta_{3i} = \gamma_{30} \\
+                      &\ \beta_{4i} = \gamma_{40}
+  \end{split} 
+\end{equation}
 
@@
 ```
+
+We find that the the model with the added predictor indeed explains more variance in outgroup attitudes than the unconditional model and we find that adding the core need adds further explained variance --- beyond the self determination needs.
+Looking at the individual coefficients, we find that the situational core need relates significantly to outgroup attitudes, that it is a stronger predictor than any of the self determination theory needs and that it assumes some of the variance explained by the self determination theory needs (when compared to a model without the core need).
+
+##### random slope
+
+We again check whether further letting the effects vary between participants explains additional variance in outgroup attitudes (i.e., random slope).
+
+\begin{equation}
+(\#eq:medicalSlopesAttNeedSdtEq)
+  \begin{split}
+    \textrm{Level 1:} &
+      \begin{aligned}[t]
+        \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                           &\ \beta_{2i}Autonomy_{ti} + \\
+                           &\ \beta_{3i}Competence_{ti} + \\
+                           &\ \beta_{4i}Relatedness_{ti} + e_{ti}
+      \end{aligned} \\
+    \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                      &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                      &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                      &\ \beta_{3i} = \gamma_{30} + u_{3i} \\
+                      &\ \beta_{4i} = \gamma_{40} + u_{4i}
+  \end{split} 
+\end{equation}
 
@@
 
+# 95%CI
 mdlMedicalOut$Att$lmerSlopesCoreSdtCI <- 
@@
 
-In a final step we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
-We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r medicalSdtCompChiSq`).
-We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFulfillment_cwc")`).
 When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, similar to the previous study, in this large sample relatedness (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffHtml(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each predicted positive outgroup attitudes independently.
+However, similar to the previous study, in this large sample relatedness, competence, and autonomy each predicted positive outgroup attitudes independently.
 However, the regression coefficient is three times as large for the core need fulfillment (with all scaling being equal).

### 2022-02-03 Methods-and-Results.Rmd
Update Methods-and-Results.Rmd

@@
 
+# 95%CI
 mdlWorker$lmerSlopesAttCoreIntCI <- 
@@
 
+# 95%CI
 mdlStudent$lmerInterceptAttTypeCI <- 
@@
 
+# 95%CI
 mdlStudent$lmerSlopesAttTypeCI <- 
@@
 
+# 95%CI
 mdlStudentOut$Att$lmerInterceptCoreCI <- 
@@
 
+# 95%CI
 mdlStudentOut$Qlt$lmerInterceptCoreCI <- 
@@
 
+# 95%CI
 mdlStudentOut$Qlt$lmerSlopesCoreCI <- 
@@
 
+# 95%CI
 mdlStudentOut$Att$lmerInterceptCoreQltCI <- 
@@
 
+# 95%CI
 mdlStudentOut$Att$lmerSlopesCoreQltCI <- 
@@
 
+# 95%CI
 mdlStudent$lmerInterceptAttCoreIntCI <- 
@@
 
+# 95%CI
 mdlStudent$lmerSlopesAttCoreIntCI <- 
@@
 
+# 95%CI
+mdlStudentOut$Att$lmerInterceptCoreSdtCI <- 
+  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCoreSdt)
+
 # To be compared against a model with only the self determination theory needs
@@
 anova(
+  mdlStudentOut$Att$lmeNull,
   mdlStudentOut$Att$lmeInterceptSdt,
@@
 
+# 95%CI
 mdlStudentOut$Att$lmerSlopesCoreSdtCI <- 

### 2022-03-01 Supplemental-Material-B-Annotated-Analysis.Rmd
I

@@
   "lubridate",
-  "purrr"
+  "purrr",
+  "metafor"
 )
@@
   mutate(
-    NonDutchContact = replace_na(NonDutchContact, 2), # make second non-Dutch countable
+    NonDutchContact = tidyr::replace_na(NonDutchContact, 2), # make second non-Dutch countable
     NonDutchContact = NonDutchContact*-1+2 # recode (yes = 1 -> 1, no = 2 -> 0)
@@
 
-df <-
+medicalWithinBetween <-
+  MlTraitState(
+    data = df,
+    id = "PID",
+    selection =
+      c(
+        "KeyNeedFulfillment",
+        "Competence",
+        "Autonomy",
+        "Relatedness",
+        "AllportsCondition",
+        "AttitudesDutch",
+        "qualityOverall",
+        "OutgroupInteraction",
+        "NonOutgroupInteraction"
+      )
+  )
+
+df <- # keep only for compatibility of old framgents
   MlTraitState(
@@
 
+# **Forest Plots of Main Analyses**
+
+## Contact Hypothesis
+
+### Aggregate Data
+
+summary of regression results from the aggregated contact and interaction quality data.
+
+```{r metaGeneralLm, include=FALSE}
+mdlTblElementsGeneralLm <- list(mdlWorker$lmAttFreqQualX,
+                                mdlStudent$lmAttFreqQualX,
+                                mdlMedical$lmAttFreqQualX)
+
+lmMetaTbl <- data.frame()
+for (i in 1:length(mdlTblElementsGeneralLm)){
+  lmTblTmp <- lmTblPrep(mdlTblElementsGeneralLm[[i]])$coeficients %>%
+  select(
+    coef,
+    B = est,
+    se,
+    lwr,
+    upr,
+    tval,
+    Rsq
+  ) %>%
+  mutate(
+    n = lmTblPrep(mdlTblElementsGeneralLm[[i]])$fit$N,
+    m = nrow(.)-1, 
+    sample = str_match(lmTblPrep(mdlTblElementsGeneralLm[[i]])$fit$data, "worker|student|medical"),
+    coef = gsub(":", ".", coef)
+  )
+  lmMetaTbl <- rbind(lmMetaTbl, lmTblTmp)
+}
+
+lmMetaTbl <- lmMetaTbl %>% arrange(coef)
+
+# extract parameter names
+  name <- "Contact Hypothesis — Aggregate Linear Regression"
+  var <- as.character(unique(lmMetaTbl$coef))[!as.character(unique(lmMetaTbl$coef)) %in% c("(Intercept)")]
+  names <- qdap::mgsub(c("SumContactNL", "AvQuality", "SumContactNL.AvQuality"),
+                       c("Number of Outgroup Contacts","Average Interaction Quality", "Contact X Quality"), 
+                       var)
+  studies <- as.character(unique(lmMetaTbl$sample))
+
+### Parametric Meta-Analysis
+    meta.parametric <- list()
+    meta.parametric.sum <- data.frame(effect = var, 
+                                      name = names, 
+                                      beta.Worker = NA, 
+                                      CI.Worker = NA,
+                                      beta.Student = NA, 
+                                      CI.Student = NA,
+                                      beta.Medical = NA,
+                                      CI.Medical = NA, 
+                                      RE.beta = NA,
+                                      RE.CI = NA,
+                                      RE.pval = NA,
+                                      RE.star = NA)
+
+# i = 1
+for(i in 1:length(var)){
+      md <- escalc(data = lmMetaTbl[lmMetaTbl$coef==var[i],],
+                   measure = "SPCOR",
+                   ti = tval,
+                   ni = n,
+                   mi = m,
+                   r2i = Rsq,
+                   var.names = c(paste(var[i],".yi",sep=""),paste(var[i],".vi",sep="")))
+
+      meta.parametric[[var[i]]] <- rma(yi = get(paste(var[i],".yi",sep="")),
+                                       vi = get(paste(var[i],".vi",sep="")), 
+                                       data = md, 
+                                       method = "FE", # "REML", 
+                                       slab = sample)
+      #metafor::forest(meta.parametric[[var[i]]],
+      #                main = paste("Meta Analysis ",names[i],sep = ""))
+
+      meta.parametric.sum$effect[i] <- var[i]
+      meta.parametric.sum$beta.Worker[i] <- meta.parametric[[var[i]]]$yi[1]
+      meta.parametric.sum$beta.Student[i] <- meta.parametric[[var[i]]]$yi[2]
+      meta.parametric.sum$beta.Medical[i] <- meta.parametric[[var[i]]]$yi[3]
+      meta.parametric.sum$CI.Worker[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),", ",round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),"]",sep="")
+      meta.parametric.sum$CI.Student[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),", ",round(meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),"]",sep="")
+      meta.parametric.sum$CI.Medical[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),", ",round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),"]",sep="")
+      meta.parametric.sum$RE.beta[i] <- meta.parametric[[var[i]]]$b
+      meta.parametric.sum$RE.CI[i] <- paste("[",
+                                            round(meta.parametric[[var[i]]]$ci.lb, 2),
+                                            ", ", round(meta.parametric[[var[i]]]$ci.ub,2),"]", sep="")
+      meta.parametric.sum$RE.pval[i] <- meta.parametric[[var[i]]]$pval
+      meta.parametric.sum$RE.star[i] <- ifelse(meta.parametric.sum$RE.pval[i]<0.001,"***",ifelse(meta.parametric.sum$RE.pval[i]<0.01,"**",ifelse(meta.parametric.sum$RE.pval[i]<0.05,"*","")))
+}
+    #meta.parametric
+
+    eff <- escalc(data = lmMetaTbl, 
+                  slab = coef,
+                  measure = "SPCOR",
+                  ti = tval,
+                  ni = n,
+                  mi = m,
+                  r2i = Rsq)
+    meta <- rma(yi = yi,
+                vi = vi, 
+                data = eff, 
+                method = "FE", # "REML", 
+                slab = paste(coef, sample, sep=" - "))
+
+    k <- length(var) * length(studies)
+    #png(file = "Figures/forestParametricGeneralLm.png", height = 200 + 40*k^.85) 
+      metafor::forest(meta, xlim=c(-2, 2), cex=0.75, ylim=c(-1, 20), rows=c(22:20,16:14,10:8,4:2), 
+                      slab = rep(c("Study 1","Study 2", "Study 3"),length(studies)+1),
+                      mlab="", main=paste0("Meta Analysis: Forest Plot [Parametric] \n(",name,")")) # , xlab = "Standardized Beta"
+      par(font=2)
+      text(-2.05, c(17,11,5), cex=0.75, pos=4, names)
+      m=1
+      for(i in 3:1){
+        addpoly(meta.parametric[[i]], row=m, cex=0.75, mlab="► Fixed Effect")
+        m <- m+6
+      }
+      text(-2.05, 19, "Predictors by study",  cex=.8, pos=4)
+      text(2, 19, "Semi-Partial Correlation [95% CI]", cex=.8, pos=2)
+    #dev.off()
+
+### Bootstrapped Meta-Analysis
+    var.boot <- var
+    names.boot <- names
+    meta.bootstrapped <- list()
+    meta.bootstrapped.sum <- data.frame(effect = var.boot, 
+                                      name = names.boot, 
+                                      beta.Worker = NA, 
+                                      CI.Worker = NA,
+                                      beta.Student = NA, 
+                                      CI.Student = NA,
+                                      beta.Medical = NA,
+                                      CI.Medical = NA, 
+                                      RE.beta = NA,
+                                      RE.CI = NA,
+                                      RE.pval = NA,
+                                      RE.star = NA)
+
+    # i = 3
+    for(i in 1:length(var.boot)){
+      md <- escalc(data = lmMetaTbl[lmMetaTbl$coef==var.boot[i],],
+                   measure = "SPCOR",
+                   yi = B,
+                   sei = se,
+                   ni = n,
+                   mi = m,
+                   var.names = c(paste(var.boot[i],".yi",sep=""),paste(var.boot[i],".vi",sep="")))
+
+      meta.bootstrapped[[var.boot[i]]] <- rma(yi = get(paste(var.boot[i],".yi",sep="")),
+                                              vi = get(paste(var.boot[i],".vi",sep="")),
+                                              data = md,
+                                              method = "FE",
+                                              slab = sample)
+      #metafor::forest(meta.bootstrapped[[var.boot[i]]],
+      #                main = paste("Meta Analysis ",names.boot[i],sep = ""))
+      meta.bootstrapped.sum$effect[i] <- var[i]
+      meta.bootstrapped.sum$beta.Worker[i] <-
+        meta.bootstrapped[[var[i]]]$yi[1]
+      meta.bootstrapped.sum$beta.Student[i] <-
+        meta.bootstrapped[[var[i]]]$yi[2]
+      meta.bootstrapped.sum$beta.Medical[i] <-
+        meta.bootstrapped[[var[i]]]$yi[3]
+      meta.bootstrapped.sum$CI.Worker[i] <-
+        paste(
+          "[",
+          round(meta.bootstrapped[[var[i]]]$yi[1] -
+                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[1]), 2),
+          ", ",
+          round(meta.bootstrapped[[var[i]]]$yi[1] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[1]), 2),
+          "]",
+          sep = ""
+        )
+      meta.bootstrapped.sum$CI.Student[i] <-
+        paste(
+          "[",
+          round(meta.bootstrapped[[var[i]]]$yi[2] -
+                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[2]), 2),
+          ", ",
+          round(meta.bootstrapped[[var[i]]]$yi[2] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[2]), 2),
+          "]",
+          sep = ""
+        )
+      meta.bootstrapped.sum$CI.Medical[i] <-
+        paste(
+          "[",
+          round(meta.bootstrapped[[var[i]]]$yi[3] -
+                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[3]), 2),
+          ", ",
+          round(meta.bootstrapped[[var[i]]]$yi[3] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[3]), 2),
+          "]",
+          sep = ""
+        )
+      meta.bootstrapped.sum$RE.beta[i] <- meta.bootstrapped[[var[i]]]$b
+      meta.bootstrapped.sum$RE.CI[i] <- paste(
+        "[",
+        round(meta.bootstrapped[[var[i]]]$ci.lb, 2),
+        ", ",
+        round(meta.bootstrapped[[var[i]]]$ci.ub, 2),
+        "]",
+        sep = ""
+      )
+      meta.bootstrapped.sum$RE.pval[i] <- meta.bootstrapped[[var[i]]]$pval
+      meta.bootstrapped.sum$RE.star[i] <-
+        ifelse(
+          meta.bootstrapped.sum$RE.pval[i] < 0.001,
+          "***",
+          ifelse(
+            meta.bootstrapped.sum$RE.pval[i] < 0.01,
+            "**",
+            ifelse(meta.bootstrapped.sum$RE.pval[i] < 0.05, "*", "")
+          )
+        )
+    }
+    #meta.bootstrapped
+
+    eff.boot <- escalc(data = lmMetaTbl %>% filter(coef != "(Intercept)"), 
+                       slab = coef,
+                       measure = "SPCOR",
+                       yi = B,
+                       sei = se,
+                       ni = n,
+                       mi = m)
+    meta.boot <- rma(yi = yi,
+                     vi = vi, 
+                     data = eff.boot, 
+                     method = "FE", 
+                     slab = paste(coef, sample, sep=" - "))
+
+    k <- 3*3
+    #png(file = "Figures/forestBootstrappedGeneralLm.png", height = 200 + 40*k^.85)
+      metafor::forest(meta.boot, cex=0.75, xlim=c(-2, 2.5), ylim=c(-1, 20), rows=c(16:14,10:8,4:2), 
+                      slab = rep(c("Study 1","Study 2", "Study 3"),length(studies)),
+                      mlab="", main=paste0("Meta Analysis: Forest Plot [Bootstrapped] \n(",name,")")) # , xlab = "Standardized Beta")
+      par(font=2)
+      text(-2.05, c(17,11,5), cex=0.75, pos=4, names)
+      m=1
+      for(i in 3:1){
+        addpoly(meta.bootstrapped[[i]], row=m, cex=0.75, mlab="► Fixed Effect")
+        m <- m+6
+      }
+      text(-2.05, 19, "Predictors by study",  cex=.8, pos=4)
+      text(2.5, 19, "Semi-Partial Correlation [95% CI]", cex=.8, pos=2)
+    #dev.off()    
+```
+
+### Multilevel Analysis
+
+summary of mixed models results of the contemporaneous contact effects.
+
+```{r metaGeneralLmer, include=FALSE}
+# lme
+# Study 1: 
+workerWithinBetween$AttitudesDutch <- workerWithinBetween$thermometerDutch_1
+mdlWorker$lmerInterceptAttTypeTbl <- lmer(
+    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    data = workerWithinBetween
+  )
+workerWithinBetween$AttitudesDutch_zwc <- workerWithinBetween$thermometerDutch_1
+mdlWorker$lmerInterceptAttTypeTblZ <- lmer(
+    AttitudesDutch_zwc ~ OutgroupInteraction_zwc + NonOutgroupInteraction_zwc + (1 | PID),
+    data = workerWithinBetween
+  )
+# Study 2:
+mdlStudent$lmerSlopesAttType <- lmer(
+    AttitudesDutch ~
+      OutgroupInteraction + NonOutgroupInteraction +
+      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+    data = studentWithinBetween
+  )
+mdlStudent$lmerSlopesAttTypeZ <- lmer(
+    AttitudesDutch_zwc ~
+      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc +
+      (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
+    data = studentWithinBetween
+  )
+# Study 3:
+mdlMedical$lmerSlopesAttType <- lmer(
+    AttitudesDutch ~
+      OutgroupInteraction + NonOutgroupInteraction +
+      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+    data = medicalWithinBetween
+  )
+mdlMedical$lmerSlopesAttTypeZ <- lmer(
+    AttitudesDutch_zwc ~
+      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc +
+      (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
+    data = medicalWithinBetween
+  )
+
+mdlTblElementsGeneralLmer <- list(
+  c(mdlWorker$lmerInterceptAttTypeTbl, mdlWorker$lmerInterceptAttTypeTblZ),
+  c(mdlStudent$lmerSlopesAttType, mdlStudent$lmerSlopesAttTypeZ),
+  c(mdlMedical$lmerSlopesAttType, mdlMedical$lmerSlopesAttTypeZ)
+  )
+
+# i =1
+GeneralLmerMetaTbl <- data.frame()
+for (i in 1:length(mdlTblElementsGeneralLmer)){
+  lmerTblTmp <- lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$beta %>%
+  select(
+    coef,
+    B = est,
+    se,
+    lwr,
+    upr,
+    tval,
+    Rsq
+  ) %>%
+  mutate(
+    n = lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$fit$N,
+    m = nrow(.), 
+    sample = str_match(lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$fit$data, "worker|student|medical"),
+    coef = gsub(":", ".", coef)
+  )
+  GeneralLmerMetaTbl <- rbind(GeneralLmerMetaTbl, lmerTblTmp)
+}
+
+GeneralLmerMetaTbl <- GeneralLmerMetaTbl %>% arrange(coef)
+
+GeneralLmerMeta <- metaLmerOut(GeneralLmerMetaTbl,
+                               type = "FE",
+                               name = "GeneralLmer",
+                               title = "Contact Hypothesis — Mixed Effects Regression")
+
+# Alternative Meta:
+      Metaan::estmeta(
+        Beta = GeneralLmerMetaTbl$B[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
+        l = GeneralLmerMetaTbl$lwr[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
+        u = GeneralLmerMetaTbl$upr[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
+        test = "FIXED", # "RANDOM"
+      )
+```
+
+## Core Need Fulfillment
+
+(a) Core Need Fulfillment predicting Interaction Quality.   
+(b) Core Need Fulfillment predicting Outgroup Attitudes.   
+(c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.
+
+```{r metaTheory, include=FALSE}
+# collect relevant models
+# Study 1:
+# Rename variables for consistency
+tblDtS1Needs <- workerOutWithinBetween %>%
+  select(
+    Attitude = thermometerDutch_1,
+    AttitudeZ = thermometerDutch_1_zwc,
+    CoreNeed = keymotive_fulfillemt_1_cwc,
+    CoreNeedZ = keymotive_fulfillemt_1_zwc,
+    QualityRaw = quality_overall_1,
+    Quality = quality_overall_1_cwc,
+    QualityZ = quality_overall_1_zwc,
+    PID = PID
+  )
+# Quality ~ CoreNeed
+tblLmerS1QltInterceptCore <- lmer(
+  QualityRaw ~ CoreNeed + (1 | PID),
+  data = tblDtS1Needs
+)
+tblLmerS1QltInterceptCoreZ <- lmer(
+  QualityZ ~ CoreNeedZ + (1 | PID),
+  data = tblDtS1Needs
+)
+# Attitude ~ CoreNeed
+tblLmerS1AttSlopeCore <- lmer(
+  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS1Needs
+)
+tblLmerS1AttSlopeCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS1Needs
+)
+# Attitude ~ CoreNeed + Quality
+tblLmerS1AttSlopeCoreQlt <- lmer(
+  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
+  data = tblDtS1Needs
+)
+tblLmerS1AttSlopeCoreQltZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
+  data = tblDtS1Needs
+)
+
+# Study 2:
+# Rename variables for consistency
+tblDtS2Needs <- studentOutWithinBetween %>%
+  select(
+    Attitude = AttitudesDutch,
+    AttitudeZ = AttitudesDutch_zwc,
+    CoreNeed = KeyNeedFullfillment_cwc,
+    CoreNeedZ = KeyNeedFullfillment_zwc,
+    QualityRaw = quality_overall,
+    Quality = quality_overall_cwc,
+    QualityZ = quality_overall_zwc,
+    PID = PID
+  )
+# Quality ~ CoreNeed
+tblLmerS2QltSlopesCore <- lmer(
+  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS2Needs
+)
+tblLmerS2QltSlopesCoreZ <- lmer(
+  QualityZ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS2Needs
+)
+# Attitude ~ CoreNeed
+tblLmerS2AttSlopesCore <- lmer(
+  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS2Needs
+)
+tblLmerS2AttSlopesCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS2Needs
+)
+# Attitude ~ CoreNeed + Quality
+tblLmerS2AttSlopesCoreQlt <- lmer(
+  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
+  data = tblDtS2Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+tblLmerS2AttSlopesCoreQltZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
+  data = tblDtS2Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+
+# Study 3:
+# Rename variables for consistency
+tblDtS3Needs <- medicalOutWithinBetween %>%
+  select(
+    Attitude = AttitudesDutch,
+    AttitudeZ = AttitudesDutch_zwc,
+    CoreNeed = KeyNeedFulfillment_cwc,
+    CoreNeedZ = KeyNeedFulfillment_zwc,
+    Allport = AllportsCondition_cwc,
+    AllportZ = AllportsCondition_zwc,
+    QualityRaw = qualityOverall,
+    Quality = qualityOverall_cwc,
+    QualityZ = qualityOverall_zwc,
+    PID = PID
+  )
+# Quality ~ CoreNeed
+tblLmerS3QltSlopesCore <- lmer(
+  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3QltSlopesCoreZ <- lmer(
+  QualityZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ CoreNeed
+tblLmerS3AttSlopesCore <- lmer(
+  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3AttSlopesCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ CoreNeed + Quality
+tblLmerS3AttSlopesCoreQlt <- lmer(
+  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+tblLmerS3AttSlopesCoreQltZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+# Quality ~ Allport
+tblLmerS3QltSlopesAllport <- lmer(
+  QualityRaw ~ Allport + (1 + Allport | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3QltSlopesAllportZ <- lmer(
+  QualityZ ~ AllportZ + (1 + AllportZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ Allport
+tblLmerS3AttSlopesAllport <- lmer(
+  Attitude ~ Allport + (1 + Allport | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3AttSlopesAllportZ <- lmer(
+  AttitudeZ ~ AllportZ + (1 + AllportZ | PID),
+  data = tblDtS3Needs
+)
+# Attitude ~ Allport + Quality
+tblLmerS3AttSlopesAllportQlt <- lmer(
+  Attitude ~ Allport + Quality + (1 + Allport + Quality | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+tblLmerS3AttSlopesAllportQltZ <- lmer(
+  AttitudeZ ~ AllportZ + QualityZ + (1 + AllportZ + QualityZ | PID),
+  data = tblDtS3Needs,
+  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+)
+# Attitude ~ Allport + CoreNeed
+tblLmerS3AttSlopesAllportCore <- lmer(
+  Attitude ~ CoreNeed + Allport + (1 + CoreNeed + Allport | PID),
+  data = tblDtS3Needs
+)
+tblLmerS3AttSlopesAllportCoreZ <- lmer(
+  AttitudeZ ~ CoreNeedZ + AllportZ + (1 + CoreNeedZ + AllportZ | PID),
+  data = tblDtS3Needs
+)
+
+mdlTblElementsTheoryLmer <- list(
+  # Study 1:
+  c(tblLmerS1QltInterceptCore, tblLmerS1QltInterceptCoreZ),
+  c(tblLmerS1AttSlopeCore, tblLmerS1AttSlopeCoreZ),
+  c(tblLmerS1AttSlopeCoreQlt, tblLmerS1AttSlopeCoreQltZ),
+  # Study 2:
+  c(tblLmerS2QltSlopesCore, tblLmerS2QltSlopesCoreZ),
+  c(tblLmerS2AttSlopesCore, tblLmerS2AttSlopesCoreZ),
+  c(tblLmerS2AttSlopesCoreQlt, tblLmerS2AttSlopesCoreQltZ),
+  # Study 3:
+  c(tblLmerS3QltSlopesCore, tblLmerS3QltSlopesCoreZ),
+  c(tblLmerS3AttSlopesCore, tblLmerS3AttSlopesCoreZ),
+  c(tblLmerS3AttSlopesCoreQlt, tblLmerS3AttSlopesCoreQltZ),
+  c(tblLmerS3QltSlopesAllport, tblLmerS3QltSlopesAllportZ),
+  c(tblLmerS3AttSlopesAllport, tblLmerS3AttSlopesAllportZ),
+  c(tblLmerS3AttSlopesAllportQlt, tblLmerS3AttSlopesAllportQltZ),
+  c(tblLmerS3AttSlopesAllportCore, tblLmerS3AttSlopesAllportCoreZ)
+  )
+
+# i =1
+theoryMetaTbl <- data.frame()
+for (i in 1:length(mdlTblElementsTheoryLmer)){
+  lmerTblTmp <- lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$beta %>%
+  select(
+    coef,
+    B = est,
+    se,
+    lwr,
+    upr,
+    tval,
+    Rsq
+  ) %>%
+  mutate(
+    n = lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$N,
+    m = nrow(.), 
+    dv = gsub("Raw", "", str_extract(lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$formula,".+?(?= ~)")),
+    sample = gsub("S", "Study", str_extract(lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$data, "S1|S2|S3")),
+    formula = lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$formula,
+    coef = gsub(":", ".", coef)
+  )
+  theoryMetaTbl <- rbind(theoryMetaTbl, lmerTblTmp)
+}
+
+theoryMetaTblNoAllport <- theoryMetaTbl %>%
+  filter(!grepl("Allport",formula)) %>% 
+  mutate(formula = gsub(" \\+ \\(.*", "", formula)) %>%
+  arrange(formula, coef, sample)
+
+TheoryMetaQualityNeed <-
+  metaLmerOut(
+    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "QualityRaw ~ CoreNeed"),
+    type = "FE",
+    name = "TheoryQualityCore",
+    title = "Quality ~ CoreNeed"
+  )
+
+TheoryMetaAttitudeNeed <-
+  metaLmerOut(
+    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed"),
+    type = "FE",
+    name = "TheoryAttitudeCore",
+    title = "Attitude ~ CoreNeed"
+  )
+
+TheoryMetaAttitudeNeedQuality <-
+  metaLmerOut(
+    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed + Quality"),
+    type = "FE",
+    name = "TheoryAttitudeCoreQuality",
+    title = "Attitude ~ CoreNeed + Quality"
+  )
+```
+
+## Robustness Analyses
+
+(a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).  
+(b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).
+
+```{r metaRobust, include=FALSE}
+# Full Sample
+# Study 1:
+robustTblWorkerFull <- 
+  workerWithinBetween %>%
+  select(
+    AttitudesDutch = thermometerDutch_1,
+    AttitudesDutch_zwc = thermometerDutch_1_zwc,
+    CoreNeed_cwc = keyMotiveFulfilled_cwc,
+    CoreNeed_zwc = keyMotiveFulfilled_zwc,
+    OutgroupInteraction = OutgroupInteraction,
+    OutgroupInteraction_zwc = OutgroupInteraction_zwc,
+    PID = PID
+  )
+mdlWorkerLmerSlopesAttCoreInt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc * OutgroupInteraction +
+      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
+    data = robustTblWorkerFull
+  )
+mdlWorkerLmerSlopesAttCoreIntZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc * OutgroupInteraction_zwc +
+      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
+    data = robustTblWorkerFull
+  )
+#Study 2:
+robustTblStudentFull <- 
+  studentWithinBetween %>%
+  select(
+    AttitudesDutch = AttitudesDutch,
+    AttitudesDutch_zwc = AttitudesDutch_zwc,
+    CoreNeed_cwc = KeyNeedFullfillment_cwc,
+    CoreNeed_zwc = KeyNeedFullfillment_zwc,
+    OutgroupInteraction = OutgroupInteraction,
+    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
+    PID = PID
+  )
+mdlStudentLmerSlopesAttCoreInt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc * OutgroupInteraction +
+      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
+    data = robustTblStudentFull
+  )
+mdlStudentLmerSlopesAttCoreIntZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc * OutgroupInteraction_zwc +
+      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
+    data = robustTblStudentFull
+  )
+#Study 3:
+robustTblMedicalFull <- 
+  medicalWithinBetween %>%
+  select(
+    AttitudesDutch = AttitudesDutch,
+    AttitudesDutch_zwc = AttitudesDutch_zwc,
+    CoreNeed_cwc = KeyNeedFulfillment_cwc,
+    CoreNeed_zwc = KeyNeedFulfillment_zwc,
+    OutgroupInteraction = OutgroupInteraction,
+    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
+    PID = PID
+  )
+mdlMedicalLmerSlopesAttCoreInt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc * OutgroupInteraction +
+      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
+    #data = dtMedical$full
+    data = robustTblMedicalFull
+  )
+mdlMedicalLmerSlopesAttCoreIntZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc * OutgroupInteraction_zwc +
+      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
+    #data = dtMedical$full
+    data = robustTblMedicalFull
+  )
+
+# SDT
+# Study 1:
+robustTblWorkerOut <- 
+  workerOutWithinBetween %>%
+  select(
+    AttitudesDutch = thermometerDutch_1,
+    AttitudesDutch_zwc = thermometerDutch_1_zwc,
+    CoreNeed_cwc = keymotive_fulfillemt_1_cwc,
+    CoreNeed_zwc = keymotive_fulfillemt_1_zwc,
+    Competence_cwc = competence_1_cwc,
+    Competence_zwc = competence_1_zwc,
+    Autonomy_cwc = autonomy_1_cwc,
+    Autonomy_zwc = autonomy_1_zwc,
+    Relatedness_cwc = relatedness_1_cwc,
+    Relatedness_zwc = relatedness_1_zwc,
+    PID = PID
+  )
+mdlWorkerOutLmerSlopesCoreSdt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = robustTblWorkerOut
+  )
+mdlWorkerOutLmerSlopesCoreSdtZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
+      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
+    data = robustTblWorkerOut
+  )
+# Study 2:
+robustTblStudentOut <- 
+  studentOutWithinBetween %>%
+  select(
+    AttitudesDutch = AttitudesDutch,
+    AttitudesDutch_zwc = AttitudesDutch_zwc,
+    CoreNeed_cwc = KeyNeedFullfillment_cwc,
+    CoreNeed_zwc = KeyNeedFullfillment_zwc,
+    Competence_cwc = Competence_cwc,
+    Competence_zwc = Competence_zwc,
+    Autonomy_cwc = Autonomy_cwc,
+    Autonomy_zwc = Autonomy_zwc,
+    Relatedness_cwc = Relatedness_cwc,
+    Relatedness_zwc = Relatedness_zwc,
+    PID = PID
+  )
+mdlStudentOutLmerSlopesCoreSdt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = robustTblStudentOut
+  )
+mdlStudentOutLmerSlopesCoreSdtZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
+      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
+    data = robustTblStudentOut
+  )
+# Study 3:
+robustTblMedicalOut <- 
+  medicalOutWithinBetween %>%
+  select(
+    AttitudesDutch = AttitudesDutch,
+    AttitudesDutch_zwc = AttitudesDutch_zwc,
+    CoreNeed_cwc = KeyNeedFulfillment_cwc,
+    CoreNeed_zwc = KeyNeedFulfillment_zwc,
+    Competence_cwc = Competence_cwc,
+    Competence_zwc = Competence_zwc,
+    Autonomy_cwc = Autonomy_cwc,
+    Autonomy_zwc = Autonomy_zwc,
+    Relatedness_cwc = Relatedness_cwc,
+    Relatedness_zwc = Relatedness_zwc,
+    PID = PID
+  )
+mdlMedicalOutLmerSlopesCoreSdt <- lmer(
+    AttitudesDutch ~
+      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
+      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
+    data = robustTblMedicalOut
+  )
+mdlMedicalOutLmerSlopesCoreSdtZ <- lmer(
+    AttitudesDutch_zwc ~
+      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
+      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
+    data = robustTblMedicalOut
+  )
+
+mdlRobustTblElements <- list(
+  # full
+  c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ),
+  c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ),
+  c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ),
+  # outgroup
+  c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ),
+  c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ),
+  c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ)
+  )
+
+# i =1
+robustMetaTbl <- data.frame()
+for (i in 1:length(mdlRobustTblElements)){
+  lmerTblTmp <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$beta %>%
+  select(
+    coef,
+    B = est,
+    se,
+    lwr,
+    upr,
+    tval,
+    Rsq
+  ) %>%
+  mutate(
+    n = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$N,
+    m = nrow(.), 
+    #dv = gsub("Dutch", "", str_extract(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,".+?(?= ~)")),
+    sample = str_match(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$data, "Tbl(.*?)(Full|Out)")[2],
+    formula = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,
+    coef = gsub(":", ".", coef)
+  )
+  robustMetaTbl <- rbind(robustMetaTbl, lmerTblTmp)
+}
+
+robustMetaTbl <- robustMetaTbl %>%
+  arrange(formula, match(
+    coef,
+    c(
+      "CoreNeed_zwc",
+      "OutgroupInteraction_zwc",
+      "CoreNeed_zwc.OutgroupInteraction_zwc",
+      "Autonomy_zwc",
+      "Competence_zwc",
+      "Relatedness_zwc"
+    )
+  )) %>% 
+  mutate(formula = gsub(" \\+ \\(.*", "", formula))
+
+robustMetaContact <-
+  metaLmerOut(
+    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc * OutgroupInteraction"),
+    type = "FE",
+    name = "RobustContact",
+    title = "Robustness — Contact and Need Fulfillment"
+  )
+
+robustMetaSDT <-
+  metaLmerOut(
+    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc + Competence_cwc + Autonomy_cwc +      Relatedness_cwc"),
+    type = "FE",
+    name = "RobustSDT",
+    title = "Robustness — Other Needs"
+  )
+```
+
 # **Export for Methods and Results**

### 2022-03-01 manuscript.tex
affil adj
Updates from Overleaf

--- 2022-01-17 manuscript.tex
@@
 \affil[1]{University of Groningen, Department of Psychology}
-\affil[2]{Any additional affiliations still need to be added.}
+\affil[2]{Any additional affiliations still need to be added}
 
@@
 \abstract{
-Abstract goes here.
+Modern intergroup contact research faces two main challenges: (1) When does a positively perceived interaction with an outgroup member translate to positive intergroup contact.
+(2) Do the often between-person studied effects hold within-person?
+Here we present three extensive longitudinal studies of recent migrants to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297).
+We find that  fulfillment of psychological needs, going through perceived interaction quality, are a strong predictor of positive intergroup attitudes.
+Across the three studies, we also find inconsistent evidence for interaction frequencies and average interaction quality in predicting outgroup attitudes.
+Finally, situational needs remained the core predictor of outgroup attitudes even after controlling for Allport's contact conditions or more general fundamental needs.
+As one of the first studies to test intergroup contact theory using extensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
 
-\noindent\textbf{Public significance statement}: Significance Statement goes here.
+\noindent\textbf{Public significance statement}: In this paper we provide evidence that the fulfillment of situational psychological needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
+This offers testament to the emerging practice of capturing real-life interactions using extensive longitudinal data.
+It also gives weight to motivational fulfillment as a flexible and relevant mechanism in understanding positive intergroup contact.
 }
@@
   \caption{Contact Hypothesis}
+  \label{fig:ContactHypothesis}
   \begin{subfigure}{\textwidth}
     \caption{}
-    \centering\includegraphics[width=0.75\textwidth]{Figures/forestBootstrappedGeneralLm.png}
+    \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricGeneralLm.png}
   \end{subfigure}
@@
 % aims re-iterated
-In this paper we set out to (1) test the basic predictions of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data, (2) we proposed that the fulfillment situational psychological needs meaningfully predicts positive outgroup attitudes, and (3) that the fulfillment of psychological needs (and Allport's conditions) have their effect (partially) through perceived interaction quality.
+The aim of this project was threefold.
+We (1) tested the basic predictions of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data.
+We also (2) proposed that the fulfillment of situational psychological needs meaningfully predicts positive outgroup attitudes.
+Finally, we (3) assessed whether the fulfillment of psychological needs (and Allport's conditions) have their effect (partially) through perceived interaction quality.
 
 % Contact hypothesis in ESM data [inconsistent in aggregate but consistent in ML analysis]
-When considering the results of the three studies jointly, we find mixed results for the basic intergroup contact hypothesis.
-The aggregated number of outgroup interactions across all measurements only had a significant effect on average outgroup attitudes in one of the three studies and in that study there was no significant effect of average interaction quality on outgroup attitudes (which was significant for the other two studies).
-This meant that only for our smallest study did we find the expected interaction between interaction frequency and interaction quality when looking at the aggregated data across all measurements.
-However, once we considered the effect of having an interaction with an outgroup member (vs.
-not having an outgroup interaction) within the participants, we find that intergroup contact is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account).
+When considering the results of the three studies jointly, we found mixed results for the basic intergroup contact hypothesis.
+More specifically, we observe that seperating between between-subjects and within-subjects effects is crucial.
+For between-subjects effects, we did not observe a consistent predictor of outgroup attitudes when aggregating people's interaction frequencies and average interaction quality; neither interaction quality, or interaction quality, nor their interaction was a significant predictor across all studies (also see Figure \ref{fig:ContactHypothesis}a).
+However, once we used multilevel modeling to separate effects into a between-subjects and within-subjects part, we found that when having an interaction with an outgroup member (vs.
+not having an outgroup interaction),intergroup contact is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account; also see Figure \ref{fig:ContactHypothesis}b).
 While this later results is in line with our expectations, the earlier aggregate findings are surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
-Even though this inconsistency with past research might be a data artefact (e.g., because most people reported more substantially mode measurements during which they did not have an outgroup interaction), the absence of this aggregate effect could underline the fact that cross-sectional retrospective data might suffer from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
-In summary, we thus find that when we aggregate interaction frequencies and interaction quality from our intensive longitudinal data we find inconsistent results from the past literature but within participants intergroup contacts are significantly related with positive outgroup attitudes.
+Even though this inconsistency with past research might be a data artefact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction), the absence of this aggregate effect could underline the fact that cross-sectional retrospective data might might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
+In summary, we thus find that when we aggregate interaction frequencies and interaction quality from our intensive longitudinal data we find inconsistent results from the past literature but in line with past literature within participants intergroup contacts are significantly related with positive outgroup attitudes.
 
@@
 We find that in all three extensive longitudinal datasets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
-We find that in all three studies the effect of core need fulfillment on outgroup attitudes is either fully or partially through its effect on quality perceptions, and we find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
-In fact we find that our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
+We find that in all three studies the effect of core need fulfillment on outgroup attitudes goes either fully or partially through interaction quality.
+We also find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
+In fact, our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
 In most cases the core need even took over the variances previously explained by the self-determination theory needs.
-We thus find strong evidence that within everyday life interactions of recent migrants with majority group members, the perception that one's interaction specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
+We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
 As such the data offers a first test of the motivational basis of intergroup contact.

### 2022-03-02 Supplemental-Material-B-Annotated-Analysis.Rmd
forest plots added

@@
 
-summary of regression results from the aggregated contact and interaction quality data.
-
 ```{r metaGeneralLm, include=FALSE}
@@
 
+![Summary of regression results from the aggregated contact and interaction quality data.](Figures/forestParametricGeneralLm.png)
+
 ### Multilevel Analysis
-
-summary of mixed models results of the contemporaneous contact effects.
 
@@
 
+![Summary of mixed models results of the contemporaneous contact effects.](Figures/forestParametricFEGeneralLmer.png)
+
 ## Core Need Fulfillment
-
-(a) Core Need Fulfillment predicting Interaction Quality.   
-(b) Core Need Fulfillment predicting Outgroup Attitudes.   
-(c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.
 
@@
 
+![Core Need Fulfillment predicting Interaction Quality.](Figures/forestParametricFETheoryQualityCore.png)
+
+![ore Need Fulfillment predicting Outgroup Attitudes.](Figures/forestParametricFETheoryAttitudeCore.png)
+
+![Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.](Figures/forestParametricFETheoryAttitudeCoreQuality.png)
+
 ## Robustness Analyses
-
-(a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).  
-(b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).
 
@@
 
+![Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).](Figures/forestParametricFERobustContact.png)
+
+![Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).](Figures/forestParametricFERobustSDT.png)
+
 # **Export for Methods and Results**

### 2022-03-04 Methods-and-Results.Rmd
Update Methods-and-Results.Rmd

@@
                                       beta.Worker = NA, 
+                                      lwr.Worker = NA, 
+                                      upr.Worker = NA, 
                                       CI.Worker = NA,
                                       beta.Student = NA, 
+                                      lwr.Student = NA, 
+                                      upr.Student = NA, 
                                       CI.Student = NA,
                                       beta.Medical = NA,
+                                      lwr.Medical = NA,
+                                      upr.Medical = NA,
                                       CI.Medical = NA, 
                                       RE.beta = NA,
+                                      lwr.RE = NA,
+                                      upr.RE = NA,
                                       RE.CI = NA,
@@
       meta.parametric.sum$beta.Medical[i] <- meta.parametric[[var[i]]]$yi[3]
+
+      meta.parametric.sum$lwr.Worker[i] <- meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1])
+      meta.parametric.sum$lwr.Student[i] <- meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2])
+      meta.parametric.sum$lwr.Medical[i] <- meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3])
+
+      meta.parametric.sum$upr.Worker[i] <- meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1])
+      meta.parametric.sum$upr.Student[i] <- meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2])
+      meta.parametric.sum$upr.Medical[i] <- meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3])
+
       meta.parametric.sum$CI.Worker[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),", ",round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),"]",sep="")
@@
       meta.parametric.sum$CI.Medical[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),", ",round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),"]",sep="")
+
       meta.parametric.sum$RE.beta[i] <- meta.parametric[[var[i]]]$b
+      meta.parametric.sum$lwr.RE[i] <- meta.parametric[[var[i]]]$ci.lb
+      meta.parametric.sum$upr.RE[i] <- meta.parametric[[var[i]]]$ci.ub
       meta.parametric.sum$RE.CI[i] <- paste("[",
@@
       meta.parametric.sum$RE.star[i] <- ifelse(meta.parametric.sum$RE.pval[i]<0.001,"***",ifelse(meta.parametric.sum$RE.pval[i]<0.01,"**",ifelse(meta.parametric.sum$RE.pval[i]<0.05,"*","")))
+
 }
     #meta.parametric
+
+    meta.parametric.plt.data <- meta.parametric.sum
+
+    meta.parametric.sum <- meta.parametric.sum %>%
+      select(-starts_with("lwr"),
+             -starts_with("upr"))
 
@@
     dev.off()
+
+    meta.parametric.plt.data <- data.table(meta.parametric.plt.data) %>% 
+        mutate(
+          beta.RE = RE.beta,
+          CI.RE = RE.CI,
+          pval.RE = RE.pval,
+          star.RE = RE.star
+        ) %>%
+      select(-starts_with("RE."))
+
+    meta.parametric.plt.widedata <- data.table::melt.data.table(
+      data = meta.parametric.plt.data,
+      id.vars = c("effect", "name"),
+      measure.vars = patterns(
+        beta = "beta",
+        lwr = "lwr",
+        upr = "upr",
+        CI = "CI",
+        pval = "pval",
+        star = "star"
+      ),
+      variable = "sample" # sample info missing
+    )
 

### 2022-03-08 Methods-and-Results.Rmd
joint forest plot function added

@@
 
-      meta.parametric.sum$CI.Worker[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),", ",round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2),"]",sep="")
-      meta.parametric.sum$CI.Student[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),", ",round(meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2),"]",sep="")
-      meta.parametric.sum$CI.Medical[i] <- paste("[",                                  round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),", ",round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2),"]",sep="")
+      meta.parametric.sum$CI.Worker[i] <- paste("[", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2)),", ", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2)),"]",sep="")
+      meta.parametric.sum$CI.Student[i] <- paste("[", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2)),", ", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2)),"]",sep="")
+      meta.parametric.sum$CI.Medical[i] <- paste("[", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2)),", ", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2)),"]",sep="")
 
@@
                   mi = m,
-                  r2i = Rsq)
+                  r2i = Rsq)  %>%
+    mutate(effLwr = yi - 1.96 * sqrt(vi),
+           effUpr = yi + 1.96 * sqrt(vi),
+           effCI = paste("[", format(round(effLwr, 2), nsmall = 2), ", ", format(round(effUpr, 2), nsmall = 2), "]", sep = ""),
+           name = strLabFix(coef),
+           study = strStudyFix(sample))
+
     meta <- rma(yi = yi,
@@
     k <- length(var) * length(studies)
-    png(file = "Figures/forestParametricGeneralLm.png", height = 200 + 40*k^.85) 
+    png(file = "Figures/forestParametricGeneralLmOld.png", height = 200 + 40*k^.85) 
       metafor::forest(meta, xlim=c(-2, 2), cex=0.75, ylim=c(-1, 20), rows=c(22:20,16:14,10:8,4:2), 
@@
 
-    meta.parametric.plt.widedata <- data.table::melt.data.table(
-      data = meta.parametric.plt.data,
-      id.vars = c("effect", "name"),
-      measure.vars = patterns(
-        beta = "beta",
-        lwr = "lwr",
-        upr = "upr",
-        CI = "CI",
-        pval = "pval",
-        star = "star"
+  library(splitstackshape)
+    meta.parametric.plt.longdata <-
+      merged.stack(
+        meta.parametric.plt.data,
+        var.stubs = c("beta", "lwr", "upr", "CI", "pval", "star"),
+        sep = "."
+      ) %>%
+      rename(sample = .time_1) %>%
+      mutate(sample = gsub('Worker', 'Study 1',
+                      gsub('Student', 'Study 2',
+                      gsub('Medical', 'Study 3', sample)
+                           ))) %>%
+    arrange(match(effect, c("SumContactNL", "AvQuality", "SumContactNL.AvQuality")), 
+            match(sample, c("Study 1", "Study 2", "Study 3", "RE")))
+
+    alpha <- 0.05
+
+  meta.parametric.plt.longdata2 <- meta.parametric.plt.longdata %>%
+    mutate(
+      index = as.integer(sapply(seq(from = 2, by=6, length.out = 3), seq, length.out=4)),
+      vi = ((upr - lwr)/(2 * qnorm(alpha/2, lower.tail = FALSE)))^2,
+      wi = 1/sqrt(vi),
+      psize = wi/sum(wi, na.rm = TRUE),
+      psize2 = (psize - min(psize, na.rm = TRUE))/(max(psize, na.rm = TRUE) - min(psize, na.rm = TRUE)),
+      psize3 = (psize2 * 1) + 0.5
+    )
+
+  polyDat <- data.frame(
+    y = c(
+      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"],
+      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"] - .25,
+      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"],
+      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"] + .25
     ),
-      variable = "sample" # sample info missing
-    )
+    x = c(
+      meta.parametric.plt.longdata2$lwr[meta.parametric.plt.longdata2$sample == "RE"],
+      meta.parametric.plt.longdata2$beta[meta.parametric.plt.longdata2$sample == "RE"],
+      meta.parametric.plt.longdata2$upr[meta.parametric.plt.longdata2$sample == "RE"],
+      meta.parametric.plt.longdata2$beta[meta.parametric.plt.longdata2$sample == "RE"]
+    ),
+    lab = rep(paste("RE", 1:3), 4)
+  )
+
+  lab <- lapply(unique(meta.parametric.plt.longdata2$name), append, c(unique(meta.parametric.plt.longdata2$sample), "")) %>% unlist
+
+  plot1 <- ggplot() +
+    geom_point(
+      data = meta.parametric.plt.longdata2[sample != "RE",],
+      aes(y = index, x = beta),
+      shape = 15,
+      size = meta.parametric.plt.longdata2[sample != "RE", psize3] * 3
+    ) +
+    geom_errorbarh(data = meta.parametric.plt.longdata2[sample != "RE",],
+                   aes(y = index, xmin = lwr, xmax = upr),
+                   height = 0.25) +
+    geom_polygon(data = polyDat, 
+                 mapping = aes(x = x, y = y, group = lab)) +
+    geom_vline(
+      xintercept = 0,
+      color = "black",
+      linetype = "dashed",
+      cex = 0.5,
+      alpha = 1
+    ) +
+    scale_y_continuous(
+      name = "",
+      expand  = expansion(add = 1),
+      breaks = seq(lab),
+      labels = lab,
+      trans = "reverse"
+    ) +
+    scale_x_continuous(
+      limits = c(-1, 1),
+      breaks = seq(-1, 1, 0.5),
+      expand = c(0, 0)
+    ) +
+    xlab("Semi-Partial Correlation (95% CI)") +
+    ggtitle("Predictors by Study") +
+    theme_Publication() +
+    theme(
+      plot.title = element_text(hjust = 0, size=12, face = "bold"),
+      plot.title.position = "plot",
+      panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      axis.line.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      axis.text.y = element_text(size = 12, colour = "black", hjust=0, face = rep(c("bold", rep("plain", 5)),3)),
+      axis.line.x = element_line(colour = "black"),
+      axis.text.x.bottom = element_text(size = 12, colour = "black"),
+      axis.title.x = element_text(size = 12, colour = "black")
+    )
+
+## Estiamte and CI table
+  tab1 <- ggplot(meta.parametric.plt.longdata2, aes(y = lab)) +
+    ylab(NULL) + xlab("  ") +
+    labs(title = "space") +
+    geom_text(aes(
+      y = rev(index),
+      x = 1,
+      label = paste(sprintf("%0.2f", round(beta, digits = 2)), CI)
+    ),
+    size = 4,
+    hjust = 1) + 
+    scale_x_continuous(
+      limits = c(-1, 1)
+    ) +
+    ggtitle("Estimate [95% CI]") +
+    theme_Publication() +
+    theme(
+      plot.title = element_text(hjust = 1, size = 12),
+      axis.line = element_blank(),
+      axis.text.x = element_text(color = "white"),
+      axis.text.y = element_blank(),
+      axis.ticks = element_blank(),
+      axis.title.y = element_blank(),
+      legend.position = "none",
+      panel.background = element_blank(),
+      panel.border = element_blank(),
+      panel.grid.major = element_blank(),
+      panel.grid.minor = element_blank(),
+      plot.background = element_blank()
+    )
+
+grid.arrange(plot1, tab1, layout_matrix = matrix(c(1,1,1,2), nrow = 1))
+
+png(file = "Figures/forestParametricGeneralLm.png", width = 700) 
+  grid.arrange(plot1, tab1, layout_matrix = matrix(c(1,1,1,2), nrow = 1))
+dev.off()
 
@@
 
-# Alternative Meta:
-      Metaan::estmeta(
-        Beta = GeneralLmerMetaTbl$B[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
-        l = GeneralLmerMetaTbl$lwr[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
-        u = GeneralLmerMetaTbl$upr[GeneralLmerMetaTbl$coef == "OutgroupInteraction_zwc"],
-        test = "FIXED", # "RANDOM"
-      )
+```
+
+```{generalForestPltComb}
+effGeneral <- rbind(
+  eff %>%
+    filter(coef != "(Intercept)") %>%
+    mutate(analysis = "(A) Aggregate Linear Regression",
+           metaId = paste(coef, analysis, sep = ".")),
+  GeneralLmerMeta$eff %>%
+    mutate(analysis = "(B) Mixed Effects Regression",
+           metaId = paste(coef, analysis, sep = "."))
+)
+
+metaSubForest(effGeneral, 
+              title = "Meta Analysis: Forest Plot Contact Hypothesis \n[Parametric]",
+              filename = "GeneralComb_WeirdScale",
+              addAbove = 5,
+              width = 600,
+              height = 600)
 ```
@@
 
+```{theoryForestPltComb}
+effTheory <- rbind(
+  TheoryMetaQualityNeed$eff %>%
+    filter(coef != "(Intercept)") %>%
+    mutate(analysis = "(A) Quality ~ Core Need",
+           metaId = paste(coef, analysis, sep = ".")),
+  TheoryMetaAttitudeNeed$eff %>%
+    mutate(analysis = "(B) Attitude ~ Core Need",
+           metaId = paste(coef, analysis, sep = ".")),
+  TheoryMetaAttitudeNeedQuality$eff %>%
+    mutate(analysis = "(C) Attitude ~ Core Need + Quality",
+           metaId = paste(coef, analysis, sep = "."))
+)
+
+metaSubForest(effTheory, 
+              title = "Meta Analysis: Forest Plot Core Need Fulfillment \n[Parametric]",
+              filename = "TheoryComb",
+              addAbove = 0,
+              width = 600,
+              height = 600)
+```
+
 ```{r metaRobust, include=FALSE}
@@
 ```
+
+```{robustForestPltComb}
+effRobust <- rbind(
+  robustMetaContact$eff %>%
+    filter(coef != "(Intercept)") %>%
+    mutate(analysis = "(A) Contact and Need Fulfillment",
+           metaId = paste(coef, analysis, sep = ".")),
+  robustMetaSDT$eff %>%
+    mutate(analysis = "(B) Other Needs",
+           metaId = paste(coef, analysis, sep = "."))
+)
+
+metaSubForest(effRobust, 
+              title = "Meta Analysis: Forest Plot Robustness Analysis \n[Parametric]",
+              filename = "RobustnessComb",
+              addAbove = 17,
+              width = 600,
+              height = 800)
+```

### 2022-03-08 scripts/functions/metaLmer.R

@@ -1,52 +1,80 @@
+strLabFix <- function(varIn, ...) {
+  stri_replace_all_fixed(
+    varIn,
+    pattern = c(
+      "SumContactNL", 
+      "AvQuality", 
+      "SumContactNL.AvQuality",
+      "NonOutgroupInteraction",
+      "OutgroupInteraction",
+      "CoreNeedZ",
+      "CoreNeed",
+      "QualityZ",
+      "_zwc",
+      "."
+    ),
+    replacement = c(
+      "Number of Outgroup Contacts",
+      "Average Interaction Quality",
+      "Contact X Quality",
+      "Non-Outgroup Interaction",
+      "Outgroup Interaction",
+      "Core Need Fulfillment",
+      "Core Need Fulfillment",
+      "Interaction Quality",
+      "",
+      " X "
+    ),
+    vectorize_all = FALSE
+  )
+}
+
+strStudyFix <- function(studyIn, ...) {
+  stri_replace_all_fixed(
+    studyIn,
+    pattern = c(
+      "Worker", 
+      "worker", 
+      "Student",
+      "student",
+      "Medical",
+      "medical"
+    ),
+    replacement = c(
+      "Study 1",
+      "Study 1",
+      "Study 2",
+      "Study 2",
+      "Study 3",
+      "Study 3"
+    ),
+    vectorize_all = FALSE
+  )
+}
+
 metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
-  # lmerDataTbl <- theoryMetaTbl
+  # lmerDataTbl <- GeneralLmerMetaTbl
   # name <- "Theory"
   # title <- "Need Fullfillment — Mixed Effects Regression"
   
   # extract parameter names
-  var <-
-    as.character(unique(lmerDataTbl$coef))[!as.character(unique(lmerDataTbl$coef)) %in% c("(Intercept)")]
-  names <-
-    stri_replace_all_fixed(
-      var,
-      pattern = c(
-        "SumContactNL", 
-        "AvQuality", 
-        "SumContactNL.AvQuality",
-        "NonOutgroupInteraction",
-        "OutgroupInteraction",
-        "CoreNeedZ",
-        "CoreNeed",
-        "QualityZ",
-        "_zwc",
-        "."
-      ),
-      replacement = c(
-        "Number of Outgroup Contacts",
-        "Average Interaction Quality",
-        "Contact X Quality",
-        "Non-Outgroup Interaction",
-        "Outgroup Interaction",
-        "Core Need Fulfillment",
[…]

### 2022-03-08 Methods-and-Results.tex
M&R re-run

@@
 
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
+
 \subsubsection{Core Need}
@@
 explained by its effect through perceived interaction quality.
+
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
 
@@
 \input{Tables/mdlRobustlong}
+
+\begin{verbatim}
+effGeneral <- rbind(
+  eff %>%
+    filter(coef != "(Intercept)") %>%
+    mutate(analysis = "(A) Aggregate Linear Regression",
+           metaId = paste(coef, analysis, sep = ".")),
+  GeneralLmerMeta$eff %>%
+    mutate(analysis = "(B) Mixed Effects Regression",
+           metaId = paste(coef, analysis, sep = "."))
+)
+
+metaSubForest(effGeneral, 
+              title = "Meta Analysis: Forest Plot Contact Hypothesis \n[Parametric]",
+              filename = "GeneralComb_WeirdScale",
+              addAbove = 5,
+              width = 600,
+              height = 600)
+\end{verbatim}
+
+\begin{verbatim}
+effTheory <- rbind(
+  TheoryMetaQualityNeed$eff %>%
+    filter(coef != "(Intercept)") %>%
+    mutate(analysis = "(A) Quality ~ Core Need",
+           metaId = paste(coef, analysis, sep = ".")),
+  TheoryMetaAttitudeNeed$eff %>%
+    mutate(analysis = "(B) Attitude ~ Core Need",
+           metaId = paste(coef, analysis, sep = ".")),
+  TheoryMetaAttitudeNeedQuality$eff %>%
+    mutate(analysis = "(C) Attitude ~ Core Need + Quality",
+           metaId = paste(coef, analysis, sep = "."))
+)
+
+metaSubForest(effTheory, 
+              title = "Meta Analysis: Forest Plot Core Need Fulfillment \n[Parametric]",
+              filename = "TheoryComb",
+              addAbove = 0,
+              width = 600,
+              height = 600)
+\end{verbatim}
+
+\begin{verbatim}
+effRobust <- rbind(
+  robustMetaContact$eff %>%
+    filter(coef != "(Intercept)") %>%
+    mutate(analysis = "(A) Contact and Need Fulfillment",
+           metaId = paste(coef, analysis, sep = ".")),
+  robustMetaSDT$eff %>%
+    mutate(analysis = "(B) Other Needs",
+           metaId = paste(coef, analysis, sep = "."))
+)
+
+metaSubForest(effRobust, 
+              title = "Meta Analysis: Forest Plot Robustness Analysis \n[Parametric]",
+              filename = "RobustnessComb",
+              addAbove = 17,
+              width = 600,
+              height = 800)
+\end{verbatim}

### 2022-03-08 Methods-and-Results.Rmd
code display fix

@@
 
-```{generalForestPltComb}
+```{generalForestPltComb, include=FALSE}
 effGeneral <- rbind(
@@
 
-```{theoryForestPltComb}
+```{theoryForestPltComb, include=FALSE}
 effTheory <- rbind(
@@
 
-```{robustForestPltComb}
+```{robustForestPltComb, include=FALSE}
 effRobust <- rbind(

### 2022-03-08 Methods-and-Results.Rmd
missing stats in-text added

@@
 pContactAvgMin <- format(round(min(rContactAvg$P[rownames(rContactAvg$P) != "AvAttitude","AvAttitude"]),3), nsmall = 3)
+
+# Average Interaction Quality and their Average Outgroup Attitudes
+rAttitudeQuality <- dtWorkerSupp$workerAvFreQual %>% 
+  select(AvQuality, AvAttitude) %>%
+  as.matrix %>%
+  rcorr
 ```
@@
 We find that neither the number of interactions nor the number of daily diary responses with an interaction were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`).
-However, we did find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = \hl{X.XX}, \textit{p} = \hl{X.XXX}.
+However, we did find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r format(round(rAttitudeQuality$r[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],2), nsmall = 2)`, \textit{p} = `r format(round(rAttitudeQuality$P[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],3), nsmall = 3)`.
 And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblLong}).
@@
 
-\faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?
+<!-- \faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?  -->
 

### 2022-03-08 Methods-and-Results.tex
code display fix
M & R re-run

--- 2022-01-18 Methods-and-Results.tex
@@
 correlation between the participants' Average Interaction Quality and
-their Average Outgroup Attitudes (\textit{r} = \hl{X.XX}, \textit{p} =
-\hl{X.XXX}. And when considering the number of interactions and average
-interaction quality jointly in a linear regression, we additionally find
-a statistically significant interaction term (\textit{b} = -0.05,
+their Average Outgroup Attitudes (\textit{r} = 0.55, \textit{p} = 0.010.
+And when considering the number of interactions and average interaction
+quality jointly in a linear regression, we additionally find a
+statistically significant interaction term (\textit{b} = -0.05,
 \textit{t}(17) = -2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34), where
@@
 quality.
-
-\faQuestionCircle~Are we sure that we don't want some sort of
-bootstrapped indirect effect?
 
@@
 by its effect through perceived interaction quality.
-
-\faQuestionCircle~Are we sure that we don't want some sort of
-bootstrapped indirect effect?
 

### 2022-03-11 Methods-and-Results.Rmd
OSF data export added

@@
 
-```{robustForestPltComb, include=FALSE}
+```{r robustForestPltComb, include=FALSE}
 effRobust <- rbind(
@@
 ```
+
+```{r OsfExport, include=FALSE}
+# export individual minimal CSV files 
+# STUDY 1:
+write.csv(
+  dtWorkerSupp$workerInteractionType %>%
+    select(
+      "PID",
+      "keyMotiveFulfilled",
+      "competence.daily.all",
+      "autonomy.daily.all",
+      "relatedness.daily.all",
+      "thermometerDutch_1",
+      "keymotive_fulfillemt_1",
+      "competence_1",
+      "autonomy_1",
+      "relatedness_1",
+      "quality_overall_1",
+      "OutgroupInteraction",
+      "NonOutgroupInteraction"
+    ),
+  file = "OSF Files/Data/Study1_minimal.csv"
+)
+
+#STUDY 2:
+write.csv(
+  dtStudentSupp$studentInteractionType %>%
+    select(
+      "PID",
+      "TIDnum",
+      "KeyNeedFullfillment",
+      "Competence",
+      "Autonomy",
+      "Relatedness",
+      "AttitudesDutch",
+      "quality_overall",
+      "OutgroupInteraction",
+      "NonOutgroupInteraction"
+    ),
+  file = "OSF Files/Data/Study2_minimal.csv"
+)
+
+# STUDY 3:
+write.csv(
+  dtMedicalSupp$medicalWithinBetween %>%
+    select(
+      "PID",
+      "TIDnum",
+      "OutgroupInteraction",
+      "NonOutgroupInteraction",
+      "AttitudesDutch",
+      "qualityOverall",
+      "AllportsCondition",
+      "KeyNeedFulfillment",
+      "Competence",
+      "Autonomy",
+      "Relatedness"
+    ),
+  file = "OSF Files/Data/Study3_minimal.csv"
+)
+
+# export joint minimal data as RData file 
+# create environment for joint export
+osfExport <- new.env()
+
+# STUDY 1:
+osfExport$dtWorkerSupp$workerInteractionType <- dtWorkerSupp$workerInteractionType %>%
+  select(
+    "PID",
+    "keyMotiveFulfilled",
+    "competence.daily.all",
+    "autonomy.daily.all",
+    "relatedness.daily.all",
+    "thermometerDutch_1",
+    "keymotive_fulfillemt_1",
+    "competence_1",
+    "autonomy_1",
+    "relatedness_1", 
+     "quality_overall_1", 
+    "OutgroupInteraction",
+    "NonOutgroupInteraction"
+  )
+
+osfExport$dtWorker$full <- dtWorker$full %>%
+  select(
+    "PID",
+    "thermometerDutch_1"
+  )
+
+osfExport$dtWorkerSupp$workerAvFreQual <- dtWorkerSupp$workerAvFreQual
+
+#STUDY 2:
+osfExport$dtStudentSupp$studentInteractionType <- dtStudentSupp$studentInteractionType %>%
+  select(
+    "PID",
+    "TIDnum", 
+    "KeyNeedFullfillment",
+    "Competence",
+    "Autonomy",
+    "Relatedness",
+    "AttitudesDutch",
+    "quality_overall",
+    "OutgroupInteraction",
+    "NonOutgroupInteraction"
+  )
+
+osfExport$dtStudents$full <- dtStudents$full %>%
+  select(
+    "PID",
+    "AttitudesDutch"
+  )
+
+osfExport$dtStudentSupp$studentOutgroupInteraction <- dtStudentSupp$studentOutgroupInteraction %>%
+  select(
+    "PID",
+    "AttitudesDutch"
+  )
+
+osfExport$dtStudentSupp$studentContactFreq <- dtStudentSupp$studentContactFreq
+
+osfExport$dtStudentSupp$studentPltIDs <- dtStudentSupp$studentPltIDs
+
+osfExport$dtStudentSupp$studentOutPltIDs <- dtStudentSupp$studentOutPltIDs
+
+# STUDY 3:
+osfExport$dtMedicalSupp$medicalWithinBetween <- dtMedicalSupp$medicalWithinBetween %>%
+  select(
+    "PID",
+    "TIDnum",
+    "OutgroupInteraction",
+    "OutgroupInteraction_cwc",
+    "OutgroupInteraction_zwc",
+    "NonOutgroupInteraction",
+    "NonOutgroupInteraction_cwc",
+    "NonOutgroupInteraction_zwc",
+    "AttitudesDutch",
+    "AttitudesDutch_cwc",
+    "AttitudesDutch_zwc",
+    "qualityOverall",
+    "qualityOverall_cwc",
+    "qualityOverall_zwc",
+    "AllportsCondition",
+    "AllportsCondition_cwc",
+    "AllportsCondition_zwc",
+    "KeyNeedFulfillment",
+    "KeyNeedFulfillment_cwc",
+    "KeyNeedFulfillment_zwc",
+    "Competence",
+    "Competence_cwc",
+    "Competence_zwc",
+    "Autonomy",
+    "Autonomy_cwc", 
+    "Autonomy_zwc", 
+    "Relatedness",
+    "Relatedness_cwc",
+    "Relatedness_zwc"
+  )
+
+osfExport$dtMedicalSupp$medicalOutWithinBetween <- dtMedicalSupp$medicalOutWithinBetween %>%
+  select(
+    "PID",
+    "TIDnum",
+    "AttitudesDutch",
+    "AttitudesDutch_cwc",
+    "AttitudesDutch_zwc",
+    "qualityOverall",
+    "qualityOverall_cwc",
+    "qualityOverall_zwc",
+    "AllportsCondition",
+    "AllportsCondition_cwc",
+    "AllportsCondition_zwc",
+    "KeyNeedFulfillment",
+    "KeyNeedFulfillment_cwc",
+    "KeyNeedFulfillment_zwc",
+    "Competence",
+    "Competence_cwc",
+    "Competence_zwc",
+    "Autonomy",
+    "Autonomy_cwc", 
+    "Autonomy_zwc", 
+    "Relatedness",
+    "Relatedness_cwc",
+    "Relatedness_zwc"
+  )
+
+osfExport$dtMedical$full <- dtMedical$full %>% 
+  select(
+    "PID",
+    "TIDnum",
+    "AttitudesDutch",
+    "OutgroupInteraction", 
+    "NonOutgroupInteraction",
+    "KeyNeedFulfillment",
+    "KeyNeedFulfillment_cwc",
+    "Competence",
+    "Autonomy", 
+    "Relatedness", 
+    "AllportsCondition", 
+    "qualityOverall"
+  )
+
+osfExport$dtMedicalSupp$medicalContactFreq <- dtMedicalSupp$medicalContactFreq
+
+osfExport$dtMedicalSupp$medicalPltIDs <- dtMedicalSupp$medicalPltIDs
+
+osfExport$dtMedicalSupp$medicalOutPltIDs <- dtMedicalSupp$medicalOutPltIDs
+
+# Export all relevant data for OSF
+save(list = ls(osfExport),
+     envir = osfExport,
+     file = "OSF Files/Data/wrangled.RData")
+```

### 2022-03-11 scripts/functions/metaLmer.R
index fixed

@@ -509,7 +509,7 @@ metaSubForest <- function(effects, title = "", addAbove = 0, filename = NULL, wi
   forestGeneral <- forest(
     metaGeneral,
     cex = 0.75,
-    ylim = c(-1, max(unlist(index)) + addAbove),
+    ylim = c(-1, max(unlist(studyIndex)) + addAbove),
     # alim = c(-1, 1), # only for General Pt.1
     # xlim = c(-2, 2), # only for General Pt.1
     # xlab = NULL, # only for General Pt.1

### 2022-03-14 OSF Files/Data Analysis/Supplemental-Material-B-Annotated-Analysis.Rmd
osf files added

--- 2022-03-02 Supplemental-Material-B-Annotated-Analysis.Rmd
@@
 )
+
+ggplot(data = workerOutWithinBetween,
+       aes(y = thermometerDutch_1, x = keymotive_fulfillemt_1, col = as.factor(PID))) +
+  geom_point(size = 1) + # change size and colour
+  labs(y = "Outgroup Attitudes", 
+       x = "Key Need Fulfillment",
+       ) + # rename axes
+  scale_y_continuous(limits = c(0, 100),
+                     breaks = c(0, 20, 40, 60, 80, 100)) + # y axis limits/range (0, 100), break points
+  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
+  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
+  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red", linetype = "longdash") +
+  geom_line(stat="smooth", 
+            method = "lm", 
+            formula = y ~ x,
+            size = 1,
+            alpha = 0.5) +
+  theme_Publication() +
+  theme(legend.position = "none")
+
 ```
@@
   lme4::VarCorr(mdlWorkerOut$Qlt$lmeSlopesCore)
+
+ggplot(data = workerOutWithinBetween,
+       aes(y = quality_overall_1, x = keymotive_fulfillemt_1, col = as.factor(PID))) +
+  geom_point(size = 1) + # change size and colour
+  labs(y = "Interaction Quality", 
+       x = "Key Need Fulfillment",
+       ) + # rename axes
+  scale_y_continuous(limits = c(-50, 50)) + # y axis limits/range (0, 100), break points
+  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
+  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
+  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red", linetype = "longdash") +
+  geom_line(stat="smooth", 
+            method = "lm", 
+            formula = y ~ x,
+            size = 1,
+            alpha = 0.5) +
+  theme_Publication() +
+  theme(legend.position = "none")
 ```
@@
 )
+
+ggplot(data = studentOutWithinBetween,
+       aes(y = AttitudesDutch, x = KeyNeedFullfillment, group = as.factor(PID))) +
+  geom_point(size = 1, alpha = .2, position = position_jitter(width = 3, height = 3)) + # change size and colour
+  labs(y = "Outgroup Attitudes", 
+       x = "Key Need Fulfillment",
+       ) + # rename axes
+  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
+  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
+  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
+  geom_line(stat="smooth", 
+            method = "lm", 
+            formula = y ~ x,
+            size = 1,
+            alpha = 0.33) +
+  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
+  theme_Publication() +
+  theme(legend.position = "none")
 ```
@@
 )
+
+ggplot(data = studentOutWithinBetween,
+       aes(y = quality_overall, x = KeyNeedFullfillment, group = as.factor(PID))) +
+  geom_point(size = 1, alpha = .2, position = position_jitter(width = 3, height = 3)) + # change size and colour
+  labs(y = "Interaction Quality", 
+       x = "Key Need Fulfillment",
+       ) + # rename axes
+  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
+  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
+  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
+  geom_line(stat="smooth", 
+            method = "lm", 
+            formula = y ~ x,
+            size = 1,
+            alpha = 0.33) +
+  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
+  theme_Publication() +
+  theme(legend.position = "none")
 ```
@@
 )
+
+ggplot(data = medicalOutWithinBetween,
+       aes(y = AttitudesDutch, x = AllportsCondition, group = as.factor(PID))) +
+  geom_point(size = 1, alpha = .15, position = position_jitter(width = 3, height = 3)) + # change size and colour
+  labs(y = "Outgroup Attitude", 
+       x = "Fulfillment Allport's Conditions",
+       ) + # rename axes
+  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
+  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
+  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
+  geom_line(stat="smooth", 
+            method = "lm", 
+            formula = y ~ x,
+            size = 1,
+            alpha = 0.33) +
+  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
+  theme_Publication() +
+  theme(legend.position = "none")
 ```
@@
 
+ggplot(data = medicalOutWithinBetween,
+       aes(y = qualityOverall, x = AllportsCondition, group = as.factor(PID))) +
+  geom_point(size = 1, alpha = .15, position = position_jitter(width = 3, height = 3)) + # change size and colour
+  labs(y = "Interaction Quality", 
+       x = "Fulfillment Allport's Conditions",
+       ) + # rename axes
+  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
+  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
+  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
+  geom_line(stat="smooth", 
+            method = "lm", 
+            formula = y ~ x,
+            size = 1,
+            alpha = 0.33) +
+  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
+  theme_Publication() +
+  theme(legend.position = "none")
 ```
@@
 )
+
+ggplot(data = medicalOutWithinBetween,
+       aes(y = AttitudesDutch, x = KeyNeedFulfillment, group = as.factor(PID))) +
+  geom_point(size = 1, alpha = .15, position = position_jitter(width = 3, height = 3)) + # change size and colour
+  labs(y = "Outgroup Attitudes", 
+       x = "Keyneed Fulfillment",
+       ) + # rename axes
+  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
+  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
+  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
+  geom_line(stat="smooth", 
+            method = "lm", 
+            formula = y ~ x,
+            size = 1,
+            alpha = 0.33) +
+  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
+  theme_Publication() +
+  theme(legend.position = "none")
 ```
@@
 )
+
+ggplot(data = medicalOutWithinBetween,
+       aes(y = qualityOverall, x = KeyNeedFulfillment, group = as.factor(PID))) +
+  geom_point(size = 1, alpha = .15, position = position_jitter(width = 3, height = 3)) + # change size and colour
+  labs(y = "Interaction Quality", 
+       x = "Keyneed Fulfillment",
+       ) + # rename axes
+  scale_y_continuous(limits = c(0, 100)) + # y axis limits/range (0, 100), break points
+  #scale_x_continuous(limits = c(90, 130)) + # x axis limits/range
+  #geom_smooth(method = 'lm', se = F, aes(group = as.factor(PID))) + # fit linear regression line
+  geom_line(stat="smooth", 
+            method = "lm", 
+            formula = y ~ x,
+            size = 1,
+            alpha = 0.33) +
+  geom_smooth(method = 'lm', se = F, aes(group = 1), col = "red") +
+  theme_Publication() +
+  theme(legend.position = "none")
 ```
@@
 
-![ore Need Fulfillment predicting Outgroup Attitudes.](Figures/forestParametricFETheoryAttitudeCore.png)
+![Core Need Fulfillment predicting Outgroup Attitudes.](Figures/forestParametricFETheoryAttitudeCore.png)
 

### 2022-03-14 Supplemental-Material-B-Annotated-Analysis.Rmd
SI blinded

@@
 author:
-- Jannis Kreienkamp^1,2^
-- Maximilian Agostini^1,2^
-- Laura Bringmann^1,2^
-- Peter de Jonge^1,2^
-- Kai Epstude^1,2^
-- ^1^University of Groningen, Department of Psychology
-- ^2^Author order to be discussed; currently alphabetic by last name
+- ██████ ██████████^1^
+- ██████████ ████████^1^
+- █████ █████████^1^
+- █████ ██ █████^1^
+- ███ ███████^1^
+- ^1^██████████ ██ █████████, Department of Psychology
 - "Author Information:"
-- "Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).
-E-mail: <a href='mailto:j.kreienkamp@rug.nl'>j.kreienkamp@rug.nl</a>"
+- "Correspondence concerning this article should be addressed to ██████ ██████████, ██████████ ██ ██████████, █████████ ██ ██████████, █████ ██████████ ███, ████ ██ █████████ ████████████████.
+E-mail: █████████████████"
 - 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
-- 'The data repository for this manuscript is available at <a href="https://osf.io" target="_blank">OSF link goes here</a>'
-- 'The GitHub repository for this manuscript is available at <a href="https://janniscodes.github.io/intergroup-contact-needs/" target="_blank">janniscodes.github.io/intergroup-contact-needs/</a>'
+- 'The data repository for this manuscript is available at <a href="https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970" target="_blank">https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970</a>'
+- 'The GitHub repository for this manuscript is available at <a href="https://github.com/maskedForPeerReview" target="_blank">github.com/maskedForPeerReview</a>'
 date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"

### 2022-03-14 manuscript.tex
Updates from Overleaf

@@
 % define document type (i.e., template. Here: A4 APA manuscript with 12pt font)
-\documentclass[man, 12pt, a4paper]{apa7}
+\documentclass[man, 12pt, a4paper, mask]{apa7}
 
@@
 % Title and header
-\title{Psychological Needs During Intergroup Contact}
+\title{Psychological Needs During Intergroup Contact: Three Experience Sampling Studies}
 \shorttitle{Needs in Intergroup Contact}
@@
 % Authors
-\author[*,1,2]{Jannis Kreienkamp}
-\author[1,2]{Maximilian Agostini}
-\author[1,2]{Laura F. Bringmann}
-\author[1,2]{Peter de Jonge}
-\author[1,2]{Kai Epstude}
+\author[*,1]{Jannis Kreienkamp}
+\author[1]{Maximilian Agostini}
+\author[1]{Laura F. Bringmann}
+\author[1]{Peter de Jonge}
+\author[1]{Kai Epstude}
 \affiliation{\hfill}
@@
 \affil[1]{University of Groningen, Department of Psychology}
-\affil[2]{Any additional affiliations still need to be added}
 
@@
 The authors received no specific funding for this work.
-Source data and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}.
-Protocols, materials, analysis data, and code are available at \url{osf.io}.
+Materials and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}  \citep{KreienkampMasked2022}.
+Protocols, materials, data, and code are available at \url{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970} \citep{KreienkampMasked2022a}.
 
@@
 \abstract{
-Modern intergroup contact research faces two main challenges: (1) When does a positively perceived interaction with an outgroup member translate to positive intergroup contact.
-(2) Do the often between-person studied effects hold within-person?
-Here we present three extensive longitudinal studies of recent migrants to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297).
-We find that  fulfillment of psychological needs, going through perceived interaction quality, are a strong predictor of positive intergroup attitudes.
-Across the three studies, we also find inconsistent evidence for interaction frequencies and average interaction quality in predicting outgroup attitudes.
-Finally, situational needs remained the core predictor of outgroup attitudes even after controlling for Allport's contact conditions or more general fundamental needs.
+One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations.
+This question becomes especially relevant when considering that negative intergroup contacts are common during everyday life.
+To understand positive intergroup interactions, we propose to consider situational motivations and psychological needs during everyday intergroup contact.
+We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total N of measurements = 10,297).
+Across the three studies, we find inconsistent results for a traditional test of the contact hypothesis with experience sampling data.
+However, when using multilevel models to test the contact hypothesis, we find that individual outgroup interactions and perceived interaction quality have a strong influence on positive outgroup attitudes.
+We find that the fulfillment of psychological needs offers a strong predictor of positive attitudes after interactions and that these positive effects emerged via perceived interaction quality.
+The situational needs remained the core predictor of outgroup attitudes even after controlling for Allport’s (\citeyear{Allport1954b}) contact conditions or more general fundamental needs.
 As one of the first studies to test intergroup contact theory using extensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
 
-\noindent\textbf{Public significance statement}: In this paper we provide evidence that the fulfillment of situational psychological needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
-This offers testament to the emerging practice of capturing real-life interactions using extensive longitudinal data.
-It also gives weight to motivational fulfillment as a flexible and relevant mechanism in understanding positive intergroup contact.
+\noindent\textbf{Public significance statement}: In this paper, we provide evidence that the fulfillment of situational psychological needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
+Methodologically, this offers testament to the emerging practice of capturing real-life interactions using extensive longitudinal data.
+Theoretically, our results give weight to motivational fulfillment as a flexible and relevant mechanism in understanding positive intergroup contact.
 }
@@
   \label{fig:ContactHypothesis}
-  \begin{subfigure}{\textwidth}
-    \caption{}
-    \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricGeneralLm.png}
-  \end{subfigure}
-  \begin{subfigure}{\textwidth}
-    \caption{}
-    \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
-  \end{subfigure}
+  \centering\includegraphics[width=\textwidth]{Figures/forestParametricGeneralComb.png}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricGeneralLm.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
+  %\end{subfigure}
   \caption*{Note: \\
@@
   \label{fig:AllportNeedFulfillment}
-  \begin{subfigure}{\textwidth}
-    \caption{}
-    \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryQualityCore.png}
-  \end{subfigure}
-  \begin{subfigure}{\textwidth}
-    \caption{}
-    \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCore.png}
-  \end{subfigure}
-  \begin{subfigure}{\textwidth}
-    \caption{}
-    \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCoreQuality.png}
-  \end{subfigure}
+  \centering\includegraphics[width=\textwidth]{Figures/forestParametricTheoryComb.png}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryQualityCore.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCore.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCoreQuality.png}
+  %\end{subfigure}
   \caption*{Note: \\
@@
   \label{fig:Robustness}
-  \begin{subfigure}{\textwidth}
-    \caption{}
-    \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
-  \end{subfigure}
-  \begin{subfigure}{\textwidth}
-    \caption{}
-    \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
-  \end{subfigure}
+  \centering\includegraphics[width=\textwidth]{Figures/forestParametricRobustnessComb.png}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
+  %\end{subfigure}
   \caption*{Note: \\
@@
 % aims re-iterated
-The aim of this project was threefold.
+The aim of this project was in essence threefold.
 We (1) tested the basic predictions of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data.
-We also (2) proposed that the fulfillment of situational psychological needs meaningfully predicts positive outgroup attitudes.
+As a flexible alternative, we (2) proposed that the fulfillment of situational psychological needs meaningfully predicts positive outgroup attitudes.
 Finally, we (3) assessed whether the fulfillment of psychological needs (and Allport's conditions) have their effect (partially) through perceived interaction quality.
@@
 When considering the results of the three studies jointly, we found mixed results for the basic intergroup contact hypothesis.
-More specifically, we observe that seperating between between-subjects and within-subjects effects is crucial.
-For between-subjects effects, we did not observe a consistent predictor of outgroup attitudes when aggregating people's interaction frequencies and average interaction quality; neither interaction quality, or interaction quality, nor their interaction was a significant predictor across all studies (also see Figure \ref{fig:ContactHypothesis}a).
-However, once we used multilevel modeling to separate effects into a between-subjects and within-subjects part, we found that when having an interaction with an outgroup member (vs.
-not having an outgroup interaction),intergroup contact is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account; also see Figure \ref{fig:ContactHypothesis}b).
-While this later results is in line with our expectations, the earlier aggregate findings are surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
-Even though this inconsistency with past research might be a data artefact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction), the absence of this aggregate effect could underline the fact that cross-sectional retrospective data might might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
-In summary, we thus find that when we aggregate interaction frequencies and interaction quality from our intensive longitudinal data we find inconsistent results from the past literature but in line with past literature within participants intergroup contacts are significantly related with positive outgroup attitudes.
+More specifically, we observe that separating between-participant and within-participant effects is crucial.
+For between-subjects effects (using aggregated reports), neither the number of interactions, nor the average interaction quality were significant predictors of positive outgroup attitudes across all studies (also see Figure \ref{fig:ContactHypothesis}a).
+The aggregate findings are surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
+The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).\footnote{It should be noted that such inconsistencies with past research might in part be a data artefact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
+However, the multilevel models we employed should in principle be resistant to such imbalances.} In support of this possibility, once we used multilevel modeling to separate effects into a between-subjects and within-subjects part, we found that when having an interaction with an outgroup member (vs.
+not having an outgroup interaction) is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account; also see Figure \ref{fig:ContactHypothesis}b).
+We thus find that when we aggregate interaction frequencies and interaction quality from our intensive longitudinal data, we find inconsistent results from the past literature, however within participants, intergroup contacts are significantly related with positive outgroup attitudes.
 
@@
 In fact, our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
-In most cases the core need even took over the variances previously explained by the self-determination theory needs.
+In most cases, the core need even took over the variances previously explained by the self-determination theory needs.
 We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
-As such the data offers a first test of the motivational basis of intergroup contact.
 
@@
 % (1) Sample = minority and (voluntary) migrants, (2) Methodology = short scales (reliability) and no lagged effects, (3) Core Need Concept = non-specific
-As with any approach our studies are not without practical and theoretical limitations.
+Among the limitations of our studies we should consider the following.
 One limitation is our choice of samples.
@@
 A second limitation lies in our methodology.
-While extensive longitudinal data is close to the real-life events this method comes at the expense of longer and more robust scales.
+While extensive longitudinal data is close to the real-life events, this method comes at the expense of longer and more robust scales.
 Long and repetitive scales are often not feasible in extensive longitudinal methods because of the increased burden to the participants.
@@
 An additional methodological question lies in the unexplored potential of the longitudinal aspects of our data.
-For our research questions we have focused on contemporaneous effects within the data set, yet future investigations should seek to extend the mechanism to developmental trajectories within and between participants.
+For our research questions, we have focused on contemporaneous effects within the data set, yet future investigations should seek to extend the mechanism to developmental trajectories within and between participants.
 And finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
-This has come at the expense of specificity in the situational needs (i.e., we have not explored which exact needs people had during their interactions).
+This has come at the expense of specificity in the situational needs (i.e., we have not explored which exact needs people had during specific interactions).
 With the adaptive measurement we have proposed such an investigation would be possible (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
@@
 In the context of intergroup contact research, we were among the first to answer calls to test intergroup contact mechanisms using on extended real-life data \citep[e.g.,][]{Pettigrew2011, MacInnis2015}.
-And in doing so, we not only collected a sizable amount of real-life data, but our consideration of extensive longitudinal data may present new inconsistencies in how participants perceive and cognitively aggregate their past interactions with other groups — which may suggest large-scale recall-biases or conflations of within and between participant effects in conventional cross-section studies.
+In doing so, we not only collected a sizable amount of real-life data, but our consideration of extensive longitudinal data may present new inconsistencies in how participants perceive and cognitively aggregate their past interactions with other groups — which may suggest large-scale recall-biases or conflations of within and between participant effects in conventional cross-section studies.
 
@@
 Our results offer a first promising test of psychological needs in intergroup contact.
-While our results are tentative given their novelty within the field, they were highly consistent across studies and may offer new theoretical avenues moving forward.
+While our results are tentative given their novelty within the field, they were highly consistent across studies and may offer new theoretical avenues.
 Psychological needs are a facet of the human experience that has thus far been under–emphasized in the intergroup contact literature.
@@
 Intergroup contact theory is among the most implemented psychological theories \citep[e.g.,][]{Pettigrew2006, AlRamiah2012a, Reimer2021}.
-Given our findings that psychological needs in every-day intergroup contacts were at least as powerful as Allport's conditions in predicting outgroup attitudes, considerations of people's needs offer a substantially simpler mechanism to address.
+Given our findings that psychological needs in every-day intergroup contacts were at least as powerful as Allport's conditions in predicting outgroup attitudes, considerations of people's needs offer a substantially more immediate mechanism to address.
 In cases where some or all optimal contact conditions are not possible to be fulfilled, needs offer an even more compelling alternative (e.g., where equal status is contextually not possible or in cases where people help despite a lack of institutional support).
@@
 
+\subsection{Conclusion}
 % Conclusion paragraph
-In sum, in this paper we used extensive longitudinal methodologies to capture real-life data of recent migrants in their interactions with the majority outgroup.
+In sum, in this paper we used extensive longitudinal methodologies to capture real-life interactions of recent migrants with the majority outgroup.
 Our three studies showcase the feasibility and utility of such data to test intergroup contact theory.

### 2022-03-14 TitlePage.tex

@@
 % Title and header
-\title{The Migration Experience: A Conceptual Framework and Systematic Review of Psychological Acculturation}
-\shorttitle{Acculturation Experience Framework}
+\title{Psychological Needs During Intergroup Contact: Three Experience Sampling Studies}
+\shorttitle{Needs in Intergroup Contact}
 
@@
 \author[*,1]{Jannis Kreienkamp}
+\author[1]{Maximilian Agostini}
 \author[1]{Laura F. Bringmann}
-\author[1]{Raili F. Engler}
 \author[1]{Peter de Jonge}
@@
 \affiliation{\hfill}
+
 \affil[1]{University of Groningen, Department of Psychology}
@@
    \addORCIDlink{* Jannis Kreienkamp}{0000-0002-1831-5604}\\
+   \addORCIDlink{Maximilian Agostini}{0000-0001-6435-7621}\\
    \addORCIDlink{Laura F. Bringmann}{0000-0002-8091-9935}\\
@@
 The authors received no specific funding for this work.
-Source data and  software is available at \url{https://github.com/JannisCodes/acculturation-review} \citep{Kreienkamp2021b}.
-Protocols, materials, analysis data, and code are available at \url{https://doi.org/10.34894/U988DU} \citep{Kreienkamp2021a}.
+Materials and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}  \citep{KreienkampMasked2022}.
+Protocols, materials, data, and code are available at \url{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970} \citep{KreienkampMasked2022a}.
 

### 2022-03-15 Methods-and-Results.Rmd
M & R feedback

@@
 
-Based on our main hypotheses, the aim of our first study is to specifically test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
+Based on our main hypotheses, the aim of our first study was to specifically test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
 To this aim, we conducted an intensive longitudinal survey study with recent migrants to the Netherlands.
@@
 
-The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
+The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
 Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
@@
 
-\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(workerSampleInfo)` migrants using the local paid participant pool and specifically targeted non-Dutch migrants to participate in our study.
+\subsubsection{Participants} After receiving ethical approval from the University Masked for Peer Review, we recruited `r nrow(workerSampleInfo)` migrants using the local paid participant pool and specifically targeted non-Dutch migrants to participate in our study.
 Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
-With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(workerSampleInfo$dailiesN)`).
+With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(workerSampleInfo$dailiesN), big.mark=",")`).
 This is a common number of measurements found in experience sampling studies and offers sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
@@
 Over the next thirty days, the participants were then invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_))) %>% as.character`).
-General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%)}.
-The response rates were approximately equal during mornings (\textit{n} = `r sum(workerSampleInfo$morningN)`) and afternoons (\textit{n} = `r sum(workerSampleInfo$afternoonN)`) and most measurements were completed within four hours of the invitation.
-After the final day of daily diary measurements, participants were invited to fill in a longer post measurement survey that mirrored the pre-measurement.
-All key variables for this study were part of the short daily diary surveys.
+General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%).}.
+The response rates were approximately equal during mornings (\textit{n} = `r format(sum(workerSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(workerSampleInfo$afternoonN), big.mark=",")`) and most measurements were completed within four hours of the invitation.
+After the final day of experience sampling measurements, participants were invited to fill in a longer post measurement survey that mirrored the pre-measurement.
+All key variables for this study were part of the short experience sampling surveys.
 
@@
 Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
-interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtWorkerSupp$workerInteractionType)` daily diary responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
+interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r format(nrow(dtWorkerSupp$workerInteractionType), big.mark=",")` experience sampling responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts.
 These participants are removed from any analyses that focus on outgroup contacts.}.
@@
 
-\paragraph{Outgroup Attitudes}At the end of every daily diary measurement we asked all participants about their current attitudes towards the Dutch – our main dependent variable.
+\paragraph{Outgroup Attitudes}At the end of every experience sampling measurement we asked all participants about their current attitudes towards the Dutch – our main dependent variable.
 To assess the momentary outgroup evaluation we used the common feeling thermometer: “How favorable do you feel towards the Dutch?” \citep[][]{Lavrakas2008}.
@@
 \subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
-First, we assessed whether more intergroup interactions were related to to more positive outgroup attitudes.
+First, we assessed whether overall between participants more intergroup interactions were related to to more positive average outgroup attitudes.
 Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
-We find that neither the number of interactions nor the number of daily diary responses with an interaction were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`).
-However, we did find a medium sized correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r format(round(rAttitudeQuality$r[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],2), nsmall = 2)`, \textit{p} = `r format(round(rAttitudeQuality$P[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],3), nsmall = 3)`.
-And when considering the number of interactions and average interaction quality jointly in a linear regression, we additionally find a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of interactions the positive effect of average interaction quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblLong}).
+We find that neither the overall number of contacts nor the number of experience sampling responses with a contact were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`).
+However, we did find a medium sized correlation between the participants' average contact quality and their average outgroup attitudes (\textit{r} = `r format(round(rAttitudeQuality$r[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],2), nsmall = 2)`, \textit{p} = `r format(round(rAttitudeQuality$P[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],3), nsmall = 3)`).
+And when considering the number of contacts and average contact quality jointly in a linear regression, we additionally found a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of contacts the positive effect of average contact quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblLong}).
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
-This is unusual and might indicate the the effect is very consistent across participants.
-However, the small number of participants, or other measurement issues provide an alternative explanation}.
-Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants (even tough the average number of interactions does seem to interact with average interaction quality to predict outgroup attitudes).
+We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+This is unusual and might indicate that the effect is very consistent across participants.
+However, the small number of participants, or other measurement issues provide an alternative explanation.}.
+Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants (even tough the average number of contacts does seem to interact with average contact quality to predict outgroup attitudes).
 However, it should be noted that the between-participant analyses in the aggregated form are based on a small sample size.
 
-\subsubsection{Core Need}The main proposal of our article is that the success of an outgroup interaction might be explained by whether or not the interaction fulfilled the person's core situational need.
-This should, in turn, be due to a higher perceived interaction quality.
-We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly (for full regression results see Table \ref{tab:intergroupNeedsTblLong}).
+\subsubsection{Core Need}The main proposal of our article is that the success of an outgroup contact might be explained by whether or not the contact fulfilled the person's core situational need.
+This should, in turn, be due to a higher perceived contact quality.
+We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived contact quality, and (3) whether the variance explained by the core need is subsumed by the perceived contact quality if considered jointly (for full regression results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
 
@@
 
-We find that in the highest multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCore, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreCI, varName = "keymotive_fulfillemt_1_cwc")`) and also predicted higher perceived interaction quality (random intercept model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Qlt$lmeInterceptCore, lmerCI = mdlWorkerOut$Qlt$lmerInterceptCoreCI, varName = "keymotive_fulfillemt_1_cwc")`).
-Moreover, when we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`).
+We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCore, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreCI, varName = "keymotive_fulfillemt_1_cwc")`) and also predicted higher perceived contact quality (random intercept model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Qlt$lmeInterceptCore, lmerCI = mdlWorkerOut$Qlt$lmerInterceptCoreCI, varName = "keymotive_fulfillemt_1_cwc")`).
+Moreover, when we consider the influences of core need fulfillment and contact quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived contact quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`).
 We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes.
-Additionally, this effect is likely being explained by its effect through perceived interaction quality.
+Additionally, this effect is likely explained by its effect through perceived contact quality.
 
@@
 To build further confidence in our results, we assessed two additional models that might offer alternative explanations.
-First, to ensure that the effect of core need fulfillment is specific to an actual interaction, we compared the effect to core need fulfillement in situations without an interaction.
-For this, we analyzed the generalized situational core need fulfillment (either during an interaction or about the daytime in general) and tested whether the effect differed during daily diary measurements with and without outgroup contacts.
-We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`; also see Table \ref{tab:robustnessTblLong}).
+First, to ensure that the effect of core need fulfillment is specific to an actual contact, we compared the effect to core need fulfillment in situations without an intergroup contact.
+For this, we analyzed the generalized situational core need fulfillment (either during a contact or about the daytime in general) and tested whether the effect differed during experience sampling measurements with and without outgroup contacts.
+We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`; also see Table \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness}).
 Together with a significant main effect of having an outgroup contact, this indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
@@
 
-# To be compared against a model with only the self determination theory needs
+# To be compared against a model with only the self-determination theory needs
 mdlWorkerOut$Att$lmeInterceptSdt <-
@@
 
-In a final step, we controlled for other fundamental psychological needs during the interaction.
-We focus on the three commonly considered self determination needs: competence, autonomy, and relatedness.
-We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r workerSdtCompChiSq`).
-We find that next to relatedness (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "relatedness_1_cwc")`), the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "keymotive_fulfillemt_1_cwc")`).
+In a final step, we controlled for other fundamental psychological needs during the contact.
+We focus on the three commonly considered self-determination needs (SDT): competence, autonomy, and relatedness.
+We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r workerSdtCompChiSq`).
+We also find that next to relatedness (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "relatedness_1_cwc")`), the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "keymotive_fulfillemt_1_cwc")`).
 When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all three fundamental needs (competence and autonomy needs turning non-significant; all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
-For full results see see Table \ref{tab:robustnessTblLong} and Online Supplementary Information B.
+For full results see see Table \ref{tab:robustnessTblLong}, Figure \ref{fig:Robustness}, and Online Supplementary Material A.
 
@@
 
-The aim of Study 2 is similar to Study 1, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
+The aim of Study 2 is similar to Study 1, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived contact quality during intergroup contacts.
 However, in this second study we collected a substantially larger sample of international students who recently arrived in the Netherlands and also improved the study design (e.g., pop-up explanations described later).
@@
 
-\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(studentSampleInfo)` international students using a local participant pool.
+\subsubsection{Participants} We recruited `r nrow(studentSampleInfo)` international students using a local participant pool.
 We specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
 Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
-With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(studentSampleInfo$dailiesN)`).
+With this design, we again aimed at receiving 50-60 measurements per participant (\textit{M} = `r format(round(mean(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(studentSampleInfo$dailiesN), big.mark=",")`).
 As with the previous study this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
@@
 
-\subsubsection{Procedure} The study procedure mirrored the setup of study one and consisted of pre-, daily diary-, and post-measurement.
-The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily))) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily)))) %>% as.character`).
+\subsubsection{Procedure} The study procedure mirrored the setup of Study 1 and consisted of pre-, experience sampling-, and post-measurements.
+The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily))) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily)))) %>% as.character`).
 General compliance was high (`r format(round(sum(studentSampleInfo$dailiesN)/(nrow(studentSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in).
-The response rates were approximately equal during mornings (\textit{n} = `r sum(studentSampleInfo$morningN)`) and afternoons (\textit{n} = `r sum(studentSampleInfo$afternoonN)`).
-All key variables for this study were part of the short daily diary surveys.
+The response rates were approximately equal during mornings (\textit{n} = `r format(sum(studentSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(studentSampleInfo$afternoonN), big.mark=",")`).
+All key variables for this study were part of the short experience sampling surveys.
 
@@
 The participants recorded between `r dtStudentSupp$studentContactFreq$SumContactNL[dtStudentSupp$studentContactFreq$SumContactNL > 0] %>% min`--`r dtStudentSupp$studentContactFreq$SumContactNL %>% max`
-interactions with Dutch majority people (`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtStudentSupp$studentContactFreq$SumContactNL) / nrow(dtStudentSupp$studentInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtStudentSupp$studentInteractionType)` daily diary responses).
-
-\paragraph{Psychological Needs}For the core situational need, we asked participants in an open ended text field: “\textit{What was your main goal [during the interaction with X / this morning / this afternoon]?}”.
+interactions with Dutch majority people (`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r (sum(dtStudentSupp$studentContactFreq$SumContactNL) / nrow(dtStudentSupp$studentInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r format(nrow(dtStudentSupp$studentInteractionType), big.mark=",")` experience sampling responses).
+
+\paragraph{Psychological Needs}For the core situational need, we asked participants in an open ended text field: “\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}” (where \textit{-X-} was dynamically replaced with the name of the interaction partner).
 Participants could additionally click on a pop-up explanation: "Your main goal during an interaction can vary depending on the interaction.
-It could be to connect with friends, to find or provide help, to achieve academic ambitions, work on your fitness, work for a job, or simply to get a coffee, just as well as many many other concrete or abstract goals that are import to you in the moment.
+It could be to connect with friends, to find or provide help, to achieve academic ambitions, work on your fitness, work for a job, or simply to get a coffee, just as well as many other concrete or abstract goals that are import to you in the moment.
 It really depends on your subjective experience of the interaction.".
-Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{During your interaction with X [this morning / this evening] your goal (-previous text entry-) was fulfilled.}” on a continuous slider scale ranging from strongly disagree (1) to strongly agree (100).
-
-The measurement of the self determination needs was identical to Study 1.
-
-\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to study one.
+Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{During your interaction with -X- [this morning / this evening] your goal (-previous text entry-) was fulfilled.}” on a continuous slider scale ranging from strongly disagree (1) to strongly agree (100).
+
+The measurement of the self-determination needs was identical to Study 1.
+
+\paragraph{Perceived Interaction Quality}The ratings of the perceived contact quality was identical to Study 1.
 
 \paragraph{Outgroup Attitudes}As in Study 1, attitudes towards the Dutch majority outgroup were again measured using the feeling thermometer.
-All survey details are also available in Online Supplemental Materials A and B.
+All survey details are also available in our OSF repository \citep{KreienkampMasked2022a} and Online Supplemental Materials A.
 
@@
 
-\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in the same manner as in Study 1.
+\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis as in Study 1.
 We found a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-However, we found no significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblLong}).
+However, we found no significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblLong} and Figure \ref{fig:ContactHypothesis}).
 We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials B).
-Thus, in our second data set we find mixed results, outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, as well as Online Supplementary Material A).
+Thus, in our second data set we find mixed results; outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
 However, we find that this effect does not depend on the average perceived interaction quality.
@@
 
-We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is subsumed by the perceived interaction quality if considered jointly.
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`).
-Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} for full results).
-These results are consistent with the results in study one and we thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
+Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment} for full results).
+These results are consistent with the results in Study 1.
+We, thus, find support for our hypotheses that the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
 
@@
 Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteraction")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous study, albeit with slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see Table \ref{tab:intergroupNeedsTblLong} and for visual comparison see Figure \ref{fig:AllportNeedFulfillment}).
+This finding is consistent with the results of the previous study, albeit with a slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see Table \ref{tab:intergroupNeedsTblLong} and for visual comparison see Figure \ref{fig:AllportNeedFulfillment}).
 
@@
 
-# To be compared against a model with only the self determination theory needs
+# To be compared against a model with only the self-determination theory needs
 mdlStudentOut$Att$lmeInterceptSdt <-
@@
 In a final step we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
-We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r studentSdtCompChiSq`).
-We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFullfillment_cwc")`).
+We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r studentSdtCompChiSq`).
+We find that the core need fulfillment explained the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFullfillment_cwc")`).
 When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
 However, different from the first study, relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes in this larger sample.
-For full results see Table \ref{tab:intergroupNeedsTblLong} and Online Supplementary Information B.
+For full results see Table \ref{tab:intergroupNeedsTblLong}, Figure \ref{fig:Robustness}, and Online Supplementary Material A.
 
@@
 
-For this study we specifically recruited international medical students, because they represent a particular group of migrants who face structural requirements to integrate and interact with Dutch majority outgroup members on a daily basis.
+For this study, we specifically recruited international medical students, because they represent a particular group of migrants who face structural requirements to integrate and interact with Dutch majority outgroup members on a daily basis.
 As part of their educational program, the migrants are required to take language courses and interact with patients as part of their medical internships and medical residency.
@@
 
-The full surveys are available in our Online Supplementary Material A and the full data description is available in Online Supplementary Materials B.
+The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
 Correlations and descriptive statistics of the included variables are available in Tables \ref{tab:descrFullWide} and \ref{tab:descrOutWide}.
@@
 
-\subsubsection{Participants} After receiving ethical approval from the University of Groningen, we recruited `r nrow(medicalSampleInfo)` international medical students using a contacts within the University Medical Department and specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
+\subsubsection{Participants} We recruited `r nrow(medicalSampleInfo)` international medical students using contacts within the University Medical School.
+We specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
 Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
-With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r sum(medicalSampleInfo$dailiesN)`).
-As with the previous study this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
-Participants were compensated for their participation with partial course credits --- depending on their participation.
+With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(medicalSampleInfo$dailiesN), big.mark=",")`).
+As with the previous studies, this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
+Participants were compensated for their participation in the same manner as during Study 1.
 The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(medicalSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(medicalSampleInfo$age),2), nsmall=2)`, `r nrow(medicalSampleInfo %>% filter(gender == "women"))` women).
-The sample fairly accurately describes the local population of international students.
-
-\subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, daily diary-, and post-measurement.
-The participants were invited for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).
-General compliance was high (`r format(round(sum(medicalSampleInfo$dailiesN)/(nrow(medicalSampleInfo)*62)*100,2), nsmall=2)`\% filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS).
-The response rates were approximately equal during mornings (\textit{n} = `r sum(medicalSampleInfo$morningN)`) and afternoons (\textit{n} = `r sum(medicalSampleInfo$afternoonN)`).
-All key variables in for this study were part of the short daily diary surveys.
+The sample fairly accurately describes the local population of young international medical professionals.
+
+\subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, experience sampling-, and post-measurement.
+The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).
+General compliance was high (`r format(round(table(medicalSampleInfo$dailiesN>30)["TRUE"]/nrow(medicalSampleInfo)*100,2), nsmall=2)`\% filled in at least 31 experience sampling surveys or more).
+The response rates were approximately equal during mornings (\textit{n} = `r format(sum(medicalSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(medicalSampleInfo$afternoonN), big.mark=",")`).
+All key variables for this study were part of the short experience sampling surveys.
 
@@
 
-\paragraph{Intergroup Contact}The measurement of intergroup contacts was identical to study two.
+\paragraph{Intergroup Contact}The measurement of intergroup contacts was identical to Study 2.
 The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
-(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual daily diary measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r nrow(dtMedical$full)` daily diary responses).
-
-\paragraph{Psychological Needs}The measurement of the core situational need and its fulfillment was identical to study two.
-Similarly, the measurement of the self determination needs was identical to studies one and two.
-
-\paragraph{Allport's Conditions}To measure how much each of the interactions fulfilled Allport's conditions of optimal contact we asked participants to rate how much the interaction had equal status ("\textit{The interaction with [name interaction partner] was on equal footing (same status)}"), a common goal ("\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}"), support of authorities ("\textit{The interaction with [name interaction partner] was voluntary}"), and intergroup cooperation ("\textit{The interaction with [name interaction partner] was cooperative}").
-
-\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to study one.
+(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r format(nrow(dtMedical$full), big.mark=",")` experience sampling responses).
+
+\paragraph{Psychological Needs}The measurement of the core situational need and its fulfillment was identical to Study 2.
+Similarly, the measurement of the self-determination needs was identical to Studies 1 and 2
+
+\paragraph{Allport's Conditions}We measured how much each of the interactions fulfilled Allport's conditions of optimal contact using a common short scale comprised of four attributes \citep{Islam1993, Voci2003, AlRamiah2012a, Dixon2005}.
+In particular, we asked participants to rate how much the interaction had equal status ("\textit{The interaction with [name interaction partner] was on equal footing (same status)}"), a common goal ("\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}"), support of authorities ("\textit{The interaction with [name interaction partner] was voluntary}"), and intergroup cooperation ("\textit{The interaction with [name interaction partner] was cooperative}").
+We create a mean-averaged index of Allport's conditions in response to past findings indicating that the conditions are best conceptualized jointly and as functioning together rather than as fully independent factors \citep[][, p.
+766]{Pettigrew2006}.
+For full psychometric information see Online Supplementary Material A.
+
+\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to Study 1.
 
 \paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup was again measured using the feeling thermometer, as in studies one and two.
-All survey details are also available in Online Supplemental Materials A and B.
+All survey details are also available in our OSF repository \citep{KreienkampMasked2022a} and Online Supplemental Materials A.
 
@@
 \subsubsection{Contact Hypothesis}As in Studies 1 and 2, we first conducted a general contact hypothesis test.
-We found no correlation between intergroup contact and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (\textit{r} < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-However, we did find a significant correlation between the participants' Average Interaction Quality and their Average Outgroup Attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+We found no correlation between the overall number of intergroup contacts and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (|\textit{r}| < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
+However, we did find a significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
 When considering the number of interactions and average interaction quality jointly in a linear regression, we only found a main effect of average perceived interaction quality on outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of the number of contacts nor an interaction effect.
-This result mirrors that of study one but is inconsistent with the second study.
-Additionally in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Table \ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials B).
+This result mirrors that of Study 1 but is inconsistent with the second study.
+Additionally, in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A).
 Thus, in our third data set we again found mixed results.
-Outgroup contacts were on average not significantly related to outgroup attitudes on a between participant level and this effect was also not suppressed by an average interaction quality (i.e., no interaction effect).
+Aggregate outgroup contacts were generally not significantly related to average outgroup attitudes on a between participant level and this effect was also not suppressed by an average interaction quality (i.e., no interaction effect).
 However, while the aggregate data was partly inconsistent with the first two studies, the within person contemporaneous effect of intergroup contact was consistent across all three studies.
@@
 
-We sequentially tested whether the fulfillment of Allport's Contact Conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly.
-We find that in the multilevel models, the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
+As we did with core need fulfillment in previous studies, we sequentially tested whether the fulfillment of Allport's contact conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly.
+In the multilevel models we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
 Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
-These results indicate that in this dataset the the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
+These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.
 
@@
 
-We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
-We find that in the multilevel models, the fulfillment of core need fulfillment during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
+Similarly, we again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+We find that the fulfillment of the core need during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
 Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
-These results indicate that in this data set the the fulfillment of core situational needs had a significant influence on outgroup attitudes and this effect is likely in parts explained by its effect through perceived interaction quality.
+These results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and this effect partially emerged via its effect on perceived interaction quality.
 
@@
 
-We again checked for alternative models.
+We again checked for alternative models of the key need fulfillment.
 First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
@@
 
-# To be compared against a model with only the self determination theory needs
+# To be compared against a model with only the self-determination theory needs
 mdlMedicalOut$Att$lmeInterceptSdt <-
@@
 
-In a final step we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
-We find that the core need adds significantly above a model with only the self determination theory needs (random slopes models; `r medicalSdtCompChiSq`).
+In a final step, we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
+We find that the core need fulfillment adds additional variance above a model with only the self-determination theory needs (random slopes models; `r medicalSdtCompChiSq`).
 We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFulfillment_cwc")`).
@@
 This being said, the regression coefficient for the core need was three times larger (with all scaling being equal).
-For full results see Table \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as Online Supplementary Information B.
+For full results see Table \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as Online Supplementary Material A.
 
@@
       format = "latex",
-      caption = "ntergroup Contact Sample: Correlation Table and Descriptive Statistics",
+      caption = "Intergroup Contact Sample: Correlation Table and Descriptive Statistics",
       booktabs = TRUE,
@@
               filename = "TheoryComb",
-              addAbove = 0,
+              addAbove = 5,
               width = 600,
@@
               filename = "RobustnessComb",
-              addAbove = 17,
+              addAbove = 5,
               width = 600,

### 2022-03-15 Methods-and-Results.tex
M & R feedback

@@
 
-Based on our main hypotheses, the aim of our first study is to
+Based on our main hypotheses, the aim of our first study was to
 specifically test the general contact hypothesis, the influence of core
@@
 
-The full surveys are available in our Online Supplementary Material A
-and the full data description is available in Online Supplementary
-Materials B. Correlations and descriptive statistics of the included
-variables are available in Table \ref{tab:descrFullWide} and Table
-\ref{tab:descrOutWide}.
+The full surveys are available in our OSF repository
+\citep{KreienkampMasked2022a} and the full data description is available
+in Online Supplementary Material A. Correlations and descriptive
+statistics of the included variables are available in Table
+\ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
 
@@
 
-After receiving ethical approval from the University of Groningen, we
-recruited 23 migrants using the local paid participant pool and
-specifically targeted non-Dutch migrants to participate in our study.
-Participants reported on their interactions for at least 30 days with
-two daily measures (capturing the morning and afternoon). With this
+After receiving ethical approval from the University Masked for Peer
+Review, we recruited 23 migrants using the local paid participant pool
+and specifically targeted non-Dutch migrants to participate in our
+study. Participants reported on their interactions for at least 30 days
+with two daily measures (capturing the morning and afternoon). With this
 design, we aimed at getting 50-60 measurements per participant
-(\textit{M} = 53.26, \textit{SD} = 16.72, \textit{total N} = 1225). This
-is a common number of measurements found in experience sampling studies
-and offers sufficient power to model processes within and between
-participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
-Participants were compensated for their participation with up to 34
-Euros -- each two Euros for pre- and post-questionnaire as well as 50
-Eurocents for every experience sampling measurement occasion. The sample
-consisted of relatively young, educated, and western migrants from the
-global north (\(M_{age}\) = 24.35, \(SD_{age}\) = 4.73, 19 women, 15
-students). The sample accurately describes the largest groups of
-migrants in the region \citep[][]{GemeenteGroningen2015}.
+(\textit{M} = 53.26, \textit{SD} = 16.72, \textit{total N} = 1,225).
+This is a common number of measurements found in experience sampling
+studies and offers sufficient power to model processes within and
+between participants
+\citep[e.g., for a systematic review see][]{AanhetRot2012}. Participants
+were compensated for their participation with up to 34 Euros -- each two
+Euros for pre- and post-questionnaire as well as 50 Eurocents for every
+experience sampling measurement occasion. The sample consisted of
+relatively young, educated, and western migrants from the global north
+(\(M_{age}\) = 24.35, \(SD_{age}\) = 4.73, 19 women, 15 students). The
+sample accurately describes the largest groups of migrants in the region
+\citep[][]{GemeenteGroningen2015}.
 
@@
 General compliance was high (85.90\% of all invited surveys were filled
-in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%)}.
+in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%).}.
 The response rates were approximately equal during mornings (\textit{n}
@@
 completed within four hours of the invitation. After the final day of
-daily diary measurements, participants were invited to fill in a longer
-post measurement survey that mirrored the pre-measurement. All key
-variables for this study were part of the short daily diary surveys.
+experience sampling measurements, participants were invited to fill in a
+longer post measurement survey that mirrored the pre-measurement. All
+key variables for this study were part of the short experience sampling
+surveys.
 
@@
 Our participants recorded between 2--51 interactions with Dutch outgroup
-members (3.23--91.07\% of individual daily diary measurements; 31.59\%
-of all 1225 daily diary
-responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
+members (3.23--91.07\% of individual experience sampling measurements;
+31.59\% of all 1,225 experience sampling
+responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts.
 These participants are removed from any analyses that focus on outgroup contacts.}.
@@
 
-At the end of every daily diary measurement we asked all participants
-about their current attitudes towards the Dutch -- our main dependent
-variable. To assess the momentary outgroup evaluation we used the common
-feeling thermometer: ``How favorable do you feel towards the Dutch?''
-\citep[][]{Lavrakas2008}. Participants then rated their attitude on a
-continuous slider scale from ``very cold -- 0'' through ``no feeling --
-50'' to ``very warm -- 100''. Both the question phrasing as well as the
-tick labels were consistent with large-scale panel surveys
-\citep[e.g.,][]{DeBell2010}.
+At the end of every experience sampling measurement we asked all
+participants about their current attitudes towards the Dutch -- our main
+dependent variable. To assess the momentary outgroup evaluation we used
+the common feeling thermometer: ``How favorable do you feel towards the
+Dutch?'' \citep[][]{Lavrakas2008}. Participants then rated their
+attitude on a continuous slider scale from ``very cold -- 0'' through
+``no feeling -- 50'' to ``very warm -- 100''. Both the question phrasing
+as well as the tick labels were consistent with large-scale panel
+surveys \citep[e.g.,][]{DeBell2010}.
 
@@
 We tested the most general contact hypothesis in two steps. First, we
-assessed whether more intergroup interactions were related to to more
-positive outgroup attitudes. Second, we tested whether a potential
-positive effect on outgroup attitudes depended on the interaction
-quality (jointly with the number of interactions). We find that neither
-the number of interactions nor the number of daily diary responses with
-an interaction were significantly related with the average outgroup
-attitudes (all \textbar{} \textit{r} \textbar{} \textless{} 0.03, all
-\textit{p} \textgreater{} 0.887). However, we did find a medium sized
-correlation between the participants' Average Interaction Quality and
-their Average Outgroup Attitudes (\textit{r} = 0.55, \textit{p} = 0.010.
-And when considering the number of interactions and average interaction
-quality jointly in a linear regression, we additionally find a
-statistically significant interaction term (\textit{b} = -0.05,
-\textit{t}(17) = -2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34), where
-in our sample with an increasing number of interactions the positive
-effect of average interaction quality becomes weaker (also see Table
+assessed whether overall between participants more intergroup
+interactions were related to to more positive average outgroup
+attitudes. Second, we tested whether a potential positive effect on
+outgroup attitudes depended on the interaction quality (jointly with the
+number of interactions). We find that neither the overall number of
+contacts nor the number of experience sampling responses with a contact
+were significantly related with the average outgroup attitudes (all
+\textbar{} \textit{r} \textbar{} \textless{} 0.03, all \textit{p}
+\textgreater{} 0.887). However, we did find a medium sized correlation
+between the participants' average contact quality and their average
+outgroup attitudes (\textit{r} = 0.55, \textit{p} = 0.010). And when
+considering the number of contacts and average contact quality jointly
+in a linear regression, we additionally found a statistically
+significant interaction term (\textit{b} = -0.05, \textit{t}(17) =
+-2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34), where in our sample
+with an increasing number of contacts the positive effect of average
+contact quality becomes weaker (also see Table
 \ref{tab:intergroupGeneralTblLong}). We additionally used a multilevel
@@
 member had a situational (i.e., contemporaneous) effect within the
-participants. We find that having an outgroup interaction is indeed
+participants. We find that having an outgroup contact is indeed
 associated with significantly more positive outgroup attitudes within
-the participants (\textit{b} = 2.48, \textit{t}(1200) = 4.36, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}1.36, 3.59{]}), even after
-controlling for having an interaction with a non-Dutch (which did not
-relate to outgroup attitudes independently; For full results see Table
-\ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials
-B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
-This is unusual and might indicate the the effect is very consistent across participants.
-However, the small number of participants, or other measurement issues provide an alternative explanation}.
+the participants (\textit{b} = 2.48, \textit{t}(1,200) = 4.36,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}1.36, 3.59{]}), even
+after controlling for having an interaction with a non-Dutch (which did
+not relate to outgroup attitudes independently; For full results see
+Table \ref{tab:intergroupGeneralTblLong}, Figure
+\ref{fig:ContactHypothesis}, and Online Supplementary Material
+A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+This is unusual and might indicate that the effect is very consistent across participants.
+However, the small number of participants, or other measurement issues provide an alternative explanation.}.
 Thus, in our first data we find mixed results, where outgroup contacts
@@
 results do not translate into average differences between participants
-(even tough the average number of interactions does seem to interact
-with average interaction quality to predict outgroup attitudes).
-However, it should be noted that the between-participant analyses in the
-aggregated form are based on a small sample size.
+(even tough the average number of contacts does seem to interact with
+average contact quality to predict outgroup attitudes). However, it
+should be noted that the between-participant analyses in the aggregated
+form are based on a small sample size.
 
@@
 The main proposal of our article is that the success of an outgroup
-interaction might be explained by whether or not the interaction
-fulfilled the person's core situational need. This should, in turn, be
-due to a higher perceived interaction quality. We sequentially test
-whether the fulfillment of the core need during an interaction is (1)
-related to more positive outgroup attitudes, (2) higher perceived
-interaction quality, and (3) whether the variance explained by the core
-need is assumed by the perceived interaction quality if considered
-jointly (for full regression results see Table
-\ref{tab:intergroupNeedsTblLong}).
+contact might be explained by whether or not the contact fulfilled the
+person's core situational need. This should, in turn, be due to a higher
+perceived contact quality. We sequentially test whether the fulfillment
+of the core need during an interaction is (1) related to more positive
+outgroup attitudes, (2) higher perceived contact quality, and (3)
+whether the variance explained by the core need is subsumed by the
+perceived contact quality if considered jointly (for full regression
+results see Table \ref{tab:intergroupNeedsTblLong} and Figure
+\ref{fig:AllportNeedFulfillment}).
 
-We find that in the highest multilevel models, the fulfillment of core
+We find that in the multilevel models, the fulfillment of core
 situational needs during outgroup contacts was associated with more
@@
 \textit{t}(365) = 2.93, \textit{p} = 0.004, \textit{95\%CI}{[}0.06,
-0.29{]}) and also predicted higher perceived interaction quality (random
+0.29{]}) and also predicted higher perceived contact quality (random
 intercept model; \textit{b} = 0.42, \textit{t}(365) = 8.07, \textit{p}
 \textless{} .001, \textit{95\%CI}{[}0.32, 0.52{]}). Moreover, when we
-consider the influences of core need fulfillment and interaction quality
-on outgroup attitudes jointly, we find that virtually all variance is
-explained by perceived interaction quality (random slopes mode;
-\textit{b} = 0.23, \textit{t}(364) = 4.22, \textit{p} \textless{} .001,
+consider the influences of core need fulfillment and contact quality on
+outgroup attitudes jointly, we find that virtually all variance is
+explained by perceived contact quality (random slopes mode; \textit{b} =
+0.23, \textit{t}(364) = 4.22, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
@@
 significant influence on outgroup attitudes. Additionally, this effect
-is likely being explained by its effect through perceived interaction
-quality.
+is likely explained by its effect through perceived contact quality.
 
@@
 models that might offer alternative explanations. First, to ensure that
-the effect of core need fulfillment is specific to an actual
-interaction, we compared the effect to core need fulfillement in
-situations without an interaction. For this, we analyzed the generalized
-situational core need fulfillment (either during an interaction or about
-the daytime in general) and tested whether the effect differed during
-daily diary measurements with and without outgroup contacts. We found no
+the effect of core need fulfillment is specific to an actual contact, we
+compared the effect to core need fulfillment in situations without an
+intergroup contact. For this, we analyzed the generalized situational
+core need fulfillment (either during a contact or about the daytime in
+general) and tested whether the effect differed during experience
+sampling measurements with and without outgroup contacts. We found no
 main effect of core need fulfillment (random slopes model; \textit{b} =
--0.10, \textit{t}(1199) = -2.22, \textit{p} = 0.026,
+-0.10, \textit{t}(1,199) = -2.22, \textit{p} = 0.026,
 \textit{95\%CI}{[}-0.18, -0.01{]}) but a significant interaction effect
 of core need fulfillment and outgroup contact (\textit{b} = 0.13,
-\textit{t}(1199) = 4.31, \textit{p} \textless{} .001,
+\textit{t}(1,199) = 4.31, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.07, 0.18{]}; also see Table
-\ref{tab:robustnessTblLong}). Together with a significant main effect of
-having an outgroup contact, this indicates that it is not key need
-fulfillment in general --- but only key need fulfillment during an
-outgroup contact that predicts more positive outgroup attitudes.
+\ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness}). Together
+with a significant main effect of having an outgroup contact, this
+indicates that it is not key need fulfillment in general --- but only
+key need fulfillment during an outgroup contact that predicts more
+positive outgroup attitudes.
 
 In a final step, we controlled for other fundamental psychological needs
-during the interaction. We focus on the three commonly considered self
-determination needs: competence, autonomy, and relatedness. We find that
-the core need adds significantly above a model with only the self
-determination theory needs (random slopes models; \(\chi^2\)(6,
-\textit{N} = 21) = 19.60, \textit{p} = 0.003). We find that next to
-relatedness (\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the core need
-explains the most variance in outgroup attitudes after an outgroup
-contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p} = 0.026,
-\textit{95\%CI}{[}0.01, 0.18{]}). When compared to the model with only
-the SDT needs, the core need fulfillment flexibly takes on some of the
-explained variance of all three fundamental needs (competence and
-autonomy needs turning non-significant; all \textit{b} \textless{} 0.05,
-all \textit{p} \textgreater{} 0.544). For full results see see Table
-\ref{tab:robustnessTblLong} and Online Supplementary Information B.
+during the contact. We focus on the three commonly considered
+self-determination needs (SDT): competence, autonomy, and relatedness.
+We find that the core need fulfillment adds significantly above a model
+with only the self-determination theory needs (random slopes models;
+\(\chi^2\)(6, \textit{N} = 21) = 19.60, \textit{p} = 0.003). We also
+find that next to relatedness (\textit{b} = 0.10, \textit{t}(361) =
+4.04, \textit{p} \textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the
+core need explains the most variance in outgroup attitudes after an
+outgroup contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p}
+= 0.026, \textit{95\%CI}{[}0.01, 0.18{]}). When compared to the model
+with only the SDT needs, the core need fulfillment flexibly takes on
+some of the explained variance of all three fundamental needs
+(competence and autonomy needs turning non-significant; all \textit{b}
+\textless{} 0.05, all \textit{p} \textgreater{} 0.544). For full results
+see see Table \ref{tab:robustnessTblLong}, Figure \ref{fig:Robustness},
+and Online Supplementary Material A.
 
@@
 contact hypothesis, the influence of core need fulfillment, and
-perceived interaction quality during intergroup contacts. However, in
-this second study we collected a substantially larger sample of
-international students who recently arrived in the Netherlands and also
-improved the study design (e.g., pop-up explanations described later).
-The survey method again offers a large body of ecologically valid data
-on need satisfaction in real-life intergroup contact situations as these
+perceived contact quality during intergroup contacts. However, in this
+second study we collected a substantially larger sample of international
+students who recently arrived in the Netherlands and also improved the
+study design (e.g., pop-up explanations described later). The survey
+method again offers a large body of ecologically valid data on need
+satisfaction in real-life intergroup contact situations as these
 students will likely interact with the Dutch majority outgroup on a
@@
 
-After receiving ethical approval from the University of Groningen, we
-recruited 113 international students using a local participant pool. We
-specifically targeted non-Dutch students, who had recently arrived in
+We recruited 113 international students using a local participant pool.
+We specifically targeted non-Dutch students, who had recently arrived in
 the Netherlands. Participants reported on their interactions for at
 least 30 days with two daily measures (capturing the morning and
-afternoon). With this design, we aimed at getting 50-60 measurements per
-participant (\textit{M} = 43.94, \textit{SD} = 15.00, \textit{total N} =
-4965). As with the previous study this should offer sufficient power to
-model processes within participants and will lend stronger weight to
-between-participant results. Participants were compensated for their
-participation with partial course credits --- depending on their
-participation. The sample consisted of relatively young migrants, who
-were mostly from the global north (\(M_{age}\) = 20.24, \(SD_{age}\) =
-2.12, 84 women). The sample fairly accurately describes the local
-population of international students.
+afternoon). With this design, we again aimed at receiving 50-60
+measurements per participant (\textit{M} = 43.94, \textit{SD} = 15.00,
+\textit{total N} = 4,965). As with the previous study this should offer
+sufficient power to model processes within participants and will lend
+stronger weight to between-participant results. Participants were
+compensated for their participation with partial course credits ---
+depending on their participation. The sample consisted of relatively
+young migrants, who were mostly from the global north (\(M_{age}\) =
+20.24, \(SD_{age}\) = 2.12, 84 women). The sample fairly accurately
+describes the local population of international students.
 
@@
 
-The study procedure mirrored the setup of study one and consisted of
-pre-, daily diary-, and post-measurement. The participants were invited
-for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days
-(\textit{median duration} = 3M 46S, \textit{MAD duration} = 1M 54S).
-General compliance was high (70.87\% of all invited surveys were filled
-in). The response rates were approximately equal during mornings
-(\textit{n} = 2608) and afternoons (\textit{n} = 2357). All key
-variables for this study were part of the short daily diary surveys.
+The study procedure mirrored the setup of Study 1 and consisted of pre-,
+experience sampling-, and post-measurements. The participants were
+invited for experience sampling measurements twice a day (at 12 pm and
+7pm) for 30 days (\textit{median duration} = 3M 46S,
+\textit{MAD duration} = 1M 54S). General compliance was high (70.87\% of
+all invited surveys were filled in). The response rates were
+approximately equal during mornings (\textit{n} = 2,608) and afternoons
+(\textit{n} = 2,357). All key variables for this study were part of the
+short experience sampling surveys.
 
@@
 interaction.''. The participants recorded between 1--43 interactions
-with Dutch majority people (1.64--93.75\% of individual daily diary
-measurements; 18.83\% of all 4965 daily diary responses).
+with Dutch majority people (1.64--93.75\% of individual experience
+sampling measurements; 18.83\% of all 4,965 experience sampling
+responses).
 
@@
 text field:
-``\textit{What was your main goal [during the interaction with X / this morning / this afternoon]?}''.
-Participants could additionally click on a pop-up explanation: ``Your
-main goal during an interaction can vary depending on the interaction.
-It could be to connect with friends, to find or provide help, to achieve
-academic ambitions, work on your fitness, work for a job, or simply to
-get a coffee, just as well as many many other concrete or abstract goals
-that are import to you in the moment. It really depends on your
-subjective experience of the interaction.''. Then, with reference to the
-text entry, we asked how much this core need was fulfilled during the
-interaction or the past daytime period:
-``\textit{During your interaction with X [this morning / this evening] your goal (-previous text entry-) was fulfilled.}''
+``\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}''
+(where \textit{-X-} was dynamically replaced with the name of the
+interaction partner). Participants could additionally click on a pop-up
+explanation: ``Your main goal during an interaction can vary depending
+on the interaction. It could be to connect with friends, to find or
+provide help, to achieve academic ambitions, work on your fitness, work
+for a job, or simply to get a coffee, just as well as many other
+concrete or abstract goals that are import to you in the moment. It
+really depends on your subjective experience of the interaction.''.
+Then, with reference to the text entry, we asked how much this core need
+was fulfilled during the interaction or the past daytime period:
+``\textit{During your interaction with -X- [this morning / this evening] your goal (-previous text entry-) was fulfilled.}''
 on a continuous slider scale ranging from strongly disagree (1) to
@@
 
-The measurement of the self determination needs was identical to Study
+The measurement of the self-determination needs was identical to Study
 1.
@@
 
-The ratings of the perceived interaction quality was identical to study
-one.
+The ratings of the perceived contact quality was identical to Study 1.
 
@@
 measured using the feeling thermometer. All survey details are also
-available in Online Supplemental Materials A and B.
+available in our OSF repository \citep{KreienkampMasked2022a} and Online
+Supplemental Materials A.
 
@@
 
-We tested the most general contact hypothesis in the same manner as in
-Study 1. We found a significant correlation with average outgroup
-attitudes for both the total number of outgroup interactions (\textit{r}
-= 0.22, \textit{p} = 0.019) and the number of measurement beeps with an
-interaction (\textit{r} = 0.28, \textit{p} = 0.003). However, we found
-no significant correlation between the participants' Average Interaction
-Quality and their Average Outgroup Attitudes (\textit{r} = 0.04,
+We tested the most general contact hypothesis as in Study 1. We found a
+significant correlation with average outgroup attitudes for both the
+total number of outgroup interactions (\textit{r} = 0.22, \textit{p} =
+0.019) and the number of measurement beeps with an interaction
+(\textit{r} = 0.28, \textit{p} = 0.003). However, we found no
+significant correlation between the participants' average interaction
+quality and their average outgroup attitudes (\textit{r} = 0.04,
 \textit{p} = 0.679). Thus, when considering the number of interactions
@@
 contact quality and no significant interaction term (for full results
-see Table \ref{tab:intergroupGeneralTblLong}). We additionally used a
-multilevel regression to check whether having an interaction with an
-outgroup member had a situational (i.e., contemporaneous) effect within
-the participants. We find that having an outgroup interaction is indeed
+see Table \ref{tab:intergroupGeneralTblLong} and Figure
+\ref{fig:ContactHypothesis}). We additionally used a multilevel
+regression to check whether having an interaction with an outgroup
+member had a situational (i.e., contemporaneous) effect within the
+participants. We find that having an outgroup interaction is indeed
 associated with significantly more positive outgroup attitudes within
 the participants (random slopes model; \textit{b} = 2.99,
-\textit{t}(4850) = 3.80, \textit{p} \textless{} .001,
+\textit{t}(4,850) = 3.80, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}1.45, 4.54{]}), even after controlling for having an
@@
 attitudes independently; For full results see Table
-\ref{tab:intergroupGeneralTblLong} and Online Supplementary Materials
-B). Thus, in our second data set we find mixed results, outgroup
-contacts show a positive effect on outgroup attitudes in the moment and
-on average between participants. However, we find that this effect does
-not depend on the average perceived interaction quality. This unexpected
-results, might be due to the aggregation process and the following
-analyses will focus in on the role of the perceived interaction quality
-during an outgroup interaction.
+\ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis},
+as well as Online Supplementary Material A). Thus, in our second data
+set we find mixed results; outgroup contacts show a positive effect on
+outgroup attitudes in the moment and on average between participants.
+However, we find that this effect does not depend on the average
+perceived interaction quality. This unexpected results, might be due to
+the aggregation process and the following analyses will focus in on the
+role of the perceived interaction quality during an outgroup
+interaction.
 
@@
 attitudes, (2) higher perceived interaction quality, and (3) whether the
-variance explained by the core need is assumed by the perceived
+variance explained by the core need is subsumed by the perceived
 interaction quality if considered jointly. We find that in the
@@
 \textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
-0.07{]}; also see Table \ref{tab:intergroupNeedsTblLong} for full
-results). These results are consistent with the results in study one and
-we thus find support for our hypotheses and can conclude that in this
-data set the fulfillment of core situational needs had a significant
-influence on outgroup attitudes and that this effect is likely explained
-by its effect through perceived interaction quality.
+0.07{]}; also see Table \ref{tab:intergroupNeedsTblLong} and Figure
+\ref{fig:AllportNeedFulfillment} for full results). These results are
+consistent with the results in Study 1. We, thus, find support for our
+hypotheses that the fulfillment of core situational needs had a
+significant influence on outgroup attitudes and that this effect is
+likely explained by its effect through perceived interaction quality.
 
@@
 main effect of core need fulfillment (random slopes model; \textit{b} =
--0.03, \textit{t}(4849) = -1.34, \textit{p} = 0.181,
+-0.03, \textit{t}(4,849) = -1.34, \textit{p} = 0.181,
 \textit{95\%CI}{[}-0.08, 0.02{]}) but a stronger interaction effect of
 core need fulfillment and outgroup contact (\textit{b} = 0.06,
-\textit{t}(4849) = 3.03, \textit{p} = 0.002, \textit{95\%CI}{[}0.02,
+\textit{t}(4,849) = 3.03, \textit{p} = 0.002, \textit{95\%CI}{[}0.02,
 0.10{]}). Together with a significant main effect of having an outgroup
-contact (\textit{b} = 2.88, \textit{t}(4849) = 3.71, \textit{p}
+contact (\textit{b} = 2.88, \textit{t}(4,849) = 3.71, \textit{p}
 \textless{} .001, \textit{95\%CI}{[}1.36, 4.40{]}), this indicates that
@@
 attitudes. This finding is consistent with the results of the previous
-study, albeit with slightly weaker effect (likely because of the large
+study, albeit with a slightly weaker effect (likely because of the large
 number of measurements that did not include an outgroup interaction; For
@@
 fundamental psychological needs into account. We find that the core need
-adds significantly above a model with only the self determination theory
-needs (random slopes models; \(\chi^2\)(6, \textit{N} = 108) = 22.90,
-\textit{p} \textless{} .001). We find that the core need explains the
-most variance in outgroup attitudes after an outgroup contact
-(\textit{b} = 0.08, \textit{t}(823) = 2.95, \textit{p} = 0.003,
-\textit{95\%CI}{[}0.03, 0.13{]}). When compared to the model with only
-the SDT needs, the core need fulfillment flexibly takes on some of the
-explained variance of all of the three fundamental needs. However,
-different from the first study, relatedness (\textit{b} = 0.07,
-\textit{t}(823) = 4.26, \textit{p} \textless{} .001,
+fulfillment adds significantly above a model with only the
+self-determination theory needs (random slopes models; \(\chi^2\)(6,
+\textit{N} = 108) = 22.90, \textit{p} \textless{} .001). We find that
+the core need fulfillment explained the most variance in outgroup
+attitudes after an outgroup contact (\textit{b} = 0.08, \textit{t}(823)
+= 2.95, \textit{p} = 0.003, \textit{95\%CI}{[}0.03, 0.13{]}). When
+compared to the model with only the SDT needs, the core need fulfillment
+flexibly takes on some of the explained variance of all of the three
+fundamental needs. However, different from the first study, relatedness
+(\textit{b} = 0.07, \textit{t}(823) = 4.26, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.04, 0.10{]}) and autonomy (\textit{b} = 0.02,
@@
 0.08{]}) also predicted positive outgroup attitudes in this larger
-sample. For full results see Table \ref{tab:intergroupNeedsTblLong} and
-Online Supplementary Information B.
+sample. For full results see Table \ref{tab:intergroupNeedsTblLong},
+Figure \ref{fig:Robustness}, and Online Supplementary Material A.
 
@@
 
-For this study we specifically recruited international medical students,
-because they represent a particular group of migrants who face
+For this study, we specifically recruited international medical
+students, because they represent a particular group of migrants who face
 structural requirements to integrate and interact with Dutch majority
@@
 
-The full surveys are available in our Online Supplementary Material A
-and the full data description is available in Online Supplementary
-Materials B. Correlations and descriptive statistics of the included
-variables are available in Tables \ref{tab:descrFullWide} and
-\ref{tab:descrOutWide}.
+The full surveys are available in our OSF repository
+\citep{KreienkampMasked2022a} and the full data description is available
+in Online Supplementary Material A. Correlations and descriptive
+statistics of the included variables are available in Tables
+\ref{tab:descrFullWide} and \ref{tab:descrOutWide}.
 
@@
 
-After receiving ethical approval from the University of Groningen, we
-recruited 71 international medical students using a contacts within the
-University Medical Department and specifically targeted non-Dutch
-students, who had recently arrived in the Netherlands. Participants
-reported on their interactions for at least 30 days with two daily
-measures (capturing the morning and afternoon). With this design, we
-aimed at getting 50-60 measurements per participant (\textit{M} = 57.85,
-\textit{SD} = 20.68, \textit{total N} = 4107). As with the previous
-study this should offer sufficient power to model processes within
+We recruited 71 international medical students using contacts within the
+University Medical School. We specifically targeted non-Dutch students,
+who had recently arrived in the Netherlands. Participants reported on
+their interactions for at least 30 days with two daily measures
+(capturing the morning and afternoon). With this design, we aimed at
+getting 50-60 measurements per participant (\textit{M} = 57.85,
+\textit{SD} = 20.68, \textit{total N} = 4,107). As with the previous
+studies, this should offer sufficient power to model processes within
 participants and will lend stronger weight to between-participant
-results. Participants were compensated for their participation with
-partial course credits --- depending on their participation. The sample
-consisted of relatively young migrants, who were mostly from the global
-north (\(M_{age}\) = 22.68, \(SD_{age}\) = 3.10, 59 women). The sample
-fairly accurately describes the local population of international
-students.
+results. Participants were compensated for their participation in the
+same manner as during Study 1. The sample consisted of relatively young
+migrants, who were mostly from the global north (\(M_{age}\) = 22.68,
+\(SD_{age}\) = 3.10, 59 women). The sample fairly accurately describes
+the local population of young international medical professionals.
 
@@
 The study procedure mirrored the setup of studies one and two, in that
-it consisted of pre-, daily diary-, and post-measurement. The
-participants were invited for daily diary measurements twice a day (at
-12 pm and 7pm) for 30 days (\textit{median duration} = 4M 13S,
-\textit{MAD duration} = 2M 6S). General compliance was high (93.30\%
-filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS).
-The response rates were approximately equal during mornings (\textit{n}
-= 2092) and afternoons (\textit{n} = 2015). All key variables in for
-this study were part of the short daily diary surveys.
+it consisted of pre-, experience sampling-, and post-measurement. The
+participants were invited for experience sampling measurements twice a
+day (at 12 pm and 7pm) for 30 days (\textit{median duration} = 4M 13S,
+\textit{MAD duration} = 2M 6S). General compliance was high (85.92\%
+filled in at least 31 experience sampling surveys or more). The response
+rates were approximately equal during mornings (\textit{n} = 2,092) and
+afternoons (\textit{n} = 2,015). All key variables for this study were
+part of the short experience sampling surveys.
 
@@
 
-The measurement of intergroup contacts was identical to study two. The
+The measurement of intergroup contacts was identical to Study 2. The
 participants recorded between 1--71 interactions with Dutch outgroup
-members (2.13--87.18\% of individual daily diary measurements; 41.44\%
-of all 4107 daily diary responses).
+members (2.13--87.18\% of individual experience sampling measurements;
+41.44\% of all 4,107 experience sampling responses).
 
@@
 The measurement of the core situational need and its fulfillment was
-identical to study two. Similarly, the measurement of the self
-determination needs was identical to studies one and two.
+identical to Study 2. Similarly, the measurement of the
+self-determination needs was identical to Studies 1 and 2
 
@@
 
-To measure how much each of the interactions fulfilled Allport's
-conditions of optimal contact we asked participants to rate how much the
-interaction had equal status
+We measured how much each of the interactions fulfilled Allport's
+conditions of optimal contact using a common short scale comprised of
+four attributes \citep{Islam1993, Voci2003, AlRamiah2012a, Dixon2005}.
+In particular, we asked participants to rate how much the interaction
+had equal status
 (``\textit{The interaction with [name interaction partner] was on equal footing (same status)}''),
@@
 (``\textit{The interaction with [name interaction partner] was cooperative}'').
+We create a mean-averaged index of Allport's conditions in response to
+past findings indicating that the conditions are best conceptualized
+jointly and as functioning together rather than as fully independent
+factors \citep[][, p. 766]{Pettigrew2006}. For full psychometric
+information see Online Supplementary Material A.
 
@@
 
-The ratings of the perceived interaction quality was identical to study
-one.
+The ratings of the perceived interaction quality was identical to Study
+1.
 
@@
 the feeling thermometer, as in studies one and two. All survey details
-are also available in Online Supplemental Materials A and B.
+are also available in our OSF repository \citep{KreienkampMasked2022a}
+and Online Supplemental Materials A.
 
@@
 As in Studies 1 and 2, we first conducted a general contact hypothesis
-test. We found no correlation between intergroup contact and average
-outgroup attitudes --- for neither the total number of outgroup
-interactions nor the number of measurement beeps with an interaction
-(\textit{r} \textless{} 0.13, \textit{p} \textgreater{} 0.291). However,
-we did find a significant correlation between the participants' Average
-Interaction Quality and their Average Outgroup Attitudes (\textit{r} =
-0.25, \textit{p} = 0.036). When considering the number of interactions
-and average interaction quality jointly in a linear regression, we only
-found a main effect of average perceived interaction quality on outgroup
-attitudes (\textit{b} = 0.36, \textit{t}(67) = 2.22, \textit{p} = 0.030,
-\(\eta_p^2\) = 0.07) but no significant effect of the number of contacts
-nor an interaction effect. This result mirrors that of study one but is
-inconsistent with the second study. Additionally in a multilevel
-regression to check for contemporaneous within person effects, we found
-that having an outgroup interaction was indeed associated with
-significantly more positive outgroup attitudes within the participants
-(random slopes model; \textit{b} = 5.63, \textit{t}(3834) = 6.61,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}3.97, 7.29{]}), even
-after controlling for having an interaction with a non-Dutch (which did
-not relate to outgroup attitudes independently; for full results see
-Table \ref{tab:intergroupGeneralTblLong} and Online Supplementary
-Materials B). Thus, in our third data set we again found mixed results.
-Outgroup contacts were on average not significantly related to outgroup
-attitudes on a between participant level and this effect was also not
-suppressed by an average interaction quality (i.e., no interaction
-effect). However, while the aggregate data was partly inconsistent with
-the first two studies, the within person contemporaneous effect of
-intergroup contact was consistent across all three studies.
+test. We found no correlation between the overall number of intergroup
+contacts and average outgroup attitudes --- for neither the total number
+of outgroup interactions nor the number of measurement beeps with an
+interaction (\textbar{}\textit{r}\textbar{} \textless{} 0.13, \textit{p}
+\textgreater{} 0.291). However, we did find a significant correlation
+between the participants' average interaction quality and their average
+outgroup attitudes (\textit{r} = 0.25, \textit{p} = 0.036). When
+considering the number of interactions and average interaction quality
+jointly in a linear regression, we only found a main effect of average
+perceived interaction quality on outgroup attitudes (\textit{b} = 0.36,
+\textit{t}(67) = 2.22, \textit{p} = 0.030, \(\eta_p^2\) = 0.07) but no
+significant effect of the number of contacts nor an interaction effect.
+This result mirrors that of Study 1 but is inconsistent with the second
+study. Additionally, in a multilevel regression to check for
+contemporaneous within person effects, we found that having an outgroup
+interaction was indeed associated with significantly more positive
+outgroup attitudes within the participants (random slopes model;
+\textit{b} = 5.63, \textit{t}(3,834) = 6.61, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}3.97, 7.29{]}), even after controlling for
+having an interaction with a non-Dutch (which did not relate to outgroup
+attitudes independently; for full results see Table
+\ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis},
+and Online Supplementary Material A). Thus, in our third data set we
+again found mixed results. Aggregate outgroup contacts were generally
+not significantly related to average outgroup attitudes on a between
+participant level and this effect was also not suppressed by an average
+interaction quality (i.e., no interaction effect). However, while the
+aggregate data was partly inconsistent with the first two studies, the
+within person contemporaneous effect of intergroup contact was
+consistent across all three studies.
 
@@
 
-We sequentially tested whether the fulfillment of Allport's Contact
-Conditions was (1) related to more positive outgroup attitudes, (2)
+As we did with core need fulfillment in previous studies, we
+sequentially tested whether the fulfillment of Allport's contact
+conditions was (1) related to more positive outgroup attitudes, (2)
 higher perceived interaction quality, and (3) whether the variance
 explained by Allport's Conditions is assumed by the perceived
-interaction quality if considered jointly. We find that in the
-multilevel models, the fulfillment of Allport's Conditions during
-outgroup contacts was associated with more positive outgroup attitudes
-(random slopes model; \textit{b} = 0.22, \textit{t}(1601) = 5.86,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.15, 0.29{]}) and also
-predicted higher perceived interaction quality (random slopes model;
-\textit{b} = 0.65, \textit{t}(1605) = 11.82, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we consider the
+interaction quality if considered jointly. In the multilevel models we
+find that the fulfillment of Allport's Conditions during outgroup
+contacts was associated with more positive outgroup attitudes (random
+slopes model; \textit{b} = 0.22, \textit{t}(1,601) = 5.86, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.15, 0.29{]}) and also predicted
+higher perceived interaction quality (random slopes model; \textit{b} =
+0.65, \textit{t}(1,605) = 11.82, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we consider the
 influences of Allport's Conditions and interaction quality on outgroup
@@
 substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
-\textit{t}(1600) = 6.25, \textit{p} \textless{} .001,
+\textit{t}(1,600) = 6.25, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
 Allport's Conditions was less than half of its original effect size
-(\textit{b} = 0.09, \textit{t}(1600) = 2.89, \textit{p} = 0.004,
+(\textit{b} = 0.09, \textit{t}(1,600) = 2.89, \textit{p} = 0.004,
 \textit{95\%CI}{[}0.03, 0.15{]}; also see Table
@@
 \ref{fig:AllportNeedFulfillment}). These results indicate that in this
-dataset the the fulfillment of Allport's conditions had a significant
-influence on outgroup attitudes and this effect is likely in parts
+data set the fulfillment of Allport's conditions had a significant
+influence on outgroup attitudes and this effect is likely, in parts,
 explained by its effect through perceived interaction quality.
@@
 
-We again sequentially tested whether the fulfillment of the core need
-during an interaction was (1) related to more positive outgroup
-attitudes, (2) higher perceived interaction quality, and (3) whether the
-variance explained by the core need is assumed by the perceived
-interaction quality if considered jointly. We find that in the
-multilevel models, the fulfillment of core need fulfillment during
-outgroup contacts was associated with more positive outgroup attitudes
-(random slopes model; \textit{b} = 0.19, \textit{t}(1601) = 5.29,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.12, 0.27{]}) and also
-predicted higher perceived interaction quality (random slopes model;
-\textit{b} = 0.43, \textit{t}(1605) = 8.35, \textit{p} \textless{} .001,
+Similarly, we again sequentially tested whether the fulfillment of the
+core need during an interaction was (1) related to more positive
+outgroup attitudes, (2) higher perceived interaction quality, and (3)
+whether the variance explained by the core need is assumed by the
+perceived interaction quality if considered jointly. We find that the
+fulfillment of the core need during outgroup contacts was associated
+with more positive outgroup attitudes (random slopes model; \textit{b} =
+0.19, \textit{t}(1,601) = 5.29, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.27{]}) and also predicted higher perceived
+interaction quality (random slopes model; \textit{b} = 0.43,
+\textit{t}(1,605) = 8.35, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.33, 0.54{]}). Additionally, once we consider the
@@
 substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
-\textit{t}(1600) = 6.86, \textit{p} \textless{} .001,
+\textit{t}(1,600) = 6.86, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.12, 0.22{]}) and the unique variance explained by
 core need fulfillment was roughly half of its original effect size
-(\textit{b} = 0.11, \textit{t}(1600) = 3.50, \textit{p} \textless{}
+(\textit{b} = 0.11, \textit{t}(1,600) = 3.50, \textit{p} \textless{}
 .001, \textit{95\%CI}{[}0.05, 0.17{]}; for full results see Table
@@
 \ref{fig:AllportNeedFulfillment}). These results indicate that in this
-data set the the fulfillment of core situational needs had a significant
-influence on outgroup attitudes and this effect is likely in parts
-explained by its effect through perceived interaction quality.
+data set outgroup attitudes were significantly predicted by the
+fulfillment of core situational needs and this effect partially emerged
+via its effect on perceived interaction quality.
 
@@
 parameters (random slopes model; Allport's Conditions: \textit{b} =
-0.16, \textit{t}(1600) = 4.92, \textit{p} \textless{} .001,
+0.16, \textit{t}(1,600) = 4.92, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.09, 0.24{]}, Core Need: \textit{b} = 0.14,
-\textit{t}(1600) = 3.85, \textit{p} \textless{} .001,
+\textit{t}(1,600) = 3.85, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.08, 0.17{]}; also see Table
@@
 
-We again checked for alternative models. First, when considering
-generalized situational core need fulfillment together with whether an
-intergroup contact took place, we find that there is no significant main
-effect of core need fulfillment (random slopes model; \textit{b} = 0.03,
-\textit{t}(3835) = 1.51, \textit{p} = 0.131, \textit{95\%CI}{[}-0.01,
-0.06{]}) but a stronger interaction effect of core need fulfillment and
-outgroup contact (\textit{b} = 0.17, \textit{t}(3835) = 7.32, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}0.12, 0.21{]}). Together with a
-significant main effect of having an outgroup contact (\textit{b} =
-5.41, \textit{t}(3835) = 6.36, \textit{p} \textless{} .001,
+We again checked for alternative models of the key need fulfillment.
+First, when considering generalized situational core need fulfillment
+together with whether an intergroup contact took place, we find that
+there is no significant main effect of core need fulfillment (random
+slopes model; \textit{b} = 0.03, \textit{t}(3,835) = 1.51, \textit{p} =
+0.131, \textit{95\%CI}{[}-0.01, 0.06{]}) but a stronger interaction
+effect of core need fulfillment and outgroup contact (\textit{b} = 0.17,
+\textit{t}(3,835) = 7.32, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.21{]}). Together with a significant main
+effect of having an outgroup contact (\textit{b} = 5.41,
+\textit{t}(3,835) = 6.36, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}3.74, 7.08{]}), this indicates that it is not key need
@@
 
-In a final step we again checked whether during the interaction the core
-situational need remains a meaningful predictor even when taking other
-fundamental psychological needs into account. We find that the core need
-adds significantly above a model with only the self determination theory
-needs (random slopes models; \(\chi^2\)(6, \textit{N} = 70) = 100.20,
-\textit{p} \textless{} .001). We find that the core need explains the
-most variance in outgroup attitudes after an outgroup contact
-(\textit{b} = 0.15, \textit{t}(1598) = 3.88, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}0.07, 0.22{]}). When compared to the model with
-only the SDT needs, the core need fulfillment flexibly takes on some of
-the explained variance of all of the three fundamental needs. However,
-similar to the previous study, in this large sample relatedness
-(\textit{b} = 0.05, \textit{t}(1598) = 3.31, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}0.02, 0.09{]}), competence (\textit{b} = 0.06,
-\textit{t}(1598) = 2.73, \textit{p} = 0.006, \textit{95\%CI}{[}0.02,
-0.10{]}) and autonomy (\textit{b} = 0.04, \textit{t}(1598) = 2.12,
-\textit{p} = 0.034, \textit{95\%CI}{[}-0.01, 0.08{]}) each also
-predicted positive outgroup attitudes independently. This being said,
-the regression coefficient for the core need was three times larger
-(with all scaling being equal). For full results see Table
+In a final step, we again checked whether during the interaction the
+core situational need remains a meaningful predictor even when taking
+other fundamental psychological needs into account. We find that the
+core need fulfillment adds additional variance above a model with only
+the self-determination theory needs (random slopes models; \(\chi^2\)(6,
+\textit{N} = 70) = 100.20, \textit{p} \textless{} .001). We find that
+the core need explains the most variance in outgroup attitudes after an
+outgroup contact (\textit{b} = 0.15, \textit{t}(1,598) = 3.88,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.22{]}). When
+compared to the model with only the SDT needs, the core need fulfillment
+flexibly takes on some of the explained variance of all of the three
+fundamental needs. However, similar to the previous study, in this large
+sample relatedness (\textit{b} = 0.05, \textit{t}(1,598) = 3.31,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.02, 0.09{]}),
+competence (\textit{b} = 0.06, \textit{t}(1,598) = 2.73, \textit{p} =
+0.006, \textit{95\%CI}{[}0.02, 0.10{]}) and autonomy (\textit{b} = 0.04,
+\textit{t}(1,598) = 2.12, \textit{p} = 0.034, \textit{95\%CI}{[}-0.01,
+0.08{]}) each also predicted positive outgroup attitudes independently.
+This being said, the regression coefficient for the core need was three
+times larger (with all scaling being equal). For full results see Table
 \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as
-Online Supplementary Information B.
+Online Supplementary Material A.
 

### 2022-03-15 scripts/functions/MlCorMat.R

@@ -275,7 +275,7 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
   if (is.null(lmerCI)) {
     paste0(
       "\\textit{b} = ", b, 
-      ", \\textit{t}(", df, ") = ", t,
+      ", \\textit{t}(", format(df, big.mark=","), ") = ", t,
       ", \\textit{p} ", p
     )
   } else {
@@ -284,7 +284,7 @@ MlCoeffLatex <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
     
     paste0(
       "\\textit{b} = ", b, 
-      ", \\textit{t}(", df, ") = ", t,
+      ", \\textit{t}(", format(df, big.mark=","), ") = ", t,
       ", \\textit{p} ", p,
       ", \\textit{95\\%CI}[", CIlwr, ", ", CIupr, "]"
     )
@@ -300,7 +300,7 @@ MlCoeffHtml <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
   if (is.null(lmerCI)) {
     paste0(
       "<i>b</i> = ", b, 
-      ", <i>t</i>(", df, ") = ", t,
+      ", <i>t</i>(", format(df, big.mark=","), ") = ", t,
       ", <i>p</i> ", p
     )
   } else {
@@ -309,7 +309,7 @@ MlCoeffHtml <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
     
     paste0(
       "<i>b</i> = ", b, 
-      ", <i>t</i>(", df, ") = ", t,
+      ", <i>t</i>(", format(df, big.mark=","), ") = ", t,
       ", <i>p</i> ", p,
       ", <i>95%CI</i>[", CIlwr, ", ", CIupr, "]"
     )

### 2022-03-15 TitlePage.tex
Updates from Overleaf

@@
 The authors received no specific funding for this work.
-Materials and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}  \citep{KreienkampMasked2022}.
-Protocols, materials, data, and code are available at \url{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970} \citep{KreienkampMasked2022a}.
+Materials and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}  \citep{Kreienkamp2022}.
+Protocols, materials, data, and code are available at \url{https://osf.io/pr9zs/?view_only=208a53a1f0ff48dda1c17357328fa578} \citep{Kreienkamp2022a}.
+The preregistration of Study 3 can be accessed as part of our Open Science Framework repository \citep{Kreienkamp2021f}.
 

### 2022-03-15 manuscript.tex
Updates from Overleaf

@@
 The authors received no specific funding for this work.
-Materials and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}  \citep{KreienkampMasked2022}.
-Protocols, materials, data, and code are available at \url{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970} \citep{KreienkampMasked2022a}.
+Materials and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}  \citep{Kreienkamp2022}.
+Protocols, materials, data, and code are available at \url{https://osf.io/pr9zs/?view_only=208a53a1f0ff48dda1c17357328fa578} \citep{Kreienkamp2022a}.
+The preregistration of Study 3 can be accessed as part of our Open Science Framework repository \citep{Kreienkamp2021f}
 
@@
 However, when using multilevel models to test the contact hypothesis, we find that individual outgroup interactions and perceived interaction quality have a strong influence on positive outgroup attitudes.
-We find that the fulfillment of psychological needs offers a strong predictor of positive attitudes after interactions and that these positive effects emerged via perceived interaction quality.
+The fulfillment of psychological needs is a strong predictor of positive attitudes after interactions and that these positive effects emerged via perceived interaction quality.
 The situational needs remained the core predictor of outgroup attitudes even after controlling for Allport’s (\citeyear{Allport1954b}) contact conditions or more general fundamental needs.
@@
 % neither are necessary or explain why an interaction is positive
-Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
+Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
 It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for such positive contact effects \citep[Allport's Optimal Contact conditions;][]{Allport1954b, Pettigrew1969}.
@@
 While we have argued that a need fulfillment mechanism is relevant to intergroup contact generally, its flexible and broad applicability might be ideally suited to address the pressing issue of understanding natural intergroup contacts outside the lab.
-Investigations of such 'real-life interactions' often suffer from the difficulty that past intergroup contact research has either focused on the mechanisms of individual interactions in artificial lab studies or has focused on longer-term recall self-reports of natural interactions \citep[e.g.,][]{Pettigrew2006}.
+Investigations of such `real-life interactions' often suffer from the difficulty that past intergroup contact research has either focused on the mechanisms of individual interactions in artificial lab studies or has focused on longer-term recall self-reports of natural interactions \citep[e.g.,][]{Pettigrew2006}.
 Even with extended intervention studies, the most fine-grained data available is usually limited to pre-post-control designs.
@@
 To test our main hypotheses, we collected three independent sets of extensive longitudinal data (Studies 1–3).
-The full surveys are available in Supplementary Materials A as well as in our open science repository (including a complete codebook, see OSF-REFERENCE).
-Our most comprehensive study (Study 3) was fully preregistered  \citep[available at][]{Kreienkamp2021f}.
+The full surveys are available in Supplementary Materials A as well as in our open science repository \citep[including a complete codebook, see][]{KreienkampMasked2022a}.
+Our most comprehensive study (Study 3) was fully preregistered  \citep[available at][]{KreienkampMasked2021f}.
+All studies received ethical approval from the University Masked for Peer Review.
 The fully annotated analyses are available in Supplementary Material B.
@@
 % aims re-iterated
-The aim of this project was in essence threefold.
+The aim of this project was threefold.
 We (1) tested the basic predictions of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data.
@@
 For between-subjects effects (using aggregated reports), neither the number of interactions, nor the average interaction quality were significant predictors of positive outgroup attitudes across all studies (also see Figure \ref{fig:ContactHypothesis}a).
-The aggregate findings are surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
+These aggregate findings are surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
 The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).\footnote{It should be noted that such inconsistencies with past research might in part be a data artefact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
-However, the multilevel models we employed should in principle be resistant to such imbalances.} In support of this possibility, once we used multilevel modeling to separate effects into a between-subjects and within-subjects part, we found that when having an interaction with an outgroup member (vs.
+However, the models we employed should in principle be resistant to such imbalances.} In support of this possibility, once we used multilevel modeling to separate effects into a between-subjects and within-subjects part, we found that when having an interaction with an outgroup member (vs.
 not having an outgroup interaction) is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account; also see Figure \ref{fig:ContactHypothesis}b).
@@
 While we believe that a need–based mechanism should be relevant to any inter-group contact, our sample has focused on a minority- and (voluntary) migrant perspective.
-Without additional evidence it thus remains difficult to judge whether motivational effects will generalize to other migrant groups (e.g., forced migrants), other intergroup contexts (e.g., gender- or sexual orientation groups), and to majority groups in their outgroup attitudes.
+Without additional evidence it thus remains difficult to judge whether motivational effects will generalize to other migrant groups (e.g., forced migrants), other intergroup contexts (e.g., gender-, religious-, or sexual orientation groups), and to majority groups in their outgroup attitudes.
 We know of no research that for other contexts psychological needs would not be relevant (once existential needs are met) but future research may extend our findings to other contexts to build an even broader understanding of psychological needs in intergroup contacts.
 A second limitation lies in our methodology.
-While extensive longitudinal data is close to the real-life events, this method comes at the expense of longer and more robust scales.
+While extensive longitudinal data is close to real-life events, this method comes at the expense of longer and more robust scales.
 Long and repetitive scales are often not feasible in extensive longitudinal methods because of the increased burden to the participants.
@@
 And finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
-This has come at the expense of specificity in the situational needs (i.e., we have not explored which exact needs people had during specific interactions).
-With the adaptive measurement we have proposed such an investigation would be possible (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
+This comes at the expense of specificity in the situational needs (i.e., we have not explored which exact needs people had during specific interactions).
+With the adaptive measurement we used such an investigation would be possible (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
 Nonetheless, future research may explore which exact needs are most important in different intergroup contexts.
@@
 % ESM data
-Given these limitations, we can draw a number of implications for other researchers and practitioners from our results.
+Given these limitations, we can nonetheless draw a number of implications for other researchers and practitioners --- ranging from the benefits of longitudinal data to theoretical implications.
 A first implication concerns the feasibility and usefulness of extensive longitudinal data for intergroup contact research and the broader field of social psychology.
-While setting up an extensive longitudinal study is in no manner easy, given the amount and quality of the data, we believe the efforts to be similar to a sizable cross-section data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with 10,000 data-points).
+While setting up an extensive longitudinal study is not easy, we believe the efforts to be similar to a sizable cross-sectional data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with over 10,000 data-points).
 Given the comparable effort, this opens up the possibility to explore research questions that focus on real-life phenomena outside the lab or focus on phenomena that depend on changes and influences over time.
@@
 However, if motivational mechanisms are indeed shown to be meaningful factors in intergroup contacts, future research may be able to integrate broader theoretical frameworks of intergroup contact (e.g., motivations guiding cognition and affect, which in turn drive behavior.
-cf., theory of reasoned goal pursuit; \citealp{Ajzen2019}).
+cf., theory of reasoned goal pursuit; \citealp{Ajzen2019}.
+Also see \citealp{Kreienkamp2022d}).
 
@@
 In cases where some or all optimal contact conditions are not possible to be fulfilled, needs offer an even more compelling alternative (e.g., where equal status is contextually not possible or in cases where people help despite a lack of institutional support).
-Additionally, our conceptualization of situational needs might offer an additional opportunity for practitioners and interventions.
+Additionally, our conceptualization of situational needs might offer an opportunity for practitioners and interventions.
 Instead of addressing needs as a one-size fits all solution (e.g., simply focusing on competence needs), one may at times ask outgroup interaction partners what they need during an interaction.
 This is not to say that we should not explore which needs tend to be relevant to specific groups in specific intergroup contact contexts.
-Rather, interventions for which such data is not available or infeasible to collect, a flexible and reactive approach to intergroup contact needs might be more fruitful.
+Rather, during interventions for which data on important need contents are not available or infeasible to collect, a flexible and reactive approach of inquiring momentary intergroup contact needs might be more fruitful.
 
@@
 % Conclusion paragraph
-In sum, in this paper we used extensive longitudinal methodologies to capture real-life interactions of recent migrants with the majority outgroup.
+In sum, we used extensive longitudinal methodologies to capture real-life interactions of recent migrants with the majority outgroup.
 Our three studies showcase the feasibility and utility of such data to test intergroup contact theory.

### 2022-03-15 Methods-and-Results.Rmd
robustness conclusions added

@@
 For full results see see Table \ref{tab:robustnessTblLong}, Figure \ref{fig:Robustness}, and Online Supplementary Material A.
+There is, thus, considerable evidence lending confidence to the stability and relevance of psychological need fulfillment as a predictor of positive outgroup attitudes for natural intergroup contacts.
 
@@
 
-In a final step we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
+In a final step, we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
 We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r studentSdtCompChiSq`).
@@
 For full results see Table \ref{tab:intergroupNeedsTblLong}, Figure \ref{fig:Robustness}, and Online Supplementary Material A.
+This means that also within this second sample, the fulfillment of psychological needs during intergroup contact remained a key predictor of positive outgroup attitudes, even when taking into account several alternative models.
 
@@
 For full results see Table \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as Online Supplementary Material A.
+Across all three studies, psychological need fulfillment, thus, remained a robust and flexible predictor of positive outgroup attitudes.
 

### 2022-03-15 Methods-and-Results.tex
M&R re-render

@@
 see see Table \ref{tab:robustnessTblLong}, Figure \ref{fig:Robustness},
-and Online Supplementary Material A.
+and Online Supplementary Material A. There is, thus, considerable
+evidence lending confidence to the stability and relevance of
+psychological need fulfillment as a predictor of positive outgroup
+attitudes for natural intergroup contacts.
 
@@
 
-In a final step we again checked whether during the interaction the core
-situational need remains a meaningful predictor even when taking other
-fundamental psychological needs into account. We find that the core need
-fulfillment adds significantly above a model with only the
+In a final step, we again checked whether during the interaction the
+core situational need remains a meaningful predictor even when taking
+other fundamental psychological needs into account. We find that the
+core need fulfillment adds significantly above a model with only the
 self-determination theory needs (random slopes models; \(\chi^2\)(6,
@@
 sample. For full results see Table \ref{tab:intergroupNeedsTblLong},
-Figure \ref{fig:Robustness}, and Online Supplementary Material A.
+Figure \ref{fig:Robustness}, and Online Supplementary Material A. This
+means that also within this second sample, the fulfillment of
+psychological needs during intergroup contact remained a key predictor
+of positive outgroup attitudes, even when taking into account several
+alternative models.
 
@@
 \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as
-Online Supplementary Material A.
-
-\input{Tables/descrFullWide}
-\input{Tables/descrOutWide}
-
-\input{Tables/mdlContactGeneralLong}
-\input{Tables/mdlTheorylong}
-\input{Tables/mdlRobustlong}
+Online Supplementary Material A. Across all three studies, psychological
+need fulfillment, thus, remained a robust and flexible predictor of
+positive outgroup attitudes.

### 2022-05-12 manuscript.tex

@@
 The authors received no specific funding for this work.
-Materials and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}  \citep{Kreienkamp2022}.
+Materials and software are available at \url{https://janniscodes.github.io/intergroup-contact-needs/}  \citep{Kreienkamp2022}.
 Protocols, materials, data, and code are available at \url{https://osf.io/pr9zs/?view_only=208a53a1f0ff48dda1c17357328fa578} \citep{Kreienkamp2022a}.
@@
 However, when using multilevel models to test the contact hypothesis, we find that individual outgroup interactions and perceived interaction quality have a strong influence on positive outgroup attitudes.
-The fulfillment of psychological needs is a strong predictor of positive attitudes after interactions and that these positive effects emerged via perceived interaction quality.
+The fulfillment of psychological needs is a strong predictor of positive attitudes after interactions and these positive effects emerged via perceived interaction quality.
 The situational needs remained the core predictor of outgroup attitudes even after controlling for Allport’s (\citeyear{Allport1954b}) contact conditions or more general fundamental needs.
@@
 
+% Methods and Results from RMarkdown render
 \input{Methods-and-Results}
-
-\begin{figure}
-  \caption{Contact Hypothesis}
-  \label{fig:ContactHypothesis}
-  \centering\includegraphics[width=\textwidth]{Figures/forestParametricGeneralComb.png}
-  %\begin{subfigure}{\textwidth}
-  %  \caption{}
-  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricGeneralLm.png}
-  %\end{subfigure}
-  %\begin{subfigure}{\textwidth}
-  %  \caption{}
-  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
-  %\end{subfigure}
-  \caption*{Note: \\
-  (a) summary of regression results from the aggregated contact and interaction quality data.\\
-  (b) summary of mixed models results of the contemporaneous contact effects.\\
-  General: Fixed effects meta analytic results are presented for completeness only.}
-\end{figure}
-
-\begin{figure}
-  \caption{Core Need Fulfillment}
-  \label{fig:AllportNeedFulfillment}
-  \centering\includegraphics[width=\textwidth]{Figures/forestParametricTheoryComb.png}
-  %\begin{subfigure}{\textwidth}
-  %  \caption{}
-  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryQualityCore.png}
-  %\end{subfigure}
-  %\begin{subfigure}{\textwidth}
-  %  \caption{}
-  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCore.png}
-  %\end{subfigure}
-  %\begin{subfigure}{\textwidth}
-  %  \caption{}
-  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCoreQuality.png}
-  %\end{subfigure}
-  \caption*{Note: \\
-  (a) Core Need Fulfillment predicting Interaction Quality.\\
-  (b) Core Need Fulfillment predicting Outgroup Attitudes.\\
-  (c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.\\
-  General: Fixed effects meta analytic results are presented for completeness only.}
-\end{figure}
-
-\begin{figure}
-  \caption{Robustness Analyses}
-  \label{fig:Robustness}
-  \centering\includegraphics[width=\textwidth]{Figures/forestParametricRobustnessComb.png}
-  %\begin{subfigure}{\textwidth}
-  %  \caption{}
-  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
-  %\end{subfigure}
-  %\begin{subfigure}{\textwidth}
-  %  \caption{}
-  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
-  %\end{subfigure}
-  \caption*{Note: \\
-  (a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).\\
-  (b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).\\
-  General: Fixed effects meta analytic results are presented for completeness only.}
-\end{figure}
 
@@
 Our results point to motivation as an understudied aspect of intergroup contact that is important in understanding when and why an interaction is perceived as positive and will lead to more positive outgroup attitudes.
+
+% Tables
+\input{Tables/descrFullWide}
+\input{Tables/descrOutWide}
+
+\input{Tables/mdlContactGeneralLong}
+\input{Tables/mdlTheorylong}
+\input{Tables/mdlRobustlong}
+
+% Figures
+\begin{figure}
+  \caption{Contact Hypothesis}
+  \label{fig:ContactHypothesis}
+  \centering\includegraphics[width=\textwidth]{Figures/forestParametricGeneralComb.png}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricGeneralLm.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
+  %\end{subfigure}
+  \caption*{Note: \\
+  (a) summary of regression results from the aggregated contact and interaction quality data.\\
+  (b) summary of mixed models results of the contemporaneous contact effects.\\
+  General: Fixed effects meta analytic results are presented for completeness only.}
+\end{figure}
+
+\begin{figure}
+  \caption{Core Need Fulfillment}
+  \label{fig:AllportNeedFulfillment}
+  \centering\includegraphics[width=\textwidth]{Figures/forestParametricTheoryComb.png}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryQualityCore.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCore.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCoreQuality.png}
+  %\end{subfigure}
+  \caption*{Note: \\
+  (a) Core Need Fulfillment predicting Interaction Quality.\\
+  (b) Core Need Fulfillment predicting Outgroup Attitudes.\\
+  (c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.\\
+  General: Fixed effects meta analytic results are presented for completeness only.}
+\end{figure}
+
+\begin{figure}
+  \caption{Robustness Analyses}
+  \label{fig:Robustness}
+  \centering\includegraphics[width=\textwidth]{Figures/forestParametricRobustnessComb.png}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
+  %\end{subfigure}
+  \caption*{Note: \\
+  (a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).\\
+  (b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).\\
+  General: Fixed effects meta analytic results are presented for completeness only.}
+\end{figure}
 

### 2022-10-20 Tables/workerVarDescr.tex
robust meta added
formulas adjusted

@@
 \midrule
-Core Need &  & 0.82*** & 0.60*** & 0.33 & 0.52** & -0.03\\
-Competence & 0.36*** &  & 0.89*** & 0.26 & 0.39 & -0.23\\
-Autonomy & 0.28*** & 0.22*** &  & 0.31 & 0.57** & 0.02\\
-Relatedness & 0.50*** & 0.39*** & 0.37*** &  & -0.07 & 0.14\\
-Quality & 0.17*** & 0.44*** & 0.27*** & 0.26*** &  & 0.50*\\
-Attitudes NL & 0.24*** & 0.36*** & 0.24*** & 0.37*** & 0.52*** & \\
+Core Need &  & 0.63*** & 0.47** & 0.00 & 0.40* & -0.22\\
+Competence & 0.37*** &  & 0.68*** & -0.13 & 0.17 & -0.26\\
+Autonomy & 0.31*** & 0.08** &  & -0.04 & 0.64*** & 0.16\\
+Relatedness & 0.45*** & 0.41*** & 0.22*** &  & 0.02 & -0.07\\
+Quality & 0.05 & 0.45*** & 0.11*** & 0.12*** &  & 0.47*\\
+Attitudes NL & 0.10*** & 0.34*** & 0.14*** & 0.14*** & 0.43*** & \\
 \addlinespace

### 2022-10-20 Methods-and-Results.Rmd
tables to Overleaf
overall correlation added

@@
   lme(
-    thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction,
+    thermometerDutch_1 ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
     random =  ~ 1 | PID,
@@
   mdlWorker$lmerInterceptAttType <- lmer(
-    thermometerDutch_1 ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    thermometerDutch_1 ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM + (1 | PID),
     data = dtWorkerSupp$workerInteractionType
@@
   confint = TRUE,
-  digits = 3,
-  center = FALSE
+  digits = 3
 )
@@
 
-\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis in two steps.
+\subsubsection{Contact Hypothesis}
+<!-- We tested the most general contact hypothesis in two steps.
 First, we assessed whether overall between participants more intergroup interactions were related to to more positive average outgroup attitudes.
@@
 And when considering the number of contacts and average contact quality jointly in a linear regression, we additionally found a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of contacts the positive effect of average contact quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblLong}).
-We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+-->
+We used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
+We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
 This is unusual and might indicate that the effect is very consistent across participants.
-However, the small number of participants, or other measurement issues provide an alternative explanation.}.
-Thus, in our first data we find mixed results, where outgroup contacts show a positive effect on outgroup attitudes in the moment but these results do not translate into average differences between participants (even tough the average number of contacts does seem to interact with average contact quality to predict outgroup attitudes).
-However, it should be noted that the between-participant analyses in the aggregated form are based on a small sample size.
+However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}.
+Thus, in our first data we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data.
+While this offers support for the most basic premise of the intergroup contact hypothesis (i.e., that any interaction will lead to more positive outgroup attitudes), this analysis does not consider any notion of interaction quality.
+We assess the conditional effects of interaction numbers and interaction quality ratings after we report on the individual studies to avoid under-powered analyses.
 
@@
 ```
-
-\input{Tables/descrFullWide}
-\input{Tables/descrOutWide}
-
-\input{Tables/mdlContactGeneralLong}
-\input{Tables/mdlTheorylong}
-\input{Tables/mdlRobustlong}
 

### 2022-10-20 Methods-and-Results.Rmd
tables adjusted

@@
 load("data/wrangled.RData")
+# remove accidental surplus to avoid conflicts
+# rm(list = ls(pattern = "mdl|medicalSdtComp"))
 ```
@@
 ```{r descrFullLong, include=FALSE}
+allMlCor <-
+  MlCorMat(
+    data = dtAll$mlAll, #%>% filter(OutgroupInteraction == "Yes"),
+    id = "ID",
+    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "qualityOverall", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+  )
+
 # Full Sample Descriptives Table [longer format (Descriptives below correlations)]
@@
     select(names(workerMlCor), "Allport") %>%
-    rownames_to_column(., "Variable")
+    rownames_to_column(., "Variable"),
+  allMlCor %>%
+    select(names(workerMlCor)) %>%
+    rownames_to_column(., "Variable") %>%
+    mutate(Allport = "")
 ) %>%
@@
             sum(nrow(workerMlCor), nrow(studentMlCor), nrow(medicalMlCor))) %>%
+  pack_rows("Across Studies", sum(nrow(workerMlCor), nrow(studentMlCor), nrow(medicalMlCor)) + 1,  
+            sum(nrow(workerMlCor), nrow(studentMlCor), nrow(medicalMlCor), nrow(allMlCor))) %>%
   gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) %>% # fix table position
@@
   studentMlCor %>%
+    select(names(workerMlCor)) %>%
     t %>%
@@
     as.data.frame %>%
-    rownames_to_column(., "Variable")
+    rownames_to_column(., "Variable"),
+  allMlCor %>%
+    select(names(workerMlCor)) %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean")
 ) %>%
@@
   pack_rows("Study 3", sum(ncol(workerMlCor), ncol(studentMlCor)) + 1,  
-            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor))) %>% # fix table position
+            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor))) %>%
+  pack_rows("Across Studies", sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor)) + 1,  
+            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor), ncol(allMlCor))) %>% # fix table position
   footnote(
@@
     mutate(analysis = "(A) Aggregate Linear Regression",
-           metaId = paste(coef, analysis, sep = ".")),
+           metaId = paste(coef, analysis, sep = ".")) %>%
+    as.data.frame,
   GeneralLmerMeta$eff %>%
     mutate(analysis = "(B) Mixed Effects Regression",
-           metaId = paste(coef, analysis, sep = "."))
+           metaId = paste(coef, analysis, sep = ".")) %>%
+    as.data.frame
 )
@@
     mutate(analysis = "(A) Contact and Need Fulfillment",
-           metaId = paste(coef, analysis, sep = ".")),
+           metaId = paste(coef, analysis, sep = ".")) %>%
+    as.data.frame,
   robustMetaSDT$eff %>%
     mutate(analysis = "(B) Other Needs",
-           metaId = paste(coef, analysis, sep = "."))
+           metaId = paste(coef, analysis, sep = ".")) %>%
+    as.data.frame
 )

### 2022-10-20 Methods-and-Results.tex
tables adjusted

@@
 
-We tested the most general contact hypothesis in two steps. First, we
-assessed whether overall between participants more intergroup
-interactions were related to to more positive average outgroup
-attitudes. Second, we tested whether a potential positive effect on
-outgroup attitudes depended on the interaction quality (jointly with the
-number of interactions). We find that neither the overall number of
-contacts nor the number of experience sampling responses with a contact
-were significantly related with the average outgroup attitudes (all
-\textbar{} \textit{r} \textbar{} \textless{} 0.03, all \textit{p}
-\textgreater{} 0.887). However, we did find a medium sized correlation
-between the participants' average contact quality and their average
-outgroup attitudes (\textit{r} = 0.55, \textit{p} = 0.010). And when
-considering the number of contacts and average contact quality jointly
-in a linear regression, we additionally found a statistically
-significant interaction term (\textit{b} = -0.05, \textit{t}(17) =
--2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34), where in our sample
-with an increasing number of contacts the positive effect of average
-contact quality becomes weaker (also see Table
-\ref{tab:intergroupGeneralTblLong}). We additionally used a multilevel
-regression to check whether having an interaction with an outgroup
-member had a situational (i.e., contemporaneous) effect within the
-participants. We find that having an outgroup contact is indeed
-associated with significantly more positive outgroup attitudes within
-the participants (\textit{b} = 2.48, \textit{t}(1,200) = 4.36,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}1.36, 3.59{]}), even
+We used a multilevel regression to check whether having an interaction
+with an outgroup member had a situational (i.e., contemporaneous) effect
+within the participants. We find that having an outgroup contact is
+indeed associated with significantly more positive outgroup attitudes
+within the participants (\textit{b} = 2.48, \textit{t}(1,200) = 4.37,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}1.37, 3.59{]}), even
 after controlling for having an interaction with a non-Dutch (which did
@@
 This is unusual and might indicate that the effect is very consistent across participants.
-However, the small number of participants, or other measurement issues provide an alternative explanation.}.
-Thus, in our first data we find mixed results, where outgroup contacts
-show a positive effect on outgroup attitudes in the moment but these
-results do not translate into average differences between participants
-(even tough the average number of contacts does seem to interact with
-average contact quality to predict outgroup attitudes). However, it
-should be noted that the between-participant analyses in the aggregated
-form are based on a small sample size.
+However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}.
+Thus, in our first data we find initial evidence that outgroup contacts
+show a positive effect on outgroup attitudes within real-life data.
+While this offers support for the most basic premise of the intergroup
+contact hypothesis (i.e., that any interaction will lead to more
+positive outgroup attitudes), this analysis does not consider any notion
+of interaction quality. We assess the conditional effects of interaction
+numbers and interaction quality ratings after we report on the
+individual studies to avoid under-powered analyses.
 

### 2022-10-20 scripts/functions/MlCorMat.R

@@ -145,16 +145,17 @@ MlCorMat <-
       `ICC(1)` =
         misty::multilevel.icc(
           data %>% select(selection),
-          cluster = data$PID,
+          cluster = data[[id]],
           type = 1
         ),
       `ICC(2)` =
         misty::multilevel.icc(
           data %>% select(selection),
-          cluster = data$PID,
+          cluster = data[[id]],
           type = 2
         )
     )
+    
     
     for (i in 1:length(selection)) {
       dataRed <- 

### 2022-10-20 Methods-and-Results.Rmd
table adjusted

@@
 ```{r descrOutLong, include=FALSE}
+#
+#       OLD!!
+#
+
 # Outgroup Interaction Sample Descriptives Table
@@
 ```{r descrOutWide, include=FALSE}
+allOutMlCor <-
+  MlCorMat(
+    data = dtAll$mlAll %>% filter(OutgroupInteraction == "Yes"),
+    id = "ID",
+    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "qualityOverall", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+  )
+
 # Outgroup Interaction Sample Descriptives Table --- wider version
@@
   studentOutMlCor %>%
+    select(names(workerOutMlCor)) %>%
     t %>%
@@
     as.data.frame %>%
-    rownames_to_column(., "Variable")
+    rownames_to_column(., "Variable"),
+  allOutMlCor %>%
+    select(names(workerOutMlCor)) %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Allport = "",
+               .before = "Grand Mean")
 ) %>%
@@
             sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor))) %>% 
+  pack_rows("Across Studies", sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor)) + 1,  
+            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor), ncol(allOutMlCor))) %>% 
   footnote(

### 2022-10-22 manuscript.tex
Updates from Overleaf

@@
    \renewcommand\thesubhyp{\thehyp\alph{subhyp}}
+
+% Analysis Plan sections (probably better as Definitions or Remarks instead of Theorems)
+\newtheorem{ap}{Hypothesis}
+
+\newtheorem{subap}{Hypothesis}
+   \renewcommand\thesubap{\theap\alph{subap}}
 
@@
     \item Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes across extensive longitudinal data.
+    \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
     \item Based on Allport’s optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
-    \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
+Based on our proposal, we expect situational need fulfillments to work at least as good as Allport's conditions in predicting outgroup attitudes.
 \end{enumerate}
 Beyond these main hypotheses we have formulated several sub-hypotheses that form the basis for our analysis plan (these sub-hypotheses also include several robustness checks and are available in Appendix \ref{app:AppendixHypotheses}).
-Given the more complex data structure of the extensive longitudinal data, we opted to test our hypotheses using a multilevel regression model, where the measurement occasions (level 1) were nested within the participants (level 2).
-Given that more complex dynamic modeling procedures are not necessary to test these more basic hypotheses, we will focus on the contemporaneous effect of the data (e.g., need fulfillment during the intergroup interaction predicts outgroup attitudes following the interaction).
-Such an approach is also tolerant to missing data and uneven case numbers within participants.
 
@@
 The fully annotated analyses are available in Supplementary Material B.
+
+\section{Analysis Plan}
+\begin{center}
+    \noindent\rule{8cm}{0.4pt}\\
+    \hl{\textit{New Section:}}\\
+    \vspace{-0.25cm}
+    \noindent\rule{8cm}{0.4pt}
+\end{center}
+
+Given the more complex data structure of the extensive longitudinal data, we opted to test most of our hypotheses using multilevel regression models, where the measurement occasions (level 1) were nested within the participants (level 2).
+Given that more complex dynamic modeling procedures are not necessary to test these more basic hypotheses, we will focus on the contemporaneous effect of the data (e.g., need fulfillment during the intergroup interaction predicts outgroup attitudes following the interaction).
+Such an approach is also tolerant to missing data and uneven case numbers within participants.
 As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text (for the full modeling process see Supplementary Material B).
+
+Statistical power is notoriously difficult to estimate for intensive longitudinal- and multilevel models because of the complex covariance structures.
+Yet, while power simulations require researchers to make a lot of assumptions, the now famous meta-analysis of the intergroup contact hypothesis estimates the average effect size of intergroup contact at around: $r$ = .21 \citep[][]{Pettigrew2006}.
+For such a relatively small effect size, cross-sectional data collections would need to collect 175 to 212 participants (for correlational- and linear regression analyses with .8 power respectively).
+Given that even our smallest sample captured 387 intergroup contacts, each of the studies should have abandoned power to detect even smaller effect sizes than the effects commonly found within the literature.
+Additionally, both the number of participants and the number of measurements are within the highest percentiles of sample sizes found within the broader intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
+
+For our main theory tests we sequentially focus on five sets of models to test and validate our hypotheses:
+
+\hl{[link sub-hypotheses to the following?]}\\
+\hl{[add formulas to the following?]}\\
+\hl{[move (parts of) the following to Appendix }\ref{app:AppendixHypotheses}\hl{?]}\\
+\hl{[I think this is too long]}
+
+\begin{enumerate}
+    \item \textbf{Contact hypothesis in extensive longitudinal data.} Within the individual studies, we begin by testing the most basic assumption of the intergroup contact hypothesis that outgroup attitudes should be more positive after outgroup interactions but not after non-outgroup interactions.
+For this we use multi-level regression analyses, predicting outgroup attitudes from outgroup interaction and non-outgroup interaction dummy variables.
+We also reintroduce the participant means as level two predictors to fully disentangle measurement- (level 1) and participant (level 2) variances.
+
+    Importantly, this initial test of the contact hypothesis in intensive longitudinal data does not consider the influence of interaction quality.
+This is due to the structural missingness of interaction quality --- where people are only able to report their interaction quality perceptions if they had an interaction.
+Such structural missingness should not be imputed, which stands in conflict with (multi-level) linear regression analyses that can only be estimated where all variables have valid data (which would only be measurements following interactions).
+The best way to assess the joint effects of interaction numbers and interaction quality is thus a test on an aggregate level.
+However, as such an aggregation reduces statistical power to the participant level, we assess the full contact hypothesis in the `embeddedness and stability across studies' section, where we combine the data of the three studies (see below).
+    \item \textbf{Core need fulfillment during intergroup contact.} The main proposal of this manuscript has been the assertion that the fulfillment of situation core needs during an interaction will be associated with more positive interaction quality perceptions and, ultimately, more positive outgroup attitudes.
+Thus, for the main set of analyses, we focus on the reported outgroup interactions only.
+For each study, we will use multi-level regressions to test the main three assertions of our proposal (mirroring the basic steps of a traditional mediation analysis).
+    \begin{enumerate}
+        \item Core need fulfillment during outgroup interactions should predict more positive outgroup attitudes.
+To test this sub-hypothesis, we use a two-level regression analysis of outgroup attitudes, with core need fulfillment as the main predictor variable.
+        \item Core need fulfillment during outgroup interactions should predict higher perceived interaction quality.
+This sub-hypothesis mirrors the one above so that perceived interaction quality is predicted by core need fulfillment in a multi-level regression analysis.
+        \item The effect of core need fulfillment on outgroup attitudes should be reduced when considered together with perceived interaction quality.
+To test whether perceived interaction quality is indeed the psychological mechanism that explains the variance in outgroup attitudes, we use a multi-level regression analysis of outgroup attitudes with core need fulfillment and perceived interaction quality as the main predictor variables.
+    \end{enumerate}
+    \item \textbf{Robustness within studies.} To build further confidence in the effect of core need fulfillment during outgroup interactions, we conduct two additional robustness analyses for each study.
+    \begin{enumerate}
+        \item To check for the role of alternate psychological needs, we add the fulfillment of self-determination theory needs (i.e., competence, autonomy, and relatedness) to the multi-level regression.
+We then also compare the model with models that predicts outgroup attitudes from self-determination theory need fulfillments or core need fulfillments only.
+        \item To ensure that the core need fulfillment is outgroup contact specific, we return to the full sample of intensive longitudinal measurements within each study and test whether there is an interaction effect of outgroup contact (vs.
+no outgroup contact) and core need fulfillment.
+We expect that the effect of core need fulfillment is specific to outgroup interactions and not merely due to a more need fulfilled life in general.
+    \end{enumerate} 
+    \item \textbf{Allport's conditions in extensive longitudinal data.} Within the third study we formally measure all of Allport's optimal contact conditions. 
+    \begin{enumerate}
+        \item We use multi-level regression models to test whether the fulfillment of Allport's conditions in real-life data predicts more positive outgroup attitudes and higher perceived interaction quality, using the same approach as for the core need fulfillment above.
+        \item We then compare the effect of Allport's contact conditions with our core need fulfillment by comparing the model fit statistics of the two individual models and by adding both concepts to a joint multi-level regression model, to see whether the two approaches explain the same variance in outgroup attitudes.
+    \end{enumerate}
+    \item \textbf{Embeddedness and stability across studies.} Within the final set of analyses, we look at the broader picture of our results and leverage the data from all participants to contextualize our results.
+    \begin{enumerate}
+        \item We first assess the stability of our main analyses. We use forest plots (including meta analytical estimates) to visualize the direction and effect sizes of our three studies. 
+        \item We then combine the data from the three studies to test the basic tenants of intergroup contact hypothesis more broadly using intensive longitudinal real-life data.
+As we have mentioned above assessing the effects of intergroup contacts and perceived interaction quality jointly is difficult within a multi-level regression because quality perceptions are only available when participants had an interaction.
+To circumvent this issue, we use the data from all participants and aggregate the number of interactions participants had, their average interaction quality perceptions, as well as their average outgroup attitudes.
+We can then use a linear regression analysis to assess the joint effects of intergroup contacts and interaction quality to predict outgroup attitudes (while controlling for the participants' study).
+This not only offers a more general test of the contact hypothesis with real-life data, but the aggregated data also mirrors the most common methodology of assessing intergroup contact effects within the cross-sectional literature --- where participants are asked to recall how many interactions they had over a one month period, how positive these interactions were, and what their general attitudes towards the outgroup are.
+This analysis will thus be able to explore potential discrepancies between our main multi-level analyses, the aggregation of extensive longitudinal data, and traditional participant recall studies.
+        \item We, finally, use the qualitative data from the participants' self-identified core needs to contextualize our results.
+We leverage machine learning to extract a topic modeling of the free-text entries across the three studies.
+We describe the extracted topics and themes, and compare them to the need contents usually found and measured within the psychological literature.
+Full methodological details and visualizations are available in Supplemental Material C.
+    \end{enumerate}
+\end{enumerate}
 

### 2022-10-22 Methods-and-Results.Rmd
simple ML contact test adapted

@@
 Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
-interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r (sum(dtWorkerSupp$workerAvFreQual$SumContactNL) / nrow(dtWorkerSupp$workerInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r format(nrow(dtWorkerSupp$workerInteractionType), big.mark=",")` experience sampling responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts.
+interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtWorkerSupp$workerAvFreQual$SumContactNL), big.mark=",")` of all `r format(nrow(dtWorkerSupp$workerInteractionType), big.mark=",")` experience sampling responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts.
 These participants are removed from any analyses that focus on outgroup contacts.}.
@@
 We used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
+Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by use centered predictors and reintroducing the means as level two predictors.
+Nonetheless, we also offer an analysis of the joint data sets in Online Supplemental Material A (for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
 This is unusual and might indicate that the effect is very consistent across participants.
@@
 The participants recorded between `r dtStudentSupp$studentContactFreq$SumContactNL[dtStudentSupp$studentContactFreq$SumContactNL > 0] %>% min`--`r dtStudentSupp$studentContactFreq$SumContactNL %>% max`
-interactions with Dutch majority people (`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r (sum(dtStudentSupp$studentContactFreq$SumContactNL) / nrow(dtStudentSupp$studentInteractionType) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r format(nrow(dtStudentSupp$studentInteractionType), big.mark=",")` experience sampling responses).
+interactions with Dutch majority people (`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtStudentSupp$studentContactFreq$SumContactNL), big.mark=",")` of all `r format(nrow(dtStudentSupp$studentInteractionType), big.mark=",")` experience sampling responses).
 
@@
   lme(
-    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction,
+    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
     random =  ~ 1 | PID,
@@
   mdlStudent$lmerInterceptAttType <- lmer(
-    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM + (1 | PID),
     data = dtStudentSupp$studentInteractionType
@@
   AttitudesDutch ~
-    OutgroupInteraction + NonOutgroupInteraction,
-  random = ~ 1 + OutgroupInteraction + NonOutgroupInteraction | PID,
+    OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
+  random = ~ 1 + OutgroupInteractionC + NonOutgroupInteractionC | PID,
   control = lmeControl(opt = "optim"),
@@
     AttitudesDutch ~
-      OutgroupInteraction + NonOutgroupInteraction +
-      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+      OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM +
+      (1 + OutgroupInteractionC + NonOutgroupInteractionC | PID),
     data = dtStudentSupp$studentInteractionType
@@
 
-\subsubsection{Contact Hypothesis}We tested the most general contact hypothesis as in Study 1.
+\subsubsection{Contact Hypothesis}
+<!-- We tested the most general contact hypothesis as in Study 1.
 We found a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
@@
 Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblLong} and Figure \ref{fig:ContactHypothesis}).
-We additionally used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently; For full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, as well as Online Supplementary Material A).
-Thus, in our second data set we find mixed results; outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
-However, we find that this effect does not depend on the average perceived interaction quality.
-This unexpected results, might be due to the aggregation process and the following analyses will focus in on the role of the perceived interaction quality during an outgroup interaction.
+-->
+We tested the most general contact hypothesis as we did for Study 1.
+We, again, used a multilevel regression analysis to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
+We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently).
+We again added the participant means back into the model.
+Because these are the means of the contact dummy variables they are the proportion of measurements that included a particular contact.
+This not only adjusts the model for unequal cell sizes but allows us to see whether between subject differences in the relative number of interactions had an effect on outgroup attitudes.
+We find that in this data set participant-level outgroup contact proportions were also a positive predictor of outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionM")`).
+The relative number of non-outgroup interactions showed no such effect (for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, as well as Online Supplementary Material A).
+Thus, in our second data set we find that outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
 
@@
 The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
-(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r (sum(dtMedicalSupp$medicalContactFreq$SumContactNL) / nrow(dtMedical$full) * 100) %>% round(2) %>% format(nsmall=2)`\% of all `r format(nrow(dtMedical$full), big.mark=",")` experience sampling responses).
+(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtMedicalSupp$medicalContactFreq$SumContactNL), big.mark=",")` of all `r format(nrow(dtMedical$full), big.mark=",")` experience sampling responses).
 
@@
   mdlMedical$lmerInterceptAttType <- lmer(
-    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM + (1 | PID),
     data = dtMedical$full
@@
     AttitudesDutch ~
-      OutgroupInteraction + NonOutgroupInteraction +
-      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+      OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM +
+      (1 + OutgroupInteractionC + NonOutgroupInteractionC | PID),
     data = dtMedical$full
@@
 
-\subsubsection{Contact Hypothesis}As in Studies 1 and 2, we first conducted a general contact hypothesis test.
+\subsubsection{Contact Hypothesis}
+<!-- As in Studies 1 and 2, we first conducted a general contact hypothesis test.
 We found no correlation between the overall number of intergroup contacts and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (|\textit{r}| < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
@@
 This result mirrors that of Study 1 but is inconsistent with the second study.
-Additionally, in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionYes")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A).
-Thus, in our third data set we again found mixed results.
-Aggregate outgroup contacts were generally not significantly related to average outgroup attitudes on a between participant level and this effect was also not suppressed by an average interaction quality (i.e., no interaction effect).
-However, while the aggregate data was partly inconsistent with the first two studies, the within person contemporaneous effect of intergroup contact was consistent across all three studies.
+-->
+Additionally, in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A).
+Thus, in our third data set we found within person contemporaneous effect of intergroup contact was consistent across all three studies.
 

### 2022-10-22 Methods-and-Results.tex
simple ML contact test adapted

@@
 members (3.23--91.07\% of individual experience sampling measurements;
-31.59\% of all 1,225 experience sampling
+387 of all 1,225 experience sampling
 responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts.
@@
 after controlling for having an interaction with a non-Dutch (which did
-not relate to outgroup attitudes independently; For full results see
-Table \ref{tab:intergroupGeneralTblLong}, Figure
+not relate to outgroup attitudes independently). Additionally, while
+multi-level regressions are generally robust against unequal cell sizes,
+we correct for inequalities by use centered predictors and reintroducing
+the means as level two predictors. Nonetheless, we also offer an
+analysis of the joint data sets in Online Supplemental Material A (for
+full results see Table \ref{tab:intergroupGeneralTblLong}, Figure
 \ref{fig:ContactHypothesis}, and Online Supplementary Material
@@
 with Dutch majority people (1.64--93.75\% of individual experience
-sampling measurements; 18.83\% of all 4,965 experience sampling
-responses).
+sampling measurements; 935 of all 4,965 experience sampling responses).
 
@@
 
-We tested the most general contact hypothesis as in Study 1. We found a
-significant correlation with average outgroup attitudes for both the
-total number of outgroup interactions (\textit{r} = 0.22, \textit{p} =
-0.019) and the number of measurement beeps with an interaction
-(\textit{r} = 0.28, \textit{p} = 0.003). However, we found no
-significant correlation between the participants' average interaction
-quality and their average outgroup attitudes (\textit{r} = 0.04,
-\textit{p} = 0.679). Thus, when considering the number of interactions
-and average interaction quality jointly in a linear regression, we find
-a main effect of intergroup contacts to predict outgroup attitudes
-(\textit{b} = 0.81, \textit{t}(109) = 3.29, \textit{p} = 0.001,
-\(\eta_p^2\) = 0.08) but no significant effect of average perceived
-contact quality and no significant interaction term (for full results
-see Table \ref{tab:intergroupGeneralTblLong} and Figure
-\ref{fig:ContactHypothesis}). We additionally used a multilevel
-regression to check whether having an interaction with an outgroup
-member had a situational (i.e., contemporaneous) effect within the
-participants. We find that having an outgroup interaction is indeed
-associated with significantly more positive outgroup attitudes within
-the participants (random slopes model; \textit{b} = 2.99,
-\textit{t}(4,850) = 3.80, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}1.45, 4.54{]}), even after controlling for having an
-interaction with a non-Dutch person (which did not relate to outgroup
-attitudes independently; For full results see Table
-\ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis},
-as well as Online Supplementary Material A). Thus, in our second data
-set we find mixed results; outgroup contacts show a positive effect on
-outgroup attitudes in the moment and on average between participants.
-However, we find that this effect does not depend on the average
-perceived interaction quality. This unexpected results, might be due to
-the aggregation process and the following analyses will focus in on the
-role of the perceived interaction quality during an outgroup
-interaction.
+We tested the most general contact hypothesis as we did for Study 1. We,
+again, used a multilevel regression analysis to check whether having an
+interaction with an outgroup member had a situational (i.e.,
+contemporaneous) effect within the participants. We find that having an
+outgroup interaction is indeed associated with significantly more
+positive outgroup attitudes within the participants (random slopes
+model; \textit{b} = 2.83, \textit{t}(4,850) = 3.57, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}1.28, 4.38{]}), even after
+controlling for having an interaction with a non-Dutch person (which did
+not relate to outgroup attitudes independently). We again added the
+participant means back into the model. Because these are the means of
+the contact dummy variables they are the proportion of measurements that
+included a particular contact. This not only adjusts the model for
+unequal cell sizes but allows us to see whether between subject
+differences in the relative number of interactions had an effect on
+outgroup attitudes. We find that in this data set participant-level
+outgroup contact proportions were also a positive predictor of outgroup
+attitudes (\textit{b} = 26.55, \textit{t}(110) = 2.90, \textit{p} =
+0.004, \textit{95\%CI}{[}8.61, 44.46{]}). The relative number of
+non-outgroup interactions showed no such effect (for full results see
+Table \ref{tab:intergroupGeneralTblLong}, Figure
+\ref{fig:ContactHypothesis}, as well as Online Supplementary Material
+A). Thus, in our second data set we find that outgroup contacts show a
+positive effect on outgroup attitudes in the moment and on average
+between participants.
 
@@
 members (2.13--87.18\% of individual experience sampling measurements;
-41.44\% of all 4,107 experience sampling responses).
+1,702 of all 4,107 experience sampling responses).
 
@@
 
-As in Studies 1 and 2, we first conducted a general contact hypothesis
-test. We found no correlation between the overall number of intergroup
-contacts and average outgroup attitudes --- for neither the total number
-of outgroup interactions nor the number of measurement beeps with an
-interaction (\textbar{}\textit{r}\textbar{} \textless{} 0.13, \textit{p}
-\textgreater{} 0.291). However, we did find a significant correlation
-between the participants' average interaction quality and their average
-outgroup attitudes (\textit{r} = 0.25, \textit{p} = 0.036). When
-considering the number of interactions and average interaction quality
-jointly in a linear regression, we only found a main effect of average
-perceived interaction quality on outgroup attitudes (\textit{b} = 0.36,
-\textit{t}(67) = 2.22, \textit{p} = 0.030, \(\eta_p^2\) = 0.07) but no
-significant effect of the number of contacts nor an interaction effect.
-This result mirrors that of Study 1 but is inconsistent with the second
-study. Additionally, in a multilevel regression to check for
-contemporaneous within person effects, we found that having an outgroup
-interaction was indeed associated with significantly more positive
-outgroup attitudes within the participants (random slopes model;
-\textit{b} = 5.63, \textit{t}(3,834) = 6.61, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}3.97, 7.29{]}), even after controlling for
-having an interaction with a non-Dutch (which did not relate to outgroup
-attitudes independently; for full results see Table
+Additionally, in a multilevel regression to check for contemporaneous
+within person effects, we found that having an outgroup interaction was
+indeed associated with significantly more positive outgroup attitudes
+within the participants (random slopes model; \textit{b} = 5.57,
+\textit{t}(3,834) = 6.52, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}3.90, 7.23{]}), even after controlling for having an
+interaction with a non-Dutch (which did not relate to outgroup attitudes
+independently; for full results see Table
 \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis},
 and Online Supplementary Material A). Thus, in our third data set we
-again found mixed results. Aggregate outgroup contacts were generally
-not significantly related to average outgroup attitudes on a between
-participant level and this effect was also not suppressed by an average
-interaction quality (i.e., no interaction effect). However, while the
-aggregate data was partly inconsistent with the first two studies, the
-within person contemporaneous effect of intergroup contact was
+found within person contemporaneous effect of intergroup contact was
 consistent across all three studies.

### 2022-10-22 Methods-and-Results.Rmd
forest and overall ols added

@@
 
+\section{Embeddedness and Stability across Studies}
+
+\begin{center}
+    \noindent\rule{8cm}{0.4pt}\\
+    \hl{\textit{New Section:}}\\
+    \vspace{-0.25cm}
+    \noindent\rule{8cm}{0.4pt}
+\end{center}
+
+Introduction sentence
+
+\hl{maybe move this first paragraph to the end?}
+\subsection{Stability}
+We begin by assessing the stability of our main analyses across the three studies.
+To do so, we plot the effect sizes of each parameter of interest in a forest plot.
+Forest plots are a popular form of evidence synthesis and are commonly found within meta-analytic efforts.
+By plotting a standardized effect size and confidence interval of key parameters for each study, forest plots offer a visual method of identifying broader patterns across studies.
+This affords users a chance to spot stable as well as unreliable effects more easily.
+While not the focus of our efforts here, forest plots are commonly accompanied with a meta-analytic effect size that summarizes the effect size across studies.
+
+We assess forest plots of the basic contact hypothesis test (Figure \ref{fig:ContactHypothesis}), the core need fulfillment proposal (Figure \ref{fig:AllportNeedFulfillment}), as well as the robustness analyses (Figure \ref{fig:Robustness}).
+For the basic contact hypothesis test we see that outgroup contact has a strong and consistent effect on outgroup attitudes while interactions with non-outgroup members consistently have no meaningful effect on outgroup attitudes.
+While this would be expected from the general intergroup contact literature, this is not a trivial finding.
+We are among the first to assess the contact hypothesis using real-life data from intensive longitudinal data and these close to event assessments are comparable but not equivalent to the assessments found in cross-sectional data (also see below).
+When looking at Figure \ref{fig:AllportNeedFulfillment}, we see that the fulfillment of core needs during intergroup contacts is consistently a meaningful predictor of outgroup attitudes and interaction quality perceptions (see Figure \ref{fig:AllportNeedFulfillment} A and B).
+We also see that the effect of core need fulfillment on outgroup attitudes is strongly reduced when modeled together with interaction quality perceptions, supporting our assertion that interaction quality offers a psychological mechanism for the direct effect.
+Additionally, the core need fulfillment is also consistently outgroup contact specific (Figure \ref{fig:Robustness} A) and remains a meaningful predictor of outgroup attitudes even when controlling for traditional psychological need fulfillments (Figure \ref{fig:Robustness} B).
+
+\subsection{General contact hypothesis}
+```{r join data sets for analysis}
+# Join aggregated data
+avS1 <- dtWorkerSupp$workerAvFreQual %>%
+  select(
+    -ExternalReference
+  ) %>%
+  mutate(
+    PID = c(1:nrow(.)),
+    study = "S1"
+  ) %>%
+  select(PID, everything())
+avS2 <- dtStudentSupp$studentContactFreq %>%
+  mutate(
+    study = "S2"
+  )
+avS3 <- dtMedicalSupp$medicalContactFreq %>%
+  mutate(
+    study = "S3"
+  )
+
+avAll <- bind_rows(avS1, avS2, avS3) %>%
+  mutate(
+    ID = c(1:nrow(.)),
+    studyNum1 = ifelse(study == "S1", 1, 0),
+    studyNum3 = ifelse(study == "S3", 1, 0)
+  )
+avAll$study2 <- relevel(as.factor(avAll$study),"S2")
+```
+```{r OLS regression across the three studies}
+lmAllAttFreqQualX <-
+  lm(
+    AvAttitude ~ SumContactNL_c * AvQuality_c + SumContactNL_c * study2 + AvQuality_c * study2,
+    data = avAll
+  )
+
+summ(
+  lmAllAttFreqQualX,
+  confint = TRUE,
+  digits = 3
+)
+
+# prepare F stat for manuscript
+fit <- summary(lmAllAttFreqQualX)
+lmAllFstatLatex <- paste(
+  "\\textit{F}(",
+  fit$fstatistic["numdf"],
+  ", ",
+  fit$fstatistic["dendf"],
+  ") = ",
+  format(round(fit$fstatistic["value"], 2), nsmall = 2),
+  ", \\textit{p} = ",
+  format(round(
+    pf(
+      fit$fstatistic["value"],
+      fit$fstatistic["numdf"],
+      fit$fstatistic["dendf"],
+      lower.tail = FALSE
+    ),
+    3
+  ), nsmall = 3),
+  ", \\textit{R\\textsuperscript{2}} = ",
+  format(round(fit$r.squared, 2), nsmall = 2),
+  sep = ""
+)
+```
+
+During the main analyses, we have thus far shown that participants held more positive outgroup attitudes following intergroup contacts and that a perceived interaction quality was associated with more positive outgroup attitudes following an intergroup contact.
+We have, however, not brought the two elements of the contact hypothesis together in a single analysis.
+This is mainly due to the difficulty that interaction quality ratings are only possible when participants had an interaction --- which means that the two factors cannot be assessed in a multilevel analysis that models individual measurement occasions.
+This has not been an issue in the past literature because experimental and cross-sectional data collections have only considered cases in which intergroup contacts were present.
+Outside of the lab, the most common method has been to ask participants to recall how many interactions they had over the past month, how positive these interactions were, and how positive they feel towards the outgroup in general.
+The effects of intergroup contacts, interaction quality, and outgroup attitudes are thus aggregated by the participant in a cognitive recall aggregation.
+Intensive longitudinal data also allows for aggregation of all three variables, with the differences that the measurements are aggregated from individual reports that are close to the actual experience.
+However, this aggregation process summarizes the dense multitude of measurement occasions as single summary statistics per participants.
+This by extension means that we face statistical power restrictions on the person level and have this decided to only present this analysis based on a combined data set of all three studies.
+
+We thus run a linear regression model where average outgroup attitudes are predicted by the number of interactions and the average interaction quality ratings of all participants across the three studies.
+We do so while controlling for the possible effects of study-specific differences.
+To include the study-membership as a control variable, we use the student sample (Study 2) as the reference group because it is both the largest and the most homogeneous study.
+Looking at the overall model, we find that the model predicts a statistically significant amount of variance in average outgroup attitudes (`r lmAllFstatLatex`).
+Looking at the individual effects, we find that only the number of outgroup interactions is associated with average outgroup attitudes (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "SumContactNL_c", ci = TRUE)`).
+Neither the average interaction quality perceptions nor an interaction of amount and quality of contact are meaningful or significant predictors of average outgroup attitudes (both \textit{b} <0.22 and \textit{p} > .201).
+In short, participants who on average had more positive interactions were not statistically more likely to show higher average outgroup attitudes.
+This result is surprising because it contradicts the tenet of the intergroup contact hypothesis that intergroup contact depends on positive contact.
+Additionally, the aggregated results contradict the results of our own multi-level regressions, where we have shown that the positive effect of individual outgroup interactions dependent on interaction quality perceptions.
+
+\subsection{Contact key need content}
+topic model
+
 ```{r intergroupGeneralTblLong, include=FALSE}

### 2022-10-22 Methods-and-Results.tex
forest and overall ols added

@@
 positive outgroup attitudes.
+
+\section{Embeddedness and Stability across Studies}
+
+\begin{center}
+    \noindent\rule{8cm}{0.4pt}\\
+    \hl{\textit{New Section:}}\\
+    \vspace{-0.25cm}
+    \noindent\rule{8cm}{0.4pt}
+\end{center}
+
+Introduction sentence
+
+\hl{maybe move this first paragraph to the end?}
+\subsection{Stability}
+
+We begin by assessing the stability of our main analyses across the
+three studies. To do so, we plot the effect sizes of each parameter of
+interest in a forest plot. Forest plots are a popular form of evidence
+synthesis and are commonly found within meta-analytic efforts. By
+plotting a standardized effect size and confidence interval of key
+parameters for each study, forest plots offer a visual method of
+identifying broader patterns across studies. This affords users a chance
+to spot stable as well as unreliable effects more easily. While not the
+focus of our efforts here, forest plots are commonly accompanied with a
+meta-analytic effect size that summarizes the effect size across
+studies.
+
+We assess forest plots of the basic contact hypothesis test (Figure
+\ref{fig:ContactHypothesis}), the core need fulfillment proposal (Figure
+\ref{fig:AllportNeedFulfillment}), as well as the robustness analyses
+(Figure \ref{fig:Robustness}). For the basic contact hypothesis test we
+see that outgroup contact has a strong and consistent effect on outgroup
+attitudes while interactions with non-outgroup members consistently have
+no meaningful effect on outgroup attitudes. While this would be expected
+from the general intergroup contact literature, this is not a trivial
+finding. We are among the first to assess the contact hypothesis using
+real-life data from intensive longitudinal data and these close to event
+assessments are comparable but not equivalent to the assessments found
+in cross-sectional data (also see below). When looking at Figure
+\ref{fig:AllportNeedFulfillment}, we see that the fulfillment of core
+needs during intergroup contacts is consistently a meaningful predictor
+of outgroup attitudes and interaction quality perceptions (see Figure
+\ref{fig:AllportNeedFulfillment} A and B). We also see that the effect
+of core need fulfillment on outgroup attitudes is strongly reduced when
+modeled together with interaction quality perceptions, supporting our
+assertion that interaction quality offers a psychological mechanism for
+the direct effect. Additionally, the core need fulfillment is also
+consistently outgroup contact specific (Figure \ref{fig:Robustness} A)
+and remains a meaningful predictor of outgroup attitudes even when
+controlling for traditional psychological need fulfillments (Figure
+\ref{fig:Robustness} B).
+
+\subsection{General contact hypothesis}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# Join aggregated data}
+\NormalTok{avS1 }\OtherTok{\textless{}{-}}\NormalTok{ dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerAvFreQual }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{select}\NormalTok{(}
+    \SpecialCharTok{{-}}\NormalTok{ExternalReference}
+\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate}\NormalTok{(}
+    \AttributeTok{PID =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(.)),}
+    \AttributeTok{study =} \StringTok{"S1"}
+\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{select}\NormalTok{(PID, }\FunctionTok{everything}\NormalTok{())}
+\NormalTok{avS2 }\OtherTok{\textless{}{-}}\NormalTok{ dtStudentSupp}\SpecialCharTok{$}\NormalTok{studentContactFreq }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate}\NormalTok{(}
+    \AttributeTok{study =} \StringTok{"S2"}
+\NormalTok{  )}
+\NormalTok{avS3 }\OtherTok{\textless{}{-}}\NormalTok{ dtMedicalSupp}\SpecialCharTok{$}\NormalTok{medicalContactFreq }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate}\NormalTok{(}
+    \AttributeTok{study =} \StringTok{"S3"}
+\NormalTok{  )}
+
+\NormalTok{avAll }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(avS1, avS2, avS3) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate}\NormalTok{(}
+    \AttributeTok{ID =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(.)),}
+    \AttributeTok{studyNum1 =} \FunctionTok{ifelse}\NormalTok{(study }\SpecialCharTok{==} \StringTok{"S1"}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{),}
+    \AttributeTok{studyNum3 =} \FunctionTok{ifelse}\NormalTok{(study }\SpecialCharTok{==} \StringTok{"S3"}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{)}
+\NormalTok{  )}
+\NormalTok{avAll}\SpecialCharTok{$}\NormalTok{study2 }\OtherTok{\textless{}{-}} \FunctionTok{relevel}\NormalTok{(}\FunctionTok{as.factor}\NormalTok{(avAll}\SpecialCharTok{$}\NormalTok{study),}\StringTok{"S2"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{lmAllAttFreqQualX }\OtherTok{\textless{}{-}}
+  \FunctionTok{lm}\NormalTok{(}
+\NormalTok{    AvAttitude }\SpecialCharTok{\textasciitilde{}}\NormalTok{ SumContactNL\_c }\SpecialCharTok{*}\NormalTok{ AvQuality\_c }\SpecialCharTok{+}\NormalTok{ SumContactNL\_c }\SpecialCharTok{*}\NormalTok{ study2 }\SpecialCharTok{+}\NormalTok{ AvQuality\_c }\SpecialCharTok{*}\NormalTok{ study2,}
+    \AttributeTok{data =}\NormalTok{ avAll}
+\NormalTok{  )}
+
+\FunctionTok{summ}\NormalTok{(}
+\NormalTok{  lmAllAttFreqQualX,}
+  \AttributeTok{confint =} \ConstantTok{TRUE}\NormalTok{,}
+  \AttributeTok{digits =} \DecValTok{3}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{table}[!h]
+\centering
+\begin{tabular}{lr}
+\toprule
+\cellcolor{gray!6}{Observations} & \cellcolor{gray!6}{205 (2 missing obs. deleted)}\\
+Dependent variable & AvAttitude\\
+\cellcolor{gray!6}{Type} & \cellcolor{gray!6}{OLS linear regression}\\
+\bottomrule
+\end{tabular}
+\end{table} \begin{table}[!h]
+\centering
+\begin{tabular}{lr}
+\toprule
+\cellcolor{gray!6}{F(9,195)} & \cellcolor{gray!6}{2.643}\\
+R² & 0.109\\
+\cellcolor{gray!6}{Adj. R²} & \cellcolor{gray!6}{0.068}\\
+\bottomrule
+\end{tabular}
+\end{table} \begin{table}[!h]
+\centering
+\begin{threeparttable}
+\begin{tabular}{lrrrrr}
+\toprule
+  & Est. & 2.5\% & 97.5\% & t val. & p\\
+\midrule
+\cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{67.297} & \cellcolor{gray!6}{64.274} & \cellcolor{gray!6}{70.319} & \cellcolor{gray!6}{43.908} & \cellcolor{gray!6}{0.000}\\
+SumContactNL\_c & 0.736 & 0.328 & 1.144 & 3.558 & 0.000\\
+\cellcolor{gray!6}{AvQuality\_c} & \cellcolor{gray!6}{0.222} & \cellcolor{gray!6}{-0.119} & \cellcolor{gray!6}{0.563} & \cellcolor{gray!6}{1.283} & \cellcolor{gray!6}{0.201}\\
+study2S1 & 3.062 & -4.600 & 10.724 & 0.788 & 0.432\\
+\cellcolor{gray!6}{study2S3} & \cellcolor{gray!6}{-2.510} & \cellcolor{gray!6}{-7.348} & \cellcolor{gray!6}{2.328} & \cellcolor{gray!6}{-1.023} & \cellcolor{gray!6}{0.307}\\
+\addlinespace
+SumContactNL\_c:AvQuality\_c & 0.002 & -0.020 & 0.024 & 0.198 & 0.843\\
+\cellcolor{gray!6}{SumContactNL\_c:study2S1} & \cellcolor{gray!6}{-0.684} & \cellcolor{gray!6}{-1.441} & \cellcolor{gray!6}{0.073} & \cellcolor{gray!6}{-1.782} & \cellcolor{gray!6}{0.076}\\
+SumContactNL\_c:study2S3 & -0.595 & -1.076 & -0.113 & -2.437 & 0.016\\
+\cellcolor{gray!6}{AvQuality\_c:study2S1} & \cellcolor{gray!6}{0.518} & \cellcolor{gray!6}{-0.313} & \cellcolor{gray!6}{1.349} & \cellcolor{gray!6}{1.229} & \cellcolor{gray!6}{0.220}\\
+AvQuality\_c:study2S3 & 0.133 & -0.367 & 0.634 & 0.526 & 0.600\\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\item Standard errors: OLS
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# prepare F stat for manuscript}
+\NormalTok{fit }\OtherTok{\textless{}{-}} \FunctionTok{summary}\NormalTok{(lmAllAttFreqQualX)}
+\NormalTok{lmAllFstatLatex }\OtherTok{\textless{}{-}} \FunctionTok{paste}\NormalTok{(}
+  \StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textit\{F\}("}\NormalTok{,}
+\NormalTok{  fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"numdf"}\NormalTok{],}
+  \StringTok{", "}\NormalTok{,}
+\NormalTok{  fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"dendf"}\NormalTok{],}
+  \StringTok{") = "}\NormalTok{,}
+  \FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"value"}\NormalTok{], }\DecValTok{2}\NormalTok{), }\AttributeTok{nsmall =} \DecValTok{2}\NormalTok{),}
+  \StringTok{", }\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textit\{p\} = "}\NormalTok{,}
+  \FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(}
+    \FunctionTok{pf}\NormalTok{(}
+\NormalTok{      fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"value"}\NormalTok{],}
+\NormalTok{      fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"numdf"}\NormalTok{],}
+\NormalTok{      fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"dendf"}\NormalTok{],}
+      \AttributeTok{lower.tail =} \ConstantTok{FALSE}
+\NormalTok{    ),}
+    \DecValTok{3}
+\NormalTok{  ), }\AttributeTok{nsmall =} \DecValTok{3}\NormalTok{),}
+  \StringTok{", }\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textit\{R}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textsuperscript\{2\}\} = "}\NormalTok{,}
+  \FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(fit}\SpecialCharTok{$}\NormalTok{r.squared, }\DecValTok{2}\NormalTok{), }\AttributeTok{nsmall =} \DecValTok{2}\NormalTok{),}
+  \AttributeTok{sep =} \StringTok{""}
+\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+During the main analyses, we have thus far shown that participants held
+more positive outgroup attitudes following intergroup contacts and that
+a perceived interaction quality was associated with more positive
+outgroup attitudes following an intergroup contact. We have, however,
+not brought the two elements of the contact hypothesis together in a
+single analysis. This is mainly due to the difficulty that interaction
+quality ratings are only possible when participants had an interaction
+--- which means that the two factors cannot be assessed in a multilevel
+analysis that models individual measurement occasions. This has not been
+an issue in the past literature because experimental and cross-sectional
+data collections have only considered cases in which intergroup contacts
+were present. Outside of the lab, the most common method has been to ask
+participants to recall how many interactions they had over the past
+month, how positive these interactions were, and how positive they feel
+towards the outgroup in general. The effects of intergroup contacts,
+interaction quality, and outgroup attitudes are thus aggregated by the
+participant in a cognitive recall aggregation. Intensive longitudinal
+data also allows for aggregation of all three variables, with the
+differences that the measurements are aggregated from individual reports
+that are close to the actual experience. However, this aggregation
+process summarizes the dense multitude of measurement occasions as
+single summary statistics per participants. This by extension means that
+we face statistical power restrictions on the person level and have this
+decided to only present this analysis based on a combined data set of
+all three studies.
+
+We thus run a linear regression model where average outgroup attitudes
+are predicted by the number of interactions and the average interaction
+quality ratings of all participants across the three studies. We do so
+while controlling for the possible effects of study-specific
+differences. To include the study-membership as a control variable, we
+use the student sample (Study 2) as the reference group because it is
+both the largest and the most homogeneous study. Looking at the overall
+model, we find that the model predicts a statistically significant
+amount of variance in average outgroup attitudes (\textit{F}(9, 195) =
+2.64, \textit{p} = 0.007, \textit{R\textsuperscript{2}} = 0.11). Looking
+at the individual effects, we find that only the number of outgroup
+interactions is associated with average outgroup attitudes (\textit{b} =
+0.74, \textit{t}(195) = 3.56, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.33, 1.14{]}). Neither the average interaction
+quality perceptions nor an interaction of amount and quality of contact
+are meaningful or significant predictors of average outgroup attitudes
+(both \textit{b} \textless0.22 and \textit{p} \textgreater{} .201). In
+short, participants who on average had more positive interactions were
+not statistically more likely to show higher average outgroup attitudes.
+This result is surprising because it contradicts the tenet of the
+intergroup contact hypothesis that intergroup contact depends on
+positive contact. Additionally, the aggregated results contradict the
+results of our own multi-level regressions, where we have shown that the
+positive effect of individual outgroup interactions dependent on
+interaction quality perceptions.
+
+\subsection{Contact key need content}
+
+topic model

### 2022-10-22 scripts/functions/MlCorMat.R

@@ -317,6 +317,39 @@ MlCoeffHtml <- function(lmeMdl = NULL, lmerCI = NULL, varName = NULL) {
   }
 }
 
+LmCoeffLatex <- function(lmMdl = NULL, varName = NULL, ci = TRUE) {
+  # lmMdl <- lmAllAttFreqQualX
+  # varName <- "SumContactNL_c"
+  
+  lmCI <-  confint(lmMdl)
+  lmEta <- effectsize::eta_squared(lmMdl)
+  
+  b <- coef(summary(lmMdl))[varName,"Estimate"] %>% round(2) %>% format(nsmall=2)
+  df <- lmMdl$df.residual %>% as.numeric
+  t <- coef(summary(lmMdl))[varName,"t value"] %>% round(2) %>% format(nsmall=2)
+  p <- ifelse(coef(summary(lmMdl))[varName,"Pr(>|t|)"]<.001, "< .001", paste0("= ", coef(summary(lmMdl))[varName,"Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)))
+  etaSqP <- lmEta$Eta2_partial[lmEta$Parameter == varName]
+  
+  if (ci == TRUE) {
+    CIlwr <- lmCI[varName, "2.5 %"] %>% round(2) %>% format(nsmall=2)
+    CIupr <- lmCI[varName, "97.5 %"] %>% round(2) %>% format(nsmall=2)
+    
+    paste0(
+      "\\textit{b} = ", b, 
+      ", \\textit{t}(", format(df, big.mark=","), ") = ", t,
+      ", \\textit{p} ", p,
+      ", \\textit{95\\%CI}[", CIlwr, ", ", CIupr, "]"
+    )
+  } else {
+    paste0(
+      "\\textit{b} = ", b, 
+      ", \\textit{t}(", format(df, big.mark=","), ") = ", t,
+      ", \\textit{p} ", p
+    )
+  }
+}
+
+
 linesep<-function(x,y=character()){
   if(!length(x))
     return(y)

### 2022-10-22 Methods-and-Results.Rmd
code hide fix

@@
 \subsection{General contact hypothesis}
-```{r join data sets for analysis}
+
+```{r join data sets for analysis, include=FALSE}
 # Join aggregated data
@@
 ```
-```{r OLS regression across the three studies}
+```{r OLS regression across the three studies, include=FALSE}
 lmAllAttFreqQualX <-

### 2022-10-22 Methods-and-Results.tex
code hide fix

@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Join aggregated data}
-\NormalTok{avS1 }\OtherTok{\textless{}{-}}\NormalTok{ dtWorkerSupp}\SpecialCharTok{$}\NormalTok{workerAvFreQual }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{select}\NormalTok{(}
-    \SpecialCharTok{{-}}\NormalTok{ExternalReference}
-\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{mutate}\NormalTok{(}
-    \AttributeTok{PID =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(.)),}
-    \AttributeTok{study =} \StringTok{"S1"}
-\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{select}\NormalTok{(PID, }\FunctionTok{everything}\NormalTok{())}
-\NormalTok{avS2 }\OtherTok{\textless{}{-}}\NormalTok{ dtStudentSupp}\SpecialCharTok{$}\NormalTok{studentContactFreq }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{mutate}\NormalTok{(}
-    \AttributeTok{study =} \StringTok{"S2"}
-\NormalTok{  )}
-\NormalTok{avS3 }\OtherTok{\textless{}{-}}\NormalTok{ dtMedicalSupp}\SpecialCharTok{$}\NormalTok{medicalContactFreq }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{mutate}\NormalTok{(}
-    \AttributeTok{study =} \StringTok{"S3"}
-\NormalTok{  )}
-
-\NormalTok{avAll }\OtherTok{\textless{}{-}} \FunctionTok{bind\_rows}\NormalTok{(avS1, avS2, avS3) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{mutate}\NormalTok{(}
-    \AttributeTok{ID =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(.)),}
-    \AttributeTok{studyNum1 =} \FunctionTok{ifelse}\NormalTok{(study }\SpecialCharTok{==} \StringTok{"S1"}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{),}
-    \AttributeTok{studyNum3 =} \FunctionTok{ifelse}\NormalTok{(study }\SpecialCharTok{==} \StringTok{"S3"}\NormalTok{, }\DecValTok{1}\NormalTok{, }\DecValTok{0}\NormalTok{)}
-\NormalTok{  )}
-\NormalTok{avAll}\SpecialCharTok{$}\NormalTok{study2 }\OtherTok{\textless{}{-}} \FunctionTok{relevel}\NormalTok{(}\FunctionTok{as.factor}\NormalTok{(avAll}\SpecialCharTok{$}\NormalTok{study),}\StringTok{"S2"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{lmAllAttFreqQualX }\OtherTok{\textless{}{-}}
-  \FunctionTok{lm}\NormalTok{(}
-\NormalTok{    AvAttitude }\SpecialCharTok{\textasciitilde{}}\NormalTok{ SumContactNL\_c }\SpecialCharTok{*}\NormalTok{ AvQuality\_c }\SpecialCharTok{+}\NormalTok{ SumContactNL\_c }\SpecialCharTok{*}\NormalTok{ study2 }\SpecialCharTok{+}\NormalTok{ AvQuality\_c }\SpecialCharTok{*}\NormalTok{ study2,}
-    \AttributeTok{data =}\NormalTok{ avAll}
-\NormalTok{  )}
-
-\FunctionTok{summ}\NormalTok{(}
-\NormalTok{  lmAllAttFreqQualX,}
-  \AttributeTok{confint =} \ConstantTok{TRUE}\NormalTok{,}
-  \AttributeTok{digits =} \DecValTok{3}
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{table}[!h]
-\centering
-\begin{tabular}{lr}
-\toprule
-\cellcolor{gray!6}{Observations} & \cellcolor{gray!6}{205 (2 missing obs. deleted)}\\
-Dependent variable & AvAttitude\\
-\cellcolor{gray!6}{Type} & \cellcolor{gray!6}{OLS linear regression}\\
-\bottomrule
-\end{tabular}
-\end{table} \begin{table}[!h]
-\centering
-\begin{tabular}{lr}
-\toprule
-\cellcolor{gray!6}{F(9,195)} & \cellcolor{gray!6}{2.643}\\
-R² & 0.109\\
-\cellcolor{gray!6}{Adj. R²} & \cellcolor{gray!6}{0.068}\\
-\bottomrule
-\end{tabular}
-\end{table} \begin{table}[!h]
-\centering
-\begin{threeparttable}
-\begin{tabular}{lrrrrr}
-\toprule
-  & Est. & 2.5\% & 97.5\% & t val. & p\\
-\midrule
-\cellcolor{gray!6}{(Intercept)} & \cellcolor{gray!6}{67.297} & \cellcolor{gray!6}{64.274} & \cellcolor{gray!6}{70.319} & \cellcolor{gray!6}{43.908} & \cellcolor{gray!6}{0.000}\\
-SumContactNL\_c & 0.736 & 0.328 & 1.144 & 3.558 & 0.000\\
-\cellcolor{gray!6}{AvQuality\_c} & \cellcolor{gray!6}{0.222} & \cellcolor{gray!6}{-0.119} & \cellcolor{gray!6}{0.563} & \cellcolor{gray!6}{1.283} & \cellcolor{gray!6}{0.201}\\
-study2S1 & 3.062 & -4.600 & 10.724 & 0.788 & 0.432\\
-\cellcolor{gray!6}{study2S3} & \cellcolor{gray!6}{-2.510} & \cellcolor{gray!6}{-7.348} & \cellcolor{gray!6}{2.328} & \cellcolor{gray!6}{-1.023} & \cellcolor{gray!6}{0.307}\\
-\addlinespace
-SumContactNL\_c:AvQuality\_c & 0.002 & -0.020 & 0.024 & 0.198 & 0.843\\
-\cellcolor{gray!6}{SumContactNL\_c:study2S1} & \cellcolor{gray!6}{-0.684} & \cellcolor{gray!6}{-1.441} & \cellcolor{gray!6}{0.073} & \cellcolor{gray!6}{-1.782} & \cellcolor{gray!6}{0.076}\\
-SumContactNL\_c:study2S3 & -0.595 & -1.076 & -0.113 & -2.437 & 0.016\\
-\cellcolor{gray!6}{AvQuality\_c:study2S1} & \cellcolor{gray!6}{0.518} & \cellcolor{gray!6}{-0.313} & \cellcolor{gray!6}{1.349} & \cellcolor{gray!6}{1.229} & \cellcolor{gray!6}{0.220}\\
-AvQuality\_c:study2S3 & 0.133 & -0.367 & 0.634 & 0.526 & 0.600\\
-\bottomrule
-\end{tabular}
-\begin{tablenotes}
-\item Standard errors: OLS
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# prepare F stat for manuscript}
-\NormalTok{fit }\OtherTok{\textless{}{-}} \FunctionTok{summary}\NormalTok{(lmAllAttFreqQualX)}
-\NormalTok{lmAllFstatLatex }\OtherTok{\textless{}{-}} \FunctionTok{paste}\NormalTok{(}
-  \StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textit\{F\}("}\NormalTok{,}
-\NormalTok{  fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"numdf"}\NormalTok{],}
-  \StringTok{", "}\NormalTok{,}
-\NormalTok{  fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"dendf"}\NormalTok{],}
-  \StringTok{") = "}\NormalTok{,}
-  \FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"value"}\NormalTok{], }\DecValTok{2}\NormalTok{), }\AttributeTok{nsmall =} \DecValTok{2}\NormalTok{),}
-  \StringTok{", }\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textit\{p\} = "}\NormalTok{,}
-  \FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(}
-    \FunctionTok{pf}\NormalTok{(}
-\NormalTok{      fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"value"}\NormalTok{],}
-\NormalTok{      fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"numdf"}\NormalTok{],}
-\NormalTok{      fit}\SpecialCharTok{$}\NormalTok{fstatistic[}\StringTok{"dendf"}\NormalTok{],}
-      \AttributeTok{lower.tail =} \ConstantTok{FALSE}
-\NormalTok{    ),}
-    \DecValTok{3}
-\NormalTok{  ), }\AttributeTok{nsmall =} \DecValTok{3}\NormalTok{),}
-  \StringTok{", }\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textit\{R}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textsuperscript\{2\}\} = "}\NormalTok{,}
-  \FunctionTok{format}\NormalTok{(}\FunctionTok{round}\NormalTok{(fit}\SpecialCharTok{$}\NormalTok{r.squared, }\DecValTok{2}\NormalTok{), }\AttributeTok{nsmall =} \DecValTok{2}\NormalTok{),}
-  \AttributeTok{sep =} \StringTok{""}
-\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
 During the main analyses, we have thus far shown that participants held

### 2022-10-23 Methods-and-Results.Rmd
code hide fix

@@
 \subsection{Contact key need content}
-topic model
+
+Because our participants jointly reported on several thousands of intergroup contacts, it would not be feasible to analyse these qualitative responses in a traditional qualitative content analysis.
+We instead rely on recent machine learning advances within the natural language processing domain.
+For our analysis we use the BERT language model.
+BERT (Bidirectional Encoder Representations from Transformers) was developed by Google in 2018 and today forms a key elements of many natural language processing workflows.
+In its essence, BERT is a framework that allows users to codify every word in relation to every other word within a large set of documents.
+This task is immensely computationally intensive and most users of the framework don't create their own model.
+We use the "all-mpnet-base-v2" language model for our embedding.
+The model is a community-based version of BERT that uses Microsoft's "mpnet-base" model and is fine-tuned with 1 Billion diverse sentence pairs.
+The model was trained with a 768 dimensional dense vector space (a relatively high number) to represent every word.
+As a result, the model is widely considered to be one of the most accurate all-purpose language models within the open-source BERT framework.
+We extracted 47 topics from the 2,983 interaction goal free-text entries --- a relatively large number of topics.
+The higher number of topics allows us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (16.64%).
+A full write up of the topic modeling process is available in Online Supplemental Material C.
+
+In terms of the content of the topics, we find that a number of topics are primarily task-oriented, where participants hope to increase their study, research, presentation, or work performance.
+Opposing the task and work oriented needs, are a wide variety of leisure-related wishes.
+Specifically, relaxation and entertainment wishes were prominent terms across several topics.
+Additionally, a number of clusters is primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself.
+Similarly, socializing and celebrations were also explicit social needs (incl., parties).
+Another set of topics was more practically oriented, when participants sought to share food and cook cook together, or had organizational needs (e.g., housing, cleaning, and living).
+
+A reasonable set of contact goals were specifically migration specific (e.g., wish to learn about culture, politics, and language) or were concerned inquiry and information needs more generally (e.g., seeking answers, banking information).
+A further set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food).
+Similarly, a number of participants had travel related goals in their interactions with the majority group members.
+
+One interesting observation was the importance of contact goals specific to contact through the medical and public health system.
+This goal type was partly specific to our young medical professionals sample (e.g., working with patients, treatment), but also more broadly interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals).
+Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members.
+A final also under-explored topic is that of spiritual, religious, and otherwise transcendental needs (incl.
+meditation, prayer, religious services).
+This seems to offer a deep and fundamental need that is mostly ignored in western secular migrant research.
+
+Thus while, medical and spiritual interaction goals were more unexpected, almost all other extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature.
+Something about need theories/models plus our own review article.
 

### 2022-10-23 Methods-and-Results.tex
code hide fix

@@
 
-topic model
+Because our participants jointly reported on several thousands of
+intergroup contacts, it would not be feasible to analyse these
+qualitative responses in a traditional qualitative content analysis. We
+instead rely on recent machine learning advances within the natural
+language processing domain. For our analysis we use the BERT language
+model. BERT (Bidirectional Encoder Representations from Transformers)
+was developed by Google in 2018 and today forms a key elements of many
+natural language processing workflows. In its essence, BERT is a
+framework that allows users to codify every word in relation to every
+other word within a large set of documents. This task is immensely
+computationally intensive and most users of the framework don't create
+their own model. We use the ``all-mpnet-base-v2'' language model for our
+embedding. The model is a community-based version of BERT that uses
+Microsoft's ``mpnet-base'' model and is fine-tuned with 1 Billion
+diverse sentence pairs. The model was trained with a 768 dimensional
+dense vector space (a relatively high number) to represent every word.
+As a result, the model is widely considered to be one of the most
+accurate all-purpose language models within the open-source BERT
+framework. We extracted 47 topics from the 2,983 interaction goal
+free-text entries --- a relatively large number of topics. The higher
+number of topics allows us to retain more of the smaller topics and
+leaves a relatively low number of 308 free-text entries unclassified
+(16.64\%). A full write up of the topic modeling process is available in
+Online Supplemental Material C.
+
+In terms of the content of the topics, we find that a number of topics
+are primarily task-oriented, where participants hope to increase their
+study, research, presentation, or work performance. Opposing the task
+and work oriented needs, are a wide variety of leisure-related wishes.
+Specifically, relaxation and entertainment wishes were prominent terms
+across several topics. Additionally, a number of clusters is primarily
+relationship-oriented, so that participants sought contact with outgroup
+members for intimate and casual social contact in itself. Similarly,
+socializing and celebrations were also explicit social needs (incl.,
+parties). Another set of topics was more practically oriented, when
+participants sought to share food and cook cook together, or had
+organizational needs (e.g., housing, cleaning, and living).
+
+A reasonable set of contact goals were specifically migration specific
+(e.g., wish to learn about culture, politics, and language) or were
+concerned inquiry and information needs more generally (e.g., seeking
+answers, banking information). A further set of topics was specifically
+geared towards a wish to experience cultural products (e.g., music,
+theater, food). Similarly, a number of participants had travel related
+goals in their interactions with the majority group members.
+
+One interesting observation was the importance of contact goals specific
+to contact through the medical and public health system. This goal type
+was partly specific to our young medical professionals sample (e.g.,
+working with patients, treatment), but also more broadly interactions of
+newcomers with the outgroup majority as patients themselves (e.g.,
+therapeutic goals). Also health, fitness, and personal improvement goals
+(e.g., sports and music) were common goals that participants shared
+during the interactions with the majority group members. A final also
+under-explored topic is that of spiritual, religious, and otherwise
+transcendental needs (incl.~meditation, prayer, religious services).
+This seems to offer a deep and fundamental need that is mostly ignored
+in western secular migrant research.
+
+Thus while, medical and spiritual interaction goals were more
+unexpected, almost all other extracted topics fall into broader or
+narrower need concepts that are commonly discussed within the
+psychological needs literature. Something about need theories/models
+plus our own review article.

### 2022-10-23 manuscript.tex
wording introduction

@@
 \abstract{
+\hl{needs to be adjusted}
 One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations.
@@
 However, when using multilevel models to test the contact hypothesis, we find that individual outgroup interactions and perceived interaction quality have a strong influence on positive outgroup attitudes.
-The fulfillment of psychological needs is a strong predictor of positive attitudes after interactions and these positive effects emerged via perceived interaction quality.
-The situational needs remained the core predictor of outgroup attitudes even after controlling for Allport’s (\citeyear{Allport1954b}) contact conditions or more general fundamental needs.
+The fulfillment of psychological needs is consistently a strong predictor of positive attitudes during intergroup interactions and these positive effects emerged via perceived interaction quality.
+The situational needs remained the core predictor of outgroup attitudes even after controlling for Allport’s (\citeyear{Allport1954b}) contact conditions or more general self-determination needs \citep[][]{Ryan2017}.
 As one of the first studies to test intergroup contact theory using extensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
@@
 Methodologically, this offers testament to the emerging practice of capturing real-life interactions using extensive longitudinal data.
-Theoretically, our results give weight to motivational fulfillment as a flexible and relevant mechanism in understanding positive intergroup contact.
+Theoretically, our results give weight to motivational fulfillment as a flexible and effective mechanism in understanding positive intergroup contact.
 }
@@
 There is now consistent evidence that negative intergroup contacts lead to worse attitudes, prejudice, and reduced future interaction motivation \citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.
-Theoretically, understanding whether an interaction is perceived as positive or negative (i.e., interaction quality) thus sits at the heart of when the intergroup contact hypothesis is successful (e.g., Brown et al.
+Theoretically, understanding interaction quality (i.e., whether an interaction is perceived as positive or negative) thus sits at the heart of understanding when an intergroup contact is successful (e.g., Brown et al.
 \citeyear{Brown2007}, Tropp et al.
@@
 % Proposal Paragraph:
-In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and positive outgroup attitudes.
+In this article, we turn towards the motivational literature and propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and positive outgroup attitudes.
 That is to say, that if a person, for example, seeks to feel accepted by their interaction partner and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
@@
 see,][]{Paolini2021}.
-Among others, researchers have for example explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}.
+Among others, researchers have explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}.
 However, all these advances share the underlying criticism that they are not geared towards understanding when and why an interaction is perceived as positive.}.
@@
 In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., situation core need) and with reference to their own response the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment).
-Such an adaptive approach would allow us to test the fundamental psychological mechanism of whether situational psychological needs indeed predict perceived interaction quality and positive outgroup attitudes.
+Such an adaptive approach would allow us to take this initial step and test whether situational psychological needs indeed generally predict perceived interaction quality and positive outgroup attitudes independent of need content.
 
@@
 However, recent technological developments allow us to easily collect experience sampling data on mobile devices \citep[e.g.,][]{Keil2020} or using web-based applications \citep[e.g.,][]{Arslan2020}.
-At the same time, analytical methods for such more complex data have become more readily available, making the analyses more approachable \citep[see, e.g.,][]{ODonnell2021}.
+At the same time, analytical methods for such more complex data have become more readily available, making the analyses more approachable \citep[e.g., see][]{ODonnell2021}.
 Given these, technological and methodological developments, we were able to collect a large amount of real-life data following the daily intergroup interactions of recent migrants with the majority group members.
@@
     \item Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes across extensive longitudinal data.
+    \item Based on Allport’s optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
     \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
-    \item Based on Allport’s optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
-Based on our proposal, we expect situational need fulfillments to work at least as good as Allport's conditions in predicting outgroup attitudes.
+We also expect situational need fulfillments to work at least as good as Allport's optimal contact conditions in predicting outgroup attitudes.
 \end{enumerate}
@@
 Statistical power is notoriously difficult to estimate for intensive longitudinal- and multilevel models because of the complex covariance structures.
-Yet, while power simulations require researchers to make a lot of assumptions, the now famous meta-analysis of the intergroup contact hypothesis estimates the average effect size of intergroup contact at around: $r$ = .21 \citep[][]{Pettigrew2006}.
+However, while power simulations require researchers to make several key assumptions, a major meta-analysis of the intergroup contact hypothesis estimates the average effect size of intergroup contact to be at around: $r$ = .21 \citep[][]{Pettigrew2006}.
 For such a relatively small effect size, cross-sectional data collections would need to collect 175 to 212 participants (for correlational- and linear regression analyses with .8 power respectively).
@@
 To test this sub-hypothesis, we use a two-level regression analysis of outgroup attitudes, with core need fulfillment as the main predictor variable.
-        \item Core need fulfillment during outgroup interactions should predict higher perceived interaction quality.
+        \item Core need fulfillment during outgroup interactions should also predict higher perceived interaction quality.
 This sub-hypothesis mirrors the one above so that perceived interaction quality is predicted by core need fulfillment in a multi-level regression analysis.
@@
         \item We first assess the stability of our main analyses. We use forest plots (including meta analytical estimates) to visualize the direction and effect sizes of our three studies. 
-        \item We then combine the data from the three studies to test the basic tenants of intergroup contact hypothesis more broadly using intensive longitudinal real-life data.
-As we have mentioned above assessing the effects of intergroup contacts and perceived interaction quality jointly is difficult within a multi-level regression because quality perceptions are only available when participants had an interaction.
+        \item We then combine the data from the three studies to test the basic tenets of intergroup contact hypothesis more broadly within the intensive longitudinal real-life data.
+As we have mentioned above, assessing the effects of intergroup contacts and perceived interaction quality jointly is difficult within a multi-level regression because quality perceptions are only available when participants had an interaction.
 To circumvent this issue, we use the data from all participants and aggregate the number of interactions participants had, their average interaction quality perceptions, as well as their average outgroup attitudes.
@@
         \item We, finally, use the qualitative data from the participants' self-identified core needs to contextualize our results.
-We leverage machine learning to extract a topic modeling of the free-text entries across the three studies.
+We leverage machine learning to extract a topic model of the free-text entries across the three studies.
 We describe the extracted topics and themes, and compare them to the need contents usually found and measured within the psychological literature.

### 2022-10-23 Methods-and-Results.Rmd
wording and order adjusted

@@
 After giving informed consent, participants started by filling in an online pre-questionnaire assessing demographics and general information about their immigration.
-Over the next thirty days, the participants were then invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_))) %>% as.character`).
+Over the next thirty days, the participants were then invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median survey duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_))) %>% as.character`).
 General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%).}.
@@
 We used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes within the participants (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
+We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
 Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by use centered predictors and reintroducing the means as level two predictors.
@@
 \subsubsection{Procedure} The study procedure mirrored the setup of Study 1 and consisted of pre-, experience sampling-, and post-measurements.
-The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily))) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily)))) %>% as.character`).
+The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median survey duration} = `r seconds_to_period(median(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily))) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily)))) %>% as.character`).
 General compliance was high (`r format(round(sum(studentSampleInfo$dailiesN)/(nrow(studentSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in).
@@
 \subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, experience sampling-, and post-measurement.
-The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median duration} = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).
+The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median survey duration} = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).
 General compliance was high (`r format(round(table(medicalSampleInfo$dailiesN>30)["TRUE"]/nrow(medicalSampleInfo)*100,2), nsmall=2)`\% filled in at least 31 experience sampling surveys or more).
@@
 
-\subsubsection{Allport's Conditions}
+\subsubsection{Core Need}
 
@@
 
-```{r medicalOutModelInterceptAttAllport, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptAllport <-
-  lme(
-    AttitudesDutch ~ AllportsCondition_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptAllport <-
-    lmer(
-      AttitudesDutch ~ AllportsCondition_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlMedicalOut$Att$lmerInterceptAllportCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllport)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeNull, 
-      mdlMedicalOut$Att$lmeInterceptAllport) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptAllport <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllport)
-```
-
-```{r medicalOutModelSlopesAttAllport, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesAllport <-
-  lme(
-    AttitudesDutch ~
-      AllportsCondition_cwc,
-    random = ~ 1 + AllportsCondition_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesAllport <- lmer(
-    AttitudesDutch ~
-      AllportsCondition_cwc +
-      (1 + AllportsCondition_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# all variables standardized within PPT
-summ(
-  mdlMedicalOut$Att$lmerSlopesAllportZ <- lmer(
-    AttitudesDutch_zwc ~
-      AllportsCondition_zwc +
-      (1 + AllportsCondition_zwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# standardized coefficients
-stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesAllport)
-
-# 95%CIs
-mdlMedicalOut$Att$lmerSlopesAllportCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllport)
-
-# Attempts at R^2
-#r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesAllport, bargraph = TRUE)
-mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesAllport)
-performance::r2(mdlMedicalOut$Att$lmerSlopesAllport)
-performance::model_performance(mdlMedicalOut$Att$lmerSlopesAllport)
-performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
-                                 mdlMedicalOut$Att$lmerInterceptAllport, 
-                                 mdlMedicalOut$Att$lmerSlopesAllport)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeNull, 
-      mdlMedicalOut$Att$lmeInterceptAllport, 
-      mdlMedicalOut$Att$lmeSlopesAllport) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesAllport <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesAllport)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesAllport <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesAllport, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesAllport[[1]],
-  mdlMedicalOut$Att$diagSlopesAllport[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesAllport[[3]],
-  mdlMedicalOut$Att$diagSlopesAllport[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesAllport <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllport,
-                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesAllport <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesAllport, 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllport.png",
-  mdlMedicalOut$Att$predPltSlopesAllport,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
 ```{r medicalOutModelMLQltNull, include=FALSE}
@@
 
+```{r medicalOutModelInterceptAttCore, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptCore <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptCore <-
+    lmer(
+      AttitudesDutch ~ KeyNeedFulfillment_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Att$lmerInterceptCoreCI <-
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCore)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull,
+      mdlMedicalOut$Att$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptCore <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCore)
+```
+
+```{r medicalOutModelSlopesAttCore, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesCore <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesCore <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc +
+      (1 + KeyNeedFulfillment_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# all variables standardized within PPT
+summ(
+  mdlMedicalOut$Att$lmerSlopesCoreZ <- lmer(
+    AttitudesDutch_zwc ~
+      KeyNeedFulfillment_zwc +
+      (1 + KeyNeedFulfillment_zwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# standardized coefficients
+stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesCore)
+
+# 95%CIs
+mdlMedicalOut$Att$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCore)
+
+# Attempts at R^2
+r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesCore, bargraph = TRUE)
+mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesCore)
+performance::r2(mdlMedicalOut$Att$lmerSlopesCore)
+performance::model_performance(mdlMedicalOut$Att$lmerSlopesCore)
+performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
+                                 mdlMedicalOut$Att$lmerInterceptCore, 
+                                 mdlMedicalOut$Att$lmerSlopesCore)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull, 
+      mdlMedicalOut$Att$lmeInterceptCore, 
+      mdlMedicalOut$Att$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesCore <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCore)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesCore <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesCore[[1]],
+  mdlMedicalOut$Att$diagSlopesCore[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesCore[[3]],
+  mdlMedicalOut$Att$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesCore <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(complete.cases(KeyNeedFulfillment)) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCore,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment)) %>% 
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesCore <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesCore, 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCore.png",
+  mdlMedicalOut$Att$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+```{r medicalOutModelInterceptQltCore, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Qlt$lmeInterceptCore <-
+  lme(
+    qualityOverall ~ KeyNeedFulfillment_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Qlt$lmerInterceptCore <-
+    lmer(
+      qualityOverall ~ KeyNeedFulfillment_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Qlt$lmerInterceptCoreCI <- 
+  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptCore)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Qlt$lmeNull, 
+      mdlMedicalOut$Qlt$lmeInterceptCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Qlt$varInterceptCore <-
+  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptCore)
+```
+
+```{r medicalOutModelSlopesQltCore, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Qlt$lmeSlopesCore <-
+  lme(
+    qualityOverall ~
+      KeyNeedFulfillment_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Qlt$lmerSlopesCore <-
+    lmer(
+      qualityOverall ~
+        KeyNeedFulfillment_cwc +
+        (1 + KeyNeedFulfillment_cwc | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Qlt$lmerSlopesCoreCI <- 
+  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesCore)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Qlt$lmeNull, 
+      mdlMedicalOut$Qlt$lmeInterceptCore, 
+      mdlMedicalOut$Qlt$lmeSlopesCore) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Qlt$varSlopesCore <- 
+  lme4::VarCorr(mdlMedicalOut$Qlt$lmeSlopesCore)
+
+# Assumption Checks:
+mdlMedicalOut$Qlt$diagSlopesCore <-
+  sjPlot::plot_model(mdlMedicalOut$Qlt$lmerSlopesCore, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Qlt$diagSlopesCore[[1]],
+  mdlMedicalOut$Qlt$diagSlopesCore[[2]]$`PID`,
+  mdlMedicalOut$Qlt$diagSlopesCore[[3]],
+  mdlMedicalOut$Qlt$diagSlopesCore[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Qlt$predSlopesCore <- 
+  dtMedicalSupp$medicalOutWithinBetween %>%
+  filter(complete.cases(KeyNeedFulfillment)) %>% 
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesCore,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment)) %>% 
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Qlt$predPltSlopesCore <-
+    ggplot(data = mdlMedicalOut$Qlt$predSlopesCore %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap(~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesCore.png",
+  mdlMedicalOut$Qlt$predPltSlopesCore,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+
+```
+
+```{r medicalOutModelInterceptAttCoreQlt, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptCoreQlt <-
+  lme(
+    AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptCoreQlt <-
+    lmer(
+      AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerInterceptCoreQltCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCoreQlt)
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull, 
+  mdlMedicalOut$Att$lmeInterceptCoreQlt
+  ) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptCoreQlt <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreQlt)
+```
+
+```{r medicalOutModelSlopesAttCoreQlt, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesCoreQlt <-
+  lme(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + qualityOverall_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesCoreQlt <- lmer(
+    AttitudesDutch ~
+      KeyNeedFulfillment_cwc + qualityOverall_cwc +
+      (1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween,
+    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
+  ),
+  confint = TRUE,
+  digits = 3
+)
+
+mdlMedicalOut$Att$lmerSlopesCoreQltCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreQlt)
+
+# Compare new model to previous step
+anova(
+  mdlMedicalOut$Att$lmeNull,
+  mdlMedicalOut$Att$lmeInterceptCoreQlt,
+  mdlMedicalOut$Att$lmeSlopesCoreQlt
+) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Medical: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesCoreQlt <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreQlt)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesCoreQlt <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreQlt, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[1]],
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[3]],
+  mdlMedicalOut$Att$diagSlopesCoreQlt[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesCoreQlt <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreQlt,
+                           dtMedicalSupp$medicalOutWithinBetween %>% 
+                             filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
+                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesCoreQlt <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreQlt.png",
+  mdlMedicalOut$Att$predPltSlopesCoreQlt,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
+Similarly to the previous studies, we again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+We find that the fulfillment of the core need during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
+Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
+These results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and this effect partially emerged via its effect on perceived interaction quality.
+
+<!-- \faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?  -->
+
+\subsubsection{Allport's Conditions}
+
+```{r medicalOutModelInterceptAttAllport, include=FALSE}
+# Create and save Model
+mdlMedicalOut$Att$lmeInterceptAllport <-
+  lme(
+    AttitudesDutch ~ AllportsCondition_cwc,
+    random = ~ 1 | PID,
+    na.action = na.omit,
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method)
+summ(
+  mdlMedicalOut$Att$lmerInterceptAllport <-
+    lmer(
+      AttitudesDutch ~ AllportsCondition_cwc + (1 | PID),
+      data = dtMedicalSupp$medicalOutWithinBetween
+    ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+mdlMedicalOut$Att$lmerInterceptAllportCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllport)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull, 
+      mdlMedicalOut$Att$lmeInterceptAllport) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varInterceptAllport <-
+  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllport)
+```
+
+```{r medicalOutModelSlopesAttAllport, include=FALSE}
+# Create and save Model (optimizer needed to reach convergence)
+mdlMedicalOut$Att$lmeSlopesAllport <-
+  lme(
+    AttitudesDutch ~
+      AllportsCondition_cwc,
+    random = ~ 1 + AllportsCondition_cwc | PID,
+    na.action = na.omit,
+    control = lmeControl(opt = "optim"),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  )
+
+# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
+summ(
+  mdlMedicalOut$Att$lmerSlopesAllport <- lmer(
+    AttitudesDutch ~
+      AllportsCondition_cwc +
+      (1 + AllportsCondition_cwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# all variables standardized within PPT
+summ(
+  mdlMedicalOut$Att$lmerSlopesAllportZ <- lmer(
+    AttitudesDutch_zwc ~
+      AllportsCondition_zwc +
+      (1 + AllportsCondition_zwc | PID),
+    data = dtMedicalSupp$medicalOutWithinBetween
+  ),
+  confint = TRUE,
+  digits = 3,
+  center = FALSE
+)
+
+# standardized coefficients
+stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesAllport)
+
+# 95%CIs
+mdlMedicalOut$Att$lmerSlopesAllportCI <- 
+  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllport)
+
+# Attempts at R^2
+#r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesAllport, bargraph = TRUE)
+mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesAllport)
+performance::r2(mdlMedicalOut$Att$lmerSlopesAllport)
+performance::model_performance(mdlMedicalOut$Att$lmerSlopesAllport)
+performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
+                                 mdlMedicalOut$Att$lmerInterceptAllport, 
+                                 mdlMedicalOut$Att$lmerSlopesAllport)
+
+# Compare new model to previous step
+anova(mdlMedicalOut$Att$lmeNull, 
+      mdlMedicalOut$Att$lmeInterceptAllport, 
+      mdlMedicalOut$Att$lmeSlopesAllport) %>%
+  as.data.frame() %>%
+  select(-call) %>%
+  mutate(
+    L.Ratio = round(L.Ratio, 3),
+    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
+  ) %>%
+  replace(is.na(.), "") %>%
+  kbl(
+    .,
+    caption = "Student: Model Comparison",
+    format = "latex",
+    linesep = "",
+    booktabs = T,
+    align = rep("c", ncol(.)),
+    digits = 3
+  ) %>%
+  kable_styling(position = "left")
+
+# Save variances
+mdlMedicalOut$Att$varSlopesAllport <- 
+  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesAllport)
+
+# Assumption Checks:
+mdlMedicalOut$Att$diagSlopesAllport <- 
+  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesAllport, type = "diag")
+grid.arrange(
+  mdlMedicalOut$Att$diagSlopesAllport[[1]],
+  mdlMedicalOut$Att$diagSlopesAllport[[2]]$`PID`,
+  mdlMedicalOut$Att$diagSlopesAllport[[3]],
+  mdlMedicalOut$Att$diagSlopesAllport[[4]]
+)
+
+# Plot prediction model
+mdlMedicalOut$Att$predSlopesAllport <- 
+  dtMedicalSupp$medicalOutWithinBetween %>% 
+  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
+  select(AttitudesDutch, TIDnum, PID) %>% 
+  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllport,
+                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
+                           re.form = NA
+                           )
+         )
+
+(
+  mdlMedicalOut$Att$predPltSlopesAllport <-
+    ggplot(data = mdlMedicalOut$Att$predSlopesAllport, 
+           aes(x = TIDnum, y = measure)) +
+    geom_line(alpha = 1, color = "blue") +
+    geom_line(aes(y = AttitudesDutch), alpha = 1) +
+    facet_wrap( ~ PID, ncol = 6) +
+    xlab("Time") +
+    ylab("Outgroup Attitudes") +
+    theme_Publication()
+)
+ggsave(
+  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllport.png",
+  mdlMedicalOut$Att$predPltSlopesAllport,
+  width = 18,
+  height = 12,
+  dpi = 800,
+  units = "cm",
+  device = "png"
+)
+```
+
 ```{r medicalOutModelInterceptQltAllport, include=FALSE}
@@
 
-As we did with core need fulfillment in previous studies, we sequentially tested whether the fulfillment of Allport's contact conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly.
+As we did with core need fulfillment, we sequentially tested whether the fulfillment of Allport's contact conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly.
 In the multilevel models we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
@@
 These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.
-
-<!-- \faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?  -->
-
-\subsubsection{Core Need}
-
-```{r medicalOutModelInterceptAttCore, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptCore <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptCore <-
-    lmer(
-      AttitudesDutch ~ KeyNeedFulfillment_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlMedicalOut$Att$lmerInterceptCoreCI <-
-  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCore)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeNull,
-      mdlMedicalOut$Att$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptCore <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCore)
-```
-
-```{r medicalOutModelSlopesAttCore, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesCore <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesCore <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc +
-      (1 + KeyNeedFulfillment_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# all variables standardized within PPT
-summ(
-  mdlMedicalOut$Att$lmerSlopesCoreZ <- lmer(
-    AttitudesDutch_zwc ~
-      KeyNeedFulfillment_zwc +
-      (1 + KeyNeedFulfillment_zwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# standardized coefficients
-stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesCore)
-
-# 95%CIs
-mdlMedicalOut$Att$lmerSlopesCoreCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCore)
-
-# Attempts at R^2
-r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesCore, bargraph = TRUE)
-mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesCore)
-performance::r2(mdlMedicalOut$Att$lmerSlopesCore)
-performance::model_performance(mdlMedicalOut$Att$lmerSlopesCore)
-performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
-                                 mdlMedicalOut$Att$lmerInterceptCore, 
-                                 mdlMedicalOut$Att$lmerSlopesCore)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeNull, 
-      mdlMedicalOut$Att$lmeInterceptCore, 
-      mdlMedicalOut$Att$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesCore <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCore)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesCore <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCore, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesCore[[1]],
-  mdlMedicalOut$Att$diagSlopesCore[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesCore[[3]],
-  mdlMedicalOut$Att$diagSlopesCore[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesCore <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(complete.cases(KeyNeedFulfillment)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCore,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(KeyNeedFulfillment)) %>% 
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesCore <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesCore, 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCore.png",
-  mdlMedicalOut$Att$predPltSlopesCore,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-```{r medicalOutModelInterceptQltCore, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Qlt$lmeInterceptCore <-
-  lme(
-    qualityOverall ~ KeyNeedFulfillment_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Qlt$lmerInterceptCore <-
-    lmer(
-      qualityOverall ~ KeyNeedFulfillment_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlMedicalOut$Qlt$lmerInterceptCoreCI <- 
-  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptCore)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Qlt$lmeNull, 
-      mdlMedicalOut$Qlt$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Qlt$varInterceptCore <-
-  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptCore)
-```
-
-```{r medicalOutModelSlopesQltCore, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Qlt$lmeSlopesCore <-
-  lme(
-    qualityOverall ~
-      KeyNeedFulfillment_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Qlt$lmerSlopesCore <-
-    lmer(
-      qualityOverall ~
-        KeyNeedFulfillment_cwc +
-        (1 + KeyNeedFulfillment_cwc | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlMedicalOut$Qlt$lmerSlopesCoreCI <- 
-  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesCore)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Qlt$lmeNull, 
-      mdlMedicalOut$Qlt$lmeInterceptCore, 
-      mdlMedicalOut$Qlt$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Qlt$varSlopesCore <- 
-  lme4::VarCorr(mdlMedicalOut$Qlt$lmeSlopesCore)
-
-# Assumption Checks:
-mdlMedicalOut$Qlt$diagSlopesCore <-
-  sjPlot::plot_model(mdlMedicalOut$Qlt$lmerSlopesCore, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Qlt$diagSlopesCore[[1]],
-  mdlMedicalOut$Qlt$diagSlopesCore[[2]]$`PID`,
-  mdlMedicalOut$Qlt$diagSlopesCore[[3]],
-  mdlMedicalOut$Qlt$diagSlopesCore[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Qlt$predSlopesCore <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
-  filter(complete.cases(KeyNeedFulfillment)) %>% 
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesCore,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(KeyNeedFulfillment)) %>% 
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Qlt$predPltSlopesCore <-
-    ggplot(data = mdlMedicalOut$Qlt$predSlopesCore %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesCore.png",
-  mdlMedicalOut$Qlt$predPltSlopesCore,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-```
-
-```{r medicalOutModelInterceptAttCoreQlt, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptCoreQlt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptCoreQlt <-
-    lmer(
-      AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerInterceptCoreQltCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCoreQlt)
-
-# Compare new model to previous step
-anova(
-  mdlMedicalOut$Att$lmeNull, 
-  mdlMedicalOut$Att$lmeInterceptCoreQlt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptCoreQlt <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreQlt)
-```
-
-```{r medicalOutModelSlopesAttCoreQlt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesCoreQlt <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + qualityOverall_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesCoreQlt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + qualityOverall_cwc +
-      (1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerSlopesCoreQltCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreQlt)
-
-# Compare new model to previous step
-anova(
-  mdlMedicalOut$Att$lmeNull,
-  mdlMedicalOut$Att$lmeInterceptCoreQlt,
-  mdlMedicalOut$Att$lmeSlopesCoreQlt
-) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesCoreQlt <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreQlt)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesCoreQlt <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreQlt, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[1]],
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[3]],
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesCoreQlt <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreQlt,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesCoreQlt <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreQlt.png",
-  mdlMedicalOut$Att$predPltSlopesCoreQlt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-Similarly, we again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
-We find that the fulfillment of the core need during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
-Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
-These results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and this effect partially emerged via its effect on perceived interaction quality.
 
@@
 To test wether Allport's conditions or the core need fulfillment are better at predicting outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
-When comparing the model selection indices we find that the fulfillment of the situational core need, indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
+When comparing the model selection indices, we find that the fulfillment of the situational core need indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
 Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
@@
 
-Introduction sentence
-
-\hl{maybe move this first paragraph to the end?}
+Beyond the individual results of three studies, we conducted three additional analyses to test the broader cross-study claims and contextualize our results.
+In particular, we aim to gain a broader picture of the individual results by considering them jointly, and we leverage the data from all participants to test between-participant contact effects and explore the content of the participants' situational contact needs.
+
 \subsection{Stability}
@@
 By plotting a standardized effect size and confidence interval of key parameters for each study, forest plots offer a visual method of identifying broader patterns across studies.
-This affords users a chance to spot stable as well as unreliable effects more easily.
+This affords us a chance to spot stable as well as unreliable effects more easily.
 While not the focus of our efforts here, forest plots are commonly accompanied with a meta-analytic effect size that summarizes the effect size across studies.
@@
 While this would be expected from the general intergroup contact literature, this is not a trivial finding.
-We are among the first to assess the contact hypothesis using real-life data from intensive longitudinal data and these close to event assessments are comparable but not equivalent to the assessments found in cross-sectional data (also see below).
+We are among the first to assess the contact hypothesis using real-life intensive longitudinal data and these close to event assessments are comparable but not equivalent to the assessments found in cross-sectional data (also see below).
 When looking at Figure \ref{fig:AllportNeedFulfillment}, we see that the fulfillment of core needs during intergroup contacts is consistently a meaningful predictor of outgroup attitudes and interaction quality perceptions (see Figure \ref{fig:AllportNeedFulfillment} A and B).
@@
   lm(
-    AvAttitude ~ SumContactNL_c * AvQuality_c + SumContactNL_c * study2 + AvQuality_c * study2,
+    AvAttitude ~ SumContactNL_c * AvQualityOut_c + SumContactNL_c * study2 + AvQualityOut_c * study2,
     data = avAll
@@
 Outside of the lab, the most common method has been to ask participants to recall how many interactions they had over the past month, how positive these interactions were, and how positive they feel towards the outgroup in general.
-The effects of intergroup contacts, interaction quality, and outgroup attitudes are thus aggregated by the participant in a cognitive recall aggregation.
+The effects of intergroup contacts, interaction quality, and outgroup attitudes are thus summarized by the participant in a cognitive recall aggregation.
 Intensive longitudinal data also allows for aggregation of all three variables, with the differences that the measurements are aggregated from individual reports that are close to the actual experience.
 However, this aggregation process summarizes the dense multitude of measurement occasions as single summary statistics per participants.
-This by extension means that we face statistical power restrictions on the person level and have this decided to only present this analysis based on a combined data set of all three studies.
-
-We thus run a linear regression model where average outgroup attitudes are predicted by the number of interactions and the average interaction quality ratings of all participants across the three studies.
+This, by extension, means that we face statistical power restrictions on the person level and have thus decided to only present this analysis based on a combined data set of all three studies.
+
+We run a linear regression model where average outgroup attitudes are predicted by the number of interactions and the average interaction quality ratings of all participants across the three studies.
 We do so while controlling for the possible effects of study-specific differences.
@@
 Looking at the overall model, we find that the model predicts a statistically significant amount of variance in average outgroup attitudes (`r lmAllFstatLatex`).
-Looking at the individual effects, we find that only the number of outgroup interactions is associated with average outgroup attitudes (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "SumContactNL_c", ci = TRUE)`).
-Neither the average interaction quality perceptions nor an interaction of amount and quality of contact are meaningful or significant predictors of average outgroup attitudes (both \textit{b} <0.22 and \textit{p} > .201).
-In short, participants who on average had more positive interactions were not statistically more likely to show higher average outgroup attitudes.
+Looking at the individual effects, we find that only the number of outgroup interactions has a clear association with average outgroup attitudes (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "SumContactNL_c", ci = TRUE)`).
+The average interaction quality perceptions had a much smaller effect (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "AvQualityOut_c", ci = TRUE)`), and we do not find the most important interaction effect at all.
+In short, the effect of outgroup interactions did not depend on the average interaction quality, so that participants who on average had more positive interactions were not statistically more likely to show higher average outgroup attitudes than those with more negative interactions.
 This result is surprising because it contradicts the tenet of the intergroup contact hypothesis that intergroup contact depends on positive contact.
-Additionally, the aggregated results contradict the results of our own multi-level regressions, where we have shown that the positive effect of individual outgroup interactions dependent on interaction quality perceptions.
 
 \subsection{Contact key need content}
-
-Because our participants jointly reported on several thousands of intergroup contacts, it would not be feasible to analyse these qualitative responses in a traditional qualitative content analysis.
+Finally, we use the qualitative data from the participants’ self-identified core needs to contextualize the results of our main analysis.
+However, because our participants jointly reported on thousands of intergroup contacts, it would not be feasible to analyse these qualitative responses in a traditional qualitative content analysis.
 We instead rely on recent machine learning advances within the natural language processing domain.
@@
 We extracted 47 topics from the 2,983 interaction goal free-text entries --- a relatively large number of topics.
-The higher number of topics allows us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (16.64%).
+The higher number of topics allows us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (10.33%).
 A full write up of the topic modeling process is available in Online Supplemental Material C.
@@
 
-A reasonable set of contact goals were specifically migration specific (e.g., wish to learn about culture, politics, and language) or were concerned inquiry and information needs more generally (e.g., seeking answers, banking information).
-A further set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food).
-Similarly, a number of participants had travel related goals in their interactions with the majority group members.
+A reasonable set of contact goals were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned inquiry and information needs more generally (e.g., seeking answers, bureaucratic information).
+A further set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel related goals in their interactions with the majority group members.
 
@@
 Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members.
-A final also under-explored topic is that of spiritual, religious, and otherwise transcendental needs (incl.
+A final topic was that of spiritual, religious, and otherwise transcendental needs (incl.
 meditation, prayer, religious services).
-This seems to offer a deep and fundamental need that is mostly ignored in western secular migrant research.
-
-Thus while, medical and spiritual interaction goals were more unexpected, almost all other extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature.
+
+Thus, almost all other extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature.
 Something about need theories/models plus our own review article.

### 2022-10-23 Methods-and-Results.tex
wording and order adjusted

@@
 fulfillments, and current attitudes towards the Dutch outgroup
-(\textit{median duration} = 2M 22S, \textit{MAD duration} = 1M 19S).
-General compliance was high (85.90\% of all invited surveys were filled
+(\textit{median survey duration} = 2M 22S, \textit{MAD duration} = 1M
+19S). General compliance was high (85.90\% of all invited surveys were
+filled
 in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%).}.
@@
 indeed associated with significantly more positive outgroup attitudes
-within the participants (\textit{b} = 2.48, \textit{t}(1,200) = 4.37,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}1.37, 3.59{]}), even
-after controlling for having an interaction with a non-Dutch (which did
-not relate to outgroup attitudes independently). Additionally, while
-multi-level regressions are generally robust against unequal cell sizes,
-we correct for inequalities by use centered predictors and reintroducing
-the means as level two predictors. Nonetheless, we also offer an
-analysis of the joint data sets in Online Supplemental Material A (for
-full results see Table \ref{tab:intergroupGeneralTblLong}, Figure
+(\textit{b} = 2.48, \textit{t}(1,200) = 4.37, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}1.37, 3.59{]}), even after controlling for
+having an interaction with a non-Dutch (which did not relate to outgroup
+attitudes independently). Additionally, while multi-level regressions
+are generally robust against unequal cell sizes, we correct for
+inequalities by use centered predictors and reintroducing the means as
+level two predictors. Nonetheless, we also offer an analysis of the
+joint data sets in Online Supplemental Material A (for full results see
+Table \ref{tab:intergroupGeneralTblLong}, Figure
 \ref{fig:ContactHypothesis}, and Online Supplementary Material
@@
 invited for experience sampling measurements twice a day (at 12 pm and
-7pm) for 30 days (\textit{median duration} = 3M 46S,
+7pm) for 30 days (\textit{median survey duration} = 3M 46S,
 \textit{MAD duration} = 1M 54S). General compliance was high (70.87\% of
@@
 participants were invited for experience sampling measurements twice a
-day (at 12 pm and 7pm) for 30 days (\textit{median duration} = 4M 13S,
-\textit{MAD duration} = 2M 6S). General compliance was high (85.92\%
-filled in at least 31 experience sampling surveys or more). The response
-rates were approximately equal during mornings (\textit{n} = 2,092) and
-afternoons (\textit{n} = 2,015). All key variables for this study were
-part of the short experience sampling surveys.
+day (at 12 pm and 7pm) for 30 days (\textit{median survey duration} = 4M
+13S, \textit{MAD duration} = 2M 6S). General compliance was high
+(85.92\% filled in at least 31 experience sampling surveys or more). The
+response rates were approximately equal during mornings (\textit{n} =
+2,092) and afternoons (\textit{n} = 2,015). All key variables for this
+study were part of the short experience sampling surveys.
 
@@
 
-\subsubsection{Allport's Conditions}
-
-As we did with core need fulfillment in previous studies, we
-sequentially tested whether the fulfillment of Allport's contact
-conditions was (1) related to more positive outgroup attitudes, (2)
-higher perceived interaction quality, and (3) whether the variance
-explained by Allport's Conditions is assumed by the perceived
-interaction quality if considered jointly. In the multilevel models we
-find that the fulfillment of Allport's Conditions during outgroup
-contacts was associated with more positive outgroup attitudes (random
-slopes model; \textit{b} = 0.22, \textit{t}(1,601) = 5.86, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}0.15, 0.29{]}) and also predicted
-higher perceived interaction quality (random slopes model; \textit{b} =
-0.65, \textit{t}(1,605) = 11.82, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we consider the
-influences of Allport's Conditions and interaction quality on outgroup
-attitudes jointly, we find that perceived interaction quality is a
-substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
-\textit{t}(1,600) = 6.25, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
-Allport's Conditions was less than half of its original effect size
-(\textit{b} = 0.09, \textit{t}(1,600) = 2.89, \textit{p} = 0.004,
-\textit{95\%CI}{[}0.03, 0.15{]}; also see Table
-\ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment}). These results indicate that in this
-data set the fulfillment of Allport's conditions had a significant
-influence on outgroup attitudes and this effect is likely, in parts,
-explained by its effect through perceived interaction quality.
-
 \subsubsection{Core Need}
 
-Similarly, we again sequentially tested whether the fulfillment of the
-core need during an interaction was (1) related to more positive
-outgroup attitudes, (2) higher perceived interaction quality, and (3)
-whether the variance explained by the core need is assumed by the
-perceived interaction quality if considered jointly. We find that the
-fulfillment of the core need during outgroup contacts was associated
-with more positive outgroup attitudes (random slopes model; \textit{b} =
-0.19, \textit{t}(1,601) = 5.29, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.27{]}) and also predicted higher perceived
-interaction quality (random slopes model; \textit{b} = 0.43,
+Similarly to the previous studies, we again sequentially tested whether
+the fulfillment of the core need during an interaction was (1) related
+to more positive outgroup attitudes, (2) higher perceived interaction
+quality, and (3) whether the variance explained by the core need is
+assumed by the perceived interaction quality if considered jointly. We
+find that the fulfillment of the core need during outgroup contacts was
+associated with more positive outgroup attitudes (random slopes model;
+\textit{b} = 0.19, \textit{t}(1,601) = 5.29, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.12, 0.27{]}) and also predicted higher
+perceived interaction quality (random slopes model; \textit{b} = 0.43,
 \textit{t}(1,605) = 8.35, \textit{p} \textless{} .001,
@@
 
+\subsubsection{Allport's Conditions}
+
+As we did with core need fulfillment, we sequentially tested whether the
+fulfillment of Allport's contact conditions was (1) related to more
+positive outgroup attitudes, (2) higher perceived interaction quality,
+and (3) whether the variance explained by Allport's Conditions is
+assumed by the perceived interaction quality if considered jointly. In
+the multilevel models we find that the fulfillment of Allport's
+Conditions during outgroup contacts was associated with more positive
+outgroup attitudes (random slopes model; \textit{b} = 0.22,
+\textit{t}(1,601) = 5.86, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.15, 0.29{]}) and also predicted higher perceived
+interaction quality (random slopes model; \textit{b} = 0.65,
+\textit{t}(1,605) = 11.82, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we consider the
+influences of Allport's Conditions and interaction quality on outgroup
+attitudes jointly, we find that perceived interaction quality is a
+substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
+\textit{t}(1,600) = 6.25, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
+Allport's Conditions was less than half of its original effect size
+(\textit{b} = 0.09, \textit{t}(1,600) = 2.89, \textit{p} = 0.004,
+\textit{95\%CI}{[}0.03, 0.15{]}; also see Table
+\ref{tab:intergroupNeedsTblLong} and Figure
+\ref{fig:AllportNeedFulfillment}). These results indicate that in this
+data set the fulfillment of Allport's conditions had a significant
+influence on outgroup attitudes and this effect is likely, in parts,
+explained by its effect through perceived interaction quality.
+
 \subsubsection{Compare Fulfillment of Core Need and Allport's Conditions}
@@
 model to see whether the two approaches predict the same variance in
-outgroup attitudes. When comparing the model selection indices we find
-that the fulfillment of the situational core need, indeed performs
+outgroup attitudes. When comparing the model selection indices, we find
+that the fulfillment of the situational core need indeed performs
 slightly better than the model using Allport's conditions
@@
 
-Introduction sentence
+Beyond the individual results of three studies, we conducted three
+additional analyses to test the broader cross-study claims and
+contextualize our results. In particular, we aim to gain a broader
+picture of the individual results by considering them jointly, and we
+leverage the data from all participants to test between-participant
+contact effects and explore the content of the participants' situational
+contact needs.
 
-\hl{maybe move this first paragraph to the end?}
 \subsection{Stability}
@@
 parameters for each study, forest plots offer a visual method of
-identifying broader patterns across studies. This affords users a chance
-to spot stable as well as unreliable effects more easily. While not the
+identifying broader patterns across studies. This affords us a chance to
+spot stable as well as unreliable effects more easily. While not the
 focus of our efforts here, forest plots are commonly accompanied with a
@@
 finding. We are among the first to assess the contact hypothesis using
-real-life data from intensive longitudinal data and these close to event
+real-life intensive longitudinal data and these close to event
 assessments are comparable but not equivalent to the assessments found
@@
 towards the outgroup in general. The effects of intergroup contacts,
-interaction quality, and outgroup attitudes are thus aggregated by the
+interaction quality, and outgroup attitudes are thus summarized by the
 participant in a cognitive recall aggregation. Intensive longitudinal
@@
 process summarizes the dense multitude of measurement occasions as
-single summary statistics per participants. This by extension means that
-we face statistical power restrictions on the person level and have this
-decided to only present this analysis based on a combined data set of
-all three studies.
+single summary statistics per participants. This, by extension, means
+that we face statistical power restrictions on the person level and have
+thus decided to only present this analysis based on a combined data set
+of all three studies.
 
-We thus run a linear regression model where average outgroup attitudes
-are predicted by the number of interactions and the average interaction
+We run a linear regression model where average outgroup attitudes are
+predicted by the number of interactions and the average interaction
 quality ratings of all participants across the three studies. We do so
@@
 model, we find that the model predicts a statistically significant
-amount of variance in average outgroup attitudes (\textit{F}(9, 195) =
-2.64, \textit{p} = 0.007, \textit{R\textsuperscript{2}} = 0.11). Looking
+amount of variance in average outgroup attitudes (\textit{F}(9, 189) =
+3.39, \textit{p} = 0.001, \textit{R\textsuperscript{2}} = 0.14). Looking
 at the individual effects, we find that only the number of outgroup
-interactions is associated with average outgroup attitudes (\textit{b} =
-0.74, \textit{t}(195) = 3.56, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.33, 1.14{]}). Neither the average interaction
-quality perceptions nor an interaction of amount and quality of contact
-are meaningful or significant predictors of average outgroup attitudes
-(both \textit{b} \textless0.22 and \textit{p} \textgreater{} .201). In
-short, participants who on average had more positive interactions were
-not statistically more likely to show higher average outgroup attitudes.
-This result is surprising because it contradicts the tenet of the
-intergroup contact hypothesis that intergroup contact depends on
-positive contact. Additionally, the aggregated results contradict the
-results of our own multi-level regressions, where we have shown that the
-positive effect of individual outgroup interactions dependent on
-interaction quality perceptions.
+interactions has a clear association with average outgroup attitudes
+(\textit{b} = 0.55, \textit{t}(189) = 2.82, \textit{p} = 0.005,
+\textit{95\%CI}{[}0.16, 0.93{]}). The average interaction quality
+perceptions had a much smaller effect (\textit{b} = 0.29,
+\textit{t}(189) = 2.09, \textit{p} = 0.038, \textit{95\%CI}{[}0.02,
+0.56{]}), and we do not find the most important interaction effect at
+all. In short, the effect of outgroup interactions did not depend on the
+average interaction quality, so that participants who on average had
+more positive interactions were not statistically more likely to show
+higher average outgroup attitudes than those with more negative
+interactions. This result is surprising because it contradicts the tenet
+of the intergroup contact hypothesis that intergroup contact depends on
+positive contact.
 
@@
 
-Because our participants jointly reported on several thousands of
-intergroup contacts, it would not be feasible to analyse these
-qualitative responses in a traditional qualitative content analysis. We
-instead rely on recent machine learning advances within the natural
-language processing domain. For our analysis we use the BERT language
-model. BERT (Bidirectional Encoder Representations from Transformers)
-was developed by Google in 2018 and today forms a key elements of many
-natural language processing workflows. In its essence, BERT is a
-framework that allows users to codify every word in relation to every
-other word within a large set of documents. This task is immensely
-computationally intensive and most users of the framework don't create
-their own model. We use the ``all-mpnet-base-v2'' language model for our
-embedding. The model is a community-based version of BERT that uses
-Microsoft's ``mpnet-base'' model and is fine-tuned with 1 Billion
-diverse sentence pairs. The model was trained with a 768 dimensional
-dense vector space (a relatively high number) to represent every word.
-As a result, the model is widely considered to be one of the most
-accurate all-purpose language models within the open-source BERT
+Finally, we use the qualitative data from the participants'
+self-identified core needs to contextualize the results of our main
+analysis. However, because our participants jointly reported on
+thousands of intergroup contacts, it would not be feasible to analyse
+these qualitative responses in a traditional qualitative content
+analysis. We instead rely on recent machine learning advances within the
+natural language processing domain. For our analysis we use the BERT
+language model. BERT (Bidirectional Encoder Representations from
+Transformers) was developed by Google in 2018 and today forms a key
+elements of many natural language processing workflows. In its essence,
+BERT is a framework that allows users to codify every word in relation
+to every other word within a large set of documents. This task is
+immensely computationally intensive and most users of the framework
+don't create their own model. We use the ``all-mpnet-base-v2'' language
+model for our embedding. The model is a community-based version of BERT
+that uses Microsoft's ``mpnet-base'' model and is fine-tuned with 1
+Billion diverse sentence pairs. The model was trained with a 768
+dimensional dense vector space (a relatively high number) to represent
+every word. As a result, the model is widely considered to be one of the
+most accurate all-purpose language models within the open-source BERT
 framework. We extracted 47 topics from the 2,983 interaction goal
@@
 leaves a relatively low number of 308 free-text entries unclassified
-(16.64\%). A full write up of the topic modeling process is available in
+(10.33\%). A full write up of the topic modeling process is available in
 Online Supplemental Material C.
@@
 
-A reasonable set of contact goals were specifically migration specific
+A reasonable set of contact goals were specifically migration-specific
 (e.g., wish to learn about culture, politics, and language) or were
 concerned inquiry and information needs more generally (e.g., seeking
-answers, banking information). A further set of topics was specifically
-geared towards a wish to experience cultural products (e.g., music,
-theater, food). Similarly, a number of participants had travel related
-goals in their interactions with the majority group members.
+answers, bureaucratic information). A further set of topics was
+specifically geared towards a wish to experience cultural products
+(e.g., music, theater, food) or had travel related goals in their
+interactions with the majority group members.
 
@@
 (e.g., sports and music) were common goals that participants shared
-during the interactions with the majority group members. A final also
-under-explored topic is that of spiritual, religious, and otherwise
-transcendental needs (incl.~meditation, prayer, religious services).
-This seems to offer a deep and fundamental need that is mostly ignored
-in western secular migrant research.
+during the interactions with the majority group members. A final topic
+was that of spiritual, religious, and otherwise transcendental needs
+(incl.~meditation, prayer, religious services).
 
-Thus while, medical and spiritual interaction goals were more
-unexpected, almost all other extracted topics fall into broader or
-narrower need concepts that are commonly discussed within the
-psychological needs literature. Something about need theories/models
-plus our own review article.
+Thus, almost all other extracted topics fall into broader or narrower
+need concepts that are commonly discussed within the psychological needs
+literature. Something about need theories/models plus our own review
+article.

### 2022-10-23 manuscript.tex
discussion wording adapted

@@
 As a flexible alternative, we (2) proposed that the fulfillment of situational psychological needs meaningfully predicts positive outgroup attitudes.
-Finally, we (3) assessed whether the fulfillment of psychological needs (and Allport's conditions) have their effect (partially) through perceived interaction quality.
+Finally, we (3) assessed whether the fulfillment of psychological needs have their effect (partially) through perceived interaction quality.
 
@@
 More specifically, we observe that separating between-participant and within-participant effects is crucial.
-For between-subjects effects (using aggregated reports), neither the number of interactions, nor the average interaction quality were significant predictors of positive outgroup attitudes across all studies (also see Figure \ref{fig:ContactHypothesis}a).
-These aggregate findings are surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
+For between-subjects effects (using aggregated reports), the positive effect of more outgroup contact did not depend on the average interaction quality.
+These aggregate findings are surprising because most past cross-sectional studies have also considered an aggregate measurement of interaction quality (albeit not one from actual daily reports).
 The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).\footnote{It should be noted that such inconsistencies with past research might in part be a data artefact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
 However, the models we employed should in principle be resistant to such imbalances.} In support of this possibility, once we used multilevel modeling to separate effects into a between-subjects and within-subjects part, we found that when having an interaction with an outgroup member (vs.
-not having an outgroup interaction) is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account; also see Figure \ref{fig:ContactHypothesis}b).
-We thus find that when we aggregate interaction frequencies and interaction quality from our intensive longitudinal data, we find inconsistent results from the past literature, however within participants, intergroup contacts are significantly related with positive outgroup attitudes.
+not having an outgroup interaction) is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account; also see Figure \ref{fig:ContactHypothesis}B).
+We thus find that the main benefits of intergroup contact remain visible across the three studies.
+However, the intensive longitudinal data of natural intergroup contacts also offers a novel opportunity to explore how people recall and cognitively aggregate outgroup interactions.
+Future studies may want to ask participants explicitly to evaluate the number and quality of outgroup interactions following a phase of intensive longitudinal data collection to disentangle the aggregation differences.
 
@@
 In most cases, the core need even took over the variances previously explained by the self-determination theory needs.
-We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
+We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction-specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
 
@@
 And finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
-This comes at the expense of specificity in the situational needs (i.e., we have not explored which exact needs people had during specific interactions).
+This comes at the expense of specificity in the situational needs (i.e., we have not explored whether different types of needs have stronger effects on interaction quality and outgroup attitudes).
 With the adaptive measurement we used such an investigation would be possible (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
@@
 A first implication concerns the feasibility and usefulness of extensive longitudinal data for intergroup contact research and the broader field of social psychology.
-While setting up an extensive longitudinal study is not easy, we believe the efforts to be similar to a sizable cross-sectional data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with over 10,000 data-points).
+While setting up an extensive longitudinal study is not easy, we believe the efforts to be similar to a sizable cross-sectional data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with roughly 3,000 intergroup interactions captured and over 10,000 data points in total).
 Given the comparable effort, this opens up the possibility to explore research questions that focus on real-life phenomena outside the lab or focus on phenomena that depend on changes and influences over time.
-In the context of intergroup contact research, we were among the first to answer calls to test intergroup contact mechanisms using on extended real-life data \citep[e.g.,][]{Pettigrew2011, MacInnis2015}.
-In doing so, we not only collected a sizable amount of real-life data, but our consideration of extensive longitudinal data may present new inconsistencies in how participants perceive and cognitively aggregate their past interactions with other groups — which may suggest large-scale recall-biases or conflations of within and between participant effects in conventional cross-section studies.
+In the context of intergroup contact research, we are among the first to answer calls to test intergroup contact mechanisms using extended real-life data \citep[e.g.,][]{Pettigrew2011, MacInnis2015}.
+In doing so, we not only collected an unprecedented amount of real-life data, but our consideration of extensive longitudinal data may present new inconsistencies in how participants perceive and cognitively aggregate their past interactions with other groups — which may suggest large-scale recall-biases or conflations of within and between participant effects in conventional cross-section studies.
 
 % Motivation and core needs 
-A broader theoretical implication relates to role of situational motivation in intergroup contacts.
+A broader theoretical implication relates to the role of situational motivation in intergroup contacts.
 Our results offer a first promising test of psychological needs in intergroup contact.
@@
 In cases where some or all optimal contact conditions are not possible to be fulfilled, needs offer an even more compelling alternative (e.g., where equal status is contextually not possible or in cases where people help despite a lack of institutional support).
-Additionally, our conceptualization of situational needs might offer an opportunity for practitioners and interventions.
+Additionally, our conceptualization of situational needs offers a clear opportunity for practitioners and interventions.
 Instead of addressing needs as a one-size fits all solution (e.g., simply focusing on competence needs), one may at times ask outgroup interaction partners what they need during an interaction.

### 2022-10-23 Methods-and-Results.Rmd
topic model conclusion added

@@
 
-Beyond the individual results of three studies, we conducted three additional analyses to test the broader cross-study claims and contextualize our results.
+Beyond the individual results of the three studies, we conducted three additional analyses to test the broader cross-study claims and contextualize our results.
 In particular, we aim to gain a broader picture of the individual results by considering them jointly, and we leverage the data from all participants to test between-participant contact effects and explore the content of the participants' situational contact needs.
@@
 
-Thus, almost all other extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature.
-Something about need theories/models plus our own review article.
+Thus, almost all other extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}.
 

### 2022-10-25 Methods-and-Results.Rmd
REML fixed

@@
         "OutgroupInteraction",
-        "NonOutgroupInteraction"
+        "NonOutgroupInteraction", 
+        "OutgroupInteractionM",
+        "NonOutgroupInteractionM"
       )
@@
         "OutgroupInteraction",
-        "NonOutgroupInteraction"
+        "NonOutgroupInteraction",
+        "OutgroupInteractionM",
+        "NonOutgroupInteractionM"
       )
@@
         "OutgroupInteraction",
-        "NonOutgroupInteraction"
-      )
-  )
+        "NonOutgroupInteraction",
+        "OutgroupInteractionM",
+        "NonOutgroupInteractionM"
+      )
+  )
+
 ```
@@
 mdlWorker$lmerInterceptAttTypeTbl <- lmer(
-    AttitudesDutch ~ OutgroupInteraction + NonOutgroupInteraction + (1 | PID),
+    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM + (1 | PID),
     data = dtWorkerSupp$workerWithinBetween
@@
 mdlWorker$lmerInterceptAttTypeTblZ <- lmer(
-    AttitudesDutch_zwc ~ OutgroupInteraction_zwc + NonOutgroupInteraction_zwc + (1 | PID),
+    AttitudesDutch_zwc ~ OutgroupInteraction_zwc + NonOutgroupInteraction_zwc + OutgroupInteractionM_gmz + NonOutgroupInteractionM_gmz + (1 | PID),
     data = dtWorkerSupp$workerWithinBetween
@@
     AttitudesDutch ~
-      OutgroupInteraction + NonOutgroupInteraction +
-      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+      OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM +
+      (1 + OutgroupInteractionC + NonOutgroupInteractionC | PID),
     data = dtStudentSupp$studentWithinBetween
@@
     AttitudesDutch_zwc ~
-      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc +
+      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc + OutgroupInteractionM_gmz + NonOutgroupInteractionM_gmz +
       (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
@@
     AttitudesDutch ~
-      OutgroupInteraction + NonOutgroupInteraction +
-      (1 + OutgroupInteraction + NonOutgroupInteraction | PID),
+      OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM +
+      (1 + OutgroupInteractionC + NonOutgroupInteractionC | PID),
     data = dtMedicalSupp$medicalWithinBetween
@@
 
+lmAllAttFreqQualX2 <-
+  lm(
+    AvAttitude ~ 
+      SumContactNL_c * AvQualityOut_c + 
+      SumContactNL_c * studyNum1 + 
+      SumContactNL_c * studyNum3 + 
+      AvQualityOut_c * studyNum1 + 
+      AvQualityOut_c * studyNum3,
+    data = avAll
+  )
+
+mdlTblGeneralLmAll <- lmTblPrep(lmAllAttFreqQualX2)$mdlTbl %>%
+  rename(., ES = Eta2_partial) %>%
+  replace(is.na(.), "") %>%
+  mutate(
+    B = ifelse(ES != "", paste(B, "; $\\eta_{partial}$ = ", ES, sep = ""), B),
+    ES = ""
+  )
+
+View(mdlTblGeneralLmAll)
+
 mdlTblGeneralLong <- 
-  rbind(mdlTblGeneralLm %>%
-                             filter(
-                               coef %in% c(
-                                 "(Intercept)",
-                                 "SumContactNL",
-                                 "AvQuality",
-                                 "SumContactNL:AvQuality",
-                                 "R2_R2_adjusted"
-                               )
-                             ),
-                           mdlTblGeneralLmer %>%
+  rbind(mdlTblGeneralLmer %>%
                              filter(
@@
                                  "NonOutgroupInteraction",
+                                 "OutgroupInteractionM",
+                                 "NonOutgroupInteractionM",
                                  "R2Marg_R2Cond"
                                )
-                             ))
+                             ),
+        mdlTblGeneralLmAll %>%
+                             filter(
+                               coef %in% c(
+                                 "(Intercept)",
+                                 "AvQualityOut",
+                                 "AvQuality",
+                                 "studyNum1",
+                                 "studyNum3",
+                                 "SumContactNL:AvQualityOut",
+                                 "SumContactNL:studyNum1",
+                                 "SumContactNL:studyNum3", 
+                                 "AvQualityOut:studyNum1",
+                                 "AvQualityOut:studyNum3",
+                                 "R2_R2_adjusted"
+                               )
+                             ) %>%
+          mutate(
+            B.1 = "",
+            ES.1 = "",
+            B.2 = "",
+            ES.2 =  ""
+          )
+                           )
 mdlTblGeneralLong$coef <- mapvalues(
@@
 )
+
+library(huxtable)
+testTbl <- mdlTblGeneralLong %>%
+  replace(is.na(.), "") %>%
+  hux(.) %>%
+  set_contents(1, 1:7, c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2))) %>%
+  insert_row("", "Study 1", "", "Study 2", "", "Study 3", "", after = 0) %>%
+  merge_cells(1, 2:3) %>% 
+  merge_cells(1, 4:5) %>% 
+  merge_cells(1, 6:7) %>% 
+  set_align(1:2, everywhere, "center") %>%
+  set_escape_contents(everywhere, everywhere, FALSE) %>%
+  set_header_rows(1, TRUE) %>%
+  theme_article %>%
+  set_bottom_border(1, 2:3, brdr(0.5, "solid", "black")) %>%
+  set_bottom_border(1, 4:5, brdr(0.5, "solid", "black")) %>%
+  set_bottom_border(1, 6:7, brdr(0.5, "solid", "black")) %>%
+  insert_column(after = 3, fill = "") %>%
+  set_bottom_border(1, 4, 0) %>%
+  insert_column(after = 6, fill = "") %>%
+  set_bottom_border(1, 7, 0) %>%
+  set_col_width(., 7, 0) %>%
+  insert_row(after = 2, "\\textbf{Within Participants [multilevel linear regression]}", fill = "", copy_cell_props = FALSE) %>%
+  merge_cells(3, 1:ncol(.)) %>%
+  insert_row(after = 9, "\\textbf{Between Participant [aggregated linear regression]}", fill = "", copy_cell_props = FALSE) %>%
+  merge_cells(10, 1:ncol(.)) %>%
+  set_left_padding(4:9, 1, 12) %>%
+  set_left_padding(11:nrow(.), 1, 12) %>%
+  set_font_size(9)
+
+for (i in 11:nrow(testTbl)) {
+  testTbl <- testTbl %>%
+    merge_cells(i, 2:ncol(.)) %>%
+    set_align(i, 2:ncol(.), "center")
+}
+testTbl %>% 
+  as_flextable
+
+capture.output(print_latex(testTbl), file = 'TableOnly.tex')
+
+quick_latex(testTbl, file = "Table.tex", open = FALSE)
+
 mdlTblGeneralLong %>%
@@
     booktabs = TRUE,
-    col.names = c("", rep(c("$B$", "Effect Size"), (ncol(.)-1)/2)),
+    col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)),
     align = c("l", rep("c", ncol(.) - 1)),
@@
   ) %>%
-  pack_rows("Between Participant [aggregated linear regression] (Effect Size = $\\eta_{partial}$)", 1, 5, escape = FALSE) %>%
-  pack_rows("Within Participants [multilevel linear regression] (Effect Size = $\\beta$)", 6, 9, escape = FALSE) %>%
-  footnote(
+  pack_rows("Between Participant [aggregated linear regression] (Effect Size = $\\eta_{partial}$)", 1, 6, escape = FALSE) %>%
+  # pack_rows("Within Participants [multilevel linear regression] (Effect Size = $\\beta$)", 6, 9, escape = FALSE) %>%
+  kableExtra::footnote(
+    .,
     general = c("**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"), 
@@
                                        data = md, 
-                                       method = "FE", # "REML", 
+                                       method = "REML", #"FE", 
                                        slab = sample)
@@
                 data = eff, 
-                method = "FE", # "REML", 
+                method = "REML", #"FE", 
                 slab = paste(coef, sample, sep=" - "))
@@
                                               data = md,
-                                              method = "FE",
+                                              method =  "REML", #"FE", 
                                               slab = sample)
@@
                      data = eff.boot, 
-                     method = "FE", 
+                     method = "REML", #"FE", 
                      slab = paste(coef, sample, sep=" - "))
@@
 GeneralLmerMeta <- metaLmerOut(GeneralLmerMetaTbl,
-                               type = "FE",
+                               type = "REML", #"FE", 
                                name = "GeneralLmer",
@@
               title = "Meta Analysis: Forest Plot Contact Hypothesis \n[Parametric]",
-              filename = "GeneralComb_WeirdScale",
+              filename = "GeneralLmer",
+              type = "REML",
               addAbove = 5,
@@
     lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "QualityRaw ~ CoreNeed"),
-    type = "FE",
+    type = "REML", #"FE", 
     name = "TheoryQualityCore",
@@
     lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed"),
-    type = "FE",
+    type = "REML", #"FE", 
     name = "TheoryAttitudeCore",
@@
     lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed + Quality"),
-    type = "FE",
+    type = "REML", #"FE", 
     name = "TheoryAttitudeCoreQuality",
@@
     mutate(analysis = "(A) Quality ~ Core Need",
-           metaId = paste(coef, analysis, sep = ".")),
+           metaId = paste(coef, analysis, sep = ".")) %>%
+    as.data.frame,
   TheoryMetaAttitudeNeed$eff %>%
     mutate(analysis = "(B) Attitude ~ Core Need",
-           metaId = paste(coef, analysis, sep = ".")),
+           metaId = paste(coef, analysis, sep = ".")) %>%
+    as.data.frame,
   TheoryMetaAttitudeNeedQuality$eff %>%
     mutate(analysis = "(C) Attitude ~ Core Need + Quality",
-           metaId = paste(coef, analysis, sep = "."))
+           metaId = paste(coef, analysis, sep = ".")) %>%
+    as.data.frame
 )
@@
               addAbove = 5,
+              type = "REML",
               width = 600,
@@
     lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc * OutgroupInteraction"),
-    type = "FE",
+    type = "REML", #"FE", 
     name = "RobustContact",
@@
     lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc + Competence_cwc + Autonomy_cwc +      Relatedness_cwc"),
-    type = "FE",
+    type = "REML", #"FE", 
     name = "RobustSDT",
@@
     filter(coef != "(Intercept)") %>%
-    mutate(analysis = "(A) Contact and Need Fulfillment",
+    mutate(analysis = "(A) Attitude ~ Contact and Need Fulfillment",
            metaId = paste(coef, analysis, sep = ".")) %>%
@@
   robustMetaSDT$eff %>%
-    mutate(analysis = "(B) Other Needs",
+    mutate(analysis = "(B) Attitude ~ Other Needs",
            metaId = paste(coef, analysis, sep = ".")) %>%

### 2022-10-25 Table.tex
REML fixed

\documentclass{article}
\usepackage{array}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[normalem]{ulem}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{hhline}
\usepackage{calc}
\usepackage{tabularx}
\usepackage{threeparttable}
\usepackage{wrapfig}
\usepackage{adjustbox}
\usepackage{hyperref}
% These are LaTeX packages. You can install them using your LaTex management software,
% or by running `huxtable::install_latex_dependencies()` from within R.
% Other packages may be required if you use non-standard tabulars (e.g. tabulary).
\pagenumbering{gobble}

\begin{document}

```{=latex}

  \providecommand{\huxb}[2]{\arrayrulecolor[RGB]{#1}\global\arrayrulewidth=#2pt}
  \providecommand{\huxvb}[2]{\color[RGB]{#1}\vrule width #2pt}
  \providecommand{\huxtpad}[1]{\rule{0pt}{#1}}
  \providecommand{\huxbpad}[1]{\rule[-#1]{0pt}{#1}}

\begin{table}[ht]
\begin{centerbox}
\begin{threeparttable}
 \label{tab:intergroupGeneralTblLong}
\setlength{\tabcolsep}{0pt}
\begin{tabular}{l l l l l l l l l}

\hhline{>{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}-}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{0pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont }} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{2}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont Study 1}} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont }} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{2}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont Study 2}} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont }} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{2}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont Study 3}} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{>{\huxb{255, 255, 255}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{255, 255, 255}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{255, 255, 255}{0.5}}->{\huxb{0, 0, 0}{0.5}}->{\huxb{0, 0, 0}{0.5}}-}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{0pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont }} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont $B$}} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont $\beta$}} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont }} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont $B$}} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont $\beta$}} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont }} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont $B$}} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} \textbf{{\fontsize{9pt}{10.8pt}\selectfont $\beta$}} \hspace{0pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{>{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}-}
\arrayrulecolor{black}

\multicolumn{9}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont $\backslash$textbf\{Within Participants [multilevel linear regression]\}} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont (Intercept)} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 74.12**** [ 56.74, 91.49]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 67.05**** [ 57.37, 76.73]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 60.36**** [ 46.45, 74.27]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{0pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont OutgroupInteraction} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  2.48**** [  1.37,  3.59]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  1.07 [ 0.59, 1.54]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  2.83*** [  1.28,  4.38]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.11 [ 0.07, 0.16]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  5.57**** [  3.90,  7.23]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.21 [ 0.15, 0.27]} \hspace{0pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont NonOutgroupInteraction} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.44 [ -0.67,  1.55]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.16 [-0.32, 0.63]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.02 [ -0.76,  0.79]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.01 [-0.03, 0.05]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.36 [ -0.48,  1.19]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.02 [-0.02, 0.05]} \hspace{0pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont OutgroupInteractionM} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.99 [-26.61, 28.59]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  1.65 [-4.27, 7.57]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 26.53** [  8.61, 44.46]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.00 [-0.03, 0.03]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 14.14 [ -2.19, 30.48]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.00 [-0.03, 0.03]} \hspace{0pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont NonOutgroupInteractionM} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -4.82 [-30.26, 20.63]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -1.08 [-7.02, 4.86]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -8.32 [-22.98,  6.35]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.00 [-0.03, 0.03]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -2.75 [-20.00, 14.50]} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.00 [-0.03, 0.03]} \hspace{0pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont $R^2_{marginal} / R^2_{conditional}$} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.009 / 0.722} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.050 / 0.818} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.049 / 0.717} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{1}{l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont } \hspace{0pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{9}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont $\backslash$textbf\{Between Participant [aggregated linear regression]\}} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont (Intercept)} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 68.15**** [65.25, 71.06]} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityOut} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.29* [ 0.02,  0.56]; $\eta_{partial}$ = 0.08} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont studyNum1} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  2.23 [-5.03,  9.48]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont studyNum3} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -3.15 [-7.78,  1.48]; $\eta_{partial}$ = 0.01} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:AvQualityOut} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.01 [-0.02,  0.01]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:studyNum1} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.46 [-1.17,  0.24]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:studyNum3} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.46* [-0.92, -0.01]; $\eta_{partial}$ = 0.02} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityOut:studyNum1} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.46 [-0.30,  1.23]; $\eta_{partial}$ = 0.01} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityOut:studyNum3} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.16 [-0.24,  0.56]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont $R^2 / R^2_{adjusted}$} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.139 / 0.098} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{>{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}-}
\arrayrulecolor{black}
\end{tabular}
\end{threeparttable}\par\end{centerbox}

\end{table}

```

\end{document}

### 2022-10-25 Tables/mdlContactGeneral.tex
meta General LM added
theory meta added
REML fixed

--- 2022-01-03 Tables/mdlContactGeneral.tex
@@
 
-\caption{\label{tab:intergroupGeneralTbl}Intergroup General}
+\caption{\label{tab:intergroupGeneralTblWide}Intergroup General}
 \centering
@@
 \midrule
-(Intercept) & 70.50**** [66.06, 74.94] &  & 67.62**** [64.16, 71.08] &  & 64.83**** [61.50, 68.16] &  & 67.44**** [61.71, 73.17] &  & 63.72**** [59.42, 68.01] &  & 56.30**** [51.58, 61.02] & \\
+(Intercept) & 70.50**** [66.06, 74.94] &  & 67.62**** [64.16, 71.08] &  & 64.83**** [61.50, 68.16] &  & 74.12**** [ 56.74, 91.49] &  & 67.05**** [ 57.37, 76.73] &  & 60.36**** [ 46.45, 74.27] & \\
 SumContactNL & 0.27 [-0.15,  0.69] & 0.02 & 0.81** [ 0.32,  1.29] & 0.08 & 0.15 [-0.08,  0.38] & 0.02 &  &  &  &  &  & \\
@@
 SumContactNL:AvQuality & -0.05** [-0.08, -0.01] & 0.34 & 0.02 [-0.03,  0.08] & 0.01 & 0.01 [-0.02,  0.03] & 0.01 &  &  &  &  &  & \\
-OutgroupInteraction &  &  &  &  &  &  & 2.48**** [ 1.36,  3.59] & 1.07 [ 0.59,  1.54] & 2.99*** [ 1.45,  4.54] & 0.11 [ 0.07, 0.16] & 5.63**** [ 3.97,  7.29] & 0.21 [ 0.15, 0.27]\\
-NonOutgroupInteraction &  &  &  &  &  &  & 0.43 [-0.68,  1.54] & 0.16 [-0.32,  0.63] & 0.01 [-0.76,  0.78] & 0.01 [-0.03, 0.05] & 0.34 [-0.49,  1.18] & 0.02 [-0.02, 0.05]\\
+OutgroupInteraction &  &  &  &  &  &  & 2.48**** [  1.37,  3.59] & 1.07 [ 0.59, 1.54] & 2.83*** [  1.28,  4.38] & 0.11 [ 0.07, 0.16] & 5.57**** [  3.90,  7.23] & 0.21 [ 0.15, 0.27]\\
+NonOutgroupInteraction &  &  &  &  &  &  & 0.44 [ -0.67,  1.55] & 0.16 [-0.32, 0.63] & 0.02 [ -0.76,  0.79] & 0.01 [-0.03, 0.05] & 0.36 [ -0.48,  1.19] & 0.02 [-0.02, 0.05]\\
 \addlinespace[0.3em]
 \multicolumn{13}{l}{\textbf{Random}}\\
-\hspace{1em}$\sigma^2$ &  &  &  &  &  &  & 69.92 &  & 77.46 &  & 88.1 & \\
-\hspace{1em}$\tau_{00}$ &  &  &  &  &  &  & 164.13 (PID) &  & 488.38 (PID) &  & 366.51 (PID) & \\
-\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & \makecell[c]{48.94 (PID.OutgroupInteraction)\\ 7.23 (PID.NonOutgroupInteraction)} &  & \makecell[c]{40.53 (PID.OutgroupInteraction)\\ 3.43 (PID.NonOutgroupInteraction)} & \\
-\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & \makecell[c]{-0.72 (PID.OutgroupInteraction)\\ 0.12 (PID.NonOutgroupInteraction)} &  & \makecell[c]{-0.70 (PID.OutgroupInteraction)\\-0.28 (PID.NonOutgroupInteraction)} & \\
-\hspace{1em}$\rho_{00}$ &  &  &  &  &  &  &  &  & 0.00 (PID.OutgroupInteraction-NonOutgroupInteraction) &  & 0.26 (PID.OutgroupInteraction-NonOutgroupInteraction) & \\
+\hspace{1em}OutgroupInteractionM &  &  &  &  &  &  & 0.99 [-26.61, 28.59] & 1.65 [-4.27, 7.57] & 26.53** [  8.61, 44.46] & 0.00 [-0.03, 0.03] & 14.14 [ -2.19, 30.48] & 0.00 [-0.03, 0.03]\\
+\hspace{1em}NonOutgroupInteractionM &  &  &  &  &  &  & -4.82 [-30.26, 20.63] & -1.08 [-7.02, 4.86] & -8.32 [-22.98,  6.35] & 0.00 [-0.03, 0.03] & -2.75 [-20.00, 14.50] & 0.00 [-0.03, 0.03]\\
+\hspace{1em}$\sigma^2$ &  &  &  &  &  &  & 69.91 &  & 77.42 &  & 88.1 & \\
+\hspace{1em}$\tau_{00}$ &  &  &  &  &  &  & 179.20 (PID) &  & 318.62 (PID) &  & 199.47 (PID) & \\
+\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & \makecell[c]{48.96 (PID.OutgroupInteractionC)\\ 7.40 (PID.NonOutgroupInteractionC)} &  & \makecell[c]{40.64 (PID.OutgroupInteractionC)\\ 3.44 (PID.NonOutgroupInteractionC)} & \\
 \addlinespace[0.3em]
 \multicolumn{13}{l}{\textbf{Fit}}\\
+\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & \makecell[c]{-0.39 (PID.OutgroupInteractionC)\\ 0.33 (PID.NonOutgroupInteractionC)} &  & \makecell[c]{-0.26 (PID.OutgroupInteractionC)\\ 0.05 (PID.NonOutgroupInteractionC)} & \\
+\hspace{1em}$\rho_{00}$ &  &  &  &  &  &  &  &  & 0.03 (PID.OutgroupInteractionC-NonOutgroupInteractionC) &  & 0.24 (PID.OutgroupInteractionC-NonOutgroupInteractionC) & \\
 \hspace{1em}Groups &  &  &  &  &  &  & 23 &  & 113 &  & 71 & \\
@@
 \hspace{1em}F Test & F(3, 17) = 6.66, p =  0.004 &  & F(3, 109) = 3.75, p =  0.013 &  & F(3, 67) = 2.15, p =  0.102 &  &  &  &  &  &  & \\
-\hspace{1em}$R^{2 (a)}$ & 0.540 / 0.459 &  & 0.094 / 0.069 &  & 0.088 / 0.047 &  & 0.006 / 0.703 &  & 0.003 / 0.817 &  & 0.026 / 0.708 & \\
-\hspace{1em}AIC &  &  &  &  &  &  & 8788 &  & 36476 &  & 29074 & \\
-\hspace{1em}BIC &  &  &  &  &  &  & 8814 &  & 36542 &  & 29137 & \\
-\hspace{1em}ICC &  &  &  &  &  &  & 0.7013 &  & 0.8167 &  & 0.7007 & \\
+\hspace{1em}$R^{2 (a)}$ & 0.540 / 0.459 &  & 0.094 / 0.069 &  & 0.088 / 0.047 &  & 0.009 / 0.722 &  & 0.050 / 0.818 &  & 0.049 / 0.717 & \\
+\hspace{1em}AIC &  &  &  &  &  &  & 8778 &  & 36461 &  & 29065 & \\
+BIC &  &  &  &  &  &  & 8814 &  & 36539 &  & 29140 & \\
+ICC &  &  &  &  &  &  & 0.7193 &  & 0.8082 &  & 0.703 & \\
 \bottomrule

### 2022-10-25 manuscript.tex
REML fixed

@@
   \label{fig:ContactHypothesis}
-  \centering\includegraphics[width=\textwidth]{Figures/forestParametricGeneralComb.png}
+  \centering\includegraphics[width=\textwidth]{Figures/forestParametricREMLGeneralLmer.png}
   %\begin{subfigure}{\textwidth}
@@
   \caption*{Note: \\
-  (a) summary of regression results from the aggregated contact and interaction quality data.\\
-  (b) summary of mixed models results of the contemporaneous contact effects.\\
-  General: Fixed effects meta analytic results are presented for completeness only.}
+  Summary of mixed models results of the contemporaneous contact effects.\\
+  General: Random effects meta analytic results are presented for completeness.}
 \end{figure}
@@
   (c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.\\
-  General: Fixed effects meta analytic results are presented for completeness only.}
+  General: Random effects meta analytic results are presented for completeness.}
 \end{figure}
@@
   (b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).\\
-  General: Fixed effects meta analytic results are presented for completeness only.}
+  General: Random effects meta analytic results are presented for completeness.}
 \end{figure}

### 2022-10-25 scripts/functions/MlCorMat.R

@@ -213,7 +213,9 @@ MlTraitState <-
       #mutate_if(is.factor, as.numeric) %>% # let's hope this doesn't cause any problems :-D
       mutate_at(selection, as.numeric) %>% # let's hope this works 
       mutate_at(selection, list(gm = ~mean(., na.rm=TRUE))) %>% # grand mean
+      mutate_at(selection, list(gsd = ~sd(., na.rm=TRUE))) %>% # grand sd
       mutate_at(selection, list(gmc = ~.-mean(., na.rm=TRUE))) %>% # grand mean centered
+      mutate_at(selection, list(gmz = ~(.-mean(., na.rm=TRUE))/sd(., na.rm=TRUE))) %>% # grand mean standardized
       group_by_at(vars(matches(id))) %>%
       mutate_at(selection, list(cm = ~mean(., na.rm=TRUE))) %>% # cluster mean
       mutate_at(selection, list(csd = ~sd(., na.rm=TRUE))) %>% # cluster sd

### 2022-10-25 scripts/functions/MlTbl.R

@@ -1,5 +1,5 @@
-#obj <- mdlWorkerLmerSlopesAttCoreInt
-#objz <- mdlWorkerLmerSlopesAttCoreIntZ
+#obj <- mdlWorker$lmerInterceptAttTypeTbl
+#objz <- mdlWorker$lmerInterceptAttTypeTblZ
 
 lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   # Summarize models
@@ -75,10 +75,10 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   coefOut <- 
     join(
       coefOut %>% 
-        mutate(coef = gsub('_cwc', '', coef)), 
+        mutate(coef = gsub('_cwc|C$', '', coef)), 
       coefZOut %>% 
         select(coef, Beta) %>% 
-        mutate(coef = gsub('_zwc|Z$', '', coef)) %>%
+        mutate(coef = gsub('_zwc|_gmz|Z$', '', coef)) %>%
         mutate(Beta = ifelse(coef == "(Intercept)", "", Beta)),
       by = "coef"
     )
@@ -182,7 +182,7 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   out
 }
 
-#obj <- mdlWorker$lmAttFreqQualX
+#obj <- lmAllAttFreqQualX2
 lmTblPrep <- function (obj, alpha = 0.05, ...) {
   # Summarize models
   smry <- summ(obj, confint = TRUE)

### 2022-10-25 scripts/functions/metaLmer.R

@@ -289,7 +289,7 @@ metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
         vi = get(paste(var.boot[i], ".vi", sep =
                          "")),
         data = md,
-        method = "FE",
+        method = type,
         slab = sample
       )
     
@@ -452,12 +452,12 @@ metaLmerOut <- function(lmerDataTbl, type = "FE", name, title, ...) {
 
 
 
-metaSubForest <- function(effects, title = "", addAbove = 0, filename = NULL, width = 600, height = 800,...) {
+metaSubForest <- function(effects, title = "", addAbove = 0, filename = NULL, type = "REML", width = 600, height = 800,...) {
   metaGeneral <- rma(
     yi = yi,
     vi = vi,
     data = effects,
-    method = "FE",
+    method = type,
     slab = paste(analysis, coef, sample, sep = " - ")
   )
   
@@ -501,7 +501,7 @@ metaSubForest <- function(effects, title = "", addAbove = 0, filename = NULL, wi
     subgroupMeta[[i]] <- rma(yi, 
                              vi, 
                              data = effects %>% filter(metaId == unique(effects$metaId)[i]), 
-                             method = "FE",
+                             method = type,
                              slab = paste(analysis, coef, sep = " - "))
   }
   
@@ -565,7 +565,7 @@ metaSubForest <- function(effects, title = "", addAbove = 0, filename = NULL, wi
     addpoly(
       subgroupMeta[[i]], 
       row = rev(unlist(rev(metaIndex)))[[i]],
-      mlab = "► Fixed Effect",
+      mlab = ifelse(type == "REML", "► Random Effect", ifelse(type == "FE", "► Fixed Effect", "► CHECK EFFECT")),
       cex = 0.75
     )
   }

### 2022-10-25 manuscript.tex
Updates from Overleaf

--- 2022-10-23 manuscript.tex
@@
 \abstract{
-\hl{needs to be adjusted}
+\hl{needs to be adjusted}\\
 One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations.

### 2022-10-26 Methods-and-Results.Rmd
path models render init

@@
 
-View(mdlTblGeneralLmAll)
-
 mdlTblGeneralLong <- 
@@
   mdlPrep[[i]] <- lmerTblPrep(mdlTblElements[[i]][[1]], mdlTblElements[[i]][[2]])
+}
+
+shortMdlPath <- list()
+for(i in 1:length(mdlPrep)){
+  study <- gsub("S", "Study", str_extract(mdlPrep[[i]]$fit$data, "S1|S2|S3"))
+  dv <- gsub("Raw", "", sub(" ~.*", "", mdlPrep[[i]]$fit$formula)) 
+  pred <- gsub("\\(Intercept\\)", "", paste(mdlPrep[[i]]$coeficients$coef, collapse = ''))
+
+  name <- paste(study, dv, pred, sep='.')
+  shortMdlPath[[name]] <- mdlPrep[[i]]$coeficients[, c("coef", "est", "Bstar", "B", "estBeta", "BetaStar", "Beta")]
 }
@@
 
+```{r Export Path Models}
+save(shortMdlPath, 
+     file = "data/theoryMdlTabl.RData")
+```
+
 ```{r OsfExport, include=FALSE}

### 2022-10-26 Methods-and-Results.tex
path models render init

@@
 
-Beyond the individual results of three studies, we conducted three
+Beyond the individual results of the three studies, we conducted three
 additional analyses to test the broader cross-study claims and
@@
 need concepts that are commonly discussed within the psychological needs
-literature. Something about need theories/models plus our own review
-article.
+literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core
+aspect of the migration experience that has remained broadly
+under-explored \citep[][]{Kreienkamp2022d}.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{save}\NormalTok{(shortMdlPath, }
+     \AttributeTok{file =} \StringTok{"data/theoryMdlTabl.RData"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}

### 2022-10-26 PathModels.Rmd
path models render init

---
output: latex_fragment
header-includes:
  - \usepackage{tikz}
  - \usepackage{pgfplots}
  - \pgfplotsset{compat=1.17}
  - \tikzset{mynode/.style={draw,text width=1in,align=center} }
  - \usetikzlibrary{positioning}
---

```{r, load_packages, include = FALSE}
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "glue"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)
```

```{r, load_function, include=FALSE}
# \\path (xd.north west) ++(-0.2, 3pt) node[above left]{(A)};
# \\path (xd.north west) ++(-0.4, 16pt) node[draw, above left, shape=circle, very thick, inner sep=2pt] {\\large \\textbf{<<fig_num>>}};
path_tikz_fig <- function(data) {
  glue::glue_data(data, 
"
\\begin{figure}
\\begin{center}
\\begin{tikzpicture}[font=\\sffamily]
    \\node[mynode] (m){<<lab_m>>};
    \\node[mynode,below left=of m](x) {<<lab_x>>};
    \\node[mynode,below right=of m](y) {<<lab_y>>};
    \\node[mynode,above left=of m](xd) {<<lab_x_direct>>};
    \\node[mynode,above right=of m](yd) {<<lab_y_direct>>};
    \\draw[-latex] (xd.east) -- node[above=2mm, align=center] {<<coef_xy_direct>>} (yd.west);
    \\draw[-latex] (x.north) -- node[auto] {<<coef_xm>>} (m.west);
    \\draw[-latex] (m.east) -- node[auto] {<<coef_my>>} (y.north);
    \\draw[-latex] (x.east) -- node[below=2mm, align=center] {<<coef_xy>>} (y.west);
    \\path (xd.north west) ++(-0.2, 6pt) node[above left]{\\textbf{(<<fig_num>>)}};
\\end{tikzpicture}
\\end{center}
\\end{figure}
", 
.open = "<<", .close = ">>"
)
}

path_tikz <- function(data) {
  glue::glue_data(data, 
"
\\begin{tikzpicture}[font=\\sffamily]
    \\node[mynode] (m){<<lab_m>>};
    \\node[mynode,below left=of m](x) {<<lab_x>>};
    \\node[mynode,below right=of m](y) {<<lab_y>>};
    \\node[mynode,above left=of m](xd) {<<lab_x_direct>>};
    \\node[mynode,above right=of m](yd) {<<lab_y_direct>>};
    \\draw[-latex] (xd.east) -- node[above=2mm, align=center] {<<coef_xy_direct>>} (yd.west);
    \\draw[-latex] (x.north) -- node[auto] {<<coef_xm>>} (m.west);
    \\draw[-latex] (m.east) -- node[auto] {<<coef_my>>} (y.north);
    \\draw[-latex] (x.east) -- node[below=2mm, align=center] {<<coef_xy>>} (y.west);
    \\path (xd.north west) ++(-0.2, 6pt) node[above left]{\\textbf{(<<fig_num>>)}};
\\end{tikzpicture}
", 
.open = "<<", .close = ">>"
)
}
```

```{r create_diagram, echo = FALSE, results = 'asis'}

load("data/theoryMdlTabl.RData")

y <- "Attitude"
x <- "CoreNeed"
m <- "Quality"
xm <- "CoreNeedQuality"

studies <- c("Study1", "Study2", "Study3")

pathCoeffs <- list()
for (study in studies) {
  mdlDir <- shortMdlPath[[paste(study, y, x, sep = ".")]]
  mdlM <- shortMdlPath[[paste(study, m, x, sep = ".")]]
  mdlFull <- shortMdlPath[[paste(study, y, xm, sep = ".")]]

  pathCoeffs[[study]] <-
    data.frame(
      xy_direct = paste(format(round(mdlDir$estBeta[mdlDir$coef==x],2), nsmall=2), mdlDir$Bstar[mdlDir$coef==x], sep=""), # c
      xm = paste(format(round(mdlM$estBeta[mdlM$coef==x],2), nsmall=2), mdlM$Bstar[mdlM$coef==x], sep=""), # a
      my = paste(format(round(mdlFull$estBeta[mdlFull$coef==m],2), nsmall=2), mdlFull$Bstar[mdlFull$coef==m], sep=""), # b
      xy = paste(format(round(mdlFull$estBeta[mdlFull$coef==x],2), nsmall=2), mdlFull$Bstar[mdlFull$coef==x], sep="") # c'
    )
}

coreNeedPathS1 <-
  data.frame(
    lab_x_direct = "Core Need\\\\Fulfillment",
    lab_y_direct   = "Outgroup\\\\Attitudes",
    lab_x   = "Core Need\\\\Fulfillment",
    lab_m   = "Interaction\\\\Quality",
    lab_y   = "Outgroup\\\\Attitudes",
    coef_xy_direct = pathCoeffs$Study1$xy_direct,
    coef_xm = pathCoeffs$Study1$xm,
    coef_my = pathCoeffs$Study1$my,
    coef_xy = pathCoeffs$Study1$xy,
    fig_num = "A"
  )
coreNeedPathS2 <-
  data.frame(
    lab_x_direct = "Core Need\\\\Fulfillment",
    lab_y_direct   = "Outgroup\\\\Attitudes",
    lab_x   = "Core Need\\\\Fulfillment",
    lab_m   = "Interaction\\\\Quality",
    lab_y   = "Outgroup\\\\Attitudes",
    coef_xy_direct = pathCoeffs$Study2$xy_direct,
    coef_xm = pathCoeffs$Study2$xm,
    coef_my = pathCoeffs$Study2$my,
    coef_xy = pathCoeffs$Study2$xy,
    fig_num = "B"
  )
coreNeedPathS3 <-
  data.frame(
    lab_x_direct = "Core Need\\\\Fulfillment",
    lab_y_direct   = "Outgroup\\\\Attitudes",
    lab_x   = "Core Need\\\\Fulfillment",
    lab_m   = "Interaction\\\\Quality",
    lab_y   = "Outgroup\\\\Attitudes",
    coef_xy_direct = pathCoeffs$Study3$xy_direct,
    coef_xm = pathCoeffs$Study3$xm,
    coef_my = pathCoeffs$Study3$my,
    coef_xy = pathCoeffs$Study3$xy,
    fig_num = "C"
  )

# requires chunk header to be set to results = 'asis'
# cat("\n", path_tikz(coreNeedPathS1), "\n")
# cat("\n", path_tikz(coreNeedPathS2), "\n")
# cat("\n", path_tikz(coreNeedPathS3), "\n")

```

`r path_tikz(coreNeedPathS1)`

\vspace{12pt}

`r path_tikz(coreNeedPathS2)`

\vspace{12pt}

`r path_tikz(coreNeedPathS3)`

<!-- \textit{Note:} Stars based on more conservative unstandardized regressions -->

### 2022-10-26 PathModels.tex
path models render init

\begin{tikzpicture}[font=\sffamily]
    \node[mynode] (m){Interaction\\Quality};
    \node[mynode,below left=of m](x) {Core Need\\Fulfillment};
    \node[mynode,below right=of m](y) {Outgroup\\Attitudes};
    \node[mynode,above left=of m](xd) {Core Need\\Fulfillment};
    \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
    \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.30**} (yd.west);
    \draw[-latex] (x.north) -- node[auto] {0.40****} (m.west);
    \draw[-latex] (m.east) -- node[auto] {0.41***} (y.north);
    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.13} (y.west);
    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(A)}};
\end{tikzpicture}

\vspace{12pt}

\begin{tikzpicture}[font=\sffamily]
    \node[mynode] (m){Interaction\\Quality};
    \node[mynode,below left=of m](x) {Core Need\\Fulfillment};
    \node[mynode,below right=of m](y) {Outgroup\\Attitudes};
    \node[mynode,above left=of m](xd) {Core Need\\Fulfillment};
    \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
    \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.14***} (yd.west);
    \draw[-latex] (x.north) -- node[auto] {0.27****} (m.west);
    \draw[-latex] (m.east) -- node[auto] {0.24****} (y.north);
    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.07} (y.west);
    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(B)}};
\end{tikzpicture}

\vspace{12pt}

\begin{tikzpicture}[font=\sffamily]
    \node[mynode] (m){Interaction\\Quality};
    \node[mynode,below left=of m](x) {Core Need\\Fulfillment};
    \node[mynode,below right=of m](y) {Outgroup\\Attitudes};
    \node[mynode,above left=of m](xd) {Core Need\\Fulfillment};
    \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
    \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.18****} (yd.west);
    \draw[-latex] (x.north) -- node[auto] {0.31****} (m.west);
    \draw[-latex] (m.east) -- node[auto] {0.23****} (y.north);
    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.10**} (y.west);
    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(C)}};
\end{tikzpicture}

### 2022-10-26 scripts/functions/MlTbl.R

@@ -1,5 +1,8 @@
-#obj <- mdlWorker$lmerInterceptAttTypeTbl
-#objz <- mdlWorker$lmerInterceptAttTypeTblZ
+#obj <- tblLmerS1AttSlopeCoreQlt
+#objz <- tblLmerS1AttSlopeCoreQltZ
+
+# obj <- mdlTblElements[[i]][[1]]
+# objz <- mdlTblElements[[i]][[2]]
 
 lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   # Summarize models
@@ -39,7 +42,6 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
       RsqUpper = upper.CL
     )
   coefZOut <- merge(coefZCI, coefZR2)
-  
   coefZOut$Beta <- paste0(
     format(round(coefZOut$est, 2), nsmall = 2),
     " [", 
@@ -48,6 +50,10 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
     format(round(coefZOut$upr, 2), nsmall = 2),
     "]"
   )
+  coefZOut$BetaStar <- ifelse(coefZOut$p < .0001, "****", 
+                          ifelse(coefZOut$p < .001, "***", 
+                                 ifelse(coefZOut$p < .01, "**", 
+                                        ifelse(coefZOut$p < .05, "*", ""))))
   
   # Get unstandardized coefficients
   coef <- smry$coeftable %>% 
@@ -72,12 +78,16 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
     format(round(coefOut$upr, 2), nsmall = 2),
     "]"
   )
+  coefOut$Bstar <- ifelse(coefOut$p < .0001, "****", 
+                          ifelse(coefOut$p < .001, "***", 
+                                 ifelse(coefOut$p < .01, "**", 
+                                        ifelse(coefOut$p < .05, "*", ""))))
   coefOut <- 
     join(
       coefOut %>% 
         mutate(coef = gsub('_cwc|C$', '', coef)), 
       coefZOut %>% 
-        select(coef, Beta) %>% 
+        select(coef, estBeta = est, Beta, BetaStar) %>% 
         mutate(coef = gsub('_zwc|_gmz|Z$', '', coef)) %>%
         mutate(Beta = ifelse(coef == "(Intercept)", "", Beta)),
       by = "coef"

### 2022-10-27 manuscript.tex
path figure added
re-render

@@
 \usepackage{tabu}
+% Path Diagrams
+\usepackage{tikz}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.17}
+\tikzset{mynode/.style={draw,text width=1in,align=center} }
+\usetikzlibrary{positioning}
 
@@
 \begin{figure}
+  \caption{Path Diagrams Situational Needs Model across Studies}
+  \label{fig:MainPaths}
+  \begin{center}
+    \input{PathModels.tex}
+  \end{center}
+  \caption*{Note: \\
+  (A) Study 1; (B) Study 2; (C) Study 3.\\
+  General: Path coefficients are standardized regression coefficients.
+Statistical significance markers are based on the unstandardized regression results (as presented in Table \ref{tab:intergroupNeedsTblLong}).\\
+  **** p < .0001, *** p < .001, ** p < .01, * p < .05}
+\end{figure}
+
+\begin{figure}
   \caption{Contact Hypothesis}

### 2022-10-27 Methods-and-Results.Rmd
Table General Footnote

@@
   set_left_padding(11:nrow(.), 1, 12) %>%
+  add_footnote(., "Note:<br>**** p < .0001, *** p < .001, ** p < .01, * p < .05") %>%
   set_font_size(9)
 
-for (i in 11:nrow(testTbl)) {
+for (i in 11:(nrow(testTbl)-1)) {
   testTbl <- testTbl %>%

### 2022-10-29 Methods-and-Results.Rmd
shaded fix
table format

@@
   replace(is.na(.), "") %>%
+  mutate(
+    B = ifelse(
+      B.1 == "", paste("\\multicolumn{6}{c}{", B, sep=""),
+      B
+    )
+  ) %>%
   kbl(
@@
   ) %>%
-  pack_rows("Between Participant [aggregated linear regression] (Effect Size = $\\eta_{partial}$)", 1, 6, escape = FALSE) %>%
-  # pack_rows("Within Participants [multilevel linear regression] (Effect Size = $\\beta$)", 6, 9, escape = FALSE) %>%
+  pack_rows("Within Participants [multilevel linear regression] (Effect Size = $\\beta$)", 1, 6, escape = FALSE) %>%
+  pack_rows("Between Participant [aggregated linear regression] (Effect Size = $\\eta_{partial}$)", 7, nrow(mdlTblGeneralLong), escape = FALSE) %>%
   kableExtra::footnote(
@@
   gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  gsub(" &  &  &  &  & \\", "}\\", ., fixed = TRUE) %>% # fix table position
   kableExtra::landscape() %>%
@@
 
-```{r Export Path Models}
+```{r Export Path Models, include=FALSE}
 save(shortMdlPath, 

### 2022-11-02 manuscript.tex
Updates from Overleaf

@@
 One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations.
-This question becomes especially relevant when considering that negative intergroup contacts are common during everyday life.
-To understand positive intergroup interactions, we propose to consider situational motivations and psychological needs during everyday intergroup contact.
+We propose to consider situational psychological needs during everyday intergroup contact.
 We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total N of measurements = 10,297).
-Across the three studies, we find inconsistent results for a traditional test of the contact hypothesis with experience sampling data.
-However, when using multilevel models to test the contact hypothesis, we find that individual outgroup interactions and perceived interaction quality have a strong influence on positive outgroup attitudes.
+\hl{We find inconsistent results for a traditional test of the contact hypothesis with experience sampling data.
+However, when using multilevel models to test the contact hypothesis, we find that individual outgroup interactions and perceived interaction quality have a strong influence on positive outgroup attitudes.}
 The fulfillment of psychological needs is consistently a strong predictor of positive attitudes during intergroup interactions and these positive effects emerged via perceived interaction quality.
@@
 One of the main examples to date are the struggles of many migrants across the world, hoping to build a positive relationship with the majority group.
-One of the main ameliorations proposed by social psychologists has been the intergroup contact hypothesis.
+One of the main ameliorations proposed has been intergroup contact.
 In its most essential interpretation, the intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
 Over the past 70 years, a plethora of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}.
-However, even though a central assumption of intergroup contact theory has been that the contact should be positive, relatively little research has thus far explained when and why people perceive their everyday inter-group interactions as positive.
+However, even though a central assumption of intergroup contact theory is that the contact should be positive, relatively little research has thus far explained when and why people perceive their everyday inter-group interactions as positive.
 

### 2022-11-02 TitlePage.tex
single page title page

@@
 
-% add reference library file
-\addbibresource{references.bib}
+% custom open science badge height
+\newlength{\badgeheight}
+\setlength{\badgeheight}{1em}
 
@@
 Correspondence concerning this article should be addressed to Jannis Kreienkamp, Department of Psychology, University of Groningen, Grote Kruisstraat 2/1, 9712 TS Groningen (The Netherlands).
-E-mail: j.kreienkamp@rug.nl}
+E-mail: j.kreienkamp@rug.nl
+
+\vspace{1.5em}
+\noindent\textit{Open Science Practices:}\\
+\noindent \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/registrationplus-color.png}} Preregistration+, 
+\href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
+\href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,
+\href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, 
+\href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements
+
+}
 
@@
 % add title information (incl. title page and abstract)
-\maketitle
+%\maketitle
+
+\makeatletter
+\vspace*{3em}
+\begin{center}
+\noindent \textbf\@title
+\vspace{1em}
+\noindent \@author
+\end{center}
+\vspace{6em}
+\begin{center}%
+    \textbf\acksname%
+\end{center}%
+\vspace{-1em}
+\protect\raggedright
+\setlength{\parindent}{0.5in}
+\indent\par\@acks%
 

### 2022-11-02 manuscript.tex
single page title page

@@
 
+% custom open science badge height
+\newlength{\badgeheight}
+\setlength{\badgeheight}{1em}
+
 % language settings
@@
 
-\keywords{Intergroup Contact, Psychological Needs, Outgroup Attitudes, Interaction Quality, Extensive Longitudinal Data}
+\keywords{
+    Intergroup Contact, Psychological Needs, Outgroup Attitudes, Interaction Quality, Extensive Longitudinal Data\\
+    \textit{Open Science Practices:}
+    \noindent \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/registrationplus-color.png}} Preregistration+, 
+    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
+    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,\break
+    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, 
+    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements
+    }
 

### 2022-11-04 manuscript.tex
general intro comments adjusted

@@
 % Relevance (Version 1 of 2): Migrant Example Version:
-Conflict between social groups and their individual members remains a prevalent feature of the modern human condition.
-One of the main examples to date are the struggles of many migrants across the world, hoping to build a positive relationship with the majority group.
-One of the main ameliorations proposed has been intergroup contact.
-In its most essential interpretation, the intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
+One of the main intergroup societal issues to date, are the struggles of many migrants across the world, hoping to build a positive relationship with the majority group.
+The intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes be increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
 Over the past 70 years, a plethora of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}.
-However, even though a central assumption of intergroup contact theory is that the contact should be positive, relatively little research has thus far explained when and why people perceive their everyday inter-group interactions as positive.
+However, even though a central assumption of intergroup contact theory is that the contact should be positive, relatively little research has thus far explained when and why people perceive their everyday intergroup interactions as positive.
 
@@
 % Problem Illustration Paragraph:       
-Importantly, not understanding when and why an interaction is perceived as positive presents substantial theoretical and practical obstacles.
+Importantly, as we still fail to understand when and why an interaction is perceived as positive, substantial theoretical and practical challenges remain.
 There is now consistent evidence that negative intergroup contacts lead to worse attitudes, prejudice, and reduced future interaction motivation \citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.
-Theoretically, understanding interaction quality (i.e., whether an interaction is perceived as positive or negative) thus sits at the heart of understanding when an intergroup contact is successful (e.g., Brown et al.
+In light of these findings, understanding interaction quality thus sits at the heart of understanding when an intergroup contact is successful (e.g., Brown et al.
 \citeyear{Brown2007}, Tropp et al.
@@
 Allport’s original sentiment, Allport \citeyear{Allport1954b}).
-Practically, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in every-day life contexts.
+Practically, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in everyday life contexts.
 Understanding the psychological mechanisms of when and why interactions are perceived as positive is, thus, an important issue for understanding whether an interaction leads to better intergroup perceptions, especially during everyday interactions outside the lab.
 
-% Aim / Solution v.02: look at need fulfillment as mechanism in daily interactions of migrants
+% Aim / Solution v.02: look at need fulfillment as a mechanism in daily interactions of migrants
 % Proposal Paragraph:
-In this article, we turn towards the motivational literature and propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and positive outgroup attitudes.
-That is to say, that if a person, for example, seeks to feel accepted by their interaction partner and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
-To test this, we collected three sets of real-life data from recent immigrants.
-More specifically, we followed their daily interactions with majority group members, tracking situational needs, interaction quality, and outgroup attitudes.
+We propose that the key to understanding how an interaction is perceived is to examine the level of need fulfillment it provided to an individual.
+As an example, if someone seeks acceptance by their interaction partner, and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
+To test this, we collected three sets of real-life data from recent immigrants, assessing their daily interactions with majority group members, tracking situational needs, interaction quality, and outgroup attitudes.
 
@@
 % past research has either focused on conditions or cognitive-affective processes
-% neither are necessary or explain why an interaction is positive
+% neither are necessary nor explain why an interaction is positive
 Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
-It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for such positive contact effects \citep[Allport's Optimal Contact conditions;][]{Allport1954b, Pettigrew1969}.
-However, a major meta-analysis of these contact conditions showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met \citep[][]{Pettigrew2006}.
-It, thus, remains unclear when and why exactly an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects\footnote{It should be noted here that following Allport's original conditions, several additional conditions of optimal contact were proposed \citep[for a critical discussion see][]{Pettigrew1986}.
+It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for such positive contact effects \citep[][]{Allport1954b, Pettigrew1969}.
+However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be essential to finding positive effects of intergroup contact \citep[][]{Pettigrew2006}.
+It, thus, remains unclear when and why an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects\footnote{It should be noted here that following Allport's original conditions, several additional conditions of optimal contact were proposed \citep[for a critical discussion see][]{Pettigrew1986}.
 Similarly, since the early 21\textsuperscript{st} century many psychological processes during intergroup contact were examined \citep[e.g.
@@
 However, all these advances share the underlying criticism that they are not geared towards understanding when and why an interaction is perceived as positive.}.
-We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
+We propose that the literature on motivation and psychological needs may help us understand when and why exactly an interaction is perceived as positive.
 
@@
 Past research has either focused on conditions under which interactions tend to have favorable effects \citep[e.g., Allport's optimal conditions;][]{Allport1954b, Pettigrew1969} or has investigated cognitive-affective processes during contact \citep[e.g., group salience, intimacy, attachment, or intergroup anxiety;][]{Brown2005, Marinucci2021, Tropp2021, Paolini2004}.
-However, neither the contact conditions nor the cognitive-affective processes are particularly well equipped to explain when and why an interaction will be perceived as positive.
+However, neither the contact conditions nor the cognitive-affective processes are particularly well-equipped to explain when and why an interaction will be perceived as positive.
 We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
@@
 % Promising for intergroup contact: Asked for in intergroup contact reviews and first research looked at social change
-And even within the field of intergroup contact the idea of need fulfillment as a psychological mechanism is not entirely novel.
-\citet{Dovidio2017} in their narrative review have suggested that understanding psychological needs might be essential to constructive intergroup contact.
-And recently first empirical research has even found psychological need fulfillment during intergroup contacts to predict support for social change \citep[][]{Hassler2021}.
-There is thus initial evidence to suggest that need fulfillment during intergroup contact might offer a promising psychological mechanism to understand perceived interaction quality and positive outgroup attitudes.
+Even within the field of intergroup contact, the idea of need fulfillment as a psychological mechanism is not entirely novel \citep[e.g.,][]{Dovidio2017}.
+First empirical research has even found psychological need fulfillment during intergroup contacts to predict support for social change \citep[][]{Hassler2021}.
+Considering need fulfillment during intergroup contact might therefore offer a promising psychological mechanism to understand perceived interaction quality and positive outgroup attitudes.
 
@@
 Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad range of fundamental psychological needs.
-To avoid this predicament we propose to start by using adaptive and responsive survey designs that allow a tailored approach based on the participants inputs \citep[e.g.,][]{Tourangeau2017}.
+To avoid this predicament we propose to start by using adaptive and responsive survey designs that allow a tailored approach based on the participants' inputs \citep[e.g.,][]{Tourangeau2017}.
 In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., situation core need) and with reference to their own response the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment).
-Such an adaptive approach would allow us to take this initial step and test whether situational psychological needs indeed generally predict perceived interaction quality and positive outgroup attitudes independent of need content.
+Such an adaptive approach allows us to take this initial step and test whether situational psychological needs indeed generally predict perceived interaction quality and positive outgroup attitudes independent of need content.
 
-\section{Real-Life Process Data}
+\section{Intergroup Contact in Daily Life}
 While we have argued that a need fulfillment mechanism is relevant to intergroup contact generally, its flexible and broad applicability might be ideally suited to address the pressing issue of understanding natural intergroup contacts outside the lab.
@@
 Even with extended intervention studies, the most fine-grained data available is usually limited to pre-post-control designs.
-Such empirical practices stand, however, in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the core idea of the contact hypothesis, which was focused on the daily interactions of people \citep[see][]{Allport1954b}.
-As a result, prominent figures within the intergroup contact field have called for studies that collect longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017, Dixon2005}.
-Such data would be able to capture real-life interactions that include interaction-specific mechanism information close the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
-Moreover, because data is nested within participants, experience-sampling data often allows to capture large amounts of high-quality data with relatively few participants.}.
+Such empirical practices stand, however, in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the core idea of the contact hypothesis, which was focused on the daily interactions of people \citep[][]{Allport1954b}.
+As a result, within the intergroup contact field researchers have called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017, Dixon2005}.
+Such data would be able to capture real-life interactions that include interaction-specific mechanism information close to the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
+Moreover, because data is nested within participants, experience-sampling data often allows capturing large amounts of high-quality data with relatively few participants.}.
 
@@
 At the same time, analytical methods for such more complex data have become more readily available, making the analyses more approachable \citep[e.g., see][]{ODonnell2021}.
-Given these, technological and methodological developments, we were able to collect a large amount of real-life data following the daily intergroup interactions of recent migrants with the majority group members.
+Given these technological and methodological developments, we were able to collect a large amount of real-life data following the daily intergroup interactions of recent migrants with the majority group members.
 
@@
 First, our study is among the first to test the fundamental tenets of intergroup contact and Allport's conditions in real-life extensive longitudinal data.
-Second, we test whether the fulfillment situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
+Second, we test whether the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
 And third, we test the role of interaction quality in  the relationship of psychological need fulfillment and outgroup attitudes.
@@
     \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
-We also expect situational need fulfillments to work at least as good as Allport's optimal contact conditions in predicting outgroup attitudes.
+We also expect situational need fulfillments to work at least as well as Allport's optimal contact conditions in predicting outgroup attitudes.
 \end{enumerate}
-Beyond these main hypotheses we have formulated several sub-hypotheses that form the basis for our analysis plan (these sub-hypotheses also include several robustness checks and are available in Appendix \ref{app:AppendixHypotheses}).
+Beyond these main hypotheses, we have formulated several sub-hypotheses that form the basis for our analysis plan (these sub-hypotheses also include several robustness checks and are available in Appendix \ref{app:AppendixHypotheses}).
 
@@
 For our main theory tests we sequentially focus on five sets of models to test and validate our hypotheses:
-
-\hl{[link sub-hypotheses to the following?]}\\
-\hl{[add formulas to the following?]}\\
-\hl{[move (parts of) the following to Appendix }\ref{app:AppendixHypotheses}\hl{?]}\\
-\hl{[I think this is too long]}
 
@@
   (a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).\\
-  (b) Core Need Fulfillment predicting Outgroup Attitudes, while controlling for self-determination theory needs (intergroup contact sample).\\
-  General: Random effects meta analytic results are presented for completeness.}
+  (b) Core Need Fulfillment predicting Outgroup Attitudes while controlling for self-determination theory needs (intergroup contact sample).\\
+  General: Random effects meta-analytic results are presented for completeness.}
 \end{figure}
@@
 \addtolength{\leftskip}{2.5em}
-Participants with more intergroup interactions should have a more favorable outgroup attitudes.
+Participants with more intergroup interactions should have more favorable outgroup attitudes.
 \end{subhyp}
@@
 \addtolength{\leftskip}{2.5em}
-Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
+Participants with more intergroup interactions should have more favorable outgroup attitudes depending on the average interaction quality.
 \end{subhyp}
@@
 \addtolength{\leftskip}{2.5em}
-Based on past research on the role of interaction quality, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extend be assumed by interaction quality.
+Based on past research on the role of interaction quality, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extent be assumed by interaction quality.
 \end{subhyp}
@@
 \addtolength{\leftskip}{2.5em}
-Outgroup attitudes should be more favorable after intergroup interactions with high key need fulfillment.
+Outgroup attitudes should be more favorable after intergroup interactions with high key-need fulfillment.
 \end{subhyp}
@@
 The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
-Thus, the effect of key need fulfillment on outgroup attitudes should stronger for intergroup interact than for ingroup interactions.
+Thus, the effect of key need fulfillment on outgroup attitudes should be stronger for intergroup interactions than for ingroup interactions.
 \end{subhyp}
@@
 \addtolength{\leftskip}{2.5em}
-The effect of key need fulfillment on outgroup attitudes should be persist even when taking other fundamental psychological needs into account.
+The effect of key need fulfillment on outgroup attitudes should persist even when taking other fundamental psychological needs into account.
 Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
@@
 
+\section{Appendix B: Robustness}
+\label{app:AppendixRobustness}
+
 \end{document}

### 2022-11-04 manuscript.tex
light discussion edits

@@
 % Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results for our main proposal regarding the importance of situational key needs, we find highly consistent positive results across all three studies.
-We find that in all three extensive longitudinal datasets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
+Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal datasets, that the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
 We find that in all three studies the effect of core need fulfillment on outgroup attitudes goes either fully or partially through interaction quality.
@@
 % (1) Sample = minority and (voluntary) migrants, (2) Methodology = short scales (reliability) and no lagged effects, (3) Core Need Concept = non-specific
-Among the limitations of our studies we should consider the following.
 One limitation is our choice of samples.
-While we believe that a need–based mechanism should be relevant to any inter-group contact, our sample has focused on a minority- and (voluntary) migrant perspective.
+While we believe that a need-based mechanism should be relevant to any inter-group contact, our sample has focused on a minority- and (voluntary) migrant perspective.
 Without additional evidence it thus remains difficult to judge whether motivational effects will generalize to other migrant groups (e.g., forced migrants), other intergroup contexts (e.g., gender-, religious-, or sexual orientation groups), and to majority groups in their outgroup attitudes.
 We know of no research that for other contexts psychological needs would not be relevant (once existential needs are met) but future research may extend our findings to other contexts to build an even broader understanding of psychological needs in intergroup contacts.
+
 A second limitation lies in our methodology.
@@
 To circumvent this shortcoming, we have ensured that the measures we used were, whenever possible, based on past validations.
-However, the circumstance remains that extensive longitudinal data often does not allow the same scrutiny of measurement reliability as single–shot cross–section data sets.
+However, the circumstance remains that extensive longitudinal data often does not allow the same scrutiny of measurement reliability as single–shot cross-sectional data sets.
 An additional methodological question lies in the unexplored potential of the longitudinal aspects of our data.
 For our research questions, we have focused on contemporaneous effects within the data set, yet future investigations should seek to extend the mechanism to developmental trajectories within and between participants.
+
 And finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
 This comes at the expense of specificity in the situational needs (i.e., we have not explored whether different types of needs have stronger effects on interaction quality and outgroup attitudes).
-With the adaptive measurement we used such an investigation would be possible (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
+With the adaptive measurement, we used such an investigation would be possible (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
 Nonetheless, future research may explore which exact needs are most important in different intergroup contexts.
@@
 % ESM data
-Given these limitations, we can nonetheless draw a number of implications for other researchers and practitioners --- ranging from the benefits of longitudinal data to theoretical implications.
+Despite these limitations, we can nonetheless draw a number of implications for other researchers and practitioners --- ranging from the benefits of longitudinal data to theoretical implications.
 A first implication concerns the feasibility and usefulness of extensive longitudinal data for intergroup contact research and the broader field of social psychology.
@@
 In the context of intergroup contact research, we are among the first to answer calls to test intergroup contact mechanisms using extended real-life data \citep[e.g.,][]{Pettigrew2011, MacInnis2015}.
-In doing so, we not only collected an unprecedented amount of real-life data, but our consideration of extensive longitudinal data may present new inconsistencies in how participants perceive and cognitively aggregate their past interactions with other groups — which may suggest large-scale recall-biases or conflations of within and between participant effects in conventional cross-section studies.
+In doing so, we not only collected an unprecedented amount of real-life data, but our consideration of extensive longitudinal data may present new inconsistencies in how participants perceive and cognitively aggregate their past interactions with other groups — which may suggest large-scale recall biases or conflations of within and between participant effects in conventional cross-section studies.
 

### 2022-11-04 Robustness-Methods-and-Results.Rmd
robustness appendix added

--- 2022-10-26 Methods-and-Results.Rmd
@@
 
-Based on our main hypotheses, the aim of our first study was to specifically test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
-To this aim, we conducted an intensive longitudinal survey study with recent migrants to the Netherlands.
-Data was collected from May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all participants started the study within the first two days).
-
 The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
@@
 rm(workerOccupation)
-
-# look at frequencies of characteristics 
-table(workerSampleInfo$gender)
-table(workerSampleInfo$edu)
-table(workerSampleInfo$occupation)
-table(as.character(workerSampleInfo$nationality))
-
-# categorical variables:
-# - outgroup contact
-# - non-outgroup contact
-
-# continuous variables:
-# - Core Need fulfillment
-# - SDT Competence
-# - SDT Autonomy
-# - SDT Relatedness
-# - Interaction Quality
-# - Outgroup Attitudes
-######
-# within cor
-# between cor
-# ---
-# Grand mean
-# SD between
-# SD within
-# Proportion of variance
-# __ __ __
-# Note:
-# N within ppt.s 
-######
 
@@
 
-```{r workerVarDescr, include=FALSE}
-workerMlCor <-
-  MlCorMat(
-    data = dtWorkerSupp$workerInteractionType,
-    id = "PID",
-    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "quality_overall_1", "thermometerDutch_1"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
-  )
-
-workerMlCor %>%
-  kable(
-    .,
-    caption = "Worker: Multilevel Core Variable Descriptives",
-    format = "latex",
-    booktabs = TRUE,
-    linesep = linesep(c(ncol(.))),
-    align = c("l", rep("c", ncol(.) - 1))
-  ) %>%
-  footnote(
-    general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
-      "*** p < .001, ** p < .01,  * p < .05"
-    )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/workerVarDescr.tex")
-```
-
-```{r workerOutVarDescr, include=FALSE}
-workerOutMlCor <-
-  MlCorMat(
-    data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
-    id = "PID",
-    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "quality_overall_1", "thermometerDutch_1"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
-  )
-
-workerOutMlCor %>%
-  kable(
-    .,
-    caption = "Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
-    format = "latex",
-    booktabs = TRUE,
-    linesep = linesep(c(ncol(.))),
-    align = c("l", rep("c", ncol(.) - 1))
-  ) %>%
-  footnote(
-    general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
-      "*** p < .001, ** p < .01,  * p < .05"
-    )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/workerOutVarDescr.tex")
-
-# misty::multilevel.descript(dtWorkerSupp$workerWithinBetween$keyMotiveFulfilled, cluster = dtWorkerSupp$workerWithinBetween$PID)
-```
-
-\subsubsection{Participants} After receiving ethical approval from the University Masked for Peer Review, we recruited `r nrow(workerSampleInfo)` migrants using the local paid participant pool and specifically targeted non-Dutch migrants to participate in our study.
-Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
-With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(workerSampleInfo$dailiesN), big.mark=",")`).
-This is a common number of measurements found in experience sampling studies and offers sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
-Participants were compensated for their participation with up to 34 Euros – each two Euros for pre- and post-questionnaire as well as 50 Eurocents for every experience sampling measurement occasion.
-The sample consisted of relatively young, educated, and western migrants from the global north ($M_{age}$ = `r format(round(mean(workerSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(workerSampleInfo$age),2), nsmall=2)`, `r nrow(workerSampleInfo %>% filter(gender == "Female"))` women, `r nrow(workerSampleInfo %>% filter(occupation == "student"))` students).
-The sample accurately describes the largest groups of migrants in the region \citep[][]{GemeenteGroningen2015}.
-
-\subsubsection{Procedure} The study itself consisted of three main parts, an introductory pre-measurement, and the daily experience sampling measurements, as well as a concluding post-measurement.
-After giving informed consent, participants started by filling in an online pre-questionnaire assessing demographics and general information about their immigration.
-Over the next thirty days, the participants were then invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median survey duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_))) %>% as.character`).
-General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%).}.
-The response rates were approximately equal during mornings (\textit{n} = `r format(sum(workerSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(workerSampleInfo$afternoonN), big.mark=",")`) and most measurements were completed within four hours of the invitation.
-After the final day of experience sampling measurements, participants were invited to fill in a longer post measurement survey that mirrored the pre-measurement.
-All key variables for this study were part of the short experience sampling surveys.
-
 \subsubsection{Materials}
 
-\paragraph{Intergroup Contact}To test the prerequisite effect of intergroup contact, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
-(In person interaction for at least 10 minutes)}”.
-Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
-interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtWorkerSupp$workerAvFreQual$SumContactNL), big.mark=",")` of all `r format(nrow(dtWorkerSupp$workerInteractionType), big.mark=",")` experience sampling responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts.
-These participants are removed from any analyses that focus on outgroup contacts.}.
-
-\paragraph{Psychological Needs}Irrespective of whether participants had an interaction with Dutch people or not, everyone answered a short series of questions on psychological need fulfillment.
-However, whereas participants with interactions reported on the need fulfillment during the interaction, people without interactions with Dutch people judged the past daytime period in general.
-To assess the fulfillment of psychological needs, we included two types of need measurement: (1) the core situational need and (2) general self-determination theory needs.
-
-For the core situational need, we asked participants in an open ended text field: “\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}”.
-Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).
-
-We, additionally, included a common measure of three self-determination theory needs \citep[see][]{Downie2008}.
+\paragraph{General Psychological Needs} In addition to the intergroup contact dummy and situational core need reported in the main text, we included a common measure of three self-determination theory needs \citep[see][]{Downie2008}.
 The items were introduced either by “\textit{During the interaction:}” or “\textit{This morning [/afternoon]:}” and measured autonomy (“\textit{I was myself.}”), competence (“\textit{I felt competent.}”), and relatedness (without intergroup contact “\textit{I had a strong need to belong}”; with intergroup contact: “\textit{I shared information about myself.}” and “\textit{The other(s) shared information about themselves.}”).
@@
 
-\paragraph{Perceived Interaction Quality}As an explanatory mechanism, we assessed ratings of the perceived interaction quality.
-As our main measurement, participants rated the statement “\textit{Overall the interaction was …}” on two continuous slider scales measuring pleasantness \citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
-
-\paragraph{Outgroup Attitudes}At the end of every experience sampling measurement we asked all participants about their current attitudes towards the Dutch – our main dependent variable.
-To assess the momentary outgroup evaluation we used the common feeling thermometer: “How favorable do you feel towards the Dutch?” \citep[][]{Lavrakas2008}.
-Participants then rated their attitude on a continuous slider scale from “very cold – 0” through “no feeling – 50” to “very warm – 100”.
-Both the question phrasing as well as the tick labels were consistent with large-scale panel surveys \citep[e.g.,][]{DeBell2010}.
-
 \subsection{Results}
-
-```{r WorkerFreqAttCor, include=FALSE}
-dtWorkerSupp$workerAvFreQual <-
-  dtWorkerSupp$workerAvFreQual %>%
-  mutate(
-    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
-    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
-    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
-    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
-  )
-
-# correlation panel
-pairs.panels.new(
-  dtWorkerSupp$workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
-    "Sum:\nNumber of Outgroup Contacts (NL)",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-
-# correlation panel with interaction sums winsorized
-pairs.panels.new(
-  dtWorkerSupp$workerAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
-    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-
-rContactAvg <- dtWorkerSupp$workerAvFreQual %>% 
-  select(SumContactNL, SumContactNLAll, AvAttitude) %>%
-  as.matrix %>%
-  rcorr
-
-rContactAvgMax <- format(round(max(abs(rContactAvg$r[rownames(rContactAvg$r) != "AvAttitude","AvAttitude"])),2), nsmall = 2)
-pContactAvgMin <- format(round(min(rContactAvg$P[rownames(rContactAvg$P) != "AvAttitude","AvAttitude"]),3), nsmall = 3)
-
-# Average Interaction Quality and their Average Outgroup Attitudes
-rAttitudeQuality <- dtWorkerSupp$workerAvFreQual %>% 
-  select(AvQuality, AvAttitude) %>%
-  as.matrix %>%
-  rcorr
-```
 
@@
 mdlWorker <- list()
-
-# regression
-mdlWorker$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtWorkerSupp$workerAvFreQual)
-# summary(lmWorkerAttFreqQualX)
-
-summ(
-  mdlWorker$lmAttFreqQualX,
-  confint = TRUE,
-  digits = 3
-)
-
-mdlWorker$lmAttFreqQualXEta <-
-  effectsize::eta_squared(mdlWorker$lmAttFreqQualX, partial = TRUE)
-
-interactions::interact_plot(
-  mdlWorker$lmAttFreqQualX,
-  pred = AvQuality_c,
-  modx = SumContactNL_c,
-  interval = TRUE,
-  partial.residuals = TRUE
-)
-
-interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
-                             pred = AvQuality_c,
-                             modx = SumContactNL_c,
-                             alpha = .05)
-
 ```
@@
 ```
-```{r workerModelInterceptAttType, include=FALSE}
-# Create and save Model
-mdlWorker$lmeInterceptAttType <-
-  lme(
-    thermometerDutch_1 ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
-    random =  ~ 1 | PID,
-    na.action=na.omit,
-    data = dtWorkerSupp$workerInteractionType
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlWorker$lmerInterceptAttType <- lmer(
-    thermometerDutch_1 ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM + (1 | PID),
-    data = dtWorkerSupp$workerInteractionType
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlWorker$lmerInterceptAttTypeCI <- 
-  confint(method = "Wald", mdlWorker$lmerInterceptAttType)
-
-# Compare new model to previous step
-anova(mdlWorker$lmeAttNull, 
-      mdlWorker$lmeInterceptAttType) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorker$varInterceptAttType <- 
-  lme4::VarCorr(mdlWorker$lmeInterceptAttType)
-```
-
-\subsubsection{Contact Hypothesis}
-<!-- We tested the most general contact hypothesis in two steps.
-First, we assessed whether overall between participants more intergroup interactions were related to to more positive average outgroup attitudes.
-Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
-We find that neither the overall number of contacts nor the number of experience sampling responses with a contact were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`).
-However, we did find a medium sized correlation between the participants' average contact quality and their average outgroup attitudes (\textit{r} = `r format(round(rAttitudeQuality$r[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],2), nsmall = 2)`, \textit{p} = `r format(round(rAttitudeQuality$P[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],3), nsmall = 3)`).
-And when considering the number of contacts and average contact quality jointly in a linear regression, we additionally found a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of contacts the positive effect of average contact quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblLong}).
--->
-We used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
-Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by use centered predictors and reintroducing the means as level two predictors.
-Nonetheless, we also offer an analysis of the joint data sets in Online Supplemental Material A (for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
-This is unusual and might indicate that the effect is very consistent across participants.
-However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}.
-Thus, in our first data we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data.
-While this offers support for the most basic premise of the intergroup contact hypothesis (i.e., that any interaction will lead to more positive outgroup attitudes), this analysis does not consider any notion of interaction quality.
-We assess the conditional effects of interaction numbers and interaction quality ratings after we report on the individual studies to avoid under-powered analyses.
-
-\subsubsection{Core Need}The main proposal of our article is that the success of an outgroup contact might be explained by whether or not the contact fulfilled the person's core situational need.
-This should, in turn, be due to a higher perceived contact quality.
-We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived contact quality, and (3) whether the variance explained by the core need is subsumed by the perceived contact quality if considered jointly (for full regression results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
 
@@
 ```
-```{r workerOutModelInterceptAttCore, include=FALSE}
-# Create and save Model
-mdlWorkerOut$Att$lmeInterceptCore <-
-  lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc,
-    random = ~ 1 | PID,
-    na.action=na.omit,
-    data = dtWorkerSupp$workerOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlWorkerOut$Att$lmerInterceptCore <-
-    lmer(
-      thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + (1 | PID),
-      data = dtWorkerSupp$workerOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlWorkerOut$Att$lmerInterceptCoreCI <- 
-  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCore)
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeNull, 
-      mdlWorkerOut$Att$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varInterceptCore <-
-  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwInterceptCore <-
-  1 - (mdlWorkerOut$Att$varInterceptCore["(Intercept)", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varNull["(Intercept)", "Variance"] %>% as.numeric)
-mdlWorkerOut$Att$varBtwPercInterceptCore <-
-  (1 - (mdlWorkerOut$Att$varInterceptCore["(Intercept)", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varNull["(Intercept)", "Variance"] %>% as.numeric)) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinInterceptCore <-
-  1 - (mdlWorkerOut$Att$varInterceptCore["Residual", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varNull["Residual", "Variance"] %>% as.numeric)
-mdlWorkerOut$Att$varWithinPercInterceptCore <-
-  (1 - (mdlWorkerOut$Att$varInterceptCore["Residual", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varNull["Residual", "Variance"] %>% as.numeric)) * 100
-```
-```{r workerOutModelSlopesAttCore, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Att$lmeSlopesCore <-
-  lme(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc,
-    random = ~ 1 + keymotive_fulfillemt_1_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    na.action=na.omit,
-    data = dtWorkerSupp$workerOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Att$lmerSlopesCore <- lmer(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc +
-      (1 + keymotive_fulfillemt_1_cwc | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# all variables standardized within PPT
-summ(
-  mdlWorkerOut$Att$lmerSlopesCoreZ <- lmer(
-    thermometerDutch_1_zwc ~
-      keymotive_fulfillemt_1_zwc +
-      (1 + keymotive_fulfillemt_1_zwc | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# standardized coefficients
-stdCoef.merMod(mdlWorkerOut$Att$lmerSlopesCore)
-
-# 95%CIs
-mdlWorkerOut$Att$lmerSlopesCoreCI <- 
-  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCore)
-
-# Attempts at R^2
-r2mlm::r2mlm(mdlWorkerOut$Att$lmerSlopesCore, bargraph = TRUE)
-mitml::multilevelR2(mdlWorkerOut$Att$lmerSlopesCore)
-performance::r2(mdlWorkerOut$Att$lmerSlopesCore)
-performance::model_performance(mdlWorkerOut$Att$lmerSlopesCore)
-performance::compare_performance(mdlWorkerOut$Att$lmerNull, 
-                                 mdlWorkerOut$Att$lmerInterceptCore, 
-                                 mdlWorkerOut$Att$lmerSlopesCore)
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeNull, 
-      mdlWorkerOut$Att$lmeInterceptCore, 
-      mdlWorkerOut$Att$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varSlopesCore <- 
-  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCore)
-
-# The estimate of between-group (or Intercept variance) explained:
-# Variance Explained = 1 – (Var with Predictor/Var without Predictor)
-mdlWorkerOut$Att$varBtwSlopesCore <-
-  1 - (mdlWorkerOut$Att$varSlopesCore["(Intercept)", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varInterceptCore["(Intercept)", "Variance"] %>% as.numeric)
-mdlWorkerOut$Att$varBtwPercSlopesCore <-
-  (1 - (mdlWorkerOut$Att$varSlopesCore["(Intercept)", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varInterceptCore["(Intercept)", "Variance"] %>% as.numeric)) * 100
-# and the estimate of within-group (or residual variance) explained is:
-mdlWorkerOut$Att$varWithinSlopesCore <-
-  1 - (mdlWorkerOut$Att$varSlopesCore["Residual", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varInterceptCore["Residual", "Variance"] %>% as.numeric)
-mdlWorkerOut$Att$varWithinPercSlopesCore <-
-  (1 - (mdlWorkerOut$Att$varSlopesCore["Residual", "Variance"] %>% as.numeric / mdlWorkerOut$Att$varInterceptCore["Residual", "Variance"] %>% as.numeric)) * 100
-
-# Assumption Checks:
-mdlWorkerOut$Att$diagSlopesCore <- 
-  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCore, type = "diag")
-grid.arrange(
-  mdlWorkerOut$Att$diagSlopesCore[[1]],
-  mdlWorkerOut$Att$diagSlopesCore[[2]]$`PID`,
-  mdlWorkerOut$Att$diagSlopesCore[[3]],
-  mdlWorkerOut$Att$diagSlopesCore[[4]]
-)
-
-# Plot prediction model
-mdlWorkerOut$Att$predSlopesCore <- 
-  dtWorkerSupp$workerOutWithinBetween %>%
-  select(thermometerDutch_1, session, PID) %>% 
-  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCore,
-                           dtWorkerSupp$workerOutWithinBetween,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorkerOut$Att$predPltSlopesCore <-
-    ggplot(data = mdlWorkerOut$Att$predSlopesCore, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCore.png",
-  mdlWorkerOut$Att$predPltSlopesCore,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
 
@@
 ```
-```{r workerOutModelInterceptQltCore, include=FALSE}
-# Create and save Model
-mdlWorkerOut$Qlt$lmeInterceptCore <-
-  lme(
-    quality_overall_1 ~ keymotive_fulfillemt_1_cwc,
-    random = ~ 1 | PID,
-    na.action=na.omit,
-    data = dtWorkerSupp$workerOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlWorkerOut$Qlt$lmerInterceptCore <-
-    lmer(
-      quality_overall_1 ~ keymotive_fulfillemt_1_cwc + (1 | PID),
-      data = dtWorkerSupp$workerOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# 95%CI
-mdlWorkerOut$Qlt$lmerInterceptCoreCI <- 
-  confint(method = "Wald", mdlWorkerOut$Qlt$lmerInterceptCore)
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Qlt$lmeNull, 
-      mdlWorkerOut$Qlt$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Qlt$varInterceptCore <-
-  lme4::VarCorr(mdlWorkerOut$Qlt$lmeInterceptCore)
-```
-```{r workerOutModelSlopesQltCore, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Qlt$lmeSlopesCore <-
-  lme(
-    quality_overall_1 ~
-      keymotive_fulfillemt_1_cwc,
-    random = ~ 1 + keymotive_fulfillemt_1_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    na.action=na.omit,
-    data = dtWorkerSupp$workerOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Qlt$lmerSlopesCore <-
-    lmer(
-      quality_overall_1 ~
-        keymotive_fulfillemt_1_cwc +
-        (1 + keymotive_fulfillemt_1_cwc | PID),
-      data = dtWorkerSupp$workerOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# 95%CI
-mdlWorkerOut$Qlt$lmerSlopesCoreCI <- 
-  confint(method = "Wald", mdlWorkerOut$Qlt$lmerSlopesCore)
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Qlt$lmeNull, 
-      mdlWorkerOut$Qlt$lmeInterceptCore, 
-      mdlWorkerOut$Qlt$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Qlt$varSlopesCore <- 
-  lme4::VarCorr(mdlWorkerOut$Qlt$lmeSlopesCore)
-```
-```{r workerOutModelInterceptAttCoreQlt, include=FALSE}
-# Create and save Model
-mdlWorkerOut$Att$lmeInterceptCoreQlt <-
-  lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + quality_overall_1_cwc,
-    random = ~ 1 | PID,
-    na.action=na.omit,
-    data = dtWorkerSupp$workerOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlWorkerOut$Att$lmerInterceptCoreQlt <-
-    lmer(
-      thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + quality_overall_1_cwc + (1 | PID),
-      data = dtWorkerSupp$workerOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95% CI
-mdlWorkerOut$Att$lmerInterceptCoreQltCI <- 
-  confint(method = "Wald", mdlWorkerOut$Att$lmerInterceptCoreQlt)
-
-# Compare new model to previous step
-anova(
-  mdlWorkerOut$Att$lmeNull, 
-  mdlWorkerOut$Att$lmeInterceptCoreQlt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varInterceptCoreQlt <-
-  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreQlt)
-```
-```{r workerOutModelSlopesAttCoreQlt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Att$lmeSlopesCoreQlt <-
-  lme(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc + quality_overall_1_cwc,
-    random = ~ 1 + keymotive_fulfillemt_1_cwc + quality_overall_1_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    na.action=na.omit,
-    data = dtWorkerSupp$workerOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Att$lmerSlopesCoreQlt <- lmer(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc + quality_overall_1_cwc +
-      (1 + keymotive_fulfillemt_1_cwc + quality_overall_1_cwc | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlWorkerOut$Att$lmerSlopesCoreQltCI <- 
-  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreQlt)
-
-# Compare new model to previous step
-anova(
-  mdlWorkerOut$Att$lmeNull,
-  mdlWorkerOut$Att$lmeInterceptCoreQlt,
-  mdlWorkerOut$Att$lmeSlopesCoreQlt
-) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varSlopesCoreQlt <- 
-  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreQlt)
-
-# Assumption Checks:
-mdlWorkerOut$Att$diagSlopesCoreQlt <- 
-  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreQlt, type = "diag")
-grid.arrange(
-  mdlWorkerOut$Att$diagSlopesCoreQlt[[1]],
-  mdlWorkerOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
-  mdlWorkerOut$Att$diagSlopesCoreQlt[[3]],
-  mdlWorkerOut$Att$diagSlopesCoreQlt[[4]]
-)
-
-# Plot prediction model
-mdlWorkerOut$Att$predSlopesCoreQlt <- 
-  dtWorkerSupp$workerOutWithinBetween %>%
-  select(thermometerDutch_1, session, PID) %>% 
-  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreQlt,
-                           dtWorkerSupp$workerOutWithinBetween,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorkerOut$Att$predPltSlopesCoreQlt <-
-    ggplot(data = mdlWorkerOut$Att$predSlopesCoreQlt, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreQlt.png",
-  mdlWorkerOut$Att$predPltSlopesCoreQlt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCore, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreCI, varName = "keymotive_fulfillemt_1_cwc")`) and also predicted higher perceived contact quality (random intercept model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Qlt$lmeInterceptCore, lmerCI = mdlWorkerOut$Qlt$lmerInterceptCoreCI, varName = "keymotive_fulfillemt_1_cwc")`).
-Moreover, when we consider the influences of core need fulfillment and contact quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived contact quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`).
-We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes.
-Additionally, this effect is likely explained by its effect through perceived contact quality.
-
-<!-- \faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?  -->
-
-\subsubsection{Robustness}
+
 ```{r workerModelInterceptAttCoreInt, include=FALSE}
@@
 \section{Study 2}
-
-The aim of Study 2 is similar to Study 1, as we again test the general contact hypothesis, the influence of core need fulfillment, and perceived contact quality during intergroup contacts.
-However, in this second study we collected a substantially larger sample of international students who recently arrived in the Netherlands and also improved the study design (e.g., pop-up explanations described later).
-The survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations as these students will likely interact with the Dutch majority outgroup on a daily basis.
-Data was collected from November 19\textsuperscript{th}, 2018 through January 6\textsuperscript{th}, 2019.
-
-The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
-Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
 
@@
 table(as.character(studentSampleInfo$nationality))
-
-# categorical variables:
-# - outgroup contact
-# - non-outgroup contact
-
-# continuous variables:
-# - Core Need fulfillment
-# - SDT Competence
-# - SDT Autonomy
-# - SDT Relatedness
-# - Interaction Quality
-# - Outgroup Attitudes
-######
-# within cor
-# between cor
-# ---
-# Grand mean
-# SD between
-# SD within
-# Proportion of variance
-# __ __ __
-# Note:
-# N within ppt.s 
-######
 
@@
 
-```{r studentVarDescr, include=FALSE}
-studentMlCor <-
-  MlCorMat(
-    data = dtStudentSupp$studentInteractionType,
-    id = "PID",
-    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "quality_overall", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
-  )
-
-studentMlCor %>%
-  kable(
-    .,
-    caption = "Student: Multilevel Core Variable Descriptives",
-    format = "latex",
-    booktabs = TRUE,
-    linesep = linesep(c(ncol(.))),
-    align = c("l", rep("c", ncol(.) - 1))
-  ) %>%
-  footnote(
-    general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
-      "*** p < .001, ** p < .01,  * p < .05"
-    )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/studentVarDescr.tex")
-```
-
-```{r studentOutVarDescr, include=FALSE}
-studentOutMlCor <-
-  MlCorMat(
-    data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
-    id = "PID",
-    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "quality_overall", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
-  )
-
-studentOutMlCor %>%
-  kable(
-    .,
-    caption = "Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
-    format = "latex",
-    booktabs = TRUE,
-    linesep = linesep(c(ncol(.))),
-    align = c("l", rep("c", ncol(.) - 1))
-  ) %>%
-  footnote(
-    general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
-      "*** p < .001, ** p < .01,  * p < .05"
-    )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/studentOutVarDescr.tex")
-
-# misty::multilevel.descript(dtStudentsSupp$studentWithinBetween$keyMotiveFulfilled, cluster = dtStudentsSupp$studentWithinBetween$PID)
-```
-
-\subsubsection{Participants} We recruited `r nrow(studentSampleInfo)` international students using a local participant pool.
-We specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
-Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
-With this design, we again aimed at receiving 50-60 measurements per participant (\textit{M} = `r format(round(mean(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(studentSampleInfo$dailiesN), big.mark=",")`).
-As with the previous study this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
-Participants were compensated for their participation with partial course credits --- depending on their participation.
-The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(studentSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(studentSampleInfo$age),2), nsmall=2)`, `r nrow(studentSampleInfo %>% filter(gender == "women"))` women).
-The sample fairly accurately describes the local population of international students.
-
-\subsubsection{Procedure} The study procedure mirrored the setup of Study 1 and consisted of pre-, experience sampling-, and post-measurements.
-The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median survey duration} = `r seconds_to_period(median(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily))) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily)))) %>% as.character`).
-General compliance was high (`r format(round(sum(studentSampleInfo$dailiesN)/(nrow(studentSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in).
-The response rates were approximately equal during mornings (\textit{n} = `r format(sum(studentSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(studentSampleInfo$afternoonN), big.mark=",")`).
-All key variables for this study were part of the short experience sampling surveys.
-
 \subsubsection{Materials}
 
-\paragraph{Intergroup Contact}To measure intergroup contacts, every experience sampling measurement started with the question “\textit{Did you meet a Dutch person this morning [/afternoon]?
-(in-person interaction for at least 10 minutes)}”.
-Participants were additionally offered a pop-up explanation: "With in-person interaction, we mean a continued interaction with another person (potentially in a group) that lasted at least 10 minutes.
-This interaction should be offline and face-to-face.
-It should include some form of verbal communication and should be uninterrupted to still count as the same interaction.
-Any individual interaction can last minutes or hours.
-If there were multiple interaction partners, we would like you to focus on the person that was most important to you during the interaction.".
-The participants recorded between `r dtStudentSupp$studentContactFreq$SumContactNL[dtStudentSupp$studentContactFreq$SumContactNL > 0] %>% min`--`r dtStudentSupp$studentContactFreq$SumContactNL %>% max`
-interactions with Dutch majority people (`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtStudentSupp$studentContactFreq$SumContactNL), big.mark=",")` of all `r format(nrow(dtStudentSupp$studentInteractionType), big.mark=",")` experience sampling responses).
-
-\paragraph{Psychological Needs}For the core situational need, we asked participants in an open ended text field: “\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}” (where \textit{-X-} was dynamically replaced with the name of the interaction partner).
-Participants could additionally click on a pop-up explanation: "Your main goal during an interaction can vary depending on the interaction.
-It could be to connect with friends, to find or provide help, to achieve academic ambitions, work on your fitness, work for a job, or simply to get a coffee, just as well as many other concrete or abstract goals that are import to you in the moment.
-It really depends on your subjective experience of the interaction.".
-Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{During your interaction with -X- [this morning / this evening] your goal (-previous text entry-) was fulfilled.}” on a continuous slider scale ranging from strongly disagree (1) to strongly agree (100).
-
-The measurement of the self-determination needs was identical to Study 1.
-
-\paragraph{Perceived Interaction Quality}The ratings of the perceived contact quality was identical to Study 1.
-
-\paragraph{Outgroup Attitudes}As in Study 1, attitudes towards the Dutch majority outgroup were again measured using the feeling thermometer.
-All survey details are also available in our OSF repository \citep{KreienkampMasked2022a} and Online Supplemental Materials A.
+\paragraph{General Psychological Needs} The measurement of the self-determination needs was identical to Study 1.
 
 \subsection{Results}
-
-```{r studentFreqAttCor, include=FALSE}
-
-dtStudentSupp$studentContactFreq <-
-  dtStudentSupp$studentContactFreq %>%
-  mutate(
-    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
-    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
-    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
-    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
-  )
-
-# correlation panel
-pairs.panels.new(
-  dtStudentSupp$studentContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
-    "Sum:\nNumber of Outgroup Contacts (NL)",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-
-# correlation panel with interaction sums winsorized
-pairs.panels.new(
-  dtStudentSupp$studentContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
-    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-```
-
 ```{r studentModelOlsAttFreqQual, include=FALSE}
@@
 mdlStudent <- list()
-
-# regression
-mdlStudent$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtStudentSupp$studentContactFreq)
-
-summ(
-  mdlStudent$lmAttFreqQualX,
-  confint = TRUE,
-  digits = 3
-)
-
-mdlStudent$lmAttFreqQualXEta <-
-  effectsize::eta_squared(mdlStudent$lmAttFreqQualX, partial = TRUE)
-
-interactions::interact_plot(
-  mdlStudent$lmAttFreqQualX,
-  pred = SumContactNL_c,
-  modx = AvQuality_c,
-  interval = TRUE,
-  partial.residuals = TRUE
-)
-
-interactions::johnson_neyman(mdlStudent$lmAttFreqQualX,
-                             pred = SumContactNL_c,
-                             modx = AvQuality_c,
-                             alpha = .05)
 ```
@@
 ```
-```{r studentModelInterceptAttType, include = FALSE}
-# Create and save Model
-mdlStudent$lmeInterceptAttType <-
-  lme(
-    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
-    random =  ~ 1 | PID,
-    data = dtStudentSupp$studentInteractionType
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudent$lmerInterceptAttType <- lmer(
-    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM + (1 | PID),
-    data = dtStudentSupp$studentInteractionType
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudent$lmerInterceptAttTypeCI <- 
-  confint(method = "Wald", mdlStudent$lmerInterceptAttType)
-
-# Compare new model to previous step
-anova(mdlStudent$lmeAttNull, 
-      mdlStudent$lmeInterceptAttType) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudent$varInterceptAttType <- 
-  lme4::VarCorr(mdlStudent$lmeInterceptAttType)
-```
-```{r studentModelSlopesInteractionType, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudent$lmeSlopesAttType <- lme(
-  AttitudesDutch ~
-    OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
-  random = ~ 1 + OutgroupInteractionC + NonOutgroupInteractionC | PID,
-  control = lmeControl(opt = "optim"),
-  data = dtStudentSupp$studentInteractionType
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudent$lmerSlopesAttType <- lmer(
-    AttitudesDutch ~
-      OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM +
-      (1 + OutgroupInteractionC + NonOutgroupInteractionC | PID),
-    data = dtStudentSupp$studentInteractionType
-  ), 
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudent$lmerSlopesAttTypeCI <- 
-  confint(method = "Wald", mdlStudent$lmerSlopesAttType)
-
-# Compare new model to previous step
-anova(mdlStudent$lmeAttNull,
-      mdlStudent$lmeInterceptAttType, 
-      mdlStudent$lmeSlopesAttType) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudent$varSlopesAttType <- 
-  lme4::VarCorr(mdlStudent$lmeSlopesAttType)
-
-# Assumption Checks:
-mdlStudent$diagSlopesAttType <-
-  sjPlot::plot_model(mdlStudent$lmerSlopesAttType, type = "diag")
-grid.arrange(
-  mdlStudent$diagSlopesAttType[[1]],
-  mdlStudent$diagSlopesAttType[[2]]$`PID`,
-  mdlStudent$diagSlopesAttType[[3]],
-  mdlStudent$diagSlopesAttType[[4]]
-)
-
-# Plot prediction model
-mdlStudent$predSlopesAttType <- 
-  dtStudentSupp$studentInteractionType %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudent$lmeSlopesAttType,
-                           dtStudentSupp$studentInteractionType,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudent$predPltSlopesAttType <-
-    ggplot(data = mdlStudent$predSlopesAttType %>% filter(PID %in% dtStudentSupp$studentPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Student_PredictionPlot_SlopesAttType.png",
-  mdlStudent$predPltSlopesAttType,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-\subsubsection{Contact Hypothesis}
-<!-- We tested the most general contact hypothesis as in Study 1.
-We found a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-However, we found no significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblLong} and Figure \ref{fig:ContactHypothesis}).
--->
-We tested the most general contact hypothesis as we did for Study 1.
-We, again, used a multilevel regression analysis to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently).
-We again added the participant means back into the model.
-Because these are the means of the contact dummy variables they are the proportion of measurements that included a particular contact.
-This not only adjusts the model for unequal cell sizes but allows us to see whether between subject differences in the relative number of interactions had an effect on outgroup attitudes.
-We find that in this data set participant-level outgroup contact proportions were also a positive predictor of outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionM")`).
-The relative number of non-outgroup interactions showed no such effect (for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, as well as Online Supplementary Material A).
-Thus, in our second data set we find that outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
-
-\subsubsection{Core Need}
+
 ```{r studentOutModelMLAttNull, include=FALSE}
@@
 ```
-```{r studentOutModelInterceptAttCore, include=FALSE}
-# Create and save Model
-mdlStudentOut$Att$lmeInterceptCore <-
-  lme(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc,
-    random = ~ 1 | PID,
-    data = dtStudentSupp$studentOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudentOut$Att$lmerInterceptCore <-
-    lmer(
-      AttitudesDutch ~ KeyNeedFullfillment_cwc + (1 | PID),
-      data = dtStudentSupp$studentOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# 95%CI
-mdlStudentOut$Att$lmerInterceptCoreCI <- 
-  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCore)
-
-# Compare new model to previous step
-anova(mdlStudentOut$Att$lmeNull, 
-      mdlStudentOut$Att$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varInterceptCore <-
-  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCore)
-```
-```{r studentOutModelSlopesAttCore, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudentOut$Att$lmeSlopesCore <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFullfillment_cwc,
-    random = ~ 1 + KeyNeedFullfillment_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtStudentSupp$studentOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Att$lmerSlopesCore <- lmer(
-    AttitudesDutch ~
-      KeyNeedFullfillment_cwc +
-      (1 + KeyNeedFullfillment_cwc | PID),
-    data = dtStudentSupp$studentOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# all variables standardized within PPT
-summ(
-  mdlStudentOut$Att$lmerSlopesCoreZ <- lmer(
-    AttitudesDutch_zwc ~
-      KeyNeedFullfillment_zwc +
-      (1 + KeyNeedFullfillment_zwc | PID),
-    data = dtStudentSupp$studentOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# standardized coefficients
-stdCoef.merMod(mdlStudentOut$Att$lmerSlopesCore)
-
-# 95%CIs
-mdlStudentOut$Att$lmerSlopesCoreCI <- 
-  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCore)
-
-# Attempts at R^2
-r2mlm::r2mlm(mdlStudentOut$Att$lmerSlopesCore, bargraph = TRUE)
-mitml::multilevelR2(mdlStudentOut$Att$lmerSlopesCore)
-performance::r2(mdlStudentOut$Att$lmerSlopesCore)
-performance::model_performance(mdlStudentOut$Att$lmerSlopesCore)
-performance::compare_performance(mdlStudentOut$Att$lmerNull, 
-                                 mdlStudentOut$Att$lmerInterceptCore, 
-                                 mdlStudentOut$Att$lmerSlopesCore)
-
-# Compare new model to previous step
-anova(mdlStudentOut$Att$lmeNull, 
-      mdlStudentOut$Att$lmeInterceptCore, 
-      mdlStudentOut$Att$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varSlopesCore <- 
-  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCore)
-
-# Assumption Checks:
-mdlStudentOut$Att$diagSlopesCore <- 
-  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCore, type = "diag")
-grid.arrange(
-  mdlStudentOut$Att$diagSlopesCore[[1]],
-  mdlStudentOut$Att$diagSlopesCore[[2]]$`PID`,
-  mdlStudentOut$Att$diagSlopesCore[[3]],
-  mdlStudentOut$Att$diagSlopesCore[[4]]
-)
-
-# Plot prediction model
-mdlStudentOut$Att$predSlopesCore <- 
-  dtStudentSupp$studentOutWithinBetween %>% 
-  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCore,
-                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudentOut$Att$predPltSlopesCore <-
-    ggplot(data = mdlStudentOut$Att$predSlopesCore, 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCore.png",
-  mdlStudentOut$Att$predPltSlopesCore,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
 
@@
 ```
-```{r studentOutModelInterceptQltCore, include=FALSE}
-# Create and save Model
-mdlStudentOut$Qlt$lmeInterceptCore <-
-  lme(
-    quality_overall ~ KeyNeedFullfillment_cwc,
-    random = ~ 1 | PID,
-    data = dtStudentSupp$studentOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudentOut$Qlt$lmerInterceptCore <-
-    lmer(
-      quality_overall ~ KeyNeedFullfillment_cwc + (1 | PID),
-      data = dtStudentSupp$studentOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# 95%CI
-mdlStudentOut$Qlt$lmerInterceptCoreCI <- 
-  confint(method = "Wald", mdlStudentOut$Qlt$lmerInterceptCore)
-
-# Compare new model to previous step
-anova(mdlStudentOut$Qlt$lmeNull, 
-      mdlStudentOut$Qlt$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Qlt$varInterceptCore <-
-  lme4::VarCorr(mdlStudentOut$Qlt$lmeInterceptCore)
-```
-```{r studentOutModelSlopesQltCore, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudentOut$Qlt$lmeSlopesCore <-
-  lme(
-    quality_overall ~
-      KeyNeedFullfillment_cwc,
-    random = ~ 1 + KeyNeedFullfillment_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtStudentSupp$studentOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Qlt$lmerSlopesCore <-
-    lmer(
-      quality_overall ~
-        KeyNeedFullfillment_cwc +
-        (1 + KeyNeedFullfillment_cwc | PID),
-      data = dtStudentSupp$studentOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# 95%CI
-mdlStudentOut$Qlt$lmerSlopesCoreCI <- 
-  confint(method = "Wald", mdlStudentOut$Qlt$lmerSlopesCore)
-
-# Compare new model to previous step
-anova(mdlStudentOut$Qlt$lmeNull, 
-      mdlStudentOut$Qlt$lmeInterceptCore, 
-      mdlStudentOut$Qlt$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Qlt$varSlopesCore <- 
-  lme4::VarCorr(mdlStudentOut$Qlt$lmeSlopesCore)
-
-# Assumption Checks:
-mdlStudentOut$Qlt$diagSlopesCore <-
-  sjPlot::plot_model(mdlStudentOut$Qlt$lmerSlopesCore, type = "diag")
-grid.arrange(
-  mdlStudentOut$Qlt$diagSlopesCore[[1]],
-  mdlStudentOut$Qlt$diagSlopesCore[[2]]$`PID`,
-  mdlStudentOut$Qlt$diagSlopesCore[[3]],
-  mdlStudentOut$Qlt$diagSlopesCore[[4]]
-)
-
-# Plot prediction model
-mdlStudentOut$Qlt$predSlopesCore <- 
-  dtStudentSupp$studentOutWithinBetween %>%
-  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudentOut$Qlt$lmeSlopesCore,
-                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudentOut$Qlt$predPltSlopesCore <-
-    ggplot(data = mdlStudentOut$Qlt$predSlopesCore %>% filter(PID %in% dtStudentSupp$studentOutPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/StudentOut_PredictionPlot_SlopesCore.png",
-  mdlStudentOut$Qlt$predPltSlopesCore,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-```
-```{r studentOutModelInterceptAttCoreQlt, include=FALSE}
-# Create and save Model
-mdlStudentOut$Att$lmeInterceptCoreQlt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc,
-    random = ~ 1 | PID,
-    data = dtStudentSupp$studentOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudentOut$Att$lmerInterceptCoreQlt <-
-    lmer(
-      AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc + (1 | PID),
-      data = dtStudentSupp$studentOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudentOut$Att$lmerInterceptCoreQltCI <- 
-  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCoreQlt)
-
-# Compare new model to previous step
-anova(
-  mdlStudentOut$Att$lmeNull, 
-  mdlStudentOut$Att$lmeInterceptCoreQlt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varInterceptCoreQlt <-
-  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreQlt)
-```
-```{r studentOutModelSlopesAttCoreQlt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudentOut$Att$lmeSlopesCoreQlt <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFullfillment_cwc + quality_overall_cwc,
-    random = ~ 1 + KeyNeedFullfillment_cwc + quality_overall_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtStudentSupp$studentOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Att$lmerSlopesCoreQlt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFullfillment_cwc + quality_overall_cwc +
-      (1 + KeyNeedFullfillment_cwc + quality_overall_cwc | PID),
-    data = dtStudentSupp$studentOutWithinBetween,
-    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudentOut$Att$lmerSlopesCoreQltCI <- 
-  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreQlt)
-
-# Compare new model to previous step
-anova(
-  mdlStudentOut$Att$lmeNull,
-  mdlStudentOut$Att$lmeInterceptCoreQlt,
-  mdlStudentOut$Att$lmeSlopesCoreQlt
-) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varSlopesCoreQlt <- 
-  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreQlt)
-
-# Assumption Checks:
-mdlStudentOut$Att$diagSlopesCoreQlt <- 
-  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreQlt, type = "diag")
-grid.arrange(
-  mdlStudentOut$Att$diagSlopesCoreQlt[[1]],
-  mdlStudentOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
-  mdlStudentOut$Att$diagSlopesCoreQlt[[3]],
-  mdlStudentOut$Att$diagSlopesCoreQlt[[4]]
-)
-
-# Plot prediction model
-mdlStudentOut$Att$predSlopesCoreQlt <- 
-  dtStudentSupp$studentOutWithinBetween %>% 
-  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreQlt,
-                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudentOut$Att$predPltSlopesCoreQlt <-
-    ggplot(data = mdlStudentOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreQlt.png",
-  mdlStudentOut$Att$predPltSlopesCoreQlt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is subsumed by the perceived interaction quality if considered jointly.
-We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`).
-Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment} for full results).
-These results are consistent with the results in Study 1.
-We, thus, find support for our hypotheses that the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
-
-<!-- \faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?  -->
 
@@
 
-We again checked for alternative models.
+Also for Study 2, we checked for alternative models.
 First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is only a minuscule main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc:OutgroupInteraction")`).
@@
 \section{Study 3}
-
-The aim of this final study is to extend the previous studies by additionally testing Allport's conditions in an extensive longitudinal design and to compare the predictive powers of Allport's conditions and the core situational need fulfillment.
-We will, thus, again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
-However, we additionally have the opportunity to also assess the role of Allport's conditions in this and to compare the two approaches (Allport's conditions and core need fulfillment) directly.
-
-For this study, we specifically recruited international medical students, because they represent a particular group of migrants who face structural requirements to integrate and interact with Dutch majority outgroup members on a daily basis.
-As part of their educational program, the migrants are required to take language courses and interact with patients as part of their medical internships and medical residency.
-The extensive longitudinal survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations.
-Data were collected from November 8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020.
-
-The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
-Correlations and descriptive statistics of the included variables are available in Tables \ref{tab:descrFullWide} and \ref{tab:descrOutWide}.
 
@@
 
-# look at frequencies of characteristics 
-table(medicalSampleInfo$age)
-table(medicalSampleInfo$gender)
-table(as.character(medicalSampleInfo$nationality))
-
 # divide into trait and state
@@
 
-```{r medicalVarDescr, include=FALSE}
-medicalMlCor <-
-  MlCorMat(
-    data = dtMedical$full,
-    id = "PID",
-    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
-  )
-
-medicalMlCor %>%
-  kable(
-    .,
-    caption = "Medical: Multilevel Core Variable Descriptives",
-    format = "latex",
-    booktabs = TRUE,
-    linesep = linesep(c(ncol(.))),
-    align = c("l", rep("c", ncol(.) - 1))
-  ) %>%
-  footnote(
-    general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
-      "*** p < .001, ** p < .01,  * p < .05"
-    )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/medicalVarDescr.tex")
-```
-
-```{r medicalOutVarDescr, include=FALSE}
-medicalOutMlCor <-
-  MlCorMat(
-    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
-    id = "PID",
-    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
-  )
-
-medicalOutMlCor %>%
-  kable(
-    .,
-    caption = "Medical: Multilevel Core Variable Descriptives (Outgroup Contact Only)",
-    format = "latex",
-    booktabs = TRUE,
-    linesep = linesep(c(ncol(.))),
-    align = c("l", rep("c", ncol(.) - 1))
-  ) %>%
-  footnote(
-    general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
-      "*** p < .001, ** p < .01,  * p < .05"
-    )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/medicalOutVarDescr.tex")
-
-# misty::multilevel.descript(dtStudentsSupp$studentWithinBetween$keyMotiveFulfilled, cluster = dtStudentsSupp$studentWithinBetween$PID)
-```
-
-\subsubsection{Participants} We recruited `r nrow(medicalSampleInfo)` international medical students using contacts within the University Medical School.
-We specifically targeted non-Dutch students, who had recently arrived in the Netherlands.
-Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
-With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(medicalSampleInfo$dailiesN), big.mark=",")`).
-As with the previous studies, this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
-Participants were compensated for their participation in the same manner as during Study 1.
-The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(medicalSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(medicalSampleInfo$age),2), nsmall=2)`, `r nrow(medicalSampleInfo %>% filter(gender == "women"))` women).
-The sample fairly accurately describes the local population of young international medical professionals.
-
-\subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, experience sampling-, and post-measurement.
-The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median survey duration} = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).
-General compliance was high (`r format(round(table(medicalSampleInfo$dailiesN>30)["TRUE"]/nrow(medicalSampleInfo)*100,2), nsmall=2)`\% filled in at least 31 experience sampling surveys or more).
-The response rates were approximately equal during mornings (\textit{n} = `r format(sum(medicalSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(medicalSampleInfo$afternoonN), big.mark=",")`).
-All key variables for this study were part of the short experience sampling surveys.
-
 \subsubsection{Materials}
 
-\paragraph{Intergroup Contact}The measurement of intergroup contacts was identical to Study 2.
-The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
-(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtMedicalSupp$medicalContactFreq$SumContactNL), big.mark=",")` of all `r format(nrow(dtMedical$full), big.mark=",")` experience sampling responses).
-
-\paragraph{Psychological Needs}The measurement of the core situational need and its fulfillment was identical to Study 2.
-Similarly, the measurement of the self-determination needs was identical to Studies 1 and 2
-
-\paragraph{Allport's Conditions}We measured how much each of the interactions fulfilled Allport's conditions of optimal contact using a common short scale comprised of four attributes \citep{Islam1993, Voci2003, AlRamiah2012a, Dixon2005}.
-In particular, we asked participants to rate how much the interaction had equal status ("\textit{The interaction with [name interaction partner] was on equal footing (same status)}"), a common goal ("\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}"), support of authorities ("\textit{The interaction with [name interaction partner] was voluntary}"), and intergroup cooperation ("\textit{The interaction with [name interaction partner] was cooperative}").
-We create a mean-averaged index of Allport's conditions in response to past findings indicating that the conditions are best conceptualized jointly and as functioning together rather than as fully independent factors \citep[][, p.
-766]{Pettigrew2006}.
-For full psychometric information see Online Supplementary Material A.
-
-\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to Study 1.
-
-\paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup was again measured using the feeling thermometer, as in studies one and two.
-All survey details are also available in our OSF repository \citep{KreienkampMasked2022a} and Online Supplemental Materials A.
+\paragraph{General Psychological Needs} The measurement of the self-determination needs was identical to Studies 1 and 2.
 
 \subsection{Results}
-
-```{r medicalFreqAttCor, include=FALSE}
-dtMedicalSupp$medicalContactFreq <-
-  dtMedicalSupp$medicalContactFreq %>%
-  mutate(
-    SumContactNL_c = SumContactNL - mean(SumContactNL, na.rm = TRUE),
-    SumContactNLAll_c = SumContactNLAll - mean(SumContactNLAll, na.rm = TRUE),
-    AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
-    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
-  )
-
-# correlation panel
-pairs.panels.new(
-  dtMedicalSupp$medicalContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)",
-    "Sum:\nNumber of Outgroup Contacts (NL)",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-
-# correlation panel with interaction sums winsorized
-pairs.panels.new(
-  dtMedicalSupp$medicalContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
-  labels = c(
-    "Sum:\nNumer of beeps with Outgroup Contact (NL)\n[Winsorized]",
-    "Sum:\nNumber of Outgroup Contacts (NL)\n[Winsorized]",
-    "Mean:\nInteraction Quality",
-    "Mean:\nOutgroup Attitudes (NL)"
-  )
-)
-```
 
@@
 mdlMedical <- list()
-
-# regression
-mdlMedical$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)
-
-summ(
-  mdlMedical$lmAttFreqQualX,
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedical$lmAttFreqQualXEta <-
-  effectsize::eta_squared(mdlMedical$lmAttFreqQualX, partial = TRUE)
-
-interactions::interact_plot(
-  mdlMedical$lmAttFreqQualX,
-  pred = SumContactNL_c,
-  modx = AvQuality_c,
-  interval = TRUE,
-  partial.residuals = TRUE
-)
-
-interactions::johnson_neyman(mdlMedical$lmAttFreqQualX,
-                             pred = SumContactNL_c,
-                             modx = AvQuality_c,
-                             alpha = .05)
 ```
@@
 
-```{r medicalModelInterceptAttType, include = FALSE}
-# Create and save Model
-mdlMedical$lmeInterceptAttType <-
-  lme(
-    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
-    random =  ~ 1 | PID,
-    na.action=na.omit,
-    data = dtMedical$full
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedical$lmerInterceptAttType <- lmer(
-    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM + (1 | PID),
-    data = dtMedical$full
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedical$lmerInterceptAttTypeCI <- 
-  confint(method = "Wald", mdlMedical$lmerInterceptAttType)
-
-# Compare new model to previous step
-anova(mdlMedical$lmeAttNullType, 
-      mdlMedical$lmeInterceptAttType) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedical$varInterceptAttType <- 
-  lme4::VarCorr(mdlMedical$lmeInterceptAttType)
-```
-
-```{r medicalModelSlopesInteractionType, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedical$lmeSlopesAttType <- lme(
-  AttitudesDutch ~
-    OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM,
-  random = ~ 1 + OutgroupInteractionC + NonOutgroupInteractionC | PID,
-  control = lmeControl(opt = "optim"),
-  na.action = na.omit,
-  data = dtMedical$full
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedical$lmerSlopesAttType <- lmer(
-    AttitudesDutch ~
-      OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM +
-      (1 + OutgroupInteractionC + NonOutgroupInteractionC | PID),
-    data = dtMedical$full
-  ), 
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedical$lmerSlopesAttTypeCI <- 
-  confint(method = "Wald", mdlMedical$lmerSlopesAttType)
-
-# Compare new model to previous step
-anova(mdlMedical$lmeAttNullType,
-      mdlMedical$lmeInterceptAttType, 
-      mdlMedical$lmeSlopesAttType) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedical$varSlopesAttType <- 
-  lme4::VarCorr(mdlMedical$lmeSlopesAttType)
-
-# Assumption Checks:
-mdlMedical$diagSlopesAttType <-
-  sjPlot::plot_model(mdlMedical$lmerSlopesAttType, type = "diag")
-grid.arrange(
-  mdlMedical$diagSlopesAttType[[1]],
-  mdlMedical$diagSlopesAttType[[2]]$`PID`,
-  mdlMedical$diagSlopesAttType[[3]],
-  mdlMedical$diagSlopesAttType[[4]]
-)
-
-# Plot prediction model
-mdlMedical$predSlopesAttType <-
-  dtMedical$full %>%
-  filter(complete.cases(OutgroupInteraction, NonOutgroupInteraction)) %>%
-  select(AttitudesDutch, TIDnum, PID) %>%
-  mutate(measure = predict(
-    mdlMedical$lmeSlopesAttType,
-    dtMedical$full %>%
-      filter(complete.cases(
-        OutgroupInteraction, NonOutgroupInteraction
-      )),
-    re.form = NA
-  ))
-
-(
-  mdlMedical$predPltSlopesAttType <-
-    ggplot(data = mdlMedical$predSlopesAttType %>% filter(PID %in% dtMedicalSupp$medicalPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Medical_PredictionPlot_SlopesAttType.png",
-  mdlMedical$predPltSlopesAttType,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-\subsubsection{Contact Hypothesis}
-<!-- As in Studies 1 and 2, we first conducted a general contact hypothesis test.
-We found no correlation between the overall number of intergroup contacts and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (|\textit{r}| < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-However, we did find a significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-When considering the number of interactions and average interaction quality jointly in a linear regression, we only found a main effect of average perceived interaction quality on outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of the number of contacts nor an interaction effect.
-This result mirrors that of Study 1 but is inconsistent with the second study.
--->
-Additionally, in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A).
-Thus, in our third data set we found within person contemporaneous effect of intergroup contact was consistent across all three studies.
-
-\subsubsection{Core Need}
-
 ```{r medicalOutModelMLAttNull, include=FALSE}
@@
 
-```{r medicalOutModelInterceptAttCore, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptCore <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptCore <-
-    lmer(
-      AttitudesDutch ~ KeyNeedFulfillment_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlMedicalOut$Att$lmerInterceptCoreCI <-
-  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCore)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeNull,
-      mdlMedicalOut$Att$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptCore <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCore)
-```
-
-```{r medicalOutModelSlopesAttCore, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesCore <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesCore <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc +
-      (1 + KeyNeedFulfillment_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# all variables standardized within PPT
-summ(
-  mdlMedicalOut$Att$lmerSlopesCoreZ <- lmer(
-    AttitudesDutch_zwc ~
-      KeyNeedFulfillment_zwc +
-      (1 + KeyNeedFulfillment_zwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# standardized coefficients
-stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesCore)
-
-# 95%CIs
-mdlMedicalOut$Att$lmerSlopesCoreCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCore)
-
-# Attempts at R^2
-r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesCore, bargraph = TRUE)
-mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesCore)
-performance::r2(mdlMedicalOut$Att$lmerSlopesCore)
-performance::model_performance(mdlMedicalOut$Att$lmerSlopesCore)
-performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
-                                 mdlMedicalOut$Att$lmerInterceptCore, 
-                                 mdlMedicalOut$Att$lmerSlopesCore)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeNull, 
-      mdlMedicalOut$Att$lmeInterceptCore, 
-      mdlMedicalOut$Att$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesCore <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCore)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesCore <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCore, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesCore[[1]],
-  mdlMedicalOut$Att$diagSlopesCore[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesCore[[3]],
-  mdlMedicalOut$Att$diagSlopesCore[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesCore <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(complete.cases(KeyNeedFulfillment)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCore,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(KeyNeedFulfillment)) %>% 
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesCore <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesCore, 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCore.png",
-  mdlMedicalOut$Att$predPltSlopesCore,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-```{r medicalOutModelInterceptQltCore, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Qlt$lmeInterceptCore <-
-  lme(
-    qualityOverall ~ KeyNeedFulfillment_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Qlt$lmerInterceptCore <-
-    lmer(
-      qualityOverall ~ KeyNeedFulfillment_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlMedicalOut$Qlt$lmerInterceptCoreCI <- 
-  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptCore)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Qlt$lmeNull, 
-      mdlMedicalOut$Qlt$lmeInterceptCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Qlt$varInterceptCore <-
-  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptCore)
-```
-
-```{r medicalOutModelSlopesQltCore, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Qlt$lmeSlopesCore <-
-  lme(
-    qualityOverall ~
-      KeyNeedFulfillment_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Qlt$lmerSlopesCore <-
-    lmer(
-      qualityOverall ~
-        KeyNeedFulfillment_cwc +
-        (1 + KeyNeedFulfillment_cwc | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlMedicalOut$Qlt$lmerSlopesCoreCI <- 
-  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesCore)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Qlt$lmeNull, 
-      mdlMedicalOut$Qlt$lmeInterceptCore, 
-      mdlMedicalOut$Qlt$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Qlt$varSlopesCore <- 
-  lme4::VarCorr(mdlMedicalOut$Qlt$lmeSlopesCore)
-
-# Assumption Checks:
-mdlMedicalOut$Qlt$diagSlopesCore <-
-  sjPlot::plot_model(mdlMedicalOut$Qlt$lmerSlopesCore, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Qlt$diagSlopesCore[[1]],
-  mdlMedicalOut$Qlt$diagSlopesCore[[2]]$`PID`,
-  mdlMedicalOut$Qlt$diagSlopesCore[[3]],
-  mdlMedicalOut$Qlt$diagSlopesCore[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Qlt$predSlopesCore <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
-  filter(complete.cases(KeyNeedFulfillment)) %>% 
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesCore,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(KeyNeedFulfillment)) %>% 
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Qlt$predPltSlopesCore <-
-    ggplot(data = mdlMedicalOut$Qlt$predSlopesCore %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesCore.png",
-  mdlMedicalOut$Qlt$predPltSlopesCore,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-```
-
-```{r medicalOutModelInterceptAttCoreQlt, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptCoreQlt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptCoreQlt <-
-    lmer(
-      AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerInterceptCoreQltCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCoreQlt)
-
-# Compare new model to previous step
-anova(
-  mdlMedicalOut$Att$lmeNull, 
-  mdlMedicalOut$Att$lmeInterceptCoreQlt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptCoreQlt <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreQlt)
-```
-
-```{r medicalOutModelSlopesAttCoreQlt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesCoreQlt <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + qualityOverall_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesCoreQlt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + qualityOverall_cwc +
-      (1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerSlopesCoreQltCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreQlt)
-
-# Compare new model to previous step
-anova(
-  mdlMedicalOut$Att$lmeNull,
-  mdlMedicalOut$Att$lmeInterceptCoreQlt,
-  mdlMedicalOut$Att$lmeSlopesCoreQlt
-) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesCoreQlt <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreQlt)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesCoreQlt <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreQlt, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[1]],
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[3]],
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesCoreQlt <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreQlt,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesCoreQlt <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreQlt.png",
-  mdlMedicalOut$Att$predPltSlopesCoreQlt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-Similarly to the previous studies, we again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
-We find that the fulfillment of the core need during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
-Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
-These results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and this effect partially emerged via its effect on perceived interaction quality.
-
-<!-- \faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?  -->
-
-\subsubsection{Allport's Conditions}
-
-```{r medicalOutModelInterceptAttAllport, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptAllport <-
-  lme(
-    AttitudesDutch ~ AllportsCondition_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptAllport <-
-    lmer(
-      AttitudesDutch ~ AllportsCondition_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlMedicalOut$Att$lmerInterceptAllportCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllport)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeNull, 
-      mdlMedicalOut$Att$lmeInterceptAllport) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptAllport <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllport)
-```
-
-```{r medicalOutModelSlopesAttAllport, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesAllport <-
-  lme(
-    AttitudesDutch ~
-      AllportsCondition_cwc,
-    random = ~ 1 + AllportsCondition_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesAllport <- lmer(
-    AttitudesDutch ~
-      AllportsCondition_cwc +
-      (1 + AllportsCondition_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# all variables standardized within PPT
-summ(
-  mdlMedicalOut$Att$lmerSlopesAllportZ <- lmer(
-    AttitudesDutch_zwc ~
-      AllportsCondition_zwc +
-      (1 + AllportsCondition_zwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-# standardized coefficients
-stdCoef.merMod(mdlMedicalOut$Att$lmerSlopesAllport)
-
-# 95%CIs
-mdlMedicalOut$Att$lmerSlopesAllportCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllport)
-
-# Attempts at R^2
-#r2mlm::r2mlm(mdlMedicalOut$Att$lmerSlopesAllport, bargraph = TRUE)
-mitml::multilevelR2(mdlMedicalOut$Att$lmerSlopesAllport)
-performance::r2(mdlMedicalOut$Att$lmerSlopesAllport)
-performance::model_performance(mdlMedicalOut$Att$lmerSlopesAllport)
-performance::compare_performance(mdlMedicalOut$Att$lmerNull, 
-                                 mdlMedicalOut$Att$lmerInterceptAllport, 
-                                 mdlMedicalOut$Att$lmerSlopesAllport)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeNull, 
-      mdlMedicalOut$Att$lmeInterceptAllport, 
-      mdlMedicalOut$Att$lmeSlopesAllport) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesAllport <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesAllport)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesAllport <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesAllport, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesAllport[[1]],
-  mdlMedicalOut$Att$diagSlopesAllport[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesAllport[[3]],
-  mdlMedicalOut$Att$diagSlopesAllport[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesAllport <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllport,
-                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesAllport <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesAllport, 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllport.png",
-  mdlMedicalOut$Att$predPltSlopesAllport,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-```{r medicalOutModelInterceptQltAllport, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Qlt$lmeInterceptAllport <-
-  lme(
-    qualityOverall ~ AllportsCondition_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Qlt$lmerInterceptAllport <-
-    lmer(
-      qualityOverall ~ AllportsCondition_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlMedicalOut$Qlt$lmerInterceptAllportCI <- 
-  confint(method = "Wald", mdlMedicalOut$Qlt$lmerInterceptAllport)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Qlt$lmeNull, 
-      mdlMedicalOut$Qlt$lmeInterceptAllport) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Qlt$varInterceptAllport <-
-  lme4::VarCorr(mdlMedicalOut$Qlt$lmeInterceptAllport)
-```
-
-```{r medicalOutModelSlopesQltAllport, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Qlt$lmeSlopesAllport <-
-  lme(
-    qualityOverall ~
-      AllportsCondition_cwc,
-    random = ~ 1 + AllportsCondition_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Qlt$lmerSlopesAllport <-
-    lmer(
-      qualityOverall ~
-        AllportsCondition_cwc +
-        (1 + AllportsCondition_cwc | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3,
-  center = FALSE
-)
-
-mdlMedicalOut$Qlt$lmerSlopesAllportCI <- 
-  confint(method = "Wald", mdlMedicalOut$Qlt$lmerSlopesAllport)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Qlt$lmeNull, 
-      mdlMedicalOut$Qlt$lmeInterceptAllport, 
-      mdlMedicalOut$Qlt$lmeSlopesAllport) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Qlt$varSlopesAllport <- 
-  lme4::VarCorr(mdlMedicalOut$Qlt$lmeSlopesAllport)
-
-# Assumption Checks:
-mdlMedicalOut$Qlt$diagSlopesAllport <-
-  sjPlot::plot_model(mdlMedicalOut$Qlt$lmerSlopesAllport, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Qlt$diagSlopesAllport[[1]],
-  mdlMedicalOut$Qlt$diagSlopesAllport[[2]]$`PID`,
-  mdlMedicalOut$Qlt$diagSlopesAllport[[3]],
-  mdlMedicalOut$Qlt$diagSlopesAllport[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Qlt$predSlopesAllport <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Qlt$lmeSlopesAllport,
-                           dtMedicalSupp$medicalOutWithinBetween %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Qlt$predPltSlopesAllport <-
-    ggplot(data = mdlMedicalOut$Qlt$predSlopesAllport %>% filter(PID %in% dtMedicalSupp$medicalOutPltIDs), 
-           aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAllport.png",
-  mdlMedicalOut$Qlt$predPltSlopesAllport,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-```
-
-```{r medicalOutModelInterceptAttAllportQlt, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptAllportQlt <-
-  lme(
-    AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptAllportQlt <-
-    lmer(
-      AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerInterceptAllportQltCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptAllportQlt)
-
-# Compare new model to previous step
-anova(
-  mdlMedicalOut$Att$lmeNull, 
-  mdlMedicalOut$Att$lmeInterceptAllportQlt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptAllportQlt <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptAllportQlt)
-```
-
-```{r medicalOutModelSlopesAttAllportQlt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesAllportQlt <-
-  lme(
-    AttitudesDutch ~
-      AllportsCondition_cwc + qualityOverall_cwc,
-    random = ~ 1 + AllportsCondition_cwc + qualityOverall_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesAllportQlt <- lmer(
-    AttitudesDutch ~
-      AllportsCondition_cwc + qualityOverall_cwc +
-      (1 + AllportsCondition_cwc + qualityOverall_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerSlopesAllportQltCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesAllportQlt)
-
-# Compare new model to previous step
-anova(
-  mdlMedicalOut$Att$lmeNull,
-  mdlMedicalOut$Att$lmeInterceptAllportQlt,
-  mdlMedicalOut$Att$lmeSlopesAllportQlt
-) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesAllportQlt <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesAllportQlt)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesAllportQlt <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesAllportQlt, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesAllportQlt[[1]],
-  mdlMedicalOut$Att$diagSlopesAllportQlt[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesAllportQlt[[3]],
-  mdlMedicalOut$Att$diagSlopesAllportQlt[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesAllportQlt <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(complete.cases(AllportsCondition, qualityOverall)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesAllportQlt,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(AllportsCondition, qualityOverall)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesAllportQlt <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesAllportQlt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttAllportQlt.png",
-  mdlMedicalOut$Att$predPltSlopesAllportQlt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-As we did with core need fulfillment, we sequentially tested whether the fulfillment of Allport's contact conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly.
-In the multilevel models we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
-Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
-These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.
-
-<!-- \faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?  -->
-
-\subsubsection{Compare Fulfillment of Core Need and Allport's Conditions}
-
-```{r AllportVsCore, include=FALSE}
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeSlopesAllport, 
-      mdlMedicalOut$Att$lmeSlopesCore) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  kbl(
-    .,
-    caption = "Medical: Comparison of Allport's Conditions to Core Situational Need",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-AIC(
-  mdlMedicalOut$Att$lmerSlopesAllport,
-  mdlMedicalOut$Att$lmerSlopesCore
-)
-
-BIC(
-  mdlMedicalOut$Att$lmerSlopesAllport,
-  mdlMedicalOut$Att$lmerSlopesCore
-)
-
-performance::compare_performance(
-  mdlMedicalOut$Att$lmerSlopesAllport,
-  mdlMedicalOut$Att$lmerSlopesCore
-)
-```
-
-```{r medicalOutModelInterceptAttCoreAllport, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptCoreAllport <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptCoreAllport <-
-    lmer(
-      AttitudesDutch ~ KeyNeedFulfillment_cwc + AllportsCondition_cwc + (1 | PID),
-      data = dtMedicalSupp$medicalOutWithinBetween
-    ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerInterceptCoreAllportCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerInterceptCoreAllport)
-
-# Compare new model to previous step
-anova(
-  mdlMedicalOut$Att$lmeNull, 
-  mdlMedicalOut$Att$lmeInterceptAllport,
-  mdlMedicalOut$Att$lmeInterceptCoreAllport
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptCoreAllport <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreAllport)
-```
-
-```{r medicalOutModelSlopesAttCoreAllport, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesCoreAllport <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + AllportsCondition_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID,
-    na.action = na.omit,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesCoreAllport <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + AllportsCondition_cwc +
-      (1 + KeyNeedFulfillment_cwc + AllportsCondition_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerSlopesCoreAllportCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreAllport)
-
-# Compare new model to previous step
-anova(
-  mdlMedicalOut$Att$lmeNull,
-  mdlMedicalOut$Att$lmeInterceptCoreAllport,
-  mdlMedicalOut$Att$lmeSlopesCoreAllport
-) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesCoreAllport <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreAllport)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesCoreAllport <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreAllport, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[1]],
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[3]],
-  mdlMedicalOut$Att$diagSlopesCoreQlt[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesCoreAllport <- 
-  dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreAllport,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(KeyNeedFulfillment, AllportsCondition)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesCoreAllport <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesCoreQlt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreAllport.png",
-  mdlMedicalOut$Att$predPltSlopesCoreAllport,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-To test wether Allport's conditions or the core need fulfillment are better at predicting outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
-When comparing the model selection indices, we find that the fulfillment of the situational core need indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
-Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
-This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
-
 \subsubsection{Robustness}
@@
 ```
+
 ```{r medicalModelSlopesAttCoreIntX, include=FALSE}
@@
 
-We again checked for alternative models of the key need fulfillment.
+As with the previous two studies, we checked for alternative models of the key need fulfillment.
 First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
@@
 
-\section{Embeddedness and Stability across Studies}
-
-\begin{center}
-    \noindent\rule{8cm}{0.4pt}\\
-    \hl{\textit{New Section:}}\\
-    \vspace{-0.25cm}
-    \noindent\rule{8cm}{0.4pt}
-\end{center}
-
-Beyond the individual results of the three studies, we conducted three additional analyses to test the broader cross-study claims and contextualize our results.
-In particular, we aim to gain a broader picture of the individual results by considering them jointly, and we leverage the data from all participants to test between-participant contact effects and explore the content of the participants' situational contact needs.
-
-\subsection{Stability}
-We begin by assessing the stability of our main analyses across the three studies.
-To do so, we plot the effect sizes of each parameter of interest in a forest plot.
-Forest plots are a popular form of evidence synthesis and are commonly found within meta-analytic efforts.
-By plotting a standardized effect size and confidence interval of key parameters for each study, forest plots offer a visual method of identifying broader patterns across studies.
-This affords us a chance to spot stable as well as unreliable effects more easily.
-While not the focus of our efforts here, forest plots are commonly accompanied with a meta-analytic effect size that summarizes the effect size across studies.
-
-We assess forest plots of the basic contact hypothesis test (Figure \ref{fig:ContactHypothesis}), the core need fulfillment proposal (Figure \ref{fig:AllportNeedFulfillment}), as well as the robustness analyses (Figure \ref{fig:Robustness}).
-For the basic contact hypothesis test we see that outgroup contact has a strong and consistent effect on outgroup attitudes while interactions with non-outgroup members consistently have no meaningful effect on outgroup attitudes.
-While this would be expected from the general intergroup contact literature, this is not a trivial finding.
-We are among the first to assess the contact hypothesis using real-life intensive longitudinal data and these close to event assessments are comparable but not equivalent to the assessments found in cross-sectional data (also see below).
-When looking at Figure \ref{fig:AllportNeedFulfillment}, we see that the fulfillment of core needs during intergroup contacts is consistently a meaningful predictor of outgroup attitudes and interaction quality perceptions (see Figure \ref{fig:AllportNeedFulfillment} A and B).
-We also see that the effect of core need fulfillment on outgroup attitudes is strongly reduced when modeled together with interaction quality perceptions, supporting our assertion that interaction quality offers a psychological mechanism for the direct effect.
-Additionally, the core need fulfillment is also consistently outgroup contact specific (Figure \ref{fig:Robustness} A) and remains a meaningful predictor of outgroup attitudes even when controlling for traditional psychological need fulfillments (Figure \ref{fig:Robustness} B).
-
-\subsection{General contact hypothesis}
-
-```{r join data sets for analysis, include=FALSE}
-# Join aggregated data
-avS1 <- dtWorkerSupp$workerAvFreQual %>%
-  select(
-    -ExternalReference
-  ) %>%
-  mutate(
-    PID = c(1:nrow(.)),
-    study = "S1"
-  ) %>%
-  select(PID, everything())
-avS2 <- dtStudentSupp$studentContactFreq %>%
-  mutate(
-    study = "S2"
-  )
-avS3 <- dtMedicalSupp$medicalContactFreq %>%
-  mutate(
-    study = "S3"
-  )
-
-avAll <- bind_rows(avS1, avS2, avS3) %>%
-  mutate(
-    ID = c(1:nrow(.)),
-    studyNum1 = ifelse(study == "S1", 1, 0),
-    studyNum3 = ifelse(study == "S3", 1, 0)
-  )
-avAll$study2 <- relevel(as.factor(avAll$study),"S2")
-```
-```{r OLS regression across the three studies, include=FALSE}
-lmAllAttFreqQualX <-
-  lm(
-    AvAttitude ~ SumContactNL_c * AvQualityOut_c + SumContactNL_c * study2 + AvQualityOut_c * study2,
-    data = avAll
-  )
-
-summ(
-  lmAllAttFreqQualX,
-  confint = TRUE,
-  digits = 3
-)
-
-# prepare F stat for manuscript
-fit <- summary(lmAllAttFreqQualX)
-lmAllFstatLatex <- paste(
-  "\\textit{F}(",
-  fit$fstatistic["numdf"],
-  ", ",
-  fit$fstatistic["dendf"],
-  ") = ",
-  format(round(fit$fstatistic["value"], 2), nsmall = 2),
-  ", \\textit{p} = ",
-  format(round(
-    pf(
-      fit$fstatistic["value"],
-      fit$fstatistic["numdf"],
-      fit$fstatistic["dendf"],
-      lower.tail = FALSE
-    ),
-    3
-  ), nsmall = 3),
-  ", \\textit{R\\textsuperscript{2}} = ",
-  format(round(fit$r.squared, 2), nsmall = 2),
-  sep = ""
-)
-```
-
-During the main analyses, we have thus far shown that participants held more positive outgroup attitudes following intergroup contacts and that a perceived interaction quality was associated with more positive outgroup attitudes following an intergroup contact.
-We have, however, not brought the two elements of the contact hypothesis together in a single analysis.
-This is mainly due to the difficulty that interaction quality ratings are only possible when participants had an interaction --- which means that the two factors cannot be assessed in a multilevel analysis that models individual measurement occasions.
-This has not been an issue in the past literature because experimental and cross-sectional data collections have only considered cases in which intergroup contacts were present.
-Outside of the lab, the most common method has been to ask participants to recall how many interactions they had over the past month, how positive these interactions were, and how positive they feel towards the outgroup in general.
-The effects of intergroup contacts, interaction quality, and outgroup attitudes are thus summarized by the participant in a cognitive recall aggregation.
-Intensive longitudinal data also allows for aggregation of all three variables, with the differences that the measurements are aggregated from individual reports that are close to the actual experience.
-However, this aggregation process summarizes the dense multitude of measurement occasions as single summary statistics per participants.
-This, by extension, means that we face statistical power restrictions on the person level and have thus decided to only present this analysis based on a combined data set of all three studies.
-
-We run a linear regression model where average outgroup attitudes are predicted by the number of interactions and the average interaction quality ratings of all participants across the three studies.
-We do so while controlling for the possible effects of study-specific differences.
-To include the study-membership as a control variable, we use the student sample (Study 2) as the reference group because it is both the largest and the most homogeneous study.
-Looking at the overall model, we find that the model predicts a statistically significant amount of variance in average outgroup attitudes (`r lmAllFstatLatex`).
-Looking at the individual effects, we find that only the number of outgroup interactions has a clear association with average outgroup attitudes (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "SumContactNL_c", ci = TRUE)`).
-The average interaction quality perceptions had a much smaller effect (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "AvQualityOut_c", ci = TRUE)`), and we do not find the most important interaction effect at all.
-In short, the effect of outgroup interactions did not depend on the average interaction quality, so that participants who on average had more positive interactions were not statistically more likely to show higher average outgroup attitudes than those with more negative interactions.
-This result is surprising because it contradicts the tenet of the intergroup contact hypothesis that intergroup contact depends on positive contact.
-
-\subsection{Contact key need content}
-Finally, we use the qualitative data from the participants’ self-identified core needs to contextualize the results of our main analysis.
-However, because our participants jointly reported on thousands of intergroup contacts, it would not be feasible to analyse these qualitative responses in a traditional qualitative content analysis.
-We instead rely on recent machine learning advances within the natural language processing domain.
-For our analysis we use the BERT language model.
-BERT (Bidirectional Encoder Representations from Transformers) was developed by Google in 2018 and today forms a key elements of many natural language processing workflows.
-In its essence, BERT is a framework that allows users to codify every word in relation to every other word within a large set of documents.
-This task is immensely computationally intensive and most users of the framework don't create their own model.
-We use the "all-mpnet-base-v2" language model for our embedding.
-The model is a community-based version of BERT that uses Microsoft's "mpnet-base" model and is fine-tuned with 1 Billion diverse sentence pairs.
-The model was trained with a 768 dimensional dense vector space (a relatively high number) to represent every word.
-As a result, the model is widely considered to be one of the most accurate all-purpose language models within the open-source BERT framework.
-We extracted 47 topics from the 2,983 interaction goal free-text entries --- a relatively large number of topics.
-The higher number of topics allows us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (10.33%).
-A full write up of the topic modeling process is available in Online Supplemental Material C.
-
-In terms of the content of the topics, we find that a number of topics are primarily task-oriented, where participants hope to increase their study, research, presentation, or work performance.
-Opposing the task and work oriented needs, are a wide variety of leisure-related wishes.
-Specifically, relaxation and entertainment wishes were prominent terms across several topics.
-Additionally, a number of clusters is primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself.
-Similarly, socializing and celebrations were also explicit social needs (incl., parties).
-Another set of topics was more practically oriented, when participants sought to share food and cook cook together, or had organizational needs (e.g., housing, cleaning, and living).
-
-A reasonable set of contact goals were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned inquiry and information needs more generally (e.g., seeking answers, bureaucratic information).
-A further set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel related goals in their interactions with the majority group members.
-
-One interesting observation was the importance of contact goals specific to contact through the medical and public health system.
-This goal type was partly specific to our young medical professionals sample (e.g., working with patients, treatment), but also more broadly interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals).
-Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members.
-A final topic was that of spiritual, religious, and otherwise transcendental needs (incl.
-meditation, prayer, religious services).
-
-Thus, almost all other extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}.
-
-```{r intergroupGeneralTblLong, include=FALSE}
-# Table of intergroup contact in ESM data:
-# lm
-#    #Contact
-#     AvQual
-#     #Contact*AvQual
-# lme
-#     OutgroupInteraction
-#     NonOutgroupInteraction
-
-# OLS 
-# Study 1:
-mdlWorker$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtWorkerSupp$workerAvFreQual)
-# Study 2:
-mdlStudent$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtStudentSupp$studentContactFreq)
-# Study 3: 
-mdlMedical$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)
-
-# tabModelTest <- tab_model(mdlWorker$lmAttFreqQualX,
-#                           mdlStudent$lmAttFreqQualX,
-#                           mdlMedical$lmAttFreqQualX)
-
-# summ(mdlWorker$lmAttFreqQualX)
-
-mdlTblElementsGeneralLm <- list(mdlWorker$lmAttFreqQualX,
-                                mdlStudent$lmAttFreqQualX,
-                                mdlMedical$lmAttFreqQualX)
-
-mdlPrepLmGeneral <- list()
-for (i in 1:length(mdlTblElementsGeneralLm)) {
-  mdlPrepLmGeneral[[i]] <- lmTblPrep(mdlTblElementsGeneralLm[[i]])
-}
-mdlTblGeneralLm <- data.frame(
-  coef = c(
-    sapply(mdlPrepLmGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique,
-    names(mdlPrepLmGeneral[[1]]$fit)
-  )
-)
-for (i in 1:length(mdlPrepLmGeneral)){
-  mdlTblGeneralLm <- join(mdlTblGeneralLm, mdlPrepLmGeneral[[i]]$mdlTbl, by = "coef")
-}
-
-# lme
-# Study 1: 
-dtWorkerSupp$workerWithinBetween$AttitudesDutch <- dtWorkerSupp$workerWithinBetween$thermometerDutch_1
-mdlWorker$lmerInterceptAttTypeTbl <- lmer(
-    AttitudesDutch ~ OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM + (1 | PID),
-    data = dtWorkerSupp$workerWithinBetween
-  )
-dtWorkerSupp$workerWithinBetween$AttitudesDutch_zwc <- dtWorkerSupp$workerWithinBetween$thermometerDutch_1
-mdlWorker$lmerInterceptAttTypeTblZ <- lmer(
-    AttitudesDutch_zwc ~ OutgroupInteraction_zwc + NonOutgroupInteraction_zwc + OutgroupInteractionM_gmz + NonOutgroupInteractionM_gmz + (1 | PID),
-    data = dtWorkerSupp$workerWithinBetween
-  )
-# Study 2:
-mdlStudent$lmerSlopesAttType <- lmer(
-    AttitudesDutch ~
-      OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM +
-      (1 + OutgroupInteractionC + NonOutgroupInteractionC | PID),
-    data = dtStudentSupp$studentWithinBetween
-  )
-mdlStudent$lmerSlopesAttTypeZ <- lmer(
-    AttitudesDutch_zwc ~
-      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc + OutgroupInteractionM_gmz + NonOutgroupInteractionM_gmz +
-      (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
-    data = dtStudentSupp$studentWithinBetween
-  )
-# Study 3:
-mdlMedical$lmerSlopesAttType <- lmer(
-    AttitudesDutch ~
-      OutgroupInteractionC + NonOutgroupInteractionC + OutgroupInteractionM + NonOutgroupInteractionM +
-      (1 + OutgroupInteractionC + NonOutgroupInteractionC | PID),
-    data = dtMedicalSupp$medicalWithinBetween
-  )
-mdlMedical$lmerSlopesAttTypeZ <- lmer(
-    AttitudesDutch_zwc ~
-      OutgroupInteraction_zwc + NonOutgroupInteraction_zwc + OutgroupInteractionM_gmz + NonOutgroupInteractionM_gmz +
-      (1 + OutgroupInteraction_zwc + NonOutgroupInteraction_zwc | PID),
-    data = dtMedicalSupp$medicalWithinBetween
-  )
-
-mdlTblElementsGeneralLmer <- list(
-  c(mdlWorker$lmerInterceptAttTypeTbl, mdlWorker$lmerInterceptAttTypeTblZ),
-  c(mdlStudent$lmerSlopesAttType, mdlStudent$lmerSlopesAttTypeZ),
-  c(mdlMedical$lmerSlopesAttType, mdlMedical$lmerSlopesAttTypeZ)
-  )
-
-mdlPrepGeneral <- list()
-for (i in 1:length(mdlTblElementsGeneralLmer)) {
-  mdlPrepGeneral[[i]] <- lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])
-}
-
-mdlTblGeneralLmer <- data.frame(
-  coef = c(
-    sapply(mdlPrepGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique,
-    names(mdlPrepGeneral[[1]]$random),
-    names(mdlPrepGeneral[[1]]$fit)
-  )
-)
-for (i in 1:length(mdlPrepGeneral)){
-  mdlTblGeneralLmer <- join(mdlTblGeneralLmer, mdlPrepGeneral[[i]]$mdlTbl, by = "coef")
-}
-
-names(mdlTblGeneralLmer) <- make.unique(names(mdlTblGeneralLmer))
-names(mdlTblGeneralLmer) <- gsub("Beta", "ES", names(mdlTblGeneralLmer))
-names(mdlTblGeneralLm) <- make.unique(names(mdlTblGeneralLm))
-names(mdlTblGeneralLm) <- gsub("Eta2_partial", "ES", names(mdlTblGeneralLm))
-
-lmAllAttFreqQualX2 <-
-  lm(
-    AvAttitude ~ 
-      SumContactNL_c * AvQualityOut_c + 
-      SumContactNL_c * studyNum1 + 
-      SumContactNL_c * studyNum3 + 
-      AvQualityOut_c * studyNum1 + 
-      AvQualityOut_c * studyNum3,
-    data = avAll
-  )
-
-mdlTblGeneralLmAll <- lmTblPrep(lmAllAttFreqQualX2)$mdlTbl %>%
-  rename(., ES = Eta2_partial) %>%
-  replace(is.na(.), "") %>%
-  mutate(
-    B = ifelse(ES != "", paste(B, "; $\\eta_{partial}$ = ", ES, sep = ""), B),
-    ES = ""
-  )
-
-mdlTblGeneralLong <- 
-  rbind(mdlTblGeneralLmer %>%
-                             filter(
-                               coef %in% c(
-                                 "(Intercept)",
-                                 "OutgroupInteraction",
-                                 "NonOutgroupInteraction",
-                                 "OutgroupInteractionM",
-                                 "NonOutgroupInteractionM",
-                                 "R2Marg_R2Cond"
-                               )
-                             ),
-        mdlTblGeneralLmAll %>%
-                             filter(
-                               coef %in% c(
-                                 "(Intercept)",
-                                 "AvQualityOut",
-                                 "AvQuality",
-                                 "studyNum1",
-                                 "studyNum3",
-                                 "SumContactNL:AvQualityOut",
-                                 "SumContactNL:studyNum1",
-                                 "SumContactNL:studyNum3", 
-                                 "AvQualityOut:studyNum1",
-                                 "AvQualityOut:studyNum3",
-                                 "R2_R2_adjusted"
-                               )
-                             ) %>%
-          mutate(
-            B.1 = "",
-            ES.1 = "",
-            B.2 = "",
-            ES.2 =  ""
-          )
-                           )
-mdlTblGeneralLong$coef <- mapvalues(
-  mdlTblGeneralLong$coef,
-  from = c(
-    "R2_R2_adjusted",
-    "R2Marg_R2Cond"
-  ),
-  to = c(
-    "$R^2 / R^2_{adjusted}$",
-    "$R^2_{marginal} / R^2_{conditional}$"
-  )
-)
-
-library(huxtable)
-testTbl <- mdlTblGeneralLong %>%
-  replace(is.na(.), "") %>%
-  hux(.) %>%
-  set_contents(1, 1:7, c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2))) %>%
-  insert_row("", "Study 1", "", "Study 2", "", "Study 3", "", after = 0) %>%
-  merge_cells(1, 2:3) %>% 
-  merge_cells(1, 4:5) %>% 
-  merge_cells(1, 6:7) %>% 
-  set_align(1:2, everywhere, "center") %>%
-  set_escape_contents(everywhere, everywhere, FALSE) %>%
-  set_header_rows(1, TRUE) %>%
-  theme_article %>%
-  set_bottom_border(1, 2:3, brdr(0.5, "solid", "black")) %>%
-  set_bottom_border(1, 4:5, brdr(0.5, "solid", "black")) %>%
-  set_bottom_border(1, 6:7, brdr(0.5, "solid", "black")) %>%
-  insert_column(after = 3, fill = "") %>%
-  set_bottom_border(1, 4, 0) %>%
-  insert_column(after = 6, fill = "") %>%
-  set_bottom_border(1, 7, 0) %>%
-  set_col_width(., 7, 0) %>%
-  insert_row(after = 2, "\\textbf{Within Participants [multilevel linear regression]}", fill = "", copy_cell_props = FALSE) %>%
-  merge_cells(3, 1:ncol(.)) %>%
-  insert_row(after = 9, "\\textbf{Between Participant [aggregated linear regression]}", fill = "", copy_cell_props = FALSE) %>%
-  merge_cells(10, 1:ncol(.)) %>%
-  set_left_padding(4:9, 1, 12) %>%
-  set_left_padding(11:nrow(.), 1, 12) %>%
-  set_font_size(9)
-
-for (i in 11:nrow(testTbl)) {
-  testTbl <- testTbl %>%
-    merge_cells(i, 2:ncol(.)) %>%
-    set_align(i, 2:ncol(.), "center")
-}
-testTbl %>% 
-  as_flextable
-
-capture.output(print_latex(testTbl), file = 'TableOnly.tex')
-
-quick_latex(testTbl, file = "Table.tex", open = FALSE)
-
-mdlTblGeneralLong %>%
-    replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Intergroup General",
-    format = "latex",
-    linesep = "",
-    booktabs = TRUE,
-    col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)),
-    align = c("l", rep("c", ncol(.) - 1)),
-    escape = FALSE,
-    digits = 3
-  )  %>%
-  kable_classic() %>%
-  add_header_above(
-    .,
-    c(
-      "",
-      "Study 1" = 2,
-      "Study 2" = 2,
-      "Study 3" = 2
-    )
-  ) %>%
-  pack_rows("Between Participant [aggregated linear regression] (Effect Size = $\\eta_{partial}$)", 1, 6, escape = FALSE) %>%
-  # pack_rows("Within Participants [multilevel linear regression] (Effect Size = $\\beta$)", 6, 9, escape = FALSE) %>%
-  kableExtra::footnote(
-    .,
-    general = c("**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"), 
-    escape = FALSE
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  kableExtra::landscape() %>%
-  save_kable("Tables/mdlContactGeneralLong.tex")
-```
-
-```{r intergroupGeneralTblWide, include=FALSE}
-mdlTblGeneral <-
-  merge(mdlTblGeneralLm,
-        mdlTblGeneralLmer %>% 
-          mutate(coef = gsub("R2Marg_R2Cond", "R2_R2_adjusted", coef)),
-        by = "coef",
-        all = TRUE) 
-names(mdlTblGeneral) <- make.unique(names(mdlTblGeneral))
-mdlTblGeneral <- mdlTblGeneral %>%
-  arrange(match(coef, c(
-    sapply(mdlPrepLmGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique,
-    sapply(mdlPrepGeneral, function(x) x[1]$coeficients$coef) %>% as.character %>% unique %>% setdiff(., "(Intercept)"),
-    names(mdlPrepGeneral[[1]]$random),
-    "Groups",
-    names(mdlPrepLmGeneral[[1]]$fit),
-    setdiff(names(mdlPrepGeneral[[1]]$fit), c(names(mdlPrepLmGeneral[[1]]$fit), "Groups"))
-  ))) %>%
-  replace(is.na(.), "")
-
-mdlTblGeneral$coef <- mapvalues(
-  mdlTblGeneral$coef,
-  from = c(
-    "sigmaSq",
-    "tau00",
-    "tau11",
-    "rho01",
-    "rho00",
-    "fTest",
-    "R2",
-    "R2_adjusted",
-    "R2_R2_adjusted",
-    "R2_marginal",
-    "R2_conditional",
-    "R2Marg_R2Cond"
-  ),
-  to = c(
-    "$\\sigma^2$",
-    "$\\tau_{00}$",
-    "$\\tau_{11}$",
-    "$\\rho_{01}$",
-    "$\\rho_{00}$",
-    "F Test",
-    "$R^2$",
-    "$R^2_{adjusted}$",
-    "$R^{2 (a)}$",
-    "$R^2_{marginal}$",
-    "$R^2_{conditional}$",
-    "$R^2_{marginal} / R^2_{conditional}$"
-  )
-)
-
-# Headers
-mdlTblGeneralHeader <- data.frame(
-  data = as.character(mdlTblGeneral[mdlTblGeneral$coef == "data",]),
-  formula = as.character(mdlTblGeneral[mdlTblGeneral$coef == "formula",])
-) %>%
-  filter(data != "",
-         data != "data") %>%
-  mutate(study = str_extract(data, "Worker|Student|Medical")) %>%
-  mutate(study = gsub("Worker", "Study 1", study)) %>%
-  mutate(study = gsub("Student", "Study 2", study)) %>%
-  mutate(study = gsub("Medical", "Study 3", study)) %>%
-  mutate(dv = sub(" ~.*", "", formula)) %>%
-  mutate(dv = gsub("Raw", " ", dv))
-
-mdlTblGeneralHeaderDv <- data.frame(names = mdlTblGeneralHeader$dv, span = 2) %>% 
-  mutate(names = as.character(names)) %>%
-  rbind(c("", 1), .) %>%
-  mutate(span = as.numeric(span))
-
-mdlTblGeneralHeaderStudy <- rbind.data.frame(rle(mdlTblGeneralHeader$study)) %>%
-  mutate(lengths = lengths*2) %>%
-  rename(names = values, span = lengths) %>%
-  rbind(c(1, ""), .) %>%
-  mutate(span = as.numeric(span)) %>%
-  select(names, span)
-
-# Long Table
-mdlTblGeneralLong <- mdlTblGeneral %>%
-  kbl(
-    .,
-    caption = "Robustness Analyses",
-    #format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.) - 1)),
-    escape = FALSE,
-    digits = 3
-  ) %>%
-  kable_classic() %>%
-  add_header_above(., mdlTblGeneralHeaderStudy) %>%
-  add_header_above(
-    .,
-    c(
-      "",
-      "Contact [Full Sample]" = 6,
-      "Self-Determination Theory [Outgroup Interactions only]" = 6
-    )
-  ) %>%
-  pack_rows("Random", 7, 11) %>%
-  pack_rows("Fit", 12, 27) %>%
-  footnote(
-    general = c("PID = Participant ID number (grouping variable)",
-                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
-                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
-    ), 
-    escape = TRUE
-  ) %>%
-  gsub("_cwc", "", ., fixed = TRUE)
-
-# shortened Table
-mdlTblGeneralShort <- mdlTblGeneral %>%
-  filter(
-    !coef %in% c(
-      "data",
-      "formula",
-      "groupId",
-      "$R^2$",
-      "$R^2_{adjusted}$",
-      "$R^2_{marginal}$",
-      "$R^2_{conditional}$",
-      "logLik",
-      "deviance"
-    )
-  ) %>%
-  mutate_all(linebreak) %>%
-  kbl(
-    .,
-    caption = "Intergroup General",
-    format = "latex",
-    linesep = "",
-    booktabs = TRUE,
-    col.names = c("", rep(c("$B$", "$\\eta_p$"), (ncol(.)-1)/4), rep(c("$B$", "$\\beta$"), (ncol(.)-1)/4)),
-    align = c("l", rep("c", ncol(.) - 1)),
-    escape = FALSE,
-    digits = 3
-  )  %>%
-  kable_classic() %>%
-  add_header_above(., mdlTblGeneralHeaderStudy) %>%
-  add_header_above(
-    .,
-    c(
-      "",
-      "Aggregated [across participants]" = 6,
-      "Contemporaneous [within participants]" = 6
-    )
-  ) %>%
-  pack_rows("Random", 7, 11) %>%
-  pack_rows("Fit", 12, 18) %>%
-  footnote(
-    general = c("PID = Participant ID number (grouping variable)",
-                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
-                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
-    ),
-    alphabet = c("For linear regression: $R^2 / R^2_{adjusted}$, for multilevel regression: $R^2_{marginal} / R^2_{conditional}$ "),
-    escape = FALSE
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("_cwc", "", ., fixed = TRUE)   %>%
-  gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>%
-  gsub("\\makecell[r]", "\\makecell[c]", ., fixed = TRUE) %>%
-  gsub("objVar$", "", ., fixed = TRUE) %>%
-  gsub("slope_intercept.", "slope.intercept", ., fixed = TRUE) %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  kableExtra::landscape() %>%
-  save_kable("Tables/mdlContactGeneral.tex")
-mdlTblGeneralShort
-```
-
-```{r intergroupNeedsTblLong, include=FALSE}
-# Table of core need and Allports Conditions (potentially two tables — e.g., needs + allport)
-# all lmer models :-)
-# make different options
-
-# collect relevant models
-# Study 1:
-# Rename variables for consistency
-tblDtS1Needs <- dtWorkerSupp$workerOutWithinBetween %>%
-  select(
-    Attitude = thermometerDutch_1,
-    AttitudeZ = thermometerDutch_1_zwc,
-    CoreNeed = keymotive_fulfillemt_1_cwc,
-    CoreNeedZ = keymotive_fulfillemt_1_zwc,
-    QualityRaw = quality_overall_1,
-    Quality = quality_overall_1_cwc,
-    QualityZ = quality_overall_1_zwc,
-    PID = PID
-  )
-# Quality ~ CoreNeed
-tblLmerS1QltInterceptCore <- lmer(
-  QualityRaw ~ CoreNeed + (1 | PID),
-  data = tblDtS1Needs
-)
-tblLmerS1QltInterceptCoreZ <- lmer(
-  QualityZ ~ CoreNeedZ + (1 | PID),
-  data = tblDtS1Needs
-)
-# Attitude ~ CoreNeed
-tblLmerS1AttSlopeCore <- lmer(
-  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
-  data = tblDtS1Needs
-)
-tblLmerS1AttSlopeCoreZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
-  data = tblDtS1Needs
-)
-# Attitude ~ CoreNeed + Quality
-tblLmerS1AttSlopeCoreQlt <- lmer(
-  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
-  data = tblDtS1Needs
-)
-tblLmerS1AttSlopeCoreQltZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
-  data = tblDtS1Needs
-)
-
-# Study 2:
-# Rename variables for consistency
-tblDtS2Needs <- dtStudentSupp$studentOutWithinBetween %>%
-  select(
-    Attitude = AttitudesDutch,
-    AttitudeZ = AttitudesDutch_zwc,
-    CoreNeed = KeyNeedFullfillment_cwc,
-    CoreNeedZ = KeyNeedFullfillment_zwc,
-    QualityRaw = quality_overall,
-    Quality = quality_overall_cwc,
-    QualityZ = quality_overall_zwc,
-    PID = PID
-  )
-# Quality ~ CoreNeed
-tblLmerS2QltSlopesCore <- lmer(
-  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
-  data = tblDtS2Needs
-)
-tblLmerS2QltSlopesCoreZ <- lmer(
-  QualityZ~ CoreNeedZ + (1 + CoreNeedZ | PID),
-  data = tblDtS2Needs
-)
-# Attitude ~ CoreNeed
-tblLmerS2AttSlopesCore <- lmer(
-  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
-  data = tblDtS2Needs
-)
-tblLmerS2AttSlopesCoreZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
-  data = tblDtS2Needs
-)
-# Attitude ~ CoreNeed + Quality
-tblLmerS2AttSlopesCoreQlt <- lmer(
-  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
-  data = tblDtS2Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-tblLmerS2AttSlopesCoreQltZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
-  data = tblDtS2Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-
-# Study 3:
-# Rename variables for consistency
-tblDtS3Needs <- dtMedicalSupp$medicalOutWithinBetween %>%
-  select(
-    Attitude = AttitudesDutch,
-    AttitudeZ = AttitudesDutch_zwc,
-    CoreNeed = KeyNeedFulfillment_cwc,
-    CoreNeedZ = KeyNeedFulfillment_zwc,
-    Allport = AllportsCondition_cwc,
-    AllportZ = AllportsCondition_zwc,
-    QualityRaw = qualityOverall,
-    Quality = qualityOverall_cwc,
-    QualityZ = qualityOverall_zwc,
-    PID = PID
-  )
-# Quality ~ CoreNeed
-tblLmerS3QltSlopesCore <- lmer(
-  QualityRaw ~ CoreNeed + (1 + CoreNeed | PID),
-  data = tblDtS3Needs
-)
-tblLmerS3QltSlopesCoreZ <- lmer(
-  QualityZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
-  data = tblDtS3Needs
-)
-# Attitude ~ CoreNeed
-tblLmerS3AttSlopesCore <- lmer(
-  Attitude ~ CoreNeed + (1 + CoreNeed | PID),
-  data = tblDtS3Needs
-)
-tblLmerS3AttSlopesCoreZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + (1 + CoreNeedZ | PID),
-  data = tblDtS3Needs
-)
-# Attitude ~ CoreNeed + Quality
-tblLmerS3AttSlopesCoreQlt <- lmer(
-  Attitude ~ CoreNeed + Quality + (1 + CoreNeed + Quality | PID),
-  data = tblDtS3Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-tblLmerS3AttSlopesCoreQltZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + QualityZ + (1 + CoreNeedZ + QualityZ | PID),
-  data = tblDtS3Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-# Quality ~ Allport
-tblLmerS3QltSlopesAllport <- lmer(
-  QualityRaw ~ Allport + (1 + Allport | PID),
-  data = tblDtS3Needs
-)
-tblLmerS3QltSlopesAllportZ <- lmer(
-  QualityZ ~ AllportZ + (1 + AllportZ | PID),
-  data = tblDtS3Needs
-)
-# Attitude ~ Allport
-tblLmerS3AttSlopesAllport <- lmer(
-  Attitude ~ Allport + (1 + Allport | PID),
-  data = tblDtS3Needs
-)
-tblLmerS3AttSlopesAllportZ <- lmer(
-  AttitudeZ ~ AllportZ + (1 + AllportZ | PID),
-  data = tblDtS3Needs
-)
-# Attitude ~ Allport + Quality
-tblLmerS3AttSlopesAllportQlt <- lmer(
-  Attitude ~ Allport + Quality + (1 + Allport + Quality | PID),
-  data = tblDtS3Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-tblLmerS3AttSlopesAllportQltZ <- lmer(
-  AttitudeZ ~ AllportZ + QualityZ + (1 + AllportZ + QualityZ | PID),
-  data = tblDtS3Needs,
-  control = lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=2e5))
-)
-# Attitude ~ Allport + CoreNeed
-tblLmerS3AttSlopesAllportCore <- lmer(
-  Attitude ~ CoreNeed + Allport + (1 + CoreNeed + Allport | PID),
-  data = tblDtS3Needs
-)
-tblLmerS3AttSlopesAllportCoreZ <- lmer(
-  AttitudeZ ~ CoreNeedZ + AllportZ + (1 + CoreNeedZ + AllportZ | PID),
-  data = tblDtS3Needs
-)
-
-mdlTblElements <- list(
-  # Study 1:
-  c(tblLmerS1QltInterceptCore, tblLmerS1QltInterceptCoreZ),
-  c(tblLmerS1AttSlopeCore, tblLmerS1AttSlopeCoreZ),
-  c(tblLmerS1AttSlopeCoreQlt, tblLmerS1AttSlopeCoreQltZ),
-  # Study 2:
-  c(tblLmerS2QltSlopesCore, tblLmerS2QltSlopesCoreZ),
-  c(tblLmerS2AttSlopesCore, tblLmerS2AttSlopesCoreZ),
-  c(tblLmerS2AttSlopesCoreQlt, tblLmerS2AttSlopesCoreQltZ),
-  # Study 3:
-  c(tblLmerS3QltSlopesCore, tblLmerS3QltSlopesCoreZ),
-  c(tblLmerS3AttSlopesCore, tblLmerS3AttSlopesCoreZ),
-  c(tblLmerS3AttSlopesCoreQlt, tblLmerS3AttSlopesCoreQltZ),
-  c(tblLmerS3QltSlopesAllport, tblLmerS3QltSlopesAllportZ),
-  c(tblLmerS3AttSlopesAllport, tblLmerS3AttSlopesAllportZ),
-  c(tblLmerS3AttSlopesAllportQlt, tblLmerS3AttSlopesAllportQltZ),
-  c(tblLmerS3AttSlopesAllportCore, tblLmerS3AttSlopesAllportCoreZ)
-  )
-
-# lmerTblPrep(mdlTblElements[[1]][[1]], mdlTblElements[[1]][[2]])
-
-mdlPrep <- list()
-for (i in 1:length(mdlTblElements)) {
-  mdlPrep[[i]] <- lmerTblPrep(mdlTblElements[[i]][[1]], mdlTblElements[[i]][[2]])
-}
-
-shortMdlPath <- list()
-for(i in 1:length(mdlPrep)){
-  study <- gsub("S", "Study", str_extract(mdlPrep[[i]]$fit$data, "S1|S2|S3"))
-  dv <- gsub("Raw", "", sub(" ~.*", "", mdlPrep[[i]]$fit$formula)) 
-  pred <- gsub("\\(Intercept\\)", "", paste(mdlPrep[[i]]$coeficients$coef, collapse = ''))
-
-  name <- paste(study, dv, pred, sep='.')
-  shortMdlPath[[name]] <- mdlPrep[[i]]$coeficients[, c("coef", "est", "Bstar", "B", "estBeta", "BetaStar", "Beta")]
-}
-
-# Long format
-shortMdlPrep <- list()
-for(i in 1:length(mdlPrep)){
-  study <- gsub("S", "Study", str_extract(mdlPrep[[i]]$fit$data, "S1|S2|S3"))
-  dv <- gsub("Raw", "", sub(" ~.*", "", mdlPrep[[i]]$fit$formula)) 
-  pred <- gsub("\\(Intercept\\)", "", paste(mdlPrep[[i]]$coeficients$coef, collapse = ''))
-
-  name <- paste(study, dv, pred, sep='.')
-  tmp <- rbind(
-    mdlPrep[[i]]$coeficients[, c("coef", "B", "Beta")],
-    data.frame(
-      coef = "R2Marg_R2Cond",
-      B = mdlPrep[[i]]$fit$R2Marg_R2Cond,
-      Beta = ""
-    )
-  )
-  shortMdlPrep[[name]] <- tmp
-}
-
-# Manual assembly
-emptyNeedTbl <- data.frame(coef = shortMdlPrep$Study3.Attitude.CoreNeedQuality$coef, B = NA, Beta = NA)
-tmp <- shortMdlPrep[grepl("Study1", names(shortMdlPrep))]
-s1MdlTbl <- data.frame(coef = shortMdlPrep$Study1.Attitude.CoreNeedQuality$coef)
-for (i in 1:length(tmp)){
-  s1MdlTbl <- join(s1MdlTbl, tmp[[i]], by = "coef")
-}
-s1MdlTbl <- s1MdlTbl %>%
-  join(., emptyNeedTbl, by = "coef")
-tmp <- shortMdlPrep[grepl("Study2", names(shortMdlPrep))]
-s2MdlTbl <- data.frame(coef = shortMdlPrep$Study2.Attitude.CoreNeedQuality$coef)
-for (i in 1:length(tmp)){
-  s2MdlTbl <- join(s2MdlTbl, tmp[[i]], by = "coef")
-}
-s2MdlTbl <- s2MdlTbl %>%
-  join(., emptyNeedTbl, by = "coef")
-
-s3NeedMdlTbl <- data.frame(coef = shortMdlPrep$Study3.Attitude.CoreNeedQuality$coef) %>%
-  join(., shortMdlPrep$Study3.Quality.CoreNeed, by = "coef") %>%
-  join(., shortMdlPrep$Study3.Attitude.CoreNeed, by = "coef") %>%
-  join(., shortMdlPrep$Study3.Attitude.CoreNeedQuality, by = "coef") %>%
-  join(., emptyNeedTbl, by = "coef")
-
-s3AllportMdlTbl <- data.frame(coef = shortMdlPrep$Study3.Attitude.AllportQuality$coef) %>%
-  join(., shortMdlPrep$Study3.Quality.Allport, by = "coef") %>%
-  join(., shortMdlPrep$Study3.Attitude.Allport, by = "coef") %>%
-  join(., shortMdlPrep$Study3.Attitude.AllportQuality, by = "coef") %>%
-  join(., emptyNeedTbl, by = "coef")
-
-emptyNeedAllportTbl <- data.frame(coef = shortMdlPrep$Study3.Attitude.CoreNeedAllport$coef, B = NA, Beta = NA)
-s3NeedAllportMdlTbl <- emptyNeedAllportTbl %>%
-  join(., emptyNeedAllportTbl, by = "coef") %>%
-  join(., emptyNeedAllportTbl, by = "coef") %>%
-  join(., shortMdlPrep$Study3.Attitude.CoreNeedAllport, by = "coef")
-
-mdlTblLong <- rbind(
-  s1MdlTbl,
-  s2MdlTbl,
-  s3NeedMdlTbl,
-  s3AllportMdlTbl,
-  s3NeedAllportMdlTbl
-)
-
-mdlTblLong$coef <- mapvalues(
-  mdlTblLong$coef,
-  from = c(
-    "R2Marg_R2Cond"
-  ),
-  to = c(
-    "$R^2_{marginal}$ / $R^2_{conditional}$"
-  )
-)
-
-mdlTblTheoreticalLong <- mdlTblLong %>%
-  replace(is.na(.), "") %>%
-  #mutate_all(linebreak) %>%
-  kbl(
-    .,
-    caption = "Theoretical Test: Core Need Fulfillment and Allport's Conditions",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.)-1)),
-    escape = FALSE
-  ) %>%
-  kable_classic() %>%
-  add_header_above(., c(" ", "Quality" = 2, "Attitude" = 6)) %>%
-  pack_rows("Study 1: Needs", 1, 4) %>%
-  pack_rows("Study 2: Needs", 5, 8) %>%
-  pack_rows("Study 3: Needs", 9, 12) %>%
-  pack_rows("Study 3: Allport", 13, 16) %>%
-  pack_rows("Study 3: Needs & Allport", 17, 20)  %>%
-  kable_styling(latex_options = "scale_down") %>%
-  kableExtra::landscape() %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/mdlTheorylong.tex")
-```
-
-```{r intergroupNeedsTblWide, include=FALSE}
-# wide format
-mdlTbl <- data.frame(
-  coef = c(
-    sapply(mdlPrep, function(x) x[1]$coeficients$coef) %>% unlist %>% unique,
-    names(mdlPrep[[1]]$random),
-    names(mdlPrep[[1]]$fit)
-  )
-)
-for (i in 1:length(mdlPrep)){
-  mdlTbl <- join(mdlTbl, mdlPrep[[i]]$mdlTbl, by = "coef")
-  #mdlTbl <- merge(mdlTbl, mdlPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", ""))
-}
-
-mdlTblHeader <- data.frame(
-  data = as.character(mdlTbl[mdlTbl$coef == "data",]),
-  formula = as.character(mdlTbl[mdlTbl$coef == "formula",])
-) %>%
-  filter(data != "",
-         data != "data") %>%
-  mutate(study = str_extract(data, "S1|S2|S3")) %>%
-  mutate(study = gsub("S", "Study ", study)) %>%
-  mutate(dv = sub(" ~.*", "", formula)) %>%
-  mutate(dv = gsub("Raw", " ", dv)) %>%
-  mutate(pred = str_extract(formula, "(CoreNeed \\+ Allport)|CoreNeed|Allport")) %>%
-  mutate(header = paste(study, pred, sep = " - "))
-
-mdlTblHeaderFreq <- rbind.data.frame(rle(mdlTblHeader$header)) %>%
-  mutate(lengths = lengths*2) %>%
-  rename(names = values, span = lengths) %>%
-  rbind(c(1, ""), .) %>%
-  mutate(span = as.numeric(span)) %>%
-  select(names, span)
-
-mdlTblHeader2 <- data.frame(names = mdlTblHeader$dv, span = 2) %>% 
-  mutate(names = as.character(names)) %>%
-  rbind(c("", 1), .) %>%
-  mutate(span = as.numeric(span))
-
-mdlTblHeader2.2 <- rbind.data.frame(rle(mdlTblHeader$dv)) %>%
-  mutate(lengths = lengths*2) %>%
-  rename(names = values, span = lengths) %>%
-  rbind(c(1, ""), .) %>%
-  mutate(span = as.numeric(span)) %>%
-  select(names, span)
-
-mdlTbl$coef <- mapvalues(
-  mdlTbl$coef,
-  from = c(
-    "sigmaSq",
-    "tau00",
-    "tau11",
-    "rho01",
-    "rho00",
-    "R2_marginal",
-    "R2_conditional", 
-    "R2Marg_R2Cond"
-  ),
-  to = c(
-    "$\\sigma^2$",
-    "$\\tau_{00}$",
-    "$\\tau_{11}$",
-    "$\\rho_{01}$",
-    "$\\rho_{00}$",
-    "$R^2_{marginal}$",
-    "$R^2_{conditional}$",
-    "$R^2_{marginal}$ / $R^2_{conditional}$"
-  )
-)
-
-# Full Table
-mdlTblTheoreticalLong <- mdlTbl %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Theoretical Test: Core Need Fulfillment and Allport's Conditions",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    escape = FALSE,
-    digits = 3
-  ) %>%
-  kable_classic() %>%
-  add_header_above(., mdlTblHeader2) %>%
-  add_header_above(., mdlTblHeaderFreq) %>%
-  pack_rows("Fixed", 1, 4) %>%
-  pack_rows("Random", 5, 9) %>%
-  pack_rows("Fit", 10, 21)
-
-# shortened Table
-mdlTblTheoreticalShort <- mdlTbl %>%
-  replace(is.na(.), "")
-names(mdlTblTheoreticalShort) <- make.unique(names(mdlTblTheoreticalShort))
-mdlTblTheoreticalShort <- mdlTblTheoreticalShort %>%
-  filter(
-    !coef %in% c(
-      "data",
-      "formula",
-      "groupId",
-      "$R^2_{marginal}$",
-      "$R^2_{conditional}$",
-      "logLik",
-      "deviance"
-    )
-  ) %>%
-  mutate_all(linebreak) %>%
-  kbl(
-    .,
-    caption = "Core Need Fulfillment and Allport's Conditions",
-    format = "latex",
-    linesep = "",
-    booktabs = TRUE,
-    col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)),
-    align = c("l", rep("c", ncol(.)-1)),
-    escape = FALSE,
-    digits = 3
-  ) %>%
-  kable_classic() %>%
-  add_header_above(., mdlTblHeader2) %>%
-  add_header_above(., mdlTblHeaderFreq) %>%
-  pack_rows("Fixed", 1, 4) %>%
-  pack_rows("Random", 5, 9) %>%
-  pack_rows("Fit", 10, 15) %>%
-  footnote(
-    general = c("PID = Participant ID number (grouping variable)",
-                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
-                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
-    ),
-    escape = FALSE
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  kableExtra::landscape() %>%
-  gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>%
-  gsub("\\makecell[r]", "\\makecell[c]", ., fixed = TRUE) %>%
-  gsub("objVar$", "", ., fixed = TRUE) %>%
-  gsub("slope_intercept.", "slope.intercept", ., fixed = TRUE) %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/mdlTheory.tex")
-mdlTblTheoreticalShort
-```
-
 ```{r robustnessTblLong, include=FALSE}
@@
   pack_rows("Self-Determination Theory [Outgroup Interactions only]", 6, 11) %>%
+  kableExtra::footnote(
+    .,
+    general = c("**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"), 
+    escape = FALSE
+  ) %>%
   kable_styling(latex_options = "scale_down") %>%
@@
 
-```{r descrFullLong, include=FALSE}
-allMlCor <-
-  MlCorMat(
-    data = dtAll$mlAll, #%>% filter(OutgroupInteraction == "Yes"),
-    id = "ID",
-    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "qualityOverall", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
-  )
-
-# Full Sample Descriptives Table [longer format (Descriptives below correlations)]
-rbind(
-  workerMlCor %>%
-    rownames_to_column(., "Variable") %>%
-    mutate(Allport = ""),
-  studentMlCor %>%
-    select(names(workerMlCor)) %>%
-    rownames_to_column(., "Variable") %>%
-    mutate(Allport = ""),
-  medicalMlCor %>%
-    select(names(workerMlCor), "Allport") %>%
-    rownames_to_column(., "Variable"),
-  allMlCor %>%
-    select(names(workerMlCor)) %>%
-    rownames_to_column(., "Variable") %>%
-    mutate(Allport = "")
-) %>%
-  kbl(.,
-      format = "latex",
-      caption = "Full Sample: Correlation Table and Descriptive Statistics",
-      booktabs = TRUE,
-      align = c("l", rep("c", ncol(.) - 1))) %>%
-  pack_rows("Study 1", 1, nrow(workerMlCor)) %>%
-  pack_rows("Study 2", nrow(workerMlCor) + 1,
-            sum(nrow(workerMlCor), nrow(studentMlCor))) %>%
-  pack_rows("Study 3", sum(nrow(workerMlCor), nrow(studentMlCor)) + 1,  
-            sum(nrow(workerMlCor), nrow(studentMlCor), nrow(medicalMlCor))) %>%
-  pack_rows("Across Studies", sum(nrow(workerMlCor), nrow(studentMlCor), nrow(medicalMlCor)) + 1,  
-            sum(nrow(workerMlCor), nrow(studentMlCor), nrow(medicalMlCor), nrow(allMlCor))) %>%
-  gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) %>% # fix table position
-  footnote(
-    general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
-      "*** p < .001, ** p < .01,  * p < .05"
-    )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/descrFullLong.tex")
-```
-
-```{r descrFullWide, include=FALSE}
-# Full Sample Descriptives Table [wider format (descriptives next to correlation)]
-rbind(
-  workerMlCor %>%
-    t %>%
-    as.data.frame %>%
-    rownames_to_column(., "Variable") %>%
-    add_column(Allport = "",
-               .before = "Grand Mean"),
-  studentMlCor %>%
-    select(names(workerMlCor)) %>%
-    t %>%
-    as.data.frame %>%
-    rownames_to_column(., "Variable") %>%
-    add_column(Allport = "",
-               .before = "Grand Mean"),
-  medicalMlCor %>%
-    select(names(workerMlCor), "Allport") %>%
-    t %>%
-    as.data.frame %>%
-    rownames_to_column(., "Variable"),
-  allMlCor %>%
-    select(names(workerMlCor)) %>%
-    t %>%
-    as.data.frame %>%
-    rownames_to_column(., "Variable") %>%
-    add_column(Allport = "",
-               .before = "Grand Mean")
-) %>%
-  kbl(.,
-      format = "latex",
-      caption = "Full Sample: Correlation Table and Descriptive Statistics",
-      booktabs = TRUE,
-      align = c("l", rep("c", ncol(.) - 1)))  %>%
-  kable_classic() %>%
-  add_header_above(
-    .,
-    c(
-      "",
-      "Correlations" = ncol(medicalMlCor),
-      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
-    )
-  ) %>%
-  pack_rows("Study 1", 1, ncol(workerMlCor)) %>%
-  pack_rows("Study 2", ncol(workerMlCor) + 1,
-            sum(ncol(workerMlCor), ncol(studentMlCor))) %>%
-  pack_rows("Study 3", sum(ncol(workerMlCor), ncol(studentMlCor)) + 1,  
-            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor))) %>%
-  pack_rows("Across Studies", sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor)) + 1,  
-            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor), ncol(allMlCor))) %>% # fix table position
-  footnote(
-    general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
-      "*** p < .001, ** p < .01,  * p < .05"
-    )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/descrFullWide.tex")
-```
-
-```{r descrOutLong, include=FALSE}
-#
-#       OLD!!
-#
-
-# Outgroup Interaction Sample Descriptives Table
-rbind(
-  workerOutMlCor %>%
-    rownames_to_column(., "Variable") %>%
-    mutate(Allport = ""),
-  studentOutMlCor %>%
-    select(names(workerOutMlCor)) %>%
-    rownames_to_column(., "Variable") %>%
-    mutate(Allport = ""),
-  medicalOutMlCor %>%
-    select(names(workerOutMlCor), "Allport") %>%
-    rownames_to_column(., "Variable")
-) %>%
-  kbl(.,
-      format = "latex",
-      caption = "Intergroup Contact Sample: Correlation Table and Descriptive Statistics",
-      booktabs = TRUE,
-      align = c("l", rep("c", ncol(.) - 1))) %>%
-  pack_rows("Study 1", 1, nrow(workerOutMlCor)) %>%
-  pack_rows("Study 2", nrow(workerOutMlCor) + 1,
-            sum(nrow(workerOutMlCor), nrow(studentOutMlCor))) %>%
-  pack_rows("Study 3", sum(nrow(workerOutMlCor), nrow(studentOutMlCor)) + 1,  
-            sum(nrow(workerOutMlCor), nrow(studentOutMlCor), nrow(medicalOutMlCor))) %>%
-  footnote(
-    general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
-      "*** p < .001, ** p < .01,  * p < .05"
-    )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/descrOutLong.tex")
-```
-
-```{r descrOutWide, include=FALSE}
-allOutMlCor <-
-  MlCorMat(
-    data = dtAll$mlAll %>% filter(OutgroupInteraction == "Yes"),
-    id = "ID",
-    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "qualityOverall", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
-  )
-
-# Outgroup Interaction Sample Descriptives Table --- wider version
-rbind(
-  workerOutMlCor %>%
-    t %>%
-    as.data.frame %>%
-    rownames_to_column(., "Variable") %>%
-    add_column(Allport = "",
-               .before = "Grand Mean"),
-  studentOutMlCor %>%
-    select(names(workerOutMlCor)) %>%
-    t %>%
-    as.data.frame %>%
-    rownames_to_column(., "Variable") %>%
-    add_column(Allport = "",
-               .before = "Grand Mean"),
-  medicalOutMlCor %>%
-    select(names(workerOutMlCor), "Allport") %>%
-    t %>%
-    as.data.frame %>%
-    rownames_to_column(., "Variable"),
-  allOutMlCor %>%
-    select(names(workerOutMlCor)) %>%
-    t %>%
-    as.data.frame %>%
-    rownames_to_column(., "Variable") %>%
-    add_column(Allport = "",
-               .before = "Grand Mean")
-) %>%
-  kbl(.,
-      format = "latex",
-      caption = "Intergroup Contact Sample: Correlation Table and Descriptive Statistics",
-      booktabs = TRUE,
-      align = c("l", rep("c", ncol(.) - 1))) %>%
-  kable_classic() %>%
-  add_header_above(
-    .,
-    c(
-      "",
-      "Correlations" = ncol(medicalMlCor),
-      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
-    )
-  ) %>%
-  pack_rows("Study 1", 1, ncol(workerOutMlCor)) %>%
-  pack_rows("Study 2", ncol(workerOutMlCor) + 1,
-            sum(ncol(workerOutMlCor), ncol(studentOutMlCor))) %>%
-  pack_rows("Study 3", sum(ncol(workerOutMlCor), ncol(studentOutMlCor)) + 1,  
-            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor))) %>% 
-  pack_rows("Across Studies", sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor)) + 1,  
-            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor), ncol(allOutMlCor))) %>% 
-  footnote(
-    general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
-      "*** p < .001, ** p < .01,  * p < .05"
-    )
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/descrOutWide.tex")
-
-```
-
 <!-- FIGURES: -->
-
-```{r metaGeneralLm, include=FALSE}
-mdlTblElementsGeneralLm <- list(mdlWorker$lmAttFreqQualX,
-                                mdlStudent$lmAttFreqQualX,
-                                mdlMedical$lmAttFreqQualX)
-
-lmMetaTbl <- data.frame()
-for (i in 1:length(mdlTblElementsGeneralLm)){
-  lmTblTmp <- lmTblPrep(mdlTblElementsGeneralLm[[i]])$coeficients %>%
-  select(
-    coef,
-    B = est,
-    se,
-    lwr,
-    upr,
-    tval,
-    Rsq
-  ) %>%
-  mutate(
-    n = lmTblPrep(mdlTblElementsGeneralLm[[i]])$fit$N,
-    m = nrow(.)-1, 
-    sample = str_match(lmTblPrep(mdlTblElementsGeneralLm[[i]])$fit$data, "dt(.*?)Supp")[2],
-    coef = gsub(":", ".", coef)
-  )
-  lmMetaTbl <- rbind(lmMetaTbl, lmTblTmp)
-}
-
-lmMetaTbl <- lmMetaTbl %>% arrange(coef)
-
-# extract parameter names
-  name <- "Contact Hypothesis — Aggregate Linear Regression"
-  var <- as.character(unique(lmMetaTbl$coef))[!as.character(unique(lmMetaTbl$coef)) %in% c("(Intercept)")]
-  names <- qdap::mgsub(c("SumContactNL", "AvQuality", "SumContactNL.AvQuality"),
-                       c("Number of Outgroup Contacts","Average Interaction Quality", "Contact X Quality"), 
-                       var)
-  studies <- as.character(unique(lmMetaTbl$sample))
-
-### Parametric Meta-Analysis
-    meta.parametric <- list()
-    meta.parametric.sum <- data.frame(effect = var, 
-                                      name = names, 
-                                      beta.Worker = NA, 
-                                      lwr.Worker = NA, 
-                                      upr.Worker = NA, 
-                                      CI.Worker = NA,
-                                      beta.Student = NA, 
-                                      lwr.Student = NA, 
-                                      upr.Student = NA, 
-                                      CI.Student = NA,
-                                      beta.Medical = NA,
-                                      lwr.Medical = NA,
-                                      upr.Medical = NA,
-                                      CI.Medical = NA, 
-                                      RE.beta = NA,
-                                      lwr.RE = NA,
-                                      upr.RE = NA,
-                                      RE.CI = NA,
-                                      RE.pval = NA,
-                                      RE.star = NA)
-
-# i = 1
-for(i in 1:length(var)){
-      md <- escalc(data = lmMetaTbl[lmMetaTbl$coef==var[i],],
-                   measure = "SPCOR",
-                   ti = tval,
-                   ni = n,
-                   mi = m,
-                   r2i = Rsq,
-                   var.names = c(paste(var[i],".yi",sep=""),paste(var[i],".vi",sep="")))
-
-      meta.parametric[[var[i]]] <- rma(yi = get(paste(var[i],".yi",sep="")),
-                                       vi = get(paste(var[i],".vi",sep="")), 
-                                       data = md, 
-                                       method = "REML", #"FE", 
-                                       slab = sample)
-      #metafor::forest(meta.parametric[[var[i]]],
-      #                main = paste("Meta Analysis ",names[i],sep = ""))
-
-      meta.parametric.sum$effect[i] <- var[i]
-      meta.parametric.sum$beta.Worker[i] <- meta.parametric[[var[i]]]$yi[1]
-      meta.parametric.sum$beta.Student[i] <- meta.parametric[[var[i]]]$yi[2]
-      meta.parametric.sum$beta.Medical[i] <- meta.parametric[[var[i]]]$yi[3]
-
-      meta.parametric.sum$lwr.Worker[i] <- meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1])
-      meta.parametric.sum$lwr.Student[i] <- meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2])
-      meta.parametric.sum$lwr.Medical[i] <- meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3])
-
-      meta.parametric.sum$upr.Worker[i] <- meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1])
-      meta.parametric.sum$upr.Student[i] <- meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2])
-      meta.parametric.sum$upr.Medical[i] <- meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3])
-
-      meta.parametric.sum$CI.Worker[i] <- paste("[", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[1]-1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2)),", ", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[1]+1.96*sqrt(meta.parametric[[var[i]]]$vi[1]),2)),"]",sep="")
-      meta.parametric.sum$CI.Student[i] <- paste("[", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[2]-1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2)),", ", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[2]+1.96*sqrt(meta.parametric[[var[i]]]$vi[2]),2)),"]",sep="")
-      meta.parametric.sum$CI.Medical[i] <- paste("[", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[3]-1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2)),", ", sprintf("%0.2f", round(meta.parametric[[var[i]]]$yi[3]+1.96*sqrt(meta.parametric[[var[i]]]$vi[3]),2)),"]",sep="")
-
-      meta.parametric.sum$RE.beta[i] <- meta.parametric[[var[i]]]$b
-      meta.parametric.sum$lwr.RE[i] <- meta.parametric[[var[i]]]$ci.lb
-      meta.parametric.sum$upr.RE[i] <- meta.parametric[[var[i]]]$ci.ub
-      meta.parametric.sum$RE.CI[i] <- paste("[",
-                                            round(meta.parametric[[var[i]]]$ci.lb, 2),
-                                            ", ", round(meta.parametric[[var[i]]]$ci.ub,2),"]", sep="")
-      meta.parametric.sum$RE.pval[i] <- meta.parametric[[var[i]]]$pval
-      meta.parametric.sum$RE.star[i] <- ifelse(meta.parametric.sum$RE.pval[i]<0.001,"***",ifelse(meta.parametric.sum$RE.pval[i]<0.01,"**",ifelse(meta.parametric.sum$RE.pval[i]<0.05,"*","")))
-
-}
-    #meta.parametric
-
-    meta.parametric.plt.data <- meta.parametric.sum
-
-    meta.parametric.sum <- meta.parametric.sum %>%
-      select(-starts_with("lwr"),
-             -starts_with("upr"))
-
-    eff <- escalc(data = lmMetaTbl, 
-                  slab = coef,
-                  measure = "SPCOR",
-                  ti = tval,
-                  ni = n,
-                  mi = m,
-                  r2i = Rsq)  %>%
-    mutate(effLwr = yi - 1.96 * sqrt(vi),
-           effUpr = yi + 1.96 * sqrt(vi),
-           effCI = paste("[", format(round(effLwr, 2), nsmall = 2), ", ", format(round(effUpr, 2), nsmall = 2), "]", sep = ""),
-           name = strLabFix(coef),
-           study = strStudyFix(sample))
-
-    meta <- rma(yi = yi,
-                vi = vi, 
-                data = eff, 
-                method = "REML", #"FE", 
-                slab = paste(coef, sample, sep=" - "))
-
-    k <- length(var) * length(studies)
-    png(file = "Figures/forestParametricGeneralLmOld.png", height = 200 + 40*k^.85) 
-      metafor::forest(meta, xlim=c(-2, 2), cex=0.75, ylim=c(-1, 20), rows=c(22:20,16:14,10:8,4:2), 
-                      slab = rep(c("Study 1","Study 2", "Study 3"),length(studies)+1),
-                      mlab="", main=paste0("Meta Analysis: Forest Plot [Parametric] \n(",name,")")) # , xlab = "Standardized Beta"
-      par(font=2)
-      text(-2.05, c(17,11,5), cex=0.75, pos=4, names)
-      m=1
-      for(i in 3:1){
-        addpoly(meta.parametric[[i]], row=m, cex=0.75, mlab="► Fixed Effect")
-        m <- m+6
-      }
-      text(-2.05, 19, "Predictors by study",  cex=.8, pos=4)
-      text(2, 19, "Semi-Partial Correlation [95% CI]", cex=.8, pos=2)
-    dev.off()
-
-    meta.parametric.plt.data <- data.table(meta.parametric.plt.data) %>% 
-        mutate(
-          beta.RE = RE.beta,
-          CI.RE = RE.CI,
-          pval.RE = RE.pval,
-          star.RE = RE.star
-        ) %>%
-      select(-starts_with("RE."))
-
-  library(splitstackshape)
-    meta.parametric.plt.longdata <-
-      merged.stack(
-        meta.parametric.plt.data,
-        var.stubs = c("beta", "lwr", "upr", "CI", "pval", "star"),
-        sep = "."
-      ) %>%
-      rename(sample = .time_1) %>%
-      mutate(sample = gsub('Worker', 'Study 1',
-                      gsub('Student', 'Study 2',
-                      gsub('Medical', 'Study 3', sample)
-                           ))) %>%
-    arrange(match(effect, c("SumContactNL", "AvQuality", "SumContactNL.AvQuality")), 
-            match(sample, c("Study 1", "Study 2", "Study 3", "RE")))
-
-    alpha <- 0.05
-
-  meta.parametric.plt.longdata2 <- meta.parametric.plt.longdata %>%
-    mutate(
-      index = as.integer(sapply(seq(from = 2, by=6, length.out = 3), seq, length.out=4)),
-      vi = ((upr - lwr)/(2 * qnorm(alpha/2, lower.tail = FALSE)))^2,
-      wi = 1/sqrt(vi),
-      psize = wi/sum(wi, na.rm = TRUE),
-      psize2 = (psize - min(psize, na.rm = TRUE))/(max(psize, na.rm = TRUE) - min(psize, na.rm = TRUE)),
-      psize3 = (psize2 * 1) + 0.5
-    )
-
-  polyDat <- data.frame(
-    y = c(
-      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"],
-      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"] - .25,
-      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"],
-      meta.parametric.plt.longdata2$index[meta.parametric.plt.longdata2$sample == "RE"] + .25
-    ),
-    x = c(
-      meta.parametric.plt.longdata2$lwr[meta.parametric.plt.longdata2$sample == "RE"],
-      meta.parametric.plt.longdata2$beta[meta.parametric.plt.longdata2$sample == "RE"],
-      meta.parametric.plt.longdata2$upr[meta.parametric.plt.longdata2$sample == "RE"],
-      meta.parametric.plt.longdata2$beta[meta.parametric.plt.longdata2$sample == "RE"]
-    ),
-    lab = rep(paste("RE", 1:3), 4)
-  )
-
-  lab <- lapply(unique(meta.parametric.plt.longdata2$name), append, c(unique(meta.parametric.plt.longdata2$sample), "")) %>% unlist
-
-  plot1 <- ggplot() +
-    geom_point(
-      data = meta.parametric.plt.longdata2[sample != "RE",],
-      aes(y = index, x = beta),
-      shape = 15,
-      size = meta.parametric.plt.longdata2[sample != "RE", psize3] * 3
-    ) +
-    geom_errorbarh(data = meta.parametric.plt.longdata2[sample != "RE",],
-                   aes(y = index, xmin = lwr, xmax = upr),
-                   height = 0.25) +
-    geom_polygon(data = polyDat, 
-                 mapping = aes(x = x, y = y, group = lab)) +
-    geom_vline(
-      xintercept = 0,
-      color = "black",
-      linetype = "dashed",
-      cex = 0.5,
-      alpha = 1
-    ) +
-    scale_y_continuous(
-      name = "",
-      expand  = expansion(add = 1),
-      breaks = seq(lab),
-      labels = lab,
-      trans = "reverse"
-    ) +
-    scale_x_continuous(
-      limits = c(-1, 1),
-      breaks = seq(-1, 1, 0.5),
-      expand = c(0, 0)
-    ) +
-    xlab("Semi-Partial Correlation (95% CI)") +
-    ggtitle("Predictors by Study") +
-    theme_Publication() +
-    theme(
-      plot.title = element_text(hjust = 0, size=12, face = "bold"),
-      plot.title.position = "plot",
-      panel.grid.major = element_blank(),
-      panel.grid.minor = element_blank(),
-      axis.line.y = element_blank(),
-      axis.ticks.y = element_blank(),
-      axis.text.y = element_text(size = 12, colour = "black", hjust=0, face = rep(c("bold", rep("plain", 5)),3)),
-      axis.line.x = element_line(colour = "black"),
-      axis.text.x.bottom = element_text(size = 12, colour = "black"),
-      axis.title.x = element_text(size = 12, colour = "black")
-    )
-
-## Estiamte and CI table
-  tab1 <- ggplot(meta.parametric.plt.longdata2, aes(y = lab)) +
-    ylab(NULL) + xlab("  ") +
-    labs(title = "space") +
-    geom_text(aes(
-      y = rev(index),
-      x = 1,
-      label = paste(sprintf("%0.2f", round(beta, digits = 2)), CI)
-    ),
-    size = 4,
-    hjust = 1) + 
-    scale_x_continuous(
-      limits = c(-1, 1)
-    ) +
-    ggtitle("Estimate [95% CI]") +
-    theme_Publication() +
-    theme(
-      plot.title = element_text(hjust = 1, size = 12),
-      axis.line = element_blank(),
-      axis.text.x = element_text(color = "white"),
-      axis.text.y = element_blank(),
-      axis.ticks = element_blank(),
-      axis.title.y = element_blank(),
-      legend.position = "none",
-      panel.background = element_blank(),
-      panel.border = element_blank(),
-      panel.grid.major = element_blank(),
-      panel.grid.minor = element_blank(),
-      plot.background = element_blank()
-    )
-
-grid.arrange(plot1, tab1, layout_matrix = matrix(c(1,1,1,2), nrow = 1))
-
-png(file = "Figures/forestParametricGeneralLm.png", width = 700) 
-  grid.arrange(plot1, tab1, layout_matrix = matrix(c(1,1,1,2), nrow = 1))
-dev.off()
-
-### Bootstrapped Meta-Analysis
-    var.boot <- var
-    names.boot <- names
-    meta.bootstrapped <- list()
-    meta.bootstrapped.sum <- data.frame(effect = var.boot, 
-                                      name = names.boot, 
-                                      beta.Worker = NA, 
-                                      CI.Worker = NA,
-                                      beta.Student = NA, 
-                                      CI.Student = NA,
-                                      beta.Medical = NA,
-                                      CI.Medical = NA, 
-                                      RE.beta = NA,
-                                      RE.CI = NA,
-                                      RE.pval = NA,
-                                      RE.star = NA)
-
-    # i = 3
-    for(i in 1:length(var.boot)){
-      md <- escalc(data = lmMetaTbl[lmMetaTbl$coef==var.boot[i],],
-                   measure = "SPCOR",
-                   yi = B,
-                   sei = se,
-                   ni = n,
-                   mi = m,
-                   var.names = c(paste(var.boot[i],".yi",sep=""),paste(var.boot[i],".vi",sep="")))
-
-      meta.bootstrapped[[var.boot[i]]] <- rma(yi = get(paste(var.boot[i],".yi",sep="")),
-                                              vi = get(paste(var.boot[i],".vi",sep="")),
-                                              data = md,
-                                              method =  "REML", #"FE", 
-                                              slab = sample)
-      #metafor::forest(meta.bootstrapped[[var.boot[i]]],
-      #                main = paste("Meta Analysis ",names.boot[i],sep = ""))
-      meta.bootstrapped.sum$effect[i] <- var[i]
-      meta.bootstrapped.sum$beta.Worker[i] <-
-        meta.bootstrapped[[var[i]]]$yi[1]
-      meta.bootstrapped.sum$beta.Student[i] <-
-        meta.bootstrapped[[var[i]]]$yi[2]
-      meta.bootstrapped.sum$beta.Medical[i] <-
-        meta.bootstrapped[[var[i]]]$yi[3]
-      meta.bootstrapped.sum$CI.Worker[i] <-
-        paste(
-          "[",
-          round(meta.bootstrapped[[var[i]]]$yi[1] -
-                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[1]), 2),
-          ", ",
-          round(meta.bootstrapped[[var[i]]]$yi[1] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[1]), 2),
-          "]",
-          sep = ""
-        )
-      meta.bootstrapped.sum$CI.Student[i] <-
-        paste(
-          "[",
-          round(meta.bootstrapped[[var[i]]]$yi[2] -
-                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[2]), 2),
-          ", ",
-          round(meta.bootstrapped[[var[i]]]$yi[2] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[2]), 2),
-          "]",
-          sep = ""
-        )
-      meta.bootstrapped.sum$CI.Medical[i] <-
-        paste(
-          "[",
-          round(meta.bootstrapped[[var[i]]]$yi[3] -
-                  1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[3]), 2),
-          ", ",
-          round(meta.bootstrapped[[var[i]]]$yi[3] + 1.96 * sqrt(meta.bootstrapped[[var[i]]]$vi[3]), 2),
-          "]",
-          sep = ""
-        )
-      meta.bootstrapped.sum$RE.beta[i] <- meta.bootstrapped[[var[i]]]$b
-      meta.bootstrapped.sum$RE.CI[i] <- paste(
-        "[",
-        round(meta.bootstrapped[[var[i]]]$ci.lb, 2),
-        ", ",
-        round(meta.bootstrapped[[var[i]]]$ci.ub, 2),
-        "]",
-        sep = ""
-      )
-      meta.bootstrapped.sum$RE.pval[i] <- meta.bootstrapped[[var[i]]]$pval
-      meta.bootstrapped.sum$RE.star[i] <-
-        ifelse(
-          meta.bootstrapped.sum$RE.pval[i] < 0.001,
-          "***",
-          ifelse(
-            meta.bootstrapped.sum$RE.pval[i] < 0.01,
-            "**",
-            ifelse(meta.bootstrapped.sum$RE.pval[i] < 0.05, "*", "")
-          )
-        )
-    }
-    #meta.bootstrapped
-
-    eff.boot <- escalc(data = lmMetaTbl %>% filter(coef != "(Intercept)"), 
-                       slab = coef,
-                       measure = "SPCOR",
-                       yi = B,
-                       sei = se,
-                       ni = n,
-                       mi = m)
-    meta.boot <- rma(yi = yi,
-                     vi = vi, 
-                     data = eff.boot, 
-                     method = "REML", #"FE", 
-                     slab = paste(coef, sample, sep=" - "))
-
-    k <- 3*3
-    png(file = "Figures/forestBootstrappedGeneralLm.png", height = 200 + 40*k^.85)
-      metafor::forest(meta.boot, cex=0.75, xlim=c(-2, 2.5), ylim=c(-1, 20), rows=c(16:14,10:8,4:2), 
-                      slab = rep(c("Study 1","Study 2", "Study 3"),length(studies)),
-                      mlab="", main=paste0("Meta Analysis: Forest Plot [Bootstrapped] \n(",name,")")) # , xlab = "Standardized Beta")
-      par(font=2)
-      text(-2.05, c(17,11,5), cex=0.75, pos=4, names)
-      m=1
-      for(i in 3:1){
-        addpoly(meta.bootstrapped[[i]], row=m, cex=0.75, mlab="► Fixed Effect")
-        m <- m+6
-      }
-      text(-2.05, 19, "Predictors by study",  cex=.8, pos=4)
-      text(2.5, 19, "Semi-Partial Correlation [95% CI]", cex=.8, pos=2)
-    dev.off()    
-```
-
-```{r metaGeneralLmer, include=FALSE}
-mdlTblElementsGeneralLmer <- list(
-  c(mdlWorker$lmerInterceptAttTypeTbl, mdlWorker$lmerInterceptAttTypeTblZ),
-  c(mdlStudent$lmerSlopesAttType, mdlStudent$lmerSlopesAttTypeZ),
-  c(mdlMedical$lmerSlopesAttType, mdlMedical$lmerSlopesAttTypeZ)
-  )
-
-# i =1
-GeneralLmerMetaTbl <- data.frame()
-for (i in 1:length(mdlTblElementsGeneralLmer)){
-  lmerTblTmp <- lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$beta %>%
-  select(
-    coef,
-    B = est,
-    se,
-    lwr,
-    upr,
-    tval,
-    Rsq
-  ) %>%
-  mutate(
-    n = lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$fit$N,
-    m = nrow(.), 
-    sample = str_match(lmerTblPrep(mdlTblElementsGeneralLmer[[i]][[1]], mdlTblElementsGeneralLmer[[i]][[2]])$fit$data, "dt(.*?)Supp")[2],
-    coef = gsub(":", ".", coef)
-  )
-  GeneralLmerMetaTbl <- rbind(GeneralLmerMetaTbl, lmerTblTmp)
-}
-
-GeneralLmerMetaTbl <- GeneralLmerMetaTbl %>% arrange(coef)
-
-GeneralLmerMeta <- metaLmerOut(GeneralLmerMetaTbl,
-                               type = "REML", #"FE", 
-                               name = "GeneralLmer",
-                               title = "Contact Hypothesis — Mixed Effects Regression")
-
-```
-
-```{generalForestPltComb, include=FALSE}
-effGeneral <- rbind(
-  eff %>%
-    filter(coef != "(Intercept)") %>%
-    mutate(analysis = "(A) Aggregate Linear Regression",
-           metaId = paste(coef, analysis, sep = ".")) %>%
-    as.data.frame,
-  GeneralLmerMeta$eff %>%
-    mutate(analysis = "(B) Mixed Effects Regression",
-           metaId = paste(coef, analysis, sep = ".")) %>%
-    as.data.frame
-)
-
-metaSubForest(effGeneral, 
-              title = "Meta Analysis: Forest Plot Contact Hypothesis \n[Parametric]",
-              filename = "GeneralLmer",
-              type = "REML",
-              addAbove = 5,
-              width = 600,
-              height = 600)
-```
-
-```{r metaTheory, include=FALSE}
-mdlTblElementsTheoryLmer <- list(
-  # Study 1:
-  c(tblLmerS1QltInterceptCore, tblLmerS1QltInterceptCoreZ),
-  c(tblLmerS1AttSlopeCore, tblLmerS1AttSlopeCoreZ),
-  c(tblLmerS1AttSlopeCoreQlt, tblLmerS1AttSlopeCoreQltZ),
-  # Study 2:
-  c(tblLmerS2QltSlopesCore, tblLmerS2QltSlopesCoreZ),
-  c(tblLmerS2AttSlopesCore, tblLmerS2AttSlopesCoreZ),
-  c(tblLmerS2AttSlopesCoreQlt, tblLmerS2AttSlopesCoreQltZ),
-  # Study 3:
-  c(tblLmerS3QltSlopesCore, tblLmerS3QltSlopesCoreZ),
-  c(tblLmerS3AttSlopesCore, tblLmerS3AttSlopesCoreZ),
-  c(tblLmerS3AttSlopesCoreQlt, tblLmerS3AttSlopesCoreQltZ),
-  c(tblLmerS3QltSlopesAllport, tblLmerS3QltSlopesAllportZ),
-  c(tblLmerS3AttSlopesAllport, tblLmerS3AttSlopesAllportZ),
-  c(tblLmerS3AttSlopesAllportQlt, tblLmerS3AttSlopesAllportQltZ),
-  c(tblLmerS3AttSlopesAllportCore, tblLmerS3AttSlopesAllportCoreZ)
-  )
-
-# i =1
-theoryMetaTbl <- data.frame()
-for (i in 1:length(mdlTblElementsTheoryLmer)){
-  lmerTblTmp <- lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$beta %>%
-  select(
-    coef,
-    B = est,
-    se,
-    lwr,
-    upr,
-    tval,
-    Rsq
-  ) %>%
-  mutate(
-    n = lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$N,
-    m = nrow(.), 
-    dv = gsub("Raw", "", str_extract(lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$formula,".+?(?= ~)")),
-    sample = gsub("S", "Study", str_extract(lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$data, "S1|S2|S3")),
-    formula = lmerTblPrep(mdlTblElementsTheoryLmer[[i]][[1]], mdlTblElementsTheoryLmer[[i]][[2]])$fit$formula,
-    coef = gsub(":", ".", coef)
-  )
-  theoryMetaTbl <- rbind(theoryMetaTbl, lmerTblTmp)
-}
-
-theoryMetaTblNoAllport <- theoryMetaTbl %>%
-  filter(!grepl("Allport",formula)) %>% 
-  mutate(formula = gsub(" \\+ \\(.*", "", formula)) %>%
-  arrange(formula, coef, sample)
-
-TheoryMetaQualityNeed <-
-  metaLmerOut(
-    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "QualityRaw ~ CoreNeed"),
-    type = "REML", #"FE", 
-    name = "TheoryQualityCore",
-    title = "Quality ~ CoreNeed"
-  )
-
-TheoryMetaAttitudeNeed <-
-  metaLmerOut(
-    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed"),
-    type = "REML", #"FE", 
-    name = "TheoryAttitudeCore",
-    title = "Attitude ~ CoreNeed"
-  )
-
-TheoryMetaAttitudeNeedQuality <-
-  metaLmerOut(
-    lmerDataTbl = theoryMetaTblNoAllport %>% filter(formula == "Attitude ~ CoreNeed + Quality"),
-    type = "REML", #"FE", 
-    name = "TheoryAttitudeCoreQuality",
-    title = "Attitude ~ CoreNeed + Quality"
-  )
-```
-
-```{theoryForestPltComb, include=FALSE}
-effTheory <- rbind(
-  TheoryMetaQualityNeed$eff %>%
-    filter(coef != "(Intercept)") %>%
-    mutate(analysis = "(A) Quality ~ Core Need",
-           metaId = paste(coef, analysis, sep = ".")) %>%
-    as.data.frame,
-  TheoryMetaAttitudeNeed$eff %>%
-    mutate(analysis = "(B) Attitude ~ Core Need",
-           metaId = paste(coef, analysis, sep = ".")) %>%
-    as.data.frame,
-  TheoryMetaAttitudeNeedQuality$eff %>%
-    mutate(analysis = "(C) Attitude ~ Core Need + Quality",
-           metaId = paste(coef, analysis, sep = ".")) %>%
-    as.data.frame
-)
-
-metaSubForest(effTheory, 
-              title = "Meta Analysis: Forest Plot Core Need Fulfillment \n[Parametric]",
-              filename = "TheoryComb",
-              addAbove = 5,
-              type = "REML",
-              width = 600,
-              height = 600)
-```
 
@@
 ```
-
-```{r Export Path Models}
-save(shortMdlPath, 
-     file = "data/theoryMdlTabl.RData")
-```
-
-```{r OsfExport, include=FALSE}
-# export individual minimal CSV files 
-# STUDY 1:
-write.csv(
-  dtWorkerSupp$workerInteractionType %>%
-    select(
-      "PID",
-      "keyMotiveFulfilled",
-      "competence.daily.all",
-      "autonomy.daily.all",
-      "relatedness.daily.all",
-      "thermometerDutch_1",
-      "keymotive_fulfillemt_1",
-      "competence_1",
-      "autonomy_1",
-      "relatedness_1",
-      "quality_overall_1",
-      "OutgroupInteraction",
-      "NonOutgroupInteraction"
-    ),
-  file = "OSF Files/Data/Study1_minimal.csv"
-)
-
-#STUDY 2:
-write.csv(
-  dtStudentSupp$studentInteractionType %>%
-    select(
-      "PID",
-      "TIDnum",
-      "KeyNeedFullfillment",
-      "Competence",
-      "Autonomy",
-      "Relatedness",
-      "AttitudesDutch",
-      "quality_overall",
-      "OutgroupInteraction",
-      "NonOutgroupInteraction"
-    ),
-  file = "OSF Files/Data/Study2_minimal.csv"
-)
-
-# STUDY 3:
-write.csv(
-  dtMedicalSupp$medicalWithinBetween %>%
-    select(
-      "PID",
-      "TIDnum",
-      "OutgroupInteraction",
-      "NonOutgroupInteraction",
-      "AttitudesDutch",
-      "qualityOverall",
-      "AllportsCondition",
-      "KeyNeedFulfillment",
-      "Competence",
-      "Autonomy",
-      "Relatedness"
-    ),
-  file = "OSF Files/Data/Study3_minimal.csv"
-)
-
-# export joint minimal data as RData file 
-# create environment for joint export
-osfExport <- new.env()
-
-# STUDY 1:
-osfExport$dtWorkerSupp$workerInteractionType <- dtWorkerSupp$workerInteractionType %>%
-  select(
-    "PID",
-    "keyMotiveFulfilled",
-    "competence.daily.all",
-    "autonomy.daily.all",
-    "relatedness.daily.all",
-    "thermometerDutch_1",
-    "keymotive_fulfillemt_1",
-    "competence_1",
-    "autonomy_1",
-    "relatedness_1", 
-     "quality_overall_1", 
-    "OutgroupInteraction",
-    "NonOutgroupInteraction"
-  )
-
-osfExport$dtWorker$full <- dtWorker$full %>%
-  select(
-    "PID",
-    "thermometerDutch_1"
-  )
-
-osfExport$dtWorkerSupp$workerAvFreQual <- dtWorkerSupp$workerAvFreQual
-
-#STUDY 2:
-osfExport$dtStudentSupp$studentInteractionType <- dtStudentSupp$studentInteractionType %>%
-  select(
-    "PID",
-    "TIDnum", 
-    "KeyNeedFullfillment",
-    "Competence",
-    "Autonomy",
-    "Relatedness",
-    "AttitudesDutch",
-    "quality_overall",
-    "OutgroupInteraction",
-    "NonOutgroupInteraction"
-  )
-
-osfExport$dtStudents$full <- dtStudents$full %>%
-  select(
-    "PID",
-    "AttitudesDutch"
-  )
-
-osfExport$dtStudentSupp$studentOutgroupInteraction <- dtStudentSupp$studentOutgroupInteraction %>%
-  select(
-    "PID",
-    "AttitudesDutch"
-  )
-
-osfExport$dtStudentSupp$studentContactFreq <- dtStudentSupp$studentContactFreq
-
-osfExport$dtStudentSupp$studentPltIDs <- dtStudentSupp$studentPltIDs
-
-osfExport$dtStudentSupp$studentOutPltIDs <- dtStudentSupp$studentOutPltIDs
-
-# STUDY 3:
-osfExport$dtMedicalSupp$medicalWithinBetween <- dtMedicalSupp$medicalWithinBetween %>%
-  select(
-    "PID",
-    "TIDnum",
-    "OutgroupInteraction",
-    "OutgroupInteraction_cwc",
-    "OutgroupInteraction_zwc",
-    "NonOutgroupInteraction",
-    "NonOutgroupInteraction_cwc",
-    "NonOutgroupInteraction_zwc",
-    "AttitudesDutch",
-    "AttitudesDutch_cwc",
-    "AttitudesDutch_zwc",
-    "qualityOverall",
-    "qualityOverall_cwc",
-    "qualityOverall_zwc",
-    "AllportsCondition",
-    "AllportsCondition_cwc",
-    "AllportsCondition_zwc",
-    "KeyNeedFulfillment",
-    "KeyNeedFulfillment_cwc",
-    "KeyNeedFulfillment_zwc",
-    "Competence",
-    "Competence_cwc",
-    "Competence_zwc",
-    "Autonomy",
-    "Autonomy_cwc", 
-    "Autonomy_zwc", 
-    "Relatedness",
-    "Relatedness_cwc",
-    "Relatedness_zwc"
-  )
-
-osfExport$dtMedicalSupp$medicalOutWithinBetween <- dtMedicalSupp$medicalOutWithinBetween %>%
-  select(
-    "PID",
-    "TIDnum",
-    "AttitudesDutch",
-    "AttitudesDutch_cwc",
-    "AttitudesDutch_zwc",
-    "qualityOverall",
-    "qualityOverall_cwc",
-    "qualityOverall_zwc",
-    "AllportsCondition",
-    "AllportsCondition_cwc",
-    "AllportsCondition_zwc",
-    "KeyNeedFulfillment",
-    "KeyNeedFulfillment_cwc",
-    "KeyNeedFulfillment_zwc",
-    "Competence",
-    "Competence_cwc",
-    "Competence_zwc",
-    "Autonomy",
-    "Autonomy_cwc", 
-    "Autonomy_zwc", 
-    "Relatedness",
-    "Relatedness_cwc",
-    "Relatedness_zwc"
-  )
-
-osfExport$dtMedical$full <- dtMedical$full %>% 
-  select(
-    "PID",
-    "TIDnum",
-    "AttitudesDutch",
-    "OutgroupInteraction", 
-    "NonOutgroupInteraction",
-    "KeyNeedFulfillment",
-    "KeyNeedFulfillment_cwc",
-    "Competence",
-    "Autonomy", 
-    "Relatedness", 
-    "AllportsCondition", 
-    "qualityOverall"
-  )
-
-osfExport$dtMedicalSupp$medicalContactFreq <- dtMedicalSupp$medicalContactFreq
-
-osfExport$dtMedicalSupp$medicalPltIDs <- dtMedicalSupp$medicalPltIDs
-
-osfExport$dtMedicalSupp$medicalOutPltIDs <- dtMedicalSupp$medicalOutPltIDs
-
-# Export all relevant data for OSF
-save(list = ls(osfExport),
-     envir = osfExport,
-     file = "OSF Files/Data/wrangled.RData")
-```

### 2022-11-04 Robustness-Methods-and-Results.tex
robustness appendix added

--- 2022-10-23 Methods-and-Results.tex
@@
 \section{Study 1}
-
-Based on our main hypotheses, the aim of our first study was to
-specifically test the general contact hypothesis, the influence of core
-need fulfillment, and perceived interaction quality during intergroup
-contacts. To this aim, we conducted an intensive longitudinal survey
-study with recent migrants to the Netherlands. Data was collected from
-May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and
-all participants started the study within the first two days).
 
@@
 
-\subsubsection{Participants}
-
-After receiving ethical approval from the University Masked for Peer
-Review, we recruited 23 migrants using the local paid participant pool
-and specifically targeted non-Dutch migrants to participate in our
-study. Participants reported on their interactions for at least 30 days
-with two daily measures (capturing the morning and afternoon). With this
-design, we aimed at getting 50-60 measurements per participant
-(\textit{M} = 53.26, \textit{SD} = 16.72, \textit{total N} = 1,225).
-This is a common number of measurements found in experience sampling
-studies and offers sufficient power to model processes within and
-between participants
-\citep[e.g., for a systematic review see][]{AanhetRot2012}. Participants
-were compensated for their participation with up to 34 Euros -- each two
-Euros for pre- and post-questionnaire as well as 50 Eurocents for every
-experience sampling measurement occasion. The sample consisted of
-relatively young, educated, and western migrants from the global north
-(\(M_{age}\) = 24.35, \(SD_{age}\) = 4.73, 19 women, 15 students). The
-sample accurately describes the largest groups of migrants in the region
-\citep[][]{GemeenteGroningen2015}.
-
-\subsubsection{Procedure}
-
-The study itself consisted of three main parts, an introductory
-pre-measurement, and the daily experience sampling measurements, as well
-as a concluding post-measurement. After giving informed consent,
-participants started by filling in an online pre-questionnaire assessing
-demographics and general information about their immigration. Over the
-next thirty days, the participants were then invited twice a day (at 12
-pm and 7pm) to reflect upon their interactions, psychological need
-fulfillments, and current attitudes towards the Dutch outgroup
-(\textit{median duration} = 2M 22S, \textit{MAD duration} = 1M 19S).
-General compliance was high (85.90\% of all invited surveys were filled
-in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%).}.
-The response rates were approximately equal during mornings (\textit{n}
-= 621) and afternoons (\textit{n} = 604) and most measurements were
-completed within four hours of the invitation. After the final day of
-experience sampling measurements, participants were invited to fill in a
-longer post measurement survey that mirrored the pre-measurement. All
-key variables for this study were part of the short experience sampling
-surveys.
-
 \subsubsection{Materials}
 
-\paragraph{Intergroup Contact}
+\paragraph{General Psychological Needs}
 
-To test the prerequisite effect of intergroup contact, every experience
-sampling measurement started with the question
-``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''.
-Our participants recorded between 2--51 interactions with Dutch outgroup
-members (3.23--91.07\% of individual experience sampling measurements;
-387 of all 1,225 experience sampling
-responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts.
-These participants are removed from any analyses that focus on outgroup contacts.}.
-
-\paragraph{Psychological Needs}
-
-Irrespective of whether participants had an interaction with Dutch
-people or not, everyone answered a short series of questions on
-psychological need fulfillment. However, whereas participants with
-interactions reported on the need fulfillment during the interaction,
-people without interactions with Dutch people judged the past daytime
-period in general. To assess the fulfillment of psychological needs, we
-included two types of need measurement: (1) the core situational need
-and (2) general self-determination theory needs.
-
-For the core situational need, we asked participants in an open ended
-text field:
-``\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}''.
-Then, with reference to the text entry, we asked how much this core need
-was fulfilled during the interaction or the past daytime period:
-``\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}''
-on a continuous slider scale ranging from strongly disagree (-50) to
-strongly agree (+50).
-
-We, additionally, included a common measure of three self-determination
-theory needs \citep[see][]{Downie2008}. The items were introduced either
-by ``\textit{During the interaction:}'' or
+In addition to the intergroup contact dummy and situational core need
+reported in the main text, we included a common measure of three
+self-determination theory needs \citep[see][]{Downie2008}. The items
+were introduced either by ``\textit{During the interaction:}'' or
 ``\textit{This morning [/afternoon]:}'' and measured autonomy
@@
 
-\paragraph{Perceived Interaction Quality}
-
-As an explanatory mechanism, we assessed ratings of the perceived
-interaction quality. As our main measurement, participants rated the
-statement ``\textit{Overall the interaction was …}'' on two continuous
-slider scales measuring pleasantness
-\citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
-
-\paragraph{Outgroup Attitudes}
-
-At the end of every experience sampling measurement we asked all
-participants about their current attitudes towards the Dutch -- our main
-dependent variable. To assess the momentary outgroup evaluation we used
-the common feeling thermometer: ``How favorable do you feel towards the
-Dutch?'' \citep[][]{Lavrakas2008}. Participants then rated their
-attitude on a continuous slider scale from ``very cold -- 0'' through
-``no feeling -- 50'' to ``very warm -- 100''. Both the question phrasing
-as well as the tick labels were consistent with large-scale panel
-surveys \citep[e.g.,][]{DeBell2010}.
-
 \subsection{Results}
-
-\subsubsection{Contact Hypothesis}
-
-We used a multilevel regression to check whether having an interaction
-with an outgroup member had a situational (i.e., contemporaneous) effect
-within the participants. We find that having an outgroup contact is
-indeed associated with significantly more positive outgroup attitudes
-within the participants (\textit{b} = 2.48, \textit{t}(1,200) = 4.37,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}1.37, 3.59{]}), even
-after controlling for having an interaction with a non-Dutch (which did
-not relate to outgroup attitudes independently). Additionally, while
-multi-level regressions are generally robust against unequal cell sizes,
-we correct for inequalities by use centered predictors and reintroducing
-the means as level two predictors. Nonetheless, we also offer an
-analysis of the joint data sets in Online Supplemental Material A (for
-full results see Table \ref{tab:intergroupGeneralTblLong}, Figure
-\ref{fig:ContactHypothesis}, and Online Supplementary Material
-A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
-This is unusual and might indicate that the effect is very consistent across participants.
-However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}.
-Thus, in our first data we find initial evidence that outgroup contacts
-show a positive effect on outgroup attitudes within real-life data.
-While this offers support for the most basic premise of the intergroup
-contact hypothesis (i.e., that any interaction will lead to more
-positive outgroup attitudes), this analysis does not consider any notion
-of interaction quality. We assess the conditional effects of interaction
-numbers and interaction quality ratings after we report on the
-individual studies to avoid under-powered analyses.
-
-\subsubsection{Core Need}
-
-The main proposal of our article is that the success of an outgroup
-contact might be explained by whether or not the contact fulfilled the
-person's core situational need. This should, in turn, be due to a higher
-perceived contact quality. We sequentially test whether the fulfillment
-of the core need during an interaction is (1) related to more positive
-outgroup attitudes, (2) higher perceived contact quality, and (3)
-whether the variance explained by the core need is subsumed by the
-perceived contact quality if considered jointly (for full regression
-results see Table \ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment}).
-
-We find that in the multilevel models, the fulfillment of core
-situational needs during outgroup contacts was associated with more
-positive outgroup attitudes (random slopes model; \textit{b} = 0.17,
-\textit{t}(365) = 2.93, \textit{p} = 0.004, \textit{95\%CI}{[}0.06,
-0.29{]}) and also predicted higher perceived contact quality (random
-intercept model; \textit{b} = 0.42, \textit{t}(365) = 8.07, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}0.32, 0.52{]}). Moreover, when we
-consider the influences of core need fulfillment and contact quality on
-outgroup attitudes jointly, we find that virtually all variance is
-explained by perceived contact quality (random slopes mode; \textit{b} =
-0.23, \textit{t}(364) = 4.22, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
-still explained by core need fulfillment (\textit{b} = 0.04,
-\textit{t}(364) = 0.64, \textit{p} = 0.523, \textit{95\%CI}{[}-0.08,
-0.15{]}). We thus find support for our hypotheses and can conclude that
-in this data set the fulfillment of core situational needs had a
-significant influence on outgroup attitudes. Additionally, this effect
-is likely explained by its effect through perceived contact quality.
-
-\subsubsection{Robustness}
 
@@
 
-The aim of Study 2 is similar to Study 1, as we again test the general
-contact hypothesis, the influence of core need fulfillment, and
-perceived contact quality during intergroup contacts. However, in this
-second study we collected a substantially larger sample of international
-students who recently arrived in the Netherlands and also improved the
-study design (e.g., pop-up explanations described later). The survey
-method again offers a large body of ecologically valid data on need
-satisfaction in real-life intergroup contact situations as these
-students will likely interact with the Dutch majority outgroup on a
-daily basis. Data was collected from November 19\textsuperscript{th},
-2018 through January 6\textsuperscript{th}, 2019.
-
-The full surveys are available in our OSF repository
-\citep{KreienkampMasked2022a} and the full data description is available
-in Online Supplementary Material A. Correlations and descriptive
-statistics of the included variables are available in Table
-\ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
-
 \subsection{Methods}
-
-\subsubsection{Participants}
-
-We recruited 113 international students using a local participant pool.
-We specifically targeted non-Dutch students, who had recently arrived in
-the Netherlands. Participants reported on their interactions for at
-least 30 days with two daily measures (capturing the morning and
-afternoon). With this design, we again aimed at receiving 50-60
-measurements per participant (\textit{M} = 43.94, \textit{SD} = 15.00,
-\textit{total N} = 4,965). As with the previous study this should offer
-sufficient power to model processes within participants and will lend
-stronger weight to between-participant results. Participants were
-compensated for their participation with partial course credits ---
-depending on their participation. The sample consisted of relatively
-young migrants, who were mostly from the global north (\(M_{age}\) =
-20.24, \(SD_{age}\) = 2.12, 84 women). The sample fairly accurately
-describes the local population of international students.
-
-\subsubsection{Procedure}
-
-The study procedure mirrored the setup of Study 1 and consisted of pre-,
-experience sampling-, and post-measurements. The participants were
-invited for experience sampling measurements twice a day (at 12 pm and
-7pm) for 30 days (\textit{median duration} = 3M 46S,
-\textit{MAD duration} = 1M 54S). General compliance was high (70.87\% of
-all invited surveys were filled in). The response rates were
-approximately equal during mornings (\textit{n} = 2,608) and afternoons
-(\textit{n} = 2,357). All key variables for this study were part of the
-short experience sampling surveys.
 
@@
 
-\paragraph{Intergroup Contact}
-
-To measure intergroup contacts, every experience sampling measurement
-started with the question
-``\textit{Did you meet a Dutch person this morning [/afternoon]? (in-person interaction for at least 10 minutes)}''.
-Participants were additionally offered a pop-up explanation: ``With
-in-person interaction, we mean a continued interaction with another
-person (potentially in a group) that lasted at least 10 minutes. This
-interaction should be offline and face-to-face. It should include some
-form of verbal communication and should be uninterrupted to still count
-as the same interaction. Any individual interaction can last minutes or
-hours. If there were multiple interaction partners, we would like you to
-focus on the person that was most important to you during the
-interaction.''. The participants recorded between 1--43 interactions
-with Dutch majority people (1.64--93.75\% of individual experience
-sampling measurements; 935 of all 4,965 experience sampling responses).
-
-\paragraph{Psychological Needs}
-
-For the core situational need, we asked participants in an open ended
-text field:
-``\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}''
-(where \textit{-X-} was dynamically replaced with the name of the
-interaction partner). Participants could additionally click on a pop-up
-explanation: ``Your main goal during an interaction can vary depending
-on the interaction. It could be to connect with friends, to find or
-provide help, to achieve academic ambitions, work on your fitness, work
-for a job, or simply to get a coffee, just as well as many other
-concrete or abstract goals that are import to you in the moment. It
-really depends on your subjective experience of the interaction.''.
-Then, with reference to the text entry, we asked how much this core need
-was fulfilled during the interaction or the past daytime period:
-``\textit{During your interaction with -X- [this morning / this evening] your goal (-previous text entry-) was fulfilled.}''
-on a continuous slider scale ranging from strongly disagree (1) to
-strongly agree (100).
+\paragraph{General Psychological Needs}
 
@@
 
-\paragraph{Perceived Interaction Quality}
-
-The ratings of the perceived contact quality was identical to Study 1.
-
-\paragraph{Outgroup Attitudes}
-
-As in Study 1, attitudes towards the Dutch majority outgroup were again
-measured using the feeling thermometer. All survey details are also
-available in our OSF repository \citep{KreienkampMasked2022a} and Online
-Supplemental Materials A.
-
 \subsection{Results}
-
-\subsubsection{Contact Hypothesis}
-
-We tested the most general contact hypothesis as we did for Study 1. We,
-again, used a multilevel regression analysis to check whether having an
-interaction with an outgroup member had a situational (i.e.,
-contemporaneous) effect within the participants. We find that having an
-outgroup interaction is indeed associated with significantly more
-positive outgroup attitudes within the participants (random slopes
-model; \textit{b} = 2.83, \textit{t}(4,850) = 3.57, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}1.28, 4.38{]}), even after
-controlling for having an interaction with a non-Dutch person (which did
-not relate to outgroup attitudes independently). We again added the
-participant means back into the model. Because these are the means of
-the contact dummy variables they are the proportion of measurements that
-included a particular contact. This not only adjusts the model for
-unequal cell sizes but allows us to see whether between subject
-differences in the relative number of interactions had an effect on
-outgroup attitudes. We find that in this data set participant-level
-outgroup contact proportions were also a positive predictor of outgroup
-attitudes (\textit{b} = 26.55, \textit{t}(110) = 2.90, \textit{p} =
-0.004, \textit{95\%CI}{[}8.61, 44.46{]}). The relative number of
-non-outgroup interactions showed no such effect (for full results see
-Table \ref{tab:intergroupGeneralTblLong}, Figure
-\ref{fig:ContactHypothesis}, as well as Online Supplementary Material
-A). Thus, in our second data set we find that outgroup contacts show a
-positive effect on outgroup attitudes in the moment and on average
-between participants.
-
-\subsubsection{Core Need}
-
-We again sequentially tested whether the fulfillment of the core need
-during an interaction was (1) related to more positive outgroup
-attitudes, (2) higher perceived interaction quality, and (3) whether the
-variance explained by the core need is subsumed by the perceived
-interaction quality if considered jointly. We find that in the
-multilevel models, the fulfillment of core situational needs during
-outgroup contacts was associated with more positive outgroup attitudes
-(random slopes model; \textit{b} = 0.13, \textit{t}(826) = 4.18,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.19{]}) and also
-predicted higher perceived interaction quality (random slopes model;
-\textit{b} = 0.40, \textit{t}(826) = 6.46, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.28, 0.52{]}). Additionally, if we consider the
-influences of core need fulfillment and interaction quality on outgroup
-attitudes jointly, we find that virtually all variance is explained by
-perceived interaction quality (random slopes mode; \textit{b} = 0.17,
-\textit{t}(825) = 5.56, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.11, 0.23{]}) and only little unique variance is
-still explained by core need fulfillment (\textit{b} = 0.03,
-\textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
-0.07{]}; also see Table \ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment} for full results). These results are
-consistent with the results in Study 1. We, thus, find support for our
-hypotheses that the fulfillment of core situational needs had a
-significant influence on outgroup attitudes and that this effect is
-likely explained by its effect through perceived interaction quality.
 
@@
 
-We again checked for alternative models. First, when considering
-generalized situational core need fulfillment together with whether an
-intergroup contact took place, we find that there is only a minuscule
-main effect of core need fulfillment (random slopes model; \textit{b} =
--0.03, \textit{t}(4,849) = -1.34, \textit{p} = 0.181,
+Also for Study 2, we checked for alternative models. First, when
+considering generalized situational core need fulfillment together with
+whether an intergroup contact took place, we find that there is only a
+minuscule main effect of core need fulfillment (random slopes model;
+\textit{b} = -0.03, \textit{t}(4,849) = -1.34, \textit{p} = 0.181,
 \textit{95\%CI}{[}-0.08, 0.02{]}) but a stronger interaction effect of
@@
 
-The aim of this final study is to extend the previous studies by
-additionally testing Allport's conditions in an extensive longitudinal
-design and to compare the predictive powers of Allport's conditions and
-the core situational need fulfillment. We will, thus, again test the
-general contact hypothesis, the influence of core need fulfillment, and
-perceived interaction quality during intergroup contacts. However, we
-additionally have the opportunity to also assess the role of Allport's
-conditions in this and to compare the two approaches (Allport's
-conditions and core need fulfillment) directly.
-
-For this study, we specifically recruited international medical
-students, because they represent a particular group of migrants who face
-structural requirements to integrate and interact with Dutch majority
-outgroup members on a daily basis. As part of their educational program,
-the migrants are required to take language courses and interact with
-patients as part of their medical internships and medical residency. The
-extensive longitudinal survey method again offers a large body of
-ecologically valid data on need satisfaction in real-life intergroup
-contact situations. Data were collected from November
-8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020.
-
-The full surveys are available in our OSF repository
-\citep{KreienkampMasked2022a} and the full data description is available
-in Online Supplementary Material A. Correlations and descriptive
-statistics of the included variables are available in Tables
-\ref{tab:descrFullWide} and \ref{tab:descrOutWide}.
-
 \subsection{Methods}
-
-\subsubsection{Participants}
-
-We recruited 71 international medical students using contacts within the
-University Medical School. We specifically targeted non-Dutch students,
-who had recently arrived in the Netherlands. Participants reported on
-their interactions for at least 30 days with two daily measures
-(capturing the morning and afternoon). With this design, we aimed at
-getting 50-60 measurements per participant (\textit{M} = 57.85,
-\textit{SD} = 20.68, \textit{total N} = 4,107). As with the previous
-studies, this should offer sufficient power to model processes within
-participants and will lend stronger weight to between-participant
-results. Participants were compensated for their participation in the
-same manner as during Study 1. The sample consisted of relatively young
-migrants, who were mostly from the global north (\(M_{age}\) = 22.68,
-\(SD_{age}\) = 3.10, 59 women). The sample fairly accurately describes
-the local population of young international medical professionals.
-
-\subsubsection{Procedure}
-
-The study procedure mirrored the setup of studies one and two, in that
-it consisted of pre-, experience sampling-, and post-measurement. The
-participants were invited for experience sampling measurements twice a
-day (at 12 pm and 7pm) for 30 days (\textit{median duration} = 4M 13S,
-\textit{MAD duration} = 2M 6S). General compliance was high (85.92\%
-filled in at least 31 experience sampling surveys or more). The response
-rates were approximately equal during mornings (\textit{n} = 2,092) and
-afternoons (\textit{n} = 2,015). All key variables for this study were
-part of the short experience sampling surveys.
 
@@
 
-\paragraph{Intergroup Contact}
+\paragraph{General Psychological Needs}
 
-The measurement of intergroup contacts was identical to Study 2. The
-participants recorded between 1--71 interactions with Dutch outgroup
-members (2.13--87.18\% of individual experience sampling measurements;
-1,702 of all 4,107 experience sampling responses).
-
-\paragraph{Psychological Needs}
-
-The measurement of the core situational need and its fulfillment was
-identical to Study 2. Similarly, the measurement of the
-self-determination needs was identical to Studies 1 and 2
-
-\paragraph{Allport's Conditions}
-
-We measured how much each of the interactions fulfilled Allport's
-conditions of optimal contact using a common short scale comprised of
-four attributes \citep{Islam1993, Voci2003, AlRamiah2012a, Dixon2005}.
-In particular, we asked participants to rate how much the interaction
-had equal status
-(``\textit{The interaction with [name interaction partner] was on equal footing (same status)}''),
-a common goal
-(``\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}''),
-support of authorities
-(``\textit{The interaction with [name interaction partner] was voluntary}''),
-and intergroup cooperation
-(``\textit{The interaction with [name interaction partner] was cooperative}'').
-We create a mean-averaged index of Allport's conditions in response to
-past findings indicating that the conditions are best conceptualized
-jointly and as functioning together rather than as fully independent
-factors \citep[][, p. 766]{Pettigrew2006}. For full psychometric
-information see Online Supplementary Material A.
-
-\paragraph{Perceived Interaction Quality}
-
-The ratings of the perceived interaction quality was identical to Study
-1.
-
-\paragraph{Outgroup Attitudes}
-
-Attitudes towards the Dutch majority outgroup was again measured using
-the feeling thermometer, as in studies one and two. All survey details
-are also available in our OSF repository \citep{KreienkampMasked2022a}
-and Online Supplemental Materials A.
+The measurement of the self-determination needs was identical to Studies
+1 and 2.
 
@@
 
-\subsubsection{Contact Hypothesis}
-
-Additionally, in a multilevel regression to check for contemporaneous
-within person effects, we found that having an outgroup interaction was
-indeed associated with significantly more positive outgroup attitudes
-within the participants (random slopes model; \textit{b} = 5.57,
-\textit{t}(3,834) = 6.52, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}3.90, 7.23{]}), even after controlling for having an
-interaction with a non-Dutch (which did not relate to outgroup attitudes
-independently; for full results see Table
-\ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis},
-and Online Supplementary Material A). Thus, in our third data set we
-found within person contemporaneous effect of intergroup contact was
-consistent across all three studies.
-
-\subsubsection{Allport's Conditions}
-
-As we did with core need fulfillment in previous studies, we
-sequentially tested whether the fulfillment of Allport's contact
-conditions was (1) related to more positive outgroup attitudes, (2)
-higher perceived interaction quality, and (3) whether the variance
-explained by Allport's Conditions is assumed by the perceived
-interaction quality if considered jointly. In the multilevel models we
-find that the fulfillment of Allport's Conditions during outgroup
-contacts was associated with more positive outgroup attitudes (random
-slopes model; \textit{b} = 0.22, \textit{t}(1,601) = 5.86, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}0.15, 0.29{]}) and also predicted
-higher perceived interaction quality (random slopes model; \textit{b} =
-0.65, \textit{t}(1,605) = 11.82, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we consider the
-influences of Allport's Conditions and interaction quality on outgroup
-attitudes jointly, we find that perceived interaction quality is a
-substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
-\textit{t}(1,600) = 6.25, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
-Allport's Conditions was less than half of its original effect size
-(\textit{b} = 0.09, \textit{t}(1,600) = 2.89, \textit{p} = 0.004,
-\textit{95\%CI}{[}0.03, 0.15{]}; also see Table
-\ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment}). These results indicate that in this
-data set the fulfillment of Allport's conditions had a significant
-influence on outgroup attitudes and this effect is likely, in parts,
-explained by its effect through perceived interaction quality.
-
-\subsubsection{Core Need}
-
-Similarly, we again sequentially tested whether the fulfillment of the
-core need during an interaction was (1) related to more positive
-outgroup attitudes, (2) higher perceived interaction quality, and (3)
-whether the variance explained by the core need is assumed by the
-perceived interaction quality if considered jointly. We find that the
-fulfillment of the core need during outgroup contacts was associated
-with more positive outgroup attitudes (random slopes model; \textit{b} =
-0.19, \textit{t}(1,601) = 5.29, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.27{]}) and also predicted higher perceived
-interaction quality (random slopes model; \textit{b} = 0.43,
-\textit{t}(1,605) = 8.35, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.33, 0.54{]}). Additionally, once we consider the
-influences of core need fulfillment and interaction quality on outgroup
-attitudes jointly, we find that perceived interaction quality is a
-substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
-\textit{t}(1,600) = 6.86, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.22{]}) and the unique variance explained by
-core need fulfillment was roughly half of its original effect size
-(\textit{b} = 0.11, \textit{t}(1,600) = 3.50, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}0.05, 0.17{]}; for full results see Table
-\ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment}). These results indicate that in this
-data set outgroup attitudes were significantly predicted by the
-fulfillment of core situational needs and this effect partially emerged
-via its effect on perceived interaction quality.
-
-\subsubsection{Compare Fulfillment of Core Need and Allport's Conditions}
-
-To test wether Allport's conditions or the core need fulfillment are
-better at predicting outgroup attitudes, we first assess relative model
-performance indices (i.e., Akaike information criterion, and Bayesian
-information criterion), and then consider the two predictors in a joint
-model to see whether the two approaches predict the same variance in
-outgroup attitudes. When comparing the model selection indices we find
-that the fulfillment of the situational core need, indeed performs
-slightly better than the model using Allport's conditions
-(\(AIC_{CoreNeed}\) 12632.02 \textless{} 12651.59 \(AIC_{Allport}\), and
-\(BIC_{CoreNeed}\) 12664.55 \textless{} 12684.12 \(BIC_{Allport}\)).
-Additionally, when considering the predictors jointly, we find that both
-significantly predict outgroup attitudes with similar sized regression
-parameters (random slopes model; Allport's Conditions: \textit{b} =
-0.16, \textit{t}(1,600) = 4.92, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.09, 0.24{]}, Core Need: \textit{b} = 0.14,
-\textit{t}(1,600) = 3.85, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.08, 0.17{]}; also see Table
-\ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment}). This indicates that, although both
-Allport's conditions and the core need fulfillment seem to (in part)
-work through perceived interaction quality, they explain different
-aspects of the variance in outgroup attitudes and do not constitute one
-another.
-
 \subsubsection{Robustness}
 
-We again checked for alternative models of the key need fulfillment.
-First, when considering generalized situational core need fulfillment
-together with whether an intergroup contact took place, we find that
-there is no significant main effect of core need fulfillment (random
-slopes model; \textit{b} = 0.03, \textit{t}(3,835) = 1.51, \textit{p} =
-0.131, \textit{95\%CI}{[}-0.01, 0.06{]}) but a stronger interaction
-effect of core need fulfillment and outgroup contact (\textit{b} = 0.17,
-\textit{t}(3,835) = 7.32, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.21{]}). Together with a significant main
-effect of having an outgroup contact (\textit{b} = 5.41,
-\textit{t}(3,835) = 6.36, \textit{p} \textless{} .001,
+As with the previous two studies, we checked for alternative models of
+the key need fulfillment. First, when considering generalized
+situational core need fulfillment together with whether an intergroup
+contact took place, we find that there is no significant main effect of
+core need fulfillment (random slopes model; \textit{b} = 0.03,
+\textit{t}(3,835) = 1.51, \textit{p} = 0.131, \textit{95\%CI}{[}-0.01,
+0.06{]}) but a stronger interaction effect of core need fulfillment and
+outgroup contact (\textit{b} = 0.17, \textit{t}(3,835) = 7.32,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.12, 0.21{]}). Together
+with a significant main effect of having an outgroup contact (\textit{b}
+= 5.41, \textit{t}(3,835) = 6.36, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}3.74, 7.08{]}), this indicates that it is not key need
@@
 positive outgroup attitudes.
-
-\section{Embeddedness and Stability across Studies}
-
-\begin{center}
-    \noindent\rule{8cm}{0.4pt}\\
-    \hl{\textit{New Section:}}\\
-    \vspace{-0.25cm}
-    \noindent\rule{8cm}{0.4pt}
-\end{center}
-
-Introduction sentence
-
-\hl{maybe move this first paragraph to the end?}
-\subsection{Stability}
-
-We begin by assessing the stability of our main analyses across the
-three studies. To do so, we plot the effect sizes of each parameter of
-interest in a forest plot. Forest plots are a popular form of evidence
-synthesis and are commonly found within meta-analytic efforts. By
-plotting a standardized effect size and confidence interval of key
-parameters for each study, forest plots offer a visual method of
-identifying broader patterns across studies. This affords users a chance
-to spot stable as well as unreliable effects more easily. While not the
-focus of our efforts here, forest plots are commonly accompanied with a
-meta-analytic effect size that summarizes the effect size across
-studies.
-
-We assess forest plots of the basic contact hypothesis test (Figure
-\ref{fig:ContactHypothesis}), the core need fulfillment proposal (Figure
-\ref{fig:AllportNeedFulfillment}), as well as the robustness analyses
-(Figure \ref{fig:Robustness}). For the basic contact hypothesis test we
-see that outgroup contact has a strong and consistent effect on outgroup
-attitudes while interactions with non-outgroup members consistently have
-no meaningful effect on outgroup attitudes. While this would be expected
-from the general intergroup contact literature, this is not a trivial
-finding. We are among the first to assess the contact hypothesis using
-real-life data from intensive longitudinal data and these close to event
-assessments are comparable but not equivalent to the assessments found
-in cross-sectional data (also see below). When looking at Figure
-\ref{fig:AllportNeedFulfillment}, we see that the fulfillment of core
-needs during intergroup contacts is consistently a meaningful predictor
-of outgroup attitudes and interaction quality perceptions (see Figure
-\ref{fig:AllportNeedFulfillment} A and B). We also see that the effect
-of core need fulfillment on outgroup attitudes is strongly reduced when
-modeled together with interaction quality perceptions, supporting our
-assertion that interaction quality offers a psychological mechanism for
-the direct effect. Additionally, the core need fulfillment is also
-consistently outgroup contact specific (Figure \ref{fig:Robustness} A)
-and remains a meaningful predictor of outgroup attitudes even when
-controlling for traditional psychological need fulfillments (Figure
-\ref{fig:Robustness} B).
-
-\subsection{General contact hypothesis}
-
-During the main analyses, we have thus far shown that participants held
-more positive outgroup attitudes following intergroup contacts and that
-a perceived interaction quality was associated with more positive
-outgroup attitudes following an intergroup contact. We have, however,
-not brought the two elements of the contact hypothesis together in a
-single analysis. This is mainly due to the difficulty that interaction
-quality ratings are only possible when participants had an interaction
---- which means that the two factors cannot be assessed in a multilevel
-analysis that models individual measurement occasions. This has not been
-an issue in the past literature because experimental and cross-sectional
-data collections have only considered cases in which intergroup contacts
-were present. Outside of the lab, the most common method has been to ask
-participants to recall how many interactions they had over the past
-month, how positive these interactions were, and how positive they feel
-towards the outgroup in general. The effects of intergroup contacts,
-interaction quality, and outgroup attitudes are thus aggregated by the
-participant in a cognitive recall aggregation. Intensive longitudinal
-data also allows for aggregation of all three variables, with the
-differences that the measurements are aggregated from individual reports
-that are close to the actual experience. However, this aggregation
-process summarizes the dense multitude of measurement occasions as
-single summary statistics per participants. This by extension means that
-we face statistical power restrictions on the person level and have this
-decided to only present this analysis based on a combined data set of
-all three studies.
-
-We thus run a linear regression model where average outgroup attitudes
-are predicted by the number of interactions and the average interaction
-quality ratings of all participants across the three studies. We do so
-while controlling for the possible effects of study-specific
-differences. To include the study-membership as a control variable, we
-use the student sample (Study 2) as the reference group because it is
-both the largest and the most homogeneous study. Looking at the overall
-model, we find that the model predicts a statistically significant
-amount of variance in average outgroup attitudes (\textit{F}(9, 195) =
-2.64, \textit{p} = 0.007, \textit{R\textsuperscript{2}} = 0.11). Looking
-at the individual effects, we find that only the number of outgroup
-interactions is associated with average outgroup attitudes (\textit{b} =
-0.74, \textit{t}(195) = 3.56, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.33, 1.14{]}). Neither the average interaction
-quality perceptions nor an interaction of amount and quality of contact
-are meaningful or significant predictors of average outgroup attitudes
-(both \textit{b} \textless0.22 and \textit{p} \textgreater{} .201). In
-short, participants who on average had more positive interactions were
-not statistically more likely to show higher average outgroup attitudes.
-This result is surprising because it contradicts the tenet of the
-intergroup contact hypothesis that intergroup contact depends on
-positive contact. Additionally, the aggregated results contradict the
-results of our own multi-level regressions, where we have shown that the
-positive effect of individual outgroup interactions dependent on
-interaction quality perceptions.
-
-\subsection{Contact key need content}
-
-Because our participants jointly reported on several thousands of
-intergroup contacts, it would not be feasible to analyse these
-qualitative responses in a traditional qualitative content analysis. We
-instead rely on recent machine learning advances within the natural
-language processing domain. For our analysis we use the BERT language
-model. BERT (Bidirectional Encoder Representations from Transformers)
-was developed by Google in 2018 and today forms a key elements of many
-natural language processing workflows. In its essence, BERT is a
-framework that allows users to codify every word in relation to every
-other word within a large set of documents. This task is immensely
-computationally intensive and most users of the framework don't create
-their own model. We use the ``all-mpnet-base-v2'' language model for our
-embedding. The model is a community-based version of BERT that uses
-Microsoft's ``mpnet-base'' model and is fine-tuned with 1 Billion
-diverse sentence pairs. The model was trained with a 768 dimensional
-dense vector space (a relatively high number) to represent every word.
-As a result, the model is widely considered to be one of the most
-accurate all-purpose language models within the open-source BERT
-framework. We extracted 47 topics from the 2,983 interaction goal
-free-text entries --- a relatively large number of topics. The higher
-number of topics allows us to retain more of the smaller topics and
-leaves a relatively low number of 308 free-text entries unclassified
-(16.64\%). A full write up of the topic modeling process is available in
-Online Supplemental Material C.
-
-In terms of the content of the topics, we find that a number of topics
-are primarily task-oriented, where participants hope to increase their
-study, research, presentation, or work performance. Opposing the task
-and work oriented needs, are a wide variety of leisure-related wishes.
-Specifically, relaxation and entertainment wishes were prominent terms
-across several topics. Additionally, a number of clusters is primarily
-relationship-oriented, so that participants sought contact with outgroup
-members for intimate and casual social contact in itself. Similarly,
-socializing and celebrations were also explicit social needs (incl.,
-parties). Another set of topics was more practically oriented, when
-participants sought to share food and cook cook together, or had
-organizational needs (e.g., housing, cleaning, and living).
-
-A reasonable set of contact goals were specifically migration specific
-(e.g., wish to learn about culture, politics, and language) or were
-concerned inquiry and information needs more generally (e.g., seeking
-answers, banking information). A further set of topics was specifically
-geared towards a wish to experience cultural products (e.g., music,
-theater, food). Similarly, a number of participants had travel related
-goals in their interactions with the majority group members.
-
-One interesting observation was the importance of contact goals specific
-to contact through the medical and public health system. This goal type
-was partly specific to our young medical professionals sample (e.g.,
-working with patients, treatment), but also more broadly interactions of
-newcomers with the outgroup majority as patients themselves (e.g.,
-therapeutic goals). Also health, fitness, and personal improvement goals
-(e.g., sports and music) were common goals that participants shared
-during the interactions with the majority group members. A final also
-under-explored topic is that of spiritual, religious, and otherwise
-transcendental needs (incl.~meditation, prayer, religious services).
-This seems to offer a deep and fundamental need that is mostly ignored
-in western secular migrant research.
-
-Thus while, medical and spiritual interaction goals were more
-unexpected, almost all other extracted topics fall into broader or
-narrower need concepts that are commonly discussed within the
-psychological needs literature. Something about need theories/models
-plus our own review article.

### 2022-11-04 Full-Methods-and-Results.Rmd
app headings adjusted

--- 2022-10-29 Methods-and-Results.Rmd
@@
   pack_rows("Study 3: Needs & Allport", 17, 20)  %>%
+  kableExtra::footnote(
+    .,
+    general = c("**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"), 
+    escape = FALSE
+  ) %>%
   kable_styling(latex_options = "scale_down") %>%

### 2022-11-04 Robustness-Methods-and-Results.Rmd
app headings adjusted

@@
 
-\section{Study 1}
-
 The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
@@
 
-\subsection{Methods}
+\subsection{Additional Materials}
+
+In addition to the measurement of whether or not participants had an intergroup interaction and their situational core need fulfillment, we also measured a set of general psychological needs.
+
+\subsubsection{General Psychological Needs} In addition to the intergroup contact dummy and situational core need reported in the main text, we included a common measure of three self-determination theory needs \citep[see][]{Downie2008}.
+The measurement was identical in all three studies.
+The items were introduced either by “\textit{During the interaction:}” or “\textit{This morning [/afternoon]:}” and measured autonomy (“\textit{I was myself.}”), competence (“\textit{I felt competent.}”), and relatedness (without intergroup contact “\textit{I had a strong need to belong}”; with intergroup contact: “\textit{I shared information about myself.}” and “\textit{The other(s) shared information about themselves.}”).
+All items were rated on a continuous slider scale from very little (-50) to a great deal (+50).
+
+\subsection{Study 1}
 
@@
 
-\subsubsection{Materials}
-
-\paragraph{General Psychological Needs} In addition to the intergroup contact dummy and situational core need reported in the main text, we included a common measure of three self-determination theory needs \citep[see][]{Downie2008}.
-The items were introduced either by “\textit{During the interaction:}” or “\textit{This morning [/afternoon]:}” and measured autonomy (“\textit{I was myself.}”), competence (“\textit{I felt competent.}”), and relatedness (without intergroup contact “\textit{I had a strong need to belong}”; with intergroup contact: “\textit{I shared information about myself.}” and “\textit{The other(s) shared information about themselves.}”).
-All items were rated on a continuous slider scale from very little (-50) to a great deal (+50).
-
-\subsection{Results}
+\subsubsection{Results}
 
@@
 
-\section{Study 2}
-
-\subsection{Methods}
+\subsection{Study 2}
 
@@
 
-\subsubsection{Materials}
-
-\paragraph{General Psychological Needs} The measurement of the self-determination needs was identical to Study 1.
-
-\subsection{Results}
+\subsubsection{Results}
+
 ```{r studentModelOlsAttFreqQual, include=FALSE}
@@
 
-\subsubsection{Robustness}
 ```{r studentModelInterceptAttCoreInt, include=FALSE}
@@
 
-\section{Study 3}
-
-\subsection{Methods}
+\subsection{Study 3}
 
@@
 
-\subsubsection{Materials}
-
-\paragraph{General Psychological Needs} The measurement of the self-determination needs was identical to Studies 1 and 2.
-
-\subsection{Results}
+\subsubsection{Results}
 
@@
 ```
-
-\subsubsection{Robustness}
 

### 2022-11-04 Robustness-Methods-and-Results.tex
app headings adjusted

@@
-\section{Study 1}
-
 The full surveys are available in our OSF repository
@@
 
-\subsection{Methods}
+\subsection{Additional Materials}
 
-\subsubsection{Materials}
+In addition to the measurement of whether or not participants had an
+intergroup interaction and their situational core need fulfillment, we
+also measured a set of general psychological needs.
 
-\paragraph{General Psychological Needs}
+\subsubsection{General Psychological Needs}
 
@@
 reported in the main text, we included a common measure of three
-self-determination theory needs \citep[see][]{Downie2008}. The items
-were introduced either by ``\textit{During the interaction:}'' or
+self-determination theory needs \citep[see][]{Downie2008}. The
+measurement was identical in all three studies. The items were
+introduced either by ``\textit{During the interaction:}'' or
 ``\textit{This morning [/afternoon]:}'' and measured autonomy
@@
 
-\subsection{Results}
+\subsection{Study 1}
+
+\subsubsection{Results}
 
@@
 
-\section{Study 2}
+\subsection{Study 2}
 
-\subsection{Methods}
-
-\subsubsection{Materials}
-
-\paragraph{General Psychological Needs}
-
-The measurement of the self-determination needs was identical to Study
-1.
-
-\subsection{Results}
-
-\subsubsection{Robustness}
+\subsubsection{Results}
 
@@
 
-\section{Study 3}
+\subsection{Study 3}
 
-\subsection{Methods}
-
-\subsubsection{Materials}
-
-\paragraph{General Psychological Needs}
-
-The measurement of the self-determination needs was identical to Studies
-1 and 2.
-
-\subsection{Results}
-
-\subsubsection{Robustness}
+\subsubsection{Results}
 

### 2022-11-04 Robustness-Methods-and-Results.Rmd
app-b tbl orientation

@@
   kable_styling(latex_options = "scale_down") %>%
-  kableExtra::landscape() %>%
+  #kableExtra::landscape() %>%
   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position

### 2022-11-04 Methods-and-Results.Rmd
robustness removed from main txt m&r

@@
 
+NEEDS TO GO SOMEWHERE: To build further confidence in our results, we assessed two additional models that might offer alternative explanations.
+First, to ensure that the effect of core need fulfillment is specific to an actual contact, we compared the effect to core need fulfillment in situations without an intergroup contact.
+
 \section{Study 1}
@@
 Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).
-
-We, additionally, included a common measure of three self-determination theory needs \citep[see][]{Downie2008}.
-The items were introduced either by “\textit{During the interaction:}” or “\textit{This morning [/afternoon]:}” and measured autonomy (“\textit{I was myself.}”), competence (“\textit{I felt competent.}”), and relatedness (without intergroup contact “\textit{I had a strong need to belong}”; with intergroup contact: “\textit{I shared information about myself.}” and “\textit{The other(s) shared information about themselves.}”).
-All items were rated on a continuous slider scale from very little (-50) to a great deal (+50).
+The self-determination theory need measurements are described in Appendix \ref{app:AppendixRobustness}.
 
@@
 <!-- \faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?  -->
-
-\subsubsection{Robustness}
-```{r workerModelInterceptAttCoreInt, include=FALSE}
-# Create and save Model
-mdlWorker$lmeInterceptAttCoreInt <-
-  lme(
-    thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction,
-    random =  ~ 1 | PID,
-    na.action=na.omit,
-    data = dtWorkerSupp$workerWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlWorker$lmerInterceptAttCoreInt <- lmer(
-    thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction + (1 | PID),
-    data = dtWorkerSupp$workerWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlWorker$lmerInterceptAttCoreIntCI <- 
-  confint(method = "Wald", mdlWorker$lmerInterceptAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlWorker$lmeAttNull, 
-      mdlWorker$lmeInterceptAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.)-1)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorker$varInterceptAttCoreInt <- 
-  lme4::VarCorr(mdlWorker$lmeInterceptAttCoreInt)
-```
-```{r workerModelSlopesAttCoreIntX, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorker$lmeSlopesAttCoreInt <- lme(
-  thermometerDutch_1 ~
-    keyMotiveFulfilled_cwc * OutgroupInteraction,
-  random = ~ 1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  na.action=na.omit,
-  data = dtWorkerSupp$workerWithinBetween
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorker$lmerSlopesAttCoreInt <- lmer(
-    thermometerDutch_1 ~
-      keyMotiveFulfilled_cwc * OutgroupInteraction +
-      (1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID),
-    data = dtWorkerSupp$workerWithinBetween
-  ), 
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlWorker$lmerSlopesAttCoreIntCI <- 
-  confint(method = "Wald", mdlWorker$lmerSlopesAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlWorker$lmeAttNull, 
-      mdlWorker$lmeInterceptAttCoreInt,
-      mdlWorker$lmeSlopesAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorker$varSlopesAttCoreInt <- 
-  lme4::VarCorr(mdlWorker$lmeSlopesAttCoreInt)
-
-# Assumption Checks:
-mdlWorker$diagSlopesAttCoreInt <-
-  sjPlot::plot_model(mdlWorker$lmerSlopesAttCoreInt, type = "diag")
-grid.arrange(
-  mdlWorker$diagSlopesAttCoreInt[[1]],
-  mdlWorker$diagSlopesAttCoreInt[[2]]$`PID`,
-  mdlWorker$diagSlopesAttCoreInt[[3]],
-  mdlWorker$diagSlopesAttCoreInt[[4]]
-)
-
-# Plot prediction model
-mdlWorker$predSlopesAttCoreInt <- 
-  dtWorkerSupp$workerWithinBetween %>%
-  select(thermometerDutch_1, session, PID) %>% 
-  mutate(measure = predict(mdlWorker$lmeSlopesAttCoreInt,
-                           dtWorkerSupp$workerWithinBetween,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorker$predPltSlopesAttCoreInt <-
-    ggplot(data = mdlWorker$predSlopesAttCoreInt, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Worker_PredictionPlot_SlopesAttCoreInt.png",
-  mdlWorker$predPltSlopesAttCoreInt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-To build further confidence in our results, we assessed two additional models that might offer alternative explanations.
-First, to ensure that the effect of core need fulfillment is specific to an actual contact, we compared the effect to core need fulfillment in situations without an intergroup contact.
-For this, we analyzed the generalized situational core need fulfillment (either during a contact or about the daytime in general) and tested whether the effect differed during experience sampling measurements with and without outgroup contacts.
-We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`; also see Table \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness}).
-Together with a significant main effect of having an outgroup contact, this indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-
-```{r workerOutModelInterceptAttCoreSdt, include=FALSE}
-# Create and save Model
-mdlWorkerOut$Att$lmeInterceptCoreSdt <-
-  lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
-    random = ~ 1 | PID,
-    data = dtWorkerSupp$workerOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlWorkerOut$Att$lmerInterceptCoreSdt <- lmer(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# To be compared against a model with only the self-determination theory needs
-mdlWorkerOut$Att$lmeInterceptSdt <-
-  lme(
-    thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
-    random = ~ 1 | PID,
-    data = dtWorkerSupp$workerOutWithinBetween,
-    na.action = na.exclude
-  )
-
-summ(
-  mdlWorkerOut$Att$lmerInterceptSdt <- lmer(
-    thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous steps
-anova(
-  mdlWorkerOut$Att$lmeInterceptSdt,
-  mdlWorkerOut$Att$lmeInterceptCoreSdt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-rm(lmeInterceptCoreRed)
-
-# Save variances
-mdlWorkerOut$Att$varInterceptCoreSdt <-
-  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreSdt)
-```
-```{r workerOutModelSlopesAttCoreSdt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Att$lmeSlopesCoreSdt <-
-  lme(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
-    random = ~ 1 + keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtWorkerSupp$workerOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Att$lmerSlopesCoreSdt <- lmer(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc +
-      (1 + keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlWorkerOut$Att$lmerSlopesCoreSdtCI <- 
-  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreSdt)
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeInterceptSdt,
-      mdlWorkerOut$Att$lmeInterceptCoreSdt, 
-      mdlWorkerOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# model with SDT only
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Att$lmeSlopesSdt <-
-  lme(
-    thermometerDutch_1 ~
-      competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
-    random = ~ 1 + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtWorkerSupp$workerOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Att$lmerSlopesSdt <- lmer(
-    thermometerDutch_1 ~
-      competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc +
-      (1 + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeInterceptSdt,
-      mdlWorkerOut$Att$lmeSlopesSdt, 
-      mdlWorkerOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varSlopesCoreSdt <- 
-  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreSdt)
-
-# Assumption Checks:
-mdlWorkerOut$Att$diagSlopesCoreSdt <- 
-  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreSdt, type = "diag")
-grid.arrange(
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[1]],
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[3]],
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[4]]
-)
-
-# Plot prediction model
-mdlWorkerOut$Att$predSlopesCoreSdt <- 
-  dtWorkerSupp$workerOutWithinBetween %>%
-  filter(!is.na(autonomy_1)) %>%
-  select(thermometerDutch_1, session, PID, autonomy_1) %>% 
-  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreSdt,
-                           dtWorkerSupp$workerOutWithinBetween %>% filter(!is.na(autonomy_1)),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorkerOut$Att$predPltSlopesCoreSdt <-
-    ggplot(data = mdlWorkerOut$Att$predSlopesCoreSdt, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreStd.png",
-  mdlWorkerOut$Att$predPltSlopesCoreSdt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-# Model comparison
-workerSdtComp <-
-  anova(
-    mdlWorkerOut$Att$lmerSlopesSdt, 
-    mdlWorkerOut$Att$lmerSlopesCoreSdt
-  ) %>%
-  as.data.frame()
-workerSdtCompDf <- workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Df"]
-workerSdtCompN <- sapply(ranef(mdlWorkerOut$Att$lmerSlopesCoreSdt), nrow)
-workerSdtCompChi <- workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
-workerSdtCompP <-
-  ifelse(workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
-         "< .001",
-         paste0("= ", workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
-
-workerSdtCompChiSq <- paste0("$\\chi^2$(", workerSdtCompDf, ", \\textit{N} = ", workerSdtCompN, ") = ", workerSdtCompChi, ", \\textit{p} ", workerSdtCompP)
-```
-
-In a final step, we controlled for other fundamental psychological needs during the contact.
-We focus on the three commonly considered self-determination needs (SDT): competence, autonomy, and relatedness.
-We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r workerSdtCompChiSq`).
-We also find that next to relatedness (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "relatedness_1_cwc")`), the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "keymotive_fulfillemt_1_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all three fundamental needs (competence and autonomy needs turning non-significant; all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
-For full results see see Table \ref{tab:robustnessTblLong}, Figure \ref{fig:Robustness}, and Online Supplementary Material A.
-There is, thus, considerable evidence lending confidence to the stability and relevance of psychological need fulfillment as a predictor of positive outgroup attitudes for natural intergroup contacts.
 
@@
 
-The measurement of the self-determination needs was identical to Study 1.
-
 \paragraph{Perceived Interaction Quality}The ratings of the perceived contact quality was identical to Study 1.
@@
 
-\subsubsection{Robustness}
-```{r studentModelInterceptAttCoreInt, include=FALSE}
-# Create and save Model
-mdlStudent$lmeInterceptAttCoreInt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction,
-    random =  ~ 1 | PID,
-    data = dtStudentSupp$studentWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudent$lmerInterceptAttCoreInt <- lmer(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction + (1 | PID),
-    data = dtStudentSupp$studentWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudent$lmerInterceptAttCoreIntCI <- 
-  confint(method = "Wald", mdlStudent$lmerInterceptAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlStudent$lmeAttNull, 
-      mdlStudent$lmeInterceptAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.)-1)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudent$varInterceptAttCoreInt <- 
-  lme4::VarCorr(mdlStudent$lmeInterceptAttCoreInt)
-```
-```{r studentModelSlopesAttCoreIntX, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudent$lmeSlopesAttCoreInt <- lme(
-  AttitudesDutch ~
-    KeyNeedFullfillment_cwc * OutgroupInteraction,
-  random = ~ 1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  data = dtStudentSupp$studentWithinBetween
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudent$lmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFullfillment_cwc * OutgroupInteraction +
-      (1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID),
-    data = dtStudentSupp$studentWithinBetween
-  ), 
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudent$lmerSlopesAttCoreIntCI <- 
-  confint(method = "Wald", mdlStudent$lmerSlopesAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlStudent$lmeAttNull, 
-      mdlStudent$lmeInterceptAttCoreInt,
-      mdlStudent$lmeSlopesAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudent$varSlopesAttCoreInt <- 
-  lme4::VarCorr(mdlStudent$lmeSlopesAttCoreInt)
-
-# Assumption Checks:
-mdlStudent$diagSlopesAttCoreInt <-
-  sjPlot::plot_model(mdlStudent$lmerSlopesAttCoreInt, type = "diag")
-grid.arrange(
-  mdlStudent$diagSlopesAttCoreInt[[1]],
-  mdlStudent$diagSlopesAttCoreInt[[2]]$`PID`,
-  mdlStudent$diagSlopesAttCoreInt[[3]],
-  mdlStudent$diagSlopesAttCoreInt[[4]]
-)
-
-# Plot prediction model
-mdlStudent$predSlopesAttCoreInt <- 
-  dtStudentSupp$studentWithinBetween %>%
-  filter(PID %in% dtStudentSupp$studentPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudent$lmeSlopesAttCoreInt,
-                           dtStudentSupp$studentWithinBetween %>% filter(PID %in% dtStudentSupp$studentPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudent$predPltSlopesAttCoreInt <-
-    ggplot(data = mdlStudent$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Student_PredictionPlot_SlopesAttCoreInt.png",
-  mdlStudent$predPltSlopesAttCoreInt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-We again checked for alternative models.
-First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is only a minuscule main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc:OutgroupInteraction")`).
-Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteraction")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous study, albeit with a slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see Table \ref{tab:intergroupNeedsTblLong} and for visual comparison see Figure \ref{fig:AllportNeedFulfillment}).
-
-```{r studentOutModelInterceptAttCoreSdt, include=FALSE}
-# Create and save Model
-mdlStudentOut$Att$lmeInterceptCoreSdt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 | PID,
-    data = dtStudentSupp$studentOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudentOut$Att$lmerInterceptCoreSdt <- lmer(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtStudentSupp$studentOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudentOut$Att$lmerInterceptCoreSdtCI <- 
-  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCoreSdt)
-
-# To be compared against a model with only the self-determination theory needs
-mdlStudentOut$Att$lmeInterceptSdt <-
-  lme(
-    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 | PID,
-    data = dtStudentSupp$studentOutWithinBetween,
-    na.action = na.exclude
-  )
-
-summ(
-  mdlStudentOut$Att$lmerInterceptSdt <- lmer(
-    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtStudentSupp$studentOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous steps
-anova(
-  mdlStudentOut$Att$lmeNull,
-  mdlStudentOut$Att$lmeInterceptSdt,
-  mdlStudentOut$Att$lmeInterceptCoreSdt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-rm(lmeInterceptCoreRed)
-
-# Save variances
-mdlStudentOut$Att$varInterceptCoreSdt <-
-  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreSdt)
-```
-```{r studentOutModelSlopesAttCoreSdt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudentOut$Att$lmeSlopesCoreSdt <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 + KeyNeedFullfillment_cwc + Competence_cwc + Relatedness_cwc | PID,
-    control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
-    data = dtStudentSupp$studentOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Att$lmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtStudentSupp$studentOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudentOut$Att$lmerSlopesCoreSdtCI <- 
-  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreSdt)
-
-# Compare new model to previous step
-anova(mdlStudentOut$Att$lmeInterceptSdt,
-      mdlStudentOut$Att$lmeInterceptCoreSdt, 
-      mdlStudentOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# model with SDT only
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudentOut$Att$lmeSlopesSdt <-
-  lme(
-    AttitudesDutch ~
-      Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtStudentSupp$studentOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Att$lmerSlopesSdt <- lmer(
-    AttitudesDutch ~
-      Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtStudentSupp$studentOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous step
-anova(mdlStudentOut$Att$lmeInterceptSdt,
-      mdlStudentOut$Att$lmeSlopesSdt, 
-      mdlStudentOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varSlopesCoreSdt <- 
-  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreSdt)
-
-# Assumption Checks:
-mdlStudentOut$Att$diagSlopesCoreSdt <- 
-  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreSdt, type = "diag")
-grid.arrange(
-  mdlStudentOut$Att$diagSlopesCoreSdt[[1]],
-  mdlStudentOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
-  mdlStudentOut$Att$diagSlopesCoreSdt[[3]],
-  mdlStudentOut$Att$diagSlopesCoreSdt[[4]]
-)
-
-# Plot prediction model
-mdlStudentOut$Att$predSlopesCoreSdt <- 
-  dtStudentSupp$studentOutWithinBetween %>%
-  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID, Autonomy) %>% 
-  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreSdt,
-                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudentOut$Att$predPltSlopesCoreSdt <-
-    ggplot(data = mdlStudentOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreStd.png",
-  mdlStudentOut$Att$predPltSlopesCoreSdt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-# Model comparison
-studentSdtComp <-
-  anova(
-    mdlStudentOut$Att$lmerSlopesSdt, 
-    mdlStudentOut$Att$lmerSlopesCoreSdt
-  ) %>%
-  as.data.frame()
-studentSdtCompDf <- studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Df"]
-studentSdtCompN <- sapply(ranef(mdlStudentOut$Att$lmerSlopesCoreSdt), nrow)
-studentSdtCompChi <- studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
-studentSdtCompP <-
-  ifelse(studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
-         "< .001",
-         paste0("= ", studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
-
-studentSdtCompChiSq <- paste0("$\\chi^2$(", studentSdtCompDf, ", \\textit{N} = ", studentSdtCompN, ") = ", studentSdtCompChi, ", \\textit{p} ", studentSdtCompP)
-```
-
-In a final step, we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
-We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r studentSdtCompChiSq`).
-We find that the core need fulfillment explained the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFullfillment_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, different from the first study, relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes in this larger sample.
-For full results see Table \ref{tab:intergroupNeedsTblLong}, Figure \ref{fig:Robustness}, and Online Supplementary Material A.
-This means that also within this second sample, the fulfillment of psychological needs during intergroup contact remained a key predictor of positive outgroup attitudes, even when taking into account several alternative models.
-
 \section{Study 3}
@@
 \paragraph{Psychological Needs}The measurement of the core situational need and its fulfillment was identical to Study 2.
-Similarly, the measurement of the self-determination needs was identical to Studies 1 and 2
 
@@
 This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
-
-\subsubsection{Robustness}
-
-```{r medicalModelAttNullInt, include=FALSE}
-# Create and save Model
-mdlMedical$lmerAttNullInt <-
-  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
-             data = dtMedical$full %>%
-               filter(complete.cases(
-                 OutgroupInteraction
-               ))) # use optim if it does not converge
-
-mdlMedical$lmeAttNullInt <-
-  lme(
-    AttitudesDutch ~ 1,
-    random = ~ 1 | PID,
-    data = dtMedical$full %>%
-      filter(complete.cases(
-        OutgroupInteraction
-      )),
-    na.action = na.omit,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(mdlMedical$lmerAttNull) #or with the lme function
-summ(mdlMedical$lmerAttNullInt, digits = 3)
-```
-
-```{r medicalModelInterceptAttCoreInt, include=FALSE}
-# Create and save Model
-mdlMedical$lmeInterceptAttCoreInt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction,
-    random =  ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedical$full
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedical$lmerInterceptAttCoreInt <- lmer(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction + (1 | PID),
-    data = dtMedical$full
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedical$lmerInterceptAttCoreIntCI <- 
-  confint(method = "Wald", mdlMedical$lmerInterceptAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlMedical$lmeAttNullInt, 
-      mdlMedical$lmeInterceptAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.)-1)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedical$varInterceptAttCoreInt <- 
-  lme4::VarCorr(mdlMedical$lmeInterceptAttCoreInt)
-```
-```{r medicalModelSlopesAttCoreIntX, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedical$lmeSlopesAttCoreInt <- lme(
-  AttitudesDutch ~
-    KeyNeedFulfillment_cwc * OutgroupInteraction,
-  random = ~ 1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  na.action = na.omit,
-  data = dtMedical$full
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedical$lmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc * OutgroupInteraction +
-      (1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID),
-    data = dtMedical$full
-  ), 
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedical$lmerSlopesAttCoreIntCI <- 
-  confint(method = "Wald", mdlMedical$lmerSlopesAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlMedical$lmeAttNullInt, 
-      mdlMedical$lmeInterceptAttCoreInt,
-      mdlMedical$lmeSlopesAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedical$varSlopesAttCoreInt <- 
-  lme4::VarCorr(mdlMedical$lmeSlopesAttCoreInt)
-
-# Assumption Checks:
-mdlMedical$diagSlopesAttCoreInt <-
-  sjPlot::plot_model(mdlMedical$lmerSlopesAttCoreInt, type = "diag")
-grid.arrange(
-  mdlMedical$diagSlopesAttCoreInt[[1]],
-  mdlMedical$diagSlopesAttCoreInt[[2]]$`PID`,
-  mdlMedical$diagSlopesAttCoreInt[[3]],
-  mdlMedical$diagSlopesAttCoreInt[[4]]
-)
-
-# Plot prediction model
-mdlMedical$predSlopesAttCoreInt <- 
-  dtMedical$full %>%
-  filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
-  filter(PID %in% dtMedicalSupp$medicalPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedical$lmeSlopesAttCoreInt,
-                           dtMedical$full %>% 
-                             filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedical$predPltSlopesAttCoreInt <-
-    ggplot(data = mdlMedical$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Medical_PredictionPlot_SlopesAttCoreInt.png",
-  mdlMedical$predPltSlopesAttCoreInt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-We again checked for alternative models of the key need fulfillment.
-First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
-Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "OutgroupInteractionYes")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous studies.
-
-```{r medicalOutModelInterceptAttCoreSdt, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptCoreSdt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 | PID,
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptCoreSdt <- lmer(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# To be compared against a model with only the self-determination theory needs
-mdlMedicalOut$Att$lmeInterceptSdt <-
-  lme(
-    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 | PID,
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-summ(
-  mdlMedicalOut$Att$lmerInterceptSdt <- lmer(
-    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous steps
-anova(
-  mdlMedicalOut$Att$lmeInterceptSdt,
-  mdlMedicalOut$Att$lmeInterceptCoreSdt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptCoreSdt <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreSdt)
-```
-
-```{r medicalOutModelSlopesAttCoreSdt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesCoreSdt <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc + Competence_cwc + Relatedness_cwc | PID,
-    control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerSlopesCoreSdtCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreSdt)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeInterceptSdt,
-      mdlMedicalOut$Att$lmeInterceptCoreSdt, 
-      mdlMedicalOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# model with SDT only
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesSdt <-
-  lme(
-    AttitudesDutch ~
-      Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesSdt <- lmer(
-    AttitudesDutch ~
-      Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeInterceptSdt,
-      mdlMedicalOut$Att$lmeSlopesSdt, 
-      mdlMedicalOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesCoreSdt <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreSdt)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesCoreSdt <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreSdt, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[1]],
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[3]],
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesCoreSdt <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
-  filter(complete.cases(
-    KeyNeedFulfillment,
-    Autonomy, Competence, Relatedness
-    )) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID, Autonomy, Competence, Relatedness) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreSdt,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(
-                               KeyNeedFulfillment,
-                               Autonomy, Competence, Relatedness
-                             )) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesCoreSdt <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreStd.png",
-  mdlMedicalOut$Att$predPltSlopesCoreSdt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-# Model comparison
-medicalSdtComp <-
-  anova(
-    mdlMedicalOut$Att$lmerSlopesSdt, 
-    mdlMedicalOut$Att$lmerSlopesCoreSdt
-  ) %>%
-  as.data.frame()
-medicalSdtCompDf <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Df"]
-medicalSdtCompN <- sapply(ranef(mdlMedicalOut$Att$lmerSlopesCoreSdt), nrow)
-medicalSdtCompChi <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
-medicalSdtCompP <-
-  ifelse(medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
-         "< .001",
-         paste0("= ", medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
-
-medicalSdtCompChiSq <- paste0("$\\chi^2$(", medicalSdtCompDf, ", \\textit{N} = ", medicalSdtCompN, ") = ", medicalSdtCompChi, ", \\textit{p} ", medicalSdtCompP)
-```
-
-In a final step, we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
-We find that the core need fulfillment adds additional variance above a model with only the self-determination theory needs (random slopes models; `r medicalSdtCompChiSq`).
-We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFulfillment_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, similar to the previous study, in this large sample relatedness (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each also predicted positive outgroup attitudes independently.
-This being said, the regression coefficient for the core need was three times larger (with all scaling being equal).
-For full results see Table \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as Online Supplementary Material A.
-Across all three studies, psychological need fulfillment, thus, remained a robust and flexible predictor of positive outgroup attitudes.
 
@@
 mdlTblTheoreticalShort
-```
-
-```{r robustnessTblLong, include=FALSE}
-# Table of all robustness checks (w/ and w/out SDT only)
-
-# Full Sample
-# Study 1:
-robustTblWorkerFull <- 
-  dtWorkerSupp$workerWithinBetween %>%
-  select(
-    AttitudesDutch = thermometerDutch_1,
-    AttitudesDutch_zwc = thermometerDutch_1_zwc,
-    CoreNeed_cwc = keyMotiveFulfilled_cwc,
-    CoreNeed_zwc = keyMotiveFulfilled_zwc,
-    OutgroupInteraction = OutgroupInteraction,
-    OutgroupInteraction_zwc = OutgroupInteraction_zwc,
-    PID = PID
-  )
-mdlWorkerLmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc * OutgroupInteraction +
-      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
-    data = robustTblWorkerFull
-  )
-mdlWorkerLmerSlopesAttCoreIntZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc * OutgroupInteraction_zwc +
-      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
-    data = robustTblWorkerFull
-  )
-#Study 2:
-robustTblStudentFull <- 
-  dtStudentSupp$studentWithinBetween %>%
-  select(
-    AttitudesDutch = AttitudesDutch,
-    AttitudesDutch_zwc = AttitudesDutch_zwc,
-    CoreNeed_cwc = KeyNeedFullfillment_cwc,
-    CoreNeed_zwc = KeyNeedFullfillment_zwc,
-    OutgroupInteraction = OutgroupInteraction,
-    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
-    PID = PID
-  )
-mdlStudentLmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc * OutgroupInteraction +
-      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
-    data = robustTblStudentFull
-  )
-mdlStudentLmerSlopesAttCoreIntZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc * OutgroupInteraction_zwc +
-      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
-    data = robustTblStudentFull
-  )
-#Study 3:
-robustTblMedicalFull <- 
-  dtMedicalSupp$medicalWithinBetween %>%
-  select(
-    AttitudesDutch = AttitudesDutch,
-    AttitudesDutch_zwc = AttitudesDutch_zwc,
-    CoreNeed_cwc = KeyNeedFulfillment_cwc,
-    CoreNeed_zwc = KeyNeedFulfillment_zwc,
-    OutgroupInteraction = OutgroupInteraction,
-    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
-    PID = PID
-  )
-mdlMedicalLmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc * OutgroupInteraction +
-      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
-    #data = dtMedical$full
-    data = robustTblMedicalFull
-  )
-mdlMedicalLmerSlopesAttCoreIntZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc * OutgroupInteraction_zwc +
-      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
-    #data = dtMedical$full
-    data = robustTblMedicalFull
-  )
-
-# SDT
-# Study 1:
-robustTblWorkerOut <- 
-  dtWorkerSupp$workerOutWithinBetween %>%
-  select(
-    AttitudesDutch = thermometerDutch_1,
-    AttitudesDutch_zwc = thermometerDutch_1_zwc,
-    CoreNeed_cwc = keymotive_fulfillemt_1_cwc,
-    CoreNeed_zwc = keymotive_fulfillemt_1_zwc,
-    Competence_cwc = competence_1_cwc,
-    Competence_zwc = competence_1_zwc,
-    Autonomy_cwc = autonomy_1_cwc,
-    Autonomy_zwc = autonomy_1_zwc,
-    Relatedness_cwc = relatedness_1_cwc,
-    Relatedness_zwc = relatedness_1_zwc,
-    PID = PID
-  )
-mdlWorkerOutLmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = robustTblWorkerOut
-  )
-mdlWorkerOutLmerSlopesCoreSdtZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
-      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
-    data = robustTblWorkerOut
-  )
-# Study 2:
-robustTblStudentOut <- 
-  dtStudentSupp$studentOutWithinBetween %>%
-  select(
-    AttitudesDutch = AttitudesDutch,
-    AttitudesDutch_zwc = AttitudesDutch_zwc,
-    CoreNeed_cwc = KeyNeedFullfillment_cwc,
-    CoreNeed_zwc = KeyNeedFullfillment_zwc,
-    Competence_cwc = Competence_cwc,
-    Competence_zwc = Competence_zwc,
-    Autonomy_cwc = Autonomy_cwc,
-    Autonomy_zwc = Autonomy_zwc,
-    Relatedness_cwc = Relatedness_cwc,
-    Relatedness_zwc = Relatedness_zwc,
-    PID = PID
-  )
-mdlStudentOutLmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = robustTblStudentOut
-  )
-mdlStudentOutLmerSlopesCoreSdtZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
-      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
-    data = robustTblStudentOut
-  )
-# Study 3:
-robustTblMedicalOut <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
-  select(
-    AttitudesDutch = AttitudesDutch,
-    AttitudesDutch_zwc = AttitudesDutch_zwc,
-    CoreNeed_cwc = KeyNeedFulfillment_cwc,
-    CoreNeed_zwc = KeyNeedFulfillment_zwc,
-    Competence_cwc = Competence_cwc,
-    Competence_zwc = Competence_zwc,
-    Autonomy_cwc = Autonomy_cwc,
-    Autonomy_zwc = Autonomy_zwc,
-    Relatedness_cwc = Relatedness_cwc,
-    Relatedness_zwc = Relatedness_zwc,
-    PID = PID
-  )
-mdlMedicalOutLmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = robustTblMedicalOut
-  )
-mdlMedicalOutLmerSlopesCoreSdtZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
-      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
-    data = robustTblMedicalOut
-  )
-
-# collect models for table
-mdlRobustTblElements <- list(
-  # full
-  c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ),
-  c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ),
-  c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ),
-  # outgroup
-  c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ),
-  c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ),
-  c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ)
-  )
-
-mdlRobustPrep <- list()
-for (i in 1:length(mdlRobustTblElements)) {
-  mdlRobustPrep[[i]] <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])
-}
-
-# manual assembly
-shortRobustPrep <- list()
-for(i in 1:length(mdlRobustPrep)){
-  study <- str_extract(mdlRobustPrep[[i]]$fit$data, "Worker|Student|Medical")
-  sample <- str_extract(mdlRobustPrep[[i]]$fit$data, "Full|Out")
-  #dv <- sub(" ~.*", "", mdlRobustPrep[[i]]$fit$formula)
-  #pred <- gsub("\\(Intercept\\)", "", paste(mdlRobustPrep[[i]]$coeficients$coef, collapse = ''))
-
-  name <- paste(study, sample, sep='.')
-  tmp <- rbind(
-    mdlRobustPrep[[i]]$coeficients[, c("coef", "B", "Beta")],
-    data.frame(
-      coef = "R2Marg_R2Cond",
-      B = mdlRobustPrep[[i]]$fit$R2Marg_R2Cond,
-      Beta = ""
-    )
-  )
-  shortRobustPrep[[name]] <- tmp
-}
-
-tmp <- shortRobustPrep[grepl("Full", names(shortRobustPrep))]
-fullRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Full$coef)
-for (i in 1:length(tmp)){
-  fullRobustTbl <- join(fullRobustTbl, tmp[[i]], by = "coef")
-}
-
-tmp <- shortRobustPrep[grepl("Out", names(shortRobustPrep))]
-outRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Out$coef)
-for (i in 1:length(tmp)){
-  outRobustTbl <- join(outRobustTbl, tmp[[i]], by = "coef")
-}
-
-robustTblLong <- rbind(
-  fullRobustTbl,
-  outRobustTbl
-)
-
-robustTblLong$coef <- mapvalues(
-  robustTblLong$coef,
-  from = c(
-    "R2Marg_R2Cond"
-  ),
-  to = c(
-    "$R^2_{marginal}$ / $R^2_{conditional}$"
-  )
-)
-
-mdlTblRobustLong <- robustTblLong %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Robustness Analyses",
-    #format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.)-1)),
-    escape = FALSE
-  ) %>%
-  kable_classic() %>%
-  add_header_above(., c(" ", "Study 1" = 2, "Study 2" = 2, "Study 3" = 2)) %>%
-  pack_rows("Contact [Full Sample]", 1, 5) %>%
-  pack_rows("Self-Determination Theory [Outgroup Interactions only]", 6, 11) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  kableExtra::landscape() %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/mdlRobustlong.tex")
-```
-
-```{r robustnessTblWide, include=FALSE}
-# Wide format
-mdlRobustTbl <- data.frame(
-  coef = c(
-    sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef) %>% unlist %>% unique,
-    names(mdlRobustPrep[[1]]$random),
-    names(mdlRobustPrep[[1]]$fit)
-  )
-)
-for (i in 1:length(mdlRobustPrep)){
-  mdlRobustTbl <- join(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef")
-  #mdlTbl <- merge(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", ""))
-}
-
-mdlRobustTblHeader <- data.frame(
-  data = as.character(mdlRobustTbl[mdlRobustTbl$coef == "data",]),
-  formula = as.character(mdlRobustTbl[mdlRobustTbl$coef == "formula",])
-) %>%
-  filter(data != "",
-         data != "data") %>%
-  mutate(study = str_extract(data, "Worker|Student|Medical")) %>%
-  mutate(study = gsub("Worker", "Study 1", study)) %>%
-  mutate(study = gsub("Student", "Study 2", study)) %>%
-  mutate(study = gsub("Medical", "Study 3", study)) %>%
-  mutate(dv = sub(" ~.*", "", formula)) %>%
-  mutate(dv = gsub("Raw", " ", dv)) %>%
-  mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>%
-  mutate(header = paste(study, pred, sep = " - "))
-
-mdlRobustTblHeaderFreq <- rbind.data.frame(rle(mdlRobustTblHeader$header)) %>%
-  mutate(lengths = lengths*2) %>%
-  rename(names = values, span = lengths) %>%
-  rbind(c(1, ""), .) %>%
-  mutate(span = as.numeric(span)) %>%
-  select(names, span)
-
-mdlRobustTblHeaderDv <- data.frame(names = mdlRobustTblHeader$dv, span = 2) %>% 
-  mutate(names = as.character(names)) %>%
-  rbind(c("", 1), .) %>%
-  mutate(span = as.numeric(span))
-
-mdlRobustTblHeaderStudy <- rbind.data.frame(rle(mdlRobustTblHeader$study)) %>%
-  mutate(lengths = lengths*2) %>%
-  rename(names = values, span = lengths) %>%
-  rbind(c(1, ""), .) %>%
-  mutate(span = as.numeric(span)) %>%
-  select(names, span)
-
-mdlRobustTbl$coef <- mapvalues(
-  mdlRobustTbl$coef,
-  from = c(
-    "sigmaSq",
-    "tau00",
-    "tau11",
-    "rho01",
-    "rho00",
-    "R2_marginal",
-    "R2_conditional", 
-    "R2Marg_R2Cond"
-  ),
-  to = c(
-    "$\\sigma^2$",
-    "$\\tau_{00}$",
-    "$\\tau_{11}$",
-    "$\\rho_{01}$",
-    "$\\rho_{00}$",
-    "$R^2_{marginal}$",
-    "$R^2_{conditional}$",
-    "$R^2_{marginal}$ / $R^2_{conditional}$"
-  )
-)
-
-# Long Table
-mdlTblRobustLong <- mdlRobustTbl %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Robustness Analyses",
-    #format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.) - 1)),
-    escape = FALSE,
-    digits = 3
-  ) %>%
-  kable_classic() %>%
-  add_header_above(., mdlRobustTblHeaderStudy) %>%
-  add_header_above(
-    .,
-    c(
-      "",
-      "Contact [Full Sample]" = 6,
-      "Self-Determination Theory [Outgroup Interactions only]" = 6
-    )
-  ) %>%
-  pack_rows("Fixed", 1, 7) %>%
-  pack_rows("Random", 8, 12) %>%
-  pack_rows("Fit", 13, 25) %>%
-  footnote(
-    general = c("PID = Participant ID number (grouping variable)",
-                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
-                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
-    ),
-    escape = FALSE
-  ) %>%
-  gsub("_cwc", "", ., fixed = TRUE)
-
-# shortened Table
-mdlTblRobustShort <- mdlRobustTbl %>%
-  replace(is.na(.), "")
-names(mdlTblRobustShort) <- make.unique(names(mdlTblRobustShort))
-mdlTblRobustShort <- mdlTblRobustShort %>%
-  filter(
-    !coef %in% c(
-      "data",
-      "formula",
-      "groupId",
-      "$R^2_{marginal}$",
-      "$R^2_{conditional}$",
-      "logLik",
-      "deviance"
-    )
-  ) %>%
-  mutate_all(linebreak) %>%
-  kbl(
-    .,
-    caption = "Robustness Analyses",
-    format = "latex",
-    linesep = "",
-    booktabs = TRUE,
-    col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)),
-    align = c("l", rep("c", ncol(.) - 1)),
-    escape = FALSE,
-    digits = 3
-  )  %>%
-  kable_classic() %>%
-  add_header_above(., mdlRobustTblHeaderStudy) %>%
-  add_header_above(
-    .,
-    c(
-      "",
-      "Contact [Full Sample]" = 6,
-      "Self-Determination Theory [Outgroup Interactions only]" = 6
-    )
-  ) %>%
-  pack_rows("Fixed", 1, 7) %>%
-  pack_rows("Random", 8, 12) %>%
-  pack_rows("Fit", 13, 18) %>%
-  footnote(
-    general = c("PID = Participant ID number (grouping variable)",
-                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
-                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
-    ), 
-    escape = FALSE
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  kableExtra::landscape() %>%
-  gsub("_cwc", "", ., fixed = TRUE)  %>%
-  gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>%
-  gsub("\\makecell[r]", "\\makecell[c]", ., fixed = TRUE) %>%
-  gsub("objVar$", "", ., fixed = TRUE) %>%
-  gsub("slope_intercept.", "slope.intercept", ., fixed = TRUE) %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/mdlRobustness.tex")
-mdlTblRobustShort
 ```
@@
 
-```{r metaRobust, include=FALSE}
-mdlRobustTblElements <- list(
-  # full
-  c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ),
-  c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ),
-  c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ),
-  # outgroup
-  c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ),
-  c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ),
-  c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ)
-  )
-
-# i =1
-robustMetaTbl <- data.frame()
-for (i in 1:length(mdlRobustTblElements)){
-  lmerTblTmp <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$beta %>%
-  select(
-    coef,
-    B = est,
-    se,
-    lwr,
-    upr,
-    tval,
-    Rsq
-  ) %>%
-  mutate(
-    n = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$N,
-    m = nrow(.), 
-    #dv = gsub("Dutch", "", str_extract(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,".+?(?= ~)")),
-    sample = str_match(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$data, "Tbl(.*?)(Full|Out)")[2],
-    formula = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,
-    coef = gsub(":", ".", coef)
-  )
-  robustMetaTbl <- rbind(robustMetaTbl, lmerTblTmp)
-}
-
-robustMetaTbl <- robustMetaTbl %>%
-  arrange(formula, match(
-    coef,
-    c(
-      "CoreNeed_zwc",
-      "OutgroupInteraction_zwc",
-      "CoreNeed_zwc.OutgroupInteraction_zwc",
-      "Autonomy_zwc",
-      "Competence_zwc",
-      "Relatedness_zwc"
-    )
-  )) %>% 
-  mutate(formula = gsub(" \\+ \\(.*", "", formula))
-
-robustMetaContact <-
-  metaLmerOut(
-    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc * OutgroupInteraction"),
-    type = "REML", #"FE", 
-    name = "RobustContact",
-    title = "Robustness — Contact and Need Fulfillment"
-  )
-
-robustMetaSDT <-
-  metaLmerOut(
-    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc + Competence_cwc + Autonomy_cwc +      Relatedness_cwc"),
-    type = "REML", #"FE", 
-    name = "RobustSDT",
-    title = "Robustness — Other Needs"
-  )
-```
-
-```{r robustForestPltComb, include=FALSE}
-effRobust <- rbind(
-  robustMetaContact$eff %>%
-    filter(coef != "(Intercept)") %>%
-    mutate(analysis = "(A) Attitude ~ Contact and Need Fulfillment",
-           metaId = paste(coef, analysis, sep = ".")) %>%
-    as.data.frame,
-  robustMetaSDT$eff %>%
-    mutate(analysis = "(B) Attitude ~ Other Needs",
-           metaId = paste(coef, analysis, sep = ".")) %>%
-    as.data.frame
-)
-
-metaSubForest(effRobust, 
-              title = "Meta Analysis: Forest Plot Robustness Analysis \n[Parametric]",
-              filename = "RobustnessComb",
-              addAbove = 5,
-              width = 600,
-              height = 800)
-```
-
 ```{r Export Path Models, include=FALSE}

### 2022-11-04 Methods-and-Results.tex
shaded fix
robustness removed from main txt m&r

@@
+NEEDS TO GO SOMEWHERE: To build further confidence in our results, we
+assessed two additional models that might offer alternative
+explanations. First, to ensure that the effect of core need fulfillment
+is specific to an actual contact, we compared the effect to core need
+fulfillment in situations without an intergroup contact.
+
 \section{Study 1}
@@
 on a continuous slider scale ranging from strongly disagree (-50) to
-strongly agree (+50).
-
-We, additionally, included a common measure of three self-determination
-theory needs \citep[see][]{Downie2008}. The items were introduced either
-by ``\textit{During the interaction:}'' or
-``\textit{This morning [/afternoon]:}'' and measured autonomy
-(``\textit{I was myself.}''), competence
-(``\textit{I felt competent.}''), and relatedness (without intergroup
-contact ``\textit{I had a strong need to belong}''; with intergroup
-contact: ``\textit{I shared information about myself.}'' and
-``\textit{The other(s) shared information about themselves.}''). All
-items were rated on a continuous slider scale from very little (-50) to
-a great deal (+50).
+strongly agree (+50). The self-determination theory need measurements
+are described in Appendix \ref{app:AppendixRobustness}.
 
@@
 is likely explained by its effect through perceived contact quality.
-
-\subsubsection{Robustness}
-
-To build further confidence in our results, we assessed two additional
-models that might offer alternative explanations. First, to ensure that
-the effect of core need fulfillment is specific to an actual contact, we
-compared the effect to core need fulfillment in situations without an
-intergroup contact. For this, we analyzed the generalized situational
-core need fulfillment (either during a contact or about the daytime in
-general) and tested whether the effect differed during experience
-sampling measurements with and without outgroup contacts. We found no
-main effect of core need fulfillment (random slopes model; \textit{b} =
--0.10, \textit{t}(1,199) = -2.22, \textit{p} = 0.026,
-\textit{95\%CI}{[}-0.18, -0.01{]}) but a significant interaction effect
-of core need fulfillment and outgroup contact (\textit{b} = 0.13,
-\textit{t}(1,199) = 4.31, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.07, 0.18{]}; also see Table
-\ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness}). Together
-with a significant main effect of having an outgroup contact, this
-indicates that it is not key need fulfillment in general --- but only
-key need fulfillment during an outgroup contact that predicts more
-positive outgroup attitudes.
-
-In a final step, we controlled for other fundamental psychological needs
-during the contact. We focus on the three commonly considered
-self-determination needs (SDT): competence, autonomy, and relatedness.
-We find that the core need fulfillment adds significantly above a model
-with only the self-determination theory needs (random slopes models;
-\(\chi^2\)(6, \textit{N} = 21) = 19.60, \textit{p} = 0.003). We also
-find that next to relatedness (\textit{b} = 0.10, \textit{t}(361) =
-4.04, \textit{p} \textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the
-core need explains the most variance in outgroup attitudes after an
-outgroup contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p}
-= 0.026, \textit{95\%CI}{[}0.01, 0.18{]}). When compared to the model
-with only the SDT needs, the core need fulfillment flexibly takes on
-some of the explained variance of all three fundamental needs
-(competence and autonomy needs turning non-significant; all \textit{b}
-\textless{} 0.05, all \textit{p} \textgreater{} 0.544). For full results
-see see Table \ref{tab:robustnessTblLong}, Figure \ref{fig:Robustness},
-and Online Supplementary Material A. There is, thus, considerable
-evidence lending confidence to the stability and relevance of
-psychological need fulfillment as a predictor of positive outgroup
-attitudes for natural intergroup contacts.
 
@@
 
-The measurement of the self-determination needs was identical to Study
-1.
-
 \paragraph{Perceived Interaction Quality}
@@
 likely explained by its effect through perceived interaction quality.
-
-\subsubsection{Robustness}
-
-We again checked for alternative models. First, when considering
-generalized situational core need fulfillment together with whether an
-intergroup contact took place, we find that there is only a minuscule
-main effect of core need fulfillment (random slopes model; \textit{b} =
--0.03, \textit{t}(4,849) = -1.34, \textit{p} = 0.181,
-\textit{95\%CI}{[}-0.08, 0.02{]}) but a stronger interaction effect of
-core need fulfillment and outgroup contact (\textit{b} = 0.06,
-\textit{t}(4,849) = 3.03, \textit{p} = 0.002, \textit{95\%CI}{[}0.02,
-0.10{]}). Together with a significant main effect of having an outgroup
-contact (\textit{b} = 2.88, \textit{t}(4,849) = 3.71, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}1.36, 4.40{]}), this indicates that
-it is not key need fulfillment in general --- but key need fulfillment
-during an outgroup contact that predicts more positive outgroup
-attitudes. This finding is consistent with the results of the previous
-study, albeit with a slightly weaker effect (likely because of the large
-number of measurements that did not include an outgroup interaction; For
-full results see Table \ref{tab:intergroupNeedsTblLong} and for visual
-comparison see Figure \ref{fig:AllportNeedFulfillment}).
-
-In a final step, we again checked whether during the interaction the
-core situational need remains a meaningful predictor even when taking
-other fundamental psychological needs into account. We find that the
-core need fulfillment adds significantly above a model with only the
-self-determination theory needs (random slopes models; \(\chi^2\)(6,
-\textit{N} = 108) = 22.90, \textit{p} \textless{} .001). We find that
-the core need fulfillment explained the most variance in outgroup
-attitudes after an outgroup contact (\textit{b} = 0.08, \textit{t}(823)
-= 2.95, \textit{p} = 0.003, \textit{95\%CI}{[}0.03, 0.13{]}). When
-compared to the model with only the SDT needs, the core need fulfillment
-flexibly takes on some of the explained variance of all of the three
-fundamental needs. However, different from the first study, relatedness
-(\textit{b} = 0.07, \textit{t}(823) = 4.26, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.04, 0.10{]}) and autonomy (\textit{b} = 0.02,
-\textit{t}(823) = 0.93, \textit{p} = 0.353, \textit{95\%CI}{[}-0.02,
-0.08{]}) also predicted positive outgroup attitudes in this larger
-sample. For full results see Table \ref{tab:intergroupNeedsTblLong},
-Figure \ref{fig:Robustness}, and Online Supplementary Material A. This
-means that also within this second sample, the fulfillment of
-psychological needs during intergroup contact remained a key predictor
-of positive outgroup attitudes, even when taking into account several
-alternative models.
 
@@
 The measurement of the core situational need and its fulfillment was
-identical to Study 2. Similarly, the measurement of the
-self-determination needs was identical to Studies 1 and 2
+identical to Study 2.
 
@@
 another.
-
-\subsubsection{Robustness}
-
-We again checked for alternative models of the key need fulfillment.
-First, when considering generalized situational core need fulfillment
-together with whether an intergroup contact took place, we find that
-there is no significant main effect of core need fulfillment (random
-slopes model; \textit{b} = 0.03, \textit{t}(3,835) = 1.51, \textit{p} =
-0.131, \textit{95\%CI}{[}-0.01, 0.06{]}) but a stronger interaction
-effect of core need fulfillment and outgroup contact (\textit{b} = 0.17,
-\textit{t}(3,835) = 7.32, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.21{]}). Together with a significant main
-effect of having an outgroup contact (\textit{b} = 5.41,
-\textit{t}(3,835) = 6.36, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}3.74, 7.08{]}), this indicates that it is not key need
-fulfillment in general --- but key need fulfillment during an outgroup
-contact that predicts more positive outgroup attitudes. This finding is
-consistent with the results of the previous studies.
-
-In a final step, we again checked whether during the interaction the
-core situational need remains a meaningful predictor even when taking
-other fundamental psychological needs into account. We find that the
-core need fulfillment adds additional variance above a model with only
-the self-determination theory needs (random slopes models; \(\chi^2\)(6,
-\textit{N} = 70) = 100.20, \textit{p} \textless{} .001). We find that
-the core need explains the most variance in outgroup attitudes after an
-outgroup contact (\textit{b} = 0.15, \textit{t}(1,598) = 3.88,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.22{]}). When
-compared to the model with only the SDT needs, the core need fulfillment
-flexibly takes on some of the explained variance of all of the three
-fundamental needs. However, similar to the previous study, in this large
-sample relatedness (\textit{b} = 0.05, \textit{t}(1,598) = 3.31,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.02, 0.09{]}),
-competence (\textit{b} = 0.06, \textit{t}(1,598) = 2.73, \textit{p} =
-0.006, \textit{95\%CI}{[}0.02, 0.10{]}) and autonomy (\textit{b} = 0.04,
-\textit{t}(1,598) = 2.12, \textit{p} = 0.034, \textit{95\%CI}{[}-0.01,
-0.08{]}) each also predicted positive outgroup attitudes independently.
-This being said, the regression coefficient for the core need was three
-times larger (with all scaling being equal). For full results see Table
-\ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as
-Online Supplementary Material A. Across all three studies, psychological
-need fulfillment, thus, remained a robust and flexible predictor of
-positive outgroup attitudes.
 
@@
 under-explored \citep[][]{Kreienkamp2022d}.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\FunctionTok{save}\NormalTok{(shortMdlPath, }
-     \AttributeTok{file =} \StringTok{"data/theoryMdlTabl.RData"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}

### 2022-11-07 manuscript.tex
app str added
app-b tbl & fgr
app-a ttl
app A written

@@
 % \usepackage{longtable}
-\usepackage{amsmath}
+\usepackage{amsmath, nccmath}
+\usepackage{mdframed}
 \usepackage{ntheorem}
@@
 }
+
+% ref labels
+\newcommand{\fgrref}[2][]{\hyperref[#2]{Figure \ref*{#2}#1}}
+\newcommand{\tblref}[2][]{\hyperref[#2]{Table \ref*{#2}#1}}
+\newcommand{\appref}[2][]{\hyperref[#2]{Appendix \ref*{#2}#1}}
 
@@
 \end{enumerate}
-Beyond these main hypotheses, we have formulated several sub-hypotheses that form the basis for our analysis plan (these sub-hypotheses also include several robustness checks and are available in Appendix \ref{app:AppendixHypotheses}).
+Beyond these main hypotheses, we have formulated several sub-hypotheses that form the basis for our analysis plan (these sub-hypotheses also include several robustness checks and are available in \appref{app:AppendixHypotheses}).
 
@@
 Such an approach is also tolerant to missing data and uneven case numbers within participants.
-As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text (for the full modeling process see Supplementary Material B).
+As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text \citep[][; for the full modeling process see Supplementary Material B]{Bliese2013}.
 
@@
 These aggregate findings are surprising because most past cross-sectional studies have also considered an aggregate measurement of interaction quality (albeit not one from actual daily reports).
-The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).\footnote{It should be noted that such inconsistencies with past research might in part be a data artefact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
+The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).\footnote{It should be noted that such inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
 However, the models we employed should in principle be resistant to such imbalances.} In support of this possibility, once we used multilevel modeling to separate effects into a between-subjects and within-subjects part, we found that when having an interaction with an outgroup member (vs.
-not having an outgroup interaction) is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account; also see Figure \ref{fig:ContactHypothesis}B).
+not having an outgroup interaction) is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account; also see \fgrref[B]{fig:ContactHypothesis}).
 We thus find that the main benefits of intergroup contact remain visible across the three studies.
@@
 \input{Tables/mdlTheorylong}
-\input{Tables/mdlRobustlong}
 
@@
   General: Path coefficients are standardized regression coefficients.
-Statistical significance markers are based on the unstandardized regression results (as presented in Table \ref{tab:intergroupNeedsTblLong}).\\
+Statistical significance markers are based on the unstandardized regression results (as presented in \tblref{tab:intergroupNeedsTblLong}).\\
   **** p < .0001, *** p < .001, ** p < .01, * p < .05}
@@
 
+\printbibliography
+
+\appendix
+
+\section{Hypotheses and Analysis Plan}
+\label{app:AppendixHypotheses}
+
+\newlength{\mdfmar}
+\setlength{\mdfmar}{1.5em}
+\mdfdefinestyle{mdfhypothesis}{
+    innerleftmargin = +1.5\mdfmar, %
+    innerrightmargin = +1.5\mdfmar, 
+    innertopmargin = +\mdfmar, 
+    innerbottommargin = +\mdfmar, 
+    skipabove = 12pt
+}
+\newlength{\subhypskip}
+\setlength{\subhypskip}{1.5em}
+\newlength{\eqskip}
+\setlength{\eqskip}{3.5em}
+
+In this appendix, we present the expanded hypotheses and their associated analysis plan.
+Given the nested structure of much of our data we test many of our hypotheses using a multilevel approach, where $y_{ti}$ denotes the response at measurement occasion $t$ ($t = 1, ...,T_i$; level 1) for individual $i$ ($i = 1, ..., n$; level 2).
+All multilevel assumptions are tested as follows (e.g., for random slopes model with $j$ within-person predictors):
+
+\begin{flalign}
+  &\textrm{Level 1 Variance:}\ e_{ti} \sim \mathcal{N}(0,\sigma^2) \\
+  &\textrm{Level 2 Variance:}\ \begin{bmatrix} u_{0i}\\ \vdots\\ u_{ji}\end{bmatrix} 
+  \sim \mathcal{N}
+  \begin{pmatrix}
+    \begin{bmatrix} 
+      0 \\ 
+      \vdots \\
+      0
+    \end{bmatrix}, 
+    \begin{bmatrix} 
+      \tau_{00}^2 &  & \\ 
+      \vdots & \ddots & \\
+      \tau_{j0} & \ldots & \tau_{jj}^2
+    \end{bmatrix}
+  \end{pmatrix}
+\end{flalign}
+
+For our main aims we sequentially focus on four sets of models to test and validate our hypotheses:
+
+\subsection{1. Contact hypothesis in extensive longitudinal data.} 
+Within the individual studies, we begin by testing the most basic assumption of the intergroup contact hypothesis that outgroup attitudes should be more positive after outgroup interactions but not after non-outgroup interactions.
+For this we use multi-level regression analyses, predicting outgroup attitudes from outgroup interaction and non-outgroup interaction dummy variables.
+We also include the participant means as level two predictors to fully disentangle within- (level 1) and between-participant (level 2) effects of intergroup contact \citep[e.g.,][Section 4.6]{Snijders2012}.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:contactHyp}] \label{hyp:contactHyp}
+        Based on the most general understanding of the contact hypothesis, positive intergroup contacts should be associated with more favorable outgroup attitudes across extensive longitudinal data.
+    \end{hyp}
+
+    \begin{subhyp}[H\ref{hyp:contactDummyML}] \label{hyp:contactDummyML}
+    \addtolength{\leftskip}{\subhypskip}
+    Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
+    \end{subhyp}
+
+    \begin{fleqn}[\eqskip] 
+    \begin{equation} \label{eq:ContactDummy}
+      \begin{split}
+        \textrm{Level 1:} &
+          \begin{aligned}[t]
+            \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
+                               &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
+          \end{aligned} \\
+        \textrm{Level 2:} &
+            \begin{aligned}[t]
+                \ \beta_{0i} = &\ \gamma_{00} + \gamma_{01}MeanOutgroupInteraction_{i} + \\
+                               &\ \gamma_{02}MeanNonOutgroupInteraction_{i} + u_{0i} \\
+                  \beta_{1i} = &\ \gamma_{10} + u_{1i} \\
+                  \beta_{2i} = &\ \gamma_{20} + u_{2i}
+            \end{aligned}
+      \end{split} 
+    \end{equation}
+    \end{fleqn}
+\end{mdframed}
+
+\hl{OPTION 1:} We then seek to investigate intergroup contacts and perceived interaction quality jointly.
+Notably, however, participants are only able to report their interaction quality perceptions if they had an interaction.
+This is considered to be structurally missing data and cannot meaningfully be imputed for modeling.
+To deal with this issue, we mimic the procedure commonly used within the cross-section literature.
+In particular, we conduct a person-level linear regression by aggregating the number of outgroup interactions participants had, their average interaction quality perceptions, as well as their average outgroup attitudes \citep[for possible alternative approaches see,][]{Enders2011}.
+To avoid an underpowered analysis, we use the aggregated data from all three studies.
+
+\hl{OPTION 2:} We then seek to test the full contact hypothesis by investigating intergroup contacts and perceived interaction quality jointly.
+To do so, we conduct a person-level linear regression using person-level aggregated data from all three studies.
+In particular, we aggregate the number of outgroup interactions participants had, their average interaction quality perceptions, as well as their average outgroup attitudes.
+This approach has three main benefits: (1) Interaction quality ratings are only available if participants had an interaction, and the aggregation deals with this structural missingness.
+(2) Using the participant-level data from all three studies, we avoid potential power issues.
+(3) This analysis mimics the analyses conducted within the cross-section literature, where participants are asked to recall how many interactions they had over a one-month period, how positive these interactions were, and what their general attitudes towards the outgroup are.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{subhyp}[H\ref{hyp:contactCor}] \label{hyp:contactCor}
+    \addtolength{\leftskip}{\subhypskip}
+    Participants with more intergroup interactions should have more favorable outgroup attitudes.
+    \end{subhyp}
+
+      \begin{fleqn}[\eqskip] 
+        \begin{equation} \label{eq:ContactCor}
+            r_{\left(ContactFrequency_{i},\ AverageQuality_{i}\right)} > 0
+        \end{equation}
+      \end{fleqn}
+
+    \begin{subhyp}[H\ref{hyp:contactQualLM}] \label{hyp:contactQualLM}
+    \addtolength{\leftskip}{\subhypskip}
+    Participants with more intergroup interactions should have more favorable outgroup attitudes depending on the average interaction quality.
+    \end{subhyp}
+
+      \begin{fleqn}[\eqskip] 
+        \begin{equation} \label{eq:contactQualLM}
+            \begin{split}
+              AverageAttitude_{i} = &\ \beta_{0} + \beta_{1}ContactFrequency_{i} + \\
+                                    &\ \beta_{2}AverageQuality_{i} +\\
+                                    &\ \beta_{3}ContactFrequency_{i} * AverageQuality_{i}
+            \end{split}
+        \end{equation}
+      \end{fleqn}
+
+    \hl{More complete but in my opinion more confusing connotation:}
+
+      \begin{fleqn}[\eqskip] 
+        \begin{equation}
+            \begin{split}
+              \overline{Attitude}_{i} = &\ \beta_{0} + \beta_{1}\left(\sum\nolimits_{t=1}^{T}OutgroupInteraction\right)_{i} + \\
+                                        &\ \beta_{2}\overline{InteractionQuality}_{i} +\\
+                                        &\ \beta_{3}\left(\sum\nolimits_{t=1}^{T}OutgroupInteraction\right)_{i} * \overline{InteractionQuality}_{i}
+            \end{split}
+        \end{equation}
+      \end{fleqn}
+
+      We additionally control for the participant's study membership.
+\end{mdframed}
+Because this analysis uses the data from all three studies, the results of this analysis are presented in the `Robustness, Stability, and Embeddedness across Studies' section.
+
+\subsection{2. Core need fulfillment during intergroup contact.}
+The main proposal of this manuscript has been the assertion that the fulfillment of situation core needs during an interaction will be associated with more positive interaction quality perceptions and, ultimately, more positive outgroup attitudes.
+Thus, for the main set of analyses, we focus on the reported outgroup interactions only.
+For each study, we will use multi-level regressions to test the main three assertions of our proposal (mirroring the basic steps of a traditional mediation analysis).
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:keyNeed}] \label{hyp:keyNeed}
+    Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+    \end{hyp}
+
+    \setcounter{subhyp}{0}
+    \begin{subhyp}[H\ref{hyp:keyNeedPred}] \label{hyp:keyNeedPred}
+    \addtolength{\leftskip}{\subhypskip}
+    Core need fulfillment during outgroup interactions should predict more positive outgroup attitudes.
+    \end{subhyp}
+
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesAttCore}
+        \begin{split}
+            \textrm{Level 1:} &\ Attitude_{ti} = \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}\\
+            \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                              &\ \beta_{1i} = \gamma_{10} + u_{1i}
+        \end{split}
+      \end{equation}
+    \end{fleqn}
+
+    \begin{subhyp}[H\ref{hyp:keyNeedQual}] \label{hyp:keyNeedQual}
+    \addtolength{\leftskip}{\subhypskip}
+    Core need fulfillment during outgroup interactions should also predict higher perceived interaction quality.
+    \end{subhyp}
+
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesQltCore}
+        \begin{split}
+            \textrm{Level 1:} &\ InteractionQuality_{ti} = \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}\\
+            \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                              &\ \beta_{1i} = \gamma_{10} + u_{1i}
+        \end{split}
+      \end{equation}
+    \end{fleqn}
+
+    \begin{subhyp}[H\ref{hyp:keyNeedMediation}] \label{hyp:keyNeedMediation}
+    \addtolength{\leftskip}{\subhypskip}
+    The effect of core need fulfillment on outgroup attitudes should be reduced when considered together with perceived interaction quality.
+    \end{subhyp}
+
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesAttCoreQual}
+        \begin{split}
+          \textrm{Level 1:} &
+            \begin{aligned}[t]
+              \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                                 &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+            \end{aligned} \\
+          \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                            &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                            &\ \beta_{2i} = \gamma_{20} + u_{2i}
+        \end{split} 
+      \end{equation}
+    \end{fleqn}
+\end{mdframed}
+
+\subsection{3. Allport's conditions in extensive longitudinal data.}
+Within the third study, we formally measure all of Allport's optimal contact conditions.
+We use multi-level regression models to test whether the fulfillment of Allport's conditions in real-life data predicts more positive outgroup attitudes and higher perceived interaction quality, using the same approach as for the core need fulfillment above.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:Allport}] \label{hyp:Allport}
+    Based on Allport's optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+    \end{hyp}
+
+    \setcounter{subhyp}{0}
+    \begin{subhyp}[H\ref{hyp:AttAllport}] \label{hyp:AttAllport}
+    \addtolength{\leftskip}{\subhypskip}
+    Higher fulfillment of Allport's conditions during outgroup interactions should predict more positive outgroup attitudes.
+    \end{subhyp}
+
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesAttAllport}
+        \begin{split}
+            \textrm{Level 1:} &\ Attitude_{ti} = \beta_{0i} + \beta_{1i}Allport_{ti} + e_{ti}\\
+            \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                              &\ \beta_{1i} = \gamma_{10} + u_{1i}
+        \end{split}
+      \end{equation}
+    \end{fleqn}
+
+    \begin{subhyp}[H\ref{hyp:QltAllport}] \label{hyp:QltAllport}
+    \addtolength{\leftskip}{\subhypskip}
+    Higher fulfillment of Allport's conditions during outgroup interactions should also predict higher perceived interaction quality.
+    \end{subhyp}
+
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesQltAllport}
+        \begin{split}
+            \textrm{Level 1:} &\ InteractionQuality_{ti} = \beta_{0i} + \beta_{1i}Allport_{ti} + e_{ti}\\
+            \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                              &\ \beta_{1i} = \gamma_{10} + u_{1i}
+        \end{split}
+      \end{equation}
+    \end{fleqn}
+
+    \begin{subhyp}[H\ref{hyp:AttAllportQual}] \label{hyp:AttAllportQual}
+    \addtolength{\leftskip}{\subhypskip}
+    The effect of higher fulfillment of Allport's conditions on outgroup attitudes should be reduced when considered together with perceived interaction quality.
+    \end{subhyp}
+
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesAttAllportQual}
+        \begin{split}
+          \textrm{Level 1:} &
+            \begin{aligned}[t]
+              \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}Allport_{ti} + \\
+                                 &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+            \end{aligned} \\
+          \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                            &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                            &\ \beta_{2i} = \gamma_{20} + u_{2i}
+        \end{split} 
+      \end{equation}
+    \end{fleqn}
+\end{mdframed}
+
+We then compare the effect of Allport's contact conditions with our core need fulfillment by comparing the model fit statistics of the two individual models and by adding both concepts to a joint multi-level regression model, to see whether the two approaches explain the same variance in outgroup attitudes.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:NeedAllport}] \label{hyp:NeedAllport}
+    Based on our proposal, the fulfillment of the core situational need should predict outgroup attitudes at least as well as Allport's conditions.
+    \end{hyp}
+
+    \setcounter{subhyp}{0}
+    \begin{subhyp}[H\ref{hyp:compModel}] \label{hyp:compModel}
+    \addtolength{\leftskip}{\subhypskip}
+    The need model (H\ref{hyp:keyNeedPred}) should predict more variance in outgroup attitudes than the model based on Allport's conditions (H\ref{hyp:AttAllport}).
+    \end{subhyp}
+
+    \begin{fleqn}[\eqskip] 
+        \begin{equation}
+            \begin{split}
+                AIC_{KeyNeedModel} & < AIC_{AllportModel} \\
+                BIC_{KeyNeedModel} & > BIC_{AllportModel}
+            \end{split}
+        \end{equation}
+    \end{fleqn}
+
+    \begin{subhyp}[H\ref{hyp:compTogether}] \label{hyp:compTogether}
+    \addtolength{\leftskip}{\subhypskip}
+    The  effect of key need fulfillment on outgroup attitudes should  persist even when taking other Allport's conditions into account.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for Allport's conditions.
+    \end{subhyp}
+
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesAttCoreAllport}
+        \begin{split}
+          \textrm{Level 1:} &
+            \begin{aligned}[t]
+              \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                                 &\ \beta_{2i}Allport_{ti} + e_{ti}
+            \end{aligned} \\
+          \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                            &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                            &\ \beta_{2i} = \gamma_{20} + u_{2i}
+        \end{split} 
+      \end{equation}
+    \end{fleqn}
+\end{mdframed}
+
+\subsection{4. Robustness, stability, and embeddedness across studies}
+Within the final set of analyses, we look at the broader picture of our results and leverage the data from all participants to contextualize our results.
+
+\paragraph{Robustness within studies}
+To build further confidence in the effect of core need fulfillment during outgroup interactions, we conduct two additional robustness analyses for each study.
+
+Firstly, to check for the role of alternate psychological needs, we add the fulfillment of self-determination theory needs (i.e., competence, autonomy, and relatedness) to the multi-level regression.
+We then also compare the model with models that predicts outgroup attitudes from self-determination theory need fulfillments or core need fulfillments only.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:keyNeedSDT}] \label{hyp:keyNeedSDT}
+    The effect of key need fulfillment on outgroup attitudes should persist even when taking other fundamental psychological needs into account.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
+    \end{hyp}
+
+    \begin{fleqn}[\eqskip-\subhypskip]
+      \begin{equation} \label{eq:SlopesAttCoreSdt}
+        \begin{split}
+          \textrm{Level 1:} &
+            \begin{aligned}[t]
+              \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \beta_{2i}Autonomy_{ti} + \\
+                                 &\ \beta_{3i}Competence_{ti} + \beta_{4i}Relatedness_{ti} + e_{ti}
+            \end{aligned} \\
+          \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                            &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                            &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                            &\ \beta_{3i} = \gamma_{30} + u_{3i} \\
+                            &\ \beta_{4i} = \gamma_{40} + u_{4i}
+        \end{split} 
+      \end{equation}
+    \end{fleqn}
+\end{mdframed}
+
+To ensure that the core need fulfillment is outgroup contact specific, we return to the full sample of intensive longitudinal measurements within each study and test whether there is an interaction effect of outgroup contact (vs.
+no outgroup contact) and core need fulfillment.
+We expect that the effect of core need fulfillment is specific to outgroup interactions and not merely due to a more need-fulfilled life in general.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:keyNeedContactType}] \label{hyp:keyNeedContactType}
+    \addtolength{\leftskip}{1em}
+    The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
+Thus, the effect of key need fulfillment on outgroup attitudes should be stronger for intergroup interactions than for ingroup interactions.
+    \end{hyp}
+
+    \begin{fleqn}[\eqskip-\subhypskip]
+      \begin{equation} \label{eq:SlopesAttCoreXContact}
+        \begin{split}
+          \textrm{Level 1:} &
+            \begin{aligned}[t]
+              \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                                 &\ \beta_{2i}OutgroupInteraction_{ti} + \\
+                                 &\ \beta_{3i}KeyNeedFulfill*OutgroupInteraction_{ti} + e_{ti}
+            \end{aligned} \\
+          \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                            &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                            &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                            &\ \beta_{3i} = \gamma_{30} + u_{3i}
+        \end{split} 
+      \end{equation}
+    \end{fleqn}
+\end{mdframed}
+The results of the robustness analyses are presented in \appref{app:AppendixRobustness} to allow for a more concise presentation of our main hypotheses in the main text.
+
+\paragraph{Stability across studies}
+We assess the stability of our main analyses. We use forest plots (including meta-analytical estimates) to visualize the direction and effect sizes of our three studies.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:Stability}] \label{hyp:Stability}
+    \addtolength{\leftskip}{1em}
+    The effects of our main hypotheses and robustness analyses should be consistent across studies.
+    \end{hyp}
+\end{mdframed}
+
+\paragraph{Embeddedness of code needs}
+We, finally, use the qualitative data from the participants' self-identified core needs to contextualize our results.
+We leverage machine learning to extract a topic model of the free-text entries across the three studies.
+We describe the extracted topics and themes and compare them to the need contents usually found and measured within the psychological literature.
+Full methodological details and visualizations are available in Supplemental Material C.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \addtolength{\leftskip}{1em}
+    \textit{This analysis is data-driven and exploratory. As such, the analysis has no associated hypothesis.}
+\end{mdframed}
+
+\section{Robustness Analyses}
+\label{app:AppendixRobustness}
+
+In this appendix, we present the two additional robustness analyses that we conducted within each of the three studies.
+These analyses are specifically designed to check for alternative need models and to check that the effect of situation core need fulfillment is contact-specific.
+(1) To check for the role of alternate psychological needs, we add the fulfillment of self-determination theory needs (i.e., competence, autonomy, and relatedness) to the multi-level regression.
+We then also compare the model with models that predicts outgroup attitudes from self-determination theory need fulfillments or core need fulfillments only.
+(2) To ensure that the core need fulfillment is outgroup contact specific, we return to the full sample of intensive longitudinal measurements within each study and test whether there is an interaction effect of outgroup contact (vs.
+no outgroup contact) and core need fulfillment.
+We expect that the effect of core need fulfillment is specific to outgroup interactions and not merely due to a more need-fulfilled life in general.
+
+\input{Robustness-Methods-and-Results.tex}
+
+\input{Tables/mdlRobustlong}
+
 \begin{figure}
@@
 
-\printbibliography
-
-\appendix
-
-\section{Appendix A: Hypotheses}
-\label{app:AppendixHypotheses}
-
-\begin{hyp}[H\ref{hyp:contact}] \label{hyp:contact}
-Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
-\end{hyp}
-
-\begin{subhyp}[H\ref{hyp:contactFreq}] \label{hyp:contactFreq}
-\addtolength{\leftskip}{2.5em}
-Participants with more intergroup interactions should have more favorable outgroup attitudes.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:contactDummy}] \label{hyp:contactDummy}
-\addtolength{\leftskip}{2.5em}
-Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:contactFreqQual}] \label{hyp:contactFreqQual}
-\addtolength{\leftskip}{2.5em}
-Participants with more intergroup interactions should have more favorable outgroup attitudes depending on the average interaction quality.
-\end{subhyp}
-
-\begin{hyp}[H\ref{hyp:AllportsConditions}] \label{hyp:AllportsConditions}
-Based on Allport's optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
-\end{hyp}
-
-\setcounter{subhyp}{0}
-\begin{subhyp}[H\ref{hyp:AllportsPred}] \label{hyp:AllportsPred}
-\addtolength{\leftskip}{2.5em}
-Based on Allport's optimal contact conditions, outgroup attitudes should be more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:AllportsQuality}] \label{hyp:AllportsQuality}
-\addtolength{\leftskip}{2.5em}
-Based on past research on the role of interaction quality, interaction quality should be more perceived as more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:AllportsQualityMediation}] \label{hyp:AllportsQualityMediation}
-\addtolength{\leftskip}{2.5em}
-Based on past research on the role of interaction quality, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extent be assumed by interaction quality.
-\end{subhyp}
-
-\begin{hyp}[H\ref{hyp:keyNeed}] \label{hyp:keyNeed}
-Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
-\end{hyp}
-
-\setcounter{subhyp}{0}
-\begin{subhyp}[H\ref{hyp:keyNeedPred}] \label{hyp:keyNeedPred}
-\addtolength{\leftskip}{2.5em}
-Outgroup attitudes should be more favorable after intergroup interactions with high key-need fulfillment.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:keyNeedQual}] \label{hyp:keyNeedQual}
-\addtolength{\leftskip}{2.5em}
-Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:keyNeedMediation}] \label{hyp:keyNeedMediation}
-\addtolength{\leftskip}{2.5em}
-The variance explained in outgroup attitudes by key need fulfillment should to a large extend be assumed by interaction quality.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:keyNeedContactType}] \label{hyp:keyNeedContactType}
-\addtolength{\leftskip}{2.5em}
-The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
-Thus, the effect of key need fulfillment on outgroup attitudes should be stronger for intergroup interactions than for ingroup interactions.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:keyNeedSDT}] \label{hyp:keyNeedSDT}
-\addtolength{\leftskip}{2.5em}
-The effect of key need fulfillment on outgroup attitudes should persist even when taking other fundamental psychological needs into account.
-Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
-\end{subhyp}
-
-\begin{hyp}[H\ref{hyp:comparison}] \label{hyp:comparison}
-Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict outgroup attitudes at least as well as Allport's conditions.
-\end{hyp}
-
-\setcounter{subhyp}{0}
-\begin{subhyp}[H\ref{hyp:compModel}] \label{hyp:compModel}
-\addtolength{\leftskip}{2.5em}
-The need model (H\ref{hyp:keyNeedPred}) should predict more variance in outgroup attitudes than the model based on Allport's conditions (H\ref{hyp:AllportsPred}).
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:compTogether}] \label{hyp:compTogether}
-\addtolength{\leftskip}{2.5em}
-The  effect of key need fulfillment on outgroup attitudes should  persist even when taking other Allport's conditions into account.
-Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for equal status, common goals, collaboration, and structural support.
-\end{subhyp}
-
-\section{Appendix B: Robustness}
-\label{app:AppendixRobustness}
-
 \end{document}

### 2022-11-07 Robustness-Methods-and-Results.Rmd
headers fixed
open science practices linked

@@
 
-The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
+As with the main analyses, full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
 Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
@@
 
-\subsection{Study 1}
+\subsection{Results}
+
+\subsubsection{Study 1}
 
@@
 
-\subsubsection{Results}
-
 ```{r workerModelOlsAttFreqQual, include=FALSE}
@@
 
-\subsection{Study 2}
+\subsubsection{Study 2}
 
@@
 
-\subsubsection{Results}
-
 ```{r studentModelOlsAttFreqQual, include=FALSE}
@@
 
-\subsection{Study 3}
+\subsubsection{Study 3}
 
@@
 ```
-
-\subsubsection{Results}
 

### 2022-11-07 Robustness-Methods-and-Results.tex
headers fixed
open science practices linked

@@
-The full surveys are available in our OSF repository
-\citep{KreienkampMasked2022a} and the full data description is available
-in Online Supplementary Material A. Correlations and descriptive
-statistics of the included variables are available in Table
+As with the main analyses, full surveys are available in our OSF
+repository \citep{KreienkampMasked2022a} and the full data description
+is available in Online Supplementary Material A. Correlations and
+descriptive statistics of the included variables are available in Table
 \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
@@
 
-\subsection{Study 1}
+\subsection{Results}
 
-\subsubsection{Results}
+\subsubsection{Study 1}
 
@@
 
-\subsection{Study 2}
-
-\subsubsection{Results}
+\subsubsection{Study 2}
 
@@
 
-\subsection{Study 3}
-
-\subsubsection{Results}
+\subsubsection{Study 3}
 

### 2022-11-07 Robustness-Methods-and-Results.Rmd
ref fix

@@
 As with the main analyses, full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
-Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
+Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
 
@@
 For this, we analyzed the generalized situational core need fulfillment (either during a contact or about the daytime in general) and tested whether the effect differed during experience sampling measurements with and without outgroup contacts.
-We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`; also see Table \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness}).
+We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`; also see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}).
 Together with a significant main effect of having an outgroup contact, this indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
@@
 When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all three fundamental needs (competence and autonomy needs turning non-significant; all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
-For full results see see Table \ref{tab:robustnessTblLong}, Figure \ref{fig:Robustness}, and Online Supplementary Material A.
+For full results see see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and Online Supplementary Material A.
 There is, thus, considerable evidence lending confidence to the stability and relevance of psychological need fulfillment as a predictor of positive outgroup attitudes for natural intergroup contacts.
@@
 Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteraction")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous study, albeit with a slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see Table \ref{tab:intergroupNeedsTblLong} and for visual comparison see Figure \ref{fig:AllportNeedFulfillment}).
+This finding is consistent with the results of the previous study, albeit with a slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see \tblref{tab:robustnessTblLong} and for visual comparison see \fgrref{fig:Robustness}).
 
@@
 However, different from the first study, relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes in this larger sample.
-For full results see Table \ref{tab:intergroupNeedsTblLong}, Figure \ref{fig:Robustness}, and Online Supplementary Material A.
+For full results see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and Online Supplementary Material A.
 This means that also within this second sample, the fulfillment of psychological needs during intergroup contact remained a key predictor of positive outgroup attitudes, even when taking into account several alternative models.
@@
 This being said, the regression coefficient for the core need was three times larger (with all scaling being equal).
-For full results see Table \ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as Online Supplementary Material A.
-Across all three studies, psychological need fulfillment, thus, remained a robust and flexible predictor of positive outgroup attitudes.
+For full results see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness} as well as Online Supplementary Material A.
 

### 2022-11-07 Robustness-Methods-and-Results.tex
ref fix

@@
 is available in Online Supplementary Material A. Correlations and
-descriptive statistics of the included variables are available in Table
-\ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
+descriptive statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
 
@@
 \textit{t}(1,199) = 4.31, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.07, 0.18{]}; also see Table
-\ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness}). Together
-with a significant main effect of having an outgroup contact, this
-indicates that it is not key need fulfillment in general --- but only
-key need fulfillment during an outgroup contact that predicts more
-positive outgroup attitudes.
+\textit{95\%CI}{[}0.07, 0.18{]}; also see \tblref{tab:robustnessTblLong}
+and \fgrref{fig:Robustness}). Together with a significant main effect of
+having an outgroup contact, this indicates that it is not key need
+fulfillment in general --- but only key need fulfillment during an
+outgroup contact that predicts more positive outgroup attitudes.
 
@@
 \textless{} 0.05, all \textit{p} \textgreater{} 0.544). For full results
-see see Table \ref{tab:robustnessTblLong}, Figure \ref{fig:Robustness},
-and Online Supplementary Material A. There is, thus, considerable
-evidence lending confidence to the stability and relevance of
-psychological need fulfillment as a predictor of positive outgroup
-attitudes for natural intergroup contacts.
+see see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and
+Online Supplementary Material A. There is, thus, considerable evidence
+lending confidence to the stability and relevance of psychological need
+fulfillment as a predictor of positive outgroup attitudes for natural
+intergroup contacts.
 
@@
 number of measurements that did not include an outgroup interaction; For
-full results see Table \ref{tab:intergroupNeedsTblLong} and for visual
-comparison see Figure \ref{fig:AllportNeedFulfillment}).
+full results see \tblref{tab:robustnessTblLong} and for visual
+comparison see \fgrref{fig:Robustness}).
 
@@
 0.08{]}) also predicted positive outgroup attitudes in this larger
-sample. For full results see Table \ref{tab:intergroupNeedsTblLong},
-Figure \ref{fig:Robustness}, and Online Supplementary Material A. This
-means that also within this second sample, the fulfillment of
-psychological needs during intergroup contact remained a key predictor
-of positive outgroup attitudes, even when taking into account several
-alternative models.
+sample. For full results see \tblref{tab:robustnessTblLong} and
+\fgrref{fig:Robustness}, and Online Supplementary Material A. This means
+that also within this second sample, the fulfillment of psychological
+needs during intergroup contact remained a key predictor of positive
+outgroup attitudes, even when taking into account several alternative
+models.
 
@@
 This being said, the regression coefficient for the core need was three
-times larger (with all scaling being equal). For full results see Table
-\ref{tab:robustnessTblLong} and Figure \ref{fig:Robustness} as well as
-Online Supplementary Material A. Across all three studies, psychological
-need fulfillment, thus, remained a robust and flexible predictor of
-positive outgroup attitudes.
+times larger (with all scaling being equal). For full results see
+\tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness} as well as
+Online Supplementary Material A.

### 2022-11-07 manuscript.tex
Updates from Overleaf
present research str

@@
 And third, we test the role of interaction quality in  the relationship of psychological need fulfillment and outgroup attitudes.
-Based on this we formulated three main hypotheses:
+Based on our three main aims we developed a set of four main hypotheses, which are formalized into individual sets of models in our analysis plan.
+
 \begin{enumerate}[label=H\arabic*:]
     \item Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes across extensive longitudinal data.
+    \begin{enumerate}[label=H1\alph*:, leftmargin=\parindent]
+        \item Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
+        \item Participants with more intergroup interactions should have more favorable outgroup attitudes
+        \item Participants with more intergroup interactions should have more favorable outgroup attitudes depending on the average interaction quality.
+    \end{enumerate}
     \item Based on Allport’s optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
+    \begin{enumerate}[label=H2\alph*:, leftmargin=\parindent]
+        \item Higher fulfillment of Allport’s conditions during out-group interactions should predict more positive outgroup attitudes.
+        \item Higher fulfillment of Allport's conditions during outgroup interactions should also predict higher perceived interaction quality.
+        \item The effect of higher fulfillment of Allport's conditions on outgroup attitudes should be reduced when considered together with perceived interaction quality.
+    \end{enumerate}
     \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
 We also expect situational need fulfillments to work at least as well as Allport's optimal contact conditions in predicting outgroup attitudes.
+    \begin{enumerate}[label=H3\alph*:, leftmargin=\parindent]
+        \item Core need fulfillment during outgroup interactions should predict more positive outgroup attitudes.
+        \item Core need fulfillment during outgroup interactions should also predict higher perceived interaction quality.
+        \item The effect of core need fulfillment on outgroup attitudes should be reduced when considered together with perceived interaction quality.
     \end{enumerate}
-Beyond these main hypotheses, we have formulated several sub-hypotheses that form the basis for our analysis plan (these sub-hypotheses also include several robustness checks and are available in \appref{app:AppendixHypotheses}).
+    \item stable and robust (To build further confidence in our results, we assessed two additional models that might offer alternative explanations).
+    \begin{enumerate}[label=H4\alph*:, leftmargin=\parindent]
+        \item The effect of key need fulfillment on outgroup attitudes should persist even when taking other fundamental psychological needs into account.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
+        \item The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
+Thus, the effect of key need fulfillment on outgroup attitudes should be stronger for intergroup interactions than for ingroup interactions.
+        \item The effects of our main hypotheses and robustness analyses should be consistent across studies.
+    \end{enumerate}
+\end{enumerate}
+Beyond these main hypotheses, we have formulated several sub-hypotheses that form the basis for our analysis plan (for the full sub-hypotheses and analysis plan see \appref{app:AppendixHypotheses}).
 
@@
 Our most comprehensive study (Study 3) was fully preregistered  \citep[available at][]{KreienkampMasked2021f}.
-All studies received ethical approval from the University Masked for Peer Review.
-The fully annotated analyses are available in Supplementary Material B.
-
-\section{Analysis Plan}
-\begin{center}
-    \noindent\rule{8cm}{0.4pt}\\
-    \hl{\textit{New Section:}}\\
-    \vspace{-0.25cm}
-    \noindent\rule{8cm}{0.4pt}
-\end{center}
+All studies received ethical approval from University Masked for Peer Review.
+The fully annotated analyses are available in Supplementary Material A.
 
 Given the more complex data structure of the extensive longitudinal data, we opted to test most of our hypotheses using multilevel regression models, where the measurement occasions (level 1) were nested within the participants (level 2).
-Given that more complex dynamic modeling procedures are not necessary to test these more basic hypotheses, we will focus on the contemporaneous effect of the data (e.g., need fulfillment during the intergroup interaction predicts outgroup attitudes following the interaction).
 Such an approach is also tolerant to missing data and uneven case numbers within participants.
@@
 Additionally, both the number of participants and the number of measurements are within the highest percentiles of sample sizes found within the broader intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
-
-For our main theory tests we sequentially focus on five sets of models to test and validate our hypotheses:
-
-\begin{enumerate}
-    \item \textbf{Contact hypothesis in extensive longitudinal data.} Within the individual studies, we begin by testing the most basic assumption of the intergroup contact hypothesis that outgroup attitudes should be more positive after outgroup interactions but not after non-outgroup interactions.
-For this we use multi-level regression analyses, predicting outgroup attitudes from outgroup interaction and non-outgroup interaction dummy variables.
-We also reintroduce the participant means as level two predictors to fully disentangle measurement- (level 1) and participant (level 2) variances.
-
-    Importantly, this initial test of the contact hypothesis in intensive longitudinal data does not consider the influence of interaction quality.
-This is due to the structural missingness of interaction quality --- where people are only able to report their interaction quality perceptions if they had an interaction.
-Such structural missingness should not be imputed, which stands in conflict with (multi-level) linear regression analyses that can only be estimated where all variables have valid data (which would only be measurements following interactions).
-The best way to assess the joint effects of interaction numbers and interaction quality is thus a test on an aggregate level.
-However, as such an aggregation reduces statistical power to the participant level, we assess the full contact hypothesis in the `embeddedness and stability across studies' section, where we combine the data of the three studies (see below).
-    \item \textbf{Core need fulfillment during intergroup contact.} The main proposal of this manuscript has been the assertion that the fulfillment of situation core needs during an interaction will be associated with more positive interaction quality perceptions and, ultimately, more positive outgroup attitudes.
-Thus, for the main set of analyses, we focus on the reported outgroup interactions only.
-For each study, we will use multi-level regressions to test the main three assertions of our proposal (mirroring the basic steps of a traditional mediation analysis).
-    \begin{enumerate}
-        \item Core need fulfillment during outgroup interactions should predict more positive outgroup attitudes.
-To test this sub-hypothesis, we use a two-level regression analysis of outgroup attitudes, with core need fulfillment as the main predictor variable.
-        \item Core need fulfillment during outgroup interactions should also predict higher perceived interaction quality.
-This sub-hypothesis mirrors the one above so that perceived interaction quality is predicted by core need fulfillment in a multi-level regression analysis.
-        \item The effect of core need fulfillment on outgroup attitudes should be reduced when considered together with perceived interaction quality.
-To test whether perceived interaction quality is indeed the psychological mechanism that explains the variance in outgroup attitudes, we use a multi-level regression analysis of outgroup attitudes with core need fulfillment and perceived interaction quality as the main predictor variables.
-    \end{enumerate}
-    \item \textbf{Robustness within studies.} To build further confidence in the effect of core need fulfillment during outgroup interactions, we conduct two additional robustness analyses for each study.
-    \begin{enumerate}
-        \item To check for the role of alternate psychological needs, we add the fulfillment of self-determination theory needs (i.e., competence, autonomy, and relatedness) to the multi-level regression.
-We then also compare the model with models that predicts outgroup attitudes from self-determination theory need fulfillments or core need fulfillments only.
-        \item To ensure that the core need fulfillment is outgroup contact specific, we return to the full sample of intensive longitudinal measurements within each study and test whether there is an interaction effect of outgroup contact (vs.
-no outgroup contact) and core need fulfillment.
-We expect that the effect of core need fulfillment is specific to outgroup interactions and not merely due to a more need fulfilled life in general.
-    \end{enumerate} 
-    \item \textbf{Allport's conditions in extensive longitudinal data.} Within the third study we formally measure all of Allport's optimal contact conditions. 
-    \begin{enumerate}
-        \item We use multi-level regression models to test whether the fulfillment of Allport's conditions in real-life data predicts more positive outgroup attitudes and higher perceived interaction quality, using the same approach as for the core need fulfillment above.
-        \item We then compare the effect of Allport's contact conditions with our core need fulfillment by comparing the model fit statistics of the two individual models and by adding both concepts to a joint multi-level regression model, to see whether the two approaches explain the same variance in outgroup attitudes.
-    \end{enumerate}
-    \item \textbf{Embeddedness and stability across studies.} Within the final set of analyses, we look at the broader picture of our results and leverage the data from all participants to contextualize our results.
-    \begin{enumerate}
-        \item We first assess the stability of our main analyses. We use forest plots (including meta analytical estimates) to visualize the direction and effect sizes of our three studies. 
-        \item We then combine the data from the three studies to test the basic tenets of intergroup contact hypothesis more broadly within the intensive longitudinal real-life data.
-As we have mentioned above, assessing the effects of intergroup contacts and perceived interaction quality jointly is difficult within a multi-level regression because quality perceptions are only available when participants had an interaction.
-To circumvent this issue, we use the data from all participants and aggregate the number of interactions participants had, their average interaction quality perceptions, as well as their average outgroup attitudes.
-We can then use a linear regression analysis to assess the joint effects of intergroup contacts and interaction quality to predict outgroup attitudes (while controlling for the participants' study).
-This not only offers a more general test of the contact hypothesis with real-life data, but the aggregated data also mirrors the most common methodology of assessing intergroup contact effects within the cross-sectional literature --- where participants are asked to recall how many interactions they had over a one month period, how positive these interactions were, and what their general attitudes towards the outgroup are.
-This analysis will thus be able to explore potential discrepancies between our main multi-level analyses, the aggregation of extensive longitudinal data, and traditional participant recall studies.
-        \item We, finally, use the qualitative data from the participants' self-identified core needs to contextualize our results.
-We leverage machine learning to extract a topic model of the free-text entries across the three studies.
-We describe the extracted topics and themes, and compare them to the need contents usually found and measured within the psychological literature.
-Full methodological details and visualizations are available in Supplemental Material C.
-    \end{enumerate}
-\end{enumerate}
 
@@
 
+\subsection{Stability and Conclusion}
+As with the main analyses, we use a forest plot and the associated meta-analytic estimates to assess the stability of the results across the three studies.
+The forest plot shows that the core need fulfillment is also consistently outgroup contact specific (\fgrref[-A]{fig:Robustness}) and remains a meaningful predictor of outgroup attitudes even when controlling for traditional psychological need fulfillments (Figure \fgrref[-B]{fig:Robustness}).
+In sum, we thus find that across all three studies, psychological need fulfillment remained a robust and flexible predictor of positive outgroup attitudes.
+
 \input{Tables/mdlRobustlong}

### 2022-11-08 Methods-and-Results.Rmd
Update Methods-and-Results.Rmd
tbl and fgr refs

@@
 
-NEEDS TO GO SOMEWHERE: To build further confidence in our results, we assessed two additional models that might offer alternative explanations.
-First, to ensure that the effect of core need fulfillment is specific to an actual contact, we compared the effect to core need fulfillment in situations without an intergroup contact.
-
 \section{Study 1}
@@
 The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
-Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
+Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
 
@@
 Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).
-The self-determination theory need measurements are described in Appendix \ref{app:AppendixRobustness}.
+The self-determination theory need measurements are described in \appref{app:AppendixRobustness}.
 
@@
 However, we did find a medium sized correlation between the participants' average contact quality and their average outgroup attitudes (\textit{r} = `r format(round(rAttitudeQuality$r[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],2), nsmall = 2)`, \textit{p} = `r format(round(rAttitudeQuality$P[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],3), nsmall = 3)`).
-And when considering the number of contacts and average contact quality jointly in a linear regression, we additionally found a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of contacts the positive effect of average contact quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblLong}).
+And when considering the number of contacts and average contact quality jointly in a linear regression, we additionally found a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of contacts the positive effect of average contact quality becomes weaker (also see \tblref{tab:intergroupGeneralTblLong}).
 -->
@@
 Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by use centered predictors and reintroducing the means as level two predictors.
-Nonetheless, we also offer an analysis of the joint data sets in Online Supplemental Material A (for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+Nonetheless, we also offer an analysis of the joint data sets in Online Supplemental Material A (for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
 This is unusual and might indicate that the effect is very consistent across participants.
@@
 This should, in turn, be due to a higher perceived contact quality.
-We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived contact quality, and (3) whether the variance explained by the core need is subsumed by the perceived contact quality if considered jointly (for full regression results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
+We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived contact quality, and (3) whether the variance explained by the core need is subsumed by the perceived contact quality if considered jointly (for full regression results see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
 
@@
 However, we found no significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblLong} and Figure \ref{fig:ContactHypothesis}).
+Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see \tblref{tab:intergroupGeneralTblLong} and \fgrref{fig:ContactHypothesis}).
 -->
@@
 We find that in this data set participant-level outgroup contact proportions were also a positive predictor of outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionM")`).
-The relative number of non-outgroup interactions showed no such effect (for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, as well as Online Supplementary Material A).
+The relative number of non-outgroup interactions showed no such effect (for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, as well as Online Supplementary Material A).
 Thus, in our second data set we find that outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
@@
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`).
-Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment} for full results).
+Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment} for full results).
 These results are consistent with the results in Study 1.
@@
 The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
-Correlations and descriptive statistics of the included variables are available in Tables \ref{tab:descrFullWide} and \ref{tab:descrOutWide}.
+Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
 
@@
 -->
-Additionally, in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A).
+Additionally, in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A).
 Thus, in our third data set we found within person contemporaneous effect of intergroup contact was consistent across all three studies.
@@
 We find that the fulfillment of the core need during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
-Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
+Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
 These results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and this effect partially emerged via its effect on perceived interaction quality.
@@
 In the multilevel models we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
-Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
+Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
 These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.
@@
 When comparing the model selection indices, we find that the fulfillment of the situational core need indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
-Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).
+Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
 This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
@@
 \section{Embeddedness and Stability across Studies}
-
-\begin{center}
-    \noindent\rule{8cm}{0.4pt}\\
-    \hl{\textit{New Section:}}\\
-    \vspace{-0.25cm}
-    \noindent\rule{8cm}{0.4pt}
-\end{center}
 
@@
 To do so, we plot the effect sizes of each parameter of interest in a forest plot.
-Forest plots are a popular form of evidence synthesis and are commonly found within meta-analytic efforts.
-By plotting a standardized effect size and confidence interval of key parameters for each study, forest plots offer a visual method of identifying broader patterns across studies.
 This affords us a chance to spot stable as well as unreliable effects more easily.
@@
 
-We assess forest plots of the basic contact hypothesis test (Figure \ref{fig:ContactHypothesis}), the core need fulfillment proposal (Figure \ref{fig:AllportNeedFulfillment}), as well as the robustness analyses (Figure \ref{fig:Robustness}).
+We assess forest plots of the basic contact hypothesis test (\fgrref{fig:ContactHypothesis}), as well as the core need fulfillment proposal (\fgrref{fig:AllportNeedFulfillment}).
 For the basic contact hypothesis test we see that outgroup contact has a strong and consistent effect on outgroup attitudes while interactions with non-outgroup members consistently have no meaningful effect on outgroup attitudes.
 While this would be expected from the general intergroup contact literature, this is not a trivial finding.
-We are among the first to assess the contact hypothesis using real-life intensive longitudinal data and these close to event assessments are comparable but not equivalent to the assessments found in cross-sectional data (also see below).
-When looking at Figure \ref{fig:AllportNeedFulfillment}, we see that the fulfillment of core needs during intergroup contacts is consistently a meaningful predictor of outgroup attitudes and interaction quality perceptions (see Figure \ref{fig:AllportNeedFulfillment} A and B).
+We are among the first to assess the contact hypothesis using real-life intensive longitudinal data and these close to event assessments are comparable but not equivalent to the assessments found in cross-sectional data.
+When looking at the fulfillment of core needs during intergroup contacts, we find that the motivational mechanism is consistently a meaningful predictor of outgroup attitudes and interaction quality perceptions (see \fgrref{fig:AllportNeedFulfillment} A and B).
 We also see that the effect of core need fulfillment on outgroup attitudes is strongly reduced when modeled together with interaction quality perceptions, supporting our assertion that interaction quality offers a psychological mechanism for the direct effect.
-Additionally, the core need fulfillment is also consistently outgroup contact specific (Figure \ref{fig:Robustness} A) and remains a meaningful predictor of outgroup attitudes even when controlling for traditional psychological need fulfillments (Figure \ref{fig:Robustness} B).
 
@@
 In its essence, BERT is a framework that allows users to codify every word in relation to every other word within a large set of documents.
-This task is immensely computationally intensive and most users of the framework don't create their own model.
-We use the "all-mpnet-base-v2" language model for our embedding.
-The model is a community-based version of BERT that uses Microsoft's "mpnet-base" model and is fine-tuned with 1 Billion diverse sentence pairs.
-The model was trained with a 768 dimensional dense vector space (a relatively high number) to represent every word.
-As a result, the model is widely considered to be one of the most accurate all-purpose language models within the open-source BERT framework.
 We extracted 47 topics from the 2,983 interaction goal free-text entries --- a relatively large number of topics.
@@
 
-Thus, almost all other extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}.
+Thus, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}.
 

### 2022-11-08 Methods-and-Results.tex
tbl and fgr refs

@@
-NEEDS TO GO SOMEWHERE: To build further confidence in our results, we
-assessed two additional models that might offer alternative
-explanations. First, to ensure that the effect of core need fulfillment
-is specific to an actual contact, we compared the effect to core need
-fulfillment in situations without an intergroup contact.
-
 \section{Study 1}
@@
 in Online Supplementary Material A. Correlations and descriptive
-statistics of the included variables are available in Table
-\ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.
+statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
 
@@
 strongly agree (+50). The self-determination theory need measurements
-are described in Appendix \ref{app:AppendixRobustness}.
+are described in \appref{app:AppendixRobustness}.
 
@@
 joint data sets in Online Supplemental Material A (for full results see
-Table \ref{tab:intergroupGeneralTblLong}, Figure
-\ref{fig:ContactHypothesis}, and Online Supplementary Material
+\tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
+and Online Supplementary Material
 A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
@@
 perceived contact quality if considered jointly (for full regression
-results see Table \ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment}).
+results see \tblref{tab:intergroupNeedsTblLong} and
+\fgrref{fig:AllportNeedFulfillment}).
 
@@
 non-outgroup interactions showed no such effect (for full results see
-Table \ref{tab:intergroupGeneralTblLong}, Figure
-\ref{fig:ContactHypothesis}, as well as Online Supplementary Material
-A). Thus, in our second data set we find that outgroup contacts show a
-positive effect on outgroup attitudes in the moment and on average
-between participants.
+\tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
+as well as Online Supplementary Material A). Thus, in our second data
+set we find that outgroup contacts show a positive effect on outgroup
+attitudes in the moment and on average between participants.
 
@@
 \textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
-0.07{]}; also see Table \ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment} for full results). These results are
+0.07{]}; also see \tblref{tab:intergroupNeedsTblLong} and
+\fgrref{fig:AllportNeedFulfillment} for full results). These results are
 consistent with the results in Study 1. We, thus, find support for our
@@
 in Online Supplementary Material A. Correlations and descriptive
-statistics of the included variables are available in Tables
-\ref{tab:descrFullWide} and \ref{tab:descrOutWide}.
+statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
 
@@
 interaction with a non-Dutch (which did not relate to outgroup attitudes
-independently; for full results see Table
-\ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis},
+independently; for full results see
+\tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
 and Online Supplementary Material A). Thus, in our third data set we
@@
 (\textit{b} = 0.11, \textit{t}(1,600) = 3.50, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}0.05, 0.17{]}; for full results see Table
-\ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment}). These results indicate that in this
-data set outgroup attitudes were significantly predicted by the
+.001, \textit{95\%CI}{[}0.05, 0.17{]}; for full results see
+\tblref{tab:intergroupNeedsTblLong} and
+\fgrref{fig:AllportNeedFulfillment}). These results indicate that in
+this data set outgroup attitudes were significantly predicted by the
 fulfillment of core situational needs and this effect partially emerged
@@
 (\textit{b} = 0.09, \textit{t}(1,600) = 2.89, \textit{p} = 0.004,
-\textit{95\%CI}{[}0.03, 0.15{]}; also see Table
-\ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment}). These results indicate that in this
-data set the fulfillment of Allport's conditions had a significant
+\textit{95\%CI}{[}0.03, 0.15{]}; also see
+\tblref{tab:intergroupNeedsTblLong} and
+\fgrref{fig:AllportNeedFulfillment}). These results indicate that in
+this data set the fulfillment of Allport's conditions had a significant
 influence on outgroup attitudes and this effect is likely, in parts,
@@
 \textit{t}(1,600) = 3.85, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.08, 0.17{]}; also see Table
-\ref{tab:intergroupNeedsTblLong} and Figure
-\ref{fig:AllportNeedFulfillment}). This indicates that, although both
+\textit{95\%CI}{[}0.08, 0.17{]}; also see
+\tblref{tab:intergroupNeedsTblLong} and
+\fgrref{fig:AllportNeedFulfillment}). This indicates that, although both
 Allport's conditions and the core need fulfillment seem to (in part)
@@
 
-We assess forest plots of the basic contact hypothesis test (Figure
-\ref{fig:ContactHypothesis}), the core need fulfillment proposal (Figure
-\ref{fig:AllportNeedFulfillment}), as well as the robustness analyses
-(Figure \ref{fig:Robustness}). For the basic contact hypothesis test we
-see that outgroup contact has a strong and consistent effect on outgroup
-attitudes while interactions with non-outgroup members consistently have
-no meaningful effect on outgroup attitudes. While this would be expected
-from the general intergroup contact literature, this is not a trivial
-finding. We are among the first to assess the contact hypothesis using
-real-life intensive longitudinal data and these close to event
-assessments are comparable but not equivalent to the assessments found
-in cross-sectional data (also see below). When looking at Figure
-\ref{fig:AllportNeedFulfillment}, we see that the fulfillment of core
-needs during intergroup contacts is consistently a meaningful predictor
-of outgroup attitudes and interaction quality perceptions (see Figure
-\ref{fig:AllportNeedFulfillment} A and B). We also see that the effect
-of core need fulfillment on outgroup attitudes is strongly reduced when
-modeled together with interaction quality perceptions, supporting our
-assertion that interaction quality offers a psychological mechanism for
-the direct effect. Additionally, the core need fulfillment is also
-consistently outgroup contact specific (Figure \ref{fig:Robustness} A)
-and remains a meaningful predictor of outgroup attitudes even when
-controlling for traditional psychological need fulfillments (Figure
-\ref{fig:Robustness} B).
+We assess forest plots of the basic contact hypothesis test
+(\fgrref{fig:ContactHypothesis}), the core need fulfillment proposal
+(\fgrref{fig:AllportNeedFulfillment}), as well as the robustness
+analyses (\fgrref{fig:Robustness}). For the basic contact hypothesis
+test we see that outgroup contact has a strong and consistent effect on
+outgroup attitudes while interactions with non-outgroup members
+consistently have no meaningful effect on outgroup attitudes. While this
+would be expected from the general intergroup contact literature, this
+is not a trivial finding. We are among the first to assess the contact
+hypothesis using real-life intensive longitudinal data and these close
+to event assessments are comparable but not equivalent to the
+assessments found in cross-sectional data (also see below). When looking
+at \fgrref{fig:AllportNeedFulfillment}, we see that the fulfillment of
+core needs during intergroup contacts is consistently a meaningful
+predictor of outgroup attitudes and interaction quality perceptions (see
+\fgrref{fig:AllportNeedFulfillment} A and B). We also see that the
+effect of core need fulfillment on outgroup attitudes is strongly
+reduced when modeled together with interaction quality perceptions,
+supporting our assertion that interaction quality offers a psychological
+mechanism for the direct effect.
 

### 2022-11-08 Methods-and-Results.tex
initial shortening

@@
 
-\begin{center}
-    \noindent\rule{8cm}{0.4pt}\\
-    \hl{\textit{New Section:}}\\
-    \vspace{-0.25cm}
-    \noindent\rule{8cm}{0.4pt}
-\end{center}
-
 Beyond the individual results of the three studies, we conducted three
@@
 three studies. To do so, we plot the effect sizes of each parameter of
-interest in a forest plot. Forest plots are a popular form of evidence
-synthesis and are commonly found within meta-analytic efforts. By
-plotting a standardized effect size and confidence interval of key
-parameters for each study, forest plots offer a visual method of
-identifying broader patterns across studies. This affords us a chance to
-spot stable as well as unreliable effects more easily. While not the
-focus of our efforts here, forest plots are commonly accompanied with a
-meta-analytic effect size that summarizes the effect size across
-studies.
+interest in a forest plot. This affords us a chance to spot stable as
+well as unreliable effects more easily. While not the focus of our
+efforts here, forest plots are commonly accompanied with a meta-analytic
+effect size that summarizes the effect size across studies.
 
 We assess forest plots of the basic contact hypothesis test
-(\fgrref{fig:ContactHypothesis}), the core need fulfillment proposal
-(\fgrref{fig:AllportNeedFulfillment}), as well as the robustness
-analyses (\fgrref{fig:Robustness}). For the basic contact hypothesis
-test we see that outgroup contact has a strong and consistent effect on
-outgroup attitudes while interactions with non-outgroup members
-consistently have no meaningful effect on outgroup attitudes. While this
-would be expected from the general intergroup contact literature, this
-is not a trivial finding. We are among the first to assess the contact
-hypothesis using real-life intensive longitudinal data and these close
-to event assessments are comparable but not equivalent to the
-assessments found in cross-sectional data (also see below). When looking
-at \fgrref{fig:AllportNeedFulfillment}, we see that the fulfillment of
-core needs during intergroup contacts is consistently a meaningful
+(\fgrref{fig:ContactHypothesis}), as well as the core need fulfillment
+proposal (\fgrref{fig:AllportNeedFulfillment}). For the basic contact
+hypothesis test we see that outgroup contact has a strong and consistent
+effect on outgroup attitudes while interactions with non-outgroup
+members consistently have no meaningful effect on outgroup attitudes.
+While this would be expected from the general intergroup contact
+literature, this is not a trivial finding. We are among the first to
+assess the contact hypothesis using real-life intensive longitudinal
+data and these close to event assessments are comparable but not
+equivalent to the assessments found in cross-sectional data. When
+looking at the fulfillment of core needs during intergroup contacts, we
+find that the motivational mechanism is consistently a meaningful
 predictor of outgroup attitudes and interaction quality perceptions (see
@@
 BERT is a framework that allows users to codify every word in relation
-to every other word within a large set of documents. This task is
-immensely computationally intensive and most users of the framework
-don't create their own model. We use the ``all-mpnet-base-v2'' language
-model for our embedding. The model is a community-based version of BERT
-that uses Microsoft's ``mpnet-base'' model and is fine-tuned with 1
-Billion diverse sentence pairs. The model was trained with a 768
-dimensional dense vector space (a relatively high number) to represent
-every word. As a result, the model is widely considered to be one of the
-most accurate all-purpose language models within the open-source BERT
-framework. We extracted 47 topics from the 2,983 interaction goal
-free-text entries --- a relatively large number of topics. The higher
-number of topics allows us to retain more of the smaller topics and
-leaves a relatively low number of 308 free-text entries unclassified
-(10.33\%). A full write up of the topic modeling process is available in
-Online Supplemental Material C.
+to every other word within a large set of documents. We extracted 47
+topics from the 2,983 interaction goal free-text entries --- a
+relatively large number of topics. The higher number of topics allows us
+to retain more of the smaller topics and leaves a relatively low number
+of 308 free-text entries unclassified (10.33\%). A full write up of the
+topic modeling process is available in Online Supplemental Material C.
 
@@
 
-Thus, almost all other extracted topics fall into broader or narrower
-need concepts that are commonly discussed within the psychological needs
+Thus, almost all extracted topics fall into broader or narrower need
+concepts that are commonly discussed within the psychological needs
 literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core

### 2022-11-08 manuscript.tex
typos
shortened present research

@@
 At the same time, analytical methods for such more complex data have become more readily available, making the analyses more approachable \citep[e.g., see][]{ODonnell2021}.
-Given these technological and methodological developments, we were able to collect a large amount of real-life data following the daily intergroup interactions of recent migrants with the majority group members.
+Given these technological and methodological developments, we were able to collect three independent studies of extensive real-life data following the daily intergroup interactions of recently arrived migrants with the majority-group members.
 
 \section{The Present Research}
-The aim of this paper is essentially threefold.
+Using three independent sets of extensive longitudinal data (Studies 1–3), the aim of this paper is essentially threefold.
 First, our study is among the first to test the fundamental tenets of intergroup contact and Allport's conditions in real-life extensive longitudinal data.
-Second, we test whether the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
-And third, we test the role of interaction quality in  the relationship of psychological need fulfillment and outgroup attitudes.
-Based on our three main aims we developed a set of four main hypotheses, which are formalized into individual sets of models in our analysis plan.
+Translating the contact hypothesis into extensive longitudinal data is not a trivial task, as past research traditions have used two fundamentally different approaches.
+While lab studies have tended to focus on the effect of a single positive interaction, cross-section studies have primarily investigated the frequency of positive interactions more generally.
+Extensive longitudinal data allows us to investigate both.
+We can test whether having an interaction vs.
+not having an interaction impacts outgroup attitudes, but we can also use the participant's 30-day contact reports to test whether participants with more positive interactions tend to have more positive outgroup attitudes.
+Testing both approaches of the contact hypothesis allows us to go beyond a replication of the basic theory but could disentangle individual- from aggregated contact effects and would allow for a direct comparison with both bodies of literature.
+We will test the effect of individual interactions within each study using a multilevel model, but to avoid power limitations, we will test the collective effect of contact frequency and -quality after the individual studies, across all participants.
+\begin{enumerate}[leftmargin=1.5\parindent]
+    \item[H1:] Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for more favorable outgroup attitudes within and across extensive longitudinal data.
+\end{enumerate}
 
-\begin{enumerate}[label=H\arabic*:]
-    \item Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes across extensive longitudinal data.
-    \begin{enumerate}[label=H1\alph*:, leftmargin=\parindent]
-        \item Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
-        \item Participants with more intergroup interactions should have more favorable outgroup attitudes
-        \item Participants with more intergroup interactions should have more favorable outgroup attitudes depending on the average interaction quality.
+The test of Allport's conditions is notably restricted to measurements that report on outgroup interactions because Allport's conditions and interaction quality ratings cannot meaningfully be measured or imputed if participants did not have an interaction.
+Focusing on the interactions in detail, we use a multi-level regression model to test whether interactions that are higher in the fulfillment of Allport's conditions predict more favorable outgroup attitudes.
+We would also expect that this is due to such interactions being perceived as higher in interaction quality.
+\begin{enumerate}[leftmargin=1.5\parindent]
+    \item[H2:] Based on the literature about Allport’s optimal contact conditions, intergroup interactions that are higher in equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
 \end{enumerate}
-    \item Based on Allport’s optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
-    \begin{enumerate}[label=H2\alph*:, leftmargin=\parindent]
-        \item Higher fulfillment of Allport’s conditions during out-group interactions should predict more positive outgroup attitudes.
-        \item Higher fulfillment of Allport's conditions during outgroup interactions should also predict higher perceived interaction quality.
-        \item The effect of higher fulfillment of Allport's conditions on outgroup attitudes should be reduced when considered together with perceived interaction quality.
+
+Our second aim is to test our main theoretical proposal that the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
+As our main proposal is concerned with the mechanisms of successful intergroup contact, we again focus on outgroup interaction reports.
+Within a multi-level model, we expect interactions that are higher in situational core need fulfillment to be perceived as more positive, and as a result that these interactions also predict more positive outgroup attitudes.
+We also expect the needs mechanism to work at least as well as Allport's conditions.
+We particularly expect part of Allport's contact conditions to be a static set of situational needs so that the situational core need fulfillment should explain some of the same variance in outgroup attitudes.
+\begin{enumerate}[leftmargin=1.5\parindent]
+    \item[H3:] Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
+We also expect situational need fulfillments to work at least as well as Allport's optimal contact conditions in predicting outgroup attitudes.
 \end{enumerate}
-    \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
-We also expect situational need fulfillments to work at least as well as Allport's optimal contact conditions in predicting outgroup attitudes.
-    \begin{enumerate}[label=H3\alph*:, leftmargin=\parindent]
-        \item Core need fulfillment during outgroup interactions should predict more positive outgroup attitudes.
-        \item Core need fulfillment during outgroup interactions should also predict higher perceived interaction quality.
-        \item The effect of core need fulfillment on outgroup attitudes should be reduced when considered together with perceived interaction quality.
-    \end{enumerate}
-    \item stable and robust (To build further confidence in our results, we assessed two additional models that might offer alternative explanations).
-    \begin{enumerate}[label=H4\alph*:, leftmargin=\parindent]
-        \item The effect of key need fulfillment on outgroup attitudes should persist even when taking other fundamental psychological needs into account.
-Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
-        \item The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
-Thus, the effect of key need fulfillment on outgroup attitudes should be stronger for intergroup interactions than for ingroup interactions.
-        \item The effects of our main hypotheses and robustness analyses should be consistent across studies.
-    \end{enumerate}
-\end{enumerate}
-Beyond these main hypotheses, we have formulated several sub-hypotheses that form the basis for our analysis plan (for the full sub-hypotheses and analysis plan see \appref{app:AppendixHypotheses}).
 
-To test our main hypotheses, we collected three independent sets of extensive longitudinal data (Studies 1–3).
-The full surveys are available in Supplementary Materials A as well as in our open science repository \citep[including a complete codebook, see][]{KreienkampMasked2022a}.
-Our most comprehensive study (Study 3) was fully preregistered  \citep[available at][]{KreienkampMasked2021f}.
-All studies received ethical approval from University Masked for Peer Review.
-The fully annotated analyses are available in Supplementary Material A.
+Our third aim is to ensure that our results are robust, stable, and ecologically valid.
+To test the robustness of our need-based mechanism we test whether the need mechanism is indeed specific to outgroup interactions and whether the process could be explained by a smaller set of fundamental needs instead.
+We present the full robustness analyses in \appref{app:AppendixRobustness}.
+To test the stability and reliability of our results, we utilize forest plots and meta-analytic estimates for our main analyses.
+To assess the embeddedness of our situational core needs, we use an exploratory topic model for the participants' free-text entries and compare the extracted content topics with themes commonly found within the motivational literature.
 
-Given the more complex data structure of the extensive longitudinal data, we opted to test most of our hypotheses using multilevel regression models, where the measurement occasions (level 1) were nested within the participants (level 2).
+Before we turn to the individual studies, we would like to discuss two methodological matters.
+Firstly, we opted to test most of our hypotheses using multilevel regression models, where the measurement occasions (level 1) were nested within the participants (level 2).
 Such an approach is also tolerant to missing data and uneven case numbers within participants.
-As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text \citep[][; for the full modeling process see Supplementary Material B]{Bliese2013}.
+As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text \citep[][; for the full modeling process see Supplementary Material A]{Bliese2013}.
+Secondly, statistical power is notoriously difficult to estimate for intensive longitudinal- and multilevel models because of the complex covariance structures.
+However, for all studies both the number of participants and the number of measurements are within the highest percentiles of sample sizes found within the broader intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
+Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes for the contemporaneous effects we assess here.
+The sample sizes were only increased to allow for between-subjects comparisons and future, more complicated, time-series modeling.
 
-Statistical power is notoriously difficult to estimate for intensive longitudinal- and multilevel models because of the complex covariance structures.
-However, while power simulations require researchers to make several key assumptions, a major meta-analysis of the intergroup contact hypothesis estimates the average effect size of intergroup contact to be at around: $r$ = .21 \citep[][]{Pettigrew2006}.
-For such a relatively small effect size, cross-sectional data collections would need to collect 175 to 212 participants (for correlational- and linear regression analyses with .8 power respectively).
-Given that even our smallest sample captured 387 intergroup contacts, each of the studies should have abandoned power to detect even smaller effect sizes than the effects commonly found within the literature.
-Additionally, both the number of participants and the number of measurements are within the highest percentiles of sample sizes found within the broader intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
+Finally, for our most comprehensive study (Study 3) we preregistered both the hypotheses as well as the analysis plan \citep[available at][]{KreienkampMasked2021f}.
+All studies received ethical approval from University Masked for Peer Review and none of the data has been published elsewhere.
+The detailed hypotheses and analysis plan are available in \appref{app:AppendixHypotheses}.
+The full surveys, code, and materials are available in our open science repository \citep[including a complete codebook;][]{KreienkampMasked2022a}.
+Additionally, the fully annotated analyses are available in Supplementary Material A.
 
@@
                 AIC_{KeyNeedModel} & < AIC_{AllportModel} \\
-                BIC_{KeyNeedModel} & > BIC_{AllportModel}
+                BIC_{KeyNeedModel} & < BIC_{AllportModel}
             \end{split}

### 2022-11-08 Methods-and-Results.Rmd
M&R shortening

@@
 Data was collected from May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all participants started the study within the first two days).
-
-The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
-Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide} (full data description is available in Online Supplementary Material A).
 
@@
 
-For the core situational need, we asked participants in an open ended text field: “\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}”.
+For the core situational need, we asked participants in an open-ended text field: “\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}”.
 Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).
@@
 \subsubsection{Contact Hypothesis}
-<!-- We tested the most general contact hypothesis in two steps.
-First, we assessed whether overall between participants more intergroup interactions were related to to more positive average outgroup attitudes.
-Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions).
-We find that neither the overall number of contacts nor the number of experience sampling responses with a contact were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`).
-However, we did find a medium sized correlation between the participants' average contact quality and their average outgroup attitudes (\textit{r} = `r format(round(rAttitudeQuality$r[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],2), nsmall = 2)`, \textit{p} = `r format(round(rAttitudeQuality$P[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],3), nsmall = 3)`).
-And when considering the number of contacts and average contact quality jointly in a linear regression, we additionally found a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of contacts the positive effect of average contact quality becomes weaker (also see \tblref{tab:intergroupGeneralTblLong}).
--->
 We used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
 We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
-Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by use centered predictors and reintroducing the means as level two predictors.
-Nonetheless, we also offer an analysis of the joint data sets in Online Supplemental Material A (for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by use centered predictors and reintroducing the means as level two predictors (\citealp{Yaremych2021}; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
 This is unusual and might indicate that the effect is very consistent across participants.
@@
 Thus, in our first data we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data.
-While this offers support for the most basic premise of the intergroup contact hypothesis (i.e., that any interaction will lead to more positive outgroup attitudes), this analysis does not consider any notion of interaction quality.
-We assess the conditional effects of interaction numbers and interaction quality ratings after we report on the individual studies to avoid under-powered analyses.
-
-\subsubsection{Core Need}The main proposal of our article is that the success of an outgroup contact might be explained by whether or not the contact fulfilled the person's core situational need.
-This should, in turn, be due to a higher perceived contact quality.
-We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived contact quality, and (3) whether the variance explained by the core need is subsumed by the perceived contact quality if considered jointly (for full regression results see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
-
+
+\subsubsection{Core Need}
 ```{r workerOutModelMLAttNull, include=FALSE}
@@
 
+The main proposal of our article is that the success of an outgroup contact might be explained by whether or not the contact fulfilled the person's core situational need.
+This should, in turn, be due to a higher perceived contact quality.
+We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived contact quality, and (3) whether the variance explained by the core need is subsumed by the perceived contact quality if considered jointly.
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCore, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreCI, varName = "keymotive_fulfillemt_1_cwc")`) and also predicted higher perceived contact quality (random intercept model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Qlt$lmeInterceptCore, lmerCI = mdlWorkerOut$Qlt$lmerInterceptCoreCI, varName = "keymotive_fulfillemt_1_cwc")`).
@@
 Data was collected from November 19\textsuperscript{th}, 2018 through January 6\textsuperscript{th}, 2019.
-
-The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
-Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+Correlations and descriptive statistics of the included variables are again available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
 
@@
 \paragraph{Outgroup Attitudes}As in Study 1, attitudes towards the Dutch majority outgroup were again measured using the feeling thermometer.
-All survey details are also available in our OSF repository \citep{KreienkampMasked2022a} and Online Supplemental Materials A.
 
@@
 \subsubsection{Contact Hypothesis}
-<!-- We tested the most general contact hypothesis as in Study 1.
-We found a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-However, we found no significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see \tblref{tab:intergroupGeneralTblLong} and \fgrref{fig:ContactHypothesis}).
--->
 We tested the most general contact hypothesis as we did for Study 1.
-We, again, used a multilevel regression analysis to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
 We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently).
 We again added the participant means back into the model.
-Because these are the means of the contact dummy variables they are the proportion of measurements that included a particular contact.
-This not only adjusts the model for unequal cell sizes but allows us to see whether between subject differences in the relative number of interactions had an effect on outgroup attitudes.
 We find that in this data set participant-level outgroup contact proportions were also a positive predictor of outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionM")`).
 The relative number of non-outgroup interactions showed no such effect (for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, as well as Online Supplementary Material A).
-Thus, in our second data set we find that outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.
+Thus, in our second data set we also find that outgroup contacts show a positive effect on outgroup attitudes in the moment.
+We additionally also find an average between participant effect of the relative number of interactions participants had.
 
@@
 Data were collected from November 8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020.
-
-The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A.
 Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
@@
 \paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup was again measured using the feeling thermometer, as in studies one and two.
-All survey details are also available in our OSF repository \citep{KreienkampMasked2022a} and Online Supplemental Materials A.
 
@@
 \subsubsection{Contact Hypothesis}
-<!-- As in Studies 1 and 2, we first conducted a general contact hypothesis test.
-We found no correlation between the overall number of intergroup contacts and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (|\textit{r}| < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-However, we did find a significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`).
-When considering the number of interactions and average interaction quality jointly in a linear regression, we only found a main effect of average perceived interaction quality on outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of the number of contacts nor an interaction effect.
-This result mirrors that of Study 1 but is inconsistent with the second study.
--->
-Additionally, in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A).
-Thus, in our third data set we found within person contemporaneous effect of intergroup contact was consistent across all three studies.
+In the multilevel regression, we find that having an outgroup interaction was again associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A).
+Thus, in our third data set we find that the within-person contemporaneous effect of intergroup contact was consistent across all three studies.
 
@@
 
-Similarly to the previous studies, we again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+Analogous to the previous studies, we again sequentially tested whether the fulfillment of the core need during an outgroup interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
 We find that the fulfillment of the core need during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
 Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
-These results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and this effect partially emerged via its effect on perceived interaction quality.
+As with the previous two studies, these results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and the results suggest that this might be due to higher perceived interaction quality.
 
@@
 
-To test wether Allport's conditions or the core need fulfillment are better at predicting outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
+To test whether Allport's conditions or the core need fulfillment are better at predicting outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
 When comparing the model selection indices, we find that the fulfillment of the situational core need indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
@@
 
-\section{Embeddedness and Stability across Studies}
+\section{Robustness, Stability, and Embeddeness across Studies}
 
@@
 While not the focus of our efforts here, forest plots are commonly accompanied with a meta-analytic effect size that summarizes the effect size across studies.
-
-We assess forest plots of the basic contact hypothesis test (\fgrref{fig:ContactHypothesis}), as well as the core need fulfillment proposal (\fgrref{fig:AllportNeedFulfillment}).
-For the basic contact hypothesis test we see that outgroup contact has a strong and consistent effect on outgroup attitudes while interactions with non-outgroup members consistently have no meaningful effect on outgroup attitudes.
+For the basic contact hypothesis test we see that outgroup contact has a strong and consistent effect on outgroup attitudes while interactions with non-outgroup members consistently have no meaningful effect on outgroup attitudes (\fgrref{fig:ContactHypothesis}).
 While this would be expected from the general intergroup contact literature, this is not a trivial finding.
 We are among the first to assess the contact hypothesis using real-life intensive longitudinal data and these close to event assessments are comparable but not equivalent to the assessments found in cross-sectional data.
-When looking at the fulfillment of core needs during intergroup contacts, we find that the motivational mechanism is consistently a meaningful predictor of outgroup attitudes and interaction quality perceptions (see \fgrref{fig:AllportNeedFulfillment} A and B).
+When looking at the fulfillment of core needs during intergroup contacts, we find that the motivational mechanism is consistently a meaningful predictor of outgroup attitudes and interaction quality perceptions (see \fgrref[ A and B]{fig:AllportNeedFulfillment}).
 We also see that the effect of core need fulfillment on outgroup attitudes is strongly reduced when modeled together with interaction quality perceptions, supporting our assertion that interaction quality offers a psychological mechanism for the direct effect.
@@
 \subsection{General contact hypothesis}
-
 ```{r join data sets for analysis, include=FALSE}
@@
 We have, however, not brought the two elements of the contact hypothesis together in a single analysis.
-This is mainly due to the difficulty that interaction quality ratings are only possible when participants had an interaction --- which means that the two factors cannot be assessed in a multilevel analysis that models individual measurement occasions.
-This has not been an issue in the past literature because experimental and cross-sectional data collections have only considered cases in which intergroup contacts were present.
-Outside of the lab, the most common method has been to ask participants to recall how many interactions they had over the past month, how positive these interactions were, and how positive they feel towards the outgroup in general.
-The effects of intergroup contacts, interaction quality, and outgroup attitudes are thus summarized by the participant in a cognitive recall aggregation.
-Intensive longitudinal data also allows for aggregation of all three variables, with the differences that the measurements are aggregated from individual reports that are close to the actual experience.
-However, this aggregation process summarizes the dense multitude of measurement occasions as single summary statistics per participants.
-This, by extension, means that we face statistical power restrictions on the person level and have thus decided to only present this analysis based on a combined data set of all three studies.
-
-We run a linear regression model where average outgroup attitudes are predicted by the number of interactions and the average interaction quality ratings of all participants across the three studies.
+To jointly test the effects of contact frequency and average interaction quality, we run a linear regression model where average outgroup attitudes are predicted by the number of interactions and the average interaction quality ratings of all participants across the three studies.
 We do so while controlling for the possible effects of study-specific differences.
@@
 The average interaction quality perceptions had a much smaller effect (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "AvQualityOut_c", ci = TRUE)`), and we do not find the most important interaction effect at all.
-In short, the effect of outgroup interactions did not depend on the average interaction quality, so that participants who on average had more positive interactions were not statistically more likely to show higher average outgroup attitudes than those with more negative interactions.
-This result is surprising because it contradicts the tenet of the intergroup contact hypothesis that intergroup contact depends on positive contact.
+In short, the effect of interaction frequency did not depend on the average interaction quality.
 
@@
 Similarly, socializing and celebrations were also explicit social needs (incl., parties).
-Another set of topics was more practically oriented, when participants sought to share food and cook cook together, or had organizational needs (e.g., housing, cleaning, and living).
-
-A reasonable set of contact goals were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned inquiry and information needs more generally (e.g., seeking answers, bureaucratic information).
-A further set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel related goals in their interactions with the majority group members.
+This also included a subtopic of social spiritual, religious, and otherwise transcendental needs (incl.
+meditation, prayer, religious services).
+Among the leisure-oriented topics was also a set of contact goals that were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned inquiry and information needs more generally (e.g., seeking answers, bureaucratic information).
+A similar set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel related goals in their interactions with the majority group members.
 
@@
 Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members.
-A final topic was that of spiritual, religious, and otherwise transcendental needs (incl.
-meditation, prayer, religious services).
-
-Thus, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}.
+Another topic less commonly found within the literature were more practically oriented needs, where participants sought to share food and cook together, or had organizational needs (e.g., housing, cleaning, and co-living).
+In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyper parameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
+The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
 

### 2022-11-08 Methods-and-Results.tex
M&R shortening

@@
 all participants started the study within the first two days).
-
-The full surveys are available in our OSF repository
-\citep{KreienkampMasked2022a} and the full data description is available
-in Online Supplementary Material A. Correlations and descriptive
-statistics of the included variables are available in
-\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+Correlations and descriptive statistics of the included variables are
+available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}
+(full data description is available in Online Supplementary Material A).
 
@@
 
-For the core situational need, we asked participants in an open ended
+For the core situational need, we asked participants in an open-ended
 text field:
@@
 inequalities by use centered predictors and reintroducing the means as
-level two predictors. Nonetheless, we also offer an analysis of the
-joint data sets in Online Supplemental Material A (for full results see
+level two predictors (\citealp{Yaremych2021}; for full results see
 \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
@@
 show a positive effect on outgroup attitudes within real-life data.
-While this offers support for the most basic premise of the intergroup
-contact hypothesis (i.e., that any interaction will lead to more
-positive outgroup attitudes), this analysis does not consider any notion
-of interaction quality. We assess the conditional effects of interaction
-numbers and interaction quality ratings after we report on the
-individual studies to avoid under-powered analyses.
 
@@
 whether the variance explained by the core need is subsumed by the
-perceived contact quality if considered jointly (for full regression
-results see \tblref{tab:intergroupNeedsTblLong} and
-\fgrref{fig:AllportNeedFulfillment}).
-
-We find that in the multilevel models, the fulfillment of core
-situational needs during outgroup contacts was associated with more
-positive outgroup attitudes (random slopes model; \textit{b} = 0.17,
-\textit{t}(365) = 2.93, \textit{p} = 0.004, \textit{95\%CI}{[}0.06,
-0.29{]}) and also predicted higher perceived contact quality (random
-intercept model; \textit{b} = 0.42, \textit{t}(365) = 8.07, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}0.32, 0.52{]}). Moreover, when we
-consider the influences of core need fulfillment and contact quality on
-outgroup attitudes jointly, we find that virtually all variance is
-explained by perceived contact quality (random slopes mode; \textit{b} =
-0.23, \textit{t}(364) = 4.22, \textit{p} \textless{} .001,
+perceived contact quality if considered jointly. We find that in the
+multilevel models, the fulfillment of core situational needs during
+outgroup contacts was associated with more positive outgroup attitudes
+(random slopes model; \textit{b} = 0.17, \textit{t}(365) = 2.93,
+\textit{p} = 0.004, \textit{95\%CI}{[}0.06, 0.29{]}) and also predicted
+higher perceived contact quality (random intercept model; \textit{b} =
+0.42, \textit{t}(365) = 8.07, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.32, 0.52{]}). Moreover, when we consider the
+influences of core need fulfillment and contact quality on outgroup
+attitudes jointly, we find that virtually all variance is explained by
+perceived contact quality (random slopes mode; \textit{b} = 0.23,
+\textit{t}(364) = 4.22, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
@@
 daily basis. Data was collected from November 19\textsuperscript{th},
-2018 through January 6\textsuperscript{th}, 2019.
-
-The full surveys are available in our OSF repository
-\citep{KreienkampMasked2022a} and the full data description is available
-in Online Supplementary Material A. Correlations and descriptive
-statistics of the included variables are available in
+2018 through January 6\textsuperscript{th}, 2019. Correlations and
+descriptive statistics of the included variables are again available in
 \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
@@
 As in Study 1, attitudes towards the Dutch majority outgroup were again
-measured using the feeling thermometer. All survey details are also
-available in our OSF repository \citep{KreienkampMasked2022a} and Online
-Supplemental Materials A.
+measured using the feeling thermometer.
 
@@
 
-We tested the most general contact hypothesis as we did for Study 1. We,
-again, used a multilevel regression analysis to check whether having an
-interaction with an outgroup member had a situational (i.e.,
-contemporaneous) effect within the participants. We find that having an
-outgroup interaction is indeed associated with significantly more
-positive outgroup attitudes within the participants (random slopes
-model; \textit{b} = 2.83, \textit{t}(4,850) = 3.57, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}1.28, 4.38{]}), even after
-controlling for having an interaction with a non-Dutch person (which did
-not relate to outgroup attitudes independently). We again added the
-participant means back into the model. Because these are the means of
-the contact dummy variables they are the proportion of measurements that
-included a particular contact. This not only adjusts the model for
-unequal cell sizes but allows us to see whether between subject
-differences in the relative number of interactions had an effect on
-outgroup attitudes. We find that in this data set participant-level
-outgroup contact proportions were also a positive predictor of outgroup
-attitudes (\textit{b} = 26.55, \textit{t}(110) = 2.90, \textit{p} =
-0.004, \textit{95\%CI}{[}8.61, 44.46{]}). The relative number of
-non-outgroup interactions showed no such effect (for full results see
-\tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
-as well as Online Supplementary Material A). Thus, in our second data
-set we find that outgroup contacts show a positive effect on outgroup
-attitudes in the moment and on average between participants.
+We tested the most general contact hypothesis as we did for Study 1. We
+find that having an outgroup interaction is indeed associated with
+significantly more positive outgroup attitudes within the participants
+(random slopes model; \textit{b} = 2.83, \textit{t}(4,850) = 3.57,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}1.28, 4.38{]}), even
+after controlling for having an interaction with a non-Dutch person
+(which did not relate to outgroup attitudes independently). We again
+added the participant means back into the model. We find that in this
+data set participant-level outgroup contact proportions were also a
+positive predictor of outgroup attitudes (\textit{b} = 26.55,
+\textit{t}(110) = 2.90, \textit{p} = 0.004, \textit{95\%CI}{[}8.61,
+44.46{]}). The relative number of non-outgroup interactions showed no
+such effect (for full results see \tblref{tab:intergroupGeneralTblLong},
+\fgrref{fig:ContactHypothesis}, as well as Online Supplementary Material
+A). Thus, in our second data set we also find that outgroup contacts
+show a positive effect on outgroup attitudes in the moment. We
+additionally also find an average between participant effect of the
+relative number of interactions participants had.
 
@@
 8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020.
-
-The full surveys are available in our OSF repository
-\citep{KreienkampMasked2022a} and the full data description is available
-in Online Supplementary Material A. Correlations and descriptive
-statistics of the included variables are available in
-\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+Correlations and descriptive statistics of the included variables are
+available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
 
@@
 Attitudes towards the Dutch majority outgroup was again measured using
-the feeling thermometer, as in studies one and two. All survey details
-are also available in our OSF repository \citep{KreienkampMasked2022a}
-and Online Supplemental Materials A.
+the feeling thermometer, as in studies one and two.
 
@@
 
-Additionally, in a multilevel regression to check for contemporaneous
-within person effects, we found that having an outgroup interaction was
-indeed associated with significantly more positive outgroup attitudes
-within the participants (random slopes model; \textit{b} = 5.57,
-\textit{t}(3,834) = 6.52, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}3.90, 7.23{]}), even after controlling for having an
-interaction with a non-Dutch (which did not relate to outgroup attitudes
-independently; for full results see
+In the multilevel regression, we find that having an outgroup
+interaction was again associated with significantly more positive
+outgroup attitudes within the participants (random slopes model;
+\textit{b} = 5.57, \textit{t}(3,834) = 6.52, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}3.90, 7.23{]}), even after controlling for
+having an interaction with a non-Dutch (which did not relate to outgroup
+attitudes independently; for full results see
 \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
 and Online Supplementary Material A). Thus, in our third data set we
-found within person contemporaneous effect of intergroup contact was
-consistent across all three studies.
+find that the within-person contemporaneous effect of intergroup contact
+was consistent across all three studies.
 
@@
 
-Similarly to the previous studies, we again sequentially tested whether
-the fulfillment of the core need during an interaction was (1) related
-to more positive outgroup attitudes, (2) higher perceived interaction
-quality, and (3) whether the variance explained by the core need is
-assumed by the perceived interaction quality if considered jointly. We
-find that the fulfillment of the core need during outgroup contacts was
-associated with more positive outgroup attitudes (random slopes model;
-\textit{b} = 0.19, \textit{t}(1,601) = 5.29, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}0.12, 0.27{]}) and also predicted higher
-perceived interaction quality (random slopes model; \textit{b} = 0.43,
-\textit{t}(1,605) = 8.35, \textit{p} \textless{} .001,
+Analogous to the previous studies, we again sequentially tested whether
+the fulfillment of the core need during an outgroup interaction was (1)
+related to more positive outgroup attitudes, (2) higher perceived
+interaction quality, and (3) whether the variance explained by the core
+need is assumed by the perceived interaction quality if considered
+jointly. We find that the fulfillment of the core need during outgroup
+contacts was associated with more positive outgroup attitudes (random
+slopes model; \textit{b} = 0.19, \textit{t}(1,601) = 5.29, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.12, 0.27{]}) and also predicted
+higher perceived interaction quality (random slopes model; \textit{b} =
+0.43, \textit{t}(1,605) = 8.35, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.33, 0.54{]}). Additionally, once we consider the
@@
 \tblref{tab:intergroupNeedsTblLong} and
-\fgrref{fig:AllportNeedFulfillment}). These results indicate that in
-this data set outgroup attitudes were significantly predicted by the
-fulfillment of core situational needs and this effect partially emerged
-via its effect on perceived interaction quality.
+\fgrref{fig:AllportNeedFulfillment}). As with the previous two studies,
+these results indicate that in this data set outgroup attitudes were
+significantly predicted by the fulfillment of core situational needs and
+the results suggest that this might be due to higher perceived
+interaction quality.
 
@@
 
-To test wether Allport's conditions or the core need fulfillment are
+To test whether Allport's conditions or the core need fulfillment are
 better at predicting outgroup attitudes, we first assess relative model
@@
 efforts here, forest plots are commonly accompanied with a meta-analytic
-effect size that summarizes the effect size across studies.
-
-We assess forest plots of the basic contact hypothesis test
-(\fgrref{fig:ContactHypothesis}), as well as the core need fulfillment
-proposal (\fgrref{fig:AllportNeedFulfillment}). For the basic contact
-hypothesis test we see that outgroup contact has a strong and consistent
-effect on outgroup attitudes while interactions with non-outgroup
-members consistently have no meaningful effect on outgroup attitudes.
-While this would be expected from the general intergroup contact
-literature, this is not a trivial finding. We are among the first to
-assess the contact hypothesis using real-life intensive longitudinal
-data and these close to event assessments are comparable but not
-equivalent to the assessments found in cross-sectional data. When
-looking at the fulfillment of core needs during intergroup contacts, we
-find that the motivational mechanism is consistently a meaningful
-predictor of outgroup attitudes and interaction quality perceptions (see
-\fgrref{fig:AllportNeedFulfillment} A and B). We also see that the
+effect size that summarizes the effect size across studies. For the
+basic contact hypothesis test we see that outgroup contact has a strong
+and consistent effect on outgroup attitudes while interactions with
+non-outgroup members consistently have no meaningful effect on outgroup
+attitudes (\fgrref{fig:ContactHypothesis}). While this would be expected
+from the general intergroup contact literature, this is not a trivial
+finding. We are among the first to assess the contact hypothesis using
+real-life intensive longitudinal data and these close to event
+assessments are comparable but not equivalent to the assessments found
+in cross-sectional data. When looking at the fulfillment of core needs
+during intergroup contacts, we find that the motivational mechanism is
+consistently a meaningful predictor of outgroup attitudes and
+interaction quality perceptions (see
+\fgrref[ A and B]{fig:AllportNeedFulfillment}). We also see that the
 effect of core need fulfillment on outgroup attitudes is strongly
@@
 not brought the two elements of the contact hypothesis together in a
-single analysis. This is mainly due to the difficulty that interaction
-quality ratings are only possible when participants had an interaction
---- which means that the two factors cannot be assessed in a multilevel
-analysis that models individual measurement occasions. This has not been
-an issue in the past literature because experimental and cross-sectional
-data collections have only considered cases in which intergroup contacts
-were present. Outside of the lab, the most common method has been to ask
-participants to recall how many interactions they had over the past
-month, how positive these interactions were, and how positive they feel
-towards the outgroup in general. The effects of intergroup contacts,
-interaction quality, and outgroup attitudes are thus summarized by the
-participant in a cognitive recall aggregation. Intensive longitudinal
-data also allows for aggregation of all three variables, with the
-differences that the measurements are aggregated from individual reports
-that are close to the actual experience. However, this aggregation
-process summarizes the dense multitude of measurement occasions as
-single summary statistics per participants. This, by extension, means
-that we face statistical power restrictions on the person level and have
-thus decided to only present this analysis based on a combined data set
-of all three studies.
-
-We run a linear regression model where average outgroup attitudes are
-predicted by the number of interactions and the average interaction
-quality ratings of all participants across the three studies. We do so
-while controlling for the possible effects of study-specific
-differences. To include the study-membership as a control variable, we
-use the student sample (Study 2) as the reference group because it is
-both the largest and the most homogeneous study. Looking at the overall
-model, we find that the model predicts a statistically significant
-amount of variance in average outgroup attitudes (\textit{F}(9, 189) =
-3.39, \textit{p} = 0.001, \textit{R\textsuperscript{2}} = 0.14). Looking
-at the individual effects, we find that only the number of outgroup
-interactions has a clear association with average outgroup attitudes
-(\textit{b} = 0.55, \textit{t}(189) = 2.82, \textit{p} = 0.005,
-\textit{95\%CI}{[}0.16, 0.93{]}). The average interaction quality
-perceptions had a much smaller effect (\textit{b} = 0.29,
-\textit{t}(189) = 2.09, \textit{p} = 0.038, \textit{95\%CI}{[}0.02,
-0.56{]}), and we do not find the most important interaction effect at
-all. In short, the effect of outgroup interactions did not depend on the
-average interaction quality, so that participants who on average had
-more positive interactions were not statistically more likely to show
-higher average outgroup attitudes than those with more negative
-interactions. This result is surprising because it contradicts the tenet
-of the intergroup contact hypothesis that intergroup contact depends on
-positive contact.
+single analysis. To jointly test the effects of contact frequency and
+average interaction quality, we run a linear regression model where
+average outgroup attitudes are predicted by the number of interactions
+and the average interaction quality ratings of all participants across
+the three studies. We do so while controlling for the possible effects
+of study-specific differences. To include the study-membership as a
+control variable, we use the student sample (Study 2) as the reference
+group because it is both the largest and the most homogeneous study.
+Looking at the overall model, we find that the model predicts a
+statistically significant amount of variance in average outgroup
+attitudes (\textit{F}(9, 189) = 3.39, \textit{p} = 0.001,
+\textit{R\textsuperscript{2}} = 0.14). Looking at the individual
+effects, we find that only the number of outgroup interactions has a
+clear association with average outgroup attitudes (\textit{b} = 0.55,
+\textit{t}(189) = 2.82, \textit{p} = 0.005, \textit{95\%CI}{[}0.16,
+0.93{]}). The average interaction quality perceptions had a much smaller
+effect (\textit{b} = 0.29, \textit{t}(189) = 2.09, \textit{p} = 0.038,
+\textit{95\%CI}{[}0.02, 0.56{]}), and we do not find the most important
+interaction effect at all. In short, the effect of interaction frequency
+did not depend on the average interaction quality.
 
@@
 socializing and celebrations were also explicit social needs (incl.,
-parties). Another set of topics was more practically oriented, when
-participants sought to share food and cook cook together, or had
-organizational needs (e.g., housing, cleaning, and living).
-
-A reasonable set of contact goals were specifically migration-specific
-(e.g., wish to learn about culture, politics, and language) or were
-concerned inquiry and information needs more generally (e.g., seeking
-answers, bureaucratic information). A further set of topics was
-specifically geared towards a wish to experience cultural products
-(e.g., music, theater, food) or had travel related goals in their
-interactions with the majority group members.
+parties). This also included a subtopic of social spiritual, religious,
+and otherwise transcendental needs (incl.~meditation, prayer, religious
+services). Among the leisure-oriented topics was also a set of contact
+goals that were specifically migration-specific (e.g., wish to learn
+about culture, politics, and language) or were concerned inquiry and
+information needs more generally (e.g., seeking answers, bureaucratic
+information). A similar set of topics was specifically geared towards a
+wish to experience cultural products (e.g., music, theater, food) or had
+travel related goals in their interactions with the majority group
+members.
 
@@
 (e.g., sports and music) were common goals that participants shared
-during the interactions with the majority group members. A final topic
-was that of spiritual, religious, and otherwise transcendental needs
-(incl.~meditation, prayer, religious services).
-
-Thus, almost all extracted topics fall into broader or narrower need
-concepts that are commonly discussed within the psychological needs
-literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core
-aspect of the migration experience that has remained broadly
-under-explored \citep[][]{Kreienkamp2022d}.
+during the interactions with the majority group members. Another topic
+less commonly found within the literature were more practically oriented
+needs, where participants sought to share food and cook together, or had
+organizational needs (e.g., housing, cleaning, and co-living). In sum,
+almost all extracted topics fall into broader or narrower need concepts
+that are commonly discussed within the psychological needs literature
+\citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the
+migration experience that has remained broadly under-explored
+\citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyper parameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
+The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.

### 2022-11-11 manuscript.tex
MA + KE intro feedback

@@
 \abstract{
-\hl{needs to be adjusted}\\
 One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations.
@@
 We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total N of measurements = 10,297).
-\hl{We find inconsistent results for a traditional test of the contact hypothesis with experience sampling data.
-However, when using multilevel models to test the contact hypothesis, we find that individual outgroup interactions and perceived interaction quality have a strong influence on positive outgroup attitudes.}
-The fulfillment of psychological needs is consistently a strong predictor of positive attitudes during intergroup interactions and these positive effects emerged via perceived interaction quality.
-The situational needs remained the core predictor of outgroup attitudes even after controlling for Allport’s (\citeyear{Allport1954b}) contact conditions or more general self-determination needs \citep[][]{Ryan2017}.
+The novel psychological needs mechanism is consistently a strong predictor of positive attitudes during intergroup interactions and these positive effects emerged via perceived interaction quality.
+The situational needs model is robust to alternative models and outperforms Allport's contact conditions.
 As one of the first studies to test intergroup contact theory using extensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
@@
 Methodologically, this offers testament to the emerging practice of capturing real-life interactions using extensive longitudinal data.
-Theoretically, our results give weight to motivational fulfillment as a flexible and effective mechanism in understanding positive intergroup contact.
+Theoretically, our results give weight to motivational fulfillment as a flexible and effective mechanism for understanding positive intergroup contact.
 }
@@
 There is now consistent evidence that negative intergroup contacts lead to worse attitudes, prejudice, and reduced future interaction motivation \citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.
-In light of these findings, understanding interaction quality thus sits at the heart of understanding when an intergroup contact is successful (e.g., Brown et al.
-\citeyear{Brown2007}, Tropp et al.
-\citeyear{Tropp2016}; also cf.
-Allport’s original sentiment, Allport \citeyear{Allport1954b}).
+In light of these findings, understanding interaction quality thus sits at the heart of understanding when an intergroup contact is successful \citep[e.g.,][]{Allport1954b, Brown2007, Tropp2016}.
 Practically, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in everyday life contexts.
@@
 Such empirical practices stand, however, in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the core idea of the contact hypothesis, which was focused on the daily interactions of people \citep[][]{Allport1954b}.
-As a result, within the intergroup contact field researchers have called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017, Dixon2005}.
+As a result, within the intergroup contact field researchers have called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017, Dixon2005}.
 Such data would be able to capture real-life interactions that include interaction-specific mechanism information close to the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
@@
 
-Before we turn to the individual studies, we would like to discuss two methodological matters.
-Firstly, we opted to test most of our hypotheses using multilevel regression models, where the measurement occasions (level 1) were nested within the participants (level 2).
-Such an approach is also tolerant to missing data and uneven case numbers within participants.
-As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text \citep[][; for the full modeling process see Supplementary Material A]{Bliese2013}.
-Secondly, statistical power is notoriously difficult to estimate for intensive longitudinal- and multilevel models because of the complex covariance structures.
-However, for all studies both the number of participants and the number of measurements are within the highest percentiles of sample sizes found within the broader intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
-Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes for the contemporaneous effects we assess here.
+Before turning to individual studies, two methodological matters need consideration.
+Firstly, we tested most of our hypotheses using multilevel regression models, where measurement occasions (level 1) were nested within participants (level 2).
+This approach is tolerant to missing data and uneven case numbers within participants.
+Furthermore, we use a hierarchical modeling approach and report the final model in-text \citep[][; for the full modeling process see Supplementary Material A]{Bliese2013}.
+Secondly, statistical power estimations for intensive longitudinal- and multilevel models are notoriously difficult due to the complex covariance structures.
+However, our sample sizes and measurement numbers are within the highest percentiles of sample sizes found within the broader intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
+Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes.
 The sample sizes were only increased to allow for between-subjects comparisons and future, more complicated, time-series modeling.
@@
 % aims re-iterated
-The aim of this project was threefold.
-We (1) tested the basic predictions of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data.
-As a flexible alternative, we (2) proposed that the fulfillment of situational psychological needs meaningfully predicts positive outgroup attitudes.
-Finally, we (3) assessed whether the fulfillment of psychological needs have their effect (partially) through perceived interaction quality.
+The main aim of this project was to test the basic tenets of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data and to test whether the fulfillment of situational psychological needs meaningfully predicts positive interaction perceptions and outgroup attitudes.
 
@@
 When considering the results of the three studies jointly, we found mixed results for the basic intergroup contact hypothesis.
-More specifically, we observe that separating between-participant and within-participant effects is crucial.
-For between-subjects effects (using aggregated reports), the positive effect of more outgroup contact did not depend on the average interaction quality.
-These aggregate findings are surprising because most past cross-sectional studies have also considered an aggregate measurement of interaction quality (albeit not one from actual daily reports).
-The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).\footnote{It should be noted that such inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
-However, the models we employed should in principle be resistant to such imbalances.} In support of this possibility, once we used multilevel modeling to separate effects into a between-subjects and within-subjects part, we found that when having an interaction with an outgroup member (vs.
-not having an outgroup interaction) is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account; also see \fgrref[B]{fig:ContactHypothesis}).
-We thus find that the main benefits of intergroup contact remain visible across the three studies.
-However, the intensive longitudinal data of natural intergroup contacts also offers a novel opportunity to explore how people recall and cognitively aggregate outgroup interactions.
-Future studies may want to ask participants explicitly to evaluate the number and quality of outgroup interactions following a phase of intensive longitudinal data collection to disentangle the aggregation differences.
+To replicate the two common approaches to the contact hypothesis, we look at both the within-person effects of individual outgroup interactions (mimicking the analysis of lab studies) as well as the joint effect of interaction frequency and average interaction quality between participants (mimicking the cross-section literature).
+For the effect of individual interactions, we find that having an outgroup interaction (vs.
+not having an interaction) is associated with more favorable outgroup attitudes.
+Similarly, we find that within outgroup interactions, the interaction quality is meaningfully associated with more favorable outgroup attitudes.
+Yet, considering interaction frequency and average interaction quality jointly is only possible on the aggregated between-participant level.
+And surprisingly, here found independent effects of interaction frequency and average interaction quality ratings but no interaction effect.
+The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations)\footnote{It should be noted that such inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction)}.
 
@@
 % Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal datasets, that the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
-We find that in all three studies the effect of core need fulfillment on outgroup attitudes goes either fully or partially through interaction quality.
+Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal datasets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
+We find that in all three studies the effect of core need fulfillment on outgroup attitudes could either fully or partially be explained by its effect on interaction quality.
 We also find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
-In fact, our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
+In fact, our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs (see \appref{app:AppendixRobustness}).
 In most cases, the core need even took over the variances previously explained by the self-determination theory needs.
@@
 % (1) Sample = minority and (voluntary) migrants, (2) Methodology = short scales (reliability) and no lagged effects, (3) Core Need Concept = non-specific
-One limitation is our choice of samples.
 While we believe that a need-based mechanism should be relevant to any inter-group contact, our sample has focused on a minority- and (voluntary) migrant perspective.
@@
                                     &\ \beta_{3}ContactFrequency_{i} * AverageQuality_{i}
-            \end{split}
-        \end{equation}
-      \end{fleqn}
-
-    \hl{More complete but in my opinion more confusing connotation:}
-
-      \begin{fleqn}[\eqskip] 
-        \begin{equation}
-            \begin{split}
-              \overline{Attitude}_{i} = &\ \beta_{0} + \beta_{1}\left(\sum\nolimits_{t=1}^{T}OutgroupInteraction\right)_{i} + \\
-                                        &\ \beta_{2}\overline{InteractionQuality}_{i} +\\
-                                        &\ \beta_{3}\left(\sum\nolimits_{t=1}^{T}OutgroupInteraction\right)_{i} * \overline{InteractionQuality}_{i}
             \end{split}

### 2022-11-11 Methods-and-Results.Rmd
feedback MA

@@
 Based on our main hypotheses, the aim of our first study was to specifically test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
-To this aim, we conducted an intensive longitudinal survey study with recent migrants to the Netherlands.
+To this aim, we recruited recent migrants to the Netherlands for an intensive longitudinal survey.
 Data was collected from May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all participants started the study within the first two days).
@@
 
-\subsubsection{Participants} After receiving ethical approval from the University Masked for Peer Review, we recruited `r nrow(workerSampleInfo)` migrants using the local paid participant pool and specifically targeted non-Dutch migrants to participate in our study.
+\subsubsection{Participants} After receiving ethical approval from the University Masked for Peer Review, we recruited `r nrow(workerSampleInfo)` non-Dutch migrants using the local paid participant pool.
 Participants reported on their interactions for at least 30 days with two daily measures (capturing the morning and afternoon).
@@
 This is a common number of measurements found in experience sampling studies and offers sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
-Participants were compensated for their participation with up to 34 Euros – each two Euros for pre- and post-questionnaire as well as 50 Eurocents for every experience sampling measurement occasion.
+Participants were compensated for their participation with up to 34 Euros – each two Euros for pre- and post-questionnaire and 50 Eurocents for every experience sampling measurement.
 The sample consisted of relatively young, educated, and western migrants from the global north ($M_{age}$ = `r format(round(mean(workerSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(workerSampleInfo$age),2), nsmall=2)`, `r nrow(workerSampleInfo %>% filter(gender == "Female"))` women, `r nrow(workerSampleInfo %>% filter(occupation == "student"))` students).
@@
 
-\subsubsection{Procedure} The study itself consisted of three main parts, an introductory pre-measurement, and the daily experience sampling measurements, as well as a concluding post-measurement.
-After giving informed consent, participants started by filling in an online pre-questionnaire assessing demographics and general information about their immigration.
-Over the next thirty days, the participants were then invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median survey duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_))) %>% as.character`).
+\subsubsection{Procedure} The study itself consisted of three main parts, an introductory pre-measurement, the daily experience sampling measurements, and a concluding post-measurement.
+After giving informed consent, participants filled in an online pre-questionnaire assessing demographics and general information about their immigration.
+Over the next thirty days, participants were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median survey duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_))) %>% as.character`).
 General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%).}.
@@
 We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
-Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by use centered predictors and reintroducing the means as level two predictors (\citealp{Yaremych2021}; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by using centered predictors and reintroducing the means as level two predictors (\citealp{Yaremych2021}; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
 This is unusual and might indicate that the effect is very consistent across participants.
@@
 Data was collected from November 19\textsuperscript{th}, 2018 through January 6\textsuperscript{th}, 2019.
-Correlations and descriptive statistics of the included variables are again available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
 
@@
 Thus, in our second data set we also find that outgroup contacts show a positive effect on outgroup attitudes in the moment.
-We additionally also find an average between participant effect of the relative number of interactions participants had.
+We additionally find an average between participant effect of the relative number of interactions participants had.
 
@@
 Data were collected from November 8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020.
+The full preregistration is available at \citet[][]{KreienkampMasked2021f}.
 Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
@@
 With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(medicalSampleInfo$dailiesN), big.mark=",")`).
-As with the previous studies, this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
-Participants were compensated for their participation in the same manner as during Study 1.
+As with the previous studies, this offered sufficient power to model processes within participants and will lend stronger weight to between-participant results.
+Participants were compensated in the same manner as during Study 1.
 The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(medicalSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(medicalSampleInfo$age),2), nsmall=2)`, `r nrow(medicalSampleInfo %>% filter(gender == "women"))` women).
@@
 In the multilevel models we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
-Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
+Moreover, when we considered the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we found that perceived interaction quality was a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
 These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.
-
-<!-- \faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?  -->
 
@@
 
-To test whether Allport's conditions or the core need fulfillment are better at predicting outgroup attitudes, we first assess relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predict the same variance in outgroup attitudes.
-When comparing the model selection indices, we find that the fulfillment of the situational core need indeed performs slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
+To test whether Allport's conditions or the core need fulfillment were better at predicting outgroup attitudes, we first assessed relative model performance indices (i.e., Akaike information criterion, and Bayesian information criterion), and then consider the two predictors in a joint model to see whether the two approaches predicted the same variance in outgroup attitudes.
+When comparing the model selection indices, we found that the fulfillment of the situational core need indeed performed slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
 Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
@@
 Beyond the individual results of the three studies, we conducted three additional analyses to test the broader cross-study claims and contextualize our results.
-In particular, we aim to gain a broader picture of the individual results by considering them jointly, and we leverage the data from all participants to test between-participant contact effects and explore the content of the participants' situational contact needs.
+In particular, we aimed to gain a broader picture of the individual results by considering them jointly.
+We also leveraged the data from all participants to test between-participant contact effects and explore the content of the participants' situational contact needs.
 
 \subsection{Stability}
-We begin by assessing the stability of our main analyses across the three studies.
-To do so, we plot the effect sizes of each parameter of interest in a forest plot.
-This affords us a chance to spot stable as well as unreliable effects more easily.
-While not the focus of our efforts here, forest plots are commonly accompanied with a meta-analytic effect size that summarizes the effect size across studies.
-For the basic contact hypothesis test we see that outgroup contact has a strong and consistent effect on outgroup attitudes while interactions with non-outgroup members consistently have no meaningful effect on outgroup attitudes (\fgrref{fig:ContactHypothesis}).
+We first assessed the stability of our main analyses across the three studies.
+Plotting the effect sizes of each parameter of interest in a forest plot, as well as the average meta-analytic effect, shows that for the basic contact hypothesis test outgroup contact had a strong and consistent effect on outgroup attitudes.
+Interactions with non-outgroup members consistently had no meaningful effect on outgroup attitudes (\fgrref{fig:ContactHypothesis}).
 While this would be expected from the general intergroup contact literature, this is not a trivial finding.
-We are among the first to assess the contact hypothesis using real-life intensive longitudinal data and these close to event assessments are comparable but not equivalent to the assessments found in cross-sectional data.
+Being among the first to assess the contact hypothesis using real-life intensive longitudinal data, we extend cross-sectional findings to individual-level assessments.
 When looking at the fulfillment of core needs during intergroup contacts, we find that the motivational mechanism is consistently a meaningful predictor of outgroup attitudes and interaction quality perceptions (see \fgrref[ A and B]{fig:AllportNeedFulfillment}).
@@
 We have, however, not brought the two elements of the contact hypothesis together in a single analysis.
-To jointly test the effects of contact frequency and average interaction quality, we run a linear regression model where average outgroup attitudes are predicted by the number of interactions and the average interaction quality ratings of all participants across the three studies.
-We do so while controlling for the possible effects of study-specific differences.
-To include the study-membership as a control variable, we use the student sample (Study 2) as the reference group because it is both the largest and the most homogeneous study.
-Looking at the overall model, we find that the model predicts a statistically significant amount of variance in average outgroup attitudes (`r lmAllFstatLatex`).
-Looking at the individual effects, we find that only the number of outgroup interactions has a clear association with average outgroup attitudes (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "SumContactNL_c", ci = TRUE)`).
-The average interaction quality perceptions had a much smaller effect (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "AvQualityOut_c", ci = TRUE)`), and we do not find the most important interaction effect at all.
+To jointly test the effects of contact frequency and average interaction quality, we ran a linear regression model where average outgroup attitudes were predicted by the number of interactions and the average interaction quality ratings of all participants across the three studies.
+We did so while controlling for the possible effects of study-specific differences.
+To include the study-membership as a control variable, we used the student sample (Study 2) as the reference group because it was both the largest and the most homogeneous study.
+Looking at the overall model, we found that the model predicted `r format(round(fit$r.squared*100, 2), nsmall = 2)`\% of the variance in average outgroup attitudes (`r lmAllFstatLatex`).
+Looking at the individual effects, we found that only the number of outgroup interactions has a clear association with average outgroup attitudes (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "SumContactNL_c", ci = TRUE)`).
+The average interaction quality perceptions had a much smaller effect (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "AvQualityOut_c", ci = TRUE)`), and importantly we found no interaction effect at all.
 In short, the effect of interaction frequency did not depend on the average interaction quality.
@@
 \subsection{Contact key need content}
-Finally, we use the qualitative data from the participants’ self-identified core needs to contextualize the results of our main analysis.
-However, because our participants jointly reported on thousands of intergroup contacts, it would not be feasible to analyse these qualitative responses in a traditional qualitative content analysis.
-We instead rely on recent machine learning advances within the natural language processing domain.
-For our analysis we use the BERT language model.
+Finally, we used the qualitative data from the participants’ self-identified core needs to contextualize the results of our main analysis.
+However, because our participants jointly reported on thousands of intergroup contacts, it would not have been feasible to analyse these qualitative responses in a traditional qualitative content analysis.
+We instead relied on recent machine learning advances within the natural language processing domain.
+For our analysis we used the BERT language model.
 BERT (Bidirectional Encoder Representations from Transformers) was developed by Google in 2018 and today forms a key elements of many natural language processing workflows.
@@
 We extracted 47 topics from the 2,983 interaction goal free-text entries --- a relatively large number of topics.
-The higher number of topics allows us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (10.33%).
-A full write up of the topic modeling process is available in Online Supplemental Material C.
+The higher number of topics allowed us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (10.33%).
+A full write up of the topic modeling process is available in Online Supplemental Material B.
 
 In terms of the content of the topics, we find that a number of topics are primarily task-oriented, where participants hope to increase their study, research, presentation, or work performance.
-Opposing the task and work oriented needs, are a wide variety of leisure-related wishes.
+Opposing the task and work oriented needs, are a wide variety of leisure-related needs.
 Specifically, relaxation and entertainment wishes were prominent terms across several topics.
-Additionally, a number of clusters is primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself.
+Additionally, a number of clusters were primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself.
 Similarly, socializing and celebrations were also explicit social needs (incl., parties).

### 2022-11-11 Methods-and-Results.tex
feedback MA

@@
 need fulfillment, and perceived interaction quality during intergroup
-contacts. To this aim, we conducted an intensive longitudinal survey
-study with recent migrants to the Netherlands. Data was collected from
-May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and
-all participants started the study within the first two days).
-Correlations and descriptive statistics of the included variables are
-available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}
-(full data description is available in Online Supplementary Material A).
+contacts. To this aim, we recruited recent migrants to the Netherlands
+for an intensive longitudinal survey. Data was collected from May
+5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all
+participants started the study within the first two days). Correlations
+and descriptive statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide} (full data
+description is available in Online Supplementary Material A).
 
@@
 After receiving ethical approval from the University Masked for Peer
-Review, we recruited 23 migrants using the local paid participant pool
-and specifically targeted non-Dutch migrants to participate in our
-study. Participants reported on their interactions for at least 30 days
-with two daily measures (capturing the morning and afternoon). With this
-design, we aimed at getting 50-60 measurements per participant
-(\textit{M} = 53.26, \textit{SD} = 16.72, \textit{total N} = 1,225).
-This is a common number of measurements found in experience sampling
-studies and offers sufficient power to model processes within and
-between participants
+Review, we recruited 23 non-Dutch migrants using the local paid
+participant pool. Participants reported on their interactions for at
+least 30 days with two daily measures (capturing the morning and
+afternoon). With this design, we aimed at getting 50-60 measurements per
+participant (\textit{M} = 53.26, \textit{SD} = 16.72, \textit{total N} =
+1,225). This is a common number of measurements found in experience
+sampling studies and offers sufficient power to model processes within
+and between participants
 \citep[e.g., for a systematic review see][]{AanhetRot2012}. Participants
 were compensated for their participation with up to 34 Euros -- each two
-Euros for pre- and post-questionnaire as well as 50 Eurocents for every
-experience sampling measurement occasion. The sample consisted of
-relatively young, educated, and western migrants from the global north
-(\(M_{age}\) = 24.35, \(SD_{age}\) = 4.73, 19 women, 15 students). The
-sample accurately describes the largest groups of migrants in the region
+Euros for pre- and post-questionnaire and 50 Eurocents for every
+experience sampling measurement. The sample consisted of relatively
+young, educated, and western migrants from the global north (\(M_{age}\)
+= 24.35, \(SD_{age}\) = 4.73, 19 women, 15 students). The sample
+accurately describes the largest groups of migrants in the region
 \citep[][]{GemeenteGroningen2015}.
@@
 The study itself consisted of three main parts, an introductory
-pre-measurement, and the daily experience sampling measurements, as well
-as a concluding post-measurement. After giving informed consent,
-participants started by filling in an online pre-questionnaire assessing
-demographics and general information about their immigration. Over the
-next thirty days, the participants were then invited twice a day (at 12
-pm and 7pm) to reflect upon their interactions, psychological need
-fulfillments, and current attitudes towards the Dutch outgroup
-(\textit{median survey duration} = 2M 22S, \textit{MAD duration} = 1M
-19S). General compliance was high (85.90\% of all invited surveys were
-filled
+pre-measurement, the daily experience sampling measurements, and a
+concluding post-measurement. After giving informed consent, participants
+filled in an online pre-questionnaire assessing demographics and general
+information about their immigration. Over the next thirty days,
+participants were invited twice a day (at 12 pm and 7pm) to reflect upon
+their interactions, psychological need fulfillments, and current
+attitudes towards the Dutch outgroup (\textit{median survey duration} =
+2M 22S, \textit{MAD duration} = 1M 19S). General compliance was high
+(85.90\% of all invited surveys were filled
 in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%).}.
@@
 are generally robust against unequal cell sizes, we correct for
-inequalities by use centered predictors and reintroducing the means as
+inequalities by using centered predictors and reintroducing the means as
 level two predictors (\citealp{Yaremych2021}; for full results see
@@
 2018 through January 6\textsuperscript{th}, 2019. Correlations and
-descriptive statistics of the included variables are again available in
+descriptive statistics of the included variables are available in
 \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
@@
 show a positive effect on outgroup attitudes in the moment. We
-additionally also find an average between participant effect of the
-relative number of interactions participants had.
+additionally find an average between participant effect of the relative
+number of interactions participants had.
 
@@
 contact situations. Data were collected from November
-8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020.
+8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020. The
+full preregistration is available at \citet[][]{KreienkampMasked2021f}.
 Correlations and descriptive statistics of the included variables are
@@
 \textit{SD} = 20.68, \textit{total N} = 4,107). As with the previous
-studies, this should offer sufficient power to model processes within
+studies, this offered sufficient power to model processes within
 participants and will lend stronger weight to between-participant
-results. Participants were compensated for their participation in the
-same manner as during Study 1. The sample consisted of relatively young
-migrants, who were mostly from the global north (\(M_{age}\) = 22.68,
-\(SD_{age}\) = 3.10, 59 women). The sample fairly accurately describes
-the local population of young international medical professionals.
+results. Participants were compensated in the same manner as during
+Study 1. The sample consisted of relatively young migrants, who were
+mostly from the global north (\(M_{age}\) = 22.68, \(SD_{age}\) = 3.10,
+59 women). The sample fairly accurately describes the local population
+of young international medical professionals.
 
@@
 \textit{t}(1,605) = 11.82, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we consider the
+\textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we considered the
 influences of Allport's Conditions and interaction quality on outgroup
-attitudes jointly, we find that perceived interaction quality is a
+attitudes jointly, we found that perceived interaction quality was a
 substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
@@
 
-To test whether Allport's conditions or the core need fulfillment are
-better at predicting outgroup attitudes, we first assess relative model
-performance indices (i.e., Akaike information criterion, and Bayesian
-information criterion), and then consider the two predictors in a joint
-model to see whether the two approaches predict the same variance in
-outgroup attitudes. When comparing the model selection indices, we find
-that the fulfillment of the situational core need indeed performs
-slightly better than the model using Allport's conditions
-(\(AIC_{CoreNeed}\) 12632.02 \textless{} 12651.59 \(AIC_{Allport}\), and
-\(BIC_{CoreNeed}\) 12664.55 \textless{} 12684.12 \(BIC_{Allport}\)).
-Additionally, when considering the predictors jointly, we find that both
-significantly predict outgroup attitudes with similar sized regression
-parameters (random slopes model; Allport's Conditions: \textit{b} =
-0.16, \textit{t}(1,600) = 4.92, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.09, 0.24{]}, Core Need: \textit{b} = 0.14,
-\textit{t}(1,600) = 3.85, \textit{p} \textless{} .001,
+To test whether Allport's conditions or the core need fulfillment were
+better at predicting outgroup attitudes, we first assessed relative
+model performance indices (i.e., Akaike information criterion, and
+Bayesian information criterion), and then consider the two predictors in
+a joint model to see whether the two approaches predicted the same
+variance in outgroup attitudes. When comparing the model selection
+indices, we found that the fulfillment of the situational core need
+indeed performed slightly better than the model using Allport's
+conditions (\(AIC_{CoreNeed}\) 12632.02 \textless{} 12651.59
+\(AIC_{Allport}\), and \(BIC_{CoreNeed}\) 12664.55 \textless{} 12684.12
+\(BIC_{Allport}\)). Additionally, when considering the predictors
+jointly, we find that both significantly predict outgroup attitudes with
+similar sized regression parameters (random slopes model; Allport's
+Conditions: \textit{b} = 0.16, \textit{t}(1,600) = 4.92, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.09, 0.24{]}, Core Need: \textit{b}
+= 0.14, \textit{t}(1,600) = 3.85, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.08, 0.17{]}; also see
@@
 additional analyses to test the broader cross-study claims and
-contextualize our results. In particular, we aim to gain a broader
-picture of the individual results by considering them jointly, and we
-leverage the data from all participants to test between-participant
+contextualize our results. In particular, we aimed to gain a broader
+picture of the individual results by considering them jointly. We also
+leveraged the data from all participants to test between-participant
 contact effects and explore the content of the participants' situational
@@
 
-We begin by assessing the stability of our main analyses across the
-three studies. To do so, we plot the effect sizes of each parameter of
-interest in a forest plot. This affords us a chance to spot stable as
-well as unreliable effects more easily. While not the focus of our
-efforts here, forest plots are commonly accompanied with a meta-analytic
-effect size that summarizes the effect size across studies. For the
-basic contact hypothesis test we see that outgroup contact has a strong
-and consistent effect on outgroup attitudes while interactions with
-non-outgroup members consistently have no meaningful effect on outgroup
-attitudes (\fgrref{fig:ContactHypothesis}). While this would be expected
-from the general intergroup contact literature, this is not a trivial
-finding. We are among the first to assess the contact hypothesis using
-real-life intensive longitudinal data and these close to event
-assessments are comparable but not equivalent to the assessments found
-in cross-sectional data. When looking at the fulfillment of core needs
-during intergroup contacts, we find that the motivational mechanism is
-consistently a meaningful predictor of outgroup attitudes and
-interaction quality perceptions (see
+We first assessed the stability of our main analyses across the three
+studies. Plotting the effect sizes of each parameter of interest in a
+forest plot, as well as the average meta-analytic effect, shows that for
+the basic contact hypothesis test outgroup contact had a strong and
+consistent effect on outgroup attitudes. Interactions with non-outgroup
+members consistently had no meaningful effect on outgroup attitudes
+(\fgrref{fig:ContactHypothesis}). While this would be expected from the
+general intergroup contact literature, this is not a trivial finding.
+Being among the first to assess the contact hypothesis using real-life
+intensive longitudinal data, we extend cross-sectional findings to
+individual-level assessments. When looking at the fulfillment of core
+needs during intergroup contacts, we find that the motivational
+mechanism is consistently a meaningful predictor of outgroup attitudes
+and interaction quality perceptions (see
 \fgrref[ A and B]{fig:AllportNeedFulfillment}). We also see that the
@@
 single analysis. To jointly test the effects of contact frequency and
-average interaction quality, we run a linear regression model where
-average outgroup attitudes are predicted by the number of interactions
+average interaction quality, we ran a linear regression model where
+average outgroup attitudes were predicted by the number of interactions
 and the average interaction quality ratings of all participants across
-the three studies. We do so while controlling for the possible effects
+the three studies. We did so while controlling for the possible effects
 of study-specific differences. To include the study-membership as a
-control variable, we use the student sample (Study 2) as the reference
-group because it is both the largest and the most homogeneous study.
-Looking at the overall model, we find that the model predicts a
-statistically significant amount of variance in average outgroup
-attitudes (\textit{F}(9, 189) = 3.39, \textit{p} = 0.001,
-\textit{R\textsuperscript{2}} = 0.14). Looking at the individual
-effects, we find that only the number of outgroup interactions has a
-clear association with average outgroup attitudes (\textit{b} = 0.55,
-\textit{t}(189) = 2.82, \textit{p} = 0.005, \textit{95\%CI}{[}0.16,
-0.93{]}). The average interaction quality perceptions had a much smaller
-effect (\textit{b} = 0.29, \textit{t}(189) = 2.09, \textit{p} = 0.038,
-\textit{95\%CI}{[}0.02, 0.56{]}), and we do not find the most important
-interaction effect at all. In short, the effect of interaction frequency
-did not depend on the average interaction quality.
+control variable, we used the student sample (Study 2) as the reference
+group because it was both the largest and the most homogeneous study.
+Looking at the overall model, we found that the model predicted 13.89\%
+of the variance in average outgroup attitudes (\textit{F}(9, 189) =
+3.39, \textit{p} = 0.001, \textit{R\textsuperscript{2}} = 0.14). Looking
+at the individual effects, we found that only the number of outgroup
+interactions has a clear association with average outgroup attitudes
+(\textit{b} = 0.55, \textit{t}(189) = 2.82, \textit{p} = 0.005,
+\textit{95\%CI}{[}0.16, 0.93{]}). The average interaction quality
+perceptions had a much smaller effect (\textit{b} = 0.29,
+\textit{t}(189) = 2.09, \textit{p} = 0.038, \textit{95\%CI}{[}0.02,
+0.56{]}), and importantly we found no interaction effect at all. In
+short, the effect of interaction frequency did not depend on the average
+interaction quality.
 
@@
 
-Finally, we use the qualitative data from the participants'
+Finally, we used the qualitative data from the participants'
 self-identified core needs to contextualize the results of our main
 analysis. However, because our participants jointly reported on
-thousands of intergroup contacts, it would not be feasible to analyse
-these qualitative responses in a traditional qualitative content
-analysis. We instead rely on recent machine learning advances within the
-natural language processing domain. For our analysis we use the BERT
-language model. BERT (Bidirectional Encoder Representations from
+thousands of intergroup contacts, it would not have been feasible to
+analyse these qualitative responses in a traditional qualitative content
+analysis. We instead relied on recent machine learning advances within
+the natural language processing domain. For our analysis we used the
+BERT language model. BERT (Bidirectional Encoder Representations from
 Transformers) was developed by Google in 2018 and today forms a key
@@
 topics from the 2,983 interaction goal free-text entries --- a
-relatively large number of topics. The higher number of topics allows us
-to retain more of the smaller topics and leaves a relatively low number
-of 308 free-text entries unclassified (10.33\%). A full write up of the
-topic modeling process is available in Online Supplemental Material C.
+relatively large number of topics. The higher number of topics allowed
+us to retain more of the smaller topics and leaves a relatively low
+number of 308 free-text entries unclassified (10.33\%). A full write up
+of the topic modeling process is available in Online Supplemental
+Material B.
 
@@
 study, research, presentation, or work performance. Opposing the task
-and work oriented needs, are a wide variety of leisure-related wishes.
+and work oriented needs, are a wide variety of leisure-related needs.
 Specifically, relaxation and entertainment wishes were prominent terms
-across several topics. Additionally, a number of clusters is primarily
+across several topics. Additionally, a number of clusters were primarily
 relationship-oriented, so that participants sought contact with outgroup

### 2022-11-11 manuscript.tex
Updates from Overleaf

@@
 Such empirical practices stand, however, in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the core idea of the contact hypothesis, which was focused on the daily interactions of people \citep[][]{Allport1954b}.
-As a result, within the intergroup contact field researchers have called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017, Dixon2005}.
+As a result, within the intergroup contact field researchers have called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
 Such data would be able to capture real-life interactions that include interaction-specific mechanism information close to the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
@@
 
-\hl{OPTION 1:} We then seek to investigate intergroup contacts and perceived interaction quality jointly.
+% We then seek to investigate intergroup contacts and perceived interaction quality jointly.
 Notably, however, participants are only able to report their interaction quality perceptions if they had an interaction.
@@
 
-\hl{OPTION 2:} We then seek to test the full contact hypothesis by investigating intergroup contacts and perceived interaction quality jointly.
-To do so, we conduct a person-level linear regression using person-level aggregated data from all three studies.
+We then seek to test the full contact hypothesis by investigating intergroup contacts and perceived interaction quality jointly.
+To do so, we conduct a linear regression using person-level aggregated data from all three studies.
 In particular, we aggregate the number of outgroup interactions participants had, their average interaction quality perceptions, as well as their average outgroup attitudes.
@@
 We describe the extracted topics and themes and compare them to the need contents usually found and measured within the psychological literature.
-Full methodological details and visualizations are available in Supplemental Material C.
+Full methodological details and visualizations are available in Supplemental Material B.
 

### 2022-11-11 Methods-and-Results.Rmd
typo

@@
 
-\paragraph{Allport's Conditions}We measured how much each of the interactions fulfilled Allport's conditions of optimal contact using a common short scale comprised of four attributes \citep{Islam1993, Voci2003, AlRamiah2012a, Dixon2005}.
+\paragraph{Allport's Conditions}We measured how much each of the interactions fulfilled Allport's conditions of optimal contact using a common short scale comprised of four attributes \citep{Islam1993, Voci2003, AlRamiah2012a}.
 In particular, we asked participants to rate how much the interaction had equal status ("\textit{The interaction with [name interaction partner] was on equal footing (same status)}"), a common goal ("\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}"), support of authorities ("\textit{The interaction with [name interaction partner] was voluntary}"), and intergroup cooperation ("\textit{The interaction with [name interaction partner] was cooperative}").

### 2022-11-11 Methods-and-Results.tex
typo

@@
 conditions of optimal contact using a common short scale comprised of
-four attributes \citep{Islam1993, Voci2003, AlRamiah2012a, Dixon2005}.
-In particular, we asked participants to rate how much the interaction
-had equal status
+four attributes \citep{Islam1993, Voci2003, AlRamiah2012a}. In
+particular, we asked participants to rate how much the interaction had
+equal status
 (``\textit{The interaction with [name interaction partner] was on equal footing (same status)}''),

### 2022-11-11 manuscript.tex
MA feedback discussion

@@
 Yet, considering interaction frequency and average interaction quality jointly is only possible on the aggregated between-participant level.
-And surprisingly, here found independent effects of interaction frequency and average interaction quality ratings but no interaction effect.
+Surprisingly, here we found independent effects of interaction frequency and average interaction quality ratings but no interaction effect.
 The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations)\footnote{It should be noted that such inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction)}.
@@
 Using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
-And when we consider interaction quality and Allport's conditions jointly, we find further evidence that part of the benefits of Allport's conditions are due to the case that such interactions are also perceived as more positive.
+When we consider interaction quality and Allport's conditions jointly, we find that Allport's conditions also predicted whether such interactions were also perceived as more positive.
 We thus find first evidence that Allport's conditions of optimal contact are also relevant to the daily interactions recent migrants have in their interactions with majority group members.
@@
 We also find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
-In fact, our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs (see \appref{app:AppendixRobustness}).
-In most cases, the core need even took over the variances previously explained by the self-determination theory needs.
+In fact, our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
+In most cases, the core need even took over the variances previously explained by the self-determination theory needs (see \appref{app:AppendixRobustness}).
 We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction-specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
@@
 % (1) Sample = minority and (voluntary) migrants, (2) Methodology = short scales (reliability) and no lagged effects, (3) Core Need Concept = non-specific
-While we believe that a need-based mechanism should be relevant to any inter-group contact, our sample has focused on a minority- and (voluntary) migrant perspective.
-Without additional evidence it thus remains difficult to judge whether motivational effects will generalize to other migrant groups (e.g., forced migrants), other intergroup contexts (e.g., gender-, religious-, or sexual orientation groups), and to majority groups in their outgroup attitudes.
-We know of no research that for other contexts psychological needs would not be relevant (once existential needs are met) but future research may extend our findings to other contexts to build an even broader understanding of psychological needs in intergroup contacts.
+While we believe that a need-based mechanism should be relevant to any inter-group contact, our samples focused on a minority- and (voluntary) migrant perspective.
+Without additional evidence it thus remains difficult to judge whether motivational effects will generalize to other migrant groups (e.g., forced migrants), other intergroup contexts (e.g., gender-, religious-, or sexual orientation groups), or to majority groups and their outgroup attitudes.
+We know of no research suggesting that in other contexts psychological needs are irrelevant (once existential needs are met) but future research may extend our findings to build an even broader understanding of psychological needs in intergroup contacts.
 
@@
 
-And finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
+Finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
 This comes at the expense of specificity in the situational needs (i.e., we have not explored whether different types of needs have stronger effects on interaction quality and outgroup attitudes).
-With the adaptive measurement, we used such an investigation would be possible (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
+Such an investigation would be possible with the adaptive measurement we used (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
 Nonetheless, future research may explore which exact needs are most important in different intergroup contexts.
@@
 This stands in stark contrast of the many cognitive \citep[e.g.,][]{Pettigrew1998, Brown2005} and emotional aspects investigated within the field \citep[e.g.,][]{Stephan2008, Paolini2004}.
-However, if motivational mechanisms are indeed shown to be meaningful factors in intergroup contacts, future research may be able to integrate broader theoretical frameworks of intergroup contact (e.g., motivations guiding cognition and affect, which in turn drive behavior.
+Future research may, therefore, be able to integrate broader theoretical frameworks of intergroup contact (e.g., motivations guiding cognition and affect, which in turn drive behavior.
 cf., theory of reasoned goal pursuit; \citealp{Ajzen2019}.
@@
 We provide evidence that the fulfillment of situational psychological needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
-Our results point to motivation as an understudied aspect of intergroup contact that is important in understanding when and why an interaction is perceived as positive and will lead to more positive outgroup attitudes.
+Our results point to motivational needs as an understudied aspect of intergroup contact that is important in understanding when and why an interaction is perceived as positive and will lead to more positive outgroup attitudes.
 

### 2022-11-11 Methods-and-Results.Rmd
typo

@@
 In terms of the content of the topics, we find that a number of topics are primarily task-oriented, where participants hope to increase their study, research, presentation, or work performance.
-Opposing the task and work oriented needs, are a wide variety of leisure-related needs.
-Specifically, relaxation and entertainment wishes were prominent terms across several topics.
-Additionally, a number of clusters were primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself.
+Opposing the task and work oriented needs, are a wide variety of leisure-related needs wishes, like relaxation and entertainment.
+Additionally, some clusters were primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself.
 Similarly, socializing and celebrations were also explicit social needs (incl., parties).
-This also included a subtopic of social spiritual, religious, and otherwise transcendental needs (incl.
+This also included a subtopic of spiritual, religious, and otherwise transcendental needs (incl.
 meditation, prayer, religious services).
-Among the leisure-oriented topics was also a set of contact goals that were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned inquiry and information needs more generally (e.g., seeking answers, bureaucratic information).
+Among the leisure-oriented topics was also a set of contact goals that were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned informational needs more generally (e.g., seeking answers, bureaucratic information).
 A similar set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel related goals in their interactions with the majority group members.
@@
 One interesting observation was the importance of contact goals specific to contact through the medical and public health system.
-This goal type was partly specific to our young medical professionals sample (e.g., working with patients, treatment), but also more broadly interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals).
+This goal type was partly specific to the medical professionals (e.g., working with patients, treatment), but also more broadly interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals).
 Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members.

### 2022-11-11 Methods-and-Results.tex
typo

@@
 study, research, presentation, or work performance. Opposing the task
-and work oriented needs, are a wide variety of leisure-related needs.
-Specifically, relaxation and entertainment wishes were prominent terms
-across several topics. Additionally, a number of clusters were primarily
-relationship-oriented, so that participants sought contact with outgroup
-members for intimate and casual social contact in itself. Similarly,
-socializing and celebrations were also explicit social needs (incl.,
-parties). This also included a subtopic of social spiritual, religious,
-and otherwise transcendental needs (incl.~meditation, prayer, religious
-services). Among the leisure-oriented topics was also a set of contact
-goals that were specifically migration-specific (e.g., wish to learn
-about culture, politics, and language) or were concerned inquiry and
-information needs more generally (e.g., seeking answers, bureaucratic
-information). A similar set of topics was specifically geared towards a
-wish to experience cultural products (e.g., music, theater, food) or had
-travel related goals in their interactions with the majority group
-members.
+and work oriented needs, are a wide variety of leisure-related needs
+wishes, like relaxation and entertainment. Additionally, some clusters
+were primarily relationship-oriented, so that participants sought
+contact with outgroup members for intimate and casual social contact in
+itself. Similarly, socializing and celebrations were also explicit
+social needs (incl., parties). This also included a subtopic of
+spiritual, religious, and otherwise transcendental needs
+(incl.~meditation, prayer, religious services). Among the
+leisure-oriented topics was also a set of contact goals that were
+specifically migration-specific (e.g., wish to learn about culture,
+politics, and language) or were concerned informational needs more
+generally (e.g., seeking answers, bureaucratic information). A similar
+set of topics was specifically geared towards a wish to experience
+cultural products (e.g., music, theater, food) or had travel related
+goals in their interactions with the majority group members.
 
@@
 to contact through the medical and public health system. This goal type
-was partly specific to our young medical professionals sample (e.g.,
-working with patients, treatment), but also more broadly interactions of
-newcomers with the outgroup majority as patients themselves (e.g.,
-therapeutic goals). Also health, fitness, and personal improvement goals
-(e.g., sports and music) were common goals that participants shared
-during the interactions with the majority group members. Another topic
-less commonly found within the literature were more practically oriented
+was partly specific to the medical professionals (e.g., working with
+patients, treatment), but also more broadly interactions of newcomers
+with the outgroup majority as patients themselves (e.g., therapeutic
+goals). Also health, fitness, and personal improvement goals (e.g.,
+sports and music) were common goals that participants shared during the
+interactions with the majority group members. Another topic less
+commonly found within the literature were more practically oriented
 needs, where participants sought to share food and cook together, or had

### 2022-11-11 TitlePage.tex
shortened + bib fixes

@@
 \noindent\textit{Open Science Practices:}\\
-\noindent \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/registrationplus-color.png}} Preregistration+, 
-\href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
-\href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,
-\href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, 
-\href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements
+\noindent \href{https://doi.org/10.17605/OSF.IO/R5E8C}{\includegraphics[height=\badgeheight]{assets/open-badges-small/registrationplus-color.png}} Preregistration+, 
+\href{https://osf.io/pr9zs/?view_only=208a53a1f0ff48dda1c17357328fa578}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
+\href{https://osf.io/pr9zs/?view_only=208a53a1f0ff48dda1c17357328fa578}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,
+\href{https://osf.io/pr9zs/?view_only=208a53a1f0ff48dda1c17357328fa578}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, 
+\href{https://osf.io/pr9zs/?view_only=208a53a1f0ff48dda1c17357328fa578}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements
 

### 2022-11-11 manuscript.tex
shortened + bib fixes

@@
 We propose to consider situational psychological needs during everyday intergroup contact.
-We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total N of measurements = 10,297).
+We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297).
 The novel psychological needs mechanism is consistently a strong predictor of positive attitudes during intergroup interactions and these positive effects emerged via perceived interaction quality.
@@
     \textit{Open Science Practices:}
-    \noindent \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/registrationplus-color.png}} Preregistration+, 
-    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
-    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,\break
-    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, 
-    \href{https://osf.io}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements
+    \noindent \href{https://osf.io/r5e8c?view_only=bfaed2196d49420385ce5fa6506a7765}{\includegraphics[height=\badgeheight]{assets/open-badges-small/registrationplus-color.png}} Preregistration+, 
+    \href{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
+    \href{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,\break
+    \href{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, 
+    \href{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements
     }
@@
 see,][]{Paolini2021}.
-Among others, researchers have explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}.
+Among others, researchers have explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and knowledge about the other group \citep[][]{Pettigrew2008c}.
 However, all these advances share the underlying criticism that they are not geared towards understanding when and why an interaction is perceived as positive.}.
@@
 To avoid this predicament we propose to start by using adaptive and responsive survey designs that allow a tailored approach based on the participants' inputs \citep[e.g.,][]{Tourangeau2017}.
-In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., situation core need) and with reference to their own response the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment).
-Such an adaptive approach allows us to take this initial step and test whether situational psychological needs indeed generally predict perceived interaction quality and positive outgroup attitudes independent of need content.
+In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., situation core need) and with reference to their own response, the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment).
+Such an adaptive approach allows us to take the initial step of testing whether situational psychological needs indeed generally predict perceived interaction quality and positive outgroup attitudes independent of need content.
 
@@
 not having an interaction impacts outgroup attitudes, but we can also use the participant's 30-day contact reports to test whether participants with more positive interactions tend to have more positive outgroup attitudes.
-Testing both approaches of the contact hypothesis allows us to go beyond a replication of the basic theory but could disentangle individual- from aggregated contact effects and would allow for a direct comparison with both bodies of literature.
+Testing both approaches to the contact hypothesis allows us to go beyond a replication of the basic theory but could disentangle individual- from aggregated contact effects and would allow for a direct comparison with both bodies of literature.
 We will test the effect of individual interactions within each study using a multilevel model, but to avoid power limitations, we will test the collective effect of contact frequency and -quality after the individual studies, across all participants.
@@
 
-Our second aim is to test our main theoretical proposal that the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
+Our second main aim is to test our main theoretical proposal that the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
 As our main proposal is concerned with the mechanisms of successful intergroup contact, we again focus on outgroup interaction reports.
@@
 This approach is tolerant to missing data and uneven case numbers within participants.
-Furthermore, we use a hierarchical modeling approach and report the final model in-text \citep[][; for the full modeling process see Supplementary Material A]{Bliese2013}.
+Furthermore, we use a hierarchical modeling approach and report the final model in-text \citep[][; for the full modeling process see Supplementary Material A]{Snijders2012}.
 Secondly, statistical power estimations for intensive longitudinal- and multilevel models are notoriously difficult due to the complex covariance structures.
-However, our sample sizes and measurement numbers are within the highest percentiles of sample sizes found within the broader intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
+However, our participant- and measurement numbers are within the highest percentiles of sample sizes found within the broader intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
 Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes.
@@
 When considering the results of the three studies jointly, we found mixed results for the basic intergroup contact hypothesis.
-To replicate the two common approaches to the contact hypothesis, we look at both the within-person effects of individual outgroup interactions (mimicking the analysis of lab studies) as well as the joint effect of interaction frequency and average interaction quality between participants (mimicking the cross-section literature).
+To replicate the two common approaches to the contact hypothesis, we looked at both the within-person effects of individual outgroup interactions (mimicking the analysis of lab studies) as well as the joint effect of interaction frequency and average interaction quality between participants (mimicking the cross-section literature).
 For the effect of individual interactions, we find that having an outgroup interaction (vs.
-not having an interaction) is associated with more favorable outgroup attitudes.
-Similarly, we find that within outgroup interactions, the interaction quality is meaningfully associated with more favorable outgroup attitudes.
-Yet, considering interaction frequency and average interaction quality jointly is only possible on the aggregated between-participant level.
+not having an interaction) was associated with more favorable outgroup attitudes.
+Similarly, we find that within outgroup interactions, the interaction quality was meaningfully associated with more favorable outgroup attitudes.
+Yet, considering interaction frequency and average interaction quality jointly was only possible on the aggregated between-participant level.
 Surprisingly, here we found independent effects of interaction frequency and average interaction quality ratings but no interaction effect.
-The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations)\footnote{It should be noted that such inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction)}.
+The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations)\footnote{It should be noted that such inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).}.
 
@@
 Using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
-When we consider interaction quality and Allport's conditions jointly, we find that Allport's conditions also predicted whether such interactions were also perceived as more positive.
+When we consider interaction quality and Allport's conditions jointly, we find that the positive effect of Allport's conditions might in part be explained by more positive interaction quality ratings.
 We thus find first evidence that Allport's conditions of optimal contact are also relevant to the daily interactions recent migrants have in their interactions with majority group members.
@@
 % Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal datasets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
+Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
 We find that in all three studies the effect of core need fulfillment on outgroup attitudes could either fully or partially be explained by its effect on interaction quality.
 We also find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
-In fact, our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
+In fact, our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance than commonly measured psychological needs.
 In most cases, the core need even took over the variances previously explained by the self-determination theory needs (see \appref{app:AppendixRobustness}).
@@
 While setting up an extensive longitudinal study is not easy, we believe the efforts to be similar to a sizable cross-sectional data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with roughly 3,000 intergroup interactions captured and over 10,000 data points in total).
-Given the comparable effort, this opens up the possibility to explore research questions that focus on real-life phenomena outside the lab or focus on phenomena that depend on changes and influences over time.
+Intensive longitudinal data, thus, opens up the possibility to explore research questions that focus on real-life phenomena outside the lab or focus on phenomena that depend on changes and influences over time.
 In the context of intergroup contact research, we are among the first to answer calls to test intergroup contact mechanisms using extended real-life data \citep[e.g.,][]{Pettigrew2011, MacInnis2015}.
@@
 While our results are tentative given their novelty within the field, they were highly consistent across studies and may offer new theoretical avenues.
-Psychological needs are a facet of the human experience that has thus far been under–emphasized in the intergroup contact literature.
+Psychological needs are a facet of the human experience that has thus far been underemphasized in the intergroup contact literature.
 This stands in stark contrast of the many cognitive \citep[e.g.,][]{Pettigrew1998, Brown2005} and emotional aspects investigated within the field \citep[e.g.,][]{Stephan2008, Paolini2004}.
@@
 Intergroup contact theory is among the most implemented psychological theories \citep[e.g.,][]{Pettigrew2006, AlRamiah2012a, Reimer2021}.
-Given our findings that psychological needs in every-day intergroup contacts were at least as powerful as Allport's conditions in predicting outgroup attitudes, considerations of people's needs offer a substantially more immediate mechanism to address.
+Given our findings that psychological needs in everyday intergroup contacts were at least as powerful as Allport's conditions in predicting outgroup attitudes, considerations of people's needs offer a substantially more immediate mechanism to address.
 In cases where some or all optimal contact conditions are not possible to be fulfilled, needs offer an even more compelling alternative (e.g., where equal status is contextually not possible or in cases where people help despite a lack of institutional support).

### 2022-11-11 Methods-and-Results.Rmd
shortened + typos + refs

@@
 With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(workerSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(workerSampleInfo$dailiesN), big.mark=",")`).
-This is a common number of measurements found in experience sampling studies and offers sufficient power to model processes within and between participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
+This is a common number of measurements found in experience sampling studies and offers sufficient power to model processes within and between participants \citep[e.g.,][]{AanhetRot2012}.
 Participants were compensated for their participation with up to 34 Euros – each two Euros for pre- and post-questionnaire and 50 Eurocents for every experience sampling measurement.
@@
 Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
-interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtWorkerSupp$workerAvFreQual$SumContactNL), big.mark=",")` of all `r format(nrow(dtWorkerSupp$workerInteractionType), big.mark=",")` experience sampling responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts.
+interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtWorkerSupp$workerAvFreQual$SumContactNL), big.mark=",")` of all `r format(nrow(dtWorkerSupp$workerInteractionType), big.mark=",")` experience sampling responses)\footnote{Two participants only recorded two experience sampling measurements each and none of these included outgroup contacts.
 These participants are removed from any analyses that focus on outgroup contacts.}.
@@
 \subsubsection{Contact Hypothesis}
-We used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants.
-We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
+Using a multilevel regression, we find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
 Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by using centered predictors and reintroducing the means as level two predictors (\citealp{Yaremych2021}; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
@@
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCore, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreCI, varName = "keymotive_fulfillemt_1_cwc")`) and also predicted higher perceived contact quality (random intercept model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Qlt$lmeInterceptCore, lmerCI = mdlWorkerOut$Qlt$lmerInterceptCoreCI, varName = "keymotive_fulfillemt_1_cwc")`).
-Moreover, when we consider the influences of core need fulfillment and contact quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived contact quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`).
+Moreover, when we consider the influences of core need fulfillment and contact quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived contact quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`, also see \fgrref[-A]{fig:MainPaths}).
 We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes.
@@
 Thus, in our second data set we also find that outgroup contacts show a positive effect on outgroup attitudes in the moment.
-We additionally find an average between participant effect of the relative number of interactions participants had.
+We additionally find an average between-participant effect of the relative number of interactions participants had.
 
@@
 
-We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is subsumed by the perceived interaction quality if considered jointly.
+We again sequentially tested the core need model as we did for Study 1.
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`).
-Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment} for full results).
+Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see \fgrref[-B]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for full results).
 These results are consistent with the results in Study 1.
@@
 The aim of this final study is to extend the previous studies by additionally testing Allport's conditions in an extensive longitudinal design and to compare the predictive powers of Allport's conditions and the core situational need fulfillment.
-We will, thus, again test the general contact hypothesis, the influence of core need fulfillment, and perceived interaction quality during intergroup contacts.
-However, we additionally have the opportunity to also assess the role of Allport's conditions in this and to compare the two approaches (Allport's conditions and core need fulfillment) directly.
-
 For this study, we specifically recruited international medical students, because they represent a particular group of migrants who face structural requirements to integrate and interact with Dutch majority outgroup members on a daily basis.
@@
 With this design, we aimed at getting 50-60 measurements per participant (\textit{M} = `r format(round(mean(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(medicalSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(medicalSampleInfo$dailiesN), big.mark=",")`).
-As with the previous studies, this offered sufficient power to model processes within participants and will lend stronger weight to between-participant results.
+As with the previous studies, this offered sufficient power to model processes within participants.
 Participants were compensated in the same manner as during Study 1.
-The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(medicalSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(medicalSampleInfo$age),2), nsmall=2)`, `r nrow(medicalSampleInfo %>% filter(gender == "women"))` women).
+The sample consisted of relatively young migrants ($M_{age}$ = `r format(round(mean(medicalSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(medicalSampleInfo$age),2), nsmall=2)`, `r nrow(medicalSampleInfo %>% filter(gender == "women"))` women).
 The sample fairly accurately describes the local population of young international medical professionals.
@@
 \subsubsection{Contact Hypothesis}
-In the multilevel regression, we find that having an outgroup interaction was again associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A).
+In a multilevel regression, we find that having an outgroup interaction was again associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong} and \fgrref{fig:ContactHypothesis}).
 Thus, in our third data set we find that the within-person contemporaneous effect of intergroup contact was consistent across all three studies.
@@
 
-Analogous to the previous studies, we again sequentially tested whether the fulfillment of the core need during an outgroup interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly.
+We tested the situational core needs model analogous to the previous studies.
 We find that the fulfillment of the core need during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
-Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
+Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; also see \fgrref[-C]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for full results).
 As with the previous two studies, these results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and the results suggest that this might be due to higher perceived interaction quality.
@@
 
-As we did with core need fulfillment, we sequentially tested whether the fulfillment of Allport's contact conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly.
+We tested the impact of Allport's conditions in the same manner as we tested our core needs model.
 In the multilevel models we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
-Moreover, when we considered the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we found that perceived interaction quality was a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
+Moreover, when we considered the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we found that perceived interaction quality was a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}).
 These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.
@@
 When comparing the model selection indices, we found that the fulfillment of the situational core need indeed performed slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
-Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).
+Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}).
 This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
@@
 When looking at the fulfillment of core needs during intergroup contacts, we find that the motivational mechanism is consistently a meaningful predictor of outgroup attitudes and interaction quality perceptions (see \fgrref[ A and B]{fig:AllportNeedFulfillment}).
-We also see that the effect of core need fulfillment on outgroup attitudes is strongly reduced when modeled together with interaction quality perceptions, supporting our assertion that interaction quality offers a psychological mechanism for the direct effect.
+We also see that the effect of core need fulfillment on outgroup attitudes is strongly reduced when modeled together with interaction quality perceptions, supporting our assertion that interaction quality offers a psychological mechanism for the direct effect (see \fgrref[-C]{fig:AllportNeedFulfillment}).
 
@@
 
-During the main analyses, we have thus far shown that participants held more positive outgroup attitudes following intergroup contacts and that a perceived interaction quality was associated with more positive outgroup attitudes following an intergroup contact.
+During the main analyses, we have thus far shown that participants held more positive outgroup attitudes following intergroup contacts and that perceived interaction quality was associated with more positive outgroup attitudes following an intergroup contact.
 We have, however, not brought the two elements of the contact hypothesis together in a single analysis.
@@
 One interesting observation was the importance of contact goals specific to contact through the medical and public health system.
-This goal type was partly specific to the medical professionals (e.g., working with patients, treatment), but also more broadly interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals).
+This goal type was partly specific to the medical professionals (e.g., working with patients, treatment), but also more broadly highlighted interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals).
 Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members.
 Another topic less commonly found within the literature were more practically oriented needs, where participants sought to share food and cook together, or had organizational needs (e.g., housing, cleaning, and co-living).
-In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyper parameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
+In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
 The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.

### 2022-11-11 Methods-and-Results.tex
shortened + typos + refs

@@
 sampling studies and offers sufficient power to model processes within
-and between participants
-\citep[e.g., for a systematic review see][]{AanhetRot2012}. Participants
+and between participants \citep[e.g.,][]{AanhetRot2012}. Participants
 were compensated for their participation with up to 34 Euros -- each two
@@
 387 of all 1,225 experience sampling
-responses)\footnote{Two participants only recorded two experience sampling measurements each and non of these included outgroup contacts.
+responses)\footnote{Two participants only recorded two experience sampling measurements each and none of these included outgroup contacts.
 These participants are removed from any analyses that focus on outgroup contacts.}.
@@
 
-We used a multilevel regression to check whether having an interaction
-with an outgroup member had a situational (i.e., contemporaneous) effect
-within the participants. We find that having an outgroup contact is
-indeed associated with significantly more positive outgroup attitudes
+Using a multilevel regression, we find that having an outgroup contact
+is indeed associated with significantly more positive outgroup attitudes
 (\textit{b} = 2.48, \textit{t}(1,200) = 4.37, \textit{p} \textless{}
@@
 attitudes jointly, we find that virtually all variance is explained by
-perceived contact quality (random slopes mode; \textit{b} = 0.23,
+perceived contact quality (random slopes model; \textit{b} = 0.23,
 \textit{t}(364) = 4.22, \textit{p} \textless{} .001,
@@
 \textit{t}(364) = 0.64, \textit{p} = 0.523, \textit{95\%CI}{[}-0.08,
-0.15{]}). We thus find support for our hypotheses and can conclude that
-in this data set the fulfillment of core situational needs had a
-significant influence on outgroup attitudes. Additionally, this effect
-is likely explained by its effect through perceived contact quality.
+0.15{]}, also see \fgrref[-A]{fig:MainPaths}). We thus find support for
+our hypotheses and can conclude that in this data set the fulfillment of
+core situational needs had a significant influence on outgroup
+attitudes. Additionally, this effect is likely explained by its effect
+through perceived contact quality.
 
@@
 show a positive effect on outgroup attitudes in the moment. We
-additionally find an average between participant effect of the relative
+additionally find an average between-participant effect of the relative
 number of interactions participants had.
@@
 
-We again sequentially tested whether the fulfillment of the core need
-during an interaction was (1) related to more positive outgroup
-attitudes, (2) higher perceived interaction quality, and (3) whether the
-variance explained by the core need is subsumed by the perceived
-interaction quality if considered jointly. We find that in the
-multilevel models, the fulfillment of core situational needs during
-outgroup contacts was associated with more positive outgroup attitudes
-(random slopes model; \textit{b} = 0.13, \textit{t}(826) = 4.18,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.19{]}) and also
-predicted higher perceived interaction quality (random slopes model;
-\textit{b} = 0.40, \textit{t}(826) = 6.46, \textit{p} \textless{} .001,
+We again sequentially tested the core need model as we did for Study 1.
+We find that in the multilevel models, the fulfillment of core
+situational needs during outgroup contacts was associated with more
+positive outgroup attitudes (random slopes model; \textit{b} = 0.13,
+\textit{t}(826) = 4.18, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.07, 0.19{]}) and also predicted higher perceived
+interaction quality (random slopes model; \textit{b} = 0.40,
+\textit{t}(826) = 6.46, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.28, 0.52{]}). Additionally, if we consider the
@@
 attitudes jointly, we find that virtually all variance is explained by
-perceived interaction quality (random slopes mode; \textit{b} = 0.17,
+perceived interaction quality (random slopes model; \textit{b} = 0.17,
 \textit{t}(825) = 5.56, \textit{p} \textless{} .001,
@@
 \textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
-0.07{]}; also see \tblref{tab:intergroupNeedsTblLong} and
-\fgrref{fig:AllportNeedFulfillment} for full results). These results are
+0.07{]}; also see \fgrref[-B]{fig:MainPaths} and
+\tblref{tab:intergroupNeedsTblLong} for full results). These results are
 consistent with the results in Study 1. We, thus, find support for our
@@
 design and to compare the predictive powers of Allport's conditions and
-the core situational need fulfillment. We will, thus, again test the
-general contact hypothesis, the influence of core need fulfillment, and
-perceived interaction quality during intergroup contacts. However, we
-additionally have the opportunity to also assess the role of Allport's
-conditions in this and to compare the two approaches (Allport's
-conditions and core need fulfillment) directly.
-
-For this study, we specifically recruited international medical
-students, because they represent a particular group of migrants who face
-structural requirements to integrate and interact with Dutch majority
-outgroup members on a daily basis. As part of their educational program,
-the migrants are required to take language courses and interact with
-patients as part of their medical internships and medical residency. The
-extensive longitudinal survey method again offers a large body of
-ecologically valid data on need satisfaction in real-life intergroup
-contact situations. Data were collected from November
-8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020. The
-full preregistration is available at \citet[][]{KreienkampMasked2021f}.
-Correlations and descriptive statistics of the included variables are
-available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+the core situational need fulfillment. For this study, we specifically
+recruited international medical students, because they represent a
+particular group of migrants who face structural requirements to
+integrate and interact with Dutch majority outgroup members on a daily
+basis. As part of their educational program, the migrants are required
+to take language courses and interact with patients as part of their
+medical internships and medical residency. The extensive longitudinal
+survey method again offers a large body of ecologically valid data on
+need satisfaction in real-life intergroup contact situations. Data were
+collected from November 8\textsuperscript{th}, 2019 to January
+10\textsuperscript{th}, 2020. The full preregistration is available at
+\citet[][]{KreienkampMasked2021f}. Correlations and descriptive
+statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
 
@@
 studies, this offered sufficient power to model processes within
-participants and will lend stronger weight to between-participant
-results. Participants were compensated in the same manner as during
-Study 1. The sample consisted of relatively young migrants, who were
-mostly from the global north (\(M_{age}\) = 22.68, \(SD_{age}\) = 3.10,
-59 women). The sample fairly accurately describes the local population
-of young international medical professionals.
+participants. Participants were compensated in the same manner as during
+Study 1. The sample consisted of relatively young migrants (\(M_{age}\)
+= 22.68, \(SD_{age}\) = 3.10, 59 women). The sample fairly accurately
+describes the local population of young international medical
+professionals.
 
@@
 
-In the multilevel regression, we find that having an outgroup
-interaction was again associated with significantly more positive
-outgroup attitudes within the participants (random slopes model;
-\textit{b} = 5.57, \textit{t}(3,834) = 6.52, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}3.90, 7.23{]}), even after controlling for
-having an interaction with a non-Dutch (which did not relate to outgroup
-attitudes independently; for full results see
-\tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
-and Online Supplementary Material A). Thus, in our third data set we
-find that the within-person contemporaneous effect of intergroup contact
-was consistent across all three studies.
+In a multilevel regression, we find that having an outgroup interaction
+was again associated with significantly more positive outgroup attitudes
+within the participants (random slopes model; \textit{b} = 5.57,
+\textit{t}(3,834) = 6.52, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}3.90, 7.23{]}), even after controlling for having an
+interaction with a non-Dutch (which did not relate to outgroup attitudes
+independently; for full results see
+\tblref{tab:intergroupGeneralTblLong} and
+\fgrref{fig:ContactHypothesis}). Thus, in our third data set we find
+that the within-person contemporaneous effect of intergroup contact was
+consistent across all three studies.
 
@@
 
-Analogous to the previous studies, we again sequentially tested whether
-the fulfillment of the core need during an outgroup interaction was (1)
-related to more positive outgroup attitudes, (2) higher perceived
-interaction quality, and (3) whether the variance explained by the core
-need is assumed by the perceived interaction quality if considered
-jointly. We find that the fulfillment of the core need during outgroup
+We tested the situational core needs model analogous to the previous
+studies. We find that the fulfillment of the core need during outgroup
 contacts was associated with more positive outgroup attitudes (random
@@
 attitudes jointly, we find that perceived interaction quality is a
-substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
-\textit{t}(1,600) = 6.86, \textit{p} \textless{} .001,
+substantially stronger predictor (random slopes model; \textit{b} =
+0.17, \textit{t}(1,600) = 6.86, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.12, 0.22{]}) and the unique variance explained by
@@
 (\textit{b} = 0.11, \textit{t}(1,600) = 3.50, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}0.05, 0.17{]}; for full results see
-\tblref{tab:intergroupNeedsTblLong} and
-\fgrref{fig:AllportNeedFulfillment}). As with the previous two studies,
-these results indicate that in this data set outgroup attitudes were
-significantly predicted by the fulfillment of core situational needs and
-the results suggest that this might be due to higher perceived
-interaction quality.
+.001, \textit{95\%CI}{[}0.05, 0.17{]}; also see
+\fgrref[-C]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for
+full results). As with the previous two studies, these results indicate
+that in this data set outgroup attitudes were significantly predicted by
+the fulfillment of core situational needs and the results suggest that
+this might be due to higher perceived interaction quality.
 
@@
 
-As we did with core need fulfillment, we sequentially tested whether the
-fulfillment of Allport's contact conditions was (1) related to more
-positive outgroup attitudes, (2) higher perceived interaction quality,
-and (3) whether the variance explained by Allport's Conditions is
-assumed by the perceived interaction quality if considered jointly. In
-the multilevel models we find that the fulfillment of Allport's
-Conditions during outgroup contacts was associated with more positive
-outgroup attitudes (random slopes model; \textit{b} = 0.22,
-\textit{t}(1,601) = 5.86, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.15, 0.29{]}) and also predicted higher perceived
-interaction quality (random slopes model; \textit{b} = 0.65,
+We tested the impact of Allport's conditions in the same manner as we
+tested our core needs model. In the multilevel models we find that the
+fulfillment of Allport's Conditions during outgroup contacts was
+associated with more positive outgroup attitudes (random slopes model;
+\textit{b} = 0.22, \textit{t}(1,601) = 5.86, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.15, 0.29{]}) and also predicted higher
+perceived interaction quality (random slopes model; \textit{b} = 0.65,
 \textit{t}(1,605) = 11.82, \textit{p} \textless{} .001,
@@
 attitudes jointly, we found that perceived interaction quality was a
-substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
-\textit{t}(1,600) = 6.25, \textit{p} \textless{} .001,
+substantially stronger predictor (random slopes model; \textit{b} =
+0.17, \textit{t}(1,600) = 6.25, \textit{p} \textless{} .001,
 \textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
@@
 \textit{95\%CI}{[}0.03, 0.15{]}; also see
-\tblref{tab:intergroupNeedsTblLong} and
-\fgrref{fig:AllportNeedFulfillment}). These results indicate that in
+\tblref{tab:intergroupNeedsTblLong}). These results indicate that in
 this data set the fulfillment of Allport's conditions had a significant
@@
 \textit{95\%CI}{[}0.08, 0.17{]}; also see
-\tblref{tab:intergroupNeedsTblLong} and
-\fgrref{fig:AllportNeedFulfillment}). This indicates that, although both
+\tblref{tab:intergroupNeedsTblLong}). This indicates that, although both
 Allport's conditions and the core need fulfillment seem to (in part)
@@
 supporting our assertion that interaction quality offers a psychological
-mechanism for the direct effect.
+mechanism for the direct effect (see
+\fgrref[-C]{fig:AllportNeedFulfillment}).
 
@@
 more positive outgroup attitudes following intergroup contacts and that
-a perceived interaction quality was associated with more positive
-outgroup attitudes following an intergroup contact. We have, however,
-not brought the two elements of the contact hypothesis together in a
-single analysis. To jointly test the effects of contact frequency and
-average interaction quality, we ran a linear regression model where
-average outgroup attitudes were predicted by the number of interactions
-and the average interaction quality ratings of all participants across
-the three studies. We did so while controlling for the possible effects
-of study-specific differences. To include the study-membership as a
-control variable, we used the student sample (Study 2) as the reference
-group because it was both the largest and the most homogeneous study.
-Looking at the overall model, we found that the model predicted 13.89\%
-of the variance in average outgroup attitudes (\textit{F}(9, 189) =
-3.39, \textit{p} = 0.001, \textit{R\textsuperscript{2}} = 0.14). Looking
-at the individual effects, we found that only the number of outgroup
+perceived interaction quality was associated with more positive outgroup
+attitudes following an intergroup contact. We have, however, not brought
+the two elements of the contact hypothesis together in a single
+analysis. To jointly test the effects of contact frequency and average
+interaction quality, we ran a linear regression model where average
+outgroup attitudes were predicted by the number of interactions and the
+average interaction quality ratings of all participants across the three
+studies. We did so while controlling for the possible effects of
+study-specific differences. To include the study-membership as a control
+variable, we used the student sample (Study 2) as the reference group
+because it was both the largest and the most homogeneous study. Looking
+at the overall model, we found that the model predicted 13.89\% of the
+variance in average outgroup attitudes (\textit{F}(9, 189) = 3.39,
+\textit{p} = 0.001, \textit{R\textsuperscript{2}} = 0.14). Looking at
+the individual effects, we found that only the number of outgroup
 interactions has a clear association with average outgroup attitudes
@@
 was partly specific to the medical professionals (e.g., working with
-patients, treatment), but also more broadly interactions of newcomers
-with the outgroup majority as patients themselves (e.g., therapeutic
-goals). Also health, fitness, and personal improvement goals (e.g.,
-sports and music) were common goals that participants shared during the
-interactions with the majority group members. Another topic less
-commonly found within the literature were more practically oriented
+patients, treatment), but also more broadly highlighted interactions of
+newcomers with the outgroup majority as patients themselves (e.g.,
+therapeutic goals). Also health, fitness, and personal improvement goals
+(e.g., sports and music) were common goals that participants shared
+during the interactions with the majority group members. Another topic
+less commonly found within the literature were more practically oriented
 needs, where participants sought to share food and cook together, or had
@@
 migration experience that has remained broadly under-explored
-\citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyper parameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
+\citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
 The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.

### 2022-11-11 manuscript.tex
typos

@@
   Summary of mixed models results of the contemporaneous contact effects.\\
-  General: Random effects meta analytic results are presented for completeness.}
+  General: Random effects meta-analytic results are presented for completeness.}
 \end{figure}
@@
   (c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.\\
-  General: Random effects meta analytic results are presented for completeness.}
+  General: Random effects meta-analytic results are presented for completeness.}
 \end{figure}
@@
 In this appendix, we present the expanded hypotheses and their associated analysis plan.
-Given the nested structure of much of our data we test many of our hypotheses using a multilevel approach, where $y_{ti}$ denotes the response at measurement occasion $t$ ($t = 1, ...,T_i$; level 1) for individual $i$ ($i = 1, ..., n$; level 2).
+Given the nested structure of much of our data, we test many of our hypotheses using a multilevel approach, where $y_{ti}$ denotes the response at measurement occasion $t$ ($t = 1, ..., T_i$; level 1) for individual $i$ ($i = 1, ..., n$; level 2).
 All multilevel assumptions are tested as follows (e.g., for random slopes model with $j$ within-person predictors):

### 2022-11-11 Methods-and-Results.Rmd
shortened

@@
 After giving informed consent, participants filled in an online pre-questionnaire assessing demographics and general information about their immigration.
-Over the next thirty days, participants were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup (\textit{median survey duration} = `r seconds_to_period(median(dtWorker$clean$Duration__in_seconds_)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(dtWorker$clean$Duration__in_seconds_))) %>% as.character`).
+Over the next thirty days, participants were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup.
 General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%).}.
@@
 \subsubsection{Procedure} The study procedure mirrored the setup of Study 1 and consisted of pre-, experience sampling-, and post-measurements.
-The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median survey duration} = `r seconds_to_period(median(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily))) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtStudents$clean$ended.daily, dtStudents$clean$created.daily)))) %>% as.character`).
+The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days.
 General compliance was high (`r format(round(sum(studentSampleInfo$dailiesN)/(nrow(studentSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in).
@@
 \subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, experience sampling-, and post-measurement.
-The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days (\textit{median survey duration} = `r seconds_to_period(median(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE)) %>% as.character`, \textit{MAD duration} = `r seconds_to_period(round(mad(difftime(dtMedical$clean$ended.daily, dtMedical$clean$created.daily, units = "secs"), na.rm=TRUE))) %>% as.character`).
+The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days.
 General compliance was high (`r format(round(table(medicalSampleInfo$dailiesN>30)["TRUE"]/nrow(medicalSampleInfo)*100,2), nsmall=2)`\% filled in at least 31 experience sampling surveys or more).

### 2022-11-11 Methods-and-Results.tex
shortened

@@
 their interactions, psychological need fulfillments, and current
-attitudes towards the Dutch outgroup (\textit{median survey duration} =
-2M 22S, \textit{MAD duration} = 1M 19S). General compliance was high
+attitudes towards the Dutch outgroup. General compliance was high
 (85.90\% of all invited surveys were filled
@@
 invited for experience sampling measurements twice a day (at 12 pm and
-7pm) for 30 days (\textit{median survey duration} = 3M 46S,
-\textit{MAD duration} = 1M 54S). General compliance was high (70.87\% of
-all invited surveys were filled in). The response rates were
-approximately equal during mornings (\textit{n} = 2,608) and afternoons
-(\textit{n} = 2,357). All key variables for this study were part of the
-short experience sampling surveys.
+7pm) for 30 days. General compliance was high (70.87\% of all invited
+surveys were filled in). The response rates were approximately equal
+during mornings (\textit{n} = 2,608) and afternoons (\textit{n} =
+2,357). All key variables for this study were part of the short
+experience sampling surveys.
 
@@
 participants were invited for experience sampling measurements twice a
-day (at 12 pm and 7pm) for 30 days (\textit{median survey duration} = 4M
-13S, \textit{MAD duration} = 2M 6S). General compliance was high
-(85.92\% filled in at least 31 experience sampling surveys or more). The
-response rates were approximately equal during mornings (\textit{n} =
-2,092) and afternoons (\textit{n} = 2,015). All key variables for this
-study were part of the short experience sampling surveys.
+day (at 12 pm and 7pm) for 30 days. General compliance was high (85.92\%
+filled in at least 31 experience sampling surveys or more). The response
+rates were approximately equal during mornings (\textit{n} = 2,092) and
+afternoons (\textit{n} = 2,015). All key variables for this study were
+part of the short experience sampling surveys.
 

### 2022-11-11 PathModels.Rmd
spacing adjusted
shortened

@@
     \\draw[-latex] (x.east) -- node[below=2mm, align=center] {<<coef_xy>>} (y.west);
-    \\path (xd.north west) ++(-0.2, 6pt) node[above left]{\\textbf{(<<fig_num>>)}};
+    \\path (xd.north west) ++(-0.2, 6pt) node[above left]{\\textbf{(<<fig_num>>) <<study_num>>}};
 \\end{tikzpicture}
@@
     coef_xy = pathCoeffs$Study1$xy,
-    fig_num = "A"
+    fig_num = "A",
+    study_num = "Study 1"
   )
@@
     coef_xy = pathCoeffs$Study2$xy,
-    fig_num = "B"
+    fig_num = "B",
+    study_num = "Study 2"
   )
@@
     coef_xy = pathCoeffs$Study3$xy,
-    fig_num = "C"
+    fig_num = "C",
+    study_num = "Study 3"
   )
@@
 
-\vspace{12pt}
+\vspace{24pt}
 

### 2022-11-11 PathModels.tex
path figure added
shortened

@@
     \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.13} (y.west);
-    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(A)}};
+    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(A) Study 1}};
 \end{tikzpicture}
 
-\vspace{12pt}
+\vspace{24pt}
 
@@
     \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.07} (y.west);
-    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(B)}};
+    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(B) Study 2}};
 \end{tikzpicture}
 
-\vspace{12pt}
+\vspace{24pt}
 
@@
     \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.10**} (y.west);
-    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(C)}};
+    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(C) Study 3}};
 \end{tikzpicture}

### 2022-11-11 Methods-and-Results.Rmd
typos

@@
 To this aim, we recruited recent migrants to the Netherlands for an intensive longitudinal survey.
-Data was collected from May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all participants started the study within the first two days).
+Data were collected from May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all participants started the study within the first two days).
 Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide} (full data description is available in Online Supplementary Material A).
@@
 After giving informed consent, participants filled in an online pre-questionnaire assessing demographics and general information about their immigration.
-Over the next thirty days, participants were invited twice a day (at 12 pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup.
+Over the next thirty days, participants were invited twice a day (at 12pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup.
 General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%).}.
@@
 
-\paragraph{Outgroup Attitudes}At the end of every experience sampling measurement we asked all participants about their current attitudes towards the Dutch – our main dependent variable.
+\paragraph{Outgroup Attitudes}At the end of every experience sampling measurement, we asked all participants about their current attitudes towards the Dutch – our main dependent variable.
 To assess the momentary outgroup evaluation we used the common feeling thermometer: “How favorable do you feel towards the Dutch?” \citep[][]{Lavrakas2008}.
@@
 However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}.
-Thus, in our first data we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data.
+Thus, in our first data, we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data.
 
@@
 The survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations as these students will likely interact with the Dutch majority outgroup on a daily basis.
-Data was collected from November 19\textsuperscript{th}, 2018 through January 6\textsuperscript{th}, 2019.
+Data were collected from November 19\textsuperscript{th}, 2018 through January 6\textsuperscript{th}, 2019.
 Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
@@
 With this design, we again aimed at receiving 50-60 measurements per participant (\textit{M} = `r format(round(mean(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{SD} = `r format(round(sd(studentSampleInfo$dailiesN),2), nsmall=2)`, \textit{total N} = `r format(sum(studentSampleInfo$dailiesN), big.mark=",")`).
-As with the previous study this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
+As with the previous study, this should offer sufficient power to model processes within participants and will lend stronger weight to between-participant results.
 Participants were compensated for their participation with partial course credits --- depending on their participation.
@@
 \subsubsection{Procedure} The study procedure mirrored the setup of Study 1 and consisted of pre-, experience sampling-, and post-measurements.
-The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days.
+The participants were invited for experience sampling measurements twice a day (at 12pm and 7pm) for 30 days.
 General compliance was high (`r format(round(sum(studentSampleInfo$dailiesN)/(nrow(studentSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in).
@@
 
-\paragraph{Psychological Needs}For the core situational need, we asked participants in an open ended text field: “\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}” (where \textit{-X-} was dynamically replaced with the name of the interaction partner).
+\paragraph{Psychological Needs}For the core situational need, we asked participants in an open-ended text field: “\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}” (where \textit{-X-} was dynamically replaced with the name of the interaction partner).
 Participants could additionally click on a pop-up explanation: "Your main goal during an interaction can vary depending on the interaction.
-It could be to connect with friends, to find or provide help, to achieve academic ambitions, work on your fitness, work for a job, or simply to get a coffee, just as well as many other concrete or abstract goals that are import to you in the moment.
+It could be to connect with friends, to find or provide help, to achieve academic ambitions, work on your fitness, work for a job, or simply to get a coffee, just as well as many other concrete or abstract goals that are important to you in the moment.
 It really depends on your subjective experience of the interaction.".
@@
 
-\paragraph{Perceived Interaction Quality}The ratings of the perceived contact quality was identical to Study 1.
+\paragraph{Perceived Interaction Quality}The ratings of the perceived contact quality were identical to Study 1.
 
@@
 \subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, experience sampling-, and post-measurement.
-The participants were invited for experience sampling measurements twice a day (at 12 pm and 7pm) for 30 days.
+The participants were invited for experience sampling measurements twice a day (at 12pm and 7pm) for 30 days.
 General compliance was high (`r format(round(table(medicalSampleInfo$dailiesN>30)["TRUE"]/nrow(medicalSampleInfo)*100,2), nsmall=2)`\% filled in at least 31 experience sampling surveys or more).
@@
 
-\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality was identical to Study 1.
-
-\paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup was again measured using the feeling thermometer, as in studies one and two.
+\paragraph{Perceived Interaction Quality}The ratings of the perceived interaction quality were identical to Study 1.
+
+\paragraph{Outgroup Attitudes}Attitudes towards the Dutch majority outgroup were again measured using the feeling thermometer, as in studies one and two.
 
@@
 In a multilevel regression, we find that having an outgroup interaction was again associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong} and \fgrref{fig:ContactHypothesis}).
-Thus, in our third data set we find that the within-person contemporaneous effect of intergroup contact was consistent across all three studies.
+Thus, in our third data set, we find that the within-person contemporaneous effect of intergroup contact was consistent across all three studies.
 
@@
 We tested the impact of Allport's conditions in the same manner as we tested our core needs model.
-In the multilevel models we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
+In the multilevel models, we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
 Moreover, when we considered the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we found that perceived interaction quality was a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}).
@@
 When comparing the model selection indices, we found that the fulfillment of the situational core need indeed performed slightly better than the model using Allport's conditions ($AIC_{CoreNeed}$ `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(AIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $AIC_{Allport}$, and $BIC_{CoreNeed}$ `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesCore), 2), nsmall = 2)` < `r format(round(BIC(mdlMedicalOut$Att$lmerSlopesAllport), 2), nsmall = 2)` $BIC_{Allport}$).
-Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}).
+Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar-sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}).
 This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
 
-\section{Robustness, Stability, and Embeddeness across Studies}
+\section{Robustness, Stability, and Embeddedness across Studies}
 
@@
 Finally, we used the qualitative data from the participants’ self-identified core needs to contextualize the results of our main analysis.
-However, because our participants jointly reported on thousands of intergroup contacts, it would not have been feasible to analyse these qualitative responses in a traditional qualitative content analysis.
+However, because our participants jointly reported on thousands of intergroup contacts, it would not have been feasible to analyze these qualitative responses in a traditional qualitative content analysis.
 We instead relied on recent machine learning advances within the natural language processing domain.
-For our analysis we used the BERT language model.
-BERT (Bidirectional Encoder Representations from Transformers) was developed by Google in 2018 and today forms a key elements of many natural language processing workflows.
+For our analysis, we used the BERT language model.
+BERT (Bidirectional Encoder Representations from Transformers) was developed by Google in 2018 and today forms a key element of many natural language processing workflows.
 In its essence, BERT is a framework that allows users to codify every word in relation to every other word within a large set of documents.
@@
 The higher number of topics allowed us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (10.33%).
-A full write up of the topic modeling process is available in Online Supplemental Material B.
+A full write-up of the topic modeling process is available in Online Supplemental Material B.
 
 In terms of the content of the topics, we find that a number of topics are primarily task-oriented, where participants hope to increase their study, research, presentation, or work performance.
-Opposing the task and work oriented needs, are a wide variety of leisure-related needs wishes, like relaxation and entertainment.
+Opposing the task- and work-oriented needs, are a wide variety of leisure-related needs wishes, like relaxation and entertainment.
 Additionally, some clusters were primarily relationship-oriented, so that participants sought contact with outgroup members for intimate and casual social contact in itself.
@@
 meditation, prayer, religious services).
-Among the leisure-oriented topics was also a set of contact goals that were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned informational needs more generally (e.g., seeking answers, bureaucratic information).
-A similar set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel related goals in their interactions with the majority group members.
+Among the leisure-oriented topics was also a set of contact goals that were specifically migration-specific (e.g., wish to learn about culture, politics, and language) or were concerned with informational needs more generally (e.g., seeking answers, bureaucratic information).
+A similar set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel-related goals in their interactions with the majority group members.
 
@@
 Also health, fitness, and personal improvement goals (e.g., sports and music) were common goals that participants shared during the interactions with the majority group members.
-Another topic less commonly found within the literature were more practically oriented needs, where participants sought to share food and cook together, or had organizational needs (e.g., housing, cleaning, and co-living).
+Another topic less commonly found within the literature were more practically oriented needs, where participants sought to share food and cook together or had organizational needs (e.g., housing, cleaning, and co-living).
 In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
-The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
+The authors have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
 

### 2022-11-11 Methods-and-Results.tex
typos

@@
 contacts. To this aim, we recruited recent migrants to the Netherlands
-for an intensive longitudinal survey. Data was collected from May
+for an intensive longitudinal survey. Data were collected from May
 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all
@@
 information about their immigration. Over the next thirty days,
-participants were invited twice a day (at 12 pm and 7pm) to reflect upon
+participants were invited twice a day (at 12pm and 7pm) to reflect upon
 their interactions, psychological need fulfillments, and current
@@
 
-At the end of every experience sampling measurement we asked all
+At the end of every experience sampling measurement, we asked all
 participants about their current attitudes towards the Dutch -- our main
@@
 However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}.
-Thus, in our first data we find initial evidence that outgroup contacts
+Thus, in our first data, we find initial evidence that outgroup contacts
 show a positive effect on outgroup attitudes within real-life data.
@@
 students will likely interact with the Dutch majority outgroup on a
-daily basis. Data was collected from November 19\textsuperscript{th},
+daily basis. Data were collected from November 19\textsuperscript{th},
 2018 through January 6\textsuperscript{th}, 2019. Correlations and
@@
 measurements per participant (\textit{M} = 43.94, \textit{SD} = 15.00,
-\textit{total N} = 4,965). As with the previous study this should offer
+\textit{total N} = 4,965). As with the previous study, this should offer
 sufficient power to model processes within participants and will lend
@@
 experience sampling-, and post-measurements. The participants were
-invited for experience sampling measurements twice a day (at 12 pm and
+invited for experience sampling measurements twice a day (at 12pm and
 7pm) for 30 days. General compliance was high (70.87\% of all invited
@@
 for a job, or simply to get a coffee, just as well as many other
-concrete or abstract goals that are import to you in the moment. It
+concrete or abstract goals that are important to you in the moment. It
 really depends on your subjective experience of the interaction.''.
@@
 
-The ratings of the perceived contact quality was identical to Study 1.
+The ratings of the perceived contact quality were identical to Study 1.
 
@@
 participants were invited for experience sampling measurements twice a
-day (at 12 pm and 7pm) for 30 days. General compliance was high (85.92\%
+day (at 12pm and 7pm) for 30 days. General compliance was high (85.92\%
 filled in at least 31 experience sampling surveys or more). The response
@@
 
-The ratings of the perceived interaction quality was identical to Study
+The ratings of the perceived interaction quality were identical to Study
 1.
@@
 
-Attitudes towards the Dutch majority outgroup was again measured using
+Attitudes towards the Dutch majority outgroup were again measured using
 the feeling thermometer, as in studies one and two.
@@
 \tblref{tab:intergroupGeneralTblLong} and
-\fgrref{fig:ContactHypothesis}). Thus, in our third data set we find
+\fgrref{fig:ContactHypothesis}). Thus, in our third data set, we find
 that the within-person contemporaneous effect of intergroup contact was
@@
 We tested the impact of Allport's conditions in the same manner as we
-tested our core needs model. In the multilevel models we find that the
+tested our core needs model. In the multilevel models, we find that the
 fulfillment of Allport's Conditions during outgroup contacts was
@@
 jointly, we find that both significantly predict outgroup attitudes with
-similar sized regression parameters (random slopes model; Allport's
+similar-sized regression parameters (random slopes model; Allport's
 Conditions: \textit{b} = 0.16, \textit{t}(1,600) = 4.92, \textit{p}
@@
 
-\section{Robustness, Stability, and Embeddeness across Studies}
+\section{Robustness, Stability, and Embeddedness across Studies}
 
@@
 thousands of intergroup contacts, it would not have been feasible to
-analyse these qualitative responses in a traditional qualitative content
+analyze these qualitative responses in a traditional qualitative content
 analysis. We instead relied on recent machine learning advances within
-the natural language processing domain. For our analysis we used the
+the natural language processing domain. For our analysis, we used the
 BERT language model. BERT (Bidirectional Encoder Representations from
 Transformers) was developed by Google in 2018 and today forms a key
-elements of many natural language processing workflows. In its essence,
+element of many natural language processing workflows. In its essence,
 BERT is a framework that allows users to codify every word in relation
@@
 us to retain more of the smaller topics and leaves a relatively low
-number of 308 free-text entries unclassified (10.33\%). A full write up
+number of 308 free-text entries unclassified (10.33\%). A full write-up
 of the topic modeling process is available in Online Supplemental
@@
 are primarily task-oriented, where participants hope to increase their
-study, research, presentation, or work performance. Opposing the task
-and work oriented needs, are a wide variety of leisure-related needs
+study, research, presentation, or work performance. Opposing the task-
+and work-oriented needs, are a wide variety of leisure-related needs
 wishes, like relaxation and entertainment. Additionally, some clusters
@@
 specifically migration-specific (e.g., wish to learn about culture,
-politics, and language) or were concerned informational needs more
+politics, and language) or were concerned with informational needs more
 generally (e.g., seeking answers, bureaucratic information). A similar
 set of topics was specifically geared towards a wish to experience
-cultural products (e.g., music, theater, food) or had travel related
+cultural products (e.g., music, theater, food) or had travel-related
 goals in their interactions with the majority group members.
@@
 less commonly found within the literature were more practically oriented
-needs, where participants sought to share food and cook together, or had
+needs, where participants sought to share food and cook together or had
 organizational needs (e.g., housing, cleaning, and co-living). In sum,
@@
 \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
-The authors have have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
+The authors have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.

### 2022-11-11 PathModels.Rmd
typo

@@
     fig_num = "A",
-    study_num = "Study 1"
+    study_num = "Study 1:"
   )
@@
     fig_num = "B",
-    study_num = "Study 2"
+    study_num = "Study 2:"
   )
@@
     fig_num = "C",
-    study_num = "Study 3"
+    study_num = "Study 3:"
   )

### 2022-11-11 PathModels.tex
typo

@@
     \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.13} (y.west);
-    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(A) Study 1}};
+    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(A) Study 1:}};
 \end{tikzpicture}
@@
     \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.07} (y.west);
-    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(B) Study 2}};
+    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(B) Study 2:}};
 \end{tikzpicture}
@@
     \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.10**} (y.west);
-    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(C) Study 3}};
+    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(C) Study 3:}};
 \end{tikzpicture}

### 2023-04-17 scripts/functions/MlTbl.R
:arrow_up: upgrade and accidental test

@@ -1,3 +1,4 @@
+library(plyr)
 #obj <- tblLmerS1AttSlopeCoreQlt
 #objz <- tblLmerS1AttSlopeCoreQltZ
 
@@ -64,7 +65,7 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
                   #method = "profile") %>% 
     as.data.frame %>%
     tibble::rownames_to_column(., "coef")
-  coefOut <- join(coef, conf, by = "coef")
+  coefOut <- plyr::join(coef, conf, by = "coef")
   colnames(coefOut) <- c("coef", "est", "se", "tval", "df", "p", "lwr", "upr")
   coefOut$B <- paste0(
     format(round(coefOut$est, 2), nsmall = 2),
@@ -83,7 +84,7 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
                                  ifelse(coefOut$p < .01, "**", 
                                         ifelse(coefOut$p < .05, "*", ""))))
   coefOut <- 
-    join(
+    plyr::join(
       coefOut %>% 
         mutate(coef = gsub('_cwc|C$', '', coef)), 
       coefZOut %>% 
@@ -209,7 +210,7 @@ lmTblPrep <- function (obj, alpha = 0.05, ...) {
     tibble::rownames_to_column(., "coef") %>%
     select(coef, se = S.E.)
   
-  coef <- join(
+  coef <- plyr::join(
     coefCI, 
     coefSE,
     by = "coef"
@@ -249,7 +250,7 @@ lmTblPrep <- function (obj, alpha = 0.05, ...) {
   
   # Merge B and effect size
   coefEta <- 
-    join(
+    plyr::join(
       coef %>% 
         mutate(coef = gsub('_c', '', coef)), 
        eta %>% 
@@ -258,7 +259,7 @@ lmTblPrep <- function (obj, alpha = 0.05, ...) {
       by = "coef"
     )
   coefOut <- 
-    join(
+    plyr::join(
       coefEta, 
       Rsq %>% 
         mutate(coef = gsub('_c', '', coef)),

### 2023-05-10 Methods-and-Results.Rmd
Updates from Overleaf

@@
 Another topic less commonly found within the literature were more practically oriented needs, where participants sought to share food and cook together or had organizational needs (e.g., housing, cleaning, and co-living).
-In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
+In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
 The authors have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.

### 2023-05-10 manuscript.tex

@@
 \newtheorem{definition}{Definition}
+\newcommand{\defref}[2][]{\hyperref[#2]{Definition \ref*{#2}#1}}
 
@@
 We propose to consider situational psychological needs during everyday intergroup contact.
-We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297).
+We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297; total \textit{N} participants = 207).
 The novel psychological needs mechanism is consistently a strong predictor of positive attitudes during intergroup interactions and these positive effects emerged via perceived interaction quality.
@@
 In light of these findings, understanding interaction quality thus sits at the heart of understanding when an intergroup contact is successful \citep[e.g.,][]{Allport1954b, Brown2007, Tropp2016}.
-Practically, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in everyday life contexts.
+But also in applied settings, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in everyday life contexts.
 Understanding the psychological mechanisms of when and why interactions are perceived as positive is, thus, an important issue for understanding whether an interaction leads to better intergroup perceptions, especially during everyday interactions outside the lab.
@@
 % Proposal Paragraph:
-We propose that the key to understanding how an interaction is perceived is to examine the level of need fulfillment it provided to an individual.
+We propose that one key to understanding how an interaction is perceived is to examine the level of need fulfillment it provided to an individual.
 As an example, if someone seeks acceptance by their interaction partner, and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
-To test this, we collected three sets of real-life data from recent immigrants, assessing their daily interactions with majority group members, tracking situational needs, interaction quality, and outgroup attitudes.
+To test this proposal, we collected three sets of real-life data from recent immigrants, assessing their daily interactions with majority group members, tracking situational needs, interaction quality, well-being, and outgroup attitudes.
 
@@
 % neither are necessary nor explain why an interaction is positive
-Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
-It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for such positive contact effects \citep[][]{Allport1954b, Pettigrew1969}.
-However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be essential to finding positive effects of intergroup contact \citep[][]{Pettigrew2006}.
-It, thus, remains unclear when and why an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects\footnote{It should be noted here that following Allport's original conditions, several additional conditions of optimal contact were proposed \citep[for a critical discussion see][]{Pettigrew1986}.
-Similarly, since the early 21\textsuperscript{st} century many psychological processes during intergroup contact were examined \citep[e.g.
+\sout{Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.} When it comes to what constitutes a positive interaction the most widely used approach has been the idea that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact effect \citep[][]{Allport1954b, Pettigrew1969}.
+However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be necessary to finding positive effects of intergroup contact \citep[][]{Pettigrew2006}.
+Following Allport's original conditions, several additional conditions of optimal contact were proposed, which have largely received the same criticism of not capturing the underlying psychological mechanisms of why an interaction is perceived as positive \citep[for a critical discussion see][]{Pettigrew1986}.
+
+Instead, since the early 21\textsuperscript{st} century, researchers have assumed positive contact and have focused on the psychological processes that explain how positive contacts improve intergroup relations \citep[e.g.
 see,][]{Paolini2021}.
-Among others, researchers have explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and knowledge about the other group \citep[][]{Pettigrew2008c}.
-However, all these advances share the underlying criticism that they are not geared towards understanding when and why an interaction is perceived as positive.}.
-We propose that the literature on motivation and psychological needs may help us understand when and why exactly an interaction is perceived as positive.
+Among others, researchers have explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008}, as well as knowledge about the other group \citep[][]{Pettigrew2008c}.
+However, all these advances share a focus on understanding when and how \textit{positive interactions} improve intergroup relations.
+Understanding when and why an interaction is perceived as positive in the first place has remained a tangential focus and it, thus, remains largely unclear which psychological mechanisms drive positive interaction perceptions.
 
-% ALTERNATIVE: SHORTER BUT NOT FOCUSED ON ALLPORT'S CONDITIONS (WHICH WE TEST LATER)
-% Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
-Past research has either focused on conditions under which interactions tend to have favorable effects \citep[e.g., Allport's optimal conditions;][]{Allport1954b, Pettigrew1969} or has investigated cognitive-affective processes during contact \citep[e.g., group salience, intimacy, attachment, or intergroup anxiety;][]{Brown2005, Marinucci2021, Tropp2021, Paolini2004}.
-However, neither the contact conditions nor the cognitive-affective processes are particularly well-equipped to explain when and why an interaction will be perceived as positive.
-We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
+In this article, we focus on the underexplored role of motivation and need fulfillment to understand when and why exactly an interaction is perceived as positive.
+We propose need fulfillment in particular, because a need mechanism builds a strong body of literature highlighting the functional role of need fulfillment in psychosocial functioning, interactions, and intergroup relations --- all of which are fundamental considerations for intergroup contact.
 
-% Important in broader field: needs have been found to be important in broader intergroup relations and interpersonal contact literature.
-Although considerations of psychological needs and motivations have remained markedly absent within the intergroup contact literature, the concepts are in no way foreign to the broader topic of intergroup relations.
-Psychological needs have for example found fruitful utility in reconciliation research \citep[][]{Shnabel2008}, the study of minority's discrimination experiences \citep[][]{Celebi2017}, and in non-intergroup interactions \citep[][]{Downie2008}.
-% On the most general level, research on intergroup conflicts has, for example, shown that addressing the group-specific needs predicts willingness to reconcile with the other group \citep[][]{Shnabel2008}.
-For the case of refugee migrants in their relationship with a majority group, a recent study found that identity needs will buffer against discrimination experiences and will protect personal health \citep[][]{Celebi2017}.
-Additionally, within the field of interpersonal relations, we find first evidence that the fulfillment of fundamental psychological needs might predict perceived interaction quality in non-intergroup interactions \citep[][]{Downie2008}.
-% Promising for intergroup contact: Asked for in intergroup contact reviews and first research looked at social change
-Even within the field of intergroup contact, the idea of need fulfillment as a psychological mechanism is not entirely novel \citep[e.g.,][]{Dovidio2017}.
-First empirical research has even found psychological need fulfillment during intergroup contacts to predict support for social change \citep[][]{Hassler2021}.
-Considering need fulfillment during intergroup contact might therefore offer a promising psychological mechanism to understand perceived interaction quality and positive outgroup attitudes.
+On an individual psychological level, need fulfillment has a long tradition of explaining what drives human adaptation and social relations.
+From the early works of \citet[][]{maslow1943} and \citet[][]{lewin1926e} to more recent works by \citet[][]{Ryan2017} or \citet[][]{Steverink2006}, the fulfillment of needs have been considered a driver of health, well-being, and psychosocial functioning.
+Most relevant to our proposal here, within experience sampling studies (psychological) need fulfillment has been found to explain variations in general well-being \citep[e.g.,][]{sheldon1996, reis2000} as well as well-being during daily interactions \citep[][]{Downie2008}.
+The importance of need fulfillment in interactions has also been substantiated by frameworks such as 'relationships motivation theory', which has collected substantive evidence for the importance of need fulfillment in understanding the success of close relationships \citep[e.g., see][]{knee2023}.
+There is, thus, a wealth of literature highlighting the importance of need fulfillment to positive everyday experiences and well-being.
+
+Beyond the well-being and psychosocial functioning perspective, need fulfillment has recently also seen application as a psychological mechanism in the intergroup relations literature.
+Social identity theory has famously focused on the role of self-esteem needs in understanding how people navigate intergroup contexts \citep[e.g.,][]{abrams1988}.
+A more recent example is the study of conflict and reconciliation where addressing differential needs of victims and perpetrators (i.e., the need for power and the need for morality respectively) increased willingness to reconcile \citep[][]{Shnabel2008}.
+And similarly, addressing a relevant need for identity continuity among refugees in Turkey bolstered resilience in the face of discrimination experiences \citep[][]{Celebi2017}.
+Most recently, an international cross-sectional study has applied a need-based approach to the effects of positive intergroup contact.
+The study found that minority members who generally perceive their positive intergroup contacts to be more empowering tended to report a smaller reduction in social change support than those who did not perceive their average interactions as empowering, especially when the inequality between groups was perceived as illegitimate \citep[][]{Hassler2021}.
+In short, an increasing amount of literature is emphasizing the significance of need satisfaction in comprehending intergroup relations.
+
+It is thus not surprising that in their perspectives paper on intergroup contact, Dovidio and colleagues propose that: "To achieve truly constructive intergroup relations, it is important that intergroup exchanges meet the psychological needs of both majority- and minority-group members." \citep[][p.
+6]{Dovidio2017}.
+A call that has thus far remained unanswered when it comes to the basic tenet that positive interactions drive the constructive part of intergroup contact.
 
@@
 % MAYBE MOVE THIS TO 'The Present Research Section'
-One reason why motivational considerations might have remained absent from the intergroup contact literature is that there is an overwhelming number of individual needs or goals that might be relevant to a person during an intergroup interaction.
-Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad range of fundamental psychological needs.
-To avoid this predicament we propose to start by using adaptive and responsive survey designs that allow a tailored approach based on the participants' inputs \citep[e.g.,][]{Tourangeau2017}.
-In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., situation core need) and with reference to their own response, the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment).
-Such an adaptive approach allows us to take the initial step of testing whether situational psychological needs indeed generally predict perceived interaction quality and positive outgroup attitudes independent of need content.
+One reason why motivational considerations might have remained absent from the intergroup contact literature is that there is an overwhelming number of individual motives or goals that might be relevant to a person during an intergroup interaction.
+Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad and diverse range of motives.
+However, while the individual need content differed between the different lines of research, what unites these approaches has been a focus on fulfilling the situationally relevant needs of people --- especially when we want to understand human functioning in social realms.
+We propose that the different lines of research share an underlying psychological mechanism, namely the motivational experience of need fulfillment.
+With motivation and need fulfillment we specifically mean the psychological experience of addressing an active and relevant need during the interaction.
+For our purposes, we define a need as:
+
+\begin{definition}[Need]\label{def:need}
+A tension or deficiency in the organism that elicits a (non-specific) motivational force organizing affect, cognition, and behavior to reduce this unsatisfactory situation, which is to some extent necessary for the individual’s overall well-being.
+\begin{flushright}
+--- based on \citet[][]{dweck2017, Hull1943, Lewin1938, McClelland1987, Ryan2017, Steverink2006}
+\end{flushright}
+\end{definition}
+
+The psychological experience of need fulfillment is, thus, distinct from the content of the need (i.e., the motive or goal).
+The content could, for example, include physical motives (such as safety or hygiene) but also psychosocial motives \citep[such as acceptance or competence; e.g., see][]{pittman2007}.
+A need arises when a motive is thwarted or situationally active and relevant \citep[][]{leander2020, lewin1926e, gollwitzer1985e}.
+It is this perceived need and the perceived fulfillment of needs that we focus on in this article.
+This is not to say that considering specific motives is irrelevant to contact situations but instead we propose that the psychological experience of perceived need fulfillment is a core mechanism in understanding interaction quality perceptions, well-being, and outgroup attitudes.
+
+To test such a proposal we can rely on adaptive and responsive survey designs that allow a tailored approach based on the participants' inputs \citep[e.g.,][]{Tourangeau2017}.
+In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., name the situationally relevant need content), and with reference to their own response, the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment mechanism).
+Such an adaptive approach allows us to take the initial step of testing whether situational need fulfillment indeed generally predicts perceived interaction quality, well-being, and positive outgroup attitudes independent of need content.
 
@@
 While we have argued that a need fulfillment mechanism is relevant to intergroup contact generally, its flexible and broad applicability might be ideally suited to address the pressing issue of understanding natural intergroup contacts outside the lab.
-Investigations of such `real-life interactions' often suffer from the difficulty that past intergroup contact research has either focused on the mechanisms of individual interactions in artificial lab studies or has focused on longer-term recall self-reports of natural interactions \citep[e.g.,][]{Pettigrew2006}.
+Investigations of such `real-life interactions' often suffer from the difficulty that past intergroup contact research has either focused on the mechanisms of individual interactions in artificial lab studies (sometimes referred to as the intergroup interaction literature) or has focused on longer-term recall self-reports of natural interactions \citep[commonly referred to as the intergroup contact literature; also see][]{Pettigrew2006}.
+\citet[][]{MacInnis2015} have even pointed out that these two approaches tend to find conflicting effects --- where individual interactions (in the lab) have more negative effects and recall of real-world contact patterns have more positive effects for intergroup relations.
+We, thus, miss data that follows people in their diverse daily interactions and investigates the psychological mechanisms of contacts, especially as they compound over time.
 Even with extended intervention studies, the most fine-grained data available is usually limited to pre-post-control designs.
-Such empirical practices stand, however, in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the core idea of the contact hypothesis, which was focused on the daily interactions of people \citep[][]{Allport1954b}.
-As a result, within the intergroup contact field researchers have called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
+
+The lack of longitudinal real-world data, however, stands in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the original contact hypothesis, which was focused on the daily interactions of people \citep[][]{Allport1954b}.
+As a result, prominent researchers in the field have long called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
 Such data would be able to capture real-life interactions that include interaction-specific mechanism information close to the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
-Moreover, because data is nested within participants, experience-sampling data often allows capturing large amounts of high-quality data with relatively few participants.}.
+Moreover, because data is nested within participants, experience-sampling data often allows capturing large amounts of high-quality data with relatively few participants \citep[][]{shiffman2008}.}.
 
@@
 We can test whether having an interaction vs.
-not having an interaction impacts outgroup attitudes, but we can also use the participant's 30-day contact reports to test whether participants with more positive interactions tend to have more positive outgroup attitudes.
+not having an interaction improves intergroup relations, but we can also use the participant's 30-day contact reports to test whether participants with more positive interactions tend to benefit more from intergroup contact.
 Testing both approaches to the contact hypothesis allows us to go beyond a replication of the basic theory but could disentangle individual- from aggregated contact effects and would allow for a direct comparison with both bodies of literature.
-We will test the effect of individual interactions within each study using a multilevel model, but to avoid power limitations, we will test the collective effect of contact frequency and -quality after the individual studies, across all participants.
+
+A second key decision was our choice to focus on the minority experience during the contact.
+While the same mechanisms should hold for the experience of members in high-powered groups, there is substantially more research available that focuses on the experience of the majority group, and minority perspectives are historically often understudied \citep[e.g.,][]{Dovidio2017}.
+At the same time, however, minority groups are often underprivileged and research is direly needed to understand the more prevalent experiences of stress and health issues among minorities \citep[e.g.,][]{alvidrez2019}.
+
+A third and final non-trivial aspect of translating the intergroup contact hypothesis into extensive real-world data was the choice of the outcome variable.
+For our main analyses, we chose outgroup attitudes --- the positive or negative evaluation of the other group.
+We chose outgroup attitudes mainly because they are the most common outcome considered within the intergroup contact literature \citep[e.g.,][]{Pettigrew2006, Paolini2021}.
+As the methodology is relatively new to the field, we sought to first replicate (and then extend) the most reliable effects of the contact hypothesis within the ESM data.
+Outgroup attitudes are, however, not without controversy, especially for minority group members' intergroup contact.
+In particular, positive outgroup attitudes have been shown to increase harmony and reduce the willingness to support social change among the disadvantaged in some cases --- even in the face of injustice \citep[e.g.,][]{dixon2012, saguy2009}.
+While a recent review found the effect to be less conclusive for longitudinally collected data and less consistent for positive interactions (rather than interactions generally), the backfire effect remains an important possibility for the present data \citep[see][]{reimer2023}.
+In order to ensure at least a direct benefit to the minority group members, we also assess the effect of the need fulfillment mechanism on well-being as the dependent variable as part of our robustness analyses below.
+
+With these important considerations in mind, we test the basic contact hypothesis within and across the three studies.
+In particular, we assess the effect of individual interactions within each study using a multilevel model, but to avoid power limitations, we test the collective effect of contact frequency and -quality after the individual studies, across all participants.
 \begin{enumerate}[leftmargin=1.5\parindent]
@@
 
-Our second main aim is to test our main theoretical proposal that the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
+Once the general contact hypothesis is established within the ESM data, our second main aim is to test our main theoretical proposal that the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
 As our main proposal is concerned with the mechanisms of successful intergroup contact, we again focus on outgroup interaction reports.
@@
 Our third aim is to ensure that our results are robust, stable, and ecologically valid.
-To test the robustness of our need-based mechanism we test whether the need mechanism is indeed specific to outgroup interactions and whether the process could be explained by a smaller set of fundamental needs instead.
+To test the robustness of our need-fulfillment mechanism we test whether the need mechanism is indeed specific to outgroup interactions and whether the process could be explained by a smaller set of fundamental psychological needs instead.
+We additionally, assess the need fulfillment mechanism in predicting individual well-being benefits and check whether different types of needs or interactions change the main results.
 We present the full robustness analyses in \appref{app:AppendixRobustness}.
@@
 This approach is tolerant to missing data and uneven case numbers within participants.
-Furthermore, we use a hierarchical modeling approach and report the final model in-text \citep[][; for the full modeling process see Supplementary Material A]{Snijders2012}.
+Furthermore, we use a hierarchical modeling approach and report the final model in-text \citep[][; for the full modeling process see Supplementary Material A]{snijders2012}.
 Secondly, statistical power estimations for intensive longitudinal- and multilevel models are notoriously difficult due to the complex covariance structures.
-However, our participant- and measurement numbers are within the highest percentiles of sample sizes found within the broader intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
-Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes.
+However, our participant- and measurement numbers are among the largest sample sizes found within the intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
+Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes (see Supplemental Material A).
 The sample sizes were only increased to allow for between-subjects comparisons and future, more complicated, time-series modeling.
@@
 % aims re-iterated
-The main aim of this project was to test the basic tenets of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data and to test whether the fulfillment of situational psychological needs meaningfully predicts positive interaction perceptions and outgroup attitudes.
+The main aim of this project was to test the basic tenets of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data and to test whether the fulfillment of situational needs meaningfully predicts positive interaction perceptions, well-being, and outgroup attitudes.
 
@@
 Surprisingly, here we found independent effects of interaction frequency and average interaction quality ratings but no interaction effect.
-The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations)\footnote{It should be noted that such inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).}.
+The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
+
+Interestingly, this effect is also inconsistent with the observations and theorizing of \citet[][]{MacInnis2015}, who observed that individual interactions showed negative effects on intergroup relations and the aggregate of past intergroup contacts showed positive effects on intergroup relations.
+There are, however, two important differences in our data compared to the past literature assessed by \citeauthor{MacInnis2015}.
+Firstly, what \citeauthor{MacInnis2015} called the intergroup interaction literature, has particularly focused on artificial lab studies where study participants meet a stranger from the outgroup.
+In our real-world data, such synthetic and controlled interactions are arguably less relevant.
+Secondly, what \citeauthor{MacInnis2015} called the intergroup contact literature, has looked at long-term recall self-reports --- where participants are asked to recall the quantity and average quality of intergroup contacts over the past month or year \citep{MacInnis2015}.
+The mental aggregation of such long-term recall surveys is substantially different from the aggregation we did based on the close-to-event reports \citep[][]{shiffman2008}.
+To truly compare our results to \citet[][]{MacInnis2015} theorizing, future studies should, thus, also collect a long-term recall report that mirrors the questions asked during intergroup contact studies.
+
+It should, however, be noted that the inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
+There is also a possibility that statistical power was a concern given our sample was relatively small with 207 participants and the effect of interest is an amplification interaction effect.
+However, if we assume an effect size of \textit{r} = -.21 for the effect of positive intergroup contacts \citep[see][]{Pettigrew2006} our sample size should approach the threshold of 80\% power at a .05 alpha level (sensitivity analysis in G*Power: $f^2 = 0.04$) --- especially if we consider the higher quality data we get from aggregating many real-world reports with less recall bias.
 
 % Allport's conditions in ESM data [consistent predictor and partially through quality]
-Using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
-When we consider interaction quality and Allport's conditions jointly, we find that the positive effect of Allport's conditions might in part be explained by more positive interaction quality ratings.
+Next, using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
+When we consider interaction quality and Allport's conditions jointly, we find that interaction quality ratings assumed a larger part of the shared variance in outgroup attitudes.
 We thus find first evidence that Allport's conditions of optimal contact are also relevant to the daily interactions recent migrants have in their interactions with majority group members.
@@
 % Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
-We find that in all three studies the effect of core need fulfillment on outgroup attitudes could either fully or partially be explained by its effect on interaction quality.
+Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions, more positive outgroup attitudes, as well as \hl{higher well-being}.
+We find that in all three studies the effect of core need fulfillment on outgroup attitudes was either fully or partially assumed by the effect of interaction quality (when considering partial regression coefficients in a joint model).
 We also find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
-In fact, our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance than commonly measured psychological needs.
+In fact, our core situational needs measure predicted outgroup attitudes at least as good as Allport's conditions and consistently explained more variance than commonly measured psychological needs.
 In most cases, the core need even took over the variances previously explained by the self-determination theory needs (see \appref{app:AppendixRobustness}).
-We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction-specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
+We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction-specific needs are fulfilled offers a meaningful and flexible predictor of interaction quality, outgroup attitudes, and well-being.
 
@@
 % (1) Sample = minority and (voluntary) migrants, (2) Methodology = short scales (reliability) and no lagged effects, (3) Core Need Concept = non-specific
-While we believe that a need-based mechanism should be relevant to any inter-group contact, our samples focused on a minority- and (voluntary) migrant perspective.
+While we believe that a need fulfillment mechanism should be relevant to any inter-group contact, our samples focused on a minority- and (voluntary) migrant perspective.
 Without additional evidence it thus remains difficult to judge whether motivational effects will generalize to other migrant groups (e.g., forced migrants), other intergroup contexts (e.g., gender-, religious-, or sexual orientation groups), or to majority groups and their outgroup attitudes.
-We know of no research suggesting that in other contexts psychological needs are irrelevant (once existential needs are met) but future research may extend our findings to build an even broader understanding of psychological needs in intergroup contacts.
+We sought to replicate our results in three studies with different types of migrants but the fact remains that all three studies had slightly more women than men participating and were younger and more educated samples overall.
+While the samples were representative of the migrant group to the focus region, the generalizability of the sample is restricted by its characteristics.
+We know of no research suggesting that in other contexts need fulfillment would be less relevant but future research may extend our findings to build an even broader understanding of need fulfillment in intergroup contacts.
+Researchers may even seek to explore the role of need fulfillment in real-world interactions more broadly \citep[also see][]{Downie2008}.
 
@@
 
+A third limitation lies in the outcome variable we chose.
+As we have focused on outgroup attitudes to ensure comparability to the past literature of the contact hypothesis and to replicate the most reliable patterns within ESM data \citep[][]{pettigrew2006}.
+However, especially for disadvantaged minority members positive outgroup attitudes may entail negative downstream consequences such as a reduced endorsement of social change --- even in the face of injustice \citep[e.g.,][]{dixon2012}.
+We have additionally tested our need-fulfillment mechanism for well-being reporst to test direct benefits of the mechanism to lived realities.
+However, we are among the first to collect intensive longitudinal data on the experience of minority migrants and it remains an open empirical question whether the more positive outgroup attitudes following need-fulfilling interactions might ironically exacerbate inequalities for the disadvantaged group.
+
 Finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
-This comes at the expense of specificity in the situational needs (i.e., we have not explored whether different types of needs have stronger effects on interaction quality and outgroup attitudes).
+This comes at the expense of specificity in the situational motives (i.e., we have not explored whether different types of needs have stronger effects on interaction quality and outgroup attitudes).
 Such an investigation would be possible with the adaptive measurement we used (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
@@
 Psychological needs are a facet of the human experience that has thus far been underemphasized in the intergroup contact literature.
-This stands in stark contrast of the many cognitive \citep[e.g.,][]{Pettigrew1998, Brown2005} and emotional aspects investigated within the field \citep[e.g.,][]{Stephan2008, Paolini2004}.
+This stands in stark contrast of the many cognitive \citep[e.g.,][]{Pettigrew1998, Brown2005} and emotional aspects investigated within the field \citep[e.g.,][]{Stephan2008}.
 Future research may, therefore, be able to integrate broader theoretical frameworks of intergroup contact (e.g., motivations guiding cognition and affect, which in turn drive behavior.

### 2023-05-16 Supplemental Material B - Coding Protocol/Supplemental Material B - Coding Protocol.tex
:tada: coding protocol template added

\documentclass[10pt,a4paper]{protocol}

% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{tcolorbox}
\usepackage[style=apa, sortcites=true, sorting=nyt, backend=biber, natbib=true, uniquename=false, uniquelist=false, useprefix=true]{biblatex}
\usepackage{authblk}
\usepackage{setspace,caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{fourier}
\usepackage{stackengine}
\usepackage{scalerel}
\usepackage{fontawesome}
\usepackage[normalem]{ulem}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{afterpage}
\usepackage{float}
\usepackage{titling}
\usepackage{censor}
\usepackage{pdfpages}
\usepackage{bashful}
% needed for the fact box label
\usepackage{xparse}
% this allows for the easy resize box
\usepackage{graphicx}

\tcbuselibrary{skins,breakable}
\usetikzlibrary{shadings,shadows}

% Turn on the style
\pagestyle{fancy}
\fancyhead{}
\fancyfoot{}

\fancyfoot[C]{%
    \vspace{-3em}
    \makebox[19cm][c]{%
        \thepage}
    }
\renewcommand{\headrulewidth}{0pt}

% If using xelatex or lualatex:
% \setmainfont{Lato}

\hypersetup{
    colorlinks=true,
    urlcolor=blue
}

% These commands create shortcuts for the nutrition label
% Modified from: https://tex.stackexchange.com/questions/118600/how-can-i-create-a-nutrition-facts-label
\newlength{\NFwidth}
\setlength{\NFwidth}{4.5in}

\NewDocumentCommand{\NFelement}{mmm}{\normalsize\textbf{#1} #2\hfill #3}
\NewDocumentCommand{\NFline}{O{l}m}{\footnotesize\makebox[\NFwidth][#1]{#2}}

\NewDocumentCommand{\NFentry}{sm}{%
  \makebox[.5\NFwidth][l]{\normalsize
    \IfBooleanT{#1}{\makebox[0pt][r]{\textbullet\ }}%
    #2}\ignorespaces}
\NewDocumentCommand{\NFtext}{+m}
 {\parbox{\NFwidth}{\raggedright#1}}

\newcommand{\NFtitle}{\multicolumn{1}{c}{\huge\bfseries Dataset Sheet}}

\newcommand{\NFRULE}{\midrule[5pt]}
\newcommand{\NFRule}{\midrule[2pt]}
\newcommand{\NFrule}{\midrule}

% Change the colours if you want to
\definecolor{Bright}{HTML}{58318f}
\definecolor{Green}{HTML}{319866}
\definecolor{Black}{HTML}{111111}
\definecolor{LightGrey}{HTML}{515c50}
\colorlet{heading}{MidnightBlue}
\colorlet{accent}{NavyBlue}
\colorlet{emphasis}{Black}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \risk if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faSpinner}

% add freetext option
\newlength{\rulewidth}
\setlength{\rulewidth}{1pt}
\newlength{\ruleandnamegap}
\setlength{\ruleandnamegap}{.4\baselineskip}
\newcommand{\namefont}{\tiny}
\newcommand{\ruleandname}[2]{%
  \par\noindent
  \rule{#2}{\rulewidth}\par
  \vspace{\dimexpr-\baselineskip+\ruleandnamegap}
  \noindent{\namefont #1}\par
  \addvspace{\baselineskip}
}
\newcommand{\rulewithattribute}[3][-.1\baselineskip]{%
  \par\noindent
  \rule[#1]{1cm}{\rulewidth} #2 \rule[#1]{#3}{\rulewidth}\par
  \vspace{\dimexpr-\baselineskip-#1+\ruleandnamegap}
  \noindent{\namefont Score}\par
  \addvspace{\baselineskip}
}

\newcommand\category[2]{
{\Large\bfseries\color{emphasis} \vspace{0.25em} #1 \hspace{0.5em} #2 \\ [-0.6em] \rule{\textwidth}{0.4pt} \vspace{0.25em}}
}

% box
\newenvironment{myblock}[1]{%
    \tcolorbox[beamer,%
    noparskip,breakable,
    colback=LightBlue,colframe=DarkBlue,%
    colbacklower=DarkBlue!75!LightBlue,%
    title=#1]}%
    {\endtcolorbox}

\newtcolorbox{topbot}[1][]{empty, notitle, sharp corners, 
borderline north={1pt}{0pt}{black},
borderline east={1pt}{0pt}{black},
borderline south={1pt}{0pt}{black},
borderline west={5pt}{0pt}{black},
#1}

%% links.bib contains references
\addbibresource{links.bib}

% create PDF of title page
\immediate\write18{pdflatex CodingProtocolTitlePage}

\begin{document}

% fix page numbering with title page
\setcounter{page}{0}

\includepdf{CodingProtocolTitlePage.pdf}

\name{Documentation: \par Coding Protocol}
\tagline{For: `The Migration Experience: A Conceptual Framework and Systematic Scoping Review of Psychological Acculturation'}
\made{February 20 2021}
%%\logo{6.8cm}{images/MJ Research Design}
%%\logo{6.8cm}{example-image}
\logo{6.8cm}{images/rugLogoBlack}
%\logo{6.8cm}{images/rugLogoBlackMasked}

\docinfo{%
  % can add more \addedtopeople
  \madeby{Jannis Kreienkamp}{j.kreienkamp@rug.nl}{February 20, 2021}
  \addedto{Laura F. Bringmann}
  \addedto{Raili F. Engler}
  \addedto{Peter de Jonge}
  \addedto{Kai Epstude}
  %\madeby{[masked for peer review]}{[masked for peer review]}{February 20, 2021}
  %\addedto{[masked for peer review]}
  %\addedto{[masked for peer review]}
  %\addedto{[masked for peer review]}
  %\addedto{[masked for peer review]}
}

\purpose{
	This protocol document lays out detailed information for coders of the (included) manuscripts. This document serves as an instructive manual to the coders and documents the operationalizations of the coded variables. The systematic review produced three literature databases that aim to capture the status quo of the (1) theoretical, (2) methodological, and (3) empirical literature on psychological acculturation. The coding procedures (i.e., data extraction) for each dataset are documented in the following document protocol.
} % add a short description of the purpose for this protocol

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makeheader
\end{fullwidth}

%% Provide the file name containing the sidebar contents as an optional parameter to \need.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \need title in the "main" bar.
\need[margins/materials]{Theoretical Literature}

\category{1}{Bibliographic Information}

\step{Theory}{What is the name of the theory?}{Bibliographic Information}
\textit{Whenever possible record the name of the theory chosen by the authors themselves.}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\step{Source}{Add the full APA 7 formatted citation of the theoretical manuscript that is being coded.}{Bibliographic Information}
\textit{Example format: Author, A. A., \& Author, B. B. (Year). Title of the work. Source where you can retrieve the work. DOI (or URL) if available.}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\step{CitationKey}{Add BibTeX citation key for the theoretical manuscript.}{Bibliographic Information}
\textit{The citation key can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
\textit{\newline Example format: Author2019}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\clearpage
\vspace*{1em}

\category{2}{Screening}

\step{MissingABCD}{Whether the experience aspects (affect, behavior, cognition, and desire) are coded.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{coded \dotfill[0]}
	\item \makebox[5cm]{missing \dotfill[1]}
\end{itemize}
\divider

\marginpar{
\vspace{2em}
Missingness Explanations

\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
>{\raggedright\arraybackslash}p{0.75\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
1 & manuscript is in a language other than English. \\
2 & rural-urban, second generation \\
3 & focus on dominant group \\
4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
5 & migration status, length of residence  \\
6 & only discusses theory of others. \\
7 & not accessible via library services \\
8 & not accessible via library services \\
9 & not accessible via library services \\
10 & not accessible via library services \\
11 & not accessible via library services \\
\bottomrule
\end{tabular*}
}

\divider
\step{NoteMissing}{If experience aspects (affect, behavior, cognition, desire) not coded, provide the reason for missing coding.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{not English \dotfill[1]}
	\item \makebox[5cm]{not migration \dotfill[2]}
	\item \makebox[5cm]{not migrant \dotfill[3]}
	\item \makebox[5cm]{not acculturation \dotfill[4]}
	\item \makebox[5cm]{not ABCD \dotfill[5]}
	\item \makebox[5cm]{not theory \dotfill[6]}
	\item \makebox[5cm]{thesis not accessible \dotfill[7]}
	\item \makebox[5cm]{article not accessible \dotfill[8]}
	\item \makebox[5cm]{book not accessible \dotfill[9]}
	\item \makebox[5cm]{chapter not accessible \dotfill[10]}
	\item \makebox[5cm]{poster not accessible \dotfill[11]}
\end{itemize}
\divider

\step{Comment}{Any necessary comments of the coder.}{Screening}
\textit{This can include additional information about the format and content of the theoretical work, as well as information on the missingness or accessibility.}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\category{3}{Theory Information}

\step{Summary}{A short summary of the theoretical work.}{Theory Information}
\textit{This summary ideally includes the sections that were relevant to the experience aspect (affect, behavior, cognition, desire) coding.}
\vspace{1.5em}

\rule{10cm}{\rulewidth}\vspace{0.75em}
\rule{10cm}{\rulewidth}\vspace{0.75em}
\rule{10cm}{\rulewidth}\vspace{0.75em}
\ruleandname{character string}{10cm}
\divider

\clearpage
\vspace*{2em}

\step{FrameworkTheoryModel}{Type of theoretical work, as identified by the author.}{Theory Information}
\textit{Please code the term that is being used by the author(s).}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{conceptualization \dotfill[1]}
	\item \makebox[5cm]{framework \dotfill[2]}
	\item \makebox[5cm]{theory \dotfill[3]}
	\item \makebox[5cm]{model \dotfill[4]}
\end{itemize}
\divider

\step{GeneralAspect}{Whether the theoretical work is about acculturation in general or whether it conceptualizes a particular aspect of acculturation.}{Theory Information}
\textit{Is acculturation in general being considered or do the authors focus on a single aspect of acculturation, such as theories on labor market integration.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{general \dotfill[1]}
	\item \makebox[5cm]{aspect \dotfill[2]}
\end{itemize}
\divider

\step{Target}{If aspect is targeted, what is the target of the theoretical work?}{Theory Information}
\textit{Example aspects might be theoretical works that exclusively focus on labor market integration or identity development.}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\category{4}{Experience}
\marginpar{
\vspace{3em}
Selected Affect Concept Examples:
\begin{itemize}
    \item loneliness
    \item feeling at home
    \item satisfaction with life
    \item pride
    \item comfortableness
    \item joy
    \item ease
    \item well-being
    \item worry
    \item trust
\end{itemize}
}

\step{Affect}{Whether the theoretical conceptualization included affect.}{Experience}
\textit{To identify whether the author(s) included affective experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of affect. Please consider affect at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `affect' or `affective' directly.\\
\textbf{Construct:} the authors might refer to affective constructs such as `emotion' or `mood'.\\
\textbf{Concept:} the authors might refer to affective concepts such as individual emotions, including `pride' or `loneliness'.\\
\textbf{Operationalization:} the authors might also include affective conceptualizations in their descriptions of experiences, such as `a person feels' or `a person enjoys'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\marginpar{
\vspace{3em}
Selected Behavior Concept Examples:
\begin{itemize}
    \item language use
    \item civic participation (voting, ...)
    \item performance (work, ...)
    \item media consumption
    \item education
    \item peer contacts
    \item food consumption
    \item cultural habits (holidays ...)
    \item delinquency
    \item marriage
\end{itemize}
}

\step{Behavior}{Whether the theoretical conceptualization included behavior(s).}{Experience}
\textit{To identify whether the author(s) included behavioral experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of behaviors. Please consider behaviors at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `behavior' or `behavioral' directly.\\
\textbf{Construct:} the authors might refer to behavioral constructs such as `activities' or `habits'.\\
\textbf{Concept:} the authors might refer to behavioral concepts, such as `language use' or `media consumption'.\\
\textbf{Operationalization:} the authors might also include behavioral conceptualizations in their descriptions of experiences, such as `a person does' or `a person works'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{3em}
Selected Cognition Concept Examples:
\begin{itemize}
    \item ethnic identification
    \item cultural values
    \item acculturation orientation
    \item preferences (food, friends, ...)
    \item knowledge
    \item importance ratings
    \item inner thought language
    \item perceived obligations
    \item beliefs
    \item stereotypes
\end{itemize}
}

\step{Cognition}{Whether the theoretical conceptualization included cognition(s).}{Experience}
\textit{To identify whether the author(s) included cognitive experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of cognitions. Please consider cognitions at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `cognition' or `cognitive' directly.\\
\textbf{Construct:} the authors might refer to cognitive constructs such as `knowledge' or `memories'.\\
\textbf{Concept:} the authors might refer to cognitive concepts, such as `cultural values' or `ethnic identification'.\\
\textbf{Operationalization:} the authors might also include cognitive conceptualizations in their descriptions of experiences, such as `a person thinks' or `a person prefers'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{3em}
Selected Desire Concept Examples:
\begin{itemize}
    \item competence
    \item independence
    \item self-coherence
    \item belonging
    \item achievement
    \item justice
    \item growth
    \item respect
    \item acceptance
    \item identity continuity
\end{itemize}
}

\step{Desire}{Whether the theoretical conceptualization included desire(s).}{Experience}
\textit{To identify whether the author(s) included motivational experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of desires. Please consider desires at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `desire' or `motivational' directly.\\
\textbf{Construct:} the authors might refer to desire constructs such as `needs' or `goals'.\\
\textbf{Concept:} the authors might refer to desire concepts, such as `belonging' or `competence'.\\
\textbf{Operationalization:} the authors might also include motivational conceptualizations in their descriptions of experiences, such as `a person wants' or `a person needs'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\category{5}{Data Collection}

\step{SourceType}{Whether the theoretical conceptualization is based on theoretical reasoning or empirical investigations.}{Data Collection}
\textit{Is the theoretical reasoning focused on past theoretical work or do the authors build a theoretical conceptualization based on (qualitative) investigations (e.g., grounded theory).}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{theoretical \dotfill[1]}
	\item \makebox[5cm]{empirical \dotfill[2]}
\end{itemize}
\divider

\category{6}{Focus}

\step{Time}{Whether the conceptualization of acculturation is dynamic or static.}{Focus}
\textit{Do the authors self-identify the theory as a dynamic process (e.g., `process,' `development,' `longitudinal,' `temporal,' `dynamic') or a static outcome (e.g., `static,' `outcome,' `markers,' `consequence')}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{static \dotfill[1]}
	\item \makebox[5cm]{dynamic \dotfill[2]}
\end{itemize}
\divider

\marginpar{
\need{Methods Dataset}
\resizebox{7cm}{!}{
    % For organization, I like to keep the actual card in a separate file:
    \input{Supplemental Material A - Coding Protocol/margins/FactSheetMethodological}
    }
}
\need{Methodological Literature}
\category{1}{Bibliographic Information}

\step{Scale}{What is the name of the scale?}{Bibliographic Information}
\textit{Whenever possible record the name of the scale chosen by the authors themselves.}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\step{Source}{Whether the scale was added as part of one of the past methodological reviews or through our own review of the empirical literature.}{Bibliographic Information}
\textit{Indicate whether the scale was included in one or multiple of the past methodological reviews or was added from our own review.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{Celenk2011 \dotfill[1]}
	\item \makebox[5cm]{Matsudaira2006 \dotfill[2]}
	\item \makebox[5cm]{Wallace2010 \dotfill[3]}
	\item \makebox[5cm]{own review \dotfill[4]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\step{CitationKey}{Add BibTeX citation key for the theoretical manuscript.}{Bibliographic Information}
\textit{The citation key can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
\textit{\newline Example format: Author2019}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\step{APACite}{Add the full APA 7 formatted citation of the theoretical manuscript that is being coded.}{Bibliographic Information.}
\textit{Example format: Author, A. A., \& Author, B. B. (Year). Title of the work. Source where you can retrieve the work. DOI (or URL) if available.}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\step{DOI}{Add Digial Object Identifier (DOI).}{Bibliographic Information}
\textit{The doi can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
\textit{\newline Example format: 10.prefix/suffix}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\category{2}{Screening}

\step{Coded}{Whether the experience aspects (affect, behavior, cognition, and desire) are coded.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{missing \dotfill[0]}
	\item \makebox[5cm]{coded \dotfill[1]}
\end{itemize}
\divider

\marginpar{
\vspace{1.4em}
Missingness Explanations

\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
>{\raggedright\arraybackslash}p{0.75\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
1 & manuscript is in a language other than English. \\
2 & rural-urban, second generation \\
3 & focus on dominant group \\
4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
5 & migration status, length of residence  \\
6 & only discusses theory of others. \\
7 & not accessible via library services \\
8 & not accessible via library services \\
9 & not accessible via library services \\
10 & not accessible via library services \\
11 & not accessible via library services \\
12 & not accessible via library services \\
\bottomrule
\end{tabular*}
}

\divider
\step{MissingNote}{If experience aspects (affect, behavior, cognition, desire) not coded, provide the reason for missing coding.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{not English \dotfill[1]}
	\item \makebox[5cm]{not migration \dotfill[2]}
	\item \makebox[5cm]{not migrant \dotfill[3]}
	\item \makebox[5cm]{not acculturation \dotfill[4]}
	\item \makebox[5cm]{not ABCD \dotfill[5]}
	\item \makebox[5cm]{not measured \dotfill[6]}
	\item \makebox[5cm]{items not accessible \dotfill[7]}
	\item \makebox[5cm]{thesis not accessible \dotfill[8]}
	\item \makebox[5cm]{article not accessible \dotfill[9]}
	\item \makebox[5cm]{book not accessible \dotfill[10]}
	\item \makebox[5cm]{chapter not accessible \dotfill[11]}
	\item \makebox[5cm]{poster not accessible \dotfill[12]}
\end{itemize}
\divider

\step{Comment}{Any necessary comments by the coder.}{Screening}
\textit{This can include additional information about the format and content of the theoretical work, as well as information on the missingness or accessibility.}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\category{3}{Scale Information}

\step{Item}{Extract all available items of the scale.}{Scale Information}
\textit{List all items of the scale as they are presented in the manuscript. If scoring is inconsistent consider adding basic scoring information to the items. Please number the items for clarity.}
\vspace{1.5em}
\par
\hspace*{1pt}1. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}2. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}3. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}4. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}5. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}6. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}7. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}8. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}9. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}... .\\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}\textit{N}.\\\rule[0.95em]{6cm}{\rulewidth}\\
\vspace{\dimexpr-\baselineskip-\ruleandnamegap}
\noindent{\namefont character string}\par
\divider

\step{NItem}{Number of items in the scale.}{Scale Information}
\textit{The total number of items should match the highest numbering in the `Item' variable. If that is not the case please explain in the `Note' section.}
\vspace{1.5em}
\par
\rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \par
\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
\noindent{\namefont numeric}\par
\divider

\step{NSubScales}{Number of sub-scales identified by the authors.}{Scale Information}
\textit{If multiple sets of sub-scales are proposed please elaborate in the `Note' section.}
\vspace{1.5em}
\par
\rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \par
\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
\noindent{\namefont numeric}\par
\divider

\clearpage
\vspace*{2em}

\step{ResponseRange}{Number of response options.}{Scale Information}
\textit{If multiple response ranges are used please specify in the `Note' section.}
\vspace{1.5em}
\par
\rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \par
\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
\noindent{\namefont numeric}\par
\divider

\step{ResponseRangeAnchors}{List the anchors associated with the reported the response range.}{Scale Information}
\textit{If multiple sets of anchors are used please specify in the `Note' section.\\ Example format for range \{-2, 2\}:}
\vspace{1.5em}
\par
\hspace*{1pt}\textit{\textcolor{body}{-2: very negative}}\\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}\textit{\textcolor{body}{-1: negative}}\\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{4pt}\textit{\textcolor{body}{0: neutral}}\\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{4pt}\textit{\textcolor{body}{1: positive}}\\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{4pt}\textit{\textcolor{body}{2: very positive}}\\\rule[0.95em]{6cm}{\rulewidth}\\
\vspace{\dimexpr-\baselineskip-\ruleandnamegap}
\noindent{\namefont character string}\par
\divider

\step{Note}{Any necessary coder comments about the scale.}{Scale Information}
\textit{Any notes on the scale, including the structure of the scale (e.g., names of the sub-scales).}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\category{4}{Experience}
\marginpar{
\vspace{3em}
Selected Affect Concept Examples:
\begin{itemize}
    \item loneliness
    \item feeling at home
    \item satisfaction with life
    \item pride
    \item comfortableness
    \item joy
    \item ease
    \item well-being
    \item worry
    \item trust
\end{itemize}
}

\step{Affect}{Whether the scale includes affect.}{Experience}
\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of affect. Please consider affect at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `affect' or `affective' directly.\\
\textbf{Construct:} the authors might refer to affective constructs such as `emotion' or `mood'.\\
\textbf{Concept:} the authors might refer to affective concepts such as individual emotions, including `pride' or `loneliness'.\\
\textbf{Operationalization:} the authors might also include affective conceptualizations in their items, such as `I feel ...' or `I enjoy ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\marginpar{
\vspace{3em}
Selected Behavior Concept Examples:
\begin{itemize}
    \item language use
    \item civic participation (voting, ...)
    \item performance (work, ...)
    \item media consumption
    \item education
    \item peer contacts
    \item food consumption
    \item cultural habits (holidays ...)
    \item delinquency
    \item marriage
\end{itemize}
}

\step{Behavior}{Whether the scale includes behavior(s).}{Experience}
\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of behaviors. Please consider behaviors at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `behavior' or `behavioral' directly.\\
\textbf{Construct:} the authors might refer to behavioral constructs such as `activities' or `habits'.\\
\textbf{Concept:} the authors might refer to behavioral concepts, such as `language use' or `media consumption'.\\
\textbf{Operationalization:} the authors might also include behavioral conceptualizations in their items, such as `I do ...' or `I speak ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{3em}
Selected Cognition Concept Examples:
\begin{itemize}
    \item ethnic identification
    \item cultural values
    \item acculturation orientation
    \item preferences (food, friends, ...)
    \item knowledge
    \item importance ratings
    \item inner thought language
    \item perceived obligations
    \item beliefs
    \item stereotypes
\end{itemize}
}

\step{Cognition}{Whether the scale includes cognition(s).}{Experience}
\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of cognitions. Please consider cognitions at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `cognition' or `cognitive' directly.\\
\textbf{Construct:} the authors might refer to cognitive constructs such as `knowledge' or `memories'.\\
\textbf{Concept:} the authors might refer to cognitive concepts, such as `cultural values' or `ethnic identification'.\\
\textbf{Operationalization:} the authors might also include cognitive conceptualizations in their items, such as `I think ...' or `I prefer ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{3em}
Selected Desire Concept Examples:
\begin{itemize}
    \item competence
    \item independence
    \item self-coherence
    \item belonging
    \item achievement
    \item justice
    \item growth
    \item respect
    \item acceptance
    \item identity continuity
\end{itemize}
}

\step{Desire}{Whether the scale includes desire(s).}{Experience}
\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of desires. Please consider desires at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `desire' or `motivational' directly.\\
\textbf{Construct:} the authors might refer to desire constructs such as `needs' or `goals'.\\
\textbf{Concept:} the authors might refer to desire concepts, such as `belonging' or `competence'.\\
\textbf{Operationalization:} the authors might also include motivational conceptualizations in their items, such as `I want ...' or `I need ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\marginpar{
\vspace{1em}
Complexity Explanations

\begin{tabular*}{6.2cm}{>{\centering\arraybackslash}p{0.08\linewidth} 
>{\raggedright\arraybackslash}p{0.76\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
1 & focused on a concept that includes multiple aspects (e.g., satisfaction, distress) \\
2 & aspects included as parts of a scale \\
3 & aspects measured as independent conceptualizations of acculturation \\
4 & aspects included as part of a review of multiple conceptualizations \\
N/A & only one aspect was included  \\
\bottomrule
\end{tabular*}
}

\step{TypeComplexity}{Type of aspect combination [if multiple experience aspects included].}{Experience}
\textit{If more than one experience aspect was coded, please specify how the multiple aspects were included. The scales might include the aspects either independently as parts of the acculturation conceptualization or as part of a scale or proxy measure that includes multiple experience aspects.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{complex concept \dotfill[1]}
	\item \makebox[5cm]{complex scale \dotfill[2]}
	\item \makebox[5cm]{independent \dotfill[3]}
	\item \makebox[5cm]{review \dotfill[4]}
	\item \makebox[5cm]{not applicable \dotfill[N/A]}
\end{itemize}
\divider

\category{5}{Data Collection}

\step{Measurement}{Levels of measurement.}{Data Collection}
\textit{Identify the measurement level of the scales. Are the items (or at least the resulting scale) measured as a continuous dimension or is the resulting measure a classification into groups. Indicate `categorical' even if there is an order to the groups. Select `both' if a the measure includes both continuous and categorical measures.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{continuous \dotfill[1]}
	\item \makebox[5cm]{categorical \dotfill[2]}
	\item \makebox[5cm]{both \dotfill[3]}
\end{itemize}
\divider

\category{6}{Focus}

\step{domainScale}{Situational focus of the scale.}{Focus}
\textit{To identify the author(s) situational focus in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of life domains.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[6cm]{spirituality/religion \dotfill[1]}
    \item \makebox[6cm]{home/family \dotfill[2]}
    \item \makebox[6cm]{health/care \dotfill[3]}
    \item \makebox[6cm]{administrative/legal matters \dotfill[4]}
    \item \makebox[6cm]{entertainment/media \dotfill[5]}
    \item \makebox[6cm]{work/money/finances \dotfill[6]}
    \item \makebox[6cm]{education/school \dotfill[7]}
    \item \makebox[6cm]{transport/travel \dotfill[8]}
    \item \makebox[6cm]{recreation/sport/art/friends \dotfill[9]}
    \item \makebox[6cm]{community/politics \dotfill[10]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\category{7}{Sample}

\step{Sample}{The sample recruited by the authors.}{Sample}
\textit{Please specify the sample requirements of the authors. If non are provided use the code `general' to indicate that the general population of migrants was targeted.}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\step{MigrationTime}{When in the migration process acculturation was assessed?}{Sample}
\textit{Please specify whether the authors considered one or multiple time-points in the migration process. And if multiple are assessed, please specify which time-points were included.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[6cm]{potential \dotfill[1]}
    \item \makebox[6cm]{pre \dotfill[2]}
    \item \makebox[6cm]{post \dotfill[3]}
    \item \makebox[6cm]{pre \& post \dotfill[4]}
    \item \makebox[6cm]{N/A \dotfill[5]}
\end{itemize}
\divider

\step{IncludesMajority}{Whether members of the dominant group in the host society were considered.}{Sample}
\textit{Please specify whether members of the dominant group in the host society were included for the scale validation.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[6cm]{no \dotfill[0]}
    \item \makebox[6cm]{yes \dotfill[1]}
\end{itemize}
\divider

\step{HostCountry}{Country or countries of settlement considered for validation.}{Sample}
\textit{Please specify the host country or countries that were included in the validation. This country is usually the country of settlement for the migrant group. If no country is focused on in particular, please use the code `any' to indicate that any host country was allowed as part of the sampling strategy.}
\vspace{1.5em}

\rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth}\\
\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
{\namefont character string\hspace{2.08cm}character string\hspace{2.08cm}character string}\par
\divider

\step{OriginCountry}{Country or countries of origin considered for validation.}{Sample}
\textit{Please specify the origin country or countries that were included in the validation. These countries usually the country of origin for the migrant group. If no country is focused on in particular, please use the code `any' to indicate that migrants from any country were included as part of the sampling strategy.}
\vspace{1.5em}

\rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth}\\
\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
{\namefont character string\hspace{2.08cm}character string\hspace{2.08cm}character string}\par
\divider

\clearpage
\vspace*{2em}

\marginpar{
\need{Empirical Dataset}
\resizebox{7cm}{!}{
    % For organization, I like to keep the actual card in a separate file:
    \input{Supplemental Material A - Coding Protocol/margins/FactSheetEmpirical}
    }
}
\need{Empirical Literature}
\category{1}{Bibliographic Information}

\begin{topbot}
\subsubsection*{Additional Bibliographic Data}
A range of additional bibliographic data fields is available in the dataset. These fields include the `type of publication', `year of publication', `author names', `title', `abstract', `DOI', `duplicate filters', as well as a range of publisher information. These fields are generated during the literature search by the bibliographic database and don't need any input from the coders. Additional information on the format and content of these fields is available in the `Codebook'.
\end{topbot}

\vspace*{2em}

\step{CitationKey}{Add BibTeX citation key for the empirical manuscript.}{Bibliographic Information}
\textit{The citation key can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
\textit{\newline Example format: Author2019}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\category{2}{Screening}

\step{TitleScreening}{Whether manuscript should be excluded during title screening.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{excluded \dotfill[0]}
	\item \makebox[5cm]{included \dotfill[1]}
\end{itemize}
\divider

\marginpar{
\vspace{1.4em}
Missingness Explanations

\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
>{\raggedright\arraybackslash}p{0.75\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
1 & manuscript is in a language other than English. \\
2 & rural-urban, second generation \\
3 & focus on dominant group \\
4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
5 & migration status, length of residence  \\
6 & only discusses theory of others. \\
7 & not accessible via library services \\
8 & not accessible via library services \\
9 & not accessible via library services \\
10 & not accessible via library services \\
11 & not accessible via library services \\
12 & not accessible via library services \\
\bottomrule
\end{tabular*}
}

\divider
\step{TitleNote}{If excluded during `TitleScreening', provide the reason for exclusion.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{not English \dotfill[1]}
	\item \makebox[5cm]{not migration \dotfill[2]}
	\item \makebox[5cm]{not migrant \dotfill[3]}
	\item \makebox[5cm]{not acculturation \dotfill[4]}
	\item \makebox[5cm]{not ABCD \dotfill[5]}
	\item \makebox[5cm]{not measured \dotfill[6]}
	\item \makebox[5cm]{items not accessible \dotfill[7]}
	\item \makebox[5cm]{thesis not accessible \dotfill[8]}
	\item \makebox[5cm]{article not accessible \dotfill[9]}
	\item \makebox[5cm]{book not accessible \dotfill[10]}
	\item \makebox[5cm]{chapter not accessible \dotfill[11]}
	\item \makebox[5cm]{poster not accessible \dotfill[12]}
\end{itemize}
\divider

\clearpage
\vspace*{1em}

\step{AbstractScreening}{Whether manuscript was excluded during abstract screening.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{excluded \dotfill[0]}
	\item \makebox[5cm]{included \dotfill[1]}
\end{itemize}

\marginpar{
\vspace{1.4em}
Missingness Explanations

\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
>{\raggedright\arraybackslash}p{0.75\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
1 & manuscript is in a language other than English. \\
2 & rural-urban, second generation \\
3 & focus on dominant group \\
4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
5 & migration status, length of residence  \\
6 & only discusses theory of others. \\
7 & not accessible via library services \\
8 & not accessible via library services \\
9 & not accessible via library services \\
10 & not accessible via library services \\
11 & not accessible via library services \\
12 & not accessible via library services \\
\bottomrule
\end{tabular*}
}
\divider

\step{AbstractNote}{If excluded during `AbstractScreening', provide the reason for exclusion.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{not English \dotfill[1]}
	\item \makebox[5cm]{not migration \dotfill[2]}
	\item \makebox[5cm]{not migrant \dotfill[3]}
	\item \makebox[5cm]{not acculturation \dotfill[4]}
	\item \makebox[5cm]{not ABCD \dotfill[5]}
	\item \makebox[5cm]{not measured \dotfill[6]}
	\item \makebox[5cm]{items not accessible \dotfill[7]}
	\item \makebox[5cm]{thesis not accessible \dotfill[8]}
	\item \makebox[5cm]{article not accessible \dotfill[9]}
	\item \makebox[5cm]{book not accessible \dotfill[10]}
	\item \makebox[5cm]{chapter not accessible \dotfill[11]}
	\item \makebox[5cm]{poster not accessible \dotfill[12]}
\end{itemize}
\divider

\step{Downloaded}{Whether full manuscript--text was downloaded.}{Screening}
\textit{If this was not possible, please describe steps taken in the `Comment' code.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{not downloaded \dotfill[0]}
	\item \makebox[5cm]{downloaded \dotfill[1]}
\end{itemize}
\divider

\step{MissingABCD}{Whether experience aspects were coded in full text.}{Screening}
\textit{Does the empirical study consider (i.e., measure) psychological acculturation? Please focus particularly on the measurement of acculturation, e.g., scale description, the (sub-)scale labels, as well as items.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{coded \dotfill[0]}
	\item \makebox[5cm]{missing \dotfill[1]}
\end{itemize}

\marginpar{
\vspace{1.4em}
Missingness Explanations

\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
>{\raggedright\arraybackslash}p{0.75\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
1 & manuscript is in a language other than English. \\
2 & rural-urban, second generation \\
3 & focus on dominant group \\
4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
5 & migration status, length of residence  \\
6 & only discusses theory of others. \\
7 & not accessible via library services \\
8 & not accessible via library services \\
9 & not accessible via library services \\
10 & not accessible via library services \\
11 & not accessible via library services \\
12 & not accessible via library services \\
\bottomrule
\end{tabular*}
}
\divider

\step{NoteMissing}{If excluded during full-text analysis, provide the reason for exclusion.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{not English \dotfill[1]}
	\item \makebox[5cm]{not migration \dotfill[2]}
	\item \makebox[5cm]{not migrant \dotfill[3]}
	\item \makebox[5cm]{not acculturation \dotfill[4]}
	\item \makebox[5cm]{not ABCD \dotfill[5]}
	\item \makebox[5cm]{not measured \dotfill[6]}
	\item \makebox[5cm]{items not accessible \dotfill[7]}
	\item \makebox[5cm]{thesis not accessible \dotfill[8]}
	\item \makebox[5cm]{article not accessible \dotfill[9]}
	\item \makebox[5cm]{book not accessible \dotfill[10]}
	\item \makebox[5cm]{chapter not accessible \dotfill[11]}
	\item \makebox[5cm]{poster not accessible \dotfill[12]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\step{Comment}{Any necessary comments of the coder.}{Screening}
\textit{This can include additional information about the format and content of the theoretical work, as well as information on the missingness or accessibility.}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\category{3}{Experience}
\marginpar{
\vspace{3em}
Selected Affect Concept Examples:
\begin{itemize}
    \item loneliness
    \item feeling at home
    \item satisfaction with life
    \item pride
    \item comfortableness
    \item joy
    \item ease
    \item well-being
    \item worry
    \item trust
\end{itemize}
}

\step{Affect}{Whether the studies included affect.}{Experience}
\textit{To identify whether the author(s) included affective experiences in their study of acculturation, you can examine the study description, the methods section, the (sub-)scale labels, as well as items for self-identified mentions of affect. Please consider affect at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `affect' or `affective' directly.\\
\textbf{Construct:} the authors might refer to affective constructs such as `emotion' or `mood'.\\
\textbf{Concept:} the authors might refer to affective concepts such as individual emotions, including `pride' or `loneliness'.\\
\textbf{Operationalization:} the authors might also include affective conceptualizations in their operationalizations, such as `I feel ...' or `I enjoy ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{3em}
Selected Behavior Concept Examples:
\begin{itemize}
    \item language use
    \item civic participation (voting, ...)
    \item performance (work, ...)
    \item media consumption
    \item education
    \item peer contacts
    \item food consumption
    \item cultural habits (holidays ...)
    \item delinquency
    \item marriage
\end{itemize}
}

\step{Behavior}{Whether the studies included behavior(s).}{Experience}
\textit{To identify whether the author(s) included affective experiences in their study of acculturation, you can examine the study description, the methods section, the (sub-)scale labels, as well as items for self-identified mentions of behaviors. Please consider behaviors at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `behavior' or `behavioral' directly.\\
\textbf{Construct:} the authors might refer to behavioral constructs such as `activities' or `habits'.\\
\textbf{Concept:} the authors might refer to behavioral concepts, such as `language use' or `media consumption'.\\
\textbf{Operationalization:} the authors might also include behavioral conceptualizations in their operationalizations, such as `I do ...' or `I speak ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\marginpar{
\vspace{3em}
Selected Cognition Concept Examples:
\begin{itemize}
    \item ethnic identification
    \item cultural values
    \item acculturation orientation
    \item preferences (food, friends, ...)
    \item knowledge
    \item importance ratings
    \item inner thought language
    \item perceived obligations
    \item beliefs
    \item stereotypes
\end{itemize}
}

\step{Cognition}{Whether the studies included cognition(s).}{Experience}
\textit{To identify whether the author(s) included affective experiences in their studies, you can examine the study description, the methods section, the (sub-)scale labels, as well as items for self-identified mentions of cognitions. Please consider cognitions at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `cognition' or `cognitive' directly.\\
\textbf{Construct:} the authors might refer to cognitive constructs such as `knowledge' or `memories'.\\
\textbf{Concept:} the authors might refer to cognitive concepts, such as `cultural values' or `ethnic identification'.\\
\textbf{Operationalization:} the authors might include cognitive conceptualizations in their operationalization, such as `I think ...' or `I prefer ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{3em}
Selected Desire Concept Examples:
\begin{itemize}
    \item competence
    \item independence
    \item self-coherence
    \item belonging
    \item achievement
    \item justice
    \item growth
    \item respect
    \item acceptance
    \item identity continuity
\end{itemize}
}

\step{Desire}{Whether the studies included desire(s).}{Experience}
\textit{To identify whether the author(s) included affective experiences in their study, you can examine the study description, the methods section, the (sub-)scale labels, as well as items for self-identified mentions of desires. Please consider desires at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `desire' or `motivational' directly.\\
\textbf{Construct:} authors might include desire constructs such as `needs' or `goals'.\\
\textbf{Concept:} authors might refer to desire concepts, such as `belonging' or `competence'.\\
\textbf{Operationalization:} the authors might include motivational conceptualizations in their study, such as `I want ...' or `I need ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{1em}
Complexity Explanations

\begin{tabular*}{6.2cm}{>{\centering\arraybackslash}p{0.08\linewidth} 
>{\raggedright\arraybackslash}p{0.76\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
1 & focused on a concept that includes multiple aspects (e.g., satisfaction, distress) \\
2 & aspects included as parts of a scale \\
3 & aspects measured as independent conceptualizations of acculturation \\
4 & aspects included as part of a review of multiple conceptualizations \\
N/A & only one aspect was included  \\
\bottomrule
\end{tabular*}
}

\step{TypeComplexity}{Type of aspect combination [if multiple experience aspects included].}{Experience}
\textit{If more than one experience aspect was coded, please specify how the multiple aspects were included. The study might include the aspects either independently as parts of the acculturation conceptualization or as part of a scale or proxy measure that includes multiple experience aspects.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{complex concept \dotfill[1]}
	\item \makebox[5cm]{complex scale \dotfill[2]}
	\item \makebox[5cm]{independent \dotfill[3]}
	\item \makebox[5cm]{review \dotfill[4]}
	\item \makebox[5cm]{not applicable \dotfill[N/A]}
\end{itemize}
\divider

\category{4}{Data Collection}

\step{empirical}{Whether the manuscript presented empirical conceptualization(s) of acculturation.}{Data Collection}
\textit{Please specify whether the authors collected (observable) data as part of their investigation.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{empirical \dotfill[1]}
	\item \makebox[5cm]{non-empirical \dotfill[0]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\step{Method}{Type of empirical data collected.}{Data Collection}
\textit{If empirical data was collected, what kind of data was collected or discussed by the author(s)?}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{quantitative \dotfill[1]}
	\item \makebox[5cm]{qualitative \dotfill[2]}
	\item \makebox[5cm]{mixed method \dotfill[3]}
	\item \makebox[5cm]{meta-analysis \dotfill[4]}
	\item \makebox[5cm]{review \dotfill[5]}
\end{itemize}
\divider

\step{MeasureDefinition}{Name of the scale used or the concepts measured as proxies.}{Data Collection}
\textit{Please specify the name of the measurement tool (e.g., scale) used by the authors. If the scale is not yet in the scale database, please look up the validation of the scale and add it to the database. Do the same for proxy measures of acculturation.}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\step{MeasurementLevels}{Levels of measurement.}{Data Collection}
\textit{Identify the measurement level of the empirical scales. Are the items (or at least the resulting scale) measured as a continuous dimension or is the resulting measure a classification into groups. Indicate `categorical' even if there is an order to the groups. Select `both' if a the measure includes both continuous and categorical measures.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{continuous \dotfill[1]}
	\item \makebox[5cm]{categorical \dotfill[2]}
	\item \makebox[5cm]{both \dotfill[3]}
\end{itemize}
\divider

\category{5}{Focus}

\marginpar{
Acculturation Term Examples:
\begin{itemize}
    \item acculturation
    \item enculturation
    \item transculturation
    \item assimilation
    \item integration
    \item social integration
    \item cultural adaptation
    \item cultural adjustment
    \item cultural transition
\end{itemize}
}

\step{term}{Acculturation term used by authors.}{Data Collection}
\textit{Please note which term the author(s) used to refer to ``psychological acculturation" (i.e., ``changes an individual experiences as a result of being in contact with other cultures").}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\step{domainPaper}{Focus concept of the manuscript.}{Data Collection}
\textit{Please specify the main focus of the manuscript. The focus is often clearest in the dependent variable within the model or analysis but should also be clearly stated within the title, abstract, or introduction. The focus could be `acculturation' but it could also be something else (that might, for example, be predicted by acculturation; e.g., depression).}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\clearpage
\vspace*{2em}

\step{domainScale}{Situational focus of the acculturation conceptualization.}{Focus}
\textit{To identify the author(s) situational focus in their conceptualization of psychological acculturation, you can examine the manuscript for self-identified mentions of life domains. Please place a particular focus on the study description, as well as the methodology, including scale descriptions, the (sub-)scale labels, and the  items themselves.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[6cm]{spirituality/religion \dotfill[1]}
    \item \makebox[6cm]{home/family \dotfill[2]}
    \item \makebox[6cm]{health/care \dotfill[3]}
    \item \makebox[6cm]{administrative/legal matters \dotfill[4]}
    \item \makebox[6cm]{entertainment/media \dotfill[5]}
    \item \makebox[6cm]{work/money/finances \dotfill[6]}
    \item \makebox[6cm]{education/school \dotfill[7]}
    \item \makebox[6cm]{transport/travel \dotfill[8]}
    \item \makebox[6cm]{recreation/sport/art/friends \dotfill[9]}
    \item \makebox[6cm]{community/politics \dotfill[10]}
\end{itemize}
\divider

\category{6}{Sample}

\step{Sample}{The sample recruited by the authors.}{Sample}
\textit{Please specify the sample requirements of the authors. If non are provided use the code `general' to indicate that the general population of migrants was targeted.}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\step{MigrationTime}{When in the migration process acculturation was assessed?}{Sample}
\textit{Please specify whether the authors considered one or multiple time-points in the migration process. And if multiple are assessed, please specify which time-points were included.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[6cm]{potential \dotfill[1]}
    \item \makebox[6cm]{pre \dotfill[2]}
    \item \makebox[6cm]{post \dotfill[3]}
    \item \makebox[6cm]{pre \& post \dotfill[4]}
    \item \makebox[6cm]{N/A \dotfill[5]}
\end{itemize}
\divider

\step{IncludesMajority}{Whether members of the dominant group in the host society were considered.}{Sample}
\textit{Please specify whether members of the dominant group in the host society were included for the study. If they were included please note in the `comment' code whether acculturation was measured for the dominant group.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[6cm]{no \dotfill[0]}
    \item \makebox[6cm]{yes \dotfill[1]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\step{HostCountry}{Country or countries of settlement considered for study.}{Sample}
\textit{Please specify the host country or countries that were included in the study. This country is usually the country of settlement for the migrant group. If no country is focused on in particular, please use the code `any' to indicate that any host country was allowed as part of the sampling strategy.}
\vspace{1.5em}

\rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth}\\
\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
{\namefont character string\hspace{2.08cm}character string\hspace{2.08cm}character string}\par
\divider

\step{OriginCountry}{Country or countries of origin considered for study.}{Sample}
\textit{Please specify the origin country or countries that were included in the study. These countries are usually the country of origin for the migrant group. If no country is focused on in particular, please use the code `any' to indicate that migrants from any country were included as part of the sampling strategy.}
\vspace{1.5em}

\rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth}\\
\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
{\namefont character string\hspace{2.08cm}character string\hspace{2.08cm}character string}\par
\divider

\category{7}{Analysis}

\marginpar{
Analysis Type Examples:
\begin{itemize}
    \item cluster analysis
    \item correlation analysis
    \item lagged regression
    \item cross-lagged panel analysis
    \item longitudinal analysis
    \item mean differences
    \item participant selection
    \item path analysis
    \item prevalence rates
    \item regression (incl. PROCESS macro)
    \item structural equation modeling
    \item social network analysis
    \item validation analyses
    \item content analysis
    \item open coding 
    \item axial coding
    \item phenomenological praxis
    \item constant comparative coding
\end{itemize}
}

\step{MainAnalysis}{Type of data analysis conducted by the authors.}{Analysis}
\textit{Please specify the type of analysis conducted by the authors. If multiple analyses were conducted please report the `main' analysis. The main analysis offers the most direct test of the hypotheses and lends the most weight during the interpretation and summary of the results. (The main analysis is often the last and most complex analysis.)}
\vspace{1.5em}
\ruleandname{character string}{5cm} 
\divider

\step{VariableType}{The place in the model that acculturation takes [if quantitative analysis]}{Analysis}
\textit{If a quantitative analysis was conducted please specify the variable type of acculturation (during the main analysis, identified during `MainAnalysis').}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{Control\dotfill[1]}
    \item \makebox[5cm]{Correlation\dotfill[2]}
    \item \makebox[5cm]{Dependent\dotfill[3]}
    \item \makebox[5cm]{Mediator\dotfill[4]}
    \item \makebox[5cm]{Moderator\dotfill[5]}
    \item \makebox[5cm]{N/A\dotfill[6]}
    \item \makebox[5cm]{Predictor\dotfill[7]}
    \item \makebox[5cm]{Predictor \& Dependent\dotfill[8]}
    \item \makebox[5cm]{selection criterion\dotfill[9]}
\end{itemize}
\divider

% --------------------------------
%           Last Page
% --------------------------------

\clearpage

\need[margins/otherinfo]{Links}

\nocite{*}

\printbibliography[heading=none]
%[reference to GitHub repository masked for peer review]

%[reference to DataVerse repository masked for peer review]

\divider

%% If the NEXT page doesn't start with a \need but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}

\end{document}

### 2023-05-16 Supplemental Material B - Coding Protocol/margins/FactSheetEmpirical.tex
:tada: coding protocol template added

\input{Supplemental Material A - Coding Protocol/margins/empNums}

\sffamily
{
\fbox{%
\begin{tabular}{@{}p{\NFwidth}@{}}

% Top Matter
\NFtitle\\
\NFrule
\NFtext{\textbf{Dataset} Empirical Acculturation Literature}\\
\NFtext{\textbf{Instances Per Dataset} \nEmp\ empirical studies from \nAllEmp\ unique manuscripts}\\

% Motivation Section
\NFRULE
\NFline{Motivation}\\
\NFrule
\NFelement{Original Authors}{}{Kreienkamp, Bringmann, Engler, de Jonge, Epstude}\\
\NFelement{Original Use Case}{}{collection of empirical works}\\
\NFelement{Original Funding}{}{None}\\

%\NFelement{Additional Field}{}{Info}\\

% Composition Section
\NFRule
\NFline{Composition}\\
\NFrule
\NFelement{Sample or Complete}{}{Sample}\\
\NFelement{Missing Data}{}{\percEmpInaccess\% not accessible \\\hfill(\percEmpItemInaccess\% items \& \percEmpThesisInaccess\% theses not accessible)\\\hfill+ see Screening}\\
\NFelement{Sensitive Information }{}{author information}\\
%\NFelement{Additional Field}{}{Info}\\

% Collection Process Section
\NFRule
\NFline{Collection}\\
\NFrule
\NFelement{Sampling Strategy}{}{systematic review (see search strategy)}\\
\NFelement{Ethical Review}{}{not applicable}\\
\NFelement{Author Consent}{}{not applicable}\\
%\NFelement{Additional Field}{}{Info}\\

% Cleaning / Labeling Section
\NFRule
\NFline{Cleaning and Labeling}\\
\NFrule
\NFelement{Cleaning Done}{}{Yes}\\
\NFelement{Labeling Done}{}{Yes}\\
%\NFelement{Additional Field}{}{Info}\\

% Uses / Distribution Section
\NFRule
\NFline{Uses and Distribution}\\
\NFrule
\NFelement{Notable Uses}{}{this systematic review}\\
\NFelement{Other Uses}{}{openly accessible for further analysis}\\
\NFelement{Distribution}{}{available on OSF and GitHub}\\
%\NFelement{Replicate Distribution}{}{Info}\\
%\NFelement{Additional Field}{}{Info}\\

% Maintenance and Evolution Section
\NFRule
\NFline{Maintenance and Evolution}\\
\NFrule
\NFelement{Corrections or Erratum}{}{None}\\
\NFelement{Methods to Extend}{}{CC BY-NC 4.0}\\
\NFelement{Replicate Maintainers}{}{Jannis Kreienkamp}\\
%\NFelement{Additional Field}{}{Info}\\

\NFRULE
\NFline{Types of publications \hfill\% of manuscripts*}\\
\NFrule
\NFelement{journal articles}{\nJournal\,manuscripts}{\percJournal\%}\\
\NFrule
\NFelement{theses}{\nThesis\,manuscripts}{\percThesis\%}\\
\NFrule
%\NFelement{book chapters}{6\,manuscripts}{1.1\%}\\
%\NFrule
%\NFelement{Another}{count}{XX\%}\\
%\NFrule
\NFentry{book chapters \percChapter\%} \\
%\NFentry*{framework 2.9\%}\\
%\NFentry{Red 1.5\%}\\
%\NFrule
%\NFtext{As identified by the author(s) of the theoretical manuscripts (also see `FrameworkTheoryModel' code).}\\
\NFrule
\NFtext{* Based on final dataset after screening.}
\end{tabular}}

\par} % to end centering

### 2023-05-16 Supplemental Material B - Coding Protocol/margins/FactSheetTheoretical.tex
:tada: coding protocol template added

--- 2023-05-16 Supplemental Material B - Coding Protocol/margins/FactSheetEmpirical.tex
@@
-\input{Supplemental Material A - Coding Protocol/margins/empNums}
+\input{Supplemental Material A - Coding Protocol/margins/theoNums}
 
@@
 \NFrule
-\NFtext{\textbf{Dataset} Empirical Acculturation Literature}\\
-\NFtext{\textbf{Instances Per Dataset} \nEmp\ empirical studies from \nAllEmp\ unique manuscripts}\\
+\NFtext{\textbf{Dataset} Theoretical Acculturation Literature}\\
+\NFtext{\textbf{Instances Per Dataset} \nTheo\ unique manuscripts}\\
 
@@
 \NFelement{Original Authors}{}{Kreienkamp, Bringmann, Engler, de Jonge, Epstude}\\
-\NFelement{Original Use Case}{}{collection of empirical works}\\
+\NFelement{Original Use Case}{}{collection of theoretical works}\\
 \NFelement{Original Funding}{}{None}\\
@@
 \NFelement{Sample or Complete}{}{Sample}\\
-\NFelement{Missing Data}{}{\percEmpInaccess\% not accessible \\\hfill(\percEmpItemInaccess\% items \& \percEmpThesisInaccess\% theses not accessible)\\\hfill+ see Screening}\\
+\NFelement{Missing Data}{}{\percTheoMissing\% not included}\\
 \NFelement{Sensitive Information }{}{author information}\\
@@
 \NFelement{Other Uses}{}{openly accessible for further analysis}\\
-\NFelement{Distribution}{}{available on OSF and GitHub}\\
+\NFelement{Distribution}{}{available on DataVerse and GitHub}\\
 %\NFelement{Replicate Distribution}{}{Info}\\
@@
 \NFRULE
-\NFline{Types of publications \hfill\% of manuscripts*}\\
+\NFline{Types of theoretical works \hfill\% of manuscripts*}\\
 \NFrule
-\NFelement{journal articles}{\nJournal\,manuscripts}{\percJournal\%}\\
+\NFelement{theory}{\nTheories\,manuscripts}{\percTheories\%}\\
 \NFrule
-\NFelement{theses}{\nThesis\,manuscripts}{\percThesis\%}\\
+\NFelement{framework}{\nFrameworks\,manuscripts}{\percFrameworks\%}\\
 \NFrule
-%\NFelement{book chapters}{6\,manuscripts}{1.1\%}\\
-%\NFrule
+\NFelement{model}{\nModels\,manuscripts}{\percModels\%}\\
+\NFrule
 %\NFelement{Another}{count}{XX\%}\\
 %\NFrule
-\NFentry{book chapters \percChapter\%} \\
+\NFentry{conceptualization \percTheoMissing\%} \\
 %\NFentry*{framework 2.9\%}\\
 %\NFentry{Red 1.5\%}\\
-%\NFrule
-%\NFtext{As identified by the author(s) of the theoretical manuscripts (also see `FrameworkTheoryModel' code).}\\
+\NFrule
+\NFtext{As identified by the author(s) of the theoretical manuscripts (also see `FrameworkTheoryModel' code).}\\
 \NFrule

### 2023-05-19 Supplemental Material B - Coding Protocol/Supplemental Material B - Coding Protocol.tex
coding protocol filled

@@
 \name{Documentation: \par Coding Protocol}
-\tagline{For: `The Migration Experience: A Conceptual Framework and Systematic Scoping Review of Psychological Acculturation'}
-\made{February 20 2021}
+\tagline{For: `Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies'}
+\made{March 10 2023}
 %%\logo{6.8cm}{images/MJ Research Design}
@@
   % can add more \addedtopeople
-  \madeby{Jannis Kreienkamp}{j.kreienkamp@rug.nl}{February 20, 2021}
+  \madeby{Jannis Kreienkamp}{j.kreienkamp@rug.nl}{March 10, 2023}
+  \addedto{Maximilian Agostini}
   \addedto{Laura F. Bringmann}
-  \addedto{Raili F. Engler}
   \addedto{Peter de Jonge}
@@
 \purpose{
-	This protocol document lays out detailed information for coders of the (included) manuscripts.
-This document serves as an instructive manual to the coders and documents the operationalizations of the coded variables.
-The systematic review produced three literature databases that aim to capture the status quo of the (1) theoretical, (2) methodological, and (3) empirical literature on psychological acculturation.
-The coding procedures (i.e., data extraction) for each dataset are documented in the following document protocol.
+	The purpose of this coding protocol is to assess the goal-directedness of participants' free-text responses regarding their main goal during interactions with outgroup members.
+The coding will capture two dimensions: practical needs and underlying psychological needs.
+Two independent coders will evaluate each response, and the dimensions will be assessed separately to ensure the validity and reliability of the coding process.
 } % add a short description of the purpose for this protocol
@@
 %% \need title in the "main" bar.
-\need[margins/materials]{Theoretical Literature}
+\need[margins/materials]{Goal Directedness}
 
-\category{1}{Bibliographic Information}
+\category{1}{Introduction}
 
-\step{Theory}{What is the name of the theory?}{Bibliographic Information}
-\textit{Whenever possible record the name of the theory chosen by the authors themselves.}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
+The goal of this coding protocol is to assess the goal-directedness of free-text responses obtained from recent migrants regarding their interactions with outgroup members.
+Each coder should independently read and analyze each free-text response.
+For each response, it is your task to determine whether the response presents a practical need and whether it presents a psychological need.
+You will be asked to assign a code to each dimension based on the presence or absence of the respective need type.
+We will first explain the coding procedure and will then provide more detailed information on the coding criteria for each dimension.
 
-\step{Source}{Add the full APA 7 formatted citation of the theoretical manuscript that is being coded.}{Bibliographic Information}
-\textit{Example format: Author, A. A., \& Author, B. B. (Year). Title of the work. Source where you can retrieve the work. DOI (or URL) if available.}
-\vspace{1.5em}
-\ruleandname{character string}{10cm}
-\divider
+\vspace{1em}
 
-\step{CitationKey}{Add BibTeX citation key for the theoretical manuscript.}{Bibliographic Information}
-\textit{The citation key can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
-\textit{\newline Example format: Author2019}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
+\category{2}{Coding Procedure}
 
-\clearpage
-\vspace*{1em}
+\begin{enumerate}
+    \item Familiarize yourself with the research objectives: Gain a clear understanding of the study's goals and the specific practical and psychological needs, as well as non-goal-directed actions.
+This understanding will guide the coding process.
+    \item Read and understand the research question prompt: Review the survey question that asks participants about their main goal during the interaction.
+Ensure a thorough understanding of the wording and context to accurately identify responses that indicate underlying needs.
+    \item Assign a rating for each dimension (0, 1, or 2) based on the criteria provided.
+    \item Rate each dimension independently without being influenced by the rating given to the other dimension.
+    \item Use the examples provided as references, but do not limit your assessment to these examples alone.
+    \item If a response contains multiple goals, consider the most prominent or emphasized goal in the rating.
+    \item In case of ambiguity or uncertainty, code conservatively and opt for a lower rating.
+    \item Document your ratings and any notes or comments regarding challenging cases or exceptional responses within the \textit{comment} field.
+    \item Regular communication with the research team is encouraged to clarify any uncertainties and maintain consistency in coding.
+\end{enumerate}
 
-\category{2}{Screening}
+\newpage
+\vspace*{3em}
+\textbf{Coding Agreement and Disagreement:}
+\begin{itemize}
+    \item After coding all responses, we compare the codes assigned by each coder.
+    \item The PI will calculate the inter-coder reliability using appropriate statistical measures (e.g., Cohen's kappa) to determine the agreement between coders.
+    \item The coders will resolve any disagreements through discussion and consensus until a final set of codes is reached.
+    \item If necessary, we will refine the coding protocol based on the discussion and repeat the coding process to ensure consistency and validity.
+\end{itemize}
 
-\step{MissingABCD}{Whether the experience aspects (affect, behavior, cognition, and desire) are coded.}{Screening}
+\vspace{1em}
+
+\category{3}{Coding Criteria}
+
+\step{practical\_need}{Practical Needs Dimension}{needs}
+\textit{Practical needs refer to specific, tangible goals or tasks that participants aimed to accomplish during the interaction.
+These instrumental goals are usually observable, concrete, and often centered on external outcomes.
+Individuals strive to fulfill these needs to navigate their daily lives efficiently and achieve desired results.
+Examples of practical needs include engaging in activities such as acquiring resources, completing tasks, and addressing immediate challenges.
+These needs are closely tied to instrumental and utilitarian considerations, highlighting the pursuit of external rewards, resource acquisition, or problem-solving.
+It is your task to assess the extent to which the free-text response captures a practical need.
+Practical needs can include activities such as getting coffee together, working on an assignment, discussing a project, or seeking information.}\\
 \vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{coded \dotfill[0]}
-	\item \makebox[5cm]{missing \dotfill[1]}
+\textit{\textbf{Options:}} \\
+\textit{Either there is no practical need to be identified (1), a vague or general mention of a practical need without specific details (2), or a clear mention of a practical need (3).}\\
+\vspace{0.5em}
+\textit{\textbf{Additional clarification no practical need:}}\\
+\textit{Given that many aspects of the human life a driven by needs or at least are recalled or perceived as need-driven, it can be difficult to identify situational reports that do not include a practical need, motive, or goal.
+Examples of responses that are not goal-directed would be:
+\begin{itemize}[nosep]
+    \item[--] "I wasn't seeking any particular outcome, I simply wanted to be present in the moment and enjoy the interaction."
+    \item[--] "There wasn't a specific objective I aimed to achieve, I just wanted to see where the conversation would take us."
+    \item[--] "I wasn't focused on achieving a particular outcome, my intention was to engage in a spontaneous and genuine conversation."
 \end{itemize}
-\divider
+These examples reflect a lack of specific goals or intentions during intergroup interactions.
+These examples express a more open and non-directed approach, where the primary focus was on the process of interaction itself rather than aiming for specific outcomes or results.}
+
+\vspace{0.5em}
+\textit{\textbf{Codes:}}
+\vspace{0.5em}
 
 \marginpar{
-\vspace{2em}
-Missingness Explanations
+\vspace{-4em}
+Practical Need Explanations
 
@@
 \midrule
-1 & manuscript is in a language other than English. \\
-2 & rural-urban, second generation \\
-3 & focus on dominant group \\
-4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
-5 & migration status, length of residence  \\
-6 & only discusses theory of others. \\
-7 & not accessible via library services \\
-8 & not accessible via library services \\
-9 & not accessible via library services \\
-10 & not accessible via library services \\
-11 & not accessible via library services \\
+0 & ``We just exchanged greetings and went our separate ways.'' \\
+1 & ``We had a task to complete.'' \\
+2 & ``We met to discuss the upcoming presentation.'' \\
 \bottomrule
@@
 }
+\begin{itemize}
+	\item \parbox[t]{6cm}{No practical need \dotfill[0]}
+	\item \parbox[t]{6cm}{Vague or general mention \dotfill[1]}
+    \item \parbox[t]{6cm}{Clear mention \dotfill[2]}
+\end{itemize}
 
-\divider
-\step{NoteMissing}{If experience aspects (affect, behavior, cognition, desire) not coded, provide the reason for missing coding.}{Screening}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{not English \dotfill[1]}
-	\item \makebox[5cm]{not migration \dotfill[2]}
-	\item \makebox[5cm]{not migrant \dotfill[3]}
-	\item \makebox[5cm]{not acculturation \dotfill[4]}
-	\item \makebox[5cm]{not ABCD \dotfill[5]}
-	\item \makebox[5cm]{not theory \dotfill[6]}
-	\item \makebox[5cm]{thesis not accessible \dotfill[7]}
-	\item \makebox[5cm]{article not accessible \dotfill[8]}
-	\item \makebox[5cm]{book not accessible \dotfill[9]}
-	\item \makebox[5cm]{chapter not accessible \dotfill[10]}
-	\item \makebox[5cm]{poster not accessible \dotfill[11]}
-\end{itemize}
+\vspace{1em}
 \divider
 
-\step{Comment}{Any necessary comments of the coder.}{Screening}
-\textit{This can include additional information about the format and content of the theoretical work, as well as information on the missingness or accessibility.}
-\vspace{1.5em}
-\ruleandname{character string}{10cm}
+\newpage
+\vspace*{3em}
 \divider
+\vspace{1em}
 
-\category{3}{Theory Information}
-
-\step{Summary}{A short summary of the theoretical work.}{Theory Information}
-\textit{This summary ideally includes the sections that were relevant to the experience aspect (affect, behavior, cognition, desire) coding.}
-\vspace{1.5em}
-
-\rule{10cm}{\rulewidth}\vspace{0.75em}
-\rule{10cm}{\rulewidth}\vspace{0.75em}
-\rule{10cm}{\rulewidth}\vspace{0.75em}
-\ruleandname{character string}{10cm}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\step{FrameworkTheoryModel}{Type of theoretical work, as identified by the author.}{Theory Information}
-\textit{Please code the term that is being used by the author(s).}
+\step{psychological\_need}{Psychological Needs Dimension}{needs}
+\textit{Psychological needs refer to underlying motives or desires that are more abstract and relate to personal fulfillment and well-being.
+In contrast to practical needs, psychological needs delve into the subjective and internal aspects of human experiences.
+These needs pertain to emotions, social connections, and cognitive processes, reflecting individuals' quest for personal growth, well-being, and thriving in social relationships.
+It is your task to assess the extent to which the free-text response captures an underlying psychological need.
+Psychological needs can include motives such as sharing and bonding, competence and mastery, feeling valued or respected, or seeking emotional support.\\
 \vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{conceptualization \dotfill[1]}
-	\item \makebox[5cm]{framework \dotfill[2]}
-	\item \makebox[5cm]{theory \dotfill[3]}
-	\item \makebox[5cm]{model \dotfill[4]}
+\textbf{Options:} \\
+Similar to the practical need coding, responses might either include no underlying psychological need identified (1), include a vague or general mention of a psychological need without specific details (2), or present a clear mention of a psychological need (3).\\
+\vspace{0.5em}
+\textbf{Additional clarification no psychological need:}\\
+Similar to the practical needs, it can be difficult to identify situational reports that do not include a any underlying psychological need, motive, or goal.
+Examples of responses that are not goal-directed would be:
+\begin{itemize}[nosep]
+    \item[--] "I didn't have any specific expectations or goals in mind, I just wanted to see how the conversation would unfold."
+    \item[--] "I didn't have a specific goal in mind, I was open to any potential insights or connections that might emerge."
 \end{itemize}
-\divider
-
-\step{GeneralAspect}{Whether the theoretical work is about acculturation in general or whether it conceptualizes a particular aspect of acculturation.}{Theory Information}
-\textit{Is acculturation in general being considered or do the authors focus on a single aspect of acculturation, such as theories on labor market integration.}
+These examples reflect a lack of specific goals or intentions during intergroup interactions.
+If in doubt, try to code conservatively (i.e., try to not infer a need that might not be present) and make a comment if necessary.
+}
 \vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{general \dotfill[1]}
-	\item \makebox[5cm]{aspect \dotfill[2]}
-\end{itemize}
-\divider
-
-\step{Target}{If aspect is targeted, what is the target of the theoretical work?}{Theory Information}
-\textit{Example aspects might be theoretical works that exclusively focus on labor market integration or identity development.}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
-
-\category{4}{Experience}
-\marginpar{
-\vspace{3em}
-Selected Affect Concept Examples:
-\begin{itemize}
-    \item loneliness
-    \item feeling at home
-    \item satisfaction with life
-    \item pride
-    \item comfortableness
-    \item joy
-    \item ease
-    \item well-being
-    \item worry
-    \item trust
-\end{itemize}
-}
-
-\step{Affect}{Whether the theoretical conceptualization included affect.}{Experience}
-\textit{To identify whether the author(s) included affective experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of affect.
-Please consider affect at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `affect' or `affective' directly.\\
-\textbf{Construct:} the authors might refer to affective constructs such as `emotion' or `mood'.\\
-\textbf{Concept:} the authors might refer to affective concepts such as individual emotions, including `pride' or `loneliness'.\\
-\textbf{Operationalization:} the authors might also include affective conceptualizations in their descriptions of experiences, such as `a person feels' or `a person enjoys'.}
+\textit{\textbf{Codes:}}
 \vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{2em}
 
 \marginpar{
-\vspace{3em}
-Selected Behavior Concept Examples:
-\begin{itemize}
-    \item language use
-    \item civic participation (voting, ...)
-    \item performance (work, ...)
-    \item media consumption
-    \item education
-    \item peer contacts
-    \item food consumption
-    \item cultural habits (holidays ...)
-    \item delinquency
-    \item marriage
-\end{itemize}
-}
-
-\step{Behavior}{Whether the theoretical conceptualization included behavior(s).}{Experience}
-\textit{To identify whether the author(s) included behavioral experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of behaviors.
-Please consider behaviors at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `behavior' or `behavioral' directly.\\
-\textbf{Construct:} the authors might refer to behavioral constructs such as `activities' or `habits'.\\
-\textbf{Concept:} the authors might refer to behavioral concepts, such as `language use' or `media consumption'.\\
-\textbf{Operationalization:} the authors might also include behavioral conceptualizations in their descriptions of experiences, such as `a person does' or `a person works'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\marginpar{
-\vspace{3em}
-Selected Cognition Concept Examples:
-\begin{itemize}
-    \item ethnic identification
-    \item cultural values
-    \item acculturation orientation
-    \item preferences (food, friends, ...)
-    \item knowledge
-    \item importance ratings
-    \item inner thought language
-    \item perceived obligations
-    \item beliefs
-    \item stereotypes
-\end{itemize}
-}
-
-\step{Cognition}{Whether the theoretical conceptualization included cognition(s).}{Experience}
-\textit{To identify whether the author(s) included cognitive experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of cognitions.
-Please consider cognitions at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `cognition' or `cognitive' directly.\\
-\textbf{Construct:} the authors might refer to cognitive constructs such as `knowledge' or `memories'.\\
-\textbf{Concept:} the authors might refer to cognitive concepts, such as `cultural values' or `ethnic identification'.\\
-\textbf{Operationalization:} the authors might also include cognitive conceptualizations in their descriptions of experiences, such as `a person thinks' or `a person prefers'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\marginpar{
-\vspace{3em}
-Selected Desire Concept Examples:
-\begin{itemize}
-    \item competence
-    \item independence
-    \item self-coherence
-    \item belonging
-    \item achievement
-    \item justice
-    \item growth
-    \item respect
-    \item acceptance
-    \item identity continuity
-\end{itemize}
-}
-
-\step{Desire}{Whether the theoretical conceptualization included desire(s).}{Experience}
-\textit{To identify whether the author(s) included motivational experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of desires.
-Please consider desires at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `desire' or `motivational' directly.\\
-\textbf{Construct:} the authors might refer to desire constructs such as `needs' or `goals'.\\
-\textbf{Concept:} the authors might refer to desire concepts, such as `belonging' or `competence'.\\
-\textbf{Operationalization:} the authors might also include motivational conceptualizations in their descriptions of experiences, such as `a person wants' or `a person needs'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\category{5}{Data Collection}
-
-\step{SourceType}{Whether the theoretical conceptualization is based on theoretical reasoning or empirical investigations.}{Data Collection}
-\textit{Is the theoretical reasoning focused on past theoretical work or do the authors build a theoretical conceptualization based on (qualitative) investigations (e.g., grounded theory).}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{theoretical \dotfill[1]}
-	\item \makebox[5cm]{empirical \dotfill[2]}
-\end{itemize}
-\divider
-
-\category{6}{Focus}
-
-\step{Time}{Whether the conceptualization of acculturation is dynamic or static.}{Focus}
-\textit{Do the authors self-identify the theory as a dynamic process (e.g., `process,' `development,' `longitudinal,' `temporal,' `dynamic') or a static outcome (e.g., `static,' `outcome,' `markers,' `consequence')}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{static \dotfill[1]}
-	\item \makebox[5cm]{dynamic \dotfill[2]}
-\end{itemize}
-\divider
-
-\marginpar{
-\need{Methods Dataset}
-\resizebox{7cm}{!}{
-    % For organization, I like to keep the actual card in a separate file:
-    \input{Supplemental Material A - Coding Protocol/margins/FactSheetMethodological}
-    }
-}
-\need{Methodological Literature}
-\category{1}{Bibliographic Information}
-
-\step{Scale}{What is the name of the scale?}{Bibliographic Information}
-\textit{Whenever possible record the name of the scale chosen by the authors themselves.}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
-
-\step{Source}{Whether the scale was added as part of one of the past methodological reviews or through our own review of the empirical literature.}{Bibliographic Information}
-\textit{Indicate whether the scale was included in one or multiple of the past methodological reviews or was added from our own review.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{Celenk2011 \dotfill[1]}
-	\item \makebox[5cm]{Matsudaira2006 \dotfill[2]}
-	\item \makebox[5cm]{Wallace2010 \dotfill[3]}
-	\item \makebox[5cm]{own review \dotfill[4]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\step{CitationKey}{Add BibTeX citation key for the theoretical manuscript.}{Bibliographic Information}
-\textit{The citation key can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
-\textit{\newline Example format: Author2019}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
-
-\step{APACite}{Add the full APA 7 formatted citation of the theoretical manuscript that is being coded.}{Bibliographic Information.}
-\textit{Example format: Author, A. A., \& Author, B. B. (Year). Title of the work. Source where you can retrieve the work. DOI (or URL) if available.}
-\vspace{1.5em}
-\ruleandname{character string}{10cm}
-\divider
-
-\step{DOI}{Add Digial Object Identifier (DOI).}{Bibliographic Information}
-\textit{The doi can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
-\textit{\newline Example format: 10.prefix/suffix}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
-
-\category{2}{Screening}
-
-\step{Coded}{Whether the experience aspects (affect, behavior, cognition, and desire) are coded.}{Screening}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{missing \dotfill[0]}
-	\item \makebox[5cm]{coded \dotfill[1]}
-\end{itemize}
-\divider
-
-\marginpar{
-\vspace{1.4em}
-Missingness Explanations
+\vspace{-4em}
+Psychological Need Explanations
 
@@
 \midrule
-1 & manuscript is in a language other than English. \\
-2 & rural-urban, second generation \\
-3 & focus on dominant group \\
-4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
-5 & migration status, length of residence  \\
-6 & only discusses theory of others. \\
-7 & not accessible via library services \\
-8 & not accessible via library services \\
-9 & not accessible via library services \\
-10 & not accessible via library services \\
-11 & not accessible via library services \\
-12 & not accessible via library services \\
+0 & ``I just wanted to pass the time.'' \\
+1 & ``I wanted to connect with someone.'' \\
+2 & ``I wanted to share experiences and build rapport.'' \\
 \bottomrule
@@
 }
+\begin{itemize}
+	\item \parbox[t]{8.5cm}{No psychological need \dotfill[0]}
+	\item \parbox[t]{8.5cm}{Vague or general mention \dotfill[1]}
+    \item \parbox[t]{8.5cm}{Clear mention \dotfill[2]}
+\end{itemize}
 
+\vspace{1em}
 \divider
-\step{MissingNote}{If experience aspects (affect, behavior, cognition, desire) not coded, provide the reason for missing coding.}{Screening}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{not English \dotfill[1]}
-	\item \makebox[5cm]{not migration \dotfill[2]}
-	\item \makebox[5cm]{not migrant \dotfill[3]}
-	\item \makebox[5cm]{not acculturation \dotfill[4]}
-	\item \makebox[5cm]{not ABCD \dotfill[5]}
-	\item \makebox[5cm]{not measured \dotfill[6]}
-	\item \makebox[5cm]{items not accessible \dotfill[7]}
-	\item \makebox[5cm]{thesis not accessible \dotfill[8]}
-	\item \makebox[5cm]{article not accessible \dotfill[9]}
-	\item \makebox[5cm]{book not accessible \dotfill[10]}
-	\item \makebox[5cm]{chapter not accessible \dotfill[11]}
-	\item \makebox[5cm]{poster not accessible \dotfill[12]}
-\end{itemize}
-\divider
+\vspace{1em}
 
-\step{Comment}{Any necessary comments by the coder.}{Screening}
-\textit{This can include additional information about the format and content of the theoretical work, as well as information on the missingness or accessibility.}
+\step{Comment}{Any necessary comments of the coder.}{context}
+\textit{This can include additional information about ambiguous, uncertain, or exceptional codings.}
 \vspace{1.5em}
 \ruleandname{character string}{10cm}
-\divider
-
-\category{3}{Scale Information}
-
-\step{Item}{Extract all available items of the scale.}{Scale Information}
-\textit{List all items of the scale as they are presented in the manuscript. If scoring is inconsistent consider adding basic scoring information to the items. Please number the items for clarity.}
-\vspace{1.5em}
-\par
-\hspace*{1pt}1. \\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}2. \\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}3. \\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}4. \\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}5. \\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}6. \\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}7. \\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}8. \\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}9. \\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}... .\\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}\textit{N}.\\\rule[0.95em]{6cm}{\rulewidth}\\
-\vspace{\dimexpr-\baselineskip-\ruleandnamegap}
-\noindent{\namefont character string}\par
-\divider
-
-\step{NItem}{Number of items in the scale.}{Scale Information}
-\textit{The total number of items should match the highest numbering in the `Item' variable. If that is not the case please explain in the `Note' section.}
-\vspace{1.5em}
-\par
-\rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \par
-\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
-\noindent{\namefont numeric}\par
-\divider
-
-\step{NSubScales}{Number of sub-scales identified by the authors.}{Scale Information}
-\textit{If multiple sets of sub-scales are proposed please elaborate in the `Note' section.}
-\vspace{1.5em}
-\par
-\rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \par
-\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
-\noindent{\namefont numeric}\par
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\step{ResponseRange}{Number of response options.}{Scale Information}
-\textit{If multiple response ranges are used please specify in the `Note' section.}
-\vspace{1.5em}
-\par
-\rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \par
-\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
-\noindent{\namefont numeric}\par
-\divider
-
-\step{ResponseRangeAnchors}{List the anchors associated with the reported the response range.}{Scale Information}
-\textit{If multiple sets of anchors are used please specify in the `Note' section.\\ Example format for range \{-2, 2\}:}
-\vspace{1.5em}
-\par
-\hspace*{1pt}\textit{\textcolor{body}{-2: very negative}}\\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{1pt}\textit{\textcolor{body}{-1: negative}}\\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{4pt}\textit{\textcolor{body}{0: neutral}}\\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{4pt}\textit{\textcolor{body}{1: positive}}\\\rule[0.95em]{6cm}{\rulewidth}\\
-\hspace*{4pt}\textit{\textcolor{body}{2: very positive}}\\\rule[0.95em]{6cm}{\rulewidth}\\
-\vspace{\dimexpr-\baselineskip-\ruleandnamegap}
-\noindent{\namefont character string}\par
-\divider
-
-\step{Note}{Any necessary coder comments about the scale.}{Scale Information}
-\textit{Any notes on the scale, including the structure of the scale (e.g., names of the sub-scales).}
-\vspace{1.5em}
-\ruleandname{character string}{10cm}
-\divider
-
-\category{4}{Experience}
-\marginpar{
-\vspace{3em}
-Selected Affect Concept Examples:
-\begin{itemize}
-    \item loneliness
-    \item feeling at home
-    \item satisfaction with life
-    \item pride
-    \item comfortableness
-    \item joy
-    \item ease
-    \item well-being
-    \item worry
-    \item trust
-\end{itemize}
-}
-
-\step{Affect}{Whether the scale includes affect.}{Experience}
-\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of affect.
-Please consider affect at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `affect' or `affective' directly.\\
-\textbf{Construct:} the authors might refer to affective constructs such as `emotion' or `mood'.\\
-\textbf{Concept:} the authors might refer to affective concepts such as individual emotions, including `pride' or `loneliness'.\\
-\textbf{Operationalization:} the authors might also include affective conceptualizations in their items, such as `I feel ...' or `I enjoy ...'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\marginpar{
-\vspace{3em}
-Selected Behavior Concept Examples:
-\begin{itemize}
-    \item language use
-    \item civic participation (voting, ...)
-    \item performance (work, ...)
-    \item media consumption
-    \item education
-    \item peer contacts
-    \item food consumption
-    \item cultural habits (holidays ...)
-    \item delinquency
-    \item marriage
-\end{itemize}
-}
-
-\step{Behavior}{Whether the scale includes behavior(s).}{Experience}
-\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of behaviors.
-Please consider behaviors at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `behavior' or `behavioral' directly.\\
-\textbf{Construct:} the authors might refer to behavioral constructs such as `activities' or `habits'.\\
-\textbf{Concept:} the authors might refer to behavioral concepts, such as `language use' or `media consumption'.\\
-\textbf{Operationalization:} the authors might also include behavioral conceptualizations in their items, such as `I do ...' or `I speak ...'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\marginpar{
-\vspace{3em}
-Selected Cognition Concept Examples:
-\begin{itemize}
-    \item ethnic identification
-    \item cultural values
-    \item acculturation orientation
-    \item preferences (food, friends, ...)
-    \item knowledge
-    \item importance ratings
-    \item inner thought language
-    \item perceived obligations
-    \item beliefs
-    \item stereotypes
-\end{itemize}
-}
-
-\step{Cognition}{Whether the scale includes cognition(s).}{Experience}
-\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of cognitions.
-Please consider cognitions at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `cognition' or `cognitive' directly.\\
-\textbf{Construct:} the authors might refer to cognitive constructs such as `knowledge' or `memories'.\\
-\textbf{Concept:} the authors might refer to cognitive concepts, such as `cultural values' or `ethnic identification'.\\
-\textbf{Operationalization:} the authors might also include cognitive conceptualizations in their items, such as `I think ...' or `I prefer ...'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\marginpar{
-\vspace{3em}
-Selected Desire Concept Examples:
-\begin{itemize}
-    \item competence
-    \item independence
-    \item self-coherence
-    \item belonging
-    \item achievement
-    \item justice
-    \item growth
-    \item respect
-    \item acceptance
-    \item identity continuity
-\end{itemize}
-}
-
-\step{Desire}{Whether the scale includes desire(s).}{Experience}
-\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of desires.
-Please consider desires at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `desire' or `motivational' directly.\\
-\textbf{Construct:} the authors might refer to desire constructs such as `needs' or `goals'.\\
-\textbf{Concept:} the authors might refer to desire concepts, such as `belonging' or `competence'.\\
-\textbf{Operationalization:} the authors might also include motivational conceptualizations in their items, such as `I want ...' or `I need ...'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\marginpar{
-\vspace{1em}
-Complexity Explanations
-
-\begin{tabular*}{6.2cm}{>{\centering\arraybackslash}p{0.08\linewidth} 
->{\raggedright\arraybackslash}p{0.76\linewidth}}
-%\begin{tabular}
-\toprule
-\# & Examples / Explanation\\
-\midrule
-1 & focused on a concept that includes multiple aspects (e.g., satisfaction, distress) \\
-2 & aspects included as parts of a scale \\
-3 & aspects measured as independent conceptualizations of acculturation \\
-4 & aspects included as part of a review of multiple conceptualizations \\
-N/A & only one aspect was included  \\
-\bottomrule
-\end{tabular*}
-}
-
-\step{TypeComplexity}{Type of aspect combination [if multiple experience aspects included].}{Experience}
-\textit{If more than one experience aspect was coded, please specify how the multiple aspects were included.
-The scales might include the aspects either independently as parts of the acculturation conceptualization or as part of a scale or proxy measure that includes multiple experience aspects.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{complex concept \dotfill[1]}
-	\item \makebox[5cm]{complex scale \dotfill[2]}
-	\item \makebox[5cm]{independent \dotfill[3]}
-	\item \makebox[5cm]{review \dotfill[4]}
-	\item \makebox[5cm]{not applicable \dotfill[N/A]}
-\end{itemize}
-\divider
-
-\category{5}{Data Collection}
-
-\step{Measurement}{Levels of measurement.}{Data Collection}
-\textit{Identify the measurement level of the scales.
-Are the items (or at least the resulting scale) measured as a continuous dimension or is the resulting measure a classification into groups.
-Indicate `categorical' even if there is an order to the groups.
-Select `both' if a the measure includes both continuous and categorical measures.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{continuous \dotfill[1]}
-	\item \makebox[5cm]{categorical \dotfill[2]}
-	\item \makebox[5cm]{both \dotfill[3]}
-\end{itemize}
-\divider
-
-\category{6}{Focus}
-
-\step{domainScale}{Situational focus of the scale.}{Focus}
-\textit{To identify the author(s) situational focus in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of life domains.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[6cm]{spirituality/religion \dotfill[1]}
-    \item \makebox[6cm]{home/family \dotfill[2]}
-    \item \makebox[6cm]{health/care \dotfill[3]}
-    \item \makebox[6cm]{administrative/legal matters \dotfill[4]}
-    \item \makebox[6cm]{entertainment/media \dotfill[5]}
-    \item \makebox[6cm]{work/money/finances \dotfill[6]}
-    \item \makebox[6cm]{education/school \dotfill[7]}
-    \item \makebox[6cm]{transport/travel \dotfill[8]}
-    \item \makebox[6cm]{recreation/sport/art/friends \dotfill[9]}
-    \item \makebox[6cm]{community/politics \dotfill[10]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\category{7}{Sample}
-
-\step{Sample}{The sample recruited by the authors.}{Sample}
-\textit{Please specify the sample requirements of the authors. If non are provided use the code `general' to indicate that the general population of migrants was targeted.}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
-
-\step{MigrationTime}{When in the migration process acculturation was assessed?}{Sample}
-\textit{Please specify whether the authors considered one or multiple time-points in the migration process. And if multiple are assessed, please specify which time-points were included.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[6cm]{potential \dotfill[1]}
-    \item \makebox[6cm]{pre \dotfill[2]}
-    \item \makebox[6cm]{post \dotfill[3]}
-    \item \makebox[6cm]{pre \& post \dotfill[4]}
-    \item \makebox[6cm]{N/A \dotfill[5]}
-\end{itemize}
-\divider
-
-\step{IncludesMajority}{Whether members of the dominant group in the host society were considered.}{Sample}
-\textit{Please specify whether members of the dominant group in the host society were included for the scale validation.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[6cm]{no \dotfill[0]}
-    \item \makebox[6cm]{yes \dotfill[1]}
-\end{itemize}
-\divider
-
-\step{HostCountry}{Country or countries of settlement considered for validation.}{Sample}
-\textit{Please specify the host country or countries that were included in the validation.
-This country is usually the country of settlement for the migrant group.
-If no country is focused on in particular, please use the code `any' to indicate that any host country was allowed as part of the sampling strategy.}
-\vspace{1.5em}
-
-\rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth}\\
-\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
-{\namefont character string\hspace{2.08cm}character string\hspace{2.08cm}character string}\par
-\divider
-
-\step{OriginCountry}{Country or countries of origin considered for validation.}{Sample}
-\textit{Please specify the origin country or countries that were included in the validation.
-These countries usually the country of origin for the migrant group.
-If no country is focused on in particular, please use the code `any' to indicate that migrants from any country were included as part of the sampling strategy.}
-\vspace{1.5em}
-
-\rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth}\\
-\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
-{\namefont character string\hspace{2.08cm}character string\hspace{2.08cm}character string}\par
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\marginpar{
-\need{Empirical Dataset}
-\resizebox{7cm}{!}{
-    % For organization, I like to keep the actual card in a separate file:
-    \input{Supplemental Material A - Coding Protocol/margins/FactSheetEmpirical}
-    }
-}
-\need{Empirical Literature}
-\category{1}{Bibliographic Information}
-
-\begin{topbot}
-\subsubsection*{Additional Bibliographic Data}
-A range of additional bibliographic data fields is available in the dataset.
-These fields include the `type of publication', `year of publication', `author names', `title', `abstract', `DOI', `duplicate filters', as well as a range of publisher information.
-These fields are generated during the literature search by the bibliographic database and don't need any input from the coders.
-Additional information on the format and content of these fields is available in the `Codebook'.
-\end{topbot}
-
-\vspace*{2em}
-
-\step{CitationKey}{Add BibTeX citation key for the empirical manuscript.}{Bibliographic Information}
-\textit{The citation key can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
-\textit{\newline Example format: Author2019}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
-
-\category{2}{Screening}
-
-\step{TitleScreening}{Whether manuscript should be excluded during title screening.}{Screening}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{excluded \dotfill[0]}
-	\item \makebox[5cm]{included \dotfill[1]}
-\end{itemize}
-\divider
-
-\marginpar{
-\vspace{1.4em}
-Missingness Explanations
-
-\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
->{\raggedright\arraybackslash}p{0.75\linewidth}}
-%\begin{tabular}
-\toprule
-\# & Examples / Explanation\\
-\midrule
-1 & manuscript is in a language other than English. \\
-2 & rural-urban, second generation \\
-3 & focus on dominant group \\
-4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
-5 & migration status, length of residence  \\
-6 & only discusses theory of others. \\
-7 & not accessible via library services \\
-8 & not accessible via library services \\
-9 & not accessible via library services \\
-10 & not accessible via library services \\
-11 & not accessible via library services \\
-12 & not accessible via library services \\
-\bottomrule
-\end{tabular*}
-}
-
-\divider
-\step{TitleNote}{If excluded during `TitleScreening', provide the reason for exclusion.}{Screening}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{not English \dotfill[1]}
-	\item \makebox[5cm]{not migration \dotfill[2]}
-	\item \makebox[5cm]{not migrant \dotfill[3]}
-	\item \makebox[5cm]{not acculturation \dotfill[4]}
-	\item \makebox[5cm]{not ABCD \dotfill[5]}
-	\item \makebox[5cm]{not measured \dotfill[6]}
-	\item \makebox[5cm]{items not accessible \dotfill[7]}
-	\item \makebox[5cm]{thesis not accessible \dotfill[8]}
-	\item \makebox[5cm]{article not accessible \dotfill[9]}
-	\item \makebox[5cm]{book not accessible \dotfill[10]}
-	\item \makebox[5cm]{chapter not accessible \dotfill[11]}
-	\item \makebox[5cm]{poster not accessible \dotfill[12]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{1em}
-
-\step{AbstractScreening}{Whether manuscript was excluded during abstract screening.}{Screening}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{excluded \dotfill[0]}
-	\item \makebox[5cm]{included \dotfill[1]}
-\end{itemize}
-
-\marginpar{
-\vspace{1.4em}
-Missingness Explanations
-
-\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
->{\raggedright\arraybackslash}p{0.75\linewidth}}
-%\begin{tabular}
-\toprule
-\# & Examples / Explanation\\
-\midrule
-1 & manuscript is in a language other than English. \\
-2 & rural-urban, second generation \\
-3 & focus on dominant group \\
-4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
-5 & migration status, length of residence  \\
-6 & only discusses theory of others. \\
-7 & not accessible via library services \\
-8 & not accessible via library services \\
-9 & not accessible via library services \\
-10 & not accessible via library services \\
-11 & not accessible via library services \\
-12 & not accessible via library services \\
-\bottomrule
-\end{tabular*}
-}
-\divider
-
-\step{AbstractNote}{If excluded during `AbstractScreening', provide the reason for exclusion.}{Screening}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{not English \dotfill[1]}
-	\item \makebox[5cm]{not migration \dotfill[2]}
-	\item \makebox[5cm]{not migrant \dotfill[3]}
-	\item \makebox[5cm]{not acculturation \dotfill[4]}
-	\item \makebox[5cm]{not ABCD \dotfill[5]}
-	\item \makebox[5cm]{not measured \dotfill[6]}
-	\item \makebox[5cm]{items not accessible \dotfill[7]}
-	\item \makebox[5cm]{thesis not accessible \dotfill[8]}
-	\item \makebox[5cm]{article not accessible \dotfill[9]}
-	\item \makebox[5cm]{book not accessible \dotfill[10]}
-	\item \makebox[5cm]{chapter not accessible \dotfill[11]}
-	\item \makebox[5cm]{poster not accessible \dotfill[12]}
-\end{itemize}
-\divider
-
-\step{Downloaded}{Whether full manuscript--text was downloaded.}{Screening}
-\textit{If this was not possible, please describe steps taken in the `Comment' code.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{not downloaded \dotfill[0]}
-	\item \makebox[5cm]{downloaded \dotfill[1]}
-\end{itemize}
-\divider
-
-\step{MissingABCD}{Whether experience aspects were coded in full text.}{Screening}
-\textit{Does the empirical study consider (i.e., measure) psychological acculturation?
-Please focus particularly on the measurement of acculturation, e.g., scale description, the (sub-)scale labels, as well as items.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{coded \dotfill[0]}
-	\item \makebox[5cm]{missing \dotfill[1]}
-\end{itemize}
-
-\marginpar{
-\vspace{1.4em}
-Missingness Explanations
-
-\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
->{\raggedright\arraybackslash}p{0.75\linewidth}}
-%\begin{tabular}
-\toprule
-\# & Examples / Explanation\\
-\midrule
-1 & manuscript is in a language other than English. \\
-2 & rural-urban, second generation \\
-3 & focus on dominant group \\
-4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
-5 & migration status, length of residence  \\
-6 & only discusses theory of others. \\
-7 & not accessible via library services \\
-8 & not accessible via library services \\
-9 & not accessible via library services \\
-10 & not accessible via library services \\
-11 & not accessible via library services \\
-12 & not accessible via library services \\
-\bottomrule
-\end{tabular*}
-}
-\divider
-
-\step{NoteMissing}{If excluded during full-text analysis, provide the reason for exclusion.}{Screening}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{not English \dotfill[1]}
-	\item \makebox[5cm]{not migration \dotfill[2]}
-	\item \makebox[5cm]{not migrant \dotfill[3]}
-	\item \makebox[5cm]{not acculturation \dotfill[4]}
-	\item \makebox[5cm]{not ABCD \dotfill[5]}
-	\item \makebox[5cm]{not measured \dotfill[6]}
-	\item \makebox[5cm]{items not accessible \dotfill[7]}
-	\item \makebox[5cm]{thesis not accessible \dotfill[8]}
-	\item \makebox[5cm]{article not accessible \dotfill[9]}
-	\item \makebox[5cm]{book not accessible \dotfill[10]}
-	\item \makebox[5cm]{chapter not accessible \dotfill[11]}
-	\item \makebox[5cm]{poster not accessible \dotfill[12]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\step{Comment}{Any necessary comments of the coder.}{Screening}
-\textit{This can include additional information about the format and content of the theoretical work, as well as information on the missingness or accessibility.}
-\vspace{1.5em}
-\ruleandname{character string}{10cm}
-\divider
-
-\category{3}{Experience}
-\marginpar{
-\vspace{3em}
-Selected Affect Concept Examples:
-\begin{itemize}
-    \item loneliness
-    \item feeling at home
-    \item satisfaction with life
-    \item pride
-    \item comfortableness
-    \item joy
-    \item ease
-    \item well-being
-    \item worry
-    \item trust
-\end{itemize}
-}
-
-\step{Affect}{Whether the studies included affect.}{Experience}
-\textit{To identify whether the author(s) included affective experiences in their study of acculturation, you can examine the study description, the methods section, the (sub-)scale labels, as well as items for self-identified mentions of affect.
-Please consider affect at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `affect' or `affective' directly.\\
-\textbf{Construct:} the authors might refer to affective constructs such as `emotion' or `mood'.\\
-\textbf{Concept:} the authors might refer to affective concepts such as individual emotions, including `pride' or `loneliness'.\\
-\textbf{Operationalization:} the authors might also include affective conceptualizations in their operationalizations, such as `I feel ...' or `I enjoy ...'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\marginpar{
-\vspace{3em}
-Selected Behavior Concept Examples:
-\begin{itemize}
-    \item language use
-    \item civic participation (voting, ...)
-    \item performance (work, ...)
-    \item media consumption
-    \item education
-    \item peer contacts
-    \item food consumption
-    \item cultural habits (holidays ...)
-    \item delinquency
-    \item marriage
-\end{itemize}
-}
-
-\step{Behavior}{Whether the studies included behavior(s).}{Experience}
-\textit{To identify whether the author(s) included affective experiences in their study of acculturation, you can examine the study description, the methods section, the (sub-)scale labels, as well as items for self-identified mentions of behaviors.
-Please consider behaviors at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `behavior' or `behavioral' directly.\\
-\textbf{Construct:} the authors might refer to behavioral constructs such as `activities' or `habits'.\\
-\textbf{Concept:} the authors might refer to behavioral concepts, such as `language use' or `media consumption'.\\
-\textbf{Operationalization:} the authors might also include behavioral conceptualizations in their operationalizations, such as `I do ...' or `I speak ...'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\marginpar{
-\vspace{3em}
-Selected Cognition Concept Examples:
-\begin{itemize}
-    \item ethnic identification
-    \item cultural values
-    \item acculturation orientation
-    \item preferences (food, friends, ...)
-    \item knowledge
-    \item importance ratings
-    \item inner thought language
-    \item perceived obligations
-    \item beliefs
-    \item stereotypes
-\end{itemize}
-}
-
-\step{Cognition}{Whether the studies included cognition(s).}{Experience}
-\textit{To identify whether the author(s) included affective experiences in their studies, you can examine the study description, the methods section, the (sub-)scale labels, as well as items for self-identified mentions of cognitions.
-Please consider cognitions at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `cognition' or `cognitive' directly.\\
-\textbf{Construct:} the authors might refer to cognitive constructs such as `knowledge' or `memories'.\\
-\textbf{Concept:} the authors might refer to cognitive concepts, such as `cultural values' or `ethnic identification'.\\
-\textbf{Operationalization:} the authors might include cognitive conceptualizations in their operationalization, such as `I think ...' or `I prefer ...'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\marginpar{
-\vspace{3em}
-Selected Desire Concept Examples:
-\begin{itemize}
-    \item competence
-    \item independence
-    \item self-coherence
-    \item belonging
-    \item achievement
-    \item justice
-    \item growth
-    \item respect
-    \item acceptance
-    \item identity continuity
-\end{itemize}
-}
-
-\step{Desire}{Whether the studies included desire(s).}{Experience}
-\textit{To identify whether the author(s) included affective experiences in their study, you can examine the study description, the methods section, the (sub-)scale labels, as well as items for self-identified mentions of desires.
-Please consider desires at the following three levels of abstraction:\\
-\textbf{Aspect:} the authors might refer to `desire' or `motivational' directly.\\
-\textbf{Construct:} authors might include desire constructs such as `needs' or `goals'.\\
-\textbf{Concept:} authors might refer to desire concepts, such as `belonging' or `competence'.\\
-\textbf{Operationalization:} the authors might include motivational conceptualizations in their study, such as `I want ...' or `I need ...'.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{included \dotfill[1]}
-	\item \makebox[5cm]{not included \dotfill[–]}
-\end{itemize}
-\divider
-
-\marginpar{
-\vspace{1em}
-Complexity Explanations
-
-\begin{tabular*}{6.2cm}{>{\centering\arraybackslash}p{0.08\linewidth} 
->{\raggedright\arraybackslash}p{0.76\linewidth}}
-%\begin{tabular}
-\toprule
-\# & Examples / Explanation\\
-\midrule
-1 & focused on a concept that includes multiple aspects (e.g., satisfaction, distress) \\
-2 & aspects included as parts of a scale \\
-3 & aspects measured as independent conceptualizations of acculturation \\
-4 & aspects included as part of a review of multiple conceptualizations \\
-N/A & only one aspect was included  \\
-\bottomrule
-\end{tabular*}
-}
-
-\step{TypeComplexity}{Type of aspect combination [if multiple experience aspects included].}{Experience}
-\textit{If more than one experience aspect was coded, please specify how the multiple aspects were included.
-The study might include the aspects either independently as parts of the acculturation conceptualization or as part of a scale or proxy measure that includes multiple experience aspects.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{complex concept \dotfill[1]}
-	\item \makebox[5cm]{complex scale \dotfill[2]}
-	\item \makebox[5cm]{independent \dotfill[3]}
-	\item \makebox[5cm]{review \dotfill[4]}
-	\item \makebox[5cm]{not applicable \dotfill[N/A]}
-\end{itemize}
-\divider
-
-\category{4}{Data Collection}
-
-\step{empirical}{Whether the manuscript presented empirical conceptualization(s) of acculturation.}{Data Collection}
-\textit{Please specify whether the authors collected (observable) data as part of their investigation.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{empirical \dotfill[1]}
-	\item \makebox[5cm]{non-empirical \dotfill[0]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\step{Method}{Type of empirical data collected.}{Data Collection}
-\textit{If empirical data was collected, what kind of data was collected or discussed by the author(s)?}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{quantitative \dotfill[1]}
-	\item \makebox[5cm]{qualitative \dotfill[2]}
-	\item \makebox[5cm]{mixed method \dotfill[3]}
-	\item \makebox[5cm]{meta-analysis \dotfill[4]}
-	\item \makebox[5cm]{review \dotfill[5]}
-\end{itemize}
-\divider
-
-\step{MeasureDefinition}{Name of the scale used or the concepts measured as proxies.}{Data Collection}
-\textit{Please specify the name of the measurement tool (e.g., scale) used by the authors.
-If the scale is not yet in the scale database, please look up the validation of the scale and add it to the database.
-Do the same for proxy measures of acculturation.}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
-
-\step{MeasurementLevels}{Levels of measurement.}{Data Collection}
-\textit{Identify the measurement level of the empirical scales.
-Are the items (or at least the resulting scale) measured as a continuous dimension or is the resulting measure a classification into groups.
-Indicate `categorical' even if there is an order to the groups.
-Select `both' if a the measure includes both continuous and categorical measures.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{continuous \dotfill[1]}
-	\item \makebox[5cm]{categorical \dotfill[2]}
-	\item \makebox[5cm]{both \dotfill[3]}
-\end{itemize}
-\divider
-
-\category{5}{Focus}
-
-\marginpar{
-Acculturation Term Examples:
-\begin{itemize}
-    \item acculturation
-    \item enculturation
-    \item transculturation
-    \item assimilation
-    \item integration
-    \item social integration
-    \item cultural adaptation
-    \item cultural adjustment
-    \item cultural transition
-\end{itemize}
-}
-
-\step{term}{Acculturation term used by authors.}{Data Collection}
-\textit{Please note which term the author(s) used to refer to ``psychological acculturation" (i.e., ``changes an individual experiences as a result of being in contact with other cultures").}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
-
-\step{domainPaper}{Focus concept of the manuscript.}{Data Collection}
-\textit{Please specify the main focus of the manuscript.
-The focus is often clearest in the dependent variable within the model or analysis but should also be clearly stated within the title, abstract, or introduction.
-The focus could be `acculturation' but it could also be something else (that might, for example, be predicted by acculturation; e.g., depression).}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\step{domainScale}{Situational focus of the acculturation conceptualization.}{Focus}
-\textit{To identify the author(s) situational focus in their conceptualization of psychological acculturation, you can examine the manuscript for self-identified mentions of life domains.
-Please place a particular focus on the study description, as well as the methodology, including scale descriptions, the (sub-)scale labels, and the  items themselves.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[6cm]{spirituality/religion \dotfill[1]}
-    \item \makebox[6cm]{home/family \dotfill[2]}
-    \item \makebox[6cm]{health/care \dotfill[3]}
-    \item \makebox[6cm]{administrative/legal matters \dotfill[4]}
-    \item \makebox[6cm]{entertainment/media \dotfill[5]}
-    \item \makebox[6cm]{work/money/finances \dotfill[6]}
-    \item \makebox[6cm]{education/school \dotfill[7]}
-    \item \makebox[6cm]{transport/travel \dotfill[8]}
-    \item \makebox[6cm]{recreation/sport/art/friends \dotfill[9]}
-    \item \makebox[6cm]{community/politics \dotfill[10]}
-\end{itemize}
-\divider
-
-\category{6}{Sample}
-
-\step{Sample}{The sample recruited by the authors.}{Sample}
-\textit{Please specify the sample requirements of the authors. If non are provided use the code `general' to indicate that the general population of migrants was targeted.}
-\vspace{1.5em}
-\ruleandname{character string}{5cm}
-\divider
-
-\step{MigrationTime}{When in the migration process acculturation was assessed?}{Sample}
-\textit{Please specify whether the authors considered one or multiple time-points in the migration process. And if multiple are assessed, please specify which time-points were included.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[6cm]{potential \dotfill[1]}
-    \item \makebox[6cm]{pre \dotfill[2]}
-    \item \makebox[6cm]{post \dotfill[3]}
-    \item \makebox[6cm]{pre \& post \dotfill[4]}
-    \item \makebox[6cm]{N/A \dotfill[5]}
-\end{itemize}
-\divider
-
-\step{IncludesMajority}{Whether members of the dominant group in the host society were considered.}{Sample}
-\textit{Please specify whether members of the dominant group in the host society were included for the study.
-If they were included please note in the `comment' code whether acculturation was measured for the dominant group.}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[6cm]{no \dotfill[0]}
-    \item \makebox[6cm]{yes \dotfill[1]}
-\end{itemize}
-\divider
-
-\clearpage
-\vspace*{2em}
-
-\step{HostCountry}{Country or countries of settlement considered for study.}{Sample}
-\textit{Please specify the host country or countries that were included in the study.
-This country is usually the country of settlement for the migrant group.
-If no country is focused on in particular, please use the code `any' to indicate that any host country was allowed as part of the sampling strategy.}
-\vspace{1.5em}
-
-\rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth}\\
-\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
-{\namefont character string\hspace{2.08cm}character string\hspace{2.08cm}character string}\par
-\divider
-
-\step{OriginCountry}{Country or countries of origin considered for study.}{Sample}
-\textit{Please specify the origin country or countries that were included in the study.
-These countries are usually the country of origin for the migrant group.
-If no country is focused on in particular, please use the code `any' to indicate that migrants from any country were included as part of the sampling strategy.}
-\vspace{1.5em}
-
-\rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth} , \rule{3cm}{\rulewidth}\\
-\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
-{\namefont character string\hspace{2.08cm}character string\hspace{2.08cm}character string}\par
-\divider
-
-\category{7}{Analysis}
-
-\marginpar{
-Analysis Type Examples:
-\begin{itemize}
-    \item cluster analysis
-    \item correlation analysis
-    \item lagged regression
-    \item cross-lagged panel analysis
-    \item longitudinal analysis
-    \item mean differences
-    \item participant selection
-    \item path analysis
-    \item prevalence rates
-    \item regression (incl. PROCESS macro)
-    \item structural equation modeling
-    \item social network analysis
-    \item validation analyses
-    \item content analysis
-    \item open coding 
-    \item axial coding
-    \item phenomenological praxis
-    \item constant comparative coding
-\end{itemize}
-}
-
-\step{MainAnalysis}{Type of data analysis conducted by the authors.}{Analysis}
-\textit{Please specify the type of analysis conducted by the authors.
-If multiple analyses were conducted please report the `main' analysis.
-The main analysis offers the most direct test of the hypotheses and lends the most weight during the interpretation and summary of the results.
-(The main analysis is often the last and most complex analysis.)}
-\vspace{1.5em}
-\ruleandname{character string}{5cm} 
-\divider
-
-\step{VariableType}{The place in the model that acculturation takes [if quantitative analysis]}{Analysis}
-\textit{If a quantitative analysis was conducted please specify the variable type of acculturation (during the main analysis, identified during `MainAnalysis').}
-\vspace{0.5em}
-\begin{itemize}
-	\item \makebox[5cm]{Control\dotfill[1]}
-    \item \makebox[5cm]{Correlation\dotfill[2]}
-    \item \makebox[5cm]{Dependent\dotfill[3]}
-    \item \makebox[5cm]{Mediator\dotfill[4]}
-    \item \makebox[5cm]{Moderator\dotfill[5]}
-    \item \makebox[5cm]{N/A\dotfill[6]}
-    \item \makebox[5cm]{Predictor\dotfill[7]}
-    \item \makebox[5cm]{Predictor \& Dependent\dotfill[8]}
-    \item \makebox[5cm]{selection criterion\dotfill[9]}
-\end{itemize}
 \divider

### 2023-05-19 Supplemental Material B - Coding Protocol/margins/FactSheet.tex
coding protocol filled

--- 2023-05-16 Supplemental Material B - Coding Protocol/margins/FactSheetEmpirical.tex
@@
-\input{Supplemental Material A - Coding Protocol/margins/empNums}
-
 \sffamily
@@
 \NFrule
-\NFtext{\textbf{Dataset} Empirical Acculturation Literature}\\
-\NFtext{\textbf{Instances Per Dataset} \nEmp\ empirical studies from \nAllEmp\ unique manuscripts}\\
+\NFtext{\textbf{Dataset} Acculturation over Time Studies}\\
+\NFtext{\textbf{Instances Per Dataset} \hl{X,XXX} free text responses in \hl{XX} topics}\\
 
@@
 \NFrule
-\NFelement{Original Authors}{}{Kreienkamp, Bringmann, Engler, de Jonge, Epstude}\\
-\NFelement{Original Use Case}{}{collection of empirical works}\\
-\NFelement{Original Funding}{}{None}\\
+\NFelement{Original Authors}{}{Kreienkamp, Agostini, Bringmann, de Jonge, Epstude}\\
+\NFelement{Original Use Case}{}{cultural adaptation in daily interactions}\\
+\NFelement{Original Funding}{}{No specific}\\
 
@@
 \NFrule
-\NFelement{Sample or Complete}{}{Sample}\\
-\NFelement{Missing Data}{}{\percEmpInaccess\% not accessible \\\hfill(\percEmpItemInaccess\% items \& \percEmpThesisInaccess\% theses not accessible)\\\hfill+ see Screening}\\
-\NFelement{Sensitive Information }{}{author information}\\
+\NFelement{Sample or Complete}{}{Complete}\\
+\NFelement{Missing Data}{}{\hl{X.X}\% excluded}\\
+\NFelement{Sensitive Information }{}{free text responses}\\
 %\NFelement{Additional Field}{}{Info}\\
@@
 \NFrule
-\NFelement{Sampling Strategy}{}{systematic review (see search strategy)}\\
-\NFelement{Ethical Review}{}{not applicable}\\
+\NFelement{Sampling Strategy}{}{experience sampling method (ESM)}\\
+\NFelement{Ethical Review}{}{University masked for Peer review}\\
 \NFelement{Author Consent}{}{not applicable}\\
@@
 \NFrule
-\NFelement{Notable Uses}{}{this systematic review}\\
-\NFelement{Other Uses}{}{openly accessible for further analysis}\\
+\NFelement{Notable Uses}{}{non published data}\\
+\NFelement{Other Uses}{}{partially open for further analysis}\\
 \NFelement{Distribution}{}{available on OSF and GitHub}\\
@@
 \NFRULE
-\NFline{Types of publications \hfill\% of manuscripts*}\\
+\NFline{Sample Sizes per study \hfill\% of total*}\\
 \NFrule
-\NFelement{journal articles}{\nJournal\,manuscripts}{\percJournal\%}\\
+\NFelement{Study 1}{\hl{X,XXX} interactions of \hl{X,XXX} measurements}{\hl{XX.X}\%}\\
 \NFrule
-\NFelement{theses}{\nThesis\,manuscripts}{\percThesis\%}\\
+\NFelement{Study 2}{\hl{X,XXX} interactions of \hl{X,XXX} measurements}{\hl{XX.X}\%}\\
 \NFrule
-%\NFelement{book chapters}{6\,manuscripts}{1.1\%}\\
-%\NFrule
+\NFelement{Study 3}{\hl{X,XXX} interactions of \hl{X,XXX} measurements}{\hl{XX.X}\%}\\
+% \NFrule
 %\NFelement{Another}{count}{XX\%}\\
 %\NFrule
-\NFentry{book chapters \percChapter\%} \\
+% \NFentry{we focus on outgroup interactions for this analysis} \\
 %\NFentry*{framework 2.9\%}\\
 %\NFentry{Red 1.5\%}\\
-%\NFrule
-%\NFtext{As identified by the author(s) of the theoretical manuscripts (also see `FrameworkTheoryModel' code).}\\
 \NFrule
-\NFtext{* Based on final dataset after screening.}
+\NFtext{For the analysis using this coding we focused on outgroup interactions only (also see `introduction').}\\
+\NFrule
+\NFtext{* based on outgroup interaction responses.}
 \end{tabular}}

### 2023-05-26 Methods-and-Results.Rmd
power sim re-added and robustness analyses extended (revision)

@@
 Using a multilevel regression, we find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
-Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by using centered predictors and reintroducing the means as level two predictors (\citealp{Yaremych2021}; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by using centered predictors and reintroducing the means as level two predictors (\citealp{yaremych2021a}; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
 This is unusual and might indicate that the effect is very consistent across participants.
@@
 
-\section{Robustness, Stability, and Embeddedness across Studies}
-
-Beyond the individual results of the three studies, we conducted three additional analyses to test the broader cross-study claims and contextualize our results.
-In particular, we aimed to gain a broader picture of the individual results by considering them jointly.
-We also leveraged the data from all participants to test between-participant contact effects and explore the content of the participants' situational contact needs.
+\section{Stability, Robustness, and Embeddedness across Studies}
+
+Beyond the individual results of the three studies, we conducted a number additional analyses to test the broader cross-study claims, account for alternative models, and contextualize our results.
+Jointly, these stability, robustness, and embeddedness analyses seek to strengthen our confidence in the results.
 
 \subsection{Stability}
+We ran two analyses that tested the stability of our results.
+We first assess the consistency of the results reported in the three studies and use a meta-analytic approach to gauge the general effect sizes.
+The second stability analysis we conduct seeks to asses the extend to which the within person contemporaneous effects extend to an aggregated version that mirrors the many cross-sectional recall studies.
+
+\subsubsection{Consistency}
 We first assessed the stability of our main analyses across the three studies.
@@
 Being among the first to assess the contact hypothesis using real-life intensive longitudinal data, we extend cross-sectional findings to individual-level assessments.
-When looking at the fulfillment of core needs during intergroup contacts, we find that the motivational mechanism is consistently a meaningful predictor of outgroup attitudes and interaction quality perceptions (see \fgrref[ A and B]{fig:AllportNeedFulfillment}).
+When looking at the fulfillment of core needs during intergroup contacts, we find that the motivational mechanism is consistently a meaningful predictor of  interaction quality perceptions and outgroup attitudes (see \fgrref[ A and B]{fig:AllportNeedFulfillment}).
 We also see that the effect of core need fulfillment on outgroup attitudes is strongly reduced when modeled together with interaction quality perceptions, supporting our assertion that interaction quality offers a psychological mechanism for the direct effect (see \fgrref[-C]{fig:AllportNeedFulfillment}).
 
-\subsection{General contact hypothesis}
+<!-- \subsection{General contact hypothesis} -->
+\subsubsection{Aggregated Analysis}
 ```{r join data sets for analysis, include=FALSE}
@@
 
+A second stability test is checking whether the within person effects translate to a broader aggregated between subjects effect, which would mirror common cross-sectional practices.
 During the main analyses, we have thus far shown that participants held more positive outgroup attitudes following intergroup contacts and that perceived interaction quality was associated with more positive outgroup attitudes following an intergroup contact.
@@
 
-\subsection{Contact key need content}
-Finally, we used the qualitative data from the participants’ self-identified core needs to contextualize the results of our main analysis.
+\subsection{Robustness}
+To check for spurious relationships, we test three additional models.
+These three models assess whether the effect is indeed specific to intergroup contact, whether the need fulillment effect is a affected by whether the contact was planned or accidental, and whether the motivational mechanism also holds direct well-being benefits for the minority members.
+We describe the full methods and results for the robustness analyses in \appref{app:AppendixRobustness}.
+We use a two-staged analysis approach for the robustness analyses.
+We first test the model `globally' --- across the three studies --- in a three level multilevel regression (i.e., measurements nested within participants, and participants nested within studies).
+Only in a second step do check for study-specific idiosyncrasies.
+
+\subsubsection{Contact specific}
+To ensure that the core need fulfillment is outgroup contact specific, we return to the full sample of intensive longitudinal measurements and test whether there is an interaction effect of outgroup contact (vs.
+no outgroup contact) and core need fulfillment.
+We expected that the effect of core need fulfillment on outgroup attitudes is specific to outgroup interactions and not merely due to a more need-fulfilled life in general.
+We find that \hl{...}.
+
+\subsubsection{Interaction intend}
+To test whether the need mechanism was affected by whether the interaction was accidental or planned we ran an exploratory moderation analysis using the participants' ratings of how much they perceived the interaction as 'accidental'.
+It should be noted at this point, that in order to keep the ESM surveys short, we asked our participants to focus on most the important interaction (i.e., "\textit{The following questions will be about the interaction \underline{you consider most significant}.}"''"; emphasis as in original).
+This was also reflected in a relatively low average and consistent right skew of the 'accidental' item.
+Nonetheless, there remained a substantial variance in the item and we continued with the moderation analysis.
+We find that \hl{...}.
+
+\subsubsection{Well-being outcome}
+Given the well-established criticism that more positive outgroup attitudes might not always be beneficial for minority group members \citep[e.g.,][]{reimer2023}, we conducted an additional exploratory analysis assessing the effect of need fulfilling outgroup interactions on reported well-being.
+Experienced well-being is a common indicator of health and an important life quality measurement in itself, especially for migrants or other minority groups \citep[e.g.,][]{bhugra2011}.
+We find that \hl{...}.
+The analysis, thus, adds weight to the importance of considering the need fulfillment experiences when it comes to outgroup interactions.
+
+\subsection{Embeddedness}
+To embed our results further, we also considered the content and types of needs that participants reported during the study.
+For these embeddedness analyses, we first assessed the self-reported motives of the participants and then also control the commonly considered self-determination theory needs.
+
+\subsubsection{Contact need content}
+We used the qualitative data from the participants’ self-identified core needs to contextualize the results of our main analysis.
 However, because our participants jointly reported on thousands of intergroup contacts, it would not have been feasible to analyze these qualitative responses in a traditional qualitative content analysis.
@@
 In its essence, BERT is a framework that allows users to codify every word in relation to every other word within a large set of documents.
-We extracted 47 topics from the 2,983 interaction goal free-text entries --- a relatively large number of topics.
+We extracted 47 topics from the 2,983 interaction goal free-text entries (after duplicate removal) --- a relatively large number of topics.
 The higher number of topics allowed us to retain more of the smaller topics and leaves a relatively low number of 308 free-text entries unclassified (10.33%).
-A full write-up of the topic modeling process is available in Online Supplemental Material B.
+A full write-up of the topic modeling process is available in Online Supplemental Material C.
 
@@
 A similar set of topics was specifically geared towards a wish to experience cultural products (e.g., music, theater, food) or had travel-related goals in their interactions with the majority group members.
-
-One interesting observation was the importance of contact goals specific to contact through the medical and public health system.
+In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the need fulfillment literature \citep[e.g.,][]{orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
+The authors have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
+
+<!-- One interesting observation was the importance of contact goals specific to contact through the medical and public health system.
 This goal type was partly specific to the medical professionals (e.g., working with patients, treatment), but also more broadly highlighted interactions of newcomers with the outgroup majority as patients themselves (e.g., therapeutic goals).
@@
 Another topic less commonly found within the literature were more practically oriented needs, where participants sought to share food and cook together or had organizational needs (e.g., housing, cleaning, and co-living).
-In sum, almost all extracted topics fall into broader or narrower need concepts that are commonly discussed within the psychological needs literature \citep[e.g.,][]{orehek2018a} and offer insight into a core aspect of the migration experience that has remained broadly under-explored \citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
-The authors have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
+-->
+
+\subsubsection{Need types}
+To ensure that our results are not impacted by differences in the reported goals and motives, we additionally coded the topics we extracted during the topic modeling on two dimensions of how much they reflect a practical and a psychological goal-directedness.
+We chose practical and psychological needs specifically as our dimensions to account for differences in the types of needs that participants commonly reported.
+With practical motives we refer to specific, tangible goals or tasks that participants aimed to accomplish during the interaction.
+These instrumental goals are usually observable, concrete, and often centered on external outcomes, such as acquiring resources, completing tasks, and addressing immediate challenges \citep[][]{}.
+With psychological motives we refer to underlying motives or desires that are more abstract and relate to personal fulfillment and well-being.
+In contrast to practical needs, psychological needs delve into the subjective and internal aspects of human experiences.
+These needs pertain to emotions, social connections, and cognitive processes, reflecting individuals' quest for personal growth, well-being, and thriving in social relationships \citep[][]{}.
+Note that with this approach any particular motive can include a practical and/or a psychological goal-directedness but can also be classified as not having any goal at all.
+
+For each of the topics, we had identified in the topic modeling analysis, we extracted the top 10 most indicative words as well as the three most representative free text responses.
+Using a detailed coding protocol for both the practical as well as the psychological motives, two independent coders rated each of the 47 topics.
+This allowed us to add the two dimensions back to each of the reported interaction motives and assess the distributions and effects of the goal-directed character.
+We found that \hl{...}.
+
+\subsubsection{Specific psychological needs}
+Finally, to ensure that a much simpler model of three fundamental psychological needs might not account for the same effect, we compared our situation core need fulfillment measurement to the three self-determination theory needs (autonomy, relatedness, competence).
 

### 2023-05-26 Robustness-Methods-and-Results.Rmd
power sim re-added and robustness analyses extended (revision)

@@
 
-```{r setup, include=FALSE}
+```{r}
+#| label: setup
+#| include: false
+
 # R Studio Clean-Up
@@
 
-```{r import, include=FALSE}
+```{r}
+#| label: import
+#| include: false
+
 load("data/wrangled.RData")
@@
 
-In addition to the measurement of whether or not participants had an intergroup interaction and their situational core need fulfillment, we also measured a set of general psychological needs.
-
-\subsubsection{General Psychological Needs} In addition to the intergroup contact dummy and situational core need reported in the main text, we included a common measure of three self-determination theory needs \citep[see][]{Downie2008}.
+In addition to the measurement of whether or not participants had an intergroup interaction and their situational core need fulfillment, we also included a number of variables that allowed us to assess the robustness of our results.
+
+\subsubsection{Specific Psychological Needs} In addition to the intergroup contact dummy and situational core need reported in the main text, we included a common measure of three self-determination theory needs \citep[see][]{Downie2008}.
 The measurement was identical in all three studies.
@@
 
+\subsubsection{Interaction Intend} To assess whether an interaction was accidental (vs.
+planned), we asked participants with a single item to report the extend to which "The interaction with -X- was accidental".
+The respondents were asked to report this context variable for all interactions they reported on using a continuous slider ranging from "not at all" (0), through "very little" (33) and "somewhat" (66), to "a great deal" (100).
+In all studies the scale showed a right skew (\textit{mean} = `r format(round(mean(dt_goal_directedness$InteractionAccidental, na.rm = TRUE), 2), nsmall = 2)`, \textit{sd} = `r format(round(sd(dt_goal_directedness$InteractionAccidental, na.rm = TRUE), 2), nsmall = 2)`).
+
+\subsubsection{Goal-directedness}
+```{r}
+#| label: goal_directedness_descr
+#| include: false
+
+kappa.full <- function(x, name, ...){
+  xtab <- table(x)
+  diagonal.counts <- diag(xtab)
+  N <- sum(xtab)
+  row.marginal.props <- rowSums(xtab)/N
+  col.marginal.props <- colSums(xtab)/N
+  # Compute kappa (k)
+  Po <- sum(diagonal.counts)/N
+  Pe <- sum(row.marginal.props*col.marginal.props)
+  k <- (Po - Pe)/(1 - Pe)
+  se <- sqrt((Po*(1-Po))/(N*(1-Pe)^2)) # according to PMID: 23092060
+  lwr <- k-1.96*se
+  upr <- k+1.96*se
+
+  data.frame(name,Po,Pe,k,se,lwr,upr)
+}
+
+irr_practical <- dt_topic_coding %>%
+  select(practical_need_01, 
+         practical_need_02) %>%
+  kappa.full(., "practical_need")
+
+irr_practical_dum <- dt_topic_coding %>%
+  transmute(
+    practical_need_01_dum = ifelse(practical_need_01 == 2, 1, practical_need_01), 
+    practical_need_02_dum = ifelse(practical_need_02 == 2, 1, practical_need_02)
+  ) %>%
+  kappa.full(., "practical_need_dum")
+
+irr_psychological <- dt_topic_coding %>%
+  select(psychological_need_01, 
+         psychological_need_02) %>%
+  kappa.full(., "psychological_need")
+
+irr_psychological_dum <- dt_topic_coding %>%
+  transmute(
+    practical_need_01_dum = ifelse(psychological_need_01 == 2, 1, psychological_need_01), 
+    practical_need_02_dum = ifelse(psychological_need_02 == 2, 1, psychological_need_02)
+  ) %>%
+  kappa.full(., "psychological_need_dum")
+
+irr <- rbind(
+  irr_practical,
+  irr_practical_dum,
+  irr_psychological, 
+  irr_psychological_dum
+)
+
+dt_topic_coding %>%
+  transmute(
+    practical_need_dum = ifelse(practical_need == 2, 1, practical_need), 
+    psychological_need_dum = ifelse(psychological_need == 2, 1, psychological_need)
+  )
+
+lab_mapping <- c("no need", "need")
+goal_directedness_dist <- dt_goal_directedness %>%
+  transmute(
+    practical_need_dum = ifelse(practical_need == 2, 1, practical_need), 
+    psychological_need_dum = ifelse(psychological_need == 2, 1, psychological_need)
+  ) %>% 
+  mutate(
+    practical_need_label = lab_mapping[match(practical_need_dum, c(0, 1))],
+    psychological_need_label = lab_mapping[match(psychological_need_dum, c(0, 1))]
+  ) %>%
+  group_by(
+    practical_need_dum,
+    practical_need_label,
+    psychological_need_dum,
+    psychological_need_label
+  ) %>%
+  summarise(count = n()) %>%
+  ungroup() %>%
+  na.omit %>%
+  mutate(
+    perc = count/sum(count)*100
+  )
+
+ggplot(
+  goal_directedness_dist,
+  aes (
+    x = reorder(practical_need_label, practical_need_dum),
+    y = reorder(psychological_need_label, psychological_need_dum),
+    fill = count,
+    label = paste0(format(round(perc, 2), nsmall = 2), "%")
+  )) +
+  geom_tile() +
+  geom_text(col = "white") +
+  labs(x = "Practical Motive",
+       y = "Psychological Motive",
+       title = "Goal Directedness Coding") +
+  theme(legend.key.size = unit(0.75, "cm"))
+```
+To assess whether the need content (i.e., the motives) would impact the effect of the need fulfillment experiences, we manually coded the topics we extracted during the topic modeling on two dimensions of how much they reflect a practical and a psychological goal-directedness.
+We chose practical and psychological needs specifically as our dimensions to account for differences in the types of needs that participants commonly reported.
+With practical motives we refer to specific, tangible goals or tasks that participants aimed to accomplish during the interaction.
+These instrumental goals are usually observable, concrete, and often centered on external outcomes, such as acquiring resources, completing tasks, and addressing immediate challenges \citep[][]{}.
+With psychological motives we refer to underlying motives or desires that are more abstract and relate to personal fulfillment and well-being.
+In contrast to practical needs, psychological needs delve into the subjective and internal aspects of human experiences.
+These needs pertain to emotions, social connections, and cognitive processes, reflecting individuals' quest for personal growth, well-being, and thriving in social relationships \citep[][]{}.
+Note that with this approach any particular motive can include a practical and/or a psychological goal-directedness but can also be classified as not having any goal at all.
+The full coding protocol we developed with examples for each of the codes is available in our Online Supplemental Material D.
+After an initial training, each of the two coders independently coded the 47 topics on the two dimensions, using one of three options each (i.e., 0 = no goal, 1 = vague goal, 2 = clear goal).
+Inter-rater reliability assessments showed that for both the practical as well as the psychological needs, agreement was not optimal using the three answer options (agreement practical = `r irr$Po[irr$name == "practical_need"] %>% round(2) %>% format(nsmall = 2)`\%, agreement psychological = `r irr$Po[irr$name == "psychological_need"] %>% round(2) %>% format(nsmall = 2)`\%).
+However, most disagreements were, if a need was present, whether that need was vague (1) or concrete (2).
+We, thus, collapsed these two categories making the ratings binary (need absent vs.
+need present).
+With the simpler coding, inter-rater agreement for practical needs (`r irr$Po[irr$name == "practical_need_dum"] %>% round(2) %>% format(nsmall = 2)`\%) and the psychological need (`r irr$Po[irr$name == "psychological_need_dum"] %>% round(2) %>% format(nsmall = 2)`\%) were much more reliable.
+Using Cohen’s $\kappa$ as our measure of inter-rater reliability, we find that both the practical need coding (\textit{Cohen's} $\kappa$ = `r irr$k[irr$name == "practical_need_dum"] %>% round(2) %>% format(nsmall = 2)`, 95\%CI[`r irr$lwr[irr$name == "practical_need_dum"] %>% round(2) %>% format(nsmall = 2)`, `r ifelse(irr$upr[irr$name == "practical_need_dum"]>1, 1 %>% round(2) %>% format(nsmall = 2), irr$upr[irr$name == "practical_need_dum"] %>% round(2) %>% format(nsmall = 2))`]) as well as the psychological need coding (\textit{Cohen's} $\kappa$ = `r irr$k[irr$name == "psychological_need_dum"] %>% round(2) %>% format(nsmall = 2)`, 95\%CI[`r irr$lwr[irr$name == "psychological_need_dum"] %>% round(2) %>% format(nsmall = 2)`, `r ifelse(irr$upr[irr$name == "psychological_need_dum"]>1, 1 %>% round(2) %>% format(nsmall = 2), irr$upr[irr$name == "psychological_need_dum"] %>% round(2) %>% format(nsmall = 2))`]) were very good.
+We thus proceeded with this collapsed coding.
+After resolving coder disagreements and merging the codings back to the free-text responses, we found that a majority of responses showed both a practical as well as a psychological need (`r goal_directedness_dist$perc[goal_directedness_dist$practical_need_dum==1 & goal_directedness_dist$psychological_need_dum==1] %>% round(2) %>% format(nsmall=2)`\%) and only few responses had no goal at all (`r goal_directedness_dist$perc[goal_directedness_dist$practical_need_dum==0 & goal_directedness_dist$psychological_need_dum==0] %>% round(2) %>% format(nsmall=2)`\%) with the remaining `r goal_directedness_dist$perc[goal_directedness_dist$practical_need_dum+goal_directedness_dist$psychological_need_dum==1] %>% sum %>% round(2) %>% format(nsmall=2)`\% having either a practical or a psychological need only (see Online Supplemental Material A for more detailed tables and visualizations).
+
+\subsubsection{Well-being} We measured experienced well-being using a visual analog scale adapted from \citet{davies2022}.
+Participants were asked to respond to the the question "How do you feel right now?" using a continuous visual slider ranging from "very sad"(-100) to "very happy" (100).
+The well-being ratings were generally normally distributed (\textit{mean} = `r format(round(mean(dt_goal_directedness$WellBeing, na.rm = TRUE), 2), nsmall = 2)`, \textit{sd} = `r format(round(sd(dt_goal_directedness$WellBeing, na.rm = TRUE), 2), nsmall = 2)`).
+
 \subsection{Results}
 
-\subsubsection{Study 1}
-
-```{r workerSampleInfo, include=FALSE}
-# combine education measure
-workerOccupation <- 
-  dtWorker$clean %>%
-  select(PID, starts_with("occupation")) %>%
-  mutate_all(as_factor) %>% 
-  mutate_all(as.character) %>%
-  replace(is.na(.), "") %>%
-  unite("occupation", -PID, sep = "/") %>%
-  mutate(occupation = trimws(occupation, which = "both", whitespace = "[/]")) %>%
-  distinct
-
-# summarize participant characteristics
-workerSampleInfo <- 
-  dtWorker$clean %>%
-  group_by(PID) %>%
-  summarise(
-    dailiesN = n(), 
-    morningN = sum(daytime=="morning"),
-    afternoonN = sum(daytime=="afternoon"),
-    age = age,
-    gender = as_factor(Gender),
-    edu = as_factor(education_level),
-    nationality = as_factor(nationality)
-  ) %>%
-  distinct
-
-# add occupation variable
-workerSampleInfo <- merge(workerSampleInfo, workerOccupation)
-rm(workerOccupation)
-
-# divide into trait and state
-dtWorkerSupp$workerWithinBetween <-
-  MlTraitState(
-    data = dtWorkerSupp$workerInteractionType,
-    id = "PID",
-    selection =
-      c(
-        "keyMotiveFulfilled",
-        "competence.daily.all",
-        "autonomy.daily.all",
-        "relatedness.daily.all",
-        "thermometerDutch_1",
-        "keymotive_fulfillemt_1",
-        "competence_1",
-        "autonomy_1",
-        "relatedness_1", 
-        "quality_overall_1", 
-        "OutgroupInteraction",
-        "NonOutgroupInteraction", 
-        "OutgroupInteractionM",
-        "NonOutgroupInteractionM"
-      )
-  )
-
-dtWorkerSupp$workerOutWithinBetween <-
-  MlTraitState(
-    data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
-    id = "PID",
-    selection =
-      c(
-        "keyMotiveFulfilled",
-        "thermometerDutch_1",
-        "keymotive_fulfillemt_1",
-        "competence_1",
-        "autonomy_1",
-        "relatedness_1", 
-        "quality_overall_1"
-      )
-  )
+To build further confidence in our results, we assessed a number of additional models that might offer alternative explanations.
+We will discuss the results in sequential order --- in every case first considering the a global test of the model across the three studies and only then assessing whether the global three-level regression model suppresses any important person-level variations within the studies.
+
+\subsubsection{Contact specific}
+
+```{r}
+#| label: contact_overall
+#| include: false
+
+dt_exp_all <- dt_exp_all %>%
+  mutate(
+    OutgroupInteraction = (OutgroupInteraction-1.5)
+  )
+
+contact_overall <- select_best_lmer_model(
+  data = dt_exp_all,
+  prediction_form = "CoreNeed * OutgroupInteraction",
+  structure = "study/PID",
+  dependent_var = "Attitude",
+  lmer_scale = TRUE
+)
+
+# contact_overall$anova
+# contact_overall$choice
+# contact_overall$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# contact_overall$lmer_model %>% summ(., confint = TRUE, digits = 3, scale = TRUE)
+
+# interactions::sim_slopes(mdl_contact$lmerAttSlopeOverall, pred = CoreNeedC, modx = OutgroupInteraction, jnplot = TRUE)
+# interactions::interact_plot(contact_overall$lmer_model, pred = CoreNeed, modx = OutgroupInteraction, interval = TRUE)
 ```
 
-```{r workerModelOlsAttFreqQual, include=FALSE}
-# create list to store Worker models
-mdlWorker <- list()
+We begin our robustness analysis by testing whether the effect of core need fulfillment is specific to an actual outgroup contact, rather than need fulfillment in general.
+For this, we analyzed the generalized situational core need fulfillment (either during a contact or about the daytime in general) and tested whether the effect differed during experience sampling measurements with and without outgroup contacts.
+We start this test by assessing the effect across all three studies, using a three-level hierarchical model, where measurements are nested within participants, and participants are nested within studies.
+In this overall model, we found no main effect of core need fulfillment (random slopes model, grand-mean standardized to account for all levels of variance; `r get_latex_coef(contact_overall$lmer_coef, "CoreNeed")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r get_latex_coef(contact_overall$lmer_coef, "CoreNeed:OutgroupInteraction")`; also see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}).
+While the three-level hierarchical model can be sensitive to scaling issues, this already indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+
+```{r}
+#| label: contact_s1
+#| include: false
+
+contact_s1 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 1),
+  prediction_form = "CoreNeedC * OutgroupInteraction",
+  structure = "PID",
+  dependent_var = "Attitude"
+)
+# contact_s1$anova
+# contact_s1$choice
+# contact_s1$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# contact_s1$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+
+# interactions::sim_slopes(mdl_contact$lmerAttSlopeOverall, pred = CoreNeedC, modx = OutgroupInteraction, jnplot = TRUE)
+# interactions::interact_plot(contact_s1$lmer_model, pred = CoreNeedC, modx = OutgroupInteraction, interval = TRUE)
 ```
 
-```{r workerModelMLAttNull, include=FALSE}
-# Create and save Model
-mdlWorker$lmerAttNull <-
-  lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID),
-    data = dtWorker$full
-  ) # use optim if it does not converge
-
-mdlWorker$lmeAttNull <-
-  lme(
-    thermometerDutch_1 ~ 1,
-    random = ~ 1 | PID,
-    data = dtWorker$full,
-    na.action=na.omit,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(lmerWorkerAttNull) #or with the lme function
-summ(mdlWorker$lmerAttNull, digits = 3, center = TRUE)
-
-# Save variances
-mdlWorker$varAttNull <- 
-  VarCorr(mdlWorker$lmeAttNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlWorker$tauAttNull <- 
-  as.numeric(mdlWorker$varAttNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlWorker$sigmaAttNull <- 
-  as.numeric(mdlWorker$varAttNull[2])
-# The ICC estimate (between/between+within) is:
-mdlWorker$IccAttNull <-
-  (as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2])))
-mdlWorker$IccPercAttNull <-
-  ((as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2])))) * 100
+```{r}
+#| label: contact_s2
+#| include: false
+
+contact_s2 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 2),
+  prediction_form = "CoreNeedC * OutgroupInteraction",
+  structure = "PID",
+  dependent_var = "Attitude"
+)
+# contact_s2$anova
+# contact_s2$choice
+# contact_s2$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# contact_s2$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+
+# interactions::sim_slopes(mdl_contact$lmerAttSlopeOverall, pred = CoreNeedC, modx = OutgroupInteraction, jnplot = TRUE)
+# interactions::interact_plot(contact_s2$lmer_model, pred = CoreNeedC, modx = OutgroupInteraction, interval = TRUE)
 ```
 
-```{r workerOutModelMLAttNull, include=FALSE}
-# create empty list to organize models
-mdlWorkerOut <- 
-  list(
-    Att = list(),
-    Qlt = list()
-  )
-
-# Create and save Model
-mdlWorkerOut$Att$lmerNull <-
-  lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID), 
-             data = dtWorkerSupp$workerOutgroupInteraction) # use optim if it does not converge
-mdlWorkerOut$Att$lmeNull <-
-  lme(
-    thermometerDutch_1 ~ 1,
-    random = ~ 1 | PID,
-    data = dtWorkerSupp$workerOutgroupInteraction,
-    na.action=na.omit,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.ML.r) #or with the lme function
-summ(mdlWorkerOut$Att$lmerNull, digits = 3, center = TRUE)
-
-# Save variances
-mdlWorkerOut$Att$varNull <- 
-  VarCorr(mdlWorkerOut$Att$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlWorkerOut$Att$tauNull <- 
-  as.numeric(mdlWorkerOut$Att$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlWorkerOut$Att$sigmaNull <- 
-  as.numeric(mdlWorkerOut$Att$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlWorkerOut$Att$IccNull <-
-  (as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2])))
-mdlWorkerOut$Att$IccPercNull <-
-  ((as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2])))) * 100
+```{r}
+#| label: contact_s3
+#| include: false
+
+contact_s3 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 3),
+  prediction_form = "CoreNeedC * OutgroupInteraction",
+  structure = "PID",
+  dependent_var = "Attitude"
+)
+# contact_s3$anova
+# contact_s3$choice
+# contact_s3$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# contact_s3$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+
+# interactions::sim_slopes(mdl_contact$lmerAttSlopeOverall, pred = CoreNeedC, modx = OutgroupInteraction, jnplot = TRUE)
+# interactions::interact_plot(contact_s3$lmer_model, pred = CoreNeedC, modx = OutgroupInteraction, interval = TRUE)
 ```
 
-```{r workerOutModelMLQltNull, include=FALSE}
-# Create and save Model
-mdlWorkerOut$Qlt$lmerNull <-
-  lme4::lmer(quality_overall_1 ~ 1 + (1 | PID), 
-             data = dtWorkerSupp$workerOutWithinBetween) # use optim if it does not converge
-
-mdlWorkerOut$Qlt$lmeNull <-
-  mdlWorkerOut$Qlt$lmeNull <- lme(
-    quality_overall_1 ~ 1,
-    random = ~ 1 | PID,
-    data = dtWorkerSupp$workerOutWithinBetween,
-    na.action=na.omit,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.Qual.ML.r) #or with the lme function
-summ(mdlWorkerOut$Qlt$lmerNull, digits = 3)
-
-# Save variances
-mdlWorkerOut$Qlt$varNull <- 
-  VarCorr(mdlWorkerOut$Qlt$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlWorkerOut$Qlt$tauNull <- 
-  as.numeric(mdlWorkerOut$Qlt$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlWorkerOut$Qlt$sigmaNull <- 
-  as.numeric(mdlWorkerOut$Qlt$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlWorkerOut$Qlt$IccNull <-
-  (as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2])))
-mdlWorkerOut$Qlt$IccPercNull <-
-  ((as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2])))) * 100
+```{r}
+#| label: contact_study_coef
+#| include: false
+
+contact_study_coef <- 
+  rbind(
+    contact_s1$lmer_coef %>% mutate(study = 1),
+    contact_s2$lmer_coef %>% mutate(study = 2),
+    contact_s3$lmer_coef %>% mutate(study = 3)
+  )
 ```
 
-```{r workerModelInterceptAttCoreInt, include=FALSE}
-# Create and save Model
-mdlWorker$lmeInterceptAttCoreInt <-
-  lme(
-    thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction,
-    random =  ~ 1 | PID,
-    na.action=na.omit,
-    data = dtWorkerSupp$workerWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlWorker$lmerInterceptAttCoreInt <- lmer(
-    thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction + (1 | PID),
-    data = dtWorkerSupp$workerWithinBetween
+To ensure that the results are not affected by scaling issues (e.g., study-level variances suppressing person-level variances) or a similar Simpson's paradox, we additionally assess the model within each of the three studies.
+Within each of the three studies, the effects are more pronounced, so that we also see a significant effect of core need fulfillemnt (all \textit{b} > `r min(abs(contact_study_coef[contact_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r max(contact_study_coef[contact_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)`) as well as outgroup contact itself (all |\textit{b}| > `r min(abs(contact_study_coef[contact_study_coef$coef == "OutgroupInteraction", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r max(contact_study_coef[contact_study_coef$coef == "OutgroupInteraction", "p"]) %>% round(3) %>% format(nsmall=3)`) but the interaction effect consistently remains the most reliable predictor of outgroup attitudes (all |\textit{b}| > `r min(abs(contact_study_coef[contact_study_coef$coef == "CoreNeedC:OutgroupInteraction", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r max(contact_study_coef[contact_study_coef$coef == "CoreNeedC:OutgroupInteraction", "p"]) %>% round(3) %>% format(nsmall=3)`, also see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}).
+There is thus consistent evidence that need fulfillment relates to outgroup attitudes for outgroup contacts in particular but not need fulfillment in general.
+
+\subsubsection{Interaction intend}
+
+```{r}
+#| label: accidental_overall
+#| include: false
+
+accidental_overall <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeed * InteractionAccidental",
+  structure = "study/PID",
+  dependent_var = "Attitude",
+  lmer_scale = TRUE
+)
+# accidental_overall$anova
+# accidental_overall$choice
+# accidental_overall$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# accidental_overall$lmer_model %>% summ(., confint = TRUE, digits = 3, scale = TRUE)
+```
+
+Secondly, to assess whether the need fulfillment mechanism affected by whether the interaction was accidental or planned we ran an exploratory moderation analysis using the participants' ratings of how much they perceived the interaction as 'accidental'.
+It should be noted that we asked our participants to focus on most the important interaction (i.e., "\textit{The following questions will be about the interaction \underline{you consider most significant}.}"''"; emphasis as in original).
+We again start our analysis approach by assessing the model across all three studies, using a three-level hierarchical model.
+In this overall model, we retain the main effect of core need fulfillment (random slopes model, grand-mean standardized to account for all levels of variance; `r get_latex_coef(accidental_overall$lmer_coef, "CoreNeed")`) but neither contact intend nor the moderation effect affect the results (all |\textit{b}| < `r max(abs(accidental_overall$lmer_coef[accidental_overall$lmer_coef$coef != c("(Intercept)", "CoreNeed"), "b"])) %>% round(2) %>% format(nsmall=2)` and all \textit{p} > `r min(accidental_overall$lmer_coef[accidental_overall$lmer_coef$coef != c("(Intercept)", "CoreNeed"), "p"]) %>% round(3) %>% format(nsmall=3)`; see \tblref{tab:robustnessTblLong} for full results).
+
+```{r}
+#| label: accidental_s1
+#| include: false
+
+accidental_s1 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 1, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC * InteractionAccidentalC",
+  structure = "PID",
+  dependent_var = "Attitude"
+)
+# accidental_s1$anova
+# accidental_s1$choice
+# accidental_s1$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# accidental_s1$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+
+# interactions::sim_slopes(accidental_s1$lmer_model, pred = CoreNeedC, modx = InteractionAccidentalC, jnplot = TRUE)
+# interactions::interact_plot(accidental_s1$lmer_model, pred = CoreNeedC, modx = InteractionAccidentalC, interval = TRUE)
+```
+
+```{r}
+#| label: accidental_s2
+#| include: false
+
+accidental_s2 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC * InteractionAccidentalC",
+  structure = "PID",
+  dependent_var = "Attitude",
+  return = "slope"
+)
+# accidental_s2$anova
+# accidental_s2$choice
+# accidental_s2$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# accidental_s2$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+# 
+# interactions::sim_slopes(accidental_s2$lmer_model, pred = CoreNeedC, modx = InteractionAccidentalC, jnplot = TRUE)
+# interactions::interact_plot(accidental_s2$lmer_model, pred = CoreNeedC, modx = InteractionAccidentalC, interval = TRUE)
+```
+
+```{r}
+#| label: accidental_s3
+#| include: false
+
+accidental_s3 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 3, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC * InteractionAccidentalC",
+  structure = "PID",
+  dependent_var = "Attitude"
+)
+# accidental_s3$anova
+# accidental_s3$choice
+# accidental_s3$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# accidental_s3$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+# 
+# interactions::sim_slopes(accidental_s3$lmer_model, pred = CoreNeedC, modx = InteractionAccidentalC, jnplot = TRUE)
+# interactions::interact_plot(accidental_s3$lmer_model, pred = CoreNeedC, modx = InteractionAccidentalC, interval = TRUE)
+```
+
+```{r}
+#| label: accidental_study_coef
+#| include: false
+
+accidental_study_coef <- 
+  rbind(
+    accidental_s1$lmer_coef %>% mutate(study = 1),
+    accidental_s2$lmer_coef %>% mutate(study = 2),
+    accidental_s3$lmer_coef %>% mutate(study = 3)
+  )
+```
+
+We again sought to ensure that the results were not affected by scaling issues by additionally assessing the interaction intentionality model within each of the three studies.
+Within each of the three studies, the effect of core need fulfillemnt became even clearer (all |\textit{b}| > `r min(abs(accidental_study_coef[accidental_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(accidental_study_coef[accidental_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(accidental_study_coef[accidental_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3))`).
+But in none of the studies neither outgroup contact intention nor the moderation effect explained a significant amount of variance in outgroup attitudes (all |\textit{b}| < `r max(abs(accidental_study_coef[accidental_study_coef$coef != c("(Intercept)", "CoreNeedC"), "b"])) %>% round(2) %>% format(nsmall=2)` and all \textit{p} > `r min(accidental_study_coef[accidental_study_coef$coef != c("(Intercept)", "CoreNeedC"), "p"]) %>% round(3) %>% format(nsmall=3)`; also see \tblref{tab:robustnessTblLong}).
+There is thus consistent evidence that need fulfillment is related to outgroup attitudes, even when taking the intentionality of the interaction into account --- at least in our three samples and with a focus on the most significant interactions.
+
+\subsubsection{Well-being outcome}
+
+```{r}
+#| label: wellbeing_core_overall
+#| include: false
+
+wellbeing_core_overall <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeed",
+  structure = "study/PID",
+  dependent_var = "WellBeing",
+  lmer_scale = TRUE
+)
+# wellbeing_core_overall$anova
+# wellbeing_core_overall$choice
+# wellbeing_core_overall$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# wellbeing_core_overall$lmer_model %>% summ(., confint = TRUE, digits = 3, scale = TRUE)
+```
+
+```{r}
+#| label: wellbeing_full_overall
+#| include: false
+
+wellbeing_full_overall <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeed + Quality",
+  structure = "study/PID",
+  dependent_var = "WellBeing",
+  lmer_scale = TRUE
+)
+# wellbeing_full_overall$anova
+# wellbeing_full_overall$choice
+# wellbeing_full_overall$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# wellbeing_full_overall$lmer_model %>% summ(., confint = TRUE, digits = 3, scale = TRUE)
+```
+
+```{r}
+#| label: wellbeing_core_s1
+#| include: false
+
+wellbeing_core_s1 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 1, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC",
+  structure = "PID",
+  dependent_var = "WellBeing"
+)
+# wellbeing_core_s1$anova
+# wellbeing_core_s1$choice
+# wellbeing_core_s1$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# wellbeing_core_s1$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+```
+
+```{r}
+#| label: wellbeing_full_s1
+#| include: false
+
+wellbeing_full_s1 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 1, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC + QualityC",
+  structure = "PID",
+  dependent_var = "WellBeing"
+)
+# wellbeing_full_s1$anova
+# wellbeing_full_s1$choice
+# wellbeing_full_s1$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# wellbeing_full_s1$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+```
+
+```{r}
+#| label: wellbeing_core_s2
+#| include: false
+
+wellbeing_core_s2 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC",
+  structure = "PID",
+  dependent_var = "WellBeing"
+)
+# wellbeing_core_s2$anova
+# wellbeing_core_s2$choice
+# wellbeing_core_s2$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# wellbeing_core_s2$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+```
+
+```{r}
+#| label: wellbeing_full_s2
+#| include: false
+
+wellbeing_full_s2 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC + QualityC",
+  structure = "PID",
+  dependent_var = "WellBeing"
+)
+# wellbeing_full_s2$anova
+# wellbeing_full_s2$choice
+# wellbeing_full_s2$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# wellbeing_full_s2$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+```
+
+```{r}
+#| label: wellbeing_core_s3
+#| include: false
+
+wellbeing_core_s3 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 3, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC",
+  structure = "PID",
+  dependent_var = "WellBeing"
+)
+# wellbeing_core_s3$anova
+# wellbeing_core_s3$choice
+# wellbeing_core_s3$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# wellbeing_core_s3$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+```
+
+```{r}
+#| label: wellbeing_full_s3
+#| include: false
+
+wellbeing_full_s3 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 3, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC + QualityC",
+  structure = "PID",
+  dependent_var = "WellBeing"
+)
+# wellbeing_full_s3$anova
+# wellbeing_full_s3$choice
+# wellbeing_full_s3$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# wellbeing_full_s3$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+```
+
+```{r}
+#| label: wellbeing_core_study_coef
+#| include: false
+
+wellbeing_core_study_coef <- 
+  rbind(
+    wellbeing_core_s1$lmer_coef %>% mutate(study = 1),
+    wellbeing_core_s2$lmer_coef %>% mutate(study = 2),
+    wellbeing_core_s3$lmer_coef %>% mutate(study = 3)
+  )
+```
+
+Thirdly, to build a stronger case for the relevance of need fulfillment to minority group members, we exploratorily assessed the effect of need fulfilling outgroup interactions on self-reported well-being.
+We, thus, re-ran our main analysis but substituted the outgroup attitudes outcome with situational well-being.
+As with the previous robustness analyses, we begin with a global three-level hierarchical model (across the three studies).
+We find that need fulfillment during outgroup contacts, indeed, has a similar effect on experienced well-being (random slopes model, grand-mean standardized to account for all levels of variance; `r get_latex_coef(wellbeing_core_overall$lmer_coef, "CoreNeed")`).
+We found the same result when we assessed each of the three studies individually.
+In each of the studies situational need fulfillment during the outgroup interaction was related with higher well-being ratings by the participants (random slopes model, centered within participants; all |\textit{b}| > `r min(abs(wellbeing_core_study_coef[wellbeing_core_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(wellbeing_core_study_coef[wellbeing_core_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(wellbeing_core_study_coef[wellbeing_core_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3))`).
+We, thus, find consistent and meaningful evidence that need fulfilling outgroup interactions also relate to higher everyday well-being.
+
+\subsubsection{Need types}
+
+\paragraph{overall}
+```{r}
+#| label: need_type_overall
+#| include: false
+
+need_type_overall <- select_best_lmer_model(
+  data = dt_goal_directedness,
+  prediction_form = "CoreNeed * practical_need_dum + CoreNeed * psychological_need_dum",
+  structure = "study/PID",
+  dependent_var = "Attitude",
+  lmer_scale = TRUE
+)
+# need_type_overall$anova
+# need_type_overall$choice
+# need_type_overall$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# need_type_overall$lmer_model %>% summ(., confint = TRUE, digits = 3, scale = TRUE)
+```
+
+Fourthly, to assess the role of different types of motives reported by our participants, we added our coding of practical and psychological goal-directedness as additional predictors to our base model.
+We thus had core need fulfillment predicting outgroup attitudes while also accounting for whether the reported motives were capturing practical and/or psychological motives.
+We again ran a global model, across the three studies first.
+We found that core need fulfillment remain a core predictor of outgroup attitudes (random slopes model, grand-mean standardized to account for all levels of variance; `r get_latex_coef(need_type_overall$lmer_coef, "CoreNeed")`), even after accounting for different types of motives.
+None of the motive types nor the moderation effects reached statistical significance within the overall analysis (all |\textit{b}| < `r max(abs(need_type_overall$lmer_coef[need_type_overall$lmer_coef$coef != c("(Intercept)", "CoreNeed"), "b"])) %>% round(2) %>% format(nsmall=2)` and all \textit{p} > `r min(need_type_overall$lmer_coef[need_type_overall$lmer_coef$coef != c("(Intercept)", "CoreNeed"), "p"]) %>% round(3) %>% format(nsmall=3)`; see \tblref{tab:robustnessTblLong} for full results).
+
+\paragraph{Study follow-up}
+```{r}
+#| label: need_type_s1
+#| include: false
+
+need_type_s1 <- select_best_lmer_model(
+  data = dt_goal_directedness %>% filter(study == 1),
+  prediction_form = "CoreNeedC * practical_need_dum + CoreNeedC * psychological_need_dum",
+  structure = "PID",
+  dependent_var = "Attitude",
+  return = "slope"
+)
+# need_type_s1$anova
+# need_type_s1$choice
+# need_type_s1$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# need_type_s1$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+```
+
+```{r}
+#| label: need_type_s2
+#| include: false
+
+need_type_s2 <- select_best_lmer_model(
+  data = dt_goal_directedness %>% filter(study == 2),
+  prediction_form = "CoreNeedC * practical_need_dum + CoreNeedC * psychological_need_dum",
+  structure = "PID",
+  dependent_var = "Attitude"
+)
+# need_type_s2$anova
+# need_type_s2$choice
+# need_type_s2$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# need_type_s2$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+```
+
+```{r}
+#| label: need_type_s3
+#| include: false
+
+need_type_s3 <- select_best_lmer_model(
+  data = dt_goal_directedness %>% filter(study == 3),
+  prediction_form = "CoreNeedC * practical_need_dum + CoreNeedC * psychological_need_dum",
+  structure = "PID",
+  dependent_var = "Attitude"
+)
+# need_type_s3$anova
+# need_type_s3$choice
+# need_type_s3$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# need_type_s3$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+```
+
+```{r}
+#| label: need_type_study_coef
+#| include: false
+
+need_type_study_coef <- 
+  rbind(
+    need_type_s1$lmer_coef %>% mutate(study = 1),
+    need_type_s2$lmer_coef %>% mutate(study = 2),
+    need_type_s3$lmer_coef %>% mutate(study = 3)
+  )
+```
+
+When looking at the individual studies, we again saw that the effect of core need fulfillemnt remained the on only clear effect (all |\textit{b}| > `r min(abs(need_type_study_coef[need_type_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(need_type_study_coef[need_type_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(need_type_study_coef[need_type_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3))`).
+Additionally, in none of the studies neither motive type dummies nor the moderation effect explained a significant amount of variance in outgroup attitudes (all |\textit{b}| < `r max(abs(need_type_study_coef[need_type_study_coef$coef != c("(Intercept)", "CoreNeedC"), "b"])) %>% round(2) %>% format(nsmall=2)` and all \textit{p} > `r min(need_type_study_coef[need_type_study_coef$coef != c("(Intercept)", "CoreNeedC"), "p"]) %>% round(3) %>% format(nsmall=3)`; also see \tblref{tab:robustnessTblLong}).
+We, thus, find consistent evidence that need fulfillment is related to outgroup attitudes, even when taking the type of need into account --- at least in our three samples.
+
+\subsubsection{Specific psychological needs}
+
+```{r}
+#| label: need_sdt_overall
+#| include: false
+
+need_sdt_overall <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeed + Competence + Autonomy + Relatednesss",
+  structure = "study/PID",
+  dependent_var = "Attitude",
+  lmer_scale = TRUE
+)
+# need_sdt_overall$anova
+# need_sdt_overall$choice
+# need_sdt_overall$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# need_sdt_overall$lmer_model %>% summ(., confint = TRUE, digits = 3, scale = TRUE)
+```
+
+In a final step, we checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
+We again take a two-step approach, starting with cross-study global three-level test and then assessing the effects within the individual studies.
+Within the overall model we find that across the studies core need fulfillment remained a strong predictor of outgroup attitudes, even after controlling for the three self-determination theory need (random slopes model, grand-mean standardized to account for all levels of variance; `r get_latex_coef(need_sdt_overall$lmer_coef, "CoreNeed")`).
+Within this overall analysis, none of the self-determination theory needs independently predicted outgroup attitudes to a statistically significant extent (all \textit{p} > `r min(need_sdt_overall$lmer_coef[need_sdt_overall$lmer_coef$coef != c("(Intercept)", "CoreNeed"), "p"]) %>% round(3) %>% format(nsmall=3)`).
+However, some of the effect sizes were largely comparable to that of the core need fulfillment (all |\textit{b}| < `r max(abs(need_sdt_overall$lmer_coef[need_sdt_overall$lmer_coef$coef != c("(Intercept)", "CoreNeed"), "b"])) %>% round(2) %>% format(nsmall=2)`, particularly that of relatedness fulfillment; see \tblref{tab:robustnessTblLong} for full results).
+
+```{r}
+#| label: need_sdt_s1
+#| include: false
+
+need_sdt_s1 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 1, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC + CompetenceC + AutonomyC + RelatednesssC",
+  structure = "PID",
+  dependent_var = "Attitude"
+)
+# need_sdt_s1$anova
+# need_sdt_s1$choice
+# need_sdt_s1$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# need_sdt_s1$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+```
+
+```{r}
+#| label: need_sdt_s2
+#| include: false
+
+# need_sdt_s2 <- select_best_lmer_model(
+#   data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes"),
+#   prediction_form = "CoreNeedC + CompetenceC + AutonomyC + RelatednesssC",
+#   structure = "PID",
+#   dependent_var = "Attitude",
+#   control = lmeControl(opt = "nlminb", msMaxIter = 500, tolerance = 1e-6)
+# )
+model0 <- lmer(
+  Attitude ~ 1 + (1 | PID),
+  data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes")
+)
+model1 <- lmer(
+  Attitude ~ CoreNeedC + CompetenceC + AutonomyC + RelatednesssC + (1 | PID),
+  data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes")
+)
+model2 <- lmer(
+  Attitude ~ CoreNeedC + CompetenceC + AutonomyC + RelatednesssC + (1 + CoreNeedC + CompetenceC + AutonomyC + RelatednesssC | PID),
+  data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes")
+)
+test <- anova(model0, model1, model2)
+test$`Pr(>Chisq)`[3] < 0.05
+rm(model0, model1, model2, test)
+
+need_sdt_s2 <- list()
+need_sdt_s2$lmer_model <- lmer(
+  Attitude ~ CoreNeedC + CompetenceC + AutonomyC + RelatednesssC + (1 | PID),
+  data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes")
+)
+need_sdt_s2$lmer_model_z <- lmer(
+  AttitudeZ ~ CoreNeedZ + CompetenceZ + AutonomyZ + RelatednesssZ + (1 | PID),
+  data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes")
+)
+
+need_sdt_s2$lmer_model %>% summ(., confint = TRUE, digits = 3)
+need_sdt_s2$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
+
+need_sdt_s2$lmer_coef <- 
+    summ(need_sdt_s2$lmer_model, confint = TRUE, scale = FALSE)$coeftable %>%
+    as_tibble %>%
+    transmute(
+      coef = rownames(summ(need_sdt_s2$lmer_model)$coeftable),
+      b = Est.,
+      df = d.f.,
+      t = `t val.`,
+      p = p,
+      lwr = `2.5%`,
+      upr = `97.5%`,
+      coef_latex = paste0(
+        "\\textit{b} = ", format(round(b, 2), nsmall = 2), 
+        ", \\textit{t}(", format(df, big.mark=","), ") = ", format(round(t, 2), nsmall = 2),
+        ", \\textit{p} ", ifelse(p < .001, "< .001", paste0("= ", format(round(p, 3), nsmall = 3))),
+        ", \\textit{95\\%CI}[",  format(round(lwr, 2), nsmall = 2), ", ",  format(round(upr, 2), nsmall = 2), "]"
       ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlWorker$lmerInterceptAttCoreIntCI <- 
-  confint(method = "Wald", mdlWorker$lmerInterceptAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlWorker$lmeAttNull, 
-      mdlWorker$lmeInterceptAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.)-1)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorker$varInterceptAttCoreInt <- 
-  lme4::VarCorr(mdlWorker$lmeInterceptAttCoreInt)
+      coef_html = paste0(
+        "<i>b</i> = ", format(round(b, 2), nsmall = 2), 
+        ", <i>t</i>(", format(df, big.mark=","), ") = ", format(round(t, 2), nsmall = 2),
+        ", <i>p</i> ", ifelse(p < .001, "< .001", paste0("= ", format(round(p, 3), nsmall = 3))),
+        ", <i>95%CI</i>[",  format(round(lwr, 2), nsmall = 2), ", ",  format(round(upr, 2), nsmall = 2), "]"
+      )
+    )
 ```
-```{r workerModelSlopesAttCoreIntX, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorker$lmeSlopesAttCoreInt <- lme(
-  thermometerDutch_1 ~
-    keyMotiveFulfilled_cwc * OutgroupInteraction,
-  random = ~ 1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  na.action=na.omit,
-  data = dtWorkerSupp$workerWithinBetween
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorker$lmerSlopesAttCoreInt <- lmer(
-    thermometerDutch_1 ~
-      keyMotiveFulfilled_cwc * OutgroupInteraction +
-      (1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID),
-    data = dtWorkerSupp$workerWithinBetween
-  ), 
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlWorker$lmerSlopesAttCoreIntCI <- 
-  confint(method = "Wald", mdlWorker$lmerSlopesAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlWorker$lmeAttNull, 
-      mdlWorker$lmeInterceptAttCoreInt,
-      mdlWorker$lmeSlopesAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorker$varSlopesAttCoreInt <- 
-  lme4::VarCorr(mdlWorker$lmeSlopesAttCoreInt)
-
-# Assumption Checks:
-mdlWorker$diagSlopesAttCoreInt <-
-  sjPlot::plot_model(mdlWorker$lmerSlopesAttCoreInt, type = "diag")
-grid.arrange(
-  mdlWorker$diagSlopesAttCoreInt[[1]],
-  mdlWorker$diagSlopesAttCoreInt[[2]]$`PID`,
-  mdlWorker$diagSlopesAttCoreInt[[3]],
-  mdlWorker$diagSlopesAttCoreInt[[4]]
-)
-
-# Plot prediction model
-mdlWorker$predSlopesAttCoreInt <- 
-  dtWorkerSupp$workerWithinBetween %>%
-  select(thermometerDutch_1, session, PID) %>% 
-  mutate(measure = predict(mdlWorker$lmeSlopesAttCoreInt,
-                           dtWorkerSupp$workerWithinBetween,
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorker$predPltSlopesAttCoreInt <-
-    ggplot(data = mdlWorker$predSlopesAttCoreInt, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Worker_PredictionPlot_SlopesAttCoreInt.png",
-  mdlWorker$predPltSlopesAttCoreInt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
+
+```{r}
+#| label: need_sdt_s3
+#| include: false
+
+need_sdt_s3 <- select_best_lmer_model(
+  data = dt_exp_all %>% filter(study == 3, OutgroupInteractionLab == "Yes"),
+  prediction_form = "CoreNeedC + CompetenceC + AutonomyC + RelatednesssC",
+  structure = "PID",
+  dependent_var = "Attitude"
+)
+# need_sdt_s3$anova
+# need_sdt_s3$choice
+# need_sdt_s3$lmer_model %>% summ(., confint = TRUE, digits = 3)
+# need_sdt_s3$lmer_model_z %>% summ(., confint = TRUE, digits = 3)
 ```
 
-To build further confidence in our results, we assessed two additional models that might offer alternative explanations.
-First, to ensure that the effect of core need fulfillment is specific to an actual contact, we compared the effect to core need fulfillment in situations without an intergroup contact.
-For this, we analyzed the generalized situational core need fulfillment (either during a contact or about the daytime in general) and tested whether the effect differed during experience sampling measurements with and without outgroup contacts.
-We found no main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeSlopesAttCoreInt, lmerCI = mdlWorker$lmerSlopesAttCoreIntCI, varName = "keyMotiveFulfilled_cwc:OutgroupInteraction")`; also see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}).
-Together with a significant main effect of having an outgroup contact, this indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-
-```{r workerOutModelInterceptAttCoreSdt, include=FALSE}
-# Create and save Model
-mdlWorkerOut$Att$lmeInterceptCoreSdt <-
-  lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
-    random = ~ 1 | PID,
-    data = dtWorkerSupp$workerOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlWorkerOut$Att$lmerInterceptCoreSdt <- lmer(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# To be compared against a model with only the self-determination theory needs
-mdlWorkerOut$Att$lmeInterceptSdt <-
-  lme(
-    thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
-    random = ~ 1 | PID,
-    data = dtWorkerSupp$workerOutWithinBetween,
-    na.action = na.exclude
-  )
-
-summ(
-  mdlWorkerOut$Att$lmerInterceptSdt <- lmer(
-    thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous steps
-anova(
-  mdlWorkerOut$Att$lmeInterceptSdt,
-  mdlWorkerOut$Att$lmeInterceptCoreSdt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-rm(lmeInterceptCoreRed)
-
-# Save variances
-mdlWorkerOut$Att$varInterceptCoreSdt <-
-  lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreSdt)
+```{r}
+#| label: need_sdt_study_coef
+#| include: false
+
+need_sdt_study_coef <- 
+  rbind(
+    need_sdt_s1$lmer_coef %>% mutate(study = 1),
+    need_sdt_s2$lmer_coef %>% mutate(study = 2),
+    need_sdt_s3$lmer_coef %>% mutate(study = 3)
+  )
+
+need_sdt_study_coef_other <- need_sdt_study_coef %>%
+  filter(
+    coef != "(Intercept)",
+    coef != "CoreNeedC"
+  ) 
 ```
-```{r workerOutModelSlopesAttCoreSdt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Att$lmeSlopesCoreSdt <-
-  lme(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
-    random = ~ 1 + keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtWorkerSupp$workerOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Att$lmerSlopesCoreSdt <- lmer(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc +
-      (1 + keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlWorkerOut$Att$lmerSlopesCoreSdtCI <- 
-  confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreSdt)
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeInterceptSdt,
-      mdlWorkerOut$Att$lmeInterceptCoreSdt, 
-      mdlWorkerOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# model with SDT only
-# Create and save Model (optimizer needed to reach convergence)
-mdlWorkerOut$Att$lmeSlopesSdt <-
-  lme(
-    thermometerDutch_1 ~
-      competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc,
-    random = ~ 1 + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtWorkerSupp$workerOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlWorkerOut$Att$lmerSlopesSdt <- lmer(
-    thermometerDutch_1 ~
-      competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc +
-      (1 + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous step
-anova(mdlWorkerOut$Att$lmeInterceptSdt,
-      mdlWorkerOut$Att$lmeSlopesSdt, 
-      mdlWorkerOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Worker: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlWorkerOut$Att$varSlopesCoreSdt <- 
-  lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreSdt)
-
-# Assumption Checks:
-mdlWorkerOut$Att$diagSlopesCoreSdt <- 
-  sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreSdt, type = "diag")
-grid.arrange(
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[1]],
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[3]],
-  mdlWorkerOut$Att$diagSlopesCoreSdt[[4]]
-)
-
-# Plot prediction model
-mdlWorkerOut$Att$predSlopesCoreSdt <- 
-  dtWorkerSupp$workerOutWithinBetween %>%
-  filter(!is.na(autonomy_1)) %>%
-  select(thermometerDutch_1, session, PID, autonomy_1) %>% 
-  mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreSdt,
-                           dtWorkerSupp$workerOutWithinBetween %>% filter(!is.na(autonomy_1)),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlWorkerOut$Att$predPltSlopesCoreSdt <-
-    ggplot(data = mdlWorkerOut$Att$predSlopesCoreSdt, aes(x = session, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = thermometerDutch_1), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreStd.png",
-  mdlWorkerOut$Att$predPltSlopesCoreSdt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-# Model comparison
-workerSdtComp <-
-  anova(
-    mdlWorkerOut$Att$lmerSlopesSdt, 
-    mdlWorkerOut$Att$lmerSlopesCoreSdt
-  ) %>%
-  as.data.frame()
-workerSdtCompDf <- workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Df"]
-workerSdtCompN <- sapply(ranef(mdlWorkerOut$Att$lmerSlopesCoreSdt), nrow)
-workerSdtCompChi <- workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
-workerSdtCompP <-
-  ifelse(workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
-         "< .001",
-         paste0("= ", workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
-
-workerSdtCompChiSq <- paste0("$\\chi^2$(", workerSdtCompDf, ", \\textit{N} = ", workerSdtCompN, ") = ", workerSdtCompChi, ", \\textit{p} ", workerSdtCompP)
-```
-
-In a final step, we controlled for other fundamental psychological needs during the contact.
-We focus on the three commonly considered self-determination needs (SDT): competence, autonomy, and relatedness.
-We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r workerSdtCompChiSq`).
-We also find that next to relatedness (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "relatedness_1_cwc")`), the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "keymotive_fulfillemt_1_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all three fundamental needs (competence and autonomy needs turning non-significant; all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
-For full results see see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and Online Supplementary Material A.
-There is, thus, considerable evidence lending confidence to the stability and relevance of psychological need fulfillment as a predictor of positive outgroup attitudes for natural intergroup contacts.
-
-\subsubsection{Study 2}
-
-```{r studentSampleInfo, include=FALSE}
-# summarize participant characteristics
-studentSampleInfo <- 
-  dtStudents$full %>%
-  mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>%
-  group_by(PID) %>%
-  summarise(
-    dailiesN = n(), 
-    morningN = sum(periodMA=="morning"),
-    afternoonN = sum(periodMA=="afternoon"),
-    age = age,
-    gender = gender,
-    nationality = nationality
-  ) %>%
-  distinct
-
-# look at frequencies of characteristics 
-table(studentSampleInfo$gender)
-table(as.character(studentSampleInfo$nationality))
-
-# divide into trait and state
-dtStudentSupp$studentWithinBetween <-
-  MlTraitState(
-    data = dtStudentSupp$studentInteractionType,
-    id = "PID",
-    selection =
-      c(
-        "KeyNeedFullfillment",
-        "Competence",
-        "Autonomy",
-        "Relatedness",
-        "AttitudesDutch",
-        "quality_overall",
-        "OutgroupInteraction",
-        "NonOutgroupInteraction",
-        "OutgroupInteractionM",
-        "NonOutgroupInteractionM"
-      )
-  )
-dtStudentSupp$studentOutWithinBetween <-
-  MlTraitState(
-    data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
-    id = "PID",
-    selection =
-      c(
-        "KeyNeedFullfillment",
-        "Competence",
-        "Autonomy",
-        "Relatedness",
-        "AttitudesDutch",
-        "quality_overall"
-      )
-  )
-```
-
-```{r studentModelOlsAttFreqQual, include=FALSE}
-# create list to store Worker models
-mdlStudent <- list()
-```
-
-```{r studentModelMLAttNull, include=FALSE}
-# Create and save Model
-mdlStudent$lmerAttNull <-
-  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
-    data = dtStudents$full
-  ) # use optim if it does not converge
-
-mdlStudent$lmeAttNull <-
-  lme(
-    AttitudesDutch ~ 1,
-    random = ~ 1 | PID,
-    data = dtStudents$full,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(mdlStudent$lmerAttNull) #or with the lme function
-summ(mdlStudent$lmerAttNull, digits = 3)
-
-# Save variances
-mdlStudent$varAttNull <- 
-  VarCorr(mdlStudent$lmeAttNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlStudent$tauAttNull <- 
-  as.numeric(mdlStudent$varAttNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlStudent$sigmaAttNull <- 
-  as.numeric(mdlStudent$varAttNull[2])
-# The ICC estimate (between/between+within) is:
-mdlStudent$IccAttNull <-
-  (as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))
-mdlStudent$IccPercAttNull <-
-  ((as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))) * 100
-```
-
-```{r studentOutModelMLAttNull, include=FALSE}
-# create empty list to organize models
-mdlStudentOut <- 
-  list(
-    Att = list(),
-    Qlt = list()
-  )
-
-# Create and save Model
-mdlStudentOut$Att$lmerNull <-
-  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), 
-             data = dtStudentSupp$studentOutgroupInteraction) # use optim if it does not converge
-mdlStudentOut$Att$lmeNull <-
-  lme(
-    AttitudesDutch ~ 1,
-    random = ~ 1 | PID,
-    data = dtStudentSupp$studentOutgroupInteraction,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.ML.r) #or with the lme function
-summ(mdlStudentOut$Att$lmerNull, digits = 3, center = TRUE)
-
-# Save variances
-mdlStudentOut$Att$varNull <- 
-  VarCorr(mdlStudentOut$Att$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlStudentOut$Att$tauNull <- 
-  as.numeric(mdlStudentOut$Att$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlStudentOut$Att$sigmaNull <- 
-  as.numeric(mdlStudentOut$Att$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlStudentOut$Att$IccNull <-
-  (as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))
-mdlStudentOut$Att$IccPercNull <-
-  ((as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))) * 100
-```
-
-```{r studentOutModelMLQltNull, include=FALSE}
-# Create and save Model
-mdlStudentOut$Qlt$lmerNull <-
-  lme4::lmer(quality_overall ~ 1 + (1 | PID), 
-             data = dtStudentSupp$studentOutWithinBetween) # use optim if it does not converge
-mdlStudentOut$Qlt$lmeNull <-
-  mdlStudentOut$Qlt$lmeNull <-lme(
-    quality_overall ~ 1,
-    random = ~ 1 | PID,
-    data = dtStudentSupp$studentOutWithinBetween,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.Qual.ML.r) #or with the lme function
-summ(mdlStudentOut$Qlt$lmerNull, digits = 3)
-
-# Save variances
-mdlStudentOut$Qlt$varNull <- 
-  VarCorr(mdlStudentOut$Qlt$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlStudentOut$Qlt$tauNull <- 
-  as.numeric(mdlStudentOut$Qlt$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlStudentOut$Qlt$sigmaNull <- 
-  as.numeric(mdlStudentOut$Qlt$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlStudentOut$Qlt$IccNull <-
-  (as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))
-mdlStudentOut$Qlt$IccPercNull <-
-  ((as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))) * 100
-```
-
-```{r studentModelInterceptAttCoreInt, include=FALSE}
-# Create and save Model
-mdlStudent$lmeInterceptAttCoreInt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction,
-    random =  ~ 1 | PID,
-    data = dtStudentSupp$studentWithinBetween
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudent$lmerInterceptAttCoreInt <- lmer(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction + (1 | PID),
-    data = dtStudentSupp$studentWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudent$lmerInterceptAttCoreIntCI <- 
-  confint(method = "Wald", mdlStudent$lmerInterceptAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlStudent$lmeAttNull, 
-      mdlStudent$lmeInterceptAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.)-1)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudent$varInterceptAttCoreInt <- 
-  lme4::VarCorr(mdlStudent$lmeInterceptAttCoreInt)
-```
-```{r studentModelSlopesAttCoreIntX, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudent$lmeSlopesAttCoreInt <- lme(
-  AttitudesDutch ~
-    KeyNeedFullfillment_cwc * OutgroupInteraction,
-  random = ~ 1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  data = dtStudentSupp$studentWithinBetween
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudent$lmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFullfillment_cwc * OutgroupInteraction +
-      (1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID),
-    data = dtStudentSupp$studentWithinBetween
-  ), 
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudent$lmerSlopesAttCoreIntCI <- 
-  confint(method = "Wald", mdlStudent$lmerSlopesAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlStudent$lmeAttNull, 
-      mdlStudent$lmeInterceptAttCoreInt,
-      mdlStudent$lmeSlopesAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudent$varSlopesAttCoreInt <- 
-  lme4::VarCorr(mdlStudent$lmeSlopesAttCoreInt)
-
-# Assumption Checks:
-mdlStudent$diagSlopesAttCoreInt <-
-  sjPlot::plot_model(mdlStudent$lmerSlopesAttCoreInt, type = "diag")
-grid.arrange(
-  mdlStudent$diagSlopesAttCoreInt[[1]],
-  mdlStudent$diagSlopesAttCoreInt[[2]]$`PID`,
-  mdlStudent$diagSlopesAttCoreInt[[3]],
-  mdlStudent$diagSlopesAttCoreInt[[4]]
-)
-
-# Plot prediction model
-mdlStudent$predSlopesAttCoreInt <- 
-  dtStudentSupp$studentWithinBetween %>%
-  filter(PID %in% dtStudentSupp$studentPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlStudent$lmeSlopesAttCoreInt,
-                           dtStudentSupp$studentWithinBetween %>% filter(PID %in% dtStudentSupp$studentPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudent$predPltSlopesAttCoreInt <-
-    ggplot(data = mdlStudent$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Student_PredictionPlot_SlopesAttCoreInt.png",
-  mdlStudent$predPltSlopesAttCoreInt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-Also for Study 2, we checked for alternative models.
-First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is only a minuscule main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc:OutgroupInteraction")`).
-Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteraction")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous study, albeit with a slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see \tblref{tab:robustnessTblLong} and for visual comparison see \fgrref{fig:Robustness}).
-
-```{r studentOutModelInterceptAttCoreSdt, include=FALSE}
-# Create and save Model
-mdlStudentOut$Att$lmeInterceptCoreSdt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 | PID,
-    data = dtStudentSupp$studentOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlStudentOut$Att$lmerInterceptCoreSdt <- lmer(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtStudentSupp$studentOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudentOut$Att$lmerInterceptCoreSdtCI <- 
-  confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCoreSdt)
-
-# To be compared against a model with only the self-determination theory needs
-mdlStudentOut$Att$lmeInterceptSdt <-
-  lme(
-    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 | PID,
-    data = dtStudentSupp$studentOutWithinBetween,
-    na.action = na.exclude
-  )
-
-summ(
-  mdlStudentOut$Att$lmerInterceptSdt <- lmer(
-    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtStudentSupp$studentOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous steps
-anova(
-  mdlStudentOut$Att$lmeNull,
-  mdlStudentOut$Att$lmeInterceptSdt,
-  mdlStudentOut$Att$lmeInterceptCoreSdt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-rm(lmeInterceptCoreRed)
-
-# Save variances
-mdlStudentOut$Att$varInterceptCoreSdt <-
-  lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreSdt)
-```
-```{r studentOutModelSlopesAttCoreSdt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudentOut$Att$lmeSlopesCoreSdt <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 + KeyNeedFullfillment_cwc + Competence_cwc + Relatedness_cwc | PID,
-    control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
-    data = dtStudentSupp$studentOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Att$lmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtStudentSupp$studentOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# 95%CI
-mdlStudentOut$Att$lmerSlopesCoreSdtCI <- 
-  confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreSdt)
-
-# Compare new model to previous step
-anova(mdlStudentOut$Att$lmeInterceptSdt,
-      mdlStudentOut$Att$lmeInterceptCoreSdt, 
-      mdlStudentOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# model with SDT only
-# Create and save Model (optimizer needed to reach convergence)
-mdlStudentOut$Att$lmeSlopesSdt <-
-  lme(
-    AttitudesDutch ~
-      Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtStudentSupp$studentOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlStudentOut$Att$lmerSlopesSdt <- lmer(
-    AttitudesDutch ~
-      Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtStudentSupp$studentOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous step
-anova(mdlStudentOut$Att$lmeInterceptSdt,
-      mdlStudentOut$Att$lmeSlopesSdt, 
-      mdlStudentOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Student: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlStudentOut$Att$varSlopesCoreSdt <- 
-  lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreSdt)
-
-# Assumption Checks:
-mdlStudentOut$Att$diagSlopesCoreSdt <- 
-  sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreSdt, type = "diag")
-grid.arrange(
-  mdlStudentOut$Att$diagSlopesCoreSdt[[1]],
-  mdlStudentOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
-  mdlStudentOut$Att$diagSlopesCoreSdt[[3]],
-  mdlStudentOut$Att$diagSlopesCoreSdt[[4]]
-)
-
-# Plot prediction model
-mdlStudentOut$Att$predSlopesCoreSdt <- 
-  dtStudentSupp$studentOutWithinBetween %>%
-  filter(PID %in% dtStudentSupp$studentOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID, Autonomy) %>% 
-  mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreSdt,
-                           dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlStudentOut$Att$predPltSlopesCoreSdt <-
-    ggplot(data = mdlStudentOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreStd.png",
-  mdlStudentOut$Att$predPltSlopesCoreSdt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-# Model comparison
-studentSdtComp <-
-  anova(
-    mdlStudentOut$Att$lmerSlopesSdt, 
-    mdlStudentOut$Att$lmerSlopesCoreSdt
-  ) %>%
-  as.data.frame()
-studentSdtCompDf <- studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Df"]
-studentSdtCompN <- sapply(ranef(mdlStudentOut$Att$lmerSlopesCoreSdt), nrow)
-studentSdtCompChi <- studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
-studentSdtCompP <-
-  ifelse(studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
-         "< .001",
-         paste0("= ", studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
-
-studentSdtCompChiSq <- paste0("$\\chi^2$(", studentSdtCompDf, ", \\textit{N} = ", studentSdtCompN, ") = ", studentSdtCompChi, ", \\textit{p} ", studentSdtCompP)
-```
-
-In a final step, we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
-We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r studentSdtCompChiSq`).
-We find that the core need fulfillment explained the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFullfillment_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, different from the first study, relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes in this larger sample.
-For full results see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and Online Supplementary Material A.
-This means that also within this second sample, the fulfillment of psychological needs during intergroup contact remained a key predictor of positive outgroup attitudes, even when taking into account several alternative models.
-
-\subsubsection{Study 3}
-
-```{r medicalSampleInfo, include=FALSE}
-# extract demographic information from eligibility questionnaire
-medicalDemographicSupp <- 
-  dtMedical$raw.eligibility %>%
-  filter(session %in% dtMedical$full$session) %>%
-  select(session, nationality, studentBachMa)
-# summarize participant characteristics
-
-medicalSampleInfo <-
-  merge(dtMedical$full, medicalDemographicSupp, by = "session") %>%
-  mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>%
-  group_by(PID) %>%
-  summarise(
-    dailiesN = n(), 
-    morningN = sum(periodMA=="morning"),
-    afternoonN = sum(periodMA=="afternoon"),
-    age = age,
-    gender = gender,
-    nationality = nationality
-  ) %>%
-  distinct
-
-# divide into trait and state
-dtMedicalSupp$medicalWithinBetween <- 
-  MlTraitState(
-    data = dtMedical$full,
-    id = "PID",
-    selection =
-      c(
-        "OutgroupInteraction",
-        "NonOutgroupInteraction",
-        "OutgroupInteractionM",
-        "NonOutgroupInteractionM"
-      )
-  )
-
-```
-
-```{r medicalModelOlsAttFreqQual, include=FALSE}
-# create list to store Worker models
-mdlMedical <- list()
-```
-
-```{r medicalModelMLAttNull, include=FALSE}
-# Create and save Model
-mdlMedical$lmerAttNullType <-
-  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
-             data = dtMedical$full %>%
-               filter(complete.cases(
-                 OutgroupInteraction, NonOutgroupInteraction
-               ))) # use optim if it does not converge
-
-mdlMedical$lmeAttNullType <-
-  lme(
-    AttitudesDutch ~ 1,
-    random = ~ 1 | PID,
-    data = dtMedical$full %>%
-      filter(complete.cases(
-        OutgroupInteraction, NonOutgroupInteraction
-      )),
-    na.action = na.omit,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(mdlMedical$lmerAttNull) #or with the lme function
-summ(mdlMedical$lmerAttNullType, digits = 3)
-
-# Save variances
-mdlMedical$varAttNullType <- 
-  VarCorr(mdlMedical$lmeAttNullType) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlMedical$tauAttNullType <- 
-  as.numeric(mdlMedical$varAttNullType[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlMedical$sigmaAttNullType <- 
-  as.numeric(mdlMedical$varAttNullType[2])
-# The ICC estimate (between/between+within) is:
-mdlMedical$IccAttNullType <-
-  (as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))
-mdlMedical$IccPercAttNull <-
-  ((as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))) * 100
-```
-
-```{r medicalOutModelMLAttNull, include=FALSE}
-# create empty list to organize models
-mdlMedicalOut <- 
-  list(
-    Att = list(),
-    Qlt = list()
-  )
-
-# Create and save Model
-mdlMedicalOut$Att$lmerNull <-
-  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
-             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
-mdlMedicalOut$Att$lmeNull <-
-  lme(
-    AttitudesDutch ~ 1,
-    random = ~ 1 | PID,
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.omit,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.ML.r) #or with the lme function
-summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE)
-
-# Save variances
-mdlMedicalOut$Att$varNull <- 
-  VarCorr(mdlMedicalOut$Att$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlMedicalOut$Att$tauNull <- 
-  as.numeric(mdlMedicalOut$Att$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlMedicalOut$Att$sigmaNull <- 
-  as.numeric(mdlMedicalOut$Att$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlMedicalOut$Att$IccNull <-
-  (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))
-mdlMedicalOut$Att$IccPercNull <-
-  ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100
-```
-
-```{r medicalOutModelMLQltNull, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Qlt$lmerNull <-
-  lme4::lmer(qualityOverall ~ 1 + (1 | PID), 
-             data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
-mdlMedicalOut$Qlt$lmeNull <-
-  mdlMedicalOut$Qlt$lmeNull <-lme(
-    qualityOverall ~ 1,
-    random = ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(Null.Out.Qual.ML.r) #or with the lme function
-summ(mdlMedicalOut$Qlt$lmerNull, digits = 3)
-
-# Save variances
-mdlMedicalOut$Qlt$varNull <- 
-  VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances
-# The estimate of (between-group or Intercept variance, tau_{00}^2):
-mdlMedicalOut$Qlt$tauNull <- 
-  as.numeric(mdlMedicalOut$Qlt$varNull[1])
-# and the estimate of (within-group or residual variance, sigma^2) is:
-mdlMedicalOut$Qlt$sigmaNull <- 
-  as.numeric(mdlMedicalOut$Qlt$varNull[2])
-# The ICC estimate (between/between+within) is:
-mdlMedicalOut$Qlt$IccNull <-
-  (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))
-mdlMedicalOut$Qlt$IccPercNull <-
-  ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100
-```
-
-```{r medicalModelAttNullInt, include=FALSE}
-# Create and save Model
-mdlMedical$lmerAttNullInt <-
-  lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),
-             data = dtMedical$full %>%
-               filter(complete.cases(
-                 OutgroupInteraction
-               ))) # use optim if it does not converge
-
-mdlMedical$lmeAttNullInt <-
-  lme(
-    AttitudesDutch ~ 1,
-    random = ~ 1 | PID,
-    data = dtMedical$full %>%
-      filter(complete.cases(
-        OutgroupInteraction
-      )),
-    na.action = na.omit,
-    control = list(opt = "nlmimb")
-  ) # use optim if it does not converge
-
-# Get summary with p-values (Satterthwaite's method)
-# summary(mdlMedical$lmerAttNull) #or with the lme function
-summ(mdlMedical$lmerAttNullInt, digits = 3)
-```
-
-```{r medicalModelInterceptAttCoreInt, include=FALSE}
-# Create and save Model
-mdlMedical$lmeInterceptAttCoreInt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction,
-    random =  ~ 1 | PID,
-    na.action = na.omit,
-    data = dtMedical$full
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedical$lmerInterceptAttCoreInt <- lmer(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction + (1 | PID),
-    data = dtMedical$full
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedical$lmerInterceptAttCoreIntCI <- 
-  confint(method = "Wald", mdlMedical$lmerInterceptAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlMedical$lmeAttNullInt, 
-      mdlMedical$lmeInterceptAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.)-1)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedical$varInterceptAttCoreInt <- 
-  lme4::VarCorr(mdlMedical$lmeInterceptAttCoreInt)
-```
-
-```{r medicalModelSlopesAttCoreIntX, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedical$lmeSlopesAttCoreInt <- lme(
-  AttitudesDutch ~
-    KeyNeedFulfillment_cwc * OutgroupInteraction,
-  random = ~ 1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID,
-  control = lmeControl(opt = "optim"),
-  na.action = na.omit,
-  data = dtMedical$full
-)
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedical$lmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc * OutgroupInteraction +
-      (1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID),
-    data = dtMedical$full
-  ), 
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedical$lmerSlopesAttCoreIntCI <- 
-  confint(method = "Wald", mdlMedical$lmerSlopesAttCoreInt)
-
-# Compare new model to previous step
-anova(mdlMedical$lmeAttNullInt, 
-      mdlMedical$lmeInterceptAttCoreInt,
-      mdlMedical$lmeSlopesAttCoreInt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  add_rownames(., var = "Description") %>%
-  mutate(Description = gsub(".*\\$", "", Description)) %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedical$varSlopesAttCoreInt <- 
-  lme4::VarCorr(mdlMedical$lmeSlopesAttCoreInt)
-
-# Assumption Checks:
-mdlMedical$diagSlopesAttCoreInt <-
-  sjPlot::plot_model(mdlMedical$lmerSlopesAttCoreInt, type = "diag")
-grid.arrange(
-  mdlMedical$diagSlopesAttCoreInt[[1]],
-  mdlMedical$diagSlopesAttCoreInt[[2]]$`PID`,
-  mdlMedical$diagSlopesAttCoreInt[[3]],
-  mdlMedical$diagSlopesAttCoreInt[[4]]
-)
-
-# Plot prediction model
-mdlMedical$predSlopesAttCoreInt <- 
-  dtMedical$full %>%
-  filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
-  filter(PID %in% dtMedicalSupp$medicalPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID) %>% 
-  mutate(measure = predict(mdlMedical$lmeSlopesAttCoreInt,
-                           dtMedical$full %>% 
-                             filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>%
-                             filter(PID %in% dtMedicalSupp$medicalPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedical$predPltSlopesAttCoreInt <-
-    ggplot(data = mdlMedical$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap(~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/Medical_PredictionPlot_SlopesAttCoreInt.png",
-  mdlMedical$predPltSlopesAttCoreInt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-```
-
-As with the previous two studies, we checked for alternative models of the key need fulfillment.
-First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
-Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "OutgroupInteractionYes")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous studies.
-
-```{r medicalOutModelInterceptAttCoreSdt, include=FALSE}
-# Create and save Model
-mdlMedicalOut$Att$lmeInterceptCoreSdt <-
-  lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 | PID,
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method)
-summ(
-  mdlMedicalOut$Att$lmerInterceptCoreSdt <- lmer(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# To be compared against a model with only the self-determination theory needs
-mdlMedicalOut$Att$lmeInterceptSdt <-
-  lme(
-    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 | PID,
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-summ(
-  mdlMedicalOut$Att$lmerInterceptSdt <- lmer(
-    AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous steps
-anova(
-  mdlMedicalOut$Att$lmeInterceptSdt,
-  mdlMedicalOut$Att$lmeInterceptCoreSdt
-  ) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varInterceptCoreSdt <-
-  lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreSdt)
-```
-
-```{r medicalOutModelSlopesAttCoreSdt, include=FALSE}
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesCoreSdt <-
-  lme(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc + Competence_cwc + Relatedness_cwc | PID,
-    control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100),
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-mdlMedicalOut$Att$lmerSlopesCoreSdtCI <- 
-  confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreSdt)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeInterceptSdt,
-      mdlMedicalOut$Att$lmeInterceptCoreSdt, 
-      mdlMedicalOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# model with SDT only
-# Create and save Model (optimizer needed to reach convergence)
-mdlMedicalOut$Att$lmeSlopesSdt <-
-  lme(
-    AttitudesDutch ~
-      Competence_cwc + Autonomy_cwc + Relatedness_cwc,
-    random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID,
-    control = lmeControl(opt = "optim"),
-    data = dtMedicalSupp$medicalOutWithinBetween,
-    na.action = na.exclude
-  )
-
-# Get summary with p-values (Satterthwaite's method) [+ save model for plotting]
-summ(
-  mdlMedicalOut$Att$lmerSlopesSdt <- lmer(
-    AttitudesDutch ~
-      Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = dtMedicalSupp$medicalOutWithinBetween
-  ),
-  confint = TRUE,
-  digits = 3
-)
-
-# Compare new model to previous step
-anova(mdlMedicalOut$Att$lmeInterceptSdt,
-      mdlMedicalOut$Att$lmeSlopesSdt, 
-      mdlMedicalOut$Att$lmeSlopesCoreSdt) %>%
-  as.data.frame() %>%
-  select(-call) %>%
-  mutate(
-    L.Ratio = round(L.Ratio, 3),
-    `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001")
-  ) %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Medical: Model Comparison",
-    format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = rep("c", ncol(.)),
-    digits = 3
-  ) %>%
-  kable_styling(position = "left")
-
-# Save variances
-mdlMedicalOut$Att$varSlopesCoreSdt <- 
-  lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreSdt)
-
-# Assumption Checks:
-mdlMedicalOut$Att$diagSlopesCoreSdt <- 
-  sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreSdt, type = "diag")
-grid.arrange(
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[1]],
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[2]]$`PID`,
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[3]],
-  mdlMedicalOut$Att$diagSlopesCoreSdt[[4]]
-)
-
-# Plot prediction model
-mdlMedicalOut$Att$predSlopesCoreSdt <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
-  filter(complete.cases(
-    KeyNeedFulfillment,
-    Autonomy, Competence, Relatedness
-    )) %>%
-  filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
-  select(AttitudesDutch, TIDnum, PID, Autonomy, Competence, Relatedness) %>% 
-  mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreSdt,
-                           dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(
-                               KeyNeedFulfillment,
-                               Autonomy, Competence, Relatedness
-                             )) %>%
-                             filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
-                           re.form = NA
-                           )
-         )
-
-(
-  mdlMedicalOut$Att$predPltSlopesCoreSdt <-
-    ggplot(data = mdlMedicalOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) +
-    geom_line(alpha = 1, color = "blue") +
-    geom_line(aes(y = AttitudesDutch), alpha = 1) +
-    facet_wrap( ~ PID, ncol = 6) +
-    xlab("Time") +
-    ylab("Outgroup Attitudes") +
-    theme_Publication()
-)
-ggsave(
-  filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreStd.png",
-  mdlMedicalOut$Att$predPltSlopesCoreSdt,
-  width = 18,
-  height = 12,
-  dpi = 800,
-  units = "cm",
-  device = "png"
-)
-
-# Model comparison
-medicalSdtComp <-
-  anova(
-    mdlMedicalOut$Att$lmerSlopesSdt, 
-    mdlMedicalOut$Att$lmerSlopesCoreSdt
-  ) %>%
-  as.data.frame()
-medicalSdtCompDf <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Df"]
-medicalSdtCompN <- sapply(ranef(mdlMedicalOut$Att$lmerSlopesCoreSdt), nrow)
-medicalSdtCompChi <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2)
-medicalSdtCompP <-
-  ifelse(medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001,
-         "< .001",
-         paste0("= ", medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3)))
-
-medicalSdtCompChiSq <- paste0("$\\chi^2$(", medicalSdtCompDf, ", \\textit{N} = ", medicalSdtCompN, ") = ", medicalSdtCompChi, ", \\textit{p} ", medicalSdtCompP)
-```
-
-In a final step, we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
-We find that the core need fulfillment adds additional variance above a model with only the self-determination theory needs (random slopes models; `r medicalSdtCompChiSq`).
-We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFulfillment_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, similar to the previous study, in this large sample relatedness (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each also predicted positive outgroup attitudes independently.
-This being said, the regression coefficient for the core need was three times larger (with all scaling being equal).
-For full results see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness} as well as Online Supplementary Material A.
-
-```{r robustnessTblLong, include=FALSE}
-# Table of all robustness checks (w/ and w/out SDT only)
-
-# Full Sample
-# Study 1:
-robustTblWorkerFull <- 
-  dtWorkerSupp$workerWithinBetween %>%
-  select(
-    AttitudesDutch = thermometerDutch_1,
-    AttitudesDutch_zwc = thermometerDutch_1_zwc,
-    CoreNeed_cwc = keyMotiveFulfilled_cwc,
-    CoreNeed_zwc = keyMotiveFulfilled_zwc,
-    OutgroupInteraction = OutgroupInteraction,
-    OutgroupInteraction_zwc = OutgroupInteraction_zwc,
-    PID = PID
-  )
-mdlWorkerLmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc * OutgroupInteraction +
-      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
-    data = robustTblWorkerFull
-  )
-mdlWorkerLmerSlopesAttCoreIntZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc * OutgroupInteraction_zwc +
-      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
-    data = robustTblWorkerFull
-  )
-#Study 2:
-robustTblStudentFull <- 
-  dtStudentSupp$studentWithinBetween %>%
-  select(
-    AttitudesDutch = AttitudesDutch,
-    AttitudesDutch_zwc = AttitudesDutch_zwc,
-    CoreNeed_cwc = KeyNeedFullfillment_cwc,
-    CoreNeed_zwc = KeyNeedFullfillment_zwc,
-    OutgroupInteraction = OutgroupInteraction,
-    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
-    PID = PID
-  )
-mdlStudentLmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc * OutgroupInteraction +
-      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
-    data = robustTblStudentFull
-  )
-mdlStudentLmerSlopesAttCoreIntZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc * OutgroupInteraction_zwc +
-      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
-    data = robustTblStudentFull
-  )
-#Study 3:
-robustTblMedicalFull <- 
-  dtMedicalSupp$medicalWithinBetween %>%
-  select(
-    AttitudesDutch = AttitudesDutch,
-    AttitudesDutch_zwc = AttitudesDutch_zwc,
-    CoreNeed_cwc = KeyNeedFulfillment_cwc,
-    CoreNeed_zwc = KeyNeedFulfillment_zwc,
-    OutgroupInteraction = OutgroupInteraction,
-    OutgroupInteraction_zwc = OutgroupInteraction_zwc, 
-    PID = PID
-  )
-mdlMedicalLmerSlopesAttCoreInt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc * OutgroupInteraction +
-      (1 + CoreNeed_cwc + OutgroupInteraction | PID),
-    #data = dtMedical$full
-    data = robustTblMedicalFull
-  )
-mdlMedicalLmerSlopesAttCoreIntZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc * OutgroupInteraction_zwc +
-      (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID),
-    #data = dtMedical$full
-    data = robustTblMedicalFull
-  )
-
-# SDT
-# Study 1:
-robustTblWorkerOut <- 
-  dtWorkerSupp$workerOutWithinBetween %>%
-  select(
-    AttitudesDutch = thermometerDutch_1,
-    AttitudesDutch_zwc = thermometerDutch_1_zwc,
-    CoreNeed_cwc = keymotive_fulfillemt_1_cwc,
-    CoreNeed_zwc = keymotive_fulfillemt_1_zwc,
-    Competence_cwc = competence_1_cwc,
-    Competence_zwc = competence_1_zwc,
-    Autonomy_cwc = autonomy_1_cwc,
-    Autonomy_zwc = autonomy_1_zwc,
-    Relatedness_cwc = relatedness_1_cwc,
-    Relatedness_zwc = relatedness_1_zwc,
-    PID = PID
-  )
-mdlWorkerOutLmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = robustTblWorkerOut
-  )
-mdlWorkerOutLmerSlopesCoreSdtZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
-      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
-    data = robustTblWorkerOut
-  )
-# Study 2:
-robustTblStudentOut <- 
-  dtStudentSupp$studentOutWithinBetween %>%
-  select(
-    AttitudesDutch = AttitudesDutch,
-    AttitudesDutch_zwc = AttitudesDutch_zwc,
-    CoreNeed_cwc = KeyNeedFullfillment_cwc,
-    CoreNeed_zwc = KeyNeedFullfillment_zwc,
-    Competence_cwc = Competence_cwc,
-    Competence_zwc = Competence_zwc,
-    Autonomy_cwc = Autonomy_cwc,
-    Autonomy_zwc = Autonomy_zwc,
-    Relatedness_cwc = Relatedness_cwc,
-    Relatedness_zwc = Relatedness_zwc,
-    PID = PID
-  )
-mdlStudentOutLmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = robustTblStudentOut
-  )
-mdlStudentOutLmerSlopesCoreSdtZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
-      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
-    data = robustTblStudentOut
-  )
-# Study 3:
-robustTblMedicalOut <- 
-  dtMedicalSupp$medicalOutWithinBetween %>%
-  select(
-    AttitudesDutch = AttitudesDutch,
-    AttitudesDutch_zwc = AttitudesDutch_zwc,
-    CoreNeed_cwc = KeyNeedFulfillment_cwc,
-    CoreNeed_zwc = KeyNeedFulfillment_zwc,
-    Competence_cwc = Competence_cwc,
-    Competence_zwc = Competence_zwc,
-    Autonomy_cwc = Autonomy_cwc,
-    Autonomy_zwc = Autonomy_zwc,
-    Relatedness_cwc = Relatedness_cwc,
-    Relatedness_zwc = Relatedness_zwc,
-    PID = PID
-  )
-mdlMedicalOutLmerSlopesCoreSdt <- lmer(
-    AttitudesDutch ~
-      CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc +
-      (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID),
-    data = robustTblMedicalOut
-  )
-mdlMedicalOutLmerSlopesCoreSdtZ <- lmer(
-    AttitudesDutch_zwc ~
-      CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc +
-      (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID),
-    data = robustTblMedicalOut
-  )
+
+When looking at the individual studies, we again saw that core need fulfillemnt remained a consistent predictor of outgroup attitudes, even after accounting for the self-determination theory need (all |\textit{b}| > `r min(abs(need_sdt_study_coef[need_sdt_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(need_sdt_study_coef[need_sdt_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(need_sdt_study_coef[need_sdt_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3))`).
+However, across all three studies the fulfillment of relatedness motives also emerged as a consistent predictor of outgroup attitudes (all |\textit{b}| > `r min(abs(need_sdt_study_coef[need_sdt_study_coef$coef == "RelatednesssC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(need_sdt_study_coef[need_sdt_study_coef$coef == "RelatednesssC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(need_sdt_study_coef[need_sdt_study_coef$coef == "RelatednesssC", "p"]) %>% round(3) %>% format(nsmall=3))`).
+Additionally, in the larger studies 2 and 3 competence fulfillment was also related to more positive outgroup attitudes (study 2: `r get_latex_coef(need_sdt_study_coef %>% filter(study == 2), "CompetenceC")`, study 3: `r get_latex_coef(need_sdt_study_coef %>% filter(study == 3), "CompetenceC")`).
+None of the autonomy fulfillment effects reached statistical significance nor did the competence fulfillment during study 1 (see \tblref{tab:robustnessTblLong} for the full results).
+In short, find that across our samples, relatedness fulfillment (and to a smaller extend competence fulfillment) are instrumental in understanding when an outgroup contact leads to more positive outgroup attitudes.
+Importantly, even when considering these effects situational core need fulfillment remains a strong and consistent predictor of outgroup attitudes.
+In some cases, we even find that core need fulfillment takes on some of the variance that would otherwise be explained by the self-determination theory needs (see Online Supplemental Material A).
+
+<!-- TABLES -->
+
+```{r}
+#| label: robustnessTblLong
+#| include: false
 
@@
 mdlRobustTblElements <- list(
-  # full
-  c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ),
-  c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ),
-  c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ),
-  # outgroup
-  c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ),
-  c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ),
-  c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ)
+  # Contact specific
+  contact_overall = c(contact_overall$lmer_model, contact_overall$lmer_model_z),
+  contact_s1 = c(contact_s1$lmer_model, contact_s1$lmer_model_z),
+  contact_s2 = c(contact_s2$lmer_model, contact_s2$lmer_model_z),
+  contact_s3 = c(contact_s3$lmer_model, contact_s3$lmer_model_z),
+  # Accidental
+  accidental_overall = c(accidental_overall$lmer_model, accidental_overall$lmer_model_z),
+  accidental_s1 = c(accidental_s1$lmer_model, accidental_s1$lmer_model_z),
+  accidental_s2 = c(accidental_s2$lmer_model, accidental_s2$lmer_model_z),
+  accidental_s3 = c(accidental_s3$lmer_model, accidental_s3$lmer_model_z),
+  # well-being core
+  wellbeing_core_overall = c(wellbeing_core_overall$lmer_model, wellbeing_core_overall$lmer_model_z),
+  wellbeing_core_s1 = c(wellbeing_core_s1$lmer_model, wellbeing_core_s1$lmer_model_z),
+  wellbeing_core_s2 = c(wellbeing_core_s2$lmer_model, wellbeing_core_s2$lmer_model_z),
+  wellbeing_core_s3 = c(wellbeing_core_s3$lmer_model, wellbeing_core_s3$lmer_model_z),
+  # # POTENTIALLT well-being full
+  # c(wellbeing_full_overall$lmer_model, wellbeing_full_s1$lmer_model_z),
+  # c(wellbeing_full_s1$lmer_model, wellbeing_full_s1$lmer_model_z),
+  # c(wellbeing_full_s2$lmer_model, wellbeing_full_s2$lmer_model_z),
+  # c(wellbeing_full_s3$lmer_model, wellbeing_full_s3$lmer_model_z),
+  # Need type
+  need_type_overall = c(need_type_overall$lmer_model, need_type_overall$lmer_model_z),
+  need_type_s1 = c(need_type_s1$lmer_model, need_type_s1$lmer_model_z),
+  need_type_s2 = c(need_type_s2$lmer_model, need_type_s2$lmer_model_z),
+  need_type_s3 = c(need_type_s3$lmer_model, need_type_s3$lmer_model_z),
+  # Need SDT
+  need_sdt_overall = c(need_sdt_overall$lmer_model, need_sdt_overall$lmer_model_z),
+  need_sdt_s1 = c(need_sdt_s1$lmer_model, need_sdt_s1$lmer_model_z),
+  need_sdt_s2 = c(need_sdt_s2$lmer_model, need_sdt_s2$lmer_model_z),
+  need_sdt_s3 = c(need_sdt_s3$lmer_model, need_sdt_s3$lmer_model_z)
   )
@@
 for (i in 1:length(mdlRobustTblElements)) {
-  mdlRobustPrep[[i]] <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])
+  mdlRobustPrep[[names(mdlRobustTblElements)[[i]]]] <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]], name = names(mdlRobustTblElements)[[i]])
 }
 
-# manual assembly
+# extract important elements
 shortRobustPrep <- list()
 for(i in 1:length(mdlRobustPrep)){
-  study <- str_extract(mdlRobustPrep[[i]]$fit$data, "Worker|Student|Medical")
-  sample <- str_extract(mdlRobustPrep[[i]]$fit$data, "Full|Out")
-  #dv <- sub(" ~.*", "", mdlRobustPrep[[i]]$fit$formula)
-  #pred <- gsub("\\(Intercept\\)", "", paste(mdlRobustPrep[[i]]$coeficients$coef, collapse = ''))
-
-  name <- paste(study, sample, sep='.')
   tmp <- rbind(
@@
   )
-  shortRobustPrep[[name]] <- tmp
+  shortRobustPrep[[mdlRobustPrep[[i]]$fit$name]] <- tmp
 }
 
-tmp <- shortRobustPrep[grepl("Full", names(shortRobustPrep))]
-fullRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Full$coef)
-for (i in 1:length(tmp)){
-  fullRobustTbl <- join(fullRobustTbl, tmp[[i]], by = "coef")
+analyses <- unique(sub("_(?!.*_).*", "", names(mdlRobustPrep), perl = TRUE))
+studies <- unique(sub(".*_(.*)", "\\1", names(mdlRobustPrep)))
+
+robustTblLong <- list()
+for (analysis in analyses) {
+  mylist <- shortRobustPrep[grepl(analysis, names(shortRobustPrep))]
+  mylist <- lapply(names(mylist), function(x) transform(mylist[[x]], name = x))
+  df <- do.call(rbind, mylist)
+  df <- melt(df, id.vars = c("coef", "name")) %>%
+    mutate(
+      name = as.character(sub(".*_(.*)", "\\1", name)),
+      coef = as.character(sub("CoreNeedC", "CoreNeed", coef)),
+      variable = as.character(variable)
+    )
+  df <- dcast(df, coef ~ name + variable, value.var = "value")
+  robustTblLong[[analysis]] <- df
 }
-
-tmp <- shortRobustPrep[grepl("Out", names(shortRobustPrep))]
-outRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Out$coef)
-for (i in 1:length(tmp)){
-  outRobustTbl <- join(outRobustTbl, tmp[[i]], by = "coef")
-}
-
-robustTblLong <- rbind(
-  fullRobustTbl,
-  outRobustTbl
-)
-
-robustTblLong$coef <- mapvalues(
+robustTblLong <- do.call(rbind, robustTblLong) %>% 
+  rownames_to_column(var = "group") %>%
+  mutate(group = factor(sub("\\.\\d+$", "", group), levels = unique(sub("\\.\\d+$", "", group))),
+         contains_colon = ifelse(grepl(":", coef), 1, 0),
+         special = case_when(
+           coef == "(Intercept)" ~ "first",
+           coef == "CoreNeed" ~ "second",
+           coef == "R2Marg_R2Cond" ~ "last",
+           TRUE ~ "middle"
+         ),
+         special = factor(special, levels = c("first", "second", "middle", "last"))) %>% 
+  arrange(group, special, contains_colon, coef) %>% 
+  select(-contains_colon, -special)
+
+replacement_mapping <- c("contact" = "Contact specific",
+                         "accidental" = "Interaction Intend",
+                         "wellbeing_core" = "Well-being Outcome",
+                         "need_type" = "Need Type",
+                         "need_sdt" = "Specific Psychological Needs")
+
+robustTblLong <- robustTblLong %>%
+  mutate(
+    group = case_when(
+      group %in% names(replacement_mapping) ~ replacement_mapping[group],
+      TRUE ~ as.character(group)
+    ),
+    coef = mapvalues(
       robustTblLong$coef,
-  from = c(
-    "R2Marg_R2Cond"
-  ),
-  to = c(
-    "$R^2_{marginal}$ / $R^2_{conditional}$"
-  )
-)
-
-mdlTblRobustLong <- robustTblLong %>%
+      from = c("R2Marg_R2Cond"),
+      to = c("$R^2_{marginal}$ / $R^2_{conditional}$")
+    )
+  )
+
+mdlTblRobustLong <- 
+  robustTblLong %>%
+  select(-group) %>%
   replace(is.na(.), "") %>%
@@
     align = c("l", rep("c", ncol(.)-1)),
-    escape = FALSE
+    escape = FALSE,
+    col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2))
   ) %>%
   kable_classic() %>%
-  add_header_above(., c(" ", "Study 1" = 2, "Study 2" = 2, "Study 3" = 2)) %>%
-  pack_rows("Contact [Full Sample]", 1, 5) %>%
-  pack_rows("Self-Determination Theory [Outgroup Interactions only]", 6, 11) %>%
+  add_header_above(., c(" ", "Overall" = 2, "Study 1" = 2, "Study 2" = 2, "Study 3" = 2)) %>%
+  pack_rows(index = table(robustTblLong$group)) %>%
   kableExtra::footnote(
@@
   save_kable("Tables/mdlRobustlong.tex")
+
 ```
 
-```{r robustnessTblWide, include=FALSE}
-# Wide format
-mdlRobustTbl <- data.frame(
-  coef = c(
-    sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef) %>% unlist %>% unique,
-    names(mdlRobustPrep[[1]]$random),
-    names(mdlRobustPrep[[1]]$fit)
-  )
-)
-for (i in 1:length(mdlRobustPrep)){
-  mdlRobustTbl <- join(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef")
-  #mdlTbl <- merge(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", ""))
-}
-
-mdlRobustTblHeader <- data.frame(
-  data = as.character(mdlRobustTbl[mdlRobustTbl$coef == "data",]),
-  formula = as.character(mdlRobustTbl[mdlRobustTbl$coef == "formula",])
-) %>%
-  filter(data != "",
-         data != "data") %>%
-  mutate(study = str_extract(data, "Worker|Student|Medical")) %>%
-  mutate(study = gsub("Worker", "Study 1", study)) %>%
-  mutate(study = gsub("Student", "Study 2", study)) %>%
-  mutate(study = gsub("Medical", "Study 3", study)) %>%
-  mutate(dv = sub(" ~.*", "", formula)) %>%
-  mutate(dv = gsub("Raw", " ", dv)) %>%
-  mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>%
-  mutate(header = paste(study, pred, sep = " - "))
-
-mdlRobustTblHeaderFreq <- rbind.data.frame(rle(mdlRobustTblHeader$header)) %>%
-  mutate(lengths = lengths*2) %>%
-  rename(names = values, span = lengths) %>%
-  rbind(c(1, ""), .) %>%
-  mutate(span = as.numeric(span)) %>%
-  select(names, span)
-
-mdlRobustTblHeaderDv <- data.frame(names = mdlRobustTblHeader$dv, span = 2) %>% 
-  mutate(names = as.character(names)) %>%
-  rbind(c("", 1), .) %>%
-  mutate(span = as.numeric(span))
-
-mdlRobustTblHeaderStudy <- rbind.data.frame(rle(mdlRobustTblHeader$study)) %>%
-  mutate(lengths = lengths*2) %>%
-  rename(names = values, span = lengths) %>%
-  rbind(c(1, ""), .) %>%
-  mutate(span = as.numeric(span)) %>%
-  select(names, span)
-
-mdlRobustTbl$coef <- mapvalues(
-  mdlRobustTbl$coef,
-  from = c(
-    "sigmaSq",
-    "tau00",
-    "tau11",
-    "rho01",
-    "rho00",
-    "R2_marginal",
-    "R2_conditional", 
-    "R2Marg_R2Cond"
-  ),
-  to = c(
-    "$\\sigma^2$",
-    "$\\tau_{00}$",
-    "$\\tau_{11}$",
-    "$\\rho_{01}$",
-    "$\\rho_{00}$",
-    "$R^2_{marginal}$",
-    "$R^2_{conditional}$",
-    "$R^2_{marginal}$ / $R^2_{conditional}$"
-  )
-)
-
-# Long Table
-mdlTblRobustLong <- mdlRobustTbl %>%
-  replace(is.na(.), "") %>%
-  kbl(
-    .,
-    caption = "Robustness Analyses",
-    #format = "latex",
-    linesep = "",
-    booktabs = T,
-    align = c("l", rep("c", ncol(.) - 1)),
-    escape = FALSE,
-    digits = 3
-  ) %>%
-  kable_classic() %>%
-  add_header_above(., mdlRobustTblHeaderStudy) %>%
-  add_header_above(
-    .,
-    c(
-      "",
-      "Contact [Full Sample]" = 6,
-      "Self-Determination Theory [Outgroup Interactions only]" = 6
-    )
-  ) %>%
-  pack_rows("Fixed", 1, 7) %>%
-  pack_rows("Random", 8, 12) %>%
-  pack_rows("Fit", 13, 25) %>%
-  footnote(
-    general = c("PID = Participant ID number (grouping variable)",
-                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
-                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
-    ),
-    escape = FALSE
-  ) %>%
-  gsub("_cwc", "", ., fixed = TRUE)
-
-# shortened Table
-mdlTblRobustShort <- mdlRobustTbl %>%
-  replace(is.na(.), "")
-names(mdlTblRobustShort) <- make.unique(names(mdlTblRobustShort))
-mdlTblRobustShort <- mdlTblRobustShort %>%
-  filter(
-    !coef %in% c(
-      "data",
-      "formula",
-      "groupId",
-      "$R^2_{marginal}$",
-      "$R^2_{conditional}$",
-      "logLik",
-      "deviance"
-    )
-  ) %>%
-  mutate_all(linebreak) %>%
-  kbl(
-    .,
-    caption = "Robustness Analyses",
-    format = "latex",
-    linesep = "",
-    booktabs = TRUE,
-    col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)),
-    align = c("l", rep("c", ncol(.) - 1)),
-    escape = FALSE,
-    digits = 3
-  )  %>%
-  kable_classic() %>%
-  add_header_above(., mdlRobustTblHeaderStudy) %>%
-  add_header_above(
-    .,
-    c(
-      "",
-      "Contact [Full Sample]" = 6,
-      "Self-Determination Theory [Outgroup Interactions only]" = 6
-    )
-  ) %>%
-  pack_rows("Fixed", 1, 7) %>%
-  pack_rows("Random", 8, 12) %>%
-  pack_rows("Fit", 13, 18) %>%
-  footnote(
-    general = c("PID = Participant ID number (grouping variable)",
-                "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes",
-                "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"
-    ), 
-    escape = FALSE
-  ) %>%
-  kable_styling(latex_options = "scale_down") %>%
-  kableExtra::landscape() %>%
-  gsub("_cwc", "", ., fixed = TRUE)  %>%
-  gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>%
-  gsub("\\makecell[r]", "\\makecell[c]", ., fixed = TRUE) %>%
-  gsub("objVar$", "", ., fixed = TRUE) %>%
-  gsub("slope_intercept.", "slope.intercept", ., fixed = TRUE) %>%
-  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
-  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
-  save_kable("Tables/mdlRobustness.tex")
-mdlTblRobustShort
-```
+<!-- ```{r} -->
+<!-- #| label: robustnessTblWide -->
+<!-- #| include: false -->
+
+<!-- # Wide format -->
+<!-- mdlRobustTbl <- data.frame( -->
+<!--   coef = c( -->
+<!--     sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef) %>% unlist %>% unique, -->
+<!--     names(mdlRobustPrep[[1]]$random), -->
+<!--     names(mdlRobustPrep[[1]]$fit) -->
+<!--   ) -->
+<!-- ) -->
+<!-- for (i in 1:length(mdlRobustPrep)){ -->
+<!--   mdlRobustTbl <- join(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef") -->
+<!--   #mdlTbl <- merge(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", "")) -->
+<!-- } -->
+
+<!-- mdlRobustTblHeader <- data.frame( -->
+<!--   data = as.character(mdlRobustTbl[mdlRobustTbl$coef == "data",]), -->
+<!--   formula = as.character(mdlRobustTbl[mdlRobustTbl$coef == "formula",]) -->
+<!-- ) %>% -->
+<!--   filter(data != "", -->
+<!--          data != "data") %>% -->
+<!--   mutate(study = str_extract(data, "Worker|Student|Medical")) %>% -->
+<!--   mutate(study = gsub("Worker", "Study 1", study)) %>% -->
+<!--   mutate(study = gsub("Student", "Study 2", study)) %>% -->
+<!--   mutate(study = gsub("Medical", "Study 3", study)) %>% -->
+<!--   mutate(dv = sub(" ~.*", "", formula)) %>% -->
+<!--   mutate(dv = gsub("Raw", " ", dv)) %>% -->
+<!--   mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>% -->
+<!--   mutate(header = paste(study, pred, sep = " - ")) -->
+
+<!-- mdlRobustTblHeaderFreq <- rbind.data.frame(rle(mdlRobustTblHeader$header)) %>% -->
+<!--   mutate(lengths = lengths*2) %>% -->
+<!--   rename(names = values, span = lengths) %>% -->
+<!--   rbind(c(1, ""), .) %>% -->
+<!--   mutate(span = as.numeric(span)) %>% -->
+<!--   select(names, span) -->
+
+<!-- mdlRobustTblHeaderDv <- data.frame(names = mdlRobustTblHeader$dv, span = 2) %>%  -->
+<!--   mutate(names = as.character(names)) %>% -->
+<!--   rbind(c("", 1), .) %>% -->
+<!--   mutate(span = as.numeric(span)) -->
+
+<!-- mdlRobustTblHeaderStudy <- rbind.data.frame(rle(mdlRobustTblHeader$study)) %>% -->
+<!--   mutate(lengths = lengths*2) %>% -->
+<!--   rename(names = values, span = lengths) %>% -->
+<!--   rbind(c(1, ""), .) %>% -->
+<!--   mutate(span = as.numeric(span)) %>% -->
+<!--   select(names, span) -->
+
+<!-- mdlRobustTbl$coef <- mapvalues( -->
+<!--   mdlRobustTbl$coef, -->
+<!--   from = c( -->
+<!--     "sigmaSq", -->
+<!--     "tau00", -->
+<!--     "tau11", -->
+<!--     "rho01", -->
+<!--     "rho00", -->
+<!--     "R2_marginal", -->
+<!--     "R2_conditional",  -->
+<!--     "R2Marg_R2Cond" -->
+<!--   ), -->
+<!--   to = c( -->
+<!--     "$\\sigma^2$", -->
+<!--     "$\\tau_{00}$", -->
+<!--     "$\\tau_{11}$", -->
+<!--     "$\\rho_{01}$", -->
+<!--     "$\\rho_{00}$", -->
+<!--     "$R^2_{marginal}$", -->
+<!--     "$R^2_{conditional}$", -->
+<!--     "$R^2_{marginal}$ / $R^2_{conditional}$" -->
+<!--   ) -->
+<!-- ) -->
+
+<!-- # Long Table -->
+<!-- mdlTblRobustLong <- mdlRobustTbl %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Robustness Analyses", -->
+<!--     #format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = c("l", rep("c", ncol(.) - 1)), -->
+<!--     escape = FALSE, -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_classic() %>% -->
+<!--   add_header_above(., mdlRobustTblHeaderStudy) %>% -->
+<!--   add_header_above( -->
+<!--     ., -->
+<!--     c( -->
+<!--       "", -->
+<!--       "Contact [Full Sample]" = 6, -->
+<!--       "Self-Determination Theory [Outgroup Interactions only]" = 6 -->
+<!--     ) -->
+<!--   ) %>% -->
+<!--   pack_rows("Fixed", 1, 7) %>% -->
+<!--   pack_rows("Random", 8, 12) %>% -->
+<!--   pack_rows("Fit", 13, 25) %>% -->
+<!--   footnote( -->
+<!--     general = c("PID = Participant ID number (grouping variable)", -->
+<!--                 "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes", -->
+<!--                 "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05" -->
+<!--     ), -->
+<!--     escape = FALSE -->
+<!--   ) %>% -->
+<!--   gsub("_cwc", "", ., fixed = TRUE)  -->
+
+<!-- # shortened Table -->
+<!-- mdlTblRobustShort <- mdlRobustTbl %>% -->
+<!--   replace(is.na(.), "") -->
+<!-- names(mdlTblRobustShort) <- make.unique(names(mdlTblRobustShort)) -->
+<!-- mdlTblRobustShort <- mdlTblRobustShort %>% -->
+<!--   filter( -->
+<!--     !coef %in% c( -->
+<!--       "data", -->
+<!--       "formula", -->
+<!--       "groupId", -->
+<!--       "$R^2_{marginal}$", -->
+<!--       "$R^2_{conditional}$", -->
+<!--       "logLik", -->
+<!--       "deviance" -->
+<!--     ) -->
+<!--   ) %>% -->
+<!--   mutate_all(linebreak) %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Robustness Analyses", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = TRUE, -->
+<!--     col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)), -->
+<!--     align = c("l", rep("c", ncol(.) - 1)), -->
+<!--     escape = FALSE, -->
+<!--     digits = 3 -->
+<!--   )  %>% -->
+<!--   kable_classic() %>% -->
+<!--   add_header_above(., mdlRobustTblHeaderStudy) %>% -->
+<!--   add_header_above( -->
+<!--     ., -->
+<!--     c( -->
+<!--       "", -->
+<!--       "Contact [Full Sample]" = 6, -->
+<!--       "Self-Determination Theory [Outgroup Interactions only]" = 6 -->
+<!--     ) -->
+<!--   ) %>% -->
+<!--   pack_rows("Fixed", 1, 7) %>% -->
+<!--   pack_rows("Random", 8, 12) %>% -->
+<!--   pack_rows("Fit", 13, 18) %>% -->
+<!--   footnote( -->
+<!--     general = c("PID = Participant ID number (grouping variable)", -->
+<!--                 "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes", -->
+<!--                 "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05" -->
+<!--     ),  -->
+<!--     escape = FALSE -->
+<!--   ) %>% -->
+<!--   kable_styling(latex_options = "scale_down") %>% -->
+<!--   kableExtra::landscape() %>% -->
+<!--   gsub("_cwc", "", ., fixed = TRUE)  %>% -->
+<!--   gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>% -->
+<!--   gsub("\\makecell[r]", "\\makecell[c]", ., fixed = TRUE) %>% -->
+<!--   gsub("objVar$", "", ., fixed = TRUE) %>% -->
+<!--   gsub("slope_intercept.", "slope.intercept", ., fixed = TRUE) %>% -->
+<!--   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position -->
+<!--   gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position -->
+<!--   save_kable("Tables/mdlRobustness.tex") -->
+<!-- mdlTblRobustShort -->
+<!-- ``` -->
 
@@
 
-```{r metaRobust, include=FALSE}
-mdlRobustTblElements <- list(
-  # full
-  c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ),
-  c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ),
-  c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ),
-  # outgroup
-  c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ),
-  c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ),
-  c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ)
-  )
-
-# i =1
+```{r}
+#| label: metaRobust
+#| include: false
+
+analyses <- unique(sub("_(?!.*_).*", "", names(mdlRobustTblElements), perl = TRUE))
+studies <- unique(sub(".*_(.*)", "\\1", names(mdlRobustTblElements)))
+
+# i = 1
 robustMetaTbl <- data.frame()
 for (i in 1:length(mdlRobustTblElements)){
-  lmerTblTmp <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$beta %>%
-  select(
-    coef,
+  Prep <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])
+  lmerTblTmp <- Prep$beta %>%
+  transmute(
+    group = names(mdlRobustTblElements)[[i]],
+    analysis = sub("_(?!.*_).*", "", names(mdlRobustTblElements)[[i]], perl = TRUE),
+    coef = gsub(":", ".", coef),
     B = est,
@@
     tval,
-    Rsq
-  ) %>%
-  mutate(
-    n = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$N,
+    Rsq,
+    n = Prep$fit$N,
     m = nrow(.), 
     #dv = gsub("Dutch", "", str_extract(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,".+?(?= ~)")),
-    sample = str_match(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$data, "Tbl(.*?)(Full|Out)")[2],
-    formula = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,
-    coef = gsub(":", ".", coef)
+    sample = sub(".*_(.*)", "\\1", names(mdlRobustTblElements)[[i]]),
+    formula = gsub("\\s+", " ", Prep$fit$formula)
   )
@@
 }
-
-robustMetaTbl <- robustMetaTbl %>%
-  arrange(formula, match(
-    coef,
-    c(
-      "CoreNeed_zwc",
-      "OutgroupInteraction_zwc",
-      "CoreNeed_zwc.OutgroupInteraction_zwc",
-      "Autonomy_zwc",
-      "Competence_zwc",
-      "Relatedness_zwc"
-    )
-  )) %>% 
+robustMetaTblSorted <- robustMetaTbl %>% 
+  mutate(group = factor(group, levels = unique(group)),
+         contains_period = ifelse(grepl("\\.", coef), 1, 0),
+         special = case_when(
+           coef == "(Intercept)" ~ "first",
+           coef == "CoreNeed" ~ "second",
+           coef == "R2Marg_R2Cond" ~ "last",
+           TRUE ~ "middle"
+         ),
+         special = factor(special, levels = c("first", "second", "middle", "last"))) %>% 
+  arrange(group, special, contains_period, coef) %>% 
+  select(-contains_period, -special) %>%
+  filter(sample != "overall") %>% 
   mutate(formula = gsub(" \\+ \\(.*", "", formula))
 
-robustMetaContact <-
-  metaLmerOut(
-    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc * OutgroupInteraction"),
+replacement_mapping <- c("contact" = "Contact Specific",
+                         "accidental" = "Interaction Intend",
+                         "wellbeing_core" = "Well-being Outcome",
+                         "need_type" = "Need Type",
+                         "need_sdt" = "Specific Psychological Needs")
+
+robustMeta <- list()
+for (name in unique(robustMetaTblSorted$analysis)) {
+  lab <- case_when(
+    name %in% names(replacement_mapping) ~ replacement_mapping[name],
+    TRUE ~ as.character(name)
+  )
+  robustMeta[[name]] <- metaLmerOut(
+    lmerDataTbl = robustMetaTblSorted %>% filter(analysis == name),
     type = "REML", #"FE", 
-    name = "RobustContact",
-    title = "Robustness — Contact and Need Fulfillment"
-  )
-
-robustMetaSDT <-
-  metaLmerOut(
-    lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc + Competence_cwc + Autonomy_cwc +      Relatedness_cwc"),
-    type = "REML", #"FE", 
-    name = "RobustSDT",
-    title = "Robustness — Other Needs"
-  )
+    name = name,
+    title = paste0("Robustness — ", lab), 
+  )
+}
 ```
 
-```{r robustForestPltComb, include=FALSE}
-effRobust <- rbind(
-  robustMetaContact$eff %>%
+```{r}
+#| label: robustForestPltComb
+#| include: false
+
+process_element <- function(element) {
+  # Apply dplyr filtering and mutating
+  df_eff_adjusted <- element$eff %>%
     filter(coef != "(Intercept)") %>%
-    mutate(analysis = "(A) Attitude ~ Contact and Need Fulfillment",
-           metaId = paste(coef, analysis, sep = ".")) %>%
-    as.data.frame,
-  robustMetaSDT$eff %>%
-    mutate(analysis = "(B) Attitude ~ Other Needs",
-           metaId = paste(coef, analysis, sep = ".")) %>%
+    mutate(metaId = paste(coef, analysis, sep = ".")) %>%
     as.data.frame
-)
-
-metaSubForest(effRobust, 
+
+  return(df_eff_adjusted)
+}
+adjusted_dataframes <- lapply(robustMeta, process_element)
+
+lookup_table <- data.frame(analysis = unique(names(adjusted_dataframes)), group_letter = LETTERS[seq_along(unique(names(adjusted_dataframes)))])
+
+effRobust <- do.call(rbind, adjusted_dataframes) %>%
+  left_join(lookup_table, by = "analysis") %>%
+  mutate(
+    analysis = paste0("(",group_letter, ") ",
+      case_when(
+        analysis %in% names(replacement_mapping) ~ replacement_mapping[analysis],
+        TRUE ~ as.character(analysis)
+      )
+    ),
+    contains_period = ifelse(grepl("\\.", coef), 1, 0),
+    special = case_when(coef == "CoreNeedZ" ~ "first", 
+                        TRUE ~ "last"),
+    special = factor(special, levels = c("first", "last"))
+  ) %>%
+  arrange(analysis, special, contains_period, coef, sample) %>%
+  select(-group_letter, -special, -contains_period)
+
+metaSubForest(effects = effRobust, 
               title = "Meta Analysis: Forest Plot Robustness Analysis \n[Parametric]",
@@
               width = 600,
-              height = 800)
+              height = 1200)
 ```
+
+<!-- -------------------------------------------------------------------- -->
+
+<!--                               OLD CODE                               -->
+
+<!-- -------------------------------------------------------------------- -->
+
+<!-- \subsubsection{Study 1} -->
+
+<!-- ```{r workerSampleInfo, include=FALSE} -->
+<!-- # combine education measure -->
+<!-- workerOccupation <-  -->
+<!--   dtWorker$clean %>% -->
+<!--   select(PID, starts_with("occupation")) %>% -->
+<!--   mutate_all(as_factor) %>%  -->
+<!--   mutate_all(as.character) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   unite("occupation", -PID, sep = "/") %>% -->
+<!--   mutate(occupation = trimws(occupation, which = "both", whitespace = "[/]")) %>% -->
+<!--   distinct -->
+
+<!-- # summarize participant characteristics -->
+<!-- workerSampleInfo <-  -->
+<!--   dtWorker$clean %>% -->
+<!--   group_by(PID) %>% -->
+<!--   summarise( -->
+<!--     dailiesN = n(),  -->
+<!--     morningN = sum(daytime=="morning"), -->
+<!--     afternoonN = sum(daytime=="afternoon"), -->
+<!--     age = age, -->
+<!--     gender = as_factor(Gender), -->
+<!--     edu = as_factor(education_level), -->
+<!--     nationality = as_factor(nationality) -->
+<!--   ) %>% -->
+<!--   distinct -->
+
+<!-- # add occupation variable -->
+<!-- workerSampleInfo <- merge(workerSampleInfo, workerOccupation) -->
+<!-- rm(workerOccupation) -->
+
+<!-- # divide into trait and state -->
+<!-- dtWorkerSupp$workerWithinBetween <- -->
+<!--   MlTraitState( -->
+<!--     data = dtWorkerSupp$workerInteractionType, -->
+<!--     id = "PID", -->
+<!--     selection = -->
+<!--       c( -->
+<!--         "keyMotiveFulfilled", -->
+<!--         "competence.daily.all", -->
+<!--         "autonomy.daily.all", -->
+<!--         "relatedness.daily.all", -->
+<!--         "thermometerDutch_1", -->
+<!--         "keymotive_fulfillemt_1", -->
+<!--         "competence_1", -->
+<!--         "autonomy_1", -->
+<!--         "relatedness_1",  -->
+<!--         "quality_overall_1",  -->
+<!--         "OutgroupInteraction", -->
+<!--         "NonOutgroupInteraction",  -->
+<!--         "OutgroupInteractionM", -->
+<!--         "NonOutgroupInteractionM" -->
+<!--       ) -->
+<!--   ) -->
+
+<!-- dtWorkerSupp$workerOutWithinBetween <- -->
+<!--   MlTraitState( -->
+<!--     data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"), -->
+<!--     id = "PID", -->
+<!--     selection = -->
+<!--       c( -->
+<!--         "keyMotiveFulfilled", -->
+<!--         "thermometerDutch_1", -->
+<!--         "keymotive_fulfillemt_1", -->
+<!--         "competence_1", -->
+<!--         "autonomy_1", -->
+<!--         "relatedness_1",  -->
+<!--         "quality_overall_1" -->
+<!--       ) -->
+<!--   ) -->
+<!-- ``` -->
+
+<!-- ```{r workerModelOlsAttFreqQual, include=FALSE} -->
+<!-- # create list to store Worker models -->
+<!-- mdlWorker <- list() -->
+<!-- ``` -->
+
+<!-- ```{r workerModelMLAttNull, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlWorker$lmerAttNull <- -->
+<!--   lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID), -->
+<!--     data = dtWorker$full -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- mdlWorker$lmeAttNull <- -->
+<!--   lme( -->
+<!--     thermometerDutch_1 ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtWorker$full, -->
+<!--     na.action=na.omit, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(lmerWorkerAttNull) #or with the lme function -->
+<!-- summ(mdlWorker$lmerAttNull, digits = 3, center = TRUE) -->
+
+<!-- # Save variances -->
+<!-- mdlWorker$varAttNull <-  -->
+<!--   VarCorr(mdlWorker$lmeAttNull) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlWorker$tauAttNull <-  -->
+<!--   as.numeric(mdlWorker$varAttNull[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlWorker$sigmaAttNull <-  -->
+<!--   as.numeric(mdlWorker$varAttNull[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlWorker$IccAttNull <- -->
+<!--   (as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2]))) -->
+<!-- mdlWorker$IccPercAttNull <- -->
+<!--   ((as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2])))) * 100 -->
+<!-- ``` -->
+
+<!-- ```{r workerOutModelMLAttNull, include=FALSE} -->
+<!-- # create empty list to organize models -->
+<!-- mdlWorkerOut <-  -->
+<!--   list( -->
+<!--     Att = list(), -->
+<!--     Qlt = list() -->
+<!--   ) -->
+
+<!-- # Create and save Model -->
+<!-- mdlWorkerOut$Att$lmerNull <- -->
+<!--   lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID),  -->
+<!--              data = dtWorkerSupp$workerOutgroupInteraction) # use optim if it does not converge -->
+<!-- mdlWorkerOut$Att$lmeNull <- -->
+<!--   lme( -->
+<!--     thermometerDutch_1 ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtWorkerSupp$workerOutgroupInteraction, -->
+<!--     na.action=na.omit, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(Null.Out.ML.r) #or with the lme function -->
+<!-- summ(mdlWorkerOut$Att$lmerNull, digits = 3, center = TRUE) -->
+
+<!-- # Save variances -->
+<!-- mdlWorkerOut$Att$varNull <-  -->
+<!--   VarCorr(mdlWorkerOut$Att$lmeNull) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlWorkerOut$Att$tauNull <-  -->
+<!--   as.numeric(mdlWorkerOut$Att$varNull[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlWorkerOut$Att$sigmaNull <-  -->
+<!--   as.numeric(mdlWorkerOut$Att$varNull[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlWorkerOut$Att$IccNull <- -->
+<!--   (as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2]))) -->
+<!-- mdlWorkerOut$Att$IccPercNull <- -->
+<!--   ((as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2])))) * 100 -->
+<!-- ``` -->
+
+<!-- ```{r workerOutModelMLQltNull, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlWorkerOut$Qlt$lmerNull <- -->
+<!--   lme4::lmer(quality_overall_1 ~ 1 + (1 | PID),  -->
+<!--              data = dtWorkerSupp$workerOutWithinBetween) # use optim if it does not converge -->
+
+<!-- mdlWorkerOut$Qlt$lmeNull <- -->
+<!--   mdlWorkerOut$Qlt$lmeNull <- lme( -->
+<!--     quality_overall_1 ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtWorkerSupp$workerOutWithinBetween, -->
+<!--     na.action=na.omit, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(Null.Out.Qual.ML.r) #or with the lme function -->
+<!-- summ(mdlWorkerOut$Qlt$lmerNull, digits = 3) -->
+
+<!-- # Save variances -->
+<!-- mdlWorkerOut$Qlt$varNull <-  -->
+<!--   VarCorr(mdlWorkerOut$Qlt$lmeNull) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlWorkerOut$Qlt$tauNull <-  -->
+<!--   as.numeric(mdlWorkerOut$Qlt$varNull[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlWorkerOut$Qlt$sigmaNull <-  -->
+<!--   as.numeric(mdlWorkerOut$Qlt$varNull[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlWorkerOut$Qlt$IccNull <- -->
+<!--   (as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2]))) -->
+<!-- mdlWorkerOut$Qlt$IccPercNull <- -->
+<!--   ((as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2])))) * 100 -->
+<!-- ``` -->
+
+<!-- ```{r workerModelInterceptAttCoreInt, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlWorker$lmeInterceptAttCoreInt <- -->
+<!--   lme( -->
+<!--     thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction, -->
+<!--     random =  ~ 1 | PID, -->
+<!--     na.action=na.omit, -->
+<!--     data = dtWorkerSupp$workerWithinBetween -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- summ( -->
+<!--   mdlWorker$lmerInterceptAttCoreInt <- lmer( -->
+<!--     thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction + (1 | PID), -->
+<!--     data = dtWorkerSupp$workerWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # 95%CI -->
+<!-- mdlWorker$lmerInterceptAttCoreIntCI <-  -->
+<!--   confint(method = "Wald", mdlWorker$lmerInterceptAttCoreInt) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlWorker$lmeAttNull,  -->
+<!--       mdlWorker$lmeInterceptAttCoreInt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   add_rownames(., var = "Description") %>% -->
+<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Worker: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = c("l", rep("c", ncol(.)-1)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # Save variances -->
+<!-- mdlWorker$varInterceptAttCoreInt <-  -->
+<!--   lme4::VarCorr(mdlWorker$lmeInterceptAttCoreInt) -->
+<!-- ``` -->
+<!-- ```{r workerModelSlopesAttCoreIntX, include=FALSE} -->
+<!-- # Create and save Model (optimizer needed to reach convergence) -->
+<!-- mdlWorker$lmeSlopesAttCoreInt <- lme( -->
+<!--   thermometerDutch_1 ~ -->
+<!--     keyMotiveFulfilled_cwc * OutgroupInteraction, -->
+<!--   random = ~ 1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID, -->
+<!--   control = lmeControl(opt = "optim"), -->
+<!--   na.action=na.omit, -->
+<!--   data = dtWorkerSupp$workerWithinBetween -->
+<!-- ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
+<!-- summ( -->
+<!--   mdlWorker$lmerSlopesAttCoreInt <- lmer( -->
+<!--     thermometerDutch_1 ~ -->
+<!--       keyMotiveFulfilled_cwc * OutgroupInteraction + -->
+<!--       (1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID), -->
+<!--     data = dtWorkerSupp$workerWithinBetween -->
+<!--   ),  -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # 95%CI -->
+<!-- mdlWorker$lmerSlopesAttCoreIntCI <-  -->
+<!--   confint(method = "Wald", mdlWorker$lmerSlopesAttCoreInt) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlWorker$lmeAttNull,  -->
+<!--       mdlWorker$lmeInterceptAttCoreInt, -->
+<!--       mdlWorker$lmeSlopesAttCoreInt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   add_rownames(., var = "Description") %>% -->
+<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Worker: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # Save variances -->
+<!-- mdlWorker$varSlopesAttCoreInt <-  -->
+<!--   lme4::VarCorr(mdlWorker$lmeSlopesAttCoreInt) -->
+
+<!-- # Assumption Checks: -->
+<!-- mdlWorker$diagSlopesAttCoreInt <- -->
+<!--   sjPlot::plot_model(mdlWorker$lmerSlopesAttCoreInt, type = "diag") -->
+<!-- grid.arrange( -->
+<!--   mdlWorker$diagSlopesAttCoreInt[[1]], -->
+<!--   mdlWorker$diagSlopesAttCoreInt[[2]]$`PID`, -->
+<!--   mdlWorker$diagSlopesAttCoreInt[[3]], -->
+<!--   mdlWorker$diagSlopesAttCoreInt[[4]] -->
+<!-- ) -->
+
+<!-- # Plot prediction model -->
+<!-- mdlWorker$predSlopesAttCoreInt <-  -->
+<!--   dtWorkerSupp$workerWithinBetween %>% -->
+<!--   select(thermometerDutch_1, session, PID) %>%  -->
+<!--   mutate(measure = predict(mdlWorker$lmeSlopesAttCoreInt, -->
+<!--                            dtWorkerSupp$workerWithinBetween, -->
+<!--                            re.form = NA -->
+<!--                            ) -->
+<!--          ) -->
+
+<!-- ( -->
+<!--   mdlWorker$predPltSlopesAttCoreInt <- -->
+<!--     ggplot(data = mdlWorker$predSlopesAttCoreInt, aes(x = session, y = measure)) + -->
+<!--     geom_line(alpha = 1, color = "blue") + -->
+<!--     geom_line(aes(y = thermometerDutch_1), alpha = 1) + -->
+<!--     facet_wrap(~ PID, ncol = 6) + -->
+<!--     xlab("Time") + -->
+<!--     ylab("Outgroup Attitudes") + -->
+<!--     theme_Publication() -->
+<!-- ) -->
+<!-- ggsave( -->
+<!--   filename = "Figures/Worker_PredictionPlot_SlopesAttCoreInt.png", -->
+<!--   mdlWorker$predPltSlopesAttCoreInt, -->
+<!--   width = 18, -->
+<!--   height = 12, -->
+<!--   dpi = 800, -->
+<!--   units = "cm", -->
+<!--   device = "png" -->
+<!-- ) -->
+<!-- ``` -->
+
+<!-- ```{r workerOutModelInterceptAttCoreSdt, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlWorkerOut$Att$lmeInterceptCoreSdt <- -->
+<!--   lme( -->
+<!--     thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtWorkerSupp$workerOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- summ( -->
+<!--   mdlWorkerOut$Att$lmerInterceptCoreSdt <- lmer( -->
+<!--     thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID), -->
+<!--     data = dtWorkerSupp$workerOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # To be compared against a model with only the self-determination theory needs -->
+<!-- mdlWorkerOut$Att$lmeInterceptSdt <- -->
+<!--   lme( -->
+<!--     thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtWorkerSupp$workerOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- summ( -->
+<!--   mdlWorkerOut$Att$lmerInterceptSdt <- lmer( -->
+<!--     thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID), -->
+<!--     data = dtWorkerSupp$workerOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # Compare new model to previous steps -->
+<!-- anova( -->
+<!--   mdlWorkerOut$Att$lmeInterceptSdt, -->
+<!--   mdlWorkerOut$Att$lmeInterceptCoreSdt -->
+<!--   ) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Worker: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+<!-- rm(lmeInterceptCoreRed) -->
+
+<!-- # Save variances -->
+<!-- mdlWorkerOut$Att$varInterceptCoreSdt <- -->
+<!--   lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreSdt) -->
+<!-- ``` -->
+<!-- ```{r workerOutModelSlopesAttCoreSdt, include=FALSE} -->
+<!-- # Create and save Model (optimizer needed to reach convergence) -->
+<!-- mdlWorkerOut$Att$lmeSlopesCoreSdt <- -->
+<!--   lme( -->
+<!--     thermometerDutch_1 ~ -->
+<!--       keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc, -->
+<!--     random = ~ 1 + keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID, -->
+<!--     control = lmeControl(opt = "optim"), -->
+<!--     data = dtWorkerSupp$workerOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
+<!-- summ( -->
+<!--   mdlWorkerOut$Att$lmerSlopesCoreSdt <- lmer( -->
+<!--     thermometerDutch_1 ~ -->
+<!--       keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + -->
+<!--       (1 + keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID), -->
+<!--     data = dtWorkerSupp$workerOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- mdlWorkerOut$Att$lmerSlopesCoreSdtCI <-  -->
+<!--   confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreSdt) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlWorkerOut$Att$lmeInterceptSdt, -->
+<!--       mdlWorkerOut$Att$lmeInterceptCoreSdt,  -->
+<!--       mdlWorkerOut$Att$lmeSlopesCoreSdt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Worker: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # model with SDT only -->
+<!-- # Create and save Model (optimizer needed to reach convergence) -->
+<!-- mdlWorkerOut$Att$lmeSlopesSdt <- -->
+<!--   lme( -->
+<!--     thermometerDutch_1 ~ -->
+<!--       competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc, -->
+<!--     random = ~ 1 + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID, -->
+<!--     control = lmeControl(opt = "optim"), -->
+<!--     data = dtWorkerSupp$workerOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
+<!-- summ( -->
+<!--   mdlWorkerOut$Att$lmerSlopesSdt <- lmer( -->
+<!--     thermometerDutch_1 ~ -->
+<!--       competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + -->
+<!--       (1 + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID), -->
+<!--     data = dtWorkerSupp$workerOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlWorkerOut$Att$lmeInterceptSdt, -->
+<!--       mdlWorkerOut$Att$lmeSlopesSdt,  -->
+<!--       mdlWorkerOut$Att$lmeSlopesCoreSdt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Worker: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # Save variances -->
+<!-- mdlWorkerOut$Att$varSlopesCoreSdt <-  -->
+<!--   lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreSdt) -->
+
+<!-- # Assumption Checks: -->
+<!-- mdlWorkerOut$Att$diagSlopesCoreSdt <-  -->
+<!--   sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreSdt, type = "diag") -->
+<!-- grid.arrange( -->
+<!--   mdlWorkerOut$Att$diagSlopesCoreSdt[[1]], -->
+<!--   mdlWorkerOut$Att$diagSlopesCoreSdt[[2]]$`PID`, -->
+<!--   mdlWorkerOut$Att$diagSlopesCoreSdt[[3]], -->
+<!--   mdlWorkerOut$Att$diagSlopesCoreSdt[[4]] -->
+<!-- ) -->
+
+<!-- # Plot prediction model -->
+<!-- mdlWorkerOut$Att$predSlopesCoreSdt <-  -->
+<!--   dtWorkerSupp$workerOutWithinBetween %>% -->
+<!--   filter(!is.na(autonomy_1)) %>% -->
+<!--   select(thermometerDutch_1, session, PID, autonomy_1) %>%  -->
+<!--   mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreSdt, -->
+<!--                            dtWorkerSupp$workerOutWithinBetween %>% filter(!is.na(autonomy_1)), -->
+<!--                            re.form = NA -->
+<!--                            ) -->
+<!--          ) -->
+
+<!-- ( -->
+<!--   mdlWorkerOut$Att$predPltSlopesCoreSdt <- -->
+<!--     ggplot(data = mdlWorkerOut$Att$predSlopesCoreSdt, aes(x = session, y = measure)) + -->
+<!--     geom_line(alpha = 1, color = "blue") + -->
+<!--     geom_line(aes(y = thermometerDutch_1), alpha = 1) + -->
+<!--     facet_wrap( ~ PID, ncol = 6) + -->
+<!--     xlab("Time") + -->
+<!--     ylab("Outgroup Attitudes") + -->
+<!--     theme_Publication() -->
+<!-- ) -->
+<!-- ggsave( -->
+<!--   filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreStd.png", -->
+<!--   mdlWorkerOut$Att$predPltSlopesCoreSdt, -->
+<!--   width = 18, -->
+<!--   height = 12, -->
+<!--   dpi = 800, -->
+<!--   units = "cm", -->
+<!--   device = "png" -->
+<!-- ) -->
+
+<!-- # Model comparison -->
+<!-- workerSdtComp <- -->
+<!--   anova( -->
+<!--     mdlWorkerOut$Att$lmerSlopesSdt,  -->
+<!--     mdlWorkerOut$Att$lmerSlopesCoreSdt -->
+<!--   ) %>% -->
+<!--   as.data.frame() -->
+<!-- workerSdtCompDf <- workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Df"] -->
+<!-- workerSdtCompN <- sapply(ranef(mdlWorkerOut$Att$lmerSlopesCoreSdt), nrow) -->
+<!-- workerSdtCompChi <- workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2) -->
+<!-- workerSdtCompP <- -->
+<!--   ifelse(workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001, -->
+<!--          "< .001", -->
+<!--          paste0("= ", workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3))) -->
+
+<!-- workerSdtCompChiSq <- paste0("$\\chi^2$(", workerSdtCompDf, ", \\textit{N} = ", workerSdtCompN, ") = ", workerSdtCompChi, ", \\textit{p} ", workerSdtCompP) -->
+<!-- ``` -->
+
+<!-- In a final step, we controlled for other fundamental psychological needs during the contact.
+We focus on the three commonly considered self-determination needs (SDT): competence, autonomy, and relatedness.
+We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r workerSdtCompChiSq`).
+We also find that next to relatedness (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "relatedness_1_cwc")`), the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "keymotive_fulfillemt_1_cwc")`).
+When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all three fundamental needs (competence and autonomy needs turning non-significant; all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
+For full results see see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and Online Supplementary Material A.
+There is, thus, considerable evidence lending confidence to the stability and relevance of psychological need fulfillment as a predictor of positive outgroup attitudes for natural intergroup contacts.
+-->
+
+<!-- \hl{Intend ...} -->
+
+<!-- \hl{Goal-directedness ...} -->
+
+<!-- \hl{Well-being ...} -->
+
+<!-- \subsubsection{Study 2} -->
+
+<!-- ```{r studentSampleInfo, include=FALSE} -->
+<!-- # summarize participant characteristics -->
+<!-- studentSampleInfo <-  -->
+<!--   dtStudents$full %>% -->
+<!--   mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>% -->
+<!--   group_by(PID) %>% -->
+<!--   summarise( -->
+<!--     dailiesN = n(),  -->
+<!--     morningN = sum(periodMA=="morning"), -->
+<!--     afternoonN = sum(periodMA=="afternoon"), -->
+<!--     age = age, -->
+<!--     gender = gender, -->
+<!--     nationality = nationality -->
+<!--   ) %>% -->
+<!--   distinct -->
+
+<!-- # look at frequencies of characteristics  -->
+<!-- table(studentSampleInfo$gender) -->
+<!-- table(as.character(studentSampleInfo$nationality)) -->
+
+<!-- # divide into trait and state -->
+<!-- dtStudentSupp$studentWithinBetween <- -->
+<!--   MlTraitState( -->
+<!--     data = dtStudentSupp$studentInteractionType, -->
+<!--     id = "PID", -->
+<!--     selection = -->
+<!--       c( -->
+<!--         "KeyNeedFullfillment", -->
+<!--         "Competence", -->
+<!--         "Autonomy", -->
+<!--         "Relatedness", -->
+<!--         "AttitudesDutch", -->
+<!--         "quality_overall", -->
+<!--         "OutgroupInteraction", -->
+<!--         "NonOutgroupInteraction", -->
+<!--         "OutgroupInteractionM", -->
+<!--         "NonOutgroupInteractionM" -->
+<!--       ) -->
+<!--   ) -->
+<!-- dtStudentSupp$studentOutWithinBetween <- -->
+<!--   MlTraitState( -->
+<!--     data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"), -->
+<!--     id = "PID", -->
+<!--     selection = -->
+<!--       c( -->
+<!--         "KeyNeedFullfillment", -->
+<!--         "Competence", -->
+<!--         "Autonomy", -->
+<!--         "Relatedness", -->
+<!--         "AttitudesDutch", -->
+<!--         "quality_overall" -->
+<!--       ) -->
+<!--   ) -->
+<!-- ``` -->
+
+<!-- ```{r studentModelOlsAttFreqQual, include=FALSE} -->
+<!-- # create list to store Worker models -->
+<!-- mdlStudent <- list() -->
+<!-- ``` -->
+
+<!-- ```{r studentModelMLAttNull, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlStudent$lmerAttNull <- -->
+<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
+<!--     data = dtStudents$full -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- mdlStudent$lmeAttNull <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtStudents$full, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(mdlStudent$lmerAttNull) #or with the lme function -->
+<!-- summ(mdlStudent$lmerAttNull, digits = 3) -->
+
+<!-- # Save variances -->
+<!-- mdlStudent$varAttNull <-  -->
+<!--   VarCorr(mdlStudent$lmeAttNull) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlStudent$tauAttNull <-  -->
+<!--   as.numeric(mdlStudent$varAttNull[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlStudent$sigmaAttNull <-  -->
+<!--   as.numeric(mdlStudent$varAttNull[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlStudent$IccAttNull <- -->
+<!--   (as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2]))) -->
+<!-- mdlStudent$IccPercAttNull <- -->
+<!--   ((as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))) * 100 -->
+<!-- ``` -->
+
+<!-- ```{r studentOutModelMLAttNull, include=FALSE} -->
+<!-- # create empty list to organize models -->
+<!-- mdlStudentOut <-  -->
+<!--   list( -->
+<!--     Att = list(), -->
+<!--     Qlt = list() -->
+<!--   ) -->
+
+<!-- # Create and save Model -->
+<!-- mdlStudentOut$Att$lmerNull <- -->
+<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),  -->
+<!--              data = dtStudentSupp$studentOutgroupInteraction) # use optim if it does not converge -->
+<!-- mdlStudentOut$Att$lmeNull <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtStudentSupp$studentOutgroupInteraction, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(Null.Out.ML.r) #or with the lme function -->
+<!-- summ(mdlStudentOut$Att$lmerNull, digits = 3, center = TRUE) -->
+
+<!-- # Save variances -->
+<!-- mdlStudentOut$Att$varNull <-  -->
+<!--   VarCorr(mdlStudentOut$Att$lmeNull) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlStudentOut$Att$tauNull <-  -->
+<!--   as.numeric(mdlStudentOut$Att$varNull[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlStudentOut$Att$sigmaNull <-  -->
+<!--   as.numeric(mdlStudentOut$Att$varNull[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlStudentOut$Att$IccNull <- -->
+<!--   (as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2]))) -->
+<!-- mdlStudentOut$Att$IccPercNull <- -->
+<!--   ((as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))) * 100 -->
+<!-- ``` -->
+
+<!-- ```{r studentOutModelMLQltNull, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlStudentOut$Qlt$lmerNull <- -->
+<!--   lme4::lmer(quality_overall ~ 1 + (1 | PID),  -->
+<!--              data = dtStudentSupp$studentOutWithinBetween) # use optim if it does not converge -->
+<!-- mdlStudentOut$Qlt$lmeNull <- -->
+<!--   mdlStudentOut$Qlt$lmeNull <-lme( -->
+<!--     quality_overall ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtStudentSupp$studentOutWithinBetween, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(Null.Out.Qual.ML.r) #or with the lme function -->
+<!-- summ(mdlStudentOut$Qlt$lmerNull, digits = 3) -->
+
+<!-- # Save variances -->
+<!-- mdlStudentOut$Qlt$varNull <-  -->
+<!--   VarCorr(mdlStudentOut$Qlt$lmeNull) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlStudentOut$Qlt$tauNull <-  -->
+<!--   as.numeric(mdlStudentOut$Qlt$varNull[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlStudentOut$Qlt$sigmaNull <-  -->
+<!--   as.numeric(mdlStudentOut$Qlt$varNull[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlStudentOut$Qlt$IccNull <- -->
+<!--   (as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2]))) -->
+<!-- mdlStudentOut$Qlt$IccPercNull <- -->
+<!--   ((as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))) * 100 -->
+<!-- ``` -->
+
+<!-- ```{r studentModelInterceptAttCoreInt, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlStudent$lmeInterceptAttCoreInt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction, -->
+<!--     random =  ~ 1 | PID, -->
+<!--     data = dtStudentSupp$studentWithinBetween -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- summ( -->
+<!--   mdlStudent$lmerInterceptAttCoreInt <- lmer( -->
+<!--     AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction + (1 | PID), -->
+<!--     data = dtStudentSupp$studentWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # 95%CI -->
+<!-- mdlStudent$lmerInterceptAttCoreIntCI <-  -->
+<!--   confint(method = "Wald", mdlStudent$lmerInterceptAttCoreInt) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlStudent$lmeAttNull,  -->
+<!--       mdlStudent$lmeInterceptAttCoreInt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   add_rownames(., var = "Description") %>% -->
+<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Student: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = c("l", rep("c", ncol(.)-1)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # Save variances -->
+<!-- mdlStudent$varInterceptAttCoreInt <-  -->
+<!--   lme4::VarCorr(mdlStudent$lmeInterceptAttCoreInt) -->
+<!-- ``` -->
+<!-- ```{r studentModelSlopesAttCoreIntX, include=FALSE} -->
+<!-- # Create and save Model (optimizer needed to reach convergence) -->
+<!-- mdlStudent$lmeSlopesAttCoreInt <- lme( -->
+<!--   AttitudesDutch ~ -->
+<!--     KeyNeedFullfillment_cwc * OutgroupInteraction, -->
+<!--   random = ~ 1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID, -->
+<!--   control = lmeControl(opt = "optim"), -->
+<!--   data = dtStudentSupp$studentWithinBetween -->
+<!-- ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
+<!-- summ( -->
+<!--   mdlStudent$lmerSlopesAttCoreInt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       KeyNeedFullfillment_cwc * OutgroupInteraction + -->
+<!--       (1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID), -->
+<!--     data = dtStudentSupp$studentWithinBetween -->
+<!--   ),  -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # 95%CI -->
+<!-- mdlStudent$lmerSlopesAttCoreIntCI <-  -->
+<!--   confint(method = "Wald", mdlStudent$lmerSlopesAttCoreInt) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlStudent$lmeAttNull,  -->
+<!--       mdlStudent$lmeInterceptAttCoreInt, -->
+<!--       mdlStudent$lmeSlopesAttCoreInt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   add_rownames(., var = "Description") %>% -->
+<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Student: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # Save variances -->
+<!-- mdlStudent$varSlopesAttCoreInt <-  -->
+<!--   lme4::VarCorr(mdlStudent$lmeSlopesAttCoreInt) -->
+
+<!-- # Assumption Checks: -->
+<!-- mdlStudent$diagSlopesAttCoreInt <- -->
+<!--   sjPlot::plot_model(mdlStudent$lmerSlopesAttCoreInt, type = "diag") -->
+<!-- grid.arrange( -->
+<!--   mdlStudent$diagSlopesAttCoreInt[[1]], -->
+<!--   mdlStudent$diagSlopesAttCoreInt[[2]]$`PID`, -->
+<!--   mdlStudent$diagSlopesAttCoreInt[[3]], -->
+<!--   mdlStudent$diagSlopesAttCoreInt[[4]] -->
+<!-- ) -->
+
+<!-- # Plot prediction model -->
+<!-- mdlStudent$predSlopesAttCoreInt <-  -->
+<!--   dtStudentSupp$studentWithinBetween %>% -->
+<!--   filter(PID %in% dtStudentSupp$studentPltIDs) %>% -->
+<!--   select(AttitudesDutch, TIDnum, PID) %>%  -->
+<!--   mutate(measure = predict(mdlStudent$lmeSlopesAttCoreInt, -->
+<!--                            dtStudentSupp$studentWithinBetween %>% filter(PID %in% dtStudentSupp$studentPltIDs), -->
+<!--                            re.form = NA -->
+<!--                            ) -->
+<!--          ) -->
+
+<!-- ( -->
+<!--   mdlStudent$predPltSlopesAttCoreInt <- -->
+<!--     ggplot(data = mdlStudent$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) + -->
+<!--     geom_line(alpha = 1, color = "blue") + -->
+<!--     geom_line(aes(y = AttitudesDutch), alpha = 1) + -->
+<!--     facet_wrap(~ PID, ncol = 6) + -->
+<!--     xlab("Time") + -->
+<!--     ylab("Outgroup Attitudes") + -->
+<!--     theme_Publication() -->
+<!-- ) -->
+<!-- ggsave( -->
+<!--   filename = "Figures/Student_PredictionPlot_SlopesAttCoreInt.png", -->
+<!--   mdlStudent$predPltSlopesAttCoreInt, -->
+<!--   width = 18, -->
+<!--   height = 12, -->
+<!--   dpi = 800, -->
+<!--   units = "cm", -->
+<!--   device = "png" -->
+<!-- ) -->
+<!-- ``` -->
+
+<!-- Also for Study 2, we checked for alternative models.
+First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is only a minuscule main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc:OutgroupInteraction")`).
+Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteraction")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+This finding is consistent with the results of the previous study, albeit with a slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see \tblref{tab:robustnessTblLong} and for visual comparison see \fgrref{fig:Robustness}).
+-->
+
+<!-- ```{r studentOutModelInterceptAttCoreSdt, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlStudentOut$Att$lmeInterceptCoreSdt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtStudentSupp$studentOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- summ( -->
+<!--   mdlStudentOut$Att$lmerInterceptCoreSdt <- lmer( -->
+<!--     AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID), -->
+<!--     data = dtStudentSupp$studentOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # 95%CI -->
+<!-- mdlStudentOut$Att$lmerInterceptCoreSdtCI <-  -->
+<!--   confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCoreSdt) -->
+
+<!-- # To be compared against a model with only the self-determination theory needs -->
+<!-- mdlStudentOut$Att$lmeInterceptSdt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtStudentSupp$studentOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- summ( -->
+<!--   mdlStudentOut$Att$lmerInterceptSdt <- lmer( -->
+<!--     AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID), -->
+<!--     data = dtStudentSupp$studentOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # Compare new model to previous steps -->
+<!-- anova( -->
+<!--   mdlStudentOut$Att$lmeNull, -->
+<!--   mdlStudentOut$Att$lmeInterceptSdt, -->
+<!--   mdlStudentOut$Att$lmeInterceptCoreSdt -->
+<!--   ) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Student: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+<!-- rm(lmeInterceptCoreRed) -->
+
+<!-- # Save variances -->
+<!-- mdlStudentOut$Att$varInterceptCoreSdt <- -->
+<!--   lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreSdt) -->
+<!-- ``` -->
+<!-- ```{r studentOutModelSlopesAttCoreSdt, include=FALSE} -->
+<!-- # Create and save Model (optimizer needed to reach convergence) -->
+<!-- mdlStudentOut$Att$lmeSlopesCoreSdt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ -->
+<!--       KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
+<!--     random = ~ 1 + KeyNeedFullfillment_cwc + Competence_cwc + Relatedness_cwc | PID, -->
+<!--     control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100), -->
+<!--     data = dtStudentSupp$studentOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
+<!-- summ( -->
+<!--   mdlStudentOut$Att$lmerSlopesCoreSdt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
+<!--       (1 + KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
+<!--     data = dtStudentSupp$studentOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # 95%CI -->
+<!-- mdlStudentOut$Att$lmerSlopesCoreSdtCI <-  -->
+<!--   confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreSdt) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlStudentOut$Att$lmeInterceptSdt, -->
+<!--       mdlStudentOut$Att$lmeInterceptCoreSdt,  -->
+<!--       mdlStudentOut$Att$lmeSlopesCoreSdt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Student: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # model with SDT only -->
+<!-- # Create and save Model (optimizer needed to reach convergence) -->
+<!-- mdlStudentOut$Att$lmeSlopesSdt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ -->
+<!--       Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
+<!--     random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID, -->
+<!--     control = lmeControl(opt = "optim"), -->
+<!--     data = dtStudentSupp$studentOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
+<!-- summ( -->
+<!--   mdlStudentOut$Att$lmerSlopesSdt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
+<!--       (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
+<!--     data = dtStudentSupp$studentOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlStudentOut$Att$lmeInterceptSdt, -->
+<!--       mdlStudentOut$Att$lmeSlopesSdt,  -->
+<!--       mdlStudentOut$Att$lmeSlopesCoreSdt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Student: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # Save variances -->
+<!-- mdlStudentOut$Att$varSlopesCoreSdt <-  -->
+<!--   lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreSdt) -->
+
+<!-- # Assumption Checks: -->
+<!-- mdlStudentOut$Att$diagSlopesCoreSdt <-  -->
+<!--   sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreSdt, type = "diag") -->
+<!-- grid.arrange( -->
+<!--   mdlStudentOut$Att$diagSlopesCoreSdt[[1]], -->
+<!--   mdlStudentOut$Att$diagSlopesCoreSdt[[2]]$`PID`, -->
+<!--   mdlStudentOut$Att$diagSlopesCoreSdt[[3]], -->
+<!--   mdlStudentOut$Att$diagSlopesCoreSdt[[4]] -->
+<!-- ) -->
+
+<!-- # Plot prediction model -->
+<!-- mdlStudentOut$Att$predSlopesCoreSdt <-  -->
+<!--   dtStudentSupp$studentOutWithinBetween %>% -->
+<!--   filter(PID %in% dtStudentSupp$studentOutPltIDs) %>% -->
+<!--   select(AttitudesDutch, TIDnum, PID, Autonomy) %>%  -->
+<!--   mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreSdt, -->
+<!--                            dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs), -->
+<!--                            re.form = NA -->
+<!--                            ) -->
+<!--          ) -->
+
+<!-- ( -->
+<!--   mdlStudentOut$Att$predPltSlopesCoreSdt <- -->
+<!--     ggplot(data = mdlStudentOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) + -->
+<!--     geom_line(alpha = 1, color = "blue") + -->
+<!--     geom_line(aes(y = AttitudesDutch), alpha = 1) + -->
+<!--     facet_wrap( ~ PID, ncol = 6) + -->
+<!--     xlab("Time") + -->
+<!--     ylab("Outgroup Attitudes") + -->
+<!--     theme_Publication() -->
+<!-- ) -->
+<!-- ggsave( -->
+<!--   filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreStd.png", -->
+<!--   mdlStudentOut$Att$predPltSlopesCoreSdt, -->
+<!--   width = 18, -->
+<!--   height = 12, -->
+<!--   dpi = 800, -->
+<!--   units = "cm", -->
+<!--   device = "png" -->
+<!-- ) -->
+
+<!-- # Model comparison -->
+<!-- studentSdtComp <- -->
+<!--   anova( -->
+<!--     mdlStudentOut$Att$lmerSlopesSdt,  -->
+<!--     mdlStudentOut$Att$lmerSlopesCoreSdt -->
+<!--   ) %>% -->
+<!--   as.data.frame() -->
+<!-- studentSdtCompDf <- studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Df"] -->
+<!-- studentSdtCompN <- sapply(ranef(mdlStudentOut$Att$lmerSlopesCoreSdt), nrow) -->
+<!-- studentSdtCompChi <- studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2) -->
+<!-- studentSdtCompP <- -->
+<!--   ifelse(studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001, -->
+<!--          "< .001", -->
+<!--          paste0("= ", studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3))) -->
+
+<!-- studentSdtCompChiSq <- paste0("$\\chi^2$(", studentSdtCompDf, ", \\textit{N} = ", studentSdtCompN, ") = ", studentSdtCompChi, ", \\textit{p} ", studentSdtCompP) -->
+<!-- ``` -->
+
+<!-- In a final step, we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
+We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r studentSdtCompChiSq`).
+We find that the core need fulfillment explained the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFullfillment_cwc")`).
+When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
+However, different from the first study, relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes in this larger sample.
+For full results see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and Online Supplementary Material A.
+This means that also within this second sample, the fulfillment of psychological needs during intergroup contact remained a key predictor of positive outgroup attitudes, even when taking into account several alternative models.
+-->
+
+<!-- \hl{Intend ...} -->
+
+<!-- \hl{Goal-directedness ...} -->
+
+<!-- \hl{Well-being ...} -->
+
+<!-- \subsubsection{Study 3} -->
+
+<!-- ```{r medicalSampleInfo, include=FALSE} -->
+<!-- # extract demographic information from eligibility questionnaire -->
+<!-- medicalDemographicSupp <-  -->
+<!--   dtMedical$raw.eligibility %>% -->
+<!--   filter(session %in% dtMedical$full$session) %>% -->
+<!--   select(session, nationality, studentBachMa) -->
+<!-- # summarize participant characteristics -->
+
+<!-- medicalSampleInfo <- -->
+<!--   merge(dtMedical$full, medicalDemographicSupp, by = "session") %>% -->
+<!--   mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>% -->
+<!--   group_by(PID) %>% -->
+<!--   summarise( -->
+<!--     dailiesN = n(),  -->
+<!--     morningN = sum(periodMA=="morning"), -->
+<!--     afternoonN = sum(periodMA=="afternoon"), -->
+<!--     age = age, -->
+<!--     gender = gender, -->
+<!--     nationality = nationality -->
+<!--   ) %>% -->
+<!--   distinct -->
+
+<!-- # divide into trait and state -->
+<!-- dtMedicalSupp$medicalWithinBetween <-  -->
+<!--   MlTraitState( -->
+<!--     data = dtMedical$full, -->
+<!--     id = "PID", -->
+<!--     selection = -->
+<!--       c( -->
+<!--         "OutgroupInteraction", -->
+<!--         "NonOutgroupInteraction", -->
+<!--         "OutgroupInteractionM", -->
+<!--         "NonOutgroupInteractionM" -->
+<!--       ) -->
+<!--   ) -->
+
+<!-- ``` -->
+
+<!-- ```{r medicalModelOlsAttFreqQual, include=FALSE} -->
+<!-- # create list to store Worker models -->
+<!-- mdlMedical <- list() -->
+<!-- ``` -->
+
+<!-- ```{r medicalModelMLAttNull, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlMedical$lmerAttNullType <- -->
+<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
+<!--              data = dtMedical$full %>% -->
+<!--                filter(complete.cases( -->
+<!--                  OutgroupInteraction, NonOutgroupInteraction -->
+<!--                ))) # use optim if it does not converge -->
+
+<!-- mdlMedical$lmeAttNullType <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtMedical$full %>% -->
+<!--       filter(complete.cases( -->
+<!--         OutgroupInteraction, NonOutgroupInteraction -->
+<!--       )), -->
+<!--     na.action = na.omit, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(mdlMedical$lmerAttNull) #or with the lme function -->
+<!-- summ(mdlMedical$lmerAttNullType, digits = 3) -->
+
+<!-- # Save variances -->
+<!-- mdlMedical$varAttNullType <-  -->
+<!--   VarCorr(mdlMedical$lmeAttNullType) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlMedical$tauAttNullType <-  -->
+<!--   as.numeric(mdlMedical$varAttNullType[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlMedical$sigmaAttNullType <-  -->
+<!--   as.numeric(mdlMedical$varAttNullType[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlMedical$IccAttNullType <- -->
+<!--   (as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2]))) -->
+<!-- mdlMedical$IccPercAttNull <- -->
+<!--   ((as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))) * 100 -->
+<!-- ``` -->
+
+<!-- ```{r medicalOutModelMLAttNull, include=FALSE} -->
+<!-- # create empty list to organize models -->
+<!-- mdlMedicalOut <-  -->
+<!--   list( -->
+<!--     Att = list(), -->
+<!--     Qlt = list() -->
+<!--   ) -->
+
+<!-- # Create and save Model -->
+<!-- mdlMedicalOut$Att$lmerNull <- -->
+<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
+<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
+<!-- mdlMedicalOut$Att$lmeNull <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
+<!--     na.action = na.omit, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(Null.Out.ML.r) #or with the lme function -->
+<!-- summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE) -->
+
+<!-- # Save variances -->
+<!-- mdlMedicalOut$Att$varNull <-  -->
+<!--   VarCorr(mdlMedicalOut$Att$lmeNull) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlMedicalOut$Att$tauNull <-  -->
+<!--   as.numeric(mdlMedicalOut$Att$varNull[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlMedicalOut$Att$sigmaNull <-  -->
+<!--   as.numeric(mdlMedicalOut$Att$varNull[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlMedicalOut$Att$IccNull <- -->
+<!--   (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2]))) -->
+<!-- mdlMedicalOut$Att$IccPercNull <- -->
+<!--   ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100 -->
+<!-- ``` -->
+
+<!-- ```{r medicalOutModelMLQltNull, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlMedicalOut$Qlt$lmerNull <- -->
+<!--   lme4::lmer(qualityOverall ~ 1 + (1 | PID),  -->
+<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
+<!-- mdlMedicalOut$Qlt$lmeNull <- -->
+<!--   mdlMedicalOut$Qlt$lmeNull <-lme( -->
+<!--     qualityOverall ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     na.action = na.omit, -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(Null.Out.Qual.ML.r) #or with the lme function -->
+<!-- summ(mdlMedicalOut$Qlt$lmerNull, digits = 3) -->
+
+<!-- # Save variances -->
+<!-- mdlMedicalOut$Qlt$varNull <-  -->
+<!--   VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances -->
+<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
+<!-- mdlMedicalOut$Qlt$tauNull <-  -->
+<!--   as.numeric(mdlMedicalOut$Qlt$varNull[1]) -->
+<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
+<!-- mdlMedicalOut$Qlt$sigmaNull <-  -->
+<!--   as.numeric(mdlMedicalOut$Qlt$varNull[2]) -->
+<!-- # The ICC estimate (between/between+within) is: -->
+<!-- mdlMedicalOut$Qlt$IccNull <- -->
+<!--   (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2]))) -->
+<!-- mdlMedicalOut$Qlt$IccPercNull <- -->
+<!--   ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100 -->
+<!-- ``` -->
+
+<!-- ```{r medicalModelAttNullInt, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlMedical$lmerAttNullInt <- -->
+<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
+<!--              data = dtMedical$full %>% -->
+<!--                filter(complete.cases( -->
+<!--                  OutgroupInteraction -->
+<!--                ))) # use optim if it does not converge -->
+
+<!-- mdlMedical$lmeAttNullInt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ 1, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtMedical$full %>% -->
+<!--       filter(complete.cases( -->
+<!--         OutgroupInteraction -->
+<!--       )), -->
+<!--     na.action = na.omit, -->
+<!--     control = list(opt = "nlmimb") -->
+<!--   ) # use optim if it does not converge -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- # summary(mdlMedical$lmerAttNull) #or with the lme function -->
+<!-- summ(mdlMedical$lmerAttNullInt, digits = 3) -->
+<!-- ``` -->
+
+<!-- ```{r medicalModelInterceptAttCoreInt, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlMedical$lmeInterceptAttCoreInt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction, -->
+<!--     random =  ~ 1 | PID, -->
+<!--     na.action = na.omit, -->
+<!--     data = dtMedical$full -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- summ( -->
+<!--   mdlMedical$lmerInterceptAttCoreInt <- lmer( -->
+<!--     AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction + (1 | PID), -->
+<!--     data = dtMedical$full -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- mdlMedical$lmerInterceptAttCoreIntCI <-  -->
+<!--   confint(method = "Wald", mdlMedical$lmerInterceptAttCoreInt) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlMedical$lmeAttNullInt,  -->
+<!--       mdlMedical$lmeInterceptAttCoreInt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   add_rownames(., var = "Description") %>% -->
+<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Medical: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = c("l", rep("c", ncol(.)-1)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # Save variances -->
+<!-- mdlMedical$varInterceptAttCoreInt <-  -->
+<!--   lme4::VarCorr(mdlMedical$lmeInterceptAttCoreInt) -->
+<!-- ``` -->
+
+<!-- ```{r medicalModelSlopesAttCoreIntX, include=FALSE} -->
+<!-- # Create and save Model (optimizer needed to reach convergence) -->
+<!-- mdlMedical$lmeSlopesAttCoreInt <- lme( -->
+<!--   AttitudesDutch ~ -->
+<!--     KeyNeedFulfillment_cwc * OutgroupInteraction, -->
+<!--   random = ~ 1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID, -->
+<!--   control = lmeControl(opt = "optim"), -->
+<!--   na.action = na.omit, -->
+<!--   data = dtMedical$full -->
+<!-- ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
+<!-- summ( -->
+<!--   mdlMedical$lmerSlopesAttCoreInt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       KeyNeedFulfillment_cwc * OutgroupInteraction + -->
+<!--       (1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID), -->
+<!--     data = dtMedical$full -->
+<!--   ),  -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- mdlMedical$lmerSlopesAttCoreIntCI <-  -->
+<!--   confint(method = "Wald", mdlMedical$lmerSlopesAttCoreInt) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlMedical$lmeAttNullInt,  -->
+<!--       mdlMedical$lmeInterceptAttCoreInt, -->
+<!--       mdlMedical$lmeSlopesAttCoreInt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   add_rownames(., var = "Description") %>% -->
+<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Medical: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # Save variances -->
+<!-- mdlMedical$varSlopesAttCoreInt <-  -->
+<!--   lme4::VarCorr(mdlMedical$lmeSlopesAttCoreInt) -->
+
+<!-- # Assumption Checks: -->
+<!-- mdlMedical$diagSlopesAttCoreInt <- -->
+<!--   sjPlot::plot_model(mdlMedical$lmerSlopesAttCoreInt, type = "diag") -->
+<!-- grid.arrange( -->
+<!--   mdlMedical$diagSlopesAttCoreInt[[1]], -->
+<!--   mdlMedical$diagSlopesAttCoreInt[[2]]$`PID`, -->
+<!--   mdlMedical$diagSlopesAttCoreInt[[3]], -->
+<!--   mdlMedical$diagSlopesAttCoreInt[[4]] -->
+<!-- ) -->
+
+<!-- # Plot prediction model -->
+<!-- mdlMedical$predSlopesAttCoreInt <-  -->
+<!--   dtMedical$full %>% -->
+<!--   filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>% -->
+<!--   filter(PID %in% dtMedicalSupp$medicalPltIDs) %>% -->
+<!--   select(AttitudesDutch, TIDnum, PID) %>%  -->
+<!--   mutate(measure = predict(mdlMedical$lmeSlopesAttCoreInt, -->
+<!--                            dtMedical$full %>%  -->
+<!--                              filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>% -->
+<!--                              filter(PID %in% dtMedicalSupp$medicalPltIDs), -->
+<!--                            re.form = NA -->
+<!--                            ) -->
+<!--          ) -->
+
+<!-- ( -->
+<!--   mdlMedical$predPltSlopesAttCoreInt <- -->
+<!--     ggplot(data = mdlMedical$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) + -->
+<!--     geom_line(alpha = 1, color = "blue") + -->
+<!--     geom_line(aes(y = AttitudesDutch), alpha = 1) + -->
+<!--     facet_wrap(~ PID, ncol = 6) + -->
+<!--     xlab("Time") + -->
+<!--     ylab("Outgroup Attitudes") + -->
+<!--     theme_Publication() -->
+<!-- ) -->
+<!-- ggsave( -->
+<!--   filename = "Figures/Medical_PredictionPlot_SlopesAttCoreInt.png", -->
+<!--   mdlMedical$predPltSlopesAttCoreInt, -->
+<!--   width = 18, -->
+<!--   height = 12, -->
+<!--   dpi = 800, -->
+<!--   units = "cm", -->
+<!--   device = "png" -->
+<!-- ) -->
+<!-- ``` -->
+
+<!-- As with the previous two studies, we checked for alternative models of the key need fulfillment.
+First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
+Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "OutgroupInteractionYes")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
+This finding is consistent with the results of the previous studies.
+-->
+
+<!-- ```{r medicalOutModelInterceptAttCoreSdt, include=FALSE} -->
+<!-- # Create and save Model -->
+<!-- mdlMedicalOut$Att$lmeInterceptCoreSdt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) -->
+<!-- summ( -->
+<!--   mdlMedicalOut$Att$lmerInterceptCoreSdt <- lmer( -->
+<!--     AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID), -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # To be compared against a model with only the self-determination theory needs -->
+<!-- mdlMedicalOut$Att$lmeInterceptSdt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
+<!--     random = ~ 1 | PID, -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- summ( -->
+<!--   mdlMedicalOut$Att$lmerInterceptSdt <- lmer( -->
+<!--     AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID), -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # Compare new model to previous steps -->
+<!-- anova( -->
+<!--   mdlMedicalOut$Att$lmeInterceptSdt, -->
+<!--   mdlMedicalOut$Att$lmeInterceptCoreSdt -->
+<!--   ) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Medical: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # Save variances -->
+<!-- mdlMedicalOut$Att$varInterceptCoreSdt <- -->
+<!--   lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreSdt) -->
+<!-- ``` -->
+
+<!-- ```{r medicalOutModelSlopesAttCoreSdt, include=FALSE} -->
+<!-- # Create and save Model (optimizer needed to reach convergence) -->
+<!-- mdlMedicalOut$Att$lmeSlopesCoreSdt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ -->
+<!--       KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
+<!--     random = ~ 1 + KeyNeedFulfillment_cwc + Competence_cwc + Relatedness_cwc | PID, -->
+<!--     control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100), -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
+<!-- summ( -->
+<!--   mdlMedicalOut$Att$lmerSlopesCoreSdt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
+<!--       (1 + KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- mdlMedicalOut$Att$lmerSlopesCoreSdtCI <-  -->
+<!--   confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreSdt) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlMedicalOut$Att$lmeInterceptSdt, -->
+<!--       mdlMedicalOut$Att$lmeInterceptCoreSdt,  -->
+<!--       mdlMedicalOut$Att$lmeSlopesCoreSdt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Medical: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # model with SDT only -->
+<!-- # Create and save Model (optimizer needed to reach convergence) -->
+<!-- mdlMedicalOut$Att$lmeSlopesSdt <- -->
+<!--   lme( -->
+<!--     AttitudesDutch ~ -->
+<!--       Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
+<!--     random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID, -->
+<!--     control = lmeControl(opt = "optim"), -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
+<!--     na.action = na.exclude -->
+<!--   ) -->
+
+<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
+<!-- summ( -->
+<!--   mdlMedicalOut$Att$lmerSlopesSdt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
+<!--       (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
+<!--     data = dtMedicalSupp$medicalOutWithinBetween -->
+<!--   ), -->
+<!--   confint = TRUE, -->
+<!--   digits = 3 -->
+<!-- ) -->
+
+<!-- # Compare new model to previous step -->
+<!-- anova(mdlMedicalOut$Att$lmeInterceptSdt, -->
+<!--       mdlMedicalOut$Att$lmeSlopesSdt,  -->
+<!--       mdlMedicalOut$Att$lmeSlopesCoreSdt) %>% -->
+<!--   as.data.frame() %>% -->
+<!--   select(-call) %>% -->
+<!--   mutate( -->
+<!--     L.Ratio = round(L.Ratio, 3), -->
+<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
+<!--   ) %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Medical: Model Comparison", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = rep("c", ncol(.)), -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_styling(position = "left") -->
+
+<!-- # Save variances -->
+<!-- mdlMedicalOut$Att$varSlopesCoreSdt <-  -->
+<!--   lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreSdt) -->
+
+<!-- # Assumption Checks: -->
+<!-- mdlMedicalOut$Att$diagSlopesCoreSdt <-  -->
+<!--   sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreSdt, type = "diag") -->
+<!-- grid.arrange( -->
+<!--   mdlMedicalOut$Att$diagSlopesCoreSdt[[1]], -->
+<!--   mdlMedicalOut$Att$diagSlopesCoreSdt[[2]]$`PID`, -->
+<!--   mdlMedicalOut$Att$diagSlopesCoreSdt[[3]], -->
+<!--   mdlMedicalOut$Att$diagSlopesCoreSdt[[4]] -->
+<!-- ) -->
+
+<!-- # Plot prediction model -->
+<!-- mdlMedicalOut$Att$predSlopesCoreSdt <-  -->
+<!--   dtMedicalSupp$medicalOutWithinBetween %>% -->
+<!--   filter(complete.cases( -->
+<!--     KeyNeedFulfillment, -->
+<!--     Autonomy, Competence, Relatedness -->
+<!--     )) %>% -->
+<!--   filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>% -->
+<!--   select(AttitudesDutch, TIDnum, PID, Autonomy, Competence, Relatedness) %>%  -->
+<!--   mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreSdt, -->
+<!--                            dtMedicalSupp$medicalOutWithinBetween %>%  -->
+<!--                              filter(complete.cases( -->
+<!--                                KeyNeedFulfillment, -->
+<!--                                Autonomy, Competence, Relatedness -->
+<!--                              )) %>% -->
+<!--                              filter(PID %in% dtMedicalSupp$medicalOutPltIDs), -->
+<!--                            re.form = NA -->
+<!--                            ) -->
+<!--          ) -->
+
+<!-- ( -->
+<!--   mdlMedicalOut$Att$predPltSlopesCoreSdt <- -->
+<!--     ggplot(data = mdlMedicalOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) + -->
+<!--     geom_line(alpha = 1, color = "blue") + -->
+<!--     geom_line(aes(y = AttitudesDutch), alpha = 1) + -->
+<!--     facet_wrap( ~ PID, ncol = 6) + -->
+<!--     xlab("Time") + -->
+<!--     ylab("Outgroup Attitudes") + -->
+<!--     theme_Publication() -->
+<!-- ) -->
+<!-- ggsave( -->
+<!--   filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreStd.png", -->
+<!--   mdlMedicalOut$Att$predPltSlopesCoreSdt, -->
+<!--   width = 18, -->
+<!--   height = 12, -->
+<!--   dpi = 800, -->
+<!--   units = "cm", -->
+<!--   device = "png" -->
+<!-- ) -->
+
+<!-- # Model comparison -->
+<!-- medicalSdtComp <- -->
+<!--   anova( -->
+<!--     mdlMedicalOut$Att$lmerSlopesSdt,  -->
+<!--     mdlMedicalOut$Att$lmerSlopesCoreSdt -->
+<!--   ) %>% -->
+<!--   as.data.frame() -->
+<!-- medicalSdtCompDf <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Df"] -->
+<!-- medicalSdtCompN <- sapply(ranef(mdlMedicalOut$Att$lmerSlopesCoreSdt), nrow) -->
+<!-- medicalSdtCompChi <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2) -->
+<!-- medicalSdtCompP <- -->
+<!--   ifelse(medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001, -->
+<!--          "< .001", -->
+<!--          paste0("= ", medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3))) -->
+
+<!-- medicalSdtCompChiSq <- paste0("$\\chi^2$(", medicalSdtCompDf, ", \\textit{N} = ", medicalSdtCompN, ") = ", medicalSdtCompChi, ", \\textit{p} ", medicalSdtCompP) -->
+<!-- ``` -->
+
+<!-- In a final step, we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
+We find that the core need fulfillment adds additional variance above a model with only the self-determination theory needs (random slopes models; `r medicalSdtCompChiSq`).
+We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFulfillment_cwc")`).
+When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
+However, similar to the previous study, in this large sample relatedness (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each also predicted positive outgroup attitudes independently.
+This being said, the regression coefficient for the core need was three times larger (with all scaling being equal).
+For full results see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness} as well as Online Supplementary Material A.
+-->
+
+<!-- \hl{Intend ...} -->
+
+<!-- \hl{Goal-directedness ...} -->
+
+<!-- \hl{Well-being ...} -->
+
+<!-- ```{r robustnessTblLong, include=FALSE} -->
+<!-- # Table of all robustness checks (w/ and w/out SDT only) -->
+
+<!-- # Full Sample -->
+<!-- # Study 1: -->
+<!-- robustTblWorkerFull <-  -->
+<!--   dtWorkerSupp$workerWithinBetween %>% -->
+<!--   select( -->
+<!--     AttitudesDutch = thermometerDutch_1, -->
+<!--     AttitudesDutch_zwc = thermometerDutch_1_zwc, -->
+<!--     CoreNeed_cwc = keyMotiveFulfilled_cwc, -->
+<!--     CoreNeed_zwc = keyMotiveFulfilled_zwc, -->
+<!--     OutgroupInteraction = OutgroupInteraction, -->
+<!--     OutgroupInteraction_zwc = OutgroupInteraction_zwc, -->
+<!--     PID = PID -->
+<!--   ) -->
+<!-- mdlWorkerLmerSlopesAttCoreInt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       CoreNeed_cwc * OutgroupInteraction + -->
+<!--       (1 + CoreNeed_cwc + OutgroupInteraction | PID), -->
+<!--     data = robustTblWorkerFull -->
+<!--   ) -->
+<!-- mdlWorkerLmerSlopesAttCoreIntZ <- lmer( -->
+<!--     AttitudesDutch_zwc ~ -->
+<!--       CoreNeed_zwc * OutgroupInteraction_zwc + -->
+<!--       (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID), -->
+<!--     data = robustTblWorkerFull -->
+<!--   ) -->
+<!-- #Study 2: -->
+<!-- robustTblStudentFull <-  -->
+<!--   dtStudentSupp$studentWithinBetween %>% -->
+<!--   select( -->
+<!--     AttitudesDutch = AttitudesDutch, -->
+<!--     AttitudesDutch_zwc = AttitudesDutch_zwc, -->
+<!--     CoreNeed_cwc = KeyNeedFullfillment_cwc, -->
+<!--     CoreNeed_zwc = KeyNeedFullfillment_zwc, -->
+<!--     OutgroupInteraction = OutgroupInteraction, -->
+<!--     OutgroupInteraction_zwc = OutgroupInteraction_zwc,  -->
+<!--     PID = PID -->
+<!--   ) -->
+<!-- mdlStudentLmerSlopesAttCoreInt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       CoreNeed_cwc * OutgroupInteraction + -->
+<!--       (1 + CoreNeed_cwc + OutgroupInteraction | PID), -->
+<!--     data = robustTblStudentFull -->
+<!--   ) -->
+<!-- mdlStudentLmerSlopesAttCoreIntZ <- lmer( -->
+<!--     AttitudesDutch_zwc ~ -->
+<!--       CoreNeed_zwc * OutgroupInteraction_zwc + -->
+<!--       (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID), -->
+<!--     data = robustTblStudentFull -->
+<!--   ) -->
+<!-- #Study 3: -->
+<!-- robustTblMedicalFull <-  -->
+<!--   dtMedicalSupp$medicalWithinBetween %>% -->
+<!--   select( -->
+<!--     AttitudesDutch = AttitudesDutch, -->
+<!--     AttitudesDutch_zwc = AttitudesDutch_zwc, -->
+<!--     CoreNeed_cwc = KeyNeedFulfillment_cwc, -->
+<!--     CoreNeed_zwc = KeyNeedFulfillment_zwc, -->
+<!--     OutgroupInteraction = OutgroupInteraction, -->
+<!--     OutgroupInteraction_zwc = OutgroupInteraction_zwc,  -->
+<!--     PID = PID -->
+<!--   ) -->
+<!-- mdlMedicalLmerSlopesAttCoreInt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       CoreNeed_cwc * OutgroupInteraction + -->
+<!--       (1 + CoreNeed_cwc + OutgroupInteraction | PID), -->
+<!--     #data = dtMedical$full -->
+<!--     data = robustTblMedicalFull -->
+<!--   ) -->
+<!-- mdlMedicalLmerSlopesAttCoreIntZ <- lmer( -->
+<!--     AttitudesDutch_zwc ~ -->
+<!--       CoreNeed_zwc * OutgroupInteraction_zwc + -->
+<!--       (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID), -->
+<!--     #data = dtMedical$full -->
+<!--     data = robustTblMedicalFull -->
+<!--   ) -->
+
+<!-- # SDT -->
+<!-- # Study 1: -->
+<!-- robustTblWorkerOut <-  -->
+<!--   dtWorkerSupp$workerOutWithinBetween %>% -->
+<!--   select( -->
+<!--     AttitudesDutch = thermometerDutch_1, -->
+<!--     AttitudesDutch_zwc = thermometerDutch_1_zwc, -->
+<!--     CoreNeed_cwc = keymotive_fulfillemt_1_cwc, -->
+<!--     CoreNeed_zwc = keymotive_fulfillemt_1_zwc, -->
+<!--     Competence_cwc = competence_1_cwc, -->
+<!--     Competence_zwc = competence_1_zwc, -->
+<!--     Autonomy_cwc = autonomy_1_cwc, -->
+<!--     Autonomy_zwc = autonomy_1_zwc, -->
+<!--     Relatedness_cwc = relatedness_1_cwc, -->
+<!--     Relatedness_zwc = relatedness_1_zwc, -->
+<!--     PID = PID -->
+<!--   ) -->
+<!-- mdlWorkerOutLmerSlopesCoreSdt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
+<!--       (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
+<!--     data = robustTblWorkerOut -->
+<!--   ) -->
+<!-- mdlWorkerOutLmerSlopesCoreSdtZ <- lmer( -->
+<!--     AttitudesDutch_zwc ~ -->
+<!--       CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc + -->
+<!--       (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID), -->
+<!--     data = robustTblWorkerOut -->
+<!--   ) -->
+<!-- # Study 2: -->
+<!-- robustTblStudentOut <-  -->
+<!--   dtStudentSupp$studentOutWithinBetween %>% -->
+<!--   select( -->
+<!--     AttitudesDutch = AttitudesDutch, -->
+<!--     AttitudesDutch_zwc = AttitudesDutch_zwc, -->
+<!--     CoreNeed_cwc = KeyNeedFullfillment_cwc, -->
+<!--     CoreNeed_zwc = KeyNeedFullfillment_zwc, -->
+<!--     Competence_cwc = Competence_cwc, -->
+<!--     Competence_zwc = Competence_zwc, -->
+<!--     Autonomy_cwc = Autonomy_cwc, -->
+<!--     Autonomy_zwc = Autonomy_zwc, -->
+<!--     Relatedness_cwc = Relatedness_cwc, -->
+<!--     Relatedness_zwc = Relatedness_zwc, -->
+<!--     PID = PID -->
+<!--   ) -->
+<!-- mdlStudentOutLmerSlopesCoreSdt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
+<!--       (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
+<!--     data = robustTblStudentOut -->
+<!--   ) -->
+<!-- mdlStudentOutLmerSlopesCoreSdtZ <- lmer( -->
+<!--     AttitudesDutch_zwc ~ -->
+<!--       CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc + -->
+<!--       (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID), -->
+<!--     data = robustTblStudentOut -->
+<!--   ) -->
+<!-- # Study 3: -->
+<!-- robustTblMedicalOut <-  -->
+<!--   dtMedicalSupp$medicalOutWithinBetween %>% -->
+<!--   select( -->
+<!--     AttitudesDutch = AttitudesDutch, -->
+<!--     AttitudesDutch_zwc = AttitudesDutch_zwc, -->
+<!--     CoreNeed_cwc = KeyNeedFulfillment_cwc, -->
+<!--     CoreNeed_zwc = KeyNeedFulfillment_zwc, -->
+<!--     Competence_cwc = Competence_cwc, -->
+<!--     Competence_zwc = Competence_zwc, -->
+<!--     Autonomy_cwc = Autonomy_cwc, -->
+<!--     Autonomy_zwc = Autonomy_zwc, -->
+<!--     Relatedness_cwc = Relatedness_cwc, -->
+<!--     Relatedness_zwc = Relatedness_zwc, -->
+<!--     PID = PID -->
+<!--   ) -->
+<!-- mdlMedicalOutLmerSlopesCoreSdt <- lmer( -->
+<!--     AttitudesDutch ~ -->
+<!--       CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
+<!--       (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
+<!--     data = robustTblMedicalOut -->
+<!--   ) -->
+<!-- mdlMedicalOutLmerSlopesCoreSdtZ <- lmer( -->
+<!--     AttitudesDutch_zwc ~ -->
+<!--       CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc + -->
+<!--       (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID), -->
+<!--     data = robustTblMedicalOut -->
+<!--   ) -->
+
+<!-- # collect models for table -->
+<!-- mdlRobustTblElements <- list( -->
+<!--   # full -->
+<!--   c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ), -->
+<!--   c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ), -->
+<!--   c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ), -->
+<!--   # outgroup -->
+<!--   c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ), -->
+<!--   c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ), -->
+<!--   c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ) -->
+<!--   ) -->
+
+<!-- mdlRobustPrep <- list() -->
+<!-- for (i in 1:length(mdlRobustTblElements)) { -->
+<!--   mdlRobustPrep[[i]] <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]]) -->
+<!-- } -->
+
+<!-- # manual assembly -->
+<!-- shortRobustPrep <- list() -->
+<!-- for(i in 1:length(mdlRobustPrep)){ -->
+<!--   study <- str_extract(mdlRobustPrep[[i]]$fit$data, "Worker|Student|Medical") -->
+<!--   sample <- str_extract(mdlRobustPrep[[i]]$fit$data, "Full|Out") -->
+<!--   #dv <- sub(" ~.*", "", mdlRobustPrep[[i]]$fit$formula) -->
+<!--   #pred <- gsub("\\(Intercept\\)", "", paste(mdlRobustPrep[[i]]$coeficients$coef, collapse = '')) -->
+
+<!--   name <- paste(study, sample, sep='.') -->
+<!--   tmp <- rbind( -->
+<!--     mdlRobustPrep[[i]]$coeficients[, c("coef", "B", "Beta")], -->
+<!--     data.frame( -->
+<!--       coef = "R2Marg_R2Cond", -->
+<!--       B = mdlRobustPrep[[i]]$fit$R2Marg_R2Cond, -->
+<!--       Beta = "" -->
+<!--     ) -->
+<!--   ) -->
+<!--   shortRobustPrep[[name]] <- tmp -->
+<!-- } -->
+
+<!-- tmp <- shortRobustPrep[grepl("Full", names(shortRobustPrep))] -->
+<!-- fullRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Full$coef) -->
+<!-- for (i in 1:length(tmp)){ -->
+<!--   fullRobustTbl <- join(fullRobustTbl, tmp[[i]], by = "coef") -->
+<!-- } -->
+
+<!-- tmp <- shortRobustPrep[grepl("Out", names(shortRobustPrep))] -->
+<!-- outRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Out$coef) -->
+<!-- for (i in 1:length(tmp)){ -->
+<!--   outRobustTbl <- join(outRobustTbl, tmp[[i]], by = "coef") -->
+<!-- } -->
+
+<!-- robustTblLong <- rbind( -->
+<!--   fullRobustTbl, -->
+<!--   outRobustTbl -->
+<!-- ) -->
+
+<!-- robustTblLong$coef <- mapvalues( -->
+<!--   robustTblLong$coef, -->
+<!--   from = c( -->
+<!--     "R2Marg_R2Cond" -->
+<!--   ), -->
+<!--   to = c( -->
+<!--     "$R^2_{marginal}$ / $R^2_{conditional}$" -->
+<!--   ) -->
+<!-- ) -->
+
+<!-- mdlTblRobustLong <- robustTblLong %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Robustness Analyses", -->
+<!--     #format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = c("l", rep("c", ncol(.)-1)), -->
+<!--     escape = FALSE -->
+<!--   ) %>% -->
+<!--   kable_classic() %>% -->
+<!--   add_header_above(., c(" ", "Study 1" = 2, "Study 2" = 2, "Study 3" = 2)) %>% -->
+<!--   pack_rows("Contact [Full Sample]", 1, 5) %>% -->
+<!--   pack_rows("Self-Determination Theory [Outgroup Interactions only]", 6, 11) %>% -->
+<!--   kableExtra::footnote( -->
+<!--     ., -->
+<!--     general = c("**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"),  -->
+<!--     escape = FALSE -->
+<!--   ) %>% -->
+<!--   kable_styling(latex_options = "scale_down") %>% -->
+<!--   #kableExtra::landscape() %>% -->
+<!--   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position -->
+<!--   gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position -->
+<!--   save_kable("Tables/mdlRobustlong.tex") -->
+<!-- ``` -->
+
+<!-- ```{r robustnessTblWide, include=FALSE} -->
+<!-- # Wide format -->
+<!-- mdlRobustTbl <- data.frame( -->
+<!--   coef = c( -->
+<!--     sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef) %>% unlist %>% unique, -->
+<!--     names(mdlRobustPrep[[1]]$random), -->
+<!--     names(mdlRobustPrep[[1]]$fit) -->
+<!--   ) -->
+<!-- ) -->
+<!-- for (i in 1:length(mdlRobustPrep)){ -->
+<!--   mdlRobustTbl <- join(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef") -->
+<!--   #mdlTbl <- merge(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", "")) -->
+<!-- } -->
+
+<!-- mdlRobustTblHeader <- data.frame( -->
+<!--   data = as.character(mdlRobustTbl[mdlRobustTbl$coef == "data",]), -->
+<!--   formula = as.character(mdlRobustTbl[mdlRobustTbl$coef == "formula",]) -->
+<!-- ) %>% -->
+<!--   filter(data != "", -->
+<!--          data != "data") %>% -->
+<!--   mutate(study = str_extract(data, "Worker|Student|Medical")) %>% -->
+<!--   mutate(study = gsub("Worker", "Study 1", study)) %>% -->
+<!--   mutate(study = gsub("Student", "Study 2", study)) %>% -->
+<!--   mutate(study = gsub("Medical", "Study 3", study)) %>% -->
+<!--   mutate(dv = sub(" ~.*", "", formula)) %>% -->
+<!--   mutate(dv = gsub("Raw", " ", dv)) %>% -->
+<!--   mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>% -->
+<!--   mutate(header = paste(study, pred, sep = " - ")) -->
+
+<!-- mdlRobustTblHeaderFreq <- rbind.data.frame(rle(mdlRobustTblHeader$header)) %>% -->
+<!--   mutate(lengths = lengths*2) %>% -->
+<!--   rename(names = values, span = lengths) %>% -->
+<!--   rbind(c(1, ""), .) %>% -->
+<!--   mutate(span = as.numeric(span)) %>% -->
+<!--   select(names, span) -->
+
+<!-- mdlRobustTblHeaderDv <- data.frame(names = mdlRobustTblHeader$dv, span = 2) %>%  -->
+<!--   mutate(names = as.character(names)) %>% -->
+<!--   rbind(c("", 1), .) %>% -->
+<!--   mutate(span = as.numeric(span)) -->
+
+<!-- mdlRobustTblHeaderStudy <- rbind.data.frame(rle(mdlRobustTblHeader$study)) %>% -->
+<!--   mutate(lengths = lengths*2) %>% -->
+<!--   rename(names = values, span = lengths) %>% -->
+<!--   rbind(c(1, ""), .) %>% -->
+<!--   mutate(span = as.numeric(span)) %>% -->
+<!--   select(names, span) -->
+
+<!-- mdlRobustTbl$coef <- mapvalues( -->
+<!--   mdlRobustTbl$coef, -->
+<!--   from = c( -->
+<!--     "sigmaSq", -->
+<!--     "tau00", -->
+<!--     "tau11", -->
+<!--     "rho01", -->
+<!--     "rho00", -->
+<!--     "R2_marginal", -->
+<!--     "R2_conditional",  -->
+<!--     "R2Marg_R2Cond" -->
+<!--   ), -->
+<!--   to = c( -->
+<!--     "$\\sigma^2$", -->
+<!--     "$\\tau_{00}$", -->
+<!--     "$\\tau_{11}$", -->
+<!--     "$\\rho_{01}$", -->
+<!--     "$\\rho_{00}$", -->
+<!--     "$R^2_{marginal}$", -->
+<!--     "$R^2_{conditional}$", -->
+<!--     "$R^2_{marginal}$ / $R^2_{conditional}$" -->
+<!--   ) -->
+<!-- ) -->
+
+<!-- # Long Table -->
+<!-- mdlTblRobustLong <- mdlRobustTbl %>% -->
+<!--   replace(is.na(.), "") %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Robustness Analyses", -->
+<!--     #format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = T, -->
+<!--     align = c("l", rep("c", ncol(.) - 1)), -->
+<!--     escape = FALSE, -->
+<!--     digits = 3 -->
+<!--   ) %>% -->
+<!--   kable_classic() %>% -->
+<!--   add_header_above(., mdlRobustTblHeaderStudy) %>% -->
+<!--   add_header_above( -->
+<!--     ., -->
+<!--     c( -->
+<!--       "", -->
+<!--       "Contact [Full Sample]" = 6, -->
+<!--       "Self-Determination Theory [Outgroup Interactions only]" = 6 -->
+<!--     ) -->
+<!--   ) %>% -->
+<!--   pack_rows("Fixed", 1, 7) %>% -->
+<!--   pack_rows("Random", 8, 12) %>% -->
+<!--   pack_rows("Fit", 13, 25) %>% -->
+<!--   footnote( -->
+<!--     general = c("PID = Participant ID number (grouping variable)", -->
+<!--                 "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes", -->
+<!--                 "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05" -->
+<!--     ), -->
+<!--     escape = FALSE -->
+<!--   ) %>% -->
+<!--   gsub("_cwc", "", ., fixed = TRUE)  -->
+
+<!-- # shortened Table -->
+<!-- mdlTblRobustShort <- mdlRobustTbl %>% -->
+<!--   replace(is.na(.), "") -->
+<!-- names(mdlTblRobustShort) <- make.unique(names(mdlTblRobustShort)) -->
+<!-- mdlTblRobustShort <- mdlTblRobustShort %>% -->
+<!--   filter( -->
+<!--     !coef %in% c( -->
+<!--       "data", -->
+<!--       "formula", -->
+<!--       "groupId", -->
+<!--       "$R^2_{marginal}$", -->
+<!--       "$R^2_{conditional}$", -->
+<!--       "logLik", -->
+<!--       "deviance" -->
+<!--     ) -->
+<!--   ) %>% -->
+<!--   mutate_all(linebreak) %>% -->
+<!--   kbl( -->
+<!--     ., -->
+<!--     caption = "Robustness Analyses", -->
+<!--     format = "latex", -->
+<!--     linesep = "", -->
+<!--     booktabs = TRUE, -->
+<!--     col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)), -->
+<!--     align = c("l", rep("c", ncol(.) - 1)), -->
+<!--     escape = FALSE, -->
+<!--     digits = 3 -->
+<!--   )  %>% -->
+<!--   kable_classic() %>% -->
+<!--   add_header_above(., mdlRobustTblHeaderStudy) %>% -->
+<!--   add_header_above( -->
+<!--     ., -->
+<!--     c( -->
+<!--       "", -->
+<!--       "Contact [Full Sample]" = 6, -->
+<!--       "Self-Determination Theory [Outgroup Interactions only]" = 6 -->
+<!--     ) -->
+<!--   ) %>% -->
+<!--   pack_rows("Fixed", 1, 7) %>% -->
+<!--   pack_rows("Random", 8, 12) %>% -->
+<!--   pack_rows("Fit", 13, 18) %>% -->
+<!--   footnote( -->
+<!--     general = c("PID = Participant ID number (grouping variable)", -->
+<!--                 "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes", -->
+<!--                 "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05" -->
+<!--     ),  -->
+<!--     escape = FALSE -->
+<!--   ) %>% -->
+<!--   kable_styling(latex_options = "scale_down") %>% -->
+<!--   kableExtra::landscape() %>% -->
+<!--   gsub("_cwc", "", ., fixed = TRUE)  %>% -->
+<!--   gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>% -->
+<!--   gsub("\\makecell[r]", "\\makecell[c]", ., fixed = TRUE) %>% -->
+<!--   gsub("objVar$", "", ., fixed = TRUE) %>% -->
+<!--   gsub("slope_intercept.", "slope.intercept", ., fixed = TRUE) %>% -->
+<!--   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position -->
+<!--   gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position -->
+<!--   save_kable("Tables/mdlRobustness.tex") -->
+<!-- mdlTblRobustShort -->
+<!-- ``` -->
+
+<!-- <!-- FIGURES: --> -->
+
+<!-- ```{r metaRobust, include=FALSE} -->
+<!-- mdlRobustTblElements <- list( -->
+<!--   # full -->
+<!--   c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ), -->
+<!--   c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ), -->
+<!--   c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ), -->
+<!--   # outgroup -->
+<!--   c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ), -->
+<!--   c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ), -->
+<!--   c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ) -->
+<!--   ) -->
+
+<!-- # i =1 -->
+<!-- robustMetaTbl <- data.frame() -->
+<!-- for (i in 1:length(mdlRobustTblElements)){ -->
+<!--   lmerTblTmp <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$beta %>% -->
+<!--   select( -->
+<!--     coef, -->
+<!--     B = est, -->
+<!--     se, -->
+<!--     lwr, -->
+<!--     upr, -->
+<!--     tval, -->
+<!--     Rsq -->
+<!--   ) %>% -->
+<!--   mutate( -->
+<!--     n = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$N, -->
+<!--     m = nrow(.),  -->
+<!--     #dv = gsub("Dutch", "", str_extract(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,".+?(?= ~)")), -->
+<!--     sample = str_match(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$data, "Tbl(.*?)(Full|Out)")[2], -->
+<!--     formula = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula, -->
+<!--     coef = gsub(":", ".", coef) -->
+<!--   ) -->
+<!--   robustMetaTbl <- rbind(robustMetaTbl, lmerTblTmp) -->
+<!-- } -->
+
+<!-- robustMetaTbl <- robustMetaTbl %>% -->
+<!--   arrange(formula, match( -->
+<!--     coef, -->
+<!--     c( -->
+<!--       "CoreNeed_zwc", -->
+<!--       "OutgroupInteraction_zwc", -->
+<!--       "CoreNeed_zwc.OutgroupInteraction_zwc", -->
+<!--       "Autonomy_zwc", -->
+<!--       "Competence_zwc", -->
+<!--       "Relatedness_zwc" -->
+<!--     ) -->
+<!--   )) %>%  -->
+<!--   mutate(formula = gsub(" \\+ \\(.*", "", formula)) -->
+
+<!-- robustMetaContact <- -->
+<!--   metaLmerOut( -->
+<!--     lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc * OutgroupInteraction"), -->
+<!--     type = "REML", #"FE",  -->
+<!--     name = "RobustContact", -->
+<!--     title = "Robustness — Contact and Need Fulfillment" -->
+<!--   ) -->
+
+<!-- robustMetaSDT <- -->
+<!--   metaLmerOut( -->
+<!--     lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc + Competence_cwc + Autonomy_cwc +      Relatedness_cwc"), -->
+<!--     type = "REML", #"FE",  -->
+<!--     name = "RobustSDT", -->
+<!--     title = "Robustness — Other Needs" -->
+<!--   ) -->
+<!-- ``` -->
+
+<!-- ```{r robustForestPltComb, include=FALSE} -->
+<!-- effRobust <- rbind( -->
+<!--   robustMetaContact$eff %>% -->
+<!--     filter(coef != "(Intercept)") %>% -->
+<!--     mutate(analysis = "(A) Attitude ~ Contact and Need Fulfillment", -->
+<!--            metaId = paste(coef, analysis, sep = ".")) %>% -->
+<!--     as.data.frame, -->
+<!--   robustMetaSDT$eff %>% -->
+<!--     mutate(analysis = "(B) Attitude ~ Other Needs", -->
+<!--            metaId = paste(coef, analysis, sep = ".")) %>% -->
+<!--     as.data.frame -->
+<!-- ) -->
+
+<!-- metaSubForest(effRobust,  -->
+<!--               title = "Meta Analysis: Forest Plot Robustness Analysis \n[Parametric]", -->
+<!--               filename = "RobustnessComb", -->
+<!--               addAbove = 5, -->
+<!--               width = 600, -->
+<!--               height = 800) -->
+<!-- ``` -->

### 2023-05-26 scripts/functions/MlCorMat.R

@@ -357,3 +357,300 @@ linesep<-function(x,y=character()){
     return(y)
   linesep(x[-length(x)], c(rep('',x[length(x)]-1),'\\addlinespace',y))  
 }
+
+select_best_lmer_model <- function(data, structure, dependent_var, prediction_form, return = "", control = list(opt = "nlmimb"), lmer_scale = FALSE) {
+  # Set the warning option to -1 to suppress all warnings
+  options(warn = -1)
+  # lm data
+  vars <- c(dependent_var, unique(unlist(strsplit(prediction_form, "\\W+"))), unique(unlist(strsplit(structure, "\\W+"))))
+  data_lme <- data %>% 
+    select(all_of(vars)) %>%
+    na.omit
+  
+  # Define model formulas
+  prediction_form_z <- gsub("(\\b[A-Za-z]*)C\\b", "\\1Z", prediction_form, perl = TRUE)
+  dependent_var_z <- paste0(dependent_var, "Z")
+  
+  null_model_formula <- as.formula(paste(dependent_var, "~ 1"))
+  random_model_formula <- as.formula(paste(dependent_var, "~", prediction_form))
+  
+  null_structure <- as.formula(paste("~ 1 |", structure))
+  slope_structure <- as.formula(paste("~ 1 +", paste(unique(unlist(strsplit(prediction_form, "\\W+"))), collapse = " + "), "|", structure))
+  
+  null_lmer <- as.formula(paste0(dependent_var, " ~ 1 + (1 | ", structure, ")"))
+  null_lmer_z <- as.formula(paste0(dependent_var_z, " ~ 1 + (1 | ", structure, ")"))
+  intercept_lmer <- as.formula(paste0(dependent_var, " ~ ", prediction_form, " + (1 | ", structure, ")"))
+  intercept_lmer_z <- as.formula(paste0(dependent_var_z, " ~ ", prediction_form_z, " + (1 | ", structure, ")"))
+  slope_lmer <-
+    as.formula(paste0(
+      dependent_var, " ~ ", prediction_form," + (1 + ",
+      paste(unique(unlist(strsplit(prediction_form, "\\W+"))), collapse = " + "),
+      " | ", structure,")"
+    ))
+  slope_lmer_z <-
+    as.formula(paste0(
+      dependent_var_z, " ~ ", prediction_form_z," + (1 + ",
+      paste(unique(unlist(strsplit(prediction_form_z, "\\W+"))), collapse = " + "),
[…]

### 2023-05-26 scripts/functions/MlTbl.R

@@ -5,7 +5,7 @@ library(plyr)
 # obj <- mdlTblElements[[i]][[1]]
 # objz <- mdlTblElements[[i]][[2]]
 
-lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
+lmerTblPrep <- function (obj, objz = NULL, name = NULL, alpha = 0.05, ...) {
   # Summarize models
   smry <- summ(obj)
   smryZ <- summ(objz)
@@ -86,10 +86,12 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   coefOut <- 
     plyr::join(
       coefOut %>% 
-        mutate(coef = gsub('_cwc|C$', '', coef)), 
+        mutate(coef = gsub('_cwc|C$', '', coef)) %>%
+        mutate(coef = gsub('C:', ':', coef)), 
       coefZOut %>% 
         select(coef, estBeta = est, Beta, BetaStar) %>% 
         mutate(coef = gsub('_zwc|_gmz|Z$', '', coef)) %>%
+        mutate(coef = gsub('Z:', ':', coef)) %>%
         mutate(Beta = ifelse(coef == "(Intercept)", "", Beta)),
       by = "coef"
     )
@@ -137,7 +139,7 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
   AIC <- AIC(obj)
   BIC <- BIC(obj)
   N <- as.numeric(obj@devcomp$dims["n"])
-  G <- as.numeric(as.data.frame(smry$gvars)["# groups"])
+  G <- as.character(as.data.frame(smry$gvars)["# groups"])
   ICC <- ifelse(
     berryFunctions::is.error(performance::icc(obj)$ICC_adjusted), 
     performance::icc(obj),
@@ -149,6 +151,7 @@ lmerTblPrep <- function (obj, objz = NULL, alpha = 0.05, ...) {
                          format(round(rSqCond, 3), nsmall = 3), 
                          sep = " / ")
   sumstat <- list(
+    name = ifelse(is.null(name), "", name),
     data = data,
     formula = formula,
     groupId = groupNam,

### 2023-05-26 scripts/functions/metaLmer.R

@@ -26,7 +26,8 @@ strLabFix <- function(varIn, ...) {
       " X "
     ),
     vectorize_all = FALSE
-  )
+  ) %>%
+    stri_replace_all_regex(., "[ZC]$", "")
 }
 
 strStudyFix <- function(studyIn, ...) {
@@ -35,16 +36,22 @@ strStudyFix <- function(studyIn, ...) {
     pattern = c(
       "Worker", 
       "worker", 
+      "s1",
       "Student",
       "student",
+      "s2",
       "Medical",
-      "medical"
+      "medical",
+      "s3"
     ),
     replacement = c(
       "Study 1",
       "Study 1",
+      "Study 1",
       "Study 2",
       "Study 2",
+      "Study 2",
+      "Study 3",
       "Study 3",
       "Study 3"
     ),
@@ -506,7 +513,7 @@ metaSubForest <- function(effects, title = "", addAbove = 0, filename = NULL, ty
   }
   
   png(file = paste0("Figures/forestParametric", filename, ".png"), width = width, height = height)
-  forestGeneral <- forest(
+  forestGeneral <- metafor::forest(
     metaGeneral,
     cex = 0.75,
     ylim = c(-1, max(unlist(studyIndex)) + addAbove),

### 2023-05-26 scripts/power-simulation_original-script.R

@@ -1,0 +1,119 @@
+### Power Analysis ###
+### Note:
+### Example marginalization
+### Becareful with running this. The simulations can only take one CPU core and take forever.
+
+# prepare for re-run:
+  cat("\014") # clear console
+  rm(list = ls()) # clear workspace
+  gc() # run garbage collector
+  setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # set working directory
+  p_load(simr, data.table, lme4, lmerTest)
+  load("df.btw.Rdata")
+  
+# set random seed for reporducibility
+  set.seed(42)
+
+# prepare data for regression (i.e, put into long format and change variable types)
+  marginalization = melt(df.btw[!is.na(df.btw$assimilation.post),c("marginalization.pre","marginalization.post",
+                                                                   "CtContactNL_c","AvKeyNeedInt_c",
+                                                                   "ExternalReference")],
+                         id=c("ExternalReference","CtContactNL_c","AvKeyNeedInt_c"))
+  marginalization$time = ifelse(grepl(".pre", marginalization$variable), "pre", "post")
+  marginalization$variable = gsub(".pre$|.post$", "", marginalization$variable)
+  marginalization$time = factor(marginalization$time)
+  marginalization$time = factor(marginalization$time,levels(marginalization$time)[c(2,1)])
+  marginalization$id = rep(seq(1:20), 2)
+
+# run regresion 
+  lm.marg <- lmer(value~
+                    AvKeyNeedInt_c*time+
+                    CtContactNL_c*time+
+                    (1|id), 
+                  data=marginalization)
+  summary(lm.marg)
+  fixef(lm.marg)
+
+# Post-hoc power analysis for single effects (example: key need)
+  powerSim(lm.marg, fixed("AvKeyNeed"), nsim=1000)
+
+
+# Simulate different N.s for all fixed effects
+  # extrapolate data:
+    sim.N <- extend(lm.marg, along="id", n=500)
+  
+  # Run and plot simulations
+    plt.pwr.contact = powerCurve(sim.N, fixed("CtContactNL_c", "t"), 
+                                 along="id", 
+                                 breaks = seq(10,100,10), 
+                                 nsim=1000)
+    plot(plt.pwr.contact)
+    
+    plt.pwr.time = powerCurve(sim.N, fixed("time"), 
+                              along="id", 
+                              breaks = seq(10,100,10), 
[…]

### 2023-05-26 Methods-and-Results.tex
methods and results re-render (in progress)

@@
 inequalities by using centered predictors and reintroducing the means as
-level two predictors (\citealp{Yaremych2021}; for full results see
+level two predictors (\citealp{yaremych2021a}; for full results see
 \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
@@
 
-\section{Robustness, Stability, and Embeddedness across Studies}
+\section{Stability, Robustness, and Embeddedness across Studies}
 
-Beyond the individual results of the three studies, we conducted three
-additional analyses to test the broader cross-study claims and
-contextualize our results. In particular, we aimed to gain a broader
-picture of the individual results by considering them jointly. We also
-leveraged the data from all participants to test between-participant
-contact effects and explore the content of the participants' situational
-contact needs.
+Beyond the individual results of the three studies, we conducted a
+number additional analyses to test the broader cross-study claims,
+account for alternative models, and contextualize our results. Jointly,
+these stability, robustness, and embeddedness analyses seek to
+strengthen our confidence in the results.
 
 \subsection{Stability}
+
+We ran two analyses that tested the stability of our results. We first
+assess the consistency of the results reported in the three studies and
+use a meta-analytic approach to gauge the general effect sizes. The
+second stability analysis we conduct seeks to asses the extend to which
+the within person contemporaneous effects extend to an aggregated
+version that mirrors the many cross-sectional recall studies.
+
+\subsubsection{Consistency}
 
@@
 needs during intergroup contacts, we find that the motivational
-mechanism is consistently a meaningful predictor of outgroup attitudes
-and interaction quality perceptions (see
+mechanism is consistently a meaningful predictor of interaction quality
+perceptions and outgroup attitudes (see
 \fgrref[ A and B]{fig:AllportNeedFulfillment}). We also see that the
@@
 
-\subsection{General contact hypothesis}
+\subsubsection{Aggregated Analysis}
 
-During the main analyses, we have thus far shown that participants held
-more positive outgroup attitudes following intergroup contacts and that
-perceived interaction quality was associated with more positive outgroup
-attitudes following an intergroup contact. We have, however, not brought
-the two elements of the contact hypothesis together in a single
-analysis. To jointly test the effects of contact frequency and average
-interaction quality, we ran a linear regression model where average
-outgroup attitudes were predicted by the number of interactions and the
-average interaction quality ratings of all participants across the three
-studies. We did so while controlling for the possible effects of
-study-specific differences. To include the study-membership as a control
-variable, we used the student sample (Study 2) as the reference group
-because it was both the largest and the most homogeneous study. Looking
-at the overall model, we found that the model predicted 13.89\% of the
-variance in average outgroup attitudes (\textit{F}(9, 189) = 3.39,
-\textit{p} = 0.001, \textit{R\textsuperscript{2}} = 0.14). Looking at
-the individual effects, we found that only the number of outgroup
-interactions has a clear association with average outgroup attitudes
-(\textit{b} = 0.55, \textit{t}(189) = 2.82, \textit{p} = 0.005,
-\textit{95\%CI}{[}0.16, 0.93{]}). The average interaction quality
-perceptions had a much smaller effect (\textit{b} = 0.29,
-\textit{t}(189) = 2.09, \textit{p} = 0.038, \textit{95\%CI}{[}0.02,
-0.56{]}), and importantly we found no interaction effect at all. In
-short, the effect of interaction frequency did not depend on the average
-interaction quality.
+A second stability test is checking whether the within person effects
+translate to a broader aggregated between subjects effect, which would
+mirror common cross-sectional practices. During the main analyses, we
+have thus far shown that participants held more positive outgroup
+attitudes following intergroup contacts and that perceived interaction
+quality was associated with more positive outgroup attitudes following
+an intergroup contact. We have, however, not brought the two elements of
+the contact hypothesis together in a single analysis. To jointly test
+the effects of contact frequency and average interaction quality, we ran
+a linear regression model where average outgroup attitudes were
+predicted by the number of interactions and the average interaction
+quality ratings of all participants across the three studies. We did so
+while controlling for the possible effects of study-specific
+differences. To include the study-membership as a control variable, we
+used the student sample (Study 2) as the reference group because it was
+both the largest and the most homogeneous study. Looking at the overall
+model, we found that the model predicted 13.89\% of the variance in
+average outgroup attitudes (\textit{F}(9, 189) = 3.39, \textit{p} =
+0.001, \textit{R\textsuperscript{2}} = 0.14). Looking at the individual
+effects, we found that only the number of outgroup interactions has a
+clear association with average outgroup attitudes (\textit{b} = 0.55,
+\textit{t}(189) = 2.82, \textit{p} = 0.005, \textit{95\%CI}{[}0.16,
+0.93{]}). The average interaction quality perceptions had a much smaller
+effect (\textit{b} = 0.29, \textit{t}(189) = 2.09, \textit{p} = 0.038,
+\textit{95\%CI}{[}0.02, 0.56{]}), and importantly we found no
+interaction effect at all. In short, the effect of interaction frequency
+did not depend on the average interaction quality.
 
-\subsection{Contact key need content}
+\subsection{Robustness}
 
-Finally, we used the qualitative data from the participants'
-self-identified core needs to contextualize the results of our main
-analysis. However, because our participants jointly reported on
-thousands of intergroup contacts, it would not have been feasible to
-analyze these qualitative responses in a traditional qualitative content
-analysis. We instead relied on recent machine learning advances within
-the natural language processing domain. For our analysis, we used the
-BERT language model. BERT (Bidirectional Encoder Representations from
-Transformers) was developed by Google in 2018 and today forms a key
-element of many natural language processing workflows. In its essence,
-BERT is a framework that allows users to codify every word in relation
-to every other word within a large set of documents. We extracted 47
-topics from the 2,983 interaction goal free-text entries --- a
-relatively large number of topics. The higher number of topics allowed
-us to retain more of the smaller topics and leaves a relatively low
-number of 308 free-text entries unclassified (10.33\%). A full write-up
-of the topic modeling process is available in Online Supplemental
-Material B.
+To check for spurious relationships, we test three additional models.
+These three models assess whether the effect is indeed specific to
+intergroup contact, whether the need fulillment effect is a affected by
+whether the contact was planned or accidental, and whether the
+motivational mechanism also holds direct well-being benefits for the
+minority members. We describe the full methods and results for the
+robustness analyses in \appref{app:AppendixRobustness}. We use a
+two-staged analysis approach for the robustness analyses. We first test
+the model `globally' --- across the three studies --- in a three level
+multilevel regression (i.e., measurements nested within participants,
+and participants nested within studies). Only in a second step do check
+for study-specific idiosyncrasies.
+
+\subsubsection{Contact specific}
+
+To ensure that the core need fulfillment is outgroup contact specific,
+we return to the full sample of intensive longitudinal measurements and
+test whether there is an interaction effect of outgroup contact (vs.~no
+outgroup contact) and core need fulfillment. We expected that the effect
+of core need fulfillment on outgroup attitudes is specific to outgroup
+interactions and not merely due to a more need-fulfilled life in
+general. We find that \hl{...}.
+
+\subsubsection{Interaction intend}
+
+To test whether the need mechanism was affected by whether the
+interaction was accidental or planned we ran an exploratory moderation
+analysis using the participants' ratings of how much they perceived the
+interaction as `accidental'. It should be noted at this point, that in
+order to keep the ESM surveys short, we asked our participants to focus
+on most the important interaction (i.e.,
+``\textit{The following questions will be about the interaction \underline{you consider most significant}.}'''```;
+emphasis as in original). This was also reflected in a relatively low
+average and consistent right skew of the 'accidental' item. Nonetheless,
+there remained a substantial variance in the item and we continued with
+the moderation analysis. We find that \hl{...}.
+
+\subsubsection{Well-being outcome}
+
+Given the well-established criticism that more positive outgroup
+attitudes might not always be beneficial for minority group members
+\citep[e.g.,][]{reimer2023}, we conducted an additional exploratory
+analysis assessing the effect of need fulfilling outgroup interactions
+on reported well-being. Experienced well-being is a common indicator of
+health and an important life quality measurement in itself, especially
+for migrants or other minority groups \citep[e.g.,][]{bhugra2011}. We
+find that \hl{...}. The analysis, thus, adds weight to the importance of
+considering the need fulfillment experiences when it comes to outgroup
+interactions.
+
+\subsection{Embeddedness}
+
+To embed our results further, we also considered the content and types
+of needs that participants reported during the study. For these
+embeddedness analyses, we first assessed the self-reported motives of
+the participants and then also control the commonly considered
+self-determination theory needs.
+
+\subsubsection{Contact need content}
+
+We used the qualitative data from the participants' self-identified core
+needs to contextualize the results of our main analysis. However,
+because our participants jointly reported on thousands of intergroup
+contacts, it would not have been feasible to analyze these qualitative
+responses in a traditional qualitative content analysis. We instead
+relied on recent machine learning advances within the natural language
+processing domain. For our analysis, we used the BERT language model.
+BERT (Bidirectional Encoder Representations from Transformers) was
+developed by Google in 2018 and today forms a key element of many
+natural language processing workflows. In its essence, BERT is a
+framework that allows users to codify every word in relation to every
+other word within a large set of documents. We extracted 47 topics from
+the 2,983 interaction goal free-text entries (after duplicate removal)
+--- a relatively large number of topics. The higher number of topics
+allowed us to retain more of the smaller topics and leaves a relatively
+low number of 308 free-text entries unclassified (10.33\%). A full
+write-up of the topic modeling process is available in Online
+Supplemental Material C.
 
@@
 cultural products (e.g., music, theater, food) or had travel-related
-goals in their interactions with the majority group members.
-
-One interesting observation was the importance of contact goals specific
-to contact through the medical and public health system. This goal type
-was partly specific to the medical professionals (e.g., working with
-patients, treatment), but also more broadly highlighted interactions of
-newcomers with the outgroup majority as patients themselves (e.g.,
-therapeutic goals). Also health, fitness, and personal improvement goals
-(e.g., sports and music) were common goals that participants shared
-during the interactions with the majority group members. Another topic
-less commonly found within the literature were more practically oriented
-needs, where participants sought to share food and cook together or had
-organizational needs (e.g., housing, cleaning, and co-living). In sum,
+goals in their interactions with the majority group members. In sum,
 almost all extracted topics fall into broader or narrower need concepts
-that are commonly discussed within the psychological needs literature
-\citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the
+that are commonly discussed within the need fulfillment literature
+\citep[e.g.,][]{orehek2018a} and offer insight into a core aspect of the
 migration experience that has remained broadly under-explored
@@
 The authors have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
+
+\subsubsection{Need types}
+
+To ensure that our results are not impacted by differences in the
+reported goals and motives, we additionally coded the topics we
+extracted during the topic modeling on two dimensions of how much they
+reflect a practical and a psychological goal-directedness. We chose
+practical and psychological needs specifically as our dimensions to
+account for differences in the types of needs that participants commonly
+reported. With practical motives we refer to specific, tangible goals or
+tasks that participants aimed to accomplish during the interaction.
+These instrumental goals are usually observable, concrete, and often
+centered on external outcomes, such as acquiring resources, completing
+tasks, and addressing immediate challenges \citep[][]{}. With
+psychological motives we refer to underlying motives or desires that are
+more abstract and relate to personal fulfillment and well-being. In
+contrast to practical needs, psychological needs delve into the
+subjective and internal aspects of human experiences. These needs
+pertain to emotions, social connections, and cognitive processes,
+reflecting individuals' quest for personal growth, well-being, and
+thriving in social relationships \citep[][]{}. Note that with this
+approach any particular motive can include a practical and/or a
+psychological goal-directedness but can also be classified as not having
+any goal at all.
+
+For each of the topics, we had identified in the topic modeling
+analysis, we extracted the top 10 most indicative words as well as the
+three most representative free text responses. Using a detailed coding
+protocol for both the practical as well as the psychological motives,
+two independent coders rated each of the 47 topics. This allowed us to
+add the two dimensions back to each of the reported interaction motives
+and assess the distributions and effects of the goal-directed character.
+We found that \hl{...}.
+
+\subsubsection{Specific psychological needs}
+
+Finally, to ensure that a much simpler model of three fundamental
+psychological needs might not account for the same effect, we compared
+our situation core need fulfillment measurement to the three
+self-determination theory needs (autonomy, relatedness, competence).

### 2023-05-26 Robustness-Methods-and-Results.Rmd
methods and results re-render (in progress)

@@
 ```
-
-<!-- -------------------------------------------------------------------- -->
-
-<!--                               OLD CODE                               -->
-
-<!-- -------------------------------------------------------------------- -->
-
-<!-- \subsubsection{Study 1} -->
-
-<!-- ```{r workerSampleInfo, include=FALSE} -->
-<!-- # combine education measure -->
-<!-- workerOccupation <-  -->
-<!--   dtWorker$clean %>% -->
-<!--   select(PID, starts_with("occupation")) %>% -->
-<!--   mutate_all(as_factor) %>%  -->
-<!--   mutate_all(as.character) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   unite("occupation", -PID, sep = "/") %>% -->
-<!--   mutate(occupation = trimws(occupation, which = "both", whitespace = "[/]")) %>% -->
-<!--   distinct -->
-
-<!-- # summarize participant characteristics -->
-<!-- workerSampleInfo <-  -->
-<!--   dtWorker$clean %>% -->
-<!--   group_by(PID) %>% -->
-<!--   summarise( -->
-<!--     dailiesN = n(),  -->
-<!--     morningN = sum(daytime=="morning"), -->
-<!--     afternoonN = sum(daytime=="afternoon"), -->
-<!--     age = age, -->
-<!--     gender = as_factor(Gender), -->
-<!--     edu = as_factor(education_level), -->
-<!--     nationality = as_factor(nationality) -->
-<!--   ) %>% -->
-<!--   distinct -->
-
-<!-- # add occupation variable -->
-<!-- workerSampleInfo <- merge(workerSampleInfo, workerOccupation) -->
-<!-- rm(workerOccupation) -->
-
-<!-- # divide into trait and state -->
-<!-- dtWorkerSupp$workerWithinBetween <- -->
-<!--   MlTraitState( -->
-<!--     data = dtWorkerSupp$workerInteractionType, -->
-<!--     id = "PID", -->
-<!--     selection = -->
-<!--       c( -->
-<!--         "keyMotiveFulfilled", -->
-<!--         "competence.daily.all", -->
-<!--         "autonomy.daily.all", -->
-<!--         "relatedness.daily.all", -->
-<!--         "thermometerDutch_1", -->
-<!--         "keymotive_fulfillemt_1", -->
-<!--         "competence_1", -->
-<!--         "autonomy_1", -->
-<!--         "relatedness_1",  -->
-<!--         "quality_overall_1",  -->
-<!--         "OutgroupInteraction", -->
-<!--         "NonOutgroupInteraction",  -->
-<!--         "OutgroupInteractionM", -->
-<!--         "NonOutgroupInteractionM" -->
-<!--       ) -->
-<!--   ) -->
-
-<!-- dtWorkerSupp$workerOutWithinBetween <- -->
-<!--   MlTraitState( -->
-<!--     data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"), -->
-<!--     id = "PID", -->
-<!--     selection = -->
-<!--       c( -->
-<!--         "keyMotiveFulfilled", -->
-<!--         "thermometerDutch_1", -->
-<!--         "keymotive_fulfillemt_1", -->
-<!--         "competence_1", -->
-<!--         "autonomy_1", -->
-<!--         "relatedness_1",  -->
-<!--         "quality_overall_1" -->
-<!--       ) -->
-<!--   ) -->
-<!-- ``` -->
-
-<!-- ```{r workerModelOlsAttFreqQual, include=FALSE} -->
-<!-- # create list to store Worker models -->
-<!-- mdlWorker <- list() -->
-<!-- ``` -->
-
-<!-- ```{r workerModelMLAttNull, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlWorker$lmerAttNull <- -->
-<!--   lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID), -->
-<!--     data = dtWorker$full -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- mdlWorker$lmeAttNull <- -->
-<!--   lme( -->
-<!--     thermometerDutch_1 ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtWorker$full, -->
-<!--     na.action=na.omit, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(lmerWorkerAttNull) #or with the lme function -->
-<!-- summ(mdlWorker$lmerAttNull, digits = 3, center = TRUE) -->
-
-<!-- # Save variances -->
-<!-- mdlWorker$varAttNull <-  -->
-<!--   VarCorr(mdlWorker$lmeAttNull) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlWorker$tauAttNull <-  -->
-<!--   as.numeric(mdlWorker$varAttNull[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlWorker$sigmaAttNull <-  -->
-<!--   as.numeric(mdlWorker$varAttNull[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlWorker$IccAttNull <- -->
-<!--   (as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2]))) -->
-<!-- mdlWorker$IccPercAttNull <- -->
-<!--   ((as.numeric(mdlWorker$varAttNull[1]) / (as.numeric(mdlWorker$varAttNull[1]) + as.numeric(mdlWorker$varAttNull[2])))) * 100 -->
-<!-- ``` -->
-
-<!-- ```{r workerOutModelMLAttNull, include=FALSE} -->
-<!-- # create empty list to organize models -->
-<!-- mdlWorkerOut <-  -->
-<!--   list( -->
-<!--     Att = list(), -->
-<!--     Qlt = list() -->
-<!--   ) -->
-
-<!-- # Create and save Model -->
-<!-- mdlWorkerOut$Att$lmerNull <- -->
-<!--   lme4::lmer(thermometerDutch_1 ~ 1 + (1 | PID),  -->
-<!--              data = dtWorkerSupp$workerOutgroupInteraction) # use optim if it does not converge -->
-<!-- mdlWorkerOut$Att$lmeNull <- -->
-<!--   lme( -->
-<!--     thermometerDutch_1 ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtWorkerSupp$workerOutgroupInteraction, -->
-<!--     na.action=na.omit, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(Null.Out.ML.r) #or with the lme function -->
-<!-- summ(mdlWorkerOut$Att$lmerNull, digits = 3, center = TRUE) -->
-
-<!-- # Save variances -->
-<!-- mdlWorkerOut$Att$varNull <-  -->
-<!--   VarCorr(mdlWorkerOut$Att$lmeNull) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlWorkerOut$Att$tauNull <-  -->
-<!--   as.numeric(mdlWorkerOut$Att$varNull[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlWorkerOut$Att$sigmaNull <-  -->
-<!--   as.numeric(mdlWorkerOut$Att$varNull[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlWorkerOut$Att$IccNull <- -->
-<!--   (as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2]))) -->
-<!-- mdlWorkerOut$Att$IccPercNull <- -->
-<!--   ((as.numeric(mdlWorkerOut$Att$varNull[1]) / (as.numeric(mdlWorkerOut$Att$varNull[1]) + as.numeric(mdlWorkerOut$Att$varNull[2])))) * 100 -->
-<!-- ``` -->
-
-<!-- ```{r workerOutModelMLQltNull, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlWorkerOut$Qlt$lmerNull <- -->
-<!--   lme4::lmer(quality_overall_1 ~ 1 + (1 | PID),  -->
-<!--              data = dtWorkerSupp$workerOutWithinBetween) # use optim if it does not converge -->
-
-<!-- mdlWorkerOut$Qlt$lmeNull <- -->
-<!--   mdlWorkerOut$Qlt$lmeNull <- lme( -->
-<!--     quality_overall_1 ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtWorkerSupp$workerOutWithinBetween, -->
-<!--     na.action=na.omit, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(Null.Out.Qual.ML.r) #or with the lme function -->
-<!-- summ(mdlWorkerOut$Qlt$lmerNull, digits = 3) -->
-
-<!-- # Save variances -->
-<!-- mdlWorkerOut$Qlt$varNull <-  -->
-<!--   VarCorr(mdlWorkerOut$Qlt$lmeNull) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlWorkerOut$Qlt$tauNull <-  -->
-<!--   as.numeric(mdlWorkerOut$Qlt$varNull[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlWorkerOut$Qlt$sigmaNull <-  -->
-<!--   as.numeric(mdlWorkerOut$Qlt$varNull[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlWorkerOut$Qlt$IccNull <- -->
-<!--   (as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2]))) -->
-<!-- mdlWorkerOut$Qlt$IccPercNull <- -->
-<!--   ((as.numeric(mdlWorkerOut$Qlt$varNull[1]) / (as.numeric(mdlWorkerOut$Qlt$varNull[1]) + as.numeric(mdlWorkerOut$Qlt$varNull[2])))) * 100 -->
-<!-- ``` -->
-
-<!-- ```{r workerModelInterceptAttCoreInt, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlWorker$lmeInterceptAttCoreInt <- -->
-<!--   lme( -->
-<!--     thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction, -->
-<!--     random =  ~ 1 | PID, -->
-<!--     na.action=na.omit, -->
-<!--     data = dtWorkerSupp$workerWithinBetween -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- summ( -->
-<!--   mdlWorker$lmerInterceptAttCoreInt <- lmer( -->
-<!--     thermometerDutch_1 ~ keyMotiveFulfilled_cwc * OutgroupInteraction + (1 | PID), -->
-<!--     data = dtWorkerSupp$workerWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # 95%CI -->
-<!-- mdlWorker$lmerInterceptAttCoreIntCI <-  -->
-<!--   confint(method = "Wald", mdlWorker$lmerInterceptAttCoreInt) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlWorker$lmeAttNull,  -->
-<!--       mdlWorker$lmeInterceptAttCoreInt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   add_rownames(., var = "Description") %>% -->
-<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Worker: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = c("l", rep("c", ncol(.)-1)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # Save variances -->
-<!-- mdlWorker$varInterceptAttCoreInt <-  -->
-<!--   lme4::VarCorr(mdlWorker$lmeInterceptAttCoreInt) -->
-<!-- ``` -->
-<!-- ```{r workerModelSlopesAttCoreIntX, include=FALSE} -->
-<!-- # Create and save Model (optimizer needed to reach convergence) -->
-<!-- mdlWorker$lmeSlopesAttCoreInt <- lme( -->
-<!--   thermometerDutch_1 ~ -->
-<!--     keyMotiveFulfilled_cwc * OutgroupInteraction, -->
-<!--   random = ~ 1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID, -->
-<!--   control = lmeControl(opt = "optim"), -->
-<!--   na.action=na.omit, -->
-<!--   data = dtWorkerSupp$workerWithinBetween -->
-<!-- ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
-<!-- summ( -->
-<!--   mdlWorker$lmerSlopesAttCoreInt <- lmer( -->
-<!--     thermometerDutch_1 ~ -->
-<!--       keyMotiveFulfilled_cwc * OutgroupInteraction + -->
-<!--       (1 + keyMotiveFulfilled_cwc + OutgroupInteraction | PID), -->
-<!--     data = dtWorkerSupp$workerWithinBetween -->
-<!--   ),  -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # 95%CI -->
-<!-- mdlWorker$lmerSlopesAttCoreIntCI <-  -->
-<!--   confint(method = "Wald", mdlWorker$lmerSlopesAttCoreInt) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlWorker$lmeAttNull,  -->
-<!--       mdlWorker$lmeInterceptAttCoreInt, -->
-<!--       mdlWorker$lmeSlopesAttCoreInt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   add_rownames(., var = "Description") %>% -->
-<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Worker: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # Save variances -->
-<!-- mdlWorker$varSlopesAttCoreInt <-  -->
-<!--   lme4::VarCorr(mdlWorker$lmeSlopesAttCoreInt) -->
-
-<!-- # Assumption Checks: -->
-<!-- mdlWorker$diagSlopesAttCoreInt <- -->
-<!--   sjPlot::plot_model(mdlWorker$lmerSlopesAttCoreInt, type = "diag") -->
-<!-- grid.arrange( -->
-<!--   mdlWorker$diagSlopesAttCoreInt[[1]], -->
-<!--   mdlWorker$diagSlopesAttCoreInt[[2]]$`PID`, -->
-<!--   mdlWorker$diagSlopesAttCoreInt[[3]], -->
-<!--   mdlWorker$diagSlopesAttCoreInt[[4]] -->
-<!-- ) -->
-
-<!-- # Plot prediction model -->
-<!-- mdlWorker$predSlopesAttCoreInt <-  -->
-<!--   dtWorkerSupp$workerWithinBetween %>% -->
-<!--   select(thermometerDutch_1, session, PID) %>%  -->
-<!--   mutate(measure = predict(mdlWorker$lmeSlopesAttCoreInt, -->
-<!--                            dtWorkerSupp$workerWithinBetween, -->
-<!--                            re.form = NA -->
-<!--                            ) -->
-<!--          ) -->
-
-<!-- ( -->
-<!--   mdlWorker$predPltSlopesAttCoreInt <- -->
-<!--     ggplot(data = mdlWorker$predSlopesAttCoreInt, aes(x = session, y = measure)) + -->
-<!--     geom_line(alpha = 1, color = "blue") + -->
-<!--     geom_line(aes(y = thermometerDutch_1), alpha = 1) + -->
-<!--     facet_wrap(~ PID, ncol = 6) + -->
-<!--     xlab("Time") + -->
-<!--     ylab("Outgroup Attitudes") + -->
-<!--     theme_Publication() -->
-<!-- ) -->
-<!-- ggsave( -->
-<!--   filename = "Figures/Worker_PredictionPlot_SlopesAttCoreInt.png", -->
-<!--   mdlWorker$predPltSlopesAttCoreInt, -->
-<!--   width = 18, -->
-<!--   height = 12, -->
-<!--   dpi = 800, -->
-<!--   units = "cm", -->
-<!--   device = "png" -->
-<!-- ) -->
-<!-- ``` -->
-
-<!-- ```{r workerOutModelInterceptAttCoreSdt, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlWorkerOut$Att$lmeInterceptCoreSdt <- -->
-<!--   lme( -->
-<!--     thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtWorkerSupp$workerOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- summ( -->
-<!--   mdlWorkerOut$Att$lmerInterceptCoreSdt <- lmer( -->
-<!--     thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID), -->
-<!--     data = dtWorkerSupp$workerOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # To be compared against a model with only the self-determination theory needs -->
-<!-- mdlWorkerOut$Att$lmeInterceptSdt <- -->
-<!--   lme( -->
-<!--     thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtWorkerSupp$workerOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- summ( -->
-<!--   mdlWorkerOut$Att$lmerInterceptSdt <- lmer( -->
-<!--     thermometerDutch_1 ~ competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + (1 | PID), -->
-<!--     data = dtWorkerSupp$workerOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # Compare new model to previous steps -->
-<!-- anova( -->
-<!--   mdlWorkerOut$Att$lmeInterceptSdt, -->
-<!--   mdlWorkerOut$Att$lmeInterceptCoreSdt -->
-<!--   ) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Worker: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-<!-- rm(lmeInterceptCoreRed) -->
-
-<!-- # Save variances -->
-<!-- mdlWorkerOut$Att$varInterceptCoreSdt <- -->
-<!--   lme4::VarCorr(mdlWorkerOut$Att$lmeInterceptCoreSdt) -->
-<!-- ``` -->
-<!-- ```{r workerOutModelSlopesAttCoreSdt, include=FALSE} -->
-<!-- # Create and save Model (optimizer needed to reach convergence) -->
-<!-- mdlWorkerOut$Att$lmeSlopesCoreSdt <- -->
-<!--   lme( -->
-<!--     thermometerDutch_1 ~ -->
-<!--       keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc, -->
-<!--     random = ~ 1 + keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID, -->
-<!--     control = lmeControl(opt = "optim"), -->
-<!--     data = dtWorkerSupp$workerOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
-<!-- summ( -->
-<!--   mdlWorkerOut$Att$lmerSlopesCoreSdt <- lmer( -->
-<!--     thermometerDutch_1 ~ -->
-<!--       keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + -->
-<!--       (1 + keymotive_fulfillemt_1_cwc + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID), -->
-<!--     data = dtWorkerSupp$workerOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- mdlWorkerOut$Att$lmerSlopesCoreSdtCI <-  -->
-<!--   confint(method = "Wald", mdlWorkerOut$Att$lmerSlopesCoreSdt) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlWorkerOut$Att$lmeInterceptSdt, -->
-<!--       mdlWorkerOut$Att$lmeInterceptCoreSdt,  -->
-<!--       mdlWorkerOut$Att$lmeSlopesCoreSdt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Worker: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # model with SDT only -->
-<!-- # Create and save Model (optimizer needed to reach convergence) -->
-<!-- mdlWorkerOut$Att$lmeSlopesSdt <- -->
-<!--   lme( -->
-<!--     thermometerDutch_1 ~ -->
-<!--       competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc, -->
-<!--     random = ~ 1 + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID, -->
-<!--     control = lmeControl(opt = "optim"), -->
-<!--     data = dtWorkerSupp$workerOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
-<!-- summ( -->
-<!--   mdlWorkerOut$Att$lmerSlopesSdt <- lmer( -->
-<!--     thermometerDutch_1 ~ -->
-<!--       competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc + -->
-<!--       (1 + competence_1_cwc + autonomy_1_cwc + relatedness_1_cwc | PID), -->
-<!--     data = dtWorkerSupp$workerOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlWorkerOut$Att$lmeInterceptSdt, -->
-<!--       mdlWorkerOut$Att$lmeSlopesSdt,  -->
-<!--       mdlWorkerOut$Att$lmeSlopesCoreSdt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Worker: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # Save variances -->
-<!-- mdlWorkerOut$Att$varSlopesCoreSdt <-  -->
-<!--   lme4::VarCorr(mdlWorkerOut$Att$lmeSlopesCoreSdt) -->
-
-<!-- # Assumption Checks: -->
-<!-- mdlWorkerOut$Att$diagSlopesCoreSdt <-  -->
-<!--   sjPlot::plot_model(mdlWorkerOut$Att$lmerSlopesCoreSdt, type = "diag") -->
-<!-- grid.arrange( -->
-<!--   mdlWorkerOut$Att$diagSlopesCoreSdt[[1]], -->
-<!--   mdlWorkerOut$Att$diagSlopesCoreSdt[[2]]$`PID`, -->
-<!--   mdlWorkerOut$Att$diagSlopesCoreSdt[[3]], -->
-<!--   mdlWorkerOut$Att$diagSlopesCoreSdt[[4]] -->
-<!-- ) -->
-
-<!-- # Plot prediction model -->
-<!-- mdlWorkerOut$Att$predSlopesCoreSdt <-  -->
-<!--   dtWorkerSupp$workerOutWithinBetween %>% -->
-<!--   filter(!is.na(autonomy_1)) %>% -->
-<!--   select(thermometerDutch_1, session, PID, autonomy_1) %>%  -->
-<!--   mutate(measure = predict(mdlWorkerOut$Att$lmeSlopesCoreSdt, -->
-<!--                            dtWorkerSupp$workerOutWithinBetween %>% filter(!is.na(autonomy_1)), -->
-<!--                            re.form = NA -->
-<!--                            ) -->
-<!--          ) -->
-
-<!-- ( -->
-<!--   mdlWorkerOut$Att$predPltSlopesCoreSdt <- -->
-<!--     ggplot(data = mdlWorkerOut$Att$predSlopesCoreSdt, aes(x = session, y = measure)) + -->
-<!--     geom_line(alpha = 1, color = "blue") + -->
-<!--     geom_line(aes(y = thermometerDutch_1), alpha = 1) + -->
-<!--     facet_wrap( ~ PID, ncol = 6) + -->
-<!--     xlab("Time") + -->
-<!--     ylab("Outgroup Attitudes") + -->
-<!--     theme_Publication() -->
-<!-- ) -->
-<!-- ggsave( -->
-<!--   filename = "Figures/WorkerOut_PredictionPlot_SlopesAttCoreStd.png", -->
-<!--   mdlWorkerOut$Att$predPltSlopesCoreSdt, -->
-<!--   width = 18, -->
-<!--   height = 12, -->
-<!--   dpi = 800, -->
-<!--   units = "cm", -->
-<!--   device = "png" -->
-<!-- ) -->
-
-<!-- # Model comparison -->
-<!-- workerSdtComp <- -->
-<!--   anova( -->
-<!--     mdlWorkerOut$Att$lmerSlopesSdt,  -->
-<!--     mdlWorkerOut$Att$lmerSlopesCoreSdt -->
-<!--   ) %>% -->
-<!--   as.data.frame() -->
-<!-- workerSdtCompDf <- workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Df"] -->
-<!-- workerSdtCompN <- sapply(ranef(mdlWorkerOut$Att$lmerSlopesCoreSdt), nrow) -->
-<!-- workerSdtCompChi <- workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2) -->
-<!-- workerSdtCompP <- -->
-<!--   ifelse(workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001, -->
-<!--          "< .001", -->
-<!--          paste0("= ", workerSdtComp["mdlWorkerOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3))) -->
-
-<!-- workerSdtCompChiSq <- paste0("$\\chi^2$(", workerSdtCompDf, ", \\textit{N} = ", workerSdtCompN, ") = ", workerSdtCompChi, ", \\textit{p} ", workerSdtCompP) -->
-<!-- ``` -->
-
-<!-- In a final step, we controlled for other fundamental psychological needs during the contact.
-We focus on the three commonly considered self-determination needs (SDT): competence, autonomy, and relatedness.
-We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r workerSdtCompChiSq`).
-We also find that next to relatedness (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "relatedness_1_cwc")`), the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreSdt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreSdtCI, varName = "keymotive_fulfillemt_1_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all three fundamental needs (competence and autonomy needs turning non-significant; all \textit{b} < `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"Value"] %>% max %>% round(2) %>% format(nsmall=2)`, all \textit{p} > `r coef(summary(mdlWorkerOut$Att$lmeSlopesCoreSdt))[c("competence_1_cwc", "autonomy_1_cwc"),"p-value"] %>% min %>% round(3) %>% format(nsmall=3)`).
-For full results see see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and Online Supplementary Material A.
-There is, thus, considerable evidence lending confidence to the stability and relevance of psychological need fulfillment as a predictor of positive outgroup attitudes for natural intergroup contacts.
--->
-
-<!-- \hl{Intend ...} -->
-
-<!-- \hl{Goal-directedness ...} -->
-
-<!-- \hl{Well-being ...} -->
-
-<!-- \subsubsection{Study 2} -->
-
-<!-- ```{r studentSampleInfo, include=FALSE} -->
-<!-- # summarize participant characteristics -->
-<!-- studentSampleInfo <-  -->
-<!--   dtStudents$full %>% -->
-<!--   mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>% -->
-<!--   group_by(PID) %>% -->
-<!--   summarise( -->
-<!--     dailiesN = n(),  -->
-<!--     morningN = sum(periodMA=="morning"), -->
-<!--     afternoonN = sum(periodMA=="afternoon"), -->
-<!--     age = age, -->
-<!--     gender = gender, -->
-<!--     nationality = nationality -->
-<!--   ) %>% -->
-<!--   distinct -->
-
-<!-- # look at frequencies of characteristics  -->
-<!-- table(studentSampleInfo$gender) -->
-<!-- table(as.character(studentSampleInfo$nationality)) -->
-
-<!-- # divide into trait and state -->
-<!-- dtStudentSupp$studentWithinBetween <- -->
-<!--   MlTraitState( -->
-<!--     data = dtStudentSupp$studentInteractionType, -->
-<!--     id = "PID", -->
-<!--     selection = -->
-<!--       c( -->
-<!--         "KeyNeedFullfillment", -->
-<!--         "Competence", -->
-<!--         "Autonomy", -->
-<!--         "Relatedness", -->
-<!--         "AttitudesDutch", -->
-<!--         "quality_overall", -->
-<!--         "OutgroupInteraction", -->
-<!--         "NonOutgroupInteraction", -->
-<!--         "OutgroupInteractionM", -->
-<!--         "NonOutgroupInteractionM" -->
-<!--       ) -->
-<!--   ) -->
-<!-- dtStudentSupp$studentOutWithinBetween <- -->
-<!--   MlTraitState( -->
-<!--     data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"), -->
-<!--     id = "PID", -->
-<!--     selection = -->
-<!--       c( -->
-<!--         "KeyNeedFullfillment", -->
-<!--         "Competence", -->
-<!--         "Autonomy", -->
-<!--         "Relatedness", -->
-<!--         "AttitudesDutch", -->
-<!--         "quality_overall" -->
-<!--       ) -->
-<!--   ) -->
-<!-- ``` -->
-
-<!-- ```{r studentModelOlsAttFreqQual, include=FALSE} -->
-<!-- # create list to store Worker models -->
-<!-- mdlStudent <- list() -->
-<!-- ``` -->
-
-<!-- ```{r studentModelMLAttNull, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlStudent$lmerAttNull <- -->
-<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
-<!--     data = dtStudents$full -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- mdlStudent$lmeAttNull <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtStudents$full, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(mdlStudent$lmerAttNull) #or with the lme function -->
-<!-- summ(mdlStudent$lmerAttNull, digits = 3) -->
-
-<!-- # Save variances -->
-<!-- mdlStudent$varAttNull <-  -->
-<!--   VarCorr(mdlStudent$lmeAttNull) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlStudent$tauAttNull <-  -->
-<!--   as.numeric(mdlStudent$varAttNull[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlStudent$sigmaAttNull <-  -->
-<!--   as.numeric(mdlStudent$varAttNull[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlStudent$IccAttNull <- -->
-<!--   (as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2]))) -->
-<!-- mdlStudent$IccPercAttNull <- -->
-<!--   ((as.numeric(mdlStudent$varAttNull[1]) / (as.numeric(mdlStudent$varAttNull[1]) + as.numeric(mdlStudent$varAttNull[2])))) * 100 -->
-<!-- ``` -->
-
-<!-- ```{r studentOutModelMLAttNull, include=FALSE} -->
-<!-- # create empty list to organize models -->
-<!-- mdlStudentOut <-  -->
-<!--   list( -->
-<!--     Att = list(), -->
-<!--     Qlt = list() -->
-<!--   ) -->
-
-<!-- # Create and save Model -->
-<!-- mdlStudentOut$Att$lmerNull <- -->
-<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID),  -->
-<!--              data = dtStudentSupp$studentOutgroupInteraction) # use optim if it does not converge -->
-<!-- mdlStudentOut$Att$lmeNull <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtStudentSupp$studentOutgroupInteraction, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(Null.Out.ML.r) #or with the lme function -->
-<!-- summ(mdlStudentOut$Att$lmerNull, digits = 3, center = TRUE) -->
-
-<!-- # Save variances -->
-<!-- mdlStudentOut$Att$varNull <-  -->
-<!--   VarCorr(mdlStudentOut$Att$lmeNull) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlStudentOut$Att$tauNull <-  -->
-<!--   as.numeric(mdlStudentOut$Att$varNull[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlStudentOut$Att$sigmaNull <-  -->
-<!--   as.numeric(mdlStudentOut$Att$varNull[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlStudentOut$Att$IccNull <- -->
-<!--   (as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2]))) -->
-<!-- mdlStudentOut$Att$IccPercNull <- -->
-<!--   ((as.numeric(mdlStudentOut$Att$varNull[1]) / (as.numeric(mdlStudentOut$Att$varNull[1]) + as.numeric(mdlStudentOut$Att$varNull[2])))) * 100 -->
-<!-- ``` -->
-
-<!-- ```{r studentOutModelMLQltNull, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlStudentOut$Qlt$lmerNull <- -->
-<!--   lme4::lmer(quality_overall ~ 1 + (1 | PID),  -->
-<!--              data = dtStudentSupp$studentOutWithinBetween) # use optim if it does not converge -->
-<!-- mdlStudentOut$Qlt$lmeNull <- -->
-<!--   mdlStudentOut$Qlt$lmeNull <-lme( -->
-<!--     quality_overall ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtStudentSupp$studentOutWithinBetween, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(Null.Out.Qual.ML.r) #or with the lme function -->
-<!-- summ(mdlStudentOut$Qlt$lmerNull, digits = 3) -->
-
-<!-- # Save variances -->
-<!-- mdlStudentOut$Qlt$varNull <-  -->
-<!--   VarCorr(mdlStudentOut$Qlt$lmeNull) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlStudentOut$Qlt$tauNull <-  -->
-<!--   as.numeric(mdlStudentOut$Qlt$varNull[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlStudentOut$Qlt$sigmaNull <-  -->
-<!--   as.numeric(mdlStudentOut$Qlt$varNull[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlStudentOut$Qlt$IccNull <- -->
-<!--   (as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2]))) -->
-<!-- mdlStudentOut$Qlt$IccPercNull <- -->
-<!--   ((as.numeric(mdlStudentOut$Qlt$varNull[1]) / (as.numeric(mdlStudentOut$Qlt$varNull[1]) + as.numeric(mdlStudentOut$Qlt$varNull[2])))) * 100 -->
-<!-- ``` -->
-
-<!-- ```{r studentModelInterceptAttCoreInt, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlStudent$lmeInterceptAttCoreInt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction, -->
-<!--     random =  ~ 1 | PID, -->
-<!--     data = dtStudentSupp$studentWithinBetween -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- summ( -->
-<!--   mdlStudent$lmerInterceptAttCoreInt <- lmer( -->
-<!--     AttitudesDutch ~ KeyNeedFullfillment_cwc * OutgroupInteraction + (1 | PID), -->
-<!--     data = dtStudentSupp$studentWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # 95%CI -->
-<!-- mdlStudent$lmerInterceptAttCoreIntCI <-  -->
-<!--   confint(method = "Wald", mdlStudent$lmerInterceptAttCoreInt) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlStudent$lmeAttNull,  -->
-<!--       mdlStudent$lmeInterceptAttCoreInt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   add_rownames(., var = "Description") %>% -->
-<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Student: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = c("l", rep("c", ncol(.)-1)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # Save variances -->
-<!-- mdlStudent$varInterceptAttCoreInt <-  -->
-<!--   lme4::VarCorr(mdlStudent$lmeInterceptAttCoreInt) -->
-<!-- ``` -->
-<!-- ```{r studentModelSlopesAttCoreIntX, include=FALSE} -->
-<!-- # Create and save Model (optimizer needed to reach convergence) -->
-<!-- mdlStudent$lmeSlopesAttCoreInt <- lme( -->
-<!--   AttitudesDutch ~ -->
-<!--     KeyNeedFullfillment_cwc * OutgroupInteraction, -->
-<!--   random = ~ 1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID, -->
-<!--   control = lmeControl(opt = "optim"), -->
-<!--   data = dtStudentSupp$studentWithinBetween -->
-<!-- ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
-<!-- summ( -->
-<!--   mdlStudent$lmerSlopesAttCoreInt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       KeyNeedFullfillment_cwc * OutgroupInteraction + -->
-<!--       (1 + KeyNeedFullfillment_cwc + OutgroupInteraction | PID), -->
-<!--     data = dtStudentSupp$studentWithinBetween -->
-<!--   ),  -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # 95%CI -->
-<!-- mdlStudent$lmerSlopesAttCoreIntCI <-  -->
-<!--   confint(method = "Wald", mdlStudent$lmerSlopesAttCoreInt) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlStudent$lmeAttNull,  -->
-<!--       mdlStudent$lmeInterceptAttCoreInt, -->
-<!--       mdlStudent$lmeSlopesAttCoreInt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   add_rownames(., var = "Description") %>% -->
-<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Student: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # Save variances -->
-<!-- mdlStudent$varSlopesAttCoreInt <-  -->
-<!--   lme4::VarCorr(mdlStudent$lmeSlopesAttCoreInt) -->
-
-<!-- # Assumption Checks: -->
-<!-- mdlStudent$diagSlopesAttCoreInt <- -->
-<!--   sjPlot::plot_model(mdlStudent$lmerSlopesAttCoreInt, type = "diag") -->
-<!-- grid.arrange( -->
-<!--   mdlStudent$diagSlopesAttCoreInt[[1]], -->
-<!--   mdlStudent$diagSlopesAttCoreInt[[2]]$`PID`, -->
-<!--   mdlStudent$diagSlopesAttCoreInt[[3]], -->
-<!--   mdlStudent$diagSlopesAttCoreInt[[4]] -->
-<!-- ) -->
-
-<!-- # Plot prediction model -->
-<!-- mdlStudent$predSlopesAttCoreInt <-  -->
-<!--   dtStudentSupp$studentWithinBetween %>% -->
-<!--   filter(PID %in% dtStudentSupp$studentPltIDs) %>% -->
-<!--   select(AttitudesDutch, TIDnum, PID) %>%  -->
-<!--   mutate(measure = predict(mdlStudent$lmeSlopesAttCoreInt, -->
-<!--                            dtStudentSupp$studentWithinBetween %>% filter(PID %in% dtStudentSupp$studentPltIDs), -->
-<!--                            re.form = NA -->
-<!--                            ) -->
-<!--          ) -->
-
-<!-- ( -->
-<!--   mdlStudent$predPltSlopesAttCoreInt <- -->
-<!--     ggplot(data = mdlStudent$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) + -->
-<!--     geom_line(alpha = 1, color = "blue") + -->
-<!--     geom_line(aes(y = AttitudesDutch), alpha = 1) + -->
-<!--     facet_wrap(~ PID, ncol = 6) + -->
-<!--     xlab("Time") + -->
-<!--     ylab("Outgroup Attitudes") + -->
-<!--     theme_Publication() -->
-<!-- ) -->
-<!-- ggsave( -->
-<!--   filename = "Figures/Student_PredictionPlot_SlopesAttCoreInt.png", -->
-<!--   mdlStudent$predPltSlopesAttCoreInt, -->
-<!--   width = 18, -->
-<!--   height = 12, -->
-<!--   dpi = 800, -->
-<!--   units = "cm", -->
-<!--   device = "png" -->
-<!-- ) -->
-<!-- ``` -->
-
-<!-- Also for Study 2, we checked for alternative models.
-First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is only a minuscule main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "KeyNeedFullfillment_cwc:OutgroupInteraction")`).
-Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttCoreInt, lmerCI = mdlStudent$lmerSlopesAttCoreIntCI, varName = "OutgroupInteraction")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous study, albeit with a slightly weaker effect (likely because of the large number of measurements that did not include an outgroup interaction; For full results see \tblref{tab:robustnessTblLong} and for visual comparison see \fgrref{fig:Robustness}).
--->
-
-<!-- ```{r studentOutModelInterceptAttCoreSdt, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlStudentOut$Att$lmeInterceptCoreSdt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtStudentSupp$studentOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- summ( -->
-<!--   mdlStudentOut$Att$lmerInterceptCoreSdt <- lmer( -->
-<!--     AttitudesDutch ~ KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID), -->
-<!--     data = dtStudentSupp$studentOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # 95%CI -->
-<!-- mdlStudentOut$Att$lmerInterceptCoreSdtCI <-  -->
-<!--   confint(method = "Wald", mdlStudentOut$Att$lmerInterceptCoreSdt) -->
-
-<!-- # To be compared against a model with only the self-determination theory needs -->
-<!-- mdlStudentOut$Att$lmeInterceptSdt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtStudentSupp$studentOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- summ( -->
-<!--   mdlStudentOut$Att$lmerInterceptSdt <- lmer( -->
-<!--     AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID), -->
-<!--     data = dtStudentSupp$studentOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # Compare new model to previous steps -->
-<!-- anova( -->
-<!--   mdlStudentOut$Att$lmeNull, -->
-<!--   mdlStudentOut$Att$lmeInterceptSdt, -->
-<!--   mdlStudentOut$Att$lmeInterceptCoreSdt -->
-<!--   ) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Student: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-<!-- rm(lmeInterceptCoreRed) -->
-
-<!-- # Save variances -->
-<!-- mdlStudentOut$Att$varInterceptCoreSdt <- -->
-<!--   lme4::VarCorr(mdlStudentOut$Att$lmeInterceptCoreSdt) -->
-<!-- ``` -->
-<!-- ```{r studentOutModelSlopesAttCoreSdt, include=FALSE} -->
-<!-- # Create and save Model (optimizer needed to reach convergence) -->
-<!-- mdlStudentOut$Att$lmeSlopesCoreSdt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ -->
-<!--       KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
-<!--     random = ~ 1 + KeyNeedFullfillment_cwc + Competence_cwc + Relatedness_cwc | PID, -->
-<!--     control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100), -->
-<!--     data = dtStudentSupp$studentOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
-<!-- summ( -->
-<!--   mdlStudentOut$Att$lmerSlopesCoreSdt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
-<!--       (1 + KeyNeedFullfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
-<!--     data = dtStudentSupp$studentOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # 95%CI -->
-<!-- mdlStudentOut$Att$lmerSlopesCoreSdtCI <-  -->
-<!--   confint(method = "Wald", mdlStudentOut$Att$lmerSlopesCoreSdt) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlStudentOut$Att$lmeInterceptSdt, -->
-<!--       mdlStudentOut$Att$lmeInterceptCoreSdt,  -->
-<!--       mdlStudentOut$Att$lmeSlopesCoreSdt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Student: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # model with SDT only -->
-<!-- # Create and save Model (optimizer needed to reach convergence) -->
-<!-- mdlStudentOut$Att$lmeSlopesSdt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ -->
-<!--       Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
-<!--     random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID, -->
-<!--     control = lmeControl(opt = "optim"), -->
-<!--     data = dtStudentSupp$studentOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
-<!-- summ( -->
-<!--   mdlStudentOut$Att$lmerSlopesSdt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
-<!--       (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
-<!--     data = dtStudentSupp$studentOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlStudentOut$Att$lmeInterceptSdt, -->
-<!--       mdlStudentOut$Att$lmeSlopesSdt,  -->
-<!--       mdlStudentOut$Att$lmeSlopesCoreSdt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Student: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # Save variances -->
-<!-- mdlStudentOut$Att$varSlopesCoreSdt <-  -->
-<!--   lme4::VarCorr(mdlStudentOut$Att$lmeSlopesCoreSdt) -->
-
-<!-- # Assumption Checks: -->
-<!-- mdlStudentOut$Att$diagSlopesCoreSdt <-  -->
-<!--   sjPlot::plot_model(mdlStudentOut$Att$lmerSlopesCoreSdt, type = "diag") -->
-<!-- grid.arrange( -->
-<!--   mdlStudentOut$Att$diagSlopesCoreSdt[[1]], -->
-<!--   mdlStudentOut$Att$diagSlopesCoreSdt[[2]]$`PID`, -->
-<!--   mdlStudentOut$Att$diagSlopesCoreSdt[[3]], -->
-<!--   mdlStudentOut$Att$diagSlopesCoreSdt[[4]] -->
-<!-- ) -->
-
-<!-- # Plot prediction model -->
-<!-- mdlStudentOut$Att$predSlopesCoreSdt <-  -->
-<!--   dtStudentSupp$studentOutWithinBetween %>% -->
-<!--   filter(PID %in% dtStudentSupp$studentOutPltIDs) %>% -->
-<!--   select(AttitudesDutch, TIDnum, PID, Autonomy) %>%  -->
-<!--   mutate(measure = predict(mdlStudentOut$Att$lmeSlopesCoreSdt, -->
-<!--                            dtStudentSupp$studentOutWithinBetween %>% filter(PID %in% dtStudentSupp$studentOutPltIDs), -->
-<!--                            re.form = NA -->
-<!--                            ) -->
-<!--          ) -->
-
-<!-- ( -->
-<!--   mdlStudentOut$Att$predPltSlopesCoreSdt <- -->
-<!--     ggplot(data = mdlStudentOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) + -->
-<!--     geom_line(alpha = 1, color = "blue") + -->
-<!--     geom_line(aes(y = AttitudesDutch), alpha = 1) + -->
-<!--     facet_wrap( ~ PID, ncol = 6) + -->
-<!--     xlab("Time") + -->
-<!--     ylab("Outgroup Attitudes") + -->
-<!--     theme_Publication() -->
-<!-- ) -->
-<!-- ggsave( -->
-<!--   filename = "Figures/StudentOut_PredictionPlot_SlopesAttCoreStd.png", -->
-<!--   mdlStudentOut$Att$predPltSlopesCoreSdt, -->
-<!--   width = 18, -->
-<!--   height = 12, -->
-<!--   dpi = 800, -->
-<!--   units = "cm", -->
-<!--   device = "png" -->
-<!-- ) -->
-
-<!-- # Model comparison -->
-<!-- studentSdtComp <- -->
-<!--   anova( -->
-<!--     mdlStudentOut$Att$lmerSlopesSdt,  -->
-<!--     mdlStudentOut$Att$lmerSlopesCoreSdt -->
-<!--   ) %>% -->
-<!--   as.data.frame() -->
-<!-- studentSdtCompDf <- studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Df"] -->
-<!-- studentSdtCompN <- sapply(ranef(mdlStudentOut$Att$lmerSlopesCoreSdt), nrow) -->
-<!-- studentSdtCompChi <- studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2) -->
-<!-- studentSdtCompP <- -->
-<!--   ifelse(studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001, -->
-<!--          "< .001", -->
-<!--          paste0("= ", studentSdtComp["mdlStudentOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3))) -->
-
-<!-- studentSdtCompChiSq <- paste0("$\\chi^2$(", studentSdtCompDf, ", \\textit{N} = ", studentSdtCompN, ") = ", studentSdtCompChi, ", \\textit{p} ", studentSdtCompP) -->
-<!-- ``` -->
-
-<!-- In a final step, we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
-We find that the core need fulfillment adds significantly above a model with only the self-determination theory needs (random slopes models; `r studentSdtCompChiSq`).
-We find that the core need fulfillment explained the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFullfillment_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, different from the first study, relatedness (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreSdt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) also predicted positive outgroup attitudes in this larger sample.
-For full results see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and Online Supplementary Material A.
-This means that also within this second sample, the fulfillment of psychological needs during intergroup contact remained a key predictor of positive outgroup attitudes, even when taking into account several alternative models.
--->
-
-<!-- \hl{Intend ...} -->
-
-<!-- \hl{Goal-directedness ...} -->
-
-<!-- \hl{Well-being ...} -->
-
-<!-- \subsubsection{Study 3} -->
-
-<!-- ```{r medicalSampleInfo, include=FALSE} -->
-<!-- # extract demographic information from eligibility questionnaire -->
-<!-- medicalDemographicSupp <-  -->
-<!--   dtMedical$raw.eligibility %>% -->
-<!--   filter(session %in% dtMedical$full$session) %>% -->
-<!--   select(session, nationality, studentBachMa) -->
-<!-- # summarize participant characteristics -->
-
-<!-- medicalSampleInfo <- -->
-<!--   merge(dtMedical$full, medicalDemographicSupp, by = "session") %>% -->
-<!--   mutate(gender = as.factor(ifelse(.$Gender == 1, "women", ifelse(.$Gender == 2, "man", ifelse(.$Gender == 3, "other", NA))))) %>% -->
-<!--   group_by(PID) %>% -->
-<!--   summarise( -->
-<!--     dailiesN = n(),  -->
-<!--     morningN = sum(periodMA=="morning"), -->
-<!--     afternoonN = sum(periodMA=="afternoon"), -->
-<!--     age = age, -->
-<!--     gender = gender, -->
-<!--     nationality = nationality -->
-<!--   ) %>% -->
-<!--   distinct -->
-
-<!-- # divide into trait and state -->
-<!-- dtMedicalSupp$medicalWithinBetween <-  -->
-<!--   MlTraitState( -->
-<!--     data = dtMedical$full, -->
-<!--     id = "PID", -->
-<!--     selection = -->
-<!--       c( -->
-<!--         "OutgroupInteraction", -->
-<!--         "NonOutgroupInteraction", -->
-<!--         "OutgroupInteractionM", -->
-<!--         "NonOutgroupInteractionM" -->
-<!--       ) -->
-<!--   ) -->
-
-<!-- ``` -->
-
-<!-- ```{r medicalModelOlsAttFreqQual, include=FALSE} -->
-<!-- # create list to store Worker models -->
-<!-- mdlMedical <- list() -->
-<!-- ``` -->
-
-<!-- ```{r medicalModelMLAttNull, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlMedical$lmerAttNullType <- -->
-<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
-<!--              data = dtMedical$full %>% -->
-<!--                filter(complete.cases( -->
-<!--                  OutgroupInteraction, NonOutgroupInteraction -->
-<!--                ))) # use optim if it does not converge -->
-
-<!-- mdlMedical$lmeAttNullType <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtMedical$full %>% -->
-<!--       filter(complete.cases( -->
-<!--         OutgroupInteraction, NonOutgroupInteraction -->
-<!--       )), -->
-<!--     na.action = na.omit, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(mdlMedical$lmerAttNull) #or with the lme function -->
-<!-- summ(mdlMedical$lmerAttNullType, digits = 3) -->
-
-<!-- # Save variances -->
-<!-- mdlMedical$varAttNullType <-  -->
-<!--   VarCorr(mdlMedical$lmeAttNullType) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlMedical$tauAttNullType <-  -->
-<!--   as.numeric(mdlMedical$varAttNullType[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlMedical$sigmaAttNullType <-  -->
-<!--   as.numeric(mdlMedical$varAttNullType[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlMedical$IccAttNullType <- -->
-<!--   (as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2]))) -->
-<!-- mdlMedical$IccPercAttNull <- -->
-<!--   ((as.numeric(mdlMedical$varAttNullType[1]) / (as.numeric(mdlMedical$varAttNullType[1]) + as.numeric(mdlMedical$varAttNullType[2])))) * 100 -->
-<!-- ``` -->
-
-<!-- ```{r medicalOutModelMLAttNull, include=FALSE} -->
-<!-- # create empty list to organize models -->
-<!-- mdlMedicalOut <-  -->
-<!--   list( -->
-<!--     Att = list(), -->
-<!--     Qlt = list() -->
-<!--   ) -->
-
-<!-- # Create and save Model -->
-<!-- mdlMedicalOut$Att$lmerNull <- -->
-<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
-<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
-<!-- mdlMedicalOut$Att$lmeNull <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
-<!--     na.action = na.omit, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(Null.Out.ML.r) #or with the lme function -->
-<!-- summ(mdlMedicalOut$Att$lmerNull, digits = 3, center = TRUE) -->
-
-<!-- # Save variances -->
-<!-- mdlMedicalOut$Att$varNull <-  -->
-<!--   VarCorr(mdlMedicalOut$Att$lmeNull) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlMedicalOut$Att$tauNull <-  -->
-<!--   as.numeric(mdlMedicalOut$Att$varNull[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlMedicalOut$Att$sigmaNull <-  -->
-<!--   as.numeric(mdlMedicalOut$Att$varNull[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlMedicalOut$Att$IccNull <- -->
-<!--   (as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2]))) -->
-<!-- mdlMedicalOut$Att$IccPercNull <- -->
-<!--   ((as.numeric(mdlMedicalOut$Att$varNull[1]) / (as.numeric(mdlMedicalOut$Att$varNull[1]) + as.numeric(mdlMedicalOut$Att$varNull[2])))) * 100 -->
-<!-- ``` -->
-
-<!-- ```{r medicalOutModelMLQltNull, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlMedicalOut$Qlt$lmerNull <- -->
-<!--   lme4::lmer(qualityOverall ~ 1 + (1 | PID),  -->
-<!--              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge -->
-<!-- mdlMedicalOut$Qlt$lmeNull <- -->
-<!--   mdlMedicalOut$Qlt$lmeNull <-lme( -->
-<!--     qualityOverall ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     na.action = na.omit, -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(Null.Out.Qual.ML.r) #or with the lme function -->
-<!-- summ(mdlMedicalOut$Qlt$lmerNull, digits = 3) -->
-
-<!-- # Save variances -->
-<!-- mdlMedicalOut$Qlt$varNull <-  -->
-<!--   VarCorr(mdlMedicalOut$Qlt$lmeNull) # save variances -->
-<!-- # The estimate of (between-group or Intercept variance, tau_{00}^2): -->
-<!-- mdlMedicalOut$Qlt$tauNull <-  -->
-<!--   as.numeric(mdlMedicalOut$Qlt$varNull[1]) -->
-<!-- # and the estimate of (within-group or residual variance, sigma^2) is: -->
-<!-- mdlMedicalOut$Qlt$sigmaNull <-  -->
-<!--   as.numeric(mdlMedicalOut$Qlt$varNull[2]) -->
-<!-- # The ICC estimate (between/between+within) is: -->
-<!-- mdlMedicalOut$Qlt$IccNull <- -->
-<!--   (as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2]))) -->
-<!-- mdlMedicalOut$Qlt$IccPercNull <- -->
-<!--   ((as.numeric(mdlMedicalOut$Qlt$varNull[1]) / (as.numeric(mdlMedicalOut$Qlt$varNull[1]) + as.numeric(mdlMedicalOut$Qlt$varNull[2])))) * 100 -->
-<!-- ``` -->
-
-<!-- ```{r medicalModelAttNullInt, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlMedical$lmerAttNullInt <- -->
-<!--   lme4::lmer(AttitudesDutch ~ 1 + (1 | PID), -->
-<!--              data = dtMedical$full %>% -->
-<!--                filter(complete.cases( -->
-<!--                  OutgroupInteraction -->
-<!--                ))) # use optim if it does not converge -->
-
-<!-- mdlMedical$lmeAttNullInt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ 1, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtMedical$full %>% -->
-<!--       filter(complete.cases( -->
-<!--         OutgroupInteraction -->
-<!--       )), -->
-<!--     na.action = na.omit, -->
-<!--     control = list(opt = "nlmimb") -->
-<!--   ) # use optim if it does not converge -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- # summary(mdlMedical$lmerAttNull) #or with the lme function -->
-<!-- summ(mdlMedical$lmerAttNullInt, digits = 3) -->
-<!-- ``` -->
-
-<!-- ```{r medicalModelInterceptAttCoreInt, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlMedical$lmeInterceptAttCoreInt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction, -->
-<!--     random =  ~ 1 | PID, -->
-<!--     na.action = na.omit, -->
-<!--     data = dtMedical$full -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- summ( -->
-<!--   mdlMedical$lmerInterceptAttCoreInt <- lmer( -->
-<!--     AttitudesDutch ~ KeyNeedFulfillment_cwc * OutgroupInteraction + (1 | PID), -->
-<!--     data = dtMedical$full -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- mdlMedical$lmerInterceptAttCoreIntCI <-  -->
-<!--   confint(method = "Wald", mdlMedical$lmerInterceptAttCoreInt) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlMedical$lmeAttNullInt,  -->
-<!--       mdlMedical$lmeInterceptAttCoreInt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   add_rownames(., var = "Description") %>% -->
-<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Medical: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = c("l", rep("c", ncol(.)-1)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # Save variances -->
-<!-- mdlMedical$varInterceptAttCoreInt <-  -->
-<!--   lme4::VarCorr(mdlMedical$lmeInterceptAttCoreInt) -->
-<!-- ``` -->
-
-<!-- ```{r medicalModelSlopesAttCoreIntX, include=FALSE} -->
-<!-- # Create and save Model (optimizer needed to reach convergence) -->
-<!-- mdlMedical$lmeSlopesAttCoreInt <- lme( -->
-<!--   AttitudesDutch ~ -->
-<!--     KeyNeedFulfillment_cwc * OutgroupInteraction, -->
-<!--   random = ~ 1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID, -->
-<!--   control = lmeControl(opt = "optim"), -->
-<!--   na.action = na.omit, -->
-<!--   data = dtMedical$full -->
-<!-- ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
-<!-- summ( -->
-<!--   mdlMedical$lmerSlopesAttCoreInt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       KeyNeedFulfillment_cwc * OutgroupInteraction + -->
-<!--       (1 + KeyNeedFulfillment_cwc + OutgroupInteraction | PID), -->
-<!--     data = dtMedical$full -->
-<!--   ),  -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- mdlMedical$lmerSlopesAttCoreIntCI <-  -->
-<!--   confint(method = "Wald", mdlMedical$lmerSlopesAttCoreInt) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlMedical$lmeAttNullInt,  -->
-<!--       mdlMedical$lmeInterceptAttCoreInt, -->
-<!--       mdlMedical$lmeSlopesAttCoreInt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   add_rownames(., var = "Description") %>% -->
-<!--   mutate(Description = gsub(".*\\$", "", Description)) %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Medical: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # Save variances -->
-<!-- mdlMedical$varSlopesAttCoreInt <-  -->
-<!--   lme4::VarCorr(mdlMedical$lmeSlopesAttCoreInt) -->
-
-<!-- # Assumption Checks: -->
-<!-- mdlMedical$diagSlopesAttCoreInt <- -->
-<!--   sjPlot::plot_model(mdlMedical$lmerSlopesAttCoreInt, type = "diag") -->
-<!-- grid.arrange( -->
-<!--   mdlMedical$diagSlopesAttCoreInt[[1]], -->
-<!--   mdlMedical$diagSlopesAttCoreInt[[2]]$`PID`, -->
-<!--   mdlMedical$diagSlopesAttCoreInt[[3]], -->
-<!--   mdlMedical$diagSlopesAttCoreInt[[4]] -->
-<!-- ) -->
-
-<!-- # Plot prediction model -->
-<!-- mdlMedical$predSlopesAttCoreInt <-  -->
-<!--   dtMedical$full %>% -->
-<!--   filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>% -->
-<!--   filter(PID %in% dtMedicalSupp$medicalPltIDs) %>% -->
-<!--   select(AttitudesDutch, TIDnum, PID) %>%  -->
-<!--   mutate(measure = predict(mdlMedical$lmeSlopesAttCoreInt, -->
-<!--                            dtMedical$full %>%  -->
-<!--                              filter(complete.cases(KeyNeedFulfillment, OutgroupInteraction)) %>% -->
-<!--                              filter(PID %in% dtMedicalSupp$medicalPltIDs), -->
-<!--                            re.form = NA -->
-<!--                            ) -->
-<!--          ) -->
-
-<!-- ( -->
-<!--   mdlMedical$predPltSlopesAttCoreInt <- -->
-<!--     ggplot(data = mdlMedical$predSlopesAttCoreInt, aes(x = TIDnum, y = measure)) + -->
-<!--     geom_line(alpha = 1, color = "blue") + -->
-<!--     geom_line(aes(y = AttitudesDutch), alpha = 1) + -->
-<!--     facet_wrap(~ PID, ncol = 6) + -->
-<!--     xlab("Time") + -->
-<!--     ylab("Outgroup Attitudes") + -->
-<!--     theme_Publication() -->
-<!-- ) -->
-<!-- ggsave( -->
-<!--   filename = "Figures/Medical_PredictionPlot_SlopesAttCoreInt.png", -->
-<!--   mdlMedical$predPltSlopesAttCoreInt, -->
-<!--   width = 18, -->
-<!--   height = 12, -->
-<!--   dpi = 800, -->
-<!--   units = "cm", -->
-<!--   device = "png" -->
-<!-- ) -->
-<!-- ``` -->
-
-<!-- As with the previous two studies, we checked for alternative models of the key need fulfillment.
-First, when considering generalized situational core need fulfillment together with whether an intergroup contact took place, we find that there is no significant main effect of core need fulfillment (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc")`) but a stronger interaction effect of core need fulfillment and outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "KeyNeedFulfillment_cwc:OutgroupInteractionYes")`).
-Together with a significant main effect of having an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttCoreInt, lmerCI = mdlMedical$lmerSlopesAttCoreIntCI, varName = "OutgroupInteractionYes")`), this indicates that it is not key need fulfillment in general --- but key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
-This finding is consistent with the results of the previous studies.
--->
-
-<!-- ```{r medicalOutModelInterceptAttCoreSdt, include=FALSE} -->
-<!-- # Create and save Model -->
-<!-- mdlMedicalOut$Att$lmeInterceptCoreSdt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) -->
-<!-- summ( -->
-<!--   mdlMedicalOut$Att$lmerInterceptCoreSdt <- lmer( -->
-<!--     AttitudesDutch ~ KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID), -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # To be compared against a model with only the self-determination theory needs -->
-<!-- mdlMedicalOut$Att$lmeInterceptSdt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
-<!--     random = ~ 1 | PID, -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- summ( -->
-<!--   mdlMedicalOut$Att$lmerInterceptSdt <- lmer( -->
-<!--     AttitudesDutch ~ Competence_cwc + Autonomy_cwc + Relatedness_cwc + (1 | PID), -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # Compare new model to previous steps -->
-<!-- anova( -->
-<!--   mdlMedicalOut$Att$lmeInterceptSdt, -->
-<!--   mdlMedicalOut$Att$lmeInterceptCoreSdt -->
-<!--   ) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Medical: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # Save variances -->
-<!-- mdlMedicalOut$Att$varInterceptCoreSdt <- -->
-<!--   lme4::VarCorr(mdlMedicalOut$Att$lmeInterceptCoreSdt) -->
-<!-- ``` -->
-
-<!-- ```{r medicalOutModelSlopesAttCoreSdt, include=FALSE} -->
-<!-- # Create and save Model (optimizer needed to reach convergence) -->
-<!-- mdlMedicalOut$Att$lmeSlopesCoreSdt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ -->
-<!--       KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
-<!--     random = ~ 1 + KeyNeedFulfillment_cwc + Competence_cwc + Relatedness_cwc | PID, -->
-<!--     control = lmeControl(opt = "optim", maxIter = 100, msMaxIter = 100), -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
-<!-- summ( -->
-<!--   mdlMedicalOut$Att$lmerSlopesCoreSdt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
-<!--       (1 + KeyNeedFulfillment_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- mdlMedicalOut$Att$lmerSlopesCoreSdtCI <-  -->
-<!--   confint(method = "Wald", mdlMedicalOut$Att$lmerSlopesCoreSdt) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlMedicalOut$Att$lmeInterceptSdt, -->
-<!--       mdlMedicalOut$Att$lmeInterceptCoreSdt,  -->
-<!--       mdlMedicalOut$Att$lmeSlopesCoreSdt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Medical: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # model with SDT only -->
-<!-- # Create and save Model (optimizer needed to reach convergence) -->
-<!-- mdlMedicalOut$Att$lmeSlopesSdt <- -->
-<!--   lme( -->
-<!--     AttitudesDutch ~ -->
-<!--       Competence_cwc + Autonomy_cwc + Relatedness_cwc, -->
-<!--     random = ~ 1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID, -->
-<!--     control = lmeControl(opt = "optim"), -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween, -->
-<!--     na.action = na.exclude -->
-<!--   ) -->
-
-<!-- # Get summary with p-values (Satterthwaite's method) [+ save model for plotting] -->
-<!-- summ( -->
-<!--   mdlMedicalOut$Att$lmerSlopesSdt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
-<!--       (1 + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
-<!--     data = dtMedicalSupp$medicalOutWithinBetween -->
-<!--   ), -->
-<!--   confint = TRUE, -->
-<!--   digits = 3 -->
-<!-- ) -->
-
-<!-- # Compare new model to previous step -->
-<!-- anova(mdlMedicalOut$Att$lmeInterceptSdt, -->
-<!--       mdlMedicalOut$Att$lmeSlopesSdt,  -->
-<!--       mdlMedicalOut$Att$lmeSlopesCoreSdt) %>% -->
-<!--   as.data.frame() %>% -->
-<!--   select(-call) %>% -->
-<!--   mutate( -->
-<!--     L.Ratio = round(L.Ratio, 3), -->
-<!--     `p-value` = ifelse(`p-value`>=.001, round(`p-value`, 3), "< .001") -->
-<!--   ) %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Medical: Model Comparison", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = rep("c", ncol(.)), -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_styling(position = "left") -->
-
-<!-- # Save variances -->
-<!-- mdlMedicalOut$Att$varSlopesCoreSdt <-  -->
-<!--   lme4::VarCorr(mdlMedicalOut$Att$lmeSlopesCoreSdt) -->
-
-<!-- # Assumption Checks: -->
-<!-- mdlMedicalOut$Att$diagSlopesCoreSdt <-  -->
-<!--   sjPlot::plot_model(mdlMedicalOut$Att$lmerSlopesCoreSdt, type = "diag") -->
-<!-- grid.arrange( -->
-<!--   mdlMedicalOut$Att$diagSlopesCoreSdt[[1]], -->
-<!--   mdlMedicalOut$Att$diagSlopesCoreSdt[[2]]$`PID`, -->
-<!--   mdlMedicalOut$Att$diagSlopesCoreSdt[[3]], -->
-<!--   mdlMedicalOut$Att$diagSlopesCoreSdt[[4]] -->
-<!-- ) -->
-
-<!-- # Plot prediction model -->
-<!-- mdlMedicalOut$Att$predSlopesCoreSdt <-  -->
-<!--   dtMedicalSupp$medicalOutWithinBetween %>% -->
-<!--   filter(complete.cases( -->
-<!--     KeyNeedFulfillment, -->
-<!--     Autonomy, Competence, Relatedness -->
-<!--     )) %>% -->
-<!--   filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>% -->
-<!--   select(AttitudesDutch, TIDnum, PID, Autonomy, Competence, Relatedness) %>%  -->
-<!--   mutate(measure = predict(mdlMedicalOut$Att$lmeSlopesCoreSdt, -->
-<!--                            dtMedicalSupp$medicalOutWithinBetween %>%  -->
-<!--                              filter(complete.cases( -->
-<!--                                KeyNeedFulfillment, -->
-<!--                                Autonomy, Competence, Relatedness -->
-<!--                              )) %>% -->
-<!--                              filter(PID %in% dtMedicalSupp$medicalOutPltIDs), -->
-<!--                            re.form = NA -->
-<!--                            ) -->
-<!--          ) -->
-
-<!-- ( -->
-<!--   mdlMedicalOut$Att$predPltSlopesCoreSdt <- -->
-<!--     ggplot(data = mdlMedicalOut$Att$predSlopesCoreSdt, aes(x = TIDnum, y = measure)) + -->
-<!--     geom_line(alpha = 1, color = "blue") + -->
-<!--     geom_line(aes(y = AttitudesDutch), alpha = 1) + -->
-<!--     facet_wrap( ~ PID, ncol = 6) + -->
-<!--     xlab("Time") + -->
-<!--     ylab("Outgroup Attitudes") + -->
-<!--     theme_Publication() -->
-<!-- ) -->
-<!-- ggsave( -->
-<!--   filename = "Figures/MedicalOut_PredictionPlot_SlopesAttCoreStd.png", -->
-<!--   mdlMedicalOut$Att$predPltSlopesCoreSdt, -->
-<!--   width = 18, -->
-<!--   height = 12, -->
-<!--   dpi = 800, -->
-<!--   units = "cm", -->
-<!--   device = "png" -->
-<!-- ) -->
-
-<!-- # Model comparison -->
-<!-- medicalSdtComp <- -->
-<!--   anova( -->
-<!--     mdlMedicalOut$Att$lmerSlopesSdt,  -->
-<!--     mdlMedicalOut$Att$lmerSlopesCoreSdt -->
-<!--   ) %>% -->
-<!--   as.data.frame() -->
-<!-- medicalSdtCompDf <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Df"] -->
-<!-- medicalSdtCompN <- sapply(ranef(mdlMedicalOut$Att$lmerSlopesCoreSdt), nrow) -->
-<!-- medicalSdtCompChi <- medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Chisq"] %>% round(2) %>% format(nsmall=2) -->
-<!-- medicalSdtCompP <- -->
-<!--   ifelse(medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] < .001, -->
-<!--          "< .001", -->
-<!--          paste0("= ", medicalSdtComp["mdlMedicalOut$Att$lmerSlopesCoreSdt", "Pr(>Chisq)"] %>% round(3) %>% format(nsmall = 3))) -->
-
-<!-- medicalSdtCompChiSq <- paste0("$\\chi^2$(", medicalSdtCompDf, ", \\textit{N} = ", medicalSdtCompN, ") = ", medicalSdtCompChi, ", \\textit{p} ", medicalSdtCompP) -->
-<!-- ``` -->
-
-<!-- In a final step, we again checked whether during the interaction the core situational need remains a meaningful predictor even when taking other fundamental psychological needs into account.
-We find that the core need fulfillment adds additional variance above a model with only the self-determination theory needs (random slopes models; `r medicalSdtCompChiSq`).
-We find that the core need explains the most variance in outgroup attitudes after an outgroup contact (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "KeyNeedFulfillment_cwc")`).
-When compared to the model with only the SDT needs, the core need fulfillment flexibly takes on some of the explained variance of all of the three fundamental needs.
-However, similar to the previous study, in this large sample relatedness (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Relatedness_cwc")`), competence (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Competence_cwc")`) and autonomy (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreSdt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreSdtCI, varName = "Autonomy_cwc")`) each also predicted positive outgroup attitudes independently.
-This being said, the regression coefficient for the core need was three times larger (with all scaling being equal).
-For full results see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness} as well as Online Supplementary Material A.
--->
-
-<!-- \hl{Intend ...} -->
-
-<!-- \hl{Goal-directedness ...} -->
-
-<!-- \hl{Well-being ...} -->
-
-<!-- ```{r robustnessTblLong, include=FALSE} -->
-<!-- # Table of all robustness checks (w/ and w/out SDT only) -->
-
-<!-- # Full Sample -->
-<!-- # Study 1: -->
-<!-- robustTblWorkerFull <-  -->
-<!--   dtWorkerSupp$workerWithinBetween %>% -->
-<!--   select( -->
-<!--     AttitudesDutch = thermometerDutch_1, -->
-<!--     AttitudesDutch_zwc = thermometerDutch_1_zwc, -->
-<!--     CoreNeed_cwc = keyMotiveFulfilled_cwc, -->
-<!--     CoreNeed_zwc = keyMotiveFulfilled_zwc, -->
-<!--     OutgroupInteraction = OutgroupInteraction, -->
-<!--     OutgroupInteraction_zwc = OutgroupInteraction_zwc, -->
-<!--     PID = PID -->
-<!--   ) -->
-<!-- mdlWorkerLmerSlopesAttCoreInt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       CoreNeed_cwc * OutgroupInteraction + -->
-<!--       (1 + CoreNeed_cwc + OutgroupInteraction | PID), -->
-<!--     data = robustTblWorkerFull -->
-<!--   ) -->
-<!-- mdlWorkerLmerSlopesAttCoreIntZ <- lmer( -->
-<!--     AttitudesDutch_zwc ~ -->
-<!--       CoreNeed_zwc * OutgroupInteraction_zwc + -->
-<!--       (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID), -->
-<!--     data = robustTblWorkerFull -->
-<!--   ) -->
-<!-- #Study 2: -->
-<!-- robustTblStudentFull <-  -->
-<!--   dtStudentSupp$studentWithinBetween %>% -->
-<!--   select( -->
-<!--     AttitudesDutch = AttitudesDutch, -->
-<!--     AttitudesDutch_zwc = AttitudesDutch_zwc, -->
-<!--     CoreNeed_cwc = KeyNeedFullfillment_cwc, -->
-<!--     CoreNeed_zwc = KeyNeedFullfillment_zwc, -->
-<!--     OutgroupInteraction = OutgroupInteraction, -->
-<!--     OutgroupInteraction_zwc = OutgroupInteraction_zwc,  -->
-<!--     PID = PID -->
-<!--   ) -->
-<!-- mdlStudentLmerSlopesAttCoreInt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       CoreNeed_cwc * OutgroupInteraction + -->
-<!--       (1 + CoreNeed_cwc + OutgroupInteraction | PID), -->
-<!--     data = robustTblStudentFull -->
-<!--   ) -->
-<!-- mdlStudentLmerSlopesAttCoreIntZ <- lmer( -->
-<!--     AttitudesDutch_zwc ~ -->
-<!--       CoreNeed_zwc * OutgroupInteraction_zwc + -->
-<!--       (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID), -->
-<!--     data = robustTblStudentFull -->
-<!--   ) -->
-<!-- #Study 3: -->
-<!-- robustTblMedicalFull <-  -->
-<!--   dtMedicalSupp$medicalWithinBetween %>% -->
-<!--   select( -->
-<!--     AttitudesDutch = AttitudesDutch, -->
-<!--     AttitudesDutch_zwc = AttitudesDutch_zwc, -->
-<!--     CoreNeed_cwc = KeyNeedFulfillment_cwc, -->
-<!--     CoreNeed_zwc = KeyNeedFulfillment_zwc, -->
-<!--     OutgroupInteraction = OutgroupInteraction, -->
-<!--     OutgroupInteraction_zwc = OutgroupInteraction_zwc,  -->
-<!--     PID = PID -->
-<!--   ) -->
-<!-- mdlMedicalLmerSlopesAttCoreInt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       CoreNeed_cwc * OutgroupInteraction + -->
-<!--       (1 + CoreNeed_cwc + OutgroupInteraction | PID), -->
-<!--     #data = dtMedical$full -->
-<!--     data = robustTblMedicalFull -->
-<!--   ) -->
-<!-- mdlMedicalLmerSlopesAttCoreIntZ <- lmer( -->
-<!--     AttitudesDutch_zwc ~ -->
-<!--       CoreNeed_zwc * OutgroupInteraction_zwc + -->
-<!--       (1 + CoreNeed_zwc + OutgroupInteraction_zwc | PID), -->
-<!--     #data = dtMedical$full -->
-<!--     data = robustTblMedicalFull -->
-<!--   ) -->
-
-<!-- # SDT -->
-<!-- # Study 1: -->
-<!-- robustTblWorkerOut <-  -->
-<!--   dtWorkerSupp$workerOutWithinBetween %>% -->
-<!--   select( -->
-<!--     AttitudesDutch = thermometerDutch_1, -->
-<!--     AttitudesDutch_zwc = thermometerDutch_1_zwc, -->
-<!--     CoreNeed_cwc = keymotive_fulfillemt_1_cwc, -->
-<!--     CoreNeed_zwc = keymotive_fulfillemt_1_zwc, -->
-<!--     Competence_cwc = competence_1_cwc, -->
-<!--     Competence_zwc = competence_1_zwc, -->
-<!--     Autonomy_cwc = autonomy_1_cwc, -->
-<!--     Autonomy_zwc = autonomy_1_zwc, -->
-<!--     Relatedness_cwc = relatedness_1_cwc, -->
-<!--     Relatedness_zwc = relatedness_1_zwc, -->
-<!--     PID = PID -->
-<!--   ) -->
-<!-- mdlWorkerOutLmerSlopesCoreSdt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
-<!--       (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
-<!--     data = robustTblWorkerOut -->
-<!--   ) -->
-<!-- mdlWorkerOutLmerSlopesCoreSdtZ <- lmer( -->
-<!--     AttitudesDutch_zwc ~ -->
-<!--       CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc + -->
-<!--       (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID), -->
-<!--     data = robustTblWorkerOut -->
-<!--   ) -->
-<!-- # Study 2: -->
-<!-- robustTblStudentOut <-  -->
-<!--   dtStudentSupp$studentOutWithinBetween %>% -->
-<!--   select( -->
-<!--     AttitudesDutch = AttitudesDutch, -->
-<!--     AttitudesDutch_zwc = AttitudesDutch_zwc, -->
-<!--     CoreNeed_cwc = KeyNeedFullfillment_cwc, -->
-<!--     CoreNeed_zwc = KeyNeedFullfillment_zwc, -->
-<!--     Competence_cwc = Competence_cwc, -->
-<!--     Competence_zwc = Competence_zwc, -->
-<!--     Autonomy_cwc = Autonomy_cwc, -->
-<!--     Autonomy_zwc = Autonomy_zwc, -->
-<!--     Relatedness_cwc = Relatedness_cwc, -->
-<!--     Relatedness_zwc = Relatedness_zwc, -->
-<!--     PID = PID -->
-<!--   ) -->
-<!-- mdlStudentOutLmerSlopesCoreSdt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
-<!--       (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
-<!--     data = robustTblStudentOut -->
-<!--   ) -->
-<!-- mdlStudentOutLmerSlopesCoreSdtZ <- lmer( -->
-<!--     AttitudesDutch_zwc ~ -->
-<!--       CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc + -->
-<!--       (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID), -->
-<!--     data = robustTblStudentOut -->
-<!--   ) -->
-<!-- # Study 3: -->
-<!-- robustTblMedicalOut <-  -->
-<!--   dtMedicalSupp$medicalOutWithinBetween %>% -->
-<!--   select( -->
-<!--     AttitudesDutch = AttitudesDutch, -->
-<!--     AttitudesDutch_zwc = AttitudesDutch_zwc, -->
-<!--     CoreNeed_cwc = KeyNeedFulfillment_cwc, -->
-<!--     CoreNeed_zwc = KeyNeedFulfillment_zwc, -->
-<!--     Competence_cwc = Competence_cwc, -->
-<!--     Competence_zwc = Competence_zwc, -->
-<!--     Autonomy_cwc = Autonomy_cwc, -->
-<!--     Autonomy_zwc = Autonomy_zwc, -->
-<!--     Relatedness_cwc = Relatedness_cwc, -->
-<!--     Relatedness_zwc = Relatedness_zwc, -->
-<!--     PID = PID -->
-<!--   ) -->
-<!-- mdlMedicalOutLmerSlopesCoreSdt <- lmer( -->
-<!--     AttitudesDutch ~ -->
-<!--       CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc + -->
-<!--       (1 + CoreNeed_cwc + Competence_cwc + Autonomy_cwc + Relatedness_cwc | PID), -->
-<!--     data = robustTblMedicalOut -->
-<!--   ) -->
-<!-- mdlMedicalOutLmerSlopesCoreSdtZ <- lmer( -->
-<!--     AttitudesDutch_zwc ~ -->
-<!--       CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc + -->
-<!--       (1 + CoreNeed_zwc + Competence_zwc + Autonomy_zwc + Relatedness_zwc | PID), -->
-<!--     data = robustTblMedicalOut -->
-<!--   ) -->
-
-<!-- # collect models for table -->
-<!-- mdlRobustTblElements <- list( -->
-<!--   # full -->
-<!--   c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ), -->
-<!--   c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ), -->
-<!--   c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ), -->
-<!--   # outgroup -->
-<!--   c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ), -->
-<!--   c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ), -->
-<!--   c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ) -->
-<!--   ) -->
-
-<!-- mdlRobustPrep <- list() -->
-<!-- for (i in 1:length(mdlRobustTblElements)) { -->
-<!--   mdlRobustPrep[[i]] <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]]) -->
-<!-- } -->
-
-<!-- # manual assembly -->
-<!-- shortRobustPrep <- list() -->
-<!-- for(i in 1:length(mdlRobustPrep)){ -->
-<!--   study <- str_extract(mdlRobustPrep[[i]]$fit$data, "Worker|Student|Medical") -->
-<!--   sample <- str_extract(mdlRobustPrep[[i]]$fit$data, "Full|Out") -->
-<!--   #dv <- sub(" ~.*", "", mdlRobustPrep[[i]]$fit$formula) -->
-<!--   #pred <- gsub("\\(Intercept\\)", "", paste(mdlRobustPrep[[i]]$coeficients$coef, collapse = '')) -->
-
-<!--   name <- paste(study, sample, sep='.') -->
-<!--   tmp <- rbind( -->
-<!--     mdlRobustPrep[[i]]$coeficients[, c("coef", "B", "Beta")], -->
-<!--     data.frame( -->
-<!--       coef = "R2Marg_R2Cond", -->
-<!--       B = mdlRobustPrep[[i]]$fit$R2Marg_R2Cond, -->
-<!--       Beta = "" -->
-<!--     ) -->
-<!--   ) -->
-<!--   shortRobustPrep[[name]] <- tmp -->
-<!-- } -->
-
-<!-- tmp <- shortRobustPrep[grepl("Full", names(shortRobustPrep))] -->
-<!-- fullRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Full$coef) -->
-<!-- for (i in 1:length(tmp)){ -->
-<!--   fullRobustTbl <- join(fullRobustTbl, tmp[[i]], by = "coef") -->
-<!-- } -->
-
-<!-- tmp <- shortRobustPrep[grepl("Out", names(shortRobustPrep))] -->
-<!-- outRobustTbl <- data.frame(coef = shortRobustPrep$Medical.Out$coef) -->
-<!-- for (i in 1:length(tmp)){ -->
-<!--   outRobustTbl <- join(outRobustTbl, tmp[[i]], by = "coef") -->
-<!-- } -->
-
-<!-- robustTblLong <- rbind( -->
-<!--   fullRobustTbl, -->
-<!--   outRobustTbl -->
-<!-- ) -->
-
-<!-- robustTblLong$coef <- mapvalues( -->
-<!--   robustTblLong$coef, -->
-<!--   from = c( -->
-<!--     "R2Marg_R2Cond" -->
-<!--   ), -->
-<!--   to = c( -->
-<!--     "$R^2_{marginal}$ / $R^2_{conditional}$" -->
-<!--   ) -->
-<!-- ) -->
-
-<!-- mdlTblRobustLong <- robustTblLong %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Robustness Analyses", -->
-<!--     #format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = c("l", rep("c", ncol(.)-1)), -->
-<!--     escape = FALSE -->
-<!--   ) %>% -->
-<!--   kable_classic() %>% -->
-<!--   add_header_above(., c(" ", "Study 1" = 2, "Study 2" = 2, "Study 3" = 2)) %>% -->
-<!--   pack_rows("Contact [Full Sample]", 1, 5) %>% -->
-<!--   pack_rows("Self-Determination Theory [Outgroup Interactions only]", 6, 11) %>% -->
-<!--   kableExtra::footnote( -->
-<!--     ., -->
-<!--     general = c("**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05"),  -->
-<!--     escape = FALSE -->
-<!--   ) %>% -->
-<!--   kable_styling(latex_options = "scale_down") %>% -->
-<!--   #kableExtra::landscape() %>% -->
-<!--   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position -->
-<!--   gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position -->
-<!--   save_kable("Tables/mdlRobustlong.tex") -->
-<!-- ``` -->
-
-<!-- ```{r robustnessTblWide, include=FALSE} -->
-<!-- # Wide format -->
-<!-- mdlRobustTbl <- data.frame( -->
-<!--   coef = c( -->
-<!--     sapply(mdlRobustPrep, function(x) x[1]$coeficients$coef) %>% unlist %>% unique, -->
-<!--     names(mdlRobustPrep[[1]]$random), -->
-<!--     names(mdlRobustPrep[[1]]$fit) -->
-<!--   ) -->
-<!-- ) -->
-<!-- for (i in 1:length(mdlRobustPrep)){ -->
-<!--   mdlRobustTbl <- join(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef") -->
-<!--   #mdlTbl <- merge(mdlRobustTbl, mdlRobustPrep[[i]]$mdlTbl, by = "coef", all = TRUE, sort = FALSE, no.dups = TRUE, suffixes=c("", "")) -->
-<!-- } -->
-
-<!-- mdlRobustTblHeader <- data.frame( -->
-<!--   data = as.character(mdlRobustTbl[mdlRobustTbl$coef == "data",]), -->
-<!--   formula = as.character(mdlRobustTbl[mdlRobustTbl$coef == "formula",]) -->
-<!-- ) %>% -->
-<!--   filter(data != "", -->
-<!--          data != "data") %>% -->
-<!--   mutate(study = str_extract(data, "Worker|Student|Medical")) %>% -->
-<!--   mutate(study = gsub("Worker", "Study 1", study)) %>% -->
-<!--   mutate(study = gsub("Student", "Study 2", study)) %>% -->
-<!--   mutate(study = gsub("Medical", "Study 3", study)) %>% -->
-<!--   mutate(dv = sub(" ~.*", "", formula)) %>% -->
-<!--   mutate(dv = gsub("Raw", " ", dv)) %>% -->
-<!--   mutate(pred = str_extract(formula, "CoreNeed|Allport")) %>% -->
-<!--   mutate(header = paste(study, pred, sep = " - ")) -->
-
-<!-- mdlRobustTblHeaderFreq <- rbind.data.frame(rle(mdlRobustTblHeader$header)) %>% -->
-<!--   mutate(lengths = lengths*2) %>% -->
-<!--   rename(names = values, span = lengths) %>% -->
-<!--   rbind(c(1, ""), .) %>% -->
-<!--   mutate(span = as.numeric(span)) %>% -->
-<!--   select(names, span) -->
-
-<!-- mdlRobustTblHeaderDv <- data.frame(names = mdlRobustTblHeader$dv, span = 2) %>%  -->
-<!--   mutate(names = as.character(names)) %>% -->
-<!--   rbind(c("", 1), .) %>% -->
-<!--   mutate(span = as.numeric(span)) -->
-
-<!-- mdlRobustTblHeaderStudy <- rbind.data.frame(rle(mdlRobustTblHeader$study)) %>% -->
-<!--   mutate(lengths = lengths*2) %>% -->
-<!--   rename(names = values, span = lengths) %>% -->
-<!--   rbind(c(1, ""), .) %>% -->
-<!--   mutate(span = as.numeric(span)) %>% -->
-<!--   select(names, span) -->
-
-<!-- mdlRobustTbl$coef <- mapvalues( -->
-<!--   mdlRobustTbl$coef, -->
-<!--   from = c( -->
-<!--     "sigmaSq", -->
-<!--     "tau00", -->
-<!--     "tau11", -->
-<!--     "rho01", -->
-<!--     "rho00", -->
-<!--     "R2_marginal", -->
-<!--     "R2_conditional",  -->
-<!--     "R2Marg_R2Cond" -->
-<!--   ), -->
-<!--   to = c( -->
-<!--     "$\\sigma^2$", -->
-<!--     "$\\tau_{00}$", -->
-<!--     "$\\tau_{11}$", -->
-<!--     "$\\rho_{01}$", -->
-<!--     "$\\rho_{00}$", -->
-<!--     "$R^2_{marginal}$", -->
-<!--     "$R^2_{conditional}$", -->
-<!--     "$R^2_{marginal}$ / $R^2_{conditional}$" -->
-<!--   ) -->
-<!-- ) -->
-
-<!-- # Long Table -->
-<!-- mdlTblRobustLong <- mdlRobustTbl %>% -->
-<!--   replace(is.na(.), "") %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Robustness Analyses", -->
-<!--     #format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = T, -->
-<!--     align = c("l", rep("c", ncol(.) - 1)), -->
-<!--     escape = FALSE, -->
-<!--     digits = 3 -->
-<!--   ) %>% -->
-<!--   kable_classic() %>% -->
-<!--   add_header_above(., mdlRobustTblHeaderStudy) %>% -->
-<!--   add_header_above( -->
-<!--     ., -->
-<!--     c( -->
-<!--       "", -->
-<!--       "Contact [Full Sample]" = 6, -->
-<!--       "Self-Determination Theory [Outgroup Interactions only]" = 6 -->
-<!--     ) -->
-<!--   ) %>% -->
-<!--   pack_rows("Fixed", 1, 7) %>% -->
-<!--   pack_rows("Random", 8, 12) %>% -->
-<!--   pack_rows("Fit", 13, 25) %>% -->
-<!--   footnote( -->
-<!--     general = c("PID = Participant ID number (grouping variable)", -->
-<!--                 "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes", -->
-<!--                 "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05" -->
-<!--     ), -->
-<!--     escape = FALSE -->
-<!--   ) %>% -->
-<!--   gsub("_cwc", "", ., fixed = TRUE)  -->
-
-<!-- # shortened Table -->
-<!-- mdlTblRobustShort <- mdlRobustTbl %>% -->
-<!--   replace(is.na(.), "") -->
-<!-- names(mdlTblRobustShort) <- make.unique(names(mdlTblRobustShort)) -->
-<!-- mdlTblRobustShort <- mdlTblRobustShort %>% -->
-<!--   filter( -->
-<!--     !coef %in% c( -->
-<!--       "data", -->
-<!--       "formula", -->
-<!--       "groupId", -->
-<!--       "$R^2_{marginal}$", -->
-<!--       "$R^2_{conditional}$", -->
-<!--       "logLik", -->
-<!--       "deviance" -->
-<!--     ) -->
-<!--   ) %>% -->
-<!--   mutate_all(linebreak) %>% -->
-<!--   kbl( -->
-<!--     ., -->
-<!--     caption = "Robustness Analyses", -->
-<!--     format = "latex", -->
-<!--     linesep = "", -->
-<!--     booktabs = TRUE, -->
-<!--     col.names = c("", rep(c("$B$", "$\\beta$"), (ncol(.)-1)/2)), -->
-<!--     align = c("l", rep("c", ncol(.) - 1)), -->
-<!--     escape = FALSE, -->
-<!--     digits = 3 -->
-<!--   )  %>% -->
-<!--   kable_classic() %>% -->
-<!--   add_header_above(., mdlRobustTblHeaderStudy) %>% -->
-<!--   add_header_above( -->
-<!--     ., -->
-<!--     c( -->
-<!--       "", -->
-<!--       "Contact [Full Sample]" = 6, -->
-<!--       "Self-Determination Theory [Outgroup Interactions only]" = 6 -->
-<!--     ) -->
-<!--   ) %>% -->
-<!--   pack_rows("Fixed", 1, 7) %>% -->
-<!--   pack_rows("Random", 8, 12) %>% -->
-<!--   pack_rows("Fit", 13, 18) %>% -->
-<!--   footnote( -->
-<!--     general = c("PID = Participant ID number (grouping variable)", -->
-<!--                 "$\\sigma^2$: residual variance, $\\tau_{00}$: random intercept variance, $\\tau_{11}$: random slope variance(s), $\\rho_{01}$: random slope-intercept correlation(s) , $\\rho_{00}$: correlation(s) between random slopes", -->
-<!--                 "**** $p$ < .0001, *** $p$ < .001, ** $p$ < .01, * $p$ < .05" -->
-<!--     ),  -->
-<!--     escape = FALSE -->
-<!--   ) %>% -->
-<!--   kable_styling(latex_options = "scale_down") %>% -->
-<!--   kableExtra::landscape() %>% -->
-<!--   gsub("_cwc", "", ., fixed = TRUE)  %>% -->
-<!--   gsub("\\makecell[l]", "\\makecell[c]", ., fixed = TRUE) %>% -->
-<!--   gsub("\\makecell[r]", "\\makecell[c]", ., fixed = TRUE) %>% -->
-<!--   gsub("objVar$", "", ., fixed = TRUE) %>% -->
-<!--   gsub("slope_intercept.", "slope.intercept", ., fixed = TRUE) %>% -->
-<!--   gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position -->
-<!--   gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position -->
-<!--   save_kable("Tables/mdlRobustness.tex") -->
-<!-- mdlTblRobustShort -->
-<!-- ``` -->
-
-<!-- <!-- FIGURES: --> -->
-
-<!-- ```{r metaRobust, include=FALSE} -->
-<!-- mdlRobustTblElements <- list( -->
-<!--   # full -->
-<!--   c(mdlWorkerLmerSlopesAttCoreInt, mdlWorkerLmerSlopesAttCoreIntZ), -->
-<!--   c(mdlStudentLmerSlopesAttCoreInt, mdlStudentLmerSlopesAttCoreIntZ), -->
-<!--   c(mdlMedicalLmerSlopesAttCoreInt, mdlMedicalLmerSlopesAttCoreIntZ), -->
-<!--   # outgroup -->
-<!--   c(mdlWorkerOutLmerSlopesCoreSdt, mdlWorkerOutLmerSlopesCoreSdtZ), -->
-<!--   c(mdlStudentOutLmerSlopesCoreSdt, mdlStudentOutLmerSlopesCoreSdtZ), -->
-<!--   c(mdlMedicalOutLmerSlopesCoreSdt, mdlMedicalOutLmerSlopesCoreSdtZ) -->
-<!--   ) -->
-
-<!-- # i =1 -->
-<!-- robustMetaTbl <- data.frame() -->
-<!-- for (i in 1:length(mdlRobustTblElements)){ -->
-<!--   lmerTblTmp <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$beta %>% -->
-<!--   select( -->
-<!--     coef, -->
-<!--     B = est, -->
-<!--     se, -->
-<!--     lwr, -->
-<!--     upr, -->
-<!--     tval, -->
-<!--     Rsq -->
-<!--   ) %>% -->
-<!--   mutate( -->
-<!--     n = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$N, -->
-<!--     m = nrow(.),  -->
-<!--     #dv = gsub("Dutch", "", str_extract(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula,".+?(?= ~)")), -->
-<!--     sample = str_match(lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$data, "Tbl(.*?)(Full|Out)")[2], -->
-<!--     formula = lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]])$fit$formula, -->
-<!--     coef = gsub(":", ".", coef) -->
-<!--   ) -->
-<!--   robustMetaTbl <- rbind(robustMetaTbl, lmerTblTmp) -->
-<!-- } -->
-
-<!-- robustMetaTbl <- robustMetaTbl %>% -->
-<!--   arrange(formula, match( -->
-<!--     coef, -->
-<!--     c( -->
-<!--       "CoreNeed_zwc", -->
-<!--       "OutgroupInteraction_zwc", -->
-<!--       "CoreNeed_zwc.OutgroupInteraction_zwc", -->
-<!--       "Autonomy_zwc", -->
-<!--       "Competence_zwc", -->
-<!--       "Relatedness_zwc" -->
-<!--     ) -->
-<!--   )) %>%  -->
-<!--   mutate(formula = gsub(" \\+ \\(.*", "", formula)) -->
-
-<!-- robustMetaContact <- -->
-<!--   metaLmerOut( -->
-<!--     lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc * OutgroupInteraction"), -->
-<!--     type = "REML", #"FE",  -->
-<!--     name = "RobustContact", -->
-<!--     title = "Robustness — Contact and Need Fulfillment" -->
-<!--   ) -->
-
-<!-- robustMetaSDT <- -->
-<!--   metaLmerOut( -->
-<!--     lmerDataTbl = robustMetaTbl %>% filter(formula == "AttitudesDutch ~ CoreNeed_cwc + Competence_cwc + Autonomy_cwc +      Relatedness_cwc"), -->
-<!--     type = "REML", #"FE",  -->
-<!--     name = "RobustSDT", -->
-<!--     title = "Robustness — Other Needs" -->
-<!--   ) -->
-<!-- ``` -->
-
-<!-- ```{r robustForestPltComb, include=FALSE} -->
-<!-- effRobust <- rbind( -->
-<!--   robustMetaContact$eff %>% -->
-<!--     filter(coef != "(Intercept)") %>% -->
-<!--     mutate(analysis = "(A) Attitude ~ Contact and Need Fulfillment", -->
-<!--            metaId = paste(coef, analysis, sep = ".")) %>% -->
-<!--     as.data.frame, -->
-<!--   robustMetaSDT$eff %>% -->
-<!--     mutate(analysis = "(B) Attitude ~ Other Needs", -->
-<!--            metaId = paste(coef, analysis, sep = ".")) %>% -->
-<!--     as.data.frame -->
-<!-- ) -->
-
-<!-- metaSubForest(effRobust,  -->
-<!--               title = "Meta Analysis: Forest Plot Robustness Analysis \n[Parametric]", -->
-<!--               filename = "RobustnessComb", -->
-<!--               addAbove = 5, -->
-<!--               width = 600, -->
-<!--               height = 800) -->
-<!-- ``` -->

### 2023-05-26 Tables/mdlTheory.tex
new mdl tbl
meta structure added
meta General LM added
theory meta added
robust meta added
methods and results re-render (in progress)

@@
 
-\caption{\label{tab:intergroupNeedsTbl}Core Need Fulfillment and Allport's Conditions}
+\caption{\label{tab:intergroupNeedsTblWide}Core Need Fulfillment and Allport's Conditions}
 \centering
@@
 \multicolumn{27}{l}{\textbf{Fixed}}\\
-\hspace{1em}(Intercept) & 24.28**** [20.20, 28.36] &  & 72.53**** [66.83, 78.24] &  & 72.50**** [66.75, 78.24] &  & 78.84**** [76.86, 80.83] &  & 70.71**** [67.55, 73.87] &  & 70.67**** [67.50, 73.84] &  & 81.36**** [78.53, 84.19] &  & 68.32**** [65.10, 71.54] &  & 68.32**** [65.09, 71.54] &  & 81.42**** [78.57, 84.26] &  & 68.36**** [65.16, 71.56] &  & 68.34**** [65.12, 71.56] &  & 68.33**** [65.05, 71.61] & \\
-\hspace{1em}CoreNeed & 0.42**** [ 0.32,  0.52] & 0.40 [ 0.31, 0.49] & 0.17** [ 0.06,  0.29] & 0.30 [ 0.18, 0.41] & 0.04 [-0.08,  0.15] & 0.13 [ 0.00, 0.26] & 0.40**** [ 0.28,  0.52] & 0.27 [ 0.18, 0.37] & 0.13*** [ 0.07,  0.19] & 0.14 [ 0.06, 0.22] & 0.03 [-0.01,  0.07] & 0.07 [-0.01, 0.15] & 0.43**** [ 0.33,  0.54] & 0.31 [ 0.24, 0.38] & 0.19**** [ 0.12,  0.27] & 0.18 [ 0.11, 0.24] & 0.11** [ 0.05,  0.17] & 0.11 [ 0.05,  0.17] &  &  &  &  &  &  & 0.13**** [ 0.08,  0.17] & 0.12 [ 0.05, 0.18]\\
-\hspace{1em}Quality &  &  &  &  & 0.23*** [ 0.12,  0.33] & 0.41 [ 0.29, 0.54] &  &  &  &  & 0.17**** [ 0.11,  0.23] & 0.24 [ 0.14, 0.34] &  &  &  &  & 0.17**** [ 0.12,  0.22] & 0.17 [ 0.12,  0.22] &  &  &  &  & 0.17**** [ 0.12,  0.23] & 0.22 [ 0.15, 0.29] &  & \\
-\hspace{1em}Allport &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 0.65**** [ 0.54,  0.76] & 0.46 [ 0.39, 0.52] & 0.22**** [ 0.15,  0.29] & 0.21 [ 0.14, 0.27] & 0.09** [ 0.03,  0.15] & 0.10 [ 0.03, 0.16] & 0.17*** [ 0.09,  0.24] & 0.17 [ 0.11, 0.23]\\
+\hspace{1em}(Intercept) & 74.28**** [70.20, 78.36] &  & 72.53**** [66.81, 78.26] &  & 72.50**** [66.74, 78.25] &  & 78.84**** [76.86, 80.83] &  & 70.71**** [67.55, 73.87] &  & 70.67**** [67.50, 73.84] &  & 81.36**** [78.53, 84.19] &  & 68.32**** [65.10, 71.54] &  & 68.32**** [65.09, 71.54] &  & 81.42**** [78.57, 84.26] &  & 68.36**** [65.16, 71.56] &  & 68.34**** [65.12, 71.56] &  & 68.33**** [65.05, 71.61] & \\
+\hspace{1em}CoreNeed & 0.42**** [ 0.32,  0.52] & 0.40 [0.31, 0.49] & 0.17** [ 0.06,  0.29] & 0.30 [0.18, 0.41] & 0.04 [-0.08,  0.15] & 0.13 [0.00, 0.26] & 0.40**** [ 0.28,  0.52] & 0.27 [0.18, 0.37] & 0.13*** [ 0.07,  0.19] & 0.14 [0.06, 0.22] & 0.03 [-0.01,  0.07] & 0.07 [-0.01, 0.15] & 0.43**** [ 0.33,  0.54] & 0.31 [0.24, 0.38] & 0.19**** [ 0.12,  0.27] & 0.18 [0.11, 0.24] & 0.11** [ 0.05,  0.17] & 0.10 [0.04, 0.16] &  &  &  &  &  &  & 0.13**** [ 0.08,  0.17] & 0.12 [0.05, 0.18]\\
+\hspace{1em}Quality &  &  &  &  & 0.23*** [ 0.12,  0.33] & 0.41 [0.29, 0.54] &  &  &  &  & 0.17**** [ 0.11,  0.23] & 0.24 [ 0.14, 0.34] &  &  &  &  & 0.17**** [ 0.12,  0.22] & 0.23 [0.17, 0.30] &  &  &  &  & 0.17**** [ 0.12,  0.23] & 0.22 [0.15, 0.29] &  & \\
+\hspace{1em}Allport &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 0.65**** [ 0.54,  0.76] & 0.46 [0.39, 0.52] & 0.22**** [ 0.15,  0.29] & 0.21 [0.14, 0.27] & 0.09** [ 0.03,  0.15] & 0.10 [0.03, 0.16] & 0.17*** [ 0.09,  0.24] & 0.17 [0.11, 0.23]\\
 \addlinespace[0.3em]
 \multicolumn{27}{l}{\textbf{Random}}\\
-\hspace{1em}$\sigma^2$ & 261.1 &  & 63.1 &  & 37.61 &  & 275.7 &  & 89.83 &  & 76.47 &  & 222.5 &  & 91.84 &  & 82.15 &  & 188.9 &  & 93.05 &  & 83.82 &  & 90.78 & \\
-\hspace{1em}$\tau_{00}$ & 71.13 (PID) &  & 172.54 (PID) &  & 177.20 (PID) &  & 63.00 (PID) &  & 259.79 (PID) &  & 264.19 (PID) &  & 131.33 (PID) &  & 182.38 (PID) &  & 183.10 (PID) &  & 134.62 (PID) &  & 179.74 (PID) &  & 182.79 (PID) &  & 189.33 (PID) & \\
+\hspace{1em}$\sigma^2$ & 261.1 &  & 63.08 &  & 37.6 &  & 275.7 &  & 89.83 &  & 76.47 &  & 222.5 &  & 91.84 &  & 82.15 &  & 188.9 &  & 93.05 &  & 83.82 &  & 90.78 & \\
+\hspace{1em}$\tau_{00}$ & 71.13 (PID) &  & 173.49 (PID) &  & 177.88 (PID) &  & 63.00 (PID) &  & 259.79 (PID) &  & 264.19 (PID) &  & 131.33 (PID) &  & 182.38 (PID) &  & 183.10 (PID) &  & 134.62 (PID) &  & 179.74 (PID) &  & 182.79 (PID) &  & 189.33 (PID) & \\
 \hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.05 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[c]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
@@
 \multicolumn{27}{l}{\textbf{Fit}}\\
+\hspace{1em}name &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
 \hspace{1em}AIC & 3294 &  & 2816 &  & 2672 &  & 8073 &  & 7222 &  & 7141 &  & 14054 &  & 12632 &  & 12494 &  & 13805 &  & 12652 &  & 12519 &  & 12625 & \\
@@
 \hspace{1em}Groups & 21 &  & 21 &  & 21 &  & 108 &  & 108 &  & 108 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 & \\
-\hspace{1em}ICC & 0.2141 &  & 0.7447 &  & 0.8399 &  & 0.2547 &  & 0.7471 &  & 0.7835 &  & 0.3933 &  & 0.6738 &  & 0.7006 &  & 0.4433 &  & 0.6679 &  & 0.6963 &  &  & \\
-\hspace{1em}$R^2_{marginal}$ / $R^2_{conditional}$ & 0.117 / 0.306 &  & 0.030 / 0.752 &  & 0.067 / 0.851 &  & 0.102 / 0.331 &  & 0.012 / 0.750 &  & 0.028 / 0.789 &  & 0.070 / 0.436 &  & 0.019 / 0.680 &  & 0.041 / 0.713 &  & 0.149 / 0.526 &  & 0.024 / 0.676 &  & 0.040 / 0.709 &  & 0.086 / NA & \\
+\hspace{1em}ICC & 0.2141 &  & 0.7458 &  & 0.8404 &  & 0.2547 &  & 0.7471 &  & 0.7835 &  & 0.3933 &  & 0.6738 &  & 0.7006 &  & 0.4433 &  & 0.6679 &  & 0.6963 &  &  & \\
+$R^2_{marginal}$ / $R^2_{conditional}$ & 0.117 / 0.306 &  & 0.030 / 0.753 &  & 0.067 / 0.851 &  & 0.102 / 0.331 &  & 0.012 / 0.750 &  & 0.028 / 0.789 &  & 0.070 / 0.436 &  & 0.019 / 0.680 &  & 0.041 / 0.713 &  & 0.149 / 0.526 &  & 0.024 / 0.676 &  & 0.040 / 0.709 &  & 0.086 / NA & \\
 \bottomrule

### 2023-05-26 Tables/studentVarDescr.tex
robust meta added
methods and results re-render (in progress)

@@
 
-\caption{Student: Multilevel Core Variable Descriptives}
+\caption{\label{tab:studentVarDescr}Student: Multilevel Core Variable Descriptives}
 \centering
@@
 \midrule
-Core Need &  & 0.60*** & 0.66*** & 0.43*** & 0.78*** & 0.11\\
-Competence & 0.24*** &  & 0.71*** & 0.65*** & 0.74*** & 0.09\\
-Autonomy & 0.15*** & 0.34*** &  & 0.56*** & 0.67*** & -0.06\\
-Relatedness & 0.45*** & 0.29*** & 0.42*** &  & 0.54*** & -0.11\\
-Quality & 0.17*** & 0.39*** & 0.08*** & 0.05** &  & 0.10\\
-Attitudes NL & 0.35*** & 0.43*** & 0.11*** & 0.10*** & 0.12*** & \\
+Core Need &  & 0.61*** & 0.66*** & 0.42*** & 0.80*** & 0.10\\
+Competence & 0.24*** &  & 0.74*** & 0.66*** & 0.75*** & 0.07\\
+Autonomy & 0.15*** & 0.34*** &  & 0.58*** & 0.69*** & -0.04\\
+Relatedness & 0.45*** & 0.29*** & 0.42*** &  & 0.55*** & -0.12\\
+Quality & 0.17*** & 0.39*** & 0.08*** & 0.05** &  & 0.09\\
+Attitudes NL & 0.35*** & 0.43*** & 0.11*** & 0.11*** & 0.13*** & \\
 \addlinespace

### 2023-05-26 Tables/workerOutVarDescr.tex
formulas adjusted
methods and results re-render (in progress)

@@
 \midrule
-Core Need &  & 0.82*** & 0.60*** & 0.32 & 0.52** & -0.03\\
-Competence & 0.36*** &  & 0.89*** & 0.24 & 0.38 & -0.24\\
-Autonomy & 0.28*** & 0.23*** &  & 0.29 & 0.56** & 0.02\\
-Relatedness & 0.51*** & 0.39*** & 0.37*** &  & -0.09 & 0.14\\
-Quality & 0.17*** & 0.44*** & 0.27*** & 0.27*** &  & 0.50*\\
-Attitudes NL & 0.24*** & 0.37*** & 0.24*** & 0.37*** & 0.52*** & \\
+Core Need &  & 0.82*** & 0.59*** & 0.31 & 0.52** & -0.02\\
+Competence & 0.36*** &  & 0.89*** & 0.23 & 0.37 & -0.25\\
+Autonomy & 0.29*** & 0.23*** &  & 0.28 & 0.55** & 0.02\\
+Relatedness & 0.51*** & 0.39*** & 0.37*** &  & -0.09 & 0.13\\
+Quality & 0.17*** & 0.44*** & 0.28*** & 0.27*** &  & 0.50*\\
+Attitudes NL & 0.24*** & 0.38*** & 0.24*** & 0.37*** & 0.52*** & \\
 \addlinespace
-Grand Mean & 32.20 & 16.53 & 22.64 & 1.58 & 24.10 & 72.46\\
+Grand Mean & 82.20 & 66.53 & 72.64 & 51.58 & 74.10 & 72.46\\
 Between SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.50 & 13.62\\

### 2023-05-26 Tables/workerVarDescr.tex
tables adjusted
methods and results re-render (in progress)

--- 2022-01-04 Tables/workerVarDescr.tex
@@
 \midrule
-Core Need &  & 0.82*** & 0.60*** & 0.33 & 0.52** & -0.03\\
-Competence & 0.36*** &  & 0.89*** & 0.26 & 0.39 & -0.23\\
-Autonomy & 0.28*** & 0.22*** &  & 0.31 & 0.57** & 0.02\\
-Relatedness & 0.50*** & 0.39*** & 0.37*** &  & -0.07 & 0.14\\
-Quality & 0.17*** & 0.44*** & 0.27*** & 0.26*** &  & 0.50*\\
-Attitudes NL & 0.24*** & 0.36*** & 0.24*** & 0.37*** & 0.52*** & \\
+Core Need &  & 0.63*** & 0.47** & 0.00 & 0.39* & -0.22\\
+Competence & 0.37*** &  & 0.68*** & -0.13 & 0.16 & -0.26\\
+Autonomy & 0.31*** & 0.08** &  & -0.04 & 0.63*** & 0.16\\
+Relatedness & 0.45*** & 0.41*** & 0.22*** &  & 0.02 & -0.07\\
+Quality & 0.05 & 0.45*** & 0.11*** & 0.12*** &  & 0.47*\\
+Attitudes NL & 0.10*** & 0.34*** & 0.14*** & 0.14*** & 0.43*** & \\
 \addlinespace
-Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 24.10 & 71.49\\
+Grand Mean & 77.95 & 62.10 & 72.17 & 55.29 & 74.10 & 71.49\\
 Between SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.50 & 12.91\\
-Within SD & NA & NA & NA & NA & NA & NA\\
+Within SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
 ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.18 & 0.70\\
 ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.79 & 0.99\\
-Within.person.SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
 \bottomrule

### 2023-05-26 Robustness-Methods-and-Results.tex
robustness re-render (in progress) + code clean-up

@@
 intergroup interaction and their situational core need fulfillment, we
-also measured a set of general psychological needs.
+also included a number of variables that allowed us to assess the
+robustness of our results.
 
-\subsubsection{General Psychological Needs}
+\subsubsection{Specific Psychological Needs}
 
@@
 
+\subsubsection{Interaction Intend}
+
+To assess whether an interaction was accidental (vs.~planned), we asked
+participants with a single item to report the extend to which ``The
+interaction with -X- was accidental''. The respondents were asked to
+report this context variable for all interactions they reported on using
+a continuous slider ranging from ``not at all'' (0), through ``very
+little'' (33) and ``somewhat'' (66), to ``a great deal'' (100). In all
+studies the scale showed a right skew (\textit{mean} = 29.60,
+\textit{sd} = 33.68).
+
+\subsubsection{Goal-directedness}
+
+To assess whether the need content (i.e., the motives) would impact the
+effect of the need fulfillment experiences, we manually coded the topics
+we extracted during the topic modeling on two dimensions of how much
+they reflect a practical and a psychological goal-directedness. We chose
+practical and psychological needs specifically as our dimensions to
+account for differences in the types of needs that participants commonly
+reported. With practical motives we refer to specific, tangible goals or
+tasks that participants aimed to accomplish during the interaction.
+These instrumental goals are usually observable, concrete, and often
+centered on external outcomes, such as acquiring resources, completing
+tasks, and addressing immediate challenges \citep[][]{}. With
+psychological motives we refer to underlying motives or desires that are
+more abstract and relate to personal fulfillment and well-being. In
+contrast to practical needs, psychological needs delve into the
+subjective and internal aspects of human experiences. These needs
+pertain to emotions, social connections, and cognitive processes,
+reflecting individuals' quest for personal growth, well-being, and
+thriving in social relationships \citep[][]{}. Note that with this
+approach any particular motive can include a practical and/or a
+psychological goal-directedness but can also be classified as not having
+any goal at all. The full coding protocol we developed with examples for
+each of the codes is available in our Online Supplemental Material D.
+After an initial training, each of the two coders independently coded
+the 47 topics on the two dimensions, using one of three options each
+(i.e., 0 = no goal, 1 = vague goal, 2 = clear goal). Inter-rater
+reliability assessments showed that for both the practical as well as
+the psychological needs, agreement was not optimal using the three
+answer options (agreement practical = 0.72\%, agreement psychological =
+0.78\%). However, most disagreements were, if a need was present,
+whether that need was vague (1) or concrete (2). We, thus, collapsed
+these two categories making the ratings binary (need absent vs.~need
+present). With the simpler coding, inter-rater agreement for practical
+needs (0.93\%) and the psychological need (0.96\%) were much more
+reliable. Using Cohen's \(\kappa\) as our measure of inter-rater
+reliability, we find that both the practical need coding
+(\textit{Cohen's} \(\kappa\) = 0.80, 95\%CI{[}0.58, 1.00{]}) as well as
+the psychological need coding (\textit{Cohen's} \(\kappa\) = 0.86,
+95\%CI{[}0.67, 1.00{]}) were very good. We thus proceeded with this
+collapsed coding. After resolving coder disagreements and merging the
+codings back to the free-text responses, we found that a majority of
+responses showed both a practical as well as a psychological need
+(57.95\%) and only few responses had no goal at all (1.03\%) with the
+remaining 41.02\% having either a practical or a psychological need only
+(see Online Supplemental Material A for more detailed tables and
+visualizations).
+
+\subsubsection{Well-being}
+
+We measured experienced well-being using a visual analog scale adapted
+from \citet{davies2022}. Participants were asked to respond to the the
+question ``How do you feel right now?'' using a continuous visual slider
+ranging from ``very sad''(-100) to ``very happy'' (100). The well-being
+ratings were generally normally distributed (\textit{mean} = 64.80,
+\textit{sd} = 19.25).
+
 \subsection{Results}
 
-\subsubsection{Study 1}
+To build further confidence in our results, we assessed a number of
+additional models that might offer alternative explanations. We will
+discuss the results in sequential order --- in every case first
+considering the a global test of the model across the three studies and
+only then assessing whether the global three-level regression model
+suppresses any important person-level variations within the studies.
 
-To build further confidence in our results, we assessed two additional
-models that might offer alternative explanations. First, to ensure that
-the effect of core need fulfillment is specific to an actual contact, we
-compared the effect to core need fulfillment in situations without an
-intergroup contact. For this, we analyzed the generalized situational
-core need fulfillment (either during a contact or about the daytime in
-general) and tested whether the effect differed during experience
-sampling measurements with and without outgroup contacts. We found no
-main effect of core need fulfillment (random slopes model; \textit{b} =
--0.10, \textit{t}(1,199) = -2.22, \textit{p} = 0.026,
-\textit{95\%CI}{[}-0.18, -0.01{]}) but a significant interaction effect
-of core need fulfillment and outgroup contact (\textit{b} = 0.13,
-\textit{t}(1,199) = 4.31, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.07, 0.18{]}; also see \tblref{tab:robustnessTblLong}
-and \fgrref{fig:Robustness}). Together with a significant main effect of
-having an outgroup contact, this indicates that it is not key need
-fulfillment in general --- but only key need fulfillment during an
-outgroup contact that predicts more positive outgroup attitudes.
+\subsubsection{Contact specific}
 
-In a final step, we controlled for other fundamental psychological needs
-during the contact. We focus on the three commonly considered
-self-determination needs (SDT): competence, autonomy, and relatedness.
-We find that the core need fulfillment adds significantly above a model
-with only the self-determination theory needs (random slopes models;
-\(\chi^2\)(6, \textit{N} = 21) = 19.60, \textit{p} = 0.003). We also
-find that next to relatedness (\textit{b} = 0.10, \textit{t}(361) =
-4.04, \textit{p} \textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the
-core need explains the most variance in outgroup attitudes after an
-outgroup contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p}
-= 0.026, \textit{95\%CI}{[}0.01, 0.18{]}). When compared to the model
-with only the SDT needs, the core need fulfillment flexibly takes on
-some of the explained variance of all three fundamental needs
-(competence and autonomy needs turning non-significant; all \textit{b}
-\textless{} 0.05, all \textit{p} \textgreater{} 0.544). For full results
-see see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and
-Online Supplementary Material A. There is, thus, considerable evidence
-lending confidence to the stability and relevance of psychological need
-fulfillment as a predictor of positive outgroup attitudes for natural
-intergroup contacts.
+We begin our robustness analysis by testing whether the effect of core
+need fulfillment is specific to an actual outgroup contact, rather than
+need fulfillment in general. For this, we analyzed the generalized
+situational core need fulfillment (either during a contact or about the
+daytime in general) and tested whether the effect differed during
+experience sampling measurements with and without outgroup contacts. We
+start this test by assessing the effect across all three studies, using
+a three-level hierarchical model, where measurements are nested within
+participants, and participants are nested within studies. In this
+overall model, we found no main effect of core need fulfillment (random
+slopes model, grand-mean standardized to account for all levels of
+variance; \textit{b} = 0.62, \textit{t}( 3.187) = 2.89, \textit{p} =
+0.058, \textit{95\%CI}{[} 0.20, 1.03{]}) but a significant interaction
+effect of core need fulfillment and outgroup contact (\textit{b} = 2.44,
+\textit{t}(4,663.172) = 8.62, \textit{p} \textless{} .001,
+\textit{95\%CI}{[} 1.89, 3.00{]}; also see
+\tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}). While the
+three-level hierarchical model can be sensitive to scaling issues, this
+already indicates that it is not key need fulfillment in general --- but
+only key need fulfillment during an outgroup contact that predicts more
+positive outgroup attitudes.
 
-\subsubsection{Study 2}
+To ensure that the results are not affected by scaling issues (e.g.,
+study-level variances suppressing person-level variances) or a similar
+Simpson's paradox, we additionally assess the model within each of the
+three studies. Within each of the three studies, the effects are more
+pronounced, so that we also see a significant effect of core need
+fulfillemnt (all \textit{b} \textgreater{} 0.06, all \textit{p}
+\textless{} 0.005) as well as outgroup contact itself (all
+\textbar{}\textit{b}\textbar{} \textgreater{} 1.81, all \textit{p}
+\textless{} 0.034) but the interaction effect consistently remains the
+most reliable predictor of outgroup attitudes (all
+\textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all \textit{p}
+\textless{} 0.002, also see \tblref{tab:robustnessTblLong} and
+\fgrref{fig:Robustness}). There is thus consistent evidence that need
+fulfillment relates to outgroup attitudes for outgroup contacts in
+particular but not need fulfillment in general.
 
-Also for Study 2, we checked for alternative models. First, when
-considering generalized situational core need fulfillment together with
-whether an intergroup contact took place, we find that there is only a
-minuscule main effect of core need fulfillment (random slopes model;
-\textit{b} = -0.03, \textit{t}(4,849) = -1.34, \textit{p} = 0.181,
-\textit{95\%CI}{[}-0.08, 0.02{]}) but a stronger interaction effect of
-core need fulfillment and outgroup contact (\textit{b} = 0.06,
-\textit{t}(4,849) = 3.03, \textit{p} = 0.002, \textit{95\%CI}{[}0.02,
-0.10{]}). Together with a significant main effect of having an outgroup
-contact (\textit{b} = 2.88, \textit{t}(4,849) = 3.71, \textit{p}
-\textless{} .001, \textit{95\%CI}{[}1.36, 4.40{]}), this indicates that
-it is not key need fulfillment in general --- but key need fulfillment
-during an outgroup contact that predicts more positive outgroup
-attitudes. This finding is consistent with the results of the previous
-study, albeit with a slightly weaker effect (likely because of the large
-number of measurements that did not include an outgroup interaction; For
-full results see \tblref{tab:robustnessTblLong} and for visual
-comparison see \fgrref{fig:Robustness}).
+\subsubsection{Interaction intend}
 
-In a final step, we again checked whether during the interaction the
-core situational need remains a meaningful predictor even when taking
-other fundamental psychological needs into account. We find that the
-core need fulfillment adds significantly above a model with only the
-self-determination theory needs (random slopes models; \(\chi^2\)(6,
-\textit{N} = 108) = 22.90, \textit{p} \textless{} .001). We find that
-the core need fulfillment explained the most variance in outgroup
-attitudes after an outgroup contact (\textit{b} = 0.08, \textit{t}(823)
-= 2.95, \textit{p} = 0.003, \textit{95\%CI}{[}0.03, 0.13{]}). When
-compared to the model with only the SDT needs, the core need fulfillment
-flexibly takes on some of the explained variance of all of the three
-fundamental needs. However, different from the first study, relatedness
-(\textit{b} = 0.07, \textit{t}(823) = 4.26, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.04, 0.10{]}) and autonomy (\textit{b} = 0.02,
-\textit{t}(823) = 0.93, \textit{p} = 0.353, \textit{95\%CI}{[}-0.02,
-0.08{]}) also predicted positive outgroup attitudes in this larger
-sample. For full results see \tblref{tab:robustnessTblLong} and
-\fgrref{fig:Robustness}, and Online Supplementary Material A. This means
-that also within this second sample, the fulfillment of psychological
-needs during intergroup contact remained a key predictor of positive
-outgroup attitudes, even when taking into account several alternative
-models.
+Secondly, to assess whether the need fulfillment mechanism affected by
+whether the interaction was accidental or planned we ran an exploratory
+moderation analysis using the participants' ratings of how much they
+perceived the interaction as `accidental'. It should be noted that we
+asked our participants to focus on most the important interaction (i.e.,
+``\textit{The following questions will be about the interaction \underline{you consider most significant}.}'''\,'\,``;
+emphasis as in original). We again start our analysis approach by
+assessing the model across all three studies, using a three-level
+hierarchical model. In this overall model, we retain the main effect of
+core need fulfillment (random slopes model, grand-mean standardized to
+account for all levels of variance; \textit{b} = 2.87, \textit{t}(
+7.979) = 7.32, \textit{p} \textless{} .001, \textit{95\%CI}{[} 2.10,
+3.64{]}) but neither contact intend nor the moderation effect affect the
+results (all \textbar{}\textit{b}\textbar{} \textless{} 0.27 and all
+\textit{p} \textgreater{} 0.225; see \tblref{tab:robustnessTblLong} for
+full results).
 
-\subsubsection{Study 3}
+We again sought to ensure that the results were not affected by scaling
+issues by additionally assessing the interaction intentionality model
+within each of the three studies. Within each of the three studies, the
+effect of core need fulfillemnt became even clearer (all
+\textbar{}\textit{b}\textbar{} \textgreater{} 0.13, all \textit{p}
+\textless{} 0.006). But in none of the studies neither outgroup contact
+intention nor the moderation effect explained a significant amount of
+variance in outgroup attitudes (all \textbar{}\textit{b}\textbar{}
+\textless{} 0.03 and all \textit{p} \textgreater{} 0.073; also see
+\tblref{tab:robustnessTblLong}). There is thus consistent evidence that
+need fulfillment is related to outgroup attitudes, even when taking the
+intentionality of the interaction into account --- at least in our three
+samples and with a focus on the most significant interactions.
 
-As with the previous two studies, we checked for alternative models of
-the key need fulfillment. First, when considering generalized
-situational core need fulfillment together with whether an intergroup
-contact took place, we find that there is no significant main effect of
-core need fulfillment (random slopes model; \textit{b} = 0.03,
-\textit{t}(3,835) = 1.51, \textit{p} = 0.131, \textit{95\%CI}{[}-0.01,
-0.06{]}) but a stronger interaction effect of core need fulfillment and
-outgroup contact (\textit{b} = 0.17, \textit{t}(3,835) = 7.32,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.12, 0.21{]}). Together
-with a significant main effect of having an outgroup contact (\textit{b}
-= 5.41, \textit{t}(3,835) = 6.36, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}3.74, 7.08{]}), this indicates that it is not key need
-fulfillment in general --- but key need fulfillment during an outgroup
-contact that predicts more positive outgroup attitudes. This finding is
-consistent with the results of the previous studies.
+\subsubsection{Well-being outcome}
 
-In a final step, we again checked whether during the interaction the
-core situational need remains a meaningful predictor even when taking
-other fundamental psychological needs into account. We find that the
-core need fulfillment adds additional variance above a model with only
-the self-determination theory needs (random slopes models; \(\chi^2\)(6,
-\textit{N} = 70) = 100.20, \textit{p} \textless{} .001). We find that
-the core need explains the most variance in outgroup attitudes after an
-outgroup contact (\textit{b} = 0.15, \textit{t}(1,598) = 3.88,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.22{]}). When
-compared to the model with only the SDT needs, the core need fulfillment
-flexibly takes on some of the explained variance of all of the three
-fundamental needs. However, similar to the previous study, in this large
-sample relatedness (\textit{b} = 0.05, \textit{t}(1,598) = 3.31,
-\textit{p} \textless{} .001, \textit{95\%CI}{[}0.02, 0.09{]}),
-competence (\textit{b} = 0.06, \textit{t}(1,598) = 2.73, \textit{p} =
-0.006, \textit{95\%CI}{[}0.02, 0.10{]}) and autonomy (\textit{b} = 0.04,
-\textit{t}(1,598) = 2.12, \textit{p} = 0.034, \textit{95\%CI}{[}-0.01,
-0.08{]}) each also predicted positive outgroup attitudes independently.
-This being said, the regression coefficient for the core need was three
-times larger (with all scaling being equal). For full results see
-\tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness} as well as
-Online Supplementary Material A.
+Thirdly, to build a stronger case for the relevance of need fulfillment
+to minority group members, we exploratorily assessed the effect of need
+fulfilling outgroup interactions on self-reported well-being. We, thus,
+re-ran our main analysis but substituted the outgroup attitudes outcome
+with situational well-being. As with the previous robustness analyses,
+we begin with a global three-level hierarchical model (across the three
+studies). We find that need fulfillment during outgroup contacts,
+indeed, has a similar effect on experienced well-being (random slopes
+model, grand-mean standardized to account for all levels of variance;
+\textit{b} = 3.50, \textit{t}(4.219) = 6.33, \textit{p} = 0.003,
+\textit{95\%CI}{[} 2.42, 4.58{]}). We found the same result when we
+assessed each of the three studies individually. In each of the studies
+situational need fulfillment during the outgroup interaction was related
+with higher well-being ratings by the participants (random slopes model,
+centered within participants; all \textbar{}\textit{b}\textbar{}
+\textgreater{} 0.10, all \textit{p} \textless{} 0.009). We, thus, find
+consistent and meaningful evidence that need fulfilling outgroup
+interactions also relate to higher everyday well-being.
+
+\subsubsection{Need types}
+
+\paragraph{overall}
+
+Fourthly, to assess the role of different types of motives reported by
+our participants, we added our coding of practical and psychological
+goal-directedness as additional predictors to our base model. We thus
+had core need fulfillment predicting outgroup attitudes while also
+accounting for whether the reported motives were capturing practical
+and/or psychological motives. We again ran a global model, across the
+three studies first. We found that core need fulfillment remain a core
+predictor of outgroup attitudes (random slopes model, grand-mean
+standardized to account for all levels of variance; \textit{b} = 2.27,
+\textit{t}( 48.194) = 2.72, \textit{p} = 0.009, \textit{95\%CI}{[} 0.63,
+3.90{]}), even after accounting for different types of motives. None of
+the motive types nor the moderation effects reached statistical
+significance within the overall analysis (all
+\textbar{}\textit{b}\textbar{} \textless{} 1.45 and all \textit{p}
+\textgreater{} 0.073; see \tblref{tab:robustnessTblLong} for full
+results).
+
+\paragraph{Study follow-up}
+
+When looking at the individual studies, we again saw that the effect of
+core need fulfillemnt remained the on only clear effect (all
+\textbar{}\textit{b}\textbar{} \textgreater{} 0.14, all \textit{p}
+\textless{} 0.015). Additionally, in none of the studies neither motive
+type dummies nor the moderation effect explained a significant amount of
+variance in outgroup attitudes (all \textbar{}\textit{b}\textbar{}
+\textless{} 1.53 and all \textit{p} \textgreater{} 0.144; also see
+\tblref{tab:robustnessTblLong}). We, thus, find consistent evidence that
+need fulfillment is related to outgroup attitudes, even when taking the
+type of need into account --- at least in our three samples.
+
+\subsubsection{Specific psychological needs}
+
+In a final step, we checked whether during the interaction the core
+situational need remains a meaningful predictor even when taking other
+fundamental psychological needs into account. We again take a two-step
+approach, starting with cross-study global three-level test and then
+assessing the effects within the individual studies. Within the overall
+model we find that across the studies core need fulfillment remained a
+strong predictor of outgroup attitudes, even after controlling for the
+three self-determination theory need (random slopes model, grand-mean
+standardized to account for all levels of variance; \textit{b} = 1.88,
+\textit{t}(2.705) = 4.75, \textit{p} = 0.022, \textit{95\%CI}{[} 1.11,
+2.66{]}). Within this overall analysis, none of the self-determination
+theory needs independently predicted outgroup attitudes to a
+statistically significant extent (all \textit{p} \textgreater{} 0.095).
+However, some of the effect sizes were largely comparable to that of the
+core need fulfillment (all \textbar{}\textit{b}\textbar{} \textless{}
+2.10, particularly that of relatedness fulfillment; see
+\tblref{tab:robustnessTblLong} for full results).
+
+When looking at the individual studies, we again saw that core need
+fulfillemnt remained a consistent predictor of outgroup attitudes, even
+after accounting for the self-determination theory need (all
+\textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all \textit{p}
+\textless{} 0.033). However, across all three studies the fulfillment of
+relatedness motives also emerged as a consistent predictor of outgroup
+attitudes (all \textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all
+\textit{p} \textless{} 0.001). Additionally, in the larger studies 2 and
+3 competence fulfillment was also related to more positive outgroup
+attitudes (study 2: \textit{b} = 0.05, \textit{t}(841.8) = 2.43,
+\textit{p} = 0.015, \textit{95\%CI}{[} 0.01, 0.10{]}, study 3:
+\textit{b} = 0.06, \textit{t}(30.20) = 2.62, \textit{p} = 0.013,
+\textit{95\%CI}{[} 0.01, 0.10{]}). None of the autonomy fulfillment
+effects reached statistical significance nor did the competence
+fulfillment during study 1 (see \tblref{tab:robustnessTblLong} for the
+full results). In short, find that across our samples, relatedness
+fulfillment (and to a smaller extend competence fulfillment) are
+instrumental in understanding when an outgroup contact leads to more
+positive outgroup attitudes. Importantly, even when considering these
+effects situational core need fulfillment remains a strong and
+consistent predictor of outgroup attitudes. In some cases, we even find
+that core need fulfillment takes on some of the variance that would
+otherwise be explained by the self-determination theory needs (see
+Online Supplemental Material A).

### 2023-05-26 manuscript.tex
coding protocol filled

@@
 % Title and header
-\title{Psychological Needs During Intergroup Contact: Three Experience Sampling Studies}
+\title{Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies}
 \shorttitle{Needs in Intergroup Contact}
@@
 A third limitation lies in the outcome variable we chose.
-As we have focused on outgroup attitudes to ensure comparability to the past literature of the contact hypothesis and to replicate the most reliable patterns within ESM data \citep[][]{pettigrew2006}.
+As we have focused on outgroup attitudes to ensure comparability to the past literature of the contact hypothesis and to replicate the most reliable patterns within ESM data \citep[][]{Pettigrew2006}.
 However, especially for disadvantaged minority members positive outgroup attitudes may entail negative downstream consequences such as a reduced endorsement of social change --- even in the face of injustice \citep[e.g.,][]{dixon2012}.
@@
 As with the main analyses, we use a forest plot and the associated meta-analytic estimates to assess the stability of the results across the three studies.
-The forest plot shows that the core need fulfillment is also consistently outgroup contact specific (\fgrref[-A]{fig:Robustness}) and remains a meaningful predictor of outgroup attitudes even when controlling for traditional psychological need fulfillments (Figure \fgrref[-B]{fig:Robustness}).
+The forest plot shows that the core need fulfillment is also consistently outgroup contact specific (\fgrref[-A]{fig:Robustness}) and remains a meaningful predictor of outgroup attitudes even when controlling for traditional psychological need fulfillments (\fgrref[-B]{fig:Robustness}).
 In sum, we thus find that across all three studies, psychological need fulfillment remained a robust and flexible predictor of positive outgroup attitudes.

### 2023-05-26 manuscript.tex
wording

@@
 As an example, if someone seeks acceptance by their interaction partner, and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
-To test this proposal, we collected three sets of real-life data from recent immigrants, assessing their daily interactions with majority group members, tracking situational needs, interaction quality, well-being, and outgroup attitudes.
+To test this idea, we collected three sets of real-life data from recent immigrants, assessing their daily interactions with majority group members, tracking situational needs, interaction quality, well-being, and outgroup attitudes.
 
@@
 % neither are necessary nor explain why an interaction is positive
-\sout{Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.} When it comes to what constitutes a positive interaction the most widely used approach has been the idea that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact effect \citep[][]{Allport1954b, Pettigrew1969}.
+% Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
+When it comes to what constitutes a positive interaction the most widely used approach has been the idea that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact effect \citep[][]{Allport1954b, Pettigrew1969}.
 However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be necessary to finding positive effects of intergroup contact \citep[][]{Pettigrew2006}.
@@
 Social identity theory has famously focused on the role of self-esteem needs in understanding how people navigate intergroup contexts \citep[e.g.,][]{abrams1988}.
-A more recent example is the study of conflict and reconciliation where addressing differential needs of victims and perpetrators (i.e., the need for power and the need for morality respectively) increased willingness to reconcile \citep[][]{Shnabel2008}.
+In the study of conflict and reconciliation, addressing differential needs of victims and perpetrators (i.e., the need for power and the need for morality respectively) increased willingness to reconcile \citep[][]{Shnabel2008}.
 And similarly, addressing a relevant need for identity continuity among refugees in Turkey bolstered resilience in the face of discrimination experiences \citep[][]{Celebi2017}.
@@
 
-It is thus not surprising that in their perspectives paper on intergroup contact, Dovidio and colleagues propose that: "To achieve truly constructive intergroup relations, it is important that intergroup exchanges meet the psychological needs of both majority- and minority-group members." \citep[][p.
+It is thus not surprising that Dovidio and colleagues propose that: "To achieve truly constructive intergroup relations, it is important that intergroup exchanges meet the psychological needs of both majority- and minority-group members." \citep[][p.
 6]{Dovidio2017}.
@@
 The content could, for example, include physical motives (such as safety or hygiene) but also psychosocial motives \citep[such as acceptance or competence; e.g., see][]{pittman2007}.
-A need arises when a motive is thwarted or situationally active and relevant \citep[][]{leander2020, lewin1926e, gollwitzer1985e}.
+The experience of needing is a more general process that arises when any important motive is thwarted or situationally active and relevant \citep[][]{leander2020, lewin1926e, gollwitzer1985e}.
 It is this perceived need and the perceived fulfillment of needs that we focus on in this article.
@@
 
-To test such a proposal we can rely on adaptive and responsive survey designs that allow a tailored approach based on the participants' inputs \citep[e.g.,][]{Tourangeau2017}.
+To test such a proposal, we can rely on adaptive and responsive survey designs that allow a tailored approach based on the participants' inputs \citep[e.g.,][]{Tourangeau2017}.
 In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., name the situationally relevant need content), and with reference to their own response, the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment mechanism).
@@
 \citet[][]{MacInnis2015} have even pointed out that these two approaches tend to find conflicting effects --- where individual interactions (in the lab) have more negative effects and recall of real-world contact patterns have more positive effects for intergroup relations.
-We, thus, miss data that follows people in their diverse daily interactions and investigates the psychological mechanisms of contacts, especially as they compound over time.
+We, thus, miss data following people in their diverse daily interactions and investigates the psychological mechanisms of contacts, especially as they compound over time.
 Even with extended intervention studies, the most fine-grained data available is usually limited to pre-post-control designs.
@@
 
-In this appendix, we present the two additional robustness analyses that we conducted within each of the three studies.
-These analyses are specifically designed to check for alternative need models and to check that the effect of situation core need fulfillment is contact-specific.
-(1) To check for the role of alternate psychological needs, we add the fulfillment of self-determination theory needs (i.e., competence, autonomy, and relatedness) to the multi-level regression.
-We then also compare the model with models that predicts outgroup attitudes from self-determination theory need fulfillments or core need fulfillments only.
-(2) To ensure that the core need fulfillment is outgroup contact specific, we return to the full sample of intensive longitudinal measurements within each study and test whether there is an interaction effect of outgroup contact (vs.
+In this appendix, we present the empirical details of our additional robustness analyses.
+These analyses are specifically designed to check for alternative models and contextualize our results.
+We (1) check whether core need fulfillment is indeed outgroup contact specific.
+For this analysis, we return to the full sample of intensive longitudinal measurements and test whether there is an interaction effect of outgroup contact (vs.
 no outgroup contact) and core need fulfillment.
 We expect that the effect of core need fulfillment is specific to outgroup interactions and not merely due to a more need-fulfilled life in general.
+We then check (2) whether the need mechanism is relevant to both planned and accidental outgroup interactions, and (3) extends to the more individual-focused experience of well-being.
+In a final set of analyses, we (4) check whether the need fulfillment mechanism is relevant to different types of need content (i.e., motives) and (5) remains relevant even when accounting for the fulfillment of fundamental psychological needs (i.e., self-determination theory needs: competence, autonomy, and relatedness).
 
@@
 
-\subsection{Stability and Conclusion}
-As with the main analyses, we use a forest plot and the associated meta-analytic estimates to assess the stability of the results across the three studies.
-The forest plot shows that the core need fulfillment is also consistently outgroup contact specific (\fgrref[-A]{fig:Robustness}) and remains a meaningful predictor of outgroup attitudes even when controlling for traditional psychological need fulfillments (\fgrref[-B]{fig:Robustness}).
-In sum, we thus find that across all three studies, psychological need fulfillment remained a robust and flexible predictor of positive outgroup attitudes.
+\subsection{Conclusion}
+Across the wide variety of robustness analyses, we thus find that the experience of psychological need fulfillment is a robust and flexible predictor of positive outgroup attitudes even when accounting for a range of other and even alternate predictors.
+However, we also find that the core need fulfillment mechanism does not account for all need-related variance in outgroup attitudes.
+Notably, the fulfillment of relatedness (and to some extent competence) needs explained additional variance in outgroup attitudes.
+Nonetheless, the situational core need fulfillment remained extremely reliably a core predictor of outgroup attitudes.
 
@@
 
-\begin{figure}
-  \caption{Robustness Analyses}
-  \label{fig:Robustness}
-  \centering\includegraphics[width=\textwidth]{Figures/forestParametricRobustnessComb.png}
-  %\begin{subfigure}{\textwidth}
-  %  \caption{}
-  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
-  %\end{subfigure}
-  %\begin{subfigure}{\textwidth}
-  %  \caption{}
-  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
-  %\end{subfigure}
-  \caption*{Note: \\
-  (a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).\\
-  (b) Core Need Fulfillment predicting Outgroup Attitudes while controlling for self-determination theory needs (intergroup contact sample).\\
-  General: Random effects meta-analytic results are presented for completeness.}
-\end{figure}
+% \begin{figure}
+%   \caption{Robustness Analyses}
+%   \label{fig:Robustness}
+%   \centering\includegraphics[width=\textwidth]{Figures/forestParametricRobustnessComb.png}
+%   %\begin{subfigure}{\textwidth}
+%   %  \caption{}
+%   %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
+%   %\end{subfigure}
+%   %\begin{subfigure}{\textwidth}
+%   %  \caption{}
+%   %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
+%   %\end{subfigure}
+%   \caption*{Note: \\
+%   (a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).\\
+%   (b) Core Need Fulfillment predicting Outgroup Attitudes while controlling for self-determination theory needs (intergroup contact sample).\\
+%   General: Random effects meta-analytic results are presented for completeness.}
+% \end{figure}
 

### 2023-05-26 Methods-and-Results.Rmd
robustness reports in main text

@@
 To check for spurious relationships, we test three additional models.
-These three models assess whether the effect is indeed specific to intergroup contact, whether the need fulillment effect is a affected by whether the contact was planned or accidental, and whether the motivational mechanism also holds direct well-being benefits for the minority members.
+These three models assess whether the effect is indeed specific to intergroup contact, whether the need fulfillment effect is a affected by whether the contact was planned or accidental, and whether the motivational mechanism also holds direct well-being benefits for the minority members.
 We describe the full methods and results for the robustness analyses in \appref{app:AppendixRobustness}.
@@
 We expected that the effect of core need fulfillment on outgroup attitudes is specific to outgroup interactions and not merely due to a more need-fulfilled life in general.
-We find that \hl{...}.
+Both in the global test, as well as in the individual studies, we consistently find a significant and meaningful interaction effect of outgroup interaction and key need fulfillment, indicating that key need fulfillment is specifically a powerful predictor of outgroup attitudes during intergroup contacts.
+When assessing the individual studies independently, we additionally find a strong main effect of contact as well as a smaller main effect of key need fulfillment, qualifying the contact-specific relationship (see \appref{app:AppendixRobustness} for full results).
+In sum, we thus find that at the effect of key need fulfillment on outgroup attitudes is particularly important for outgroup interactions (rather than only need fulfillment in general).
 
@@
 To test whether the need mechanism was affected by whether the interaction was accidental or planned we ran an exploratory moderation analysis using the participants' ratings of how much they perceived the interaction as 'accidental'.
-It should be noted at this point, that in order to keep the ESM surveys short, we asked our participants to focus on most the important interaction (i.e., "\textit{The following questions will be about the interaction \underline{you consider most significant}.}"''"; emphasis as in original).
+It should be noted that, in order to keep the ESM surveys short, we asked our participants to focus on most the important interaction (i.e., "\textit{The following questions will be about the interaction \underline{you consider most significant}.}"; emphasis as in original).
 This was also reflected in a relatively low average and consistent right skew of the 'accidental' item.
 Nonetheless, there remained a substantial variance in the item and we continued with the moderation analysis.
-We find that \hl{...}.
+We found that both in the overall test as in all studies individually key need fulfillment remained a strong predictor of outgroup attitudes, even when accounting for differences in whether the interaction was accidental (rather than planned).
+Moreover, in none of the analysis did we see a moderation effect of interaction intend nor did we find a main effect of interaction intend.
+There is, thus, consistent evidence that the need fulfillment mechanism was not meaningfully different for more accidental interactions.
 
@@
 Experienced well-being is a common indicator of health and an important life quality measurement in itself, especially for migrants or other minority groups \citep[e.g.,][]{bhugra2011}.
-We find that \hl{...}.
-The analysis, thus, adds weight to the importance of considering the need fulfillment experiences when it comes to outgroup interactions.
+We find that the results with well-being as the outcome variable mirror our main results in effect size and interpretation.
+The results are consistent across and within studies and, thus, add weight to the importance of considering the need fulfillment experiences when it comes to outgroup interactions.
 
@@
 With practical motives we refer to specific, tangible goals or tasks that participants aimed to accomplish during the interaction.
-These instrumental goals are usually observable, concrete, and often centered on external outcomes, such as acquiring resources, completing tasks, and addressing immediate challenges \citep[][]{}.
+These instrumental goals are usually observable, concrete, and often centered on external outcomes, such as acquiring resources, completing tasks, and addressing immediate challenges \citep[e.g.,][]{oduntan2019}.
 With psychological motives we refer to underlying motives or desires that are more abstract and relate to personal fulfillment and well-being.
 In contrast to practical needs, psychological needs delve into the subjective and internal aspects of human experiences.
-These needs pertain to emotions, social connections, and cognitive processes, reflecting individuals' quest for personal growth, well-being, and thriving in social relationships \citep[][]{}.
+These needs pertain to emotions, social connections, and cognitive processes, reflecting individuals' quest for personal growth, well-being, and thriving in social relationships \citep[e.g.,][]{dweck2017}.
 Note that with this approach any particular motive can include a practical and/or a psychological goal-directedness but can also be classified as not having any goal at all.
-
-For each of the topics, we had identified in the topic modeling analysis, we extracted the top 10 most indicative words as well as the three most representative free text responses.
-Using a detailed coding protocol for both the practical as well as the psychological motives, two independent coders rated each of the 47 topics.
-This allowed us to add the two dimensions back to each of the reported interaction motives and assess the distributions and effects of the goal-directed character.
-We found that \hl{...}.
+We found high inter-rater reliability for the two independent coders, who coded all 47 topics.
+The codings revealed considerable variance, which allowed us to add the two dimensions back to each of the reported interaction motives and assess the effects of the goal-directed character.
+
+We found that neither in the overall analysis nor within any of the individual studies did different types of motives impact the positive effect of situational need fulfillment on outgroup attitudes.
+Situational need fulfillment ratings remained the only reliable predictor of outgroup attitudes, when controlling for practical and psychological goal-directedness as well as their interaction effect with the need fulfillment itself.
+This result underscores the importance of the experience of perceived need fulfillment (i.e., the perception that one got what one needed), rather than the type of need or the content of the need (i.e., the exact motive).
 
@@
 Finally, to ensure that a much simpler model of three fundamental psychological needs might not account for the same effect, we compared our situation core need fulfillment measurement to the three self-determination theory needs (autonomy, relatedness, competence).
+Within the overall model we found that across the studies core need fulfillment remained a strong predictor of outgroup attitudes, even after controlling for the three self-determination theory need.
+Additionally, within this overall analysis, none of the self-determination theory needs independently predicted outgroup attitudes to a statistically significant extent (despite similar effect sizes of relatedness).
+When looking at the individual studies, we again saw that core need fulfillment remained a consistent predictor of outgroup attitudes.
+However, across all three studies the fulfillment of relatedness motives also emerged as a consistent predictor of outgroup attitudes.
+Additionally, in the larger studies 2 and 3 competence fulfillment was also related to more positive outgroup attitudes.
+None of the autonomy fulfillment effects reached statistical significance.
+In short, find that across our samples, relatedness fulfillment (and to a smaller extend competence fulfillment) are instrumental in understanding when an outgroup contact leads to more positive outgroup attitudes.
+Importantly, even when considering these effects situational core need fulfillment remains a strong and consistent predictor of outgroup attitudes.
 

### 2023-05-26 Methods-and-Results.tex
robustness reports in main text

@@
 These three models assess whether the effect is indeed specific to
-intergroup contact, whether the need fulillment effect is a affected by
+intergroup contact, whether the need fulfillment effect is a affected by
 whether the contact was planned or accidental, and whether the
@@
 interactions and not merely due to a more need-fulfilled life in
-general. We find that \hl{...}.
+general. Both in the global test, as well as in the individual studies,
+we consistently find a significant and meaningful interaction effect of
+outgroup interaction and key need fulfillment, indicating that key need
+fulfillment is specifically a powerful predictor of outgroup attitudes
+during intergroup contacts. When assessing the individual studies
+independently, we additionally find a strong main effect of contact as
+well as a smaller main effect of key need fulfillment, qualifying the
+contact-specific relationship (see \appref{app:AppendixRobustness} for
+full results). In sum, we thus find that at the effect of key need
+fulfillment on outgroup attitudes is particularly important for outgroup
+interactions (rather than only need fulfillment in general).
 
@@
 analysis using the participants' ratings of how much they perceived the
-interaction as `accidental'. It should be noted at this point, that in
-order to keep the ESM surveys short, we asked our participants to focus
-on most the important interaction (i.e.,
-``\textit{The following questions will be about the interaction \underline{you consider most significant}.}'''```;
+interaction as `accidental'. It should be noted that, in order to keep
+the ESM surveys short, we asked our participants to focus on most the
+important interaction (i.e.,
+``\textit{The following questions will be about the interaction \underline{you consider most significant}.}'';
 emphasis as in original). This was also reflected in a relatively low
-average and consistent right skew of the 'accidental' item. Nonetheless,
+average and consistent right skew of the `accidental' item. Nonetheless,
 there remained a substantial variance in the item and we continued with
-the moderation analysis. We find that \hl{...}.
+the moderation analysis. We found that both in the overall test as in
+all studies individually key need fulfillment remained a strong
+predictor of outgroup attitudes, even when accounting for differences in
+whether the interaction was accidental (rather than planned). Moreover,
+in none of the analysis did we see a moderation effect of interaction
+intend nor did we find a main effect of interaction intend. There is,
+thus, consistent evidence that the need fulfillment mechanism was not
+meaningfully different for more accidental interactions.
 
@@
 for migrants or other minority groups \citep[e.g.,][]{bhugra2011}. We
-find that \hl{...}. The analysis, thus, adds weight to the importance of
-considering the need fulfillment experiences when it comes to outgroup
-interactions.
+find that the results with well-being as the outcome variable mirror our
+main results in effect size and interpretation. The results are
+consistent across and within studies and, thus, add weight to the
+importance of considering the need fulfillment experiences when it comes
+to outgroup interactions.
 
@@
 centered on external outcomes, such as acquiring resources, completing
-tasks, and addressing immediate challenges \citep[][]{}. With
-psychological motives we refer to underlying motives or desires that are
-more abstract and relate to personal fulfillment and well-being. In
-contrast to practical needs, psychological needs delve into the
-subjective and internal aspects of human experiences. These needs
-pertain to emotions, social connections, and cognitive processes,
+tasks, and addressing immediate challenges \citep[e.g.,][]{oduntan2019}.
+With psychological motives we refer to underlying motives or desires
+that are more abstract and relate to personal fulfillment and
+well-being. In contrast to practical needs, psychological needs delve
+into the subjective and internal aspects of human experiences. These
+needs pertain to emotions, social connections, and cognitive processes,
 reflecting individuals' quest for personal growth, well-being, and
-thriving in social relationships \citep[][]{}. Note that with this
-approach any particular motive can include a practical and/or a
-psychological goal-directedness but can also be classified as not having
-any goal at all.
+thriving in social relationships \citep[e.g.,][]{dweck2017}. Note that
+with this approach any particular motive can include a practical and/or
+a psychological goal-directedness but can also be classified as not
+having any goal at all. We found high inter-rater reliability for the
+two independent coders, who coded all 47 topics. The codings revealed
+considerable variance, which allowed us to add the two dimensions back
+to each of the reported interaction motives and assess the effects of
+the goal-directed character.
 
-For each of the topics, we had identified in the topic modeling
-analysis, we extracted the top 10 most indicative words as well as the
-three most representative free text responses. Using a detailed coding
-protocol for both the practical as well as the psychological motives,
-two independent coders rated each of the 47 topics. This allowed us to
-add the two dimensions back to each of the reported interaction motives
-and assess the distributions and effects of the goal-directed character.
-We found that \hl{...}.
+We found that neither in the overall analysis nor within any of the
+individual studies did different types of motives impact the positive
+effect of situational need fulfillment on outgroup attitudes.
+Situational need fulfillment ratings remained the only reliable
+predictor of outgroup attitudes, when controlling for practical and
+psychological goal-directedness as well as their interaction effect with
+the need fulfillment itself. This result underscores the importance of
+the experience of perceived need fulfillment (i.e., the perception that
+one got what one needed), rather than the type of need or the content of
+the need (i.e., the exact motive).
 
@@
 self-determination theory needs (autonomy, relatedness, competence).
+Within the overall model we found that across the studies core need
+fulfillment remained a strong predictor of outgroup attitudes, even
+after controlling for the three self-determination theory need.
+Additionally, within this overall analysis, none of the
+self-determination theory needs independently predicted outgroup
+attitudes to a statistically significant extent (despite similar effect
+sizes of relatedness). When looking at the individual studies, we again
+saw that core need fulfillment remained a consistent predictor of
+outgroup attitudes. However, across all three studies the fulfillment of
+relatedness motives also emerged as a consistent predictor of outgroup
+attitudes. Additionally, in the larger studies 2 and 3 competence
+fulfillment was also related to more positive outgroup attitudes. None
+of the autonomy fulfillment effects reached statistical significance. In
+short, find that across our samples, relatedness fulfillment (and to a
+smaller extend competence fulfillment) are instrumental in understanding
+when an outgroup contact leads to more positive outgroup attitudes.
+Importantly, even when considering these effects situational core need
+fulfillment remains a strong and consistent predictor of outgroup
+attitudes.

### 2023-05-26 Robustness-Methods-and-Results.Rmd
robustness reports in main text

@@
 We start this test by assessing the effect across all three studies, using a three-level hierarchical model, where measurements are nested within participants, and participants are nested within studies.
-In this overall model, we found no main effect of core need fulfillment (random slopes model, grand-mean standardized to account for all levels of variance; `r get_latex_coef(contact_overall$lmer_coef, "CoreNeed")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r get_latex_coef(contact_overall$lmer_coef, "CoreNeed:OutgroupInteraction")`; also see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}).
+In this overall model, we found no main effect of core need fulfillment (random slopes model, grand-mean standardized to account for all levels of variance; `r get_latex_coef(contact_overall$lmer_coef, "CoreNeed")`) but a significant interaction effect of core need fulfillment and outgroup contact (`r get_latex_coef(contact_overall$lmer_coef, "CoreNeed:OutgroupInteraction")`; also see \tblref{tab:robustnessTblLong}).
 While the three-level hierarchical model can be sensitive to scaling issues, this already indicates that it is not key need fulfillment in general --- but only key need fulfillment during an outgroup contact that predicts more positive outgroup attitudes.
@@
 To ensure that the results are not affected by scaling issues (e.g., study-level variances suppressing person-level variances) or a similar Simpson's paradox, we additionally assess the model within each of the three studies.
-Within each of the three studies, the effects are more pronounced, so that we also see a significant effect of core need fulfillemnt (all \textit{b} > `r min(abs(contact_study_coef[contact_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r max(contact_study_coef[contact_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)`) as well as outgroup contact itself (all |\textit{b}| > `r min(abs(contact_study_coef[contact_study_coef$coef == "OutgroupInteraction", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r max(contact_study_coef[contact_study_coef$coef == "OutgroupInteraction", "p"]) %>% round(3) %>% format(nsmall=3)`) but the interaction effect consistently remains the most reliable predictor of outgroup attitudes (all |\textit{b}| > `r min(abs(contact_study_coef[contact_study_coef$coef == "CoreNeedC:OutgroupInteraction", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r max(contact_study_coef[contact_study_coef$coef == "CoreNeedC:OutgroupInteraction", "p"]) %>% round(3) %>% format(nsmall=3)`, also see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}).
+Within each of the three studies, the effects are more pronounced, so that we also see a significant effect of core need fulfillment (all \textit{b} > `r min(abs(contact_study_coef[contact_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r max(contact_study_coef[contact_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)`) as well as outgroup contact itself (all |\textit{b}| > `r min(abs(contact_study_coef[contact_study_coef$coef == "OutgroupInteraction", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r max(contact_study_coef[contact_study_coef$coef == "OutgroupInteraction", "p"]) %>% round(3) %>% format(nsmall=3)`) but the interaction effect consistently remains the most reliable predictor of outgroup attitudes (all |\textit{b}| > `r min(abs(contact_study_coef[contact_study_coef$coef == "CoreNeedC:OutgroupInteraction", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r max(contact_study_coef[contact_study_coef$coef == "CoreNeedC:OutgroupInteraction", "p"]) %>% round(3) %>% format(nsmall=3)`, also see \tblref{tab:robustnessTblLong}).
 There is thus consistent evidence that need fulfillment relates to outgroup attitudes for outgroup contacts in particular but not need fulfillment in general.
@@
 We again sought to ensure that the results were not affected by scaling issues by additionally assessing the interaction intentionality model within each of the three studies.
-Within each of the three studies, the effect of core need fulfillemnt became even clearer (all |\textit{b}| > `r min(abs(accidental_study_coef[accidental_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(accidental_study_coef[accidental_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(accidental_study_coef[accidental_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3))`).
+Within each of the three studies, the effect of core need fulfillment became even clearer (all |\textit{b}| > `r min(abs(accidental_study_coef[accidental_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(accidental_study_coef[accidental_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(accidental_study_coef[accidental_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3))`).
 But in none of the studies neither outgroup contact intention nor the moderation effect explained a significant amount of variance in outgroup attitudes (all |\textit{b}| < `r max(abs(accidental_study_coef[accidental_study_coef$coef != c("(Intercept)", "CoreNeedC"), "b"])) %>% round(2) %>% format(nsmall=2)` and all \textit{p} > `r min(accidental_study_coef[accidental_study_coef$coef != c("(Intercept)", "CoreNeedC"), "p"]) %>% round(3) %>% format(nsmall=3)`; also see \tblref{tab:robustnessTblLong}).
@@
 
-When looking at the individual studies, we again saw that the effect of core need fulfillemnt remained the on only clear effect (all |\textit{b}| > `r min(abs(need_type_study_coef[need_type_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(need_type_study_coef[need_type_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(need_type_study_coef[need_type_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3))`).
+When looking at the individual studies, we again saw that the effect of core need fulfillment remained the on only clear effect (all |\textit{b}| > `r min(abs(need_type_study_coef[need_type_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(need_type_study_coef[need_type_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(need_type_study_coef[need_type_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3))`).
 Additionally, in none of the studies neither motive type dummies nor the moderation effect explained a significant amount of variance in outgroup attitudes (all |\textit{b}| < `r max(abs(need_type_study_coef[need_type_study_coef$coef != c("(Intercept)", "CoreNeedC"), "b"])) %>% round(2) %>% format(nsmall=2)` and all \textit{p} > `r min(need_type_study_coef[need_type_study_coef$coef != c("(Intercept)", "CoreNeedC"), "p"]) %>% round(3) %>% format(nsmall=3)`; also see \tblref{tab:robustnessTblLong}).
@@
 
-When looking at the individual studies, we again saw that core need fulfillemnt remained a consistent predictor of outgroup attitudes, even after accounting for the self-determination theory need (all |\textit{b}| > `r min(abs(need_sdt_study_coef[need_sdt_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(need_sdt_study_coef[need_sdt_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(need_sdt_study_coef[need_sdt_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3))`).
+When looking at the individual studies, we again saw that core need fulfillment remained a consistent predictor of outgroup attitudes, even after accounting for the self-determination theory need (all |\textit{b}| > `r min(abs(need_sdt_study_coef[need_sdt_study_coef$coef == "CoreNeedC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(need_sdt_study_coef[need_sdt_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(need_sdt_study_coef[need_sdt_study_coef$coef == "CoreNeedC", "p"]) %>% round(3) %>% format(nsmall=3))`).
 However, across all three studies the fulfillment of relatedness motives also emerged as a consistent predictor of outgroup attitudes (all |\textit{b}| > `r min(abs(need_sdt_study_coef[need_sdt_study_coef$coef == "RelatednesssC", "b"])) %>% round(2) %>% format(nsmall=2)`, all \textit{p} < `r ifelse(max(need_sdt_study_coef[need_sdt_study_coef$coef == "RelatednesssC", "p"]) %>% round(3) %>% format(nsmall=3)<.001, ".001", max(need_sdt_study_coef[need_sdt_study_coef$coef == "RelatednesssC", "p"]) %>% round(3) %>% format(nsmall=3))`).
@@
   # Contact specific
-  contact_overall = c(contact_overall$lmer_model, contact_overall$lmer_model_z),
-  contact_s1 = c(contact_s1$lmer_model, contact_s1$lmer_model_z),
-  contact_s2 = c(contact_s2$lmer_model, contact_s2$lmer_model_z),
-  contact_s3 = c(contact_s3$lmer_model, contact_s3$lmer_model_z),
+  contact_overall = c(contact_overall$lmer_model, contact_overall$lmer_model_z, TRUE),
+  contact_s1 = c(contact_s1$lmer_model, contact_s1$lmer_model_z, FALSE),
+  contact_s2 = c(contact_s2$lmer_model, contact_s2$lmer_model_z, FALSE),
+  contact_s3 = c(contact_s3$lmer_model, contact_s3$lmer_model_z, FALSE),
   # Accidental
-  accidental_overall = c(accidental_overall$lmer_model, accidental_overall$lmer_model_z),
-  accidental_s1 = c(accidental_s1$lmer_model, accidental_s1$lmer_model_z),
-  accidental_s2 = c(accidental_s2$lmer_model, accidental_s2$lmer_model_z),
-  accidental_s3 = c(accidental_s3$lmer_model, accidental_s3$lmer_model_z),
+  accidental_overall = c(accidental_overall$lmer_model, accidental_overall$lmer_model_z, TRUE),
+  accidental_s1 = c(accidental_s1$lmer_model, accidental_s1$lmer_model_z, FALSE),
+  accidental_s2 = c(accidental_s2$lmer_model, accidental_s2$lmer_model_z, FALSE),
+  accidental_s3 = c(accidental_s3$lmer_model, accidental_s3$lmer_model_z, FALSE),
   # well-being core
-  wellbeing_core_overall = c(wellbeing_core_overall$lmer_model, wellbeing_core_overall$lmer_model_z),
-  wellbeing_core_s1 = c(wellbeing_core_s1$lmer_model, wellbeing_core_s1$lmer_model_z),
-  wellbeing_core_s2 = c(wellbeing_core_s2$lmer_model, wellbeing_core_s2$lmer_model_z),
-  wellbeing_core_s3 = c(wellbeing_core_s3$lmer_model, wellbeing_core_s3$lmer_model_z),
+  wellbeing_core_overall = c(wellbeing_core_overall$lmer_model, wellbeing_core_overall$lmer_model_z, TRUE),
+  wellbeing_core_s1 = c(wellbeing_core_s1$lmer_model, wellbeing_core_s1$lmer_model_z, FALSE),
+  wellbeing_core_s2 = c(wellbeing_core_s2$lmer_model, wellbeing_core_s2$lmer_model_z, FALSE),
+  wellbeing_core_s3 = c(wellbeing_core_s3$lmer_model, wellbeing_core_s3$lmer_model_z, FALSE),
   # # POTENTIALLT well-being full
@@
   # Need type
-  need_type_overall = c(need_type_overall$lmer_model, need_type_overall$lmer_model_z),
-  need_type_s1 = c(need_type_s1$lmer_model, need_type_s1$lmer_model_z),
-  need_type_s2 = c(need_type_s2$lmer_model, need_type_s2$lmer_model_z),
-  need_type_s3 = c(need_type_s3$lmer_model, need_type_s3$lmer_model_z),
+  need_type_overall = c(need_type_overall$lmer_model, need_type_overall$lmer_model_z, TRUE),
+  need_type_s1 = c(need_type_s1$lmer_model, need_type_s1$lmer_model_z, FALSE),
+  need_type_s2 = c(need_type_s2$lmer_model, need_type_s2$lmer_model_z, FALSE),
+  need_type_s3 = c(need_type_s3$lmer_model, need_type_s3$lmer_model_z, FALSE),
   # Need SDT
-  need_sdt_overall = c(need_sdt_overall$lmer_model, need_sdt_overall$lmer_model_z),
-  need_sdt_s1 = c(need_sdt_s1$lmer_model, need_sdt_s1$lmer_model_z),
-  need_sdt_s2 = c(need_sdt_s2$lmer_model, need_sdt_s2$lmer_model_z),
-  need_sdt_s3 = c(need_sdt_s3$lmer_model, need_sdt_s3$lmer_model_z)
+  need_sdt_overall = c(need_sdt_overall$lmer_model, need_sdt_overall$lmer_model_z, TRUE),
+  need_sdt_s1 = c(need_sdt_s1$lmer_model, need_sdt_s1$lmer_model_z, FALSE),
+  need_sdt_s2 = c(need_sdt_s2$lmer_model, need_sdt_s2$lmer_model_z, FALSE),
+  need_sdt_s3 = c(need_sdt_s3$lmer_model, need_sdt_s3$lmer_model_z, FALSE)
   )
@@
 for (i in 1:length(mdlRobustTblElements)) {
-  mdlRobustPrep[[names(mdlRobustTblElements)[[i]]]] <- lmerTblPrep(mdlRobustTblElements[[i]][[1]], mdlRobustTblElements[[i]][[2]], name = names(mdlRobustTblElements)[[i]])
+  mdlRobustPrep[[names(mdlRobustTblElements)[[i]]]] <- lmerTblPrep(obj = mdlRobustTblElements[[i]][[1]], 
+                                                                   objz = mdlRobustTblElements[[i]][[2]], 
+                                                                   lmer_scale = mdlRobustTblElements[[i]][[3]],
+                                                                   name = names(mdlRobustTblElements)[[i]])
 }
@@
       robustTblLong$coef,
-      from = c("R2Marg_R2Cond"),
-      to = c("$R^2_{marginal}$ / $R^2_{conditional}$")
+      from = c("R2Marg_R2Cond", "practical_need_dum", "psychological_need_dum", "CoreNeed:practical_need_dum", "CoreNeed:psychological_need_dum"),
+      to = c("$R^2_{marginal}$ / $R^2_{conditional}$", "practical need", "psychological need", "CoreNeed:practical need", "CoreNeed:psychological need")
     )
@@
   add_header_above(., c(" ", "Overall" = 2, "Study 1" = 2, "Study 2" = 2, "Study 3" = 2)) %>%
-  pack_rows(index = table(robustTblLong$group)) %>%
+  pack_rows(index = table(factor(robustTblLong$group, levels = unique(robustTblLong$group)))) %>%
   kableExtra::footnote(

### 2023-05-26 scripts/functions/MlTbl.R

@@ -5,9 +5,9 @@ library(plyr)
 # obj <- mdlTblElements[[i]][[1]]
 # objz <- mdlTblElements[[i]][[2]]
 
-lmerTblPrep <- function (obj, objz = NULL, name = NULL, alpha = 0.05, ...) {
+lmerTblPrep <- function (obj, objz = NULL, name = NULL, alpha = 0.05, lmer_scale = FALSE, ...) {
   # Summarize models
-  smry <- summ(obj)
+  smry <- summ(obj, scale = lmer_scale)
   smryZ <- summ(objz)
   
   # save grouing variable

### 2023-05-26 Robustness-Methods-and-Results.tex
robustness reports in main text
typos

@@
 
-\subsubsection{Interaction Intend}
+\subsubsection{Interaction Intent}
 
 To assess whether an interaction was accidental (vs.~planned), we asked
-participants with a single item to report the extend to which ``The
+participants with a single item to report the extent to which ``The
 interaction with -X- was accidental''. The respondents were asked to
@@
 little'' (33) and ``somewhat'' (66), to ``a great deal'' (100). In all
-studies the scale showed a right skew (\textit{mean} = 29.60,
+studies, the scale showed a right skew (\textit{mean} = 29.60,
 \textit{sd} = 33.68).
@@
 account for differences in the types of needs that participants commonly
-reported. With practical motives we refer to specific, tangible goals or
+reported. With practical motives, we refer to specific, tangible goals or
 tasks that participants aimed to accomplish during the interaction.
@@
 tasks, and addressing immediate challenges \citep[][]{}. With
-psychological motives we refer to underlying motives or desires that are
+psychological motives, we refer to underlying motives or desires that are
 more abstract and relate to personal fulfillment and well-being. In
@@
 whether that need was vague (1) or concrete (2). We, thus, collapsed
-these two categories making the ratings binary (need absent vs.~need
+these two categories, making the ratings binary (need absent vs.~need
 present). With the simpler coding, inter-rater agreement for practical
@@
 We measured experienced well-being using a visual analog scale adapted
-from \citet{davies2022}. Participants were asked to respond to the the
+from \citet{davies2022}. Participants were asked to respond to the
 question ``How do you feel right now?'' using a continuous visual slider
@@
 discuss the results in sequential order --- in every case first
-considering the a global test of the model across the three studies and
+considering a global test of the model across the three studies and
 only then assessing whether the global three-level regression model
@@
 \textit{95\%CI}{[} 1.89, 3.00{]}; also see
-\tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}). While the
-three-level hierarchical model can be sensitive to scaling issues, this
-already indicates that it is not key need fulfillment in general --- but
-only key need fulfillment during an outgroup contact that predicts more
-positive outgroup attitudes.
+\tblref{tab:robustnessTblLong}). While the three-level hierarchical
+model can be sensitive to scaling issues, this already indicates that it
+is not key need fulfillment in general --- but only key need fulfillment
+during an outgroup contact that predicts more positive outgroup
+attitudes.
 
@@
 pronounced, so that we also see a significant effect of core need
-fulfillemnt (all \textit{b} \textgreater{} 0.06, all \textit{p}
+fulfillment (all \textit{b} \textgreater{} 0.06, all \textit{p}
 \textless{} 0.005) as well as outgroup contact itself (all
@@
 \textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all \textit{p}
-\textless{} 0.002, also see \tblref{tab:robustnessTblLong} and
-\fgrref{fig:Robustness}). There is thus consistent evidence that need
-fulfillment relates to outgroup attitudes for outgroup contacts in
-particular but not need fulfillment in general.
+\textless{} 0.002, also see \tblref{tab:robustnessTblLong}). There is
+thus consistent evidence that need fulfillment relates to outgroup
+attitudes for outgroup contacts in particular but not need fulfillment
+in general.
 
-\subsubsection{Interaction intend}
+\subsubsection{Interaction intent}
 
@@
 7.979) = 7.32, \textit{p} \textless{} .001, \textit{95\%CI}{[} 2.10,
-3.64{]}) but neither contact intend nor the moderation effect affect the
+3.64{]}) but neither contact intent nor the moderation effect affect the
 results (all \textbar{}\textit{b}\textbar{} \textless{} 0.27 and all
@@
 within each of the three studies. Within each of the three studies, the
-effect of core need fulfillemnt became even clearer (all
+effect of core need fulfillment became even clearer (all
 \textbar{}\textit{b}\textbar{} \textgreater{} 0.13, all \textit{p}
@@
 \textit{95\%CI}{[} 2.42, 4.58{]}). We found the same result when we
-assessed each of the three studies individually. In each of the studies
+assessed each of the three studies individually. In each of the studies,
 situational need fulfillment during the outgroup interaction was related
-with higher well-being ratings by the participants (random slopes model,
+to higher well-being ratings by the participants (random slopes model,
 centered within participants; all \textbar{}\textit{b}\textbar{}
@@
 and/or psychological motives. We again ran a global model, across the
-three studies first. We found that core need fulfillment remain a core
+three studies first. We found that core need fulfillment remains a core
 predictor of outgroup attitudes (random slopes model, grand-mean
@@
 When looking at the individual studies, we again saw that the effect of
-core need fulfillemnt remained the on only clear effect (all
+core need fulfillment remained the on only clear effect (all
 \textbar{}\textit{b}\textbar{} \textgreater{} 0.14, all \textit{p}
@@
 assessing the effects within the individual studies. Within the overall
-model we find that across the studies core need fulfillment remained a
+model, we find that across the studies core need fulfillment remained a
 strong predictor of outgroup attitudes, even after controlling for the
@@
 When looking at the individual studies, we again saw that core need
-fulfillemnt remained a consistent predictor of outgroup attitudes, even
+fulfillment remained a consistent predictor of outgroup attitudes, even
 after accounting for the self-determination theory need (all
 \textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all \textit{p}
-\textless{} 0.033). However, across all three studies the fulfillment of
+\textless{} 0.033). However, across all three studies, the fulfillment of
 relatedness motives also emerged as a consistent predictor of outgroup
@@
 full results). In short, find that across our samples, relatedness
-fulfillment (and to a smaller extend competence fulfillment) are
+fulfillment (and to a smaller extent competence fulfillment) are
 instrumental in understanding when an outgroup contact leads to more

### 2023-05-26 manuscript.tex
typos

@@
 urlcolor     = blue, %Colour for external hyperlinks
-linkcolor    = blue, %Colour of internal links
+linkcolor    = black, %Colour of internal links
 citecolor   = cyan, %Colour of citations
@@
 \title{Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies}
-\shorttitle{Needs in Intergroup Contact}
+\shorttitle{Need Fulfillment in Intergroup Contact}
 
@@
 % Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions, more positive outgroup attitudes, as well as \hl{higher well-being}.
+Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions, more positive outgroup attitudes, as well as higher well-being.
 We find that in all three studies the effect of core need fulfillment on outgroup attitudes was either fully or partially assumed by the effect of interaction quality (when considering partial regression coefficients in a joint model).
@@
   General: Path coefficients are standardized regression coefficients.
-Statistical significance markers are based on the unstandardized regression results (as presented in \tblref{tab:intergroupNeedsTblLong}).\\
+Statistical significance markers are based on the unstandardized regression results (as presented in \tblref{tab:intergroupNeedsTblLong}).
+Note that we do not test a mediation model.
+The path diagram only illustrates the included concepts and partial regression parameters.\\
   **** p < .0001, *** p < .001, ** p < .01, * p < .05}

### 2023-05-26 Methods-and-Results.Rmd
track changes added

@@
 
-\subsubsection{Interaction intend}
+\subsubsection{Interaction intent}
 To test whether the need mechanism was affected by whether the interaction was accidental or planned we ran an exploratory moderation analysis using the participants' ratings of how much they perceived the interaction as 'accidental'.
@@
 We found that both in the overall test as in all studies individually key need fulfillment remained a strong predictor of outgroup attitudes, even when accounting for differences in whether the interaction was accidental (rather than planned).
-Moreover, in none of the analysis did we see a moderation effect of interaction intend nor did we find a main effect of interaction intend.
+Moreover, in none of the analysis did we see a moderation effect of interaction intent nor did we find a main effect of interaction intent.
 There is, thus, consistent evidence that the need fulfillment mechanism was not meaningfully different for more accidental interactions.

### 2023-05-26 Tracked changes/comparison/main.tex
track changes added

--- 2022-01-06 Backup/Before General Test Shortening/manuscript.tex
@@
 % add reference library file
-\addbibresource{references.bib}
+\addbibresource{../../references.bib}
 
@@
 
-\input{Methods-and-Results}
+\section{Study 1}
+
+Based on our main hypotheses, the aim of our first study is to
+specifically test the general contact hypothesis, the influence of core
+need fulfillment, and perceived interaction quality during intergroup
+contacts. To this aim, we conducted an intensive longitudinal survey
+study with recent migrants to the Netherlands. Data was collected from
+May 5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and
+all participants started the study within the first two days).
+
+The full surveys are available in our Online Supplementary Material A
+and the full data description is available in Online Supplementary
+Materials B. Correlations and descriptive statistics of the included
+variables are available in Table \ref{tab:descrFullLong} and Table
+\ref{tab:descrOutLong}.
+
+\subsection{Methods}
+
+\subsubsection{Participants}
+
+After receiving ethical approval from the University of Groningen, we
+recruited 23 migrants using the local paid participant pool and
+specifically targeted non-Dutch migrants to participate in our study.
+Participants reported on their interactions for at least 30 days with
+two daily measures (capturing the morning and afternoon). With this
+design, we aimed at getting 50-60 measurements per participant
+(\textit{M} = 53.26, \textit{SD} = 16.72, \textit{total N} = 1225). This
+is a common number of measurements found in experience sampling studies
+and offers sufficient power to model processes within and between
+participants \citep[e.g., for a systematic review see][]{AanhetRot2012}.
+Participants were compensated for their participation with up to 34
+Euros -- each two Euros for pre- and post-questionnaire as well as 50
+Eurocents for every experience sampling measurement occasion. The sample
+consisted of relatively young, educated, and western migrants from the
+global north (\(M_{age}\) = 24.35, \(SD_{age}\) = 4.73, 19 women, 15
+students). The sample accurately describes one of the largest groups of
+migrants in the region \citep[][]{GemeenteGroningen2015}.
+
+\subsubsection{Procedure}
+
+The study itself consisted of three main parts, an introductory
+pre-measurement, and the daily experience sampling measurements, as well
+as a concluding post-measurement. After giving informed consent,
+participants started by filling in an online pre-questionnaire assessing
+demographics and general information about their immigration. Over the
+next thirty days, the participants then were invited twice a day (at 12
+pm and 7pm) to reflect upon their interactions, psychological need
+fulfillments, and current attitudes towards the Dutch outgroup
+(\textit{median duration} = 2M 22S, \textit{MAD duration} = 1M 19S).
+General compliance was high (85.90\% of all invited surveys were filled
+in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%)}.
+The response rates were approximately equal during mornings (\textit{n}
+= 621) and afternoons (\textit{n} = 604) and most measurements were
+completed within four hours of the invitation. After the final day of
+daily diary measurements, participants were invited to fill in a longer
+post measurement survey that mirrored the pre-measurement. All key
+variables for this study were part of the short daily diary surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+To test the prerequisite effect of intergroup contact, every experience
+sampling measurement started with the question
+``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''.
+Our participants recorded between 2--51 (3.23--91.07\% of individual
+daily diary measurements; 31.59\% of all 1225 daily diary
+responses)\footnote{Two participants only recorded two daily diary measurements each and non of these included outgroup contacts.
+These participants are removed from any analyses including outgroup contacts.}.
+
+\paragraph{Psychological Needs}
+
+Irrespective of whether participants had an interaction with Dutch
+people or not, everyone answered a short series of questions on
+psychological need fulfillment. However, whereas participants with
+interactions reported on the need fulfillment during the interaction,
+people without interactions with Dutch people judged the past daytime
+period in general. To assess the fulfillment of psychological needs, we
+included two types of need measurement: (1) the core situational need
+and (2) general self-determination theory needs.
+
+For the core situational need, we asked participants in an open ended
+text field:
+``\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}''.
+Then, with reference to the text entry, we asked how much this core need
+was fulfilled during the interaction or the past daytime period:
+``\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}''
+on a continuous slider scale ranging from strongly disagree (-50) to
+strongly agree (+50).
+
+We, additionally, included a common measure of three self-determination
+theory needs \citep[see][]{Downie2008}. The items were introduced either
+by ``\textit{During the interaction:}'' or
+``\textit{This morning [/afternoon]:}'' and measured autonomy
+(``\textit{I was myself.}''), competence
+(``\textit{I felt competent.}''), and relatedness (without intergroup
+contact ``\textit{I had a strong need to belong}''; with intergroup
+contact: ``\textit{I shared information about myself.}'' and
+``\textit{The other(s) shared information about themselves.}''). All
+items were rated on a continuous slider scale from very little (-50) to
+a great deal (+50).
+
+\paragraph{Perceived Interaction Quality}
+
+As an explanatory mechanism, we assessed ratings of the perceived
+interaction quality. As our main measurement, participants rated the
+statement ``\textit{Overall the interaction was …}'' on two continuous
+slider scales measuring pleasantness
+\citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
+
+\paragraph{Outgroup Attitudes}
+
+At the end of every daily diary measurement we asked all participants
+about their current attitudes towards the Dutch -- our main dependent
+variable. To assess the momentary outgroup evaluation we used the common
+feeling thermometer: ``How favorable do you feel towards the Dutch?''
+\citep[][]{Lavrakas2008}. Participants then rated their attitude on a
+continuous slider scale from ``very cold -- 0'' through ``no feeling --
+50'' to ``very warm -- 100''. Both the question phrasing as well as the
+tick labels were consistent with large-scale panel surveys
+\citep[e.g.,][]{DeBell2010}.
+
+\subsection{Results}
+
+\subsubsection{Contact Hypothesis}
+
+We tested the most general contact hypothesis in two steps. First, we
+assessed whether more intergroup interactions were related to to more
+positive outgroup attitudes. Second, we tested whether a potential
+positive effect on outgroup attitudes depended on the interaction
+quality (jointly with the number of interactions). We find that neither
+the number of interactions nor the number of daily diary responses with
+an interaction were significantly related with the average outgroup
+attitudes (all \textbar{} \textit{r} \textbar{} \textless{} 0.03, all
+\textit{p} \textgreater{} 0.887). This is to say that within our data,
+participants with more outgroup interactions did not have significantly
+more positive outgroup attitudes. This might be due to the aggregation
+within the participants or the small sample size of between participant
+data. Nonetheless, the aggregated data does not support the notion that
+simply having more interactions with an outgroup results in more
+positive outgroup attitudes.
+
+However, despite the missing relationship with the number of
+interactions, we find a medium sized correlation between the
+participants' Average Interaction Quality and their Average Outgroup
+Attitudes. Thus within our data participants with a higher quality
+outgroup interactions also held more positive attitudes towards that
+group. And when considering the number of interactions and average
+interaction quality jointly in a linear regression, we additionally find
+a statistically significant interaction term (\textit{b} = -0.05,
+\textit{t}(17) = -2.95, \textit{p} = 0.009, \(\eta_p^2\) = 0.34).
+Looking at a floodlight analysis of the effect, we find that in our
+sample with an increasing number of interactions the positive effect of
+average interaction quality becomes weaker. However, it should be noted
+that this is based on data aggregating all within participant nuances
+and is only based on 21 people.
+
+We additionally used a multilevel regression to check whether having an
+interaction with an outgroup member had a situational (i.e.,
+contemporaneous) effect within the participants. We find that having an
+outgroup interaction is indeed associated with significantly more
+positive outgroup attitudes within the participants (\textit{b} = 2.48,
+\textit{t}(1200) = 4.36, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}1.36, 3.59{]}), even after controlling for having an
+interaction with a non-Dutch (which did not relate to outgroup attitudes
+independently; For full results see Online Supplementary Materials
+B)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+This is unusual and might indicate the the effect is very consistent across participants.
+However, the small number of participants, or other measurement issues provide an alternative explanation}.
+Thus, in our first data we find mixed results, where outgroup contacts
+show a positive effect on outgroup attitudes in the moment but these
+results do not translate into average differences between participants,
+keeping in mind that the between-participant analyses in the aggregated
+form are based on a small sample size.
+
+\subsubsection{Core Need}
+
+The main proposal of our article is that the success of an outgroup
+interaction might be explained by whether or not the interaction
+fulfilled the person's core situational need. This should, in turn, be
+due to a higher perceived interaction quality. We sequentially test
+whether the fulfillment of the core need during an interaction is (1)
+related to more positive outgroup attitudes, (2) higher perceived
+interaction quality, and (3) whether the variance explained by the core
+need is assumed by the perceived interaction quality if considered
+jointly.
+
+We find that in the highest multilevel models, the fulfillment of core
+situational needs during outgroup contacts was associated with more
+positive outgroup attitudes (random slopes model; \textit{b} = 0.17,
+\textit{t}(365) = 2.93, \textit{p} = 0.004, \textit{95\%CI}{[}0.06,
+0.29{]}) and also predicted higher perceived interaction quality (random
+intercept model; \textit{b} = 0.42, \textit{t}(365) = 8.07, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.32, 0.52{]}). Moreover, when we
+consider the influences of core need fulfillment and interaction quality
+on outgroup attitudes jointly, we find that virtually all variance is
+explained by perceived interaction quality (random slopes mode;
+\textit{b} = 0.23, \textit{t}(364) = 4.22, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
+still explained by core need fulfillment (\textit{b} = 0.04,
+\textit{t}(364) = 0.64, \textit{p} = 0.523, \textit{95\%CI}{[}-0.08,
+0.15{]}). We thus find support for our hypotheses and can conclude that
+in this data set the fulfillment of core situational needs had a
+significant influence on outgroup attitudes. Additionally, this effect
+is likely being explained by its effect through perceived interaction
+quality.
+
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
+
+\subsubsection{Robustness}
+
+To build further confidence in our results, we assessed two additional
+models that might offer alternative explanations. First, to ensure that
+the effect of core need fulfillment is specific to an actual
+interaction, we compared the effect to core need fulfillement in
+situations without an interaction. For this, we analyzed the generalized
+situational core need fulfillment (either during an interaction or about
+the daytime in general) and tested whether the effect differed during
+daily diary measurements with and without outgroup contacts. We found no
+main effect of core need fulfillment (random slopes model; \textit{b} =
+-0.10, \textit{t}(1199) = -2.22, \textit{p} = 0.026,
+\textit{95\%CI}{[}-0.18, -0.01{]}) but a significant interaction effect
+of core need fulfillment and outgroup contact (\textit{b} = 0.13,
+\textit{t}(1199) = 4.31, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.07, 0.18{]}). Together with a significant main
+effect of having an outgroup contact, this indicates that it is not key
+need fulfillment in general --- but only key need fulfillment during an
+outgroup contact that predicts more positive outgroup attitudes.
+
+In a final step, we controlled for other fundamental psychological needs
+during the interaction. We focus on the three commonly considered self
+determination needs: competence, autonomy, and relatedness. We find that
+the core need adds significantly above a model with only the self
+determination theory needs (random slopes models; \(\chi^2\)(6,
+\textit{N} = 21) = 19.60, \textit{p} = 0.003). We find that next to
+relatedness (\textit{b} = 0.10, \textit{t}(361) = 4.04, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the core need
+explains the most variance in outgroup attitudes after an outgroup
+contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p} = 0.026,
+\textit{95\%CI}{[}0.01, 0.18{]}). When compared to the model with only
+the SDT needs, the core need fulfillment flexibly takes on some of the
+explained variance of all three fundamental needs (competence and
+autonomy needs turning non-significant; all \textit{b} \textless{} 0.05,
+all \textit{p} \textgreater{} 0.544). For full results see Online
+Supplementary Information B.
+
+\section{Study 2}
+
+The aim of Study 2 is similar to Study 1, as we again test the general
+contact hypothesis, the influence of core need fulfillment, and
+perceived interaction quality during intergroup contacts. However, in
+this second study we collected a substantially larger sample of
+international students who recently arrived in the Netherlands and also
+improved the study design (e.g., pop up explanations described later).
+The survey method again offers a large body of ecologically valid data
+on need satisfaction in real-life intergroup contact situations as these
+students will likely interact with the Dutch majority outgroup on a
+daily basis. Data was collected from November 19\textsuperscript{th},
+2018 through January 6\textsuperscript{th}, 2019.
+
+The full surveys are available in our Online Supplementary Material A
+and the full data description is available in Online Supplementary
+Materials B. Correlations and descriptive statistics of the included
+variables are available in Table \ref{tab:descrFullLong} and Table
+\ref{tab:descrOutLong}.
+
+\subsection{Methods}
+
+\subsubsection{Participants}
+
+After receiving ethical approval from the University of Groningen, we
+recruited 113 international students using a local participant pool. We
+specifically targeted non-Dutch students, who had recently arrived in
+the Netherlands. Participants reported on their interactions for at
+least 30 days with two daily measures (capturing the morning and
+afternoon). With this design, we aimed at getting 50-60 measurements per
+participant (\textit{M} = 43.94, \textit{SD} = 15.00, \textit{total N} =
+4965). As with the previous study this should offer sufficient power to
+model processes within participants and will lend stronger weight to
+between-participant results. Participants were compensated for their
+participation with partial course credits --- depending on their
+participation. The sample consisted of relatively young migrants, who
+were mostly from the global north (\(M_{age}\) = 20.24, \(SD_{age}\) =
+2.12, 84 women). The sample fairly accurately describes the local
+population of international students.
+
+\subsubsection{Procedure}
+
+The study procedure mirrored the setup of study one and consisted of
+pre-, daily diary-, and post-measurement. The participants were invited
+for daily diary measurements twice a day (at 12 pm and 7pm) for 30 days
+(\textit{median duration} = 3M 46S, \textit{MAD duration} = 1M 54S).
+General compliance was high (70.87\% of all invited surveys were filled
+in). The response rates were approximately equal during mornings
+(\textit{n} = 2608) and afternoons (\textit{n} = 2357). All key
+variables for this study were part of the short daily diary surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+To measure intergroup contacts, every experience sampling measurement
+started with the question
+``\textit{Did you meet a Dutch person this morning [/afternoon]? (in-person interaction for at least 10 minutes)}''.
+Participants were additionally offered a pop-up explanation: ``With
+in-person interaction, we mean a continued interaction with another
+person (potentially in a group) that lasted at least 10 minutes. This
+interaction should be offline and face-to-face. It should include some
+form of verbal communication and should be uninterrupted to still count
+as the same interaction. Any individual interaction can last minutes or
+hours. If there were multiple interaction partners, we would like you to
+focus on the person that was most important to you during the
+interaction.''. The participants recorded between 1--43 interactions
+with Dutch majority people (1.64--93.75\% of individual daily diary
+measurements; 18.83\% of all 4965 daily diary responses).
+
+\paragraph{Psychological Needs}
+
+For the core situational need, we asked participants in an open ended
+text field:
+``\textit{What was your main goal [during the interaction with X / this morning / this afternoon]?}''.
+Participants could additionally click on a pop-up explanation: ``Your
+main goal during an interaction can vary depending on the interaction.
+It could be to connect with friends, to find or provide help, to achieve
+academic ambitions, work on your fitness, work for a job, or simply to
+get a coffee, just as well as many many other concrete or abstract goals
+that are import to you in the moment. It really depends on your
+subjective experience of the interaction.''. Then, with reference to the
+text entry, we asked how much this core need was fulfilled during the
+interaction or the past daytime period:
+``\textit{During your interaction with X [this morning / this evening] your goal (-previous text entry-) was fulfilled.}''
+on a continuous slider scale ranging from strongly disagree (1) to
+strongly agree (100).
+
+The measurement of the self determination needs was identical to study
+1.
+
+\paragraph{Perceived Interaction Quality}
+
+The ratings of the perceived interaction quality was identical to study
+one.
+
+\paragraph{Outgroup Attitudes}
+
+As in Study 1, attitudes towards the Dutch majority outgroup were again
+measured using the feeling thermometer. All survey details are also
+available in Online Supplemental Materials A and B.
+
+\subsection{Results}
+
+\subsubsection{Contact Hypothesis}
+
+We tested the most general contact hypothesis in two steps. First, we
+assessed whether more intergroup interactions were related to to more
+positive outgroup attitudes. Second, we tested whether a potential
+positive effect on outgroup attitudes depended on the interaction
+quality (jointly with the number of interactions). We find a significant
+correlation with average outgroup attitudes for both the total number of
+outgroup interactions (\textit{r} = 0.22, \textit{p} = 0.019) and the
+number of measurement beeps with an interaction (\textit{r} = 0.28,
+\textit{p} = 0.003). This is to say that within our data, participants
+with more outgroup interactions did have significantly more positive
+outgroup attitudes. This is inconsistent with the results we found in
+the first study and might be due to the larger number of participants.
+
+However, we find no significant correlation between the participants'
+Average Interaction Quality and their Average Outgroup Attitudes
+(\textit{r} = 0.04, \textit{p} = 0.679). Thus, when considering the
+number of interactions and average interaction quality jointly in a
+linear regression, we find a main effect of intergroup contacts to
+predict outgroup attitudes (\textit{b} = 0.81, \textit{t}(109) = 3.29,
+\textit{p} = 0.001, \(\eta_p^2\) = 0.08). Given the missing aggregate
+relationship between average interaction quality and outgroup attitudes,
+we find no significant effect of average perceived contact quality. We
+also do not find that in this sample the impact of the number of
+interactions is moderated by the average contact quality. This is not
+entirely consistent with the first study, where average contact quality
+did have a meaningful effect on outgroup attitudes. This finding is not
+necessarily surprising given that the variables aggregate all within
+person variation and there were substantially more measurements where
+participants did not have an interaction (but reported their outgroup
+attitudes) than measurements that followed an outgroup contact.
+
+We additionally used a multilevel regression to check whether having an
+interaction with an outgroup member had a situational (i.e.,
+contemporaneous) effect within the participants. We find that having an
+outgroup interaction is indeed associated with significantly more
+positive outgroup attitudes within the participants (random slopes
+model; \textit{b} = 2.99, \textit{t}(4850) = 3.80, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}1.45, 4.54{]}), even after
+controlling for having an interaction with a non-Dutch person (which did
+not relate to outgroup attitudes independently; For full results see
+Online Supplementary Materials B). Thus, in our second dataset we find
+mixed results, outgroup contacts show a positive effect on outgroup
+attitudes in the moment and on average between participants. However, we
+find that this effect does not depend on the average perceived
+interaction quality. This unexpected results, might be due to the
+aggregation process and the following analyses will focus in on the role
+of the perceived interaction quality during an outgroup interaction.
+
+\subsubsection{Core Need}
+
+We again sequentially tested whether the fulfillment of the core need
+during an interaction was (1) related to more positive outgroup
+attitudes, (2) higher perceived interaction quality, and (3) whether the
+variance explained by the core need is assumed by the perceived
+interaction quality if considered jointly. We find that in the
+multilevel models, the fulfillment of core situational needs during
+outgroup contacts was associated with more positive outgroup attitudes
+(random slopes model; \textit{b} = 0.13, \textit{t}(826) = 4.18,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.19{]}) and also
+predicted higher perceived interaction quality (random slopes model;
+\textit{b} = 0.40, \textit{t}(826) = 6.46, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.28, 0.52{]}). Additionally, if we consider the
+influences of core need fulfillment and interaction quality on outgroup
+attitudes jointly, we find that virtually all variance is explained by
+perceived interaction quality (random slopes mode; \textit{b} = 0.17,
+\textit{t}(825) = 5.56, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.11, 0.23{]}) and only little unique variance is
+still explained by core need fulfillment (\textit{b} = 0.03,
+\textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
+0.07{]}). These results are consistent with the results in study one and
+we thus find support for our hypotheses and can conclude that in this
+data set the fulfillment of core situational needs had a significant
+influence on outgroup attitudes and that this effect is likely explained
+by its effect through perceived interaction quality.
+
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
+
+\subsubsection{Robustness}
+
+We again checked for alternative models. First, when considering
+generalized situational core need fulfillment together with whether an
+intergroup contact took place, we find that there is only a minuscule
+main effect of core need fulfillment (random slopes model; \textit{b} =
+-0.03, \textit{t}(4849) = -1.34, \textit{p} = 0.181,
+\textit{95\%CI}{[}-0.08, 0.02{]}) but a stronger interaction effect of
+core need fulfillment and outgroup contact (\textit{b} = 0.06,
+\textit{t}(4849) = 3.03, \textit{p} = 0.002, \textit{95\%CI}{[}0.02,
+0.10{]}). Together with a significant main effect of having an outgroup
+contact (\textit{b} = 2.88, \textit{t}(4849) = 3.71, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}1.36, 4.40{]}), this indicates that
+it is not key need fulfillment in general --- but key need fulfillment
+during an outgroup contact that predicts more positive outgroup
+attitudes. This finding is consistent with the results of the previous
+study, albeit with slightly weaker effect (likely because of the large
+number of measurements that did not include an outgroup interaction).
+
+In a final step we again checked whether during the interaction the core
+situational need remains a meaningful predictor even when taking other
+fundamental psychological needs into account. We find that the core need
+adds significantly above a model with only the self determination theory
+needs (random slopes models; \(\chi^2\)(6, \textit{N} = 108) = 22.90,
+\textit{p} \textless{} .001). We find that the core need explains the
+most variance in outgroup attitudes after an outgroup contact
+(\textit{b} = 0.08, \textit{t}(823) = 2.95, \textit{p} = 0.003,
+\textit{95\%CI}{[}0.03, 0.13{]}). When compared to the model with only
+the SDT needs, the core need fulfillment flexibly takes on some of the
+explained variance of all of the three fundamental needs. However,
+different from the first study, relatedness (\textit{b} = 0.07,
+\textit{t}(823) = 4.26, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.04, 0.10{]}) and autonomy (\textit{b} = 0.02,
+\textit{t}(823) = 0.93, \textit{p} = 0.353, \textit{95\%CI}{[}-0.02,
+0.08{]}) also predicted positive outgroup attitudes in this larger
+sample. For full results see Online Supplementary Information B.
+
+\section{Study 3}
+
+The aim of this final study is to extend the previous studies by
+additionally testing Allport's conditions in an extensive longitudinal
+design and to compare the predictive powers of Allport's conditions and
+the core situational need fulfillment. We will, thus, again test the
+general contact hypothesis, the influence of core need fulfillment, and
+perceived interaction quality during intergroup contacts. However, we
+additionally have the opportunity to also assess the role of Allport's
+conditions in this and to compare the two approaches (Allport's
+conditions and core need fulfillment) directly.
+
+For this study we specifically recruited international medical students,
+because they represent a particular group of migrants who face
+structural requirements to integrate and interact with Dutch majority
+outgroup members on a daily basis. As part of their educational program,
+the migrants are required to take language courses and interact with
+patients as part of their medical internships and medical residency. The
+extensive longitudinal survey method again offers a large body of
+ecologically valid data on need satisfaction in real-life intergroup
+contact situations. Data were collected from November
+8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020.
+
+The full surveys are available in our Online Supplementary Material A
+and the full data description is available in Online Supplementary
+Materials B. Correlations and descriptive statistics of the included
+variables are available in Tables \ref{tab:descrFullLong} and
+\ref{tab:descrOutLong}.
+
+\subsection{Methods}
+
+\subsubsection{Participants}
+
+After receiving ethical approval from the University of Groningen, we
+recruited 71 international medical students using a contacts within the
+University Medical Department and specifically targeted non-Dutch
+students, who had recently arrived in the Netherlands. Participants
+reported on their interactions for at least 30 days with two daily
+measures (capturing the morning and afternoon). With this design, we
+aimed at getting 50-60 measurements per participant (\textit{M} = 57.85,
+\textit{SD} = 20.68, \textit{total N} = 4107). As with the previous
+study this should offer sufficient power to model processes within
+participants and will lend stronger weight to between-participant
+results. Participants were compensated for their participation with
+partial course credits --- depending on their participation. The sample
+consisted of relatively young migrants, who were mostly from the global
+north (\(M_{age}\) = 22.68, \(SD_{age}\) = 3.10, 59 women). The sample
+fairly accurately describes the local population of international
+students.
+
+\subsubsection{Procedure}
+
+The study procedure mirrored the setup of studies one and two, in that
+it consisted of pre-, daily diary-, and post-measurement. The
+participants were invited for daily diary measurements twice a day (at
+12 pm and 7pm) for 30 days (\textit{median duration} = 4M 13S,
+\textit{MAD duration} = 2M 6S). General compliance was high (93.30\%
+filled daily diary surveys for 31 days or more NEED TO RE-CHECK THIS).
+The response rates were approximately equal during mornings (\textit{n}
+= 2092) and afternoons (\textit{n} = 2015). All key variables in for
+this study were part of the short daily diary surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+The measurement of intergroup contacts was identical to study two. The
+participants recorded between 1--71 interactions with Dutch outgroup
+members (2.13--87.18\% of individual daily diary measurements; 41.44\%
+of all 4107 daily diary responses).
+
+\paragraph{Psychological Needs}
+
+The measurement of the core situational need and its fulfillment was
+identical to study two. Similarly, the measurement of the self
+determination needs was identical to studies one and two.
+
+\paragraph{Allport's Conditions}
+
+To measure how much each of the interactions fulfilled Allport's
+conditions of optimal contact we asked participants to rate how much the
+interaction had equal status
+(``\textit{The interaction with [name interaction partner] was on equal footing (same status)}''),
+a common goal
+(``\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}''),
+support of authorities
+(``\textit{The interaction with [name interaction partner] was voluntary}''),
+and intergroup cooperation
+(``\textit{The interaction with [name interaction partner] was cooperative}'').
+
+\paragraph{Perceived Interaction Quality}
+
+The ratings of the perceived interaction quality was identical to study
+one.
+
+\paragraph{Outgroup Attitudes}
+
+Attitudes towards the Dutch majority outgroup was again measured using
+the feeling thermometer, as in studies one and two. All survey details
+are also available in Online Supplemental Materials A and B.
+
+\subsection{Results}
+
+\subsubsection{Contact Hypothesis}
+
+We tested the most general contact hypothesis in two steps. First, we
+assessed whether more intergroup interactions were related to to more
+positive outgroup attitudes. Second, we tested whether a potential
+positive effect on outgroup attitudes depended on the interaction
+quality (jointly with the number of interactions). We find no
+significant correlation between intergroup contact and average outgroup
+attitudes --- for neither the total number of outgroup interactions
+(\textit{r} = 0.01, \textit{p} = 0.946) and the number of measurement
+beeps with an interaction (\textit{r} = 0.13, \textit{p} = 0.291). This
+is to say that within our data, participants with more outgroup
+interactions did not have significantly more positive or negative
+outgroup attitudes. This is again consistent with the results we found
+in the first study but inconsitent with the significant relationship we
+find in the second study.
+
+However, we do find a significant correlation between the participants'
+Average Interaction Quality and their Average Outgroup Attitudes
+(\textit{r} = 0.25, \textit{p} = 0.036). Thus, when considering the
+number of interactions and average interaction quality jointly in a
+linear regression, we only find a main effect of average perceived
+interaction quality on predict outgroup attitudes (\textit{b} = 0.36,
+\textit{t}(67) = 2.22, \textit{p} = 0.030, \(\eta_p^2\) = 0.07). Given
+the missing aggregate relationship between number of interactions and
+outgroup attitudes, we find no significant effect of interactions
+themselves nor do we find a significant interaction effect. This result
+mirrors that of study one but is inconsistent with the second study. But
+again this inconsistency is not necessarily surprising given that the
+variables aggregate all within person variation and there were
+substantially more measurements where participants did not have an
+interaction (but reported their outgroup attitudes) than measurements
+that followed an outgroup contact.
+
+We additionally used a multilevel regression to check whether having an
+interaction with an outgroup member had a situational (i.e.,
+contemporaneous) effect within the participants. We find that having an
+outgroup interaction is indeed associated with significantly more
+positive outgroup attitudes within the participants (random slopes
+model; \textit{b} = 5.63, \textit{t}(3834) = 6.61, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}3.97, 7.29{]}), even after
+controlling for having an interaction with a non-Dutch (which did not
+relate to outgroup attitudes independently; For full results see Online
+Supplementary Materials B). Thus, in our third dataset we find some
+mixed results, outgroup contacts are not significantly related to
+outgroup attitudes on aggregate between participants and this effect is
+also not suppressed by a average interaction quality (i.e., no
+interaction effect). However, while the aggregate data is partly
+inconsistent with the first two studies, the within person contemoranous
+effect of intergroup contact is consistent across all three studies.
+
+\subsubsection{Allport's Conditions}
+
+We sequentially tested whether the fulfillment of Allport's Contact
+Conditions was (1) related to more positive outgroup attitudes, (2)
+higher perceived interaction quality, and (3) whether the variance
+explained by Allport's Conditions is assumed by the perceived
+interaction quality if considered jointly. We find that in the
+multilevel models, the fulfillment of Allport's Conditions during
+outgroup contacts was associated with more positive outgroup attitudes
+(random slopes model; \textit{b} = 0.22, \textit{t}(1601) = 5.86,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.15, 0.29{]}) and also
+predicted higher perceived interaction quality (random slopes model;
+\textit{b} = 0.65, \textit{t}(1605) = 11.82, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we consider the
+influences of Allport's Conditions and interaction quality on outgroup
+attitudes jointly, we find that perceived interaction quality is a
+substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
+\textit{t}(1600) = 6.25, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
+Allport's Conditions was less than half of its original effect size
+(\textit{b} = 0.09, \textit{t}(1600) = 2.89, \textit{p} = 0.004,
+\textit{95\%CI}{[}0.03, 0.15{]}). These results indicate that in this
+dataset the the fulfillment of Allport's conditions had a significant
+influence on outgroup attitudes and this effect is likely in parts
+explained by its effect through perceived interaction quality.
+
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
+
+\subsubsection{Core Need}
+
+We again sequentially tested whether the fulfillment of the core need
+during an interaction was (1) related to more positive outgroup
+attitudes, (2) higher perceived interaction quality, and (3) whether the
+variance explained by the core need is assumed by the perceived
+interaction quality if considered jointly. We find that in the
+multilevel models, the fulfillment of core need fulfillment during
+outgroup contacts was associated with more positive outgroup attitudes
+(random slopes model; \textit{b} = 0.19, \textit{t}(1601) = 5.29,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.12, 0.27{]}) and also
+predicted higher perceived interaction quality (random slopes model;
+\textit{b} = 0.43, \textit{t}(1605) = 8.35, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.33, 0.54{]}). Additionally, once we consider the
+influences of core need fulfillment and interaction quality on outgroup
+attitudes jointly, we find that perceived interaction quality is a
+substantially stronger predictor (random slopes mode; \textit{b} = 0.17,
+\textit{t}(1600) = 6.86, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.22{]}) and the unique variance explained by
+core need fulfillment was roughly half of its original effect size
+(\textit{b} = 0.11, \textit{t}(1600) = 3.50, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.05, 0.17{]}). These results indicate that in
+this dataset the the fulfillment of core situational needs had a
+significant influence on outgroup attitudes and this effect is likely in
+parts explained by its effect through perceived interaction quality.
+
+\faQuestionCircle~Are we sure that we don't want some sort of
+bootstrapped indirect effect?
+
+\subsubsection{Compare Fulfillment of Core Need and Allport's Conditions}
+
+To compare the models using either Allport's conditions or the core need
+fulfillment to predict outgroup attitudes, we first assess relative
+model performance indices (i.e., Akaike information criterion, and
+Bayesian information criterion), and then consider the two predictors in
+a joint model to see whether the two approaches predict the same
+variance in outgroup attitudes. When comparing the model selection
+indices we find that the fulfillment of the situation core need, indeed
+performs slightly better than the model using Allport's conditions
+(\(AIC_{CoreNeed}\) 12632.02 \textless{} 12651.59 \(AIC_{Allport}\), and
+\(BIC_{CoreNeed}\) 12664.55 \textless{} 12684.12 \(BIC_{Allport}\)).
+Additionally, when considering the predictors jointly, we find that both
+significantly predict outgroup attitudes with similar sized regression
+parameters (random slopes model; Allport's Conditions: \textit{b} =
+0.16, \textit{t}(1600) = 4.92, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.09, 0.24{]}, Core Need: \textit{b} = 0.14,
+\textit{t}(1600) = 3.85, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.08, 0.17{]}). This indicates that, although both
+Allport's conditions and the core need fulfillment seem to (in part)
+work through perceived interaction quality, they explain different
+aspects of the variance in outgroup attitudes and do not constitute one
+another.
+
+\subsubsection{Robustness}
+
+We again checked for alternative models to the core need fulfillment.
+First, when considering generalized situational core need fulfillment
+together with whether an intergroup contact took place, we find that
+there is no significant main effect of core need fulfillment (random
+slopes model; \textit{b} = 0.03, \textit{t}(3835) = 1.51, \textit{p} =
+0.131, \textit{95\%CI}{[}-0.01, 0.06{]}) but a stronger interaction
+effect of core need fulfillment and outgroup contact (\textit{b} = 0.17,
+\textit{t}(3835) = 7.32, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.21{]}). Together with a significant main
+effect of having an outgroup contact (\textit{b} = 5.41,
+\textit{t}(3835) = 6.36, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}3.74, 7.08{]}), this indicates that it is not key need
+fulfillment in general --- but key need fulfillment during an outgroup
+contact that predicts more positive outgroup attitudes. This finding is
+consistent with the results of the previous studies.
+
+In a final step we again checked whether during the interaction the core
+situational need remains a meaningful predictor even when taking other
+fundamental psychological needs into account. We find that the core need
+adds significantly above a model with only the self determination theory
+needs (random slopes models; \(\chi^2\)(6, \textit{N} = 70) = 100.20,
+\textit{p} \textless{} .001). We find that the core need explains the
+most variance in outgroup attitudes after an outgroup contact
+(\textit{b} = 0.15, \textit{t}(1598) = 3.88, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.07, 0.22{]}). When compared to the model with
+only the SDT needs, the core need fulfillment flexibly takes on some of
+the explained variance of all of the three fundamental needs. However,
+similar to the previous study, in this large sample relatedness
+(\textit{b} = 0.05, \textit{t}(1598) = 3.31, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.02, 0.09{]}), competence (\textit{b} = 0.06,
+\textit{t}(1598) = 2.73, \textit{p} = 0.006, \textit{95\%CI}{[}0.02,
+0.10{]}) and autonomy (\textit{b} = 0.04, \textit{t}(1598) = 2.12,
+\textit{p} = 0.034, \textit{95\%CI}{[}-0.01, 0.08{]}) each also
+predicted positive outgroup attitudes independently. However, the
+regression coefficient is three times as large for the core need
+fulfillment (with all scaling being equal). For full results see Online
+Supplementary Information B.
+
+\input{Tables/descrFullLong}
+\input{Tables/descrOutLong}
+
+\input{Tables/mdlContactGeneralLong}
+
+\input{Tables/mdlTheorylong}
+
+\input{Tables/mdlRobustlong}
 

### 2023-05-26 Tracked changes/comparison/main_rev.tex
track changes added

--- 2023-05-26 manuscript.tex
@@
 % Methods and Results from RMarkdown render
-\input{Methods-and-Results}
+\section{Study 1}
+
+Based on our main hypotheses, the aim of our first study was to
+specifically test the general contact hypothesis, the influence of core
+need fulfillment, and perceived interaction quality during intergroup
+contacts. To this aim, we recruited recent migrants to the Netherlands
+for an intensive longitudinal survey. Data were collected from May
+5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all
+participants started the study within the first two days). Correlations
+and descriptive statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide} (full data
+description is available in Online Supplementary Material A).
+
+\subsection{Methods}
+
+\subsubsection{Participants}
+
+After receiving ethical approval from the University Masked for Peer
+Review, we recruited 23 non-Dutch migrants using the local paid
+participant pool. Participants reported on their interactions for at
+least 30 days with two daily measures (capturing the morning and
+afternoon). With this design, we aimed at getting 50-60 measurements per
+participant (\textit{M} = 53.26, \textit{SD} = 16.72, \textit{total N} =
+1,225). This is a common number of measurements found in experience
+sampling studies and offers sufficient power to model processes within
+and between participants \citep[e.g.,][]{AanhetRot2012}. Participants
+were compensated for their participation with up to 34 Euros -- each two
+Euros for pre- and post-questionnaire and 50 Eurocents for every
+experience sampling measurement. The sample consisted of relatively
+young, educated, and western migrants from the global north (\(M_{age}\)
+= 24.35, \(SD_{age}\) = 4.73, 19 women, 15 students). The sample
+accurately describes the largest groups of migrants in the region
+\citep[][]{GemeenteGroningen2015}.
+
+\subsubsection{Procedure}
+
+The study itself consisted of three main parts, an introductory
+pre-measurement, the daily experience sampling measurements, and a
+concluding post-measurement. After giving informed consent, participants
+filled in an online pre-questionnaire assessing demographics and general
+information about their immigration. Over the next thirty days,
+participants were invited twice a day (at 12pm and 7pm) to reflect upon
+their interactions, psychological need fulfillments, and current
+attitudes towards the Dutch outgroup. General compliance was high
+(85.90\% of all invited surveys were filled
+in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%).}.
+The response rates were approximately equal during mornings (\textit{n}
+= 621) and afternoons (\textit{n} = 604) and most measurements were
+completed within four hours of the invitation. After the final day of
+experience sampling measurements, participants were invited to fill in a
+longer post measurement survey that mirrored the pre-measurement. All
+key variables for this study were part of the short experience sampling
+surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+To test the prerequisite effect of intergroup contact, every experience
+sampling measurement started with the question
+``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''.
+Our participants recorded between 2--51 interactions with Dutch outgroup
+members (3.23--91.07\% of individual experience sampling measurements;
+387 of all 1,225 experience sampling
+responses)\footnote{Two participants only recorded two experience sampling measurements each and none of these included outgroup contacts.
+These participants are removed from any analyses that focus on outgroup contacts.}.
+
+\paragraph{Psychological Needs}
+
+Irrespective of whether participants had an interaction with Dutch
+people or not, everyone answered a short series of questions on
+psychological need fulfillment. However, whereas participants with
+interactions reported on the need fulfillment during the interaction,
+people without interactions with Dutch people judged the past daytime
+period in general. To assess the fulfillment of psychological needs, we
+included two types of need measurement: (1) the core situational need
+and (2) general self-determination theory needs.
+
+For the core situational need, we asked participants in an open-ended
+text field:
+``\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}''.
+Then, with reference to the text entry, we asked how much this core need
+was fulfilled during the interaction or the past daytime period:
+``\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}''
+on a continuous slider scale ranging from strongly disagree (-50) to
+strongly agree (+50). The self-determination theory need measurements
+are described in \appref{app:AppendixRobustness}.
+
+\paragraph{Perceived Interaction Quality}
+
+As an explanatory mechanism, we assessed ratings of the perceived
+interaction quality. As our main measurement, participants rated the
+statement ``\textit{Overall the interaction was …}'' on two continuous
+slider scales measuring pleasantness
+\citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
+
+\paragraph{Outgroup Attitudes}
+
+At the end of every experience sampling measurement, we asked all
+participants about their current attitudes towards the Dutch -- our main
+dependent variable. To assess the momentary outgroup evaluation we used
+the common feeling thermometer: ``How favorable do you feel towards the
+Dutch?'' \citep[][]{Lavrakas2008}. Participants then rated their
+attitude on a continuous slider scale from ``very cold -- 0'' through
+``no feeling -- 50'' to ``very warm -- 100''. Both the question phrasing
+as well as the tick labels were consistent with large-scale panel
+surveys \citep[e.g.,][]{DeBell2010}.
+
+\subsection{Results}
+
+\subsubsection{Contact Hypothesis}
+
+Using a multilevel regression, we find that having an outgroup contact
+is indeed associated with significantly more positive outgroup attitudes
+(\textit{b} = 2.48, \textit{t}(1,200) = 4.37, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}1.37, 3.59{]}), even after controlling for
+having an interaction with a non-Dutch (which did not relate to outgroup
+attitudes independently). Additionally, while multi-level regressions
+are generally robust against unequal cell sizes, we correct for
+inequalities by using centered predictors and reintroducing the means as
+level two predictors (\citealp{yaremych2021a}; for full results see
+\tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
+and Online Supplementary Material
+A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+This is unusual and might indicate that the effect is very consistent across participants.
+However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}.
+Thus, in our first data, we find initial evidence that outgroup contacts
+show a positive effect on outgroup attitudes within real-life data.
+
+\subsubsection{Core Need}
+
+The main proposal of our article is that the success of an outgroup
+contact might be explained by whether or not the contact fulfilled the
+person's core situational need. This should, in turn, be due to a higher
+perceived contact quality. We sequentially test whether the fulfillment
+of the core need during an interaction is (1) related to more positive
+outgroup attitudes, (2) higher perceived contact quality, and (3)
+whether the variance explained by the core need is subsumed by the
+perceived contact quality if considered jointly. We find that in the
+multilevel models, the fulfillment of core situational needs during
+outgroup contacts was associated with more positive outgroup attitudes
+(random slopes model; \textit{b} = 0.17, \textit{t}(365) = 2.93,
+\textit{p} = 0.004, \textit{95\%CI}{[}0.06, 0.29{]}) and also predicted
+higher perceived contact quality (random intercept model; \textit{b} =
+0.42, \textit{t}(365) = 8.07, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.32, 0.52{]}). Moreover, when we consider the
+influences of core need fulfillment and contact quality on outgroup
+attitudes jointly, we find that virtually all variance is explained by
+perceived contact quality (random slopes model; \textit{b} = 0.23,
+\textit{t}(364) = 4.22, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
+still explained by core need fulfillment (\textit{b} = 0.04,
+\textit{t}(364) = 0.64, \textit{p} = 0.523, \textit{95\%CI}{[}-0.08,
+0.15{]}, also see \fgrref[-A]{fig:MainPaths}). We thus find support for
+our hypotheses and can conclude that in this data set the fulfillment of
+core situational needs had a significant influence on outgroup
+attitudes. Additionally, this effect is likely explained by its effect
+through perceived contact quality.
+
+\section{Study 2}
+
+The aim of Study 2 is similar to Study 1, as we again test the general
+contact hypothesis, the influence of core need fulfillment, and
+perceived contact quality during intergroup contacts. However, in this
+second study we collected a substantially larger sample of international
+students who recently arrived in the Netherlands and also improved the
+study design (e.g., pop-up explanations described later). The survey
+method again offers a large body of ecologically valid data on need
+satisfaction in real-life intergroup contact situations as these
+students will likely interact with the Dutch majority outgroup on a
+daily basis. Data were collected from November 19\textsuperscript{th},
+2018 through January 6\textsuperscript{th}, 2019. Correlations and
+descriptive statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+
+\subsection{Methods}
+
+\subsubsection{Participants}
+
+We recruited 113 international students using a local participant pool.
+We specifically targeted non-Dutch students, who had recently arrived in
+the Netherlands. Participants reported on their interactions for at
+least 30 days with two daily measures (capturing the morning and
+afternoon). With this design, we again aimed at receiving 50-60
+measurements per participant (\textit{M} = 43.94, \textit{SD} = 15.00,
+\textit{total N} = 4,965). As with the previous study, this should offer
+sufficient power to model processes within participants and will lend
+stronger weight to between-participant results. Participants were
+compensated for their participation with partial course credits ---
+depending on their participation. The sample consisted of relatively
+young migrants, who were mostly from the global north (\(M_{age}\) =
+20.24, \(SD_{age}\) = 2.12, 84 women). The sample fairly accurately
+describes the local population of international students.
+
+\subsubsection{Procedure}
+
+The study procedure mirrored the setup of Study 1 and consisted of pre-,
+experience sampling-, and post-measurements. The participants were
+invited for experience sampling measurements twice a day (at 12pm and
+7pm) for 30 days. General compliance was high (70.87\% of all invited
+surveys were filled in). The response rates were approximately equal
+during mornings (\textit{n} = 2,608) and afternoons (\textit{n} =
+2,357). All key variables for this study were part of the short
+experience sampling surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+To measure intergroup contacts, every experience sampling measurement
+started with the question
+``\textit{Did you meet a Dutch person this morning [/afternoon]? (in-person interaction for at least 10 minutes)}''.
+Participants were additionally offered a pop-up explanation: ``With
+in-person interaction, we mean a continued interaction with another
+person (potentially in a group) that lasted at least 10 minutes. This
+interaction should be offline and face-to-face. It should include some
+form of verbal communication and should be uninterrupted to still count
+as the same interaction. Any individual interaction can last minutes or
+hours. If there were multiple interaction partners, we would like you to
+focus on the person that was most important to you during the
+interaction.''. The participants recorded between 1--43 interactions
+with Dutch majority people (1.64--93.75\% of individual experience
+sampling measurements; 935 of all 4,965 experience sampling responses).
+
+\paragraph{Psychological Needs}
+
+For the core situational need, we asked participants in an open-ended
+text field:
+``\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}''
+(where \textit{-X-} was dynamically replaced with the name of the
+interaction partner). Participants could additionally click on a pop-up
+explanation: ``Your main goal during an interaction can vary depending
+on the interaction. It could be to connect with friends, to find or
+provide help, to achieve academic ambitions, work on your fitness, work
+for a job, or simply to get a coffee, just as well as many other
+concrete or abstract goals that are important to you in the moment. It
+really depends on your subjective experience of the interaction.''.
+Then, with reference to the text entry, we asked how much this core need
+was fulfilled during the interaction or the past daytime period:
+``\textit{During your interaction with -X- [this morning / this evening] your goal (-previous text entry-) was fulfilled.}''
+on a continuous slider scale ranging from strongly disagree (1) to
+strongly agree (100).
+
+\paragraph{Perceived Interaction Quality}
+
+The ratings of the perceived contact quality were identical to Study 1.
+
+\paragraph{Outgroup Attitudes}
+
+As in Study 1, attitudes towards the Dutch majority outgroup were again
+measured using the feeling thermometer.
+
+\subsection{Results}
+
+\subsubsection{Contact Hypothesis}
+
+We tested the most general contact hypothesis as we did for Study 1. We
+find that having an outgroup interaction is indeed associated with
+significantly more positive outgroup attitudes within the participants
+(random slopes model; \textit{b} = 2.83, \textit{t}(4,850) = 3.57,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}1.28, 4.38{]}), even
+after controlling for having an interaction with a non-Dutch person
+(which did not relate to outgroup attitudes independently). We again
+added the participant means back into the model. We find that in this
+data set participant-level outgroup contact proportions were also a
+positive predictor of outgroup attitudes (\textit{b} = 26.55,
+\textit{t}(110) = 2.90, \textit{p} = 0.004, \textit{95\%CI}{[}8.61,
+44.46{]}). The relative number of non-outgroup interactions showed no
+such effect (for full results see \tblref{tab:intergroupGeneralTblLong},
+\fgrref{fig:ContactHypothesis}, as well as Online Supplementary Material
+A). Thus, in our second data set we also find that outgroup contacts
+show a positive effect on outgroup attitudes in the moment. We
+additionally find an average between-participant effect of the relative
+number of interactions participants had.
+
+\subsubsection{Core Need}
+
+We again sequentially tested the core need model as we did for Study 1.
+We find that in the multilevel models, the fulfillment of core
+situational needs during outgroup contacts was associated with more
+positive outgroup attitudes (random slopes model; \textit{b} = 0.13,
+\textit{t}(826) = 4.18, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.07, 0.19{]}) and also predicted higher perceived
+interaction quality (random slopes model; \textit{b} = 0.40,
+\textit{t}(826) = 6.46, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.28, 0.52{]}). Additionally, if we consider the
+influences of core need fulfillment and interaction quality on outgroup
+attitudes jointly, we find that virtually all variance is explained by
+perceived interaction quality (random slopes model; \textit{b} = 0.17,
+\textit{t}(825) = 5.56, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.11, 0.23{]}) and only little unique variance is
+still explained by core need fulfillment (\textit{b} = 0.03,
+\textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
+0.07{]}; also see \fgrref[-B]{fig:MainPaths} and
+\tblref{tab:intergroupNeedsTblLong} for full results). These results are
+consistent with the results in Study 1. We, thus, find support for our
+hypotheses that the fulfillment of core situational needs had a
+significant influence on outgroup attitudes and that this effect is
+likely explained by its effect through perceived interaction quality.
+
+\section{Study 3}
+
+The aim of this final study is to extend the previous studies by
+additionally testing Allport's conditions in an extensive longitudinal
+design and to compare the predictive powers of Allport's conditions and
+the core situational need fulfillment. For this study, we specifically
+recruited international medical students, because they represent a
+particular group of migrants who face structural requirements to
+integrate and interact with Dutch majority outgroup members on a daily
+basis. As part of their educational program, the migrants are required
+to take language courses and interact with patients as part of their
+medical internships and medical residency. The extensive longitudinal
+survey method again offers a large body of ecologically valid data on
+need satisfaction in real-life intergroup contact situations. Data were
+collected from November 8\textsuperscript{th}, 2019 to January
+10\textsuperscript{th}, 2020. The full preregistration is available at
+\citet[][]{KreienkampMasked2021f}. Correlations and descriptive
+statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+
+\subsection{Methods}
+
+\subsubsection{Participants}
+
+We recruited 71 international medical students using contacts within the
+University Medical School. We specifically targeted non-Dutch students,
+who had recently arrived in the Netherlands. Participants reported on
+their interactions for at least 30 days with two daily measures
+(capturing the morning and afternoon). With this design, we aimed at
+getting 50-60 measurements per participant (\textit{M} = 57.85,
+\textit{SD} = 20.68, \textit{total N} = 4,107). As with the previous
+studies, this offered sufficient power to model processes within
+participants. Participants were compensated in the same manner as during
+Study 1. The sample consisted of relatively young migrants (\(M_{age}\)
+= 22.68, \(SD_{age}\) = 3.10, 59 women). The sample fairly accurately
+describes the local population of young international medical
+professionals.
+
+\subsubsection{Procedure}
+
+The study procedure mirrored the setup of studies one and two, in that
+it consisted of pre-, experience sampling-, and post-measurement. The
+participants were invited for experience sampling measurements twice a
+day (at 12pm and 7pm) for 30 days. General compliance was high (85.92\%
+filled in at least 31 experience sampling surveys or more). The response
+rates were approximately equal during mornings (\textit{n} = 2,092) and
+afternoons (\textit{n} = 2,015). All key variables for this study were
+part of the short experience sampling surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+The measurement of intergroup contacts was identical to Study 2. The
+participants recorded between 1--71 interactions with Dutch outgroup
+members (2.13--87.18\% of individual experience sampling measurements;
+1,702 of all 4,107 experience sampling responses).
+
+\paragraph{Psychological Needs}
+
+The measurement of the core situational need and its fulfillment was
+identical to Study 2.
+
+\paragraph{Allport's Conditions}
+
+We measured how much each of the interactions fulfilled Allport's
+conditions of optimal contact using a common short scale comprised of
+four attributes \citep{Islam1993, Voci2003, AlRamiah2012a}. In
+particular, we asked participants to rate how much the interaction had
+equal status
+(``\textit{The interaction with [name interaction partner] was on equal footing (same status)}''),
+a common goal
+(``\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}''),
+support of authorities
+(``\textit{The interaction with [name interaction partner] was voluntary}''),
+and intergroup cooperation
+(``\textit{The interaction with [name interaction partner] was cooperative}'').
+We create a mean-averaged index of Allport's conditions in response to
+past findings indicating that the conditions are best conceptualized
+jointly and as functioning together rather than as fully independent
+factors \citep[][, p. 766]{Pettigrew2006}. For full psychometric
+information see Online Supplementary Material A.
+
+\paragraph{Perceived Interaction Quality}
+
+The ratings of the perceived interaction quality were identical to Study
+1.
+
+\paragraph{Outgroup Attitudes}
+
+Attitudes towards the Dutch majority outgroup were again measured using
+the feeling thermometer, as in studies one and two.
+
+\subsection{Results}
+
+\subsubsection{Contact Hypothesis}
+
+In a multilevel regression, we find that having an outgroup interaction
+was again associated with significantly more positive outgroup attitudes
+within the participants (random slopes model; \textit{b} = 5.57,
+\textit{t}(3,834) = 6.52, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}3.90, 7.23{]}), even after controlling for having an
+interaction with a non-Dutch (which did not relate to outgroup attitudes
+independently; for full results see
+\tblref{tab:intergroupGeneralTblLong} and
+\fgrref{fig:ContactHypothesis}). Thus, in our third data set, we find
+that the within-person contemporaneous effect of intergroup contact was
+consistent across all three studies.
+
+\subsubsection{Core Need}
+
+We tested the situational core needs model analogous to the previous
+studies. We find that the fulfillment of the core need during outgroup
+contacts was associated with more positive outgroup attitudes (random
+slopes model; \textit{b} = 0.19, \textit{t}(1,601) = 5.29, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.12, 0.27{]}) and also predicted
+higher perceived interaction quality (random slopes model; \textit{b} =
+0.43, \textit{t}(1,605) = 8.35, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.33, 0.54{]}). Additionally, once we consider the
+influences of core need fulfillment and interaction quality on outgroup
+attitudes jointly, we find that perceived interaction quality is a
+substantially stronger predictor (random slopes model; \textit{b} =
+0.17, \textit{t}(1,600) = 6.86, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.22{]}) and the unique variance explained by
+core need fulfillment was roughly half of its original effect size
+(\textit{b} = 0.11, \textit{t}(1,600) = 3.50, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.05, 0.17{]}; also see
+\fgrref[-C]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for
+full results). As with the previous two studies, these results indicate
+that in this data set outgroup attitudes were significantly predicted by
+the fulfillment of core situational needs and the results suggest that
+this might be due to higher perceived interaction quality.
+
+\subsubsection{Allport's Conditions}
+
+We tested the impact of Allport's conditions in the same manner as we
+tested our core needs model. In the multilevel models, we find that the
+fulfillment of Allport's Conditions during outgroup contacts was
+associated with more positive outgroup attitudes (random slopes model;
+\textit{b} = 0.22, \textit{t}(1,601) = 5.86, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.15, 0.29{]}) and also predicted higher
+perceived interaction quality (random slopes model; \textit{b} = 0.65,
+\textit{t}(1,605) = 11.82, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we considered the
+influences of Allport's Conditions and interaction quality on outgroup
+attitudes jointly, we found that perceived interaction quality was a
+substantially stronger predictor (random slopes model; \textit{b} =
+0.17, \textit{t}(1,600) = 6.25, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
+Allport's Conditions was less than half of its original effect size
+(\textit{b} = 0.09, \textit{t}(1,600) = 2.89, \textit{p} = 0.004,
+\textit{95\%CI}{[}0.03, 0.15{]}; also see
+\tblref{tab:intergroupNeedsTblLong}). These results indicate that in
+this data set the fulfillment of Allport's conditions had a significant
+influence on outgroup attitudes and this effect is likely, in parts,
+explained by its effect through perceived interaction quality.
+
+\subsubsection{Compare Fulfillment of Core Need and Allport's Conditions}
+
+To test whether Allport's conditions or the core need fulfillment were
+better at predicting outgroup attitudes, we first assessed relative
+model performance indices (i.e., Akaike information criterion, and
+Bayesian information criterion), and then consider the two predictors in
+a joint model to see whether the two approaches predicted the same
+variance in outgroup attitudes. When comparing the model selection
+indices, we found that the fulfillment of the situational core need
+indeed performed slightly better than the model using Allport's
+conditions (\(AIC_{CoreNeed}\) 12632.02 \textless{} 12651.59
+\(AIC_{Allport}\), and \(BIC_{CoreNeed}\) 12664.55 \textless{} 12684.12
+\(BIC_{Allport}\)). Additionally, when considering the predictors
+jointly, we find that both significantly predict outgroup attitudes with
+similar-sized regression parameters (random slopes model; Allport's
+Conditions: \textit{b} = 0.16, \textit{t}(1,600) = 4.92, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.09, 0.24{]}, Core Need: \textit{b}
+= 0.14, \textit{t}(1,600) = 3.85, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.08, 0.17{]}; also see
+\tblref{tab:intergroupNeedsTblLong}). This indicates that, although both
+Allport's conditions and the core need fulfillment seem to (in part)
+work through perceived interaction quality, they explain different
+aspects of the variance in outgroup attitudes and do not constitute one
+another.
+
+\section{Stability, Robustness, and Embeddedness across Studies}
+
+Beyond the individual results of the three studies, we conducted a
+number additional analyses to test the broader cross-study claims,
+account for alternative models, and contextualize our results. Jointly,
+these stability, robustness, and embeddedness analyses seek to
+strengthen our confidence in the results.
+
+\subsection{Stability}
+
+We ran two analyses that tested the stability of our results. We first
+assess the consistency of the results reported in the three studies and
+use a meta-analytic approach to gauge the general effect sizes. The
+second stability analysis we conduct seeks to asses the extend to which
+the within person contemporaneous effects extend to an aggregated
+version that mirrors the many cross-sectional recall studies.
+
+\subsubsection{Consistency}
+
+We first assessed the stability of our main analyses across the three
+studies. Plotting the effect sizes of each parameter of interest in a
+forest plot, as well as the average meta-analytic effect, shows that for
+the basic contact hypothesis test outgroup contact had a strong and
+consistent effect on outgroup attitudes. Interactions with non-outgroup
+members consistently had no meaningful effect on outgroup attitudes
+(\fgrref{fig:ContactHypothesis}). While this would be expected from the
+general intergroup contact literature, this is not a trivial finding.
+Being among the first to assess the contact hypothesis using real-life
+intensive longitudinal data, we extend cross-sectional findings to
+individual-level assessments. When looking at the fulfillment of core
+needs during intergroup contacts, we find that the motivational
+mechanism is consistently a meaningful predictor of interaction quality
+perceptions and outgroup attitudes (see
+\fgrref[ A and B]{fig:AllportNeedFulfillment}). We also see that the
+effect of core need fulfillment on outgroup attitudes is strongly
+reduced when modeled together with interaction quality perceptions,
+supporting our assertion that interaction quality offers a psychological
+mechanism for the direct effect (see
+\fgrref[-C]{fig:AllportNeedFulfillment}).
+
+\subsubsection{Aggregated Analysis}
+
+A second stability test is checking whether the within person effects
+translate to a broader aggregated between subjects effect, which would
+mirror common cross-sectional practices. During the main analyses, we
+have thus far shown that participants held more positive outgroup
+attitudes following intergroup contacts and that perceived interaction
+quality was associated with more positive outgroup attitudes following
+an intergroup contact. We have, however, not brought the two elements of
+the contact hypothesis together in a single analysis. To jointly test
+the effects of contact frequency and average interaction quality, we ran
+a linear regression model where average outgroup attitudes were
+predicted by the number of interactions and the average interaction
+quality ratings of all participants across the three studies. We did so
+while controlling for the possible effects of study-specific
+differences. To include the study-membership as a control variable, we
+used the student sample (Study 2) as the reference group because it was
+both the largest and the most homogeneous study. Looking at the overall
+model, we found that the model predicted 13.89\% of the variance in
+average outgroup attitudes (\textit{F}(9, 189) = 3.39, \textit{p} =
+0.001, \textit{R\textsuperscript{2}} = 0.14). Looking at the individual
+effects, we found that only the number of outgroup interactions has a
+clear association with average outgroup attitudes (\textit{b} = 0.55,
+\textit{t}(189) = 2.82, \textit{p} = 0.005, \textit{95\%CI}{[}0.16,
+0.93{]}). The average interaction quality perceptions had a much smaller
+effect (\textit{b} = 0.29, \textit{t}(189) = 2.09, \textit{p} = 0.038,
+\textit{95\%CI}{[}0.02, 0.56{]}), and importantly we found no
+interaction effect at all. In short, the effect of interaction frequency
+did not depend on the average interaction quality.
+
+\subsection{Robustness}
+
+To check for spurious relationships, we test three additional models.
+These three models assess whether the effect is indeed specific to
+intergroup contact, whether the need fulfillment effect is a affected by
+whether the contact was planned or accidental, and whether the
+motivational mechanism also holds direct well-being benefits for the
+minority members. We describe the full methods and results for the
+robustness analyses in \appref{app:AppendixRobustness}. We use a
+two-staged analysis approach for the robustness analyses. We first test
+the model `globally' --- across the three studies --- in a three level
+multilevel regression (i.e., measurements nested within participants,
+and participants nested within studies). Only in a second step do check
+for study-specific idiosyncrasies.
+
+\subsubsection{Contact specific}
+
+To ensure that the core need fulfillment is outgroup contact specific,
+we return to the full sample of intensive longitudinal measurements and
+test whether there is an interaction effect of outgroup contact (vs.~no
+outgroup contact) and core need fulfillment. We expected that the effect
+of core need fulfillment on outgroup attitudes is specific to outgroup
+interactions and not merely due to a more need-fulfilled life in
+general. Both in the global test, as well as in the individual studies,
+we consistently find a significant and meaningful interaction effect of
+outgroup interaction and key need fulfillment, indicating that key need
+fulfillment is specifically a powerful predictor of outgroup attitudes
+during intergroup contacts. When assessing the individual studies
+independently, we additionally find a strong main effect of contact as
+well as a smaller main effect of key need fulfillment, qualifying the
+contact-specific relationship (see \appref{app:AppendixRobustness} for
+full results). In sum, we thus find that at the effect of key need
+fulfillment on outgroup attitudes is particularly important for outgroup
+interactions (rather than only need fulfillment in general).
+
+\subsubsection{Interaction intend}
+
+To test whether the need mechanism was affected by whether the
+interaction was accidental or planned we ran an exploratory moderation
+analysis using the participants' ratings of how much they perceived the
+interaction as `accidental'. It should be noted that, in order to keep
+the ESM surveys short, we asked our participants to focus on most the
+important interaction (i.e.,
+``\textit{The following questions will be about the interaction \underline{you consider most significant}.}'';
+emphasis as in original). This was also reflected in a relatively low
+average and consistent right skew of the `accidental' item. Nonetheless,
+there remained a substantial variance in the item and we continued with
+the moderation analysis. We found that both in the overall test as in
+all studies individually key need fulfillment remained a strong
+predictor of outgroup attitudes, even when accounting for differences in
+whether the interaction was accidental (rather than planned). Moreover,
+in none of the analysis did we see a moderation effect of interaction
+intend nor did we find a main effect of interaction intend. There is,
+thus, consistent evidence that the need fulfillment mechanism was not
+meaningfully different for more accidental interactions.
+
+\subsubsection{Well-being outcome}
+
+Given the well-established criticism that more positive outgroup
+attitudes might not always be beneficial for minority group members
+\citep[e.g.,][]{reimer2023}, we conducted an additional exploratory
+analysis assessing the effect of need fulfilling outgroup interactions
+on reported well-being. Experienced well-being is a common indicator of
+health and an important life quality measurement in itself, especially
+for migrants or other minority groups \citep[e.g.,][]{bhugra2011}. We
+find that the results with well-being as the outcome variable mirror our
+main results in effect size and interpretation. The results are
+consistent across and within studies and, thus, add weight to the
+importance of considering the need fulfillment experiences when it comes
+to outgroup interactions.
+
+\subsection{Embeddedness}
+
+To embed our results further, we also considered the content and types
+of needs that participants reported during the study. For these
+embeddedness analyses, we first assessed the self-reported motives of
+the participants and then also control the commonly considered
+self-determination theory needs.
+
+\subsubsection{Contact need content}
+
+We used the qualitative data from the participants' self-identified core
+needs to contextualize the results of our main analysis. However,
+because our participants jointly reported on thousands of intergroup
+contacts, it would not have been feasible to analyze these qualitative
+responses in a traditional qualitative content analysis. We instead
+relied on recent machine learning advances within the natural language
+processing domain. For our analysis, we used the BERT language model.
+BERT (Bidirectional Encoder Representations from Transformers) was
+developed by Google in 2018 and today forms a key element of many
+natural language processing workflows. In its essence, BERT is a
+framework that allows users to codify every word in relation to every
+other word within a large set of documents. We extracted 47 topics from
+the 2,983 interaction goal free-text entries (after duplicate removal)
+--- a relatively large number of topics. The higher number of topics
+allowed us to retain more of the smaller topics and leaves a relatively
+low number of 308 free-text entries unclassified (10.33\%). A full
+write-up of the topic modeling process is available in Online
+Supplemental Material C.
+
+In terms of the content of the topics, we find that a number of topics
+are primarily task-oriented, where participants hope to increase their
+study, research, presentation, or work performance. Opposing the task-
+and work-oriented needs, are a wide variety of leisure-related needs
+wishes, like relaxation and entertainment. Additionally, some clusters
+were primarily relationship-oriented, so that participants sought
+contact with outgroup members for intimate and casual social contact in
+itself. Similarly, socializing and celebrations were also explicit
+social needs (incl., parties). This also included a subtopic of
+spiritual, religious, and otherwise transcendental needs
+(incl.~meditation, prayer, religious services). Among the
+leisure-oriented topics was also a set of contact goals that were
+specifically migration-specific (e.g., wish to learn about culture,
+politics, and language) or were concerned with informational needs more
+generally (e.g., seeking answers, bureaucratic information). A similar
+set of topics was specifically geared towards a wish to experience
+cultural products (e.g., music, theater, food) or had travel-related
+goals in their interactions with the majority group members. In sum,
+almost all extracted topics fall into broader or narrower need concepts
+that are commonly discussed within the need fulfillment literature
+\citep[e.g.,][]{orehek2018a} and offer insight into a core aspect of the
+migration experience that has remained broadly under-explored
+\citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
+The authors have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
+
+\subsubsection{Need types}
+
+To ensure that our results are not impacted by differences in the
+reported goals and motives, we additionally coded the topics we
+extracted during the topic modeling on two dimensions of how much they
+reflect a practical and a psychological goal-directedness. We chose
+practical and psychological needs specifically as our dimensions to
+account for differences in the types of needs that participants commonly
+reported. With practical motives we refer to specific, tangible goals or
+tasks that participants aimed to accomplish during the interaction.
+These instrumental goals are usually observable, concrete, and often
+centered on external outcomes, such as acquiring resources, completing
+tasks, and addressing immediate challenges \citep[e.g.,][]{oduntan2019}.
+With psychological motives we refer to underlying motives or desires
+that are more abstract and relate to personal fulfillment and
+well-being. In contrast to practical needs, psychological needs delve
+into the subjective and internal aspects of human experiences. These
+needs pertain to emotions, social connections, and cognitive processes,
+reflecting individuals' quest for personal growth, well-being, and
+thriving in social relationships \citep[e.g.,][]{dweck2017}. Note that
+with this approach any particular motive can include a practical and/or
+a psychological goal-directedness but can also be classified as not
+having any goal at all. We found high inter-rater reliability for the
+two independent coders, who coded all 47 topics. The codings revealed
+considerable variance, which allowed us to add the two dimensions back
+to each of the reported interaction motives and assess the effects of
+the goal-directed character.
+
+We found that neither in the overall analysis nor within any of the
+individual studies did different types of motives impact the positive
+effect of situational need fulfillment on outgroup attitudes.
+Situational need fulfillment ratings remained the only reliable
+predictor of outgroup attitudes, when controlling for practical and
+psychological goal-directedness as well as their interaction effect with
+the need fulfillment itself. This result underscores the importance of
+the experience of perceived need fulfillment (i.e., the perception that
+one got what one needed), rather than the type of need or the content of
+the need (i.e., the exact motive).
+
+\subsubsection{Specific psychological needs}
+
+Finally, to ensure that a much simpler model of three fundamental
+psychological needs might not account for the same effect, we compared
+our situation core need fulfillment measurement to the three
+self-determination theory needs (autonomy, relatedness, competence).
+Within the overall model we found that across the studies core need
+fulfillment remained a strong predictor of outgroup attitudes, even
+after controlling for the three self-determination theory need.
+Additionally, within this overall analysis, none of the
+self-determination theory needs independently predicted outgroup
+attitudes to a statistically significant extent (despite similar effect
+sizes of relatedness). When looking at the individual studies, we again
+saw that core need fulfillment remained a consistent predictor of
+outgroup attitudes. However, across all three studies the fulfillment of
+relatedness motives also emerged as a consistent predictor of outgroup
+attitudes. Additionally, in the larger studies 2 and 3 competence
+fulfillment was also related to more positive outgroup attitudes. None
+of the autonomy fulfillment effects reached statistical significance. In
+short, find that across our samples, relatedness fulfillment (and to a
+smaller extend competence fulfillment) are instrumental in understanding
+when an outgroup contact leads to more positive outgroup attitudes.
+Importantly, even when considering these effects situational core need
+fulfillment remains a strong and consistent predictor of outgroup
+attitudes.
 
@@
 
-\input{Robustness-Methods-and-Results.tex}
+As with the main analyses, full surveys are available in our OSF
+repository \citep{KreienkampMasked2022a} and the full data description
+is available in Online Supplementary Material A. Correlations and
+descriptive statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+
+\subsection{Additional Materials}
+
+In addition to the measurement of whether or not participants had an
+intergroup interaction and their situational core need fulfillment, we
+also included a number of variables that allowed us to assess the
+robustness of our results.
+
+\subsubsection{Specific Psychological Needs}
+
+In addition to the intergroup contact dummy and situational core need
+reported in the main text, we included a common measure of three
+self-determination theory needs \citep[see][]{Downie2008}. The
+measurement was identical in all three studies. The items were
+introduced either by ``\textit{During the interaction:}'' or
+``\textit{This morning [/afternoon]:}'' and measured autonomy
+(``\textit{I was myself.}''), competence
+(``\textit{I felt competent.}''), and relatedness (without intergroup
+contact ``\textit{I had a strong need to belong}''; with intergroup
+contact: ``\textit{I shared information about myself.}'' and
+``\textit{The other(s) shared information about themselves.}''). All
+items were rated on a continuous slider scale from very little (-50) to
+a great deal (+50).
+
+\subsubsection{Interaction Intent}
+
+To assess whether an interaction was accidental (vs.~planned), we asked
+participants with a single item to report the extent to which ``The
+interaction with -X- was accidental''. The respondents were asked to
+report this context variable for all interactions they reported on using
+a continuous slider ranging from ``not at all'' (0), through ``very
+little'' (33) and ``somewhat'' (66), to ``a great deal'' (100). In all
+studies, the scale showed a right skew (\textit{mean} = 29.60,
+\textit{sd} = 33.68).
+
+\subsubsection{Goal-directedness}
+
+To assess whether the need content (i.e., the motives) would impact the
+effect of the need fulfillment experiences, we manually coded the topics
+we extracted during the topic modeling on two dimensions of how much
+they reflect a practical and a psychological goal-directedness. We chose
+practical and psychological needs specifically as our dimensions to
+account for differences in the types of needs that participants commonly
+reported. With practical motives, we refer to specific, tangible goals or
+tasks that participants aimed to accomplish during the interaction.
+These instrumental goals are usually observable, concrete, and often
+centered on external outcomes, such as acquiring resources, completing
+tasks, and addressing immediate challenges \citep[][]{}. With
+psychological motives, we refer to underlying motives or desires that are
+more abstract and relate to personal fulfillment and well-being. In
+contrast to practical needs, psychological needs delve into the
+subjective and internal aspects of human experiences. These needs
+pertain to emotions, social connections, and cognitive processes,
+reflecting individuals' quest for personal growth, well-being, and
+thriving in social relationships \citep[][]{}. Note that with this
+approach any particular motive can include a practical and/or a
+psychological goal-directedness but can also be classified as not having
+any goal at all. The full coding protocol we developed with examples for
+each of the codes is available in our Online Supplemental Material D.
+After an initial training, each of the two coders independently coded
+the 47 topics on the two dimensions, using one of three options each
+(i.e., 0 = no goal, 1 = vague goal, 2 = clear goal). Inter-rater
+reliability assessments showed that for both the practical as well as
+the psychological needs, agreement was not optimal using the three
+answer options (agreement practical = 0.72\%, agreement psychological =
+0.78\%). However, most disagreements were, if a need was present,
+whether that need was vague (1) or concrete (2). We, thus, collapsed
+these two categories, making the ratings binary (need absent vs.~need
+present). With the simpler coding, inter-rater agreement for practical
+needs (0.93\%) and the psychological need (0.96\%) were much more
+reliable. Using Cohen's \(\kappa\) as our measure of inter-rater
+reliability, we find that both the practical need coding
+(\textit{Cohen's} \(\kappa\) = 0.80, 95\%CI{[}0.58, 1.00{]}) as well as
+the psychological need coding (\textit{Cohen's} \(\kappa\) = 0.86,
+95\%CI{[}0.67, 1.00{]}) were very good. We thus proceeded with this
+collapsed coding. After resolving coder disagreements and merging the
+codings back to the free-text responses, we found that a majority of
+responses showed both a practical as well as a psychological need
+(57.95\%) and only few responses had no goal at all (1.03\%) with the
+remaining 41.02\% having either a practical or a psychological need only
+(see Online Supplemental Material A for more detailed tables and
+visualizations).
+
+\subsubsection{Well-being}
+
+We measured experienced well-being using a visual analog scale adapted
+from \citet{davies2022}. Participants were asked to respond to the
+question ``How do you feel right now?'' using a continuous visual slider
+ranging from ``very sad''(-100) to ``very happy'' (100). The well-being
+ratings were generally normally distributed (\textit{mean} = 64.80,
+\textit{sd} = 19.25).
+
+\subsection{Results}
+
+To build further confidence in our results, we assessed a number of
+additional models that might offer alternative explanations. We will
+discuss the results in sequential order --- in every case first
+considering a global test of the model across the three studies and
+only then assessing whether the global three-level regression model
+suppresses any important person-level variations within the studies.
+
+\subsubsection{Contact specific}
+
+We begin our robustness analysis by testing whether the effect of core
+need fulfillment is specific to an actual outgroup contact, rather than
+need fulfillment in general. For this, we analyzed the generalized
+situational core need fulfillment (either during a contact or about the
+daytime in general) and tested whether the effect differed during
+experience sampling measurements with and without outgroup contacts. We
+start this test by assessing the effect across all three studies, using
+a three-level hierarchical model, where measurements are nested within
+participants, and participants are nested within studies. In this
+overall model, we found no main effect of core need fulfillment (random
+slopes model, grand-mean standardized to account for all levels of
+variance; \textit{b} = 0.62, \textit{t}( 3.187) = 2.89, \textit{p} =
+0.058, \textit{95\%CI}{[} 0.20, 1.03{]}) but a significant interaction
+effect of core need fulfillment and outgroup contact (\textit{b} = 2.44,
+\textit{t}(4,663.172) = 8.62, \textit{p} \textless{} .001,
+\textit{95\%CI}{[} 1.89, 3.00{]}; also see
+\tblref{tab:robustnessTblLong}). While the three-level hierarchical
+model can be sensitive to scaling issues, this already indicates that it
+is not key need fulfillment in general --- but only key need fulfillment
+during an outgroup contact that predicts more positive outgroup
+attitudes.
+
+To ensure that the results are not affected by scaling issues (e.g.,
+study-level variances suppressing person-level variances) or a similar
+Simpson's paradox, we additionally assess the model within each of the
+three studies. Within each of the three studies, the effects are more
+pronounced, so that we also see a significant effect of core need
+fulfillment (all \textit{b} \textgreater{} 0.06, all \textit{p}
+\textless{} 0.005) as well as outgroup contact itself (all
+\textbar{}\textit{b}\textbar{} \textgreater{} 1.81, all \textit{p}
+\textless{} 0.034) but the interaction effect consistently remains the
+most reliable predictor of outgroup attitudes (all
+\textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all \textit{p}
+\textless{} 0.002, also see \tblref{tab:robustnessTblLong}). There is
+thus consistent evidence that need fulfillment relates to outgroup
+attitudes for outgroup contacts in particular but not need fulfillment
+in general.
+
+\subsubsection{Interaction intent}
+
+Secondly, to assess whether the need fulfillment mechanism affected by
+whether the interaction was accidental or planned we ran an exploratory
+moderation analysis using the participants' ratings of how much they
+perceived the interaction as `accidental'. It should be noted that we
+asked our participants to focus on most the important interaction (i.e.,
+``\textit{The following questions will be about the interaction \underline{you consider most significant}.}'''\,'\,``;
+emphasis as in original). We again start our analysis approach by
+assessing the model across all three studies, using a three-level
+hierarchical model. In this overall model, we retain the main effect of
+core need fulfillment (random slopes model, grand-mean standardized to
+account for all levels of variance; \textit{b} = 2.87, \textit{t}(
+7.979) = 7.32, \textit{p} \textless{} .001, \textit{95\%CI}{[} 2.10,
+3.64{]}) but neither contact intent nor the moderation effect affect the
+results (all \textbar{}\textit{b}\textbar{} \textless{} 0.27 and all
+\textit{p} \textgreater{} 0.225; see \tblref{tab:robustnessTblLong} for
+full results).
+
+We again sought to ensure that the results were not affected by scaling
+issues by additionally assessing the interaction intentionality model
+within each of the three studies. Within each of the three studies, the
+effect of core need fulfillment became even clearer (all
+\textbar{}\textit{b}\textbar{} \textgreater{} 0.13, all \textit{p}
+\textless{} 0.006). But in none of the studies neither outgroup contact
+intention nor the moderation effect explained a significant amount of
+variance in outgroup attitudes (all \textbar{}\textit{b}\textbar{}
+\textless{} 0.03 and all \textit{p} \textgreater{} 0.073; also see
+\tblref{tab:robustnessTblLong}). There is thus consistent evidence that
+need fulfillment is related to outgroup attitudes, even when taking the
+intentionality of the interaction into account --- at least in our three
+samples and with a focus on the most significant interactions.
+
+\subsubsection{Well-being outcome}
+
+Thirdly, to build a stronger case for the relevance of need fulfillment
+to minority group members, we exploratorily assessed the effect of need
+fulfilling outgroup interactions on self-reported well-being. We, thus,
+re-ran our main analysis but substituted the outgroup attitudes outcome
+with situational well-being. As with the previous robustness analyses,
+we begin with a global three-level hierarchical model (across the three
+studies). We find that need fulfillment during outgroup contacts,
+indeed, has a similar effect on experienced well-being (random slopes
+model, grand-mean standardized to account for all levels of variance;
+\textit{b} = 3.50, \textit{t}(4.219) = 6.33, \textit{p} = 0.003,
+\textit{95\%CI}{[} 2.42, 4.58{]}). We found the same result when we
+assessed each of the three studies individually. In each of the studies,
+situational need fulfillment during the outgroup interaction was related
+to higher well-being ratings by the participants (random slopes model,
+centered within participants; all \textbar{}\textit{b}\textbar{}
+\textgreater{} 0.10, all \textit{p} \textless{} 0.009). We, thus, find
+consistent and meaningful evidence that need fulfilling outgroup
+interactions also relate to higher everyday well-being.
+
+\subsubsection{Need types}
+
+\paragraph{overall}
+
+Fourthly, to assess the role of different types of motives reported by
+our participants, we added our coding of practical and psychological
+goal-directedness as additional predictors to our base model. We thus
+had core need fulfillment predicting outgroup attitudes while also
+accounting for whether the reported motives were capturing practical
+and/or psychological motives. We again ran a global model, across the
+three studies first. We found that core need fulfillment remains a core
+predictor of outgroup attitudes (random slopes model, grand-mean
+standardized to account for all levels of variance; \textit{b} = 2.27,
+\textit{t}( 48.194) = 2.72, \textit{p} = 0.009, \textit{95\%CI}{[} 0.63,
+3.90{]}), even after accounting for different types of motives. None of
+the motive types nor the moderation effects reached statistical
+significance within the overall analysis (all
+\textbar{}\textit{b}\textbar{} \textless{} 1.45 and all \textit{p}
+\textgreater{} 0.073; see \tblref{tab:robustnessTblLong} for full
+results).
+
+\paragraph{Study follow-up}
+
+When looking at the individual studies, we again saw that the effect of
+core need fulfillment remained the on only clear effect (all
+\textbar{}\textit{b}\textbar{} \textgreater{} 0.14, all \textit{p}
+\textless{} 0.015). Additionally, in none of the studies neither motive
+type dummies nor the moderation effect explained a significant amount of
+variance in outgroup attitudes (all \textbar{}\textit{b}\textbar{}
+\textless{} 1.53 and all \textit{p} \textgreater{} 0.144; also see
+\tblref{tab:robustnessTblLong}). We, thus, find consistent evidence that
+need fulfillment is related to outgroup attitudes, even when taking the
+type of need into account --- at least in our three samples.
+
+\subsubsection{Specific psychological needs}
+
+In a final step, we checked whether during the interaction the core
+situational need remains a meaningful predictor even when taking other
+fundamental psychological needs into account. We again take a two-step
+approach, starting with cross-study global three-level test and then
+assessing the effects within the individual studies. Within the overall
+model, we find that across the studies core need fulfillment remained a
+strong predictor of outgroup attitudes, even after controlling for the
+three self-determination theory need (random slopes model, grand-mean
+standardized to account for all levels of variance; \textit{b} = 1.88,
+\textit{t}(2.705) = 4.75, \textit{p} = 0.022, \textit{95\%CI}{[} 1.11,
+2.66{]}). Within this overall analysis, none of the self-determination
+theory needs independently predicted outgroup attitudes to a
+statistically significant extent (all \textit{p} \textgreater{} 0.095).
+However, some of the effect sizes were largely comparable to that of the
+core need fulfillment (all \textbar{}\textit{b}\textbar{} \textless{}
+2.10, particularly that of relatedness fulfillment; see
+\tblref{tab:robustnessTblLong} for full results).
+
+When looking at the individual studies, we again saw that core need
+fulfillment remained a consistent predictor of outgroup attitudes, even
+after accounting for the self-determination theory need (all
+\textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all \textit{p}
+\textless{} 0.033). However, across all three studies, the fulfillment of
+relatedness motives also emerged as a consistent predictor of outgroup
+attitudes (all \textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all
+\textit{p} \textless{} 0.001). Additionally, in the larger studies 2 and
+3 competence fulfillment was also related to more positive outgroup
+attitudes (study 2: \textit{b} = 0.05, \textit{t}(841.8) = 2.43,
+\textit{p} = 0.015, \textit{95\%CI}{[} 0.01, 0.10{]}, study 3:
+\textit{b} = 0.06, \textit{t}(30.20) = 2.62, \textit{p} = 0.013,
+\textit{95\%CI}{[} 0.01, 0.10{]}). None of the autonomy fulfillment
+effects reached statistical significance nor did the competence
+fulfillment during study 1 (see \tblref{tab:robustnessTblLong} for the
+full results). In short, find that across our samples, relatedness
+fulfillment (and to a smaller extent competence fulfillment) are
+instrumental in understanding when an outgroup contact leads to more
+positive outgroup attitudes. Importantly, even when considering these
+effects situational core need fulfillment remains a strong and
+consistent predictor of outgroup attitudes. In some cases, we even find
+that core need fulfillment takes on some of the variance that would
+otherwise be explained by the self-determination theory needs (see
+Online Supplemental Material A).
 

### 2023-05-26 Tracked changes/comparison/main.tex
tracked changes updated

--- 2022-01-06 Backup/Before General Test Shortening/manuscript.tex
@@
 
+% ref labels
+\newcommand{\fgrref}[2][]{\hyperref[#2]{Figure \ref*{#2}#1}}
+\newcommand{\tblref}[2][]{\hyperref[#2]{Table \ref*{#2}#1}}
+\newcommand{\appref}[2][]{\hyperref[#2]{Appendix \ref*{#2}#1}}
+
+% custom open science badge height
+\newlength{\badgeheight}
+\setlength{\badgeheight}{1em}
+
 % language settings
@@
 % add reference library file
-\addbibresource{references.bib}
+\addbibresource{../../references.bib}
 
 % Title and header
-\title{Psychological Needs During Intergroup Contact}
+\title{Psychological Needs During Intergroup Contact: Three Experience Sampling Studies}
 \shorttitle{Needs in Intergroup Contact}
@@
 \affil[1]{University of Groningen, Department of Psychology}
-\affil[2]{Author-order to be discussed; currently alphabetic by last name.}
 
@@
 The authors received no specific funding for this work.
-Source data and  software is available at \url{https://janniscodes.github.io/intergroup-contact-needs/}.
-Protocols, materials, analysis data, and code are available at \url{osf.io}.
+Materials and software are available at \url{https://janniscodes.github.io/intergroup-contact-needs/}  \citep{Kreienkamp2022}.
+Protocols, materials, data, and code are available at \url{https://osf.io/pr9zs/?view_only=208a53a1f0ff48dda1c17357328fa578} \citep{Kreienkamp2022a}.
+The preregistration of Study 3 can be accessed as part of our Open Science Framework repository \citep{Kreienkamp2021f}
 
@@
 \abstract{
-Abstract goes here.
+One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations.
+We propose to consider situational psychological needs during everyday intergroup contact.
+We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297; total \textit{N} participants = 207).
+The novel psychological needs mechanism is consistently a strong predictor of positive attitudes during intergroup interactions and these positive effects emerged via perceived interaction quality.
+The situational needs model is robust to alternative models and outperforms Allport's contact conditions.
+As one of the first studies to test intergroup contact theory using extensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
 
-\noindent\textbf{Public significance statement}: Significance Statement goes here.
+\noindent\textbf{Public significance statement}: In this paper, we provide evidence that the fulfillment of situational psychological needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
+Methodologically, this offers testament to the emerging practice of capturing real-life interactions using extensive longitudinal data.
+Theoretically, our results give weight to motivational fulfillment as a flexible and effective mechanism for understanding positive intergroup contact.
 }
 
-\keywords{Intergroup Contact, Psychological Needs, Outgroup Attitudes, Interaction Quality, Extensive Longitudinal Data}
+\keywords{
+    Intergroup Contact, Psychological Needs, Outgroup Attitudes, Interaction Quality, Extensive Longitudinal Data\\
+    \textit{Open Science Practices:}
+    \noindent \href{https://osf.io/r5e8c?view_only=bfaed2196d49420385ce5fa6506a7765}{\includegraphics[height=\badgeheight]{assets/open-badges-small/registrationplus-color.png}} Preregistration+, 
+    \href{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970}{\includegraphics[height=\badgeheight]{assets/open-badges-small/material-color.png}} Open Materials, 
+    \href{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970}{\includegraphics[height=\badgeheight]{assets/open-badges-small/data-color.png}} Open Data,\break
+    \href{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970}{\includegraphics[height=\badgeheight]{assets/open-badges-small/code-color.png}} Open Code, 
+    \href{https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970}{\includegraphics[height=\badgeheight]{assets/open-badges-small/supplements-color.png}} Open Supplements
+    }
 
@@
 % Migrant Example Pathways
-\textbf{Relevance (Version 1 of 2): Migrant Example Version:}
-
-Conflict between social groups and their individual members remains a prevalent feature of the modern human condition.
-One of the main examples to date are the struggles of many migrants across the world, hoping to build a positive relationship with the majority group.
-One of the main ameliorations proposed by social psychologists has been the intergroup contact hypothesis.
-In its most essential interpretation, the intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
+% Relevance (Version 1 of 2): Migrant Example Version:
+One of the main intergroup societal issues to date, are the struggles of many migrants across the world, hoping to build a positive relationship with the majority group.
+The intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes be increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
 Over the past 70 years, a plethora of studies and interventions have shown the general effectiveness of positive intergroup contact \citep[e.g.,][]{Pettigrew2006}.
-However, even though a central assumption of intergroup contact theory has been that the contact should be positive, relatively little research has thus far explained when and why people perceive their everyday inter-group interactions as positive.
+However, even though a central assumption of intergroup contact theory is that the contact should be positive, relatively little research has thus far explained when and why people perceive their everyday intergroup interactions as positive.
 
 % Full Migrant Pathway
-\textbf{Relevance (Version 2 of 2): Full Migrant Focus Version:}
-
-The adaptation of migrants in new cultural contexts has become an important issue for many societies around the world.
+% Relevance (Version 2 of 2): Full Migrant Focus Version:
+%The adaptation of migrants in new cultural contexts has become an important issue for many societies around the world.
 A major aspect of such migrant adaptation arguably unfolds during the daily interactions migrants have with the cultural majority members \citep{Maxwell2017, Sam2010}.
-One of the main social psychological theories proposed for understanding how contact between groups functions has been the ’intergroup contact hypothesis’.
+One of the main social psychological theories aimed at understanding contact between social groups is ’intergroup contact hypothesis’.
 In its most essential interpretation, the intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
@@
 % Problem v.02: theoretical interaction quality central to understanding outcomes, practical many impactful negative interactions in everyday life
-\textbf{Problem Illustration Paragraph:}
-
-Importantly, not understanding when and why an interaction is perceived as positive presents substantial theoretical and practical obstacles.
-There is now consistent evidence that negative intergroup contacts lead to worse attitudes, prejudice, and future interaction motivation \citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.
-Theoretically, understanding whether an interaction is perceived as positive or negative (i.e., interaction quality) thus sits at the heart of when the intergroup contact hypothesis is successful (e.g., Brown et al.
-\citeyear{Brown2007}, Tropp et al.
-\citeyear{Tropp2016}; also cf.
-Allport’s original sentiment, Allport \citeyear{Allport1954b}).
-Practically, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in every-day life contexts.
+% Problem Illustration Paragraph:       
+Importantly, as we still fail to understand when and why an interaction is perceived as positive, substantial theoretical and practical challenges remain.
+There is now consistent evidence that negative intergroup contacts lead to worse attitudes, prejudice, and reduced future interaction motivation \citep[e.g.,][]{Barlow2012, Prati2021, Graf2014}.
+In light of these findings, understanding interaction quality thus sits at the heart of understanding when an intergroup contact is successful \citep[e.g.,][]{Allport1954b, Brown2007, Tropp2016}.
+But also in applied settings, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in everyday life contexts.
 Understanding the psychological mechanisms of when and why interactions are perceived as positive is, thus, an important issue for understanding whether an interaction leads to better intergroup perceptions, especially during everyday interactions outside the lab.
 
-% Aim / Solution v.02: look at need fulfillment as mechanism in daily interactions of migrants
-\textbf{Proposal Paragraph:}
-
-In this article, we propose that the fulfillment of fundamental psychological needs might offer a psycho-social mechanism for understanding and explaining contact quality and positive outgroup attitudes.
-That is to say, that if a person, for example, seeks to feel accepted by their interaction partner and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
-To test this, we collected three sets of real-life data from recent immigrants, tracking situational needs, interaction quality, and outgroup attitudes, following their daily interactions with majority group members.
+% Aim / Solution v.02: look at need fulfillment as a mechanism in daily interactions of migrants
+% Proposal Paragraph:
+We propose that one key to understanding how an interaction is perceived is to examine the level of need fulfillment it provided to an individual.
+As an example, if someone seeks acceptance by their interaction partner, and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
+To test this proposal, we collected three sets of real-life data from recent immigrants, assessing their daily interactions with majority group members, tracking situational needs, interaction quality, well-being, and outgroup attitudes.
 
@@
 % past research has either focused on conditions or cognitive-affective processes
-% neither are necessary or explain why an interaction is positive
+% neither are necessary nor explain why an interaction is positive
+\sout{Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.} When it comes to what constitutes a positive interaction the most widely used approach has been the idea that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact effect \citep[][]{Allport1954b, Pettigrew1969}.
+However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be necessary to finding positive effects of intergroup contact \citep[][]{Pettigrew2006}.
+Following Allport's original conditions, several additional conditions of optimal contact were proposed, which have largely received the same criticism of not capturing the underlying psychological mechanisms of why an interaction is perceived as positive \citep[for a critical discussion see][]{Pettigrew1986}.
 
-Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
-It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for such positive contact effects \citep[Allport's Optimal Contact conditions;][]{Allport1954b, Pettigrew1969}.
-However, a major meta-analysis of these contact conditions showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met \citep[][]{Pettigrew2006}.
-It, thus, remains unclear when and why exactly an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects\footnote{It should be noted here that following Allport's original conditions, several additional conditions of optimal contact were proposed \citep[for a critical discussion see][]{Pettigrew1986}.
-Similarly, since the early 21\textsuperscript{st} century many psychological processes during intergroup contact were examined \citep[e.g.
+Instead, since the early 21\textsuperscript{st} century, researchers have assumed positive contact and have focused on the psychological processes that explain how positive contacts improve intergroup relations \citep[e.g.
 see,][]{Paolini2021}.
-Among others, researchers have for example explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}.
-However, all these advances share the underlying criticism that they are not geared towards understanding when and why an interaction is perceived as positive.}.
-We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
+Among others, researchers have explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008}, as well as knowledge about the other group \citep[][]{Pettigrew2008c}.
+However, all these advances share a focus on understanding when and how \textit{positive interactions} improve intergroup relations.
+Understanding when and why an interaction is perceived as positive in the first place has remained a tangential focus and it, thus, remains largely unclear which psychological mechanisms drive positive interaction perceptions.
 
-% ALTERNATIVE: SHORTER BUT NOT FOCUSED ON ALLPORT'S CONDITIONS (WHICH WE TEST LATER)
-% Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
-Past research has either focused on conditions under which interactions tend to have favorable effects \citep[e.g., Allport's optimal conditions;][]{Allport1954b, Pettigrew1969} or has investigated cognitive-affective processes during contact \citep[e.g., group salience, intimacy, attachment, or intergroup anxiety;][]{Brown2005, Marinucci2021, Tropp2021, Paolini2004}.
-However, neither the contact conditions nor the cognitive-affective processes are particularly well equipped to explain when and why an interaction will be perceived as positive.
-We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
+In this article, we focus on the underexplored role of motivation and need fulfillment to understand when and why exactly an interaction is perceived as positive.
+We propose need fulfillment in particular, because a need mechanism builds a strong body of literature highlighting the functional role of need fulfillment in psychosocial functioning, interactions, and intergroup relations --- all of which are fundamental considerations for intergroup contact.
 
-% Important in broader field: needs have been found to be important in broader intergroup relations and interpersonal contact literature.
-Although considerations of psychological needs and motivations have remained markedly absent within the intergroup contact literature, the concepts are in no way foreign to the broader topic of intergroup relations.
-Psychological needs have for example found fruitful utility in reconciliation research \citep[][]{Shnabel2008}, the study of minority's discrimination experiences \citep[][]{Celebi2017}, and in non-intergroup interactions \citep[][]{Downie2008}.
-% On the most general level, research on intergroup conflicts has, for example, shown that addressing the group-specific needs predicts willingness to reconcile with the other group \citep[][]{Shnabel2008}.
-For the case of refugee migrants in their relationship with a majority group, a recent study found that identity needs will buffer against discrimination experiences and will protect personal health \citep[][]{Celebi2017}.
-Additionally, within the field of interpersonal relations, we find first evidence that the fulfillment of fundamental psychological needs might predict perceived interaction quality in non-intergroup interactions \citep[][]{Downie2008}.
-% Promising for intergroup contact: Asked for in intergroup contact reviews and first research looked at social change
-And even within the field of intergroup contact the idea of need fulfillment as a psychological mechanism is not entirely novel.
-\citet{Dovidio2017} in their narrative review have suggested that understanding psychological needs might be essential to constructive intergroup contact.
-And recently first empirical research has even found psychological need fulfillment during intergroup contacts to predict support for social change \citep[][]{Hassler2021}.
-There is thus initial evidence to suggest that need fulfillment during intergroup contact might offer a promising psychological mechanism to understand perceived interaction quality and positive outgroup attitudes.
+On an individual psychological level, need fulfillment has a long tradition of explaining what drives human adaptation and social relations.
+From the early works of \citet[][]{maslow1943} and \citet[][]{lewin1926e} to more recent works by \citet[][]{Ryan2017} or \citet[][]{Steverink2006}, the fulfillment of needs have been considered a driver of health, well-being, and psychosocial functioning.
+Most relevant to our proposal here, within experience sampling studies (psychological) need fulfillment has been found to explain variations in general well-being \citep[e.g.,][]{sheldon1996, reis2000} as well as well-being during daily interactions \citep[][]{Downie2008}.
+The importance of need fulfillment in interactions has also been substantiated by frameworks such as 'relationships motivation theory', which has collected substantive evidence for the importance of need fulfillment in understanding the success of close relationships \citep[e.g., see][]{knee2023}.
+There is, thus, a wealth of literature highlighting the importance of need fulfillment to positive everyday experiences and well-being.
+
+Beyond the well-being and psychosocial functioning perspective, need fulfillment has recently also seen application as a psychological mechanism in the intergroup relations literature.
+Social identity theory has famously focused on the role of self-esteem needs in understanding how people navigate intergroup contexts \citep[e.g.,][]{abrams1988}.
+A more recent example is the study of conflict and reconciliation where addressing differential needs of victims and perpetrators (i.e., the need for power and the need for morality respectively) increased willingness to reconcile \citep[][]{Shnabel2008}.
+And similarly, addressing a relevant need for identity continuity among refugees in Turkey bolstered resilience in the face of discrimination experiences \citep[][]{Celebi2017}.
+Most recently, an international cross-sectional study has applied a need-based approach to the effects of positive intergroup contact.
+The study found that minority members who generally perceive their positive intergroup contacts to be more empowering tended to report a smaller reduction in social change support than those who did not perceive their average interactions as empowering, especially when the inequality between groups was perceived as illegitimate \citep[][]{Hassler2021}.
+In short, an increasing amount of literature is emphasizing the significance of need satisfaction in comprehending intergroup relations.
+
+It is thus not surprising that in their perspectives paper on intergroup contact, Dovidio and colleagues propose that: "To achieve truly constructive intergroup relations, it is important that intergroup exchanges meet the psychological needs of both majority- and minority-group members." \citep[][p.
+6]{Dovidio2017}.
+A call that has thus far remained unanswered when it comes to the basic tenet that positive interactions drive the constructive part of intergroup contact.
 
@@
 % MAYBE MOVE THIS TO 'The Present Research Section'
-One reason why motivational considerations might have remained absent from the intergroup contact literature is that there is an overwhelming number of individual needs or goals that might be relevant to a person during an intergroup interaction.
-Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad range of fundamental psychological needs.
-To avoid this predicament we propose to start by using adaptive and responsive survey designs that allow a tailored approach based on the participants inputs \citep[e.g.,][]{Tourangeau2017}.
-In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., situation core need) and with reference to their own response the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment).
-Such an adaptive approach would allow us to test the fundamental psychological mechanism of whether situational psychological needs indeed predict perceived interaction quality and positive outgroup attitudes.
+One reason why motivational considerations might have remained absent from the intergroup contact literature is that there is an overwhelming number of individual motives or goals that might be relevant to a person during an intergroup interaction.
+Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad and diverse range of motives.
+However, while the individual need content differed between the different lines of research, what unites these approaches has been a focus on fulfilling the situationally relevant needs of people --- especially when we want to understand human functioning in social realms.
+We propose that the different lines of research share an underlying psychological mechanism, namely the motivational experience of need fulfillment.
+With motivation and need fulfillment we specifically mean the psychological experience of addressing an active and relevant need during the interaction.
+For our purposes, we define a need as:
 
-\section{Real-Life Process Data}
+\begin{definition}[Need]\label{def:need}
+A tension or deficiency in the organism that elicits a (non-specific) motivational force organizing affect, cognition, and behavior to reduce this unsatisfactory situation, which is to some extent necessary for the individual’s overall well-being.
+\begin{flushright}
+--- based on \citet[][]{dweck2017, Hull1943, Lewin1938, McClelland1987, Ryan2017, Steverink2006}
+\end{flushright}
+\end{definition}
+
+The psychological experience of need fulfillment is, thus, distinct from the content of the need (i.e., the motive or goal).
+The content could, for example, include physical motives (such as safety or hygiene) but also psychosocial motives \citep[such as acceptance or competence; e.g., see][]{pittman2007}.
+A need arises when a motive is thwarted or situationally active and relevant \citep[][]{leander2020, lewin1926e, gollwitzer1985e}.
+It is this perceived need and the perceived fulfillment of needs that we focus on in this article.
+This is not to say that considering specific motives is irrelevant to contact situations but instead we propose that the psychological experience of perceived need fulfillment is a core mechanism in understanding interaction quality perceptions, well-being, and outgroup attitudes.
+
+To test such a proposal we can rely on adaptive and responsive survey designs that allow a tailored approach based on the participants' inputs \citep[e.g.,][]{Tourangeau2017}.
+In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., name the situationally relevant need content), and with reference to their own response, the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment mechanism).
+Such an adaptive approach allows us to take the initial step of testing whether situational need fulfillment indeed generally predicts perceived interaction quality, well-being, and positive outgroup attitudes independent of need content.
+
+\section{Intergroup Contact in Daily Life}
 While we have argued that a need fulfillment mechanism is relevant to intergroup contact generally, its flexible and broad applicability might be ideally suited to address the pressing issue of understanding natural intergroup contacts outside the lab.
-Investigations of such 'real-life interactions' often suffer from the difficulty that past intergroup contact research has either focused on the mechanisms of individual interactions in artificial lab studies or has focused on longer-term recall self-reports of natural interactions \citep[e.g.,][]{Pettigrew2006}.
+Investigations of such `real-life interactions' often suffer from the difficulty that past intergroup contact research has either focused on the mechanisms of individual interactions in artificial lab studies (sometimes referred to as the intergroup interaction literature) or has focused on longer-term recall self-reports of natural interactions \citep[commonly referred to as the intergroup contact literature; also see][]{Pettigrew2006}.
+\citet[][]{MacInnis2015} have even pointed out that these two approaches tend to find conflicting effects --- where individual interactions (in the lab) have more negative effects and recall of real-world contact patterns have more positive effects for intergroup relations.
+We, thus, miss data that follows people in their diverse daily interactions and investigates the psychological mechanisms of contacts, especially as they compound over time.
 Even with extended intervention studies, the most fine-grained data available is usually limited to pre-post-control designs.
-Such empirical practices stand, however, in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the core idea of the contact hypothesis, which was focused on the daily interactions of people \citep[see][]{Allport1954b}.
-As a result, prominent figures within the intergroup contact field have called for studies that collect longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2008b, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017, Dixon2005}.
-Such data would be able to capture real-life interactions that include interaction-specific mechanism information close the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
-Moreover, because data is nested within participants, experience-sampling data often allows to capture large amounts of high-quality data with relatively few participants.}.
+
+The lack of longitudinal real-world data, however, stands in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the original contact hypothesis, which was focused on the daily interactions of people \citep[][]{Allport1954b}.
+As a result, prominent researchers in the field have long called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
+Such data would be able to capture real-life interactions that include interaction-specific mechanism information close to the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
+Moreover, because data is nested within participants, experience-sampling data often allows capturing large amounts of high-quality data with relatively few participants \citep[][]{shiffman2008}.}.
 
@@
 However, recent technological developments allow us to easily collect experience sampling data on mobile devices \citep[e.g.,][]{Keil2020} or using web-based applications \citep[e.g.,][]{Arslan2020}.
-At the same time, analytical methods for such more complex data have become more readily available, making the analyses more approachable \citep[see, e.g.,][]{ODonnell2021}.
-Given these, technological and methodological developments, we were able to collect a large amount of real-life data following the daily intergroup interactions of recent migrants with the majority group members.
+At the same time, analytical methods for such more complex data have become more readily available, making the analyses more approachable \citep[e.g., see][]{ODonnell2021}.
+Given these technological and methodological developments, we were able to collect three independent studies of extensive real-life data following the daily intergroup interactions of recently arrived migrants with the majority-group members.
 
 \section{The Present Research}
-The aim of this paper is essentially threefold.
+Using three independent sets of extensive longitudinal data (Studies 1–3), the aim of this paper is essentially threefold.
 First, our study is among the first to test the fundamental tenets of intergroup contact and Allport's conditions in real-life extensive longitudinal data.
-Second, we test whether the fulfillment situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
-And third, we test the role of interaction quality in  the relationship of psychological need fulfillment and outgroup attitudes.
-Based on this we formulated three main hypotheses:
-\begin{enumerate}[label=H\arabic*:]
-    \item Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes across extensive longitudinal data.
-    \item Based on Allport’s optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
-    \item Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
+Translating the contact hypothesis into extensive longitudinal data is not a trivial task, as past research traditions have used two fundamentally different approaches.
+While lab studies have tended to focus on the effect of a single positive interaction, cross-section studies have primarily investigated the frequency of positive interactions more generally.
+Extensive longitudinal data allows us to investigate both.
+We can test whether having an interaction vs.
+not having an interaction improves intergroup relations, but we can also use the participant's 30-day contact reports to test whether participants with more positive interactions tend to benefit more from intergroup contact.
+Testing both approaches to the contact hypothesis allows us to go beyond a replication of the basic theory but could disentangle individual- from aggregated contact effects and would allow for a direct comparison with both bodies of literature.
+
+A second key decision was our choice to focus on the minority experience during the contact.
+While the same mechanisms should hold for the experience of members in high-powered groups, there is substantially more research available that focuses on the experience of the majority group, and minority perspectives are historically often understudied \citep[e.g.,][]{Dovidio2017}.
+At the same time, however, minority groups are often underprivileged and research is direly needed to understand the more prevalent experiences of stress and health issues among minorities \citep[e.g.,][]{alvidrez2019}.
+
+A third and final non-trivial aspect of translating the intergroup contact hypothesis into extensive real-world data was the choice of the outcome variable.
+For our main analyses, we chose outgroup attitudes --- the positive or negative evaluation of the other group.
+We chose outgroup attitudes mainly because they are the most common outcome considered within the intergroup contact literature \citep[e.g.,][]{Pettigrew2006, Paolini2021}.
+As the methodology is relatively new to the field, we sought to first replicate (and then extend) the most reliable effects of the contact hypothesis within the ESM data.
+Outgroup attitudes are, however, not without controversy, especially for minority group members' intergroup contact.
+In particular, positive outgroup attitudes have been shown to increase harmony and reduce the willingness to support social change among the disadvantaged in some cases --- even in the face of injustice \citep[e.g.,][]{dixon2012, saguy2009}.
+While a recent review found the effect to be less conclusive for longitudinally collected data and less consistent for positive interactions (rather than interactions generally), the backfire effect remains an important possibility for the present data \citep[see][]{reimer2023}.
+In order to ensure at least a direct benefit to the minority group members, we also assess the effect of the need fulfillment mechanism on well-being as the dependent variable as part of our robustness analyses below.
+
+With these important considerations in mind, we test the basic contact hypothesis within and across the three studies.
+In particular, we assess the effect of individual interactions within each study using a multilevel model, but to avoid power limitations, we test the collective effect of contact frequency and -quality after the individual studies, across all participants.
+\begin{enumerate}[leftmargin=1.5\parindent]
+    \item[H1:] Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for more favorable outgroup attitudes within and across extensive longitudinal data.
 \end{enumerate}
-Beyond these main hypotheses we have formulated several sub-hypotheses that form the basis for our analysis plan (these sub-hypotheses also include several robustness checks and are available in Appendix \ref{app:AppendixHypotheses}).
-Given the more complex data structure of the extensive longitudinal data, we opted to test our hypotheses using a multilevel regression model, where the measurement occasions (level 1) were nested within the participants (level 2).
-Given that more complex dynamic modeling procedures are not necessary to test these more basic hypotheses, we will focus on the contemporaneous effect of the data (e.g., need fulfillment during the intergroup interaction predicts outgroup attitudes following the interaction).
-Such an approach is also tolerant to missing data and uneven case numbers within participants.
 
-To test our main hypotheses, we collected three independent sets of extensive longitudinal data (Studies 1–3).
-The full surveys are available in Supplementary Materials A as well as in our open science repository (including a complete codebook, see OSF-REFERENCE).
-Our most comprehensive study (Study 3) was fully preregistered  \citep[available at][]{Kreienkamp2021f}.
-The fully annotated analyses are available in Supplementary Material B.
-As is common with multilevel analyses, we use a hierarchical modeling approach and always report the final model in-text (for the full modeling process see Supplementary Material B).
+The test of Allport's conditions is notably restricted to measurements that report on outgroup interactions because Allport's conditions and interaction quality ratings cannot meaningfully be measured or imputed if participants did not have an interaction.
+Focusing on the interactions in detail, we use a multi-level regression model to test whether interactions that are higher in the fulfillment of Allport's conditions predict more favorable outgroup attitudes.
+We would also expect that this is due to such interactions being perceived as higher in interaction quality.
+\begin{enumerate}[leftmargin=1.5\parindent]
+    \item[H2:] Based on the literature about Allport’s optimal contact conditions, intergroup interactions that are higher in equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
+\end{enumerate}
 
-\input{Methods-and-Results}
+Once the general contact hypothesis is established within the ESM data, our second main aim is to test our main theoretical proposal that the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
+As our main proposal is concerned with the mechanisms of successful intergroup contact, we again focus on outgroup interaction reports.
+Within a multi-level model, we expect interactions that are higher in situational core need fulfillment to be perceived as more positive, and as a result that these interactions also predict more positive outgroup attitudes.
+We also expect the needs mechanism to work at least as well as Allport's conditions.
+We particularly expect part of Allport's contact conditions to be a static set of situational needs so that the situational core need fulfillment should explain some of the same variance in outgroup attitudes.
+\begin{enumerate}[leftmargin=1.5\parindent]
+    \item[H3:] Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
+We also expect situational need fulfillments to work at least as well as Allport's optimal contact conditions in predicting outgroup attitudes.
+\end{enumerate}
+
+Our third aim is to ensure that our results are robust, stable, and ecologically valid.
+To test the robustness of our need-fulfillment mechanism we test whether the need mechanism is indeed specific to outgroup interactions and whether the process could be explained by a smaller set of fundamental psychological needs instead.
+We additionally, assess the need fulfillment mechanism in predicting individual well-being benefits and check whether different types of needs or interactions change the main results.
+We present the full robustness analyses in \appref{app:AppendixRobustness}.
+To test the stability and reliability of our results, we utilize forest plots and meta-analytic estimates for our main analyses.
+To assess the embeddedness of our situational core needs, we use an exploratory topic model for the participants' free-text entries and compare the extracted content topics with themes commonly found within the motivational literature.
+
+Before turning to individual studies, two methodological matters need consideration.
+Firstly, we tested most of our hypotheses using multilevel regression models, where measurement occasions (level 1) were nested within participants (level 2).
+This approach is tolerant to missing data and uneven case numbers within participants.
+Furthermore, we use a hierarchical modeling approach and report the final model in-text \citep[][; for the full modeling process see Supplementary Material A]{snijders2012}.
+Secondly, statistical power estimations for intensive longitudinal- and multilevel models are notoriously difficult due to the complex covariance structures.
+However, our participant- and measurement numbers are among the largest sample sizes found within the intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
+Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes (see Supplemental Material A).
+The sample sizes were only increased to allow for between-subjects comparisons and future, more complicated, time-series modeling.
+
+Finally, for our most comprehensive study (Study 3) we preregistered both the hypotheses as well as the analysis plan \citep[available at][]{KreienkampMasked2021f}.
+All studies received ethical approval from University Masked for Peer Review and none of the data has been published elsewhere.
+The detailed hypotheses and analysis plan are available in \appref{app:AppendixHypotheses}.
+The full surveys, code, and materials are available in our open science repository \citep[including a complete codebook;][]{KreienkampMasked2022a}.
+Additionally, the fully annotated analyses are available in Supplementary Material A.
+
+% Methods and Results from RMarkdown render
+\section{Study 1}
+
+Based on our main hypotheses, the aim of our first study was to
+specifically test the general contact hypothesis, the influence of core
+need fulfillment, and perceived interaction quality during intergroup
+contacts. To this aim, we recruited recent migrants to the Netherlands
+for an intensive longitudinal survey. Data were collected from May
+5\textsuperscript{th} through June 6\textsuperscript{th}, 2018 (and all
+participants started the study within the first two days). Correlations
+and descriptive statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide} (full data
+description is available in Online Supplementary Material A).
+
+\subsection{Methods}
+
+\subsubsection{Participants}
+
+After receiving ethical approval from the University Masked for Peer
+Review, we recruited 23 non-Dutch migrants using the local paid
+participant pool. Participants reported on their interactions for at
+least 30 days with two daily measures (capturing the morning and
+afternoon). With this design, we aimed at getting 50-60 measurements per
+participant (\textit{M} = 53.26, \textit{SD} = 16.72, \textit{total N} =
+1,225). This is a common number of measurements found in experience
+sampling studies and offers sufficient power to model processes within
+and between participants \citep[e.g.,][]{AanhetRot2012}. Participants
+were compensated for their participation with up to 34 Euros -- each two
+Euros for pre- and post-questionnaire and 50 Eurocents for every
+experience sampling measurement. The sample consisted of relatively
+young, educated, and western migrants from the global north (\(M_{age}\)
+= 24.35, \(SD_{age}\) = 4.73, 19 women, 15 students). The sample
+accurately describes the largest groups of migrants in the region
+\citep[][]{GemeenteGroningen2015}.
+
+\subsubsection{Procedure}
+
+The study itself consisted of three main parts, an introductory
+pre-measurement, the daily experience sampling measurements, and a
+concluding post-measurement. After giving informed consent, participants
+filled in an online pre-questionnaire assessing demographics and general
+information about their immigration. Over the next thirty days,
+participants were invited twice a day (at 12pm and 7pm) to reflect upon
+their interactions, psychological need fulfillments, and current
+attitudes towards the Dutch outgroup. General compliance was high
+(85.90\% of all invited surveys were filled
+in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%).}.
+The response rates were approximately equal during mornings (\textit{n}
+= 621) and afternoons (\textit{n} = 604) and most measurements were
+completed within four hours of the invitation. After the final day of
+experience sampling measurements, participants were invited to fill in a
+longer post measurement survey that mirrored the pre-measurement. All
+key variables for this study were part of the short experience sampling
+surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+To test the prerequisite effect of intergroup contact, every experience
+sampling measurement started with the question
+``\textit{Did you meet a Dutch person this morning [/afternoon]? (In person interaction for at least 10 minutes)}''.
+Our participants recorded between 2--51 interactions with Dutch outgroup
+members (3.23--91.07\% of individual experience sampling measurements;
+387 of all 1,225 experience sampling
+responses)\footnote{Two participants only recorded two experience sampling measurements each and none of these included outgroup contacts.
+These participants are removed from any analyses that focus on outgroup contacts.}.
+
+\paragraph{Psychological Needs}
+
+Irrespective of whether participants had an interaction with Dutch
+people or not, everyone answered a short series of questions on
+psychological need fulfillment. However, whereas participants with
+interactions reported on the need fulfillment during the interaction,
+people without interactions with Dutch people judged the past daytime
+period in general. To assess the fulfillment of psychological needs, we
+included two types of need measurement: (1) the core situational need
+and (2) general self-determination theory needs.
+
+For the core situational need, we asked participants in an open-ended
+text field:
+``\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}''.
+Then, with reference to the text entry, we asked how much this core need
+was fulfilled during the interaction or the past daytime period:
+``\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}''
+on a continuous slider scale ranging from strongly disagree (-50) to
+strongly agree (+50). The self-determination theory need measurements
+are described in \appref{app:AppendixRobustness}.
+
+\paragraph{Perceived Interaction Quality}
+
+As an explanatory mechanism, we assessed ratings of the perceived
+interaction quality. As our main measurement, participants rated the
+statement ``\textit{Overall the interaction was …}'' on two continuous
+slider scales measuring pleasantness
+\citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
+
+\paragraph{Outgroup Attitudes}
+
+At the end of every experience sampling measurement, we asked all
+participants about their current attitudes towards the Dutch -- our main
+dependent variable. To assess the momentary outgroup evaluation we used
+the common feeling thermometer: ``How favorable do you feel towards the
+Dutch?'' \citep[][]{Lavrakas2008}. Participants then rated their
+attitude on a continuous slider scale from ``very cold -- 0'' through
+``no feeling -- 50'' to ``very warm -- 100''. Both the question phrasing
+as well as the tick labels were consistent with large-scale panel
+surveys \citep[e.g.,][]{DeBell2010}.
+
+\subsection{Results}
+
+\subsubsection{Contact Hypothesis}
+
+Using a multilevel regression, we find that having an outgroup contact
+is indeed associated with significantly more positive outgroup attitudes
+(\textit{b} = 2.48, \textit{t}(1,200) = 4.37, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}1.37, 3.59{]}), even after controlling for
+having an interaction with a non-Dutch (which did not relate to outgroup
+attitudes independently). Additionally, while multi-level regressions
+are generally robust against unequal cell sizes, we correct for
+inequalities by using centered predictors and reintroducing the means as
+level two predictors (\citealp{Yaremych2021}; for full results see
+\tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
+and Online Supplementary Material
+A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+This is unusual and might indicate that the effect is very consistent across participants.
+However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}.
+Thus, in our first data, we find initial evidence that outgroup contacts
+show a positive effect on outgroup attitudes within real-life data.
+
+\subsubsection{Core Need}
+
+The main proposal of our article is that the success of an outgroup
+contact might be explained by whether or not the contact fulfilled the
+person's core situational need. This should, in turn, be due to a higher
+perceived contact quality. We sequentially test whether the fulfillment
+of the core need during an interaction is (1) related to more positive
+outgroup attitudes, (2) higher perceived contact quality, and (3)
+whether the variance explained by the core need is subsumed by the
+perceived contact quality if considered jointly. We find that in the
+multilevel models, the fulfillment of core situational needs during
+outgroup contacts was associated with more positive outgroup attitudes
+(random slopes model; \textit{b} = 0.17, \textit{t}(365) = 2.93,
+\textit{p} = 0.004, \textit{95\%CI}{[}0.06, 0.29{]}) and also predicted
+higher perceived contact quality (random intercept model; \textit{b} =
+0.42, \textit{t}(365) = 8.07, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.32, 0.52{]}). Moreover, when we consider the
+influences of core need fulfillment and contact quality on outgroup
+attitudes jointly, we find that virtually all variance is explained by
+perceived contact quality (random slopes model; \textit{b} = 0.23,
+\textit{t}(364) = 4.22, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
+still explained by core need fulfillment (\textit{b} = 0.04,
+\textit{t}(364) = 0.64, \textit{p} = 0.523, \textit{95\%CI}{[}-0.08,
+0.15{]}, also see \fgrref[-A]{fig:MainPaths}). We thus find support for
+our hypotheses and can conclude that in this data set the fulfillment of
+core situational needs had a significant influence on outgroup
+attitudes. Additionally, this effect is likely explained by its effect
+through perceived contact quality.
+
+\section{Study 2}
+
+The aim of Study 2 is similar to Study 1, as we again test the general
+contact hypothesis, the influence of core need fulfillment, and
+perceived contact quality during intergroup contacts. However, in this
+second study we collected a substantially larger sample of international
+students who recently arrived in the Netherlands and also improved the
+study design (e.g., pop-up explanations described later). The survey
+method again offers a large body of ecologically valid data on need
+satisfaction in real-life intergroup contact situations as these
+students will likely interact with the Dutch majority outgroup on a
+daily basis. Data were collected from November 19\textsuperscript{th},
+2018 through January 6\textsuperscript{th}, 2019. Correlations and
+descriptive statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+
+\subsection{Methods}
+
+\subsubsection{Participants}
+
+We recruited 113 international students using a local participant pool.
+We specifically targeted non-Dutch students, who had recently arrived in
+the Netherlands. Participants reported on their interactions for at
+least 30 days with two daily measures (capturing the morning and
+afternoon). With this design, we again aimed at receiving 50-60
+measurements per participant (\textit{M} = 43.94, \textit{SD} = 15.00,
+\textit{total N} = 4,965). As with the previous study, this should offer
+sufficient power to model processes within participants and will lend
+stronger weight to between-participant results. Participants were
+compensated for their participation with partial course credits ---
+depending on their participation. The sample consisted of relatively
+young migrants, who were mostly from the global north (\(M_{age}\) =
+20.24, \(SD_{age}\) = 2.12, 84 women). The sample fairly accurately
+describes the local population of international students.
+
+\subsubsection{Procedure}
+
+The study procedure mirrored the setup of Study 1 and consisted of pre-,
+experience sampling-, and post-measurements. The participants were
+invited for experience sampling measurements twice a day (at 12pm and
+7pm) for 30 days. General compliance was high (70.87\% of all invited
+surveys were filled in). The response rates were approximately equal
+during mornings (\textit{n} = 2,608) and afternoons (\textit{n} =
+2,357). All key variables for this study were part of the short
+experience sampling surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+To measure intergroup contacts, every experience sampling measurement
+started with the question
+``\textit{Did you meet a Dutch person this morning [/afternoon]? (in-person interaction for at least 10 minutes)}''.
+Participants were additionally offered a pop-up explanation: ``With
+in-person interaction, we mean a continued interaction with another
+person (potentially in a group) that lasted at least 10 minutes. This
+interaction should be offline and face-to-face. It should include some
+form of verbal communication and should be uninterrupted to still count
+as the same interaction. Any individual interaction can last minutes or
+hours. If there were multiple interaction partners, we would like you to
+focus on the person that was most important to you during the
+interaction.''. The participants recorded between 1--43 interactions
+with Dutch majority people (1.64--93.75\% of individual experience
+sampling measurements; 935 of all 4,965 experience sampling responses).
+
+\paragraph{Psychological Needs}
+
+For the core situational need, we asked participants in an open-ended
+text field:
+``\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}''
+(where \textit{-X-} was dynamically replaced with the name of the
+interaction partner). Participants could additionally click on a pop-up
+explanation: ``Your main goal during an interaction can vary depending
+on the interaction. It could be to connect with friends, to find or
+provide help, to achieve academic ambitions, work on your fitness, work
+for a job, or simply to get a coffee, just as well as many other
+concrete or abstract goals that are important to you in the moment. It
+really depends on your subjective experience of the interaction.''.
+Then, with reference to the text entry, we asked how much this core need
+was fulfilled during the interaction or the past daytime period:
+``\textit{During your interaction with -X- [this morning / this evening] your goal (-previous text entry-) was fulfilled.}''
+on a continuous slider scale ranging from strongly disagree (1) to
+strongly agree (100).
+
+\paragraph{Perceived Interaction Quality}
+
+The ratings of the perceived contact quality were identical to Study 1.
+
+\paragraph{Outgroup Attitudes}
+
+As in Study 1, attitudes towards the Dutch majority outgroup were again
+measured using the feeling thermometer.
+
+\subsection{Results}
+
+\subsubsection{Contact Hypothesis}
+
+We tested the most general contact hypothesis as we did for Study 1. We
+find that having an outgroup interaction is indeed associated with
+significantly more positive outgroup attitudes within the participants
+(random slopes model; \textit{b} = 2.83, \textit{t}(4,850) = 3.57,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}1.28, 4.38{]}), even
+after controlling for having an interaction with a non-Dutch person
+(which did not relate to outgroup attitudes independently). We again
+added the participant means back into the model. We find that in this
+data set participant-level outgroup contact proportions were also a
+positive predictor of outgroup attitudes (\textit{b} = 26.55,
+\textit{t}(110) = 2.90, \textit{p} = 0.004, \textit{95\%CI}{[}8.61,
+44.46{]}). The relative number of non-outgroup interactions showed no
+such effect (for full results see \tblref{tab:intergroupGeneralTblLong},
+\fgrref{fig:ContactHypothesis}, as well as Online Supplementary Material
+A). Thus, in our second data set we also find that outgroup contacts
+show a positive effect on outgroup attitudes in the moment. We
+additionally find an average between-participant effect of the relative
+number of interactions participants had.
+
+\subsubsection{Core Need}
+
+We again sequentially tested the core need model as we did for Study 1.
+We find that in the multilevel models, the fulfillment of core
+situational needs during outgroup contacts was associated with more
+positive outgroup attitudes (random slopes model; \textit{b} = 0.13,
+\textit{t}(826) = 4.18, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.07, 0.19{]}) and also predicted higher perceived
+interaction quality (random slopes model; \textit{b} = 0.40,
+\textit{t}(826) = 6.46, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.28, 0.52{]}). Additionally, if we consider the
+influences of core need fulfillment and interaction quality on outgroup
+attitudes jointly, we find that virtually all variance is explained by
+perceived interaction quality (random slopes model; \textit{b} = 0.17,
+\textit{t}(825) = 5.56, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.11, 0.23{]}) and only little unique variance is
+still explained by core need fulfillment (\textit{b} = 0.03,
+\textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
+0.07{]}; also see \fgrref[-B]{fig:MainPaths} and
+\tblref{tab:intergroupNeedsTblLong} for full results). These results are
+consistent with the results in Study 1. We, thus, find support for our
+hypotheses that the fulfillment of core situational needs had a
+significant influence on outgroup attitudes and that this effect is
+likely explained by its effect through perceived interaction quality.
+
+\section{Study 3}
+
+The aim of this final study is to extend the previous studies by
+additionally testing Allport's conditions in an extensive longitudinal
+design and to compare the predictive powers of Allport's conditions and
+the core situational need fulfillment. For this study, we specifically
+recruited international medical students, because they represent a
+particular group of migrants who face structural requirements to
+integrate and interact with Dutch majority outgroup members on a daily
+basis. As part of their educational program, the migrants are required
+to take language courses and interact with patients as part of their
+medical internships and medical residency. The extensive longitudinal
+survey method again offers a large body of ecologically valid data on
+need satisfaction in real-life intergroup contact situations. Data were
+collected from November 8\textsuperscript{th}, 2019 to January
+10\textsuperscript{th}, 2020. The full preregistration is available at
+\citet[][]{KreienkampMasked2021f}. Correlations and descriptive
+statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+
+\subsection{Methods}
+
+\subsubsection{Participants}
+
+We recruited 71 international medical students using contacts within the
+University Medical School. We specifically targeted non-Dutch students,
+who had recently arrived in the Netherlands. Participants reported on
+their interactions for at least 30 days with two daily measures
+(capturing the morning and afternoon). With this design, we aimed at
+getting 50-60 measurements per participant (\textit{M} = 57.85,
+\textit{SD} = 20.68, \textit{total N} = 4,107). As with the previous
+studies, this offered sufficient power to model processes within
+participants. Participants were compensated in the same manner as during
+Study 1. The sample consisted of relatively young migrants (\(M_{age}\)
+= 22.68, \(SD_{age}\) = 3.10, 59 women). The sample fairly accurately
+describes the local population of young international medical
+professionals.
+
+\subsubsection{Procedure}
+
+The study procedure mirrored the setup of studies one and two, in that
+it consisted of pre-, experience sampling-, and post-measurement. The
+participants were invited for experience sampling measurements twice a
+day (at 12pm and 7pm) for 30 days. General compliance was high (85.92\%
+filled in at least 31 experience sampling surveys or more). The response
+rates were approximately equal during mornings (\textit{n} = 2,092) and
+afternoons (\textit{n} = 2,015). All key variables for this study were
+part of the short experience sampling surveys.
+
+\subsubsection{Materials}
+
+\paragraph{Intergroup Contact}
+
+The measurement of intergroup contacts was identical to Study 2. The
+participants recorded between 1--71 interactions with Dutch outgroup
+members (2.13--87.18\% of individual experience sampling measurements;
+1,702 of all 4,107 experience sampling responses).
+
+\paragraph{Psychological Needs}
+
+The measurement of the core situational need and its fulfillment was
+identical to Study 2.
+
+\paragraph{Allport's Conditions}
+
+We measured how much each of the interactions fulfilled Allport's
+conditions of optimal contact using a common short scale comprised of
+four attributes \citep{Islam1993, Voci2003, AlRamiah2012a}. In
+particular, we asked participants to rate how much the interaction had
+equal status
+(``\textit{The interaction with [name interaction partner] was on equal footing (same status)}''),
+a common goal
+(``\textit{[name interaction partner] shared your goal ([free-text entry interaction key need])}''),
+support of authorities
+(``\textit{The interaction with [name interaction partner] was voluntary}''),
+and intergroup cooperation
+(``\textit{The interaction with [name interaction partner] was cooperative}'').
+We create a mean-averaged index of Allport's conditions in response to
+past findings indicating that the conditions are best conceptualized
+jointly and as functioning together rather than as fully independent
+factors \citep[][, p. 766]{Pettigrew2006}. For full psychometric
+information see Online Supplementary Material A.
+
+\paragraph{Perceived Interaction Quality}
+
+The ratings of the perceived interaction quality were identical to Study
+1.
+
+\paragraph{Outgroup Attitudes}
+
+Attitudes towards the Dutch majority outgroup were again measured using
+the feeling thermometer, as in studies one and two.
+
+\subsection{Results}
+
+\subsubsection{Contact Hypothesis}
+
+In a multilevel regression, we find that having an outgroup interaction
+was again associated with significantly more positive outgroup attitudes
+within the participants (random slopes model; \textit{b} = 5.57,
+\textit{t}(3,834) = 6.52, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}3.90, 7.23{]}), even after controlling for having an
+interaction with a non-Dutch (which did not relate to outgroup attitudes
+independently; for full results see
+\tblref{tab:intergroupGeneralTblLong} and
+\fgrref{fig:ContactHypothesis}). Thus, in our third data set, we find
+that the within-person contemporaneous effect of intergroup contact was
+consistent across all three studies.
+
+\subsubsection{Core Need}
+
+We tested the situational core needs model analogous to the previous
+studies. We find that the fulfillment of the core need during outgroup
+contacts was associated with more positive outgroup attitudes (random
+slopes model; \textit{b} = 0.19, \textit{t}(1,601) = 5.29, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.12, 0.27{]}) and also predicted
+higher perceived interaction quality (random slopes model; \textit{b} =
+0.43, \textit{t}(1,605) = 8.35, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.33, 0.54{]}). Additionally, once we consider the
+influences of core need fulfillment and interaction quality on outgroup
+attitudes jointly, we find that perceived interaction quality is a
+substantially stronger predictor (random slopes model; \textit{b} =
+0.17, \textit{t}(1,600) = 6.86, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.22{]}) and the unique variance explained by
+core need fulfillment was roughly half of its original effect size
+(\textit{b} = 0.11, \textit{t}(1,600) = 3.50, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.05, 0.17{]}; also see
+\fgrref[-C]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for
+full results). As with the previous two studies, these results indicate
+that in this data set outgroup attitudes were significantly predicted by
+the fulfillment of core situational needs and the results suggest that
+this might be due to higher perceived interaction quality.
+
+\subsubsection{Allport's Conditions}
+
+We tested the impact of Allport's conditions in the same manner as we
+tested our core needs model. In the multilevel models, we find that the
+fulfillment of Allport's Conditions during outgroup contacts was
+associated with more positive outgroup attitudes (random slopes model;
+\textit{b} = 0.22, \textit{t}(1,601) = 5.86, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.15, 0.29{]}) and also predicted higher
+perceived interaction quality (random slopes model; \textit{b} = 0.65,
+\textit{t}(1,605) = 11.82, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we considered the
+influences of Allport's Conditions and interaction quality on outgroup
+attitudes jointly, we found that perceived interaction quality was a
+substantially stronger predictor (random slopes model; \textit{b} =
+0.17, \textit{t}(1,600) = 6.25, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
+Allport's Conditions was less than half of its original effect size
+(\textit{b} = 0.09, \textit{t}(1,600) = 2.89, \textit{p} = 0.004,
+\textit{95\%CI}{[}0.03, 0.15{]}; also see
+\tblref{tab:intergroupNeedsTblLong}). These results indicate that in
+this data set the fulfillment of Allport's conditions had a significant
+influence on outgroup attitudes and this effect is likely, in parts,
+explained by its effect through perceived interaction quality.
+
+\subsubsection{Compare Fulfillment of Core Need and Allport's Conditions}
+
+To test whether Allport's conditions or the core need fulfillment were
+better at predicting outgroup attitudes, we first assessed relative
+model performance indices (i.e., Akaike information criterion, and
+Bayesian information criterion), and then consider the two predictors in
+a joint model to see whether the two approaches predicted the same
+variance in outgroup attitudes. When comparing the model selection
+indices, we found that the fulfillment of the situational core need
+indeed performed slightly better than the model using Allport's
+conditions (\(AIC_{CoreNeed}\) 12632.02 \textless{} 12651.59
+\(AIC_{Allport}\), and \(BIC_{CoreNeed}\) 12664.55 \textless{} 12684.12
+\(BIC_{Allport}\)). Additionally, when considering the predictors
+jointly, we find that both significantly predict outgroup attitudes with
+similar-sized regression parameters (random slopes model; Allport's
+Conditions: \textit{b} = 0.16, \textit{t}(1,600) = 4.92, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}0.09, 0.24{]}, Core Need: \textit{b}
+= 0.14, \textit{t}(1,600) = 3.85, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.08, 0.17{]}; also see
+\tblref{tab:intergroupNeedsTblLong}). This indicates that, although both
+Allport's conditions and the core need fulfillment seem to (in part)
+work through perceived interaction quality, they explain different
+aspects of the variance in outgroup attitudes and do not constitute one
+another.
+
+\section{Robustness, Stability, and Embeddedness across Studies}
+
+Beyond the individual results of the three studies, we conducted three
+additional analyses to test the broader cross-study claims and
+contextualize our results. In particular, we aimed to gain a broader
+picture of the individual results by considering them jointly. We also
+leveraged the data from all participants to test between-participant
+contact effects and explore the content of the participants' situational
+contact needs.
+
+\subsection{Stability}
+
+We first assessed the stability of our main analyses across the three
+studies. Plotting the effect sizes of each parameter of interest in a
+forest plot, as well as the average meta-analytic effect, shows that for
+the basic contact hypothesis test outgroup contact had a strong and
+consistent effect on outgroup attitudes. Interactions with non-outgroup
+members consistently had no meaningful effect on outgroup attitudes
+(\fgrref{fig:ContactHypothesis}). While this would be expected from the
+general intergroup contact literature, this is not a trivial finding.
+Being among the first to assess the contact hypothesis using real-life
+intensive longitudinal data, we extend cross-sectional findings to
+individual-level assessments. When looking at the fulfillment of core
+needs during intergroup contacts, we find that the motivational
+mechanism is consistently a meaningful predictor of outgroup attitudes
+and interaction quality perceptions (see
+\fgrref[ A and B]{fig:AllportNeedFulfillment}). We also see that the
+effect of core need fulfillment on outgroup attitudes is strongly
+reduced when modeled together with interaction quality perceptions,
+supporting our assertion that interaction quality offers a psychological
+mechanism for the direct effect (see
+\fgrref[-C]{fig:AllportNeedFulfillment}).
+
+\subsection{General contact hypothesis}
+
+During the main analyses, we have thus far shown that participants held
+more positive outgroup attitudes following intergroup contacts and that
+perceived interaction quality was associated with more positive outgroup
+attitudes following an intergroup contact. We have, however, not brought
+the two elements of the contact hypothesis together in a single
+analysis. To jointly test the effects of contact frequency and average
+interaction quality, we ran a linear regression model where average
+outgroup attitudes were predicted by the number of interactions and the
+average interaction quality ratings of all participants across the three
+studies. We did so while controlling for the possible effects of
+study-specific differences. To include the study-membership as a control
+variable, we used the student sample (Study 2) as the reference group
+because it was both the largest and the most homogeneous study. Looking
+at the overall model, we found that the model predicted 13.89\% of the
+variance in average outgroup attitudes (\textit{F}(9, 189) = 3.39,
+\textit{p} = 0.001, \textit{R\textsuperscript{2}} = 0.14). Looking at
+the individual effects, we found that only the number of outgroup
+interactions has a clear association with average outgroup attitudes
+(\textit{b} = 0.55, \textit{t}(189) = 2.82, \textit{p} = 0.005,
+\textit{95\%CI}{[}0.16, 0.93{]}). The average interaction quality
+perceptions had a much smaller effect (\textit{b} = 0.29,
+\textit{t}(189) = 2.09, \textit{p} = 0.038, \textit{95\%CI}{[}0.02,
+0.56{]}), and importantly we found no interaction effect at all. In
+short, the effect of interaction frequency did not depend on the average
+interaction quality.
+
+\subsection{Contact key need content}
+
+Finally, we used the qualitative data from the participants'
+self-identified core needs to contextualize the results of our main
+analysis. However, because our participants jointly reported on
+thousands of intergroup contacts, it would not have been feasible to
+analyze these qualitative responses in a traditional qualitative content
+analysis. We instead relied on recent machine learning advances within
+the natural language processing domain. For our analysis, we used the
+BERT language model. BERT (Bidirectional Encoder Representations from
+Transformers) was developed by Google in 2018 and today forms a key
+element of many natural language processing workflows. In its essence,
+BERT is a framework that allows users to codify every word in relation
+to every other word within a large set of documents. We extracted 47
+topics from the 2,983 interaction goal free-text entries --- a
+relatively large number of topics. The higher number of topics allowed
+us to retain more of the smaller topics and leaves a relatively low
+number of 308 free-text entries unclassified (10.33\%). A full write-up
+of the topic modeling process is available in Online Supplemental
+Material B.
+
+In terms of the content of the topics, we find that a number of topics
+are primarily task-oriented, where participants hope to increase their
+study, research, presentation, or work performance. Opposing the task-
+and work-oriented needs, are a wide variety of leisure-related needs
+wishes, like relaxation and entertainment. Additionally, some clusters
+were primarily relationship-oriented, so that participants sought
+contact with outgroup members for intimate and casual social contact in
+itself. Similarly, socializing and celebrations were also explicit
+social needs (incl., parties). This also included a subtopic of
+spiritual, religious, and otherwise transcendental needs
+(incl.~meditation, prayer, religious services). Among the
+leisure-oriented topics was also a set of contact goals that were
+specifically migration-specific (e.g., wish to learn about culture,
+politics, and language) or were concerned with informational needs more
+generally (e.g., seeking answers, bureaucratic information). A similar
+set of topics was specifically geared towards a wish to experience
+cultural products (e.g., music, theater, food) or had travel-related
+goals in their interactions with the majority group members.
+
+One interesting observation was the importance of contact goals specific
+to contact through the medical and public health system. This goal type
+was partly specific to the medical professionals (e.g., working with
+patients, treatment), but also more broadly highlighted interactions of
+newcomers with the outgroup majority as patients themselves (e.g.,
+therapeutic goals). Also health, fitness, and personal improvement goals
+(e.g., sports and music) were common goals that participants shared
+during the interactions with the majority group members. Another topic
+less commonly found within the literature were more practically oriented
+needs, where participants sought to share food and cook together or had
+organizational needs (e.g., housing, cleaning, and co-living). In sum,
+almost all extracted topics fall into broader or narrower need concepts
+that are commonly discussed within the psychological needs literature
+\citep[e.g.,][]{orehek2018a} and offer insight into a core aspect of the
+migration experience that has remained broadly under-explored
+\citep[][]{Kreienkamp2022d}\footnote{It should be noted that these topic models are not without limitations, especially because they depend on a small set of hyperparameters that determine the characteristics of the embedding, dimension reduction, clustering, and core term extraction.
+The authors have also inspected a major subset of the free-text responses manually and are under the impression that the topics described here accurately represent the broader content.}.
 
@@
 % aims re-iterated
-In this paper we set out to (1) test the basic predictions of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data, (2) we proposed that the fulfillment situational psychological needs meaningfully predicts positive outgroup attitudes, and (3) that the fulfillment of psychological needs (and Allport's conditions) have their effect (partially) through perceived interaction quality.
+The main aim of this project was to test the basic tenets of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data and to test whether the fulfillment of situational needs meaningfully predicts positive interaction perceptions, well-being, and outgroup attitudes.
 
 % Contact hypothesis in ESM data [inconsistent in aggregate but consistent in ML analysis]
-When considering the results of the three studies jointly, we find mixed results for the basic intergroup contact hypothesis.
-The aggregated number of outgroup interactions across all measurements only had a significant effect on average outgroup attitudes in one of the three studies and in that study there was no significant effect of average interaction quality on outgroup attitudes (which was significant for the other two studies).
-This meant that only for our smallest study did we find the expected interaction between interaction frequency and interaction quality when looking at the aggregated data across all measurements.
-However, once we considered the effect of having an interaction with an outgroup member (vs.
-not having an outgroup interaction) within the participants, we find that intergroup contact is a strong predictor of outgroup attitudes across all three studies (even when taking other non-outgroup interactions into account).
-While this later results is in line with our expectations, the earlier aggregate findings are surprising because most past cross-sectional studies that have investigated the effect of interaction frequency have also considered an aggregate measurement (albeit not one from actual daily reports).
-Even though this inconsistency with past research might be a data artefact (e.g., because most people reported more substantially mode measurements during which they did not have an outgroup interaction), the absence of this aggregate effect could underline the fact that cross-sectional retrospective data might suffer from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
-In summary, we thus find that when we aggregate interaction frequencies and interaction quality from our intensive longitudinal data we find inconsistent results from the past literature but within participants intergroup contacts are significantly related with positive outgroup attitudes.
+When considering the results of the three studies jointly, we found mixed results for the basic intergroup contact hypothesis.
+To replicate the two common approaches to the contact hypothesis, we looked at both the within-person effects of individual outgroup interactions (mimicking the analysis of lab studies) as well as the joint effect of interaction frequency and average interaction quality between participants (mimicking the cross-section literature).
+For the effect of individual interactions, we find that having an outgroup interaction (vs.
+not having an interaction) was associated with more favorable outgroup attitudes.
+Similarly, we find that within outgroup interactions, the interaction quality was meaningfully associated with more favorable outgroup attitudes.
+Yet, considering interaction frequency and average interaction quality jointly was only possible on the aggregated between-participant level.
+Surprisingly, here we found independent effects of interaction frequency and average interaction quality ratings but no interaction effect.
+The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
+
+Interestingly, this effect is also inconsistent with the observations and theorizing of \citet[][]{MacInnis2015}, who observed that individual interactions showed negative effects on intergroup relations and the aggregate of past intergroup contacts showed positive effects on intergroup relations.
+There are, however, two important differences in our data compared to the past literature assessed by \citeauthor{MacInnis2015}.
+Firstly, what \citeauthor{MacInnis2015} called the intergroup interaction literature, has particularly focused on artificial lab studies where study participants meet a stranger from the outgroup.
+In our real-world data, such synthetic and controlled interactions are arguably less relevant.
+Secondly, what \citeauthor{MacInnis2015} called the intergroup contact literature, has looked at long-term recall self-reports --- where participants are asked to recall the quantity and average quality of intergroup contacts over the past month or year \citep{MacInnis2015}.
+The mental aggregation of such long-term recall surveys is substantially different from the aggregation we did based on the close-to-event reports \citep[][]{shiffman2008}.
+To truly compare our results to \citet[][]{MacInnis2015} theorizing, future studies should, thus, also collect a long-term recall report that mirrors the questions asked during intergroup contact studies.
+
+It should, however, be noted that the inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
+There is also a possibility that statistical power was a concern given our sample was relatively small with 207 participants and the effect of interest is an amplification interaction effect.
+However, if we assume an effect size of \textit{r} = -.21 for the effect of positive intergroup contacts \citep[see][]{Pettigrew2006} our sample size should approach the threshold of 80\% power at a .05 alpha level (sensitivity analysis in G*Power: $f^2 = 0.04$) --- especially if we consider the higher quality data we get from aggregating many real-world reports with less recall bias.
 
 % Allport's conditions in ESM data [consistent predictor and partially through quality]
-Using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
-And when we consider interaction quality and Allport's conditions jointly, we find further evidence that part of the benefits of Allport's conditions are due to the case that such interactions are also perceived as more positive.
+Next, using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
+When we consider interaction quality and Allport's conditions jointly, we find that interaction quality ratings assumed a larger part of the shared variance in outgroup attitudes.
 We thus find first evidence that Allport's conditions of optimal contact are also relevant to the daily interactions recent migrants have in their interactions with majority group members.
@@
 % Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results for our main proposal regarding the importance of situational key needs, we find highly consistent positive results across all three studies.
-We find that in all three extensive longitudinal datasets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
-We find that in all three studies the effect of core need fulfillment on outgroup attitudes is either fully or partially through its effect on quality perceptions, and we find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
-In fact we find that our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance in outgroup attitudes than any of the other psychological needs.
-In most cases the core need even took over the variances previously explained by the self-determination theory needs.
-We thus find strong evidence that within everyday life interactions of recent migrants with majority group members, the perception that one's interaction specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
-As such the data offers a first test of the motivational basis of intergroup contact.
+Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions, more positive outgroup attitudes, as well as \hl{higher well-being}.
+We find that in all three studies the effect of core need fulfillment on outgroup attitudes was either fully or partially assumed by the effect of interaction quality (when considering partial regression coefficients in a joint model).
+We also find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
+In fact, our core situational needs measure predicted outgroup attitudes at least as good as Allport's conditions and consistently explained more variance than commonly measured psychological needs.
+In most cases, the core need even took over the variances previously explained by the self-determination theory needs (see \appref{app:AppendixRobustness}).
+We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction-specific needs are fulfilled offers a meaningful and flexible predictor of interaction quality, outgroup attitudes, and well-being.
 
 \subsection{Limitations}
-to be discussed, potentially:
-\begin{enumerate}
-    \item migrants are not refugees (generalizability potentially even more relevant?)
-    \item minority perspective only
-    \item lagged effects left for future studies (potentially not relevant, time scale)
-    \item ESM: real-life data comes at the expense of having short/single item operationalizations
-\end{enumerate}
+% (1) Sample = minority and (voluntary) migrants, (2) Methodology = short scales (reliability) and no lagged effects, (3) Core Need Concept = non-specific
+While we believe that a need fulfillment mechanism should be relevant to any inter-group contact, our samples focused on a minority- and (voluntary) migrant perspective.
+Without additional evidence it thus remains difficult to judge whether motivational effects will generalize to other migrant groups (e.g., forced migrants), other intergroup contexts (e.g., gender-, religious-, or sexual orientation groups), or to majority groups and their outgroup attitudes.
+We sought to replicate our results in three studies with different types of migrants but the fact remains that all three studies had slightly more women than men participating and were younger and more educated samples overall.
+While the samples were representative of the migrant group to the focus region, the generalizability of the sample is restricted by its characteristics.
+We know of no research suggesting that in other contexts need fulfillment would be less relevant but future research may extend our findings to build an even broader understanding of need fulfillment in intergroup contacts.
+Researchers may even seek to explore the role of need fulfillment in real-world interactions more broadly \citep[also see][]{Downie2008}.
+
+A second limitation lies in our methodology.
+While extensive longitudinal data is close to real-life events, this method comes at the expense of longer and more robust scales.
+Long and repetitive scales are often not feasible in extensive longitudinal methods because of the increased burden to the participants.
+To circumvent this shortcoming, we have ensured that the measures we used were, whenever possible, based on past validations.
+However, the circumstance remains that extensive longitudinal data often does not allow the same scrutiny of measurement reliability as single–shot cross-sectional data sets.
+An additional methodological question lies in the unexplored potential of the longitudinal aspects of our data.
+For our research questions, we have focused on contemporaneous effects within the data set, yet future investigations should seek to extend the mechanism to developmental trajectories within and between participants.
+
+A third limitation lies in the outcome variable we chose.
+As we have focused on outgroup attitudes to ensure comparability to the past literature of the contact hypothesis and to replicate the most reliable patterns within ESM data \citep[][]{pettigrew2006}.
+However, especially for disadvantaged minority members positive outgroup attitudes may entail negative downstream consequences such as a reduced endorsement of social change --- even in the face of injustice \citep[e.g.,][]{dixon2012}.
+We have additionally tested our need-fulfillment mechanism for well-being reporst to test direct benefits of the mechanism to lived realities.
+However, we are among the first to collect intensive longitudinal data on the experience of minority migrants and it remains an open empirical question whether the more positive outgroup attitudes following need-fulfilling interactions might ironically exacerbate inequalities for the disadvantaged group.
+
+Finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
+This comes at the expense of specificity in the situational motives (i.e., we have not explored whether different types of needs have stronger effects on interaction quality and outgroup attitudes).
+Such an investigation would be possible with the adaptive measurement we used (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
+Nonetheless, future research may explore which exact needs are most important in different intergroup contexts.
 
 \subsection{Implications}
-to be discussed, potentially:
-\begin{enumerate}
-    \item feasible to collect large amount of data on intergroup contact using ESM method (do we have a formR ref in there?; set up is feasible but not the easiest; maybe even advertise the reusability of the formR survey?)
-    \item role of motivation in intergroup contact promising (potential for interventions, e.g., most immediate to the data: settlement practices). 
-    \item potential to identify context specific needs
-\end{enumerate}
+% ESM data
+Despite these limitations, we can nonetheless draw a number of implications for other researchers and practitioners --- ranging from the benefits of longitudinal data to theoretical implications.
+A first implication concerns the feasibility and usefulness of extensive longitudinal data for intergroup contact research and the broader field of social psychology.
+While setting up an extensive longitudinal study is not easy, we believe the efforts to be similar to a sizable cross-sectional data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with roughly 3,000 intergroup interactions captured and over 10,000 data points in total).
+Intensive longitudinal data, thus, opens up the possibility to explore research questions that focus on real-life phenomena outside the lab or focus on phenomena that depend on changes and influences over time.
+In the context of intergroup contact research, we are among the first to answer calls to test intergroup contact mechanisms using extended real-life data \citep[e.g.,][]{Pettigrew2011, MacInnis2015}.
+In doing so, we not only collected an unprecedented amount of real-life data, but our consideration of extensive longitudinal data may present new inconsistencies in how participants perceive and cognitively aggregate their past interactions with other groups — which may suggest large-scale recall biases or conflations of within and between participant effects in conventional cross-section studies.
 
-\subsection{Conclusion paragraph (not a real heading)}
-to be written after co-author meeting.
+% Motivation and core needs 
+A broader theoretical implication relates to the role of situational motivation in intergroup contacts.
+Our results offer a first promising test of psychological needs in intergroup contact.
+While our results are tentative given their novelty within the field, they were highly consistent across studies and may offer new theoretical avenues.
+Psychological needs are a facet of the human experience that has thus far been underemphasized in the intergroup contact literature.
+This stands in stark contrast of the many cognitive \citep[e.g.,][]{Pettigrew1998, Brown2005} and emotional aspects investigated within the field \citep[e.g.,][]{Stephan2008}.
+Future research may, therefore, be able to integrate broader theoretical frameworks of intergroup contact (e.g., motivations guiding cognition and affect, which in turn drive behavior.
+cf., theory of reasoned goal pursuit; \citealp{Ajzen2019}.
+Also see \citealp{Kreienkamp2022d}).
+
+% practical use of needs
+Additionally, situational motivations in intergroup contact also offer promising avenues for practitioners and policy-makers.
+Intergroup contact theory is among the most implemented psychological theories \citep[e.g.,][]{Pettigrew2006, AlRamiah2012a, Reimer2021}.
+Given our findings that psychological needs in everyday intergroup contacts were at least as powerful as Allport's conditions in predicting outgroup attitudes, considerations of people's needs offer a substantially more immediate mechanism to address.
+In cases where some or all optimal contact conditions are not possible to be fulfilled, needs offer an even more compelling alternative (e.g., where equal status is contextually not possible or in cases where people help despite a lack of institutional support).
+Additionally, our conceptualization of situational needs offers a clear opportunity for practitioners and interventions.
+Instead of addressing needs as a one-size fits all solution (e.g., simply focusing on competence needs), one may at times ask outgroup interaction partners what they need during an interaction.
+This is not to say that we should not explore which needs tend to be relevant to specific groups in specific intergroup contact contexts.
+Rather, during interventions for which data on important need contents are not available or infeasible to collect, a flexible and reactive approach of inquiring momentary intergroup contact needs might be more fruitful.
+
+\subsection{Conclusion}
+% Conclusion paragraph
+In sum, we used extensive longitudinal methodologies to capture real-life interactions of recent migrants with the majority outgroup.
+Our three studies showcase the feasibility and utility of such data to test intergroup contact theory.
+We provide evidence that the fulfillment of situational psychological needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
+Our results point to motivational needs as an understudied aspect of intergroup contact that is important in understanding when and why an interaction is perceived as positive and will lead to more positive outgroup attitudes.
+
+% Tables
+\input{Tables/descrFullWide}
+\input{Tables/descrOutWide}
+
+\input{Tables/mdlContactGeneralLong}
+\input{Tables/mdlTheorylong}
+
+% Figures
+\begin{figure}
+  \caption{Path Diagrams Situational Needs Model across Studies}
+  \label{fig:MainPaths}
+  \begin{center}
+    \input{PathModels.tex}
+  \end{center}
+  \caption*{Note: \\
+  (A) Study 1; (B) Study 2; (C) Study 3.\\
+  General: Path coefficients are standardized regression coefficients.
+Statistical significance markers are based on the unstandardized regression results (as presented in \tblref{tab:intergroupNeedsTblLong}).\\
+  **** p < .0001, *** p < .001, ** p < .01, * p < .05}
+\end{figure}
+
+\begin{figure}
+  \caption{Contact Hypothesis}
+  \label{fig:ContactHypothesis}
+  \centering\includegraphics[width=\textwidth]{Figures/forestParametricREMLGeneralLmer.png}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricGeneralLm.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.75\textwidth]{Figures/forestParametricFEGeneralLmer.png}
+  %\end{subfigure}
+  \caption*{Note: \\
+  Summary of mixed models results of the contemporaneous contact effects.\\
+  General: Random effects meta-analytic results are presented for completeness.}
+\end{figure}
+
+\begin{figure}
+  \caption{Core Need Fulfillment}
+  \label{fig:AllportNeedFulfillment}
+  \centering\includegraphics[width=\textwidth]{Figures/forestParametricTheoryComb.png}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryQualityCore.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCore.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.6\textwidth]{Figures/forestParametricFETheoryAttitudeCoreQuality.png}
+  %\end{subfigure}
+  \caption*{Note: \\
+  (a) Core Need Fulfillment predicting Interaction Quality.\\
+  (b) Core Need Fulfillment predicting Outgroup Attitudes.\\
+  (c) Core Need Fulfillment and Interaction Quality predicting Outgroup Attitudes.\\
+  General: Random effects meta-analytic results are presented for completeness.}
+\end{figure}
 
@@
 
-\section{Appendix A: Hypotheses}
+\section{Hypotheses and Analysis Plan}
 \label{app:AppendixHypotheses}
 
-\begin{hyp}[H\ref{hyp:contact}] \label{hyp:contact}
-Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for changes in more favorable outgroup attitudes.
+\newlength{\mdfmar}
+\setlength{\mdfmar}{1.5em}
+\mdfdefinestyle{mdfhypothesis}{
+    innerleftmargin = +1.5\mdfmar, %
+    innerrightmargin = +1.5\mdfmar, 
+    innertopmargin = +\mdfmar, 
+    innerbottommargin = +\mdfmar, 
+    skipabove = 12pt
+}
+\newlength{\subhypskip}
+\setlength{\subhypskip}{1.5em}
+\newlength{\eqskip}
+\setlength{\eqskip}{3.5em}
+
+In this appendix, we present the expanded hypotheses and their associated analysis plan.
+Given the nested structure of much of our data, we test many of our hypotheses using a multilevel approach, where $y_{ti}$ denotes the response at measurement occasion $t$ ($t = 1, ..., T_i$; level 1) for individual $i$ ($i = 1, ..., n$; level 2).
+All multilevel assumptions are tested as follows (e.g., for random slopes model with $j$ within-person predictors):
+
+\begin{flalign}
+  &\textrm{Level 1 Variance:}\ e_{ti} \sim \mathcal{N}(0,\sigma^2) \\
+  &\textrm{Level 2 Variance:}\ \begin{bmatrix} u_{0i}\\ \vdots\\ u_{ji}\end{bmatrix} 
+  \sim \mathcal{N}
+  \begin{pmatrix}
+    \begin{bmatrix} 
+      0 \\ 
+      \vdots \\
+      0
+    \end{bmatrix}, 
+    \begin{bmatrix} 
+      \tau_{00}^2 &  & \\ 
+      \vdots & \ddots & \\
+      \tau_{j0} & \ldots & \tau_{jj}^2
+    \end{bmatrix}
+  \end{pmatrix}
+\end{flalign}
+
+For our main aims we sequentially focus on four sets of models to test and validate our hypotheses:
+
+\subsection{1. Contact hypothesis in extensive longitudinal data.} 
+Within the individual studies, we begin by testing the most basic assumption of the intergroup contact hypothesis that outgroup attitudes should be more positive after outgroup interactions but not after non-outgroup interactions.
+For this we use multi-level regression analyses, predicting outgroup attitudes from outgroup interaction and non-outgroup interaction dummy variables.
+We also include the participant means as level two predictors to fully disentangle within- (level 1) and between-participant (level 2) effects of intergroup contact \citep[e.g.,][Section 4.6]{Snijders2012}.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:contactHyp}] \label{hyp:contactHyp}
+        Based on the most general understanding of the contact hypothesis, positive intergroup contacts should be associated with more favorable outgroup attitudes across extensive longitudinal data.
     \end{hyp}
 
-\begin{subhyp}[H\ref{hyp:contactFreq}] \label{hyp:contactFreq}
-\addtolength{\leftskip}{2.5em}
-Participants with more intergroup interactions should have a more favorable outgroup attitudes.
-\end{subhyp}
-
-\begin{subhyp}[H\ref{hyp:contactDummy}] \label{hyp:contactDummy}
-\addtolength{\leftskip}{2.5em}
+    \begin{subhyp}[H\ref{hyp:contactDummyML}] \label{hyp:contactDummyML}
+    \addtolength{\leftskip}{\subhypskip}
     Outgroup attitudes should be more positive after an intergroup interaction compared to a non-outgroup interaction.
@@
 
-\begin{subhyp}[H\ref{hyp:contactFreqQual}] \label{hyp:contactFreqQual}
-\addtolength{\leftskip}{2.5em}
-Participants with more intergroup interactions should have a more favorable outgroup attitudes depending on the average interaction quality.
+    \begin{fleqn}[\eqskip] 
+    \begin{equation} \label{eq:ContactDummy}
+      \begin{split}
+        \textrm{Level 1:} &
+          \begin{aligned}[t]
+            \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}OutgroupInteraction_{ti} + \\
+                               &\ \beta_{2i}NonOutgroupInteraction_{ti} + e_{ti}
+          \end{aligned} \\
+        \textrm{Level 2:} &
+            \begin{aligned}[t]
+                \ \beta_{0i} = &\ \gamma_{00} + \gamma_{01}MeanOutgroupInteraction_{i} + \\
+                               &\ \gamma_{02}MeanNonOutgroupInteraction_{i} + u_{0i} \\
+                  \beta_{1i} = &\ \gamma_{10} + u_{1i} \\
+                  \beta_{2i} = &\ \gamma_{20} + u_{2i}
+            \end{aligned}
+      \end{split} 
+    \end{equation}
+    \end{fleqn}
+\end{mdframed}
+
+% We then seek to investigate intergroup contacts and perceived interaction quality jointly.
+Notably, however, participants are only able to report their interaction quality perceptions if they had an interaction.
+This is considered to be structurally missing data and cannot meaningfully be imputed for modeling.
+To deal with this issue, we mimic the procedure commonly used within the cross-section literature.
+In particular, we conduct a person-level linear regression by aggregating the number of outgroup interactions participants had, their average interaction quality perceptions, as well as their average outgroup attitudes \citep[for possible alternative approaches see,][]{Enders2011}.
+To avoid an underpowered analysis, we use the aggregated data from all three studies.
+
+We then seek to test the full contact hypothesis by investigating intergroup contacts and perceived interaction quality jointly.
+To do so, we conduct a linear regression using person-level aggregated data from all three studies.
+In particular, we aggregate the number of outgroup interactions participants had, their average interaction quality perceptions, as well as their average outgroup attitudes.
+This approach has three main benefits: (1) Interaction quality ratings are only available if participants had an interaction, and the aggregation deals with this structural missingness.
+(2) Using the participant-level data from all three studies, we avoid potential power issues.
+(3) This analysis mimics the analyses conducted within the cross-section literature, where participants are asked to recall how many interactions they had over a one-month period, how positive these interactions were, and what their general attitudes towards the outgroup are.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{subhyp}[H\ref{hyp:contactCor}] \label{hyp:contactCor}
+    \addtolength{\leftskip}{\subhypskip}
+    Participants with more intergroup interactions should have more favorable outgroup attitudes.
     \end{subhyp}
 
-\begin{hyp}[H\ref{hyp:AllportsConditions}] \label{hyp:AllportsConditions}
-Based on Allport's optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
-\end{hyp}
+      \begin{fleqn}[\eqskip] 
+        \begin{equation} \label{eq:ContactCor}
+            r_{\left(ContactFrequency_{i},\ AverageQuality_{i}\right)} > 0
+        \end{equation}
+      \end{fleqn}
 
-\setcounter{subhyp}{0}
-\begin{subhyp}[H\ref{hyp:AllportsPred}] \label{hyp:AllportsPred}
-\addtolength{\leftskip}{2.5em}
-Based on Allport's optimal contact conditions, outgroup attitudes should be more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
+    \begin{subhyp}[H\ref{hyp:contactQualLM}] \label{hyp:contactQualLM}
+    \addtolength{\leftskip}{\subhypskip}
+    Participants with more intergroup interactions should have more favorable outgroup attitudes depending on the average interaction quality.
     \end{subhyp}
 
-\begin{subhyp}[H\ref{hyp:AllportsQuality}] \label{hyp:AllportsQuality}
-\addtolength{\leftskip}{2.5em}
-Based on past research on the role of interaction quality, interaction quality should be more perceived as more favorable after intergroup interactions with equal status, common goals, collaboration, and structural support.
-\end{subhyp}
+      \begin{fleqn}[\eqskip] 
+        \begin{equation} \label{eq:contactQualLM}
+            \begin{split}
+              AverageAttitude_{i} = &\ \beta_{0} + \beta_{1}ContactFrequency_{i} + \\
+                                    &\ \beta_{2}AverageQuality_{i} +\\
+                                    &\ \beta_{3}ContactFrequency_{i} * AverageQuality_{i}
+            \end{split}
+        \end{equation}
+      \end{fleqn}
 
-\begin{subhyp}[H\ref{hyp:AllportsQualityMediation}] \label{hyp:AllportsQualityMediation}
-\addtolength{\leftskip}{2.5em}
-Based on past research on the role of interaction quality, the variance explained in outgroup attitudes by Allport's optimal contact should to a large extend be assumed by interaction quality.
-\end{subhyp}
+      We additionally control for the participant's study membership.
+\end{mdframed}
+Because this analysis uses the data from all three studies, the results of this analysis are presented in the `Robustness, Stability, and Embeddedness across Studies' section.
 
+\subsection{2. Core need fulfillment during intergroup contact.}
+The main proposal of this manuscript has been the assertion that the fulfillment of situation core needs during an interaction will be associated with more positive interaction quality perceptions and, ultimately, more positive outgroup attitudes.
+Thus, for the main set of analyses, we focus on the reported outgroup interactions only.
+For each study, we will use multi-level regressions to test the main three assertions of our proposal (mirroring the basic steps of a traditional mediation analysis).
+
+\begin{mdframed}[style=mdfhypothesis]
     \begin{hyp}[H\ref{hyp:keyNeed}] \label{hyp:keyNeed}
@@
     \begin{subhyp}[H\ref{hyp:keyNeedPred}] \label{hyp:keyNeedPred}
-\addtolength{\leftskip}{2.5em}
-Outgroup attitudes should be more favorable after intergroup interactions with high key need fulfillment.
+    \addtolength{\leftskip}{\subhypskip}
+    Core need fulfillment during outgroup interactions should predict more positive outgroup attitudes.
     \end{subhyp}
 
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesAttCore}
+        \begin{split}
+            \textrm{Level 1:} &\ Attitude_{ti} = \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}\\
+            \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                              &\ \beta_{1i} = \gamma_{10} + u_{1i}
+        \end{split}
+      \end{equation}
+    \end{fleqn}
+
     \begin{subhyp}[H\ref{hyp:keyNeedQual}] \label{hyp:keyNeedQual}
-\addtolength{\leftskip}{2.5em}
-Interaction Quality should be perceived as more positive after intergroup interactions with higher key need fulfillment.
+    \addtolength{\leftskip}{\subhypskip}
+    Core need fulfillment during outgroup interactions should also predict higher perceived interaction quality.
     \end{subhyp}
 
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesQltCore}
+        \begin{split}
+            \textrm{Level 1:} &\ InteractionQuality_{ti} = \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + e_{ti}\\
+            \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                              &\ \beta_{1i} = \gamma_{10} + u_{1i}
+        \end{split}
+      \end{equation}
+    \end{fleqn}
+
     \begin{subhyp}[H\ref{hyp:keyNeedMediation}] \label{hyp:keyNeedMediation}
-\addtolength{\leftskip}{2.5em}
-The variance explained in outgroup attitudes by key need fulfillment should to a large extend be assumed by interaction quality.
+    \addtolength{\leftskip}{\subhypskip}
+    The effect of core need fulfillment on outgroup attitudes should be reduced when considered together with perceived interaction quality.
     \end{subhyp}
 
-\begin{subhyp}[H\ref{hyp:keyNeedContactType}] \label{hyp:keyNeedContactType}
-\addtolength{\leftskip}{2.5em}
-The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
-Thus, the effect of key need fulfillment on outgroup attitudes should stronger for intergroup interact than for ingroup interactions.
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesAttCoreQual}
+        \begin{split}
+          \textrm{Level 1:} &
+            \begin{aligned}[t]
+              \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                                 &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+            \end{aligned} \\
+          \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                            &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                            &\ \beta_{2i} = \gamma_{20} + u_{2i}
+        \end{split} 
+      \end{equation}
+    \end{fleqn}
+\end{mdframed}
+
+\subsection{3. Allport's conditions in extensive longitudinal data.}
+Within the third study, we formally measure all of Allport's optimal contact conditions.
+We use multi-level regression models to test whether the fulfillment of Allport's conditions in real-life data predicts more positive outgroup attitudes and higher perceived interaction quality, using the same approach as for the core need fulfillment above.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:Allport}] \label{hyp:Allport}
+    Based on Allport's optimal contact conditions, intergroup interactions with equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions.
+    \end{hyp}
+
+    \setcounter{subhyp}{0}
+    \begin{subhyp}[H\ref{hyp:AttAllport}] \label{hyp:AttAllport}
+    \addtolength{\leftskip}{\subhypskip}
+    Higher fulfillment of Allport's conditions during outgroup interactions should predict more positive outgroup attitudes.
     \end{subhyp}
 
-\begin{subhyp}[H\ref{hyp:keyNeedSDT}] \label{hyp:keyNeedSDT}
-\addtolength{\leftskip}{2.5em}
-The effect of key need fulfillment on outgroup attitudes should be persist even when taking other fundamental psychological needs into account.
-Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesAttAllport}
+        \begin{split}
+            \textrm{Level 1:} &\ Attitude_{ti} = \beta_{0i} + \beta_{1i}Allport_{ti} + e_{ti}\\
+            \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                              &\ \beta_{1i} = \gamma_{10} + u_{1i}
+        \end{split}
+      \end{equation}
+    \end{fleqn}
+
+    \begin{subhyp}[H\ref{hyp:QltAllport}] \label{hyp:QltAllport}
+    \addtolength{\leftskip}{\subhypskip}
+    Higher fulfillment of Allport's conditions during outgroup interactions should also predict higher perceived interaction quality.
     \end{subhyp}
 
-\begin{hyp}[H\ref{hyp:comparison}] \label{hyp:comparison}
-Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict outgroup attitudes at least as well as Allport's conditions.
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesQltAllport}
+        \begin{split}
+            \textrm{Level 1:} &\ InteractionQuality_{ti} = \beta_{0i} + \beta_{1i}Allport_{ti} + e_{ti}\\
+            \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                              &\ \beta_{1i} = \gamma_{10} + u_{1i}
+        \end{split}
+      \end{equation}
+    \end{fleqn}
+
+    \begin{subhyp}[H\ref{hyp:AttAllportQual}] \label{hyp:AttAllportQual}
+    \addtolength{\leftskip}{\subhypskip}
+    The effect of higher fulfillment of Allport's conditions on outgroup attitudes should be reduced when considered together with perceived interaction quality.
+    \end{subhyp}
+
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesAttAllportQual}
+        \begin{split}
+          \textrm{Level 1:} &
+            \begin{aligned}[t]
+              \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}Allport_{ti} + \\
+                                 &\ \beta_{2i}InteractionQuality_{ti} + e_{ti}
+            \end{aligned} \\
+          \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                            &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                            &\ \beta_{2i} = \gamma_{20} + u_{2i}
+        \end{split} 
+      \end{equation}
+    \end{fleqn}
+\end{mdframed}
+
+We then compare the effect of Allport's contact conditions with our core need fulfillment by comparing the model fit statistics of the two individual models and by adding both concepts to a joint multi-level regression model, to see whether the two approaches explain the same variance in outgroup attitudes.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:NeedAllport}] \label{hyp:NeedAllport}
+    Based on our proposal, the fulfillment of the core situational need should predict outgroup attitudes at least as well as Allport's conditions.
     \end{hyp}
@@
     \begin{subhyp}[H\ref{hyp:compModel}] \label{hyp:compModel}
-\addtolength{\leftskip}{2.5em}
-The need model (H\ref{hyp:keyNeedPred}) should predict more variance in outgroup attitudes than the model based on Allport's conditions (H\ref{hyp:AllportsPred}).
+    \addtolength{\leftskip}{\subhypskip}
+    The need model (H\ref{hyp:keyNeedPred}) should predict more variance in outgroup attitudes than the model based on Allport's conditions (H\ref{hyp:AttAllport}).
     \end{subhyp}
 
+    \begin{fleqn}[\eqskip] 
+        \begin{equation}
+            \begin{split}
+                AIC_{KeyNeedModel} & < AIC_{AllportModel} \\
+                BIC_{KeyNeedModel} & < BIC_{AllportModel}
+            \end{split}
+        \end{equation}
+    \end{fleqn}
+
     \begin{subhyp}[H\ref{hyp:compTogether}] \label{hyp:compTogether}
-\addtolength{\leftskip}{2.5em}
+    \addtolength{\leftskip}{\subhypskip}
     The  effect of key need fulfillment on outgroup attitudes should  persist even when taking other Allport's conditions into account.
-Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for equal status, common goals, collaboration, and structural support.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for Allport's conditions.
     \end{subhyp}
 
+    \begin{fleqn}[\eqskip]
+      \begin{equation} \label{eq:SlopesAttCoreAllport}
+        \begin{split}
+          \textrm{Level 1:} &
+            \begin{aligned}[t]
+              \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                                 &\ \beta_{2i}Allport_{ti} + e_{ti}
+            \end{aligned} \\
+          \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                            &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                            &\ \beta_{2i} = \gamma_{20} + u_{2i}
+        \end{split} 
+      \end{equation}
+    \end{fleqn}
+\end{mdframed}
+
+\subsection{4. Robustness, stability, and embeddedness across studies}
+Within the final set of analyses, we look at the broader picture of our results and leverage the data from all participants to contextualize our results.
+
+\paragraph{Robustness within studies}
+To build further confidence in the effect of core need fulfillment during outgroup interactions, we conduct two additional robustness analyses for each study.
+
+Firstly, to check for the role of alternate psychological needs, we add the fulfillment of self-determination theory needs (i.e., competence, autonomy, and relatedness) to the multi-level regression.
+We then also compare the model with models that predicts outgroup attitudes from self-determination theory need fulfillments or core need fulfillments only.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:keyNeedSDT}] \label{hyp:keyNeedSDT}
+    The effect of key need fulfillment on outgroup attitudes should persist even when taking other fundamental psychological needs into account.
+Thus, the effect of key need fulfillment on outgroup attitudes should remain strong even after controlling for autonomy, competence, and relatedness fulfillment during the interaction (cf., self-determination theory).
+    \end{hyp}
+
+    \begin{fleqn}[\eqskip-\subhypskip]
+      \begin{equation} \label{eq:SlopesAttCoreSdt}
+        \begin{split}
+          \textrm{Level 1:} &
+            \begin{aligned}[t]
+              \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \beta_{2i}Autonomy_{ti} + \\
+                                 &\ \beta_{3i}Competence_{ti} + \beta_{4i}Relatedness_{ti} + e_{ti}
+            \end{aligned} \\
+          \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                            &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                            &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                            &\ \beta_{3i} = \gamma_{30} + u_{3i} \\
+                            &\ \beta_{4i} = \gamma_{40} + u_{4i}
+        \end{split} 
+      \end{equation}
+    \end{fleqn}
+\end{mdframed}
+
+To ensure that the core need fulfillment is outgroup contact specific, we return to the full sample of intensive longitudinal measurements within each study and test whether there is an interaction effect of outgroup contact (vs.
+no outgroup contact) and core need fulfillment.
+We expect that the effect of core need fulfillment is specific to outgroup interactions and not merely due to a more need-fulfilled life in general.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:keyNeedContactType}] \label{hyp:keyNeedContactType}
+    \addtolength{\leftskip}{1em}
+    The effect of key need fulfillment on outgroup attitudes should be specific to intergroup interactions and not be due to need fulfillment in general.
+Thus, the effect of key need fulfillment on outgroup attitudes should be stronger for intergroup interactions than for ingroup interactions.
+    \end{hyp}
+
+    \begin{fleqn}[\eqskip-\subhypskip]
+      \begin{equation} \label{eq:SlopesAttCoreXContact}
+        \begin{split}
+          \textrm{Level 1:} &
+            \begin{aligned}[t]
+              \ Attitude_{ti} =  &\ \beta_{0i} + \beta_{1i}KeyNeedFulfill_{ti} + \\
+                                 &\ \beta_{2i}OutgroupInteraction_{ti} + \\
+                                 &\ \beta_{3i}KeyNeedFulfill*OutgroupInteraction_{ti} + e_{ti}
+            \end{aligned} \\
+          \textrm{Level 2:} &\ \beta_{0i} = \gamma_{00} + u_{0i} \\
+                            &\ \beta_{1i} = \gamma_{10} + u_{1i} \\
+                            &\ \beta_{2i} = \gamma_{20} + u_{2i} \\
+                            &\ \beta_{3i} = \gamma_{30} + u_{3i}
+        \end{split} 
+      \end{equation}
+    \end{fleqn}
+\end{mdframed}
+The results of the robustness analyses are presented in \appref{app:AppendixRobustness} to allow for a more concise presentation of our main hypotheses in the main text.
+
+\paragraph{Stability across studies}
+We assess the stability of our main analyses. We use forest plots (including meta-analytical estimates) to visualize the direction and effect sizes of our three studies.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \begin{hyp}[H\ref{hyp:Stability}] \label{hyp:Stability}
+    \addtolength{\leftskip}{1em}
+    The effects of our main hypotheses and robustness analyses should be consistent across studies.
+    \end{hyp}
+\end{mdframed}
+
+\paragraph{Embeddedness of code needs}
+We, finally, use the qualitative data from the participants' self-identified core needs to contextualize our results.
+We leverage machine learning to extract a topic model of the free-text entries across the three studies.
+We describe the extracted topics and themes and compare them to the need contents usually found and measured within the psychological literature.
+Full methodological details and visualizations are available in Supplemental Material B.
+
+\begin{mdframed}[style=mdfhypothesis]
+    \addtolength{\leftskip}{1em}
+    \textit{This analysis is data-driven and exploratory. As such, the analysis has no associated hypothesis.}
+\end{mdframed}
+
+\section{Robustness Analyses}
+\label{app:AppendixRobustness}
+
+In this appendix, we present the two additional robustness analyses that we conducted within each of the three studies.
+These analyses are specifically designed to check for alternative need models and to check that the effect of situation core need fulfillment is contact-specific.
+(1) To check for the role of alternate psychological needs, we add the fulfillment of self-determination theory needs (i.e., competence, autonomy, and relatedness) to the multi-level regression.
+We then also compare the model with models that predicts outgroup attitudes from self-determination theory need fulfillments or core need fulfillments only.
+(2) To ensure that the core need fulfillment is outgroup contact specific, we return to the full sample of intensive longitudinal measurements within each study and test whether there is an interaction effect of outgroup contact (vs.
+no outgroup contact) and core need fulfillment.
+We expect that the effect of core need fulfillment is specific to outgroup interactions and not merely due to a more need-fulfilled life in general.
+
+As with the main analyses, full surveys are available in our OSF
+repository \citep{KreienkampMasked2022a} and the full data description
+is available in Online Supplementary Material A. Correlations and
+descriptive statistics of the included variables are available in
+\tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.
+
+\subsection{Additional Materials}
+
+In addition to the measurement of whether or not participants had an
+intergroup interaction and their situational core need fulfillment, we
+also measured a set of general psychological needs.
+
+\subsubsection{General Psychological Needs}
+
+In addition to the intergroup contact dummy and situational core need
+reported in the main text, we included a common measure of three
+self-determination theory needs \citep[see][]{Downie2008}. The
+measurement was identical in all three studies. The items were
+introduced either by ``\textit{During the interaction:}'' or
+``\textit{This morning [/afternoon]:}'' and measured autonomy
+(``\textit{I was myself.}''), competence
+(``\textit{I felt competent.}''), and relatedness (without intergroup
+contact ``\textit{I had a strong need to belong}''; with intergroup
+contact: ``\textit{I shared information about myself.}'' and
+``\textit{The other(s) shared information about themselves.}''). All
+items were rated on a continuous slider scale from very little (-50) to
+a great deal (+50).
+
+\subsection{Results}
+
+\subsubsection{Study 1}
+
+To build further confidence in our results, we assessed two additional
+models that might offer alternative explanations. First, to ensure that
+the effect of core need fulfillment is specific to an actual contact, we
+compared the effect to core need fulfillment in situations without an
+intergroup contact. For this, we analyzed the generalized situational
+core need fulfillment (either during a contact or about the daytime in
+general) and tested whether the effect differed during experience
+sampling measurements with and without outgroup contacts. We found no
+main effect of core need fulfillment (random slopes model; \textit{b} =
+-0.10, \textit{t}(1,199) = -2.22, \textit{p} = 0.026,
+\textit{95\%CI}{[}-0.18, -0.01{]}) but a significant interaction effect
+of core need fulfillment and outgroup contact (\textit{b} = 0.13,
+\textit{t}(1,199) = 4.31, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.07, 0.18{]}; also see \tblref{tab:robustnessTblLong}
+and \fgrref{fig:Robustness}). Together with a significant main effect of
+having an outgroup contact, this indicates that it is not key need
+fulfillment in general --- but only key need fulfillment during an
+outgroup contact that predicts more positive outgroup attitudes.
+
+In a final step, we controlled for other fundamental psychological needs
+during the contact. We focus on the three commonly considered
+self-determination needs (SDT): competence, autonomy, and relatedness.
+We find that the core need fulfillment adds significantly above a model
+with only the self-determination theory needs (random slopes models;
+\(\chi^2\)(6, \textit{N} = 21) = 19.60, \textit{p} = 0.003). We also
+find that next to relatedness (\textit{b} = 0.10, \textit{t}(361) =
+4.04, \textit{p} \textless{} .001, \textit{95\%CI}{[}0.05, 0.14{]}), the
+core need explains the most variance in outgroup attitudes after an
+outgroup contact (\textit{b} = 0.09, \textit{t}(361) = 2.23, \textit{p}
+= 0.026, \textit{95\%CI}{[}0.01, 0.18{]}). When compared to the model
+with only the SDT needs, the core need fulfillment flexibly takes on
+some of the explained variance of all three fundamental needs
+(competence and autonomy needs turning non-significant; all \textit{b}
+\textless{} 0.05, all \textit{p} \textgreater{} 0.544). For full results
+see see \tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness}, and
+Online Supplementary Material A. There is, thus, considerable evidence
+lending confidence to the stability and relevance of psychological need
+fulfillment as a predictor of positive outgroup attitudes for natural
+intergroup contacts.
+
+\subsubsection{Study 2}
+
+Also for Study 2, we checked for alternative models. First, when
+considering generalized situational core need fulfillment together with
+whether an intergroup contact took place, we find that there is only a
+minuscule main effect of core need fulfillment (random slopes model;
+\textit{b} = -0.03, \textit{t}(4,849) = -1.34, \textit{p} = 0.181,
+\textit{95\%CI}{[}-0.08, 0.02{]}) but a stronger interaction effect of
+core need fulfillment and outgroup contact (\textit{b} = 0.06,
+\textit{t}(4,849) = 3.03, \textit{p} = 0.002, \textit{95\%CI}{[}0.02,
+0.10{]}). Together with a significant main effect of having an outgroup
+contact (\textit{b} = 2.88, \textit{t}(4,849) = 3.71, \textit{p}
+\textless{} .001, \textit{95\%CI}{[}1.36, 4.40{]}), this indicates that
+it is not key need fulfillment in general --- but key need fulfillment
+during an outgroup contact that predicts more positive outgroup
+attitudes. This finding is consistent with the results of the previous
+study, albeit with a slightly weaker effect (likely because of the large
+number of measurements that did not include an outgroup interaction; For
+full results see \tblref{tab:robustnessTblLong} and for visual
+comparison see \fgrref{fig:Robustness}).
+
+In a final step, we again checked whether during the interaction the
+core situational need remains a meaningful predictor even when taking
+other fundamental psychological needs into account. We find that the
+core need fulfillment adds significantly above a model with only the
+self-determination theory needs (random slopes models; \(\chi^2\)(6,
+\textit{N} = 108) = 22.90, \textit{p} \textless{} .001). We find that
+the core need fulfillment explained the most variance in outgroup
+attitudes after an outgroup contact (\textit{b} = 0.08, \textit{t}(823)
+= 2.95, \textit{p} = 0.003, \textit{95\%CI}{[}0.03, 0.13{]}). When
+compared to the model with only the SDT needs, the core need fulfillment
+flexibly takes on some of the explained variance of all of the three
+fundamental needs. However, different from the first study, relatedness
+(\textit{b} = 0.07, \textit{t}(823) = 4.26, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.04, 0.10{]}) and autonomy (\textit{b} = 0.02,
+\textit{t}(823) = 0.93, \textit{p} = 0.353, \textit{95\%CI}{[}-0.02,
+0.08{]}) also predicted positive outgroup attitudes in this larger
+sample. For full results see \tblref{tab:robustnessTblLong} and
+\fgrref{fig:Robustness}, and Online Supplementary Material A. This means
+that also within this second sample, the fulfillment of psychological
+needs during intergroup contact remained a key predictor of positive
+outgroup attitudes, even when taking into account several alternative
+models.
+
+\subsubsection{Study 3}
+
+As with the previous two studies, we checked for alternative models of
+the key need fulfillment. First, when considering generalized
+situational core need fulfillment together with whether an intergroup
+contact took place, we find that there is no significant main effect of
+core need fulfillment (random slopes model; \textit{b} = 0.03,
+\textit{t}(3,835) = 1.51, \textit{p} = 0.131, \textit{95\%CI}{[}-0.01,
+0.06{]}) but a stronger interaction effect of core need fulfillment and
+outgroup contact (\textit{b} = 0.17, \textit{t}(3,835) = 7.32,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.12, 0.21{]}). Together
+with a significant main effect of having an outgroup contact (\textit{b}
+= 5.41, \textit{t}(3,835) = 6.36, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}3.74, 7.08{]}), this indicates that it is not key need
+fulfillment in general --- but key need fulfillment during an outgroup
+contact that predicts more positive outgroup attitudes. This finding is
+consistent with the results of the previous studies.
+
+In a final step, we again checked whether during the interaction the
+core situational need remains a meaningful predictor even when taking
+other fundamental psychological needs into account. We find that the
+core need fulfillment adds additional variance above a model with only
+the self-determination theory needs (random slopes models; \(\chi^2\)(6,
+\textit{N} = 70) = 100.20, \textit{p} \textless{} .001). We find that
+the core need explains the most variance in outgroup attitudes after an
+outgroup contact (\textit{b} = 0.15, \textit{t}(1,598) = 3.88,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.07, 0.22{]}). When
+compared to the model with only the SDT needs, the core need fulfillment
+flexibly takes on some of the explained variance of all of the three
+fundamental needs. However, similar to the previous study, in this large
+sample relatedness (\textit{b} = 0.05, \textit{t}(1,598) = 3.31,
+\textit{p} \textless{} .001, \textit{95\%CI}{[}0.02, 0.09{]}),
+competence (\textit{b} = 0.06, \textit{t}(1,598) = 2.73, \textit{p} =
+0.006, \textit{95\%CI}{[}0.02, 0.10{]}) and autonomy (\textit{b} = 0.04,
+\textit{t}(1,598) = 2.12, \textit{p} = 0.034, \textit{95\%CI}{[}-0.01,
+0.08{]}) each also predicted positive outgroup attitudes independently.
+This being said, the regression coefficient for the core need was three
+times larger (with all scaling being equal). For full results see
+\tblref{tab:robustnessTblLong} and \fgrref{fig:Robustness} as well as
+Online Supplementary Material A.
+
+\subsection{Stability and Conclusion}
+As with the main analyses, we use a forest plot and the associated meta-analytic estimates to assess the stability of the results across the three studies.
+The forest plot shows that the core need fulfillment is also consistently outgroup contact specific (\fgrref[-A]{fig:Robustness}) and remains a meaningful predictor of outgroup attitudes even when controlling for traditional psychological need fulfillments (Figure \fgrref[-B]{fig:Robustness}).
+In sum, we thus find that across all three studies, psychological need fulfillment remained a robust and flexible predictor of positive outgroup attitudes.
+
+\input{Tables/mdlRobustlong}
+
+\begin{figure}
+  \caption{Robustness Analyses}
+  \label{fig:Robustness}
+  \centering\includegraphics[width=\textwidth]{Figures/forestParametricRobustnessComb.png}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustContact.png}
+  %\end{subfigure}
+  %\begin{subfigure}{\textwidth}
+  %  \caption{}
+  %  \centering\includegraphics[width=0.65\textwidth]{Figures/forestParametricFERobustSDT.png}
+  %\end{subfigure}
+  \caption*{Note: \\
+  (a) Need Fulfillment and Intergroup Contact predicting Outgroup Attitudes (full sample).\\
+  (b) Core Need Fulfillment predicting Outgroup Attitudes while controlling for self-determination theory needs (intergroup contact sample).\\
+  General: Random effects meta-analytic results are presented for completeness.}
+\end{figure}
+
 \end{document}

### 2023-05-26 Tracked changes/comparison/main.tex
tracked changes updated

@@
 \newtheorem{definition}{Definition}
-\newcommand{\defref}[2][]{\hyperref[#2]{Definition \ref*{#2}#1}}
 
@@
 We propose to consider situational psychological needs during everyday intergroup contact.
-We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297; total \textit{N} participants = 207).
+We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297).
 The novel psychological needs mechanism is consistently a strong predictor of positive attitudes during intergroup interactions and these positive effects emerged via perceived interaction quality.
@@
 In light of these findings, understanding interaction quality thus sits at the heart of understanding when an intergroup contact is successful \citep[e.g.,][]{Allport1954b, Brown2007, Tropp2016}.
-But also in applied settings, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in everyday life contexts.
+Practically, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in everyday life contexts.
 Understanding the psychological mechanisms of when and why interactions are perceived as positive is, thus, an important issue for understanding whether an interaction leads to better intergroup perceptions, especially during everyday interactions outside the lab.
@@
 % Proposal Paragraph:
-We propose that one key to understanding how an interaction is perceived is to examine the level of need fulfillment it provided to an individual.
+We propose that the key to understanding how an interaction is perceived is to examine the level of need fulfillment it provided to an individual.
 As an example, if someone seeks acceptance by their interaction partner, and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
-To test this proposal, we collected three sets of real-life data from recent immigrants, assessing their daily interactions with majority group members, tracking situational needs, interaction quality, well-being, and outgroup attitudes.
+To test this, we collected three sets of real-life data from recent immigrants, assessing their daily interactions with majority group members, tracking situational needs, interaction quality, and outgroup attitudes.
 
@@
 % neither are necessary nor explain why an interaction is positive
-\sout{Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.} When it comes to what constitutes a positive interaction the most widely used approach has been the idea that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact effect \citep[][]{Allport1954b, Pettigrew1969}.
-However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be necessary to finding positive effects of intergroup contact \citep[][]{Pettigrew2006}.
-Following Allport's original conditions, several additional conditions of optimal contact were proposed, which have largely received the same criticism of not capturing the underlying psychological mechanisms of why an interaction is perceived as positive \citep[for a critical discussion see][]{Pettigrew1986}.
-
-Instead, since the early 21\textsuperscript{st} century, researchers have assumed positive contact and have focused on the psychological processes that explain how positive contacts improve intergroup relations \citep[e.g.
+Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
+It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for such positive contact effects \citep[][]{Allport1954b, Pettigrew1969}.
+However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be essential to finding positive effects of intergroup contact \citep[][]{Pettigrew2006}.
+It, thus, remains unclear when and why an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects\footnote{It should be noted here that following Allport's original conditions, several additional conditions of optimal contact were proposed \citep[for a critical discussion see][]{Pettigrew1986}.
+Similarly, since the early 21\textsuperscript{st} century many psychological processes during intergroup contact were examined \citep[e.g.
 see,][]{Paolini2021}.
-Among others, researchers have explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008}, as well as knowledge about the other group \citep[][]{Pettigrew2008c}.
-However, all these advances share a focus on understanding when and how \textit{positive interactions} improve intergroup relations.
-Understanding when and why an interaction is perceived as positive in the first place has remained a tangential focus and it, thus, remains largely unclear which psychological mechanisms drive positive interaction perceptions.
-
-In this article, we focus on the underexplored role of motivation and need fulfillment to understand when and why exactly an interaction is perceived as positive.
-We propose need fulfillment in particular, because a need mechanism builds a strong body of literature highlighting the functional role of need fulfillment in psychosocial functioning, interactions, and intergroup relations --- all of which are fundamental considerations for intergroup contact.
-
-On an individual psychological level, need fulfillment has a long tradition of explaining what drives human adaptation and social relations.
-From the early works of \citet[][]{maslow1943} and \citet[][]{lewin1926e} to more recent works by \citet[][]{Ryan2017} or \citet[][]{Steverink2006}, the fulfillment of needs have been considered a driver of health, well-being, and psychosocial functioning.
-Most relevant to our proposal here, within experience sampling studies (psychological) need fulfillment has been found to explain variations in general well-being \citep[e.g.,][]{sheldon1996, reis2000} as well as well-being during daily interactions \citep[][]{Downie2008}.
-The importance of need fulfillment in interactions has also been substantiated by frameworks such as 'relationships motivation theory', which has collected substantive evidence for the importance of need fulfillment in understanding the success of close relationships \citep[e.g., see][]{knee2023}.
-There is, thus, a wealth of literature highlighting the importance of need fulfillment to positive everyday experiences and well-being.
-
-Beyond the well-being and psychosocial functioning perspective, need fulfillment has recently also seen application as a psychological mechanism in the intergroup relations literature.
-Social identity theory has famously focused on the role of self-esteem needs in understanding how people navigate intergroup contexts \citep[e.g.,][]{abrams1988}.
-A more recent example is the study of conflict and reconciliation where addressing differential needs of victims and perpetrators (i.e., the need for power and the need for morality respectively) increased willingness to reconcile \citep[][]{Shnabel2008}.
-And similarly, addressing a relevant need for identity continuity among refugees in Turkey bolstered resilience in the face of discrimination experiences \citep[][]{Celebi2017}.
-Most recently, an international cross-sectional study has applied a need-based approach to the effects of positive intergroup contact.
-The study found that minority members who generally perceive their positive intergroup contacts to be more empowering tended to report a smaller reduction in social change support than those who did not perceive their average interactions as empowering, especially when the inequality between groups was perceived as illegitimate \citep[][]{Hassler2021}.
-In short, an increasing amount of literature is emphasizing the significance of need satisfaction in comprehending intergroup relations.
-
-It is thus not surprising that in their perspectives paper on intergroup contact, Dovidio and colleagues propose that: "To achieve truly constructive intergroup relations, it is important that intergroup exchanges meet the psychological needs of both majority- and minority-group members." \citep[][p.
-6]{Dovidio2017}.
-A call that has thus far remained unanswered when it comes to the basic tenet that positive interactions drive the constructive part of intergroup contact.
+Among others, researchers have explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and knowledge about the other group \citep[][]{Pettigrew2008c}.
+However, all these advances share the underlying criticism that they are not geared towards understanding when and why an interaction is perceived as positive.}.
+We propose that the literature on motivation and psychological needs may help us understand when and why exactly an interaction is perceived as positive.
+
+% ALTERNATIVE: SHORTER BUT NOT FOCUSED ON ALLPORT'S CONDITIONS (WHICH WE TEST LATER)
+% Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
+Past research has either focused on conditions under which interactions tend to have favorable effects \citep[e.g., Allport's optimal conditions;][]{Allport1954b, Pettigrew1969} or has investigated cognitive-affective processes during contact \citep[e.g., group salience, intimacy, attachment, or intergroup anxiety;][]{Brown2005, Marinucci2021, Tropp2021, Paolini2004}.
+However, neither the contact conditions nor the cognitive-affective processes are particularly well-equipped to explain when and why an interaction will be perceived as positive.
+We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
+
+% Important in broader field: needs have been found to be important in broader intergroup relations and interpersonal contact literature.
+Although considerations of psychological needs and motivations have remained markedly absent within the intergroup contact literature, the concepts are in no way foreign to the broader topic of intergroup relations.
+Psychological needs have for example found fruitful utility in reconciliation research \citep[][]{Shnabel2008}, the study of minority's discrimination experiences \citep[][]{Celebi2017}, and in non-intergroup interactions \citep[][]{Downie2008}.
+% On the most general level, research on intergroup conflicts has, for example, shown that addressing the group-specific needs predicts willingness to reconcile with the other group \citep[][]{Shnabel2008}.
+For the case of refugee migrants in their relationship with a majority group, a recent study found that identity needs will buffer against discrimination experiences and will protect personal health \citep[][]{Celebi2017}.
+Additionally, within the field of interpersonal relations, we find first evidence that the fulfillment of fundamental psychological needs might predict perceived interaction quality in non-intergroup interactions \citep[][]{Downie2008}.
+% Promising for intergroup contact: Asked for in intergroup contact reviews and first research looked at social change
+Even within the field of intergroup contact, the idea of need fulfillment as a psychological mechanism is not entirely novel \citep[e.g.,][]{Dovidio2017}.
+First empirical research has even found psychological need fulfillment during intergroup contacts to predict support for social change \citep[][]{Hassler2021}.
+Considering need fulfillment during intergroup contact might therefore offer a promising psychological mechanism to understand perceived interaction quality and positive outgroup attitudes.
 
@@
 % MAYBE MOVE THIS TO 'The Present Research Section'
-One reason why motivational considerations might have remained absent from the intergroup contact literature is that there is an overwhelming number of individual motives or goals that might be relevant to a person during an intergroup interaction.
-Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad and diverse range of motives.
-However, while the individual need content differed between the different lines of research, what unites these approaches has been a focus on fulfilling the situationally relevant needs of people --- especially when we want to understand human functioning in social realms.
-We propose that the different lines of research share an underlying psychological mechanism, namely the motivational experience of need fulfillment.
-With motivation and need fulfillment we specifically mean the psychological experience of addressing an active and relevant need during the interaction.
-For our purposes, we define a need as:
-
-\begin{definition}[Need]\label{def:need}
-A tension or deficiency in the organism that elicits a (non-specific) motivational force organizing affect, cognition, and behavior to reduce this unsatisfactory situation, which is to some extent necessary for the individual’s overall well-being.
-\begin{flushright}
---- based on \citet[][]{dweck2017, Hull1943, Lewin1938, McClelland1987, Ryan2017, Steverink2006}
-\end{flushright}
-\end{definition}
-
-The psychological experience of need fulfillment is, thus, distinct from the content of the need (i.e., the motive or goal).
-The content could, for example, include physical motives (such as safety or hygiene) but also psychosocial motives \citep[such as acceptance or competence; e.g., see][]{pittman2007}.
-A need arises when a motive is thwarted or situationally active and relevant \citep[][]{leander2020, lewin1926e, gollwitzer1985e}.
-It is this perceived need and the perceived fulfillment of needs that we focus on in this article.
-This is not to say that considering specific motives is irrelevant to contact situations but instead we propose that the psychological experience of perceived need fulfillment is a core mechanism in understanding interaction quality perceptions, well-being, and outgroup attitudes.
-
-To test such a proposal we can rely on adaptive and responsive survey designs that allow a tailored approach based on the participants' inputs \citep[e.g.,][]{Tourangeau2017}.
-In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., name the situationally relevant need content), and with reference to their own response, the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment mechanism).
-Such an adaptive approach allows us to take the initial step of testing whether situational need fulfillment indeed generally predicts perceived interaction quality, well-being, and positive outgroup attitudes independent of need content.
+One reason why motivational considerations might have remained absent from the intergroup contact literature is that there is an overwhelming number of individual needs or goals that might be relevant to a person during an intergroup interaction.
+Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad range of fundamental psychological needs.
+To avoid this predicament we propose to start by using adaptive and responsive survey designs that allow a tailored approach based on the participants' inputs \citep[e.g.,][]{Tourangeau2017}.
+In particular, we propose to ask the participants to report their main goal during the interaction in a short open-ended question (i.e., situation core need) and with reference to their own response, the participants can then indicate how much this need was fulfilled during the interaction (i.e., need fulfillment).
+Such an adaptive approach allows us to take the initial step of testing whether situational psychological needs indeed generally predict perceived interaction quality and positive outgroup attitudes independent of need content.
 
@@
 While we have argued that a need fulfillment mechanism is relevant to intergroup contact generally, its flexible and broad applicability might be ideally suited to address the pressing issue of understanding natural intergroup contacts outside the lab.
-Investigations of such `real-life interactions' often suffer from the difficulty that past intergroup contact research has either focused on the mechanisms of individual interactions in artificial lab studies (sometimes referred to as the intergroup interaction literature) or has focused on longer-term recall self-reports of natural interactions \citep[commonly referred to as the intergroup contact literature; also see][]{Pettigrew2006}.
-\citet[][]{MacInnis2015} have even pointed out that these two approaches tend to find conflicting effects --- where individual interactions (in the lab) have more negative effects and recall of real-world contact patterns have more positive effects for intergroup relations.
-We, thus, miss data that follows people in their diverse daily interactions and investigates the psychological mechanisms of contacts, especially as they compound over time.
+Investigations of such `real-life interactions' often suffer from the difficulty that past intergroup contact research has either focused on the mechanisms of individual interactions in artificial lab studies or has focused on longer-term recall self-reports of natural interactions \citep[e.g.,][]{Pettigrew2006}.
 Even with extended intervention studies, the most fine-grained data available is usually limited to pre-post-control designs.
-
-The lack of longitudinal real-world data, however, stands in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the original contact hypothesis, which was focused on the daily interactions of people \citep[][]{Allport1954b}.
-As a result, prominent researchers in the field have long called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
+Such empirical practices stand, however, in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the core idea of the contact hypothesis, which was focused on the daily interactions of people \citep[][]{Allport1954b}.
+As a result, within the intergroup contact field researchers have called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
 Such data would be able to capture real-life interactions that include interaction-specific mechanism information close to the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
-Moreover, because data is nested within participants, experience-sampling data often allows capturing large amounts of high-quality data with relatively few participants \citep[][]{shiffman2008}.}.
+Moreover, because data is nested within participants, experience-sampling data often allows capturing large amounts of high-quality data with relatively few participants.}.
 
@@
 We can test whether having an interaction vs.
-not having an interaction improves intergroup relations, but we can also use the participant's 30-day contact reports to test whether participants with more positive interactions tend to benefit more from intergroup contact.
+not having an interaction impacts outgroup attitudes, but we can also use the participant's 30-day contact reports to test whether participants with more positive interactions tend to have more positive outgroup attitudes.
 Testing both approaches to the contact hypothesis allows us to go beyond a replication of the basic theory but could disentangle individual- from aggregated contact effects and would allow for a direct comparison with both bodies of literature.
-
-A second key decision was our choice to focus on the minority experience during the contact.
-While the same mechanisms should hold for the experience of members in high-powered groups, there is substantially more research available that focuses on the experience of the majority group, and minority perspectives are historically often understudied \citep[e.g.,][]{Dovidio2017}.
-At the same time, however, minority groups are often underprivileged and research is direly needed to understand the more prevalent experiences of stress and health issues among minorities \citep[e.g.,][]{alvidrez2019}.
-
-A third and final non-trivial aspect of translating the intergroup contact hypothesis into extensive real-world data was the choice of the outcome variable.
-For our main analyses, we chose outgroup attitudes --- the positive or negative evaluation of the other group.
-We chose outgroup attitudes mainly because they are the most common outcome considered within the intergroup contact literature \citep[e.g.,][]{Pettigrew2006, Paolini2021}.
-As the methodology is relatively new to the field, we sought to first replicate (and then extend) the most reliable effects of the contact hypothesis within the ESM data.
-Outgroup attitudes are, however, not without controversy, especially for minority group members' intergroup contact.
-In particular, positive outgroup attitudes have been shown to increase harmony and reduce the willingness to support social change among the disadvantaged in some cases --- even in the face of injustice \citep[e.g.,][]{dixon2012, saguy2009}.
-While a recent review found the effect to be less conclusive for longitudinally collected data and less consistent for positive interactions (rather than interactions generally), the backfire effect remains an important possibility for the present data \citep[see][]{reimer2023}.
-In order to ensure at least a direct benefit to the minority group members, we also assess the effect of the need fulfillment mechanism on well-being as the dependent variable as part of our robustness analyses below.
-
-With these important considerations in mind, we test the basic contact hypothesis within and across the three studies.
-In particular, we assess the effect of individual interactions within each study using a multilevel model, but to avoid power limitations, we test the collective effect of contact frequency and -quality after the individual studies, across all participants.
+We will test the effect of individual interactions within each study using a multilevel model, but to avoid power limitations, we will test the collective effect of contact frequency and -quality after the individual studies, across all participants.
 \begin{enumerate}[leftmargin=1.5\parindent]
@@
 
-Once the general contact hypothesis is established within the ESM data, our second main aim is to test our main theoretical proposal that the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
+Our second main aim is to test our main theoretical proposal that the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
 As our main proposal is concerned with the mechanisms of successful intergroup contact, we again focus on outgroup interaction reports.
@@
 Our third aim is to ensure that our results are robust, stable, and ecologically valid.
-To test the robustness of our need-fulfillment mechanism we test whether the need mechanism is indeed specific to outgroup interactions and whether the process could be explained by a smaller set of fundamental psychological needs instead.
-We additionally, assess the need fulfillment mechanism in predicting individual well-being benefits and check whether different types of needs or interactions change the main results.
+To test the robustness of our need-based mechanism we test whether the need mechanism is indeed specific to outgroup interactions and whether the process could be explained by a smaller set of fundamental needs instead.
 We present the full robustness analyses in \appref{app:AppendixRobustness}.
@@
 This approach is tolerant to missing data and uneven case numbers within participants.
-Furthermore, we use a hierarchical modeling approach and report the final model in-text \citep[][; for the full modeling process see Supplementary Material A]{snijders2012}.
+Furthermore, we use a hierarchical modeling approach and report the final model in-text \citep[][; for the full modeling process see Supplementary Material A]{Snijders2012}.
 Secondly, statistical power estimations for intensive longitudinal- and multilevel models are notoriously difficult due to the complex covariance structures.
-However, our participant- and measurement numbers are among the largest sample sizes found within the intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
-Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes (see Supplemental Material A).
+However, our participant- and measurement numbers are within the highest percentiles of sample sizes found within the broader intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
+Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes.
 The sample sizes were only increased to allow for between-subjects comparisons and future, more complicated, time-series modeling.
@@
 that are commonly discussed within the psychological needs literature
-\citep[e.g.,][]{orehek2018a} and offer insight into a core aspect of the
+\citep[e.g.,][]{Orehek2018a} and offer insight into a core aspect of the
 migration experience that has remained broadly under-explored
@@
 % aims re-iterated
-The main aim of this project was to test the basic tenets of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data and to test whether the fulfillment of situational needs meaningfully predicts positive interaction perceptions, well-being, and outgroup attitudes.
+The main aim of this project was to test the basic tenets of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data and to test whether the fulfillment of situational psychological needs meaningfully predicts positive interaction perceptions and outgroup attitudes.
 
@@
 Surprisingly, here we found independent effects of interaction frequency and average interaction quality ratings but no interaction effect.
-The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations).
-
-Interestingly, this effect is also inconsistent with the observations and theorizing of \citet[][]{MacInnis2015}, who observed that individual interactions showed negative effects on intergroup relations and the aggregate of past intergroup contacts showed positive effects on intergroup relations.
-There are, however, two important differences in our data compared to the past literature assessed by \citeauthor{MacInnis2015}.
-Firstly, what \citeauthor{MacInnis2015} called the intergroup interaction literature, has particularly focused on artificial lab studies where study participants meet a stranger from the outgroup.
-In our real-world data, such synthetic and controlled interactions are arguably less relevant.
-Secondly, what \citeauthor{MacInnis2015} called the intergroup contact literature, has looked at long-term recall self-reports --- where participants are asked to recall the quantity and average quality of intergroup contacts over the past month or year \citep{MacInnis2015}.
-The mental aggregation of such long-term recall surveys is substantially different from the aggregation we did based on the close-to-event reports \citep[][]{shiffman2008}.
-To truly compare our results to \citet[][]{MacInnis2015} theorizing, future studies should, thus, also collect a long-term recall report that mirrors the questions asked during intergroup contact studies.
-
-It should, however, be noted that the inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
-There is also a possibility that statistical power was a concern given our sample was relatively small with 207 participants and the effect of interest is an amplification interaction effect.
-However, if we assume an effect size of \textit{r} = -.21 for the effect of positive intergroup contacts \citep[see][]{Pettigrew2006} our sample size should approach the threshold of 80\% power at a .05 alpha level (sensitivity analysis in G*Power: $f^2 = 0.04$) --- especially if we consider the higher quality data we get from aggregating many real-world reports with less recall bias.
+The absence of this aggregate effect could underline the fact that cross-sectional retrospective data might be misleading because (1) it presents a mixture of within and between-subjects effects \citep[][]{Hamaker2020}, or (2) suffers from recall biases (e.g., where times with no outgroup interactions are undervalued by participants during the retrospective evaluations)\footnote{It should be noted that such inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).}.
 
 % Allport's conditions in ESM data [consistent predictor and partially through quality]
-Next, using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
-When we consider interaction quality and Allport's conditions jointly, we find that interaction quality ratings assumed a larger part of the shared variance in outgroup attitudes.
+Using the data from our third study, we find that Allport's conditions are related to higher interaction quality perceptions and more positive outgroup attitudes.
+When we consider interaction quality and Allport's conditions jointly, we find that the positive effect of Allport's conditions might in part be explained by more positive interaction quality ratings.
 We thus find first evidence that Allport's conditions of optimal contact are also relevant to the daily interactions recent migrants have in their interactions with majority group members.
@@
 % Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions, more positive outgroup attitudes, as well as \hl{higher well-being}.
-We find that in all three studies the effect of core need fulfillment on outgroup attitudes was either fully or partially assumed by the effect of interaction quality (when considering partial regression coefficients in a joint model).
+Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions and more positive outgroup attitudes.
+We find that in all three studies the effect of core need fulfillment on outgroup attitudes could either fully or partially be explained by its effect on interaction quality.
 We also find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
-In fact, our core situational needs measure predicted outgroup attitudes at least as good as Allport's conditions and consistently explained more variance than commonly measured psychological needs.
+In fact, our core situational needs measure predicted outgroup attitudes slightly better than Allport's conditions and consistently explained more variance than commonly measured psychological needs.
 In most cases, the core need even took over the variances previously explained by the self-determination theory needs (see \appref{app:AppendixRobustness}).
-We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction-specific needs are fulfilled offers a meaningful and flexible predictor of interaction quality, outgroup attitudes, and well-being.
+We thus find strong evidence that within everyday life interactions of recent migrants with majority outgroup members, the perception that one's interaction-specific psychological needs are fulfilled offers a meaningful and flexible predictor of outgroup attitudes.
 
@@
 % (1) Sample = minority and (voluntary) migrants, (2) Methodology = short scales (reliability) and no lagged effects, (3) Core Need Concept = non-specific
-While we believe that a need fulfillment mechanism should be relevant to any inter-group contact, our samples focused on a minority- and (voluntary) migrant perspective.
+While we believe that a need-based mechanism should be relevant to any inter-group contact, our samples focused on a minority- and (voluntary) migrant perspective.
 Without additional evidence it thus remains difficult to judge whether motivational effects will generalize to other migrant groups (e.g., forced migrants), other intergroup contexts (e.g., gender-, religious-, or sexual orientation groups), or to majority groups and their outgroup attitudes.
-We sought to replicate our results in three studies with different types of migrants but the fact remains that all three studies had slightly more women than men participating and were younger and more educated samples overall.
-While the samples were representative of the migrant group to the focus region, the generalizability of the sample is restricted by its characteristics.
-We know of no research suggesting that in other contexts need fulfillment would be less relevant but future research may extend our findings to build an even broader understanding of need fulfillment in intergroup contacts.
-Researchers may even seek to explore the role of need fulfillment in real-world interactions more broadly \citep[also see][]{Downie2008}.
+We know of no research suggesting that in other contexts psychological needs are irrelevant (once existential needs are met) but future research may extend our findings to build an even broader understanding of psychological needs in intergroup contacts.
 
@@
 
-A third limitation lies in the outcome variable we chose.
-As we have focused on outgroup attitudes to ensure comparability to the past literature of the contact hypothesis and to replicate the most reliable patterns within ESM data \citep[][]{pettigrew2006}.
-However, especially for disadvantaged minority members positive outgroup attitudes may entail negative downstream consequences such as a reduced endorsement of social change --- even in the face of injustice \citep[e.g.,][]{dixon2012}.
-We have additionally tested our need-fulfillment mechanism for well-being reporst to test direct benefits of the mechanism to lived realities.
-However, we are among the first to collect intensive longitudinal data on the experience of minority migrants and it remains an open empirical question whether the more positive outgroup attitudes following need-fulfilling interactions might ironically exacerbate inequalities for the disadvantaged group.
-
 Finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
-This comes at the expense of specificity in the situational motives (i.e., we have not explored whether different types of needs have stronger effects on interaction quality and outgroup attitudes).
+This comes at the expense of specificity in the situational needs (i.e., we have not explored whether different types of needs have stronger effects on interaction quality and outgroup attitudes).
 Such an investigation would be possible with the adaptive measurement we used (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
@@
 Psychological needs are a facet of the human experience that has thus far been underemphasized in the intergroup contact literature.
-This stands in stark contrast of the many cognitive \citep[e.g.,][]{Pettigrew1998, Brown2005} and emotional aspects investigated within the field \citep[e.g.,][]{Stephan2008}.
+This stands in stark contrast of the many cognitive \citep[e.g.,][]{Pettigrew1998, Brown2005} and emotional aspects investigated within the field \citep[e.g.,][]{Stephan2008, Paolini2004}.
 Future research may, therefore, be able to integrate broader theoretical frameworks of intergroup contact (e.g., motivations guiding cognition and affect, which in turn drive behavior.

### 2023-05-30 Methods-and-Results.Rmd
robustness re-render

@@
 # divide into trait and state
-dtWorkerSupp$workerWithinBetween <-
-  MlTraitState(
-    data = dtWorkerSupp$workerInteractionType,
-    id = "PID",
-    selection =
-      c(
-        "keyMotiveFulfilled",
-        "competence.daily.all",
-        "autonomy.daily.all",
-        "relatedness.daily.all",
-        "thermometerDutch_1",
-        "keymotive_fulfillemt_1",
-        "competence_1",
-        "autonomy_1",
-        "relatedness_1", 
-        "quality_overall_1", 
-        "OutgroupInteraction",
-        "NonOutgroupInteraction", 
-        "OutgroupInteractionM",
-        "NonOutgroupInteractionM"
-      )
-  )
-
-dtWorkerSupp$workerOutWithinBetween <-
-  MlTraitState(
-    data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
-    id = "PID",
-    selection =
-      c(
-        "keyMotiveFulfilled",
-        "thermometerDutch_1",
-        "keymotive_fulfillemt_1",
-        "competence_1",
-        "autonomy_1",
-        "relatedness_1", 
-        "quality_overall_1"
-      )
-  )
+# dtWorkerSupp$workerWithinBetween <-
+#   MlTraitState(
+#     data = dtWorkerSupp$workerInteractionType,
+#     id = "PID",
+#     selection =
+#       c(
+#         "keyMotiveFulfilled",
+#         "competence.daily.all",
+#         "autonomy.daily.all",
+#         "relatedness.daily.all",
+#         "thermometerDutch_1",
+#         "keymotive_fulfillemt_1",
+#         "competence_1",
+#         "autonomy_1",
+#         "relatedness_1", 
+#         "quality_overall_1", 
+#         "OutgroupInteraction",
+#         "NonOutgroupInteraction", 
+#         "OutgroupInteractionM",
+#         "NonOutgroupInteractionM"
+#       )
+#   )
+# 
+# dtWorkerSupp$workerOutWithinBetween <-
+#   MlTraitState(
+#     data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
+#     id = "PID",
+#     selection =
+#       c(
+#         "keyMotiveFulfilled",
+#         "thermometerDutch_1",
+#         "keymotive_fulfillemt_1",
+#         "competence_1",
+#         "autonomy_1",
+#         "relatedness_1", 
+#         "quality_overall_1"
+#       )
+#   )
 ```
@@
 
-# divide into trait and state
-dtStudentSupp$studentWithinBetween <-
-  MlTraitState(
-    data = dtStudentSupp$studentInteractionType,
-    id = "PID",
-    selection =
-      c(
-        "KeyNeedFullfillment",
-        "Competence",
-        "Autonomy",
-        "Relatedness",
-        "AttitudesDutch",
-        "quality_overall",
-        "OutgroupInteraction",
-        "NonOutgroupInteraction",
-        "OutgroupInteractionM",
-        "NonOutgroupInteractionM"
-      )
-  )
-dtStudentSupp$studentOutWithinBetween <-
-  MlTraitState(
-    data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
-    id = "PID",
-    selection =
-      c(
-        "KeyNeedFullfillment",
-        "Competence",
-        "Autonomy",
-        "Relatedness",
-        "AttitudesDutch",
-        "quality_overall"
-      )
-  )
+# # divide into trait and state
+# dtStudentSupp$studentWithinBetween <-
+#   MlTraitState(
+#     data = dtStudentSupp$studentInteractionType,
+#     id = "PID",
+#     selection =
+#       c(
+#         "KeyNeedFullfillment",
+#         "Competence",
+#         "Autonomy",
+#         "Relatedness",
+#         "AttitudesDutch",
+#         "quality_overall",
+#         "OutgroupInteraction",
+#         "NonOutgroupInteraction",
+#         "OutgroupInteractionM",
+#         "NonOutgroupInteractionM"
+#       )
+#   )
+# dtStudentSupp$studentOutWithinBetween <-
+#   MlTraitState(
+#     data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
+#     id = "PID",
+#     selection =
+#       c(
+#         "KeyNeedFullfillment",
+#         "Competence",
+#         "Autonomy",
+#         "Relatedness",
+#         "AttitudesDutch",
+#         "quality_overall"
+#       )
+#   )
 ```
@@
 
-# divide into trait and state
-dtMedicalSupp$medicalWithinBetween <- 
-  MlTraitState(
-    data = dtMedical$full,
-    id = "PID",
-    selection =
-      c(
-        "OutgroupInteraction",
-        "NonOutgroupInteraction",
-        "OutgroupInteractionM",
-        "NonOutgroupInteractionM"
-      )
-  )
+# # divide into trait and state
+# dtMedicalSupp$medicalWithinBetween <- 
+#   MlTraitState(
+#     data = dtMedical$full,
+#     id = "PID",
+#     selection =
+#       c(
+#         "OutgroupInteraction",
+#         "NonOutgroupInteraction",
+#         "OutgroupInteractionM",
+#         "NonOutgroupInteractionM"
+#       )
+#   )
 
@@
 # make different options
+# way easier version in robustness analyses!! Check that out first!!
 
@@
     CoreNeedZ = keymotive_fulfillemt_1_zwc,
-    QualityRaw = quality_overall_1,
-    Quality = quality_overall_1_cwc,
-    QualityZ = quality_overall_1_zwc,
+    QualityRaw = interaction_quality, # quality_overall_1,
+    Quality = interaction_quality_cwc, # quality_overall_1_cwc,
+    QualityZ = interaction_quality_zwc, # quality_overall_1_zwc,
     PID = PID
@@
     CoreNeedZ = KeyNeedFullfillment_zwc,
-    QualityRaw = quality_overall,
-    Quality = quality_overall_cwc,
-    QualityZ = quality_overall_zwc,
+    QualityRaw = interaction_quality, #quality_overall,
+    Quality = interaction_quality_cwc, #quality_overall_cwc,
+    QualityZ = interaction_quality_zwc, #quality_overall_zwc,
     PID = PID
@@
     AllportZ = AllportsCondition_zwc,
-    QualityRaw = qualityOverall,
-    Quality = qualityOverall_cwc,
-    QualityZ = qualityOverall_zwc,
+    QualityRaw = interaction_quality, #qualityOverall,
+    Quality = interaction_quality_cwc, #qualityOverall_cwc,
+    QualityZ = interaction_quality_zwc, #qualityOverall_zwc,
     PID = PID
@@
      file = "data/theoryMdlTabl.RData")
+rmarkdown::render("PathModels.Rmd")
 ```

### 2023-05-30 PathModels.tex
robustness re-render

@@
     \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.30**} (yd.west);
-    \draw[-latex] (x.north) -- node[auto] {0.40****} (m.west);
-    \draw[-latex] (m.east) -- node[auto] {0.41***} (y.north);
-    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.13} (y.west);
+    \draw[-latex] (x.north) -- node[auto] {0.39****} (m.west);
+    \draw[-latex] (m.east) -- node[auto] {0.45***} (y.north);
+    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.12} (y.west);
     \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(A) Study 1:}};
@@
     \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.14***} (yd.west);
-    \draw[-latex] (x.north) -- node[auto] {0.27****} (m.west);
-    \draw[-latex] (m.east) -- node[auto] {0.24****} (y.north);
-    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.07} (y.west);
+    \draw[-latex] (x.north) -- node[auto] {0.20****} (m.west);
+    \draw[-latex] (m.east) -- node[auto] {0.22****} (y.north);
+    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.09*} (y.west);
     \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(B) Study 2:}};
@@
     \draw[-latex] (x.north) -- node[auto] {0.31****} (m.west);
-    \draw[-latex] (m.east) -- node[auto] {0.23****} (y.north);
-    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.10**} (y.west);
+    \draw[-latex] (m.east) -- node[auto] {0.24****} (y.north);
+    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.10***} (y.west);
     \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(C) Study 3:}};

### 2023-05-30 Robustness-Methods-and-Results.Rmd
robustness re-render

@@
 
-\subsubsection{Interaction Intend} To assess whether an interaction was accidental (vs.
+\subsubsection{Interaction Intent} To assess whether an interaction was accidental (vs.
 planned), we asked participants with a single item to report the extend to which "The interaction with -X- was accidental".
@@
 
-\subsubsection{Interaction intend}
+\subsubsection{Interaction intent}
 
@@
 We again start our analysis approach by assessing the model across all three studies, using a three-level hierarchical model.
-In this overall model, we retain the main effect of core need fulfillment (random slopes model, grand-mean standardized to account for all levels of variance; `r get_latex_coef(accidental_overall$lmer_coef, "CoreNeed")`) but neither contact intend nor the moderation effect affect the results (all |\textit{b}| < `r max(abs(accidental_overall$lmer_coef[accidental_overall$lmer_coef$coef != c("(Intercept)", "CoreNeed"), "b"])) %>% round(2) %>% format(nsmall=2)` and all \textit{p} > `r min(accidental_overall$lmer_coef[accidental_overall$lmer_coef$coef != c("(Intercept)", "CoreNeed"), "p"]) %>% round(3) %>% format(nsmall=3)`; see \tblref{tab:robustnessTblLong} for full results).
+In this overall model, we retain the main effect of core need fulfillment (random slopes model, grand-mean standardized to account for all levels of variance; `r get_latex_coef(accidental_overall$lmer_coef, "CoreNeed")`) but neither contact intent nor the moderation effect affect the results (all |\textit{b}| < `r max(abs(accidental_overall$lmer_coef[accidental_overall$lmer_coef$coef != c("(Intercept)", "CoreNeed"), "b"])) %>% round(2) %>% format(nsmall=2)` and all \textit{p} > `r min(accidental_overall$lmer_coef[accidental_overall$lmer_coef$coef != c("(Intercept)", "CoreNeed"), "p"]) %>% round(3) %>% format(nsmall=3)`; see \tblref{tab:robustnessTblLong} for full results).
 
@@
 replacement_mapping <- c("contact" = "Contact specific",
-                         "accidental" = "Interaction Intend",
+                         "accidental" = "Interaction Intent",
                          "wellbeing_core" = "Well-being Outcome",
@@
 replacement_mapping <- c("contact" = "Contact Specific",
-                         "accidental" = "Interaction Intend",
+                         "accidental" = "Interaction Intent",
                          "wellbeing_core" = "Well-being Outcome",

### 2023-05-30 Robustness-Methods-and-Results.tex
robustness re-render

--- 2023-05-26 Robustness-Methods-and-Results.tex
@@
 
-\subsubsection{Interaction Intend}
+\subsubsection{Interaction Intent}
 
@@
 When looking at the individual studies, we again saw that core need
-fulfillemnt remained a consistent predictor of outgroup attitudes, even
+fulfillment remained a consistent predictor of outgroup attitudes, even
 after accounting for the self-determination theory need (all

### 2023-05-30 Tables/mdlTheory.tex
robustness re-render

@@
 \multicolumn{27}{l}{\textbf{Fixed}}\\
-\hspace{1em}(Intercept) & 74.28**** [70.20, 78.36] &  & 72.53**** [66.81, 78.26] &  & 72.50**** [66.74, 78.25] &  & 78.84**** [76.86, 80.83] &  & 70.71**** [67.55, 73.87] &  & 70.67**** [67.50, 73.84] &  & 81.36**** [78.53, 84.19] &  & 68.32**** [65.10, 71.54] &  & 68.32**** [65.09, 71.54] &  & 81.42**** [78.57, 84.26] &  & 68.36**** [65.16, 71.56] &  & 68.34**** [65.12, 71.56] &  & 68.33**** [65.05, 71.61] & \\
-\hspace{1em}CoreNeed & 0.42**** [ 0.32,  0.52] & 0.40 [0.31, 0.49] & 0.17** [ 0.06,  0.29] & 0.30 [0.18, 0.41] & 0.04 [-0.08,  0.15] & 0.13 [0.00, 0.26] & 0.40**** [ 0.28,  0.52] & 0.27 [0.18, 0.37] & 0.13*** [ 0.07,  0.19] & 0.14 [0.06, 0.22] & 0.03 [-0.01,  0.07] & 0.07 [-0.01, 0.15] & 0.43**** [ 0.33,  0.54] & 0.31 [0.24, 0.38] & 0.19**** [ 0.12,  0.27] & 0.18 [0.11, 0.24] & 0.11** [ 0.05,  0.17] & 0.10 [0.04, 0.16] &  &  &  &  &  &  & 0.13**** [ 0.08,  0.17] & 0.12 [0.05, 0.18]\\
-\hspace{1em}Quality &  &  &  &  & 0.23*** [ 0.12,  0.33] & 0.41 [0.29, 0.54] &  &  &  &  & 0.17**** [ 0.11,  0.23] & 0.24 [ 0.14, 0.34] &  &  &  &  & 0.17**** [ 0.12,  0.22] & 0.23 [0.17, 0.30] &  &  &  &  & 0.17**** [ 0.12,  0.23] & 0.22 [0.15, 0.29] &  & \\
-\hspace{1em}Allport &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 0.65**** [ 0.54,  0.76] & 0.46 [0.39, 0.52] & 0.22**** [ 0.15,  0.29] & 0.21 [0.14, 0.27] & 0.09** [ 0.03,  0.15] & 0.10 [0.03, 0.16] & 0.17*** [ 0.09,  0.24] & 0.17 [0.11, 0.23]\\
+\hspace{1em}(Intercept) & 67.16**** [62.99, 71.34] &  & 72.53**** [66.81, 78.26] &  & 72.50**** [66.74, 78.26] &  & 67.46**** [65.17, 69.76] &  & 70.71**** [67.55, 73.87] &  & 70.69**** [67.52, 73.85] &  & 72.20**** [68.71, 75.70] &  & 68.32**** [65.10, 71.54] &  & 68.32**** [65.10, 71.54] &  & 72.23**** [68.75, 75.72] &  & 68.36**** [65.16, 71.56] &  & 68.36**** [65.14, 71.58] &  & 68.33**** [65.05, 71.61] & \\
+\hspace{1em}CoreNeed & 0.37**** [ 0.28,  0.47] & 0.39 [0.30, 0.48] & 0.17** [ 0.06,  0.29] & 0.30 [0.18, 0.41] & 0.05 [-0.05,  0.14] & 0.12 [0.00, 0.24] & 0.29**** [ 0.19,  0.40] & 0.20 [0.10, 0.31] & 0.13*** [ 0.07,  0.19] & 0.14 [0.06, 0.22] & 0.06* [ 0.01,  0.11] & 0.09 [0.01, 0.17] & 0.45**** [ 0.36,  0.54] & 0.31 [0.24, 0.37] & 0.19**** [ 0.12,  0.27] & 0.18 [0.11, 0.24] & 0.12*** [ 0.06,  0.19] & 0.10 [0.04, 0.16] &  &  &  &  &  &  & 0.13**** [ 0.08,  0.17] & 0.12 [0.05, 0.18]\\
+\hspace{1em}Quality &  &  &  &  & 0.24*** [ 0.13,  0.35] & 0.45 [0.31, 0.59] &  &  &  &  & 0.16**** [ 0.11,  0.21] & 0.22 [0.13, 0.30] &  &  &  &  & 0.16**** [ 0.11,  0.20] & 0.24 [0.18, 0.31] &  &  &  &  & 0.16**** [ 0.11,  0.21] & 0.23 [0.16, 0.29] &  & \\
+\hspace{1em}Allport &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & 0.62**** [ 0.49,  0.74] & 0.40 [0.33, 0.47] & 0.22**** [ 0.15,  0.29] & 0.21 [0.14, 0.27] & 0.11** [ 0.05,  0.18] & 0.11 [0.05, 0.17] & 0.17*** [ 0.09,  0.24] & 0.17 [0.11, 0.23]\\
 \addlinespace[0.3em]
 \multicolumn{27}{l}{\textbf{Random}}\\
-\hspace{1em}$\sigma^2$ & 261.1 &  & 63.08 &  & 37.6 &  & 275.7 &  & 89.83 &  & 76.47 &  & 222.5 &  & 91.84 &  & 82.15 &  & 188.9 &  & 93.05 &  & 83.82 &  & 90.78 & \\
-\hspace{1em}$\tau_{00}$ & 71.13 (PID) &  & 173.49 (PID) &  & 177.88 (PID) &  & 63.00 (PID) &  & 259.79 (PID) &  & 264.19 (PID) &  & 131.33 (PID) &  & 182.38 (PID) &  & 183.10 (PID) &  & 134.62 (PID) &  & 179.74 (PID) &  & 182.79 (PID) &  & 189.33 (PID) & \\
-\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.05 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Quality)} &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[c]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
-\hspace{1em}$\rho_{01}$ &  &  & 0.03 (cor.slope.intercept) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.22 (PID.Quality)} &  & -0.09 (cor.slope.intercept) &  & -0.16 (cor.slope.intercept) &  & \makecell[c]{-0.18 (PID.CoreNeed)\\-0.06 (PID.Quality)} &  & -0.26 (cor.slope.intercept) &  & -0.26 (cor.slope.intercept) &  & \makecell[c]{-0.14 (PID.CoreNeed)\\-0.41 (PID.Quality)} &  & -0.07 (cor.slope.intercept) &  & -0.19 (cor.slope.intercept) &  & \makecell[c]{ 0.12 (PID.Allport)\\-0.51 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
-\hspace{1em}$\rho_{00}$ &  &  &  &  & -0.47 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.79 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.10 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.11 (PID.Allport-Quality) &  & 0.07 (PID.CoreNeed-Allport) & \\
+\hspace{1em}$\sigma^2$ & 224.8 &  & 63.08 &  & 35.4 &  & 267.5 &  & 89.83 &  & 79.34 &  & 230 &  & 91.84 &  & 84.56 &  & 197.5 &  & 93.05 &  & 86.99 &  & 90.78 & \\
+\hspace{1em}$\tau_{00}$ & 77.54 (PID) &  & 173.49 (PID) &  & 178.05 (PID) &  & 98.57 (PID) &  & 259.79 (PID) &  & 263.15 (PID) &  & 207.01 (PID) &  & 182.38 (PID) &  & 182.78 (PID) &  & 207.46 (PID) &  & 179.74 (PID) &  & 182.20 (PID) &  & 189.33 (PID) & \\
+\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.05 (PID.Quality)} &  & 0.07 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & \makecell[c]{0.01 (PID.CoreNeed)\\0.02 (PID.Quality)} &  & 0.07 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & \makecell[c]{0.03 (PID.CoreNeed)\\0.01 (PID.Quality)} &  & 0.17 (PID.Allport) &  & 0.05 (PID.Allport) &  & \makecell[c]{0.02 (PID.Allport)\\0.02 (PID.Quality)} &  & \makecell[c]{0.00 (PID.CoreNeed)\\0.04 (PID.Allport)} & \\
+\hspace{1em}$\rho_{01}$ &  &  & 0.03 (cor.slope.intercept) &  & \makecell[c]{ 0.37 (PID.CoreNeed)\\-0.26 (PID.Quality)} &  & 0.27 (cor.slope.intercept) &  & -0.16 (cor.slope.intercept) &  & \makecell[c]{-0.10 (PID.CoreNeed)\\-0.27 (PID.Quality)} &  & 0.06 (cor.slope.intercept) &  & -0.26 (cor.slope.intercept) &  & \makecell[c]{-0.27 (PID.CoreNeed)\\-0.27 (PID.Quality)} &  & 0.24 (cor.slope.intercept) &  & -0.19 (cor.slope.intercept) &  & \makecell[c]{-0.10 (PID.Allport)\\-0.38 (PID.Quality)} &  & \makecell[c]{-1.00 (PID.CoreNeed)\\-0.07 (PID.Allport)} & \\
+\hspace{1em}$\rho_{00}$ &  &  &  &  & -0.34 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.74 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.36 (PID.CoreNeed-Quality) &  &  &  &  &  & 0.09 (PID.Allport-Quality) &  & 0.07 (PID.CoreNeed-Allport) & \\
 \addlinespace[0.3em]
@@
 \hspace{1em}name &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  &  & \\
-\hspace{1em}AIC & 3294 &  & 2816 &  & 2672 &  & 8073 &  & 7222 &  & 7141 &  & 14054 &  & 12632 &  & 12494 &  & 13805 &  & 12652 &  & 12519 &  & 12625 & \\
-\hspace{1em}BIC & 3309 &  & 2839 &  & 2712 &  & 8102 &  & 7251 &  & 7190 &  & 14087 &  & 12665 &  & 12548 &  & 13838 &  & 12684 &  & 12573 &  & 12679 & \\
+\hspace{1em}AIC & 3240 &  & 2816 &  & 2651 &  & 8062 &  & 7222 &  & 7158 &  & 14129 &  & 12632 &  & 12538 &  & 13918 &  & 12652 &  & 12576 &  & 12625 & \\
+\hspace{1em}BIC & 3255 &  & 2839 &  & 2690 &  & 8091 &  & 7251 &  & 7206 &  & 14161 &  & 12665 &  & 12592 &  & 13950 &  & 12684 &  & 12630 &  & 12679 & \\
 \hspace{1em}N & 387 &  & 387 &  & 387 &  & 935 &  & 935 &  & 935 &  & 1676 &  & 1672 &  & 1672 &  & 1676 &  & 1672 &  & 1672 &  & 1672 & \\
 \hspace{1em}Groups & 21 &  & 21 &  & 21 &  & 108 &  & 108 &  & 108 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 &  & 70 & \\
-\hspace{1em}ICC & 0.2141 &  & 0.7458 &  & 0.8404 &  & 0.2547 &  & 0.7471 &  & 0.7835 &  & 0.3933 &  & 0.6738 &  & 0.7006 &  & 0.4433 &  & 0.6679 &  & 0.6963 &  &  & \\
-$R^2_{marginal}$ / $R^2_{conditional}$ & 0.117 / 0.306 &  & 0.030 / 0.753 &  & 0.067 / 0.851 &  & 0.102 / 0.331 &  & 0.012 / 0.750 &  & 0.028 / 0.789 &  & 0.070 / 0.436 &  & 0.019 / 0.680 &  & 0.041 / 0.713 &  & 0.149 / 0.526 &  & 0.024 / 0.676 &  & 0.040 / 0.709 &  & 0.086 / NA & \\
+\hspace{1em}ICC & 0.2565 &  & 0.7458 &  & 0.8472 &  & 0.3052 &  & 0.7471 &  & 0.7741 &  & 0.485 &  & 0.6738 &  & 0.6943 &  & 0.5399 &  & 0.6679 &  & 0.6863 &  &  & \\
+$R^2_{marginal}$ / $R^2_{conditional}$ & 0.103 / 0.333 &  & 0.030 / 0.753 &  & 0.068 / 0.858 &  & 0.054 / 0.343 &  & 0.012 / 0.750 &  & 0.024 / 0.780 &  & 0.063 / 0.517 &  & 0.019 / 0.680 &  & 0.039 / 0.706 &  & 0.111 / 0.591 &  & 0.024 / 0.676 &  & 0.041 / 0.699 &  & 0.086 / NA & \\
 \bottomrule

### 2023-05-30 manuscript.tex
phrasing

@@
 linkcolor    = black, %Colour of internal links
-citecolor   = cyan, %Colour of citations
+citecolor   = black, %Colour of citations
 pdfstartview={FitV},
@@
 The experience of needing is a more general process that arises when any important motive is thwarted or situationally active and relevant \citep[][]{leander2020, lewin1926e, gollwitzer1985e}.
-It is this perceived need and the perceived fulfillment of needs that we focus on in this article.
+It is this perceived needing and the perceived fulfillment of needs that we focus on in this article.
 This is not to say that considering specific motives is irrelevant to contact situations but instead we propose that the psychological experience of perceived need fulfillment is a core mechanism in understanding interaction quality perceptions, well-being, and outgroup attitudes.
@@
 The lack of longitudinal real-world data, however, stands in stark contrast to many of the theoretical advances that have focused on the dynamic nature of intergroup relations \citep[e.g.,][]{Pettigrew1998}, as well as the original contact hypothesis, which was focused on the daily interactions of people \citep[][]{Allport1954b}.
-As a result, prominent researchers in the field have long called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[][]{MacInnis2015, McKeown2017}.
+As a result, prominent researchers in the field have long called for longitudinal \citep[][]{Pettigrew1998, Pettigrew2008, Pettigrew2011} and real-life experience-sampling data outside the lab \citep[ESM][]{MacInnis2015, McKeown2017}.
 Such data would be able to capture real-life interactions that include interaction-specific mechanism information close to the actual experience\footnote{Additionally, such experience-sampling data can be collected close to the intergroup interactions and would, thus, largely mitigate recall biases.
@@
 Using three independent sets of extensive longitudinal data (Studies 1–3), the aim of this paper is essentially threefold.
-First, our study is among the first to test the fundamental tenets of intergroup contact and Allport's conditions in real-life extensive longitudinal data.
+We (1) seek to test the basic ideas of the contact theory within real-world experience sampling data.
+We (2) aim to test the core need fulfillment mechanism within the real-world data.
+And we (3) seek to ensure the stability, robustness, and embeddedness of our results.
+
+Firstly, for the general contact hypothesis test, our study is among the first to test the fundamental tenets of intergroup contact and Allport's conditions in real-life extensive longitudinal data.
 Translating the contact hypothesis into extensive longitudinal data is not a trivial task, as past research traditions have used two fundamentally different approaches.
@@
 Extensive longitudinal data allows us to investigate both.
-We can test whether having an interaction vs.
+We can test whether having a specific type of interaction vs.
 not having an interaction improves intergroup relations, but we can also use the participant's 30-day contact reports to test whether participants with more positive interactions tend to benefit more from intergroup contact.
@@
 
-A second key decision was our choice to focus on the minority experience during the contact.
-While the same mechanisms should hold for the experience of members in high-powered groups, there is substantially more research available that focuses on the experience of the majority group, and minority perspectives are historically often understudied \citep[e.g.,][]{Dovidio2017}.
-At the same time, however, minority groups are often underprivileged and research is direly needed to understand the more prevalent experiences of stress and health issues among minorities \citep[e.g.,][]{alvidrez2019}.
-
-A third and final non-trivial aspect of translating the intergroup contact hypothesis into extensive real-world data was the choice of the outcome variable.
-For our main analyses, we chose outgroup attitudes --- the positive or negative evaluation of the other group.
-We chose outgroup attitudes mainly because they are the most common outcome considered within the intergroup contact literature \citep[e.g.,][]{Pettigrew2006, Paolini2021}.
-As the methodology is relatively new to the field, we sought to first replicate (and then extend) the most reliable effects of the contact hypothesis within the ESM data.
-Outgroup attitudes are, however, not without controversy, especially for minority group members' intergroup contact.
-In particular, positive outgroup attitudes have been shown to increase harmony and reduce the willingness to support social change among the disadvantaged in some cases --- even in the face of injustice \citep[e.g.,][]{dixon2012, saguy2009}.
-While a recent review found the effect to be less conclusive for longitudinally collected data and less consistent for positive interactions (rather than interactions generally), the backfire effect remains an important possibility for the present data \citep[see][]{reimer2023}.
-In order to ensure at least a direct benefit to the minority group members, we also assess the effect of the need fulfillment mechanism on well-being as the dependent variable as part of our robustness analyses below.
-
-With these important considerations in mind, we test the basic contact hypothesis within and across the three studies.
+We test the basic contact hypothesis within and across the three studies.
 In particular, we assess the effect of individual interactions within each study using a multilevel model, but to avoid power limitations, we test the collective effect of contact frequency and -quality after the individual studies, across all participants.
@@
 Focusing on the interactions in detail, we use a multi-level regression model to test whether interactions that are higher in the fulfillment of Allport's conditions predict more favorable outgroup attitudes.
-We would also expect that this is due to such interactions being perceived as higher in interaction quality.
+We would also expect that such interactions are perceived as higher in interaction quality.
 \begin{enumerate}[leftmargin=1.5\parindent]
@@
 
-Once the general contact hypothesis is established within the ESM data, our second main aim is to test our main theoretical proposal that the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
+Once the general contact hypothesis is established within the ESM data, our second main aim is to test our main theoretical proposal that the fulfillment of situational needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
 As our main proposal is concerned with the mechanisms of successful intergroup contact, we again focus on outgroup interaction reports.
@@
 
-Our third aim is to ensure that our results are robust, stable, and ecologically valid.
+Our third main aim is to ensure that our results are robust, stable, and ecologically valid.
 To test the robustness of our need-fulfillment mechanism we test whether the need mechanism is indeed specific to outgroup interactions and whether the process could be explained by a smaller set of fundamental psychological needs instead.
@@
 
-Before turning to individual studies, two methodological matters need consideration.
-Firstly, we tested most of our hypotheses using multilevel regression models, where measurement occasions (level 1) were nested within participants (level 2).
+Before turning to individual studies, we would like to address a number of conceptual, practical, and methodological considerations.
+One key decision for our studies has been to focus on the minority experience during the contact.
+While the same mechanisms should hold for the experience of members in high-powered groups, there is substantially more research available that focuses on the experience of the majority group, and minority perspectives are historically often understudied \citep[e.g.,][]{Dovidio2017}.
+At the same time, however, minority groups are often underprivileged and research is direly needed to understand the more prevalent experiences of stress and health issues among minorities \citep[e.g.,][]{alvidrez2019}.
+
+A second non-trivial aspect of translating the intergroup contact hypothesis into extensive real-world data was the choice of the outcome variable.
+For our main analyses, we chose outgroup attitudes --- the positive or negative evaluation of the other group.
+We chose outgroup attitudes mainly because they are the most common outcome considered within the intergroup contact literature \citep[e.g.,][]{Pettigrew2006, Paolini2021}.
+As the methodology is relatively new to the field, we sought to first replicate (and then extend) the most reliable effects of the contact hypothesis within the ESM data.
+Outgroup attitudes are, however, not without controversy, especially for minority group members' intergroup contact.
+In particular, positive outgroup attitudes have been shown to increase harmony and reduce the willingness to support social change among the disadvantaged in some cases --- even in the face of injustice \citep[e.g.,][]{dixon2012, saguy2009}.
+While a recent review found the effect to be less conclusive for longitudinally collected data and less consistent for positive interactions (rather than interactions generally), the backfire effect remains an important possibility for the present data \citep[see][]{reimer2023}.
+In order to ensure at least a direct benefit to the minority group members, we also assess the effect of the need fulfillment mechanism on well-being as the dependent variable as part of our robustness analyses below.
+
+In terms of methodological considerations, it is important to note we tested most of our hypotheses using multilevel regression models, where measurement occasions (level 1) were nested within participants (level 2).
 This approach is tolerant to missing data and uneven case numbers within participants.
@@
 The full surveys, code, and materials are available in our open science repository \citep[including a complete codebook;][]{KreienkampMasked2022a}.
-Additionally, the fully annotated analyses are available in Supplementary Material A.
+Additionally, the fully annotated analyses are available in Supplementary Materials A, B, and C.
 

### 2023-05-30 manuscript.tex
mechanism intro phrasing adj

@@
 % Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
-When it comes to what constitutes a positive interaction the most widely used approach has been the idea that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact effect \citep[][]{Allport1954b, Pettigrew1969}.
-However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be necessary to finding positive effects of intergroup contact \citep[][]{Pettigrew2006}.
-Following Allport's original conditions, several additional conditions of optimal contact were proposed, which have largely received the same criticism of not capturing the underlying psychological mechanisms of why an interaction is perceived as positive \citep[for a critical discussion see][]{Pettigrew1986}.
-
-Instead, since the early 21\textsuperscript{st} century, researchers have assumed positive contact and have focused on the psychological processes that explain how positive contacts improve intergroup relations \citep[e.g.
+
+Looking at the past literature, we can essentially separate intergroup contact theory research into a two-step problem.
+Firstly, we need to understand when and why contact becomes a positive contact (contact $\rightarrow$ positive contact) and, secondly, we need to understand when and why positive contacts drive better intergroup relations \citep[positive contact $\rightarrow$ better relations; e.g., see ][]{Allport1954b, Hewstone1996, Pettigrew1998}.
+
+In recent years, research has focused on the second step of understanding the psychological processes that explain how positive contacts improve intergroup relations \citep[e.g.
 see,][]{Paolini2021}.
 Among others, researchers have explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008}, as well as knowledge about the other group \citep[][]{Pettigrew2008c}.
-However, all these advances share a focus on understanding when and how \textit{positive interactions} improve intergroup relations.
-Understanding when and why an interaction is perceived as positive in the first place has remained a tangential focus and it, thus, remains largely unclear which psychological mechanisms drive positive interaction perceptions.
-
-In this article, we focus on the underexplored role of motivation and need fulfillment to understand when and why exactly an interaction is perceived as positive.
-We propose need fulfillment in particular, because a need mechanism builds a strong body of literature highlighting the functional role of need fulfillment in psychosocial functioning, interactions, and intergroup relations --- all of which are fundamental considerations for intergroup contact.
+Most recently, researchers have even looked at how empowerment need fulfillment during positive intergroup contact can explain some of the beneficial intergroup effects \citep[][]{Hassler2021}.
+There is thus, substantial evidence on the psychological mechanisms that explain the effects of positive contact.
+
+Research on the first step of what makes an interaction positive to begin with tends to be much older, and often more static and contextual.
+The most widely used approach has been the idea that equal status, common goals, collaboration, and structural support during the interaction form Allport's optimal conditions for positive contacts \citep[][]{Allport1954b, Pettigrew1969}.
+Following Allport's original conditions, several additional conditions of optimal contact were proposed, including, stereotype disconfirmation \citep[][]{cook1978} or common language and voluntary interaction (\citealp{wagner1986}; for a critical discussion see \citealp{Pettigrew1986}).
+However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be necessary to finding positive effects of intergroup contact \citep[][]{Pettigrew2006} and more fundamentally, the conditions often do not capture any underlying psychological mechanisms of why an interaction is perceived as positive \citep[e.g.,][]{Pettigrew1998}.
+
+In this article, we focus on the role of motivation and need fulfillment to understand when and why exactly an interaction is perceived as positive.
+We propose need fulfillment in particular because needs are a fundamental aspect of the human experience that governs a significant number of emotional, cognitive, and behavioral facets \citep[][]{kreienkamp2022d, kruglanski2002}.
+Importantly to the case of positive intergroup contact, need fulfillment has been highlighted in explaining the success of (close) relationships, psychosocial functioning, as well as reducing conflict between groups.
 
 On an individual psychological level, need fulfillment has a long tradition of explaining what drives human adaptation and social relations.
-From the early works of \citet[][]{maslow1943} and \citet[][]{lewin1926e} to more recent works by \citet[][]{Ryan2017} or \citet[][]{Steverink2006}, the fulfillment of needs have been considered a driver of health, well-being, and psychosocial functioning.
-Most relevant to our proposal here, within experience sampling studies (psychological) need fulfillment has been found to explain variations in general well-being \citep[e.g.,][]{sheldon1996, reis2000} as well as well-being during daily interactions \citep[][]{Downie2008}.
-The importance of need fulfillment in interactions has also been substantiated by frameworks such as 'relationships motivation theory', which has collected substantive evidence for the importance of need fulfillment in understanding the success of close relationships \citep[e.g., see][]{knee2023}.
-There is, thus, a wealth of literature highlighting the importance of need fulfillment to positive everyday experiences and well-being.
-
-Beyond the well-being and psychosocial functioning perspective, need fulfillment has recently also seen application as a psychological mechanism in the intergroup relations literature.
+From the early works of \citet[][]{maslow1943} and \citet[][]{lewin1926e} to more recent works by \citet[][]{Ryan2017} or \citet[][]{Steverink2006}, the fulfillment of needs have been considered a driver of psychosocial functioning.
+Most relevant to our proposal here, within experience sampling studies need fulfillment has been found to explain variations in well-being during daily interactions \citep[][]{Downie2008} and has been found to be important in understanding the success of close relationships \citep[e.g., see][]{knee2023}.
+In short, an extensive body of scholarly work underscores the significance of need satisfaction in fostering favorable social relationships and social functioning.
+
+Beyond the individual relations literature, need fulfillment has recently also seen application as a psychological mechanism in the intergroup relations literature.
 Social identity theory has famously focused on the role of self-esteem needs in understanding how people navigate intergroup contexts \citep[e.g.,][]{abrams1988}.
@@
 And similarly, addressing a relevant need for identity continuity among refugees in Turkey bolstered resilience in the face of discrimination experiences \citep[][]{Celebi2017}.
-Most recently, an international cross-sectional study has applied a need-based approach to the effects of positive intergroup contact.
-The study found that minority members who generally perceive their positive intergroup contacts to be more empowering tended to report a smaller reduction in social change support than those who did not perceive their average interactions as empowering, especially when the inequality between groups was perceived as illegitimate \citep[][]{Hassler2021}.
-In short, an increasing amount of literature is emphasizing the significance of need satisfaction in comprehending intergroup relations.
+In short, an increasing amount of literature is emphasizing the significance of need satisfaction in understanding intergroup dynamics.
 
@@
 6]{Dovidio2017}.
-A call that has thus far remained unanswered when it comes to the basic tenet that positive interactions drive the constructive part of intergroup contact.
+A call that has thus far remained unanswered when it comes to the basic tenet that need fulfillment underpins positive and constructive interactions.
 
@@
 Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad and diverse range of motives.
-However, while the individual need content differed between the different lines of research, what unites these approaches has been a focus on fulfilling the situationally relevant needs of people --- especially when we want to understand human functioning in social realms.
-We propose that the different lines of research share an underlying psychological mechanism, namely the motivational experience of need fulfillment.
+However, while the specific need content differed within the different lines of research, what unites most motivational researchers has been a focus on fulfilling the situationally relevant needs of people.
+This motivational experience of need fulfillment, thus, brings many of the diverse need content theories together and offers a common psychological mechanism for understanding positive intergroup contact.
+
+Here it is important to briefly define what exactly we mean by need fulfillment and how it differs from need content theories.
 With motivation and need fulfillment we specifically mean the psychological experience of addressing an active and relevant need during the interaction.
@@
 \begin{flushright}
---- based on \citet[][]{dweck2017, Hull1943, Lewin1938, McClelland1987, Ryan2017, Steverink2006}
+--- based on \citet[][]{dweck2017, Hull1943, kruglanski2002, Lewin1938, McClelland1987, Ryan2017, Steverink2006}
 \end{flushright}
@@
 It is this perceived needing and the perceived fulfillment of needs that we focus on in this article.
-This is not to say that considering specific motives is irrelevant to contact situations but instead we propose that the psychological experience of perceived need fulfillment is a core mechanism in understanding interaction quality perceptions, well-being, and outgroup attitudes.
+This is not to say that considering specific motives is irrelevant to contact situations but instead, we propose that the psychological experience of perceived need fulfillment is a core mechanism in understanding interaction quality perceptions, well-being, and outgroup attitudes.
 
@@
 \citet[][]{MacInnis2015} have even pointed out that these two approaches tend to find conflicting effects --- where individual interactions (in the lab) have more negative effects and recall of real-world contact patterns have more positive effects for intergroup relations.
-We, thus, miss data following people in their diverse daily interactions and investigates the psychological mechanisms of contacts, especially as they compound over time.
+We, thus, miss data following people in their diverse daily interactions and investigating the psychological mechanisms of contacts, especially as they compound over time.
 Even with extended intervention studies, the most fine-grained data available is usually limited to pre-post-control designs.
@@
 % aims re-iterated
-The main aim of this project was to test the basic tenets of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data and to test whether the fulfillment of situational needs meaningfully predicts positive interaction perceptions, well-being, and outgroup attitudes.
+The main aim of this project was to test the basic tenets of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data as well as to test whether the fulfillment of situational needs meaningfully predicts positive interaction perceptions and outgroup attitudes.
 
@@
 
-It should, however, be noted that the inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
+It should also be noted that the inconsistencies with past research might in part be a data artifact (e.g., because most people reported substantially more measurements during which they did not have an outgroup interaction).
 There is also a possibility that statistical power was a concern given our sample was relatively small with 207 participants and the effect of interest is an amplification interaction effect.
-However, if we assume an effect size of \textit{r} = -.21 for the effect of positive intergroup contacts \citep[see][]{Pettigrew2006} our sample size should approach the threshold of 80\% power at a .05 alpha level (sensitivity analysis in G*Power: $f^2 = 0.04$) --- especially if we consider the higher quality data we get from aggregating many real-world reports with less recall bias.
+However, if we assume an effect size of \textit{r} = -.21 for the effect of positive intergroup contacts \citep[see][]{Pettigrew2006} our sample size should be at the threshold of 80\% power with a .05 alpha level (sensitivity analysis in G*Power: $f^2 = 0.04$) --- even more so if we consider the higher quality data we get from aggregating many real-world reports with less recall bias.
 
@@
 % Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results regarding the importance of situational key needs, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions, more positive outgroup attitudes, as well as higher well-being.
-We find that in all three studies the effect of core need fulfillment on outgroup attitudes was either fully or partially assumed by the effect of interaction quality (when considering partial regression coefficients in a joint model).
-We also find that need fulfillment is an important predictor even when taking other fundamental psychological needs or Allport's conditions into account.
+Finally, when looking at the results regarding the importance of situational key need fulfillment, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions, more positive outgroup attitudes, as well as higher well-being.
+We also find that in all three studies, need fulfillment and perceived interaction quality likely shared a large part of the variance they explained in outgroup attitudes (when considering partial regression coefficients in a joint model).
+We would like to reiterate here that we specifically did not seek to test a mediation-style model.
+Even though the shared explained variance was predicted in our pre-registration based on a theoretical model, and the pattern was stable across the three studies, it is important to note that the data is none-causal, and the effect might alternatively be driven by an unobserved third variable or by multicollinearity.
+
+We, additionally, find that need fulfillment is an important predictor even when taking basic fundamental psychological needs or Allport's conditions into account.
 In fact, our core situational needs measure predicted outgroup attitudes at least as good as Allport's conditions and consistently explained more variance than commonly measured psychological needs.
@@
 However, especially for disadvantaged minority members positive outgroup attitudes may entail negative downstream consequences such as a reduced endorsement of social change --- even in the face of injustice \citep[e.g.,][]{dixon2012}.
-We have additionally tested our need-fulfillment mechanism for well-being reporst to test direct benefits of the mechanism to lived realities.
-However, we are among the first to collect intensive longitudinal data on the experience of minority migrants and it remains an open empirical question whether the more positive outgroup attitudes following need-fulfilling interactions might ironically exacerbate inequalities for the disadvantaged group.
+We have additionally tested our need-fulfillment mechanism for well-being reports to test the direct benefits of the mechanism to lived realities.
+However, we are among the first to collect intensive longitudinal data on the experience of minority migrants and it remains an open empirical question whether the more positive outgroup attitudes following need-fulfilling interactions might ironically exacerbate inequalities for the disadvantaged group \citep[also see][]{reimer2023}.
 
 Finally, our conceptualization of core situational needs has been focused on the most essential test of a motivational mechanism.
-This comes at the expense of specificity in the situational motives (i.e., we have not explored whether different types of needs have stronger effects on interaction quality and outgroup attitudes).
-Such an investigation would be possible with the adaptive measurement we used (e.g., by clustering or classifying the free text entries) but would not have been relevant to our theory–focused research question.
-Nonetheless, future research may explore which exact needs are most important in different intergroup contexts.
+This comes at the expense of specificity in the situational motives (i.e., we have not explored whether different individual motives have stronger effects on interaction quality and outgroup attitudes).
+Such an investigation would be possible with the adaptive measurement we used (e.g., by looking at the differential effects of the clustered motives) but would not have been relevant to our theory–focused research question.
+Nonetheless, future research may explore which exact motives are most important in different intergroup contexts.
 
@@
 A first implication concerns the feasibility and usefulness of extensive longitudinal data for intergroup contact research and the broader field of social psychology.
-While setting up an extensive longitudinal study is not easy, we believe the efforts to be similar to a sizable cross-sectional data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with roughly 3,000 intergroup interactions captured and over 10,000 data points in total).
+While setting up an extensive longitudinal study is not easy, we believe the efforts to be similar to a sizable cross-sectional data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with over 3,000 intergroup interactions captured and over 10,000 data points in total).
 Intensive longitudinal data, thus, opens up the possibility to explore research questions that focus on real-life phenomena outside the lab or focus on phenomena that depend on changes and influences over time.
@@
 A broader theoretical implication relates to the role of situational motivation in intergroup contacts.
-Our results offer a first promising test of psychological needs in intergroup contact.
+Our results offer a first promising test of a psychological mechanism of need fulfillment in intergroup contact.
 While our results are tentative given their novelty within the field, they were highly consistent across studies and may offer new theoretical avenues.
-Psychological needs are a facet of the human experience that has thus far been underemphasized in the intergroup contact literature.
-This stands in stark contrast of the many cognitive \citep[e.g.,][]{Pettigrew1998, Brown2005} and emotional aspects investigated within the field \citep[e.g.,][]{Stephan2008}.
+Experiences of need fulfillment are a facet of the human experience that has thus far been underemphasized in the intergroup contact literature.
+This stands in stark contrast to the many cognitive \citep[e.g.,][]{Pettigrew1998, Brown2005} and emotional aspects investigated within the field \citep[e.g.,][]{Stephan2008}.
 Future research may, therefore, be able to integrate broader theoretical frameworks of intergroup contact (e.g., motivations guiding cognition and affect, which in turn drive behavior.
 cf., theory of reasoned goal pursuit; \citealp{Ajzen2019}.
-Also see \citealp{Kreienkamp2022d}).
+Also see \citealp{kreienkamp2022d}).
 
@@
 Intergroup contact theory is among the most implemented psychological theories \citep[e.g.,][]{Pettigrew2006, AlRamiah2012a, Reimer2021}.
-Given our findings that psychological needs in everyday intergroup contacts were at least as powerful as Allport's conditions in predicting outgroup attitudes, considerations of people's needs offer a substantially more immediate mechanism to address.
+Given our findings that need fulfillment in everyday intergroup contacts was at least as powerful as Allport's conditions in predicting outgroup attitudes, considerations of people's needs offer a substantially more immediate mechanism to address.
 In cases where some or all optimal contact conditions are not possible to be fulfilled, needs offer an even more compelling alternative (e.g., where equal status is contextually not possible or in cases where people help despite a lack of institutional support).
@@
 Instead of addressing needs as a one-size fits all solution (e.g., simply focusing on competence needs), one may at times ask outgroup interaction partners what they need during an interaction.
-This is not to say that we should not explore which needs tend to be relevant to specific groups in specific intergroup contact contexts.
+This is not to say that we should not explore which motives tend to be relevant to specific groups in specific intergroup contact contexts.
 Rather, during interventions for which data on important need contents are not available or infeasible to collect, a flexible and reactive approach of inquiring momentary intergroup contact needs might be more fruitful.
@@
 Our three studies showcase the feasibility and utility of such data to test intergroup contact theory.
-We provide evidence that the fulfillment of situational psychological needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
+We provide evidence that the fulfillment of situational needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
 Our results point to motivational needs as an understudied aspect of intergroup contact that is important in understanding when and why an interaction is perceived as positive and will lead to more positive outgroup attitudes.
@@
 \begin{figure}
-  \caption{Path Diagrams Situational Needs Model across Studies}
+  \caption{Partial Regression Diagrams of Situational Needs Model across Studies}
   \label{fig:MainPaths}
@@
   \end{center}
-  \caption*{Note: \\
-  (A) Study 1; (B) Study 2; (C) Study 3.\\
-  General: Path coefficients are standardized regression coefficients.
+  \caption*{Note: Coefficients are standardized (partial) regression coefficients.
 Statistical significance markers are based on the unstandardized regression results (as presented in \tblref{tab:intergroupNeedsTblLong}).
 Note that we do not test a mediation model.
-The path diagram only illustrates the included concepts and partial regression parameters.\\
+The diagram only illustrates the included concepts and partial regression parameters.\\
   **** p < .0001, *** p < .001, ** p < .01, * p < .05}
@@
 For this we use multi-level regression analyses, predicting outgroup attitudes from outgroup interaction and non-outgroup interaction dummy variables.
-We also include the participant means as level two predictors to fully disentangle within- (level 1) and between-participant (level 2) effects of intergroup contact \citep[e.g.,][Section 4.6]{Snijders2012}.
+We also include the participant means as level two predictors to fully disentangle within- (level 1) and between-participant (level 2) effects of intergroup contact \citep[e.g.,][Section 4.6]{snijders2012}.
 
@@
 \subsection{Conclusion}
-Across the wide variety of robustness analyses, we thus find that the experience of psychological need fulfillment is a robust and flexible predictor of positive outgroup attitudes even when accounting for a range of other and even alternate predictors.
+Across the wide variety of robustness analyses, we thus find that the experience of need fulfillment is a robust and flexible predictor of positive outgroup attitudes even when accounting for a range of other and even alternate predictors.
 However, we also find that the core need fulfillment mechanism does not account for all need-related variance in outgroup attitudes.

### 2023-05-30 Methods-and-Results.Rmd
typos

@@
 After giving informed consent, participants filled in an online pre-questionnaire assessing demographics and general information about their immigration.
-Over the next thirty days, participants were invited twice a day (at 12pm and 7pm) to reflect upon their interactions, psychological need fulfillments, and current attitudes towards the Dutch outgroup.
-General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%).}.
+Over the next thirty days, participants were invited twice a day (at 12pm and 7pm) to reflect upon their interactions, situational need fulfillments, and current attitudes towards the Dutch outgroup.
+General compliance was high (`r format(round(sum(workerSampleInfo$dailiesN)/(nrow(workerSampleInfo)*62)*100,2), nsmall=2)`\% of all invited surveys were filled in)\footnote{Two participants completed only two days (among the others, participation was `r format(round(sum(workerSampleInfo$dailiesN[workerSampleInfo$dailiesN>3])/(nrow(workerSampleInfo[workerSampleInfo$dailiesN>3,])*62)*100,2), nsmall=2)`\%).
+These two participants also reported no outgroup contacts.
+These participants are removed from any analyses that focus on outgroup contacts.}.
 The response rates were approximately equal during mornings (\textit{n} = `r format(sum(workerSampleInfo$morningN), big.mark=",")`) and afternoons (\textit{n} = `r format(sum(workerSampleInfo$afternoonN), big.mark=",")`) and most measurements were completed within four hours of the invitation.
@@
 Our participants recorded between `r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% min`--`r dtWorkerSupp$workerAvFreQual$SumContactNL[dtWorkerSupp$workerAvFreQual$SumContactNL > 0] %>% max`
-interactions with Dutch outgroup members (`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtWorkerSupp$workerAvFreQual$SumContactNL), big.mark=",")` of all `r format(nrow(dtWorkerSupp$workerInteractionType), big.mark=",")` experience sampling responses)\footnote{Two participants only recorded two experience sampling measurements each and none of these included outgroup contacts.
-These participants are removed from any analyses that focus on outgroup contacts.}.
-
-\paragraph{Psychological Needs}Irrespective of whether participants had an interaction with Dutch people or not, everyone answered a short series of questions on psychological need fulfillment.
+interactions with Dutch outgroup members ($M$ = `r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% mean %>% round(2) %>% format(nsmall=2)`\%, $SD$ = `r dtWorkerSupp$workerAvFreQual$PercContactNL[dtWorkerSupp$workerAvFreQual$PercContactNL > 0] %>% sd %>% round(2) %>% format(nsmall=2)`\% of the individuals' experience sampling measurements; `r format(sum(dtWorkerSupp$workerAvFreQual$SumContactNL), big.mark=",")` of all `r format(nrow(dtWorkerSupp$workerInteractionType), big.mark=",")` experience sampling responses)Two participants only recorded two experience sampling measurements each and none of these included outgroup contacts.
+These participants are removed from any analyses that focus on outgroup contacts.
+
+\paragraph{Need Fulfillment}Irrespective of whether participants had an interaction with Dutch people or not, everyone answered a short series of questions on situational need fulfillment.
 However, whereas participants with interactions reported on the need fulfillment during the interaction, people without interactions with Dutch people judged the past daytime period in general.
-To assess the fulfillment of psychological needs, we included two types of need measurement: (1) the core situational need and (2) general self-determination theory needs.
+To assess the fulfillment of needs, we included two types of need measurement: (1) the core situational need and (2) general self-determination theory needs.
 
@@
 Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50).
-The self-determination theory need measurements are described in \appref{app:AppendixRobustness}.
-
-\paragraph{Perceived Interaction Quality}As an explanatory mechanism, we assessed ratings of the perceived interaction quality.
-As our main measurement, participants rated the statement “\textit{Overall the interaction was …}” on two continuous slider scales measuring pleasantness \citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
-
-\paragraph{Outgroup Attitudes}At the end of every experience sampling measurement, we asked all participants about their current attitudes towards the Dutch – our main dependent variable.
+The self-determination theory need measurements were collected for robustness analyses and are described in \appref{app:AppendixRobustness}.
+
+\paragraph{Perceived Interaction Quality}To assess ratings of the perceived interaction quality, participants rated the statement “\textit{Overall the interaction was …}” on two continuous slider scales measuring pleasantness \citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
+
+\paragraph{Outgroup Attitudes}At the end of every experience sampling measurement, we asked all participants about their current attitudes towards the Dutch.
 To assess the momentary outgroup evaluation we used the common feeling thermometer: “How favorable do you feel towards the Dutch?” \citep[][]{Lavrakas2008}.
@@
 This is unusual and might indicate that the effect is very consistent across participants.
-However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}.
+However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analysis as part of our stability analyses.}.
 Thus, in our first data, we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data.
 
-\subsubsection{Core Need}
+\subsubsection{Core Need Fulfillment}
 ```{r workerOutModelMLAttNull, include=FALSE}
@@
 The main proposal of our article is that the success of an outgroup contact might be explained by whether or not the contact fulfilled the person's core situational need.
-This should, in turn, be due to a higher perceived contact quality.
+This should, in turn, be reflected in higher perceived contact quality and more positive outgroup attitudes.
 We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived contact quality, and (3) whether the variance explained by the core need is subsumed by the perceived contact quality if considered jointly.
-We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCore, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreCI, varName = "keymotive_fulfillemt_1_cwc")`) and also predicted higher perceived contact quality (random intercept model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Qlt$lmeInterceptCore, lmerCI = mdlWorkerOut$Qlt$lmerInterceptCoreCI, varName = "keymotive_fulfillemt_1_cwc")`).
-Moreover, when we consider the influences of core need fulfillment and contact quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived contact quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`, also see \fgrref[-A]{fig:MainPaths}).
+We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCore, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreCI, varName = "keymotive_fulfillemt_1_cwc")`) and also related to higher perceived contact quality (random intercept model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Qlt$lmeInterceptCore, lmerCI = mdlWorkerOut$Qlt$lmerInterceptCoreCI, varName = "keymotive_fulfillemt_1_cwc")`).
+Moreover, when we consider the influences of core need fulfillment and contact quality on outgroup attitudes jointly, we find that the two predictors share a large part of the variance explained in outgroup attitudes, so that perceived contact quality showed a strong effect on outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`, also see \fgrref[-A]{fig:MainPaths}).
 We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes.
-Additionally, this effect is likely explained by its effect through perceived contact quality.
+Additionally, this effect seemingly addresses the same variance that is accounted for by perceived contact quality.
 
@@
 The participants recorded between `r dtStudentSupp$studentContactFreq$SumContactNL[dtStudentSupp$studentContactFreq$SumContactNL > 0] %>% min`--`r dtStudentSupp$studentContactFreq$SumContactNL %>% max`
-interactions with Dutch majority people (`r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtStudentSupp$studentContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtStudentSupp$studentContactFreq$SumContactNL), big.mark=",")` of all `r format(nrow(dtStudentSupp$studentInteractionType), big.mark=",")` experience sampling responses).
-
-\paragraph{Psychological Needs}For the core situational need, we asked participants in an open-ended text field: “\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}” (where \textit{-X-} was dynamically replaced with the name of the interaction partner).
+interactions with Dutch majority people ($M$ = `r dtStudentSupp$studentContactFreq$PercContactNL[dtStudentSupp$studentContactFreq$PercContactNL > 0] %>% mean %>% round(2) %>% format(nsmall=2)`\%, $SD$ = `r dtStudentSupp$studentContactFreq$PercContactNL %>% sd %>% round(2) %>% format(nsmall=2)`\% of the individual's experience sampling measurements; `r format(sum(dtStudentSupp$studentContactFreq$SumContactNL), big.mark=",")` of all `r format(nrow(dtStudentSupp$studentInteractionType), big.mark=",")` experience sampling responses).
+
+\paragraph{Need Fulfillment}For the core situational need, we asked participants in an open-ended text field: “\textit{What was your main goal [during the interaction with -X- / this morning / this afternoon]?}” (where \textit{-X-} was dynamically replaced with the name of the interaction partner).
 Participants could additionally click on a pop-up explanation: "Your main goal during an interaction can vary depending on the interaction.
@@
 Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{During your interaction with -X- [this morning / this evening] your goal (-previous text entry-) was fulfilled.}” on a continuous slider scale ranging from strongly disagree (1) to strongly agree (100).
+See \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide} for descriptive statistics.
 
@@
 
-\subsubsection{Core Need}
+\subsubsection{Core Need Fulfillment}
 ```{r studentOutModelMLAttNull, include=FALSE}
@@
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`).
-Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see \fgrref[-B]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for full results).
+Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we again find that much of the explained variance is shared by the predictor variables, so that perceived interaction quality remains a strong predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see \fgrref[-B]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for full results).
 These results are consistent with the results in Study 1.
-We, thus, find support for our hypotheses that the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.
-
-<!-- \faQuestionCircle\ Are we sure that we don't want some sort of bootstrapped indirect effect?  -->
+We, thus, find support for our hypotheses that the fulfillment of core situational needs had a significant influence on perceived interaction quality and outgroup attitudes.
 
@@
 
-\subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, in that it consisted of pre-, experience sampling-, and post-measurement.
-The participants were invited for experience sampling measurements twice a day (at 12pm and 7pm) for 30 days.
+\subsubsection{Procedure} The study procedure mirrored the setup of studies one and two, and included the same pre-, experience sampling-, and post-measurement phases.
+The participants were invited for experience sampling measurements twice a day (at 12pm and 7pm) for at least 30 days.
 General compliance was high (`r format(round(table(medicalSampleInfo$dailiesN>30)["TRUE"]/nrow(medicalSampleInfo)*100,2), nsmall=2)`\% filled in at least 31 experience sampling surveys or more).
@@
 The participants recorded between `r dtMedicalSupp$medicalContactFreq$SumContactNL[dtMedicalSupp$medicalContactFreq$SumContactNL > 0] %>% min`--`r dtMedicalSupp$medicalContactFreq$SumContactNL %>% max` interactions with Dutch outgroup members
-(`r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% min %>% round(2) %>% format(nsmall=2)`--`r dtMedicalSupp$medicalContactFreq$PercContactNL %>% max %>% round(2) %>% format(nsmall=2)`\% of individual experience sampling measurements; `r format(sum(dtMedicalSupp$medicalContactFreq$SumContactNL), big.mark=",")` of all `r format(nrow(dtMedical$full), big.mark=",")` experience sampling responses).
+($M$ = `r dtMedicalSupp$medicalContactFreq$PercContactNL[dtMedicalSupp$medicalContactFreq$PercContactNL > 0] %>% mean %>% round(2) %>% format(nsmall=2)`\%, $SD$ = `r dtMedicalSupp$medicalContactFreq$PercContactNL %>% sd %>% round(2) %>% format(nsmall=2)`\% of the individuals' experience sampling measurements; `r format(sum(dtMedicalSupp$medicalContactFreq$SumContactNL), big.mark=",")` of all `r format(nrow(dtMedical$full), big.mark=",")` experience sampling responses).
 
@@
 \subsubsection{Contact Hypothesis}
-In a multilevel regression, we find that having an outgroup interaction was again associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong} and \fgrref{fig:ContactHypothesis}).
+In a multilevel regression, we find that having an outgroup interaction was again associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having a non-Dutch interaction (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong} and \fgrref{fig:ContactHypothesis}).
 Thus, in our third data set, we find that the within-person contemporaneous effect of intergroup contact was consistent across all three studies.
 
-\subsubsection{Core Need}
+\subsubsection{Core Need Fulfillment}
 
@@
 Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; also see \fgrref[-C]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for full results).
-As with the previous two studies, these results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and the results suggest that this might be due to higher perceived interaction quality.
+As with the previous two studies, these results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and the results suggest that this explained variance is shared with perceived interaction quality.
 
@@
 Moreover, when we considered the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we found that perceived interaction quality was a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}).
-These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.
+These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, related to the effect of perceived interaction quality.
 
@@
 Additionally, when considering the predictors jointly, we find that both significantly predict outgroup attitudes with similar-sized regression parameters (random slopes model; Allport's Conditions: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "AllportsCondition_cwc")`, Core Need: `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreAllportCI, varName = "KeyNeedFulfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}).
-This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) work through perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
+This indicates that, although both Allport's conditions and the core need fulfillment seem to (in part) relate to perceived interaction quality, they explain different aspects of the variance in outgroup attitudes and do not constitute one another.
 
@@
 When looking at the fulfillment of core needs during intergroup contacts, we find that the motivational mechanism is consistently a meaningful predictor of  interaction quality perceptions and outgroup attitudes (see \fgrref[ A and B]{fig:AllportNeedFulfillment}).
-We also see that the effect of core need fulfillment on outgroup attitudes is strongly reduced when modeled together with interaction quality perceptions, supporting our assertion that interaction quality offers a psychological mechanism for the direct effect (see \fgrref[-C]{fig:AllportNeedFulfillment}).
+We also see that the effect of core need fulfillment on outgroup attitudes is strongly reduced when modeled together with interaction quality perceptions, supporting our assertion that interaction quality and need fulfillment share the same variance explained in outgroup attitudes (see \fgrref[-C]{fig:AllportNeedFulfillment}).
+Note that this joint effect is not meant to resemble a mediation analysis.
+Particularly, since the data is non-causal, and because multicollinearity and potential third variables could result in similar results.
 
@@
 During the main analyses, we have thus far shown that participants held more positive outgroup attitudes following intergroup contacts and that perceived interaction quality was associated with more positive outgroup attitudes following an intergroup contact.
-We have, however, not brought the two elements of the contact hypothesis together in a single analysis.
+We have, however, not brought the two quantity and quality elements of the contact hypothesis together in a single analysis.
 To jointly test the effects of contact frequency and average interaction quality, we ran a linear regression model where average outgroup attitudes were predicted by the number of interactions and the average interaction quality ratings of all participants across the three studies.
@@
 To check for spurious relationships, we test three additional models.
-These three models assess whether the effect is indeed specific to intergroup contact, whether the need fulfillment effect is a affected by whether the contact was planned or accidental, and whether the motivational mechanism also holds direct well-being benefits for the minority members.
+These three models assess whether the effect is indeed specific to intergroup contact, whether the need fulfillment effect is a affected by whether the contact was planned or accidental, and whether the motivational mechanism also holds for direct well-being benefits for the minority members.
 We describe the full methods and results for the robustness analyses in \appref{app:AppendixRobustness}.
@@
 When assessing the individual studies independently, we additionally find a strong main effect of contact as well as a smaller main effect of key need fulfillment, qualifying the contact-specific relationship (see \appref{app:AppendixRobustness} for full results).
-In sum, we thus find that at the effect of key need fulfillment on outgroup attitudes is particularly important for outgroup interactions (rather than only need fulfillment in general).
+In sum, we thus find that at the effect of key need fulfillment on outgroup attitudes is particularly important for outgroup interactions (rather than need fulfillment in general).
 
@@
 It should be noted that, in order to keep the ESM surveys short, we asked our participants to focus on most the important interaction (i.e., "\textit{The following questions will be about the interaction \underline{you consider most significant}.}"; emphasis as in original).
-This was also reflected in a relatively low average and consistent right skew of the 'accidental' item.
+This was also reflected in a relatively low mean and consistent right skew of the 'accidental' item.
 Nonetheless, there remained a substantial variance in the item and we continued with the moderation analysis.
@@
 To ensure that our results are not impacted by differences in the reported goals and motives, we additionally coded the topics we extracted during the topic modeling on two dimensions of how much they reflect a practical and a psychological goal-directedness.
-We chose practical and psychological needs specifically as our dimensions to account for differences in the types of needs that participants commonly reported.
+We chose practical and psychological needs specifically as our dimensions to mirror our instructions to the participants and to account for differences in the types of needs that participants commonly reported.
 With practical motives we refer to specific, tangible goals or tasks that participants aimed to accomplish during the interaction.
@@
 Note that with this approach any particular motive can include a practical and/or a psychological goal-directedness but can also be classified as not having any goal at all.
+See Supplemental Materials D for the detailed coding protocol, including instructions for the coders.
 We found high inter-rater reliability for the two independent coders, who coded all 47 topics.
@@
 \subsubsection{Specific psychological needs}
-Finally, to ensure that a much simpler model of three fundamental psychological needs might not account for the same effect, we compared our situation core need fulfillment measurement to the three self-determination theory needs (autonomy, relatedness, competence).
+Finally, to ensure that a much simpler model of three fundamental psychological needs might not account for the same effect, we compared our situation core need fulfillment measurement to the commonly studied self-determination theory needs (autonomy, relatedness, competence).
 Within the overall model we found that across the studies core need fulfillment remained a strong predictor of outgroup attitudes, even after controlling for the three self-determination theory need.
-Additionally, within this overall analysis, none of the self-determination theory needs independently predicted outgroup attitudes to a statistically significant extent (despite similar effect sizes of relatedness).
+Additionally, within this overall analysis, none of the self-determination theory needs independently predicted outgroup attitudes to a statistically significant extent (despite a similar effect size of relatedness).
 When looking at the individual studies, we again saw that core need fulfillment remained a consistent predictor of outgroup attitudes.
@@
 None of the autonomy fulfillment effects reached statistical significance.
-In short, find that across our samples, relatedness fulfillment (and to a smaller extend competence fulfillment) are instrumental in understanding when an outgroup contact leads to more positive outgroup attitudes.
+In short, we find that across our samples, relatedness fulfillment (and to a smaller extend competence fulfillment) are instrumental in understanding when an outgroup contact leads to more positive outgroup attitudes.
 Importantly, even when considering these effects situational core need fulfillment remains a strong and consistent predictor of outgroup attitudes.
+
+Overall, we find that our situation need fulfillment model is consistent across samples and contexts, and that the need fulfillment effect is robust to a wide variety of alternate explanations.
 

### 2023-05-30 Robustness-Methods-and-Results.Rmd
typo
typos

@@
 With practical motives we refer to specific, tangible goals or tasks that participants aimed to accomplish during the interaction.
-These instrumental goals are usually observable, concrete, and often centered on external outcomes, such as acquiring resources, completing tasks, and addressing immediate challenges \citep[][]{}.
+These instrumental goals are usually observable, concrete, and often centered on external outcomes, such as acquiring resources, completing tasks, and addressing immediate challenges \citep[e.g.,][]{oduntan2019}.
 With psychological motives we refer to underlying motives or desires that are more abstract and relate to personal fulfillment and well-being.
 In contrast to practical needs, psychological needs delve into the subjective and internal aspects of human experiences.
-These needs pertain to emotions, social connections, and cognitive processes, reflecting individuals' quest for personal growth, well-being, and thriving in social relationships \citep[][]{}.
+These needs pertain to emotions, social connections, and cognitive processes, reflecting individuals' quest for personal growth, well-being, and thriving in social relationships \citep[][]{dweck2017}.
 Note that with this approach any particular motive can include a practical and/or a psychological goal-directedness but can also be classified as not having any goal at all.
@@
 Secondly, to assess whether the need fulfillment mechanism affected by whether the interaction was accidental or planned we ran an exploratory moderation analysis using the participants' ratings of how much they perceived the interaction as 'accidental'.
-It should be noted that we asked our participants to focus on most the important interaction (i.e., "\textit{The following questions will be about the interaction \underline{you consider most significant}.}"''"; emphasis as in original).
+It should be noted that we asked our participants to focus on most the important interaction (i.e., "\textit{The following questions will be about the interaction \underline{you consider most significant}.}"; emphasis as in original).
 We again start our analysis approach by assessing the model across all three studies, using a three-level hierarchical model.
@@
 
-\paragraph{overall}
 ```{r}
@@
 
-\paragraph{Study follow-up}
 ```{r}

### 2023-05-30 manuscript.tex
feedback KE

@@
 
-On an individual psychological level, need fulfillment has a long tradition of explaining what drives human adaptation and social relations.
+On an individual psychological level, there is a long tradition of using need fulfillment to explain what drives human adaptation and social relations.
 From the early works of \citet[][]{maslow1943} and \citet[][]{lewin1926e} to more recent works by \citet[][]{Ryan2017} or \citet[][]{Steverink2006}, the fulfillment of needs have been considered a driver of psychosocial functioning.
@@
 Beyond the individual relations literature, need fulfillment has recently also seen application as a psychological mechanism in the intergroup relations literature.
-Social identity theory has famously focused on the role of self-esteem needs in understanding how people navigate intergroup contexts \citep[e.g.,][]{abrams1988}.
+Social identity theory has focused on the role of self-esteem needs in understanding how people navigate intergroup contexts \citep[e.g.,][]{abrams1988}.
 In the study of conflict and reconciliation, addressing differential needs of victims and perpetrators (i.e., the need for power and the need for morality respectively) increased willingness to reconcile \citep[][]{Shnabel2008}.
@@
 Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad and diverse range of motives.
-However, while the specific need content differed within the different lines of research, what unites most motivational researchers has been a focus on fulfilling the situationally relevant needs of people.
+However, while the specific need content differed within the different lines of research, what unites most motivational researchers is a focus on fulfilling the situationally relevant needs of people.
 This motivational experience of need fulfillment, thus, brings many of the diverse need content theories together and offers a common psychological mechanism for understanding positive intergroup contact.
@@
 One key decision for our studies has been to focus on the minority experience during the contact.
-While the same mechanisms should hold for the experience of members in high-powered groups, there is substantially more research available that focuses on the experience of the majority group, and minority perspectives are historically often understudied \citep[e.g.,][]{Dovidio2017}.
+While the same mechanisms should hold for the experience of members in high-power groups, there is substantially more research available that focuses on the experience of the majority group, and minority perspectives are historically often understudied \citep[e.g.,][]{Dovidio2017}.
 At the same time, however, minority groups are often underprivileged and research is direly needed to understand the more prevalent experiences of stress and health issues among minorities \citep[e.g.,][]{alvidrez2019}.
@@
 As the methodology is relatively new to the field, we sought to first replicate (and then extend) the most reliable effects of the contact hypothesis within the ESM data.
-Outgroup attitudes are, however, not without controversy, especially for minority group members' intergroup contact.
-In particular, positive outgroup attitudes have been shown to increase harmony and reduce the willingness to support social change among the disadvantaged in some cases --- even in the face of injustice \citep[e.g.,][]{dixon2012, saguy2009}.
+Outgroup attitudes are, however, not without controversy, especially for minority group members.
+Positive outgroup attitudes can increase harmony and reduce the willingness to support social change among the disadvantaged in some cases --- even in the face of injustice \citep[e.g.,][]{dixon2012, saguy2009}.
 While a recent review found the effect to be less conclusive for longitudinally collected data and less consistent for positive interactions (rather than interactions generally), the backfire effect remains an important possibility for the present data \citep[see][]{reimer2023}.

### 2023-05-30 Methods-and-Results.Rmd
re-render

@@
     id = "PID",
-    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "quality_overall_1", "thermometerDutch_1"),
+    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "interaction_quality", "thermometerDutch_1"),
     labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
@@
     id = "PID",
-    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "quality_overall_1", "thermometerDutch_1"),
+    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "interaction_quality", "thermometerDutch_1"),
     labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
@@
     AvAttitude_c = AvAttitude - mean(AvAttitude, na.rm = TRUE),
-    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE)
+    AvQuality_c = AvQuality - mean(AvQuality, na.rm = TRUE),
+    AvQualityComb_c = AvQualityComb - mean(AvQualityComb, na.rm = TRUE)
   )
@@
 pairs.panels.new(
-  dtWorkerSupp$workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  dtWorkerSupp$workerAvFreQual %>% select(SumContactNL, SumContactNLAll, AvQualityComb, AvAttitude),
   labels = c(
@@
 pairs.panels.new(
-  dtWorkerSupp$workerAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  dtWorkerSupp$workerAvFreQual %>% select(WinSumContactNL, WinSumContactNLAll, AvQualityComb, AvAttitude),
   labels = c(
@@
 rAttitudeQuality <- dtWorkerSupp$workerAvFreQual %>% 
-  select(AvQuality, AvAttitude) %>%
+  select(AvQualityComb, AvAttitude) %>%
   as.matrix %>%
@@
 mdlWorker$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtWorkerSupp$workerAvFreQual)
+  lm(AvAttitude ~ SumContactNL_c * AvQualityComb_c, data = dtWorkerSupp$workerAvFreQual)
 # summary(lmWorkerAttFreqQualX)
@@
   mdlWorker$lmAttFreqQualX,
-  pred = AvQuality_c,
+  pred = AvQualityComb_c,
   modx = SumContactNL_c,
@@
 interactions::johnson_neyman(mdlWorker$lmAttFreqQualX,
-                             pred = AvQuality_c,
+                             pred = AvQualityComb_c,
                              modx = SumContactNL_c,
@@
 mdlWorkerOut$Qlt$lmerNull <-
-  lme4::lmer(quality_overall_1 ~ 1 + (1 | PID), 
+  lme4::lmer(interaction_quality ~ 1 + (1 | PID), 
              data = dtWorkerSupp$workerOutWithinBetween) # use optim if it does not converge
@@
   mdlWorkerOut$Qlt$lmeNull <- lme(
-    quality_overall_1 ~ 1,
+    interaction_quality ~ 1,
     random = ~ 1 | PID,
@@
   lme(
-    quality_overall_1 ~ keymotive_fulfillemt_1_cwc,
+    interaction_quality ~ keymotive_fulfillemt_1_cwc,
     random = ~ 1 | PID,
@@
     lmer(
-      quality_overall_1 ~ keymotive_fulfillemt_1_cwc + (1 | PID),
+      interaction_quality ~ keymotive_fulfillemt_1_cwc + (1 | PID),
       data = dtWorkerSupp$workerOutWithinBetween
@@
   lme(
-    quality_overall_1 ~
+    interaction_quality ~
       keymotive_fulfillemt_1_cwc,
@@
     lmer(
-      quality_overall_1 ~
+      interaction_quality ~
         keymotive_fulfillemt_1_cwc +
@@
   lme(
-    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + quality_overall_1_cwc,
+    thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + interaction_quality_cwc,
     random = ~ 1 | PID,
@@
     lmer(
-      thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + quality_overall_1_cwc + (1 | PID),
+      thermometerDutch_1 ~ keymotive_fulfillemt_1_cwc + interaction_quality_cwc + (1 | PID),
       data = dtWorkerSupp$workerOutWithinBetween
@@
     thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc + quality_overall_1_cwc,
-    random = ~ 1 + keymotive_fulfillemt_1_cwc + quality_overall_1_cwc | PID,
+      keymotive_fulfillemt_1_cwc + interaction_quality_cwc,
+    random = ~ 1 + keymotive_fulfillemt_1_cwc + interaction_quality_cwc | PID,
     control = lmeControl(opt = "optim"),
@@
     thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc + quality_overall_1_cwc +
-      (1 + keymotive_fulfillemt_1_cwc + quality_overall_1_cwc | PID),
+      keymotive_fulfillemt_1_cwc + interaction_quality_cwc +
+      (1 + keymotive_fulfillemt_1_cwc + interaction_quality_cwc | PID),
     data = dtWorkerSupp$workerOutWithinBetween
@@
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCore, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreCI, varName = "keymotive_fulfillemt_1_cwc")`) and also related to higher perceived contact quality (random intercept model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Qlt$lmeInterceptCore, lmerCI = mdlWorkerOut$Qlt$lmerInterceptCoreCI, varName = "keymotive_fulfillemt_1_cwc")`).
-Moreover, when we consider the influences of core need fulfillment and contact quality on outgroup attitudes jointly, we find that the two predictors share a large part of the variance explained in outgroup attitudes, so that perceived contact quality showed a strong effect on outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_1_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`, also see \fgrref[-A]{fig:MainPaths}).
+Moreover, when we consider the influences of core need fulfillment and contact quality on outgroup attitudes jointly, we find that the two predictors share a large part of the variance explained in outgroup attitudes, so that perceived contact quality showed a strong effect on outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "interaction_quality_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlWorkerOut$Att$lmeSlopesCoreQlt, lmerCI = mdlWorkerOut$Att$lmerSlopesCoreQltCI, varName = "keymotive_fulfillemt_1_cwc")`, also see \fgrref[-A]{fig:MainPaths}).
 We thus find support for our hypotheses and can conclude that in this data set the fulfillment of core situational needs had a significant influence on outgroup attitudes.
@@
     id = "PID",
-    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "quality_overall", "AttitudesDutch"),
+    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
     labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
@@
 pairs.panels.new(
-  dtStudentSupp$studentContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  dtStudentSupp$studentContactFreq %>% select(SumContactNL, SumContactNLAll, AvQualityComb, AvAttitude),
   labels = c(
@@
 pairs.panels.new(
-  dtStudentSupp$studentContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  dtStudentSupp$studentContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQualityComb, AvAttitude),
   labels = c(
@@
 mdlStudent$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtStudentSupp$studentContactFreq)
+  lm(AvAttitude ~ SumContactNL_c * AvQualityComb_c, data = dtStudentSupp$studentContactFreq)
 
@@
   pred = SumContactNL_c,
-  modx = AvQuality_c,
+  modx = AvQualityComb_c,
   interval = TRUE,
@@
                              pred = SumContactNL_c,
-                             modx = AvQuality_c,
+                             modx = AvQualityComb_c,
                              alpha = .05)
@@
 mdlStudentOut$Qlt$lmerNull <-
-  lme4::lmer(quality_overall ~ 1 + (1 | PID), 
+  lme4::lmer(interaction_quality ~ 1 + (1 | PID), 
              data = dtStudentSupp$studentOutWithinBetween) # use optim if it does not converge
@@
   mdlStudentOut$Qlt$lmeNull <-lme(
-    quality_overall ~ 1,
+    interaction_quality ~ 1,
     random = ~ 1 | PID,
@@
   lme(
-    quality_overall ~ KeyNeedFullfillment_cwc,
+    interaction_quality ~ KeyNeedFullfillment_cwc,
     random = ~ 1 | PID,
@@
     lmer(
-      quality_overall ~ KeyNeedFullfillment_cwc + (1 | PID),
+      interaction_quality ~ KeyNeedFullfillment_cwc + (1 | PID),
       data = dtStudentSupp$studentOutWithinBetween
@@
   lme(
-    quality_overall ~
+    interaction_quality ~
       KeyNeedFullfillment_cwc,
@@
     lmer(
-      quality_overall ~
+      interaction_quality ~
         KeyNeedFullfillment_cwc +
@@
   lme(
-    AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc,
+    AttitudesDutch ~ KeyNeedFullfillment_cwc + interaction_quality_cwc,
     random = ~ 1 | PID,
@@
     lmer(
-      AttitudesDutch ~ KeyNeedFullfillment_cwc + quality_overall_cwc + (1 | PID),
+      AttitudesDutch ~ KeyNeedFullfillment_cwc + interaction_quality_cwc + (1 | PID),
       data = dtStudentSupp$studentOutWithinBetween
@@
     AttitudesDutch ~
-      KeyNeedFullfillment_cwc + quality_overall_cwc,
-    random = ~ 1 + KeyNeedFullfillment_cwc + quality_overall_cwc | PID,
+      KeyNeedFullfillment_cwc + interaction_quality_cwc,
+    random = ~ 1 + KeyNeedFullfillment_cwc + interaction_quality_cwc | PID,
     control = lmeControl(opt = "optim"),
@@
     AttitudesDutch ~
-      KeyNeedFullfillment_cwc + quality_overall_cwc +
-      (1 + KeyNeedFullfillment_cwc + quality_overall_cwc | PID),
+      KeyNeedFullfillment_cwc + interaction_quality_cwc +
+      (1 + KeyNeedFullfillment_cwc + interaction_quality_cwc | PID),
     data = dtStudentSupp$studentOutWithinBetween,
@@
 We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`).
-Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we again find that much of the explained variance is shared by the predictor variables, so that perceived interaction quality remains a strong predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see \fgrref[-B]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for full results).
+Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we again find that much of the explained variance is shared by the predictor variables, so that perceived interaction quality remains a strong predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "interaction_quality_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see \fgrref[-B]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for full results).
 These results are consistent with the results in Study 1.
@@
     id = "PID",
-    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "qualityOverall", "AttitudesDutch"),
+    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "interaction_quality", "AttitudesDutch"),
     labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
@@
 pairs.panels.new(
-  dtMedicalSupp$medicalContactFreq %>% select(SumContactNL, SumContactNLAll, AvQuality, AvAttitude),
+  dtMedicalSupp$medicalContactFreq %>% select(SumContactNL, SumContactNLAll, AvQualityComb, AvAttitude),
   labels = c(
@@
 pairs.panels.new(
-  dtMedicalSupp$medicalContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQuality, AvAttitude),
+  dtMedicalSupp$medicalContactFreq %>% select(WinSumContactNL, WinSumContactNLAll, AvQualityComb, AvAttitude),
   labels = c(
@@
 mdlMedical$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)
+  lm(AvAttitude ~ SumContactNL_c * AvQualityComb_c, data = dtMedicalSupp$medicalContactFreq)
 
@@
 mdlMedicalOut$Qlt$lmerNull <-
-  lme4::lmer(qualityOverall ~ 1 + (1 | PID), 
+  lme4::lmer(interaction_quality ~ 1 + (1 | PID), 
              data = dtMedicalSupp$medicalOutWithinBetween) # use optim if it does not converge
@@
   mdlMedicalOut$Qlt$lmeNull <-lme(
-    qualityOverall ~ 1,
+    interaction_quality ~ 1,
     random = ~ 1 | PID,
@@
   lme(
-    qualityOverall ~ KeyNeedFulfillment_cwc,
+    interaction_quality ~ KeyNeedFulfillment_cwc,
     random = ~ 1 | PID,
@@
     lmer(
-      qualityOverall ~ KeyNeedFulfillment_cwc + (1 | PID),
+      interaction_quality ~ KeyNeedFulfillment_cwc + (1 | PID),
       data = dtMedicalSupp$medicalOutWithinBetween
@@
   lme(
-    qualityOverall ~
+    interaction_quality ~
       KeyNeedFulfillment_cwc,
@@
     lmer(
-      qualityOverall ~
+      interaction_quality ~
         KeyNeedFulfillment_cwc +
@@
   lme(
-    AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc,
+    AttitudesDutch ~ KeyNeedFulfillment_cwc + interaction_quality_cwc,
     random = ~ 1 | PID,
@@
     lmer(
-      AttitudesDutch ~ KeyNeedFulfillment_cwc + qualityOverall_cwc + (1 | PID),
+      AttitudesDutch ~ KeyNeedFulfillment_cwc + interaction_quality_cwc + (1 | PID),
       data = dtMedicalSupp$medicalOutWithinBetween
@@
     AttitudesDutch ~
-      KeyNeedFulfillment_cwc + qualityOverall_cwc,
-    random = ~ 1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID,
+      KeyNeedFulfillment_cwc + interaction_quality_cwc,
+    random = ~ 1 + KeyNeedFulfillment_cwc + interaction_quality_cwc | PID,
     na.action = na.omit,
@@
     AttitudesDutch ~
-      KeyNeedFulfillment_cwc + qualityOverall_cwc +
-      (1 + KeyNeedFulfillment_cwc + qualityOverall_cwc | PID),
+      KeyNeedFulfillment_cwc + interaction_quality_cwc +
+      (1 + KeyNeedFulfillment_cwc + interaction_quality_cwc | PID),
     data = dtMedicalSupp$medicalOutWithinBetween,
@@
   dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
+  filter(complete.cases(KeyNeedFulfillment, interaction_quality)) %>%
   filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
@@
                            dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(KeyNeedFulfillment, qualityOverall)) %>%
+                             filter(complete.cases(KeyNeedFulfillment, interaction_quality)) %>%
                              filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
@@
 We find that the fulfillment of the core need during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`).
-Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; also see \fgrref[-C]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for full results).
+Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "interaction_quality_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; also see \fgrref[-C]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for full results).
 As with the previous two studies, these results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and the results suggest that this explained variance is shared with perceived interaction quality.
@@
   lme(
-    qualityOverall ~ AllportsCondition_cwc,
+    interaction_quality ~ AllportsCondition_cwc,
     random = ~ 1 | PID,
@@
     lmer(
-      qualityOverall ~ AllportsCondition_cwc + (1 | PID),
+      interaction_quality ~ AllportsCondition_cwc + (1 | PID),
       data = dtMedicalSupp$medicalOutWithinBetween
@@
   lme(
-    qualityOverall ~
+    interaction_quality ~
       AllportsCondition_cwc,
@@
     lmer(
-      qualityOverall ~
+      interaction_quality ~
         AllportsCondition_cwc +
@@
   lme(
-    AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc,
+    AttitudesDutch ~ AllportsCondition_cwc + interaction_quality_cwc,
     random = ~ 1 | PID,
@@
     lmer(
-      AttitudesDutch ~ AllportsCondition_cwc + qualityOverall_cwc + (1 | PID),
+      AttitudesDutch ~ AllportsCondition_cwc + interaction_quality_cwc + (1 | PID),
       data = dtMedicalSupp$medicalOutWithinBetween
@@
     AttitudesDutch ~
-      AllportsCondition_cwc + qualityOverall_cwc,
-    random = ~ 1 + AllportsCondition_cwc + qualityOverall_cwc | PID,
+      AllportsCondition_cwc + interaction_quality_cwc,
+    random = ~ 1 + AllportsCondition_cwc + interaction_quality_cwc | PID,
     na.action = na.omit,
@@
     AttitudesDutch ~
-      AllportsCondition_cwc + qualityOverall_cwc +
-      (1 + AllportsCondition_cwc + qualityOverall_cwc | PID),
+      AllportsCondition_cwc + interaction_quality_cwc +
+      (1 + AllportsCondition_cwc + interaction_quality_cwc | PID),
     data = dtMedicalSupp$medicalOutWithinBetween,
@@
   dtMedicalSupp$medicalOutWithinBetween %>% 
-  filter(complete.cases(AllportsCondition, qualityOverall)) %>%
+  filter(complete.cases(AllportsCondition, interaction_quality)) %>%
   filter(PID %in% dtMedicalSupp$medicalOutPltIDs) %>%
@@
                            dtMedicalSupp$medicalOutWithinBetween %>% 
-                             filter(complete.cases(AllportsCondition, qualityOverall)) %>%
+                             filter(complete.cases(AllportsCondition, interaction_quality)) %>%
                              filter(PID %in% dtMedicalSupp$medicalOutPltIDs),
@@
 In the multilevel models, we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`).
-Moreover, when we considered the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we found that perceived interaction quality was a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}).
+Moreover, when we considered the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we found that perceived interaction quality was a substantially stronger predictor (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "interaction_quality_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong}).
 These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, related to the effect of perceived interaction quality.
@@
   lm(
-    AvAttitude ~ SumContactNL_c * AvQualityOut_c + SumContactNL_c * study2 + AvQualityOut_c * study2,
+    AvAttitude ~ SumContactNL_c * AvQualityCombOut_c + SumContactNL_c * study2 + AvQualityCombOut_c * study2,
     data = avAll
@@
 Looking at the individual effects, we found that only the number of outgroup interactions has a clear association with average outgroup attitudes (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "SumContactNL_c", ci = TRUE)`).
-The average interaction quality perceptions had a much smaller effect (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "AvQualityOut_c", ci = TRUE)`), and importantly we found no interaction effect at all.
+The average interaction quality perceptions had a much smaller effect (`r LmCoeffLatex(lmMdl = lmAllAttFreqQualX, varName = "AvQualityCombOut_c", ci = TRUE)`), and importantly we found no interaction effect at all.
 In short, the effect of interaction frequency did not depend on the average interaction quality.
@@
 mdlWorker$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtWorkerSupp$workerAvFreQual)
+  lm(AvAttitude ~ SumContactNL_c * AvQualityComb_c, data = dtWorkerSupp$workerAvFreQual)
 # Study 2:
 mdlStudent$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtStudentSupp$studentContactFreq)
+  lm(AvAttitude ~ SumContactNL_c * AvQualityComb_c, data = dtStudentSupp$studentContactFreq)
 # Study 3: 
 mdlMedical$lmAttFreqQualX <-
-  lm(AvAttitude ~ SumContactNL_c * AvQuality_c, data = dtMedicalSupp$medicalContactFreq)
+  lm(AvAttitude ~ SumContactNL_c * AvQualityComb_c, data = dtMedicalSupp$medicalContactFreq)
 
@@
     AvAttitude ~ 
-      SumContactNL_c * AvQualityOut_c + 
+      SumContactNL_c * AvQualityCombOut_c + 
       SumContactNL_c * studyNum1 + 
       SumContactNL_c * studyNum3 + 
-      AvQualityOut_c * studyNum1 + 
-      AvQualityOut_c * studyNum3,
+      AvQualityCombOut_c * studyNum1 + 
+      AvQualityCombOut_c * studyNum3,
     data = avAll
@@
                                  "(Intercept)",
-                                 "AvQualityOut",
-                                 "AvQuality",
+                                 "AvQualityCombOut",
+                                 "AvQualityComb",
                                  "studyNum1",
                                  "studyNum3",
-                                 "SumContactNL:AvQualityOut",
+                                 "SumContactNL:AvQualityCombOut",
                                  "SumContactNL:studyNum1",
                                  "SumContactNL:studyNum3", 
-                                 "AvQualityOut:studyNum1",
-                                 "AvQualityOut:studyNum3",
+                                 "AvQualityCombOut:studyNum1",
+                                 "AvQualityCombOut:studyNum3",
                                  "R2_R2_adjusted"
@@
   var <- as.character(unique(lmMetaTbl$coef))[!as.character(unique(lmMetaTbl$coef)) %in% c("(Intercept)")]
-  names <- qdap::mgsub(c("SumContactNL", "AvQuality", "SumContactNL.AvQuality"),
+  names <- qdap::mgsub(c("SumContactNL", "AvQualityComb", "SumContactNL.AvQualityComb"),
                        c("Number of Outgroup Contacts","Average Interaction Quality", "Contact X Quality"), 
@@
                            ))) %>%
-    arrange(match(effect, c("SumContactNL", "AvQuality", "SumContactNL.AvQuality")), 
+    arrange(match(effect, c("SumContactNL", "AvQualityComb", "SumContactNL.AvQualityComb")), 
             match(sample, c("Study 1", "Study 2", "Study 3", "RE")))
@@
 
-```{generalForestPltComb, include=FALSE}
+```{r generalForestPltComb, include=FALSE}
 effGeneral <- rbind(
@@
       "relatedness_1",
-      "quality_overall_1",
+      "interaction_quality",
       "OutgroupInteraction",
@@
       "AttitudesDutch",
-      "quality_overall",
+      "interaction_quality",
       "OutgroupInteraction",
@@
       "AttitudesDutch",
-      "qualityOverall",
+      "interaction_quality",
       "AllportsCondition",
@@
     "relatedness_1", 
-     "quality_overall_1", 
+     "interaction_quality", 
     "OutgroupInteraction",
@@
     "AttitudesDutch",
-    "quality_overall",
+    "interaction_quality",
     "OutgroupInteraction",
@@
     "AttitudesDutch_zwc",
-    "qualityOverall",
-    "qualityOverall_cwc",
-    "qualityOverall_zwc",
+    "interaction_quality",
+    "interaction_quality_cwc",
+    "interaction_quality_zwc",
     "AllportsCondition",
@@
     "AllportsCondition", 
-    "qualityOverall"
+    "interaction_quality"
   )

### 2023-05-30 Methods-and-Results.tex
robustness re-render
re-render

@@
 participants were invited twice a day (at 12pm and 7pm) to reflect upon
-their interactions, psychological need fulfillments, and current
-attitudes towards the Dutch outgroup. General compliance was high
-(85.90\% of all invited surveys were filled
-in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%).}.
+their interactions, situational need fulfillments, and current attitudes
+towards the Dutch outgroup. General compliance was high (85.90\% of all
+invited surveys were filled
+in)\footnote{Two participants completed only two days (among the others, participation was 93.70\%).
+These two participants also reported no outgroup contacts.
+These participants are removed from any analyses that focus on outgroup contacts.}.
 The response rates were approximately equal during mornings (\textit{n}
@@
 Our participants recorded between 2--51 interactions with Dutch outgroup
-members (3.23--91.07\% of individual experience sampling measurements;
-387 of all 1,225 experience sampling
-responses)\footnote{Two participants only recorded two experience sampling measurements each and none of these included outgroup contacts.
-These participants are removed from any analyses that focus on outgroup contacts.}.
+members (\(M\) = 31.71\%, \(SD\) = 19.88\% of the individuals'
+experience sampling measurements; 387 of all 1,225 experience sampling
+responses)Two participants only recorded two experience sampling
+measurements each and none of these included outgroup contacts. These
+participants are removed from any analyses that focus on outgroup
+contacts.
 
-\paragraph{Psychological Needs}
+\paragraph{Need Fulfillment}
 
@@
 people or not, everyone answered a short series of questions on
-psychological need fulfillment. However, whereas participants with
+situational need fulfillment. However, whereas participants with
 interactions reported on the need fulfillment during the interaction,
 people without interactions with Dutch people judged the past daytime
-period in general. To assess the fulfillment of psychological needs, we
-included two types of need measurement: (1) the core situational need
-and (2) general self-determination theory needs.
+period in general. To assess the fulfillment of needs, we included two
+types of need measurement: (1) the core situational need and (2) general
+self-determination theory needs.
 
@@
 strongly agree (+50). The self-determination theory need measurements
-are described in \appref{app:AppendixRobustness}.
+were collected for robustness analyses and are described in
+\appref{app:AppendixRobustness}.
 
@@
 
-As an explanatory mechanism, we assessed ratings of the perceived
-interaction quality. As our main measurement, participants rated the
-statement ``\textit{Overall the interaction was …}'' on two continuous
-slider scales measuring pleasantness
+To assess ratings of the perceived interaction quality, participants
+rated the statement ``\textit{Overall the interaction was …}'' on two
+continuous slider scales measuring pleasantness
 \citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
@@
 At the end of every experience sampling measurement, we asked all
-participants about their current attitudes towards the Dutch -- our main
-dependent variable. To assess the momentary outgroup evaluation we used
-the common feeling thermometer: ``How favorable do you feel towards the
-Dutch?'' \citep[][]{Lavrakas2008}. Participants then rated their
-attitude on a continuous slider scale from ``very cold -- 0'' through
-``no feeling -- 50'' to ``very warm -- 100''. Both the question phrasing
-as well as the tick labels were consistent with large-scale panel
-surveys \citep[e.g.,][]{DeBell2010}.
+participants about their current attitudes towards the Dutch. To assess
+the momentary outgroup evaluation we used the common feeling
+thermometer: ``How favorable do you feel towards the Dutch?''
+\citep[][]{Lavrakas2008}. Participants then rated their attitude on a
+continuous slider scale from ``very cold -- 0'' through ``no feeling --
+50'' to ``very warm -- 100''. Both the question phrasing as well as the
+tick labels were consistent with large-scale panel surveys
+\citep[e.g.,][]{DeBell2010}.
 
@@
 This is unusual and might indicate that the effect is very consistent across participants.
-However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}.
+However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analysis as part of our stability analyses.}.
 Thus, in our first data, we find initial evidence that outgroup contacts
@@
 
-\subsubsection{Core Need}
+\subsubsection{Core Need Fulfillment}
 
@@
 contact might be explained by whether or not the contact fulfilled the
-person's core situational need. This should, in turn, be due to a higher
-perceived contact quality. We sequentially test whether the fulfillment
-of the core need during an interaction is (1) related to more positive
-outgroup attitudes, (2) higher perceived contact quality, and (3)
-whether the variance explained by the core need is subsumed by the
-perceived contact quality if considered jointly. We find that in the
-multilevel models, the fulfillment of core situational needs during
-outgroup contacts was associated with more positive outgroup attitudes
-(random slopes model; \textit{b} = 0.17, \textit{t}(365) = 2.93,
-\textit{p} = 0.004, \textit{95\%CI}{[}0.06, 0.29{]}) and also predicted
-higher perceived contact quality (random intercept model; \textit{b} =
-0.42, \textit{t}(365) = 8.07, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.32, 0.52{]}). Moreover, when we consider the
+person's core situational need. This should, in turn, be reflected in
+higher perceived contact quality and more positive outgroup attitudes.
+We sequentially test whether the fulfillment of the core need during an
+interaction is (1) related to more positive outgroup attitudes, (2)
+higher perceived contact quality, and (3) whether the variance explained
+by the core need is subsumed by the perceived contact quality if
+considered jointly. We find that in the multilevel models, the
+fulfillment of core situational needs during outgroup contacts was
+associated with more positive outgroup attitudes (random slopes model;
+\textit{b} = 0.17, \textit{t}(365) = 2.93, \textit{p} = 0.004,
+\textit{95\%CI}{[}0.06, 0.29{]}) and also related to higher perceived
+contact quality (random intercept model; \textit{b} = 0.37,
+\textit{t}(365) = 7.73, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.28, 0.47{]}). Moreover, when we consider the
 influences of core need fulfillment and contact quality on outgroup
-attitudes jointly, we find that virtually all variance is explained by
-perceived contact quality (random slopes model; \textit{b} = 0.23,
-\textit{t}(364) = 4.22, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
-still explained by core need fulfillment (\textit{b} = 0.04,
-\textit{t}(364) = 0.64, \textit{p} = 0.523, \textit{95\%CI}{[}-0.08,
-0.15{]}, also see \fgrref[-A]{fig:MainPaths}). We thus find support for
+attitudes jointly, we find that the two predictors share a large part of
+the variance explained in outgroup attitudes, so that perceived contact
+quality showed a strong effect on outgroup attitudes (random slopes
+model; \textit{b} = 0.24, \textit{t}(364) = 4.33, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.13, 0.35{]}) and only little unique variance
+is still explained by core need fulfillment (\textit{b} = 0.05,
+\textit{t}(364) = 0.94, \textit{p} = 0.348, \textit{95\%CI}{[}-0.05,
+0.14{]}, also see \fgrref[-A]{fig:MainPaths}). We thus find support for
 our hypotheses and can conclude that in this data set the fulfillment of
 core situational needs had a significant influence on outgroup
-attitudes. Additionally, this effect is likely explained by its effect
-through perceived contact quality.
+attitudes. Additionally, this effect seemingly addresses the same
+variance that is accounted for by perceived contact quality.
 
@@
 interaction.''. The participants recorded between 1--43 interactions
-with Dutch majority people (1.64--93.75\% of individual experience
-sampling measurements; 935 of all 4,965 experience sampling responses).
+with Dutch majority people (\(M\) = 20.70\%, \(SD\) = 17.31\% of the
+individual's experience sampling measurements; 935 of all 4,965
+experience sampling responses).
 
-\paragraph{Psychological Needs}
+\paragraph{Need Fulfillment}
 
@@
 on a continuous slider scale ranging from strongly disagree (1) to
-strongly agree (100).
+strongly agree (100). See \tblref{tab:descrFullWide} and
+\tblref{tab:descrOutWide} for descriptive statistics.
 
@@
 \textit{95\%CI}{[}0.07, 0.19{]}) and also predicted higher perceived
-interaction quality (random slopes model; \textit{b} = 0.40,
-\textit{t}(826) = 6.46, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.28, 0.52{]}). Additionally, if we consider the
+interaction quality (random slopes model; \textit{b} = 0.29,
+\textit{t}(826) = 5.43, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.19, 0.40{]}). Additionally, if we consider the
 influences of core need fulfillment and interaction quality on outgroup
-attitudes jointly, we find that virtually all variance is explained by
-perceived interaction quality (random slopes model; \textit{b} = 0.17,
-\textit{t}(825) = 5.56, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.11, 0.23{]}) and only little unique variance is
-still explained by core need fulfillment (\textit{b} = 0.03,
-\textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
-0.07{]}; also see \fgrref[-B]{fig:MainPaths} and
+attitudes jointly, we again find that much of the explained variance is
+shared by the predictor variables, so that perceived interaction quality
+remains a strong predictor (random slopes model; \textit{b} = 0.16,
+\textit{t}(825) = 5.93, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.11, 0.21{]}) and only little unique variance is
+still explained by core need fulfillment (\textit{b} = 0.06,
+\textit{t}(825) = 2.47, \textit{p} = 0.014, \textit{95\%CI}{[}0.01,
+0.11{]}; also see \fgrref[-B]{fig:MainPaths} and
 \tblref{tab:intergroupNeedsTblLong} for full results). These results are
@@
 hypotheses that the fulfillment of core situational needs had a
-significant influence on outgroup attitudes and that this effect is
-likely explained by its effect through perceived interaction quality.
+significant influence on perceived interaction quality and outgroup
+attitudes.
 
@@
 
-The study procedure mirrored the setup of studies one and two, in that
-it consisted of pre-, experience sampling-, and post-measurement. The
-participants were invited for experience sampling measurements twice a
-day (at 12pm and 7pm) for 30 days. General compliance was high (85.92\%
-filled in at least 31 experience sampling surveys or more). The response
-rates were approximately equal during mornings (\textit{n} = 2,092) and
-afternoons (\textit{n} = 2,015). All key variables for this study were
-part of the short experience sampling surveys.
+The study procedure mirrored the setup of studies one and two, and
+included the same pre-, experience sampling-, and post-measurement
+phases. The participants were invited for experience sampling
+measurements twice a day (at 12pm and 7pm) for at least 30 days. General
+compliance was high (85.92\% filled in at least 31 experience sampling
+surveys or more). The response rates were approximately equal during
+mornings (\textit{n} = 2,092) and afternoons (\textit{n} = 2,015). All
+key variables for this study were part of the short experience sampling
+surveys.
 
@@
 participants recorded between 1--71 interactions with Dutch outgroup
-members (2.13--87.18\% of individual experience sampling measurements;
-1,702 of all 4,107 experience sampling responses).
+members (\(M\) = 42.22\%, \(SD\) = 19.96\% of the individuals'
+experience sampling measurements; 1,702 of all 4,107 experience sampling
+responses).
 
@@
 \textit{t}(3,834) = 6.52, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}3.90, 7.23{]}), even after controlling for having an
-interaction with a non-Dutch (which did not relate to outgroup attitudes
+\textit{95\%CI}{[}3.90, 7.23{]}), even after controlling for having a
+non-Dutch interaction (which did not relate to outgroup attitudes
 independently; for full results see
@@
 higher perceived interaction quality (random slopes model; \textit{b} =
-0.43, \textit{t}(1,605) = 8.35, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.33, 0.54{]}). Additionally, once we consider the
+0.45, \textit{t}(1,605) = 9.32, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.36, 0.54{]}). Additionally, once we consider the
 influences of core need fulfillment and interaction quality on outgroup
@@
 substantially stronger predictor (random slopes model; \textit{b} =
-0.17, \textit{t}(1,600) = 6.86, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.22{]}) and the unique variance explained by
+0.16, \textit{t}(1,600) = 7.03, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.11, 0.20{]}) and the unique variance explained by
 core need fulfillment was roughly half of its original effect size
-(\textit{b} = 0.11, \textit{t}(1,600) = 3.50, \textit{p} \textless{}
-.001, \textit{95\%CI}{[}0.05, 0.17{]}; also see
+(\textit{b} = 0.12, \textit{t}(1,600) = 3.61, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.06, 0.19{]}; also see
 \fgrref[-C]{fig:MainPaths} and \tblref{tab:intergroupNeedsTblLong} for
@@
 the fulfillment of core situational needs and the results suggest that
-this might be due to higher perceived interaction quality.
+this explained variance is shared with perceived interaction quality.
 
@@
 .001, \textit{95\%CI}{[}0.15, 0.29{]}) and also predicted higher
-perceived interaction quality (random slopes model; \textit{b} = 0.65,
-\textit{t}(1,605) = 11.82, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.54, 0.76{]}). Moreover, when we considered the
+perceived interaction quality (random slopes model; \textit{b} = 0.62,
+\textit{t}(1,605) = 9.60, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.49, 0.74{]}). Moreover, when we considered the
 influences of Allport's Conditions and interaction quality on outgroup
@@
 substantially stronger predictor (random slopes model; \textit{b} =
-0.17, \textit{t}(1,600) = 6.25, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
+0.16, \textit{t}(1,600) = 6.56, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.11, 0.21{]}) and the unique variance explained by
 Allport's Conditions was less than half of its original effect size
-(\textit{b} = 0.09, \textit{t}(1,600) = 2.89, \textit{p} = 0.004,
-\textit{95\%CI}{[}0.03, 0.15{]}; also see
+(\textit{b} = 0.11, \textit{t}(1,600) = 3.54, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.05, 0.18{]}; also see
 \tblref{tab:intergroupNeedsTblLong}). These results indicate that in
 this data set the fulfillment of Allport's conditions had a significant
-influence on outgroup attitudes and this effect is likely, in parts,
-explained by its effect through perceived interaction quality.
+influence on outgroup attitudes and this effect is likely, related to
+the effect of perceived interaction quality.
 
@@
 Allport's conditions and the core need fulfillment seem to (in part)
-work through perceived interaction quality, they explain different
-aspects of the variance in outgroup attitudes and do not constitute one
-another.
+relate to perceived interaction quality, they explain different aspects
+of the variance in outgroup attitudes and do not constitute one another.
 
@@
 reduced when modeled together with interaction quality perceptions,
-supporting our assertion that interaction quality offers a psychological
-mechanism for the direct effect (see
-\fgrref[-C]{fig:AllportNeedFulfillment}).
+supporting our assertion that interaction quality and need fulfillment
+share the same variance explained in outgroup attitudes (see
+\fgrref[-C]{fig:AllportNeedFulfillment}). Note that this joint effect is
+not meant to resemble a mediation analysis. Particularly, since the data
+is non-causal, and because multicollinearity and potential third
+variables could result in similar results.
 
@@
 quality was associated with more positive outgroup attitudes following
-an intergroup contact. We have, however, not brought the two elements of
-the contact hypothesis together in a single analysis. To jointly test
-the effects of contact frequency and average interaction quality, we ran
-a linear regression model where average outgroup attitudes were
-predicted by the number of interactions and the average interaction
-quality ratings of all participants across the three studies. We did so
-while controlling for the possible effects of study-specific
-differences. To include the study-membership as a control variable, we
-used the student sample (Study 2) as the reference group because it was
-both the largest and the most homogeneous study. Looking at the overall
-model, we found that the model predicted 13.89\% of the variance in
-average outgroup attitudes (\textit{F}(9, 189) = 3.39, \textit{p} =
-0.001, \textit{R\textsuperscript{2}} = 0.14). Looking at the individual
-effects, we found that only the number of outgroup interactions has a
-clear association with average outgroup attitudes (\textit{b} = 0.55,
-\textit{t}(189) = 2.82, \textit{p} = 0.005, \textit{95\%CI}{[}0.16,
-0.93{]}). The average interaction quality perceptions had a much smaller
-effect (\textit{b} = 0.29, \textit{t}(189) = 2.09, \textit{p} = 0.038,
-\textit{95\%CI}{[}0.02, 0.56{]}), and importantly we found no
-interaction effect at all. In short, the effect of interaction frequency
-did not depend on the average interaction quality.
+an intergroup contact. We have, however, not brought the two quantity
+and quality elements of the contact hypothesis together in a single
+analysis. To jointly test the effects of contact frequency and average
+interaction quality, we ran a linear regression model where average
+outgroup attitudes were predicted by the number of interactions and the
+average interaction quality ratings of all participants across the three
+studies. We did so while controlling for the possible effects of
+study-specific differences. To include the study-membership as a control
+variable, we used the student sample (Study 2) as the reference group
+because it was both the largest and the most homogeneous study. Looking
+at the overall model, we found that the model predicted 11.84\% of the
+variance in average outgroup attitudes (\textit{F}(9, 189) = 2.82,
+\textit{p} = 0.004, \textit{R\textsuperscript{2}} = 0.12). Looking at
+the individual effects, we found that only the number of outgroup
+interactions has a clear association with average outgroup attitudes
+(\textit{b} = 0.51, \textit{t}(189) = 2.61, \textit{p} = 0.010,
+\textit{95\%CI}{[}0.12, 0.89{]}). The average interaction quality
+perceptions had a much smaller effect (\textit{b} = 0.27,
+\textit{t}(189) = 2.24, \textit{p} = 0.026, \textit{95\%CI}{[}0.03,
+0.50{]}), and importantly we found no interaction effect at all. In
+short, the effect of interaction frequency did not depend on the average
+interaction quality.
 
@@
 whether the contact was planned or accidental, and whether the
-motivational mechanism also holds direct well-being benefits for the
+motivational mechanism also holds for direct well-being benefits for the
 minority members. We describe the full methods and results for the
@@
 fulfillment on outgroup attitudes is particularly important for outgroup
-interactions (rather than only need fulfillment in general).
+interactions (rather than need fulfillment in general).
 
-\subsubsection{Interaction intend}
+\subsubsection{Interaction intent}
 
@@
 emphasis as in original). This was also reflected in a relatively low
-average and consistent right skew of the `accidental' item. Nonetheless,
+mean and consistent right skew of the `accidental' item. Nonetheless,
 there remained a substantial variance in the item and we continued with
@@
 in none of the analysis did we see a moderation effect of interaction
-intend nor did we find a main effect of interaction intend. There is,
+intent nor did we find a main effect of interaction intent. There is,
 thus, consistent evidence that the need fulfillment mechanism was not
@@
 practical and psychological needs specifically as our dimensions to
-account for differences in the types of needs that participants commonly
-reported. With practical motives we refer to specific, tangible goals or
-tasks that participants aimed to accomplish during the interaction.
-These instrumental goals are usually observable, concrete, and often
-centered on external outcomes, such as acquiring resources, completing
-tasks, and addressing immediate challenges \citep[e.g.,][]{oduntan2019}.
-With psychological motives we refer to underlying motives or desires
-that are more abstract and relate to personal fulfillment and
-well-being. In contrast to practical needs, psychological needs delve
-into the subjective and internal aspects of human experiences. These
-needs pertain to emotions, social connections, and cognitive processes,
+mirror our instructions to the participants and to account for
+differences in the types of needs that participants commonly reported.
+With practical motives we refer to specific, tangible goals or tasks
+that participants aimed to accomplish during the interaction. These
+instrumental goals are usually observable, concrete, and often centered
+on external outcomes, such as acquiring resources, completing tasks, and
+addressing immediate challenges \citep[e.g.,][]{oduntan2019}. With
+psychological motives we refer to underlying motives or desires that are
+more abstract and relate to personal fulfillment and well-being. In
+contrast to practical needs, psychological needs delve into the
+subjective and internal aspects of human experiences. These needs
+pertain to emotions, social connections, and cognitive processes,
 reflecting individuals' quest for personal growth, well-being, and
@@
 a psychological goal-directedness but can also be classified as not
-having any goal at all. We found high inter-rater reliability for the
-two independent coders, who coded all 47 topics. The codings revealed
-considerable variance, which allowed us to add the two dimensions back
-to each of the reported interaction motives and assess the effects of
-the goal-directed character.
+having any goal at all. See Supplemental Materials D for the detailed
+coding protocol, including instructions for the coders. We found high
+inter-rater reliability for the two independent coders, who coded all 47
+topics. The codings revealed considerable variance, which allowed us to
+add the two dimensions back to each of the reported interaction motives
+and assess the effects of the goal-directed character.
 
@@
 psychological needs might not account for the same effect, we compared
-our situation core need fulfillment measurement to the three
+our situation core need fulfillment measurement to the commonly studied
 self-determination theory needs (autonomy, relatedness, competence).
@@
 self-determination theory needs independently predicted outgroup
-attitudes to a statistically significant extent (despite similar effect
-sizes of relatedness). When looking at the individual studies, we again
-saw that core need fulfillment remained a consistent predictor of
+attitudes to a statistically significant extent (despite a similar
+effect size of relatedness). When looking at the individual studies, we
+again saw that core need fulfillment remained a consistent predictor of
 outgroup attitudes. However, across all three studies the fulfillment of
@@
 of the autonomy fulfillment effects reached statistical significance. In
-short, find that across our samples, relatedness fulfillment (and to a
-smaller extend competence fulfillment) are instrumental in understanding
-when an outgroup contact leads to more positive outgroup attitudes.
-Importantly, even when considering these effects situational core need
-fulfillment remains a strong and consistent predictor of outgroup
-attitudes.
+short, we find that across our samples, relatedness fulfillment (and to
+a smaller extend competence fulfillment) are instrumental in
+understanding when an outgroup contact leads to more positive outgroup
+attitudes. Importantly, even when considering these effects situational
+core need fulfillment remains a strong and consistent predictor of
+outgroup attitudes.
+
+Overall, we find that our situation need fulfillment model is consistent
+across samples and contexts, and that the need fulfillment effect is
+robust to a wide variety of alternate explanations.

### 2023-05-30 PathModels.Rmd
re-render

@@
     \\node[mynode,above right=of m](yd) {<<lab_y_direct>>};
-    \\draw[-latex] (xd.east) -- node[above=2mm, align=center] {<<coef_xy_direct>>} (yd.west);
-    \\draw[-latex] (x.north) -- node[auto] {<<coef_xm>>} (m.west);
-    \\draw[-latex] (m.east) -- node[auto] {<<coef_my>>} (y.north);
-    \\draw[-latex] (x.east) -- node[below=2mm, align=center] {<<coef_xy>>} (y.west);
+    \\draw[latex-latex] (xd.east) -- node[above=2mm, align=center] {<<coef_xy_direct>>} (yd.west);
+    \\draw[latex-latex] (x.north) -- node[auto] {<<coef_xm>>} (m.west);
+    \\draw[latex-latex] (m.east) -- node[auto] {<<coef_my>>} (y.north);
+    \\draw[latex-latex] (x.east) -- node[below=2mm, align=center] {<<coef_xy>>} (y.west);
     \\path (xd.north west) ++(-0.2, 6pt) node[above left]{\\textbf{(<<fig_num>>) <<study_num>>}};

### 2023-05-30 PathModels.tex
re-render

--- 2022-11-11 PathModels.tex
@@
     \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
-    \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.30**} (yd.west);
-    \draw[-latex] (x.north) -- node[auto] {0.40****} (m.west);
-    \draw[-latex] (m.east) -- node[auto] {0.41***} (y.north);
-    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.13} (y.west);
+    \draw[latex-latex] (xd.east) -- node[above=2mm, align=center] {0.30**} (yd.west);
+    \draw[latex-latex] (x.north) -- node[auto] {0.39****} (m.west);
+    \draw[latex-latex] (m.east) -- node[auto] {0.45***} (y.north);
+    \draw[latex-latex] (x.east) -- node[below=2mm, align=center] {0.12} (y.west);
     \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(A) Study 1:}};
@@
     \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
-    \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.14***} (yd.west);
-    \draw[-latex] (x.north) -- node[auto] {0.27****} (m.west);
-    \draw[-latex] (m.east) -- node[auto] {0.24****} (y.north);
-    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.07} (y.west);
+    \draw[latex-latex] (xd.east) -- node[above=2mm, align=center] {0.14***} (yd.west);
+    \draw[latex-latex] (x.north) -- node[auto] {0.20****} (m.west);
+    \draw[latex-latex] (m.east) -- node[auto] {0.22****} (y.north);
+    \draw[latex-latex] (x.east) -- node[below=2mm, align=center] {0.09*} (y.west);
     \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(B) Study 2:}};
@@
     \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
-    \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.18****} (yd.west);
-    \draw[-latex] (x.north) -- node[auto] {0.31****} (m.west);
-    \draw[-latex] (m.east) -- node[auto] {0.23****} (y.north);
-    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.10**} (y.west);
+    \draw[latex-latex] (xd.east) -- node[above=2mm, align=center] {0.18****} (yd.west);
+    \draw[latex-latex] (x.north) -- node[auto] {0.31****} (m.west);
+    \draw[latex-latex] (m.east) -- node[auto] {0.24****} (y.north);
+    \draw[latex-latex] (x.east) -- node[below=2mm, align=center] {0.10***} (y.west);
     \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(C) Study 3:}};

### 2023-05-30 Robustness-Methods-and-Results.tex
re-render

@@
 centered on external outcomes, such as acquiring resources, completing
-tasks, and addressing immediate challenges \citep[][]{}. With
-psychological motives we refer to underlying motives or desires that are
-more abstract and relate to personal fulfillment and well-being. In
-contrast to practical needs, psychological needs delve into the
-subjective and internal aspects of human experiences. These needs
-pertain to emotions, social connections, and cognitive processes,
+tasks, and addressing immediate challenges \citep[e.g.,][]{oduntan2019}.
+With psychological motives we refer to underlying motives or desires
+that are more abstract and relate to personal fulfillment and
+well-being. In contrast to practical needs, psychological needs delve
+into the subjective and internal aspects of human experiences. These
+needs pertain to emotions, social connections, and cognitive processes,
 reflecting individuals' quest for personal growth, well-being, and
-thriving in social relationships \citep[][]{}. Note that with this
-approach any particular motive can include a practical and/or a
+thriving in social relationships \citep[][]{dweck2017}. Note that with
+this approach any particular motive can include a practical and/or a
 psychological goal-directedness but can also be classified as not having
@@
 asked our participants to focus on most the important interaction (i.e.,
-``\textit{The following questions will be about the interaction \underline{you consider most significant}.}'''\,'\,``;
+``\textit{The following questions will be about the interaction \underline{you consider most significant}.}'';
 emphasis as in original). We again start our analysis approach by
@@
 
-\paragraph{overall}
-
 Fourthly, to assess the role of different types of motives reported by
@@
 results).
-
-\paragraph{Study follow-up}
 

### 2023-05-30 Table.tex
Table General Footnote
re-render

@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont (Intercept)} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 68.15**** [65.25, 71.06]} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 68.24**** [65.30, 71.18]} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityOut} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.29* [ 0.02,  0.56]; $\eta_{partial}$ = 0.08} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityCombOut} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.27* [ 0.03,  0.50]; $\eta_{partial}$ = 0.05} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont studyNum1} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  2.23 [-5.03,  9.48]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  2.50 [-4.86,  9.85]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont studyNum3} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -3.15 [-7.78,  1.48]; $\eta_{partial}$ = 0.01} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -2.97 [-7.67,  1.72]; $\eta_{partial}$ = 0.01} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:AvQualityOut} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.01 [-0.02,  0.01]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:AvQualityCombOut} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.01 [-0.03,  0.00]; $\eta_{partial}$ = 0.01} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:studyNum1} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.46 [-1.17,  0.24]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.38 [-1.14,  0.37]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:studyNum3} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.46* [-0.92, -0.01]; $\eta_{partial}$ = 0.02} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.45 [-0.91,  0.02]; $\eta_{partial}$ = 0.02} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityOut:studyNum1} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.46 [-0.30,  1.23]; $\eta_{partial}$ = 0.01} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityCombOut:studyNum1} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.07 [-0.76,  0.90]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 
-\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityOut:studyNum3} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.16 [-0.24,  0.56]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityCombOut:studyNum3} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.01 [-0.35,  0.33]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
@@
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont $R^2 / R^2_{adjusted}$} \hspace{6pt}\huxbpad{6pt}} &
-\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.139 / 0.098} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.118 / 0.076} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
 
-\hhline{>{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}-}
+\hhline{>{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}-}
+\arrayrulecolor{black}
+
+\multicolumn{9}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont Note:$<$br$>$**** p $<$ .0001, *** p $<$ .001, ** p $<$ .01, * p $<$ .05} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
 \arrayrulecolor{black}

### 2023-05-30 TableOnly.tex
REML fixed
Table General Footnote
re-render

--- 2022-10-25 Table.tex
@@
-\documentclass{article}
-\usepackage{array}
-\usepackage{caption}
-\usepackage{graphicx}
-\usepackage{siunitx}
-\usepackage[normalem]{ulem}
-\usepackage{colortbl}
-\usepackage{multirow}
-\usepackage{hhline}
-\usepackage{calc}
-\usepackage{tabularx}
-\usepackage{threeparttable}
-\usepackage{wrapfig}
-\usepackage{adjustbox}
-\usepackage{hyperref}
-% These are LaTeX packages. You can install them using your LaTex management software,
-% or by running `huxtable::install_latex_dependencies()` from within R.
-% Other packages may be required if you use non-standard tabulars (e.g. tabulary).
-\pagenumbering{gobble}
-
-\begin{document}
-
 ```{=latex}
@@
 ```
-
-\end{document}

### 2023-05-30 Tables/studentOutVarDescr.tex
meta structure added
re-render

@@
 \midrule
-Core Need &  & 0.44** & 0.49*** & -0.22 & 0.51*** & 0.14\\
-Competence & 0.23*** &  & 0.58*** & 0.40** & 0.55*** & 0.21\\
-Autonomy & 0.12*** & 0.24*** &  & 0.22 & 0.61*** & 0.05\\
-Relatedness & 0.48*** & 0.31*** & 0.38*** &  & 0.35* & -0.09\\
-Quality & 0.19*** & 0.40*** & 0.16*** & 0.15*** &  & 0.16\\
-Attitudes NL & 0.32*** & 0.36*** & 0.19*** & 0.23*** & 0.30*** & \\
+Core Need &  & 0.44** & 0.49*** & -0.22 & 0.29 & 0.15\\
+Competence & 0.23*** &  & 0.58*** & 0.38** & 0.46*** & 0.22\\
+Autonomy & 0.12*** & 0.25*** &  & 0.21 & 0.50*** & 0.06\\
+Relatedness & 0.49*** & 0.22*** & 0.46*** &  & 0.48*** & -0.10\\
+Quality & 0.19*** & 0.38*** & 0.16*** & 0.15*** &  & 0.08\\
+Attitudes NL & 0.32*** & 0.36*** & 0.19*** & 0.22*** & 0.29*** & \\
 \addlinespace
-Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 78.80 & 70.41\\
-Between SD & 11.20 & 13.95 & 14.07 & 17.35 & 10.71 & 17.13\\
-Within SD & 15.87 & 16.81 & 14.24 & 26.14 & 17.88 & 9.87\\
-ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.14 & 0.72\\
-ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.59 & 0.96\\
+Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 67.08 & 70.41\\
+Between SD & 11.20 & 13.95 & 14.07 & 17.35 & 12.54 & 17.13\\
+Within SD & 15.87 & 16.81 & 14.24 & 26.14 & 16.54 & 9.87\\
+ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.24 & 0.72\\
+ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.73 & 0.96\\
 \bottomrule

### 2023-05-30 Tables/studentVarDescr.tex
re-render

@@
 \midrule
-Core Need &  & 0.61*** & 0.66*** & 0.42*** & 0.80*** & 0.10\\
-Competence & 0.24*** &  & 0.74*** & 0.66*** & 0.75*** & 0.07\\
-Autonomy & 0.15*** & 0.34*** &  & 0.58*** & 0.69*** & -0.04\\
-Relatedness & 0.45*** & 0.29*** & 0.42*** &  & 0.55*** & -0.12\\
-Quality & 0.17*** & 0.39*** & 0.08*** & 0.05** &  & 0.09\\
-Attitudes NL & 0.35*** & 0.43*** & 0.11*** & 0.11*** & 0.13*** & \\
+Core Need &  & 0.60*** & 0.66*** & 0.41*** & 0.59*** & 0.11\\
+Competence & 0.24*** &  & 0.73*** & 0.66*** & 0.72*** & 0.06\\
+Autonomy & 0.16*** & 0.34*** &  & 0.57*** & 0.65*** & -0.05\\
+Relatedness & 0.45*** & 0.22*** & 0.52*** &  & 0.66*** & -0.13\\
+Quality & 0.17*** & 0.36*** & 0.08*** & 0.05** &  & 0.11\\
+Attitudes NL & 0.35*** & 0.42*** & 0.11*** & 0.11*** & 0.09*** & \\
 \addlinespace
-Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 83.77 & 67.26\\
-Between SD & 9.17 & 14.47 & 11.21 & 13.36 & 9.12 & 18.64\\
-Within SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
-ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.20 & 0.80\\
-ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.88 & 0.99\\
+Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 74.51 & 67.26\\
+Between SD & 9.17 & 14.47 & 11.21 & 13.36 & 11.24 & 18.64\\
+Within SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.59 & 9.40\\
+ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.29 & 0.80\\
+ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.92 & 0.99\\
 \bottomrule

### 2023-05-30 Tables/workerOutVarDescr.tex
re-render

--- 2022-01-04 Tables/workerOutVarDescr.tex
@@
 \midrule
-Core Need &  & 0.82*** & 0.60*** & 0.32 & 0.52** & -0.03\\
-Competence & 0.36*** &  & 0.89*** & 0.24 & 0.38 & -0.24\\
-Autonomy & 0.28*** & 0.23*** &  & 0.29 & 0.56** & 0.02\\
-Relatedness & 0.51*** & 0.39*** & 0.37*** &  & -0.09 & 0.14\\
-Quality & 0.17*** & 0.44*** & 0.27*** & 0.27*** &  & 0.50*\\
-Attitudes NL & 0.24*** & 0.37*** & 0.24*** & 0.37*** & 0.52*** & \\
+Core Need &  & 0.83*** & 0.59*** & 0.26 & 0.36 & -0.02\\
+Competence & 0.36*** &  & 0.88*** & 0.16 & 0.31 & -0.25\\
+Autonomy & 0.29*** & 0.23*** &  & 0.21 & 0.35 & 0.03\\
+Relatedness & 0.50*** & 0.38*** & 0.48*** &  & 0.25 & 0.18\\
+Quality & 0.17** & 0.43*** & 0.27*** & 0.27*** &  & 0.23\\
+Attitudes NL & 0.24*** & 0.37*** & 0.25*** & 0.37*** & 0.55*** & \\
 \addlinespace
-Grand Mean & 32.20 & 16.53 & 22.64 & 1.58 & 24.10 & 72.46\\
-Between SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.50 & 13.62\\
-Within SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.85 & 9.50\\
-ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.18 & 0.68\\
-ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.80 & 0.98\\
+Grand Mean & 82.20 & 66.53 & 72.64 & 51.58 & 67.00 & 72.46\\
+Between SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.26 & 13.62\\
+Within SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.24 & 9.50\\
+ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.23 & 0.68\\
+ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.84 & 0.98\\
 \bottomrule

### 2023-05-30 Tables/workerVarDescr.tex
re-render

@@
 \midrule
-Core Need &  & 0.63*** & 0.47** & 0.00 & 0.39* & -0.22\\
-Competence & 0.37*** &  & 0.68*** & -0.13 & 0.16 & -0.26\\
-Autonomy & 0.31*** & 0.08** &  & -0.04 & 0.63*** & 0.16\\
-Relatedness & 0.45*** & 0.41*** & 0.22*** &  & 0.02 & -0.07\\
-Quality & 0.05 & 0.45*** & 0.11*** & 0.12*** &  & 0.47*\\
-Attitudes NL & 0.10*** & 0.34*** & 0.14*** & 0.14*** & 0.43*** & \\
+Core Need &  & 0.62*** & 0.49** & 0.00 & 0.33 & -0.20\\
+Competence & 0.37*** &  & 0.69*** & -0.14 & 0.25 & -0.21\\
+Autonomy & 0.32*** & 0.09** &  & -0.04 & 0.21 & 0.19\\
+Relatedness & 0.45*** & 0.37*** & 0.35*** &  & 0.09 & -0.06\\
+Quality & 0.05 & 0.42*** & 0.11*** & 0.12*** &  & 0.14\\
+Attitudes NL & 0.10*** & 0.31*** & 0.15*** & 0.14*** & 0.44*** & \\
 \addlinespace
-Grand Mean & 77.95 & 62.10 & 72.17 & 55.29 & 74.10 & 71.49\\
-Between SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.50 & 12.91\\
-Within SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
-ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.18 & 0.70\\
-ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.79 & 0.99\\
+Grand Mean & 77.95 & 62.10 & 72.17 & 55.29 & 67.00 & 71.49\\
+Between SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.26 & 12.91\\
+Within SD & 20.83 & 20.89 & 15.15 & 23.29 & 17.43 & 8.11\\
+ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.23 & 0.70\\
+ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.83 & 0.99\\
 \bottomrule

### 2023-05-30 manuscript.tex
typos

@@
 One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations.
-We propose to consider situational psychological needs during everyday intergroup contact.
+We propose to consider the fulfillment of situationally relevant needs during everyday intergroup contact.
 We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297; total \textit{N} participants = 207).
-The novel psychological needs mechanism is consistently a strong predictor of positive attitudes during intergroup interactions and these positive effects emerged via perceived interaction quality.
-The situational needs model is robust to alternative models and outperforms Allport's contact conditions.
+The novel need fulfillment mechanism is consistently a strong predictor of perceived interaction quality as well as positive outgroup attitudes following intergroup interactions.
+The situational needs model is robust to alternative models and works at least as well as Allport's contact conditions.
 As one of the first studies to test intergroup contact theory using extensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
 
-\noindent\textbf{Public significance statement}: In this paper, we provide evidence that the fulfillment of situational psychological needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
+\noindent\textbf{Public significance statement}: In this paper, we provide evidence that the fulfillment of situational needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
 Methodologically, this offers testament to the emerging practice of capturing real-life interactions using extensive longitudinal data.
@@
 \keywords{
-    Intergroup Contact, Psychological Needs, Outgroup Attitudes, Interaction Quality, Extensive Longitudinal Data\\
+    Intergroup Contact, Need Fulfillment, Outgroup Attitudes, Interaction Quality, Extensive Longitudinal Data\\
     \textit{Open Science Practices:}

### 2023-05-30 Methods-and-Results.Rmd
tbl reduced

@@
     id = "PID",
-    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "interaction_quality", "thermometerDutch_1"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+    # selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "interaction_quality", "thermometerDutch_1"),
+    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+    selection = c("keyMotiveFulfilled", "interaction_quality", "thermometerDutch_1"),
+    labels = c("Core Need", "Quality", "Attitudes NL")
   )
@@
     id = "PID",
-    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "interaction_quality", "thermometerDutch_1"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+    # selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "interaction_quality", "thermometerDutch_1"),
+    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+    selection = c("keymotive_fulfillemt_1", "interaction_quality", "thermometerDutch_1"),
+    labels = c("Core Need", "Quality", "Attitudes NL")
   )
@@
     id = "PID",
-    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+    # selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
+    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+    selection = c("KeyNeedFullfillment", "interaction_quality", "AttitudesDutch"),
+    labels = c("Core Need", "Competence", "Quality", "Attitudes NL")
   )
@@
     id = "PID",
-    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+    # selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
+    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+    selection = c("KeyNeedFullfillment", "interaction_quality", "AttitudesDutch"),
+    labels = c("Core Need", "Quality", "Attitudes NL")
   )
@@
     id = "PID",
-    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "interaction_quality", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
+    # selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "interaction_quality", "AttitudesDutch"),
+    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
+    selection = c("KeyNeedFulfillment", "AllportsCondition", "interaction_quality", "AttitudesDutch"),
+    labels = c("Core Need", "Allport", "Quality", "Attitudes NL")
   )
@@
                                  "(Intercept)",
+                                 "SumContactNL",
                                  "AvQualityCombOut",
-                                 "AvQualityComb",
                                  "studyNum1",
@@
     id = "ID",
-    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "qualityOverall", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+    # selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "qualityOverall", "AttitudesDutch"),
+    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
+    selection = c("KeyNeedFullfillment", "qualityOverall", "AttitudesDutch"),
+    labels = c("Core Need", "Quality", "Attitudes NL")
   )

### 2023-05-30 Methods-and-Results.Rmd
descr tbl red

@@
     selection = c("KeyNeedFullfillment", "interaction_quality", "AttitudesDutch"),
-    labels = c("Core Need", "Competence", "Quality", "Attitudes NL")
+    labels = c("Core Need", "Quality", "Attitudes NL")
   )

### 2023-05-30 Table.tex
descr tbl red

@@
 
+\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL} \hspace{6pt}\huxbpad{6pt}} &
+\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.51** [ 0.12,  0.89]; $\eta_{partial}$ = 0.03} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]
+
+\hhline{}
+\arrayrulecolor{black}
+
 \multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityCombOut} \hspace{6pt}\huxbpad{6pt}} &

### 2023-05-30 Tables/studentOutVarDescr.tex
descr tbl red

@@
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llccccc}
+\begin{tabular}[t]{llcc}
 \toprule
-  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
+  & Core Need & Quality & Attitudes NL\\
 \midrule
-Core Need &  & 0.44** & 0.49*** & -0.22 & 0.29 & 0.15\\
-Competence & 0.23*** &  & 0.58*** & 0.38** & 0.46*** & 0.22\\
-Autonomy & 0.12*** & 0.25*** &  & 0.21 & 0.50*** & 0.06\\
-Relatedness & 0.49*** & 0.22*** & 0.46*** &  & 0.48*** & -0.10\\
-Quality & 0.19*** & 0.38*** & 0.16*** & 0.15*** &  & 0.08\\
-Attitudes NL & 0.32*** & 0.36*** & 0.19*** & 0.22*** & 0.29*** & \\
+Core Need &  & 0.23 & 0.17\\
+Quality & 0.23*** &  & 0.06\\
+Attitudes NL & 0.16*** & 0.29*** & \\
 \addlinespace
-Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 67.08 & 70.41\\
-Between SD & 11.20 & 13.95 & 14.07 & 17.35 & 12.54 & 17.13\\
-Within SD & 15.87 & 16.81 & 14.24 & 26.14 & 16.54 & 9.87\\
-ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.24 & 0.72\\
-ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.73 & 0.96\\
+Grand Mean & 86.86 & 67.08 & 70.41\\
+Between SD & 11.20 & 12.54 & 17.13\\
+Within SD & 15.87 & 16.54 & 9.87\\
+\addlinespace
+ICC(1) & 0.14 & 0.24 & 0.72\\
+ICC(2) & 0.58 & 0.73 & 0.96\\
 \bottomrule
-\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
 \end{tabular}}

### 2023-05-30 Tables/studentVarDescr.tex
descr tbl red

--- 2023-05-26 Tables/studentVarDescr.tex
@@
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llccccc}
+\begin{tabular}[t]{llcc}
 \toprule
-  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
+  & Core Need & Quality & Attitudes NL\\
 \midrule
-Core Need &  & 0.61*** & 0.66*** & 0.42*** & 0.80*** & 0.10\\
-Competence & 0.24*** &  & 0.74*** & 0.66*** & 0.75*** & 0.07\\
-Autonomy & 0.15*** & 0.34*** &  & 0.58*** & 0.69*** & -0.04\\
-Relatedness & 0.45*** & 0.29*** & 0.42*** &  & 0.55*** & -0.12\\
-Quality & 0.17*** & 0.39*** & 0.08*** & 0.05** &  & 0.09\\
-Attitudes NL & 0.35*** & 0.43*** & 0.11*** & 0.11*** & 0.13*** & \\
+Core Need &  & 0.61*** & 0.03\\
+Quality & 0.21*** &  & 0.02\\
+Attitudes NL & 0.08*** & 0.09*** & \\
 \addlinespace
-Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 83.77 & 67.26\\
-Between SD & 9.17 & 14.47 & 11.21 & 13.36 & 9.12 & 18.64\\
-Within SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
-ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.20 & 0.80\\
-ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.88 & 0.99\\
+Grand Mean & 84.87 & 74.51 & 67.26\\
+Between SD & 9.17 & 11.24 & 18.64\\
+Within SD & 20.33 & 16.59 & 9.40\\
+\addlinespace
+ICC(1) & 0.15 & 0.29 & 0.80\\
+ICC(2) & 0.89 & 0.92 & 0.99\\
 \bottomrule
-\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
 \end{tabular}}

### 2023-05-30 Tables/workerOutVarDescr.tex
descr tbl red

@@
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llccccc}
+\begin{tabular}[t]{llcc}
 \toprule
-  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
+  & Core Need & Quality & Attitudes NL\\
 \midrule
-Core Need &  & 0.83*** & 0.59*** & 0.26 & 0.36 & -0.02\\
-Competence & 0.36*** &  & 0.88*** & 0.16 & 0.31 & -0.25\\
-Autonomy & 0.29*** & 0.23*** &  & 0.21 & 0.35 & 0.03\\
-Relatedness & 0.50*** & 0.38*** & 0.48*** &  & 0.25 & 0.18\\
-Quality & 0.17** & 0.43*** & 0.27*** & 0.27*** &  & 0.23\\
-Attitudes NL & 0.24*** & 0.37*** & 0.25*** & 0.37*** & 0.55*** & \\
+Core Need &  & 0.40 & -0.03\\
+Quality & 0.37*** &  & 0.21\\
+Attitudes NL & 0.27*** & 0.55*** & \\
 \addlinespace
-Grand Mean & 82.20 & 66.53 & 72.64 & 51.58 & 67.00 & 72.46\\
-Between SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.26 & 13.62\\
-Within SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.24 & 9.50\\
-ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.23 & 0.68\\
-ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.84 & 0.98\\
+Grand Mean & 82.20 & 67.00 & 72.46\\
+Between SD & 12.42 & 9.26 & 13.62\\
+Within SD & 17.66 & 18.24 & 9.50\\
+\addlinespace
+ICC(1) & 0.33 & 0.23 & 0.68\\
+ICC(2) & 0.90 & 0.84 & 0.98\\
 \bottomrule
-\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
 \end{tabular}}

### 2023-05-30 Tables/workerVarDescr.tex
descr tbl red

@@
 \resizebox{\linewidth}{!}{
-\begin{tabular}[t]{llccccc}
+\begin{tabular}[t]{llcc}
 \toprule
-  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
+  & Core Need & Quality & Attitudes NL\\
 \midrule
-Core Need &  & 0.62*** & 0.49** & 0.00 & 0.33 & -0.20\\
-Competence & 0.37*** &  & 0.69*** & -0.14 & 0.25 & -0.21\\
-Autonomy & 0.32*** & 0.09** &  & -0.04 & 0.21 & 0.19\\
-Relatedness & 0.45*** & 0.37*** & 0.35*** &  & 0.09 & -0.06\\
-Quality & 0.05 & 0.42*** & 0.11*** & 0.12*** &  & 0.14\\
-Attitudes NL & 0.10*** & 0.31*** & 0.15*** & 0.14*** & 0.44*** & \\
+Core Need &  & 0.46* & -0.18\\
+Quality & 0.37*** &  & 0.19\\
+Attitudes NL & 0.11*** & 0.50*** & \\
 \addlinespace
-Grand Mean & 77.95 & 62.10 & 72.17 & 55.29 & 67.00 & 71.49\\
-Between SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.26 & 12.91\\
-Within SD & 20.83 & 20.89 & 15.15 & 23.29 & 17.43 & 8.11\\
-ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.23 & 0.70\\
-ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.83 & 0.99\\
+Grand Mean & 77.95 & 67.00 & 71.49\\
+Between SD & 14.68 & 9.26 & 12.91\\
+Within SD & 20.83 & 17.43 & 8.11\\
+\addlinespace
+ICC(1) & 0.29 & 0.23 & 0.70\\
+ICC(2) & 0.96 & 0.83 & 0.99\\
 \bottomrule
-\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
-\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
+\multicolumn{4}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
 \end{tabular}}

### 2023-05-31 Robustness-Methods-and-Results.Rmd
robustness re-render with descr

@@
 <!-- TABLES -->
+
+```{r}
+#| label: descrFullWideAppB
+
+vars_full <- c(
+  "Core Need" = "CoreNeed",
+  "Competence" = "Competence",
+  "Autonomy" = "Autonomy",
+  "Relatednesss" = "Relatednesss",
+  "Outgroup Interaction" = "OutgroupInteraction",
+  "Accidental" = "InteractionAccidental",
+  "Quality" = "Quality",
+  "Attitudes NL" = "Attitude"
+)
+
+dt_exp_all <- dt_exp_all %>% 
+  mutate(
+    OutgroupInteraction = (OutgroupInteraction-1.5)
+  )
+
+s1_MlCor_full <- 
+  MlCorMat(
+    data = dt_exp_all %>% filter(study == 1),
+    id = "PID",
+    selection = setdiff(as.character(vars_full), c("InteractionAccidental", "Quality")),
+    labels = setdiff(names(vars_full), c("Accidental", "Quality"))
+  ) 
+s2_MlCor_full <- 
+  MlCorMat(
+    data = dt_exp_all %>% filter(study == 2),
+    id = "PID",
+    selection = as.character(vars_full),
+    labels = names(vars_full)
+  ) 
+s3_MlCor_full <- 
+  MlCorMat(
+    data = dt_exp_all %>% filter(study == 3),
+    id = "PID",
+    selection = as.character(vars_full),
+    labels = names(vars_full)
+  ) 
+all_MlCor_full <- 
+  MlCorMat(
+    data = dt_exp_all,
+    id = "PID",
+    selection = as.character(vars_full),
+    labels = names(vars_full)
+  )
+
+rbind(
+  s1_MlCor_full %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Accidental = "",
+               .before = "Attitudes NL") %>%
+    add_column(Quality = "",
+               .before = "Attitudes NL"),
+  s2_MlCor_full %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable"),
+  s3_MlCor_full %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable"),
+  all_MlCor_full %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      caption = "Full Sample: Correlation Table and Descriptive Statistics",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1)))  %>%
+  kable_classic() %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Correlations" = ncol(s3_MlCor_full),
+      "Descriptives" = nrow(s3_MlCor_full) - ncol(s3_MlCor_full)
+    )
+  ) %>%
+  pack_rows("Study 1", 1, ncol(s1_MlCor_full)) %>%
+  pack_rows("Study 2", ncol(s1_MlCor_full) + 1,
+            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full))) %>%
+  pack_rows("Study 3", sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full)) + 1,  
+            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full))) %>%
+  pack_rows("Across Studies", sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full)) + 1,  
+            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full), ncol(all_MlCor_full))) %>% # fix table position
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05",
+      "Interaction Intent and Interaction Quality were only measured for outgroup interactions in Study 1."
+    )
+  ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/descrFullWideAppB.tex")
+
+```
+
+```{r}
+#| label: descrOutWideAppB
+
+vars_out <- c(
+  "Core Need" = "CoreNeed",
+  "Competence" = "Competence",
+  "Autonomy" = "Autonomy",
+  "Relatednesss" = "Relatednesss",
+  "Practical Need" = "practical_need_dum",
+  "Psychological Need" = "psychological_need_dum",
+  "Accidental" = "InteractionAccidental",
+  "Quality" = "Quality",
+  "Attitudes NL" = "Attitude"
+)
+
+s1_MlCor_out <- 
+  MlCorMat(
+    data = dt_goal_directedness %>% filter(study == 1, OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = as.character(vars_out),
+    labels = names(vars_out)
+  ) 
+s2_MlCor_out <- 
+  MlCorMat(
+    data = dt_goal_directedness %>% filter(study == 2, OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = as.character(vars_out),
+    labels = names(vars_out)
+  ) 
+s3_MlCor_out <- 
+  MlCorMat(
+    data = dt_goal_directedness %>% filter(study == 3, OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = as.character(vars_out),
+    labels = names(vars_out)
+  ) 
+all_MlCor_out <- 
+  MlCorMat(
+    data = dt_goal_directedness %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = as.character(vars_out),
+    labels = names(vars_out)
+  )
+
+rbind(
+  s1_MlCor_out %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable"),
+  s2_MlCor_out %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable"),
+  s3_MlCor_out %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable"),
+  all_MlCor_out %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      caption = "Outgroup Interaction Sample: Correlation Table and Descriptive Statistics",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1)))  %>%
+  kable_classic() %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Correlations" = ncol(s3_MlCor_out),
+      "Descriptives" = nrow(s3_MlCor_out) - ncol(s3_MlCor_out)
+    )
+  ) %>%
+  pack_rows("Study 1", 1, ncol(s1_MlCor_out)) %>%
+  pack_rows("Study 2", ncol(s1_MlCor_out) + 1,
+            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out))) %>%
+  pack_rows("Study 3", sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out)) + 1,  
+            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out))) %>%
+  pack_rows("Across Studies", sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out)) + 1,  
+            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out), ncol(all_MlCor_out))) %>% # fix table position
+  footnote(
+    general = c(
+      "Upper triangle: Between-person correlations;",
+      "Lower triangle: Within-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/descrOutWideAppB.tex")
+
+```
 

### 2023-05-31 Robustness-Methods-and-Results.tex
robustness re-render with descr

@@
 standardized to account for all levels of variance; \textit{b} = 1.88,
-\textit{t}(2.705) = 4.75, \textit{p} = 0.022, \textit{95\%CI}{[} 1.11,
+\textit{t}(2.702) = 4.75, \textit{p} = 0.022, \textit{95\%CI}{[} 1.11,
 2.66{]}). Within this overall analysis, none of the self-determination
 theory needs independently predicted outgroup attitudes to a
-statistically significant extent (all \textit{p} \textgreater{} 0.095).
+statistically significant extent (all \textit{p} \textgreater{} 0.093).
 However, some of the effect sizes were largely comparable to that of the
@@
 \textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all \textit{p}
-\textless{} 0.033). However, across all three studies the fulfillment of
+\textless{} 0.030). However, across all three studies the fulfillment of
 relatedness motives also emerged as a consistent predictor of outgroup
@@
 Online Supplemental Material A).
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{vars\_full }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}
+  \StringTok{"Core Need"} \OtherTok{=} \StringTok{"CoreNeed"}\NormalTok{,}
+  \StringTok{"Competence"} \OtherTok{=} \StringTok{"Competence"}\NormalTok{,}
+  \StringTok{"Autonomy"} \OtherTok{=} \StringTok{"Autonomy"}\NormalTok{,}
+  \StringTok{"Relatednesss"} \OtherTok{=} \StringTok{"Relatednesss"}\NormalTok{,}
+  \StringTok{"Outgroup Interaction"} \OtherTok{=} \StringTok{"OutgroupInteraction"}\NormalTok{,}
+  \StringTok{"Accidental"} \OtherTok{=} \StringTok{"InteractionAccidental"}\NormalTok{,}
+  \StringTok{"Quality"} \OtherTok{=} \StringTok{"Quality"}\NormalTok{,}
+  \StringTok{"Attitudes NL"} \OtherTok{=} \StringTok{"Attitude"}
+\NormalTok{)}
+
+\NormalTok{dt\_exp\_all }\OtherTok{\textless{}{-}}\NormalTok{ dt\_exp\_all }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{mutate}\NormalTok{(}
+    \AttributeTok{OutgroupInteraction =}\NormalTok{ (OutgroupInteraction}\FloatTok{{-}1.5}\NormalTok{)}
+\NormalTok{  )}
+
+\NormalTok{s1\_MlCor\_full }\OtherTok{\textless{}{-}} 
+  \FunctionTok{MlCorMat}\NormalTok{(}
+    \AttributeTok{data =}\NormalTok{ dt\_exp\_all }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{1}\NormalTok{),}
+    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
+    \AttributeTok{selection =} \FunctionTok{setdiff}\NormalTok{(}\FunctionTok{as.character}\NormalTok{(vars\_full), }\FunctionTok{c}\NormalTok{(}\StringTok{"InteractionAccidental"}\NormalTok{, }\StringTok{"Quality"}\NormalTok{)),}
+    \AttributeTok{labels =} \FunctionTok{setdiff}\NormalTok{(}\FunctionTok{names}\NormalTok{(vars\_full), }\FunctionTok{c}\NormalTok{(}\StringTok{"Accidental"}\NormalTok{, }\StringTok{"Quality"}\NormalTok{))}
+\NormalTok{  ) }
+\NormalTok{s2\_MlCor\_full }\OtherTok{\textless{}{-}} 
+  \FunctionTok{MlCorMat}\NormalTok{(}
+    \AttributeTok{data =}\NormalTok{ dt\_exp\_all }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{2}\NormalTok{),}
+    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
+    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_full),}
+    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_full)}
+\NormalTok{  ) }
+\NormalTok{s3\_MlCor\_full }\OtherTok{\textless{}{-}} 
+  \FunctionTok{MlCorMat}\NormalTok{(}
+    \AttributeTok{data =}\NormalTok{ dt\_exp\_all }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{3}\NormalTok{),}
+    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
+    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_full),}
+    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_full)}
+\NormalTok{  ) }
+\NormalTok{all\_MlCor\_full }\OtherTok{\textless{}{-}} 
+  \FunctionTok{MlCorMat}\NormalTok{(}
+    \AttributeTok{data =}\NormalTok{ dt\_exp\_all,}
+    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
+    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_full),}
+    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_full)}
+\NormalTok{  ) }
+
+\FunctionTok{rbind}\NormalTok{(}
+\NormalTok{  s1\_MlCor\_full }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
+    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+    \FunctionTok{add\_column}\NormalTok{(}\AttributeTok{Accidental =} \StringTok{""}\NormalTok{,}
+               \AttributeTok{.before =} \StringTok{"Attitudes NL"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+    \FunctionTok{add\_column}\NormalTok{(}\AttributeTok{Quality =} \StringTok{""}\NormalTok{,}
+               \AttributeTok{.before =} \StringTok{"Attitudes NL"}\NormalTok{),}
+\NormalTok{  s2\_MlCor\_full }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
+    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{),}
+\NormalTok{  s3\_MlCor\_full }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
+    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{),}
+\NormalTok{  all\_MlCor\_full }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
+    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{)}
+\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kbl}\NormalTok{(.,}
+      \AttributeTok{format =} \StringTok{"latex"}\NormalTok{,}
+      \AttributeTok{caption =} \StringTok{"Full Sample: Correlation Table and Descriptive Statistics"}\NormalTok{,}
+      \AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
+      \AttributeTok{align =} \FunctionTok{c}\NormalTok{(}\StringTok{"l"}\NormalTok{, }\FunctionTok{rep}\NormalTok{(}\StringTok{"c"}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(.) }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)))  }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kable\_classic}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{add\_header\_above}\NormalTok{(}
+\NormalTok{    .,}
+    \FunctionTok{c}\NormalTok{(}
+      \StringTok{""}\NormalTok{,}
+      \StringTok{"Correlations"} \OtherTok{=} \FunctionTok{ncol}\NormalTok{(s3\_MlCor\_full),}
+      \StringTok{"Descriptives"} \OtherTok{=} \FunctionTok{nrow}\NormalTok{(s3\_MlCor\_full) }\SpecialCharTok{{-}} \FunctionTok{ncol}\NormalTok{(s3\_MlCor\_full)}
+\NormalTok{    )}
+\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 1"}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 2"}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,}
+            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_full))) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 3"}\NormalTok{, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_full)) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,  }
+            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_full))) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Across Studies"}\NormalTok{, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_full)) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,  }
+            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_full), }\FunctionTok{ncol}\NormalTok{(all\_MlCor\_full))) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
+  \FunctionTok{footnote}\NormalTok{(}
+    \AttributeTok{general =} \FunctionTok{c}\NormalTok{(}
+      \StringTok{"Upper triangle: Between{-}person correlations;"}\NormalTok{,}
+      \StringTok{"Lower triangle: Within{-}person correlations;"}\NormalTok{,}
+      \StringTok{"*** p \textless{} .001, ** p \textless{} .01,  * p \textless{} .05"}\NormalTok{,}
+      \StringTok{"Interaction Intent and Interaction Quality were only measured for outgroup interactions in Study 1."}
+\NormalTok{    )}
+\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{latex\_options =} \StringTok{"scale\_down"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{begin\{table\}"}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{begin\{table\}}\SpecialCharTok{\textbackslash{}n\textbackslash{}\textbackslash{}}\StringTok{begin\{minipage\}[t][}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textheight][t]\{}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textwidth\}"}\NormalTok{, ., }\AttributeTok{fixed =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
+  \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{end\{table\}"}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{end\{minipage\}}\SpecialCharTok{\textbackslash{}n\textbackslash{}\textbackslash{}}\StringTok{end\{table\}"}\NormalTok{, ., }\AttributeTok{fixed =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
+  \FunctionTok{save\_kable}\NormalTok{(}\StringTok{"Tables/descrFullWideAppB.tex"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{vars\_out }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}
+  \StringTok{"Core Need"} \OtherTok{=} \StringTok{"CoreNeed"}\NormalTok{,}
+  \StringTok{"Competence"} \OtherTok{=} \StringTok{"Competence"}\NormalTok{,}
+  \StringTok{"Autonomy"} \OtherTok{=} \StringTok{"Autonomy"}\NormalTok{,}
+  \StringTok{"Relatednesss"} \OtherTok{=} \StringTok{"Relatednesss"}\NormalTok{,}
+  \StringTok{"Practical Need"} \OtherTok{=} \StringTok{"practical\_need\_dum"}\NormalTok{,}
+  \StringTok{"Psychological Need"} \OtherTok{=} \StringTok{"psychological\_need\_dum"}\NormalTok{,}
+  \StringTok{"Accidental"} \OtherTok{=} \StringTok{"InteractionAccidental"}\NormalTok{,}
+  \StringTok{"Quality"} \OtherTok{=} \StringTok{"Quality"}\NormalTok{,}
+  \StringTok{"Attitudes NL"} \OtherTok{=} \StringTok{"Attitude"}
+\NormalTok{)}
+
+\NormalTok{s1\_MlCor\_out }\OtherTok{\textless{}{-}} 
+  \FunctionTok{MlCorMat}\NormalTok{(}
+    \AttributeTok{data =}\NormalTok{ dt\_goal\_directedness }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{1}\NormalTok{, OutgroupInteraction }\SpecialCharTok{==} \StringTok{"Yes"}\NormalTok{),}
+    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
+    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_out),}
+    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_out)}
+\NormalTok{  ) }
+\NormalTok{s2\_MlCor\_out }\OtherTok{\textless{}{-}} 
+  \FunctionTok{MlCorMat}\NormalTok{(}
+    \AttributeTok{data =}\NormalTok{ dt\_goal\_directedness }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{2}\NormalTok{, OutgroupInteraction }\SpecialCharTok{==} \StringTok{"Yes"}\NormalTok{),}
+    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
+    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_out),}
+    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_out)}
+\NormalTok{  ) }
+\NormalTok{s3\_MlCor\_out }\OtherTok{\textless{}{-}} 
+  \FunctionTok{MlCorMat}\NormalTok{(}
+    \AttributeTok{data =}\NormalTok{ dt\_goal\_directedness }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(study }\SpecialCharTok{==} \DecValTok{3}\NormalTok{, OutgroupInteraction }\SpecialCharTok{==} \StringTok{"Yes"}\NormalTok{),}
+    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
+    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_out),}
+    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_out)}
+\NormalTok{  ) }
+\NormalTok{all\_MlCor\_out }\OtherTok{\textless{}{-}} 
+  \FunctionTok{MlCorMat}\NormalTok{(}
+    \AttributeTok{data =}\NormalTok{ dt\_goal\_directedness }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(OutgroupInteraction }\SpecialCharTok{==} \StringTok{"Yes"}\NormalTok{),}
+    \AttributeTok{id =} \StringTok{"PID"}\NormalTok{,}
+    \AttributeTok{selection =} \FunctionTok{as.character}\NormalTok{(vars\_out),}
+    \AttributeTok{labels =} \FunctionTok{names}\NormalTok{(vars\_out)}
+\NormalTok{  ) }
+
+\FunctionTok{rbind}\NormalTok{(}
+\NormalTok{  s1\_MlCor\_out }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
+    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{),}
+\NormalTok{  s2\_MlCor\_out }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
+    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{),}
+\NormalTok{  s3\_MlCor\_out }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
+    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{),}
+\NormalTok{  all\_MlCor\_out }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    t }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{    as.data.frame }\SpecialCharTok{\%\textgreater{}\%}
+    \FunctionTok{rownames\_to\_column}\NormalTok{(., }\StringTok{"Variable"}\NormalTok{)}
+\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kbl}\NormalTok{(.,}
+      \AttributeTok{format =} \StringTok{"latex"}\NormalTok{,}
+      \AttributeTok{caption =} \StringTok{"Outgroup Interaction Sample: Correlation Table and Descriptive Statistics"}\NormalTok{,}
+      \AttributeTok{booktabs =} \ConstantTok{TRUE}\NormalTok{,}
+      \AttributeTok{align =} \FunctionTok{c}\NormalTok{(}\StringTok{"l"}\NormalTok{, }\FunctionTok{rep}\NormalTok{(}\StringTok{"c"}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(.) }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{)))  }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kable\_classic}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{add\_header\_above}\NormalTok{(}
+\NormalTok{    .,}
+    \FunctionTok{c}\NormalTok{(}
+      \StringTok{""}\NormalTok{,}
+      \StringTok{"Correlations"} \OtherTok{=} \FunctionTok{ncol}\NormalTok{(s3\_MlCor\_out),}
+      \StringTok{"Descriptives"} \OtherTok{=} \FunctionTok{nrow}\NormalTok{(s3\_MlCor\_out) }\SpecialCharTok{{-}} \FunctionTok{ncol}\NormalTok{(s3\_MlCor\_out)}
+\NormalTok{    )}
+\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 1"}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 2"}\NormalTok{, }\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,}
+            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_out))) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Study 3"}\NormalTok{, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_out)) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,  }
+            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_out))) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{pack\_rows}\NormalTok{(}\StringTok{"Across Studies"}\NormalTok{, }\FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_out)) }\SpecialCharTok{+} \DecValTok{1}\NormalTok{,  }
+            \FunctionTok{sum}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(s1\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s2\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(s3\_MlCor\_out), }\FunctionTok{ncol}\NormalTok{(all\_MlCor\_out))) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
+  \FunctionTok{footnote}\NormalTok{(}
+    \AttributeTok{general =} \FunctionTok{c}\NormalTok{(}
+      \StringTok{"Upper triangle: Between{-}person correlations;"}\NormalTok{,}
+      \StringTok{"Lower triangle: Within{-}person correlations;"}\NormalTok{,}
+      \StringTok{"*** p \textless{} .001, ** p \textless{} .01,  * p \textless{} .05"}
+\NormalTok{    )}
+\NormalTok{  ) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{kable\_styling}\NormalTok{(}\AttributeTok{latex\_options =} \StringTok{"scale\_down"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{begin\{table\}"}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{begin\{table\}}\SpecialCharTok{\textbackslash{}n\textbackslash{}\textbackslash{}}\StringTok{begin\{minipage\}[t][}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textheight][t]\{}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{textwidth\}"}\NormalTok{, ., }\AttributeTok{fixed =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
+  \FunctionTok{gsub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{end\{table\}"}\NormalTok{, }\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{end\{minipage\}}\SpecialCharTok{\textbackslash{}n\textbackslash{}\textbackslash{}}\StringTok{end\{table\}"}\NormalTok{, ., }\AttributeTok{fixed =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%} \CommentTok{\# fix table position}
+  \FunctionTok{save\_kable}\NormalTok{(}\StringTok{"Tables/descrOutWideAppB.tex"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}

### 2023-05-31 Methods-and-Results.tex
typos

@@
 having an interaction with a non-Dutch (which did not relate to outgroup
-attitudes independently). Additionally, while multi-level regressions
+attitudes independently). Additionally, while multilevel regressions
 are generally robust against unequal cell sizes, we correct for

### 2023-05-31 manuscript.tex
shading fix
typos

@@
 \keywords{
-    Intergroup Contact, Need Fulfillment, Outgroup Attitudes, Interaction Quality, Extensive Longitudinal Data\\
+    Intergroup Contact, Need Fulfillment, Outgroup Attitudes, Interaction Quality, Intensive Longitudinal Data\\
     \textit{Open Science Practices:}
@@
 % Relevance (Version 1 of 2): Migrant Example Version:
-One of the main intergroup societal issues to date, are the struggles of many migrants across the world, hoping to build a positive relationship with the majority group.
+One of the main intergroup societal issues to date, are the struggles of many migrants across the world, hoping to build a new life that includes a positive relationship with the majority group.
 The intergroup contact hypothesis postulates that prejudice can be reduced and favorable attitudes be increased if members of two groups have frequent and positive contact \citep[e.g.,][]{Allport1954b, Hewstone1996, Pettigrew1998}.
@@
 But also in applied settings, policymakers and practitioners are thus far often under-prepared to deal with the occurrences of negative interactions, especially in everyday life contexts.
-Understanding the psychological mechanisms of when and why interactions are perceived as positive is, thus, an important issue for understanding whether an interaction leads to better intergroup perceptions, especially during everyday interactions outside the lab.
+Understanding the psychological mechanisms of when and why interactions are perceived as positive is, thus, an important issue for understanding whether an interaction leads to better intergroup perceptions, especially during everyday interactions.
 
@@
 We propose need fulfillment in particular because needs are a fundamental aspect of the human experience that governs a significant number of emotional, cognitive, and behavioral facets \citep[][]{kreienkamp2022d, kruglanski2002}.
-Importantly to the case of positive intergroup contact, need fulfillment has been highlighted in explaining the success of (close) relationships, psychosocial functioning, as well as reducing conflict between groups.
+Importantly, need fulfillment has particularly been highlighted in explaining the success of (close) relationships, psychosocial functioning, as well as reducing conflict between groups --- all of which are essential to positive intergroup interactions.
 
@@
 The test of Allport's conditions is notably restricted to measurements that report on outgroup interactions because Allport's conditions and interaction quality ratings cannot meaningfully be measured or imputed if participants did not have an interaction.
-Focusing on the interactions in detail, we use a multi-level regression model to test whether interactions that are higher in the fulfillment of Allport's conditions predict more favorable outgroup attitudes.
+Focusing on the interactions in detail, we use a multilevel regression model to test whether interactions that are higher in the fulfillment of Allport's conditions predict more favorable outgroup attitudes.
 We would also expect that such interactions are perceived as higher in interaction quality.
@@
 As our main proposal is concerned with the mechanisms of successful intergroup contact, we again focus on outgroup interaction reports.
-Within a multi-level model, we expect interactions that are higher in situational core need fulfillment to be perceived as more positive, and as a result that these interactions also predict more positive outgroup attitudes.
+Within a multilevel model, we expect interactions that are higher in situational core need fulfillment to be perceived as more positive, and as a result that these interactions also predict more positive outgroup attitudes.
 We also expect the needs mechanism to work at least as well as Allport's conditions.
@@
 Within the individual studies, we begin by testing the most basic assumption of the intergroup contact hypothesis that outgroup attitudes should be more positive after outgroup interactions but not after non-outgroup interactions.
-For this we use multi-level regression analyses, predicting outgroup attitudes from outgroup interaction and non-outgroup interaction dummy variables.
+For this we use multilevel regression analyses, predicting outgroup attitudes from outgroup interaction and non-outgroup interaction dummy variables.
 We also include the participant means as level two predictors to fully disentangle within- (level 1) and between-participant (level 2) effects of intergroup contact \citep[e.g.,][Section 4.6]{snijders2012}.
@@
 Thus, for the main set of analyses, we focus on the reported outgroup interactions only.
-For each study, we will use multi-level regressions to test the main three assertions of our proposal (mirroring the basic steps of a traditional mediation analysis).
+For each study, we will use multilevel regressions to test the main three assertions of our proposal (mirroring the basic steps of a traditional mediation analysis).
 
@@
 Within the third study, we formally measure all of Allport's optimal contact conditions.
-We use multi-level regression models to test whether the fulfillment of Allport's conditions in real-life data predicts more positive outgroup attitudes and higher perceived interaction quality, using the same approach as for the core need fulfillment above.
+We use multilevel regression models to test whether the fulfillment of Allport's conditions in real-life data predicts more positive outgroup attitudes and higher perceived interaction quality, using the same approach as for the core need fulfillment above.
 
@@
 
-We then compare the effect of Allport's contact conditions with our core need fulfillment by comparing the model fit statistics of the two individual models and by adding both concepts to a joint multi-level regression model, to see whether the two approaches explain the same variance in outgroup attitudes.
+We then compare the effect of Allport's contact conditions with our core need fulfillment by comparing the model fit statistics of the two individual models and by adding both concepts to a joint multilevel regression model, to see whether the two approaches explain the same variance in outgroup attitudes.
 
@@
 
-Firstly, to check for the role of alternate psychological needs, we add the fulfillment of self-determination theory needs (i.e., competence, autonomy, and relatedness) to the multi-level regression.
+Firstly, to check for the role of alternate psychological needs, we add the fulfillment of self-determination theory needs (i.e., competence, autonomy, and relatedness) to the multilevel regression.
 We then also compare the model with models that predicts outgroup attitudes from self-determination theory need fulfillments or core need fulfillments only.
@@
 \input{Robustness-Methods-and-Results.tex}
+
+% Tables
+\input{Tables/descrFullWideAppB.tex}
+\input{Tables/descrOutWideAppB.tex}
 

### 2023-05-31 Tracked changes/comparison/main_rev.tex
tracked changes

@@
 % add reference library file
-\addbibresource{../../references.bib}
+\addbibresource{../references.bib}
 
@@
 \keywords{
-    Intergroup Contact, Psychological Needs, Outgroup Attitudes, Interaction Quality, Extensive Longitudinal Data\\
+    Intergroup Contact, Need Fulfillment, Outgroup Attitudes, Interaction Quality, Intensive Longitudinal Data\\
     \textit{Open Science Practices:}
@@
 % Several meta-analytic reviews have found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006}, as well as in intergroup contact interventions outside the lab \citep[][]{Beelmann2014, Lemmer2015}.
-When it comes to what constitutes a positive interaction the most widely used approach has been the idea that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact effect \citep[][]{Allport1954b, Pettigrew1969}.
-However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be necessary to finding positive effects of intergroup contact \citep[][]{Pettigrew2006}.
-Following Allport's original conditions, several additional conditions of optimal contact were proposed, which have largely received the same criticism of not capturing the underlying psychological mechanisms of why an interaction is perceived as positive \citep[for a critical discussion see][]{Pettigrew1986}.
-
-Instead, since the early 21\textsuperscript{st} century, researchers have assumed positive contact and have focused on the psychological processes that explain how positive contacts improve intergroup relations \citep[e.g.
+
+Looking at the past literature, we can essentially separate intergroup contact theory research into a two-step problem.
+Firstly, we need to understand when and why contact becomes a positive contact (contact $\rightarrow$ positive contact) and, secondly, we need to understand when and why positive contacts drive better intergroup relations \citep[positive contact $\rightarrow$ better relations; e.g., see ][]{Allport1954b, Hewstone1996, Pettigrew1998}.
+
+In recent years, research has focused on the second step of understanding the psychological processes that explain how positive contacts improve intergroup relations \citep[e.g.
 see,][]{Paolini2021}.
 Among others, researchers have explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008}, as well as knowledge about the other group \citep[][]{Pettigrew2008c}.
-However, all these advances share a focus on understanding when and how \textit{positive interactions} improve intergroup relations.
-Understanding when and why an interaction is perceived as positive in the first place has remained a tangential focus and it, thus, remains largely unclear which psychological mechanisms drive positive interaction perceptions.
-
-In this article, we focus on the underexplored role of motivation and need fulfillment to understand when and why exactly an interaction is perceived as positive.
-We propose need fulfillment in particular, because a need mechanism builds a strong body of literature highlighting the functional role of need fulfillment in psychosocial functioning, interactions, and intergroup relations --- all of which are fundamental considerations for intergroup contact.
-
-On an individual psychological level, need fulfillment has a long tradition of explaining what drives human adaptation and social relations.
-From the early works of \citet[][]{maslow1943} and \citet[][]{lewin1926e} to more recent works by \citet[][]{Ryan2017} or \citet[][]{Steverink2006}, the fulfillment of needs have been considered a driver of health, well-being, and psychosocial functioning.
-Most relevant to our proposal here, within experience sampling studies (psychological) need fulfillment has been found to explain variations in general well-being \citep[e.g.,][]{sheldon1996, reis2000} as well as well-being during daily interactions \citep[][]{Downie2008}.
-The importance of need fulfillment in interactions has also been substantiated by frameworks such as 'relationships motivation theory', which has collected substantive evidence for the importance of need fulfillment in understanding the success of close relationships \citep[e.g., see][]{knee2023}.
-There is, thus, a wealth of literature highlighting the importance of need fulfillment to positive everyday experiences and well-being.
-
-Beyond the well-being and psychosocial functioning perspective, need fulfillment has recently also seen application as a psychological mechanism in the intergroup relations literature.
-Social identity theory has famously focused on the role of self-esteem needs in understanding how people navigate intergroup contexts \citep[e.g.,][]{abrams1988}.
+Most recently, researchers have even looked at how empowerment need fulfillment during positive intergroup contact can explain some of the beneficial intergroup effects \citep[][]{Hassler2021}.
+There is thus, substantial evidence on the psychological mechanisms that explain the effects of positive contact.
+
+Research on the first step of what makes an interaction positive to begin with tends to be much older, and often more static and contextual.
+The most widely used approach has been the idea that equal status, common goals, collaboration, and structural support during the interaction form Allport's optimal conditions for positive contacts \citep[][]{Allport1954b, Pettigrew1969}.
+Following Allport's original conditions, several additional conditions of optimal contact were proposed, including, stereotype disconfirmation \citep[][]{cook1978} or common language and voluntary interaction (\citealp{wagner1986}; for a critical discussion see \citealp{Pettigrew1986}).
+However, despite their prominence in guiding research on this topic, meeting the contact conditions does not seem to be necessary to finding positive effects of intergroup contact \citep[][]{Pettigrew2006} and more fundamentally, the conditions often do not capture any underlying psychological mechanisms of why an interaction is perceived as positive \citep[e.g.,][]{Pettigrew1998}.
+
+In this article, we focus on the role of motivation and need fulfillment to understand when and why exactly an interaction is perceived as positive.
+We propose need fulfillment in particular because needs are a fundamental aspect of the human experience that governs a significant number of emotional, cognitive, and behavioral facets \citep[][]{kreienkamp2022d, kruglanski2002}.
+Importantly, need fulfillment has particularly been highlighted in explaining the success of (close) relationships, psychosocial functioning, as well as reducing conflict between groups --- all of which are essential to positive intergroup interactions.
+
+On an individual psychological level, there is a long tradition of using need fulfillment to explain what drives human adaptation and social relations.
+From the early works of \citet[][]{maslow1943} and \citet[][]{lewin1926e} to more recent works by \citet[][]{Ryan2017} or \citet[][]{Steverink2006}, the fulfillment of needs have been considered a driver of psychosocial functioning.
+Most relevant to our proposal here, within experience sampling studies need fulfillment has been found to explain variations in well-being during daily interactions \citep[][]{Downie2008} and has been found to be important in understanding the success of close relationships \citep[e.g., see][]{knee2023}.
+In short, an extensive body of scholarly work underscores the significance of need satisfaction in fostering favorable social relationships and social functioning.
+
+Beyond the individual relations literature, need fulfillment has recently also seen application as a psychological mechanism in the intergroup relations literature.
+Social identity theory has focused on the role of self-esteem needs in understanding how people navigate intergroup contexts \citep[e.g.,][]{abrams1988}.
 In the study of conflict and reconciliation, addressing differential needs of victims and perpetrators (i.e., the need for power and the need for morality respectively) increased willingness to reconcile \citep[][]{Shnabel2008}.
 And similarly, addressing a relevant need for identity continuity among refugees in Turkey bolstered resilience in the face of discrimination experiences \citep[][]{Celebi2017}.
-Most recently, an international cross-sectional study has applied a need-based approach to the effects of positive intergroup contact.
-The study found that minority members who generally perceive their positive intergroup contacts to be more empowering tended to report a smaller reduction in social change support than those who did not perceive their average interactions as empowering, especially when the inequality between groups was perceived as illegitimate \citep[][]{Hassler2021}.
-In short, an increasing amount of literature is emphasizing the significance of need satisfaction in comprehending intergroup relations.
+In short, an increasing amount of literature is emphasizing the significance of need satisfaction in understanding intergroup dynamics.
 
@@
 Researchers considering the motivational content would, thus, either test few hyper-specific needs that might not be transferable to other intergroup contexts or they may need to assess a broad and diverse range of motives.
-However, while the individual need content differed between the different lines of research, what unites these approaches has been a focus on fulfilling the situationally relevant needs of people --- especially when we want to understand human functioning in social realms.
-We propose that the different lines of research share an underlying psychological mechanism, namely the motivational experience of need fulfillment.
+However, while the specific need content differed within the different lines of research, what unites most motivational researchers is a focus on fulfilling the situationally relevant needs of people.
+This motivational experience of need fulfillment, thus, brings many of the diverse need content theories together and offers a common psychological mechanism for understanding positive intergroup contact.
+
+Here it is important to briefly define what exactly we mean by need fulfillment and how it differs from need content theories.
 With motivation and need fulfillment we specifically mean the psychological experience of addressing an active and relevant need during the interaction.
@@
 The experience of needing is a more general process that arises when any important motive is thwarted or situationally active and relevant \citep[][]{leander2020, lewin1926e, gollwitzer1985e}.
-It is this perceived need and the perceived fulfillment of needs that we focus on in this article.
-This is not to say that considering specific motives is irrelevant to contact situations but instead we propose that the psychological experience of perceived need fulfillment is a core mechanism in understanding interaction quality perceptions, well-being, and outgroup attitudes.
+It is this perceived needing and the perceived fulfillment of needs that we focus on in this article.
+This is not to say that considering specific motives is irrelevant to contact situations but instead, we propose that the psychological experience of perceived need fulfillment is a core mechanism in understanding interaction quality perceptions, well-being, and outgroup attitudes.
 
@@
 The test of Allport's conditions is notably restricted to measurements that report on outgroup interactions because Allport's conditions and interaction quality ratings cannot meaningfully be measured or imputed if participants did not have an interaction.
-Focusing on the interactions in detail, we use a multi-level regression model to test whether interactions that are higher in the fulfillment of Allport's conditions predict more favorable outgroup attitudes.
-We would also expect that this is due to such interactions being perceived as higher in interaction quality.
+Focusing on the interactions in detail, we use a multilevel regression model to test whether interactions that are higher in the fulfillment of Allport's conditions predict more favorable outgroup attitudes.
+We would also expect that such interactions are perceived as higher in interaction quality.
 \begin{enumerate}[leftmargin=1.5\parindent]
@@
 
-Once the general contact hypothesis is established within the ESM data, our second main aim is to test our main theoretical proposal that the fulfillment of situational psychological needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
+Once the general contact hypothesis is established within the ESM data, our second main aim is to test our main theoretical proposal that the fulfillment of situational needs is meaningfully related to more positive outgroup attitudes following intergroup interactions.
 As our main proposal is concerned with the mechanisms of successful intergroup contact, we again focus on outgroup interaction reports.
-Within a multi-level model, we expect interactions that are higher in situational core need fulfillment to be perceived as more positive, and as a result that these interactions also predict more positive outgroup attitudes.
+Within a multilevel model, we expect interactions that are higher in situational core need fulfillment to be perceived as more positive, and as a result that these interactions also predict more positive outgroup attitudes.
 We also expect the needs mechanism to work at least as well as Allport's conditions.
@@
 
-Before turning to individual studies, two methodological matters need consideration.
-Firstly, we tested most of our hypotheses using multilevel regression models, where measurement occasions (level 1) were nested within participants (level 2).
+Before turning to individual studies, we would like to address a number of conceptual, practical, and methodological considerations.
+One key decision for our studies has been to focus on the minority experience during the contact.
+While the same mechanisms should hold for the experience of members in high-power groups, there is substantially more research available that focuses on the experience of the majority group, and minority perspectives are historically often understudied \citep[e.g.,][]{Dovidio2017}.
+At the same time, however, minority groups are often underprivileged and research is direly needed to understand the more prevalent experiences of stress and health issues among minorities \citep[e.g.,][]{alvidrez2019}.
+
+A second non-trivial aspect of translating the intergroup contact hypothesis into extensive real-world data was the choice of the outcome variable.
+For our main analyses, we chose outgroup attitudes --- the positive or negative evaluation of the other group.
+We chose outgroup attitudes mainly because they are the most common outcome considered within the intergroup contact literature \citep[e.g.,][]{Pettigrew2006, Paolini2021}.
+As the methodology is relatively new to the field, we sought to first replicate (and then extend) the most reliable effects of the contact hypothesis within the ESM data.
+Outgroup attitudes are, however, not without controversy, especially for minority group members.
+Positive outgroup attitudes can increase harmony and reduce the willingness to support social change among the disadvantaged in some cases --- even in the face of injustice \citep[e.g.,][]{dixon2012, saguy2009}.
+While a recent review found the effect to be less conclusive for longitudinally collected data and less consistent for positive interactions (rather than interactions generally), the backfire effect remains an important possibility for the present data \citep[see][]{reimer2023}.
+In order to ensure at least a direct benefit to the minority group members, we also assess the effect of the need fulfillment mechanism on well-being as the dependent variable as part of our robustness analyses below.
+
+In terms of methodological considerations, it is important to note we tested most of our hypotheses using multilevel regression models, where measurement occasions (level 1) were nested within participants (level 2).
 This approach is tolerant to missing data and uneven case numbers within participants.
@@
 Our participants recorded between 2--51 interactions with Dutch outgroup
-members (3.23--91.07\% of individual experience sampling measurements;
-387 of all 1,225 experience sampling
-responses)\footnote{Two participants only recorded two experience sampling measurements each and none of these included outgroup contacts.
-These participants are removed from any analyses that focus on outgroup contacts.}.
-
-\paragraph{Psychological Needs}
+members (\(M\) = 31.71\%, \(SD\) = 19.88\% of the individuals'
+experience sampling measurements; 387 of all 1,225 experience sampling
+responses)Two participants only recorded two experience sampling
+measurements each and none of these included outgroup contacts. These
+participants are removed from any analyses that focus on outgroup
+contacts.
+
+\paragraph{Need Fulfillment}
 
@@
 interaction.''. The participants recorded between 1--43 interactions
-with Dutch majority people (1.64--93.75\% of individual experience
-sampling measurements; 935 of all 4,965 experience sampling responses).
-
-\paragraph{Psychological Needs}
+with Dutch majority people (\(M\) = 20.70\%, \(SD\) = 17.31\% of the
+individual's experience sampling measurements; 935 of all 4,965
+experience sampling responses).
+
+\paragraph{Need Fulfillment}
 
@@
 fulfillment on outgroup attitudes is particularly important for outgroup
-interactions (rather than only need fulfillment in general).
-
-\subsubsection{Interaction intend}
+interactions (rather than need fulfillment in general).
+
+\subsubsection{Interaction intent}
 
@@
 of the autonomy fulfillment effects reached statistical significance. In
-short, find that across our samples, relatedness fulfillment (and to a
-smaller extend competence fulfillment) are instrumental in understanding
-when an outgroup contact leads to more positive outgroup attitudes.
-Importantly, even when considering these effects situational core need
-fulfillment remains a strong and consistent predictor of outgroup
-attitudes.
+short, we find that across our samples, relatedness fulfillment (and to
+a smaller extend competence fulfillment) are instrumental in
+understanding when an outgroup contact leads to more positive outgroup
+attitudes. Importantly, even when considering these effects situational
+core need fulfillment remains a strong and consistent predictor of
+outgroup attitudes.
+
+Overall, we find that our situation need fulfillment model is consistent
+across samples and contexts, and that the need fulfillment effect is
+robust to a wide variety of alternate explanations.
 
@@
 Within the individual studies, we begin by testing the most basic assumption of the intergroup contact hypothesis that outgroup attitudes should be more positive after outgroup interactions but not after non-outgroup interactions.
-For this we use multi-level regression analyses, predicting outgroup attitudes from outgroup interaction and non-outgroup interaction dummy variables.
-We also include the participant means as level two predictors to fully disentangle within- (level 1) and between-participant (level 2) effects of intergroup contact \citep[e.g.,][Section 4.6]{Snijders2012}.
+For this we use multilevel regression analyses, predicting outgroup attitudes from outgroup interaction and non-outgroup interaction dummy variables.
+We also include the participant means as level two predictors to fully disentangle within- (level 1) and between-participant (level 2) effects of intergroup contact \citep[e.g.,][Section 4.6]{snijders2012}.
 
@@
 To assess whether an interaction was accidental (vs.~planned), we asked
-participants with a single item to report the extent to which ``The
+participants with a single item to report the extend to which ``The
 interaction with -X- was accidental''. The respondents were asked to
@@
 little'' (33) and ``somewhat'' (66), to ``a great deal'' (100). In all
-studies, the scale showed a right skew (\textit{mean} = 29.60,
+studies the scale showed a right skew (\textit{mean} = 29.60,
 \textit{sd} = 33.68).
@@
 account for differences in the types of needs that participants commonly
-reported. With practical motives, we refer to specific, tangible goals or
+reported. With practical motives we refer to specific, tangible goals or
 tasks that participants aimed to accomplish during the interaction.
@@
 centered on external outcomes, such as acquiring resources, completing
-tasks, and addressing immediate challenges \citep[][]{}. With
-psychological motives, we refer to underlying motives or desires that are
-more abstract and relate to personal fulfillment and well-being. In
-contrast to practical needs, psychological needs delve into the
-subjective and internal aspects of human experiences. These needs
-pertain to emotions, social connections, and cognitive processes,
+tasks, and addressing immediate challenges \citep[e.g.,][]{oduntan2019}.
+With psychological motives we refer to underlying motives or desires
+that are more abstract and relate to personal fulfillment and
+well-being. In contrast to practical needs, psychological needs delve
+into the subjective and internal aspects of human experiences. These
+needs pertain to emotions, social connections, and cognitive processes,
 reflecting individuals' quest for personal growth, well-being, and
-thriving in social relationships \citep[][]{}. Note that with this
-approach any particular motive can include a practical and/or a
+thriving in social relationships \citep[][]{dweck2017}. Note that with
+this approach any particular motive can include a practical and/or a
 psychological goal-directedness but can also be classified as not having
@@
 whether that need was vague (1) or concrete (2). We, thus, collapsed
-these two categories, making the ratings binary (need absent vs.~need
+these two categories making the ratings binary (need absent vs.~need
 present). With the simpler coding, inter-rater agreement for practical
@@
 We measured experienced well-being using a visual analog scale adapted
-from \citet{davies2022}. Participants were asked to respond to the
+from \citet{davies2022}. Participants were asked to respond to the the
 question ``How do you feel right now?'' using a continuous visual slider
@@
 discuss the results in sequential order --- in every case first
-considering a global test of the model across the three studies and
+considering the a global test of the model across the three studies and
 only then assessing whether the global three-level regression model
@@
 \textit{95\%CI}{[} 2.42, 4.58{]}). We found the same result when we
-assessed each of the three studies individually. In each of the studies,
+assessed each of the three studies individually. In each of the studies
 situational need fulfillment during the outgroup interaction was related
-to higher well-being ratings by the participants (random slopes model,
+with higher well-being ratings by the participants (random slopes model,
 centered within participants; all \textbar{}\textit{b}\textbar{}
@@
 \subsubsection{Need types}
-
-\paragraph{overall}
 
@@
 and/or psychological motives. We again ran a global model, across the
-three studies first. We found that core need fulfillment remains a core
+three studies first. We found that core need fulfillment remain a core
 predictor of outgroup attitudes (random slopes model, grand-mean
@@
 assessing the effects within the individual studies. Within the overall
-model, we find that across the studies core need fulfillment remained a
+model we find that across the studies core need fulfillment remained a
 strong predictor of outgroup attitudes, even after controlling for the
@@
 \textbar{}\textit{b}\textbar{} \textgreater{} 0.06, all \textit{p}
-\textless{} 0.033). However, across all three studies, the fulfillment of
+\textless{} 0.030). However, across all three studies the fulfillment of
 relatedness motives also emerged as a consistent predictor of outgroup
@@
 full results). In short, find that across our samples, relatedness
-fulfillment (and to a smaller extent competence fulfillment) are
+fulfillment (and to a smaller extend competence fulfillment) are
 instrumental in understanding when an outgroup contact leads to more
@@
 
+% Tables
+\input{Tables/descrFullWideAppB.tex}
+\input{Tables/descrOutWideAppB.tex}
+
 \subsection{Conclusion}
-Across the wide variety of robustness analyses, we thus find that the experience of psychological need fulfillment is a robust and flexible predictor of positive outgroup attitudes even when accounting for a range of other and even alternate predictors.
+Across the wide variety of robustness analyses, we thus find that the experience of need fulfillment is a robust and flexible predictor of positive outgroup attitudes even when accounting for a range of other and even alternate predictors.
 However, we also find that the core need fulfillment mechanism does not account for all need-related variance in outgroup attitudes.

### 2023-05-31 Methods-and-Results.tex
typos

@@
 accurately describes the largest groups of migrants in the region
-\citep[][]{GemeenteGroningen2015}.
+\citep[see][for a recent report on the largest migrant groups and see Supplemental Material A for a full overview of the demographic composition, including country of origin]{GemeenteGroningen2015}.
 
@@
 describes the local population of young international medical
-professionals.
+professionals (see Supplemental Materials A for additional demographic information).
 
@@
 there remained a substantial variance in the item and we continued with
-the moderation analysis. We found that both in the overall test as in
+the moderation analysis. We found that both in the overall test and in
 all studies individually key need fulfillment remained a strong
@@
 whether the interaction was accidental (rather than planned). Moreover,
-in none of the analysis did we see a moderation effect of interaction
+in none of the analyses did we see a moderation effect of interaction
 intent nor did we find a main effect of interaction intent. There is,
@@
 \citep[e.g.,][]{reimer2023}, we conducted an additional exploratory
-analysis assessing the effect of need fulfilling outgroup interactions
+analysis assessing the effect of need-fulfilling outgroup interactions
 on reported well-being. Experienced well-being is a common indicator of

### 2023-05-31 manuscript.tex
typos

@@
 One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations.
-We propose to consider the fulfillment of situationally relevant needs during everyday intergroup contact.
+We propose to consider the perceived fulfillment of the situationally most relevant need during everyday intergroup contact.
 We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297; total \textit{N} participants = 207).
-The novel need fulfillment mechanism is consistently a strong predictor of perceived interaction quality as well as positive outgroup attitudes following intergroup interactions.
-The situational needs model is robust to alternative models and works at least as well as Allport's contact conditions.
-As one of the first studies to test intergroup contact theory using extensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
+The novel core need fulfillment mechanism is consistently a strong predictor of perceived interaction quality as well as positive outgroup attitudes following intergroup interactions.
+The model is specific to outgroup contact, robust to various need types, and works at least as well as Allport's contact conditions.
+As one of the first studies to test intergroup contact theory using intensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
 
@@
 However, our participant- and measurement numbers are among the largest sample sizes found within the intensive longitudinal literature \citep[e.g.,][]{AanhetRot2012}.
-Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes (see Supplemental Material A).
-The sample sizes were only increased to allow for between-subjects comparisons and future, more complicated, time-series modeling.
+Additionally, power simulations after the first study showed that our data was sufficiently powered for even small effect sizes (see Supplemental Material B).
+In particular, we found that even our smallest effects of interest would be detectable with 22 participants and 24 measurements per person (assuming the effect sizes of Study 1 and focusing on a power of .8 with a .05 alpha level; see Supplemental Material B for the full analyses).
+We only increased the participant sample sizes in Studies 2 and 3 to allow for between-participant effects across studies and more complicated trajectory analyses, which are not necessary for the hypotheses tested here.
 
@@
 Such an investigation would be possible with the adaptive measurement we used (e.g., by looking at the differential effects of the clustered motives) but would not have been relevant to our theory–focused research question.
-Nonetheless, future research may explore which exact motives are most important in different intergroup contexts.
+Identifying cases where a specific minority faces a common need frustration could be instrumental in addressing systemic challenges.
+Future research may, thus, explore which situations activate or threaten specific motives \citep[e.g.,][]{gollwitzer1985e, leander2020} and which exact motives are most important in different intergroup contexts.
 

### 2023-05-31 Methods-and-Results.Rmd
robustness re-render with descr
interaction qual cor added

@@
 The sample consisted of relatively young, educated, and western migrants from the global north ($M_{age}$ = `r format(round(mean(workerSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(workerSampleInfo$age),2), nsmall=2)`, `r nrow(workerSampleInfo %>% filter(gender == "Female"))` women, `r nrow(workerSampleInfo %>% filter(occupation == "student"))` students).
-The sample accurately describes the largest groups of migrants in the region \citep[][]{GemeenteGroningen2015}.
+The sample accurately describes the largest groups of migrants in the region \citep[see][for a recent report on the largest migrant groups and see Supplemental Material A for a full overview of the demographic composition, including country of origin]{GemeenteGroningen2015}.
 
@@
 
-\paragraph{Perceived Interaction Quality}To assess ratings of the perceived interaction quality, participants rated the statement “\textit{Overall the interaction was …}” on two continuous slider scales measuring pleasantness \citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
+```{r}
+#| label: s1_quality_cor
+#| include: false
+library(correlation)
+
+s1_quality_cor <- misty::multilevel.cor(
+  dtWorkerSupp$workerInteractionType %>%
+    filter(OutgroupInteractionLab == "Yes") %>%
+    select(quality_overall_1, quality_meaning_1),
+  dtWorkerSupp$workerInteractionType %>%
+    filter(OutgroupInteractionLab == "Yes") %>%
+    select(PID),
+  output = FALSE
+)
+```
+
+\paragraph{Perceived Interaction Quality}To assess ratings of the perceived interaction quality, participants rated the statement “\textit{Overall the interaction was …}” on two continuous slider scales measuring pleasantness (from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50)).
+The items formed a coherent concept within the participants ($r_{within}$ = `r s1_quality_cor$result$with.cor[2] %>% round(2) %>% format(., nsmall = 2)`, \textit{p} `r ifelse(s1_quality_cor$result$with.p[3] < 0.001, "< .001", paste0("= ", s1_quality_cor$result$with.p[3] %>% round(3) %>% format(., nsmall = 3)))`).
+We adapted the from \citet[][]{Downie2008}, who validated the approach.
 
@@
 Using a multilevel regression, we find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently).
-Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by using centered predictors and reintroducing the means as level two predictors (\citealp{yaremych2021a}; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
+Additionally, while multilevel regressions are generally robust against unequal cell sizes, we correct for inequalities by using centered predictors and reintroducing the means as level two predictors (\citealp{yaremych2021a}; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance.
 This is unusual and might indicate that the effect is very consistent across participants.
@@
 The sample consisted of relatively young migrants, who were mostly from the global north ($M_{age}$ = `r format(round(mean(studentSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(studentSampleInfo$age),2), nsmall=2)`, `r nrow(studentSampleInfo %>% filter(gender == "women"))` women).
-The sample fairly accurately describes the local population of international students.
+The sample fairly accurately describes the local population of international students (see Supplemental Materials A for additional demographic information).
 
@@
 
-\paragraph{Perceived Interaction Quality}The ratings of the perceived contact quality were identical to Study 1.
+```{r}
+#| label: s2_quality_cor
+#| include: false
+
+s2_quality_cor <- misty::multilevel.cor(
+  dtStudentSupp$studentInteractionType %>%
+    filter(OutgroupInteractionLab == "Yes") %>%
+    select(quality_overall, quality_meaning),
+  dtStudentSupp$studentInteractionType %>%
+    filter(OutgroupInteractionLab == "Yes") %>%
+    select(PID),
+  output = FALSE
+)
+```
+
+\paragraph{Perceived Interaction Quality}The ratings of the perceived contact quality were identical to Study 1 (item correlation: $r_{within}$ = `r s2_quality_cor$result$with.cor[2] %>% round(2) %>% format(., nsmall = 2)`, \textit{p} `r ifelse(s2_quality_cor$result$with.p[3] < 0.001, "< .001", paste0("= ", s2_quality_cor$result$with.p[3] %>% round(3) %>% format(., nsmall = 3)))`).
 
@@
 The sample consisted of relatively young migrants ($M_{age}$ = `r format(round(mean(medicalSampleInfo$age),2), nsmall=2)`, $SD_{age}$ = `r format(round(sd(medicalSampleInfo$age),2), nsmall=2)`, `r nrow(medicalSampleInfo %>% filter(gender == "women"))` women).
-The sample fairly accurately describes the local population of young international medical professionals.
+The sample fairly accurately describes the local population of young international medical professionals (see Supplemental Materials A for additional demographic information).
 
@@
 
-\paragraph{Psychological Needs}The measurement of the core situational need and its fulfillment was identical to Study 2.
+\paragraph{Need Fulfillment}The measurement of the core situational need and its fulfillment was identical to Study 2.
 
@@
 For full psychometric information see Online Supplementary Material A.
+
+```{r}
+#| label: s3_quality_cor
+#| include: false
+
+s3_quality_cor <- misty::multilevel.cor(
+  dtMedical$full %>%
+    filter(OutgroupInteractionLab == "Yes") %>%
+    select(qualityOverall, qualityMeaning),
+  dtMedical$full %>%
+    filter(OutgroupInteractionLab == "Yes") %>%
+    select(PID),
+  output = FALSE
+)
+```
+
+\paragraph{Perceived Interaction Quality}The ratings of the perceived contact quality were identical to Study 1 and 2 (item correlation: $r_{within}$ = `r s3_quality_cor$result$with.cor[2] %>% round(2) %>% format(., nsmall = 2)`, \textit{p} `r ifelse(s3_quality_cor$result$with.p[3] < 0.001, "< .001", paste0("= ", s3_quality_cor$result$with.p[3] %>% round(3) %>% format(., nsmall = 3)))`).
 
@@
 Nonetheless, there remained a substantial variance in the item and we continued with the moderation analysis.
-We found that both in the overall test as in all studies individually key need fulfillment remained a strong predictor of outgroup attitudes, even when accounting for differences in whether the interaction was accidental (rather than planned).
-Moreover, in none of the analysis did we see a moderation effect of interaction intent nor did we find a main effect of interaction intent.
+We found that both in the overall test and in all studies individually key need fulfillment remained a strong predictor of outgroup attitudes, even when accounting for differences in whether the interaction was accidental (rather than planned).
+Moreover, in none of the analyses did we see a moderation effect of interaction intent nor did we find a main effect of interaction intent.
 There is, thus, consistent evidence that the need fulfillment mechanism was not meaningfully different for more accidental interactions.
@@
 \subsubsection{Well-being outcome}
-Given the well-established criticism that more positive outgroup attitudes might not always be beneficial for minority group members \citep[e.g.,][]{reimer2023}, we conducted an additional exploratory analysis assessing the effect of need fulfilling outgroup interactions on reported well-being.
+Given the well-established criticism that more positive outgroup attitudes might not always be beneficial for minority group members \citep[e.g.,][]{reimer2023}, we conducted an additional exploratory analysis assessing the effect of need-fulfilling outgroup interactions on reported well-being.
 Experienced well-being is a common indicator of health and an important life quality measurement in itself, especially for migrants or other minority groups \citep[e.g.,][]{bhugra2011}.

### 2023-05-31 Methods-and-Results.tex
interaction qual cor added

@@
 rated the statement ``\textit{Overall the interaction was …}'' on two
-continuous slider scales measuring pleasantness
-\citep[from unpleasant (-50) to pleasant (+50)) and meaningfulness (from superficial (-50) to meaningful (+50); both items adapted from][]{Downie2008}.
+continuous slider scales measuring pleasantness (from unpleasant (-50)
+to pleasant (+50)) and meaningfulness (from superficial (-50) to
+meaningful (+50)). The items formed a coherent concept within the
+participants (\(r_{within}\) = 0.54, \textit{p} \textless{} .001). We
+adapted the from \citet[][]{Downie2008}, who validated the approach.
 
@@
 having an interaction with a non-Dutch (which did not relate to outgroup
-attitudes independently). Additionally, while multilevel regressions
-are generally robust against unequal cell sizes, we correct for
-inequalities by using centered predictors and reintroducing the means as
-level two predictors (\citealp{yaremych2021a}; for full results see
+attitudes independently). Additionally, while multilevel regressions are
+generally robust against unequal cell sizes, we correct for inequalities
+by using centered predictors and reintroducing the means as level two
+predictors (\citealp{yaremych2021a}; for full results see
 \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis},
@@
 20.24, \(SD_{age}\) = 2.12, 84 women). The sample fairly accurately
-describes the local population of international students.
+describes the local population of international students (see
+Supplemental Materials A for additional demographic information).
 
@@
 
-The ratings of the perceived contact quality were identical to Study 1.
+The ratings of the perceived contact quality were identical to Study 1
+(item correlation: \(r_{within}\) = 0.39, \textit{p} \textless{} .001).
 
@@
 describes the local population of young international medical
-professionals (see Supplemental Materials A for additional demographic information).
+professionals (see Supplemental Materials A for additional demographic
+information).
 
@@
 
-\paragraph{Psychological Needs}
+\paragraph{Need Fulfillment}
 
@@
 information see Online Supplementary Material A.
+
+\paragraph{Perceived Interaction Quality}
+
+The ratings of the perceived contact quality were identical to Study 1
+and 2 (item correlation: \(r_{within}\) = 0.46, \textit{p} \textless{}
+.001).
 

### 2023-06-01 Supplemental Material D - Coding Protocol/margins/FactSheet.tex
SI D masked

--- 2023-05-19 Supplemental Material B - Coding Protocol/margins/FactSheet.tex
@@
 \NFtext{\textbf{Dataset} Acculturation over Time Studies}\\
-\NFtext{\textbf{Instances Per Dataset} \hl{X,XXX} free text responses in \hl{XX} topics}\\
+\NFtext{\textbf{Instances Per Dataset} 2,995 free text responses in 47 topics}\\
 
@@
 \NFelement{Sample or Complete}{}{Complete}\\
-\NFelement{Missing Data}{}{\hl{X.X}\% excluded}\\
+\NFelement{Missing Data}{}{10.33\% excluded}\\
 \NFelement{Sensitive Information }{}{free text responses}\\
@@
 \NFrule
-\NFelement{Study 1}{\hl{X,XXX} interactions of \hl{X,XXX} measurements}{\hl{XX.X}\%}\\
+\NFelement{Study 1}{387 interactions of 1,225 measurements}{31.59\%}\\
 \NFrule
-\NFelement{Study 2}{\hl{X,XXX} interactions of \hl{X,XXX} measurements}{\hl{XX.X}\%}\\
+\NFelement{Study 2}{931 interactions of 4,965 measurements}{18.75\%}\\
 \NFrule
-\NFelement{Study 3}{\hl{X,XXX} interactions of \hl{X,XXX} measurements}{\hl{XX.X}\%}\\
+\NFelement{Study 3}{1,677 interactions of 4,107 measurements}{40.83\%}\\
 % \NFrule

### 2023-06-01 Supplemental Material A - Annotated Analysis/Supplemental-Material-A-Annotated-Analysis.tex
supplemental doc init

% define document type (i.e., template. Here: A4 APA manuscript with 12pt font)
\documentclass[man, 12pt, a4paper]{apa7}

% add packages
\usepackage[american]{babel}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[style=apa, sortcites=true, sorting=nyt, backend=biber, natbib=true, uniquename=false, uniquelist=false, useprefix=true]{biblatex}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{setspace,caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{lipsum}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{fourier}
\usepackage{stackengine}
\usepackage{scalerel}
\usepackage{fontawesome}
\usepackage[normalem]{ulem}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{afterpage}
\usepackage{float}
\usepackage{titling}
\usepackage{censor}
\usepackage{tcolorbox}

% formatting links in the PDF file
\hypersetup{
pdfpagemode={UseOutlines},
bookmarksopen=true,
bookmarksopenlevel=0,
hypertexnames=false,
colorlinks   = true, %Colours links instead of ugly boxes
urlcolor     = blue, %Colour for external hyperlinks
linkcolor    = blue, %Colour of internal links
citecolor   = cyan, %Colour of citations
pdfstartview={FitV},
unicode,
breaklinks=true,
}

% language settings
\DeclareLanguageMapping{american}{american-apa}

% add reference library file
\addbibresource{../references.bib}

% Title and header
\title{Supplemental Information B: Annotated Analyses Scoping Review}
\shorttitle{SI B: Annotated Analyses}
\author{Jannis Kreienkamp, Laura F. Bringmann, Raili F. Engler, Peter de Jonge, Kai Epstude}
%\author{[authors masked for peer review]}

% set indentation size
\setlength\parindent{1.27cm}

% adapt table and figure labels
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

% Start of the main document:
\begin{document}

% add title information (incl. title page and abstract)
\begin{titlepage}
	{\noindent\Large Supplementary Information for \par}
	\vspace{0.5cm}
	{\noindent\Large The Migration Experience: A Conceptual Framework and Systematic Scoping Review of Psychological Acculturation\par}
	\vspace{1.5cm}
	{\noindent\LARGE\bfseries \thetitle \par}
	\vspace{2cm}
	{\noindent\Large\itshape \theauthor \par}
	\vfill
	\noindent Corresponding Author: Jannis Kreienkamp\par
	\noindent E-mail: j.kreienkamp@rug.nl\par
	%\noindent Corresponding Author: [masked for peer review]\par
	%\noindent E-mail: [masked for peer review]\par
	\vfill

    % Bottom of the page
	{\noindent Last updated: \today\par}
\end{titlepage}

% add title again on page 1 (after title page)
\begin{center}
   \textbf{\thetitle} 
\end{center}

This supplementary information documents the methodology and results of our systematic scoping review. As part of our open supplemental materials, we share the full RMarkdown file which offers an annotated version of our all analysis steps. This file offers a transparent and reproducible analysis code, which includes full author commentary. We rendered the RMarkdown as an interactive HTML file, which we host as part of our open GitHub repository. We recommend the rendered version for almost all readers (full R code is also available via the rendered version).

\vspace{.5cm}
\begin{tcolorbox}
    \vspace{0.2cm} \centering 
    \href{https://janniscodes.github.io/acculturation-review/Supplemental-Material-B-Annotated-Analysis}{https://acculturation-review.com/Supplemental-Material-B-Annotated-Analysis}
    \vspace{0.2cm} 
\end{tcolorbox}

For readers interested in the raw files, the raw RMarkdown file is available in our OSF repository \citep[see][]{Kreienkamp2021a} and can also be accessed as part of the full GitHub repository \citep[][]{Kreienkamp2021b}.

\printbibliography

\end{document}

### 2023-06-01 Supplemental-Material-B-Power-Simulation.Rmd
supplemental doc init

---
title: "Supplemental Information C: Power Simulations"
subtitle: "Supplemental Material for 'Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies'"
author:
- ██████ ██████████^1^
- ██████████ ████████^1^
- █████ █████████^1^
- █████ ██ █████^1^
- ███ ███████^1^
- ^1^██████████ ██ █████████, Department of Psychology
- "Author Information:"
- "Correspondence concerning this article should be addressed to ██████ ██████████, ██████████ ██ ██████████, █████████ ██ ██████████, █████ ██████████ ███, ████ ██ █████████ ████████████████. E-mail: █████████████████"
- 'The main manuscript is available at <a href="https://www.doi.org/ToBePublished" target="_blank">doi.org/ToBePublished</a>'
- 'The data repository for this manuscript is available at <a href="https://osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970" target="_blank">osf.io/pr9zs/?view_only=1ea47bb646694632a764dead807ef970</a>'
- 'The GitHub repository for this manuscript is available at <a href="https://github.com/maskedForPeerReview" target="_blank">github.com/maskedForPeerReview</a>'
date: "Last updated: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::html_document2:
    fig_caption: yes
    md_extensions: +footnotes
    code_folding: hide
    mathjax: default
    theme: yeti
    toc: yes
    toc_float: yes
    number_sections: false
    css: style.css
    includes:
      in_header: "_includes/head-custom-rmd.html" 
editor_options:
  chunk_output_type: console
bibliography: references.bib
csl: apa.csl
header-includes:
   - \usepackage{amsmath, nccmath}
---

<style type="text/css">
.main-container {
  max-width: 1300px;
  margin-left: auto;
  margin-right: auto;
}
.table {
  margin-left:auto; 
  margin-right:auto;
}
</style>

```{r setup, include=FALSE}
# R Studio Clean-Up
cat("\014") # clear console
# rm(list=ls()) # clear workspace - use restart R instead [cmd/alt + shift + F10]
gc() # garbage collector

# Install and Load Packages
# !IMPORTANT!
# BEFORE FIRST RENDER:
# To install all relevant packages please run "renv::restore()" (or renv::init() and then initiate from lockfile) in the console before the first use to ensure that all packages are using the correct version.
# to store the packages in a contained library within the project folder: renv::settings$use.cache(FALSE) and add 'RENV_CONFIG_SANDBOX_ENABLED = FALSE' to an '.Renviron' file
lib <- c(
  "rmarkdown",
  "knitr",
  "remedy",
  "bookdown",
  "brms",
  "psych",
  "ggplot2",
  "ggthemes",
  # "haven",
  "RColorBrewer",
  # "plotly",
  "gridExtra",
  "ggpattern",
  "ggridges",
  "binom",
  "iterators",
  "pbkrtest",
  "plotrix",
  "RLRsim",
  "stats",
  "methods",
  "utils",
  "graphics",
  "grDevices",
  "car",
  "testthat",
  "simr",
  "data.table",
  "lme4",
  "lmerTest",
  # "nlme",
  "jtools",
  # "gtsummary",
  "sessioninfo",
  # "tibble",
  "pander",
  # "devtools",
  # "mada",
  #"tidyr",
  #"tidyverse",
  "plyr",
  "dplyr",
  # "Hmisc",
  "kableExtra",
  # "papaja",
  "stringr"#,
  # "stringi",
  # "reshape2",
  # "lubridate",
  # "purrr",
  # "metafor"
)
invisible(lapply(lib, library, character.only = TRUE))
rm(lib)

# Load Custom Packages
source("./scripts/functions/fun.panel.R")
source("./scripts/functions/themes.R")
# source("./scripts/functions/binaryCor.R")
# source("./scripts/functions/MlCorMat.R")
# source("./scripts/functions/MlTbl.R")
# source("./scripts/functions/metaLmer.R")

# Markdown Options
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) # set working directory
knitr::opts_knit$get("root.dir") # check working directory
options(
  scipen = 999,
  digits = 4,
  width = 400
) # removes scientific quotation
# knitr::opts_chunk$set(echo = TRUE, cache = F, cache.path = rprojroot::find_rstudio_root_file('cache/')) # cache settings
knitr::knit_hooks$set(
  error = function(x, options) {
    paste('\n\n<div class="alert alert-danger">',
      gsub("##", "\n", gsub("^##\ Error", "**Error**", x)),
      "</div>",
      sep = "\n"
    )
  },
  warning = function(x, options) {
    paste('\n\n<div class="alert alert-warning">',
      gsub("##", "\n", gsub("^##\ Warning:", "**Warning**", x)),
      "</div>",
      sep = "\n"
    )
  },
  message = function(x, options) {
    paste('\n\n<div class="alert alert-info">',
      gsub("##", "\n", x),
      "</div>",
      sep = "\n"
    )
  }
)
htmltools::tagList(rmarkdown::html_dependency_font_awesome())

# Global Chunk Options
knitr::opts_chunk$set(
  fig.width = 12,
  fig.height = 8,
  fig.path = "Figures/",
  echo = TRUE,
  cache = TRUE,
  warning = FALSE,
  message = FALSE
)

# set ggplot theme
theme_set(theme_Publication())
```

<br/>

<i class="fas fa-exclamation-circle"></i> Note. Boxplots display the interquartile range (IQR, center box), and the whiskers extend 1.5*IQR from the lower and upper hinge. The white point indicates the mean and the white center line indicates the median.

<br/>

# Data Import

```{r}
#| label: import data

load("data/wrangled.RData")
```

# Extract Effects for Simulation

## Prepare Data

```{r}
#| label: data prep

# TBD
```

# ML Regression

Run multilevel regression to extract the effect sizes and covariance matrices

```{r}
#| label: run regression

# run regresion 
lmer_quality_contemporary <-
  lmer(
    quality_overall_1 ~ 
      keymotive_fulfillemt_1_cwc + (1 + keymotive_fulfillemt_1_cwc | PID),
    data = dtWorkerSupp$workerOutWithinBetween
  )
lmer_attitude_contemporary <-
  lmer(
    thermometerDutch_1 ~ 
      keymotive_fulfillemt_1_cwc + (1 + keymotive_fulfillemt_1_cwc | PID),
    data = dtWorkerSupp$workerOutWithinBetween
  )
lmer_attitude_need_quality_contemporary <-
  lmer(
    thermometerDutch_1 ~
      keymotive_fulfillemt_1_cwc + quality_overall_1_cwc + (1 + keymotive_fulfillemt_1_cwc + quality_overall_1_cwc | PID),
    data = dtWorkerSupp$workerOutWithinBetween
  )

```

For the main analyses we have four fixed effects of interest. (1) The effect of need fulfillment on interaction quality: _b_ = `r round(fixef(lmer_quality_contemporary)['keymotive_fulfillemt_1_cwc'], 3)`, (2) the effect of need fulfillment on outgroup attitudes: _b_ = `r round(fixef(lmer_attitude_contemporary)['keymotive_fulfillemt_1_cwc'], 3)`, (3) the effect of need fulfillment on outgroup attitudes while controlling for interaction quality: _b_ = `r round(fixef(lmer_attitude_need_quality_contemporary)['keymotive_fulfillemt_1_cwc'], 3)`, as well as (4) the effect of interaction quality on outgroup attitudes while controlling for need fulfillment: _b_ = `r round(fixef(lmer_attitude_need_quality_contemporary)['quality_overall_1_cwc'], 3)`.

# Power Simulation Parameters

```{r}
#| label: simulation setup
nsim <- 1000
progress <- FALSE
n_ppt <- 250
n_measure <- 180 # 3 months with 2 measurements per day

# extrapolate data:
sim_n_quality <- extend(lmer_quality_contemporary, along="PID", n = n_ppt)
sim_n_attitude <- extend(lmer_attitude_contemporary, along="PID", n = n_ppt)
sim_n_attitude_full <- extend(lmer_attitude_need_quality_contemporary, along="PID", n = n_ppt)

# extrapolate data:
sim_t_quality <- extend(lmer_quality_contemporary, within="PID", n = n_measure)
sim_t_attitude <- extend(lmer_attitude_contemporary, within="PID", n = n_measure)
sim_t_attitude_full <- extend(lmer_attitude_need_quality_contemporary, within="PID", n = n_measure)
```

# Power Simulation Participant Numbers

Simulate different participant numbers for all fixed effects.

## Power of `Quality ~ NeedFulfill` for different numbers of participants

```{r}
#| label: participant simulation Quality NeedFulfill
#| warning: FALSE
#| error: FALSE

# Run and plot simulations
pc_n_quality_need = powerCurve(
  fit = sim_n_quality,
  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
  along = "PID",
  progress = progress,
  breaks = seq(1, 12, 1),
  nsim = nsim
)
plot(pc_n_quality_need) +
  title("Quality given Need Fulfillment [participant numbers]")
```

## Power of `Attitude ~ NeedFulfill` for different numbers of participants

```{r}
#| label: participant simulation Attitude NeedFulfill
#| warning: FALSE
#| error: FALSE

# Run and plot simulations
pc_n_attitude_need = powerCurve(
  fit = sim_n_attitude,
  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
  along = "PID",
  progress = progress,
  breaks = seq(1, 45, 1),
  nsim = nsim
)
plot(pc_n_attitude_need) +
  title("Attitudes given Need Fulfillment [participant numbers]")
```

## Power of `Attitude ~ NeedFulfill + Quality` for different numbers of participants

we expect this to be super small. Keep in mind that the _b_ = `r round(fixef(lmer_attitude_need_quality_contemporary)["keymotive_fulfillemt_1_cwc"],3)`. So even with a large number of participants, we would not expect these effects to be meaningful.

```{r}
#| label: participant simulation Attitude NeedFulfill given Quality
#| warning: FALSE
#| error: FALSE

# Run and plot simulations
pc_n_attitude_need = powerCurve(
  fit = sim_n_attitude_full,
  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
  along = "PID",
  progress = progress,
  breaks = seq(10, 250, 10),
  nsim = nsim
)
plot(pc_n_attitude_need) +
  title("Attitudes given Need Fulfillment (controling for Quality) [participant numbers]")
```

## Power of `Attitude ~ Quality` given NeedFulfill for different numbers of participants

```{r}
#| label: participant simulation Attitude Qaulity given NeedFulfill
#| warning: FALSE
#| error: FALSE

# Run and plot simulations
pc_n_attitude_full_quality = powerCurve(
  fit = sim_t_attitude_full,
  test = simr::fixed("quality_overall_1_cwc", "t"),
  along = "PID",
  progress = progress,
  breaks = c(seq(1, 25, 1), seq(30, 100, 10)),
  nsim = nsim
)
plot(pc_n_attitude_full_quality) +
  title("Attitudes given Quality (controlling for Need Fulfillment) [participant numbers]")
```

# Power Simulation Measurement Numbers

Simulate different number of within person measurements.

## Power of `Quality ~ NeedFulfill` for different numbers of measurements

```{r}
#| label: measurement simulation Quality NeedFulfill
#| warning: FALSE
#| error: FALSE

# Run and plot simulations
pc_t_quality_need = powerCurve(
  fit = sim_t_quality,
  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
  within = "PID",
  progress = progress,
  breaks = seq(1, 20, 1),
  nsim = nsim
)
plot(pc_t_quality_need) +
  title("Quality given Need Fulfillment [measurement numbers]")
```

## Power of `Attitude ~ NeedFulfill` for different numbers of measurements

```{r}
#| label: measurement simulation Attitude NeedFulfill
#| warning: FALSE
#| error: FALSE

# Run and plot simulations
pc_t_attitude_need = powerCurve(
  fit = sim_t_attitude,
  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
  within = "PID",
  progress = progress,
  breaks = seq(1, 25, 1),
  nsim = nsim
)
plot(pc_t_attitude_need) +
  title("Attitudes given Need Fulfillment [measurement numbers]")
```

## Power of `Attitude ~ NeedFulfill` given Quality for different numbers of measurements

we expect this to be super small. Keep in mind that the _b_ = `r round(fixef(lmer_attitude_need_quality_contemporary)["keymotive_fulfillemt_1_cwc"],3)`. So even with a large number of measurements, we would not expect these effects to be meaningful.

```{r}
#| label: measurement simulation Attitude NeedFulfill given Quality
#| warning: FALSE
#| error: FALSE

# Run and plot simulations
pc_t_attitude_full_need = powerCurve(
  fit = sim_t_attitude_full,
  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
  within = "PID",
  progress = progress,
  breaks = seq(10, 180, 10),
  nsim = nsim
)
plot(pc_t_attitude_full_need) +
  title("Attitudes given Need Fulfillment (controlling for Quality) [measurement numbers]")
```

## Power of `Attitude ~ Quality` given NeedFulfill for different numbers of measurements

```{r}
#| label: measurement simulation Attitude Qaulity given NeedFulfill
#| warning: FALSE
#| error: FALSE

# Run and plot simulations
pc_t_attitude_full_quality = powerCurve(
  fit = sim_t_attitude_full,
  test = simr::fixed("quality_overall_1_cwc", "t"),
  within = "PID",
  progress = progress,
  breaks = seq(1, 15, 1),
  nsim = nsim
)
plot(pc_t_attitude_full_quality) +
  title("Attitudes given Quality (controlling for Need Fulfillment) [measurement numbers]")
```

# Export data and plots

```{r}
#| label: export

# save simulations, because this takes for freakin' ever.      
save(list = ls(pattern = "plt."), 
     file = "data/S1_Workers/processed/PowerSimPlots.RData")

#load("PowerSimPlots.RData")
```

# Software Information

The full session information with all relevant system information and all loaded and installed packages is available in the collapsible section below.

<details>
  <summary>System Info</summary>

  \renewcommand{\arraystretch}{0.8} <!-- decrease line spacing for the table -->
```{r Reproducibility-SessionInfo-R-environment, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center", out.width='100%', results='asis'}
df_session_platform <- devtools::session_info()$platform %>%
  unlist(.) %>%
  as.data.frame(.) %>%
  rownames_to_column(.)

colnames(df_session_platform) <- c("Setting", "Value")

kbl(
  df_session_platform,
  booktabs = T,
  align = "l",
  caption = "R environment session info for reproducibility of results" # complete caption for main document
) %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```
  \renewcommand{\arraystretch}{1} <!-- reset row height/line spacing -->
 </details>
 <br>
 <details>
  <summary>Package Info</summary>

\renewcommand{\arraystretch}{0.6} <!-- decrease line spacing for the table -->
```{r Reproducibility-SessionInfo-R-packages, echo=FALSE, message=FALSE, warning=FALSE, fig.align="center", out.width='100%', results='asis'}
df_session_packages <- devtools::session_info()$packages %>%
  as.data.frame(.) %>%
  filter(attached == TRUE) %>%
  dplyr::select(loadedversion, date, source) %>%
  rownames_to_column()

colnames(df_session_packages) <- c("Package", "Loaded version", "Date", "Source")

kbl(
  df_session_packages,
  booktabs = T,
  align = "l",
  caption = "Package info for reproducibility of results" # complete caption for main document
) %>%
  kable_classic(
    full_width = F,
    lightable_options = "hover",
    html_font = "Cambria"
  )
```
\renewcommand{\arraystretch}{1} <!-- reset row height/line spacing -->
</details>
<br>
<details>
  <summary>Full Session Info (including loaded but unattached packages --- for troubleshooting only)</summary>
    `r pander(sessionInfo(), compact = FALSE)`
</details>

--------------------------------------------------------------------

</br>

### 2023-06-01 Supplemental-Material-B-Power-Simulation_between.Rmd
supplemental doc init

--- 2023-06-01 Supplemental-Material-B-Power-Simulation.Rmd
@@
   # "nlme",
-  "jtools",
+  # "jtools",
   # "gtsummary",
@@
 
+Generally, power considerations of mixed effects model such as repeated measures ANCOVAs and multi-level regressions are difficult to estimate because of the complex covariance structures.
+We ran simulation-studies based on our initial results following the first study.
+We found that sufficient sample sizes heavily depended on the type and size of the effect.
+When we simulated models with the marginalization sub-scale (which was the best distributed with mostly small to medium effect sizes), we found that for between-subjects effects, a sample size of 80 participants would have been sufficient (power above .8) with two measurements (see Figure 9 for an illustration).
+However, for the same between-subject effects we did not reach a power above .8 with any increase of repeated follow-up measurements (based on model extrapolations with a fixed _n_ = 20; tested up to 12 months).
+The within time effect, on the other hand, was estimated well above .8 by the seventh measurement (i.e., after six months, see Figure 9).
+The cross-level interaction effects (within-between) were largely a mixture of their individual effects and changes in measurement numbers and sample size affected the models accordingly.
+We, therefore, urge researchers to rely on pilot data and to run extensive simulation studies to maximize effort and feasibility (i.e., sufficient power).
+
 # Data Import
@@
 
-load("data/wrangled.RData")
+load("data/S1_Workers/processed/df.btw.RData")
 ```
@@
 
-# TBD
+# prepare data for regression (i.e, put into long format and change variable types)
+marginalization = melt(df.btw[!is.na(df.btw$assimilation.post),c("marginalization.pre","marginalization.post",
+                                                                 "CtContactNL_c","AvKeyNeedInt_c",
+                                                                 "ExternalReference")],
+                       id=c("ExternalReference","CtContactNL_c","AvKeyNeedInt_c"))
+marginalization$time = ifelse(grepl(".pre", marginalization$variable), "pre", "post")
+marginalization$variable = gsub(".pre$|.post$", "", marginalization$variable)
+marginalization$time = factor(marginalization$time)
+marginalization$time = factor(marginalization$time,levels(marginalization$time)[c(2,1)])
+marginalization$id = rep(seq(1:20), 2)
 ```
@@
 # run regresion 
-lmer_quality_contemporary <-
-  lmer(
-    quality_overall_1 ~ 
-      keymotive_fulfillemt_1_cwc + (1 + keymotive_fulfillemt_1_cwc | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  )
-lmer_attitude_contemporary <-
-  lmer(
-    thermometerDutch_1 ~ 
-      keymotive_fulfillemt_1_cwc + (1 + keymotive_fulfillemt_1_cwc | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  )
-lmer_attitude_need_quality_contemporary <-
-  lmer(
-    thermometerDutch_1 ~
-      keymotive_fulfillemt_1_cwc + quality_overall_1_cwc + (1 + keymotive_fulfillemt_1_cwc + quality_overall_1_cwc | PID),
-    data = dtWorkerSupp$workerOutWithinBetween
-  )
-
+lm.marg <- lmer(value~
+                  AvKeyNeedInt_c*time+
+                  CtContactNL_c*time+
+                  (1|id), 
+                data=marginalization)
+summary(lm.marg)
+fixef(lm.marg)
 ```
 
-For the main analyses we have four fixed effects of interest.
-(1) The effect of need fulfillment on interaction quality: _b_ = `r round(fixef(lmer_quality_contemporary)['keymotive_fulfillemt_1_cwc'], 3)`, (2) the effect of need fulfillment on outgroup attitudes: _b_ = `r round(fixef(lmer_attitude_contemporary)['keymotive_fulfillemt_1_cwc'], 3)`, (3) the effect of need fulfillment on outgroup attitudes while controlling for interaction quality: _b_ = `r round(fixef(lmer_attitude_need_quality_contemporary)['keymotive_fulfillemt_1_cwc'], 3)`, as well as (4) the effect of interaction quality on outgroup attitudes while controlling for need fulfillment: _b_ = `r round(fixef(lmer_attitude_need_quality_contemporary)['quality_overall_1_cwc'], 3)`.
+# Post-Hoc Power
 
-# Power Simulation Parameters
+Check post-hoc power for comparison.
 
 ```{r}
-#| label: simulation setup
-nsim <- 1000
-progress <- FALSE
-n_ppt <- 250
-n_measure <- 180 # 3 months with 2 measurements per day
+#| label: post hoc simulation
 
-# extrapolate data:
-sim_n_quality <- extend(lmer_quality_contemporary, along="PID", n = n_ppt)
-sim_n_attitude <- extend(lmer_attitude_contemporary, along="PID", n = n_ppt)
-sim_n_attitude_full <- extend(lmer_attitude_need_quality_contemporary, along="PID", n = n_ppt)
-
-# extrapolate data:
-sim_t_quality <- extend(lmer_quality_contemporary, within="PID", n = n_measure)
-sim_t_attitude <- extend(lmer_attitude_contemporary, within="PID", n = n_measure)
-sim_t_attitude_full <- extend(lmer_attitude_need_quality_contemporary, within="PID", n = n_measure)
+# Post-hoc power analysis for single effects (example: key need)
+post_hoc <- powerSim(lm.marg, fixed("AvKeyNeed"), nsim=1000)
+post_hoc
 ```
@@
 
-## Power of `Quality ~ NeedFulfill` for different numbers of participants
+## Power of contact effect for different numbers of participants
 
 ```{r}
-#| label: participant simulation Quality NeedFulfill
-#| warning: FALSE
-#| error: FALSE
+#| label: participant simulation contact
+
+# extrapolate data:
+sim.N <- extend(lm.marg, along="id", n=500)
 
 # Run and plot simulations
-pc_n_quality_need = powerCurve(
-  fit = sim_n_quality,
-  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
-  along = "PID",
-  progress = progress,
-  breaks = seq(1, 12, 1),
-  nsim = nsim
-)
-plot(pc_n_quality_need) +
-  title("Quality given Need Fulfillment [participant numbers]")
+plt.pwr.contact = powerCurve(fit = sim.N, 
+                             test = simr::fixed("CtContactNL_c", "t"), 
+                             along="id", 
+                             progress = FALSE,
+                             breaks = seq(10,100,10), 
+                             nsim=1000)
+plot(plt.pwr.contact) +
+  title("Outgroup Contact Count [participant numbers]")
 ```
 
-## Power of `Attitude ~ NeedFulfill` for different numbers of participants
+## Power of time effect for different numbers of participants
 
 ```{r}
-#| label: participant simulation Attitude NeedFulfill
-#| warning: FALSE
-#| error: FALSE
+#| label: participant simulation time
 
-# Run and plot simulations
-pc_n_attitude_need = powerCurve(
-  fit = sim_n_attitude,
-  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
-  along = "PID",
-  progress = progress,
-  breaks = seq(1, 45, 1),
-  nsim = nsim
-)
-plot(pc_n_attitude_need) +
-  title("Attitudes given Need Fulfillment [participant numbers]")
+plt.pwr.time = powerCurve(sim.N, simr::fixed("time"), 
+                          along="id", 
+                          progress = FALSE, 
+                          breaks = seq(10,100,10), 
+                          nsim=1000)
+plot(plt.pwr.time) +
+  title("Time [participant numbers]")
 ```
 
-## Power of `Attitude ~ NeedFulfill + Quality` for different numbers of participants
-
-we expect this to be super small.
-Keep in mind that the _b_ = `r round(fixef(lmer_attitude_need_quality_contemporary)["keymotive_fulfillemt_1_cwc"],3)`.
-So even with a large number of participants, we would not expect these effects to be meaningful.
+## Power of need fulfillment effect for different numbers of participants
 
 ```{r}
-#| label: participant simulation Attitude NeedFulfill given Quality
-#| warning: FALSE
-#| error: FALSE
+#| label: participant simulation avg need fulfillment
 
-# Run and plot simulations
-pc_n_attitude_need = powerCurve(
-  fit = sim_n_attitude_full,
-  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
-  along = "PID",
-  progress = progress,
-  breaks = seq(10, 250, 10),
-  nsim = nsim
-)
-plot(pc_n_attitude_need) +
-  title("Attitudes given Need Fulfillment (controling for Quality) [participant numbers]")
+plt.pwr.Need = powerCurve(sim.N, simr::fixed("AvKeyNeedInt_c", "t"), 
+                          along="id", 
+                          progress = FALSE, 
+                          breaks = seq(10,100,10), 
+                          nsim=1000)
+plot(plt.pwr.Need) +
+  title("Avergage Need Fulfillment [participant numbers]")
 ```
 
-## Power of `Attitude ~ Quality` given NeedFulfill for different numbers of participants
+## Power of time by contact effect for different numbers of participants
 
 ```{r}
-#| label: participant simulation Attitude Qaulity given NeedFulfill
-#| warning: FALSE
-#| error: FALSE
+#| label: participant simulation contact by time
 
-# Run and plot simulations
-pc_n_attitude_full_quality = powerCurve(
-  fit = sim_t_attitude_full,
-  test = simr::fixed("quality_overall_1_cwc", "t"),
-  along = "PID",
-  progress = progress,
-  breaks = c(seq(1, 25, 1), seq(30, 100, 10)),
-  nsim = nsim
-)
-plot(pc_n_attitude_full_quality) +
-  title("Attitudes given Quality (controlling for Need Fulfillment) [participant numbers]")
+plt.pwr.timeCont = powerCurve(sim.N, simr::fixed("time:CtContactNL_c"), 
+                             along="id", 
+                             progress = FALSE, 
+                             breaks = seq(10,500,50), 
+                             nsim=1000)
+plot(plt.pwr.timeCont) +
+  title("Time X Outgroup Contact Count [participant numbers]")
+```
+
+## Power of time by need fulfillment effect for different numbers of participants
+
+```{r}
+#| label: participant simulation need fulfillment by time
+
+plt.pwr.timeNeed = powerCurve(sim.N, simr::fixed("AvKeyNeedInt_c:time"), 
+                              along="id", 
+                              progress = FALSE, 
+                              breaks = seq(10,50,5), 
+                              nsim=1000)
+plot(plt.pwr.timeNeed) +
+  title("Time X Avergage Need Fulfillment [participant numbers]")
 ```
@@
 
-## Power of `Quality ~ NeedFulfill` for different numbers of measurements
+## Power of time effect for different numbers of measurements
 
 ```{r}
-#| label: measurement simulation Quality NeedFulfill
-#| warning: FALSE
-#| error: FALSE
+#| label: measurement simulation time
+
+# extrapolate data:
+sim.within <- extend(lm.marg, within="id", n=12)
 
 # Run and plot simulations
-pc_t_quality_need = powerCurve(
-  fit = sim_t_quality,
-  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
-  within = "PID",
-  progress = progress,
-  breaks = seq(1, 20, 1),
-  nsim = nsim
-)
-plot(pc_t_quality_need) +
-  title("Quality given Need Fulfillment [measurement numbers]")
+plt.pwr.t.time = powerCurve(sim.within, simr::fixed("time"), 
+                          within="id", 
+                          progress = FALSE, 
+                          breaks = seq(2,12,1), 
+                          nsim=1000)
+plot(plt.pwr.t.time) +
+  title("Time [measurement numbers]")
 ```
 
-## Power of `Attitude ~ NeedFulfill` for different numbers of measurements
+## Power of contact effect for different numbers of measurements
 
 ```{r}
-#| label: measurement simulation Attitude NeedFulfill
-#| warning: FALSE
-#| error: FALSE
+#| label: measurement simulation contact count
 
-# Run and plot simulations
-pc_t_attitude_need = powerCurve(
-  fit = sim_t_attitude,
-  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
-  within = "PID",
-  progress = progress,
-  breaks = seq(1, 25, 1),
-  nsim = nsim
-)
-plot(pc_t_attitude_need) +
-  title("Attitudes given Need Fulfillment [measurement numbers]")
+plt.pwr.t.contact = powerCurve(sim.within, simr::fixed("CtContactNL_c", "t"), 
+                               within="id", 
+                               progress = FALSE, 
+                               breaks = seq(2,12,1), 
+                               nsim=1000)
+plot(plt.pwr.t.contact) +
+  title("Outgroup Contact Count [measurement numbers]")
 ```
 
-## Power of `Attitude ~ NeedFulfill` given Quality for different numbers of measurements
-
-we expect this to be super small.
-Keep in mind that the _b_ = `r round(fixef(lmer_attitude_need_quality_contemporary)["keymotive_fulfillemt_1_cwc"],3)`.
-So even with a large number of measurements, we would not expect these effects to be meaningful.
+## Power of need fulfillment effect for different numbers of measurements
 
 ```{r}
-#| label: measurement simulation Attitude NeedFulfill given Quality
-#| warning: FALSE
-#| error: FALSE
+#| label: measurement simulation contact need fulfillment
 
-# Run and plot simulations
-pc_t_attitude_full_need = powerCurve(
-  fit = sim_t_attitude_full,
-  test = simr::fixed("keymotive_fulfillemt_1_cwc", "t"),
-  within = "PID",
-  progress = progress,
-  breaks = seq(10, 180, 10),
-  nsim = nsim
-)
-plot(pc_t_attitude_full_need) +
-  title("Attitudes given Need Fulfillment (controlling for Quality) [measurement numbers]")
+plt.pwr.t.Need = powerCurve(sim.within, simr::fixed("AvKeyNeedInt_c", "t"), 
+                            within="id", 
+                            progress = FALSE, 
+                            breaks = seq(2,12,1), 
+                            nsim=1000)
+plot(plt.pwr.t.Need) +
+  title("Average Need Fulfillment [measurement numbers]")
 ```
 
-## Power of `Attitude ~ Quality` given NeedFulfill for different numbers of measurements
+## Power of time by contact effect for different numbers of measurements
 
 ```{r}
-#| label: measurement simulation Attitude Qaulity given NeedFulfill
-#| warning: FALSE
-#| error: FALSE
+#| label: measurement simulation contact time by contact count
 
-# Run and plot simulations
-pc_t_attitude_full_quality = powerCurve(
-  fit = sim_t_attitude_full,
-  test = simr::fixed("quality_overall_1_cwc", "t"),
-  within = "PID",
-  progress = progress,
-  breaks = seq(1, 15, 1),
-  nsim = nsim
-)
-plot(pc_t_attitude_full_quality) +
-  title("Attitudes given Quality (controlling for Need Fulfillment) [measurement numbers]")
+plt.pwr.t.timeCont = powerCurve(sim.within, simr::fixed("time:CtContactNL_c"), 
+                          within="id", 
+                          progress = FALSE, 
+                          breaks = seq(2,12,1), 
+                          nsim=1000)
+plot(plt.pwr.t.timeCont) +
+  title("Time X Outgroup Contact Count [measurement numbers]")
+```
+
+## Power of time by need fulfillment effect for different numbers of measurements
+
+```{r}
+#| label: measurement simulation need fulfillment by time
+
+plt.pwr.t.timeNeed = powerCurve(sim.within, simr::fixed("AvKeyNeedInt_c:time"), 
+                               within="id", 
+                               progress = FALSE, 
+                               breaks = seq(2,12,1), 
+                               nsim=1000)
+plot(plt.pwr.t.timeNeed) +
+  title("Time X Average Need Fulfillment [measurement numbers]")
 ```
@@
 
-# save simulations, because this takes for freakin' ever.      
-save(list = ls(pattern = "plt."), 
+# save simulations, because this takes for freakin ever.      
+save(plt.pwr.contact,plt.pwr.Need,plt.pwr.t.contact,plt.pwr.t.Need,
+     plt.pwr.t.time,plt.pwr.t.timeCont,plt.pwr.t.timeNeed,plt.pwr.time,
+     plt.pwr.timeCont,plt.pwr.timeNeed, 
      file = "data/S1_Workers/processed/PowerSimPlots.RData")

### 2023-06-01 Supplemental Material A - Annotated Analysis/Supplemental-Material-A-Annotated-Analysis.tex
si a doc adj

@@
 % Title and header
-\title{Supplemental Information B: Annotated Analyses Scoping Review}
-\shorttitle{SI B: Annotated Analyses}
-\author{Jannis Kreienkamp, Laura F. Bringmann, Raili F. Engler, Peter de Jonge, Kai Epstude}
-%\author{[authors masked for peer review]}
+\title{Supplemental Information A: Annotated Analyses}
+\shorttitle{SI A: Annotated Analyses}
+%\author{Jannis Kreienkamp, Laura F. Bringmann, Raili F. Engler, Peter de Jonge, Kai Epstude}
+\author{[authors masked for peer review]}
 
@@
 	\vspace{0.5cm}
-	{\noindent\Large The Migration Experience: A Conceptual Framework and Systematic Scoping Review of Psychological Acculturation\par}
+	{\noindent\Large Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies\par}
 	\vspace{1.5cm}
@@
 	\vfill
-	\noindent Corresponding Author: Jannis Kreienkamp\par
-	\noindent E-mail: j.kreienkamp@rug.nl\par
-	%\noindent Corresponding Author: [masked for peer review]\par
-	%\noindent E-mail: [masked for peer review]\par
+	%\noindent Corresponding Author: Jannis Kreienkamp\par
+	%\noindent E-mail: j.kreienkamp@rug.nl\par
+	\noindent Corresponding Author: [masked for peer review]\par
+	\noindent E-mail: [masked for peer review]\par
 	\vfill
@@
 
-This supplementary information documents the methodology and results of our systematic scoping review.
+This supplementary information documents the methodology and results of all three studies.
 As part of our open supplemental materials, we share the full RMarkdown file which offers an annotated version of our all analysis steps.
@@
     \vspace{0.2cm} \centering 
-    \href{https://janniscodes.github.io/acculturation-review/Supplemental-Material-B-Annotated-Analysis}{https://acculturation-review.com/Supplemental-Material-B-Annotated-Analysis}
+    \href{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-A-Annotated-Analysis}{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-A-Annotated-Analysis}
     \vspace{0.2cm} 
@@
 
-For readers interested in the raw files, the raw RMarkdown file is available in our OSF repository \citep[see][]{Kreienkamp2021a} and can also be accessed as part of the full GitHub repository \citep[][]{Kreienkamp2021b}.
+For readers interested in the raw files, the raw RMarkdown file is available in our OSF repository \citep[see][]{KreienkampMasked2022a} and can also be accessed as part of the full GitHub repository \citep[][]{KreienkampMasked2022}.
 

### 2023-06-01 Supplemental Material B - Power Simulation/Supplemental-Material-B-Power-Simulation.tex
si links adj

--- 2023-06-01 Supplemental Material A - Annotated Analysis/Supplemental-Material-A-Annotated-Analysis.tex
@@
 % Title and header
-\title{Supplemental Information A: Annotated Analyses}
-\shorttitle{SI A: Annotated Analyses}
+\title{Supplemental Information B: Power Simulation}
+\shorttitle{SI B: Power Simulation}
 %\author{Jannis Kreienkamp, Laura F. Bringmann, Raili F. Engler, Peter de Jonge, Kai Epstude}
@@
 
-This supplementary information documents the methodology and results of all three studies.
-As part of our open supplemental materials, we share the full RMarkdown file which offers an annotated version of our all analysis steps.
-This file offers a transparent and reproducible analysis code, which includes full author commentary.
-We rendered the RMarkdown as an interactive HTML file, which we host as part of our open GitHub repository.
+This supplementary information documents the power simulations we conducted after Study 1.
+As part of our open supplemental materials, we share the full RMarkdown file which includes transparent and reproducible analysis code.
+We rendered the RMarkdown as an interactive HTML report, which we host as part of our open GitHub repository.
 We recommend the rendered version for almost all readers (full R code is also available via the rendered version).
@@
     \vspace{0.2cm} \centering 
-    \href{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-A-Annotated-Analysis}{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-A-Annotated-Analysis}
+    \href{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-B-Power-Simulation}{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-B-Power-Simulation}
     \vspace{0.2cm} 

### 2023-06-01 Supplemental Material C - Motives Topic Model/Supplemental-Material-C-Topic-Model.tex
si links adj

--- 2023-06-01 Supplemental Material A - Annotated Analysis/Supplemental-Material-A-Annotated-Analysis.tex
@@
 % Title and header
-\title{Supplemental Information A: Annotated Analyses}
-\shorttitle{SI A: Annotated Analyses}
+\title{Supplemental Information C: Motives Topic Model}
+\shorttitle{SI C: Topic Model}
 %\author{Jannis Kreienkamp, Laura F. Bringmann, Raili F. Engler, Peter de Jonge, Kai Epstude}
@@
 
-This supplementary information documents the methodology and results of all three studies.
-As part of our open supplemental materials, we share the full RMarkdown file which offers an annotated version of our all analysis steps.
+This supplementary information documents the methodology and results of the BERT topic model we conducted as part of embeddedness analyses.
+To make all supplemental materials as open as possible, we share the full Python Jupyter Notebook file which offers an annotated version of our all analysis steps.
 This file offers a transparent and reproducible analysis code, which includes full author commentary.
-We rendered the RMarkdown as an interactive HTML file, which we host as part of our open GitHub repository.
-We recommend the rendered version for almost all readers (full R code is also available via the rendered version).
+An interactive HTML render of the notebook is part of our open GitHub repository.
+We recommend the rendered version for almost all readers (full Python code is also available via the rendered version).
 
@@
     \vspace{0.2cm} \centering 
-    \href{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-A-Annotated-Analysis}{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-A-Annotated-Analysis}
+    \href{https://janniscodes.github.io/bert-migrant-need-content/Supplemental-Material-C-BERT-topic-model-outgroup}{https://janniscodes.github.io/bert-migrant-need-content/Supplemental-Material-C-BERT-topic-model-outgroup}
     \vspace{0.2cm} 
@@
 
-For readers interested in the raw files, the raw RMarkdown file is available in our OSF repository \citep[see][]{KreienkampMasked2022a} and can also be accessed as part of the full GitHub repository \citep[][]{KreienkampMasked2022}.
+For readers interested in the raw files, the raw Jupyter notebook is available in our OSF repository \citep[see][]{KreienkampMasked2022a} and can also be accessed as part of the full GitHub repository \citep[][]{KreienkampMasked2022}.
+Please note that this analysis used free text responses from our participants.
+To protect the privacy and confidentiality of our participants, we do not make the raw data openly accessible.
+If you would like to request access to the raw data, please reach out to the corresponding author.
 

### 2023-06-01 manuscript.tex

@@
 \abstract{
-One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations.
-We propose to consider the perceived fulfillment of the situationally most relevant need during everyday intergroup contact.
-We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297; total \textit{N} participants = 207).
-The novel core need fulfillment mechanism is consistently a strong predictor of perceived interaction quality as well as positive outgroup attitudes following intergroup interactions.
+One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and improves intergroup relations.
+We propose to consider the perceived fulfillment of the situationally most relevant need.
+We conducted three intensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup ($N_{measurements}$ = 10,297; $N_{participants}$ = 207).
+The core need fulfillment mechanism is consistently a strong predictor of perceived interaction quality and positive outgroup attitudes following intergroup interactions.
 The model is specific to outgroup contact, robust to various need types, and works at least as well as Allport's contact conditions.
-As one of the first studies to test intergroup contact theory using intensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
+As one of the first studies to test intergroup contact theory using intensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block for understanding and addressing positive intergroup interactions.
 
@@
 As an example, if someone seeks acceptance by their interaction partner, and this need is fulfilled during the interaction, the person should rate the interaction and the group of the interaction partner more favorably.
-To test this idea, we collected three sets of real-life data from recent immigrants, assessing their daily interactions with majority group members, tracking situational needs, interaction quality, well-being, and outgroup attitudes.
+To test this idea, we collected three sets of real-life data from recent immigrants, assessing their daily interactions with majority group members, tracking situational needs, interaction quality, and outgroup attitudes.
 

### 2023-06-01 manuscript.tex
zotero update

@@
 In this article, we focus on the role of motivation and need fulfillment to understand when and why exactly an interaction is perceived as positive.
-We propose need fulfillment in particular because needs are a fundamental aspect of the human experience that governs a significant number of emotional, cognitive, and behavioral facets \citep[][]{kreienkamp2022d, kruglanski2002}.
+We propose need fulfillment in particular because needs are a fundamental aspect of the human experience that governs a significant number of emotional, cognitive, and behavioral facets \citep[][]{Kreienkamp2022d, kruglanski2002}.
 Importantly, need fulfillment has particularly been highlighted in explaining the success of (close) relationships, psychosocial functioning, as well as reducing conflict between groups --- all of which are essential to positive intergroup interactions.
@@
 cf., theory of reasoned goal pursuit; \citealp{Ajzen2019}.
-Also see \citealp{kreienkamp2022d}).
+Also see \citealp{Kreienkamp2022d}).
 
@@
 We describe the extracted topics and themes and compare them to the need contents usually found and measured within the psychological literature.
-Full methodological details and visualizations are available in Supplemental Material B.
+Full methodological details and visualizations are available in Supplemental Material C.
 

### 2023-06-01 Tracked changes/comparison/main_rev.tex
re-render latexdiff

@@
 % add reference library file
-\addbibresource{../references.bib}
+\addbibresource{../../references.bib}
 
@@
 \abstract{
-One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations.
-We propose to consider the fulfillment of situationally relevant needs during everyday intergroup contact.
-We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297; total \textit{N} participants = 207).
-The novel need fulfillment mechanism is consistently a strong predictor of perceived interaction quality as well as positive outgroup attitudes following intergroup interactions.
-The situational needs model is robust to alternative models and works at least as well as Allport's contact conditions.
-As one of the first studies to test intergroup contact theory using extensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.
+One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and improves intergroup relations.
+We propose to consider the perceived fulfillment of the situationally most relevant need.
+We conducted three intensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup ($N_{measurements}$ = 10,297; $N_{participants}$ = 207).
+The core need fulfillment mechanism is consistently a strong predictor of perceived interaction quality and positive outgroup attitudes following intergroup interactions.
+The model is specific to outgroup contact, robust to various need types, and works at least as well as Allport's contact conditions.
+As one of the first studies to test intergroup contact theory using intensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block for understanding and addressing positive intergroup interactions.
 
@@
 describes the local population of young international medical
-professionals.
+professionals (see Supplemental Materials A for additional demographic
+information).
 

### 2023-06-01 Methods-and-Results.Rmd
tbl lab

@@
 
-The aim of this final study is to extend the previous studies by additionally testing Allport's conditions in an extensive longitudinal design and to compare the predictive powers of Allport's conditions and the core situational need fulfillment.
+The aim of this final study is to extend the previous studies by additionally testing Allport's conditions in an intensive longitudinal design and to compare the predictive powers of Allport's conditions and the core situational need fulfillment.
 For this study, we specifically recruited international medical students, because they represent a particular group of migrants who face structural requirements to integrate and interact with Dutch majority outgroup members on a daily basis.
 As part of their educational program, the migrants are required to take language courses and interact with patients as part of their medical internships and medical residency.
-The extensive longitudinal survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations.
+The intensive longitudinal survey method again offers a large body of ecologically valid data on need satisfaction in real-life intergroup contact situations.
 Data were collected from November 8\textsuperscript{th}, 2019 to January 10\textsuperscript{th}, 2020.
@@
     general = c(
-      "Upper triangle: Between-person correlations;",
-      "Lower triangle: Within-person correlations;",
+      "Upper triangle: Within-person correlations;",
+      "Lower triangle: Between-person correlations;",
       "*** p < .001, ** p < .01,  * p < .05"

### 2023-06-01 Methods-and-Results.tex
tbl lab

@@
 The aim of this final study is to extend the previous studies by
-additionally testing Allport's conditions in an extensive longitudinal
+additionally testing Allport's conditions in an intensive longitudinal
 design and to compare the predictive powers of Allport's conditions and
@@
 to take language courses and interact with patients as part of their
-medical internships and medical residency. The extensive longitudinal
+medical internships and medical residency. The intensive longitudinal
 survey method again offers a large body of ecologically valid data on

### 2023-06-01 Robustness-Methods-and-Results.Rmd
Update Robustness-Methods-and-Results.Rmd
tbl lab

--- 2023-05-30 Robustness-Methods-and-Results.Rmd
@@
 <!-- TABLES -->
+
+```{r}
+#| label: descrFullWideAppB
+#| include: false
+
+vars_full <- c(
+  "Core Need" = "CoreNeed",
+  "Competence" = "Competence",
+  "Autonomy" = "Autonomy",
+  "Relatednesss" = "Relatednesss",
+  "Outgroup Interaction" = "OutgroupInteraction",
+  "Accidental" = "InteractionAccidental",
+  "Quality" = "Quality",
+  "Attitudes NL" = "Attitude"
+)
+
+dt_exp_all <- dt_exp_all %>% 
+  mutate(
+    OutgroupInteraction = (OutgroupInteraction-1.5)
+  )
+
+s1_MlCor_full <- 
+  MlCorMat(
+    data = dt_exp_all %>% filter(study == 1),
+    id = "PID",
+    selection = setdiff(as.character(vars_full), c("InteractionAccidental", "Quality")),
+    labels = setdiff(names(vars_full), c("Accidental", "Quality"))
+  ) 
+s2_MlCor_full <- 
+  MlCorMat(
+    data = dt_exp_all %>% filter(study == 2),
+    id = "PID",
+    selection = as.character(vars_full),
+    labels = names(vars_full)
+  ) 
+s3_MlCor_full <- 
+  MlCorMat(
+    data = dt_exp_all %>% filter(study == 3),
+    id = "PID",
+    selection = as.character(vars_full),
+    labels = names(vars_full)
+  ) 
+all_MlCor_full <- 
+  MlCorMat(
+    data = dt_exp_all,
+    id = "PID",
+    selection = as.character(vars_full),
+    labels = names(vars_full)
+  )
+
+rbind(
+  s1_MlCor_full %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable") %>%
+    add_column(Accidental = "",
+               .before = "Attitudes NL") %>%
+    add_column(Quality = "",
+               .before = "Attitudes NL"),
+  s2_MlCor_full %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable"),
+  s3_MlCor_full %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable"),
+  all_MlCor_full %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      caption = "Full Sample: Correlation Table and Descriptive Statistics",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1)))  %>%
+  kable_classic() %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Correlations" = ncol(s3_MlCor_full),
+      "Descriptives" = nrow(s3_MlCor_full) - ncol(s3_MlCor_full)
+    )
+  ) %>%
+  pack_rows("Study 1", 1, ncol(s1_MlCor_full)) %>%
+  pack_rows("Study 2", ncol(s1_MlCor_full) + 1,
+            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full))) %>%
+  pack_rows("Study 3", sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full)) + 1,  
+            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full))) %>%
+  pack_rows("Across Studies", sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full)) + 1,  
+            sum(ncol(s1_MlCor_full), ncol(s2_MlCor_full), ncol(s3_MlCor_full), ncol(all_MlCor_full))) %>% # fix table position
+  footnote(
+    general = c(
+      "Upper triangle: Within-person correlations;",
+      "Lower triangle: Between-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05",
+      "Interaction Intent and Interaction Quality were only measured for outgroup interactions in Study 1."
+    )
+  ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/descrFullWideAppB.tex")
+
+```
+
+```{r}
+#| label: descrOutWideAppB
+#| include: false
+
+vars_out <- c(
+  "Core Need" = "CoreNeed",
+  "Competence" = "Competence",
+  "Autonomy" = "Autonomy",
+  "Relatednesss" = "Relatednesss",
+  "Practical Need" = "practical_need_dum",
+  "Psychological Need" = "psychological_need_dum",
+  "Accidental" = "InteractionAccidental",
+  "Quality" = "Quality",
+  "Attitudes NL" = "Attitude"
+)
+
+s1_MlCor_out <- 
+  MlCorMat(
+    data = dt_goal_directedness %>% filter(study == 1, OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = as.character(vars_out),
+    labels = names(vars_out)
+  ) 
+s2_MlCor_out <- 
+  MlCorMat(
+    data = dt_goal_directedness %>% filter(study == 2, OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = as.character(vars_out),
+    labels = names(vars_out)
+  ) 
+s3_MlCor_out <- 
+  MlCorMat(
+    data = dt_goal_directedness %>% filter(study == 3, OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = as.character(vars_out),
+    labels = names(vars_out)
+  ) 
+all_MlCor_out <- 
+  MlCorMat(
+    data = dt_goal_directedness %>% filter(OutgroupInteraction == "Yes"),
+    id = "PID",
+    selection = as.character(vars_out),
+    labels = names(vars_out)
+  )
+
+rbind(
+  s1_MlCor_out %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable"),
+  s2_MlCor_out %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable"),
+  s3_MlCor_out %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable"),
+  all_MlCor_out %>%
+    t %>%
+    as.data.frame %>%
+    rownames_to_column(., "Variable")
+) %>%
+  kbl(.,
+      format = "latex",
+      caption = "Outgroup Interaction Sample: Correlation Table and Descriptive Statistics",
+      booktabs = TRUE,
+      align = c("l", rep("c", ncol(.) - 1)))  %>%
+  kable_classic() %>%
+  add_header_above(
+    .,
+    c(
+      "",
+      "Correlations" = ncol(s3_MlCor_out),
+      "Descriptives" = nrow(s3_MlCor_out) - ncol(s3_MlCor_out)
+    )
+  ) %>%
+  pack_rows("Study 1", 1, ncol(s1_MlCor_out)) %>%
+  pack_rows("Study 2", ncol(s1_MlCor_out) + 1,
+            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out))) %>%
+  pack_rows("Study 3", sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out)) + 1,  
+            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out))) %>%
+  pack_rows("Across Studies", sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out)) + 1,  
+            sum(ncol(s1_MlCor_out), ncol(s2_MlCor_out), ncol(s3_MlCor_out), ncol(all_MlCor_out))) %>% # fix table position
+  footnote(
+    general = c(
+      "Upper triangle: Within-person correlations;",
+      "Lower triangle: Between-person correlations;",
+      "*** p < .001, ** p < .01,  * p < .05"
+    )
+  ) %>%
+  kable_styling(latex_options = "scale_down") %>%
+  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
+  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
+  save_kable("Tables/descrOutWideAppB.tex")
+
+```
 

### 2023-06-01 manuscript.tex
tbl lab

@@
 \noindent\textbf{Public significance statement}: In this paper, we provide evidence that the fulfillment of situational needs during real-life intergroup contacts meaningfully predicts perceived interaction quality and positive outgroup attitudes.
-Methodologically, this offers testament to the emerging practice of capturing real-life interactions using extensive longitudinal data.
+Methodologically, this offers testament to the emerging practice of capturing real-life interactions using intensive longitudinal data.
 Theoretically, our results give weight to motivational fulfillment as a flexible and effective mechanism for understanding positive intergroup contact.
@@
 \section{The Present Research}
-Using three independent sets of extensive longitudinal data (Studies 1–3), the aim of this paper is essentially threefold.
+Using three independent sets of intensive longitudinal data (Studies 1–3), the aim of this paper is essentially threefold.
 We (1) seek to test the basic ideas of the contact theory within real-world experience sampling data.
@@
 
-Firstly, for the general contact hypothesis test, our study is among the first to test the fundamental tenets of intergroup contact and Allport's conditions in real-life extensive longitudinal data.
-Translating the contact hypothesis into extensive longitudinal data is not a trivial task, as past research traditions have used two fundamentally different approaches.
+Firstly, for the general contact hypothesis test, our study is among the first to test the fundamental tenets of intergroup contact and Allport's conditions in real-life intensive longitudinal data.
+Translating the contact hypothesis into intensive longitudinal data is not a trivial task, as past research traditions have used two fundamentally different approaches.
 While lab studies have tended to focus on the effect of a single positive interaction, cross-section studies have primarily investigated the frequency of positive interactions more generally.
-Extensive longitudinal data allows us to investigate both.
+Intensive longitudinal data allows us to investigate both.
 We can test whether having a specific type of interaction vs.
@@
 \begin{enumerate}[leftmargin=1.5\parindent]
-    \item[H1:] Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for more favorable outgroup attitudes within and across extensive longitudinal data.
+    \item[H1:] Based on the most general understanding of the contact hypothesis, an increase in frequency and quality of contact should jointly account for more favorable outgroup attitudes within and across intensive longitudinal data.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=1.5\parindent]
-    \item[H2:] Based on the literature about Allport’s optimal contact conditions, intergroup interactions that are higher in equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
+    \item[H2:] Based on the literature about Allport’s optimal contact conditions, intergroup interactions that are higher in equal status, common goals, collaboration, and structural support should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the intensive longitudinal data.
 \end{enumerate}
@@
 \begin{enumerate}[leftmargin=1.5\parindent]
-    \item[H3:] Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the extensive longitudinal data.
+    \item[H3:] Based on our proposal, intergroup interactions with higher situational core need fulfillment should predict more favorable outgroup attitudes due to more positive interaction quality perceptions within the intensive longitudinal data.
 We also expect situational need fulfillments to work at least as well as Allport's optimal contact conditions in predicting outgroup attitudes.
@@
 
-A second non-trivial aspect of translating the intergroup contact hypothesis into extensive real-world data was the choice of the outcome variable.
+A second non-trivial aspect of translating the intergroup contact hypothesis into intensive real-world data was the choice of the outcome variable.
 For our main analyses, we chose outgroup attitudes --- the positive or negative evaluation of the other group.
@@
 % aims re-iterated
-The main aim of this project was to test the basic tenets of the intergroup contact hypothesis and Allport's optimal conditions in real-life extensive longitudinal data as well as to test whether the fulfillment of situational needs meaningfully predicts positive interaction perceptions and outgroup attitudes.
+The main aim of this project was to test the basic tenets of the intergroup contact hypothesis and Allport's optimal conditions in real-life intensive longitudinal data as well as to test whether the fulfillment of situational needs meaningfully predicts positive interaction perceptions and outgroup attitudes.
 
@@
 % Need fulfillment in intergroup contact [consistent predictor, through quality, slightly better than Allport and SDT]
-Finally, when looking at the results regarding the importance of situational key need fulfillment, we find that in all three extensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions, more positive outgroup attitudes, as well as higher well-being.
+Finally, when looking at the results regarding the importance of situational key need fulfillment, we find that in all three intensive longitudinal data sets, the fulfillment of core needs during intergroup contacts predicts higher interaction quality perceptions, more positive outgroup attitudes, as well as higher well-being.
 We also find that in all three studies, need fulfillment and perceived interaction quality likely shared a large part of the variance they explained in outgroup attitudes (when considering partial regression coefficients in a joint model).
@@
 A second limitation lies in our methodology.
-While extensive longitudinal data is close to real-life events, this method comes at the expense of longer and more robust scales.
-Long and repetitive scales are often not feasible in extensive longitudinal methods because of the increased burden to the participants.
+While intensive longitudinal data is close to real-life events, this method comes at the expense of longer and more robust scales.
+Long and repetitive scales are often not feasible in intensive longitudinal methods because of the increased burden to the participants.
 To circumvent this shortcoming, we have ensured that the measures we used were, whenever possible, based on past validations.
-However, the circumstance remains that extensive longitudinal data often does not allow the same scrutiny of measurement reliability as single–shot cross-sectional data sets.
+However, the circumstance remains that intensive longitudinal data often does not allow the same scrutiny of measurement reliability as single–shot cross-sectional data sets.
 An additional methodological question lies in the unexplored potential of the longitudinal aspects of our data.
@@
 Despite these limitations, we can nonetheless draw a number of implications for other researchers and practitioners --- ranging from the benefits of longitudinal data to theoretical implications.
-A first implication concerns the feasibility and usefulness of extensive longitudinal data for intergroup contact research and the broader field of social psychology.
-While setting up an extensive longitudinal study is not easy, we believe the efforts to be similar to a sizable cross-sectional data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with over 3,000 intergroup interactions captured and over 10,000 data points in total).
+A first implication concerns the feasibility and usefulness of intensive longitudinal data for intergroup contact research and the broader field of social psychology.
+While setting up an intensive longitudinal study is not easy, we believe the efforts to be similar to a sizable cross-sectional data collection (i.e., for a longitudinal or a high-quality cross-sectional data set with over 3,000 intergroup interactions captured and over 10,000 data points in total).
 Intensive longitudinal data, thus, opens up the possibility to explore research questions that focus on real-life phenomena outside the lab or focus on phenomena that depend on changes and influences over time.
 In the context of intergroup contact research, we are among the first to answer calls to test intergroup contact mechanisms using extended real-life data \citep[e.g.,][]{Pettigrew2011, MacInnis2015}.
-In doing so, we not only collected an unprecedented amount of real-life data, but our consideration of extensive longitudinal data may present new inconsistencies in how participants perceive and cognitively aggregate their past interactions with other groups — which may suggest large-scale recall biases or conflations of within and between participant effects in conventional cross-section studies.
+In doing so, we not only collected an unprecedented amount of real-life data, but our consideration of intensive longitudinal data may present new inconsistencies in how participants perceive and cognitively aggregate their past interactions with other groups — which may suggest large-scale recall biases or conflations of within and between participant effects in conventional cross-section studies.
 
@@
 % Conclusion paragraph
-In sum, we used extensive longitudinal methodologies to capture real-life interactions of recent migrants with the majority outgroup.
+In sum, we used intensive longitudinal methodologies to capture real-life interactions of recent migrants with the majority outgroup.
 Our three studies showcase the feasibility and utility of such data to test intergroup contact theory.
@@
 
-\subsection{1. Contact hypothesis in extensive longitudinal data.} 
+\subsection{1. Contact hypothesis in intensive longitudinal data.} 
 Within the individual studies, we begin by testing the most basic assumption of the intergroup contact hypothesis that outgroup attitudes should be more positive after outgroup interactions but not after non-outgroup interactions.
@@
     \begin{hyp}[H\ref{hyp:contactHyp}] \label{hyp:contactHyp}
-        Based on the most general understanding of the contact hypothesis, positive intergroup contacts should be associated with more favorable outgroup attitudes across extensive longitudinal data.
+        Based on the most general understanding of the contact hypothesis, positive intergroup contacts should be associated with more favorable outgroup attitudes across intensive longitudinal data.
     \end{hyp}
@@
 
-\subsection{3. Allport's conditions in extensive longitudinal data.}
+\subsection{3. Allport's conditions in intensive longitudinal data.}
 Within the third study, we formally measure all of Allport's optimal contact conditions.

### 2023-06-01 Robustness-Methods-and-Results.Rmd
mlcor tbl lab fix

@@
   "Relatednesss" = "Relatednesss",
-  "Outgroup Interaction" = "OutgroupInteraction",
+  #"Outgroup Interaction" = "OutgroupInteraction",
   "Accidental" = "InteractionAccidental",
@@
   "Relatednesss" = "Relatednesss",
-  "Practical Need" = "practical_need_dum",
-  "Psychological Need" = "psychological_need_dum",
+  # "Practical Need" = "practical_need_dum",
+  # "Psychological Need" = "psychological_need_dum",
   "Accidental" = "InteractionAccidental",
@@
   MlCorMat(
-    data = dt_goal_directedness %>% filter(study == 1, OutgroupInteraction == "Yes"),
+    data = dt_exp_all %>% filter(study == 1, OutgroupInteractionLab == "Yes", PID != 21), # PP 21 has inflated zero for Accidental
     id = "PID",
@@
   MlCorMat(
-    data = dt_goal_directedness %>% filter(study == 2, OutgroupInteraction == "Yes"),
+    data = dt_exp_all %>% filter(study == 2, OutgroupInteractionLab == "Yes"),
     id = "PID",
@@
   MlCorMat(
-    data = dt_goal_directedness %>% filter(study == 3, OutgroupInteraction == "Yes"),
+    data = dt_exp_all %>% filter(study == 3, OutgroupInteractionLab == "Yes"),
     id = "PID",
@@
   MlCorMat(
-    data = dt_goal_directedness %>% filter(OutgroupInteraction == "Yes"),
+    data = dt_exp_all %>% filter(OutgroupInteractionLab == "Yes"),
     id = "PID",

### 2023-06-01 scripts/functions/MlCorMat.R

@@ -124,7 +124,7 @@ MlCorMat <-
     
     rMlComb <- matrix("", nrow = length(selection), ncol = length(selection))
     rMlComb[upper.tri(rMlComb, diag = FALSE)] <- rMlWitBtw[upper.tri(rMlWitBtw, diag = FALSE)]
-    rMlComb[lower.tri(rMlComb, diag = FALSE)] <- rMlWitStar[upper.tri(rMlWitStar, diag = FALSE)]
+    rMlComb[lower.tri(rMlComb, diag = FALSE)] <- rMlWitStar[lower.tri(rMlWitStar, diag = FALSE)]
     rownames(rMlComb) <- labels
     colnames(rMlComb) <- paste(labels, "", sep="")
     

### 2023-06-09 Supplemental-Material-B-Power-Simulation.Rmd
typo

@@
 ---
-title: "Supplemental Information C: Power Simulations"
+title: "Supplemental Information B: Power Simulations"
 subtitle: "Supplemental Material for 'Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies'"

### 2023-08-17 PathModels.Rmd
phrasing adjusted

@@
   data.frame(
-    lab_x_direct = "Core Need\\\\Fulfillment",
+    lab_x_direct = "Situational Need\\\\Fulfillment",
     lab_y_direct   = "Outgroup\\\\Attitudes",
-    lab_x   = "Core Need\\\\Fulfillment",
+    lab_x   = "Situational Need\\\\Fulfillment",
     lab_m   = "Interaction\\\\Quality",

### 2023-08-17 scripts/functions/metaLmer.R

@@ -19,8 +19,8 @@ strLabFix <- function(varIn, ...) {
       "Contact X Quality",
       "Non-Outgroup Interaction",
       "Outgroup Interaction",
-      "Core Need Fulfillment",
-      "Core Need Fulfillment",
+      "Situational Need Fulfillment",
+      "Outgroup Need Fulfillment",
       "Interaction Quality",
       "",
       " X "

### 2023-08-17 PathModels.Rmd
path model adj

--- 2023-05-30 PathModels.Rmd
@@
   data.frame(
-    lab_x_direct = "Core Need\\\\Fulfillment",
+    lab_x_direct = "Sit. Need\\\\Fulfillment",
     lab_y_direct   = "Outgroup\\\\Attitudes",
-    lab_x   = "Core Need\\\\Fulfillment",
+    lab_x   = "Sit. Need\\\\Fulfillment",
     lab_m   = "Interaction\\\\Quality",

### 2023-09-11 Tracked changes/comparison/main.tex
Revert "Delete Tracked changes directory"
This reverts commit 89b30dec4bd46fa6c8fd596818e02c9d886bdb8c.

@@
 \textit{p} = 0.004, \textit{95\%CI}{[}0.06, 0.29{]}) and also predicted
-higher perceived contact quality (random intercept model; \textit{b} =
-0.42, \textit{t}(365) = 8.07, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.32, 0.52{]}). Moreover, when we consider the
+higher perceived contact quality (random intercept model; \textit{b} = 0.37,
+\textit{t}(365) = 7.73, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.28, 0.47{]}). Moreover, when we consider the
 influences of core need fulfillment and contact quality on outgroup
 attitudes jointly, we find that virtually all variance is explained by
-perceived contact quality (random slopes model; \textit{b} = 0.23,
-\textit{t}(364) = 4.22, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.33{]}) and only little unique variance is
-still explained by core need fulfillment (\textit{b} = 0.04,
-\textit{t}(364) = 0.64, \textit{p} = 0.523, \textit{95\%CI}{[}-0.08,
-0.15{]}, also see \fgrref[-A]{fig:MainPaths}). We thus find support for
+perceived contact quality (random slopes model; \textit{b} = 0.24, 
+\textit{t}(364) = 4.33, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.13, 0.35{]}) and only little unique variance
+is still explained by core need fulfillment (\textit{b} = 0.05,
+\textit{t}(364) = 0.94, \textit{p} = 0.348, \textit{95\%CI}{[}-0.05,
+0.14{]}, also see \fgrref[-A]{fig:MainPaths}). We thus find support for
 our hypotheses and can conclude that in this data set the fulfillment of
@@
 \textit{95\%CI}{[}0.07, 0.19{]}) and also predicted higher perceived
-interaction quality (random slopes model; \textit{b} = 0.40,
-\textit{t}(826) = 6.46, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.28, 0.52{]}). Additionally, if we consider the
+interaction quality (random slopes model; \textit{b} = 0.29,
+\textit{t}(826) = 5.43, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.19, 0.40{]}). Additionally, if we consider the
 influences of core need fulfillment and interaction quality on outgroup
 attitudes jointly, we find that virtually all variance is explained by
-perceived interaction quality (random slopes model; \textit{b} = 0.17,
-\textit{t}(825) = 5.56, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.11, 0.23{]}) and only little unique variance is
-still explained by core need fulfillment (\textit{b} = 0.03,
-\textit{t}(825) = 1.47, \textit{p} = 0.141, \textit{95\%CI}{[}-0.01,
-0.07{]}; also see \fgrref[-B]{fig:MainPaths} and
+perceived interaction quality (random slopes model; \textit{b} = 0.16,
+\textit{t}(825) = 5.93, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.11, 0.21{]}) and only little unique variance is
+still explained by core need fulfillment (\textit{b} = 0.06,
+\textit{t}(825) = 2.47, \textit{p} = 0.014, \textit{95\%CI}{[}0.01,
+0.11{]}; also see \fgrref[-B]{fig:MainPaths} and
 \tblref{tab:intergroupNeedsTblLong} for full results). These results are
@@
 substantially stronger predictor (random slopes model; \textit{b} =
-0.17, \textit{t}(1,600) = 6.25, \textit{p} \textless{} .001,
-\textit{95\%CI}{[}0.12, 0.23{]}) and the unique variance explained by
+0.16, \textit{t}(1,600) = 6.56, \textit{p} \textless{} .001,
+\textit{95\%CI}{[}0.11, 0.21{]}) and the unique variance explained by
 Allport's Conditions was less than half of its original effect size
-(\textit{b} = 0.09, \textit{t}(1,600) = 2.89, \textit{p} = 0.004,
-\textit{95\%CI}{[}0.03, 0.15{]}; also see
+(\textit{b} = 0.11, \textit{t}(1,600) = 3.54, \textit{p} \textless{}
+.001, \textit{95\%CI}{[}0.05, 0.18{]}; also see
 \tblref{tab:intergroupNeedsTblLong}). These results indicate that in

### 2023-09-11 Tracked changes/comparison/main_rev.tex
Revert "Delete Tracked changes directory"
This reverts commit 89b30dec4bd46fa6c8fd596818e02c9d886bdb8c.

@@
 % add reference library file
-\addbibresource{../../references.bib}
+\addbibresource{references.bib}
 

### 2023-09-11 Backup/OldVersions.tex
Revert "Delete Backup directory"
This reverts commit 30e00d7e66e51d65dee1c66eb4e627a1a284178d.

\section{Introduction}

% Problem: NEEDS REFORMULATION (in line with aims of present study. should include main aims [see email 2021-11-25])
In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group \citep[e.g.,][]{Hewstone1996, Pettigrew1998}. A key condition for these contact benefits, has been that the interaction is indeed perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact \citep[e.g.,][]{MacInnis2015}. It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact \citep[Allport's Optimal Contact conditions,][]{Allport1954b, Pettigrew1969}. And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met. However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met \citep[][]{Pettigrew2006}\footnote{It should be noted here that following Allport's original conditions, several additional conditions of optimal contact were proposed \citep[for a critical discussion see][]{Pettigrew1986}. Similarly, since the early 21\textsuperscript{st} century many psychological processes during intergroup contact were examined \citep[e.g. see,][]{Paolini2021}. Among others, researchers have for example explored different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}. However, all these advances share the underlying criticism that they are not geared towards understanding when and why an interaction is perceived as positive.}. It, thus, remains unclear when and why exactly an interaction is perceived as positive and what factors (beyond Allport's conditions) explain positive contact effects.

% Problem: focus on everyday life interactions: 
As one of the most researched and practically implemented theories of social psychology, intergroup contact has received a vast amount of empirical attention \citep[][]{Dovidio2017}. Several meta-analytic reviews found that positive intergroup contact reduces prejudice and increases positive attitudes in experimental and cross-sectional studies \citep[][]{Tropp2005, Pettigrew2006, Davies2011}. Later meta-analyses have shown that intergroup contact interventions outside the lab show similarly positive effects \citep[][]{Beelmann2014, Lemmer2015}\footnote{Additional reviews have shown similar effects for online contact \citep[][]{White2020}, as well as during several more indirect forms of contact \citep[][]{Miles2014, Zhou2019, Harwood2021}}. \hl{However, an increasing number of reviews and perspective papers has pointed out that in order to truly understand intergroup contacts we need more fine grained data of how intergroup contacts unfolded in people's everyday lives} \citep[e.g.,][]{MacInnis2015}.

This criticism of understudying the real-life mechanisms of intergroup contact, can be separated into two interconnected issues. Firstly, the focus on lab experiments, interventions, and cross-sectional survey designs are not aligned with the experiences of people in everyday life and the theories proposed around these natural interactions. Secondly, this methodological disconnect has led to an underdeveloped understanding of when and why an interaction is positive in everyday life.

We propose to test a motivational mechanism using a daily dairy study design.

Method:

so far the only studies that have focused on interaction specific mechanisms have been artificial lab studies or structured interventions.

Whenever natural interactions were assessed they were assessed in cross-sectional recall studies.

Method that brings these together is extensive longitudinal: Allows us to assess event-specific mechanism while being close to the natural event.

---------

However, an increasing number of reviews and perspective papers has pointed out these broader findings might not generalize to the more common everyday interactions.

that these broader findings might not be useful if we want to understand how such intergroup contact evolves/works/functions/unfold during natural interactions in everyday life.

However, an increasing number of reviews and perspective papers has pointed out that in order to truly understand intergroup contacts ...

However, an increasing number of reviews and perspective papers has pointed out that in order to move forward ...

However, virtually no research

---------

... we need to understand/investigate how intergroup contacts unfolded in people's everyday lives

... we need to understand/investigate what actually makes for a positive intergroup contact in real life.

... we need more fine grained data of how intergroup contacts unfolded in people's everyday lives \citep[e.g.,][]{MacInnis2015}.

... we need to gain a deeper understanding of the psychological mechanisms .

---------

\section{Intergroup Contact Mechanisms}
\faQuestionCircle\ \textit{Not sure whether we need this section.}

\faExclamationCircle\ \textit{This section has become way too complex (i.e., too many arguments to get to our own proposed work). I think we ultimately need to introduce the concept of interaction quality and that we don't necessarily know why interactions are perceived as positive, therefore we propose that we can look towards the motivational literature for this. The difficulties started for me when I tried to give credit to past theoretical work (which I thought we need to acknowledge in some way).}

% Intergroup contact = Robust and strong effect (from meta-analyses) → much theoretical interest
As one of the most researched and practically implemented theories of social psychology, intergroup contact has received a vast amount of empirical, and theoretical attention \citep[][]{Dovidio2017}. Several meta-analytic reviews have found moderately sized positive effects of intergroup contact \citep[][]{Tropp2005, Pettigrew2006, Davies2011} and later meta-analyses have additionally shown that intergroup contact is also effective outside the lab \citep[][]{Beelmann2014, Lemmer2015}, during online contact \citep[][]{White2020}, as well as during several more indirect forms of contact \citep[][]{Miles2014, Zhou2019, Harwood2021}. With such a persistent and meaningful effect, researchers have long proposed theoretical models to understand these intergroup contact effects.

% what makes a 'positive contact' has received much theoretical interest. (1) conditions of positive contact, then (2) contact quality. But why is it perceived as positive? 
Interestingly, one concept that has arguably remained at the center of theoretical debates throughout the decades has been the role of 'positive' contact. In his now famous chapter on 'the effects of contact', Gordon Allport (\citeyear{Allport1954b}) set out to summarize under what circumstances an interaction between groups tends to be positive, leading to favourable attitudes and reduced prejudice. In the years that followed, several additional conditions were proposed under which a positive intergroup contact would occur \citep[for a critical review see][]{Pettigrew1986}. As a counter-movement to this rather restrictive approach, with the beginning of the 21\textsuperscript{st} century attention had shifted towards investigating the psychological mechanisms of intergroup contact \citep[e.g. see,][]{Paolini2021}. With this shift in focus, the idea of 'positive contact' has seemingly seen a renaissance, where the adjective 'positive' is now not merely an evaluation of the outcome, but rather a feature of the interaction itself. As such, recent work has focused on the role of 'perceived interaction quality' \citep[e.g.,][]{Brown2007, Voci2003} or 'interaction valence' \citep[e.g.,][]{Tropp2016, Barlow2012}, to show that only if an interaction is perceived as positive will it lead to more favourable intergroup relations. And inversely interactions that are perceived as negative have the strong propensity to harm outgroup attitudes. However, relatively little research has investigated why interactions are perceived as positive.

% many moderators and mediators but none of these necessarily leads to higher interaction quality. Solution: look at need fulfillment (motivational literature)
Thus although a sizeable number of moderators and mediators of intergroup contact have been proposed, their effects might be undermined if they do not result in a 'positive' contact. As an example, important moderators and mediators that have been identified are different forms of social categorizations \citep[][]{Pettigrew1998}, the salience of social categories \citep[][]{Brown2005}, intimacy \citep[e.g.,][]{Marinucci2021} and attachment \citep[e.g.,][]{Tropp2021}, threat and intergroup anxiety \citep[e.g.,][]{Stephan2008, Paolini2004}, and to a lesser extent knowledge about the other group \citep[][]{Pettigrew2008c}. However, there is a discernible disconnect between these mechanisms and perceptions that an interaction is positive. That is to say that, just because someone learns something new about the other group, or reduces their threat perceptions does not mean that such an interaction is perceived as positive. Or inversely, an interaction can, for example, be very intimate but perceived as negative. If that were the case, there is a reasonable chance that such an interaction might not translate into improved outgroup attitudes \citep[e.g.,][]{Barlow2012}. We propose that we may look to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.

ALTERNATIVE: One potential remedy might come from looking to the literature on motivation and psychological needs to understand when and why exactly an interaction is perceived as positive.
